### 2013-03-18 figurefactory/files/limno_bgape_cl.tex
First few pages of motivation

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (1478,0)(1478,-0.181818181818182)(1478,-0.363636363636364)(1478,-0.545454545454545)(1478,-0.727272727272727)(1478,-0.909090909090909)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454545)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454545)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454545)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478.00016587919,-9.09090909090909)(1478.00033175469,-9.27272727272727)(1478.00033175469,-9.45454545454546)(1478.00016587919,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454545)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454545)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454545)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.909090909090909)(0,-0.727272727272727)(0,-0.545454545454545)(0,-0.363636363636364)(0,-0.181818181818182)(0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1448.14141414141,-9.07482483753433)(1449.38005040762,-9.09090909090909)(1458.72266748613,-9.27272727272727)(1462.16461608434,-9.45454545454546)(1457.93739588908,-9.63636363636364)(1448.14141414141,-9.76880948045942)(1443.79101312806,-9.81818181818182)(1433.21212121212,-9.89042536657361)(1418.28282828283,-9.97220402070884)(1411.64380927072,-10)(1403.35353535354,-10.0268854789336)(1388.42424242424,-10.0624512420213)(1373.49494949495,-10.0858912269465)(1358.56565656566,-10.0987182864105)(1343.63636363636,-10.102962992112)(1328.70707070707,-10.1010832499639)(1313.77777777778,-10.0957594734832)(1298.84848484848,-10.0895855113828)(1283.91919191919,-10.0847193351369)(1268.9898989899,-10.0825928939416)(1254.06060606061,-10.083784643917)(1239.13131313131,-10.0881421355553)(1224.20202020202,-10.0951010924332)(1209.27272727273,-10.1039452569402)(1194.34343434343,-10.1139499357554)(1179.41414141414,-10.1244504589076)(1164.48484848485,-10.1348650752363)(1149.55555555556,-10.1446919253603)(1134.62626262626,-10.1534885135226)(1119.69696969697,-10.1608315698405)(1104.76767676768,-10.1662517457766)(1089.83838383838,-10.1691748423721)(1074.90909090909,-10.1689575399048)(1059.9797979798,-10.1649715724152)(1045.05050505051,-10.1566770588623)(1030.12121212121,-10.1436963503898)(1015.19191919192,-10.125889781726)(1000.26262626263,-10.1034124247913)(985.333333333333,-10.0767151822671)(970.40404040404,-10.0464552735906)(955.474747474747,-10.013307823769)(949.978893163733,-10)(940.545454545455,-9.97807181148041)(925.616161616162,-9.94087063608248)(910.686868686869,-9.90105170089348)(895.757575757576,-9.8577226257769)(883.509186627693,-9.81818181818182)(880.828282828283,-9.80934461405926)(865.89898989899,-9.75303239531643)(850.969696969697,-9.68820509581558)(840.658582570405,-9.63636363636364)(836.040404040404,-9.60972698978828)(821.111111111111,-9.51036769366592)(813.765122243986,-9.45454545454546)(806.181818181818,-9.37884030418043)(796.52670901727,-9.27272727272727)(791.252525252525,-9.18172850331714)(786.1120165418,-9.09090909090909)(781.350004048785,-8.90909090909091)(781.700292860412,-8.72727272727273)(787.055375547823,-8.54545454545455)(791.252525252525,-8.46953330263129)(797.389084244081,-8.36363636363636)(806.181818181818,-8.25527238039726)(812.491262287979,-8.18181818181818)(821.111111111111,-8.09778589767859)(831.615728238001,-8)(836.040404040404,-7.96248037720495)(850.969696969697,-7.83881685491404)(853.498612390076,-7.81818181818182)(865.89898989899,-7.72191737491956)(877.441030726608,-7.63636363636364)(880.828282828283,-7.61233969300808)(895.757575757576,-7.51269570109658)(905.474751568828,-7.45454545454546)(910.686868686869,-7.42514082302524)(925.616161616162,-7.35260757307406)(940.545454545455,-7.29483688348728)(948.20983898438,-7.27272727272727)(955.474747474747,-7.25281917827936)(970.40404040404,-7.22671168195057)(985.333333333333,-7.21599459418017)(1000.26262626263,-7.22086934225301)(1015.19191919192,-7.24145872752697)(1028.19889936542,-7.27272727272727)(1030.12121212121,-7.27753437771899)(1045.05050505051,-7.3274095902308)(1059.9797979798,-7.38713601418184)(1074.90909090909,-7.45220989134266)(1075.44825719334,-7.45454545454546)(1089.83838383838,-7.51534267826917)(1104.76767676768,-7.57160221512044)(1119.69696969697,-7.61795889862764)(1127.48665225104,-7.63636363636364)(1134.62626262626,-7.65266400945172)(1149.55555555556,-7.67569822949993)(1164.48484848485,-7.68847110284722)(1179.41414141414,-7.69265816226828)(1194.34343434343,-7.6901830729894)(1209.27272727273,-7.68316533122948)(1224.20202020202,-7.67397725334571)(1239.13131313131,-7.66538965087568)(1254.06060606061,-7.66076041767317)(1268.9898989899,-7.66414041509026)(1283.91919191919,-7.68014015763703)(1298.84848484848,-7.71349387267142)(1313.77777777778,-7.76842040428974)(1323.34244512792,-7.81818181818182)(1328.70707070707,-7.85007561262625)(1343.63636363636,-7.9609183391006)(1348.14561466569,-8)(1358.56565656566,-8.0977740197848)(1366.90866754043,-8.18181818181818)(1373.49494949495,-8.25076188175244)(1384.2176058536,-8.36363636363636)(1388.42424242424,-8.4089083491506)(1401.52980262361,-8.54545454545455)(1403.35353535354,-8.56527958618061)(1418.28282828283,-8.72039779999265)(1418.96751701876,-8.72727272727273)(1433.21212121212,-8.88456727515451)(1435.49658592742,-8.90909090909091)(1448.14141414141,-9.07482483753433)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (432.949494949495,-7.62537808110239)(447.878787878788,-7.49515945642039)(453.634273405795,-7.45454545454546)(462.808080808081,-7.40824862633082)(477.737373737374,-7.3473805919878)(492.666666666667,-7.3028531014644)(507.59595959596,-7.27314545133157)(507.971324441396,-7.27272727272727)(522.525252525253,-7.25757880472974)(537.454545454546,-7.25458343000404)(552.383838383838,-7.26514500602056)(556.76546517783,-7.27272727272727)(567.313131313131,-7.29243391259954)(582.242424242424,-7.34173271265313)(597.171717171717,-7.42061591326051)(601.732815751869,-7.45454545454546)(612.10101010101,-7.5550535180392)(618.323625701474,-7.63636363636364)(627.030303030303,-7.81386668638062)(627.208049689042,-7.81818181818182)(631.340965192909,-8)(632.004804095685,-8.18181818181818)(629.389256087845,-8.36363636363636)(627.030303030303,-8.43471171011093)(623.324643902992,-8.54545454545455)(613.424218243758,-8.72727272727273)(612.10101010101,-8.74457614261215)(598.308154116587,-8.90909090909091)(597.171717171717,-8.91954081438586)(582.242424242424,-9.03637501436889)(573.133372914227,-9.09090909090909)(567.313131313131,-9.11967949971697)(552.383838383838,-9.16910271704596)(537.454545454546,-9.1926915906799)(522.525252525253,-9.19017711734558)(507.59595959596,-9.16118788005291)(492.666666666667,-9.10554360347104)(489.876759750011,-9.09090909090909)(477.737373737374,-9.00950811684864)(465.842909877035,-8.90909090909091)(462.808080808081,-8.87505513198468)(450.744269474239,-8.72727272727273)(447.878787878788,-8.67986623616029)(439.49329629746,-8.54545454545455)(432.949494949495,-8.40359706858181)(430.814624854265,-8.36363636363636)(424.148612809654,-8.18181818181818)(420.777096197368,-8)(422.257083613328,-7.81818181818182)(431.799598096469,-7.63636363636364)(432.949494949495,-7.62537808110239)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (119.434343434343,-7.92037924231854)(122.79885412663,-7.81818181818182)(134.363636363636,-7.73778282591567)(149.292929292929,-7.69947037438622)(164.222222222222,-7.69597240685678)(179.151515151515,-7.7116912954455)(194.080808080808,-7.73959272188856)(209.010101010101,-7.77631163252306)(223.22348855859,-7.81818181818182)(223.939393939394,-7.82088268510329)(238.868686868687,-7.88589235730763)(253.79797979798,-7.96215394608578)(260.195186932805,-8)(268.727272727273,-8.0909207600127)(275.609446204187,-8.18181818181818)(278.558915117606,-8.36363636363636)(273.150031331953,-8.54545454545455)(268.727272727273,-8.60336562419625)(258.062723933781,-8.72727272727273)(253.79797979798,-8.75528927680203)(238.868686868687,-8.82877256167601)(223.939393939394,-8.87148838869149)(209.010101010101,-8.88240467359964)(194.080808080808,-8.86254345832509)(179.151515151515,-8.81420352665458)(164.222222222222,-8.7402069702458)(162.255837112136,-8.72727272727273)(149.292929292929,-8.61230482699614)(142.731707572687,-8.54545454545455)(134.363636363636,-8.42739270293778)(130.062418671086,-8.36363636363636)(121.748906826838,-8.18181818181818)(119.434343434343,-8.06796056232384)(117.963012369102,-8)(119.434343434343,-7.92037924231854)};

\end{axis}
\end{tikzpicture}%

### 2013-03-18 figurefactory/files/limno_bgape_sc.tex
First few pages of motivation

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{mycolor1}{rgb}{0,0,0.5625}
\definecolor{mycolor2}{rgb}{0,0,0.625}
\definecolor{mycolor3}{rgb}{0,0,0.6875}
\definecolor{mycolor4}{rgb}{0,0,0.8125}
\definecolor{mycolor5}{rgb}{0,0,0.875}
\definecolor{mycolor6}{rgb}{0,0,0.9375}
\definecolor{mycolor7}{rgb}{0,0.0625,1}
\definecolor{mycolor8}{rgb}{0,0.125,1}
\definecolor{mycolor9}{rgb}{0,0.1875,1}
\definecolor{mycolor10}{rgb}{0,0.25,1}
\definecolor{mycolor11}{rgb}{0,0.3125,1}
\definecolor{mycolor12}{rgb}{0,0.375,1}
\definecolor{mycolor13}{rgb}{0,0.4375,1}
\definecolor{mycolor14}{rgb}{0,0.5,1}
\definecolor{mycolor15}{rgb}{0,0.5625,1}
\definecolor{mycolor16}{rgb}{0,0.625,1}
\definecolor{mycolor17}{rgb}{0,0.6875,1}
\definecolor{mycolor18}{rgb}{0,0.75,1}
\definecolor{mycolor19}{rgb}{0,0.8125,1}
\definecolor{mycolor20}{rgb}{0,0.875,1}
\definecolor{mycolor21}{rgb}{0,0.9375,1}
\definecolor{mycolor22}{rgb}{0,1,1}
\definecolor{mycolor23}{rgb}{0.0625,1,0.9375}
\definecolor{mycolor24}{rgb}{0.125,1,0.875}
\definecolor{mycolor25}{rgb}{0.1875,1,0.8125}
\definecolor{mycolor26}{rgb}{0.25,1,0.75}
\definecolor{mycolor27}{rgb}{0.3125,1,0.6875}
\definecolor{mycolor28}{rgb}{0.375,1,0.625}
\definecolor{mycolor29}{rgb}{0.4375,1,0.5625}
\definecolor{mycolor30}{rgb}{0.5,1,0.5}
\definecolor{mycolor31}{rgb}{0.5625,1,0.4375}
\definecolor{mycolor32}{rgb}{0.625,1,0.375}
\definecolor{mycolor33}{rgb}{0.6875,1,0.3125}
\definecolor{mycolor34}{rgb}{0.75,1,0.25}
\definecolor{mycolor35}{rgb}{0.8125,1,0.1875}
\definecolor{mycolor36}{rgb}{0.875,1,0.125}
\definecolor{mycolor37}{rgb}{0.9375,1,0.0625}
\definecolor{mycolor38}{rgb}{1,1,0}
\definecolor{mycolor39}{rgb}{1,0.9375,0}
\definecolor{mycolor40}{rgb}{1,0.875,0}
\definecolor{mycolor41}{rgb}{1,0.8125,0}
\definecolor{mycolor42}{rgb}{1,0.75,0}
\definecolor{mycolor43}{rgb}{1,0.6875,0}
\definecolor{mycolor44}{rgb}{1,0.625,0}
\definecolor{mycolor45}{rgb}{1,0.5625,0}
\definecolor{mycolor46}{rgb}{1,0.4375,0}
\definecolor{mycolor47}{rgb}{1,0.375,0}
\definecolor{mycolor48}{rgb}{1,0.3125,0}
\definecolor{mycolor49}{rgb}{1,0.25,0}
\definecolor{mycolor50}{rgb}{1,0.1875,0}
\definecolor{mycolor51}{rgb}{1,0.125,0}
\definecolor{mycolor52}{rgb}{1,0.0625,0}
\definecolor{mycolor53}{rgb}{0.9375,0,0}
\definecolor{mycolor54}{rgb}{0.875,0,0}
\definecolor{mycolor55}{rgb}{0.8125,0,0}
\definecolor{mycolor56}{rgb}{0.6875,0,0}
\definecolor{mycolor57}{rgb}{0.625,0,0}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
unbounded coords=jump,
colormap/jet,
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.04, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
colorbar/width=0.15cm,
tickwidth=0.1cm,
point meta min=0.9,
point meta max=9.3
]

\addplot[scatter,only marks,mark size=0.6pt,scatter src=explicit,scatter/use mapped color={mark=*,draw=mapped color,fill=mapped color}] plot coordinates{ (0,-0.831) [9.000000e-01] (0.396123095452957,-0.832) [9.000000e-01] (16.8850657170843,-2.228) [9.000000e-01] (19.386309378027,-2.485) [1] (20.7170231970803,-2.774) [1] (21.6989675078734,-3.031) [1.200000e+00] (22.8071472777201,-3.289) [1.400000e+00] (24.5610830029506,-3.559) [1.500000e+00] (25.9984308826544,-3.773) [1.700000e+00] (27.8988551242371,-4.005) [1.800000e+00] (29.1617886372451,-4.262) [2.200000e+00] (62.5565899293934,-9.656) [4.900000e+00] (62.5565899293934,-9.727) [4.800000e+00] (70.9331967712539,-9.716) [4.700000e+00] (70.5118107778974,-9.674) [4.600000e+00] (71.7410292630623,-9.816) [4.500000e+00] (72.8642052039513,-9.938) [4.400000e+00] (75.0082362859188,-9.97) [4.300000e+00] (76.7726194267189,-10.033) [4.200000e+00] (78.6602249298857,-10.233) [4.100000e+00] (80.0953847487801,-10.526) [4] (81.4237947228505,-10.853) [3.800000e+00] (82.4094012394071,-11.137) [3.800000e+00] (90.4064215094236,-12.599) [3.200000e+00] (91.7791118891167,-12.761) [3.200000e+00] (93.2690607870255,-12.927) [3.300000e+00] (94.9258643776602,-13.131) [3.200000e+00] (96.4233119768856,-13.315) [3.100000e+00] (97.7794091531292,-13.539) [3] (99.2566050421831,-13.721) [2.900000e+00] (100.834528136853,-13.918) [2.800000e+00] (102.038059375172,-14.076) [2.700000e+00] (103.564851467609,-14.21) [2.700000e+00] (105.10292010624,-14.316) [2.500000e+00] (106.352328039151,-14.45) [2.500000e+00] (107.570853984965,-14.606) [2.400000e+00] (109.162235182079,-14.748) [2.400000e+00] (110.512369431851,-14.892) [2.300000e+00] (111.678350262332,-15.037) [2.300000e+00] (113.235254720706,-15.144) [2.200000e+00] (114.500486265143,-15.249) [2.200000e+00] (115.691203492305,-15.382) [2.100000e+00] (115.815129572001,-15.528) [2.100000e+00] (117.676456857818,-15.642) [2] (119.477680213669,-15.649) [2] (121.68110463208,-15.667) [1.900000e+00] (123.336430499725,-15.756) [1.900000e+00] (124.837654253971,-15.889) [1.900000e+00] (125.874974432477,-16.079) [1.900000e+00] (127.464940685869,-16.178) [1.800000e+00] (129.19548862963,-16.275) [1.800000e+00] (130.857541771519,-16.416) [1.800000e+00] (132.21363502171,-16.627) [1.800000e+00] (133.550247559459,-16.799) [1.900000e+00] (134.959009363721,-16.962) [2] (136.520336217567,-17.12) [1.800000e+00] (137.872711335487,-17.243) [1.800000e+00] (139.076945489566,-17.415) [1.700000e+00] (140.399268842806,-17.544) [1.800000e+00] (141.977956830779,-17.703) [1.800000e+00] (143.325077182371,-17.802) [1.700000e+00] (144.660151796424,-17.868) [1.800000e+00] (146.571133738,-17.888) [1.800000e+00] (148.269322831534,-17.76) [1.800000e+00] (149.626182665483,-17.551) [1.800000e+00] (151.662688380933,-17.391) [1.800000e+00] (152.718137136586,-17.26) [1.900000e+00] (153.837406694506,-17.099) [1.800000e+00] (155.125065343297,-16.946) [1.800000e+00] (157.211165026066,-16.724) [1.700000e+00] (158.777742720471,-16.503) [1.700000e+00] (160.189513695575,-16.363) [1.900000e+00] (161.502800912108,-16.229) [1.900000e+00] (162.89502879595,-16.13) [1.800000e+00] (164.148212512045,-15.928) [1.800000e+00] (165.084159331749,-15.722) [1.900000e+00] (166.140376448098,-15.548) [1.900000e+00] (168.073974836101,-15.419) [1.900000e+00] (171.903368566451,-15.398) [1.700000e+00] (173.569902526982,-17.024) [1.300000e+00] (175.53259191065,-16.566) [1.400000e+00] (177.935861325938,-16.19) [1.500000e+00] (179.811407222947,-15.874) [1.600000e+00] (181.880781436237,-15.569) [1.600000e+00] (183.237574077208,-15.215) [1.700000e+00] (184.995797300345,-14.884) [1.800000e+00] (186.783495133997,-14.578) [1.900000e+00] (187.952482126714,-14.274) [2.100000e+00] (189.258334913618,-13.899) [2.200000e+00] (190.738599459577,-13.554) [2.200000e+00] (192.463118747332,-13.211) [2.200000e+00] (194.003421319868,-12.947) [2.300000e+00] (195.57383981248,-12.748) [2.300000e+00] (196.983300606632,-12.597) [2.300000e+00] (198.481506135811,-12.432) [2.300000e+00] (200.168477251637,-12.264) [2.300000e+00] (201.114162264182,-12.13) [2.400000e+00] (202.394383846677,-12.051) [2.400000e+00] (203.75431396949,-11.953) [2.400000e+00] (205.330754700682,-11.83) [2.400000e+00] (206.892138374923,-11.74) [2.500000e+00] (207.741581757429,-11.685) [2.500000e+00] (209.102985706053,-11.61) [2.600000e+00] (211.135704464084,-11.467) [2.700000e+00] (212.557210594941,-11.291) [2.700000e+00] (214.108788883075,-11.101) [2.800000e+00] (215.157375520155,-11.056) [2.900000e+00] (216.15643461017,-10.923) [3.100000e+00] (217.950858027716,-10.784) [3.300000e+00] (219.060511686867,-10.537) [3.300000e+00] (220.557241700015,-10.4) [3.500000e+00] (221.391560315826,-10.222) [3.800000e+00] (222.696512075325,-10.14) [4.100000e+00] (224.639715159097,-9.899) [4.500000e+00] (226.372497123793,-9.749) [4.800000e+00] (227.744407109268,-9.586) [5.500000e+00] (228.880265172045,-9.464) [5.900000e+00] (230.235578800823,-9.304) [6.500000e+00] (231.748069617228,-9.108) [6.800000e+00] (233.558252978639,-8.875) [7] (235.063246470297,-8.73) [7.100000e+00] (236.020206310127,-8.554) [7.100000e+00] (237.432741377094,-8.429) [7.200000e+00] (238.858024551416,-8.262) [7.100000e+00] (240.511864989205,-8.107) [6.800000e+00] (242.258165228102,-7.934) [6.600000e+00] (243.650385776785,-7.836) [6.400000e+00] (245.109501714279,-7.66) [6.200000e+00] (246.41003125226,-7.468) [6] (247.91047415366,-7.229) [5.800000e+00] (249.408674496533,-7.087) [5.500000e+00] (250.905335539608,-6.901) [5.300000e+00] (252.429101641981,-6.732) [5.100000e+00] (254.261837265445,-6.508) [4.900000e+00] (256.077338317457,-6.347) [4.700000e+00] (257.562018696169,-6.134) [4.500000e+00] (258.874594918112,-6.023) [4.300000e+00] (260.562968311294,-5.811) [4.100000e+00] (262.146131130528,-5.613) [3.900000e+00] (263.724810180359,-5.365) [3.800000e+00] (265.261324877772,-5.226) [3.500000e+00] (266.695641668371,-4.999) [3.400000e+00] (268.071397382789,-4.805) [3.200000e+00] (269.50725304322,-4.552) [3] (270.879226899651,-4.345) [2.800000e+00] (272.529283359421,-4.089) [2.700000e+00] (274.421414868838,-3.899) [2.500000e+00] (276.528515938972,-3.657) [2.400000e+00] (278.224450469698,-3.467) [2.300000e+00] (279.852654000009,-3.213) [2.200000e+00] (281.380900404519,-2.967) [2.100000e+00] (282.910687914953,-2.692) [2.100000e+00] (284.340519646842,-2.457) [2] (285.643290082154,-2.181) [1.900000e+00] (286.883581618075,-1.945) [1.800000e+00] (288.129196146879,-1.684) [1.800000e+00] (289.668018103901,-1.46) [1.700000e+00] (291.718798937234,-1.22) [1.700000e+00] (293.480855222687,-0.988) [1.600000e+00] (295.087271814318,-0.83) [1.600000e+00] (296.946972721786,-0.798) [1.500000e+00] (298.652642321077,-0.83) [1.500000e+00] (300.10874040534,-0.909) [1.400000e+00] (301.305531104619,-0.978) [1.400000e+00] (302.585043928458,-1.136) [1.400000e+00] (303.913378375254,-1.404) [1.500000e+00] (305.470971595757,-1.672) [1.500000e+00] (306.92854127026,-1.939) [1.500000e+00] (308.210996786529,-2.209) [1.500000e+00] (309.714513617752,-2.477) [1.500000e+00] (310.96089607739,-2.74) [1.500000e+00] (312.301209440349,-3.024) [1.500000e+00] (313.842201832416,-3.269) [1.600000e+00] (314.94653232983,-3.551) [1.800000e+00] (316.189901233967,-3.763) [1.900000e+00] (317.843665738257,-4.031) [2] (319.262080173156,-4.255) [2.100000e+00] (320.718176108592,-4.52) [2.200000e+00] (321.911954198816,-4.732) [2.500000e+00] (323.378556571735,-5.026) [2.800000e+00] (324.913593203712,-5.256) [3.100000e+00] (326.006645836546,-5.507) [3.500000e+00] (327.553729582038,-5.694) [4] (328.869245116202,-5.916) [4.500000e+00] (330.669681375372,-6.094) [4.900000e+00] (331.861986586285,-6.351) [5.200000e+00] (333.832351781839,-6.545) [5.700000e+00] (335.219313382338,-6.757) [6.100000e+00] (336.676178566863,-6.917) [6.500000e+00] (337.793956904831,-7.134) [6.800000e+00] (339.0560970724,-7.311) [7] (340.45279368349,-7.528) [7.100000e+00] (341.845707518994,-7.672) [7.100000e+00] (343.47089012962,-7.851) [7.200000e+00] (345.114845293166,-7.963) [7.200000e+00] (346.776171422735,-8.152) [7.100000e+00] (348.35036028571,-8.301) [7.100000e+00] (349.459871648953,-8.528) [7.100000e+00] (350.616033398694,-8.703) [7] (351.497758437856,-8.86) [6.900000e+00] (353.034334026721,-8.989) [6.700000e+00] (354.586669071716,-9.074) [6.600000e+00] (356.179630516457,-9.155) [6.400000e+00] (357.438757186451,-9.271) [6.200000e+00] (358.529425133756,-9.39) [6.100000e+00] (359.478813004749,-9.532) [5.800000e+00] (361.113870203384,-9.675) [5.700000e+00] (362.460972905081,-9.782) [5.500000e+00] (363.784751087263,-9.879) [5.300000e+00] (365.233348925488,-9.969) [5.200000e+00] (366.592499170642,-10.101) [5] (368.268111476218,-10.237) [4.900000e+00] (369.818974559425,-10.419) [4.700000e+00] (371.642733276156,-10.685) [4.600000e+00] (372.877833114694,-11.001) [4.400000e+00] (373.847532867175,-11.19) [4.300000e+00] (375.693074138188,-11.412) [4.100000e+00] (377.630304671522,-11.463) [4] (379.09697275044,-11.528) [3.800000e+00] (380.372556803692,-11.64) [3.700000e+00] (381.856454982116,-11.776) [3.500000e+00] (383.005119923821,-11.919) [3.300000e+00] (384.857455777906,-12.088) [3.200000e+00] (386.078266002381,-12.239) [3.200000e+00] (387.260475696,-12.362) [3.200000e+00] (389.108956134072,-12.409) [3.100000e+00] (390.953653796453,-12.432) [2.900000e+00] (392.525527147113,-12.5) [2.800000e+00] (393.960604190631,-12.689) [2.800000e+00] (395.779878336545,-12.859) [2.800000e+00] (397.904264438766,-13.094) [2.700000e+00] (399.214520508063,-13.314) [2.600000e+00] (400.393232341897,-13.571) [2.500000e+00] (401.647874011237,-13.774) [2.500000e+00] (402.939357986557,-13.984) [2.400000e+00] (404.591714086049,-14.176) [2.400000e+00] (406.2718054043,-14.32) [2.400000e+00] (407.533939067413,-14.519) [2.400000e+00] (408.688554066189,-14.637) [2.400000e+00] (410.549851784699,-14.788) [2.300000e+00] (412.090132781494,-14.83) [2.200000e+00] (413.592872714638,-15.015) [2.200000e+00] (414.827198547541,-15.209) [2.200000e+00] (416.789364884208,-15.394) [2.200000e+00] (418.043378717052,-15.55) [2.100000e+00] (419.387464912905,-15.93) [2] (420.472873767022,-16.192) [2] (421.724427922257,-16.478) [2] (423.503552062762,-16.562) [1.900000e+00] (424.828169183932,-16.685) [1.900000e+00] (426.354087009002,-16.739) [1.900000e+00] (427.785377809461,-16.807) [1.700000e+00] (429.073076401396,-16.926) [1.700000e+00] (430.106652771831,-17.068) [1.600000e+00] (431.401219934598,-17.158) [1.600000e+00] (433.205431349417,-17.248) [1.600000e+00] (434.578866109566,-17.353) [1.500000e+00] (436.204110128149,-17.507) [1.500000e+00] (437.46701398703,-17.658) [1.400000e+00] (438.906569154545,-17.852) [1.400000e+00] (440.101808404137,-17.969) [1.500000e+00] (441.330806400502,-18.097) [1.500000e+00] (443.360487222009,-18.182) [1.400000e+00] (444.585774223355,-18.25) [1.400000e+00] (445.447251768488,-18.17) [1.400000e+00] (447.12362865369,-17.912) [1.300000e+00] (448.757908036852,-17.697) [1.400000e+00] (450.639589132766,-17.439) [1.400000e+00] (451.816205698007,-17.237) [1.300000e+00] (452.9941430965,-17.065) [1.400000e+00] (454.324782973168,-16.989) [1.400000e+00] (455.645539375936,-16.878) [1.400000e+00] (456.434723634116,-16.729) [1.500000e+00] (456.720912797513,-16.525) [1.400000e+00] (457.811644272833,-16.327) [1.600000e+00] (459.498525417922,-16.033) [1.600000e+00] (461.469577023641,-15.747) [1.600000e+00] (463.191832955192,-15.465) [1.600000e+00] (464.677192693975,-15.222) [1.600000e+00] (466.37086931058,-14.943) [1.600000e+00] (468.175076857479,-14.739) [1.600000e+00] (470.070274909105,-14.536) [1.500000e+00] (471.191898749391,-14.413) [1.600000e+00] (472.485619237177,-14.316) [1.800000e+00] (473.894352188464,-14.297) [1.800000e+00] (475.2843152821,-14.247) [1.800000e+00] (476.772760414979,-14.174) [1.900000e+00] (477.794282650237,-14.062) [1.900000e+00] (479.272147329054,-13.973) [2] (481.272548904457,-13.839) [2] (483.080465268393,-13.733) [2.100000e+00] (484.381601955964,-13.665) [2.200000e+00] (485.775969040986,-13.563) [2.300000e+00] (487.077181092446,-13.401) [2.300000e+00] (489.279028768061,-13.204) [2.400000e+00] (490.763687600189,-13.02) [2.500000e+00] (491.869402232016,-12.837) [2.500000e+00] (493.070662947826,-12.64) [2.500000e+00] (494.53802035846,-12.458) [2.700000e+00] (496.492539449225,-12.275) [2.800000e+00] (497.893005483946,-12.122) [2.800000e+00] (499.123616082126,-11.968) [2.800000e+00] (500.490249812515,-11.835) [2.900000e+00] (501.848619204718,-11.682) [2.900000e+00] (503.312963977375,-11.566) [3] (504.493136941834,-11.409) [3.100000e+00] (505.878540989002,-11.274) [3.300000e+00] (507.491032689709,-11.118) [3.400000e+00] (508.862918091176,-10.935) [3.500000e+00] (511.147488495327,-10.796) [3.800000e+00] (512.948604172493,-10.614) [4] (514.328755259145,-10.438) [4.200000e+00] (516.083989741004,-10.3) [4.400000e+00] (517.537827675343,-10.172) [4.800000e+00] (519.392317458851,-10.061) [5.200000e+00] (520.815259503113,-9.944) [5.600000e+00] (522.379553032858,-9.792) [6] (523.810063323146,-9.61) [6.400000e+00] (525.637516703518,-9.414) [6.800000e+00] (527.023691376214,-9.321) [7.300000e+00] (528.15651341941,-9.149) [7.400000e+00] (529.172082217439,-8.984) [7.700000e+00] (530.85293204054,-8.836) [7.800000e+00] (532.357130095883,-8.71) [8] (533.626051093809,-8.573) [8.200000e+00] (534.898679503406,-8.452) [8.300000e+00] (536.107429634038,-8.264) [8.200000e+00] (537.799631396382,-8.075) [8.100000e+00] (540.384899305627,-7.876) [8] (541.339910154951,-7.715) [7.700000e+00] (542.511119680717,-7.661) [7.300000e+00] (543.880839780806,-7.633) [7.100000e+00] (545.200893674116,-7.409) [6.800000e+00] (546.475838257982,-7.245) [6.600000e+00] (547.608736611513,-7.032) [6.300000e+00] (549.143057840604,-6.86) [6] (550.521736593632,-6.726) [5.800000e+00] (552.116151548903,-6.522) [5.500000e+00] (553.811287547934,-6.305) [5.400000e+00] (555.298181574116,-6.105) [5.300000e+00] (556.74073906526,-5.926) [5.100000e+00] (557.826209757301,-5.717) [4.800000e+00] (559.27401937813,-5.489) [4.600000e+00] (559.306150016763,-5.28) [4.500000e+00] (554.03698251721,-5.057) [4.200000e+00] (550.895504015747,-5.033) [4.100000e+00] (557.717371908828,-5.156) [3.900000e+00] (561.272322234517,-5.281) [3.800000e+00] (563.747903483793,-5.203) [3.600000e+00] (564.998287509892,-4.978) [3.500000e+00] (566.837092085808,-4.748) [3.300000e+00] (568.695439782222,-4.514) [3.200000e+00] (569.834361750772,-4.302) [3.100000e+00] (571.248417125722,-4.023) [2.800000e+00] (572.80529153421,-3.801) [2.600000e+00] (574.549320164143,-3.571) [2.500000e+00] (576.188068158497,-3.327) [2.400000e+00] (578.026021500922,-3.09) [2.200000e+00] (579.600891674788,-2.832) [2.200000e+00] (581.740317445334,-2.59) [2.100000e+00] (583.303910184611,-2.314) [1.900000e+00] (584.752411942598,-2.064) [1.800000e+00] (586.321176517195,-1.813) [1.800000e+00] (588.424530119685,-1.551) [1.700000e+00] (590.44747590734,-1.304) [1.700000e+00] (592.019332554757,-1.041) [1.700000e+00] (593.690365127009,-0.8) [1.600000e+00] (595.153075403151,-0.696) [1.600000e+00] (596.676036840976,-0.739) [1.500000e+00] (598.709327188053,-0.795) [1.400000e+00] (601.300749078113,-2.544) [1.300000e+00] (602.105991355403,-2.71) [1.400000e+00] (602.931707421628,-2.856) [1.400000e+00] (604.097821108785,-3.021) [1.400000e+00] (605.605105678937,-3.159) [1.500000e+00] (606.909319136346,-3.331) [1.600000e+00] (607.979110811731,-3.493) [1.600000e+00] (609.188014567845,-3.646) [1.800000e+00] (610.690046607554,-3.809) [1.900000e+00] (612.411437982475,-4.003) [2] (614.375596230447,-4.17) [2.100000e+00] (616.187897873787,-4.376) [2.400000e+00] (617.94682586952,-4.576) [2.400000e+00] (618.749668182145,-4.779) [2.600000e+00] (620.273480998677,-4.971) [2.900000e+00] (621.701663395038,-5.196) [3.300000e+00] (623.128379160792,-5.442) [3.700000e+00] (624.704017811359,-5.668) [4.100000e+00] (625.890205708112,-5.859) [4.500000e+00] (627.184768119437,-6.025) [4.900000e+00] (628.376288411573,-6.173) [5.400000e+00] (629.95416652508,-6.417) [5.900000e+00] (631.361339658358,-6.624) [6.100000e+00] (632.467039445835,-6.799) [6.500000e+00] (633.877225704956,-6.956) [6.700000e+00] (634.377821438691,-7.18) [6.900000e+00] (635.886569630999,-7.328) [7] (637.87413280914,-7.457) [7.100000e+00] (639.081327361336,-7.556) [7.200000e+00] (640.297640667434,-7.738) [7.300000e+00] (641.772475802155,-7.909) [7.300000e+00] (643.080473498388,-8.053) [7.500000e+00] (644.590686114394,-8.199) [7.400000e+00] (646.167016013546,-8.389) [7.300000e+00] (647.243442658802,-8.559) [7.300000e+00] (648.343970668986,-8.723) [7.100000e+00] (649.684333638446,-8.831) [7] (651.167431792837,-8.938) [6.700000e+00] (652.901641882458,-9.081) [6.600000e+00] (654.338248404371,-9.243) [6.300000e+00] (655.474846404656,-9.424) [6.100000e+00] (657.13915376985,-9.627) [6] (658.702740091544,-9.773) [5.900000e+00] (660.580459086924,-9.973) [5.700000e+00] (662.026020678454,-10.183) [5.400000e+00] (663.454278583737,-10.426) [5.200000e+00] (664.918608256291,-10.574) [5.100000e+00] (666.458173966181,-10.646) [4.900000e+00] (668.330721643186,-10.788) [4.600000e+00] (669.558311123957,-10.94) [4.400000e+00] (671.25188905276,-11.118) [4.200000e+00] (672.389951047011,-11.246) [4] (674.707480115744,-11.353) [3.900000e+00] (675.728374949706,-11.489) [3.700000e+00] (677.108510448648,-11.599) [3.600000e+00] (679.2440557551,-11.705) [3.500000e+00] (681.03990082214,-11.873) [3.300000e+00] (682.434326451909,-12.131) [3.200000e+00] (683.467879725312,-12.398) [3] (684.649502814835,-12.614) [2.900000e+00] (685.759066706,-12.651) [2.900000e+00] (687.378953344612,-12.667) [2.900000e+00] (689.062024894014,-12.646) [2.700000e+00] (690.203181255074,-12.758) [2.600000e+00] (691.420265703543,-12.874) [2.600000e+00] (692.68013752651,-13.063) [2.400000e+00] (694.521863875757,-13.218) [2.300000e+00] (695.88632611914,-13.466) [2.400000e+00] (697.552177888773,-13.663) [2.300000e+00] (698.993949654389,-13.954) [2.200000e+00] (699.936593147191,-14.207) [2.100000e+00] (701.709024055777,-14.439) [2.100000e+00] (703.513131741756,-14.529) [2.200000e+00] (704.763963356725,-14.689) [2.100000e+00] (706.036575719774,-14.831) [2.100000e+00] (707.20080998498,-15.004) [2.100000e+00] (708.929071683957,-15.065) [2] (710.481543569578,-15.128) [1.900000e+00] (712.215914938905,-15.152) [1.900000e+00] (713.715535694763,-15.381) [1.900000e+00] (714.842317245742,-15.592) [2] (716.293816454677,-15.756) [1.900000e+00] (717.707006268394,-15.856) [1.900000e+00] (718.838180573656,-15.98) [2] (719.965567172751,-16.117) [1.900000e+00] (721.823820049284,-16.151) [1.900000e+00] (723.697136289684,-16.202) [1.900000e+00] (725.150266789064,-16.221) [1.900000e+00] (726.538141129001,-16.297) [1.900000e+00] (727.790604063571,-16.461) [1.800000e+00] (729.143013490269,-16.715) [1.800000e+00] (730.396856512014,-16.988) [1.800000e+00] (731.709323504927,-17.227) [1.700000e+00] (733.194736747184,-17.449) [1.600000e+00] (734.552313078727,-17.626) [1.500000e+00] (736.01284813964,-17.818) [1.400000e+00] (737.570231800915,-18) [1.400000e+00] (739.057883158724,-18.103) [1.300000e+00] (740.58160404782,-18.17) [1.300000e+00] (741.891057055759,-18.245) [1.400000e+00] (743.346254819787,-18.143) [1.400000e+00] (743.715041281529,-17.892) [1.500000e+00] (743.372501862502,-17.724) [1.400000e+00] (745.983919066963,-17.728) [1.400000e+00] (747.118878011834,-17.766) [1.400000e+00] (748.204335323046,-17.714) [1.500000e+00] (749.921836001063,-17.627) [1.600000e+00] (751.85808119249,-17.399) [1.600000e+00] (753.443353552948,-17.167) [1.500000e+00] (755.020276379409,-16.882) [1.500000e+00] (756.722107327212,-16.622) [1.600000e+00] (758.217849965371,-16.404) [1.700000e+00] (759.600472320502,-16.237) [1.700000e+00] (760.890382266074,-16.048) [1.800000e+00] (762.251915034731,-15.834) [1.900000e+00] (763.556890150241,-15.676) [1.900000e+00] (764.824330880797,-15.518) [1.800000e+00] (766.085660622746,-15.363) [1.700000e+00] (767.303515412042,-15.243) [1.800000e+00] (768.707746775803,-15.12) [1.800000e+00] (770.035275901486,-14.985) [1.900000e+00] (771.45749898875,-14.849) [1.800000e+00] (772.960126365527,-14.688) [1.900000e+00] (774.436410707631,-14.525) [2] (775.964604761534,-14.353) [2] (777.462755076765,-14.189) [1.900000e+00] (778.832378667063,-14.032) [1.900000e+00] (780.093793662851,-13.878) [1.800000e+00] (781.446113566901,-13.752) [1.900000e+00] (782.834503461074,-13.586) [1.800000e+00] (784.288319505995,-13.497) [1.800000e+00] (785.599318236394,-13.405) [1.900000e+00] (786.924607986195,-13.283) [2.100000e+00] (788.248433341269,-13.18) [2.200000e+00] (789.524138038227,-13.07) [2.400000e+00] (790.91709024823,-12.952) [2.500000e+00] (792.288176484898,-12.877) [2.500000e+00] (793.366829955702,-12.776) [2.600000e+00] (794.642446761998,-12.629) [2.800000e+00] (796.212734421098,-12.47) [3] (797.200481206599,-12.267) [3.100000e+00] (798.647581243616,-12.004) [3.200000e+00] (800.583991269068,-11.717) [3.500000e+00] (802.90744059022,-11.483) [3.700000e+00] (804.338700017224,-11.325) [3.800000e+00] (806.056278527151,-11.18) [4.200000e+00] (807.985111391972,-11.039) [4.300000e+00] (809.40285440908,-10.905) [4.600000e+00] (810.612357085689,-10.72) [4.800000e+00] (811.859479372142,-10.588) [5] (813.389994187876,-10.469) [5.300000e+00] (814.731034966986,-10.353) [5.900000e+00] (816.271277168218,-10.164) [6.400000e+00] (817.730428419094,-10.007) [6.800000e+00] (819.284273172684,-9.883) [7] (820.654668793693,-9.801) [7.300000e+00] (822.52108780309,-9.643) [7.500000e+00] (824.253041726866,-9.508) [7.800000e+00] (824.840833412025,-9.375) [8.100000e+00] (825.621798949205,-9.168) [8.300000e+00] (826.630547947332,-8.977) [8.400000e+00] (831.387618680305,-8.688) [8.100000e+00] (832.009593889613,-8.736) [8] (833.13129049664,-8.678) [7.700000e+00] (834.55738448232,-8.491) [7.300000e+00] (836.29381328966,-8.28) [7.100000e+00] (837.783693679666,-8.09) [6.800000e+00] (838.642402030511,-7.945) [6.500000e+00] (839.946772788831,-7.77) [6.200000e+00] (841.338348668701,-7.611) [6] (842.878677529188,-7.483) [5.800000e+00] (844.115207810356,-7.353) [5.600000e+00] (845.405796651774,-7.164) [5.400000e+00] (847.348138962983,-6.937) [5.300000e+00] (849.439057126407,-6.71) [5.100000e+00] (851.269312551894,-6.508) [4.800000e+00] (852.633501755337,-6.361) [4.500000e+00] (853.946733414982,-6.169) [4.400000e+00] (855.284935676456,-5.981) [4.200000e+00] (856.693903191344,-5.759) [4] (857.946273251773,-5.559) [3.800000e+00] (859.17385121571,-5.328) [3.600000e+00] (860.447224319571,-5.155) [3.400000e+00] (861.974037716558,-4.943) [3.300000e+00] (863.154179017472,-4.784) [3.100000e+00] (864.559686758026,-4.588) [2.900000e+00] (865.969848287846,-4.383) [2.900000e+00] (867.286867711739,-4.149) [2.800000e+00] (868.260319609999,-3.964) [2.600000e+00] (869.90360330309,-3.753) [2.500000e+00] (871.737734871017,-3.54) [2.400000e+00] (873.290023959297,-3.36) [2.400000e+00] (875.221085368602,-3.144) [2.400000e+00] (876.822958650073,-2.923) [2.300000e+00] (878.168558335542,-2.678) [2.200000e+00] (879.80133966195,-2.437) [2.100000e+00] (881.004900626457,-2.218) [2] (882.346711287478,-1.994) [1.900000e+00] (883.697561755581,-1.767) [1.700000e+00] (885.452750792101,-1.535) [1.600000e+00] (887.555980861665,-1.306) [1.500000e+00] (889.205200278853,-1.061) [1.600000e+00] (890.644715820389,-0.827) [1.600000e+00] (892.012869115298,-0.748) [1.600000e+00] (893.553879938004,-0.801) [1.500000e+00] (894.906967633035,-0.868) [1.500000e+00] (896.429897494422,-0.934) [1.500000e+00] (898.206359610865,-0.995) [1.300000e+00] (899.742210724292,-1.063) [1.300000e+00] (901.288470982272,-1.254) [1.200000e+00] (903.073700720065,-1.51) [1.100000e+00] (904.056099232407,-1.782) [1.200000e+00] (905.661577359442,-2.038) [1.300000e+00] (907.309240966211,-2.306) [1.400000e+00] (909.364346881288,-2.578) [1.500000e+00] (910.446869560287,-2.838) [1.600000e+00] (911.88862146923,-3.104) [1.700000e+00] (913.17326682145,-3.367) [1.900000e+00] (914.652547754957,-3.618) [2.100000e+00] (916.223188387228,-3.881) [2.100000e+00] (916.929453947779,-4.175) [2.300000e+00] (949.594894040151,-9.763) [7.400000e+00] (949.808442506302,-9.812) [7.200000e+00] (954.119267223631,-10.245) [6.100000e+00] (955.077367636151,-10.285) [6] (955.870193070796,-10.436) [5.900000e+00] (956.973622504513,-10.602) [5.700000e+00] (957.974781187876,-10.738) [5.400000e+00] (959.174455579098,-10.807) [5.200000e+00] (960.59579086236,-10.891) [5.100000e+00] (962.045024189117,-10.985) [4.900000e+00] (963.425911060813,-11.064) [4.800000e+00] (964.813321619232,-11.136) [4.700000e+00] (966.231642458392,-11.247) [4.600000e+00] (966.694102289736,-11.395) [4.400000e+00] (967.312982504803,-11.498) [4.200000e+00] (968.686475163626,-11.494) [4] (970.423758967149,-11.394) [3.800000e+00] (971.967186212811,-11.307) [3.700000e+00] (973.608225517697,-11.336) [3.600000e+00] (975.241000484524,-11.459) [3.600000e+00] (976.294257303585,-11.632) [3.500000e+00] (977.599308908957,-11.904) [3.500000e+00] (978.903584586514,-12.164) [3.400000e+00] (980.006235914641,-12.393) [3.200000e+00] (981.364566598335,-12.584) [3.100000e+00] (982.397411548232,-12.729) [2.900000e+00] (983.378530622847,-12.912) [2.900000e+00] (989.79094801466,-13.235) [2.600000e+00] (995.224455677119,-13.41) [2.500000e+00] (1000.14019726013,-13.706) [2.400000e+00] (1002.25207355658,-14.247) [2.200000e+00] (1000.65341649522,-14.931) [2.200000e+00] (997.295887116171,-15.812) [2.200000e+00] (994.919876553112,-16.289) [2.100000e+00] (994.332094927043,-16.622) [2.100000e+00] (995.485103280614,-16.682) [2.100000e+00] (996.923150762594,-16.607) [2] (998.196112979616,-16.548) [1.900000e+00] (1000.67604527668,-17.357) [1.500000e+00] (1001.93259553678,-17.288) [1.500000e+00] (1002.22561334395,-17.297) [1.600000e+00] (1003.20868579264,-17.338) [1.600000e+00] (1004.78410622502,-17.339) [1.600000e+00] (1005.48465970795,-17.355) [1.600000e+00] (1005.85593613862,-17.341) [1.500000e+00] (1007.06785016757,-17.295) [1.600000e+00] (1008.06297600792,-17.305) [1.500000e+00] (1008.80348316173,-17.345) [1.600000e+00] (1009.85654903618,-17.359) [1.600000e+00] (1011.20282240245,-17.344) [1.600000e+00] (1012.60324586046,-17.296) [1.600000e+00] (1014.21473272895,-17.231) [1.600000e+00] (1015.62342006652,-17.223) [1.600000e+00] (1017.13758234084,-17.182) [1.700000e+00] (1018.17431059987,-17.194) [1.700000e+00] (1019.64239789447,-17.222) [1.700000e+00] (1021.02026602436,-17.262) [1.600000e+00] (1022.49030262215,-17.315) [1.700000e+00] (1023.69162054579,-17.364) [1.600000e+00] (1024.8659118696,-17.41) [1.500000e+00] (1026.33623415529,-17.439) [1.500000e+00] (1027.80879272144,-17.5) [1.500000e+00] (1029.3551368915,-17.576) [1.500000e+00] (1030.66543718858,-17.673) [1.500000e+00] (1031.78538741735,-17.819) [1.400000e+00] (1033.27379069361,-17.983) [1.300000e+00] (1034.9056886297,-18.147) [1.400000e+00] (1036.38719108639,-18.326) [1.500000e+00] (1038.29470453214,-18.468) [1.500000e+00] (1039.41241759212,-18.662) [1.500000e+00] (1039.85018497153,-18.872) [1.500000e+00] (1041.09272505679,-18.793) [1.500000e+00] (1041.98129417478,-18.667) [1.500000e+00] (1043.34030054281,-18.513) [1.500000e+00] (1044.48960879633,-18.295) [1.500000e+00] (1045.85843405255,-18.043) [1.600000e+00] (1047.17096979954,-17.765) [1.600000e+00] (1048.3632461971,-17.507) [1.600000e+00] (1049.54725960384,-17.334) [1.600000e+00] (1050.59594536694,-17.217) [1.600000e+00] (1051.87085792077,-17.119) [1.500000e+00] (1052.99090194634,-17.03) [1.500000e+00] (1054.12971004,-16.957) [1.500000e+00] (1055.32266730831,-16.84) [1.500000e+00] (1056.72979576895,-16.701) [1.500000e+00] (1058.11738334515,-16.545) [1.500000e+00] (1059.3733385923,-16.392) [1.500000e+00] (1060.89401664355,-16.143) [1.600000e+00] (1062.18623248286,-15.915) [1.600000e+00] (1063.40329834032,-15.696) [1.600000e+00] (1064.57895149249,-15.546) [1.500000e+00] (1065.70579996237,-15.429) [1.600000e+00] (1066.97701680064,-15.293) [1.600000e+00] (1068.1782366588,-15.225) [1.600000e+00] (1069.49067382348,-15.171) [1.700000e+00] (1070.63327145846,-15.094) [1.700000e+00] (1071.61050304224,-14.96) [1.800000e+00] (1072.80938929815,-14.838) [1.800000e+00] (1073.96248623326,-14.688) [1.800000e+00] (1075.20648142696,-14.503) [1.700000e+00] (1076.64150979507,-14.343) [1.800000e+00] (1078.19601714235,-14.142) [1.900000e+00] (1079.76851039381,-13.994) [1.900000e+00] (1081.18623283987,-13.781) [2] (1082.59792771605,-13.623) [2.100000e+00] (1084.10431214011,-13.514) [2.100000e+00] (1085.90234959274,-13.381) [2.100000e+00] (1087.05398663402,-13.231) [2.200000e+00] (1088.57087081702,-13.053) [2.100000e+00] (1090.09008725511,-12.9) [2.100000e+00] (1091.4769918407,-12.772) [2.100000e+00] (1092.84513281712,-12.649) [2.200000e+00] (1094.24341218875,-12.522) [2.300000e+00] (1095.51394781334,-12.438) [2.400000e+00] (1096.1619996381,-12.383) [2.600000e+00] (1097.01206795742,-12.425) [2.700000e+00] (1099.014838651,-12.447) [2.900000e+00] (1100.39396114136,-12.309) [3.400000e+00] (1102.24594919868,-11.997) [3.800000e+00] (1104.00344501749,-11.681) [4.100000e+00] (1105.51128452111,-11.427) [4.400000e+00] (1107.12577098928,-11.181) [4.800000e+00] (1107.86715291421,-10.985) [5.200000e+00] (1109.350979832,-10.768) [5.500000e+00] (1110.98977308767,-10.523) [5.700000e+00] (1112.74367271982,-10.308) [6] (1114.19308776837,-10.146) [6.400000e+00] (1115.51086868174,-10.013) [6.800000e+00] (1116.88056518392,-9.896) [7.200000e+00] (1118.40123673035,-9.858) [7.700000e+00] (1119.77161229719,-9.812) [8.100000e+00] (1120.82456904281,-9.688) [8.500000e+00] (1121.82123851495,-9.578) [8.800000e+00] (1122.88575493397,-9.357) [9] (1124.42451016549,-9.221) [9.300000e+00] (1126.24355474329,-9.142) [9] (1127.67945653535,-8.966) [9] (1129.14763301534,-8.868) [9.100000e+00] (1130.56612978604,-8.765) [9] (1131.53665172696,-8.636) [8.900000e+00] (1132.91976023767,-8.484) [8.800000e+00] (1134.07684413984,-8.301) [8.500000e+00] (1135.01780587406,-8.116) [8.200000e+00] (1136.86260253337,-7.922) [7.700000e+00] (1143.78281335461,-7.406) [5.900000e+00] (1144.95183244868,-7.148) [5.700000e+00] (1147.24158909297,-6.876) [5.400000e+00] (1147.44895053885,-6.646) [5.200000e+00] (1146.53928710166,-6.497) [5] (1145.94752157509,-6.361) [4.900000e+00] (1147.76499124173,-6.235) [4.700000e+00] (1149.71565228853,-6.108) [4.600000e+00] (1151.26402471399,-5.943) [4.400000e+00] (1152.86976213877,-5.753) [4.200000e+00] (1154.37011162885,-5.579) [4] (1155.88854477508,-5.444) [3.800000e+00] (1157.56709413638,-5.27) [3.500000e+00] (1158.84511433255,-5.088) [3.400000e+00] (1160.10796309328,-4.93) [3.100000e+00] (1161.46492281255,-4.745) [3] (1162.9720785239,-4.565) [2.800000e+00] (1164.44841634584,-4.378) [2.600000e+00] (1165.9428369353,-4.157) [2.400000e+00] (1167.50035013104,-3.934) [2.300000e+00] (1169.04600948072,-3.706) [2.200000e+00] (1170.1113188371,-3.482) [2.100000e+00] (1171.51531979886,-3.269) [2] (1172.97279402392,-3.059) [1.900000e+00] (1174.45204455426,-2.837) [1.800000e+00] (1176.02296795244,-2.635) [1.700000e+00] (1177.56940506485,-2.405) [1.700000e+00] (1179.12691785991,-2.181) [1.400000e+00] (1179.88384728466,-1.953) [1.400000e+00] (1180.87157080448,-1.718) [1.400000e+00] (1182.22230031307,-1.514) [1.300000e+00] (1183.39191592362,-1.309) [1.200000e+00] (1183.84659478021,-1.093) [1.200000e+00] (1186.07762491598,-0.919) [1.200000e+00] (1188.46440227703,-0.789) [1.200000e+00] (1190.661499174,-0.73) [1.200000e+00] (1192.57219419704,-0.788) [1.300000e+00] (1195.23748059964,-0.842) [1.300000e+00] (1196.96939848037,-0.906) [1.300000e+00] (1198.78337303955,-0.975) [1.300000e+00] (1200.24250369573,-1.105) [1.300000e+00] (1201.64145577211,-1.351) [1.300000e+00] (1203.01707432754,-1.622) [1.300000e+00] (1204.39648551966,-1.878) [1.400000e+00] (1205.68266482191,-2.171) [1.500000e+00] (1206.99508854765,-2.433) [1.500000e+00] (1208.22555873589,-2.689) [1.600000e+00] (1209.34335883212,-2.959) [1.700000e+00] (1210.60464559154,-3.221) [1.600000e+00] (1211.8946179894,-3.473) [1.600000e+00] (1213.3189327837,-3.719) [1.700000e+00] (1214.61784457113,-3.975) [1.800000e+00] (1216.00619472316,-4.227) [1.700000e+00] (1217.34652371687,-4.479) [1.900000e+00] (1218.87097976344,-4.721) [2] (1220.7248737587,-4.977) [2.100000e+00] (1221.98626234077,-5.247) [2.200000e+00] (1222.78938611222,-5.557) [2.400000e+00] (1223.98009727317,-5.796) [2.600000e+00] (1224.93486893376,-6.018) [3.100000e+00] (1225.9325136813,-6.22) [3.500000e+00] (1227.33447808197,-6.436) [3.800000e+00] (1228.50195886306,-6.668) [4.200000e+00] (1229.63238698508,-6.932) [4.700000e+00] (1230.80433677276,-7.124) [5.100000e+00] (1231.89511164539,-7.285) [5.600000e+00] (1233.07667630422,-7.435) [6.200000e+00] (1234.66354595031,-7.585) [6.500000e+00] (1236.33964681948,-7.713) [7] (1238.30573416926,-7.911) [7.400000e+00] (1239.19284199324,-8.064) [7.800000e+00] (1240.2670895661,-8.168) [8.200000e+00] (1241.95088108564,-8.293) [8.400000e+00] (1243.16793852173,-8.474) [8.600000e+00] (1244.56756398881,-8.701) [8.800000e+00] (1246.10485348372,-8.901) [8.900000e+00] (1247.40745218822,-9.047) [9] (1248.77703927679,-9.187) [8.900000e+00] (1250.789999579,-9.341) [8.900000e+00] (1251.89563609244,-9.476) [8.600000e+00] (1253.28486677653,-9.659) [8.300000e+00] (1254.62955908615,-9.837) [8] (1256.26075601036,-10.015) [7.600000e+00] (1257.4101500688,-10.185) [7.300000e+00] (1258.91438674125,-10.325) [7] (1260.31099690458,-10.502) [6.700000e+00] (1261.60688989225,-10.664) [6.500000e+00] (1263.21350636205,-10.809) [6.300000e+00] (1264.71685952279,-10.954) [6] (1265.98338961353,-11.19) [5.700000e+00] (1266.73226112732,-11.393) [5.500000e+00] (1267.7071425454,-11.554) [5.300000e+00] (1269.72903828236,-11.626) [5] (1270.27325560719,-11.698) [4.800000e+00] (1271.18437252059,-11.796) [4.700000e+00] (1272.74691494272,-11.9) [4.500000e+00] (1274.05309607591,-11.959) [4.400000e+00] (1276.06158390439,-11.954) [4.200000e+00] (1278.22795215536,-11.968) [3.800000e+00] (1280.0078803631,-12.01) [3.700000e+00] (1281.5564452019,-12.113) [3.500000e+00] (1283.19143353155,-12.287) [3.300000e+00] (1285.03008670274,-12.514) [3.200000e+00] (1286.80476550434,-12.713) [3.100000e+00] (1288.14353123638,-12.931) [2.900000e+00] (1289.43484858004,-13.167) [2.900000e+00] (1290.8908552334,-13.364) [2.900000e+00] (1292.49112588285,-13.555) [2.800000e+00] (1294.02986696077,-13.741) [2.700000e+00] (1294.75384418361,-13.958) [2.600000e+00] (1295.804755227,-14.182) [2.500000e+00] (1297.13000945056,-14.372) [2.400000e+00] (1298.48217956594,-14.497) [2.300000e+00] (1299.9620885554,-14.599) [2.200000e+00] (1301.49033216845,-14.715) [2.200000e+00] (1302.84349389597,-14.882) [2.200000e+00] (1304.19977636202,-15.022) [2.200000e+00] (1305.4980057917,-15.231) [2] (1307.01788060733,-15.459) [1.900000e+00] (1308.40622256463,-15.637) [1.900000e+00] (1309.7847402734,-15.805) [1.800000e+00] (1311.17542256977,-15.963) [1.800000e+00] (1312.40364871271,-16.098) [1.700000e+00] (1313.88298765571,-16.257) [1.600000e+00] (1315.07436739274,-16.415) [1.600000e+00] (1316.41458462095,-16.57) [1.400000e+00] (1317.71001305514,-16.709) [1.400000e+00] (1318.98558132077,-16.852) [1.400000e+00] (1319.83116048681,-17.064) [1.400000e+00] (1320.98959498518,-17.268) [1.400000e+00] (1322.46882723301,-17.461) [1.400000e+00] (1323.97362799299,-17.56) [1.300000e+00] (1325.32221361779,-17.597) [1.300000e+00] (1326.85627103847,-17.614) [1.300000e+00] (1328.30177718925,-17.633) [1.300000e+00] (1329.71043785175,-17.698) [1.300000e+00] (1331.10827995892,-17.768) [1.300000e+00] (1332.6523732995,-17.822) [1.400000e+00] (1334.47783129625,-17.829) [1.400000e+00] (1335.85120592223,-17.945) [1.400000e+00] (1337.10688025979,-18.177) [1.500000e+00] (1338.26063147237,-18.392) [1.500000e+00] (1339.68323188759,-18.67) [1.300000e+00] (1339.9581389525,-18.799) [1.300000e+00] (1340.67732573557,-18.784) [1.300000e+00] (1341.21753081328,-18.63) [1.300000e+00] (1342.94957195777,-18.381) [1.300000e+00] (1344.40323176751,-18.093) [1.400000e+00] (1346.17052779674,-17.84) [1.400000e+00] (1347.9066835279,-17.536) [1.400000e+00] (1349.55060342417,-17.276) [1.400000e+00] (1351.14047768772,-17.017) [1.400000e+00] (1352.44473305526,-16.732) [1.500000e+00] (1353.96839755711,-16.419) [1.500000e+00] (1355.50635264854,-16.138) [1.500000e+00] (1357.11129881878,-15.86) [1.500000e+00] (1358.53513639307,-15.575) [1.500000e+00] (1359.70261216194,-15.361) [1.500000e+00] (1361.2488302731,-15.218) [1.600000e+00] (1362.58088957364,-15.111) [1.600000e+00] (1363.61236525458,-15.043) [1.600000e+00] (1364.85041088957,-15.045) [1.600000e+00] (1366.07036971485,-15.082) [1.500000e+00] (1367.13400802831,-15.091) [1.500000e+00] (1368.40588516614,-15.031) [1.500000e+00] (1369.5347367272,-14.91) [1.600000e+00] (1370.90576622876,-14.792) [1.600000e+00] (1372.24140296951,-14.659) [1.600000e+00] (1373.52700687035,-14.42) [1.600000e+00] (1375.30111058419,-14.254) [1.600000e+00] (1376.63384049369,-14.122) [1.500000e+00] (1377.83404143197,-14.026) [1.500000e+00] (1378.87590570485,-13.925) [1.600000e+00] (1379.9274857251,-13.773) [1.500000e+00] (1381.43852547062,-13.578) [1.600000e+00] (1382.91104905107,-13.409) [1.500000e+00] (1384.29569773182,-13.288) [1.500000e+00] (1385.56679272203,-13.196) [1.700000e+00] (1386.99130139299,-13.068) [1.600000e+00] (1388.34524157429,-12.941) [1.700000e+00] (1389.21124576909,-12.901) [1.800000e+00] (1389.98334522926,-12.9) [1.800000e+00] (1391.0488726273,-12.801) [2] (1393.74950605546,-12.776) [2.400000e+00] (1394.97002432265,-12.698) [2.700000e+00] (1396.22504644985,-12.473) [2.900000e+00] (1398.05555037586,-12.144) [3.200000e+00] (1399.1181873029,-11.824) [3.600000e+00] (1401.64920663085,-11.48) [4.200000e+00] (1403.44642385463,-11.258) [4.600000e+00] (1404.68926236817,-11.005) [4.800000e+00] (1405.90709396026,-10.804) [5.100000e+00] (1407.43600136379,-10.614) [5.400000e+00] (1409.00622151415,-10.435) [5.600000e+00] (1410.64722942181,-10.298) [6] (1411.94634451724,-10.143) [6.400000e+00] (1413.21297101755,-10.041) [6.700000e+00] (1414.46385239472,-9.968) [7] (1415.92431418593,-9.906) [7.200000e+00] (1417.36155049859,-9.807) [7.200000e+00] (1418.68221953631,-9.675) [7.200000e+00] (1420.20967378253,-9.48) [7.300000e+00] (1421.67091600235,-9.317) [7.200000e+00] (1422.98923979945,-9.171) [7.200000e+00] (1424.22582926871,-8.984) [7.200000e+00] (1425.78477066576,-8.755) [6.900000e+00] (1427.58712355013,-8.535) [6.600000e+00] (1429.05573673518,-8.346) [6.300000e+00] (1430.79142762825,-8.097) [6.200000e+00] (1432.37147033703,-7.846) [5.900000e+00] (1433.98701834985,-7.676) [5.600000e+00] (1435.64912808587,-7.556) [5.500000e+00] (1437.12320908543,-7.416) [5.300000e+00] (1438.75282710198,-7.268) [5.200000e+00] (1440.11402407316,-7.118) [5] (1441.70590362958,-6.951) [4.800000e+00] (1443.1476036757,-6.699) [4.700000e+00] (1444.73378655567,-6.53) [4.600000e+00] (1446.3830544746,-6.366) [4.500000e+00] (1447.90001042533,-6.182) [4.400000e+00] (1449.34405574091,-5.969) [4.400000e+00] (1450.64607334099,-5.769) [4.200000e+00] (1452.09670606906,-5.551) [4.100000e+00] (1453.60740936325,-5.32) [4] (1454.97072700506,-5.149) [3.900000e+00] (1456.47640506205,-4.964) [3.700000e+00] (1458.17245669575,-4.764) [3.500000e+00] (1459.46085205005,-4.569) [3.300000e+00] (1460.82818876259,-4.343) [3] (1462.50827288093,-4.125) [2.800000e+00] (1463.84244686445,-3.909) [2.600000e+00] (1465.40149558962,-3.698) [2.400000e+00] (1466.52676194585,-3.463) [2.300000e+00] (1467.92871193727,-3.244) [2.100000e+00] (1469.68617260176,-3.026) [2.100000e+00] (1471.11201506838,-2.817) [2.100000e+00] (1472.59748306645,-2.601) [2] (1474.07546982089,-2.369) [1.800000e+00] (1475.78156797342,-2.13) [1.700000e+00] (1477.61472914717,-1.899) [1.600000e+00] (1467.60446488409,-18.751) [1.100000e+00] (1466.58437849054,-18.578) [1.100000e+00] (1465.49115594547,-18.426) [1.200000e+00] (1464.4061968499,-18.23) [1.100000e+00] (1463.37929844506,-18.173) [1.100000e+00] (1462.43658902727,-18.086) [1.200000e+00] (1461.23204683625,-17.887) [1.200000e+00] (1459.85287508218,-17.681) [1.200000e+00] (1458.36015006729,-17.466) [1.200000e+00] (1456.86731162039,-17.203) [1.300000e+00] (1455.5192925405,-16.868) [1.300000e+00] (1454.31419145351,-16.542) [1.300000e+00] (1450.64071654329,-15.98) [1.500000e+00] (1448.138509899,-15.593) [1.600000e+00] (1446.51134828992,-15.316) [1.600000e+00] (1444.69694014989,-14.952) [1.700000e+00] (1442.94628759967,-14.61) [1.700000e+00] (1441.41503928239,-14.241) [1.700000e+00] (1440.04692088087,-13.935) [1.700000e+00] (1438.41953602032,-13.647) [1.900000e+00] (1436.88002474145,-13.396) [2.100000e+00] (1435.2195896949,-13.153) [2.100000e+00] (1433.90182745959,-12.964) [2.300000e+00] (1432.13029292342,-12.785) [2.500000e+00] (1430.76217231493,-12.641) [2.600000e+00] (1429.47600842649,-12.489) [2.700000e+00] (1428.02749550952,-12.368) [2.700000e+00] (1426.41976101012,-12.238) [2.700000e+00] (1424.70595225822,-12.071) [2.700000e+00] (1423.23633762869,-11.893) [2.700000e+00] (1421.55479823343,-11.719) [2.800000e+00] (1420.07479730604,-11.573) [2.900000e+00] (1417.8192306451,-11.462) [3.100000e+00] (1415.249793885,-11.356) [3.100000e+00] (1413.73606909636,-11.402) [3.400000e+00] (1413.25438261309,-11.716) [3.400000e+00] (1413.83120554272,-12.001) [3.500000e+00] (1413.97837015015,-12.097) [3.700000e+00] (1413.27080885722,-12.012) [3.900000e+00] (1412.51813951515,-11.777) [4.200000e+00] (1411.39130711559,-11.52) [4.600000e+00] (1410.17649085623,-11.307) [4.900000e+00] (1408.79720226103,-11.078) [5.300000e+00] (1407.37213280066,-10.896) [5.700000e+00] (1406.17462295122,-10.718) [6] (1405.24084633161,-10.546) [6.600000e+00] (1403.56767805647,-10.304) [7] (1402.06299671626,-10.116) [7.300000e+00] (1400.53029312182,-9.965) [7.600000e+00] (1399.1975649316,-9.821) [7.900000e+00] (1397.75128348039,-9.642) [7.900000e+00] (1396.53501406379,-9.446) [7.900000e+00] (1395.05724325484,-9.277) [8] (1393.55691886572,-9.113) [7.800000e+00] (1392.22865747505,-8.993) [7.600000e+00] (1390.74641900698,-8.828) [7.500000e+00] (1389.36177164464,-8.623) [7.200000e+00] (1387.89673019638,-8.443) [7] (1386.15589676663,-8.302) [6.600000e+00] (1384.65177529787,-8.161) [6.400000e+00] (1383.41808922181,-7.995) [6.100000e+00] (1382.23933724953,-7.785) [5.900000e+00] (1380.6360629875,-7.596) [5.800000e+00] (1378.8869657072,-7.399) [5.500000e+00] (1377.46781319561,-7.191) [5.200000e+00] (1376.0102530205,-6.949) [5.100000e+00] (1374.66088951669,-6.727) [4.800000e+00] (1373.08619735126,-6.59) [4.700000e+00] (1371.94585264192,-6.422) [4.500000e+00] (1370.66940066178,-6.242) [4.400000e+00] (1369.69576279155,-6.048) [4.300000e+00] (1368.43214999165,-5.859) [4.100000e+00] (1367.11750557345,-5.68) [4] (1365.82687018668,-5.514) [3.800000e+00] (1358.0491112121,-4.428) [3] (1356.91412223239,-4.282) [2.800000e+00] (1355.4671650152,-4.083) [2.700000e+00] (1354.08631040554,-3.901) [2.600000e+00] (1352.36802622931,-3.685) [2.500000e+00] (1350.49576365711,-3.505) [2.400000e+00] (1349.08263794274,-3.322) [2.300000e+00] (1347.21473544621,-3.093) [2.200000e+00] (1345.5444662084,-2.864) [2.200000e+00] (1343.97647319727,-2.6) [2] (1342.33177247173,-2.367) [1.900000e+00] (1340.28900331513,-2.124) [1.800000e+00] (1338.82317714085,-1.871) [1.800000e+00] (1336.97346597111,-1.607) [1.600000e+00] (1335.13113023837,-1.339) [1.700000e+00] (1333.24893362696,-1.07) [1.600000e+00] (1331.79807220526,-0.794) [1.600000e+00] (1330.28412264903,-0.73) [1.600000e+00] (1328.05924709374,-0.783) [1.600000e+00] (1326.7399172119,-0.846) [1.500000e+00] (1325.14567940565,-0.905) [1.500000e+00] (1323.7947525533,-0.995) [1.500000e+00] (1321.92305171687,-1.226) [1.500000e+00] (1320.43321613918,-1.499) [1.500000e+00] (1319.30113144111,-1.77) [1.600000e+00] (1318.25993743423,-2.048) [1.600000e+00] (1316.62193764001,-2.31) [1.700000e+00] (1315.36133409805,-2.583) [1.700000e+00] (1314.59515654598,-2.852) [1.800000e+00] (1313.05049450631,-3.124) [1.800000e+00] (1311.33911983747,-3.365) [1.900000e+00] (1310.13344862224,-3.644) [2] (1309.00895235099,-3.905) [2.200000e+00] (1307.89864040397,-4.17) [2.300000e+00] (1306.45245882977,-4.393) [2.400000e+00] (1305.17454847706,-4.631) [2.400000e+00] (1304.16115840331,-4.913) [2.500000e+00] (1303.13269599313,-5.173) [2.600000e+00] (1301.98028958134,-5.379) [2.700000e+00] (1300.21096728202,-5.571) [2.900000e+00] (1299.56582512303,-5.78) [3.200000e+00] (1298.72684237099,-6.01) [3.500000e+00] (1296.73062616818,-6.193) [4] (1295.25965387372,-6.341) [4.500000e+00] (1294.18696787251,-6.551) [5.100000e+00] (1292.99111826921,-6.768) [5.600000e+00] (1291.57429744316,-6.969) [6.100000e+00] (1289.70883195093,-7.141) [6.600000e+00] (1288.40010416754,-7.292) [6.900000e+00] (1286.97860315129,-7.521) [7.300000e+00] (1285.72090744522,-7.685) [7.600000e+00] (1284.36483533216,-7.817) [7.800000e+00] (1282.95539129053,-7.971) [7.900000e+00] (1281.72705808084,-8.094) [7.900000e+00] (1280.01848277533,-8.247) [8.100000e+00] (1278.56704875759,-8.42) [8.300000e+00] (1276.54536417516,-8.63) [8.300000e+00] (1275.55083824411,-8.945) [8.100000e+00] (1274.74490616559,-9.244) [8.100000e+00] (1274.4520582803,-9.45) [7.800000e+00] (1272.55857732872,-9.553) [7.600000e+00] (1270.99951456589,-9.636) [7.400000e+00] (1269.97562573783,-9.723) [7.200000e+00] (1268.23030811423,-9.793) [7] (1267.44012253526,-9.92) [6.800000e+00] (1265.98556826663,-10.057) [6.600000e+00] (1264.77687956989,-10.214) [6.400000e+00] (1263.81093573556,-10.345) [6.200000e+00] (1262.33684147126,-10.419) [6] (1260.453389761,-10.418) [5.800000e+00] (1259.69246261962,-10.516) [5.600000e+00] (1258.29517832209,-10.658) [5.300000e+00] (1256.87377918654,-10.789) [5.200000e+00] (1255.54628833979,-10.886) [5] (1253.79270600637,-10.99) [4.800000e+00] (1252.19554818548,-11.13) [4.700000e+00] (1250.33755918074,-11.308) [4.500000e+00] (1248.78384727515,-11.516) [4.400000e+00] (1247.65300567139,-11.736) [4.100000e+00] (1246.14731314699,-11.923) [3.900000e+00] (1244.15690734271,-12.099) [3.700000e+00] (1242.85254201573,-12.238) [3.700000e+00] (1241.5257249022,-12.453) [3.600000e+00] (1239.70827050957,-12.646) [3.400000e+00] (1238.47401072197,-12.812) [3.300000e+00] (1237.18102511146,-12.951) [3.200000e+00] (1235.77838608894,-13.092) [3] (1234.92724201865,-13.271) [2.800000e+00] (1233.25862419952,-13.427) [2.800000e+00] (1231.69373668181,-13.516) [2.700000e+00] (1230.16413608929,-13.684) [2.600000e+00] (1228.80067933978,-13.848) [2.500000e+00] (1227.52879323466,-13.989) [2.300000e+00] (1225.76169411969,-14.134) [2.300000e+00] (1224.39064988976,-14.318) [2.200000e+00] (1223.29374430628,-14.448) [2.100000e+00] (1221.75655623334,-14.598) [2] (1220.28178216083,-14.719) [1.900000e+00] (1218.84754398989,-14.884) [1.800000e+00] (1217.48320418753,-15.031) [1.600000e+00] (1216.02864650973,-15.162) [1.700000e+00] (1214.52305365948,-15.266) [1.700000e+00] (1213.09629942697,-15.383) [1.600000e+00] (1211.73866451105,-15.477) [1.600000e+00] (1210.3088953757,-15.589) [1.600000e+00] (1208.98509239242,-15.678) [1.600000e+00] (1207.56514484015,-15.779) [1.600000e+00] (1206.20984579138,-15.881) [1.500000e+00] (1204.76063891286,-15.962) [1.300000e+00] (1203.44821429867,-16.075) [1.400000e+00] (1202.04255779459,-16.209) [1.500000e+00] (1200.58129397006,-16.332) [1.500000e+00] (1199.21326203556,-16.458) [1.500000e+00] (1197.77980076775,-16.585) [1.600000e+00] (1196.51695501576,-16.73) [1.600000e+00] (1195.36901388762,-16.876) [1.500000e+00] (1193.99942338997,-16.995) [1.600000e+00] (1192.64110946744,-17.121) [1.600000e+00] (1191.25197854405,-17.236) [1.600000e+00] (1189.8470998028,-17.356) [1.600000e+00] (1188.55489161248,-17.476) [1.700000e+00] (1187.30555785631,-17.587) [1.600000e+00] (1185.71956521724,-17.698) [1.700000e+00] (1184.48899151613,-17.768) [1.700000e+00] (1183.20504677524,-17.891) [1.700000e+00] (1181.87006597298,-17.857) [1.600000e+00] (1180.51408748793,-17.71) [1.700000e+00] (1179.21527491556,-17.532) [1.700000e+00] (1177.55267730216,-17.397) [1.700000e+00] (1175.8991208432,-17.283) [1.800000e+00] (1174.75798642428,-17.231) [1.900000e+00] (1174.10827590382,-17.186) [1.800000e+00] (1173.41559139117,-17.132) [1.700000e+00] (1171.92049305529,-16.974) [1.700000e+00] (1170.73736461812,-16.889) [1.700000e+00] (1169.62044235932,-16.756) [1.700000e+00] (1168.32901196076,-16.614) [1.800000e+00] (1167.16833665748,-16.422) [1.800000e+00] (1166.17759826385,-16.263) [1.800000e+00] (1164.65100297407,-16.072) [1.900000e+00] (1163.09047622275,-15.905) [1.800000e+00] (1161.57194348978,-15.672) [1.800000e+00] (1160.0347489412,-15.497) [1.800000e+00] (1158.69966508499,-15.299) [1.900000e+00] (1156.7492062204,-15.122) [2] (1155.41577959662,-14.99) [2.100000e+00] (1154.00944150736,-14.904) [2.200000e+00] (1152.70283927249,-14.772) [2.200000e+00] (1151.45485883103,-14.676) [2.200000e+00] (1149.95305257152,-14.522) [2.200000e+00] (1148.63615195832,-14.381) [2.300000e+00] (1147.34102719149,-14.204) [2.400000e+00] (1145.82103639964,-14.04) [2.400000e+00] (1144.74892179738,-13.848) [2.600000e+00] (1143.56792615695,-13.716) [2.600000e+00] (1142.35018458587,-13.602) [2.600000e+00] (1141.65187477676,-13.491) [2.600000e+00] (1140.30425583196,-13.382) [2.600000e+00] (1138.82791586104,-13.233) [2.600000e+00] (1137.18251807842,-13.105) [2.700000e+00] (1135.59875521519,-12.947) [2.700000e+00] (1134.26075561296,-12.762) [2.800000e+00] (1133.03698558365,-12.587) [2.800000e+00] (1131.26015143414,-12.428) [2.800000e+00] (1130.22575918218,-12.33) [2.900000e+00] (1128.87269085595,-12.251) [3] (1127.56463102108,-12.13) [3.100000e+00] (1126.03793230557,-12.02) [3.100000e+00] (1124.6570592156,-11.9) [3.300000e+00] (1123.48141170852,-11.745) [3.400000e+00] (1122.05251433599,-11.596) [3.500000e+00] (1120.54166164881,-11.451) [3.700000e+00] (1119.30359974042,-11.308) [3.900000e+00] (1117.97084917283,-11.201) [4.200000e+00] (1116.76506195247,-11.128) [4.700000e+00] (1115.52388738955,-10.998) [5.100000e+00] (1114.06708615421,-10.884) [5.500000e+00] (1112.90203572806,-10.767) [5.900000e+00] (1111.48742851512,-10.605) [6.400000e+00] (1109.30596956348,-10.398) [6.800000e+00] (1107.88902697108,-10.193) [7.100000e+00] (1106.47286300133,-10.049) [7.600000e+00] (1105.07322590136,-9.923) [8] (1103.8073583699,-9.776) [8.300000e+00] (1102.3896380727,-9.614) [8.500000e+00] (1101.1365061219,-9.466) [8.700000e+00] (1099.64742802074,-9.296) [8.700000e+00] (1098.08096586433,-9.195) [8.800000e+00] (1097.40520745745,-9.079) [8.800000e+00] (1097.40520745745,-8.921) [8.900000e+00] (1094.21064647718,-8.686) [8.600000e+00] (1091.40446483745,-8.448) [8.200000e+00] (1089.8424730639,-8.213) [8] (1087.99475856794,-7.98) [7.600000e+00] (1086.07160169445,-7.758) [7.300000e+00] (1084.60935340063,-7.561) [7] (1083.08799843377,-7.451) [6.500000e+00] (1081.81619933602,-7.328) [6.300000e+00] (1079.1385388049,-6.985) [5.700000e+00] (1077.74570397125,-6.806) [5.500000e+00] (1075.8613386601,-6.601) [5.300000e+00] (1074.6226901946,-6.406) [5.200000e+00] (1073.3772368842,-6.223) [5.100000e+00] (1071.81679794179,-6.058) [4.900000e+00] (1070.29388578812,-5.885) [4.700000e+00] (1069.06184758176,-5.705) [4.400000e+00] (1067.97097000306,-5.499) [4.100000e+00] (1066.61410523025,-5.298) [3.900000e+00] (1065.01001506618,-5.076) [3.700000e+00] (1063.42099365522,-4.917) [3.500000e+00] (1061.67934088511,-4.744) [3.300000e+00] (1060.29311502131,-4.554) [3.200000e+00] (1058.8272692515,-4.356) [3.100000e+00] (1057.35101926743,-4.137) [2.900000e+00] (1055.91375421798,-3.9) [2.800000e+00] (1054.31345448368,-3.696) [2.600000e+00] (1052.81309462103,-3.482) [2.500000e+00] (1051.1007989871,-3.245) [2.500000e+00] (1049.3847134108,-3.021) [2.200000e+00] (1048.03309632509,-2.8) [2.100000e+00] (1046.54547161327,-2.547) [2] (1044.95256033064,-2.301) [1.800000e+00] (1043.36723208579,-2.06) [1.800000e+00] (1041.79240268213,-1.822) [1.600000e+00] (1040.44904904586,-1.568) [1.600000e+00] (1039.08693180037,-1.321) [1.600000e+00] (1037.69623386343,-1.079) [1.600000e+00] (1036.08465451642,-0.868) [1.500000e+00] (1034.44371585572,-0.783) [1.400000e+00] (1033.01169895211,-0.809) [1.300000e+00] (1031.81047651529,-0.884) [1.300000e+00] (1030.48452302764,-0.952) [1.300000e+00] (1029.18034673384,-1.076) [1.200000e+00] (1027.77389653641,-1.321) [1.100000e+00] (1026.29161594517,-1.603) [1.200000e+00] (1024.95963488762,-1.873) [1.100000e+00] (1023.55473969911,-2.15) [1.100000e+00] (1022.15509437549,-2.42) [1.200000e+00] (1020.91547149935,-2.691) [1.300000e+00] (1019.53760293993,-2.956) [1.400000e+00] (1018.0906119683,-3.226) [1.500000e+00] (1016.85176547873,-3.472) [1.700000e+00] (1015.44609304413,-3.729) [1.700000e+00] (1013.98549327128,-3.968) [1.900000e+00] (1012.72564643332,-4.216) [2] (1011.50040877402,-4.458) [2.100000e+00] (1010.18271655804,-4.693) [2.200000e+00] (1008.81690184902,-4.906) [2.400000e+00] (1007.49541834364,-5.12) [2.600000e+00] (1006.07924486067,-5.318) [2.700000e+00] (1004.80656649648,-5.51) [2.900000e+00] (1003.43919637738,-5.701) [3.300000e+00] (1001.96439935303,-5.881) [3.800000e+00] (1000.42952018238,-6.067) [4.100000e+00] (999.025399661174,-6.246) [4.500000e+00] (997.639265044581,-6.463) [5.100000e+00] (996.359876921423,-6.666) [5.600000e+00] (995.352506686828,-6.863) [6.400000e+00] (994.088185969619,-7.043) [6.900000e+00] (992.909420795723,-7.216) [7.500000e+00] (991.676506447192,-7.366) [7.800000e+00] (990.383509522842,-7.546) [8.300000e+00] (989.014679080286,-7.697) [8.600000e+00] (987.664612705648,-7.809) [8.900000e+00] (986.142468285034,-7.963) [9] (984.908188211044,-8.161) [9.200000e+00] (983.809139806535,-8.371) [9.300000e+00] (982.538014273264,-8.517) [9.200000e+00] (981.584017314541,-8.678) [9.100000e+00] (980.236963636116,-8.833) [9] (978.820009840593,-8.966) [8.900000e+00] (977.579702196686,-9.142) [8.700000e+00] (976.333366983251,-9.291) [8.400000e+00] (974.995354029198,-9.436) [8.100000e+00] (973.748335279327,-9.584) [8] (972.383977025846,-9.742) [7.700000e+00] (970.971589587974,-9.878) [7.400000e+00] (969.771046389772,-9.985) [7] (968.438965977565,-10.063) [7] (967.252713368873,-10.184) [6.700000e+00] (965.947755072429,-10.319) [6.500000e+00] (964.704432125032,-10.502) [6.200000e+00] (963.615200860472,-10.611) [5.900000e+00] (962.416210435395,-10.753) [5.700000e+00] (961.219550058383,-10.836) [5.400000e+00] (960.044667305046,-10.976) [5.300000e+00] (958.835175372754,-11.115) [5.100000e+00] (957.424246998191,-11.266) [4.900000e+00] (956.046466991233,-11.354) [4.700000e+00] (954.647592008332,-11.481) [4.500000e+00] (953.57187362845,-11.668) [4.300000e+00] (952.314259690758,-11.837) [4.300000e+00] (950.79357218468,-11.974) [4.100000e+00] (949.145137406695,-12.058) [3.900000e+00] (947.571076682795,-12.207) [3.700000e+00] (946.170647637567,-12.346) [3.400000e+00] (944.661235818084,-12.487) [3.400000e+00] (943.210447999136,-12.585) [3.300000e+00] (941.662730797541,-12.775) [3.200000e+00] (940.293027279379,-12.973) [3.200000e+00] (939.004594592698,-13.165) [3.100000e+00] (937.636536209829,-13.33) [3.100000e+00] (936.11507059816,-13.467) [3] (934.62150079421,-13.592) [3] (933.23759910671,-13.692) [2.900000e+00] (931.893555574444,-13.848) [2.800000e+00] (930.551748781447,-13.986) [2.700000e+00] (929.248247399485,-14.097) [2.600000e+00] (927.747098170069,-14.231) [2.600000e+00] (926.301559385583,-14.371) [2.500000e+00] (924.867388650044,-14.492) [2.400000e+00] (923.572242650441,-14.625) [2.300000e+00] (922.27097892514,-14.741) [2.200000e+00] (920.924697335324,-14.918) [2.200000e+00] (919.688082514908,-15.092) [2.100000e+00] (918.430465539635,-15.243) [2] (917.186364114915,-15.374) [2.100000e+00] (915.82200202236,-15.502) [2.100000e+00] (914.424583065523,-15.625) [2.100000e+00] (913.015111634495,-15.772) [2] (911.719873731302,-15.879) [1.900000e+00] (910.212788033911,-15.976) [1.900000e+00] (908.793591023742,-16.075) [1.900000e+00] (907.31577047193,-16.206) [1.800000e+00] (906.010031061392,-16.345) [1.800000e+00] (904.674249259621,-16.479) [1.700000e+00] (903.277606718308,-16.586) [1.700000e+00] (902.046332405872,-16.711) [1.500000e+00] (900.691784759011,-16.787) [1.500000e+00] (899.168855327436,-16.949) [1.500000e+00] (897.633871185916,-17.075) [1.500000e+00] (896.286811060699,-17.175) [1.500000e+00] (894.941212205776,-17.279) [1.500000e+00] (893.451337431782,-17.408) [1.500000e+00] (892.046429692659,-17.514) [1.700000e+00] (890.675262842406,-17.627) [1.600000e+00] (889.465676485758,-17.746) [1.500000e+00] (888.108799766306,-17.857) [1.500000e+00] (886.656545061023,-17.962) [1.500000e+00] (885.383859907284,-17.912) [1.500000e+00] (884.01889959068,-17.724) [1.600000e+00] (882.901082477351,-17.523) [1.600000e+00] (881.802806248483,-17.323) [1.600000e+00] (880.498616544693,-17.138) [1.700000e+00] (879.026820095559,-16.931) [1.600000e+00] (877.809744039519,-16.644) [1.700000e+00] (876.429627107761,-16.397) [1.700000e+00] (875.025493577463,-16.178) [1.800000e+00] (873.410104774697,-16) [1.700000e+00] (871.791017962395,-15.804) [1.800000e+00] (870.537186602619,-15.615) [1.800000e+00] (868.694701458534,-15.415) [1.700000e+00] (867.08757745238,-15.223) [1.800000e+00] (865.614227399732,-15.017) [1.900000e+00] (864.385873937612,-14.841) [2] (862.610365940251,-14.677) [2] (861.020455064246,-14.538) [2] (859.453187436334,-14.406) [2] (857.99033937838,-14.318) [2] (856.571822954067,-14.22) [2] (854.978212291562,-14.087) [1.900000e+00] (853.520614127641,-13.95) [2] (852.117851340282,-13.827) [2.100000e+00] (850.861692255118,-13.705) [2.100000e+00] (849.461255932683,-13.577) [2.100000e+00] (848.147248345326,-13.504) [2.100000e+00] (846.819725236414,-13.433) [2] (845.412486304952,-13.343) [2] (844.093228422723,-13.258) [2] (843.008464706853,-13.176) [2] (841.739565598268,-13.075) [2.100000e+00] (840.369171696223,-12.955) [2.100000e+00] (838.998090674602,-12.825) [2.100000e+00] (837.579663116557,-12.692) [2.100000e+00] (836.165709954415,-12.531) [2.100000e+00] (834.610492651815,-12.388) [2.200000e+00] (833.273929335062,-12.189) [2.100000e+00] (831.820893974603,-12.039) [2.300000e+00] (830.445248000617,-11.842) [2.300000e+00] (829.067364399022,-11.769) [2.400000e+00] (827.567756652624,-11.585) [2.500000e+00] (826.543678783466,-11.478) [2.700000e+00] (825.166569332433,-11.338) [2.800000e+00] (824.108060359763,-11.327) [3] (822.891246831437,-11.222) [3.100000e+00] (821.550981951035,-11.135) [3.200000e+00] (820.181273908338,-10.933) [3.300000e+00] (818.591447513916,-10.779) [3.300000e+00] (816.733293301337,-10.624) [3.500000e+00] (815.407406012638,-10.487) [3.600000e+00] (814.196441607155,-10.307) [3.800000e+00] (812.971186182143,-10.191) [4.200000e+00] (811.725702753407,-10.067) [4.500000e+00] (810.427532796457,-9.957) [4.900000e+00] (809.264602505868,-9.838) [5.200000e+00] (807.970133253125,-9.748) [5.600000e+00] (806.181878268759,-9.589) [5.900000e+00] (804.594287782957,-9.559) [6.300000e+00] (802.105555486717,-9.486) [6.700000e+00] (800.381863293485,-9.376) [7] (798.783770412051,-9.249) [7.300000e+00] (797.011179855664,-9.063) [7.800000e+00] (795.607037184189,-8.843) [7.700000e+00] (794.659749559802,-8.668) [7.700000e+00] (793.302178844221,-8.469) [7.500000e+00] (791.987392378577,-8.3) [7.300000e+00] (790.411766075439,-8.112) [7.200000e+00] (788.89407616534,-7.907) [6.900000e+00] (787.509387404899,-7.692) [6.600000e+00] (786.169032943847,-7.578) [6.300000e+00] (784.654355729727,-7.359) [6.100000e+00] (783.2185318382,-7.2) [5.900000e+00] (781.634727798284,-7.013) [5.600000e+00] (780.26510374907,-6.825) [5.400000e+00] (778.882739217905,-6.62) [5.200000e+00] (777.507088946264,-6.467) [5] (776.020216065958,-6.23) [4.900000e+00] (774.687436157821,-6.063) [4.600000e+00] (773.289231904957,-5.865) [4.500000e+00] (771.727205517642,-5.652) [4.200000e+00] (770.211063508091,-5.418) [4] (768.843677144825,-5.289) [3.600000e+00] (767.339499718543,-5.098) [3.400000e+00] (765.648947064977,-4.894) [3.300000e+00] (763.967431982819,-4.717) [3.100000e+00] (762.349793431481,-4.537) [3] (760.780966270365,-4.291) [2.800000e+00] (759.322585789947,-4.052) [2.700000e+00] (757.678604662749,-3.841) [2.500000e+00] (756.224011888574,-3.615) [2.500000e+00] (754.822708024827,-3.376) [2.400000e+00] (753.404959821386,-3.137) [2.400000e+00] (752.036797588258,-2.926) [2.300000e+00] (750.655119833938,-2.693) [2.300000e+00] (749.306499373713,-2.454) [2.300000e+00] (747.881175786812,-2.226) [2.200000e+00] (746.286089956341,-2.016) [2.100000e+00] (744.90819901951,-1.767) [2] (743.457393550743,-1.543) [1.900000e+00] (742.086218221031,-1.313) [1.900000e+00] (740.592541529239,-1.089) [1.900000e+00] (739.105665640431,-0.847) [1.900000e+00] (737.7164968392,-0.676) [1.700000e+00] (736.467131767602,-0.628) [1.700000e+00] (735.135123890202,-0.685) [1.600000e+00] (733.718148548226,-0.741) [1.600000e+00] (732.301173664802,-0.81) [1.700000e+00] (730.732427802551,-0.883) [1.600000e+00] (729.376400202102,-0.948) [1.600000e+00] (728.017359475809,-1.048) [1.700000e+00] (726.529017903125,-1.291) [1.700000e+00] (725.048855443399,-1.575) [1.700000e+00] (724.063259916447,-1.853) [1.600000e+00] (722.862015102309,-2.127) [1.600000e+00] (721.779400983767,-2.401) [1.700000e+00] (721.059813058517,-2.663) [1.700000e+00] (719.74355749989,-2.924) [1.700000e+00] (718.640712252961,-3.171) [1.700000e+00] (717.080312399596,-3.439) [1.800000e+00] (715.637162724711,-3.711) [1.900000e+00] (714.717848681874,-3.989) [2] (713.795522402028,-4.25) [2.200000e+00] (712.4732401908,-4.505) [2.300000e+00] (711.563571891685,-4.745) [2.400000e+00] (710.429215845819,-5.008) [2.700000e+00] (708.613226077895,-5.21) [2.800000e+00] (707.463805349647,-5.419) [2.900000e+00] (706.149788365231,-5.616) [3.200000e+00] (704.48264035703,-5.833) [3.600000e+00] (703.082964775302,-5.999) [4.100000e+00] (701.378971766709,-6.211) [4.700000e+00] (699.766577063555,-6.414) [5] (698.412010820508,-6.62) [5.100000e+00] (697.28135820226,-6.828) [5.300000e+00] (695.723027419745,-7.009) [5.500000e+00] (693.925028085888,-7.176) [5.500000e+00] (692.01046930519,-7.311) [5.500000e+00] (690.546833372907,-7.521) [5.500000e+00] (688.969042947106,-7.744) [5.300000e+00] (687.477600932657,-7.97) [5.200000e+00] (686.001222740964,-8.176) [5.100000e+00] (684.535347403717,-8.413) [5.100000e+00] (683.18448415858,-8.566) [5] (681.766730826862,-8.751) [4.800000e+00] (680.154334404616,-8.881) [4.900000e+00] (678.643350216711,-9.073) [4.800000e+00] (677.427647231597,-9.246) [4.700000e+00] (675.909172397437,-9.432) [4.500000e+00] (674.521463292103,-9.613) [4.400000e+00] (673.066173827466,-9.773) [4.200000e+00] (671.757405935361,-9.883) [4.100000e+00] (670.499079748215,-10.018) [3.900000e+00] (669.162587845816,-10.214) [3.800000e+00] (667.686982056748,-10.411) [3.700000e+00] (666.335425013387,-10.614) [3.700000e+00] (664.983012665348,-10.763) [3.700000e+00] (663.78245649205,-10.844) [3.500000e+00] (662.517331307941,-10.916) [3.400000e+00] (661.261162053384,-11.024) [3.300000e+00] (659.833676951407,-11.13) [3.100000e+00] (658.893880722283,-11.263) [3] (657.489723293332,-11.381) [3] (656.038218468331,-11.511) [2.800000e+00] (654.64077845257,-11.601) [2.700000e+00] (653.198310310169,-11.77) [2.600000e+00] (652.005325995222,-11.966) [2.600000e+00] (650.819832756161,-12.174) [2.500000e+00] (649.680913250323,-12.358) [2.400000e+00] (648.514961354301,-12.52) [2.400000e+00] (647.255779032033,-12.684) [2.300000e+00] (645.969645043784,-12.852) [2.200000e+00] (644.835285588577,-12.973) [2.200000e+00] (643.809057558051,-13.065) [2.100000e+00] (642.577681346561,-13.175) [2] (641.42532707258,-13.286) [2.100000e+00] (640.168464937323,-13.368) [2] (639.223335911926,-13.427) [2] (638.222755741307,-13.542) [2] (637.205727647829,-13.651) [2] (636.106746591512,-13.781) [2] (635.017575881011,-13.872) [1.900000e+00] (633.795317993951,-13.939) [1.800000e+00] (632.0468972664,-13.954) [1.800000e+00] (630.951008283034,-13.974) [1.800000e+00] (629.405737615541,-13.993) [1.800000e+00] (627.225769032791,-14.015) [1.800000e+00] (625.121887779129,-14.154) [1.700000e+00] (621.551514734018,-14.31) [1.800000e+00] (619.900719910773,-14.515) [1.800000e+00] (618.054506527998,-14.815) [1.900000e+00] (616.722406206452,-15.044) [1.900000e+00] (615.389453246023,-15.222) [1.900000e+00] (613.606504179905,-15.332) [1.900000e+00] (611.7717275025,-15.455) [1.800000e+00] (610.45383747623,-15.615) [1.700000e+00] (609.309504508075,-15.77) [1.700000e+00] (607.701578271135,-15.912) [1.700000e+00] (606.007140826818,-16.065) [1.600000e+00] (604.578876846683,-16.26) [1.600000e+00] (604.579944728651,-16.448) [1.600000e+00] (602.816058880144,-17.675) [1.500000e+00] (601.360921292768,-17.85) [1.400000e+00] (600.091391460551,-17.933) [1.500000e+00] (598.824794459762,-17.917) [1.500000e+00] (597.396609455813,-17.918) [1.400000e+00] (596.325431902945,-17.884) [1.400000e+00] (594.77543626897,-17.841) [1.400000e+00] (593.20219325654,-17.849) [1.400000e+00] (591.218648551032,-17.893) [1.400000e+00] (589.956529988152,-18.024) [1.400000e+00] (588.412638664266,-18.182) [1.400000e+00] (582.336623377122,-17.886) [1.400000e+00] (581.114974725035,-17.673) [1.500000e+00] (579.406245030146,-17.449) [1.500000e+00] (577.859181396896,-17.216) [1.500000e+00] (576.218036074547,-16.96) [1.500000e+00] (574.871644878632,-16.696) [1.600000e+00] (574.101622676206,-16.423) [1.500000e+00] (573.088755141335,-16.269) [1.600000e+00] (572.01765346925,-16.235) [1.500000e+00] (571.115710711763,-16.258) [1.500000e+00] (570.11366093119,-16.202) [1.500000e+00] (568.835089143089,-16.04) [1.500000e+00] (567.203989259495,-15.781) [1.500000e+00] (565.714856658791,-15.552) [1.500000e+00] (564.110633535895,-15.333) [1.600000e+00] (562.323118373242,-15.117) [1.700000e+00] (560.845956633901,-14.925) [1.700000e+00] (558.693089904352,-14.678) [1.700000e+00] (556.77395379491,-14.459) [1.700000e+00] (555.322281132898,-14.267) [1.800000e+00] (553.985698563551,-14.124) [1.800000e+00] (552.830168170264,-13.968) [1.800000e+00] (551.241779437419,-13.825) [1.900000e+00] (550.045775579096,-13.684) [2] (548.78365311927,-13.566) [2] (547.64094573849,-13.475) [2.100000e+00] (546.247281709027,-13.393) [2.200000e+00] (544.864894225709,-13.29) [2.200000e+00] (543.675610016303,-13.124) [2.200000e+00] (542.262402895629,-12.959) [2.100000e+00] (540.754421576806,-12.819) [2.100000e+00] (539.812463344637,-12.683) [2.200000e+00] (538.417254196222,-12.56) [2.200000e+00] (537.355726574113,-12.45) [2.300000e+00] (536.175479506121,-12.368) [2.300000e+00] (535.025355553696,-12.339) [2.400000e+00] (533.976650514154,-12.292) [2.300000e+00] (532.90840327187,-12.193) [2.400000e+00] (531.945358606919,-12.092) [2.400000e+00] (530.807284462883,-12.001) [2.400000e+00] (527.235027128636,-11.747) [2.900000e+00] (526.042883274045,-11.672) [3] (524.60040034535,-11.509) [3.300000e+00] (522.839914622353,-11.305) [3.400000e+00] (521.397431263821,-11.086) [3.700000e+00] (519.694103741061,-10.819) [3.800000e+00] (518.208827218271,-10.547) [3.900000e+00] (516.93241250787,-10.353) [4] (515.450071510865,-10.218) [4.300000e+00] (514.217993765289,-10.058) [4.700000e+00] (512.707073453311,-9.95) [5.100000e+00] (511.298496015165,-9.809) [5.400000e+00] (509.637339639398,-9.679) [5.900000e+00] (508.222356493428,-9.598) [6.400000e+00] (506.457387488947,-9.468) [6.500000e+00] (503.337214264038,-9.275) [6.900000e+00] (504.013696442417,-9.182) [7.100000e+00] (500.802379777837,-8.83) [7.400000e+00] (496.377132778696,-8.687) [7.400000e+00] (494.824658580862,-8.493) [7.700000e+00] (493.371515019616,-8.271) [8] (491.46364903889,-8.071) [8] (490.176029649865,-7.884) [7.900000e+00] (488.813799911123,-7.688) [7.700000e+00] (487.44716532124,-7.51) [7.400000e+00] (485.841467802819,-7.344) [7] (484.422154797968,-7.157) [6.800000e+00] (482.920192767225,-6.919) [6.600000e+00] (481.396448211589,-6.719) [6.400000e+00] (479.886992869078,-6.51) [6.200000e+00] (478.461654988851,-6.314) [5.800000e+00] (477.141597285648,-6.113) [5.400000e+00] (476.059754372661,-5.864) [5.100000e+00] (474.662298856012,-5.656) [4.800000e+00] (473.372288015914,-5.452) [4.500000e+00] (472.003336909058,-5.306) [4.300000e+00] (470.420267446521,-5.114) [4] (469.318957264921,-4.93) [3.800000e+00] (468.328178443739,-4.74) [3.700000e+00] (466.802192276234,-4.557) [3.400000e+00] (466.072110445456,-4.38) [3.300000e+00] (464.397353067545,-4.175) [3.200000e+00] (463.323849885504,-3.982) [3] (462.121816453522,-3.843) [2.900000e+00] (460.885179290108,-3.638) [2.800000e+00] (459.689169873697,-3.435) [2.700000e+00] (458.499109538703,-3.256) [2.600000e+00] (457.153558373643,-3.062) [2.400000e+00] (455.846319727767,-2.881) [2.200000e+00] (454.849515601345,-2.71) [2.200000e+00] (453.717386270204,-2.514) [2.100000e+00] (452.289108938242,-2.32) [2.100000e+00] (450.942784998619,-2.134) [2] (449.543858896415,-1.925) [1.900000e+00] (448.331392642486,-1.733) [1.800000e+00] (447.124876387937,-1.526) [1.700000e+00] (445.53037884952,-1.316) [1.500000e+00] (444.043474938491,-1.118) [1.600000e+00] (442.586692337034,-0.911) [1.500000e+00] (441.311814492722,-0.735) [1.600000e+00] (440.0640461795,-0.656) [1.400000e+00] (438.629046132091,-0.692) [1.400000e+00] (437.292602570498,-0.756) [1.300000e+00] (435.862927751959,-0.824) [1.300000e+00] (434.345202885215,-0.889) [1.300000e+00] (432.884562631887,-0.966) [1.300000e+00] (431.354788444461,-1.04) [1.200000e+00] (429.827255038153,-1.249) [1.100000e+00] (428.154660527987,-1.524) [1.100000e+00] (426.650452558797,-1.795) [1.200000e+00] (425.147016934149,-2.061) [1.100000e+00] (423.91794452047,-2.341) [1.100000e+00] (422.603906506131,-2.611) [1.200000e+00] (421.437942262887,-2.879) [1.200000e+00] (420.039710992459,-3.129) [1.300000e+00] (418.866951765254,-3.384) [1.400000e+00] (417.506262475924,-3.65) [1.400000e+00] (416.27417696535,-3.909) [1.500000e+00] (414.786499019738,-4.183) [1.600000e+00] (413.449907053332,-4.418) [1.700000e+00] (411.87208275713,-4.638) [1.900000e+00] (410.711371532222,-4.879) [2.300000e+00] (409.558925075052,-5.088) [2.600000e+00] (408.143464651823,-5.339) [3.100000e+00] (406.213105668329,-5.576) [3.500000e+00] (404.934368453107,-5.82) [4] (403.509798706878,-6.026) [4.500000e+00] (402.231832488814,-6.248) [4.700000e+00] (400.939648408512,-6.508) [5.200000e+00] (399.8000218685,-6.782) [5.600000e+00] (398.428897091865,-7.009) [6.100000e+00] (397.144207670668,-7.19) [6.400000e+00] (395.809926976744,-7.373) [6.500000e+00] (394.264390812682,-7.487) [6.500000e+00] (392.887242049321,-7.659) [6.400000e+00] (391.595057539338,-7.824) [6.400000e+00] (389.945084922732,-7.994) [6.200000e+00] (388.619768242425,-8.137) [6] (387.257607478938,-8.319) [5.800000e+00] (386.070628670456,-8.481) [5.600000e+00] (384.63709276194,-8.642) [5.500000e+00] (383.298256547178,-8.788) [5.400000e+00] (381.759442296891,-8.932) [5.200000e+00] (380.392028114153,-9.128) [5.100000e+00] (378.620245872335,-9.316) [5] (377.146853672631,-9.45) [4.800000e+00] (375.758425755201,-9.586) [4.600000e+00] (374.431636654369,-9.812) [4.500000e+00] (373.026749634537,-9.992) [4.200000e+00] (371.633767944389,-10.181) [4] (370.147556344525,-10.372) [3.900000e+00] (368.772645754694,-10.537) [3.800000e+00] (367.419520384683,-10.72) [3.800000e+00] (365.718340112779,-10.891) [3.700000e+00] (364.53731402696,-11.024) [3.500000e+00] (363.142860804626,-11.194) [3.400000e+00] (361.837854716421,-11.343) [3.200000e+00] (360.308845968063,-11.465) [3.100000e+00] (358.891067337667,-11.541) [3.100000e+00] (357.468805826649,-11.64) [3] (356.081846833763,-11.805) [3.100000e+00] (354.687393640509,-12.03) [3.100000e+00] (353.56436406112,-12.177) [2.900000e+00] (352.092439955415,-12.367) [2.800000e+00] (350.815941430591,-12.459) [2.700000e+00] (349.210231907574,-12.532) [2.600000e+00] (347.835320487121,-12.681) [2.500000e+00] (346.313734675275,-12.842) [2.400000e+00] (344.722313476962,-12.962) [2.400000e+00] (343.578129296234,-13.139) [2.400000e+00] (342.343797417454,-13.309) [2.400000e+00] (341.160528831294,-13.438) [2.300000e+00] (339.802917084292,-13.576) [2.200000e+00] (338.470872415071,-13.772) [2.100000e+00] (337.123067430278,-13.946) [2] (335.963122504192,-14.113) [1.900000e+00] (334.516833731827,-14.28) [2] (333.135967010073,-14.407) [1.900000e+00] (331.800138705769,-14.518) [1.900000e+00] (330.585278625369,-14.621) [1.900000e+00] (328.944333951,-14.743) [1.900000e+00] (327.462672256065,-14.817) [2] (325.863053656869,-14.956) [1.900000e+00] (324.267147858687,-15.048) [1.800000e+00] (322.789267162244,-15.187) [1.800000e+00] (321.547368901744,-15.314) [1.900000e+00] (320.434774066272,-15.475) [1.900000e+00] (318.941063968179,-15.593) [1.900000e+00] (317.374505816666,-15.746) [1.800000e+00] (315.678644240174,-15.888) [1.800000e+00] (314.236836199551,-16.018) [1.700000e+00] (313.025055694277,-16.127) [1.700000e+00] (311.47194713154,-16.285) [1.600000e+00] (309.951197964876,-16.378) [1.600000e+00] (308.346255112257,-16.52) [1.600000e+00] (307.066041265706,-16.728) [1.600000e+00] (305.757950015311,-16.904) [1.500000e+00] (304.228166000962,-17.04) [1.400000e+00] (302.837420393518,-17.21) [1.500000e+00] (301.38888694296,-17.305) [1.500000e+00] (300.125972740781,-17.421) [1.400000e+00] (298.885545669475,-17.498) [1.400000e+00] (297.497812299326,-17.64) [1.400000e+00] (296.186777955744,-17.75) [1.400000e+00] (295.077193179508,-17.95) [1.400000e+00] (293.818061323182,-18.021) [1.300000e+00] (292.831688676552,-18.15) [1.400000e+00] (291.631116119339,-18.135) [1.500000e+00] (290.767321429905,-18.024) [1.600000e+00] (289.851691562145,-17.851) [1.500000e+00] (288.879675867614,-17.737) [1.500000e+00] (287.788162191773,-17.6) [1.500000e+00] (286.795130956376,-17.523) [1.500000e+00] (285.551827183263,-17.406) [1.500000e+00] (284.290452797649,-17.276) [1.500000e+00] (282.823845639159,-17.113) [1.600000e+00] (281.499290901627,-16.954) [1.500000e+00] (280.021405878581,-16.781) [1.500000e+00] (278.72767166716,-16.576) [1.500000e+00] (277.142268008781,-16.423) [1.500000e+00] (275.607996729204,-16.27) [1.500000e+00] (274.272934235597,-16.157) [1.500000e+00] (272.625255381976,-15.987) [1.500000e+00] (271.167749090406,-15.859) [1.600000e+00] (269.557615771968,-15.682) [1.600000e+00] (268.169177453186,-15.495) [1.500000e+00] (267.007054756922,-15.455) [1.500000e+00] (266.115383180306,-15.444) [1.500000e+00] (265.284515238342,-15.483) [1.400000e+00] (264.289942954844,-15.486) [1.400000e+00] (263.362968860198,-15.512) [1.500000e+00] (262.368396576777,-15.477) [1.500000e+00] (261.624099037979,-15.475) [1.600000e+00] (260.974571138378,-15.504) [1.600000e+00] (260.234825136624,-15.507) [1.700000e+00] (259.516929398633,-15.546) [1.700000e+00] (258.667489942075,-15.551) [1.700000e+00] (257.718797047891,-15.541) [1.700000e+00] (256.513805422619,-15.453) [1.700000e+00] (255.238842044868,-15.289) [1.700000e+00] (253.892500397529,-15.069) [1.700000e+00] (252.540905301887,-14.791) [1.800000e+00] (251.135934381069,-14.547) [1.800000e+00] (249.629469270326,-14.262) [1.700000e+00] (248.307154512368,-14.009) [1.800000e+00] (247.062306625014,-13.859) [1.800000e+00] (245.870064483537,-13.79) [1.800000e+00] (244.640275918067,-13.678) [1.900000e+00] (243.466872720712,-13.62) [1.800000e+00] (242.302504399783,-13.493) [1.800000e+00] (241.107250050036,-13.362) [1.900000e+00] (240.115622294194,-13.256) [1.900000e+00] (239.07145656035,-13.162) [1.900000e+00] (237.810011427514,-13.081) [2] (236.76731771346,-12.946) [2] (235.572062933929,-12.859) [2] (234.058166030276,-12.752) [2.100000e+00] (232.803513215808,-12.602) [2.200000e+00] (231.524832652155,-12.382) [2.400000e+00] (230.312276909916,-12.242) [2.500000e+00] (228.961382465307,-12.025) [2.500000e+00] (227.440625992459,-11.781) [2.600000e+00] (225.910834642978,-11.517) [2.600000e+00] (224.328437147144,-11.306) [2.700000e+00] (222.966265726449,-11.074) [2.900000e+00] (221.624405728609,-10.955) [2.900000e+00] (220.277291393918,-10.845) [3] (219.176034396724,-10.817) [3.200000e+00] (217.876271471216,-10.759) [3.300000e+00] (216.625397907096,-10.632) [3.400000e+00] (215.474481010066,-10.524) [3.600000e+00] (214.282940866645,-10.368) [3.900000e+00] (212.944860519937,-10.21) [4.100000e+00] (211.566222000067,-10.085) [4.500000e+00] (210.420559010051,-9.937) [4.800000e+00] (209.215497984919,-9.768) [5.200000e+00] (208.040487836099,-9.618) [5.900000e+00] (206.379213886203,-9.469) [6.300000e+00] (205.008775090025,-9.312) [6.700000e+00] (203.713495991791,-9.097) [7] (202.159674285664,-8.827) [7.200000e+00] (201.018496441257,-8.636) [7.300000e+00] (199.746540973915,-8.446) [7.500000e+00] (198.303952481099,-8.305) [7.900000e+00] (196.941075223403,-8.194) [7.800000e+00] (195.637530038682,-8.056) [7.700000e+00] (194.636163375407,-7.879) [7.600000e+00] (193.422195413169,-7.748) [7.300000e+00] (192.200538519048,-7.601) [7] (190.756347918267,-7.416) [6.700000e+00] (189.429479590574,-7.281) [6.500000e+00] (188.240244012092,-7.165) [6.200000e+00] (187.114956199569,-7.004) [6] (185.752076734914,-6.85) [5.700000e+00] (184.34408844842,-6.649) [5.400000e+00] (182.866899406683,-6.41) [5] (181.335629962636,-6.237) [4.800000e+00] (179.841203225041,-6.022) [4.400000e+00] (178.464803796198,-5.851) [4.200000e+00] (177.109421255634,-5.659) [4] (175.454870195167,-5.414) [3.800000e+00] (173.674795848668,-5.182) [3.600000e+00] (171.965332357637,-4.993) [3.400000e+00] (170.288226915292,-4.724) [3.200000e+00] (168.632138361122,-4.528) [3] (166.890380117385,-4.347) [2.900000e+00] (165.223781571413,-4.123) [2.700000e+00] (163.664702090405,-3.934) [2.600000e+00] (162.044750347582,-3.72) [2.400000e+00] (160.566853662593,-3.461) [2.200000e+00] (159.021292856571,-3.226) [2.100000e+00] (157.400571463901,-2.964) [2] (155.943754504227,-2.722) [2] (154.368910264961,-2.511) [2] (152.584284927235,-2.268) [2] (150.923708189979,-2.007) [1.900000e+00] (149.460804894204,-1.76) [1.700000e+00] (147.84309307329,-1.507) [1.700000e+00] (146.244924802141,-1.238) [1.500000e+00] (144.900815770371,-1.004) [1.600000e+00] (143.470269634734,-0.819) [1.600000e+00] (141.974301936405,-0.758) [1.500000e+00] (140.533951733203,-0.813) [1.500000e+00] (139.065024938698,-0.907) [1.400000e+00] (137.659980837027,-0.95) [1.400000e+00] (136.259484689078,-1.016) [1.400000e+00] (134.810100097212,-1.159) [1.300000e+00] (133.352449848955,-1.397) [1.300000e+00] (132.065432597066,-1.666) [1.200000e+00] (130.707802712561,-1.954) [1.200000e+00] (129.47492781155,-2.229) [1.100000e+00] (128.01958207023,-2.481) [1.200000e+00] (126.909988785689,-2.77) [1.200000e+00] (125.711714491731,-3.053) [1.200000e+00] (124.473584824369,-3.305) [1.300000e+00] (123.188103776746,-3.56) [1.400000e+00] (121.783120764148,-3.843) [1.500000e+00] (120.439010013312,-4.074) [1.600000e+00] (119.167817290445,-4.314) [1.800000e+00] (118.014589468897,-4.555) [2] (116.73359445556,-4.806) [2.200000e+00] (115.336876669515,-5.006) [2.500000e+00] (114.089006230463,-5.247) [2.900000e+00] (112.845621366624,-5.501) [3.200000e+00] (111.442112638754,-5.695) [3.700000e+00] (110.116776246778,-5.903) [4.300000e+00] (108.766641997032,-6.131) [4.700000e+00] (107.363900253314,-6.301) [5] (105.871709197718,-6.442) [5.300000e+00] (104.399829536001,-6.645) [5.900000e+00] (103.164710357685,-6.891) [6.200000e+00] (101.764211631149,-7.088) [6.500000e+00] (100.452455403654,-7.248) [6.900000e+00] (99.1256434665944,-7.419) [6.800000e+00] (97.8138262082112,-7.572) [6.900000e+00] (96.4456837531614,-7.747) [6.800000e+00] (95.0910621799263,-7.904) [6.700000e+00] (93.8258894888612,-8.108) [6.600000e+00] (92.4712674857886,-8.265) [6.500000e+00] (91.1993042826323,-8.413) [6.300000e+00] (89.8108500040459,-8.586) [6.200000e+00] (88.4675045472981,-8.778) [6] (87.2233505504801,-8.882) [5.900000e+00] (85.9964957392214,-9.078) [5.600000e+00] (84.5538977914222,-9.213) [5.500000e+00] (82.9722548164121,-9.334) [5.300000e+00] (81.6845268547643,-9.468) [5.200000e+00] (80.2584611374513,-9.613) [5] (78.8421963632209,-9.803) [4.900000e+00] (77.4747594605468,-9.955) [4.700000e+00] (76.0201768357193,-10.138) [4.600000e+00] (74.4649253703916,-10.29) [4.400000e+00] (73.0658395257547,-10.487) [4.300000e+00] (72.0216639070358,-10.694) [4.200000e+00] (70.9030332254584,-10.903) [4.100000e+00] (69.6167808958216,-11.103) [4] (68.3109841567949,-11.223) [3.900000e+00] (66.8631301533118,-11.33) [3.800000e+00] (65.4543627619866,-11.421) [3.700000e+00] (64.0959585290907,-11.544) [3.500000e+00] (62.7428099801227,-11.67) [3.400000e+00] (61.499422137068,-11.78) [3.300000e+00] (60.0959086527029,-11.931) [3.100000e+00] (58.7314822392054,-12.087) [3] (57.4038976438461,-12.225) [3] (56.0259503486373,-12.377) [2.900000e+00] (54.5811059167043,-12.505) [2.800000e+00] (53.3647589774474,-12.611) [2.700000e+00] (51.9417028894792,-12.698) [2.600000e+00] (50.5945747730972,-12.829) [2.600000e+00] (49.2136152988279,-12.976) [2.500000e+00] (47.7905574337383,-13.137) [2.400000e+00] (46.4434302349562,-13.28) [2.200000e+00] (45.2263154517417,-13.464) [2.100000e+00] (43.9813901439844,-13.587) [2] (42.7237127157393,-13.721) [2] (41.2721370546646,-13.854) [2] (39.9024541265132,-13.976) [1.900000e+00] (38.4576088640612,-14.069) [1.800000e+00] (37.0571054390084,-14.173) [1.800000e+00] (35.595727516336,-14.264) [1.800000e+00] (34.1794588741853,-14.401) [1.700000e+00] (32.8030437995526,-14.528) [1.800000e+00] (31.4867349197922,-14.672) [1.700000e+00] (30.2493666784941,-14.846) [1.800000e+00] (28.8631506897011,-14.954) [1.700000e+00] (27.5378083096434,-15.088) [1.600000e+00] (26.0328551041201,-15.203) [1.700000e+00] (24.6022977364807,-15.333) [1.600000e+00] (23.2303696133712,-15.447) [1.600000e+00] (21.8215983541257,-15.571) [1.500000e+00] (20.4962555443606,-15.687) [1.600000e+00] (19.0717190389646,-15.846) [1.500000e+00] (17.706521773341,-15.959) [1.500000e+00] (16.3338258065844,-16.087) [1.400000e+00] (14.8694353038863,-16.235) [1.500000e+00] (13.476428402087,-16.436) [1.400000e+00] (11.8399253450121,-16.599) [1.300000e+00] (10.4807502888891,-16.697) [1.300000e+00] (9.08927689692154,-16.787) [1.200000e+00] (7.78347631897693,-16.917) [1.200000e+00] (5.9876150635571,-17.024) [1.200000e+00] (4.93215682376435,-17.209) [1.200000e+00] (3.75188262730727,-17.434) [1.200000e+00] };

\end{axis}
\end{tikzpicture}%

### 2013-03-18 msthpres.tex
First few pages of motivation

% $Header: /Users/joseph/Documents/LaTeX/beamer/solutions/conference-talks/conference-ornate-20min.en.tex,v 90e850259b8b 2007/01/28 20:48:30 tantau $

\documentclass[10pt]{beamer}

% This file is a solution template for:

% - Talk at a conference/colloquium.
% - Talk length is about 20min.
% - Style is ornate.

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\usetheme{Boadilla}
\usecolortheme{seahorse}

%\setbeamercovered{transparent}

\setbeamertemplate{section in toc}{$\circ$ \inserttocsection}
\setbeamertemplate{itemize item}{\scriptsize\raise1.25pt\hbox{\donotcoloroutermaths$\blacktriangleright$}}
\setbeamertemplate{itemize subitem}{\tiny\raise1.5pt\hbox{\donotcoloroutermaths$\blacktriangleright$}}
\setbeamertemplate{itemize subsubitem}{\tiny\raise1.5pt\hbox{\donotcoloroutermaths$\blacktriangleright$}}
\setbeamertemplate{enumerate item}{\insertenumlabel.}
\setbeamertemplate{enumerate subitem}{\insertenumlabel.\insertsubenumlabel}
\setbeamertemplate{enumerate subsubitem}{\insertenumlabel.\insertsubenumlabel.\insertsubsubenumlabel}
\setbeamertemplate{enumerate mini template}{\insertenumlabel}

\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{libertine}
\usepackage[T1]{fontenc}

\newcommand{\qauth}[1]{{\footnotesize\par\normalfont\hfill---\ \emph{#1}\par}}

\title[Active Learning for Level Set Estimation]
{Active Learning for Level Set Estimation}

\author[Alkis Gkotovos]{
\footnotesize
M.Sc. Thesis by Alkis Gkotovos\\
Department of Computer Science\\
ETH Zurich
}

\date[M.Sc. Thesis presentation]{
\footnotesize
Supervised by Prof. Andreas Krause

}

%\subject{Theoretical Computer Science}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>{Outline}
%    \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

\section{Motivation and Background}

\begin{frame}
\begin{center}
Swimmers of Lake Zurich, beware!
\vspace{0.2in}
\begin{columns}[c]
\column{0.4\textwidth}
\minipage[c][0.75\textheight][s]{\columnwidth}
\includegraphics[width=1.7in]{figures/pr.jpeg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}\\
\vfill
\includegraphics[width=1.7in]{figures/bloom.jpg}\\[-0.5em]
{\tiny (Source: Flickr/Dr. Jennifer L. Graham/U.S. Geological Survey)}
\endminipage

\column{0.6\textwidth}
\minipage[c][0.75\textheight][s]{\columnwidth}
{\small
``The warming waters of one of central Europe's most popular holiday
destinations, Switzerland's Lake Zurich, have created an ideal environment
for a population explosion of algae including \emph{Planktothrix rubescens},
[...]''
\qauth{Scientific American}
\vfill

``\emph{Planktotrhix rubescens} can account for half of the total
phytoplankton biomass in Lake Zurich in summer [...]''
\vfill

``\emph{Planktotrhix rubescens} are among the most important
producers of hepatotoxic microcystins in freshwaters [...]''
\qauth{Silke Van den Wyngaert \emph{et al.}, ASLO, 2011}
\vfill

``Microcystins [...] are cyanotoxins and can be very toxic for plants and
animals including humans.
Their hepatotoxicity may cause serious damage to the liver.''}
\qauth{Wikipedia}
\endminipage
\end{columns}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=2in]{figures/manual.jpg}\\
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4in]{figures/boat.jpg}\\
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4in]{figures/lake.png}\\
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4.7in]{figures/limno_bgape_sc}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4.7in]{figures/limno_bgape}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4.7in]{figures/limno_bgape_ls}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\hspace{-2em}\includegraphics[width=4.45in]{figures/limno_bgape_cl}
\end{center}
\end{frame}

\section{The LSE algorithm}

\begin{frame}
\begin{enumerate}
\item bla
\end{enumerate}
\end{frame}

\section{Extensions}

\begin{frame}
\begin{enumerate}
\item bla
\end{enumerate}
\end{frame}

\section{Results}

\begin{frame}
\begin{enumerate}
\item bla
\end{enumerate}
\end{frame}

\section*{Conclusion}

\begin{frame}
\begin{enumerate}
\item bla
\end{enumerate}
\end{frame}

%\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
%  % - A title should summarize the slide in an understandable fashion
%  %   for anyone how does not follow everything on the slide itself.
%
%  \begin{itemize}
%  \item
%    Use \texttt{itemize} a lot.
%  \item
%    Use very short sentences or short phrases.
%  \end{itemize}
%\end{frame}
%
%\begin{frame}{Make Titles Informative.}
%
%  You can create overlays\dots
%  \begin{itemize}
%  \item using the \texttt{pause} command:
%    \begin{itemize}
%    \item
%      First item.
%      \pause
%    \item    
%      Second item.
%    \end{itemize}
%  \item
%    using overlay specifications:
%    \begin{itemize}
%    \item<3->
%      First item.
%    \item<4->
%      Second item.
%    \end{itemize}
%  \item
%    using the general \texttt{uncover} command:
%    \begin{itemize}
%      \uncover<5->{\item
%        First item.}
%      \uncover<6->{\item
%        Second item.}
%    \end{itemize}
%  \end{itemize}
%\end{frame}

%\begin{frame}{Summary}
%
%  % Keep the summary *very short*.
%  \begin{itemize}
%  \item
%    The \alert{first main message} of your talk in one or two lines.
%  \item
%    The \alert{second main message} of your talk in one or two lines.
%  \item
%    Perhaps a \alert{third message}, but not more than that.
%  \end{itemize}
%  
%  % The following outlook is optional.
%  \vskip0pt plus.5fill
%  \begin{itemize}
%  \item
%    Outlook
%    \begin{itemize}
%    \item
%      Something you haven't solved.
%    \item
%      Something else you haven't solved.
%    \end{itemize}
%  \end{itemize}
%\end{frame}

\end{document}

### 2013-03-18 msthpres.tex
Extra intro figure; timings; add general problem statement

@@
-% $Header: /Users/joseph/Documents/LaTeX/beamer/solutions/conference-talks/conference-ornate-20min.en.tex,v 90e850259b8b 2007/01/28 20:48:30 tantau $
-
 \documentclass[10pt]{beamer}
-
-% This file is a solution template for:
-
-% - Talk at a conference/colloquium.
-% - Talk length is about 20min.
-% - Style is ornate.
-
-% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
-%
-% In principle, this file can be redistributed and/or modified under
-% the terms of the GNU Public License, version 2.
-%
-% However, this file is supposed to be a template to be modified
-% for your own needs. For this reason, if you use this file as a
-% template and not specifically distribute it as part of a another
-% package/program, I grant the extra permission to freely copy and
-% modify this file as you see fit and even to delete this copyright
-% notice.
 
@@
 
-% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
-% \logo{\pgfuseimage{university-logo}}
-
-% Delete this, if you do not want the table of contents to pop up at
-% the beginning of each subsection:
-%\AtBeginSubsection[]
-%{
-%  \begin{frame}<beamer>{Outline}
-%    \tableofcontents[currentsection,currentsubsection]
-%  \end{frame}
-%}
+%\pgfdeclareimage[height=0.5cm]{university-logo}{figures/eth_logo_black.pdf}
+%\logo{\pgfuseimage{university-logo}}
 
@@
 % the following command: 
-
 %\beamerdefaultoverlayspecification{<+->}
@@
 \begin{center}
-Swimmers of Lake Zurich, beware!
+Swimmers of Lake Zurich, beware!\\
+\vspace{0.2in}
+\includegraphics[width=4in]{figures/swimmers.jpg}\\[-0.5em]
+{\tiny (Source: Steffen Schmidt / EPA)}
+\end{center}
+\end{frame}
+
+\begin{frame}
+\begin{center}
+\uncover<1->{Swimmers of Lake Zurich, beware!}
 \vspace{0.2in}
@@
 \column{0.4\textwidth}
+\uncover<1->{
 \minipage[c][0.75\textheight][s]{\columnwidth}
@@
 \endminipage
+}
 
@@
 \minipage[c][0.75\textheight][s]{\columnwidth}
-{\small
+\uncover<1->{
+\small
 ``The warming waters of one of central Europe's most popular holiday
@@
 \qauth{Scientific American}
+}
 \vfill
-
+\uncover<2->{
+\small
 ``\emph{Planktotrhix rubescens} can account for half of the total
 phytoplankton biomass in Lake Zurich in summer [...]''
-\vfill
+\vspace{1em}
 
@@
 \qauth{Silke Van den Wyngaert \emph{et al.}, ASLO, 2011}
+}
 \vfill
-
+\uncover<3->{
+\small
 ``Microcystins [...] are cyanotoxins and can be very toxic for plants and
 animals including humans.
-Their hepatotoxicity may cause serious damage to the liver.''}
+Their hepatotoxicity may cause serious damage to the liver.''
 \qauth{Wikipedia}
+}
 \endminipage
@@
 \vspace{0.2in}
-\includegraphics[width=2in]{figures/manual.jpg}\\
+\includegraphics[width=2in]{figures/manual.jpg}\\[-0.5em]
 {\tiny (Source: www.limnobotics.ch)}
@@
 \vspace{0.2in}
-\includegraphics[width=4in]{figures/boat.jpg}\\
+\includegraphics[width=4in]{figures/boat.jpg}\\[-0.5em]
 {\tiny (Source: www.limnobotics.ch)}
@@
 \vspace{0.2in}
-\includegraphics[width=4in]{figures/lake.png}\\
+\includegraphics[width=4in]{figures/lake.png}\\[-0.5em]
 {\tiny (Source: www.limnobotics.ch)}
@@
 \hspace{-2em}\includegraphics[width=4.45in]{figures/limno_bgape_cl}
+\end{center}
+\end{frame}
+
+\begin{frame}
+\begin{itemize}
+\item<1-> Pose as a sequential decision making problem (\emph{pool-based active learning}):
+\begin{itemize}
+\item<2-> No measurements available in advance, just a set (pool) of possible sampling locations ($D$)
+\vspace{0.5em}
+\item<3->[]\hspace{-1.5em} At each iteration $t \geq 1$:
+\item<3-> Decide where to measure next ($x_t$)
+\item<4-> Obtain noisy observation ($y_t = f(x_t) + n_t$)
+\item<5-> Update our estimate of the underlying function (e.g. algae concentration)
+\end{itemize}
+\end{itemize}
+\begin{center}
+\color{white}
+\includegraphics<1>[draft,width=4.45in]{figures/oned_0}
+\color{black}
+\includegraphics<2>[width=4.45in]{figures/oned_0}
+\includegraphics<3>[width=4.45in]{figures/oned_1_0}
+\includegraphics<4>[width=4.45in]{figures/oned_1_1}
+\includegraphics<5>[width=4.45in]{figures/oned_1_2}
+\includegraphics<6>[width=4.45in]{figures/oned_2_0}
+\includegraphics<7>[width=4.45in]{figures/oned_2_1}
+\includegraphics<8>[width=4.45in]{figures/oned_2_2}
+\end{center}
+\end{frame}
+
+\begin{frame}
+\begin{enumerate}
+\item<1-> How do we \textbf{model} the function?
+\vspace{1em}
+\item<2-> How do we \textbf{classify}?
+\vspace{1em}
+\item<3-> Each measurement is expensive (time, battery power).\\
+      How do we \textbf{select} ``informative'' measurements?
+\end{enumerate}
+\vspace{2em}
+\begin{center}
+\uncover<4->{\large
+Gaussian processes to the rescue!
+}
 \end{center}

### 2013-03-19 figurefactory/files/voned_0.tex
GP explanation and intro to LSE

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
% 
\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

\addplot [fill=olive!20!lightgray,draw=none,forget plot] coordinates{ (0,3)(0.01,3)(0.02,3)(0.03,3)(0.04,3)(0.05,3)(0.06,3)(0.07,3)(0.08,3)(0.09,3)(0.1,3)(0.11,3)(0.12,3)(0.13,3)(0.14,3)(0.15,3)(0.16,3)(0.17,3)(0.18,3)(0.19,3)(0.2,3)(0.21,3)(0.22,3)(0.23,3)(0.24,3)(0.25,3)(0.26,3)(0.27,3)(0.28,3)(0.29,3)(0.3,3)(0.31,3)(0.32,3)(0.33,3)(0.34,3)(0.35,3)(0.36,3)(0.37,3)(0.38,3)(0.39,3)(0.4,3)(0.41,3)(0.42,3)(0.43,3)(0.44,3)(0.45,3)(0.46,3)(0.47,3)(0.48,3)(0.49,3)(0.5,3)(0.51,3)(0.52,3)(0.53,3)(0.54,3)(0.55,3)(0.56,3)(0.57,3)(0.58,3)(0.59,3)(0.6,3)(0.61,3)(0.62,3)(0.63,3)(0.64,3)(0.65,3)(0.66,3)(0.67,3)(0.68,3)(0.69,3)(0.7,3)(0.71,3)(0.72,3)(0.73,3)(0.74,3)(0.75,3)(0.76,3)(0.77,3)(0.78,3)(0.79,3)(0.8,3)(0.81,3)(0.82,3)(0.83,3)(0.84,3)(0.85,3)(0.86,3)(0.87,3)(0.88,3)(0.89,3)(0.9,3)(0.91,3)(0.92,3)(0.93,3)(0.94,3)(0.95,3)(0.96,3)(0.97,3)(0.98,3)(0.99,3)(1,3)(1.01,3)(1.02,3)(1.03,3)(1.04,3)(1.05,3)(1.06,3)(1.07,3)(1.08,3)(1.09,3)(1.1,3)(1.11,3)(1.12,3)(1.13,3)(1.14,3)(1.15,3)(1.16,3)(1.17,3)(1.18,3)(1.19,3)(1.2,3)(1.21,3)(1.22,3)(1.23,3)(1.24,3)(1.25,3)(1.26,3)(1.27,3)(1.28,3)(1.29,3)(1.3,3)(1.31,3)(1.32,3)(1.33,3)(1.34,3)(1.35,3)(1.36,3)(1.37,3)(1.38,3)(1.39,3)(1.4,3)(1.41,3)(1.42,3)(1.43,3)(1.44,3)(1.45,3)(1.46,3)(1.47,3)(1.48,3)(1.49,3)(1.5,3)(1.51,3)(1.52,3)(1.53,3)(1.54,3)(1.55,3)(1.56,3)(1.57,3)(1.58,3)(1.59,3)(1.6,3)(1.61,3)(1.62,3)(1.63,3)(1.64,3)(1.65,3)(1.66,3)(1.67,3)(1.68,3)(1.69,3)(1.7,3)(1.71,3)(1.72,3)(1.73,3)(1.74,3)(1.75,3)(1.76,3)(1.77,3)(1.78,3)(1.79,3)(1.8,3)(1.81,3)(1.82,3)(1.83,3)(1.84,3)(1.85,3)(1.86,3)(1.87,3)(1.88,3)(1.89,3)(1.9,3)(1.91,3)(1.92,3)(1.93,3)(1.94,3)(1.95,3)(1.96,3)(1.97,3)(1.98,3)(1.99,3)(2,3)(2,-1)(1.99,-1)(1.98,-1)(1.97,-1)(1.96,-1)(1.95,-1)(1.94,-1)(1.93,-1)(1.92,-1)(1.91,-1)(1.9,-1)(1.89,-1)(1.88,-1)(1.87,-1)(1.86,-1)(1.85,-1)(1.84,-1)(1.83,-1)(1.82,-1)(1.81,-1)(1.8,-1)(1.79,-1)(1.78,-1)(1.77,-1)(1.76,-1)(1.75,-1)(1.74,-1)(1.73,-1)(1.72,-1)(1.71,-1)(1.7,-1)(1.69,-1)(1.68,-1)(1.67,-1)(1.66,-1)(1.65,-1)(1.64,-1)(1.63,-1)(1.62,-1)(1.61,-1)(1.6,-1)(1.59,-1)(1.58,-1)(1.57,-1)(1.56,-1)(1.55,-1)(1.54,-1)(1.53,-1)(1.52,-1)(1.51,-1)(1.5,-1)(1.49,-1)(1.48,-1)(1.47,-1)(1.46,-1)(1.45,-1)(1.44,-1)(1.43,-1)(1.42,-1)(1.41,-1)(1.4,-1)(1.39,-1)(1.38,-1)(1.37,-1)(1.36,-1)(1.35,-1)(1.34,-1)(1.33,-1)(1.32,-1)(1.31,-1)(1.3,-1)(1.29,-1)(1.28,-1)(1.27,-1)(1.26,-1)(1.25,-1)(1.24,-1)(1.23,-1)(1.22,-1)(1.21,-1)(1.2,-1)(1.19,-1)(1.18,-1)(1.17,-1)(1.16,-1)(1.15,-1)(1.14,-1)(1.13,-1)(1.12,-1)(1.11,-1)(1.1,-1)(1.09,-1)(1.08,-1)(1.07,-1)(1.06,-1)(1.05,-1)(1.04,-1)(1.03,-1)(1.02,-1)(1.01,-1)(1,-1)(0.99,-1)(0.98,-1)(0.97,-1)(0.96,-1)(0.95,-1)(0.94,-1)(0.93,-1)(0.92,-1)(0.91,-1)(0.9,-1)(0.89,-1)(0.88,-1)(0.87,-1)(0.86,-1)(0.85,-1)(0.84,-1)(0.83,-1)(0.82,-1)(0.81,-1)(0.8,-1)(0.79,-1)(0.78,-1)(0.77,-1)(0.76,-1)(0.75,-1)(0.74,-1)(0.73,-1)(0.72,-1)(0.71,-1)(0.7,-1)(0.69,-1)(0.68,-1)(0.67,-1)(0.66,-1)(0.65,-1)(0.64,-1)(0.63,-1)(0.62,-1)(0.61,-1)(0.6,-1)(0.59,-1)(0.58,-1)(0.57,-1)(0.56,-1)(0.55,-1)(0.54,-1)(0.53,-1)(0.52,-1)(0.51,-1)(0.5,-1)(0.49,-1)(0.48,-1)(0.47,-1)(0.46,-1)(0.45,-1)(0.44,-1)(0.43,-1)(0.42,-1)(0.41,-1)(0.4,-1)(0.39,-1)(0.38,-1)(0.37,-1)(0.36,-1)(0.35,-1)(0.34,-1)(0.33,-1)(0.32,-1)(0.31,-1)(0.3,-1)(0.29,-1)(0.28,-1)(0.27,-1)(0.26,-1)(0.25,-1)(0.24,-1)(0.23,-1)(0.22,-1)(0.21,-1)(0.2,-1)(0.19,-1)(0.18,-1)(0.17,-1)(0.16,-1)(0.15,-1)(0.14,-1)(0.13,-1)(0.12,-1)(0.11,-1)(0.1,-1)(0.09,-1)(0.08,-1)(0.07,-1)(0.06,-1)(0.05,-1)(0.04,-1)(0.03,-1)(0.02,-1)(0.01,-1)(0,-1)};

\addplot [
color=olive!70!black,
solid,
line width=2.0pt,
forget plot
]
coordinates{
(0,1)(2,1)
};

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/voned_1_1.tex
GP explanation and intro to LSE

--- 2013-03-19 figurefactory/files/voned_0.tex
@@
 
+\addplot [
+color=green!60!black,
+densely dotted,
+line width=1.0pt,
+forget plot
+]
+coordinates{
+ (1.5,-2)(1.5,2)
+};
+
+\addplot [
+color=green!60!black,
+only marks,
+mark=*,
+mark size=2.5pt,
+line width=1.0pt,
+forget plot
+]
+coordinates{
+ (1.5,-2)
+};
+
+\addplot [
+color=green!60!black,
+only marks,
+mark=x,
+mark size=3.5pt,
+line width=1.5pt,
+forget plot
+]
+coordinates{
+ (1.5,2)
+};
+
 \end{axis}

### 2013-03-19 figurefactory/files/voned_1_2.tex
GP explanation and intro to LSE

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
% 
\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

\addplot [fill=olive!20!lightgray,draw=none,forget plot] coordinates{ (0,3.00405948968096)(0.01,3.00426406394551)(0.02,3.00447860979409)(0.03,3.00470358994989)(0.04,3.00493948692744)(0.05,3.00518680375087)(0.06,3.00544606468753)(0.07,3.00571781599646)(0.08,3.00600262669061)(0.09,3.00630108931215)(0.1,3.00661382071944)(0.11,3.00694146288451)(0.12,3.00728468369953)(0.13,3.00764417779044)(0.14,3.00802066733599)(0.15,3.00841490288972)(0.16,3.00882766420274)(0.17,3.00925976104432)(0.18,3.00971203401727)(0.19,3.01018535536484)(0.2,3.0106806297652)(0.21,3.01119879510944)(0.22,3.01174082325852)(0.23,3.012307720774)(0.24,3.01290052961726)(0.25,3.01352032781092)(0.26,3.01416823005603)(0.27,3.01484538829772)(0.28,3.01555299223157)(0.29,3.0162922697421)(0.3,3.01706448726417)(0.31,3.01787095005733)(0.32,3.01871300238221)(0.33,3.01959202756734)(0.34,3.0205094479538)(0.35,3.02146672470404)(0.36,3.02246535746042)(0.37,3.02350688383777)(0.38,3.02459287873308)(0.39,3.02572495343459)(0.4,3.02690475451079)(0.41,3.0281339624591)(0.42,3.02941429009222)(0.43,3.03074748063894)(0.44,3.03213530553473)(0.45,3.03357956187592)(0.46,3.03508206950958)(0.47,3.03664466772985)(0.48,3.03826921154973)(0.49,3.0399575675154)(0.5,3.04171160902898)(0.51,3.04353321114326)(0.52,3.04542424479078)(0.53,3.04738657040727)(0.54,3.04942203090831)(0.55,3.0515324439758)(0.56,3.05371959360932)(0.57,3.05598522089594)(0.58,3.05833101394996)(0.59,3.06075859697291)(0.6,3.06326951838249)(0.61,3.06586523795771)(0.62,3.06854711294636)(0.63,3.07131638307979)(0.64,3.07417415443909)(0.65,3.07712138211621)(0.66,3.08015885161281)(0.67,3.08328715891981)(0.68,3.08650668922046)(0.69,3.08981759416052)(0.7,3.09321976762968)(0.71,3.09671281999994)(0.72,3.1002960507682)(0.73,3.10396841955286)(0.74,3.1077285153967)(0.75,3.11157452433218)(0.76,3.11550419516906)(0.77,3.11951480346934)(0.78,3.12360311367997)(0.79,3.12776533940035)(0.8,3.13199710176903)(0.81,3.13629338596207)(0.82,3.14064849580542)(0.83,3.14505600651351)(0.84,3.14950871557854)(0.85,3.1539985918473)(0.86,3.15851672283708)(0.87,3.16305326035778)(0.88,3.16759736452434)(0.89,3.172137146263)(0.9,3.17665960843504)(0.91,3.18115058572431)(0.92,3.18559468345955)(0.93,3.18997521556861)(0.94,3.19427414189104)(0.95,3.19847200510653)(0.96,3.20254786757065)(0.97,3.20647924838623)(0.98,3.21024206107832)(0.99,3.21381055228393)(1,3.21715724191413)(1.01,3.22025286529712)(1.02,3.223066317865)(1.03,3.22556460300701)(1.04,3.22771278377613)(1.05,3.22947393920636)(1.06,3.23080912607447)(1.07,3.23167734702335)(1.08,3.2320355260559)(1.09,3.23183849250862)(1.1,3.23103897472494)(1.11,3.22958760477095)(1.12,3.2274329356729)(1.13,3.22452147280872)(1.14,3.22079772125822)(1.15,3.21620425111303)(1.16,3.210681782972)(1.17,3.20416929610886)(1.18,3.19660416210425)(1.19,3.18792230709721)(1.2,3.17805840624695)(1.21,3.16694611452772)(1.22,3.15451833863763)(1.23,3.14070755562896)(1.24,3.12544618492303)(1.25,3.10866702174)(1.26,3.09030374177493)(1.27,3.07029148935924)(1.28,3.0485675646173)(1.29,3.02507222963895)(1.3,2.99974966000901)(1.31,2.9725490770283)(1.32,2.9434261089661)(1.33,2.91234444879772)(1.34,2.87927790445372)(1.35,2.84421298107019)(1.36,2.80715220205927)(1.37,2.76811848209943)(1.38,2.72716103618234)(1.39,2.68436358948199)(1.4,2.6398561218657)(1.41,2.59383217748261)(1.42,2.54657513623406)(1.43,2.49849917893294)(1.44,2.45021453042913)(1.45,2.40263220045413)(1.46,2.35712849040268)(1.47,2.31577983705733)(1.48,2.28160327978947)(1.49,2.25849531293989)(1.5,2.25023914277021)(1.51,2.25849531293989)(1.52,2.28160327978947)(1.53,2.31577983705733)(1.54,2.35712849040268)(1.55,2.40263220045413)(1.56,2.45021453042913)(1.57,2.49849917893294)(1.58,2.54657513623407)(1.59,2.59383217748261)(1.6,2.6398561218657)(1.61,2.68436358948199)(1.62,2.72716103618234)(1.63,2.76811848209943)(1.64,2.80715220205927)(1.65,2.84421298107019)(1.66,2.87927790445372)(1.67,2.91234444879772)(1.68,2.9434261089661)(1.69,2.97254907702831)(1.7,2.99974966000901)(1.71,3.02507222963895)(1.72,3.0485675646173)(1.73,3.07029148935924)(1.74,3.09030374177493)(1.75,3.10866702174)(1.76,3.12544618492303)(1.77,3.14070755562896)(1.78,3.15451833863763)(1.79,3.16694611452772)(1.8,3.17805840624695)(1.81,3.18792230709721)(1.82,3.19660416210425)(1.83,3.20416929610886)(1.84,3.21068178297201)(1.85,3.21620425111303)(1.86,3.22079772125822)(1.87,3.22452147280872)(1.88,3.2274329356729)(1.89,3.22958760477095)(1.9,3.23103897472494)(1.91,3.23183849250862)(1.92,3.2320355260559)(1.93,3.23167734702335)(1.94,3.23080912607447)(1.95,3.22947393920636)(1.96,3.22771278377613)(1.97,3.22556460300701)(1.98,3.223066317865)(1.99,3.22025286529712)(2,3.21715724191413)(2,-0.547855845922187)(1.99,-0.527263965504428)(1.98,-0.505788009766045)(1.97,-0.483396179083081)(1.96,-0.460056220235874)(1.95,-0.435735499999608)(1.94,-0.410401089005194)(1.93,-0.384019856679305)(1.92,-0.356558578115416)(1.91,-0.327984053773209)(1.9,-0.298263242952087)(1.89,-0.267363412036782)(1.88,-0.235252298570199)(1.87,-0.201898292272354)(1.86,-0.167270634196579)(1.85,-0.131339635298263)(1.84,-0.0940769157910251)(1.83,-0.0554556667863313)(1.82,-0.0154509358624957)(1.81,0.0259600616013633)(1.8,0.068797603246997)(1.79,0.113079090316272)(1.78,0.15881864516803)(1.77,0.206026672346912)(1.76,0.254709379052199)(1.75,0.304868249805843)(1.74,0.356499468669974)(1.73,0.409593280343953)(1.72,0.464133278627427)(1.71,0.52009560669452)(1.7,0.577448047820867)(1.69,0.636148976778726)(1.68,0.696146129733814)(1.67,0.757375132046748)(1.66,0.819757695559522)(1.65,0.883199354305343)(1.64,0.947586541150821)(1.63,1.0127827025836)(1.62,1.07862297889869)(1.61,1.1449066975866)(1.6,1.21138645995895)(1.59,1.27775180583925)(1.58,1.34360407631222)(1.57,1.40841676119969)(1.56,1.47147176728893)(1.55,1.53175640985815)(1.54,1.58780088375249)(1.53,1.63744566984478)(1.52,1.6776036197675)(1.51,1.7043239894427)(1.5,1.71378843730561)(1.49,1.7043239894427)(1.48,1.6776036197675)(1.47,1.63744566984478)(1.46,1.58780088375249)(1.45,1.53175640985815)(1.44,1.47147176728893)(1.43,1.40841676119969)(1.42,1.34360407631223)(1.41,1.27775180583925)(1.4,1.21138645995896)(1.39,1.1449066975866)(1.38,1.07862297889869)(1.37,1.0127827025836)(1.36,0.947586541150821)(1.35,0.883199354305343)(1.34,0.819757695559521)(1.33,0.757375132046748)(1.32,0.696146129733814)(1.31,0.636148976778728)(1.3,0.577448047820867)(1.29,0.520095606694521)(1.28,0.464133278627426)(1.27,0.409593280343953)(1.26,0.356499468669972)(1.25,0.304868249805843)(1.24,0.254709379052201)(1.23,0.206026672346912)(1.22,0.15881864516803)(1.21,0.113079090316273)(1.2,0.0687976032469968)(1.19,0.0259600616013622)(1.18,-0.0154509358624968)(1.17,-0.0554556667863313)(1.16,-0.094076915791024)(1.15,-0.131339635298263)(1.14,-0.167270634196579)(1.13,-0.201898292272354)(1.12,-0.235252298570199)(1.11,-0.267363412036783)(1.1,-0.298263242952087)(1.09,-0.327984053773209)(1.08,-0.356558578115416)(1.07,-0.384019856679306)(1.06,-0.410401089005195)(1.05,-0.435735499999608)(1.04,-0.460056220235874)(1.03,-0.483396179083081)(1.02,-0.505788009766045)(1.01,-0.527263965504428)(1,-0.547855845922187)(0.99,-0.567594932959715)(0.98,-0.58651193556049)(0.97,-0.604636942442146)(0.96,-0.62199938229867)(0.95,-0.638627990816008)(0.94,-0.654550783917867)(0.93,-0.669795036691896)(0.92,-0.684387267478763)(0.91,-0.698353226637922)(0.9,-0.711717889534112)(0.89,-0.724505453317808)(0.88,-0.736739337100937)(0.87,-0.748442185156271)(0.86,-0.759635872794845)(0.85,-0.77034151460069)(0.84,-0.780579474725984)(0.83,-0.790369378972483)(0.82,-0.799730128406764)(0.81,-0.808679914277439)(0.8,-0.817236234022034)(0.79,-0.825415908169748)(0.78,-0.833235097963765)(0.77,-0.840709323543267)(0.76,-0.847853482540755)(0.75,-0.854681868964777)(0.74,-0.861208192251741)(0.73,-0.867445596383093)(0.72,-0.873406678975932)(0.71,-0.879103510265999)(0.7,-0.884547651912082)(0.69,-0.889750175560155)(0.68,-0.894721681114113)(0.67,-0.899472314667793)(0.66,-0.904011786060114)(0.65,-0.908349386021669)(0.64,-0.912494002886998)(0.63,-0.916454138852106)(0.62,-0.92023792576156)(0.61,-0.923853140413804)(0.6,-0.927307219377159)(0.59,-0.930607273312352)(0.58,-0.933760100800408)(0.57,-0.936772201677387)(0.56,-0.939649789879698)(0.55,-0.9423988058057)(0.54,-0.945024928201005)(0.53,-0.9475335855763)(0.52,-0.9499299671677)(0.51,-0.952219033450653)(0.5,-0.954405526219157)(0.49,-0.956493978242716)(0.48,-0.958488722513901)(0.47,-0.960393901099713)(0.46,-0.962213473610178)(0.45,-0.963951225297682)(0.44,-0.965610774800598)(0.43,-0.967195581544668)(0.42,-0.9687089528155)(0.41,-0.970154050515327)(0.4,-0.971533897616946)(0.39,-0.972851384327491)(0.38,-0.974109273974362)(0.37,-0.975310208625306)(0.36,-0.976456714454296)(0.35,-0.977551206864464)(0.34,-0.978595995378974)(0.33,-0.97959328831033)(0.32,-0.980545197218213)(0.31,-0.981453741165549)(0.3,-0.982320850782134)(0.29,-0.983148372144719)(0.28,-0.983938070482126)(0.27,-0.984691633713544)(0.26,-0.985410675827823)(0.25,-0.986096740111221)(0.24,-0.986751302230704)(0.23,-0.987375773179584)(0.22,-0.987971502091947)(0.21,-0.988539778932026)(0.2,-0.989081837064361)(0.19,-0.989598855710323)(0.18,-0.990091962296299)(0.17,-0.990562234698562)(0.16,-0.991010703389634)(0.15,-0.991438353490681)(0.14,-0.991846126734268)(0.13,-0.992234923341592)(0.12,-0.992605603818107)(0.11,-0.992958990671239)(0.1,-0.993295870053748)(0.09,-0.993616993336077)(0.08,-0.993923078610886)(0.07,-0.994214812132822)(0.06,-0.994492849696389)(0.05,-0.994757817954686)(0.04,-0.995010315681626)(0.03,-0.995250914980116)(0.02,-0.995480162438577)(0.01,-0.995698580238063)(0,-0.995906667212118)};

\addplot [
color=olive!70!black,
solid,
line width=2.0pt,
forget plot
]
coordinates{
 (0,1.0040897452219)(0.01,1.00429675075101)(0.02,1.00451394068955)(0.03,1.00474179738852)(0.04,1.00498082483891)(0.05,1.00523154956363)(0.06,1.00549452154094)(0.07,1.00577031516001)(0.08,1.00605953020939)(0.09,1.00636279289909)(0.1,1.00668075691684)(0.11,1.0070141045194)(0.12,1.00736354765928)(0.13,1.00772982914765)(0.14,1.00811372385394)(0.15,1.00851603994254)(0.16,1.00893762014722)(0.17,1.00937934308348)(0.18,1.00984212459929)(0.19,1.01032691916444)(0.2,1.01083472129863)(0.21,1.01136656703844)(0.22,1.01192353544313)(0.23,1.01250675013919)(0.24,1.01311738090328)(0.25,1.01375664528338)(0.26,1.01442581025747)(0.27,1.01512619392907)(0.28,1.01585916725891)(0.29,1.01662615583157)(0.3,1.01742864165593)(0.31,1.01826816499799)(0.32,1.01914632624425)(0.33,1.02006478779388)(0.34,1.0210252759773)(0.35,1.02202958299879)(0.36,1.02307956890017)(0.37,1.02417716354244)(0.38,1.02532436860184)(0.39,1.0265232595763)(0.4,1.02777598779804)(0.41,1.02908478244737)(0.42,1.03045195256247)(0.43,1.03187988903927)(0.44,1.03337106661514)(0.45,1.03492804582929)(0.46,1.03655347495241)(0.47,1.03825009187723)(0.48,1.04002072596113)(0.49,1.04186829981092)(0.5,1.04379583099951)(0.51,1.04580643370286)(0.52,1.04790332024529)(0.53,1.05008980253964)(0.54,1.05236929340842)(0.55,1.05474530777048)(0.56,1.05722146367707)(0.57,1.0598014831797)(0.58,1.06248919301117)(0.59,1.06528852505978)(0.6,1.06820351661536)(0.61,1.07123831036455)(0.62,1.07439715411089)(0.63,1.07768440019436)(0.64,1.08110450458274)(0.65,1.08466202560602)(0.66,1.08836162230311)(0.67,1.0922080523484)(0.68,1.09620616952385)(0.69,1.10036092070029)(0.7,1.10467734228994)(0.71,1.10916055612972)(0.72,1.11381576475312)(0.73,1.11864824600634)(0.74,1.12366334696196)(0.75,1.12886647708148)(0.76,1.13426310057572)(0.77,1.13985872790991)(0.78,1.14565890639797)(0.79,1.15166920982834)(0.8,1.15789522706149)(0.81,1.16434254953709)(0.82,1.17101675762665)(0.83,1.17792340576555)(0.84,1.18506800629633)(0.85,1.19245601195347)(0.86,1.20009279691821)(0.87,1.20798363637049)(0.88,1.21613368446413)(0.89,1.22454795065031)(0.9,1.233231274274)(0.91,1.24218829736773)(0.92,1.2514234355676)(0.93,1.2609408470771)(0.94,1.27074439960581)(0.95,1.28083763521224)(0.96,1.29122373298292)(0.97,1.30190546948369)(0.98,1.31288517692387)(0.99,1.32416469897996)(1,1.33574534423277)(1.01,1.34762783718023)(1.02,1.35981226679868)(1.03,1.37229803263705)(1.04,1.3850837884424)(1.05,1.39816738333153)(1.06,1.41154580054166)(1.07,1.42521509381473)(1.08,1.43917032149395)(1.09,1.45340547843888)(1.1,1.46791342589672)(1.11,1.48268581950264)(1.12,1.49771303562191)(1.13,1.51298409629154)(1.14,1.52848659306892)(1.15,1.54420661015185)(1.16,1.56012864719645)(1.17,1.57623554233018)(1.18,1.59250839593491)(1.19,1.60892649586181)(1.2,1.6254672448364)(1.21,1.64210609091893)(1.22,1.65881646200356)(1.23,1.67556970547131)(1.24,1.69233503425594)(1.25,1.70907948074268)(1.26,1.72576786009534)(1.27,1.74236274480266)(1.28,1.75882445244819)(1.29,1.77511104894428)(1.3,1.79117836972934)(1.31,1.80698006171278)(1.32,1.82246764906407)(1.33,1.83759062628575)(1.34,1.85229658238609)(1.35,1.86653136037919)(1.36,1.88023925679178)(1.37,1.89336326634995)(1.38,1.90584537755949)(1.39,1.91762692548457)(1.4,1.92864900867555)(1.41,1.9388529779019)(1.42,1.94818100511719)(1.43,1.95657674192344)(1.44,1.96398607771993)(1.45,1.97035800872147)(1.46,1.97564563012208)(1.47,1.97980726486781)(1.48,1.98280774379692)(1.49,1.98461985331508)(1.5,1.98522596830673)(1.51,1.98461985331508)(1.52,1.98280774379692)(1.53,1.97980726486781)(1.54,1.97564563012208)(1.55,1.97035800872147)(1.56,1.96398607771993)(1.57,1.95657674192344)(1.58,1.94818100511719)(1.59,1.9388529779019)(1.6,1.92864900867555)(1.61,1.91762692548457)(1.62,1.90584537755949)(1.63,1.89336326634995)(1.64,1.88023925679178)(1.65,1.86653136037919)(1.66,1.85229658238609)(1.67,1.83759062628575)(1.68,1.82246764906407)(1.69,1.80698006171278)(1.7,1.79117836972934)(1.71,1.77511104894428)(1.72,1.75882445244819)(1.73,1.74236274480266)(1.74,1.72576786009534)(1.75,1.70907948074268)(1.76,1.69233503425594)(1.77,1.67556970547131)(1.78,1.65881646200356)(1.79,1.64210609091893)(1.8,1.6254672448364)(1.81,1.60892649586181)(1.82,1.59250839593491)(1.83,1.57623554233018)(1.84,1.56012864719645)(1.85,1.54420661015185)(1.86,1.52848659306892)(1.87,1.51298409629154)(1.88,1.49771303562191)(1.89,1.48268581950264)(1.9,1.46791342589672)(1.91,1.45340547843888)(1.92,1.43917032149395)(1.93,1.42521509381473)(1.94,1.41154580054166)(1.95,1.39816738333153)(1.96,1.3850837884424)(1.97,1.37229803263705)(1.98,1.35981226679868)(1.99,1.34762783718023)(2,1.33574534423277) 
};

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=green!60!black,
densely dotted,
line width=1.0pt,
forget plot
]
coordinates{
 (1.5,-2)(1.5,2)
};

\addplot [
color=green!60!black,
only marks,
mark=*,
mark size=2.5pt,
line width=1.0pt,
forget plot
]
coordinates{
 (1.5,-2)
};

\addplot [
color=green!60!black,
only marks,
mark=x,
mark size=3.5pt,
line width=1.5pt,
forget plot
]
coordinates{
 (1.5,2)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/voned_2_0.tex
GP explanation and intro to LSE

--- 2013-03-19 figurefactory/files/voned_1_2.tex
@@
 color=green!60!black,
-densely dotted,
-line width=1.0pt,
-forget plot
-]
-coordinates{
- (1.5,-2)(1.5,2)
-};
-
-\addplot [
-color=green!60!black,
 only marks,
@@
 coordinates{
- (1.5,-2)
-};
-
-\addplot [
-color=green!60!black,
-only marks,
-mark=x,
-mark size=3.5pt,
-line width=1.5pt,
-forget plot
-]
-coordinates{
- (1.5,2)
+ (0.5,-2)
 };

### 2013-03-19 figurefactory/files/voned_2_2.tex
GP explanation and intro to LSE

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

\addplot [fill=olive!20!lightgray,draw=none,forget plot] coordinates{ (0,3.47503448812459)(0.01,3.48731049975084)(0.02,3.49954194559996)(0.03,3.51169580854478)(0.04,3.52373658736368)(0.05,3.53562620953933)(0.06,3.54732394772005)(0.07,3.5587863408048)(0.08,3.56996712072292)(0.09,3.58081714610148)(0.1,3.59128434414726)(0.11,3.60131366222062)(0.12,3.61084703074508)(0.13,3.61982333928357)(0.14,3.62817842782351)(0.15,3.63584509555128)(0.16,3.64275312967022)(0.17,3.64882935713003)(0.18,3.6539977225008)(0.19,3.658179395654)(0.2,3.66129291342205)(0.21,3.66325436002188)(0.22,3.66397759177629)(0.23,3.66337451259421)(0.24,3.66135540783692)(0.25,3.65782934568775)(0.26,3.65270465707885)(0.27,3.64588950778609)(0.28,3.63729257973882)(0.29,3.62682388328426)(0.3,3.61439572866668)(0.31,3.59992389419638)(0.32,3.58332904183065)(0.33,3.56453845026926)(0.34,3.54348816452895)(0.35,3.5201257047368)(0.36,3.49441354454039)(0.37,3.46633367614049)(0.38,3.43589375027455)(0.39,3.40313556025084)(0.4,3.36814710795555)(0.41,3.33108028520932)(0.42,3.29217756679695)(0.43,3.25181343758871)(0.44,3.21056010648069)(0.45,3.16929264219669)(0.46,3.12935359666131)(0.47,3.09278728032563)(0.48,3.06257850973023)(0.49,3.04258948800252)(0.5,3.03657032527763)(0.51,3.04616393918492)(0.52,3.06971970397476)(0.53,3.10348382437098)(0.54,3.14359463326134)(0.55,3.18707028212863)(0.56,3.23187043785894)(0.57,3.27665683261068)(0.58,3.3205586920134)(0.59,3.36300798850483)(0.6,3.40363425050598)(0.61,3.44219882010877)(0.62,3.47855340793708)(0.63,3.51261338586195)(0.64,3.5443400923476)(0.65,3.57372875283708)(0.66,3.6007999811883)(0.67,3.62559362391807)(0.68,3.64816417797094)(0.69,3.66857729356851)(0.7,3.68690704505127)(0.71,3.70323375925228)(0.72,3.71764225861017)(0.73,3.73022042001256)(0.74,3.74105797922785)(0.75,3.75024553016918)(0.76,3.7578736814865)(0.77,3.76403234220293)(0.78,3.76881011463808)(0.79,3.77229377756097)(0.8,3.7745678459584)(0.81,3.77571419637071)(0.82,3.77581174869288)(0.83,3.7749361968396)(0.84,3.77315978185159)(0.85,3.77055110196015)(0.86,3.76717495489046)(0.87,3.76309220831331)(0.88,3.75835969488208)(0.89,3.75303012873943)(0.9,3.74715204076432)(0.91,3.74076973016611)(0.92,3.73392323033013)(0.93,3.72664828708403)(0.94,3.71897634779377)(0.95,3.71093455991574)(0.96,3.7025457778319)(0.97,3.69382857698031)(0.98,3.68479727446696)(0.99,3.67546195550829)(1,3.66582850520942)(1.01,3.65589864533175)(1.02,3.64566997584782)(1.03,3.63513602122168)(1.04,3.62428628149047)(1.05,3.61310628836048)(1.06,3.60157766666724)(1.07,3.58967820168808)(1.08,3.57738191293649)(1.09,3.56465913521318)(1.1,3.55147660784019)(1.11,3.53779757316361)(1.12,3.52358188557994)(1.13,3.50878613252339)(1.14,3.49336376905008)(1.15,3.47726526787405)(1.16,3.46043828695531)(1.17,3.44282785701784)(1.18,3.42437659169612)(1.19,3.40502492338305)(1.2,3.38471136829835)(1.21,3.36337282483493)(1.22,3.34094490990433)(1.23,3.3173623388315)(1.24,3.29255935540499)(1.25,3.2664702200547)(1.26,3.23902976592618)(1.27,3.21017403502275)(1.28,3.17984100984943)(1.29,3.14797146049419)(1.3,3.11450993339101)(1.31,3.07940591698944)(1.32,3.04261523254619)(1.33,3.0041017173509)(1.34,2.96383929625123)(1.35,2.9218145807794)(1.36,2.8780302024732)(1.37,2.83250919319779)(1.38,2.78530089617875)(1.39,2.73648917180149)(1.4,2.68620413065109)(1.41,2.63463942142347)(1.42,2.58207846429752)(1.43,2.52893534728687)(1.44,2.47581993642005)(1.45,2.42364234178214)(1.46,2.37377683652712)(1.47,2.32829548695259)(1.48,2.29020653454021)(1.49,2.26339149122763)(1.5,2.25161608648422)(1.51,2.2565334667147)(1.52,2.2764929186673)(1.53,2.30772712055712)(1.54,2.34634874201905)(1.55,2.38934128375939)(1.56,2.43462340262617)(1.57,2.48081122987684)(1.58,2.52698503543485)(1.59,2.57252543016284)(1.6,2.61700895300433)(1.61,2.66014298752552)(1.62,2.70172488214706)(1.63,2.74161572983533)(1.64,2.77972309256712)(1.65,2.8159892812743)(1.66,2.85038316427975)(1.67,2.8828942721013)(1.68,2.91352843478383)(1.69,2.94230446819852)(1.7,2.96925159661914)(1.71,2.9944074050817)(1.72,3.01781618231458)(1.73,3.0395275584581)(1.74,3.05959537034055)(1.75,3.07807670617191)(1.76,3.09503109450287)(1.77,3.110519811274)(1.78,3.12460528508395)(1.79,3.13735058530242)(1.8,3.14881898090992)(1.81,3.15907356034207)(1.82,3.16817690440477)(1.83,3.17619080568347)(1.84,3.18317602891506)(1.85,3.1891921076087)(1.86,3.19429717285143)(1.87,3.19854781075901)(1.88,3.20199894546136)(1.89,3.2047037448685)(1.9,3.20671354676306)(1.91,3.20807780302101)(1.92,3.2088440399828)(1.93,3.20905783318921)(1.94,3.20876279486513)(1.95,3.20800057268415)(1.96,3.20681085848069)(1.97,3.20523140569645)(1.98,3.20329805445655)(1.99,3.20104476326931)(2,3.19850364643326)(2,-0.56626896144308)(1.99,-0.5462160000136)(1.98,-0.525283818332375)(1.97,-0.503439715088015)(1.96,-0.480650441382582)(1.95,-0.456882268460431)(1.94,-0.43210106548919)(1.93,-0.406272388206559)(1.92,-0.379361579291655)(1.91,-0.351333881367478)(1.9,-0.32215456359208)(1.89,-0.291789062851237)(1.88,-0.260203140625971)(1.87,-0.227363056675648)(1.86,-0.193235760754053)(1.85,-0.157789103664555)(1.84,-0.120992069065456)(1.83,-0.0828150275636714)(1.82,-0.0432300147913194)(1.81,-0.00221103535694378)(1.8,0.040265605185011)(1.79,0.0842209378749517)(1.78,0.129672934495549)(1.77,0.176636074845227)(1.76,0.225120872878144)(1.75,0.27513335638814)(1.74,0.326674493449472)(1.73,0.379739556789333)(1.72,0.434317414403876)(1.71,0.490389730666115)(1.7,0.547930056345932)(1.69,0.606902777508557)(1.68,0.667261880845712)(1.67,0.728949474529893)(1.66,0.791893975825184)(1.65,0.856007834013682)(1.64,0.921184590745083)(1.63,0.987294974628876)(1.62,1.05418155701083)(1.61,1.12165121668306)(1.6,1.18946419418054)(1.59,1.25731772274879)(1.58,1.3248208621786)(1.57,1.39145483785665)(1.56,1.45650935952315)(1.55,1.51897981458641)(1.54,1.57740530309109)(1.53,1.62963738594122)(1.52,1.67260476553454)(1.51,1.70238028131943)(1.5,1.71517476059299)(1.49,1.70933693899395)(1.48,1.68654270693122)(1.47,1.65060184815967)(1.46,1.60545792902056)(1.45,1.55419624455546)(1.44,1.49897825318704)(1.43,1.44127760590081)(1.42,1.3821117013744)(1.41,1.32220378072731)(1.4,1.26208579512996)(1.39,1.20216212070966)(1.38,1.14274924211746)(1.37,1.08410093677044)(1.36,1.02642466013697)(1.35,0.969892507044983)(1.34,0.914648762446204)(1.33,0.860815261205179)(1.32,0.808495309244627)(1.31,0.757776639115429)(1.3,0.70873370314298)(1.29,0.661429501990403)(1.28,0.615917080011931)(1.27,0.572240776083215)(1.26,0.530437290727531)(1.25,0.490536611882969)(1.24,0.452562829233078)(1.23,0.416534858558752)(1.22,0.38246709172952)(1.21,0.35036998387673)(1.2,0.320250586414766)(1.19,0.29211303252461)(1.18,0.265958980234497)(1.17,0.241788017153657)(1.16,0.219598030119439)(1.15,0.199385542423449)(1.14,0.181146020831719)(1.13,0.164874154266725)(1.12,0.150564105746791)(1.11,0.138209738960353)(1.1,0.127804820674168)(1.09,0.119343200024961)(1.08,0.112818965615813)(1.07,0.108226581225861)(1.06,0.10556100084091)(1.05,0.104817763620081)(1.04,0.105993069327776)(1.03,0.109083834679302)(1.02,0.114087730971477)(1.01,0.121003203295626)(1,0.129829471559083)(0.99,0.140566513472174)(0.98,0.153215029590611)(0.97,0.167776390437933)(0.96,0.184252565669204)(0.95,0.202646035175346)(0.94,0.222959681967449)(0.93,0.245196666621817)(0.92,0.269360283009454)(0.91,0.295453794977895)(0.9,0.323480253598301)(0.89,0.353442294536177)(0.88,0.385341915048931)(0.87,0.419180230056646)(0.86,0.454957206672098)(0.85,0.492671376509548)(0.84,0.532319525015719)(0.83,0.573896356975411)(0.82,0.617394137231257)(0.81,0.662802305512272)(0.8,0.710107064074811)(0.79,0.759290936602772)(0.78,0.810332296463266)(0.77,0.863204861930176)(0.76,0.917877155314581)(0.75,0.974311921997447)(0.74,1.0324655040292)(0.73,1.09228716107302)(0.72,1.15371832877268)(0.71,1.21669180074849)(0.7,1.28113081480325)(0.69,1.34694801569449)(0.68,1.41404425466938)(0.67,1.48230716777235)(0.66,1.55160944738328)(0.65,1.62180667910266)(0.64,1.69273455001136)(0.63,1.76420512943459)(0.62,1.8360017538758)(0.61,1.90787176901693)(0.6,1.97951591498485)(0.59,2.05057234780867)(0.58,2.12059192909028)(0.57,2.18899909122462)(0.56,2.25502875462593)(0.55,2.31762418490194)(0.54,2.37527572575478)(0.53,2.42579018557806)(0.52,2.46605587636579)(0.51,2.49210938695124)(0.5,2.5001289993864)(0.49,2.48843630260724)(0.48,2.45869035659747)(0.47,2.41469754570973)(0.46,2.36041015773334)(0.45,2.2989311730237)(0.44,2.23244606337767)(0.43,2.16245704556852)(0.42,2.09001339354071)(0.41,2.01587257779527)(0.4,1.94060234913175)(0.39,1.86464378940838)(0.38,1.78835042513833)(0.37,1.71201292093404)(0.36,1.63587504271835)(0.35,1.56014425747618)(0.34,1.48499897607437)(0.33,1.41059365269786)(0.32,1.33706248789253)(0.31,1.26452220350642)(0.3,1.19307418839348)(0.29,1.12280620886868)(0.28,1.05379381182811)(0.27,0.986101506117318)(0.26,0.919783780187773)(0.25,0.854885995903985)(0.24,0.79144518621219)(0.23,0.72949077616544)(0.22,0.669045241187887)(0.21,0.61012471259441)(0.2,0.552739537697143)(0.19,0.496894799954984)(0.18,0.442590803304707)(0.17,0.389823523882892)(0.16,0.338585031689705)(0.15,0.288863884278023)(0.14,0.240645494218025)(0.13,0.193912471848914)(0.12,0.14864494465775)(0.11,0.104820854500891)(0.1,0.0624162337921177)(0.09,0.0214054617129871)(0.08,-0.0182384985515351)(0.07,-0.0565438805909741)(0.06,-0.0935399126342655)(0.05,-0.129256631605251)(0.04,-0.163724712499596)(0.03,-0.196975312239681)(0.02,-0.229039927188963)(0.01,-0.259950263532067)(0,-0.289738119751751)};

\addplot [
color=olive!70!black,
solid,
line width=2.0pt,
forget plot
]
coordinates{
 (0,1.59454509563606)(0.01,1.61564433597658)(0.02,1.63728425737121)(0.03,1.65946424845868)(0.04,1.68218240555269)(0.05,1.70543542995183)(0.06,1.72921852101884)(0.07,1.75352526512571)(0.08,1.77834752060356)(0.09,1.8036752988852)(0.1,1.82949664208298)(0.11,1.85579749730685)(0.12,1.88256158809745)(0.13,1.90977028342819)(0.14,1.93740246481817)(0.15,1.96543439219707)(0.16,1.99383956927345)(0.17,2.02258860928123)(0.18,2.05164910211666)(0.19,2.08098548403023)(0.2,2.11055891120819)(0.21,2.14032713876594)(0.22,2.17024440688404)(0.23,2.20026133604814)(0.24,2.23032483360879)(0.25,2.26037801415861)(0.26,2.29036013653446)(0.27,2.32020656059454)(0.28,2.34984872729673)(0.29,2.37921416601959)(0.3,2.40822653352234)(0.31,2.43680568944179)(0.32,2.46486781377326)(0.33,2.49232557238627)(0.34,2.51908833728684)(0.35,2.5450624690635)(0.36,2.57015166974765)(0.37,2.59425741518815)(0.38,2.61727947699051)(0.39,2.63911654511093)(0.4,2.65966696333104)(0.41,2.67882959108098)(0.42,2.69650480643314)(0.43,2.71259566656815)(0.44,2.72700924362848)(0.45,2.73965815563429)(0.46,2.75046231405488)(0.47,2.7593509117187)(0.48,2.76626467702202)(0.49,2.7711584228752)(0.5,2.77400392152397)(0.51,2.77479307537906)(0.52,2.7735398209958)(0.53,2.7702782278499)(0.54,2.76505933023799)(0.55,2.75794825513593)(0.56,2.74902167585604)(0.57,2.73836556033998)(0.58,2.72607318562214)(0.59,2.71224339247685)(0.6,2.6969790565389)(0.61,2.6803857542764)(0.62,2.66257060411225)(0.63,2.64364126474949)(0.64,2.62370507436833)(0.65,2.60286831584075)(0.66,2.58123559446248)(0.67,2.55890931594234)(0.68,2.53598925352349)(0.69,2.51257219414939)(0.7,2.48875165453657)(0.71,2.46461765888356)(0.72,2.44025657073788)(0.73,2.41575097226585)(0.74,2.39117958483002)(0.75,2.36661722538023)(0.76,2.34213479371238)(0.77,2.31779928614789)(0.78,2.29367383164069)(0.79,2.26981774673115)(0.8,2.24628660614135)(0.81,2.22313232614613)(0.82,2.20040325816301)(0.83,2.1781442902837)(0.84,2.15639695472304)(0.85,2.13519953939011)(0.86,2.1145872019932)(0.87,2.09459208527738)(0.88,2.07524343216166)(0.89,2.05656769969487)(0.9,2.03858867088633)(0.91,2.02132756359039)(0.92,2.00480313573499)(0.93,1.98903178628391)(0.94,1.97402765141244)(0.95,1.95980269545653)(0.96,1.94636679626872)(0.97,1.93372782467942)(0.98,1.92189171782199)(0.99,1.91086254613373)(1,1.90064257389451)(1.01,1.89123231320991)(1.02,1.88263057138807)(1.03,1.8748344916985)(1.04,1.86783958753873)(1.05,1.86163977007047)(1.06,1.85622736942201)(1.07,1.85159314958828)(1.08,1.8477263171952)(1.09,1.84461452433064)(1.1,1.84224386568177)(1.11,1.84059887025782)(1.12,1.83966248801905)(1.13,1.83941607177821)(1.14,1.83983935478899)(1.15,1.84091042449025)(1.16,1.84260569293244)(1.17,1.84489986447787)(1.18,1.84776590143712)(1.19,1.85117498838264)(1.2,1.85509649596757)(1.21,1.85949794517392)(1.22,1.86434497302089)(1.23,1.86960130088174)(1.24,1.87522870668825)(1.25,1.88118700244557)(1.26,1.88743401863969)(1.27,1.89392559729533)(1.28,1.90061559563584)(1.29,1.90745590251041)(1.3,1.91439646998892)(1.31,1.92138536278378)(1.32,1.92836882844262)(1.33,1.93529139156831)(1.34,1.9420959756662)(1.35,1.94872405659499)(1.36,1.95511585201063)(1.37,1.96121055164501)(1.38,1.96694659375663)(1.39,1.97226199363248)(1.4,1.97709473061332)(1.41,1.98138320076256)(1.42,1.98506674300701)(1.43,1.98808624735089)(1.44,1.99038485460839)(1.45,1.99190875802053)(1.46,1.99260811812604)(1.47,1.99243810335014)(1.48,1.99136006996721)(1.49,1.98934289639183)(1.5,1.98636448816631)(1.51,1.98241343801314)(1.52,1.97749002123169)(1.53,1.97160519504836)(1.54,1.96477893335906)(1.55,1.95703871663312)(1.56,1.94841819265865)(1.57,1.93895599181062)(1.58,1.92869468193723)(1.59,1.91767984925921)(1.6,1.90595929287052)(1.61,1.89358232152374)(1.62,1.88059914238955)(1.63,1.86706033240106)(1.64,1.85301638364022)(1.65,1.83851731499822)(1.66,1.82361234305209)(1.67,1.80834960575026)(1.68,1.79277593309509)(1.69,1.77693665955524)(1.7,1.76087547343885)(1.71,1.74463429891398)(1.72,1.72825320677865)(1.73,1.71177035046275)(1.74,1.69522192409063)(1.75,1.67864213974918)(1.76,1.66206322139461)(1.77,1.64551541309303)(1.78,1.62902699952919)(1.79,1.61262433693457)(1.8,1.59633189278366)(1.81,1.58017229278628)(1.82,1.56416637386654)(1.83,1.54833324196633)(1.84,1.53269033364492)(1.85,1.51725348056665)(1.86,1.50203697607831)(1.87,1.48705364317591)(1.88,1.47231490324964)(1.89,1.45783084507571)(1.9,1.44361029359572)(1.91,1.42966087808879)(1.92,1.41598909939962)(1.93,1.40260039593744)(1.94,1.38949920820709)(1.95,1.37668904167482)(1.96,1.36417252780801)(1.97,1.35195148316067)(1.98,1.34002696640539)(1.99,1.3283993332378)(2,1.31706828910212) 
};

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=green!60!black,
densely dotted,
line width=1.0pt,
forget plot
]
coordinates{
 (0.5,-2)(0.5,2.8)
};

\addplot [
color=green!60!black,
only marks,
mark=*,
mark size=2.5pt,
line width=1.0pt,
forget plot
]
coordinates{
 (0.5,-2)
};

\addplot [
color=green!60!black,
only marks,
mark=x,
mark size=3.5pt,
line width=1.5pt,
forget plot
]
coordinates{
 (0.5,2.8)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/voned_3_0.tex
GP explanation and intro to LSE

--- 2013-03-19 figurefactory/files/voned_2_2.tex
@@
 % 
-\definecolor{locol}{rgb}{0.26, 0.45, 0.65}
-
 \begin{tikzpicture}
@@
 color=green!60!black,
-densely dotted,
-line width=1.0pt,
-forget plot
-]
-coordinates{
- (0.5,-2)(0.5,2.8)
-};
-
-\addplot [
-color=green!60!black,
 only marks,
@@
 coordinates{
- (0.5,-2)
-};
-
-\addplot [
-color=green!60!black,
-only marks,
-mark=x,
-mark size=3.5pt,
-line width=1.5pt,
-forget plot
-]
-coordinates{
- (0.5,2.8)
+ (1,-2)
 };

### 2013-03-19 figurefactory/files/voned_3_2.tex
GP explanation and intro to LSE

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

\addplot [fill=olive!20!lightgray,draw=none,forget plot] coordinates{ (0,3.58482942463052)(0.01,3.60004798891101)(0.02,3.61522857444221)(0.03,3.63033189586352)(0.04,3.64531565363331)(0.05,3.66013442184805)(0.06,3.67473953961915)(0.07,3.68907900710597)(0.08,3.70309738743443)(0.09,3.71673571587552)(0.1,3.72993141781888)(0.11,3.742618237255)(0.12,3.75472617767874)(0.13,3.76618145754966)(0.14,3.77690648269497)(0.15,3.78681983832409)(0.16,3.79583630364506)(0.17,3.80386689244192)(0.18,3.81081892339735)(0.19,3.81659612444073)(0.2,3.82109877598645)(0.21,3.82422389862386)(0.22,3.82586549166252)(0.23,3.82591482996835)(0.24,3.82426082780994)(0.25,3.82079048005803)(0.26,3.81538939316725)(0.27,3.80794242109654)(0.28,3.79833442495176)(0.29,3.78645118004131)(0.3,3.77218046079061)(0.31,3.7554133434235)(0.32,3.73604577980269)(0.33,3.71398051537493)(0.34,3.68912945302201)(0.35,3.66141660795913)(0.36,3.63078186508568)(0.37,3.59718585332289)(0.38,3.56061641480533)(0.39,3.52109740977021)(0.4,3.47870102745279)(0.41,3.43356548123227)(0.42,3.3859211324836)(0.43,3.33612996677294)(0.44,3.28474615977828)(0.45,3.23260879787809)(0.46,3.18097820535255)(0.47,3.13171088766885)(0.48,3.08739598582499)(0.49,3.05119669234731)(0.5,3.0259838611258)(0.51,3.01284772838793)(0.52,3.01029666091057)(0.53,3.01514563996159)(0.54,3.02402797128164)(0.55,3.0342360054454)(0.56,3.04384617507831)(0.57,3.0515590388948)(0.58,3.05651103425065)(0.59,3.05813122154211)(0.6,3.05604507798808)(0.61,3.05001223160369)(0.62,3.0398862161563)(0.63,3.02558807820813)(0.64,3.00708869268196)(0.65,2.9843966280902)(0.66,2.95754962228728)(0.67,2.92660846538683)(0.68,2.89165253089039)(0.69,2.85277646735342)(0.7,2.81008773105625)(0.71,2.76370474622489)(0.72,2.71375554757698)(0.73,2.66037680479363)(0.74,2.6037131586945)(0.75,2.54391681983164)(0.76,2.48114739535772)(0.77,2.41557192163831)(0.78,2.34736508976863)(0.79,2.27670966017863)(0.8,2.20379707201033)(0.81,2.12882826416686)(0.82,2.05201473942949)(0.83,1.97357992300915)(0.84,1.89376089562466)(0.85,1.81281062378027)(0.86,1.73100087447615)(0.87,1.64862610128955)(0.88,1.56600874517876)(0.89,1.48350664197121)(0.9,1.40152362731363)(0.91,1.32052507105654)(0.92,1.24106109190918)(0.93,1.16380175577295)(0.94,1.0895906611355)(0.95,1.01952516621653)(0.96,0.955069311764951)(0.97,0.898186752650931)(0.98,0.851416932475347)(0.99,0.817685171628646)(1,0.799565107889029)(1.01,0.798121861452096)(1.02,0.812289633856214)(1.03,0.8394941968923)(1.04,0.876809815423523)(1.05,0.921696894661266)(1.06,0.972191980008956)(1.07,1.026831670377)(1.08,1.08451977451554)(1.09,1.1444144761036)(1.1,1.2058481943895)(1.11,1.26827408639539)(1.12,1.33123093587662)(1.13,1.39432002549962)(1.14,1.45718968863576)(1.15,1.51952478969417)(1.16,1.58103940072838)(1.17,1.6414715831874)(1.18,1.70057958243273)(1.19,1.7581389911792)(1.2,1.81394059435028)(1.21,1.86778870745259)(1.22,1.91949988503488)(1.23,1.96890191826689)(1.24,2.01583306927621)(1.25,2.06014150971716)(1.26,2.10168494539283)(1.27,2.14033041980383)(1.28,2.17595429881624)(1.29,2.20844244746681)(1.3,2.23769061939598)(1.31,2.26360509077436)(1.32,2.28610358546564)(1.33,2.30511655881966)(1.34,2.32058893735021)(1.35,2.33248245603253)(1.36,2.34077880280757)(1.37,2.34548388554397)(1.38,2.34663370439796)(1.39,2.34430258329642)(1.4,2.33861495813319)(1.41,2.32976265446075)(1.42,2.31803080653477)(1.43,2.30383755357099)(1.44,2.28779567363942)(1.45,2.27080806509891)(1.46,2.25421017454742)(1.47,2.2399573025432)(1.48,2.23078349147602)(1.49,2.23007528043064)(1.5,2.24102962233239)(1.51,2.2651406710595)(1.52,2.30131039476205)(1.53,2.34665072790035)(1.54,2.3979733507103)(1.55,2.45265743944081)(1.56,2.50880945592376)(1.57,2.56512775906107)(1.58,2.62072860112149)(1.59,2.67501062618579)(1.6,2.72756287250157)(1.61,2.7781048370449)(1.62,2.82644754667784)(1.63,2.87246790701773)(1.64,2.91609141311241)(1.65,2.95728018449664)(1.66,2.99602445277282)(1.67,3.03233633720696)(1.68,3.06624517275588)(1.69,3.09779391742564)(1.7,3.12703632874307)(1.71,3.15403470183875)(1.72,3.17885802752753)(1.73,3.20158047176855)(1.74,3.22228010642895)(1.75,3.24103784054218)(1.76,3.25793651447589)(1.77,3.27306012864814)(1.78,3.28649318497019)(1.79,3.2983201239044)(1.8,3.30862484347432)(1.81,3.3174902891288)(1.82,3.32499810530132)(1.83,3.33122834099536)(1.84,3.3362592028899)(1.85,3.34016685038152)(1.86,3.34302522772289)(1.87,3.34490592902509)(1.88,3.34587809239502)(1.89,3.34600831990287)(1.9,3.34536062043468)(1.91,3.34399637279505)(1.92,3.34197430669431)(1.93,3.33935049949039)(1.94,3.33617838676422)(1.95,3.33250878499287)(1.96,3.32838992475032)(1.97,3.32386749301519)(1.98,3.31898468329879)(1.99,3.31378225242948)(2,3.30829858293919)(2,-0.444829374793357)(1.99,-0.421098651071882)(1.98,-0.396446336163294)(1.97,-0.370845345516832)(1.96,-0.344268698795504)(1.95,-0.316689632748587)(1.94,-0.288081726215209)(1.93,-0.25841903808521)(1.92,-0.227676259077674)(1.91,-0.195828878232804)(1.9,-0.162853365049562)(1.89,-0.128727368240436)(1.88,-0.0934299321168721)(1.87,-0.0569417316656629)(1.86,-0.0192453274299609)(1.85,0.0196745586284737)(1.84,0.0598307450330455)(1.83,0.101233269114178)(1.82,0.143889040279859)(1.81,0.187801466606901)(1.8,0.23297005291475)(1.79,0.279389968201148)(1.78,0.327051579935454)(1.77,0.375939952180139)(1.76,0.426034303786354)(1.75,0.477307421903277)(1.74,0.529725024634428)(1.73,0.583245064695554)(1.72,0.637816963125363)(1.71,0.693380758098698)(1.7,0.749866148131158)(1.69,0.807191400594332)(1.68,0.865262084174702)(1.67,0.923969565669119)(1.66,0.983189184093607)(1.65,1.04277797331801)(1.64,1.10257173990012)(1.63,1.16238120155058)(1.62,1.22198673039036)(1.61,1.28113098443977)(1.6,1.33950828377602)(1.59,1.39674888254904)(1.58,1.45239512476716)(1.57,1.50586459578307)(1.56,1.55639257115558)(1.55,1.60294274080495)(1.54,1.64407480352181)(1.53,1.67777397387581)(1.52,1.70131956298155)(1.51,1.71144924430573)(1.5,1.70523183993032)(1.49,1.68156264538277)(1.48,1.64196899135767)(1.47,1.58971783498313)(1.46,1.52829738913243)(1.45,1.46057039095885)(1.44,1.38864376767554)(1.43,1.31402394188051)(1.42,1.23780101275596)(1.41,1.1607884731007)(1.4,1.08361635276817)(1.39,1.00679085020874)(1.38,0.930732327842318)(1.37,0.855799800322401)(1.36,0.782307022733014)(1.35,0.710533304055332)(1.34,0.640730954228341)(1.33,0.573130539780742)(1.32,0.507944680783682)(1.31,0.445370852532745)(1.3,0.385593488936256)(1.29,0.328785580005791)(1.28,0.275109888906981)(1.27,0.224719870300608)(1.26,0.177760342439145)(1.25,0.134367945276811)(1.24,0.094671402268187)(1.23,0.0587915923031793)(1.22,0.0268414287544383)(1.21,-0.00107446635636632)(1.2,-0.0248603146781139)(1.19,-0.0444299934333956)(1.18,-0.0597081549437549)(1.17,-0.0706317224008323)(1.16,-0.0771518600220896)(1.15,-0.079236559279762)(1.14,-0.0768740486083972)(1.13,-0.0700773350515127)(1.12,-0.0588903442762789)(1.11,-0.0433963757642554)(1.1,-0.0237299907984804)(1.09,-9.40942984856141e-05)(1.08,0.0272150070885241)(1.07,0.0577702328946769)(1.06,0.0909576019586149)(1.05,0.125893055316186)(1.04,0.161306130482944)(1.03,0.195403125446262)(1.02,0.225786465151679)(1.01,0.249639542185894)(1,0.264458529378529)(0.99,0.26920285236244)(0.98,0.264913763770812)(0.97,0.254095681204893)(0.96,0.239565626824373)(0.95,0.223721326871451)(0.94,0.208356283085153)(0.93,0.194740318290634)(0.92,0.183756324482167)(0.91,0.176016500654449)(0.9,0.171945442125653)(0.89,0.171836179811568)(0.88,0.175887465025862)(0.87,0.184228740738409)(0.86,0.196937137231983)(0.85,0.214049274806336)(0.84,0.23556963487419)(0.83,0.261476617420922)(0.82,0.291727002053005)(0.81,0.326259279554266)(0.8,0.364996162981932)(0.79,0.407846486369675)(0.78,0.454706633488184)(0.77,0.505461595674604)(0.76,0.55998572834969)(0.75,0.618143255391288)(0.74,0.679788555740815)(0.73,0.744766255290415)(0.72,0.812911137667727)(0.71,0.884047878763875)(0.7,0.957990600596524)(0.69,1.0345422291118)(0.68,1.11349362620844)(0.67,1.19462244634792)(0.66,1.27769163916542)(0.65,1.36244747611301)(0.64,1.4486169126074)(0.63,1.53590399298656)(0.62,1.62398483960066)(0.61,1.71250049851602)(0.6,1.80104647262306)(0.59,1.88915704018206)(0.58,1.97628124047184)(0.57,2.06174542720433)(0.56,2.14469426911443)(0.55,2.22399833130533)(0.54,2.29811518586665)(0.53,2.36490617240151)(0.52,2.42148216079223)(0.51,2.46433509334006)(0.5,2.49018607872373)(0.49,2.49750526559355)(0.48,2.48740515404448)(0.47,2.46283413364432)(0.46,2.42707965816406)(0.45,2.38289409924225)(0.44,2.3323292750101)(0.43,2.27686680349494)(0.42,2.21758765612926)(0.41,2.15530373759552)(0.4,2.09064643872724)(0.39,2.02412355716508)(0.38,1.95615559851786)(0.37,1.88709914785574)(0.36,1.81726219187339)(0.35,1.7469143967805)(0.34,1.6762941843428)(0.33,1.60561374383708)(0.32,1.53506269122152)(0.31,1.46481082659219)(0.3,1.3950102801787)(0.29,1.32579723630126)(0.28,1.2572933605496)(0.27,1.18960701402354)(0.26,1.12283431137273)(0.25,1.05706006141912)(0.24,0.992358617120402)(0.23,0.928794653500352)(0.22,0.866423886627792)(0.21,0.805293742920604)(0.2,0.745443985426882)(0.19,0.686907301918829)(0.18,0.629709858375887)(0.17,0.573871820560741)(0.16,0.519407845788207)(0.15,0.466327546571051)(0.14,0.414635927542119)(0.13,0.364333796858902)(0.12,0.315418153166848)(0.11,0.267882549111694)(0.1,0.221717432334636)(0.09,0.176910464847661)(0.08,0.133446821662446)(0.07,0.091309469530374)(0.06,0.0504794266397142)(0.05,0.010936004106592)(0.04,-0.0273429699125187)(0.03,-0.0643809426684996)(0.02,-0.100202445019883)(0.01,-0.13483291459035)(0,-0.168298533102028)};

\addplot [
color=olive!70!black,
solid,
line width=2.0pt,
forget plot
]
coordinates{
  (0,1.70826544576424)(0.01,1.73260753716033)(0.02,1.75751306471116)(0.03,1.78297547659751)(0.04,1.8089863418604)(0.05,1.83553521297732)(0.06,1.86260948312943)(0.07,1.89019423831817)(0.08,1.91827210454844)(0.09,1.94682309036159)(0.1,1.97582442507676)(0.11,2.00525039318335)(0.12,2.0350721654228)(0.13,2.06525762720428)(0.14,2.09577120511855)(0.15,2.12657369244757)(0.16,2.15762207471663)(0.17,2.18886935650133)(0.18,2.22026439088662)(0.19,2.25175171317978)(0.2,2.28327138070667)(0.21,2.31475882077223)(0.22,2.34614468914516)(0.23,2.37735474173435)(0.24,2.40830972246517)(0.25,2.43892527073858)(0.26,2.46911185226999)(0.27,2.49877471756004)(0.28,2.52781389275068)(0.29,2.55612420817129)(0.3,2.58359537048465)(0.31,2.61011208500784)(0.32,2.6355542355121)(0.33,2.659797129606)(0.34,2.6827118186824)(0.35,2.70416550236982)(0.36,2.72402202847953)(0.37,2.74214250058932)(0.38,2.75838600666159)(0.39,2.77261048346765)(0.4,2.78467373309002)(0.41,2.7944346094139)(0.42,2.80175439430643)(0.43,2.80649838513394)(0.44,2.80853771739419)(0.45,2.80775144856017)(0.46,2.8040289317583)(0.47,2.79727251065658)(0.48,2.78740056993473)(0.49,2.77435097897043)(0.5,2.75808496992476)(0.51,2.738591410864)(0.52,2.7158894108514)(0.53,2.69002590618155)(0.54,2.66107157857415)(0.55,2.62911716837536)(0.56,2.59427022209637)(0.57,2.55665223304956)(0.58,2.51639613736124)(0.59,2.47364413086208)(0.6,2.42854577530557)(0.61,2.38125636505986)(0.62,2.33193552787848)(0.63,2.28074603559734)(0.64,2.22785280264468)(0.65,2.1734220521016)(0.66,2.11762063072635)(0.67,2.06061545586737)(0.68,2.00257307854941)(0.69,1.94365934823261)(0.7,1.88403916582639)(0.71,1.82387631249438)(0.72,1.76333334262236)(0.73,1.70257153004202)(0.74,1.64175085721766)(0.75,1.58103003761146)(0.76,1.5205665618537)(0.77,1.46051675865646)(0.78,1.40103586162841)(0.79,1.34227807327415)(0.8,1.28439661749613)(0.81,1.22754377186056)(0.82,1.17187087074125)(0.83,1.11752827021504)(0.84,1.06466526524942)(0.85,1.01342994929331)(0.86,0.963969005854064)(0.87,0.916427421013977)(0.88,0.87094810510231)(0.89,0.82767141089139)(0.9,0.786734534719644)(0.91,0.748270785855492)(0.92,0.712408708195676)(0.93,0.679271037031793)(0.94,0.648973472110324)(0.95,0.621623246543991)(0.96,0.597317469294662)(0.97,0.576141216927912)(0.98,0.55816534812308)(0.99,0.543444011995543)(1,0.532011818633779)(1.01,0.523880701818995)(1.02,0.519038049503947)(1.03,0.517448661169281)(1.04,0.519057972953233)(1.05,0.523794974988726)(1.06,0.531574790983785)(1.07,0.542300951635837)(1.08,0.555867390802034)(1.09,0.572160190902558)(1.1,0.591059101795511)(1.11,0.612438855315566)(1.12,0.63617029580017)(1.13,0.662121345224055)(1.14,0.690157820013684)(1.15,0.720144115207205)(1.16,0.751943770353143)(1.17,0.785419930393282)(1.18,0.820435713744487)(1.19,0.856854498872902)(1.2,0.894540139836085)(1.21,0.933357120548111)(1.22,0.973170656894659)(1.23,1.01384675528503)(1.24,1.0552522357722)(1.25,1.09725472749698)(1.26,1.13972264391599)(1.27,1.18252514505222)(1.28,1.22553209386161)(1.29,1.2686140137363)(1.3,1.31164205416612)(1.31,1.35448797165355)(1.32,1.39702413312466)(1.33,1.4391235493002)(1.34,1.48065994578927)(1.35,1.52150788004393)(1.36,1.56154291277029)(1.37,1.60064184293319)(1.38,1.63868301612014)(1.39,1.67554671675258)(1.4,1.71111565545068)(1.41,1.74527556378072)(1.42,1.77791590964536)(1.43,1.80893074772575)(1.44,1.83821972065748)(1.45,1.86568922802888)(1.46,1.89125378183992)(1.47,1.91483756876317)(1.48,1.93637624141684)(1.49,1.9558189629067)(1.5,1.97313073113136)(1.51,1.98829495768261)(1.52,2.0013149788718)(1.53,2.01221235088808)(1.54,2.02102407711605)(1.55,2.02780009012288)(1.56,2.03260101353967)(1.57,2.03549617742207)(1.58,2.03656186294433)(1.59,2.03587975436742)(1.6,2.0335355781388)(1.61,2.02961791074233)(1.62,2.0242171385341)(1.63,2.01742455428415)(1.64,2.00933157650626)(1.65,2.00002907890732)(1.66,1.98960681843321)(1.67,1.97815295143804)(1.68,1.96575362846529)(1.69,1.95249265900999)(1.7,1.93845123843711)(1.71,1.92370772996873)(1.72,1.90833749532644)(1.73,1.89241276823205)(1.74,1.87600256553169)(1.75,1.85917263122273)(1.76,1.84198540913112)(1.77,1.82450004041414)(1.78,1.80677238245282)(1.79,1.78885504605277)(1.8,1.77079744819454)(1.81,1.75264587786785)(1.82,1.73444357279059)(1.83,1.71623080505477)(1.84,1.69804497396147)(1.85,1.67992070450499)(1.86,1.66188995014647)(1.87,1.64398209867971)(1.88,1.62622408013907)(1.89,1.60864047583122)(1.9,1.59125362769256)(1.91,1.57408374728112)(1.92,1.55714902380832)(1.93,1.54046573070259)(1.94,1.52404833027451)(1.95,1.50790957612214)(1.96,1.49206061297741)(1.97,1.47651107374918)(1.98,1.46126917356775)(1.99,1.4463418006788)(2,1.43173460407292) 
};

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=green!60!black,
densely dotted,
line width=1.0pt,
forget plot
]
coordinates{
 (1,-2)(1,0.5)
};

\addplot [
color=green!60!black,
only marks,
mark=*,
mark size=2.5pt,
line width=1.0pt,
forget plot
]
coordinates{
 (1,-2)
};

\addplot [
color=green!60!black,
only marks,
mark=x,
mark size=3.5pt,
line width=1.5pt,
forget plot
]
coordinates{
 (1,0.5)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/voned_cl_00.tex
GP explanation and intro to LSE

--- 2013-03-19 figurefactory/files/voned_3_2.tex
@@
 
-\addplot [
-color=green!60!black,
-densely dotted,
-line width=1.0pt,
-forget plot
-]
-coordinates{
- (1,-2)(1,0.5)
-};
-
-\addplot [
-color=green!60!black,
-only marks,
-mark=*,
-mark size=2.5pt,
-line width=1.0pt,
-forget plot
-]
-coordinates{
- (1,-2)
-};
-
-\addplot [
-color=green!60!black,
-only marks,
-mark=x,
-mark size=3.5pt,
-line width=1.5pt,
-forget plot
-]
-coordinates{
- (1,0.5)
-};
-
 \end{axis}

### 2013-03-19 figurefactory/files/voned_cl_10.tex
GP explanation and intro to LSE

--- 2013-03-19 figurefactory/files/voned_cl_00.tex
@@
 
+\addplot [
+color=red,
+densely dashed,
+line width=2.0pt,
+forget plot
+]
+coordinates{
+ (0,1.2)(2,1.2)
+};
+
+\addplot [
+color=black,
+solid,
+line width=1.5pt,
+mark size=3pt,
+mark=-,
+forget plot
+]
+coordinates{
+ (0.5,2.4902)(0.5,3.026)
+};
+
+\node at (axis cs:0.45, 3) [anchor=south west,minimum size=16pt] {$Q_4(\*x_{0.5})$};
+
 \end{axis}

### 2013-03-19 figurefactory/files/voned_cl_20.tex
GP explanation and intro to LSE

--- 2013-03-19 figurefactory/files/voned_cl_00.tex
@@
 
+\addplot [
+color=red!40!yellow,
+solid,
+only marks,
+mark=*,
+mark size=2.5pt,
+forget plot
+]
+coordinates{
+ (0.5,-2)
+};
+
+\addplot [
+color=red,
+densely dashed,
+line width=2.0pt,
+forget plot
+]
+coordinates{
+ (0,1.2)(2,1.2)
+};
+
+\addplot [
+color=black,
+solid,
+line width=1.5pt,
+mark size=3pt,
+mark=-,
+forget plot
+]
+coordinates{
+ (1.5,1.7052)(1.5,2.241)
+};
+
+\node at (axis cs:1.4, 2.3) [anchor=south west,minimum size=16pt] {$Q_4(\*x_{1.5})$};
+
 \end{axis}

### 2013-03-19 figurefactory/files/voned_cl_30.tex
GP explanation and intro to LSE

--- 2013-03-19 figurefactory/files/voned_cl_00.tex
@@
 
+\addplot [
+color=red!40!yellow,
+solid,
+only marks,
+mark=*,
+mark size=2.5pt,
+forget plot
+]
+coordinates{
+ (0.5,-2)(1.5,-2)
+};
+
+\addplot [
+color=red,
+densely dashed,
+line width=2.0pt,
+forget plot
+]
+coordinates{
+ (0,1.2)(2,1.2)
+};
+
+\addplot [
+color=black,
+solid,
+line width=1.5pt,
+mark size=3pt,
+mark=-,
+forget plot
+]
+coordinates{
+ (1,0.2645)(1,0.7996)
+};
+
+\node at (axis cs:0.88, -0.4) [anchor=south west,minimum size=16pt] {$Q_4(\*x_1)$};
+
 \end{axis}

### 2013-03-19 figurefactory/files/voned_cl_40.tex
GP explanation and intro to LSE

--- 2013-03-19 figurefactory/files/voned_cl_30.tex
@@
 \addplot [
+color=locol,
+solid,
+only marks,
+mark=*,
+mark size=2.5pt,
+forget plot
+]
+coordinates{
+ (1,-2)
+};
+
+\addplot [
 color=red,
@@
 coordinates{
- (1,0.2645)(1,0.7996)
+ (0,-0.1683)(0,3.5848)
 };
 
-\node at (axis cs:0.88, -0.4) [anchor=south west,minimum size=16pt] {$Q_4(\*x_1)$};
+\addplot [
+color=black,
+solid,
+line width=1.5pt,
+mark size=3pt,
+mark=-,
+forget plot
+]
+coordinates{
+ (2,-0.4448)(2,3.3083)
+};
+
+\node at (axis cs:0, -0.8) [anchor=south west,minimum size=16pt] {$Q_4(\*x_0)$};
+
+\node at (axis cs:1.78, -1) [anchor=south west,minimum size=16pt] {$Q_4(\*x_2)$};
 

### 2013-03-19 figurefactory/files/voned_cl_41.tex
GP explanation and intro to LSE

--- 2013-03-19 figurefactory/files/voned_cl_20.tex
@@
 only marks,
-mark=*,
+mark=square*,
 mark size=2.5pt,
@@
 coordinates{
- (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
+ %(0,-2)
+ (0.01,-2)(0.02,-2)(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)(1.98,-2)(1.99,-2)
+ %(2,-2) 
 };
@@
 coordinates{
- (0.5,-2)
+ (0.28,-2)(0.29,-2)(0.3,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)(0.35,-2)(0.36,-2)(0.37,-2)(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2)
+};
+
+\addplot [
+color=locol,
+solid,
+only marks,
+mark=square*,
+mark size=2.5pt,
+forget plot
+]
+coordinates{
+ (0.93,-2)(0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2)(1.09,-2) 
 };
@@
 
-\addplot [
-color=black,
-solid,
-line width=1.5pt,
-mark size=3pt,
-mark=-,
-forget plot
-]
-coordinates{
- (1.5,1.7052)(1.5,2.241)
-};
-
-\node at (axis cs:1.4, 2.3) [anchor=south west,minimum size=16pt] {$Q_4(\*x_{1.5})$};
-
 \end{axis}

### 2013-03-19 msthpres.tex
GP explanation and intro to LSE

@@
 \begin{enumerate}
-\item<1-> How do we \textbf{model} the function?
+\item<1-> How do we \textbf{estimate} the function?
 \vspace{1em}
@@
 }
+\end{center}
+\end{frame}
+
+\begin{frame}
+\begin{center}
+\uncover<1->{\large Why GPs are nice}
+\end{center}
+\begin{itemize}
+\item<2-> \textbf{Nonparametric}:\\
+      Impose ``smoothness'' assumptions via kernel $k(x, x')$.
+\vspace{1em}
+\item<3-> \textbf{Bayesian}, yet \textbf{efficient}:
+      \begin{align*}
+        \mu_t(\*x) &= \*k_t(\*x)^T\left(\*K_t + \sigma^2 \*I\right)^{-1}\*y_t\\
+        k_t(\*x, \*x') &= k(\*x, \*x') - \*k_t(\*x)^T\left(\*K_t + \sigma^2 \*I\right)^{-1}\*k_t(\*x)\notag\\
+        \sigma_t^2(\*x) &= k_t(\*x, \*x)
+      \end{align*}
+      Suitable for step-by-step updates.
+\vspace{1em}
+\item<4-> More importantly: they provide \textbf{variance estimates}!\\
+          Construct confidence intervals: $Q_t(\*x) = \left[\mu_{t-1}(\*x) \pm \beta_t \sigma_{t-1}(\*x)\right]$
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\begin{center}
+\includegraphics<1>[width=4.45in]{figures/voned_0}
+\includegraphics<2>[width=4.45in]{figures/voned_1_0}
+\includegraphics<3>[width=4.45in]{figures/voned_1_1}
+\includegraphics<4>[width=4.45in]{figures/voned_1_2}
+\includegraphics<5>[width=4.45in]{figures/voned_2_0}
+\includegraphics<6>[width=4.45in]{figures/voned_2_1}
+\includegraphics<7>[width=4.45in]{figures/voned_2_2}
+\includegraphics<8>[width=4.45in]{figures/voned_3_0}
+\includegraphics<9>[width=4.45in]{figures/voned_3_1}
+\includegraphics<10>[width=4.45in]{figures/voned_3_2}
+\end{center}
+\end{frame}
+
+\begin{frame}
+\begin{enumerate}
+\item<1-> How do we \textbf{estimate} the function? \uncover<3->{\Large\color{green!70!black}\checkmark}
+\vspace{0em}
+\item<4-> How do we \textbf{classify}? \uncover<14->{\Large\color{green!70!black}\checkmark}
+\vspace{0.3em}
+\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<16->{\Large\color{green!70!black}\checkmark}
+\end{enumerate}
+
+\begin{center}
+\color{white}
+\includegraphics<1>[draft,width=3.5in]{figures/voned_cl_00}
+\color{black}
+\includegraphics<2-4>[width=3.5in]{figures/voned_cl_00}
+\includegraphics<5>[width=3.5in]{figures/voned_cl_01}
+\includegraphics<6>[width=3.5in]{figures/voned_cl_10}
+\includegraphics<7>[width=3.5in]{figures/voned_cl_11}
+\includegraphics<8>[width=3.5in]{figures/voned_cl_20}
+\includegraphics<9>[width=3.5in]{figures/voned_cl_21}
+\includegraphics<10>[width=3.5in]{figures/voned_cl_30}
+\includegraphics<11>[width=3.5in]{figures/voned_cl_31}
+\includegraphics<12>[width=3.5in]{figures/voned_cl_40}
+\includegraphics<13->[width=3.5in]{figures/voned_cl_41}
 \end{center}

### 2013-03-19 figurefactory/files/limno_bgape_class_0.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,1.0100953990001e-06)(358.30303030303,4.04031425463559e-06)(373.232323232323,7.07043210985092e-06)(388.161616161616,9.09045456864996e-06)(403.090909090909,9.09045456864996e-06)(418.020202020202,9.09045456864996e-06)(432.949494949495,9.09045456864996e-06)(447.878787878788,9.09045456864996e-06)(462.808080808081,9.09045456864996e-06)(477.737373737374,9.09045456864996e-06)(492.666666666667,9.09045456864996e-06)(507.59595959596,9.09045456864996e-06)(522.525252525253,9.09045456864996e-06)(537.454545454546,9.09045456864996e-06)(552.383838383838,9.09045456864996e-06)(567.313131313131,9.09045456864996e-06)(582.242424242424,9.09045456864996e-06)(597.171717171717,9.09045456864996e-06)(612.10101010101,9.09045456864996e-06)(627.030303030303,9.09045456864996e-06)(641.959595959596,9.09045456864996e-06)(656.888888888889,9.09045456864996e-06)(671.818181818182,9.09045456864996e-06)(686.747474747475,9.09045456864996e-06)(701.676767676768,9.09045456864996e-06)(716.606060606061,9.09045456864996e-06)(731.535353535354,9.09045456864996e-06)(746.464646464646,9.09045456864996e-06)(761.393939393939,9.09045456864996e-06)(776.323232323232,9.09045456864996e-06)(791.252525252525,9.09045456864996e-06)(806.181818181818,9.09045456864996e-06)(821.111111111111,9.09045456864996e-06)(836.040404040404,9.09045456864996e-06)(850.969696969697,9.09045456864996e-06)(865.89898989899,9.09045456864996e-06)(880.828282828283,9.09045456864996e-06)(895.757575757576,9.09045456864996e-06)(910.686868686869,9.09045456864996e-06)(925.616161616162,9.09045456864996e-06)(940.545454545455,9.09045456864996e-06)(955.474747474747,9.09045456864996e-06)(970.40404040404,9.09045456864996e-06)(985.333333333333,9.09045456864996e-06)(1000.26262626263,9.09045456864996e-06)(1015.19191919192,9.09045456864996e-06)(1030.12121212121,9.09045456864996e-06)(1045.05050505051,9.09045456864996e-06)(1059.9797979798,9.09045456864996e-06)(1074.90909090909,9.09045456864996e-06)(1089.83838383838,9.09045456864996e-06)(1104.76767676768,9.09045456864996e-06)(1119.69696969697,9.09045456864996e-06)(1134.62626262626,9.09045456864996e-06)(1149.55555555556,9.09045456864996e-06)(1164.48484848485,9.09045456864996e-06)(1179.41414141414,9.09045456864996e-06)(1194.34343434343,9.09045456864996e-06)(1209.27272727273,9.09045456864996e-06)(1224.20202020202,9.09045456864996e-06)(1239.13131313131,9.09045456864996e-06)(1254.06060606061,9.09045456864996e-06)(1268.9898989899,9.09045456864996e-06)(1283.91919191919,9.09045456864996e-06)(1298.84848484848,9.09045456864996e-06)(1313.77777777778,9.09045456864996e-06)(1328.70707070707,9.09045456864996e-06)(1343.63636363636,9.09045456864996e-06)(1358.56565656566,9.09045456864996e-06)(1373.49494949495,9.09045456864996e-06)(1388.42424242424,9.09045456864996e-06)(1403.35353535354,9.09045456864996e-06)(1418.28282828283,9.09045456864996e-06)(1433.21212121212,9.09045456864996e-06)(1448.14141414141,9.09045456864996e-06)(1463.07070707071,9.09045456864996e-06)(1478,9.09045456864996e-06)(1478.00074642733,0)(1478.00074642733,-0.181818181818183)(1478.00074642733,-0.363636363636363)(1478.00074642733,-0.545454545454547)(1478.00074642733,-0.727272727272727)(1478.00074642733,-0.90909090909091)(1478.00074642733,-1.09090909090909)(1478.00074642733,-1.27272727272727)(1478.00074642733,-1.45454545454545)(1478.00074642733,-1.63636363636364)(1478.00074642733,-1.81818181818182)(1478.00049762651,-2)(1478.0002488174,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478.0002488174,-6.54545454545455)(1478.00049762651,-6.72727272727273)(1478.00074642733,-6.90909090909091)(1478.00074642733,-7.09090909090909)(1478.00074642733,-7.27272727272727)(1478.00074642733,-7.45454545454546)(1478.00074642733,-7.63636363636364)(1478.00074642733,-7.81818181818182)(1478.00074642733,-8)(1478.00074642733,-8.18181818181818)(1478.00074642733,-8.36363636363636)(1478.00074642733,-8.54545454545455)(1478.00074642733,-8.72727272727273)(1478.00074642733,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00074642733,-9.27272727272727)(1478.00074642733,-9.45454545454546)(1478.00074642733,-9.63636363636364)(1478.00074642733,-9.81818181818182)(1478.00074642733,-10)(1478.00074642733,-10.1818181818182)(1478.00074642733,-10.3636363636364)(1478.00074642733,-10.5454545454545)(1478.00074642733,-10.7272727272727)(1478.00074642733,-10.9090909090909)(1478.00074642733,-11.0909090909091)(1478.00074642733,-11.2727272727273)(1478.00074642733,-11.4545454545455)(1478.00074642733,-11.6363636363636)(1478.00074642733,-11.8181818181818)(1478.00074642733,-12)(1478.00049762651,-12.1818181818182)(1478.0002488174,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478.0002488174,-17.2727272727273)(1478.00049762651,-17.4545454545455)(1478.00074642733,-17.6363636363636)(1478.00074642733,-17.8181818181818)(1478.00074642733,-18)(1478,-18.0000090904546)(1463.07070707071,-18.0000090904546)(1448.14141414141,-18.0000090904546)(1433.21212121212,-18.0000090904546)(1418.28282828283,-18.0000090904546)(1403.35353535354,-18.0000090904546)(1388.42424242424,-18.0000090904546)(1373.49494949495,-18.0000090904546)(1358.56565656566,-18.0000090904546)(1343.63636363636,-18.0000090904546)(1328.70707070707,-18.0000090904546)(1313.77777777778,-18.0000090904546)(1298.84848484848,-18.0000090904546)(1283.91919191919,-18.0000090904546)(1268.9898989899,-18.0000090904546)(1254.06060606061,-18.0000090904546)(1239.13131313131,-18.0000090904546)(1224.20202020202,-18.0000090904546)(1209.27272727273,-18.0000090904546)(1194.34343434343,-18.0000090904546)(1179.41414141414,-18.0000090904546)(1164.48484848485,-18.0000090904546)(1149.55555555556,-18.0000090904546)(1134.62626262626,-18.0000090904546)(1119.69696969697,-18.0000090904546)(1104.76767676768,-18.0000090904546)(1089.83838383838,-18.0000090904546)(1074.90909090909,-18.0000090904546)(1059.9797979798,-18.0000090904546)(1045.05050505051,-18.0000090904546)(1030.12121212121,-18.0000090904546)(1015.19191919192,-18.0000090904546)(1000.26262626263,-18.0000090904546)(985.333333333333,-18.0000090904546)(970.40404040404,-18.0000090904546)(955.474747474747,-18.0000090904546)(940.545454545455,-18.0000090904546)(925.616161616162,-18.0000090904546)(910.686868686869,-18.0000090904546)(895.757575757576,-18.0000090904546)(880.828282828283,-18.0000090904546)(865.89898989899,-18.0000090904546)(850.969696969697,-18.0000090904546)(836.040404040404,-18.0000090904546)(821.111111111111,-18.0000090904546)(806.181818181818,-18.0000090904546)(791.252525252525,-18.0000090904546)(776.323232323232,-18.0000090904546)(761.393939393939,-18.0000090904546)(746.464646464646,-18.0000090904546)(731.535353535354,-18.0000090904546)(716.606060606061,-18.0000090904546)(701.676767676768,-18.0000090904546)(686.747474747475,-18.0000090904546)(671.818181818182,-18.0000090904546)(656.888888888889,-18.0000090904546)(641.959595959596,-18.0000090904546)(627.030303030303,-18.0000090904546)(612.10101010101,-18.0000090904546)(597.171717171717,-18.0000090904546)(582.242424242424,-18.0000090904546)(567.313131313131,-18.0000090904546)(552.383838383838,-18.0000090904546)(537.454545454546,-18.0000090904546)(522.525252525253,-18.0000090904546)(507.59595959596,-18.0000090904546)(492.666666666667,-18.0000090904546)(477.737373737374,-18.0000090904546)(462.808080808081,-18.0000090904546)(447.878787878788,-18.0000090904546)(432.949494949495,-18.0000090904546)(418.020202020202,-18.000006060404)(403.090909090909,-18.0000030302525)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(-0.000248817401863321,-15.0909090909091)(-0.000497626510092015,-14.9090909090909)(-0.000746427325097138,-14.7272727272727)(-0.000746427325097138,-14.5454545454545)(-0.000746427325097138,-14.3636363636364)(-0.000746427325097138,-14.1818181818182)(-0.000746427325097138,-14)(-0.000746427325097138,-13.8181818181818)(-0.000746427325097138,-13.6363636363636)(-0.000746427325097138,-13.4545454545455)(-0.000746427325097138,-13.2727272727273)(-0.000746427325097138,-13.0909090909091)(-0.000746427325097138,-12.9090909090909)(-0.000746427325097138,-12.7272727272727)(-0.000746427325097138,-12.5454545454545)(-0.000746427325097138,-12.3636363636364)(-0.000746427325097138,-12.1818181818182)(-0.000746427325097138,-12)(-0.000746427325097138,-11.8181818181818)(-0.000746427325097138,-11.6363636363636)(-0.000746427325097138,-11.4545454545455)(-0.000746427325097138,-11.2727272727273)(-0.000746427325097138,-11.0909090909091)(-0.000746427325097138,-10.9090909090909)(-0.000746427325097138,-10.7272727272727)(-0.000746427325097138,-10.5454545454545)(-0.000746427325097138,-10.3636363636364)(-0.000746427325097138,-10.1818181818182)(-0.000746427325097138,-10)(-0.000746427325097138,-9.81818181818182)(-0.000497626510092015,-9.63636363636364)(-0.000248817401863321,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(-0.000248817401863321,-8)(-0.000497626510092015,-7.81818181818182)(-0.000746427325097138,-7.63636363636364)(-0.000746427325097138,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000497626510092015,-7.09090909090909)(-0.000248817401863321,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(-0.000248817401863321,-4.36363636363636)(-0.000497626510092015,-4.18181818181818)(-0.000746427325097138,-4)(-0.000746427325097138,-3.81818181818182)(-0.000746427325097138,-3.63636363636364)(-0.000746427325097138,-3.45454545454546)(-0.000746427325097138,-3.27272727272727)(-0.000746427325097138,-3.09090909090909)(-0.000746427325097138,-2.90909090909091)(-0.000746427325097138,-2.72727272727273)(-0.000497626510092015,-2.54545454545455)(-0.000248817401863321,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

%\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-2.45454545454545)(14.9292929292929,-2.45454545454545)(29.8585858585859,-2.45454545454545)(44.7878787878788,-2.45454545454545)(59.7171717171717,-2.45454545454545)(74.6464646464647,-2.45454545454545)(89.5757575757576,-2.39393939393939)(97.040404040404,-2.36363636363636)(104.505050505051,-2.33333333333333)(119.434343434343,-2.27272727272727)(134.363636363636,-2.27272727272727)(149.292929292929,-2.21212121212121)(156.757575757576,-2.18181818181818)(164.222222222222,-2.15151515151515)(179.151515151515,-2.09090909090909)(194.080808080808,-2.03030303030303)(201.545454545455,-2)(209.010101010101,-1.96969696969697)(223.939393939394,-1.84848484848485)(231.40404040404,-1.81818181818182)(238.868686868687,-1.78787878787879)(253.79797979798,-1.66666666666667)(257.530303030303,-1.63636363636364)(268.727272727273,-1.54545454545455)(279.924242424242,-1.45454545454545)(283.656565656566,-1.42424242424242)(298.585858585859,-1.3030303030303)(302.318181818182,-1.27272727272727)(313.515151515152,-1.18181818181818)(320.979797979798,-1.09090909090909)(328.444444444444,-0.954545454545455)(330.93265993266,-0.90909090909091)(340.885521885522,-0.727272727272727)(343.373737373737,-0.636363636363637)(345.861952861953,-0.545454545454547)(350.838383838384,-0.363636363636363)(355.814814814815,-0.181818181818183)(358.30303030303,-0.0909090909090917)(360.791245791246,0)(373.232323232323,2.52515432531587e-06)(388.161616161616,4.54522728432498e-06)(403.090909090909,4.54522728432498e-06)(418.020202020202,4.54522728432498e-06)(432.949494949495,4.54522728432498e-06)(447.878787878788,4.54522728432498e-06)(462.808080808081,4.54522728432498e-06)(477.737373737374,4.54522728432498e-06)(492.666666666667,4.54522728432498e-06)(507.59595959596,4.54522728432498e-06)(522.525252525253,4.54522728432498e-06)(537.454545454546,4.54522728432498e-06)(552.383838383838,4.54522728432498e-06)(567.313131313131,4.54522728432498e-06)(582.242424242424,4.54522728432498e-06)(597.171717171717,4.54522728432498e-06)(612.10101010101,4.54522728432498e-06)(627.030303030303,4.54522728432498e-06)(641.959595959596,4.54522728432498e-06)(656.888888888889,4.54522728432498e-06)(671.818181818182,4.54522728432498e-06)(686.747474747475,4.54522728432498e-06)(701.676767676768,4.54522728432498e-06)(716.606060606061,4.54522728432498e-06)(731.535353535354,4.54522728432498e-06)(746.464646464646,4.54522728432498e-06)(761.393939393939,4.54522728432498e-06)(776.323232323232,4.54522728432498e-06)(791.252525252525,4.54522728432498e-06)(806.181818181818,4.54522728432498e-06)(821.111111111111,4.54522728432498e-06)(836.040404040404,4.54522728432498e-06)(850.969696969697,4.54522728432498e-06)(865.89898989899,4.54522728432498e-06)(880.828282828283,4.54522728432498e-06)(895.757575757576,4.54522728432498e-06)(910.686868686869,4.54522728432498e-06)(925.616161616162,4.54522728432498e-06)(940.545454545455,4.54522728432498e-06)(955.474747474747,4.54522728432498e-06)(970.40404040404,4.54522728432498e-06)(985.333333333333,4.54522728432498e-06)(1000.26262626263,4.54522728432498e-06)(1015.19191919192,4.54522728432498e-06)(1030.12121212121,4.54522728432498e-06)(1045.05050505051,4.54522728432498e-06)(1059.9797979798,4.54522728432498e-06)(1074.90909090909,4.54522728432498e-06)(1089.83838383838,4.54522728432498e-06)(1104.76767676768,4.54522728432498e-06)(1119.69696969697,4.54522728432498e-06)(1134.62626262626,4.54522728432498e-06)(1149.55555555556,4.54522728432498e-06)(1164.48484848485,4.54522728432498e-06)(1179.41414141414,4.54522728432498e-06)(1194.34343434343,4.54522728432498e-06)(1209.27272727273,4.54522728432498e-06)(1224.20202020202,4.54522728432498e-06)(1239.13131313131,4.54522728432498e-06)(1254.06060606061,4.54522728432498e-06)(1268.9898989899,4.54522728432498e-06)(1283.91919191919,4.54522728432498e-06)(1298.84848484848,4.54522728432498e-06)(1313.77777777778,4.54522728432498e-06)(1328.70707070707,4.54522728432498e-06)(1343.63636363636,4.54522728432498e-06)(1358.56565656566,4.54522728432498e-06)(1373.49494949495,4.54522728432498e-06)(1388.42424242424,4.54522728432498e-06)(1403.35353535354,4.54522728432498e-06)(1418.28282828283,4.54522728432498e-06)(1433.21212121212,4.54522728432498e-06)(1448.14141414141,4.54522728432498e-06)(1463.07070707071,4.54522728432498e-06)(1478,4.54522728432498e-06)(1478.00037321366,0)(1478.00037321366,-0.181818181818183)(1478.00037321366,-0.363636363636363)(1478.00037321366,-0.545454545454547)(1478.00037321366,-0.727272727272727)(1478.00037321366,-0.90909090909091)(1478.00037321366,-1.09090909090909)(1478.00037321366,-1.27272727272727)(1478.00037321366,-1.45454545454545)(1478.00037321366,-1.63636363636364)(1478.00037321366,-1.81818181818182)(1478.00012440663,-2)(1478,-2.09090909090909)(1463.07070707071,-2.09090909090909)(1448.14141414141,-2.09090909090909)(1433.21212121212,-2.03030303030303)(1425.74747474747,-2)(1418.28282828283,-1.96969696969697)(1403.35353535354,-1.90909090909091)(1388.42424242424,-1.90909090909091)(1373.49494949495,-1.90909090909091)(1358.56565656566,-1.90909090909091)(1343.63636363636,-1.90909090909091)(1328.70707070707,-1.90909090909091)(1313.77777777778,-1.90909090909091)(1298.84848484848,-1.96969696969697)(1291.38383838384,-2)(1283.91919191919,-2.03030303030303)(1268.9898989899,-2.09090909090909)(1254.06060606061,-2.09090909090909)(1239.13131313131,-2.09090909090909)(1224.20202020202,-2.09090909090909)(1209.27272727273,-2.15151515151515)(1201.80808080808,-2.18181818181818)(1194.34343434343,-2.21212121212121)(1179.41414141414,-2.27272727272727)(1164.48484848485,-2.33333333333333)(1157.0202020202,-2.36363636363636)(1149.55555555556,-2.39393939393939)(1134.62626262626,-2.51515151515151)(1127.16161616162,-2.54545454545455)(1119.69696969697,-2.57575757575758)(1104.76767676768,-2.6969696969697)(1097.30303030303,-2.72727272727273)(1089.83838383838,-2.75757575757576)(1074.90909090909,-2.87878787878788)(1067.44444444444,-2.90909090909091)(1059.9797979798,-2.93939393939394)(1045.05050505051,-3.06060606060606)(1041.31818181818,-3.09090909090909)(1030.12121212121,-3.18181818181818)(1022.65656565657,-3.27272727272727)(1015.19191919192,-3.36363636363636)(1007.72727272727,-3.45454545454546)(1000.26262626263,-3.54545454545455)(992.79797979798,-3.63636363636364)(985.333333333333,-3.72727272727273)(977.868686868687,-3.81818181818182)(970.40404040404,-3.90909090909091)(962.939393939394,-4)(955.474747474747,-4.09090909090909)(948.010101010101,-4.18181818181818)(940.545454545455,-4.27272727272727)(933.080808080808,-4.36363636363636)(925.616161616162,-4.45454545454545)(914.419191919192,-4.54545454545455)(910.686868686869,-4.57575757575758)(895.757575757576,-4.6969696969697)(888.292929292929,-4.72727272727273)(880.828282828283,-4.75757575757576)(865.89898989899,-4.87878787878788)(858.434343434343,-4.90909090909091)(850.969696969697,-4.93939393939394)(836.040404040404,-5)(821.111111111111,-5)(806.181818181818,-5.06060606060606)(798.717171717172,-5.09090909090909)(791.252525252525,-5.12121212121212)(776.323232323232,-5.18181818181818)(761.393939393939,-5.18181818181818)(746.464646464646,-5.24242424242424)(739,-5.27272727272727)(731.535353535354,-5.3030303030303)(716.606060606061,-5.36363636363636)(701.676767676768,-5.36363636363636)(686.747474747475,-5.42424242424242)(679.282828282828,-5.45454545454546)(671.818181818182,-5.48484848484849)(656.888888888889,-5.54545454545455)(641.959595959596,-5.54545454545455)(627.030303030303,-5.54545454545455)(612.10101010101,-5.54545454545455)(597.171717171717,-5.54545454545455)(582.242424242424,-5.54545454545455)(567.313131313131,-5.54545454545455)(552.383838383838,-5.54545454545455)(537.454545454546,-5.54545454545455)(522.525252525253,-5.54545454545455)(507.59595959596,-5.54545454545455)(492.666666666667,-5.54545454545455)(477.737373737374,-5.54545454545455)(462.808080808081,-5.54545454545455)(447.878787878788,-5.54545454545455)(432.949494949495,-5.54545454545455)(418.020202020202,-5.54545454545455)(403.090909090909,-5.54545454545455)(388.161616161616,-5.54545454545455)(373.232323232323,-5.54545454545455)(358.30303030303,-5.60606060606061)(350.838383838384,-5.63636363636364)(343.373737373737,-5.66666666666667)(328.444444444444,-5.72727272727273)(313.515151515152,-5.78787878787879)(309.782828282828,-5.81818181818182)(298.585858585859,-5.95454545454546)(296.097643097643,-6)(291.121212121212,-6.18181818181818)(296.097643097643,-6.36363636363636)(298.585858585859,-6.40909090909091)(306.050505050505,-6.54545454545455)(313.515151515152,-6.63636363636364)(320.979797979798,-6.72727272727273)(328.444444444444,-6.81818181818182)(339.641414141414,-6.90909090909091)(343.373737373737,-6.93939393939394)(358.30303030303,-7.06060606060606)(365.767676767677,-7.09090909090909)(373.232323232323,-7.12121212121212)(388.161616161616,-7.18181818181818)(403.090909090909,-7.18181818181818)(418.020202020202,-7.24242424242424)(432.949494949495,-7.24242424242424)(447.878787878788,-7.24242424242424)(462.808080808081,-7.18181818181818)(477.737373737374,-7.18181818181818)(492.666666666667,-7.12121212121212)(500.131313131313,-7.09090909090909)(507.59595959596,-7.06060606060606)(522.525252525253,-7)(537.454545454546,-6.93939393939394)(544.919191919192,-6.90909090909091)(552.383838383838,-6.87878787878788)(567.313131313131,-6.81818181818182)(582.242424242424,-6.81818181818182)(597.171717171717,-6.81818181818182)(612.10101010101,-6.81818181818182)(627.030303030303,-6.81818181818182)(641.959595959596,-6.81818181818182)(656.888888888889,-6.81818181818182)(671.818181818182,-6.81818181818182)(686.747474747475,-6.87878787878788)(694.212121212121,-6.90909090909091)(701.676767676768,-6.93939393939394)(716.606060606061,-7)(731.535353535354,-7.06060606060606)(739,-7.09090909090909)(746.464646464646,-7.12121212121212)(761.393939393939,-7.18181818181818)(776.323232323232,-7.24242424242424)(783.787878787879,-7.27272727272727)(791.252525252525,-7.3030303030303)(806.181818181818,-7.36363636363636)(821.111111111111,-7.36363636363636)(836.040404040404,-7.36363636363636)(850.969696969697,-7.36363636363636)(865.89898989899,-7.36363636363636)(880.828282828283,-7.36363636363636)(895.757575757576,-7.3030303030303)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(925.616161616162,-7.18181818181818)(940.545454545455,-7.18181818181818)(955.474747474747,-7.18181818181818)(970.40404040404,-7.18181818181818)(985.333333333333,-7.12121212121212)(992.79797979798,-7.09090909090909)(1000.26262626263,-7.06060606060606)(1015.19191919192,-7)(1030.12121212121,-7)(1045.05050505051,-7)(1059.9797979798,-7)(1074.90909090909,-7)(1089.83838383838,-7)(1104.76767676768,-7)(1119.69696969697,-7)(1134.62626262626,-7)(1149.55555555556,-7)(1164.48484848485,-7)(1179.41414141414,-7)(1194.34343434343,-7)(1209.27272727273,-7)(1224.20202020202,-7)(1239.13131313131,-7)(1254.06060606061,-7)(1268.9898989899,-7.06060606060606)(1276.45454545455,-7.09090909090909)(1283.91919191919,-7.12121212121212)(1298.84848484848,-7.18181818181818)(1313.77777777778,-7.18181818181818)(1328.70707070707,-7.18181818181818)(1343.63636363636,-7.18181818181818)(1358.56565656566,-7.12121212121212)(1366.0303030303,-7.09090909090909)(1373.49494949495,-7.06060606060606)(1388.42424242424,-6.93939393939394)(1395.88888888889,-6.90909090909091)(1403.35353535354,-6.87878787878788)(1418.28282828283,-6.75757575757576)(1425.74747474747,-6.72727272727273)(1433.21212121212,-6.6969696969697)(1448.14141414141,-6.63636363636364)(1463.07070707071,-6.63636363636364)(1478,-6.63636363636364)(1478.00012440663,-6.72727272727273)(1478.00037321366,-6.90909090909091)(1478.00037321366,-7.09090909090909)(1478.00037321366,-7.27272727272727)(1478.00037321366,-7.45454545454546)(1478.00037321366,-7.63636363636364)(1478.00037321366,-7.81818181818182)(1478.00037321366,-8)(1478.00037321366,-8.18181818181818)(1478.00037321366,-8.36363636363636)(1478.00037321366,-8.54545454545455)(1478.00037321366,-8.72727272727273)(1478.00037321366,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00037321366,-9.27272727272727)(1478.00037321366,-9.45454545454546)(1478.00037321366,-9.63636363636364)(1478.00037321366,-9.81818181818182)(1478.00037321366,-10)(1478.00037321366,-10.1818181818182)(1478.00037321366,-10.3636363636364)(1478.00037321366,-10.5454545454545)(1478.00037321366,-10.7272727272727)(1478.00037321366,-10.9090909090909)(1478.00037321366,-11.0909090909091)(1478.00037321366,-11.2727272727273)(1478.00037321366,-11.4545454545455)(1478.00037321366,-11.6363636363636)(1478.00037321366,-11.8181818181818)(1478.00037321366,-12)(1478.00012440663,-12.1818181818182)(1478,-12.2727272727273)(1463.07070707071,-12.2727272727273)(1448.14141414141,-12.2727272727273)(1433.21212121212,-12.2727272727273)(1418.28282828283,-12.2727272727273)(1403.35353535354,-12.2727272727273)(1388.42424242424,-12.2727272727273)(1373.49494949495,-12.2121212121212)(1366.0303030303,-12.1818181818182)(1358.56565656566,-12.1515151515152)(1343.63636363636,-12.0909090909091)(1328.70707070707,-12.030303030303)(1324.97474747475,-12)(1313.77777777778,-11.9090909090909)(1306.31313131313,-11.8181818181818)(1298.84848484848,-11.6818181818182)(1296.36026936027,-11.6363636363636)(1286.40740740741,-11.4545454545455)(1283.91919191919,-11.3636363636364)(1281.43097643098,-11.2727272727273)(1268.9898989899,-11.1212121212121)(1265.25757575758,-11.0909090909091)(1254.06060606061,-11)(1239.13131313131,-11)(1224.20202020202,-11)(1209.27272727273,-11)(1194.34343434343,-11.0606060606061)(1186.87878787879,-11.0909090909091)(1179.41414141414,-11.1212121212121)(1164.48484848485,-11.2424242424242)(1157.0202020202,-11.2727272727273)(1149.55555555556,-11.3030303030303)(1134.62626262626,-11.4242424242424)(1127.16161616162,-11.4545454545455)(1119.69696969697,-11.4848484848485)(1104.76767676768,-11.5454545454545)(1089.83838383838,-11.4848484848485)(1082.37373737374,-11.4545454545455)(1074.90909090909,-11.4242424242424)(1059.9797979798,-11.3030303030303)(1052.51515151515,-11.2727272727273)(1045.05050505051,-11.2424242424242)(1030.12121212121,-11.1212121212121)(1026.38888888889,-11.0909090909091)(1015.19191919192,-11)(1007.72727272727,-10.9090909090909)(1000.26262626263,-10.8181818181818)(992.79797979798,-10.7272727272727)(985.333333333333,-10.6363636363636)(974.136363636364,-10.5454545454545)(970.40404040404,-10.5151515151515)(955.474747474747,-10.3939393939394)(948.010101010101,-10.3636363636364)(940.545454545455,-10.3333333333333)(925.616161616162,-10.2727272727273)(910.686868686869,-10.2727272727273)(895.757575757576,-10.2727272727273)(880.828282828283,-10.2727272727273)(865.89898989899,-10.2121212121212)(858.434343434343,-10.1818181818182)(850.969696969697,-10.1515151515152)(836.040404040404,-10.0909090909091)(821.111111111111,-10.030303030303)(813.646464646465,-10)(806.181818181818,-9.96969696969697)(791.252525252525,-9.84848484848485)(783.787878787879,-9.81818181818182)(776.323232323232,-9.78787878787879)(761.393939393939,-9.66666666666667)(753.929292929293,-9.63636363636364)(746.464646464646,-9.60606060606061)(731.535353535354,-9.48484848484848)(724.070707070707,-9.45454545454546)(716.606060606061,-9.42424242424243)(701.676767676768,-9.36363636363636)(686.747474747475,-9.36363636363636)(671.818181818182,-9.36363636363636)(656.888888888889,-9.36363636363636)(641.959595959596,-9.36363636363636)(627.030303030303,-9.36363636363636)(612.10101010101,-9.36363636363636)(597.171717171717,-9.36363636363636)(582.242424242424,-9.36363636363636)(567.313131313131,-9.36363636363636)(552.383838383838,-9.42424242424243)(544.919191919192,-9.45454545454546)(537.454545454546,-9.48484848484848)(522.525252525253,-9.60606060606061)(515.060606060606,-9.63636363636364)(507.59595959596,-9.66666666666667)(492.666666666667,-9.78787878787879)(485.20202020202,-9.81818181818182)(477.737373737374,-9.84848484848485)(462.808080808081,-9.96969696969697)(455.343434343434,-10)(447.878787878788,-10.030303030303)(432.949494949495,-10.0909090909091)(418.020202020202,-10.0909090909091)(403.090909090909,-10.0909090909091)(388.161616161616,-10.1515151515152)(380.69696969697,-10.1818181818182)(373.232323232323,-10.2121212121212)(358.30303030303,-10.2727272727273)(343.373737373737,-10.2727272727273)(328.444444444444,-10.2727272727273)(313.515151515152,-10.2727272727273)(298.585858585859,-10.2727272727273)(283.656565656566,-10.2727272727273)(268.727272727273,-10.2727272727273)(253.79797979798,-10.2727272727273)(238.868686868687,-10.3333333333333)(231.40404040404,-10.3636363636364)(223.939393939394,-10.3939393939394)(209.010101010101,-10.4545454545455)(194.080808080808,-10.4545454545455)(179.151515151515,-10.5151515151515)(171.686868686869,-10.5454545454545)(164.222222222222,-10.5757575757576)(149.292929292929,-10.6969696969697)(145.560606060606,-10.7272727272727)(134.363636363636,-10.8181818181818)(126.89898989899,-10.9090909090909)(119.434343434343,-11)(111.969696969697,-11.0909090909091)(104.505050505051,-11.1818181818182)(97.040404040404,-11.2727272727273)(89.5757575757576,-11.4090909090909)(87.0875420875421,-11.4545454545455)(82.1111111111111,-11.6363636363636)(82.1111111111111,-11.8181818181818)(82.1111111111111,-12)(82.1111111111111,-12.1818181818182)(82.1111111111111,-12.3636363636364)(87.0875420875421,-12.5454545454545)(89.5757575757576,-12.6363636363636)(92.0639730639731,-12.7272727272727)(102.016835016835,-12.9090909090909)(104.505050505051,-13)(106.993265993266,-13.0909090909091)(116.946127946128,-13.2727272727273)(119.434343434343,-13.3181818181818)(126.89898989899,-13.4545454545455)(134.363636363636,-13.5454545454545)(145.560606060606,-13.6363636363636)(149.292929292929,-13.6666666666667)(164.222222222222,-13.7878787878788)(171.686868686869,-13.8181818181818)(179.151515151515,-13.8484848484849)(194.080808080808,-13.969696969697)(201.545454545455,-14)(209.010101010101,-14.030303030303)(223.939393939394,-14.0909090909091)(238.868686868687,-14.0909090909091)(253.79797979798,-14.0909090909091)(268.727272727273,-14.0909090909091)(283.656565656566,-14.0909090909091)(298.585858585859,-14.0909090909091)(313.515151515152,-14.0909090909091)(328.444444444444,-14.0909090909091)(343.373737373737,-14.0909090909091)(358.30303030303,-14.0909090909091)(373.232323232323,-14.0909090909091)(388.161616161616,-14.0909090909091)(403.090909090909,-14.030303030303)(410.555555555556,-14)(418.020202020202,-13.969696969697)(432.949494949495,-13.9090909090909)(447.878787878788,-13.9090909090909)(462.808080808081,-13.8484848484849)(470.272727272727,-13.8181818181818)(477.737373737374,-13.7878787878788)(492.666666666667,-13.7272727272727)(507.59595959596,-13.7272727272727)(522.525252525253,-13.6666666666667)(529.989898989899,-13.6363636363636)(537.454545454546,-13.6060606060606)(552.383838383838,-13.5454545454545)(567.313131313131,-13.5454545454545)(582.242424242424,-13.4848484848485)(589.707070707071,-13.4545454545455)(597.171717171717,-13.4242424242424)(612.10101010101,-13.3636363636364)(627.030303030303,-13.3030303030303)(634.494949494949,-13.2727272727273)(641.959595959596,-13.2424242424242)(656.888888888889,-13.1818181818182)(671.818181818182,-13.1212121212121)(679.282828282828,-13.0909090909091)(686.747474747475,-13.0606060606061)(701.676767676768,-13)(716.606060606061,-12.9393939393939)(724.070707070707,-12.9090909090909)(731.535353535354,-12.8787878787879)(746.464646464646,-12.8181818181818)(761.393939393939,-12.7575757575758)(768.858585858586,-12.7272727272727)(776.323232323232,-12.6969696969697)(791.252525252525,-12.6363636363636)(806.181818181818,-12.6363636363636)(821.111111111111,-12.5757575757576)(828.575757575758,-12.5454545454545)(836.040404040404,-12.5151515151515)(850.969696969697,-12.4545454545455)(865.89898989899,-12.4545454545455)(880.828282828283,-12.4545454545455)(895.757575757576,-12.4545454545455)(910.686868686869,-12.3939393939394)(918.151515151515,-12.3636363636364)(925.616161616162,-12.3333333333333)(940.545454545455,-12.2727272727273)(955.474747474747,-12.2727272727273)(970.40404040404,-12.2727272727273)(985.333333333333,-12.2727272727273)(1000.26262626263,-12.2121212121212)(1007.72727272727,-12.1818181818182)(1015.19191919192,-12.1515151515152)(1030.12121212121,-12.0909090909091)(1045.05050505051,-12.0909090909091)(1059.9797979798,-12.030303030303)(1067.44444444444,-12)(1074.90909090909,-11.969696969697)(1089.83838383838,-11.9090909090909)(1104.76767676768,-11.9090909090909)(1119.69696969697,-11.969696969697)(1123.42929292929,-12)(1134.62626262626,-12.1363636363636)(1137.11447811448,-12.1818181818182)(1142.09090909091,-12.3636363636364)(1142.09090909091,-12.5454545454545)(1137.11447811448,-12.7272727272727)(1134.62626262626,-12.8181818181818)(1132.13804713805,-12.9090909090909)(1122.18518518519,-13.0909090909091)(1119.69696969697,-13.1818181818182)(1117.20875420875,-13.2727272727273)(1107.25589225589,-13.4545454545455)(1104.76767676768,-13.5454545454545)(1102.27946127946,-13.6363636363636)(1097.30303030303,-13.8181818181818)(1097.30303030303,-14)(1092.3265993266,-14.1818181818182)(1089.83838383838,-14.2727272727273)(1087.35016835017,-14.3636363636364)(1087.35016835017,-14.5454545454545)(1089.83838383838,-14.6363636363636)(1092.3265993266,-14.7272727272727)(1097.30303030303,-14.9090909090909)(1097.30303030303,-15.0909090909091)(1102.27946127946,-15.2727272727273)(1104.76767676768,-15.3181818181818)(1112.23232323232,-15.4545454545455)(1119.69696969697,-15.5909090909091)(1122.18518518519,-15.6363636363636)(1132.13804713805,-15.8181818181818)(1134.62626262626,-15.8636363636364)(1142.09090909091,-16)(1149.55555555556,-16.0909090909091)(1160.75252525253,-16.1818181818182)(1164.48484848485,-16.2121212121212)(1179.41414141414,-16.3333333333333)(1183.14646464646,-16.3636363636364)(1194.34343434343,-16.4545454545455)(1205.5404040404,-16.5454545454545)(1209.27272727273,-16.5757575757576)(1224.20202020202,-16.6969696969697)(1231.66666666667,-16.7272727272727)(1239.13131313131,-16.7575757575758)(1254.06060606061,-16.8181818181818)(1268.9898989899,-16.8787878787879)(1276.45454545455,-16.9090909090909)(1283.91919191919,-16.9393939393939)(1298.84848484848,-17)(1313.77777777778,-17.0606060606061)(1321.24242424242,-17.0909090909091)(1328.70707070707,-17.1212121212121)(1343.63636363636,-17.1818181818182)(1358.56565656566,-17.1818181818182)(1373.49494949495,-17.1818181818182)(1388.42424242424,-17.1818181818182)(1403.35353535354,-17.1818181818182)(1418.28282828283,-17.2424242424242)(1425.74747474747,-17.2727272727273)(1433.21212121212,-17.3030303030303)(1448.14141414141,-17.3636363636364)(1463.07070707071,-17.3636363636364)(1478,-17.3636363636364)(1478.00012440663,-17.4545454545455)(1478.00037321366,-17.6363636363636)(1478.00037321366,-17.8181818181818)(1478.00037321366,-18)(1478,-18.0000045452273)(1463.07070707071,-18.0000045452273)(1448.14141414141,-18.0000045452273)(1433.21212121212,-18.0000045452273)(1418.28282828283,-18.0000045452273)(1403.35353535354,-18.0000045452273)(1388.42424242424,-18.0000045452273)(1373.49494949495,-18.0000045452273)(1358.56565656566,-18.0000045452273)(1343.63636363636,-18.0000045452273)(1328.70707070707,-18.0000045452273)(1313.77777777778,-18.0000045452273)(1298.84848484848,-18.0000045452273)(1283.91919191919,-18.0000045452273)(1268.9898989899,-18.0000045452273)(1254.06060606061,-18.0000045452273)(1239.13131313131,-18.0000045452273)(1224.20202020202,-18.0000045452273)(1209.27272727273,-18.0000045452273)(1194.34343434343,-18.0000045452273)(1179.41414141414,-18.0000045452273)(1164.48484848485,-18.0000045452273)(1149.55555555556,-18.0000045452273)(1134.62626262626,-18.0000045452273)(1119.69696969697,-18.0000045452273)(1104.76767676768,-18.0000045452273)(1089.83838383838,-18.0000045452273)(1074.90909090909,-18.0000045452273)(1059.9797979798,-18.0000045452273)(1045.05050505051,-18.0000045452273)(1030.12121212121,-18.0000045452273)(1015.19191919192,-18.0000045452273)(1000.26262626263,-18.0000045452273)(985.333333333333,-18.0000045452273)(970.40404040404,-18.0000045452273)(955.474747474747,-18.0000045452273)(940.545454545455,-18.0000045452273)(925.616161616162,-18.0000045452273)(910.686868686869,-18.0000045452273)(895.757575757576,-18.0000045452273)(880.828282828283,-18.0000045452273)(865.89898989899,-18.0000045452273)(850.969696969697,-18.0000045452273)(836.040404040404,-18.0000045452273)(821.111111111111,-18.0000045452273)(806.181818181818,-18.0000045452273)(791.252525252525,-18.0000045452273)(776.323232323232,-18.0000045452273)(761.393939393939,-18.0000045452273)(746.464646464646,-18.0000045452273)(731.535353535354,-18.0000045452273)(716.606060606061,-18.0000045452273)(701.676767676768,-18.0000045452273)(686.747474747475,-18.0000045452273)(671.818181818182,-18.0000045452273)(656.888888888889,-18.0000045452273)(641.959595959596,-18.0000045452273)(627.030303030303,-18.0000045452273)(612.10101010101,-18.0000045452273)(597.171717171717,-18.0000045452273)(582.242424242424,-18.0000045452273)(567.313131313131,-18.0000045452273)(552.383838383838,-18.0000045452273)(537.454545454546,-18.0000045452273)(522.525252525253,-18.0000045452273)(507.59595959596,-18.0000045452273)(492.666666666667,-18.0000045452273)(477.737373737374,-18.0000045452273)(462.808080808081,-18.0000045452273)(447.878787878788,-18.0000045452273)(432.949494949495,-18.0000045452273)(418.020202020202,-18.000001515101)(410.555555555556,-18)(410.555555555556,-17.8181818181818)(410.555555555556,-17.6363636363636)(405.579124579125,-17.4545454545455)(403.090909090909,-17.3636363636364)(400.602693602694,-17.2727272727273)(390.649831649832,-17.0909090909091)(388.161616161616,-17)(385.673400673401,-16.9090909090909)(375.720538720539,-16.7272727272727)(373.232323232323,-16.6818181818182)(365.767676767677,-16.5454545454545)(358.30303030303,-16.4545454545455)(350.838383838384,-16.3636363636364)(343.373737373737,-16.2727272727273)(335.909090909091,-16.1818181818182)(328.444444444444,-16.0909090909091)(320.979797979798,-16)(313.515151515152,-15.9090909090909)(306.050505050505,-15.8181818181818)(298.585858585859,-15.7272727272727)(291.121212121212,-15.6363636363636)(283.656565656566,-15.5454545454545)(272.459595959596,-15.4545454545455)(268.727272727273,-15.4242424242424)(253.79797979798,-15.3030303030303)(246.333333333333,-15.2727272727273)(238.868686868687,-15.2424242424242)(223.939393939394,-15.1212121212121)(216.474747474747,-15.0909090909091)(209.010101010101,-15.0606060606061)(194.080808080808,-15)(179.151515151515,-15)(164.222222222222,-15)(149.292929292929,-15)(134.363636363636,-15)(119.434343434343,-15)(104.505050505051,-15)(89.5757575757576,-15)(74.6464646464647,-15)(59.7171717171717,-15)(44.7878787878788,-15)(29.8585858585859,-15)(14.9292929292929,-15)(0,-15)(-0.000124406627521346,-14.9090909090909)(-0.000373213662548569,-14.7272727272727)(-0.000373213662548569,-14.5454545454545)(-0.000373213662548569,-14.3636363636364)(-0.000373213662548569,-14.1818181818182)(-0.000373213662548569,-14)(-0.000373213662548569,-13.8181818181818)(-0.000373213662548569,-13.6363636363636)(-0.000373213662548569,-13.4545454545455)(-0.000373213662548569,-13.2727272727273)(-0.000373213662548569,-13.0909090909091)(-0.000373213662548569,-12.9090909090909)(-0.000373213662548569,-12.7272727272727)(-0.000373213662548569,-12.5454545454545)(-0.000373213662548569,-12.3636363636364)(-0.000373213662548569,-12.1818181818182)(-0.000373213662548569,-12)(-0.000373213662548569,-11.8181818181818)(-0.000373213662548569,-11.6363636363636)(-0.000373213662548569,-11.4545454545455)(-0.000373213662548569,-11.2727272727273)(-0.000373213662548569,-11.0909090909091)(-0.000373213662548569,-10.9090909090909)(-0.000373213662548569,-10.7272727272727)(-0.000373213662548569,-10.5454545454545)(-0.000373213662548569,-10.3636363636364)(-0.000373213662548569,-10.1818181818182)(-0.000373213662548569,-10)(-0.000373213662548569,-9.81818181818182)(-0.000124406627521346,-9.63636363636364)(0,-9.54545454545455)(14.9292929292929,-9.54545454545455)(29.8585858585859,-9.54545454545455)(44.7878787878788,-9.48484848484848)(48.520202020202,-9.45454545454546)(59.7171717171717,-9.36363636363636)(67.1818181818182,-9.27272727272727)(74.6464646464647,-9.13636363636364)(77.1346801346801,-9.09090909090909)(87.0875420875421,-8.90909090909091)(87.0875420875421,-8.72727272727273)(87.0875420875421,-8.54545454545455)(74.6464646464647,-8.39393939393939)(72.1582491582492,-8.36363636363636)(59.7171717171717,-8.21212121212121)(52.2525252525253,-8.18181818181818)(44.7878787878788,-8.15151515151515)(29.8585858585859,-8.03030303030303)(22.3939393939394,-8)(14.9292929292929,-7.96969696969697)(0,-7.90909090909091)(-0.000124406627521346,-7.81818181818182)(-0.000373213662548569,-7.63636363636364)(-0.000373213662548569,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000124406627521346,-7.09090909090909)(0,-7)(14.9292929292929,-6.93939393939394)(22.3939393939394,-6.90909090909091)(29.8585858585859,-6.87878787878788)(44.7878787878788,-6.81818181818182)(59.7171717171717,-6.75757575757576)(67.1818181818182,-6.72727272727273)(74.6464646464647,-6.6969696969697)(89.5757575757576,-6.63636363636364)(104.505050505051,-6.57575757575758)(111.969696969697,-6.54545454545455)(119.434343434343,-6.51515151515151)(134.363636363636,-6.45454545454545)(149.292929292929,-6.39393939393939)(156.757575757576,-6.36363636363636)(164.222222222222,-6.33333333333333)(179.151515151515,-6.21212121212121)(186.616161616162,-6.18181818181818)(194.080808080808,-6.15151515151515)(206.521885521886,-6)(209.010101010101,-5.95454545454546)(216.474747474747,-5.81818181818182)(216.474747474747,-5.63636363636364)(211.498316498317,-5.45454545454546)(209.010101010101,-5.40909090909091)(201.545454545455,-5.27272727272727)(194.080808080808,-5.18181818181818)(186.616161616162,-5.09090909090909)(179.151515151515,-5)(167.954545454545,-4.90909090909091)(164.222222222222,-4.87878787878788)(149.292929292929,-4.75757575757576)(141.828282828283,-4.72727272727273)(134.363636363636,-4.6969696969697)(119.434343434343,-4.57575757575758)(111.969696969697,-4.54545454545455)(104.505050505051,-4.51515151515151)(89.5757575757576,-4.45454545454545)(74.6464646464647,-4.39393939393939)(67.1818181818182,-4.36363636363636)(59.7171717171717,-4.33333333333333)(44.7878787878788,-4.27272727272727)(29.8585858585859,-4.27272727272727)(14.9292929292929,-4.27272727272727)(0,-4.27272727272727)(-0.000124406627521346,-4.18181818181818)(-0.000373213662548569,-4)(-0.000373213662548569,-3.81818181818182)(-0.000373213662548569,-3.63636363636364)(-0.000373213662548569,-3.45454545454546)(-0.000373213662548569,-3.27272727272727)(-0.000373213662548569,-3.09090909090909)(-0.000373213662548569,-2.90909090909091)(-0.000373213662548569,-2.72727272727273)(-0.000124406627521346,-2.54545454545455)(0,-2.45454545454545)};

%\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1298.84848484848,-8.68181818181818)(1301.3367003367,-8.72727272727273)(1306.31313131313,-8.90909090909091)(1301.3367003367,-9.09090909090909)(1298.84848484848,-9.13636363636364)(1291.38383838384,-9.27272727272727)(1283.91919191919,-9.36363636363636)(1272.72222222222,-9.45454545454546)(1268.9898989899,-9.48484848484848)(1254.06060606061,-9.54545454545455)(1239.13131313131,-9.60606060606061)(1231.66666666667,-9.63636363636364)(1224.20202020202,-9.66666666666667)(1209.27272727273,-9.72727272727273)(1194.34343434343,-9.72727272727273)(1179.41414141414,-9.72727272727273)(1164.48484848485,-9.72727272727273)(1149.55555555556,-9.72727272727273)(1134.62626262626,-9.66666666666667)(1127.16161616162,-9.63636363636364)(1119.69696969697,-9.60606060606061)(1104.76767676768,-9.54545454545455)(1089.83838383838,-9.54545454545455)(1074.90909090909,-9.48484848484848)(1067.44444444444,-9.45454545454546)(1059.9797979798,-9.42424242424243)(1045.05050505051,-9.3030303030303)(1037.58585858586,-9.27272727272727)(1030.12121212121,-9.24242424242424)(1017.68013468013,-9.09090909090909)(1015.19191919192,-9.06060606060606)(1002.75084175084,-8.90909090909091)(1002.75084175084,-8.72727272727273)(1011.4595959596,-8.54545454545455)(1015.19191919192,-8.51515151515152)(1030.12121212121,-8.39393939393939)(1037.58585858586,-8.36363636363636)(1045.05050505051,-8.33333333333333)(1059.9797979798,-8.27272727272727)(1074.90909090909,-8.21212121212121)(1082.37373737374,-8.18181818181818)(1089.83838383838,-8.15151515151515)(1104.76767676768,-8.09090909090909)(1119.69696969697,-8.09090909090909)(1134.62626262626,-8.09090909090909)(1149.55555555556,-8.09090909090909)(1164.48484848485,-8.09090909090909)(1179.41414141414,-8.09090909090909)(1194.34343434343,-8.09090909090909)(1209.27272727273,-8.15151515151515)(1216.73737373737,-8.18181818181818)(1224.20202020202,-8.21212121212121)(1239.13131313131,-8.27272727272727)(1254.06060606061,-8.33333333333333)(1261.52525252525,-8.36363636363636)(1268.9898989899,-8.39393939393939)(1283.91919191919,-8.51515151515152)(1287.65151515152,-8.54545454545455)(1298.84848484848,-8.68181818181818)};

\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_100.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478.00008294006,-8.54545454545455)(1478.00033175469,-8.72727272727273)(1478.00058056104,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00066349464,-9.27272727272727)(1478.00066349464,-9.45454545454546)(1478.00066349464,-9.63636363636364)(1478.00074642733,-9.81818181818182)(1478.00049762651,-10)(1478.0002488174,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478.0002488174,-17.4545454545455)(1478.00049762651,-17.6363636363636)(1478.00074642733,-17.8181818181818)(1478.00074642733,-18)(1478,-18.0000090904546)(1463.07070707071,-18.0000090904546)(1448.14141414141,-18.0000090904546)(1433.21212121212,-18.0000090904546)(1418.28282828283,-18.0000090904546)(1403.35353535354,-18.000008080449)(1388.42424242424,-18.0000070704321)(1373.49494949495,-18.0000040403143)(1358.56565656566,-18.0000020201796)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(-0.000248817401863321,-8)(-0.000497626510092015,-7.81818181818182)(-0.000746427325097138,-7.63636363636364)(-0.000746427325097138,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000497626510092015,-7.09090909090909)(-0.000248817401863321,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(-0.000248817401863321,-3.81818181818182)(-0.000497626510092015,-3.63636363636364)(-0.000746427325097138,-3.45454545454546)(-0.000746427325097138,-3.27272727272727)(-0.000746427325097138,-3.09090909090909)(-0.000497626510092015,-2.90909090909091)(-0.000248817401863321,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-7)(14.9292929292929,-7)(29.8585858585859,-7)(44.7878787878788,-7)(59.7171717171717,-7)(74.6464646464647,-7)(89.5757575757576,-7)(104.505050505051,-7)(119.434343434343,-7)(134.363636363636,-7)(149.292929292929,-7)(164.222222222222,-7.06060606060606)(171.686868686869,-7.09090909090909)(179.151515151515,-7.12121212121212)(194.080808080808,-7.18181818181818)(209.010101010101,-7.18181818181818)(223.939393939394,-7.18181818181818)(238.868686868687,-7.18181818181818)(253.79797979798,-7.24242424242424)(261.262626262626,-7.27272727272727)(268.727272727273,-7.3030303030303)(283.656565656566,-7.36363636363636)(298.585858585859,-7.36363636363636)(313.515151515152,-7.36363636363636)(328.444444444444,-7.36363636363636)(343.373737373737,-7.36363636363636)(358.30303030303,-7.36363636363636)(373.232323232323,-7.36363636363636)(388.161616161616,-7.36363636363636)(403.090909090909,-7.36363636363636)(418.020202020202,-7.34090909090909)(432.949494949495,-7.34090909090909)(447.878787878788,-7.34090909090909)(462.808080808081,-7.3030303030303)(470.272727272727,-7.27272727272727)(477.737373737374,-7.22727272727273)(492.666666666667,-7.18181818181818)(507.59595959596,-7.18181818181818)(522.525252525253,-7.18181818181818)(537.454545454546,-7.20454545454546)(552.383838383838,-7.18181818181818)(567.313131313131,-7.20454545454546)(582.242424242424,-7.15909090909091)(597.171717171717,-7.18181818181818)(612.10101010101,-7.15909090909091)(627.030303030303,-7.24242424242424)(634.494949494949,-7.27272727272727)(641.959595959596,-7.3030303030303)(656.888888888889,-7.42424242424243)(660.621212121212,-7.45454545454546)(671.818181818182,-7.54545454545455)(679.282828282828,-7.63636363636364)(686.747474747475,-7.77272727272727)(689.23569023569,-7.81818181818182)(701.676767676768,-7.96969696969697)(705.409090909091,-8)(716.606060606061,-8.09090909090909)(731.535353535354,-8.09090909090909)(746.464646464646,-8.09090909090909)(761.393939393939,-8.09090909090909)(776.323232323232,-8.03030303030303)(791.252525252525,-8.02272727272727)(793.740740740741,-8)(806.181818181818,-7.88636363636364)(817.378787878788,-7.81818181818182)(821.111111111111,-7.77272727272727)(832.308080808081,-7.63636363636364)(836.040404040404,-7.60606060606061)(850.969696969697,-7.48484848484849)(854.70202020202,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.36363636363636)(895.757575757576,-7.29545454545455)(910.686868686869,-7.29545454545455)(914.419191919192,-7.27272727272727)(925.616161616162,-7.18181818181818)(940.545454545455,-7.18181818181818)(955.474747474748,-7.15909090909091)(970.40404040404,-7.24242424242424)(985.333333333333,-7.24242424242424)(1000.26262626263,-7.18181818181818)(1011.4595959596,-7.09090909090909)(1015.19191919192,-7.06060606060606)(1030.12121212121,-7.06060606060606)(1037.58585858586,-7.09090909090909)(1045.05050505051,-7.11363636363636)(1059.9797979798,-7.14545454545455)(1074.90909090909,-7.20454545454546)(1089.83838383838,-7.25)(1093.57070707071,-7.27272727272727)(1104.76767676768,-7.36363636363636)(1119.69696969697,-7.36363636363636)(1127.16161616162,-7.45454545454546)(1134.62626262626,-7.5)(1149.55555555556,-7.54545454545455)(1164.48484848485,-7.61363636363636)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.65151515151515)(1194.34343434343,-7.68181818181818)(1209.27272727273,-7.65151515151515)(1224.20202020202,-7.65151515151515)(1231.66666666667,-7.63636363636364)(1239.13131313131,-7.61363636363636)(1246.59595959596,-7.63636363636364)(1254.06060606061,-7.65909090909091)(1268.9898989899,-7.66666666666667)(1283.91919191919,-7.72727272727273)(1298.84848484848,-7.72727272727273)(1313.77777777778,-7.77272727272727)(1328.70707070707,-7.77272727272727)(1336.17171717172,-7.81818181818182)(1343.63636363636,-7.84090909090909)(1358.56565656566,-7.84090909090909)(1373.49494949495,-7.96969696969697)(1380.9595959596,-8)(1388.42424242424,-8.09090909090909)(1395.88888888889,-8.18181818181818)(1403.35353535354,-8.21212121212121)(1418.28282828283,-8.27272727272727)(1429.4797979798,-8.36363636363636)(1433.21212121212,-8.38636363636364)(1448.14141414141,-8.51515151515152)(1451.87373737374,-8.54545454545455)(1463.07070707071,-8.63636363636364)(1474.26767676768,-8.72727272727273)(1478,-8.75757575757576)(1478.00020734323,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00029027891,-9.27272727272727)(1478.00029027891,-9.45454545454546)(1478.00029027891,-9.63636363636364)(1478.00037321366,-9.81818181818182)(1478.00012440663,-10)(1478,-10.0909090909091)(1463.07070707071,-10.0909090909091)(1448.14141414141,-10.1515151515152)(1440.67676767677,-10.1818181818182)(1433.21212121212,-10.2121212121212)(1418.28282828283,-10.2272727272727)(1403.35353535354,-10.2272727272727)(1388.42424242424,-10.2272727272727)(1373.49494949495,-10.3409090909091)(1358.56565656566,-10.3409090909091)(1343.63636363636,-10.3409090909091)(1328.70707070707,-10.2727272727273)(1313.77777777778,-10.2727272727273)(1298.84848484848,-10.2727272727273)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2272727272727)(1254.06060606061,-10.2727272727273)(1239.13131313131,-10.2727272727273)(1224.20202020202,-10.2954545454545)(1209.27272727273,-10.2727272727273)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.2121212121212)(1149.55555555556,-10.2121212121212)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.2121212121212)(1104.76767676768,-10.2121212121212)(1089.83838383838,-10.2727272727273)(1082.37373737374,-10.3636363636364)(1074.90909090909,-10.4318181818182)(1059.9797979798,-10.4772727272727)(1045.05050505051,-10.4909090909091)(1030.12121212121,-10.4545454545455)(1015.19191919192,-10.3939393939394)(1011.4595959596,-10.3636363636364)(1000.26262626263,-10.2727272727273)(985.333333333333,-10.2727272727273)(970.40404040404,-10.2727272727273)(955.474747474747,-10.2727272727273)(944.277777777778,-10.1818181818182)(940.545454545455,-10.1636363636364)(925.616161616162,-10.0681818181818)(914.419191919192,-10)(910.686868686869,-9.98484848484848)(903.222222222222,-10)(895.757575757576,-10.030303030303)(888.292929292929,-10)(880.828282828283,-9.98181818181818)(865.89898989899,-9.94545454545455)(850.969696969697,-9.84090909090909)(836.040404040404,-9.84090909090909)(833.552188552189,-9.81818181818182)(822.977272727273,-9.63636363636364)(821.111111111111,-9.61363636363636)(806.181818181818,-9.54545454545455)(791.252525252525,-9.48484848484848)(787.520202020202,-9.45454545454546)(776.323232323232,-9.36363636363636)(768.858585858586,-9.27272727272727)(761.393939393939,-9.13636363636364)(757.661616161616,-9.09090909090909)(746.464646464646,-8.95454545454546)(743.976430976431,-8.90909090909091)(731.535353535354,-8.75757575757576)(727.80303030303,-8.72727272727273)(716.606060606061,-8.63636363636364)(701.676767676768,-8.63636363636364)(686.747474747475,-8.63636363636364)(671.818181818182,-8.6969696969697)(664.353535353535,-8.72727272727273)(656.888888888889,-8.75757575757576)(641.959595959596,-8.81818181818182)(627.030303030303,-8.87878787878788)(619.565656565657,-8.90909090909091)(612.10101010101,-8.93939393939394)(597.171717171717,-9.02272727272727)(582.242424242424,-9.06818181818182)(574.777777777778,-9.09090909090909)(567.313131313131,-9.11363636363636)(552.383838383838,-9.15909090909091)(537.454545454546,-9.18181818181818)(522.525252525253,-9.20454545454546)(507.59595959596,-9.20454545454546)(492.666666666667,-9.25454545454546)(477.737373737374,-9.25)(462.808080808081,-9.20454545454546)(450.367003367003,-9.09090909090909)(447.878787878788,-9.06060606060606)(432.949494949495,-8.93939393939394)(418.020202020202,-8.93939393939394)(410.555555555556,-8.90909090909091)(403.090909090909,-8.86363636363636)(388.161616161616,-8.86363636363636)(373.232323232323,-8.77272727272727)(358.30303030303,-8.81818181818182)(343.373737373737,-8.81818181818182)(328.444444444444,-8.81818181818182)(313.515151515152,-8.84090909090909)(298.585858585859,-8.88636363636364)(291.121212121212,-8.90909090909091)(283.656565656566,-8.93939393939394)(268.727272727273,-9.06060606060606)(264.99494949495,-9.09090909090909)(253.79797979798,-9.18181818181818)(242.60101010101,-9.27272727272727)(238.868686868687,-9.3030303030303)(223.939393939394,-9.42424242424243)(216.474747474747,-9.45454545454546)(209.010101010101,-9.48484848484848)(194.080808080808,-9.60606060606061)(186.616161616162,-9.63636363636364)(179.151515151515,-9.66666666666667)(164.222222222222,-9.72727272727273)(149.292929292929,-9.66666666666667)(145.560606060606,-9.63636363636364)(134.363636363636,-9.5)(131.875420875421,-9.45454545454546)(126.89898989899,-9.27272727272727)(121.922558922559,-9.09090909090909)(119.434343434343,-9)(116.946127946128,-8.90909090909091)(111.969696969697,-8.72727272727273)(106.993265993266,-8.54545454545455)(104.505050505051,-8.5)(97.040404040404,-8.36363636363636)(89.5757575757576,-8.27272727272727)(78.3787878787879,-8.18181818181818)(74.6464646464647,-8.15151515151515)(59.7171717171717,-8.09090909090909)(44.7878787878788,-8.03030303030303)(37.3232323232323,-8)(29.8585858585859,-7.96969696969697)(14.9292929292929,-7.90909090909091)(0,-7.90909090909091)(-0.000124406627521346,-7.81818181818182)(-0.000373213662548569,-7.63636363636364)(-0.000373213662548569,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000124406627521346,-7.09090909090909)(0,-7)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-9)(1407.08585858586,-9.09090909090909)(1414.5505050505,-9.27272727272727)(1410.81818181818,-9.45454545454546)(1403.35353535354,-9.5)(1392.15656565657,-9.63636363636364)(1388.42424242424,-9.65909090909091)(1375.36111111111,-9.81818181818182)(1373.49494949495,-9.86363636363636)(1358.56565656566,-9.95454545454546)(1351.10101010101,-10)(1343.63636363636,-10.0151515151515)(1339.90404040404,-10)(1328.70707070707,-9.90909090909091)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.90909090909091)(1283.91919191919,-9.90909090909091)(1268.9898989899,-9.84848484848485)(1254.06060606061,-9.90909090909091)(1239.13131313131,-9.90909090909091)(1224.20202020202,-9.96969696969697)(1209.27272727273,-9.90909090909091)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.88636363636364)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.88636363636364)(1104.76767676768,-9.88636363636364)(1089.83838383838,-9.88636363636364)(1074.90909090909,-9.95454545454546)(1059.9797979798,-9.95454545454546)(1052.51515151515,-10)(1045.05050505051,-10.030303030303)(1041.31818181818,-10)(1030.12121212121,-9.90909090909091)(1015.19191919192,-9.90909090909091)(1000.26262626263,-9.88636363636364)(985.333333333333,-9.90909090909091)(970.40404040404,-9.90909090909091)(955.474747474747,-9.90909090909091)(944.277777777778,-9.81818181818182)(940.545454545455,-9.79545454545455)(925.616161616162,-9.72727272727273)(910.686868686869,-9.69090909090909)(895.757575757576,-9.70454545454546)(884.560606060606,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.61363636363636)(850.969696969697,-9.50909090909091)(843.505050505051,-9.45454545454546)(836.040404040404,-9.31818181818182)(833.552188552189,-9.27272727272727)(821.111111111111,-9.15909090909091)(815.512626262626,-9.09090909090909)(808.04797979798,-8.90909090909091)(806.181818181818,-8.81818181818182)(804.315656565657,-8.72727272727273)(798.717171717172,-8.54545454545455)(803.693602693603,-8.36363636363636)(806.181818181818,-8.33333333333333)(821.111111111111,-8.20454545454546)(823.599326599327,-8.18181818181818)(836.040404040404,-8.03030303030303)(843.505050505051,-8)(850.969696969697,-7.95454545454546)(862.166666666667,-7.81818181818182)(865.89898989899,-7.8)(880.828282828283,-7.75)(895.757575757576,-7.72727272727273)(910.686868686869,-7.70454545454546)(921.883838383838,-7.63636363636364)(925.616161616162,-7.60606060606061)(940.545454545455,-7.54545454545455)(955.474747474747,-7.48484848484849)(970.40404040404,-7.56818181818182)(985.333333333333,-7.56818181818182)(1000.26262626263,-7.56818181818182)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.48484848484849)(1052.51515151515,-7.45454545454546)(1059.9797979798,-7.43939393939394)(1062.46801346801,-7.45454545454546)(1074.90909090909,-7.56818181818182)(1089.83838383838,-7.61818181818182)(1093.57070707071,-7.63636363636364)(1104.76767676768,-7.72727272727273)(1119.69696969697,-7.72727272727273)(1134.62626262626,-7.8)(1142.09090909091,-7.81818181818182)(1149.55555555556,-7.84090909090909)(1164.48484848485,-7.90909090909091)(1179.41414141414,-7.94545454545455)(1194.34343434343,-7.95454545454546)(1209.27272727273,-7.94545454545455)(1224.20202020202,-7.94545454545455)(1239.13131313131,-7.94545454545455)(1254.06060606061,-7.98484848484848)(1261.52525252525,-8)(1268.9898989899,-8.04545454545455)(1283.91919191919,-8.09090909090909)(1298.84848484848,-8.15151515151515)(1302.58080808081,-8.18181818181818)(1313.77777777778,-8.25)(1328.70707070707,-8.29545454545455)(1339.90404040404,-8.36363636363636)(1343.63636363636,-8.40909090909091)(1351.10101010101,-8.54545454545455)(1358.56565656566,-8.61363636363636)(1373.49494949495,-8.70909090909091)(1377.22727272727,-8.72727272727273)(1388.42424242424,-8.81818181818182)(1399.62121212121,-8.90909090909091)(1403.35353535354,-9)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-2.81818181818182)(14.9292929292929,-2.81818181818182)(29.8585858585859,-2.81818181818182)(44.7878787878788,-2.81818181818182)(59.7171717171717,-2.81818181818182)(74.6464646464647,-2.81818181818182)(89.5757575757576,-2.81818181818182)(104.505050505051,-2.81818181818182)(119.434343434343,-2.81818181818182)(134.363636363636,-2.81818181818182)(149.292929292929,-2.75757575757576)(156.757575757576,-2.72727272727273)(164.222222222222,-2.6969696969697)(179.151515151515,-2.63636363636364)(194.080808080808,-2.57575757575758)(201.545454545455,-2.54545454545455)(209.010101010101,-2.51515151515151)(223.939393939394,-2.45454545454545)(238.868686868687,-2.45454545454545)(253.79797979798,-2.39393939393939)(261.262626262626,-2.36363636363636)(268.727272727273,-2.33333333333333)(283.656565656566,-2.27272727272727)(298.585858585859,-2.21212121212121)(306.050505050505,-2.18181818181818)(313.515151515152,-2.15151515151515)(328.444444444444,-2.09090909090909)(343.373737373737,-2.03030303030303)(350.838383838384,-2)(358.30303030303,-1.96969696969697)(373.232323232323,-1.90909090909091)(388.161616161616,-1.90909090909091)(403.090909090909,-1.90909090909091)(418.020202020202,-1.90909090909091)(432.949494949495,-1.90909090909091)(447.878787878788,-1.90909090909091)(462.808080808081,-1.90909090909091)(477.737373737374,-1.90909090909091)(492.666666666667,-1.96969696969697)(500.131313131313,-2)(507.59595959596,-2.03030303030303)(522.525252525253,-2.15151515151515)(526.257575757576,-2.18181818181818)(537.454545454546,-2.27272727272727)(548.651515151515,-2.36363636363636)(552.383838383838,-2.39393939393939)(567.313131313131,-2.51515151515151)(571.045454545455,-2.54545454545455)(582.242424242424,-2.68181818181818)(584.73063973064,-2.72727272727273)(594.683501683502,-2.90909090909091)(597.171717171717,-3)(599.659932659933,-3.09090909090909)(599.659932659933,-3.27272727272727)(597.171717171717,-3.31818181818182)(589.707070707071,-3.45454545454546)(582.242424242424,-3.54545454545455)(571.045454545455,-3.63636363636364)(567.313131313131,-3.66666666666667)(552.383838383838,-3.78787878787879)(544.919191919192,-3.81818181818182)(537.454545454546,-3.84848484848485)(522.525252525253,-3.90909090909091)(507.59595959596,-3.90909090909091)(492.666666666667,-3.90909090909091)(477.737373737374,-3.96969696969697)(470.272727272727,-4)(462.808080808081,-4.03030303030303)(447.878787878788,-4.09090909090909)(432.949494949495,-4.09090909090909)(418.020202020202,-4.09090909090909)(403.090909090909,-4.09090909090909)(388.161616161616,-4.15151515151515)(380.69696969697,-4.18181818181818)(373.232323232323,-4.21212121212121)(358.30303030303,-4.27272727272727)(343.373737373737,-4.27272727272727)(328.444444444444,-4.27272727272727)(313.515151515152,-4.27272727272727)(298.585858585859,-4.27272727272727)(283.656565656566,-4.27272727272727)(268.727272727273,-4.27272727272727)(253.79797979798,-4.27272727272727)(238.868686868687,-4.21212121212121)(231.40404040404,-4.18181818181818)(223.939393939394,-4.15151515151515)(209.010101010101,-4.09090909090909)(194.080808080808,-4.09090909090909)(179.151515151515,-4.03030303030303)(171.686868686869,-4)(164.222222222222,-3.96969696969697)(149.292929292929,-3.90909090909091)(134.363636363636,-3.84848484848485)(126.89898989899,-3.81818181818182)(119.434343434343,-3.78787878787879)(104.505050505051,-3.72727272727273)(89.5757575757576,-3.72727272727273)(74.6464646464647,-3.72727272727273)(59.7171717171717,-3.72727272727273)(44.7878787878788,-3.72727272727273)(29.8585858585859,-3.72727272727273)(14.9292929292929,-3.72727272727273)(0,-3.72727272727273)(-0.000124406627521346,-3.63636363636364)(-0.000373213662548569,-3.45454545454546)(-0.000373213662548569,-3.27272727272727)(-0.000373213662548569,-3.09090909090909)(-0.000124406627521346,-2.90909090909091)(0,-2.81818181818182)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (462.808080808081,-14.6818181818182)(470.272727272727,-14.5454545454545)(477.737373737374,-14.4545454545455)(488.934343434343,-14.3636363636364)(492.666666666667,-14.3333333333333)(507.59595959596,-14.2727272727273)(522.525252525253,-14.2727272727273)(537.454545454546,-14.2727272727273)(552.383838383838,-14.2727272727273)(567.313131313131,-14.2727272727273)(582.242424242424,-14.2727272727273)(597.171717171717,-14.2727272727273)(612.10101010101,-14.2727272727273)(627.030303030303,-14.2727272727273)(641.959595959596,-14.2727272727273)(656.888888888889,-14.2727272727273)(671.818181818182,-14.2727272727273)(686.747474747475,-14.3181818181818)(690.479797979798,-14.3636363636364)(690.479797979798,-14.5454545454545)(686.747474747475,-14.5757575757576)(671.818181818182,-14.6969696969697)(664.353535353535,-14.7272727272727)(656.888888888889,-14.7575757575758)(641.959595959596,-14.8787878787879)(634.494949494949,-14.9090909090909)(627.030303030303,-14.9393939393939)(612.10101010101,-15.0606060606061)(604.636363636364,-15.0909090909091)(597.171717171717,-15.1212121212121)(582.242424242424,-15.1818181818182)(567.313131313131,-15.2424242424242)(559.848484848485,-15.2727272727273)(552.383838383838,-15.3030303030303)(537.454545454546,-15.3636363636364)(522.525252525253,-15.3636363636364)(507.59595959596,-15.3636363636364)(492.666666666667,-15.3636363636364)(477.737373737374,-15.3030303030303)(474.005050505051,-15.2727272727273)(462.808080808081,-15.1363636363636)(460.319865319865,-15.0909090909091)(455.343434343434,-14.9090909090909)(460.319865319865,-14.7272727272727)(462.808080808081,-14.6818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (462.808080808081,-7.84848484848485)(465.296296296296,-7.81818181818182)(477.737373737374,-7.70454545454546)(488.934343434343,-7.63636363636364)(492.666666666667,-7.60606060606061)(507.59595959596,-7.54545454545455)(522.525252525253,-7.54545454545455)(537.454545454546,-7.52272727272727)(552.383838383838,-7.47727272727273)(567.313131313131,-7.52272727272727)(582.242424242424,-7.54545454545455)(593.439393939394,-7.63636363636364)(597.171717171717,-7.66666666666667)(609.612794612795,-7.81818181818182)(612.10101010101,-7.90909090909091)(614.589225589226,-8)(615.833333333333,-8.18181818181818)(612.10101010101,-8.21212121212121)(599.659932659933,-8.36363636363636)(597.171717171717,-8.40909090909091)(585.974747474747,-8.54545454545455)(582.242424242424,-8.59090909090909)(574.777777777778,-8.72727272727273)(567.313131313131,-8.78181818181818)(552.383838383838,-8.79545454545455)(537.454545454546,-8.81818181818182)(522.525252525253,-8.87878787878788)(507.59595959596,-8.81818181818182)(492.666666666667,-8.86363636363636)(485.20202020202,-8.72727272727273)(477.737373737374,-8.59090909090909)(474.005050505051,-8.54545454545455)(462.808080808081,-8.45454545454545)(455.343434343434,-8.36363636363636)(450.367003367003,-8.18181818181818)(450.367003367003,-8)(462.808080808081,-7.84848484848485)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-17.5454545454545)(1478.00012440663,-17.6363636363636)(1478.00037321366,-17.8181818181818)(1478.00037321366,-18)(1478,-18.0000045452273)(1463.07070707071,-18.0000045452273)(1448.14141414141,-18.0000045452273)(1433.21212121212,-18.0000045452273)(1418.28282828283,-18.0000045452273)(1403.35353535354,-18.0000035351964)(1388.42424242424,-18.0000025251543)(1375.98316498317,-18)(1388.42424242424,-17.8484848484848)(1395.88888888889,-17.8181818181818)(1403.35353535354,-17.7878787878788)(1418.28282828283,-17.7272727272727)(1433.21212121212,-17.7272727272727)(1448.14141414141,-17.6666666666667)(1455.60606060606,-17.6363636363636)(1463.07070707071,-17.6060606060606)(1478,-17.5454545454545)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_120.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478.00008294006,-8.54545454545455)(1478.00033175469,-8.72727272727273)(1478.00058056104,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00066349464,-9.27272727272727)(1478.00066349464,-9.45454545454546)(1478.00066349464,-9.63636363636364)(1478.00074642733,-9.81818181818182)(1478.00049762651,-10)(1478.0002488174,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478.0002488174,-17.4545454545455)(1478.00049762651,-17.6363636363636)(1478.00074642733,-17.8181818181818)(1478.00074642733,-18)(1478,-18.0000090904546)(1463.07070707071,-18.0000090904546)(1448.14141414141,-18.0000090904546)(1433.21212121212,-18.0000090904546)(1418.28282828283,-18.0000090904546)(1403.35353535354,-18.000008080449)(1388.42424242424,-18.0000070704321)(1373.49494949495,-18.0000040403143)(1358.56565656566,-18.0000020201796)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(-8.29400554937089e-05,-7.81818181818182)(-0.000331754692765745,-7.63636363636364)(-0.000331754692765745,-7.45454545454546)(-0.000248817401863321,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.75757575757576)(1478.00020734323,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00029027891,-9.27272727272727)(1478.00029027891,-9.45454545454546)(1478.00029027891,-9.63636363636364)(1478.00037321366,-9.81818181818182)(1478.00012440663,-10)(1478,-10.0909090909091)(1463.07070707071,-10.0909090909091)(1448.14141414141,-10.1515151515152)(1440.67676767677,-10.1818181818182)(1433.21212121212,-10.2121212121212)(1418.28282828283,-10.2272727272727)(1403.35353535354,-10.2272727272727)(1388.42424242424,-10.2727272727273)(1373.49494949495,-10.3454545454545)(1358.56565656566,-10.3454545454545)(1343.63636363636,-10.3409090909091)(1328.70707070707,-10.2727272727273)(1313.77777777778,-10.2727272727273)(1298.84848484848,-10.2727272727273)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2272727272727)(1254.06060606061,-10.2727272727273)(1239.13131313131,-10.2727272727273)(1224.20202020202,-10.2954545454545)(1209.27272727273,-10.2727272727273)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.2121212121212)(1149.55555555556,-10.2121212121212)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.2121212121212)(1104.76767676768,-10.25)(1089.83838383838,-10.2727272727273)(1074.90909090909,-10.3484848484848)(1067.44444444444,-10.3636363636364)(1059.9797979798,-10.3818181818182)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2727272727273)(1000.26262626263,-10.2045454545455)(985.333333333333,-10.2121212121212)(970.40404040404,-10.2727272727273)(955.474747474747,-10.2121212121212)(951.742424242424,-10.1818181818182)(940.545454545455,-10.1363636363636)(925.616161616162,-10.0545454545455)(910.686868686869,-10.0227272727273)(895.757575757576,-10.030303030303)(888.292929292929,-10)(880.828282828283,-9.98181818181818)(865.89898989899,-9.94545454545455)(850.969696969697,-9.84090909090909)(836.040404040404,-9.84090909090909)(833.552188552189,-9.81818181818182)(822.977272727273,-9.63636363636364)(821.111111111111,-9.61363636363636)(806.181818181818,-9.54545454545455)(791.252525252525,-9.48484848484848)(787.520202020202,-9.45454545454546)(776.323232323232,-9.36363636363636)(768.858585858586,-9.27272727272727)(761.393939393939,-9.13636363636364)(757.661616161616,-9.09090909090909)(746.464646464646,-8.95454545454546)(743.976430976431,-8.90909090909091)(731.535353535354,-8.75757575757576)(727.80303030303,-8.72727272727273)(716.606060606061,-8.63636363636364)(701.676767676768,-8.63636363636364)(686.747474747475,-8.63636363636364)(671.818181818182,-8.6969696969697)(664.353535353535,-8.72727272727273)(656.888888888889,-8.75757575757576)(641.959595959596,-8.81818181818182)(627.030303030303,-8.87878787878788)(619.565656565657,-8.90909090909091)(612.10101010101,-8.93939393939394)(597.171717171717,-8.97727272727273)(582.242424242424,-9.02272727272727)(567.313131313131,-9.07272727272727)(563.580808080808,-9.09090909090909)(552.383838383838,-9.15909090909091)(537.454545454546,-9.18181818181818)(522.525252525253,-9.20454545454546)(507.59595959596,-9.20454545454546)(492.666666666667,-9.25454545454546)(477.737373737374,-9.25)(462.808080808081,-9.20454545454546)(450.367003367003,-9.09090909090909)(447.878787878788,-9.06060606060606)(432.949494949495,-8.93939393939394)(418.020202020202,-8.93939393939394)(410.555555555556,-8.90909090909091)(403.090909090909,-8.86363636363636)(388.161616161616,-8.86363636363636)(373.232323232323,-8.77272727272727)(358.30303030303,-8.81818181818182)(343.373737373737,-8.81818181818182)(328.444444444444,-8.81818181818182)(313.515151515152,-8.84090909090909)(298.585858585859,-8.88636363636364)(291.121212121212,-8.90909090909091)(283.656565656566,-8.93939393939394)(268.727272727273,-9.06060606060606)(264.99494949495,-9.09090909090909)(253.79797979798,-9.18181818181818)(242.60101010101,-9.27272727272727)(238.868686868687,-9.3030303030303)(223.939393939394,-9.42424242424243)(216.474747474747,-9.45454545454546)(209.010101010101,-9.48484848484848)(194.080808080808,-9.60606060606061)(186.616161616162,-9.63636363636364)(179.151515151515,-9.66666666666667)(164.222222222222,-9.72727272727273)(149.292929292929,-9.66666666666667)(145.560606060606,-9.63636363636364)(134.363636363636,-9.5)(131.875420875421,-9.45454545454546)(126.89898989899,-9.27272727272727)(121.922558922559,-9.09090909090909)(119.434343434343,-9)(116.946127946128,-8.90909090909091)(111.969696969697,-8.72727272727273)(106.993265993266,-8.54545454545455)(104.505050505051,-8.45454545454545)(100.772727272727,-8.36363636363636)(89.5757575757576,-8.27272727272727)(78.3787878787879,-8.18181818181818)(74.6464646464647,-8.15151515151515)(59.7171717171717,-8.09090909090909)(44.7878787878788,-8.03030303030303)(41.0555555555556,-8)(29.8585858585859,-7.86363636363636)(26.1262626262626,-7.81818181818182)(14.9292929292929,-7.72727272727273)(3.73232323232323,-7.63636363636364)(7.46464646464646,-7.45454545454546)(14.9292929292929,-7.40909090909091)(29.8585858585859,-7.40909090909091)(44.7878787878788,-7.31818181818182)(52.2525252525253,-7.27272727272727)(59.7171717171717,-7.24242424242424)(74.6464646464647,-7.12121212121212)(82.1111111111111,-7.09090909090909)(89.5757575757576,-7.06060606060606)(104.505050505051,-7)(119.434343434343,-7)(134.363636363636,-7)(149.292929292929,-7)(164.222222222222,-7.06060606060606)(171.686868686869,-7.09090909090909)(179.151515151515,-7.12121212121212)(194.080808080808,-7.18181818181818)(209.010101010101,-7.18181818181818)(223.939393939394,-7.18181818181818)(238.868686868687,-7.24242424242424)(246.333333333333,-7.27272727272727)(253.79797979798,-7.3030303030303)(268.727272727273,-7.42424242424243)(276.191919191919,-7.45454545454546)(283.656565656566,-7.48484848484849)(298.585858585859,-7.54545454545455)(313.515151515152,-7.60606060606061)(317.247474747475,-7.63636363636364)(328.444444444444,-7.77272727272727)(335.909090909091,-7.81818181818182)(343.373737373737,-7.84848484848485)(350.838383838384,-7.81818181818182)(358.30303030303,-7.77272727272727)(369.5,-7.63636363636364)(373.232323232323,-7.60606060606061)(388.161616161616,-7.59090909090909)(403.090909090909,-7.5)(406.823232323232,-7.45454545454546)(418.020202020202,-7.38636363636364)(432.949494949495,-7.34090909090909)(447.878787878788,-7.34090909090909)(462.808080808081,-7.3030303030303)(470.272727272727,-7.27272727272727)(477.737373737374,-7.22727272727273)(492.666666666667,-7.18181818181818)(507.59595959596,-7.18181818181818)(522.525252525253,-7.18181818181818)(537.454545454546,-7.20454545454546)(552.383838383838,-7.18181818181818)(567.313131313131,-7.20454545454546)(582.242424242424,-7.15909090909091)(597.171717171717,-7.18181818181818)(612.10101010101,-7.15909090909091)(627.030303030303,-7.24242424242424)(634.494949494949,-7.27272727272727)(641.959595959596,-7.3030303030303)(656.888888888889,-7.42424242424243)(660.621212121212,-7.45454545454546)(671.818181818182,-7.54545454545455)(679.282828282828,-7.63636363636364)(686.747474747475,-7.77272727272727)(689.23569023569,-7.81818181818182)(701.676767676768,-7.96969696969697)(705.409090909091,-8)(716.606060606061,-8.09090909090909)(731.535353535354,-8.09090909090909)(746.464646464646,-8.09090909090909)(761.393939393939,-8.09090909090909)(776.323232323232,-8.03030303030303)(791.252525252525,-8.02272727272727)(793.740740740741,-8)(806.181818181818,-7.88636363636364)(817.378787878788,-7.81818181818182)(821.111111111111,-7.77272727272727)(832.308080808081,-7.63636363636364)(836.040404040404,-7.60606060606061)(850.969696969697,-7.48484848484849)(854.70202020202,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.36363636363636)(895.757575757576,-7.29545454545455)(910.686868686869,-7.29545454545455)(914.419191919192,-7.27272727272727)(925.616161616162,-7.18181818181818)(940.545454545455,-7.18181818181818)(955.474747474748,-7.15909090909091)(970.40404040404,-7.24242424242424)(985.333333333333,-7.24242424242424)(1000.26262626263,-7.18181818181818)(1011.4595959596,-7.09090909090909)(1015.19191919192,-7.06060606060606)(1030.12121212121,-7.06060606060606)(1037.58585858586,-7.09090909090909)(1045.05050505051,-7.11363636363636)(1059.9797979798,-7.14545454545455)(1074.90909090909,-7.20454545454546)(1089.83838383838,-7.25)(1093.57070707071,-7.27272727272727)(1104.76767676768,-7.36363636363636)(1119.69696969697,-7.36363636363636)(1127.16161616162,-7.45454545454546)(1134.62626262626,-7.5)(1149.55555555556,-7.54545454545455)(1164.48484848485,-7.61363636363636)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.65151515151515)(1194.34343434343,-7.68181818181818)(1209.27272727273,-7.65151515151515)(1224.20202020202,-7.65151515151515)(1231.66666666667,-7.63636363636364)(1239.13131313131,-7.61363636363636)(1246.59595959596,-7.63636363636364)(1254.06060606061,-7.65909090909091)(1268.9898989899,-7.66666666666667)(1283.91919191919,-7.72727272727273)(1298.84848484848,-7.70454545454546)(1313.77777777778,-7.72727272727273)(1328.70707070707,-7.72727272727273)(1339.90404040404,-7.81818181818182)(1343.63636363636,-7.84090909090909)(1358.56565656566,-7.84090909090909)(1373.49494949495,-7.96969696969697)(1380.9595959596,-8)(1388.42424242424,-8.09090909090909)(1395.88888888889,-8.18181818181818)(1403.35353535354,-8.21212121212121)(1418.28282828283,-8.27272727272727)(1429.4797979798,-8.36363636363636)(1433.21212121212,-8.38636363636364)(1448.14141414141,-8.51515151515152)(1451.87373737374,-8.54545454545455)(1463.07070707071,-8.63636363636364)(1474.26767676768,-8.72727272727273)(1478,-8.75757575757576)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-9)(1407.08585858586,-9.09090909090909)(1414.5505050505,-9.27272727272727)(1410.81818181818,-9.45454545454546)(1403.35353535354,-9.5)(1392.15656565657,-9.63636363636364)(1388.42424242424,-9.66666666666667)(1379.09343434343,-9.81818181818182)(1373.49494949495,-9.95454545454546)(1366.0303030303,-10)(1358.56565656566,-10.0181818181818)(1343.63636363636,-10.0151515151515)(1339.90404040404,-10)(1328.70707070707,-9.90909090909091)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.90909090909091)(1283.91919191919,-9.90909090909091)(1268.9898989899,-9.84848484848485)(1254.06060606061,-9.90909090909091)(1239.13131313131,-9.90909090909091)(1224.20202020202,-9.96969696969697)(1209.27272727273,-9.90909090909091)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.88636363636364)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.88636363636364)(1104.76767676768,-9.93181818181818)(1089.83838383838,-9.97727272727273)(1087.35016835017,-10)(1074.90909090909,-10.0757575757576)(1059.9797979798,-10.1060606060606)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1017.68013468013,-10)(1015.19191919192,-9.97727272727273)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.88636363636364)(970.40404040404,-9.90909090909091)(955.474747474748,-9.88636363636364)(940.545454545455,-9.83636363636364)(936.813131313131,-9.81818181818182)(925.616161616162,-9.76363636363636)(910.686868686869,-9.72727272727273)(895.757575757576,-9.70454545454546)(884.560606060606,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.61363636363636)(850.969696969697,-9.50909090909091)(843.505050505051,-9.45454545454546)(836.040404040404,-9.31818181818182)(833.552188552189,-9.27272727272727)(821.111111111111,-9.15909090909091)(815.512626262626,-9.09090909090909)(808.04797979798,-8.90909090909091)(806.181818181818,-8.81818181818182)(804.315656565657,-8.72727272727273)(798.717171717172,-8.54545454545455)(803.693602693603,-8.36363636363636)(806.181818181818,-8.33333333333333)(821.111111111111,-8.20454545454546)(823.599326599327,-8.18181818181818)(836.040404040404,-8.03030303030303)(843.505050505051,-8)(850.969696969697,-7.95454545454546)(862.166666666667,-7.81818181818182)(865.89898989899,-7.8)(880.828282828283,-7.75)(895.757575757576,-7.72727272727273)(910.686868686869,-7.70454545454546)(921.883838383838,-7.63636363636364)(925.616161616162,-7.60606060606061)(940.545454545455,-7.54545454545455)(955.474747474747,-7.48484848484849)(970.40404040404,-7.56818181818182)(985.333333333333,-7.56818181818182)(1000.26262626263,-7.56818181818182)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.48484848484849)(1052.51515151515,-7.45454545454546)(1059.9797979798,-7.43939393939394)(1062.46801346801,-7.45454545454546)(1074.90909090909,-7.56818181818182)(1089.83838383838,-7.61818181818182)(1093.57070707071,-7.63636363636364)(1104.76767676768,-7.72727272727273)(1119.69696969697,-7.72727272727273)(1134.62626262626,-7.8)(1142.09090909091,-7.81818181818182)(1149.55555555556,-7.84090909090909)(1164.48484848485,-7.90909090909091)(1179.41414141414,-7.94545454545455)(1194.34343434343,-7.95454545454546)(1209.27272727273,-7.94545454545455)(1224.20202020202,-7.94545454545455)(1239.13131313131,-7.94545454545455)(1254.06060606061,-7.98484848484848)(1261.52525252525,-8)(1268.9898989899,-8.04545454545455)(1283.91919191919,-8.09090909090909)(1298.84848484848,-8.09090909090909)(1310.04545454545,-8.18181818181818)(1313.77777777778,-8.21212121212121)(1328.70707070707,-8.27272727272727)(1343.63636363636,-8.34090909090909)(1346.12457912458,-8.36363636363636)(1356.07744107744,-8.54545454545455)(1358.56565656566,-8.56818181818182)(1373.49494949495,-8.67272727272727)(1380.9595959596,-8.72727272727273)(1388.42424242424,-8.81818181818182)(1399.62121212121,-8.90909090909091)(1403.35353535354,-9)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (462.808080808081,-14.6818181818182)(470.272727272727,-14.5454545454545)(477.737373737374,-14.4545454545455)(488.934343434343,-14.3636363636364)(492.666666666667,-14.3333333333333)(507.59595959596,-14.2727272727273)(522.525252525253,-14.2727272727273)(537.454545454546,-14.2727272727273)(552.383838383838,-14.2727272727273)(567.313131313131,-14.2727272727273)(582.242424242424,-14.2727272727273)(597.171717171717,-14.2727272727273)(612.10101010101,-14.2727272727273)(627.030303030303,-14.2727272727273)(641.959595959596,-14.2727272727273)(656.888888888889,-14.2727272727273)(671.818181818182,-14.2727272727273)(686.747474747475,-14.3181818181818)(690.479797979798,-14.3636363636364)(690.479797979798,-14.5454545454545)(686.747474747475,-14.5757575757576)(671.818181818182,-14.6969696969697)(664.353535353535,-14.7272727272727)(656.888888888889,-14.7575757575758)(641.959595959596,-14.8787878787879)(634.494949494949,-14.9090909090909)(627.030303030303,-14.9393939393939)(612.10101010101,-15.0606060606061)(604.636363636364,-15.0909090909091)(597.171717171717,-15.1212121212121)(582.242424242424,-15.1818181818182)(567.313131313131,-15.2424242424242)(559.848484848485,-15.2727272727273)(552.383838383838,-15.3030303030303)(537.454545454546,-15.3636363636364)(522.525252525253,-15.3636363636364)(507.59595959596,-15.3636363636364)(492.666666666667,-15.3636363636364)(477.737373737374,-15.3030303030303)(474.005050505051,-15.2727272727273)(462.808080808081,-15.1363636363636)(460.319865319865,-15.0909090909091)(455.343434343434,-14.9090909090909)(460.319865319865,-14.7272727272727)(462.808080808081,-14.6818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (462.808080808081,-7.84848484848485)(465.296296296296,-7.81818181818182)(477.737373737374,-7.70454545454546)(488.934343434343,-7.63636363636364)(492.666666666667,-7.60606060606061)(507.59595959596,-7.54545454545455)(522.525252525253,-7.54545454545455)(537.454545454546,-7.52272727272727)(552.383838383838,-7.47727272727273)(567.313131313131,-7.52272727272727)(582.242424242424,-7.54545454545455)(593.439393939394,-7.63636363636364)(597.171717171717,-7.66666666666667)(609.612794612795,-7.81818181818182)(612.10101010101,-7.90909090909091)(614.589225589226,-8)(615.833333333333,-8.18181818181818)(612.10101010101,-8.21212121212121)(599.659932659933,-8.36363636363636)(597.171717171717,-8.40909090909091)(585.974747474747,-8.54545454545455)(582.242424242424,-8.57575757575757)(569.801346801347,-8.72727272727273)(567.313131313131,-8.74545454545454)(552.383838383838,-8.79545454545455)(537.454545454546,-8.81818181818182)(522.525252525253,-8.87878787878788)(507.59595959596,-8.81818181818182)(492.666666666667,-8.86363636363636)(485.20202020202,-8.72727272727273)(477.737373737374,-8.59090909090909)(474.005050505051,-8.54545454545455)(462.808080808081,-8.45454545454545)(455.343434343434,-8.36363636363636)(450.367003367003,-8.18181818181818)(450.367003367003,-8)(462.808080808081,-7.84848484848485)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-17.5454545454545)(1478.00012440663,-17.6363636363636)(1478.00037321366,-17.8181818181818)(1478.00037321366,-18)(1478,-18.0000045452273)(1463.07070707071,-18.0000045452273)(1448.14141414141,-18.0000045452273)(1433.21212121212,-18.0000045452273)(1418.28282828283,-18.0000045452273)(1403.35353535354,-18.0000035351964)(1388.42424242424,-18.0000025251543)(1375.98316498317,-18)(1388.42424242424,-17.8484848484848)(1395.88888888889,-17.8181818181818)(1403.35353535354,-17.7878787878788)(1418.28282828283,-17.7272727272727)(1433.21212121212,-17.7272727272727)(1448.14141414141,-17.6666666666667)(1455.60606060606,-17.6363636363636)(1463.07070707071,-17.6060606060606)(1478,-17.5454545454545)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (179.151515151515,-8.31818181818182)(186.616161616162,-8.36363636363636)(179.151515151515,-8.40909090909091)(175.419191919192,-8.36363636363636)(179.151515151515,-8.31818181818182)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_140.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.0002488174,-8.72727272727273)(1478.00049762651,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00066349464,-9.27272727272727)(1478.00058056104,-9.45454545454546)(1478.00058056104,-9.63636363636364)(1478.00066349464,-9.81818181818182)(1478.00049762651,-10)(1478.0002488174,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(-8.29400554937089e-05,-7.81818181818182)(-0.000331754692765745,-7.63636363636364)(-0.000331754692765745,-7.45454545454546)(-0.000248817401863321,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.81818181818182)(1478.00012440663,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00029027891,-9.27272727272727)(1478.00020734323,-9.45454545454546)(1478.00020734323,-9.63636363636364)(1478.00029027891,-9.81818181818182)(1478.00012440663,-10)(1478,-10.0909090909091)(1463.07070707071,-10.0909090909091)(1448.14141414141,-10.1590909090909)(1440.67676767677,-10.1818181818182)(1433.21212121212,-10.2121212121212)(1418.28282828283,-10.2272727272727)(1403.35353535354,-10.2272727272727)(1388.42424242424,-10.2727272727273)(1373.49494949495,-10.3454545454545)(1358.56565656566,-10.3454545454545)(1343.63636363636,-10.3409090909091)(1328.70707070707,-10.2727272727273)(1313.77777777778,-10.2727272727273)(1298.84848484848,-10.2727272727273)(1283.91919191919,-10.2954545454545)(1268.9898989899,-10.2727272727273)(1254.06060606061,-10.2954545454545)(1239.13131313131,-10.2727272727273)(1224.20202020202,-10.2954545454545)(1209.27272727273,-10.2727272727273)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.2121212121212)(1149.55555555556,-10.2121212121212)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.2121212121212)(1104.76767676768,-10.25)(1089.83838383838,-10.2727272727273)(1074.90909090909,-10.3484848484848)(1067.44444444444,-10.3636363636364)(1059.9797979798,-10.3818181818182)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2727272727273)(1000.26262626263,-10.2045454545455)(985.333333333333,-10.2121212121212)(970.40404040404,-10.2727272727273)(955.474747474748,-10.25)(944.277777777778,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.0909090909091)(910.686868686869,-10.0227272727273)(895.757575757576,-10.030303030303)(888.292929292929,-10)(880.828282828283,-9.98181818181818)(865.89898989899,-9.94545454545455)(852.835858585859,-9.81818181818182)(850.969696969697,-9.8)(836.040404040404,-9.78787878787879)(826.709595959596,-9.63636363636364)(821.111111111111,-9.54545454545455)(806.181818181818,-9.5)(798.717171717172,-9.45454545454546)(791.252525252525,-9.42424242424243)(776.323232323232,-9.31818181818182)(773.835016835017,-9.27272727272727)(772.590909090909,-9.09090909090909)(765.126262626263,-8.90909090909091)(761.393939393939,-8.81818181818182)(757.661616161616,-8.72727272727273)(753.929292929293,-8.54545454545455)(758.905723905724,-8.36363636363636)(761.393939393939,-8.31818181818182)(768.858585858586,-8.18181818181818)(776.323232323232,-8.09090909090909)(791.252525252525,-8.02272727272727)(793.740740740741,-8)(806.181818181818,-7.88636363636364)(821.111111111111,-7.83636363636364)(822.60404040404,-7.81818181818182)(833.552188552189,-7.63636363636364)(836.040404040404,-7.61363636363636)(850.969696969697,-7.52272727272727)(858.434343434343,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.36363636363636)(895.757575757576,-7.29545454545455)(910.686868686869,-7.29545454545455)(914.419191919192,-7.27272727272727)(925.616161616162,-7.18181818181818)(940.545454545455,-7.18181818181818)(955.474747474748,-7.15909090909091)(970.40404040404,-7.24242424242424)(985.333333333333,-7.24242424242424)(1000.26262626263,-7.18181818181818)(1011.4595959596,-7.09090909090909)(1015.19191919192,-7.06060606060606)(1030.12121212121,-7.06060606060606)(1037.58585858586,-7.09090909090909)(1045.05050505051,-7.11363636363636)(1059.9797979798,-7.14545454545455)(1074.90909090909,-7.20454545454546)(1089.83838383838,-7.25)(1093.57070707071,-7.27272727272727)(1104.76767676768,-7.36363636363636)(1119.69696969697,-7.36363636363636)(1127.16161616162,-7.45454545454546)(1134.62626262626,-7.5)(1149.55555555556,-7.54545454545455)(1164.48484848485,-7.61363636363636)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.65151515151515)(1194.34343434343,-7.68181818181818)(1209.27272727273,-7.65151515151515)(1216.73737373737,-7.63636363636364)(1224.20202020202,-7.61363636363636)(1239.13131313131,-7.58181818181818)(1254.06060606061,-7.61818181818182)(1261.52525252525,-7.63636363636364)(1268.9898989899,-7.66666666666667)(1283.91919191919,-7.72727272727273)(1298.84848484848,-7.70454545454546)(1313.77777777778,-7.72727272727273)(1328.70707070707,-7.72727272727273)(1339.90404040404,-7.81818181818182)(1343.63636363636,-7.84090909090909)(1358.56565656566,-7.84090909090909)(1373.49494949495,-7.96969696969697)(1377.22727272727,-8)(1384.69191919192,-8.18181818181818)(1388.42424242424,-8.27272727272727)(1395.88888888889,-8.36363636363636)(1403.35353535354,-8.39393939393939)(1418.28282828283,-8.43181818181818)(1433.21212121212,-8.47727272727273)(1440.67676767677,-8.54545454545455)(1448.14141414141,-8.61363636363636)(1460.58249158249,-8.72727272727273)(1463.07070707071,-8.77272727272727)(1478,-8.81818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.43181818181818)(1434.70505050505,-9.45454545454546)(1435.07828282828,-9.63636363636364)(1433.21212121212,-9.72727272727273)(1418.28282828283,-9.72727272727273)(1403.35353535354,-9.70454545454546)(1388.42424242424,-9.78787878787879)(1385.93602693603,-9.81818181818182)(1375.36111111111,-10)(1373.49494949495,-10.0181818181818)(1358.56565656566,-10.0454545454545)(1343.63636363636,-10.0151515151515)(1339.90404040404,-10)(1328.70707070707,-9.90909090909091)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.90909090909091)(1283.91919191919,-9.96969696969697)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.96969696969697)(1239.13131313131,-9.90909090909091)(1224.20202020202,-9.96969696969697)(1209.27272727273,-9.90909090909091)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.88636363636364)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.88636363636364)(1104.76767676768,-9.93181818181818)(1089.83838383838,-9.97727272727273)(1087.35016835017,-10)(1074.90909090909,-10.0757575757576)(1059.9797979798,-10.1060606060606)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1017.68013468013,-10)(1015.19191919192,-9.97727272727273)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.88636363636364)(970.40404040404,-9.90909090909091)(955.474747474748,-9.93181818181818)(940.545454545455,-9.87272727272727)(929.348484848485,-9.81818181818182)(925.616161616162,-9.79545454545455)(910.686868686869,-9.72727272727273)(895.757575757576,-9.70454545454546)(884.560606060606,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.61363636363636)(850.969696969697,-9.47272727272727)(848.481481481482,-9.45454545454546)(836.040404040404,-9.3030303030303)(834.174242424242,-9.27272727272727)(821.111111111111,-9.11363636363636)(819.244949494949,-9.09090909090909)(808.04797979798,-8.90909090909091)(807.674747474747,-8.72727272727273)(806.181818181818,-8.63636363636364)(803.693602693603,-8.54545454545455)(806.181818181818,-8.45454545454545)(808.04797979798,-8.36363636363636)(821.111111111111,-8.20454545454546)(823.599326599327,-8.18181818181818)(834.547474747475,-8)(836.040404040404,-7.98181818181818)(850.969696969697,-7.90909090909091)(858.434343434343,-7.81818181818182)(865.89898989899,-7.76363636363636)(880.828282828283,-7.75)(895.757575757576,-7.72727272727273)(910.686868686869,-7.70454545454546)(921.883838383838,-7.63636363636364)(925.616161616162,-7.60606060606061)(940.545454545455,-7.54545454545455)(955.474747474747,-7.48484848484849)(970.40404040404,-7.56818181818182)(985.333333333333,-7.56818181818182)(1000.26262626263,-7.56818181818182)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.48484848484849)(1052.51515151515,-7.45454545454546)(1059.9797979798,-7.43939393939394)(1062.46801346801,-7.45454545454546)(1074.90909090909,-7.56818181818182)(1089.83838383838,-7.61818181818182)(1093.57070707071,-7.63636363636364)(1104.76767676768,-7.72727272727273)(1119.69696969697,-7.72727272727273)(1134.62626262626,-7.8)(1142.09090909091,-7.81818181818182)(1149.55555555556,-7.84090909090909)(1164.48484848485,-7.90909090909091)(1179.41414141414,-7.94545454545455)(1194.34343434343,-7.95454545454546)(1209.27272727273,-7.94545454545455)(1224.20202020202,-7.90909090909091)(1239.13131313131,-7.90909090909091)(1254.06060606061,-7.95454545454546)(1265.25757575758,-8)(1268.9898989899,-8.04545454545455)(1283.91919191919,-8.09090909090909)(1298.84848484848,-8.09090909090909)(1310.04545454545,-8.18181818181818)(1313.77777777778,-8.21212121212121)(1328.70707070707,-8.27272727272727)(1343.63636363636,-8.34090909090909)(1346.12457912458,-8.36363636363636)(1356.07744107744,-8.54545454545455)(1358.56565656566,-8.56818181818182)(1373.49494949495,-8.67272727272727)(1379.09343434343,-8.72727272727273)(1388.42424242424,-8.84090909090909)(1399.62121212121,-8.90909090909091)(1403.35353535354,-8.95454545454546)(1418.28282828283,-9.04545454545455)(1420.14898989899,-9.09090909090909)(1422.76161616162,-9.27272727272727)(1433.21212121212,-9.43181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (14.9292929292929,-7.40909090909091)(29.8585858585859,-7.40909090909091)(44.7878787878788,-7.31818181818182)(52.2525252525253,-7.27272727272727)(59.7171717171717,-7.24242424242424)(74.6464646464647,-7.18181818181818)(89.5757575757576,-7.12121212121212)(97.040404040404,-7.09090909090909)(104.505050505051,-7.06060606060606)(119.434343434343,-7)(134.363636363636,-7)(149.292929292929,-7)(164.222222222222,-7.06060606060606)(171.686868686869,-7.09090909090909)(179.151515151515,-7.12121212121212)(194.080808080808,-7.18181818181818)(209.010101010101,-7.18181818181818)(223.939393939394,-7.18181818181818)(238.868686868687,-7.24242424242424)(246.333333333333,-7.27272727272727)(253.79797979798,-7.3030303030303)(268.727272727273,-7.42424242424243)(276.191919191919,-7.45454545454546)(283.656565656566,-7.48484848484849)(298.585858585859,-7.54545454545455)(313.515151515152,-7.60606060606061)(317.247474747475,-7.63636363636364)(328.444444444444,-7.77272727272727)(335.909090909091,-7.81818181818182)(343.373737373737,-7.84848484848485)(358.30303030303,-7.86363636363636)(360.791245791246,-7.81818181818182)(373.232323232323,-7.66666666666667)(388.161616161616,-7.66666666666667)(403.090909090909,-7.66666666666667)(406.823232323232,-7.63636363636364)(414.287878787879,-7.45454545454546)(418.020202020202,-7.43181818181818)(432.949494949495,-7.36363636363636)(447.878787878788,-7.32727272727273)(462.808080808081,-7.29545454545455)(470.272727272727,-7.27272727272727)(477.737373737374,-7.22727272727273)(492.666666666667,-7.18181818181818)(507.59595959596,-7.18181818181818)(522.525252525253,-7.18181818181818)(537.454545454546,-7.20454545454546)(552.383838383838,-7.18181818181818)(567.313131313131,-7.20454545454546)(582.242424242424,-7.15909090909091)(597.171717171717,-7.22727272727273)(612.10101010101,-7.18181818181818)(623.29797979798,-7.27272727272727)(627.030303030303,-7.29545454545455)(641.959595959596,-7.3030303030303)(656.888888888889,-7.42424242424243)(660.621212121212,-7.45454545454546)(671.818181818182,-7.54545454545455)(679.282828282828,-7.63636363636364)(686.747474747475,-7.77272727272727)(689.23569023569,-7.81818181818182)(694.212121212121,-8)(694.212121212121,-8.18181818181818)(689.23569023569,-8.36363636363636)(686.747474747475,-8.40909090909091)(679.282828282828,-8.54545454545455)(671.818181818182,-8.63636363636364)(660.621212121212,-8.72727272727273)(656.888888888889,-8.75757575757576)(641.959595959596,-8.81818181818182)(627.030303030303,-8.81818181818182)(612.10101010101,-8.86363636363636)(604.636363636364,-8.90909090909091)(597.171717171717,-8.93939393939394)(582.242424242424,-9.02272727272727)(567.313131313131,-9.07272727272727)(563.580808080808,-9.09090909090909)(552.383838383838,-9.15909090909091)(537.454545454546,-9.18181818181818)(522.525252525253,-9.20454545454546)(507.59595959596,-9.20454545454546)(492.666666666667,-9.25454545454546)(477.737373737374,-9.25)(462.808080808081,-9.20454545454546)(450.367003367003,-9.09090909090909)(447.878787878788,-9.06060606060606)(432.949494949495,-8.93939393939394)(418.020202020202,-8.93939393939394)(410.555555555556,-8.90909090909091)(403.090909090909,-8.87878787878788)(388.161616161616,-8.86363636363636)(373.232323232323,-8.77272727272727)(358.30303030303,-8.81818181818182)(343.373737373737,-8.81818181818182)(328.444444444444,-8.81818181818182)(313.515151515152,-8.84090909090909)(298.585858585859,-8.88636363636364)(291.121212121212,-8.90909090909091)(283.656565656566,-8.93939393939394)(268.727272727273,-9.06060606060606)(264.99494949495,-9.09090909090909)(253.79797979798,-9.18181818181818)(242.60101010101,-9.27272727272727)(238.868686868687,-9.3030303030303)(223.939393939394,-9.42424242424243)(216.474747474747,-9.45454545454546)(209.010101010101,-9.48484848484848)(194.080808080808,-9.54545454545455)(179.151515151515,-9.60606060606061)(164.222222222222,-9.60606060606061)(149.292929292929,-9.60606060606061)(136.851851851852,-9.45454545454546)(134.363636363636,-9.40909090909091)(126.89898989899,-9.27272727272727)(121.922558922559,-9.09090909090909)(119.434343434343,-9)(116.946127946128,-8.90909090909091)(111.969696969697,-8.72727272727273)(106.993265993266,-8.54545454545455)(104.505050505051,-8.45454545454545)(100.772727272727,-8.36363636363636)(89.5757575757576,-8.27272727272727)(78.3787878787879,-8.18181818181818)(74.6464646464647,-8.15151515151515)(59.7171717171717,-8.09090909090909)(44.7878787878788,-8.03030303030303)(41.0555555555556,-8)(29.8585858585859,-7.86363636363636)(26.1262626262626,-7.81818181818182)(14.9292929292929,-7.72727272727273)(3.73232323232323,-7.63636363636364)(7.46464646464646,-7.45454545454546)(14.9292929292929,-7.40909090909091)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (462.808080808081,-14.6818181818182)(470.272727272727,-14.5454545454545)(477.737373737374,-14.4545454545455)(488.934343434343,-14.3636363636364)(492.666666666667,-14.3333333333333)(507.59595959596,-14.2727272727273)(522.525252525253,-14.2727272727273)(537.454545454546,-14.2727272727273)(552.383838383838,-14.2727272727273)(567.313131313131,-14.2727272727273)(582.242424242424,-14.2727272727273)(597.171717171717,-14.2727272727273)(612.10101010101,-14.2727272727273)(627.030303030303,-14.2727272727273)(641.959595959596,-14.2727272727273)(656.888888888889,-14.2727272727273)(671.818181818182,-14.2727272727273)(686.747474747475,-14.3181818181818)(690.479797979798,-14.3636363636364)(690.479797979798,-14.5454545454545)(686.747474747475,-14.5757575757576)(671.818181818182,-14.6969696969697)(664.353535353535,-14.7272727272727)(656.888888888889,-14.7575757575758)(641.959595959596,-14.8787878787879)(634.494949494949,-14.9090909090909)(627.030303030303,-14.9393939393939)(612.10101010101,-15.0606060606061)(604.636363636364,-15.0909090909091)(597.171717171717,-15.1212121212121)(582.242424242424,-15.1818181818182)(567.313131313131,-15.2424242424242)(559.848484848485,-15.2727272727273)(552.383838383838,-15.3030303030303)(537.454545454546,-15.3636363636364)(522.525252525253,-15.3636363636364)(507.59595959596,-15.3636363636364)(492.666666666667,-15.3636363636364)(477.737373737374,-15.3030303030303)(474.005050505051,-15.2727272727273)(462.808080808081,-15.1363636363636)(460.319865319865,-15.0909090909091)(455.343434343434,-14.9090909090909)(460.319865319865,-14.7272727272727)(462.808080808081,-14.6818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (462.808080808081,-7.78787878787879)(477.737373737374,-7.70454545454546)(488.934343434343,-7.63636363636364)(492.666666666667,-7.60606060606061)(507.59595959596,-7.54545454545455)(522.525252525253,-7.54545454545455)(537.454545454546,-7.52272727272727)(552.383838383838,-7.47727272727273)(567.313131313131,-7.52272727272727)(582.242424242424,-7.54545454545455)(589.707070707071,-7.63636363636364)(597.171717171717,-7.70454545454546)(609.612794612795,-7.81818181818182)(612.10101010101,-7.90909090909091)(614.589225589226,-8)(614.589225589226,-8.18181818181818)(612.10101010101,-8.21212121212121)(599.659932659933,-8.36363636363636)(597.171717171717,-8.39393939393939)(584.73063973064,-8.54545454545455)(582.242424242424,-8.57575757575757)(569.801346801347,-8.72727272727273)(567.313131313131,-8.74545454545454)(552.383838383838,-8.79545454545455)(537.454545454546,-8.81818181818182)(522.525252525253,-8.87878787878788)(507.59595959596,-8.81818181818182)(492.666666666667,-8.86363636363636)(485.20202020202,-8.72727272727273)(477.737373737374,-8.59090909090909)(474.005050505051,-8.54545454545455)(462.808080808081,-8.45454545454545)(455.343434343434,-8.36363636363636)(450.367003367003,-8.18181818181818)(450.367003367003,-8)(455.343434343434,-7.81818181818182)(462.808080808081,-7.78787878787879)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (179.151515151515,-8.27272727272727)(190.348484848485,-8.36363636363636)(179.151515151515,-8.5)(167.954545454545,-8.36363636363636)(179.151515151515,-8.27272727272727)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_160.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.0002488174,-8.72727272727273)(1478.00049762651,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00066349464,-9.27272727272727)(1478.00058056104,-9.45454545454546)(1478.00058056104,-9.63636363636364)(1478.00066349464,-9.81818181818182)(1478.00049762651,-10)(1478.0002488174,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.81818181818182)(1478.00012440663,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00029027891,-9.27272727272727)(1478.00020734323,-9.45454545454546)(1478.00020734323,-9.63636363636364)(1478.00029027891,-9.81818181818182)(1478.00012440663,-10)(1478,-10.0909090909091)(1463.07070707071,-10.0909090909091)(1448.14141414141,-10.1590909090909)(1440.67676767677,-10.1818181818182)(1433.21212121212,-10.2121212121212)(1418.28282828283,-10.2272727272727)(1403.35353535354,-10.2272727272727)(1388.42424242424,-10.2727272727273)(1373.49494949495,-10.3454545454545)(1358.56565656566,-10.3454545454545)(1343.63636363636,-10.3409090909091)(1328.70707070707,-10.2727272727273)(1313.77777777778,-10.2727272727273)(1298.84848484848,-10.2727272727273)(1283.91919191919,-10.2954545454545)(1268.9898989899,-10.2727272727273)(1254.06060606061,-10.2954545454545)(1239.13131313131,-10.2727272727273)(1224.20202020202,-10.2954545454545)(1209.27272727273,-10.2727272727273)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.2121212121212)(1149.55555555556,-10.2121212121212)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.2121212121212)(1104.76767676768,-10.25)(1089.83838383838,-10.2727272727273)(1074.90909090909,-10.3484848484848)(1067.44444444444,-10.3636363636364)(1059.9797979798,-10.3818181818182)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2727272727273)(1000.26262626263,-10.2045454545455)(985.333333333333,-10.2121212121212)(970.40404040404,-10.2727272727273)(955.474747474748,-10.25)(944.277777777778,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.0909090909091)(910.686868686869,-10.0227272727273)(895.757575757576,-10.030303030303)(888.292929292929,-10)(880.828282828283,-9.98181818181818)(865.89898989899,-9.94545454545455)(852.835858585859,-9.81818181818182)(850.969696969697,-9.8)(836.040404040404,-9.78787878787879)(826.709595959596,-9.63636363636364)(821.111111111111,-9.54545454545455)(806.181818181818,-9.5)(798.717171717172,-9.45454545454546)(791.252525252525,-9.42424242424243)(776.323232323232,-9.31818181818182)(773.835016835017,-9.27272727272727)(772.590909090909,-9.09090909090909)(765.126262626263,-8.90909090909091)(761.393939393939,-8.81818181818182)(757.661616161616,-8.72727272727273)(758.905723905724,-8.54545454545455)(761.393939393939,-8.45454545454545)(765.126262626263,-8.36363636363636)(776.323232323232,-8.22727272727273)(778.811447811448,-8.18181818181818)(791.252525252525,-8.06818181818182)(798.717171717172,-8)(806.181818181818,-7.93181818181818)(821.111111111111,-7.83636363636364)(822.60404040404,-7.81818181818182)(833.552188552189,-7.63636363636364)(836.040404040404,-7.61363636363636)(850.969696969697,-7.52272727272727)(858.434343434343,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.36363636363636)(893.26936026936,-7.27272727272727)(895.757575757576,-7.25)(910.686868686869,-7.24242424242424)(925.616161616162,-7.15909090909091)(940.545454545455,-7.15909090909091)(955.474747474747,-7.10606060606061)(970.40404040404,-7.13636363636364)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1003.99494949495,-7.09090909090909)(1015.19191919192,-7.03636363636364)(1030.12121212121,-7.06818181818182)(1037.58585858586,-7.09090909090909)(1045.05050505051,-7.10606060606061)(1059.9797979798,-7.13636363636364)(1074.90909090909,-7.20454545454546)(1089.83838383838,-7.25)(1092.3265993266,-7.27272727272727)(1104.76767676768,-7.42424242424243)(1112.23232323232,-7.45454545454546)(1119.69696969697,-7.46969696969697)(1134.62626262626,-7.56060606060606)(1149.55555555556,-7.58181818181818)(1164.48484848485,-7.61363636363636)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.65151515151515)(1194.34343434343,-7.68181818181818)(1209.27272727273,-7.68181818181818)(1224.20202020202,-7.65151515151515)(1231.66666666667,-7.63636363636364)(1239.13131313131,-7.61818181818182)(1254.06060606061,-7.61818181818182)(1261.52525252525,-7.63636363636364)(1268.9898989899,-7.66666666666667)(1283.91919191919,-7.72727272727273)(1298.84848484848,-7.70454545454546)(1313.77777777778,-7.72727272727273)(1328.70707070707,-7.72727272727273)(1339.90404040404,-7.81818181818182)(1343.63636363636,-7.84848484848485)(1358.56565656566,-7.84848484848485)(1371.00673400673,-8)(1373.49494949495,-8.09090909090909)(1380.9595959596,-8.18181818181818)(1388.42424242424,-8.27272727272727)(1395.88888888889,-8.36363636363636)(1403.35353535354,-8.39393939393939)(1418.28282828283,-8.43181818181818)(1433.21212121212,-8.47727272727273)(1440.67676767677,-8.54545454545455)(1448.14141414141,-8.61363636363636)(1460.58249158249,-8.72727272727273)(1463.07070707071,-8.77272727272727)(1478,-8.81818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.43181818181818)(1434.70505050505,-9.45454545454546)(1435.07828282828,-9.63636363636364)(1433.21212121212,-9.72727272727273)(1418.28282828283,-9.72727272727273)(1403.35353535354,-9.70454545454546)(1388.42424242424,-9.78787878787879)(1385.93602693603,-9.81818181818182)(1375.36111111111,-10)(1373.49494949495,-10.0181818181818)(1358.56565656566,-10.0454545454545)(1343.63636363636,-10.0151515151515)(1339.90404040404,-10)(1328.70707070707,-9.90909090909091)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.90909090909091)(1283.91919191919,-9.96969696969697)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.96969696969697)(1239.13131313131,-9.90909090909091)(1224.20202020202,-9.96969696969697)(1209.27272727273,-9.90909090909091)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.88636363636364)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.88636363636364)(1104.76767676768,-9.93181818181818)(1089.83838383838,-9.97727272727273)(1087.35016835017,-10)(1074.90909090909,-10.0757575757576)(1059.9797979798,-10.1060606060606)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1017.68013468013,-10)(1015.19191919192,-9.97727272727273)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.88636363636364)(970.40404040404,-9.90909090909091)(955.474747474748,-9.93181818181818)(940.545454545455,-9.87272727272727)(929.348484848485,-9.81818181818182)(925.616161616162,-9.79545454545455)(910.686868686869,-9.72727272727273)(895.757575757576,-9.70454545454546)(884.560606060606,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.61363636363636)(850.969696969697,-9.47272727272727)(848.481481481482,-9.45454545454546)(836.040404040404,-9.3030303030303)(834.174242424242,-9.27272727272727)(821.111111111111,-9.11363636363636)(819.244949494949,-9.09090909090909)(808.04797979798,-8.90909090909091)(807.674747474747,-8.72727272727273)(806.181818181818,-8.63636363636364)(803.693602693603,-8.54545454545455)(806.181818181818,-8.45454545454545)(808.04797979798,-8.36363636363636)(821.111111111111,-8.20454545454546)(823.599326599327,-8.18181818181818)(834.547474747475,-8)(836.040404040404,-7.98181818181818)(850.969696969697,-7.90909090909091)(856.568181818182,-7.81818181818182)(865.89898989899,-7.72727272727273)(880.828282828283,-7.70454545454546)(888.292929292929,-7.63636363636364)(895.757575757576,-7.58181818181818)(910.686868686869,-7.61363636363636)(925.616161616162,-7.48484848484849)(940.545454545455,-7.48484848484849)(943.03367003367,-7.45454545454546)(955.474747474747,-7.37878787878788)(970.40404040404,-7.40909090909091)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1015.19191919192,-7.32727272727273)(1030.12121212121,-7.36363636363636)(1045.05050505051,-7.4)(1059.9797979798,-7.40909090909091)(1065.57828282828,-7.45454545454546)(1074.90909090909,-7.56818181818182)(1089.83838383838,-7.61818181818182)(1092.3265993266,-7.63636363636364)(1104.76767676768,-7.75)(1119.69696969697,-7.79545454545455)(1127.16161616162,-7.81818181818182)(1134.62626262626,-7.83636363636364)(1149.55555555556,-7.87272727272727)(1164.48484848485,-7.90909090909091)(1179.41414141414,-7.94545454545455)(1194.34343434343,-7.95454545454546)(1209.27272727273,-7.95454545454546)(1224.20202020202,-7.92424242424242)(1239.13131313131,-7.92424242424242)(1254.06060606061,-7.95454545454546)(1265.25757575758,-8)(1268.9898989899,-8.04545454545455)(1283.91919191919,-8.09090909090909)(1298.84848484848,-8.09090909090909)(1310.04545454545,-8.18181818181818)(1313.77777777778,-8.21212121212121)(1328.70707070707,-8.27272727272727)(1339.90404040404,-8.36363636363636)(1343.63636363636,-8.39393939393939)(1356.07744107744,-8.54545454545455)(1358.56565656566,-8.56818181818182)(1373.49494949495,-8.67272727272727)(1379.09343434343,-8.72727272727273)(1388.42424242424,-8.84090909090909)(1399.62121212121,-8.90909090909091)(1403.35353535354,-8.95454545454546)(1418.28282828283,-9.04545454545455)(1420.14898989899,-9.09090909090909)(1422.76161616162,-9.27272727272727)(1433.21212121212,-9.43181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (59.7171717171717,-7.77272727272727)(67.1818181818182,-7.63636363636364)(74.6464646464647,-7.54545454545455)(85.8434343434344,-7.45454545454546)(89.5757575757576,-7.42424242424243)(104.505050505051,-7.36363636363636)(119.434343434343,-7.3030303030303)(126.89898989899,-7.27272727272727)(134.363636363636,-7.24242424242424)(149.292929292929,-7.18181818181818)(164.222222222222,-7.24242424242424)(171.686868686869,-7.27272727272727)(179.151515151515,-7.31818181818182)(194.080808080808,-7.40909090909091)(209.010101010101,-7.36363636363636)(223.939393939394,-7.36363636363636)(238.868686868687,-7.36363636363636)(253.79797979798,-7.42424242424243)(261.262626262626,-7.45454545454546)(268.727272727273,-7.48484848484849)(283.656565656566,-7.54545454545455)(298.585858585859,-7.54545454545455)(313.515151515152,-7.60606060606061)(317.247474747475,-7.63636363636364)(328.444444444444,-7.77272727272727)(335.909090909091,-7.81818181818182)(343.373737373737,-7.84848484848485)(358.30303030303,-7.86363636363636)(360.791245791246,-7.81818181818182)(373.232323232323,-7.66666666666667)(388.161616161616,-7.66666666666667)(403.090909090909,-7.66666666666667)(406.823232323232,-7.63636363636364)(414.287878787879,-7.45454545454546)(418.020202020202,-7.43181818181818)(432.949494949495,-7.36363636363636)(447.878787878788,-7.32727272727273)(462.808080808081,-7.29545454545455)(470.272727272727,-7.27272727272727)(477.737373737374,-7.22727272727273)(492.666666666667,-7.18181818181818)(507.59595959596,-7.18181818181818)(522.525252525253,-7.24242424242424)(537.454545454546,-7.25)(552.383838383838,-7.21818181818182)(567.313131313131,-7.20454545454546)(582.242424242424,-7.15909090909091)(597.171717171717,-7.22727272727273)(612.10101010101,-7.18181818181818)(623.29797979798,-7.27272727272727)(627.030303030303,-7.29545454545455)(641.959595959596,-7.3030303030303)(656.888888888889,-7.42424242424243)(660.621212121212,-7.45454545454546)(671.818181818182,-7.54545454545455)(679.282828282828,-7.63636363636364)(686.747474747475,-7.77272727272727)(689.23569023569,-7.81818181818182)(694.212121212121,-8)(694.212121212121,-8.18181818181818)(689.23569023569,-8.36363636363636)(686.747474747475,-8.40909090909091)(679.282828282828,-8.54545454545455)(671.818181818182,-8.63636363636364)(660.621212121212,-8.72727272727273)(656.888888888889,-8.75757575757576)(641.959595959596,-8.81818181818182)(627.030303030303,-8.81818181818182)(612.10101010101,-8.86363636363636)(604.636363636364,-8.90909090909091)(597.171717171717,-8.93939393939394)(582.242424242424,-9.02272727272727)(567.313131313131,-9.07272727272727)(563.580808080808,-9.09090909090909)(552.383838383838,-9.15909090909091)(537.454545454546,-9.18181818181818)(522.525252525253,-9.20454545454546)(507.59595959596,-9.21818181818182)(492.666666666667,-9.25757575757576)(477.737373737374,-9.25454545454546)(462.808080808081,-9.20454545454546)(450.367003367003,-9.09090909090909)(447.878787878788,-9.06060606060606)(432.949494949495,-8.93939393939394)(425.484848484849,-8.90909090909091)(418.020202020202,-8.88636363636364)(403.090909090909,-8.81818181818182)(388.161616161616,-8.77272727272727)(373.232323232323,-8.77272727272727)(358.30303030303,-8.81818181818182)(343.373737373737,-8.81818181818182)(328.444444444444,-8.81818181818182)(313.515151515152,-8.84090909090909)(298.585858585859,-8.88636363636364)(291.121212121212,-8.90909090909091)(283.656565656566,-8.93939393939394)(268.727272727273,-9.06060606060606)(264.99494949495,-9.09090909090909)(253.79797979798,-9.18181818181818)(242.60101010101,-9.27272727272727)(238.868686868687,-9.3030303030303)(223.939393939394,-9.42424242424243)(216.474747474747,-9.45454545454546)(209.010101010101,-9.48484848484848)(194.080808080808,-9.54545454545455)(179.151515151515,-9.54545454545455)(164.222222222222,-9.54545454545455)(149.292929292929,-9.54545454545455)(138.09595959596,-9.45454545454546)(134.363636363636,-9.40909090909091)(126.89898989899,-9.27272727272727)(121.922558922559,-9.09090909090909)(119.434343434343,-9)(116.946127946128,-8.90909090909091)(111.969696969697,-8.72727272727273)(106.993265993266,-8.54545454545455)(104.505050505051,-8.45454545454545)(100.772727272727,-8.36363636363636)(89.5757575757576,-8.27272727272727)(78.3787878787879,-8.18181818181818)(74.6464646464647,-8.15151515151515)(62.2053872053872,-8)(59.7171717171717,-7.90909090909091)(57.2289562289562,-7.81818181818182)(59.7171717171717,-7.77272727272727)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.78787878787879)(462.808080808081,-7.75)(477.737373737374,-7.70454545454546)(488.934343434343,-7.63636363636364)(492.666666666667,-7.60606060606061)(507.59595959596,-7.54545454545455)(522.525252525253,-7.56818181818182)(537.454545454546,-7.54545454545455)(552.383838383838,-7.50909090909091)(567.313131313131,-7.52272727272727)(582.242424242424,-7.54545454545455)(589.707070707071,-7.63636363636364)(597.171717171717,-7.70454545454546)(609.612794612795,-7.81818181818182)(612.10101010101,-7.90909090909091)(614.589225589226,-8)(614.589225589226,-8.18181818181818)(612.10101010101,-8.21212121212121)(599.659932659933,-8.36363636363636)(597.171717171717,-8.39393939393939)(584.73063973064,-8.54545454545455)(582.242424242424,-8.57575757575757)(569.801346801347,-8.72727272727273)(567.313131313131,-8.74545454545454)(552.383838383838,-8.79545454545455)(537.454545454546,-8.81818181818182)(522.525252525253,-8.87878787878788)(507.59595959596,-8.87878787878788)(500.131313131313,-8.90909090909091)(492.666666666667,-8.93181818181818)(488.934343434343,-8.90909090909091)(480.225589225589,-8.72727272727273)(477.737373737374,-8.63636363636364)(474.005050505051,-8.54545454545455)(462.808080808081,-8.45454545454545)(455.343434343434,-8.36363636363636)(447.878787878788,-8.22727272727273)(445.390572390572,-8.18181818181818)(446.012626262626,-8)(445.390572390572,-7.81818181818182)(447.878787878788,-7.78787878787879)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (477.737373737374,-14.6818181818182)(488.934343434343,-14.5454545454545)(492.666666666667,-14.5151515151515)(507.59595959596,-14.3939393939394)(515.060606060606,-14.3636363636364)(522.525252525253,-14.3333333333333)(537.454545454546,-14.2727272727273)(552.383838383838,-14.2727272727273)(567.313131313131,-14.2727272727273)(582.242424242424,-14.2727272727273)(597.171717171717,-14.2727272727273)(612.10101010101,-14.2727272727273)(627.030303030303,-14.2727272727273)(641.959595959596,-14.2727272727273)(656.888888888889,-14.2727272727273)(671.818181818182,-14.2727272727273)(686.747474747475,-14.3181818181818)(690.479797979798,-14.3636363636364)(690.479797979798,-14.5454545454545)(686.747474747475,-14.5757575757576)(671.818181818182,-14.6969696969697)(664.353535353535,-14.7272727272727)(656.888888888889,-14.7575757575758)(641.959595959596,-14.8787878787879)(634.494949494949,-14.9090909090909)(627.030303030303,-14.9393939393939)(612.10101010101,-15.0606060606061)(604.636363636364,-15.0909090909091)(597.171717171717,-15.1212121212121)(582.242424242424,-15.1818181818182)(567.313131313131,-15.2424242424242)(559.848484848485,-15.2727272727273)(552.383838383838,-15.3030303030303)(537.454545454546,-15.3636363636364)(522.525252525253,-15.3636363636364)(507.59595959596,-15.3636363636364)(492.666666666667,-15.3030303030303)(488.934343434343,-15.2727272727273)(477.737373737374,-15.1363636363636)(475.249158249158,-15.0909090909091)(470.272727272727,-14.9090909090909)(475.249158249158,-14.7272727272727)(477.737373737374,-14.6818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (164.222222222222,-8.31818181818182)(179.151515151515,-8.21212121212121)(194.080808080808,-8.21212121212121)(206.521885521886,-8.36363636363636)(209.010101010101,-8.45454545454545)(211.498316498317,-8.54545454545455)(209.010101010101,-8.63636363636364)(194.080808080808,-8.68181818181818)(179.151515151515,-8.65909090909091)(166.710437710438,-8.54545454545455)(164.222222222222,-8.45454545454545)(161.734006734007,-8.36363636363636)(164.222222222222,-8.31818181818182)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_180.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.0002488174,-8.72727272727273)(1478.00049762651,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00066349464,-9.27272727272727)(1478.00058056104,-9.45454545454546)(1478.00058056104,-9.63636363636364)(1478.00066349464,-9.81818181818182)(1478.00049762651,-10)(1478.0002488174,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.81818181818182)(1478.00012440663,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00029027891,-9.27272727272727)(1478.00020734323,-9.45454545454546)(1478.00020734323,-9.63636363636364)(1478.00029027891,-9.81818181818182)(1478.00012440663,-10)(1478,-10.0909090909091)(1463.07070707071,-10.0909090909091)(1448.14141414141,-10.1590909090909)(1433.21212121212,-10.1590909090909)(1418.28282828283,-10.1590909090909)(1403.35353535354,-10.1590909090909)(1399.62121212121,-10.1818181818182)(1388.42424242424,-10.2727272727273)(1373.49494949495,-10.3454545454545)(1358.56565656566,-10.3454545454545)(1343.63636363636,-10.3409090909091)(1328.70707070707,-10.2727272727273)(1313.77777777778,-10.2727272727273)(1298.84848484848,-10.2954545454545)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2045454545455)(1261.52525252525,-10.1818181818182)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1666666666667)(1209.27272727273,-10.1666666666667)(1205.5404040404,-10.1818181818182)(1194.34343434343,-10.25)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.2121212121212)(1149.55555555556,-10.2121212121212)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.2121212121212)(1104.76767676768,-10.2045454545455)(1089.83838383838,-10.2363636363636)(1074.90909090909,-10.3181818181818)(1063.71212121212,-10.3636363636364)(1059.9797979798,-10.3818181818182)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2727272727273)(1000.26262626263,-10.2045454545455)(985.333333333333,-10.2121212121212)(970.40404040404,-10.2727272727273)(955.474747474748,-10.25)(944.277777777778,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.0909090909091)(910.686868686869,-10.0227272727273)(895.757575757576,-10.030303030303)(888.292929292929,-10)(880.828282828283,-9.98181818181818)(865.89898989899,-9.94545454545455)(852.835858585859,-9.81818181818182)(850.969696969697,-9.8)(836.040404040404,-9.78787878787879)(826.709595959596,-9.63636363636364)(821.111111111111,-9.54545454545455)(806.181818181818,-9.5)(798.717171717172,-9.45454545454546)(791.252525252525,-9.43181818181818)(776.323232323232,-9.36363636363636)(770.724747474747,-9.27272727272727)(768.858585858586,-9.09090909090909)(763.260101010101,-8.90909090909091)(761.393939393939,-8.81818181818182)(757.661616161616,-8.72727272727273)(758.905723905724,-8.54545454545455)(761.393939393939,-8.45454545454545)(765.126262626263,-8.36363636363636)(776.323232323232,-8.22727272727273)(778.189393939394,-8.18181818181818)(791.252525252525,-8.02272727272727)(794.984848484849,-8)(806.181818181818,-7.94545454545455)(821.111111111111,-7.86363636363636)(825.589898989899,-7.81818181818182)(833.552188552189,-7.63636363636364)(836.040404040404,-7.61363636363636)(850.969696969697,-7.52272727272727)(858.434343434343,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.34848484848485)(893.26936026936,-7.27272727272727)(895.757575757576,-7.25)(910.686868686869,-7.24242424242424)(925.616161616162,-7.20454545454546)(940.545454545455,-7.20454545454546)(955.474747474747,-7.13636363636364)(970.40404040404,-7.13636363636364)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1007.72727272727,-7.09090909090909)(1015.19191919192,-7.06818181818182)(1022.65656565657,-7.09090909090909)(1030.12121212121,-7.10606060606061)(1045.05050505051,-7.13636363636364)(1059.9797979798,-7.13636363636364)(1074.90909090909,-7.20454545454546)(1089.83838383838,-7.25)(1092.3265993266,-7.27272727272727)(1104.76767676768,-7.42424242424243)(1112.23232323232,-7.45454545454546)(1119.69696969697,-7.46969696969697)(1134.62626262626,-7.56060606060606)(1149.55555555556,-7.58181818181818)(1164.48484848485,-7.61363636363636)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.65151515151515)(1194.34343434343,-7.68181818181818)(1209.27272727273,-7.71212121212121)(1224.20202020202,-7.68181818181818)(1239.13131313131,-7.65454545454546)(1246.59595959596,-7.63636363636364)(1254.06060606061,-7.61818181818182)(1261.52525252525,-7.63636363636364)(1268.9898989899,-7.66666666666667)(1283.91919191919,-7.72727272727273)(1298.84848484848,-7.70454545454546)(1313.77777777778,-7.72727272727273)(1328.70707070707,-7.72727272727273)(1339.90404040404,-7.81818181818182)(1343.63636363636,-7.84848484848485)(1358.56565656566,-7.84848484848485)(1371.00673400673,-8)(1373.49494949495,-8.09090909090909)(1380.9595959596,-8.18181818181818)(1388.42424242424,-8.27272727272727)(1395.88888888889,-8.36363636363636)(1403.35353535354,-8.39393939393939)(1418.28282828283,-8.43181818181818)(1433.21212121212,-8.47727272727273)(1440.67676767677,-8.54545454545455)(1448.14141414141,-8.61363636363636)(1460.58249158249,-8.72727272727273)(1463.07070707071,-8.77272727272727)(1478,-8.81818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.43181818181818)(1434.70505050505,-9.45454545454546)(1435.07828282828,-9.63636363636364)(1433.21212121212,-9.68181818181818)(1418.28282828283,-9.70454545454546)(1403.35353535354,-9.72727272727273)(1390.91245791246,-9.81818181818182)(1388.42424242424,-9.84848484848485)(1379.09343434343,-10)(1373.49494949495,-10.0454545454545)(1358.56565656566,-10.0454545454545)(1343.63636363636,-10.0151515151515)(1339.90404040404,-10)(1328.70707070707,-9.90909090909091)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.96969696969697)(1283.91919191919,-9.97727272727273)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.89393939393939)(1239.13131313131,-9.83333333333333)(1224.20202020202,-9.89393939393939)(1209.27272727273,-9.87272727272727)(1194.34343434343,-9.93181818181818)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.88636363636364)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.88636363636364)(1104.76767676768,-9.90909090909091)(1089.83838383838,-9.94545454545455)(1082.37373737374,-10)(1074.90909090909,-10.0454545454545)(1059.9797979798,-10.1060606060606)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1017.68013468013,-10)(1015.19191919192,-9.97727272727273)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.88636363636364)(970.40404040404,-9.90909090909091)(955.474747474748,-9.93181818181818)(940.545454545455,-9.87272727272727)(929.348484848485,-9.81818181818182)(925.616161616162,-9.79545454545455)(910.686868686869,-9.72727272727273)(895.757575757576,-9.70454545454546)(884.560606060606,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.61363636363636)(850.969696969697,-9.47272727272727)(848.481481481482,-9.45454545454546)(836.040404040404,-9.3030303030303)(834.174242424242,-9.27272727272727)(821.111111111111,-9.11363636363636)(818.622895622896,-9.09090909090909)(806.181818181818,-8.97727272727273)(800.583333333333,-8.90909090909091)(804.315656565657,-8.72727272727273)(798.717171717172,-8.54545454545455)(803.693602693603,-8.36363636363636)(806.181818181818,-8.34090909090909)(821.111111111111,-8.2)(824.843434343434,-8.18181818181818)(836.040404040404,-8.04545454545455)(839.772727272727,-8)(850.969696969697,-7.90909090909091)(856.568181818182,-7.81818181818182)(865.89898989899,-7.72727272727273)(880.828282828283,-7.65909090909091)(883.316498316498,-7.63636363636364)(895.757575757576,-7.54545454545455)(910.686868686869,-7.56818181818182)(925.616161616162,-7.52272727272727)(940.545454545455,-7.52272727272727)(948.010101010101,-7.45454545454546)(955.474747474747,-7.40909090909091)(970.40404040404,-7.40909090909091)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1015.19191919192,-7.36363636363636)(1030.12121212121,-7.4)(1045.05050505051,-7.43636363636364)(1059.9797979798,-7.40909090909091)(1065.57828282828,-7.45454545454546)(1074.90909090909,-7.56818181818182)(1089.83838383838,-7.61818181818182)(1092.3265993266,-7.63636363636364)(1104.76767676768,-7.75)(1119.69696969697,-7.79545454545455)(1127.16161616162,-7.81818181818182)(1134.62626262626,-7.83636363636364)(1149.55555555556,-7.87272727272727)(1164.48484848485,-7.90909090909091)(1179.41414141414,-7.94545454545455)(1194.34343434343,-7.95454545454546)(1209.27272727273,-7.98484848484848)(1224.20202020202,-7.95454545454546)(1239.13131313131,-7.95454545454546)(1254.06060606061,-7.95454545454546)(1265.25757575758,-8)(1268.9898989899,-8.04545454545455)(1283.91919191919,-8.09090909090909)(1298.84848484848,-8.09090909090909)(1310.04545454545,-8.18181818181818)(1313.77777777778,-8.21212121212121)(1328.70707070707,-8.27272727272727)(1339.90404040404,-8.36363636363636)(1343.63636363636,-8.39393939393939)(1356.07744107744,-8.54545454545455)(1358.56565656566,-8.56818181818182)(1373.49494949495,-8.67272727272727)(1379.09343434343,-8.72727272727273)(1388.42424242424,-8.84090909090909)(1399.62121212121,-8.90909090909091)(1403.35353535354,-8.95454545454546)(1418.28282828283,-9.04545454545455)(1420.14898989899,-9.09090909090909)(1422.76161616162,-9.27272727272727)(1433.21212121212,-9.43181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-7.68181818181818)(77.1346801346801,-7.63636363636364)(89.5757575757576,-7.48484848484849)(97.040404040404,-7.45454545454546)(104.505050505051,-7.42424242424243)(119.434343434343,-7.36363636363636)(134.363636363636,-7.36363636363636)(149.292929292929,-7.36363636363636)(164.222222222222,-7.40909090909091)(179.151515151515,-7.40909090909091)(194.080808080808,-7.40909090909091)(209.010101010101,-7.36363636363636)(223.939393939394,-7.36363636363636)(238.868686868687,-7.36363636363636)(253.79797979798,-7.42424242424243)(261.262626262626,-7.45454545454546)(268.727272727273,-7.48484848484849)(283.656565656566,-7.54545454545455)(298.585858585859,-7.54545454545455)(313.515151515152,-7.60606060606061)(317.247474747475,-7.63636363636364)(328.444444444444,-7.77272727272727)(335.909090909091,-7.81818181818182)(343.373737373737,-7.84848484848485)(358.30303030303,-7.86363636363636)(360.791245791246,-7.81818181818182)(373.232323232323,-7.66666666666667)(388.161616161616,-7.66666666666667)(403.090909090909,-7.66666666666667)(406.823232323232,-7.63636363636364)(414.287878787879,-7.45454545454546)(418.020202020202,-7.43181818181818)(432.949494949495,-7.36363636363636)(447.878787878788,-7.32727272727273)(459.075757575758,-7.27272727272727)(462.808080808081,-7.24242424242424)(477.737373737374,-7.18181818181818)(492.666666666667,-7.15909090909091)(507.59595959596,-7.18181818181818)(522.525252525253,-7.24242424242424)(537.454545454546,-7.25)(552.383838383838,-7.21818181818182)(567.313131313131,-7.20454545454546)(582.242424242424,-7.15909090909091)(597.171717171717,-7.22727272727273)(612.10101010101,-7.18181818181818)(623.29797979798,-7.27272727272727)(627.030303030303,-7.3030303030303)(641.959595959596,-7.40909090909091)(645.691919191919,-7.45454545454546)(656.888888888889,-7.59090909090909)(660.621212121212,-7.63636363636364)(671.818181818182,-7.77272727272727)(674.306397306397,-7.81818181818182)(684.259259259259,-8)(686.747474747475,-8.09090909090909)(689.23569023569,-8.18181818181818)(689.23569023569,-8.36363636363636)(686.747474747475,-8.40909090909091)(679.282828282828,-8.54545454545455)(671.818181818182,-8.63636363636364)(660.621212121212,-8.72727272727273)(656.888888888889,-8.75757575757576)(641.959595959596,-8.81818181818182)(627.030303030303,-8.81818181818182)(612.10101010101,-8.86363636363636)(604.636363636364,-8.90909090909091)(597.171717171717,-8.93939393939394)(582.242424242424,-9.02272727272727)(567.313131313131,-9.07272727272727)(563.580808080808,-9.09090909090909)(552.383838383838,-9.15909090909091)(537.454545454546,-9.18181818181818)(522.525252525253,-9.20454545454546)(507.59595959596,-9.21818181818182)(492.666666666667,-9.25757575757576)(477.737373737374,-9.25454545454546)(462.808080808081,-9.20454545454546)(450.367003367003,-9.09090909090909)(447.878787878788,-9.06060606060606)(432.949494949495,-8.93939393939394)(425.484848484849,-8.90909090909091)(418.020202020202,-8.88636363636364)(403.090909090909,-8.81818181818182)(388.161616161616,-8.77272727272727)(373.232323232323,-8.77272727272727)(358.30303030303,-8.81818181818182)(343.373737373737,-8.81818181818182)(328.444444444444,-8.81818181818182)(313.515151515152,-8.84090909090909)(298.585858585859,-8.88636363636364)(291.121212121212,-8.90909090909091)(283.656565656566,-8.93939393939394)(268.727272727273,-9.06060606060606)(264.99494949495,-9.09090909090909)(253.79797979798,-9.18181818181818)(242.60101010101,-9.27272727272727)(238.868686868687,-9.3030303030303)(223.939393939394,-9.42424242424243)(216.474747474747,-9.45454545454546)(209.010101010101,-9.48484848484848)(194.080808080808,-9.54545454545455)(179.151515151515,-9.54545454545455)(164.222222222222,-9.54545454545455)(149.292929292929,-9.54545454545455)(138.09595959596,-9.45454545454546)(134.363636363636,-9.40909090909091)(126.89898989899,-9.27272727272727)(121.922558922559,-9.09090909090909)(119.434343434343,-9)(116.946127946128,-8.90909090909091)(110.103535353535,-8.72727272727273)(110.103535353535,-8.54545454545455)(106.993265993266,-8.36363636363636)(104.505050505051,-8.31818181818182)(89.5757575757576,-8.27272727272727)(82.1111111111111,-8.18181818181818)(74.6464646464647,-8.04545454545455)(72.1582491582492,-8)(67.1818181818182,-7.81818181818182)(74.6464646464647,-7.68181818181818)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.78787878787879)(462.808080808081,-7.66666666666667)(470.272727272727,-7.63636363636364)(477.737373737374,-7.60606060606061)(492.666666666667,-7.48484848484849)(507.59595959596,-7.54545454545455)(522.525252525253,-7.56818181818182)(537.454545454546,-7.54545454545455)(552.383838383838,-7.50909090909091)(567.313131313131,-7.52272727272727)(582.242424242424,-7.54545454545455)(589.707070707071,-7.63636363636364)(597.171717171717,-7.70454545454546)(606.502525252525,-7.81818181818182)(612.10101010101,-7.95454545454546)(615.833333333333,-8)(615.833333333333,-8.18181818181818)(612.10101010101,-8.21212121212121)(599.659932659933,-8.36363636363636)(597.171717171717,-8.39393939393939)(584.73063973064,-8.54545454545455)(582.242424242424,-8.57575757575757)(569.801346801347,-8.72727272727273)(567.313131313131,-8.74545454545454)(552.383838383838,-8.79545454545455)(537.454545454546,-8.81818181818182)(522.525252525253,-8.87878787878788)(507.59595959596,-8.87878787878788)(500.131313131313,-8.90909090909091)(492.666666666667,-8.93181818181818)(488.934343434343,-8.90909090909091)(480.225589225589,-8.72727272727273)(477.737373737374,-8.63636363636364)(474.005050505051,-8.54545454545455)(462.808080808081,-8.45454545454545)(455.343434343434,-8.36363636363636)(447.878787878788,-8.22727272727273)(445.390572390572,-8.18181818181818)(446.012626262626,-8)(445.390572390572,-7.81818181818182)(447.878787878788,-7.78787878787879)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (477.737373737374,-14.6818181818182)(488.934343434343,-14.5454545454545)(492.666666666667,-14.5151515151515)(507.59595959596,-14.3939393939394)(515.060606060606,-14.3636363636364)(522.525252525253,-14.3333333333333)(537.454545454546,-14.2727272727273)(552.383838383838,-14.2727272727273)(567.313131313131,-14.2727272727273)(582.242424242424,-14.2727272727273)(597.171717171717,-14.2727272727273)(612.10101010101,-14.2727272727273)(627.030303030303,-14.2727272727273)(641.959595959596,-14.2727272727273)(656.888888888889,-14.2727272727273)(671.818181818182,-14.2727272727273)(686.747474747475,-14.3181818181818)(690.479797979798,-14.3636363636364)(690.479797979798,-14.5454545454545)(686.747474747475,-14.5757575757576)(671.818181818182,-14.6969696969697)(664.353535353535,-14.7272727272727)(656.888888888889,-14.7575757575758)(641.959595959596,-14.8787878787879)(634.494949494949,-14.9090909090909)(627.030303030303,-14.9393939393939)(612.10101010101,-15.0606060606061)(604.636363636364,-15.0909090909091)(597.171717171717,-15.1212121212121)(582.242424242424,-15.1818181818182)(567.313131313131,-15.2424242424242)(559.848484848485,-15.2727272727273)(552.383838383838,-15.3030303030303)(537.454545454546,-15.3636363636364)(522.525252525253,-15.3636363636364)(507.59595959596,-15.3636363636364)(492.666666666667,-15.3030303030303)(488.934343434343,-15.2727272727273)(477.737373737374,-15.1363636363636)(475.249158249158,-15.0909090909091)(470.272727272727,-14.9090909090909)(475.249158249158,-14.7272727272727)(477.737373737374,-14.6818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (164.222222222222,-8.31818181818182)(179.151515151515,-8.21212121212121)(194.080808080808,-8.21212121212121)(209.010101010101,-8.22727272727273)(220.207070707071,-8.36363636363636)(221.451178451178,-8.54545454545455)(211.498316498317,-8.72727272727273)(209.010101010101,-8.75757575757576)(201.545454545455,-8.72727272727273)(194.080808080808,-8.68181818181818)(179.151515151515,-8.65909090909091)(166.710437710438,-8.54545454545455)(164.222222222222,-8.45454545454545)(160.489898989899,-8.36363636363636)(164.222222222222,-8.31818181818182)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091)(119.434343434343,-8.36363636363636)(791.252525252525,-8.72727272727273)(627.030303030303,-7.63636363636364)(1224.20202020202,-7.81818181818182)(791.252525252525,-9.09090909090909)(1089.83838383838,-10.1818181818182)(806.181818181818,-8.18181818181818)(641.959595959596,-8)(821.111111111111,-8)(940.545454545455,-7.27272727272727)(1030.12121212121,-7.27272727272727)(403.090909090909,-8.36363636363636)(1418.28282828283,-10)(283.656565656566,-8.18181818181818)(268.727272727273,-8)(477.737373737374,-7.45454545454546)(1224.20202020202,-10)(1209.27272727273,-10)(1283.91919191919,-10)(134.363636363636,-8.54545454545455) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_20.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,1.0100953990001e-06)(358.30303030303,4.04031425463559e-06)(373.232323232323,7.07043210985092e-06)(388.161616161616,9.09045456864996e-06)(403.090909090909,9.09045456864996e-06)(418.020202020202,9.09045456864996e-06)(432.949494949495,9.09045456864996e-06)(447.878787878788,9.09045456864996e-06)(462.808080808081,9.09045456864996e-06)(477.737373737374,9.09045456864996e-06)(492.666666666667,9.09045456864996e-06)(507.59595959596,9.09045456864996e-06)(522.525252525253,9.09045456864996e-06)(537.454545454546,9.09045456864996e-06)(552.383838383838,9.09045456864996e-06)(567.313131313131,9.09045456864996e-06)(582.242424242424,9.09045456864996e-06)(597.171717171717,9.09045456864996e-06)(612.10101010101,9.09045456864996e-06)(627.030303030303,9.09045456864996e-06)(641.959595959596,9.09045456864996e-06)(656.888888888889,9.09045456864996e-06)(671.818181818182,9.09045456864996e-06)(686.747474747475,9.09045456864996e-06)(701.676767676768,9.09045456864996e-06)(716.606060606061,9.09045456864996e-06)(731.535353535354,9.09045456864996e-06)(746.464646464646,9.09045456864996e-06)(761.393939393939,9.09045456864996e-06)(776.323232323232,9.09045456864996e-06)(791.252525252525,9.09045456864996e-06)(806.181818181818,9.09045456864996e-06)(821.111111111111,9.09045456864996e-06)(836.040404040404,9.09045456864996e-06)(850.969696969697,9.09045456864996e-06)(865.89898989899,9.09045456864996e-06)(880.828282828283,9.09045456864996e-06)(895.757575757576,9.09045456864996e-06)(910.686868686869,9.09045456864996e-06)(925.616161616162,9.09045456864996e-06)(940.545454545455,9.09045456864996e-06)(955.474747474747,9.09045456864996e-06)(970.40404040404,9.09045456864996e-06)(985.333333333333,9.09045456864996e-06)(1000.26262626263,9.09045456864996e-06)(1015.19191919192,9.09045456864996e-06)(1030.12121212121,9.09045456864996e-06)(1045.05050505051,9.09045456864996e-06)(1059.9797979798,9.09045456864996e-06)(1074.90909090909,9.09045456864996e-06)(1089.83838383838,9.09045456864996e-06)(1104.76767676768,9.09045456864996e-06)(1119.69696969697,9.09045456864996e-06)(1134.62626262626,9.09045456864996e-06)(1149.55555555556,9.09045456864996e-06)(1164.48484848485,9.09045456864996e-06)(1179.41414141414,9.09045456864996e-06)(1194.34343434343,9.09045456864996e-06)(1209.27272727273,9.09045456864996e-06)(1224.20202020202,9.09045456864996e-06)(1239.13131313131,9.09045456864996e-06)(1254.06060606061,9.09045456864996e-06)(1268.9898989899,9.09045456864996e-06)(1283.91919191919,9.09045456864996e-06)(1298.84848484848,9.09045456864996e-06)(1313.77777777778,9.09045456864996e-06)(1328.70707070707,9.09045456864996e-06)(1343.63636363636,9.09045456864996e-06)(1358.56565656566,9.09045456864996e-06)(1373.49494949495,9.09045456864996e-06)(1388.42424242424,9.09045456864996e-06)(1403.35353535354,9.09045456864996e-06)(1418.28282828283,9.09045456864996e-06)(1433.21212121212,9.09045456864996e-06)(1448.14141414141,9.09045456864996e-06)(1463.07070707071,9.09045456864996e-06)(1478,9.09045456864996e-06)(1478.00074642733,0)(1478.00074642733,-0.181818181818183)(1478.00074642733,-0.363636363636363)(1478.00074642733,-0.545454545454547)(1478.00074642733,-0.727272727272727)(1478.00074642733,-0.90909090909091)(1478.00074642733,-1.09090909090909)(1478.00074642733,-1.27272727272727)(1478.00074642733,-1.45454545454545)(1478.00074642733,-1.63636363636364)(1478.00074642733,-1.81818181818182)(1478.00049762651,-2)(1478.0002488174,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478.0002488174,-6.54545454545455)(1478.00049762651,-6.72727272727273)(1478.00074642733,-6.90909090909091)(1478.00074642733,-7.09090909090909)(1478.00074642733,-7.27272727272727)(1478.00074642733,-7.45454545454546)(1478.00074642733,-7.63636363636364)(1478.00074642733,-7.81818181818182)(1478.00074642733,-8)(1478.00074642733,-8.18181818181818)(1478.00074642733,-8.36363636363636)(1478.00074642733,-8.54545454545455)(1478.00074642733,-8.72727272727273)(1478.00074642733,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00074642733,-9.27272727272727)(1478.00074642733,-9.45454545454546)(1478.00074642733,-9.63636363636364)(1478.00074642733,-9.81818181818182)(1478.00074642733,-10)(1478.00074642733,-10.1818181818182)(1478.00074642733,-10.3636363636364)(1478.00074642733,-10.5454545454545)(1478.00074642733,-10.7272727272727)(1478.00074642733,-10.9090909090909)(1478.00074642733,-11.0909090909091)(1478.00074642733,-11.2727272727273)(1478.00074642733,-11.4545454545455)(1478.00074642733,-11.6363636363636)(1478.00074642733,-11.8181818181818)(1478.00074642733,-12)(1478.00049762651,-12.1818181818182)(1478.0002488174,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478.0002488174,-17.2727272727273)(1478.00049762651,-17.4545454545455)(1478.00074642733,-17.6363636363636)(1478.00074642733,-17.8181818181818)(1478.00074642733,-18)(1478,-18.0000090904546)(1463.07070707071,-18.0000090904546)(1448.14141414141,-18.0000090904546)(1433.21212121212,-18.0000090904546)(1418.28282828283,-18.0000090904546)(1403.35353535354,-18.0000090904546)(1388.42424242424,-18.0000090904546)(1373.49494949495,-18.0000090904546)(1358.56565656566,-18.0000090904546)(1343.63636363636,-18.0000090904546)(1328.70707070707,-18.0000090904546)(1313.77777777778,-18.0000090904546)(1298.84848484848,-18.0000090904546)(1283.91919191919,-18.0000090904546)(1268.9898989899,-18.0000090904546)(1254.06060606061,-18.0000090904546)(1239.13131313131,-18.0000090904546)(1224.20202020202,-18.0000090904546)(1209.27272727273,-18.0000090904546)(1194.34343434343,-18.0000090904546)(1179.41414141414,-18.0000090904546)(1164.48484848485,-18.0000090904546)(1149.55555555556,-18.0000090904546)(1134.62626262626,-18.0000090904546)(1119.69696969697,-18.0000090904546)(1104.76767676768,-18.0000090904546)(1089.83838383838,-18.0000090904546)(1074.90909090909,-18.0000090904546)(1059.9797979798,-18.0000090904546)(1045.05050505051,-18.0000090904546)(1030.12121212121,-18.0000090904546)(1015.19191919192,-18.0000090904546)(1000.26262626263,-18.0000090904546)(985.333333333333,-18.0000090904546)(970.40404040404,-18.0000090904546)(955.474747474747,-18.0000090904546)(940.545454545455,-18.0000090904546)(925.616161616162,-18.0000090904546)(910.686868686869,-18.0000090904546)(895.757575757576,-18.0000090904546)(880.828282828283,-18.0000090904546)(865.89898989899,-18.0000090904546)(850.969696969697,-18.0000090904546)(836.040404040404,-18.0000090904546)(821.111111111111,-18.0000090904546)(806.181818181818,-18.0000090904546)(791.252525252525,-18.0000090904546)(776.323232323232,-18.0000090904546)(761.393939393939,-18.0000090904546)(746.464646464646,-18.0000090904546)(731.535353535354,-18.0000090904546)(716.606060606061,-18.0000090904546)(701.676767676768,-18.0000090904546)(686.747474747475,-18.0000090904546)(671.818181818182,-18.0000090904546)(656.888888888889,-18.0000090904546)(641.959595959596,-18.0000090904546)(627.030303030303,-18.0000090904546)(612.10101010101,-18.0000090904546)(597.171717171717,-18.0000090904546)(582.242424242424,-18.0000090904546)(567.313131313131,-18.0000090904546)(552.383838383838,-18.0000090904546)(537.454545454546,-18.0000090904546)(522.525252525253,-18.0000090904546)(507.59595959596,-18.0000090904546)(492.666666666667,-18.0000090904546)(477.737373737374,-18.0000090904546)(462.808080808081,-18.0000090904546)(447.878787878788,-18.0000090904546)(432.949494949495,-18.0000090904546)(418.020202020202,-18.000006060404)(403.090909090909,-18.0000030302525)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(-0.000248817401863321,-15.0909090909091)(-0.000497626510092015,-14.9090909090909)(-0.000746427325097138,-14.7272727272727)(-0.000746427325097138,-14.5454545454545)(-0.000746427325097138,-14.3636363636364)(-0.000746427325097138,-14.1818181818182)(-0.000746427325097138,-14)(-0.000746427325097138,-13.8181818181818)(-0.000746427325097138,-13.6363636363636)(-0.000746427325097138,-13.4545454545455)(-0.000746427325097138,-13.2727272727273)(-0.000746427325097138,-13.0909090909091)(-0.000746427325097138,-12.9090909090909)(-0.000746427325097138,-12.7272727272727)(-0.000746427325097138,-12.5454545454545)(-0.000746427325097138,-12.3636363636364)(-0.000746427325097138,-12.1818181818182)(-0.000746427325097138,-12)(-0.000746427325097138,-11.8181818181818)(-0.000746427325097138,-11.6363636363636)(-0.000746427325097138,-11.4545454545455)(-0.000746427325097138,-11.2727272727273)(-0.000746427325097138,-11.0909090909091)(-0.000746427325097138,-10.9090909090909)(-0.000746427325097138,-10.7272727272727)(-0.000746427325097138,-10.5454545454545)(-0.000746427325097138,-10.3636363636364)(-0.000746427325097138,-10.1818181818182)(-0.000746427325097138,-10)(-0.000746427325097138,-9.81818181818182)(-0.000497626510092015,-9.63636363636364)(-0.000248817401863321,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(-0.000248817401863321,-8)(-0.000497626510092015,-7.81818181818182)(-0.000746427325097138,-7.63636363636364)(-0.000746427325097138,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000497626510092015,-7.09090909090909)(-0.000248817401863321,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(-0.000248817401863321,-4.36363636363636)(-0.000497626510092015,-4.18181818181818)(-0.000746427325097138,-4)(-0.000746427325097138,-3.81818181818182)(-0.000746427325097138,-3.63636363636364)(-0.000746427325097138,-3.45454545454546)(-0.000746427325097138,-3.27272727272727)(-0.000746427325097138,-3.09090909090909)(-0.000746427325097138,-2.90909090909091)(-0.000746427325097138,-2.72727272727273)(-0.000497626510092015,-2.54545454545455)(-0.000248817401863321,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-2.45454545454545)(14.9292929292929,-2.45454545454545)(29.8585858585859,-2.45454545454545)(44.7878787878788,-2.45454545454545)(59.7171717171717,-2.45454545454545)(74.6464646464647,-2.45454545454545)(89.5757575757576,-2.39393939393939)(97.040404040404,-2.36363636363636)(104.505050505051,-2.33333333333333)(119.434343434343,-2.27272727272727)(134.363636363636,-2.27272727272727)(149.292929292929,-2.21212121212121)(156.757575757576,-2.18181818181818)(164.222222222222,-2.15151515151515)(179.151515151515,-2.09090909090909)(194.080808080808,-2.03030303030303)(201.545454545455,-2)(209.010101010101,-1.96969696969697)(223.939393939394,-1.84848484848485)(231.40404040404,-1.81818181818182)(238.868686868687,-1.78787878787879)(253.79797979798,-1.66666666666667)(257.530303030303,-1.63636363636364)(268.727272727273,-1.54545454545455)(279.924242424242,-1.45454545454545)(283.656565656566,-1.42424242424242)(298.585858585859,-1.3030303030303)(302.318181818182,-1.27272727272727)(313.515151515152,-1.18181818181818)(320.979797979798,-1.09090909090909)(328.444444444444,-0.954545454545455)(330.93265993266,-0.90909090909091)(340.885521885522,-0.727272727272727)(343.373737373737,-0.636363636363637)(345.861952861953,-0.545454545454547)(350.838383838384,-0.363636363636363)(355.814814814815,-0.181818181818183)(358.30303030303,-0.0909090909090917)(360.791245791246,0)(373.232323232323,2.52515432531587e-06)(388.161616161616,4.54522728432498e-06)(403.090909090909,4.54522728432498e-06)(418.020202020202,4.54522728432498e-06)(432.949494949495,4.54522728432498e-06)(447.878787878788,4.54522728432498e-06)(462.808080808081,4.54522728432498e-06)(477.737373737374,4.54522728432498e-06)(492.666666666667,4.54522728432498e-06)(507.59595959596,4.54522728432498e-06)(522.525252525253,4.54522728432498e-06)(537.454545454546,4.54522728432498e-06)(552.383838383838,4.54522728432498e-06)(567.313131313131,4.54522728432498e-06)(582.242424242424,4.54522728432498e-06)(597.171717171717,4.54522728432498e-06)(612.10101010101,4.54522728432498e-06)(627.030303030303,4.54522728432498e-06)(641.959595959596,4.54522728432498e-06)(656.888888888889,4.54522728432498e-06)(671.818181818182,4.54522728432498e-06)(686.747474747475,4.54522728432498e-06)(701.676767676768,4.54522728432498e-06)(716.606060606061,4.54522728432498e-06)(731.535353535354,4.54522728432498e-06)(746.464646464646,4.54522728432498e-06)(761.393939393939,4.54522728432498e-06)(776.323232323232,4.54522728432498e-06)(791.252525252525,4.54522728432498e-06)(806.181818181818,4.54522728432498e-06)(821.111111111111,4.54522728432498e-06)(836.040404040404,4.54522728432498e-06)(850.969696969697,4.54522728432498e-06)(865.89898989899,4.54522728432498e-06)(880.828282828283,4.54522728432498e-06)(895.757575757576,4.54522728432498e-06)(910.686868686869,4.54522728432498e-06)(925.616161616162,4.54522728432498e-06)(940.545454545455,4.54522728432498e-06)(955.474747474747,4.54522728432498e-06)(970.40404040404,4.54522728432498e-06)(985.333333333333,4.54522728432498e-06)(1000.26262626263,4.54522728432498e-06)(1015.19191919192,4.54522728432498e-06)(1030.12121212121,4.54522728432498e-06)(1045.05050505051,4.54522728432498e-06)(1059.9797979798,4.54522728432498e-06)(1074.90909090909,4.54522728432498e-06)(1089.83838383838,4.54522728432498e-06)(1104.76767676768,4.54522728432498e-06)(1119.69696969697,4.54522728432498e-06)(1134.62626262626,4.54522728432498e-06)(1149.55555555556,4.54522728432498e-06)(1164.48484848485,4.54522728432498e-06)(1179.41414141414,4.54522728432498e-06)(1194.34343434343,4.54522728432498e-06)(1209.27272727273,4.54522728432498e-06)(1224.20202020202,4.54522728432498e-06)(1239.13131313131,4.54522728432498e-06)(1254.06060606061,4.54522728432498e-06)(1268.9898989899,4.54522728432498e-06)(1283.91919191919,4.54522728432498e-06)(1298.84848484848,4.54522728432498e-06)(1313.77777777778,4.54522728432498e-06)(1328.70707070707,4.54522728432498e-06)(1343.63636363636,4.54522728432498e-06)(1358.56565656566,4.54522728432498e-06)(1373.49494949495,4.54522728432498e-06)(1388.42424242424,4.54522728432498e-06)(1403.35353535354,4.54522728432498e-06)(1418.28282828283,4.54522728432498e-06)(1433.21212121212,4.54522728432498e-06)(1448.14141414141,4.54522728432498e-06)(1463.07070707071,4.54522728432498e-06)(1478,4.54522728432498e-06)(1478.00037321366,0)(1478.00037321366,-0.181818181818183)(1478.00037321366,-0.363636363636363)(1478.00037321366,-0.545454545454547)(1478.00037321366,-0.727272727272727)(1478.00037321366,-0.90909090909091)(1478.00037321366,-1.09090909090909)(1478.00037321366,-1.27272727272727)(1478.00037321366,-1.45454545454545)(1478.00037321366,-1.63636363636364)(1478.00037321366,-1.81818181818182)(1478.00012440663,-2)(1478,-2.09090909090909)(1463.07070707071,-2.09090909090909)(1448.14141414141,-2.09090909090909)(1433.21212121212,-2.03030303030303)(1425.74747474747,-2)(1418.28282828283,-1.96969696969697)(1403.35353535354,-1.90909090909091)(1388.42424242424,-1.90909090909091)(1373.49494949495,-1.90909090909091)(1358.56565656566,-1.90909090909091)(1343.63636363636,-1.90909090909091)(1328.70707070707,-1.90909090909091)(1313.77777777778,-1.90909090909091)(1298.84848484848,-1.96969696969697)(1291.38383838384,-2)(1283.91919191919,-2.03030303030303)(1268.9898989899,-2.09090909090909)(1254.06060606061,-2.09090909090909)(1239.13131313131,-2.09090909090909)(1224.20202020202,-2.09090909090909)(1209.27272727273,-2.15151515151515)(1201.80808080808,-2.18181818181818)(1194.34343434343,-2.21212121212121)(1179.41414141414,-2.27272727272727)(1164.48484848485,-2.33333333333333)(1157.0202020202,-2.36363636363636)(1149.55555555556,-2.39393939393939)(1134.62626262626,-2.51515151515151)(1127.16161616162,-2.54545454545455)(1119.69696969697,-2.57575757575758)(1104.76767676768,-2.6969696969697)(1097.30303030303,-2.72727272727273)(1089.83838383838,-2.75757575757576)(1074.90909090909,-2.87878787878788)(1067.44444444444,-2.90909090909091)(1059.9797979798,-2.93939393939394)(1045.05050505051,-3.06060606060606)(1041.31818181818,-3.09090909090909)(1030.12121212121,-3.18181818181818)(1022.65656565657,-3.27272727272727)(1015.19191919192,-3.36363636363636)(1007.72727272727,-3.45454545454546)(1000.26262626263,-3.54545454545455)(992.79797979798,-3.63636363636364)(985.333333333333,-3.72727272727273)(977.868686868687,-3.81818181818182)(970.40404040404,-3.90909090909091)(962.939393939394,-4)(955.474747474747,-4.09090909090909)(948.010101010101,-4.18181818181818)(940.545454545455,-4.27272727272727)(933.080808080808,-4.36363636363636)(925.616161616162,-4.45454545454545)(914.419191919192,-4.54545454545455)(910.686868686869,-4.57575757575758)(895.757575757576,-4.6969696969697)(888.292929292929,-4.72727272727273)(880.828282828283,-4.75757575757576)(865.89898989899,-4.87878787878788)(858.434343434343,-4.90909090909091)(850.969696969697,-4.93939393939394)(836.040404040404,-5)(821.111111111111,-5)(806.181818181818,-5.06060606060606)(798.717171717172,-5.09090909090909)(791.252525252525,-5.12121212121212)(776.323232323232,-5.18181818181818)(761.393939393939,-5.18181818181818)(746.464646464646,-5.24242424242424)(739,-5.27272727272727)(731.535353535354,-5.3030303030303)(716.606060606061,-5.36363636363636)(701.676767676768,-5.36363636363636)(686.747474747475,-5.42424242424242)(679.282828282828,-5.45454545454546)(671.818181818182,-5.48484848484849)(656.888888888889,-5.54545454545455)(641.959595959596,-5.54545454545455)(627.030303030303,-5.54545454545455)(612.10101010101,-5.54545454545455)(597.171717171717,-5.54545454545455)(582.242424242424,-5.54545454545455)(567.313131313131,-5.54545454545455)(552.383838383838,-5.54545454545455)(537.454545454546,-5.54545454545455)(522.525252525253,-5.54545454545455)(507.59595959596,-5.54545454545455)(492.666666666667,-5.54545454545455)(477.737373737374,-5.54545454545455)(462.808080808081,-5.54545454545455)(447.878787878788,-5.54545454545455)(432.949494949495,-5.54545454545455)(418.020202020202,-5.54545454545455)(403.090909090909,-5.54545454545455)(388.161616161616,-5.54545454545455)(373.232323232323,-5.54545454545455)(358.30303030303,-5.60606060606061)(350.838383838384,-5.63636363636364)(343.373737373737,-5.66666666666667)(328.444444444444,-5.72727272727273)(313.515151515152,-5.78787878787879)(309.782828282828,-5.81818181818182)(298.585858585859,-5.95454545454546)(296.097643097643,-6)(291.121212121212,-6.18181818181818)(296.097643097643,-6.36363636363636)(298.585858585859,-6.40909090909091)(306.050505050505,-6.54545454545455)(313.515151515152,-6.63636363636364)(320.979797979798,-6.72727272727273)(328.444444444444,-6.81818181818182)(339.641414141414,-6.90909090909091)(343.373737373737,-6.93939393939394)(358.30303030303,-7.06060606060606)(365.767676767677,-7.09090909090909)(373.232323232323,-7.12121212121212)(388.161616161616,-7.18181818181818)(403.090909090909,-7.18181818181818)(418.020202020202,-7.24242424242424)(432.949494949495,-7.24242424242424)(447.878787878788,-7.24242424242424)(462.808080808081,-7.18181818181818)(477.737373737374,-7.18181818181818)(492.666666666667,-7.12121212121212)(500.131313131313,-7.09090909090909)(507.59595959596,-7.06060606060606)(522.525252525253,-7)(537.454545454546,-6.93939393939394)(544.919191919192,-6.90909090909091)(552.383838383838,-6.87878787878788)(567.313131313131,-6.81818181818182)(582.242424242424,-6.81818181818182)(597.171717171717,-6.81818181818182)(612.10101010101,-6.81818181818182)(627.030303030303,-6.81818181818182)(641.959595959596,-6.81818181818182)(656.888888888889,-6.81818181818182)(671.818181818182,-6.81818181818182)(686.747474747475,-6.87878787878788)(694.212121212121,-6.90909090909091)(701.676767676768,-6.93939393939394)(716.606060606061,-7)(731.535353535354,-7.06060606060606)(739,-7.09090909090909)(746.464646464646,-7.12121212121212)(761.393939393939,-7.18181818181818)(776.323232323232,-7.24242424242424)(783.787878787879,-7.27272727272727)(791.252525252525,-7.3030303030303)(806.181818181818,-7.36363636363636)(821.111111111111,-7.36363636363636)(836.040404040404,-7.36363636363636)(850.969696969697,-7.36363636363636)(865.89898989899,-7.36363636363636)(880.828282828283,-7.36363636363636)(895.757575757576,-7.3030303030303)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(925.616161616162,-7.18181818181818)(940.545454545455,-7.18181818181818)(955.474747474747,-7.18181818181818)(970.40404040404,-7.18181818181818)(985.333333333333,-7.12121212121212)(992.79797979798,-7.09090909090909)(1000.26262626263,-7.06060606060606)(1015.19191919192,-7)(1030.12121212121,-7)(1045.05050505051,-7)(1059.9797979798,-7)(1074.90909090909,-7)(1089.83838383838,-7)(1104.76767676768,-7)(1119.69696969697,-7)(1134.62626262626,-7)(1149.55555555556,-7)(1164.48484848485,-7)(1179.41414141414,-7)(1194.34343434343,-7)(1209.27272727273,-7)(1224.20202020202,-7)(1239.13131313131,-7)(1254.06060606061,-7)(1268.9898989899,-7.06060606060606)(1276.45454545455,-7.09090909090909)(1283.91919191919,-7.12121212121212)(1298.84848484848,-7.18181818181818)(1313.77777777778,-7.18181818181818)(1328.70707070707,-7.18181818181818)(1343.63636363636,-7.18181818181818)(1358.56565656566,-7.12121212121212)(1366.0303030303,-7.09090909090909)(1373.49494949495,-7.06060606060606)(1388.42424242424,-6.93939393939394)(1395.88888888889,-6.90909090909091)(1403.35353535354,-6.87878787878788)(1418.28282828283,-6.75757575757576)(1425.74747474747,-6.72727272727273)(1433.21212121212,-6.6969696969697)(1448.14141414141,-6.63636363636364)(1463.07070707071,-6.63636363636364)(1478,-6.63636363636364)(1478.00012440663,-6.72727272727273)(1478.00037321366,-6.90909090909091)(1478.00037321366,-7.09090909090909)(1478.00037321366,-7.27272727272727)(1478.00037321366,-7.45454545454546)(1478.00037321366,-7.63636363636364)(1478.00037321366,-7.81818181818182)(1478.00037321366,-8)(1478.00037321366,-8.18181818181818)(1478.00037321366,-8.36363636363636)(1478.00037321366,-8.54545454545455)(1478.00037321366,-8.72727272727273)(1478.00037321366,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00037321366,-9.27272727272727)(1478.00037321366,-9.45454545454546)(1478.00037321366,-9.63636363636364)(1478.00037321366,-9.81818181818182)(1478.00037321366,-10)(1478.00037321366,-10.1818181818182)(1478.00037321366,-10.3636363636364)(1478.00037321366,-10.5454545454545)(1478.00037321366,-10.7272727272727)(1478.00037321366,-10.9090909090909)(1478.00037321366,-11.0909090909091)(1478.00037321366,-11.2727272727273)(1478.00037321366,-11.4545454545455)(1478.00037321366,-11.6363636363636)(1478.00037321366,-11.8181818181818)(1478.00037321366,-12)(1478.00012440663,-12.1818181818182)(1478,-12.2727272727273)(1463.07070707071,-12.2727272727273)(1448.14141414141,-12.2727272727273)(1433.21212121212,-12.2727272727273)(1418.28282828283,-12.2727272727273)(1403.35353535354,-12.2727272727273)(1388.42424242424,-12.2727272727273)(1373.49494949495,-12.2121212121212)(1366.0303030303,-12.1818181818182)(1358.56565656566,-12.1515151515152)(1343.63636363636,-12.0909090909091)(1328.70707070707,-12.030303030303)(1324.97474747475,-12)(1313.77777777778,-11.9090909090909)(1306.31313131313,-11.8181818181818)(1298.84848484848,-11.6818181818182)(1296.36026936027,-11.6363636363636)(1286.40740740741,-11.4545454545455)(1283.91919191919,-11.3636363636364)(1281.43097643098,-11.2727272727273)(1268.9898989899,-11.1212121212121)(1265.25757575758,-11.0909090909091)(1254.06060606061,-11)(1239.13131313131,-11)(1224.20202020202,-11)(1209.27272727273,-11)(1194.34343434343,-11.0606060606061)(1186.87878787879,-11.0909090909091)(1179.41414141414,-11.1212121212121)(1164.48484848485,-11.2424242424242)(1157.0202020202,-11.2727272727273)(1149.55555555556,-11.3030303030303)(1134.62626262626,-11.4242424242424)(1127.16161616162,-11.4545454545455)(1119.69696969697,-11.4848484848485)(1104.76767676768,-11.5454545454545)(1089.83838383838,-11.4848484848485)(1082.37373737374,-11.4545454545455)(1074.90909090909,-11.4242424242424)(1059.9797979798,-11.3030303030303)(1052.51515151515,-11.2727272727273)(1045.05050505051,-11.2424242424242)(1030.12121212121,-11.1212121212121)(1026.38888888889,-11.0909090909091)(1015.19191919192,-11)(1007.72727272727,-10.9090909090909)(1000.26262626263,-10.8181818181818)(992.79797979798,-10.7272727272727)(985.333333333333,-10.6363636363636)(974.136363636364,-10.5454545454545)(970.40404040404,-10.5151515151515)(955.474747474747,-10.3939393939394)(948.010101010101,-10.3636363636364)(940.545454545455,-10.3333333333333)(925.616161616162,-10.2727272727273)(910.686868686869,-10.2727272727273)(895.757575757576,-10.2727272727273)(880.828282828283,-10.2727272727273)(865.89898989899,-10.2121212121212)(858.434343434343,-10.1818181818182)(850.969696969697,-10.1515151515152)(836.040404040404,-10.0909090909091)(821.111111111111,-10.030303030303)(813.646464646465,-10)(806.181818181818,-9.96969696969697)(791.252525252525,-9.84848484848485)(783.787878787879,-9.81818181818182)(776.323232323232,-9.78787878787879)(761.393939393939,-9.66666666666667)(753.929292929293,-9.63636363636364)(746.464646464646,-9.60606060606061)(731.535353535354,-9.48484848484848)(724.070707070707,-9.45454545454546)(716.606060606061,-9.42424242424243)(701.676767676768,-9.36363636363636)(686.747474747475,-9.36363636363636)(671.818181818182,-9.36363636363636)(656.888888888889,-9.36363636363636)(641.959595959596,-9.36363636363636)(627.030303030303,-9.36363636363636)(612.10101010101,-9.36363636363636)(597.171717171717,-9.36363636363636)(582.242424242424,-9.36363636363636)(567.313131313131,-9.36363636363636)(552.383838383838,-9.42424242424243)(544.919191919192,-9.45454545454546)(537.454545454546,-9.48484848484848)(522.525252525253,-9.60606060606061)(515.060606060606,-9.63636363636364)(507.59595959596,-9.66666666666667)(492.666666666667,-9.78787878787879)(485.20202020202,-9.81818181818182)(477.737373737374,-9.84848484848485)(462.808080808081,-9.96969696969697)(455.343434343434,-10)(447.878787878788,-10.030303030303)(432.949494949495,-10.0909090909091)(418.020202020202,-10.0909090909091)(403.090909090909,-10.0909090909091)(388.161616161616,-10.1515151515152)(380.69696969697,-10.1818181818182)(373.232323232323,-10.2121212121212)(358.30303030303,-10.2727272727273)(343.373737373737,-10.2727272727273)(328.444444444444,-10.2727272727273)(313.515151515152,-10.2727272727273)(298.585858585859,-10.2727272727273)(283.656565656566,-10.2727272727273)(268.727272727273,-10.2727272727273)(253.79797979798,-10.2727272727273)(238.868686868687,-10.3333333333333)(231.40404040404,-10.3636363636364)(223.939393939394,-10.3939393939394)(209.010101010101,-10.4545454545455)(194.080808080808,-10.4545454545455)(179.151515151515,-10.5151515151515)(171.686868686869,-10.5454545454545)(164.222222222222,-10.5757575757576)(149.292929292929,-10.6969696969697)(145.560606060606,-10.7272727272727)(134.363636363636,-10.8181818181818)(126.89898989899,-10.9090909090909)(119.434343434343,-11)(111.969696969697,-11.0909090909091)(104.505050505051,-11.1818181818182)(97.040404040404,-11.2727272727273)(89.5757575757576,-11.4090909090909)(87.0875420875421,-11.4545454545455)(82.1111111111111,-11.6363636363636)(82.1111111111111,-11.8181818181818)(82.1111111111111,-12)(82.1111111111111,-12.1818181818182)(82.1111111111111,-12.3636363636364)(87.0875420875421,-12.5454545454545)(89.5757575757576,-12.6363636363636)(92.0639730639731,-12.7272727272727)(102.016835016835,-12.9090909090909)(104.505050505051,-13)(106.993265993266,-13.0909090909091)(116.946127946128,-13.2727272727273)(119.434343434343,-13.3181818181818)(126.89898989899,-13.4545454545455)(134.363636363636,-13.5454545454545)(145.560606060606,-13.6363636363636)(149.292929292929,-13.6666666666667)(164.222222222222,-13.7878787878788)(171.686868686869,-13.8181818181818)(179.151515151515,-13.8484848484849)(194.080808080808,-13.969696969697)(201.545454545455,-14)(209.010101010101,-14.030303030303)(223.939393939394,-14.0909090909091)(238.868686868687,-14.0909090909091)(253.79797979798,-14.0909090909091)(268.727272727273,-14.0909090909091)(283.656565656566,-14.0909090909091)(298.585858585859,-14.0909090909091)(313.515151515152,-14.0909090909091)(328.444444444444,-14.0909090909091)(343.373737373737,-14.0909090909091)(358.30303030303,-14.0909090909091)(373.232323232323,-14.0909090909091)(388.161616161616,-14.0909090909091)(403.090909090909,-14.030303030303)(410.555555555556,-14)(418.020202020202,-13.969696969697)(432.949494949495,-13.9090909090909)(447.878787878788,-13.9090909090909)(462.808080808081,-13.8484848484849)(470.272727272727,-13.8181818181818)(477.737373737374,-13.7878787878788)(492.666666666667,-13.7272727272727)(507.59595959596,-13.7272727272727)(522.525252525253,-13.6666666666667)(529.989898989899,-13.6363636363636)(537.454545454546,-13.6060606060606)(552.383838383838,-13.5454545454545)(567.313131313131,-13.5454545454545)(582.242424242424,-13.4848484848485)(589.707070707071,-13.4545454545455)(597.171717171717,-13.4242424242424)(612.10101010101,-13.3636363636364)(627.030303030303,-13.3030303030303)(634.494949494949,-13.2727272727273)(641.959595959596,-13.2424242424242)(656.888888888889,-13.1818181818182)(671.818181818182,-13.1212121212121)(679.282828282828,-13.0909090909091)(686.747474747475,-13.0606060606061)(701.676767676768,-13)(716.606060606061,-12.9393939393939)(724.070707070707,-12.9090909090909)(731.535353535354,-12.8787878787879)(746.464646464646,-12.8181818181818)(761.393939393939,-12.7575757575758)(768.858585858586,-12.7272727272727)(776.323232323232,-12.6969696969697)(791.252525252525,-12.6363636363636)(806.181818181818,-12.6363636363636)(821.111111111111,-12.5757575757576)(828.575757575758,-12.5454545454545)(836.040404040404,-12.5151515151515)(850.969696969697,-12.4545454545455)(865.89898989899,-12.4545454545455)(880.828282828283,-12.4545454545455)(895.757575757576,-12.4545454545455)(910.686868686869,-12.3939393939394)(918.151515151515,-12.3636363636364)(925.616161616162,-12.3333333333333)(940.545454545455,-12.2727272727273)(955.474747474747,-12.2727272727273)(970.40404040404,-12.2727272727273)(985.333333333333,-12.2727272727273)(1000.26262626263,-12.2121212121212)(1007.72727272727,-12.1818181818182)(1015.19191919192,-12.1515151515152)(1030.12121212121,-12.0909090909091)(1045.05050505051,-12.0909090909091)(1059.9797979798,-12.030303030303)(1067.44444444444,-12)(1074.90909090909,-11.969696969697)(1089.83838383838,-11.9090909090909)(1104.76767676768,-11.9090909090909)(1119.69696969697,-11.969696969697)(1123.42929292929,-12)(1134.62626262626,-12.1363636363636)(1137.11447811448,-12.1818181818182)(1142.09090909091,-12.3636363636364)(1142.09090909091,-12.5454545454545)(1137.11447811448,-12.7272727272727)(1134.62626262626,-12.8181818181818)(1132.13804713805,-12.9090909090909)(1122.18518518519,-13.0909090909091)(1119.69696969697,-13.1818181818182)(1117.20875420875,-13.2727272727273)(1107.25589225589,-13.4545454545455)(1104.76767676768,-13.5454545454545)(1102.27946127946,-13.6363636363636)(1097.30303030303,-13.8181818181818)(1097.30303030303,-14)(1092.3265993266,-14.1818181818182)(1089.83838383838,-14.2727272727273)(1087.35016835017,-14.3636363636364)(1087.35016835017,-14.5454545454545)(1089.83838383838,-14.6363636363636)(1092.3265993266,-14.7272727272727)(1097.30303030303,-14.9090909090909)(1097.30303030303,-15.0909090909091)(1102.27946127946,-15.2727272727273)(1104.76767676768,-15.3181818181818)(1112.23232323232,-15.4545454545455)(1119.69696969697,-15.5909090909091)(1122.18518518519,-15.6363636363636)(1132.13804713805,-15.8181818181818)(1134.62626262626,-15.8636363636364)(1142.09090909091,-16)(1149.55555555556,-16.0909090909091)(1160.75252525253,-16.1818181818182)(1164.48484848485,-16.2121212121212)(1179.41414141414,-16.3333333333333)(1183.14646464646,-16.3636363636364)(1194.34343434343,-16.4545454545455)(1205.5404040404,-16.5454545454545)(1209.27272727273,-16.5757575757576)(1224.20202020202,-16.6969696969697)(1231.66666666667,-16.7272727272727)(1239.13131313131,-16.7575757575758)(1254.06060606061,-16.8181818181818)(1268.9898989899,-16.8787878787879)(1276.45454545455,-16.9090909090909)(1283.91919191919,-16.9393939393939)(1298.84848484848,-17)(1313.77777777778,-17.0606060606061)(1321.24242424242,-17.0909090909091)(1328.70707070707,-17.1212121212121)(1343.63636363636,-17.1818181818182)(1358.56565656566,-17.1818181818182)(1373.49494949495,-17.1818181818182)(1388.42424242424,-17.1818181818182)(1403.35353535354,-17.1818181818182)(1418.28282828283,-17.2424242424242)(1425.74747474747,-17.2727272727273)(1433.21212121212,-17.3030303030303)(1448.14141414141,-17.3636363636364)(1463.07070707071,-17.3636363636364)(1478,-17.3636363636364)(1478.00012440663,-17.4545454545455)(1478.00037321366,-17.6363636363636)(1478.00037321366,-17.8181818181818)(1478.00037321366,-18)(1478,-18.0000045452273)(1463.07070707071,-18.0000045452273)(1448.14141414141,-18.0000045452273)(1433.21212121212,-18.0000045452273)(1418.28282828283,-18.0000045452273)(1403.35353535354,-18.0000045452273)(1388.42424242424,-18.0000045452273)(1373.49494949495,-18.0000045452273)(1358.56565656566,-18.0000045452273)(1343.63636363636,-18.0000045452273)(1328.70707070707,-18.0000045452273)(1313.77777777778,-18.0000045452273)(1298.84848484848,-18.0000045452273)(1283.91919191919,-18.0000045452273)(1268.9898989899,-18.0000045452273)(1254.06060606061,-18.0000045452273)(1239.13131313131,-18.0000045452273)(1224.20202020202,-18.0000045452273)(1209.27272727273,-18.0000045452273)(1194.34343434343,-18.0000045452273)(1179.41414141414,-18.0000045452273)(1164.48484848485,-18.0000045452273)(1149.55555555556,-18.0000045452273)(1134.62626262626,-18.0000045452273)(1119.69696969697,-18.0000045452273)(1104.76767676768,-18.0000045452273)(1089.83838383838,-18.0000045452273)(1074.90909090909,-18.0000045452273)(1059.9797979798,-18.0000045452273)(1045.05050505051,-18.0000045452273)(1030.12121212121,-18.0000045452273)(1015.19191919192,-18.0000045452273)(1000.26262626263,-18.0000045452273)(985.333333333333,-18.0000045452273)(970.40404040404,-18.0000045452273)(955.474747474747,-18.0000045452273)(940.545454545455,-18.0000045452273)(925.616161616162,-18.0000045452273)(910.686868686869,-18.0000045452273)(895.757575757576,-18.0000045452273)(880.828282828283,-18.0000045452273)(865.89898989899,-18.0000045452273)(850.969696969697,-18.0000045452273)(836.040404040404,-18.0000045452273)(821.111111111111,-18.0000045452273)(806.181818181818,-18.0000045452273)(791.252525252525,-18.0000045452273)(776.323232323232,-18.0000045452273)(761.393939393939,-18.0000045452273)(746.464646464646,-18.0000045452273)(731.535353535354,-18.0000045452273)(716.606060606061,-18.0000045452273)(701.676767676768,-18.0000045452273)(686.747474747475,-18.0000045452273)(671.818181818182,-18.0000045452273)(656.888888888889,-18.0000045452273)(641.959595959596,-18.0000045452273)(627.030303030303,-18.0000045452273)(612.10101010101,-18.0000045452273)(597.171717171717,-18.0000045452273)(582.242424242424,-18.0000045452273)(567.313131313131,-18.0000045452273)(552.383838383838,-18.0000045452273)(537.454545454546,-18.0000045452273)(522.525252525253,-18.0000045452273)(507.59595959596,-18.0000045452273)(492.666666666667,-18.0000045452273)(477.737373737374,-18.0000045452273)(462.808080808081,-18.0000045452273)(447.878787878788,-18.0000045452273)(432.949494949495,-18.0000045452273)(418.020202020202,-18.000001515101)(410.555555555556,-18)(410.555555555556,-17.8181818181818)(410.555555555556,-17.6363636363636)(405.579124579125,-17.4545454545455)(403.090909090909,-17.3636363636364)(400.602693602694,-17.2727272727273)(390.649831649832,-17.0909090909091)(388.161616161616,-17)(385.673400673401,-16.9090909090909)(375.720538720539,-16.7272727272727)(373.232323232323,-16.6818181818182)(365.767676767677,-16.5454545454545)(358.30303030303,-16.4545454545455)(350.838383838384,-16.3636363636364)(343.373737373737,-16.2727272727273)(335.909090909091,-16.1818181818182)(328.444444444444,-16.0909090909091)(320.979797979798,-16)(313.515151515152,-15.9090909090909)(306.050505050505,-15.8181818181818)(298.585858585859,-15.7272727272727)(291.121212121212,-15.6363636363636)(283.656565656566,-15.5454545454545)(272.459595959596,-15.4545454545455)(268.727272727273,-15.4242424242424)(253.79797979798,-15.3030303030303)(246.333333333333,-15.2727272727273)(238.868686868687,-15.2424242424242)(223.939393939394,-15.1212121212121)(216.474747474747,-15.0909090909091)(209.010101010101,-15.0606060606061)(194.080808080808,-15)(179.151515151515,-15)(164.222222222222,-15)(149.292929292929,-15)(134.363636363636,-15)(119.434343434343,-15)(104.505050505051,-15)(89.5757575757576,-15)(74.6464646464647,-15)(59.7171717171717,-15)(44.7878787878788,-15)(29.8585858585859,-15)(14.9292929292929,-15)(0,-15)(-0.000124406627521346,-14.9090909090909)(-0.000373213662548569,-14.7272727272727)(-0.000373213662548569,-14.5454545454545)(-0.000373213662548569,-14.3636363636364)(-0.000373213662548569,-14.1818181818182)(-0.000373213662548569,-14)(-0.000373213662548569,-13.8181818181818)(-0.000373213662548569,-13.6363636363636)(-0.000373213662548569,-13.4545454545455)(-0.000373213662548569,-13.2727272727273)(-0.000373213662548569,-13.0909090909091)(-0.000373213662548569,-12.9090909090909)(-0.000373213662548569,-12.7272727272727)(-0.000373213662548569,-12.5454545454545)(-0.000373213662548569,-12.3636363636364)(-0.000373213662548569,-12.1818181818182)(-0.000373213662548569,-12)(-0.000373213662548569,-11.8181818181818)(-0.000373213662548569,-11.6363636363636)(-0.000373213662548569,-11.4545454545455)(-0.000373213662548569,-11.2727272727273)(-0.000373213662548569,-11.0909090909091)(-0.000373213662548569,-10.9090909090909)(-0.000373213662548569,-10.7272727272727)(-0.000373213662548569,-10.5454545454545)(-0.000373213662548569,-10.3636363636364)(-0.000373213662548569,-10.1818181818182)(-0.000373213662548569,-10)(-0.000373213662548569,-9.81818181818182)(-0.000124406627521346,-9.63636363636364)(0,-9.54545454545455)(14.9292929292929,-9.54545454545455)(29.8585858585859,-9.54545454545455)(44.7878787878788,-9.48484848484848)(48.520202020202,-9.45454545454546)(59.7171717171717,-9.36363636363636)(67.1818181818182,-9.27272727272727)(74.6464646464647,-9.13636363636364)(77.1346801346801,-9.09090909090909)(87.0875420875421,-8.90909090909091)(87.0875420875421,-8.72727272727273)(87.0875420875421,-8.54545454545455)(74.6464646464647,-8.39393939393939)(72.1582491582492,-8.36363636363636)(59.7171717171717,-8.21212121212121)(52.2525252525253,-8.18181818181818)(44.7878787878788,-8.15151515151515)(29.8585858585859,-8.03030303030303)(22.3939393939394,-8)(14.9292929292929,-7.96969696969697)(0,-7.90909090909091)(-0.000124406627521346,-7.81818181818182)(-0.000373213662548569,-7.63636363636364)(-0.000373213662548569,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000124406627521346,-7.09090909090909)(0,-7)(14.9292929292929,-6.93939393939394)(22.3939393939394,-6.90909090909091)(29.8585858585859,-6.87878787878788)(44.7878787878788,-6.81818181818182)(59.7171717171717,-6.75757575757576)(67.1818181818182,-6.72727272727273)(74.6464646464647,-6.6969696969697)(89.5757575757576,-6.63636363636364)(104.505050505051,-6.57575757575758)(111.969696969697,-6.54545454545455)(119.434343434343,-6.51515151515151)(134.363636363636,-6.45454545454545)(149.292929292929,-6.39393939393939)(156.757575757576,-6.36363636363636)(164.222222222222,-6.33333333333333)(179.151515151515,-6.21212121212121)(186.616161616162,-6.18181818181818)(194.080808080808,-6.15151515151515)(206.521885521886,-6)(209.010101010101,-5.95454545454546)(216.474747474747,-5.81818181818182)(216.474747474747,-5.63636363636364)(211.498316498317,-5.45454545454546)(209.010101010101,-5.40909090909091)(201.545454545455,-5.27272727272727)(194.080808080808,-5.18181818181818)(186.616161616162,-5.09090909090909)(179.151515151515,-5)(167.954545454545,-4.90909090909091)(164.222222222222,-4.87878787878788)(149.292929292929,-4.75757575757576)(141.828282828283,-4.72727272727273)(134.363636363636,-4.6969696969697)(119.434343434343,-4.57575757575758)(111.969696969697,-4.54545454545455)(104.505050505051,-4.51515151515151)(89.5757575757576,-4.45454545454545)(74.6464646464647,-4.39393939393939)(67.1818181818182,-4.36363636363636)(59.7171717171717,-4.33333333333333)(44.7878787878788,-4.27272727272727)(29.8585858585859,-4.27272727272727)(14.9292929292929,-4.27272727272727)(0,-4.27272727272727)(-0.000124406627521346,-4.18181818181818)(-0.000373213662548569,-4)(-0.000373213662548569,-3.81818181818182)(-0.000373213662548569,-3.63636363636364)(-0.000373213662548569,-3.45454545454546)(-0.000373213662548569,-3.27272727272727)(-0.000373213662548569,-3.09090909090909)(-0.000373213662548569,-2.90909090909091)(-0.000373213662548569,-2.72727272727273)(-0.000124406627521346,-2.54545454545455)(0,-2.45454545454545)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1298.84848484848,-8.68181818181818)(1301.3367003367,-8.72727272727273)(1306.31313131313,-8.90909090909091)(1301.3367003367,-9.09090909090909)(1298.84848484848,-9.13636363636364)(1291.38383838384,-9.27272727272727)(1283.91919191919,-9.36363636363636)(1272.72222222222,-9.45454545454546)(1268.9898989899,-9.48484848484848)(1254.06060606061,-9.54545454545455)(1239.13131313131,-9.60606060606061)(1231.66666666667,-9.63636363636364)(1224.20202020202,-9.66666666666667)(1209.27272727273,-9.72727272727273)(1194.34343434343,-9.72727272727273)(1179.41414141414,-9.72727272727273)(1164.48484848485,-9.72727272727273)(1149.55555555556,-9.72727272727273)(1134.62626262626,-9.66666666666667)(1127.16161616162,-9.63636363636364)(1119.69696969697,-9.60606060606061)(1104.76767676768,-9.54545454545455)(1089.83838383838,-9.54545454545455)(1074.90909090909,-9.48484848484848)(1067.44444444444,-9.45454545454546)(1059.9797979798,-9.42424242424243)(1045.05050505051,-9.3030303030303)(1037.58585858586,-9.27272727272727)(1030.12121212121,-9.24242424242424)(1017.68013468013,-9.09090909090909)(1015.19191919192,-9.06060606060606)(1002.75084175084,-8.90909090909091)(1002.75084175084,-8.72727272727273)(1011.4595959596,-8.54545454545455)(1015.19191919192,-8.51515151515152)(1030.12121212121,-8.39393939393939)(1037.58585858586,-8.36363636363636)(1045.05050505051,-8.33333333333333)(1059.9797979798,-8.27272727272727)(1074.90909090909,-8.21212121212121)(1082.37373737374,-8.18181818181818)(1089.83838383838,-8.15151515151515)(1104.76767676768,-8.09090909090909)(1119.69696969697,-8.09090909090909)(1134.62626262626,-8.09090909090909)(1149.55555555556,-8.09090909090909)(1164.48484848485,-8.09090909090909)(1179.41414141414,-8.09090909090909)(1194.34343434343,-8.09090909090909)(1209.27272727273,-8.15151515151515)(1216.73737373737,-8.18181818181818)(1224.20202020202,-8.21212121212121)(1239.13131313131,-8.27272727272727)(1254.06060606061,-8.33333333333333)(1261.52525252525,-8.36363636363636)(1268.9898989899,-8.39393939393939)(1283.91919191919,-8.51515151515152)(1287.65151515152,-8.54545454545455)(1298.84848484848,-8.68181818181818)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_200.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.00008294006,-8.72727272727273)(1478.00033175469,-8.90909090909091)(1478.00058056104,-9.09090909090909)(1478.00066349464,-9.27272727272727)(1478.00058056104,-9.45454545454546)(1478.00058056104,-9.63636363636364)(1478.00049762651,-9.81818181818182)(1478.00033175469,-10)(1478.00008294006,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.93939393939394)(1478.00020734323,-9.09090909090909)(1478.00029027891,-9.27272727272727)(1478.00020734323,-9.45454545454546)(1478.00020734323,-9.63636363636364)(1478.00012440663,-9.81818181818182)(1478,-9.95454545454546)(1463.07070707071,-9.96969696969697)(1459.33838383838,-10)(1448.14141414141,-10.0909090909091)(1433.21212121212,-10.0909090909091)(1418.28282828283,-10.1136363636364)(1403.35353535354,-10.1590909090909)(1399.62121212121,-10.1818181818182)(1388.42424242424,-10.2727272727273)(1373.49494949495,-10.3454545454545)(1358.56565656566,-10.3454545454545)(1343.63636363636,-10.3409090909091)(1328.70707070707,-10.2727272727273)(1313.77777777778,-10.2727272727273)(1298.84848484848,-10.2954545454545)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2045454545455)(1261.52525252525,-10.1818181818182)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1666666666667)(1209.27272727273,-10.1666666666667)(1205.5404040404,-10.1818181818182)(1194.34343434343,-10.25)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.2121212121212)(1149.55555555556,-10.2121212121212)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.2121212121212)(1104.76767676768,-10.2045454545455)(1089.83838383838,-10.2)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1056.24747474747,-10.3636363636364)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2727272727273)(1000.26262626263,-10.2045454545455)(985.333333333333,-10.2121212121212)(970.40404040404,-10.2727272727273)(955.474747474748,-10.25)(944.277777777778,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0545454545455)(895.757575757576,-10.0909090909091)(880.828282828283,-10.030303030303)(873.363636363636,-10)(865.89898989899,-9.98484848484848)(850.969696969697,-9.84090909090909)(843.505050505051,-9.81818181818182)(836.040404040404,-9.78787878787879)(826.709595959596,-9.63636363636364)(821.111111111111,-9.54545454545455)(806.181818181818,-9.5)(798.717171717172,-9.45454545454546)(791.252525252525,-9.43181818181818)(776.323232323232,-9.36363636363636)(770.724747474747,-9.27272727272727)(768.858585858586,-9.09090909090909)(766.992424242424,-8.90909090909091)(765.126262626263,-8.72727272727273)(763.260101010101,-8.54545454545455)(763.882154882155,-8.36363636363636)(773.835016835017,-8.18181818181818)(776.323232323232,-8.15151515151515)(791.252525252525,-8.01818181818182)(794.984848484849,-8)(806.181818181818,-7.94545454545455)(821.111111111111,-7.86363636363636)(825.589898989899,-7.81818181818182)(833.552188552189,-7.63636363636364)(836.040404040404,-7.61363636363636)(850.969696969697,-7.52272727272727)(858.434343434343,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.37878787878788)(895.757575757576,-7.28787878787879)(910.686868686869,-7.28787878787879)(914.419191919192,-7.27272727272727)(925.616161616162,-7.20454545454546)(940.545454545455,-7.15909090909091)(955.474747474747,-7.10606060606061)(970.40404040404,-7.10606060606061)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1007.72727272727,-7.09090909090909)(1015.19191919192,-7.06818181818182)(1022.65656565657,-7.09090909090909)(1030.12121212121,-7.10606060606061)(1045.05050505051,-7.13636363636364)(1059.9797979798,-7.13636363636364)(1074.90909090909,-7.20454545454546)(1089.83838383838,-7.25)(1092.3265993266,-7.27272727272727)(1104.76767676768,-7.42424242424243)(1112.23232323232,-7.45454545454546)(1119.69696969697,-7.46969696969697)(1134.62626262626,-7.56060606060606)(1149.55555555556,-7.58181818181818)(1164.48484848485,-7.61363636363636)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.65151515151515)(1194.34343434343,-7.65151515151515)(1209.27272727273,-7.68181818181818)(1224.20202020202,-7.65151515151515)(1239.13131313131,-7.65454545454546)(1246.59595959596,-7.63636363636364)(1254.06060606061,-7.61818181818182)(1261.52525252525,-7.63636363636364)(1268.9898989899,-7.66666666666667)(1283.91919191919,-7.72727272727273)(1298.84848484848,-7.70454545454546)(1313.77777777778,-7.72727272727273)(1328.70707070707,-7.72727272727273)(1339.90404040404,-7.81818181818182)(1343.63636363636,-7.84848484848485)(1358.56565656566,-7.84848484848485)(1371.00673400673,-8)(1373.49494949495,-8.09090909090909)(1380.9595959596,-8.18181818181818)(1388.42424242424,-8.27272727272727)(1395.88888888889,-8.36363636363636)(1403.35353535354,-8.39393939393939)(1418.28282828283,-8.47727272727273)(1433.21212121212,-8.52272727272727)(1435.70033670034,-8.54545454545455)(1448.14141414141,-8.65909090909091)(1455.60606060606,-8.72727272727273)(1463.07070707071,-8.86363636363636)(1470.53535353535,-8.90909090909091)(1478,-8.93939393939394)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.43181818181818)(1434.70505050505,-9.45454545454546)(1433.21212121212,-9.54545454545455)(1429.4797979798,-9.63636363636364)(1418.28282828283,-9.70454545454546)(1403.35353535354,-9.72727272727273)(1390.91245791246,-9.81818181818182)(1388.42424242424,-9.84848484848485)(1379.09343434343,-10)(1373.49494949495,-10.0454545454545)(1358.56565656566,-10.0454545454545)(1343.63636363636,-10.0151515151515)(1339.90404040404,-10)(1328.70707070707,-9.90909090909091)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.96969696969697)(1283.91919191919,-9.97727272727273)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.89393939393939)(1239.13131313131,-9.83333333333333)(1224.20202020202,-9.89393939393939)(1209.27272727273,-9.87272727272727)(1194.34343434343,-9.93181818181818)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.88636363636364)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.88636363636364)(1104.76767676768,-9.90909090909091)(1089.83838383838,-9.92424242424243)(1077.39730639731,-10)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1017.68013468013,-10)(1015.19191919192,-9.97727272727273)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.88636363636364)(970.40404040404,-9.90909090909091)(955.474747474748,-9.93181818181818)(940.545454545455,-9.87272727272727)(925.616161616162,-9.83333333333333)(921.883838383838,-9.81818181818182)(910.686868686869,-9.76363636363636)(895.757575757576,-9.79545454545455)(880.828282828283,-9.70454545454546)(865.89898989899,-9.69090909090909)(861.420202020202,-9.63636363636364)(850.969696969697,-9.50909090909091)(845.371212121212,-9.45454545454546)(836.040404040404,-9.3030303030303)(834.174242424242,-9.27272727272727)(821.111111111111,-9.11363636363636)(818.622895622896,-9.09090909090909)(806.181818181818,-8.97727272727273)(801.70303030303,-8.90909090909091)(804.688888888889,-8.72727272727273)(796.85101010101,-8.54545454545455)(798.717171717172,-8.36363636363636)(806.181818181818,-8.29545454545455)(821.111111111111,-8.2)(824.843434343434,-8.18181818181818)(836.040404040404,-8.04545454545455)(839.772727272727,-8)(850.969696969697,-7.90909090909091)(856.568181818182,-7.81818181818182)(865.89898989899,-7.72727272727273)(880.828282828283,-7.69090909090909)(888.292929292929,-7.63636363636364)(895.757575757576,-7.58181818181818)(910.686868686869,-7.61363636363636)(925.616161616162,-7.52272727272727)(940.545454545455,-7.48484848484849)(943.03367003367,-7.45454545454546)(955.474747474747,-7.37878787878788)(970.40404040404,-7.37878787878788)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1015.19191919192,-7.36363636363636)(1030.12121212121,-7.4)(1045.05050505051,-7.43636363636364)(1059.9797979798,-7.40909090909091)(1065.57828282828,-7.45454545454546)(1074.90909090909,-7.56818181818182)(1089.83838383838,-7.61818181818182)(1092.3265993266,-7.63636363636364)(1104.76767676768,-7.75)(1119.69696969697,-7.79545454545455)(1127.16161616162,-7.81818181818182)(1134.62626262626,-7.83636363636364)(1149.55555555556,-7.87272727272727)(1164.48484848485,-7.90909090909091)(1179.41414141414,-7.94545454545455)(1194.34343434343,-7.92424242424242)(1209.27272727273,-7.95454545454546)(1224.20202020202,-7.92424242424242)(1239.13131313131,-7.95454545454546)(1254.06060606061,-7.95454545454546)(1265.25757575758,-8)(1268.9898989899,-8.04545454545455)(1283.91919191919,-8.09090909090909)(1298.84848484848,-8.09090909090909)(1310.04545454545,-8.18181818181818)(1313.77777777778,-8.21212121212121)(1328.70707070707,-8.27272727272727)(1339.90404040404,-8.36363636363636)(1343.63636363636,-8.39393939393939)(1356.07744107744,-8.54545454545455)(1358.56565656566,-8.56818181818182)(1373.49494949495,-8.67272727272727)(1379.09343434343,-8.72727272727273)(1388.42424242424,-8.84090909090909)(1399.62121212121,-8.90909090909091)(1403.35353535354,-8.95454545454546)(1418.28282828283,-9.04545454545455)(1420.14898989899,-9.09090909090909)(1422.76161616162,-9.27272727272727)(1433.21212121212,-9.43181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-7.77272727272727)(85.8434343434344,-7.63636363636364)(89.5757575757576,-7.60606060606061)(104.505050505051,-7.48484848484849)(111.969696969697,-7.45454545454546)(119.434343434343,-7.42424242424243)(134.363636363636,-7.36363636363636)(149.292929292929,-7.36363636363636)(164.222222222222,-7.40909090909091)(179.151515151515,-7.40909090909091)(194.080808080808,-7.40909090909091)(209.010101010101,-7.36363636363636)(223.939393939394,-7.42424242424243)(231.40404040404,-7.45454545454546)(238.868686868687,-7.48484848484849)(253.79797979798,-7.54545454545455)(268.727272727273,-7.54545454545455)(283.656565656566,-7.54545454545455)(298.585858585859,-7.54545454545455)(313.515151515152,-7.60606060606061)(317.247474747475,-7.63636363636364)(328.444444444444,-7.77272727272727)(335.909090909091,-7.81818181818182)(343.373737373737,-7.84848484848485)(358.30303030303,-7.86363636363636)(360.791245791246,-7.81818181818182)(373.232323232323,-7.66666666666667)(388.161616161616,-7.65909090909091)(403.090909090909,-7.65909090909091)(406.823232323232,-7.63636363636364)(414.287878787879,-7.45454545454546)(418.020202020202,-7.43181818181818)(432.949494949495,-7.36363636363636)(447.878787878788,-7.32727272727273)(459.075757575758,-7.27272727272727)(462.808080808081,-7.24242424242424)(477.737373737374,-7.18181818181818)(492.666666666667,-7.15909090909091)(507.59595959596,-7.24242424242424)(515.060606060606,-7.27272727272727)(522.525252525253,-7.28787878787879)(537.454545454546,-7.28787878787879)(541.186868686869,-7.27272727272727)(552.383838383838,-7.21818181818182)(567.313131313131,-7.20454545454546)(582.242424242424,-7.15909090909091)(597.171717171717,-7.22727272727273)(612.10101010101,-7.24242424242424)(615.833333333333,-7.27272727272727)(627.030303030303,-7.36363636363636)(638.227272727273,-7.45454545454546)(641.959595959596,-7.5)(656.888888888889,-7.59090909090909)(660.621212121212,-7.63636363636364)(671.818181818182,-7.77272727272727)(674.306397306397,-7.81818181818182)(684.259259259259,-8)(686.747474747475,-8.09090909090909)(689.23569023569,-8.18181818181818)(689.23569023569,-8.36363636363636)(686.747474747475,-8.40909090909091)(679.282828282828,-8.54545454545455)(671.818181818182,-8.63636363636364)(660.621212121212,-8.72727272727273)(656.888888888889,-8.75757575757576)(641.959595959596,-8.77272727272727)(627.030303030303,-8.77272727272727)(612.10101010101,-8.81818181818182)(604.636363636364,-8.90909090909091)(597.171717171717,-8.93939393939394)(582.242424242424,-9.02272727272727)(567.313131313131,-9.07272727272727)(563.580808080808,-9.09090909090909)(552.383838383838,-9.15909090909091)(537.454545454546,-9.18181818181818)(522.525252525253,-9.20454545454546)(507.59595959596,-9.21818181818182)(492.666666666667,-9.25757575757576)(477.737373737374,-9.25757575757576)(462.808080808081,-9.21818181818182)(447.878787878788,-9.11363636363636)(445.390572390572,-9.09090909090909)(432.949494949495,-8.93939393939394)(429.217171717172,-8.90909090909091)(418.020202020202,-8.84090909090909)(403.090909090909,-8.81818181818182)(388.161616161616,-8.77272727272727)(380.69696969697,-8.72727272727273)(373.232323232323,-8.68181818181818)(365.767676767677,-8.72727272727273)(358.30303030303,-8.75757575757576)(343.373737373737,-8.75757575757576)(328.444444444444,-8.81818181818182)(313.515151515152,-8.84090909090909)(298.585858585859,-8.88636363636364)(283.656565656566,-8.89090909090909)(281.16835016835,-8.90909090909091)(268.727272727273,-9.06060606060606)(264.99494949495,-9.09090909090909)(253.79797979798,-9.18181818181818)(242.60101010101,-9.27272727272727)(238.868686868687,-9.3030303030303)(223.939393939394,-9.42424242424243)(216.474747474747,-9.45454545454546)(209.010101010101,-9.48484848484848)(194.080808080808,-9.54545454545455)(179.151515151515,-9.54545454545455)(164.222222222222,-9.54545454545455)(149.292929292929,-9.54545454545455)(138.09595959596,-9.45454545454546)(134.363636363636,-9.40909090909091)(126.89898989899,-9.27272727272727)(121.922558922559,-9.09090909090909)(121.922558922559,-8.90909090909091)(119.434343434343,-8.86363636363636)(111.969696969697,-8.72727272727273)(111.969696969697,-8.54545454545455)(106.993265993266,-8.36363636363636)(104.505050505051,-8.31818181818182)(89.5757575757576,-8.27272727272727)(82.1111111111111,-8.18181818181818)(74.6464646464647,-8.04545454545455)(72.1582491582492,-8)(72.1582491582492,-7.81818181818182)(74.6464646464647,-7.77272727272727)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.72727272727273)(459.075757575758,-7.63636363636364)(462.808080808081,-7.61363636363636)(477.737373737374,-7.60606060606061)(492.666666666667,-7.48484848484849)(507.59595959596,-7.56818181818182)(522.525252525253,-7.58181818181818)(537.454545454546,-7.56060606060606)(552.383838383838,-7.50909090909091)(567.313131313131,-7.52272727272727)(582.242424242424,-7.54545454545455)(589.707070707071,-7.63636363636364)(597.171717171717,-7.70454545454546)(606.502525252525,-7.81818181818182)(612.10101010101,-7.95454545454546)(615.833333333333,-8)(615.833333333333,-8.18181818181818)(612.10101010101,-8.20454545454546)(599.037878787879,-8.36363636363636)(597.171717171717,-8.39393939393939)(584.73063973064,-8.54545454545455)(582.242424242424,-8.57575757575757)(569.801346801347,-8.72727272727273)(567.313131313131,-8.74545454545454)(552.383838383838,-8.79545454545455)(537.454545454546,-8.81818181818182)(522.525252525253,-8.87878787878788)(515.060606060606,-8.90909090909091)(507.59595959596,-8.92424242424242)(492.666666666667,-8.96363636363636)(477.737373737374,-8.93181818181818)(474.005050505051,-8.90909090909091)(462.808080808081,-8.77272727272727)(460.319865319865,-8.72727272727273)(455.343434343434,-8.54545454545455)(447.878787878788,-8.40909090909091)(444.146464646465,-8.36363636363636)(440.414141414141,-8.18181818181818)(442.280303030303,-8)(440.414141414141,-7.81818181818182)(447.878787878788,-7.72727272727273)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (477.737373737374,-14.6818181818182)(488.934343434343,-14.5454545454545)(492.666666666667,-14.5151515151515)(507.59595959596,-14.3939393939394)(515.060606060606,-14.3636363636364)(522.525252525253,-14.3333333333333)(537.454545454546,-14.2727272727273)(552.383838383838,-14.2727272727273)(567.313131313131,-14.2727272727273)(582.242424242424,-14.2727272727273)(597.171717171717,-14.2727272727273)(612.10101010101,-14.2727272727273)(627.030303030303,-14.2727272727273)(641.959595959596,-14.2727272727273)(656.888888888889,-14.2727272727273)(671.818181818182,-14.2727272727273)(686.747474747475,-14.3181818181818)(690.479797979798,-14.3636363636364)(690.479797979798,-14.5454545454545)(686.747474747475,-14.5757575757576)(671.818181818182,-14.6969696969697)(664.353535353535,-14.7272727272727)(656.888888888889,-14.7575757575758)(641.959595959596,-14.8787878787879)(634.494949494949,-14.9090909090909)(627.030303030303,-14.9393939393939)(612.10101010101,-15.0606060606061)(604.636363636364,-15.0909090909091)(597.171717171717,-15.1212121212121)(582.242424242424,-15.1818181818182)(567.313131313131,-15.2424242424242)(559.848484848485,-15.2727272727273)(552.383838383838,-15.3030303030303)(537.454545454546,-15.3636363636364)(522.525252525253,-15.3636363636364)(507.59595959596,-15.3636363636364)(492.666666666667,-15.3030303030303)(488.934343434343,-15.2727272727273)(477.737373737374,-15.1363636363636)(475.249158249158,-15.0909090909091)(470.272727272727,-14.9090909090909)(475.249158249158,-14.7272727272727)(477.737373737374,-14.6818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (164.222222222222,-8.33333333333333)(176.6632996633,-8.18181818181818)(179.151515151515,-8.15909090909091)(194.080808080808,-8.12727272727273)(209.010101010101,-8.12727272727273)(223.939393939394,-8.15909090909091)(231.40404040404,-8.18181818181818)(229.537878787879,-8.36363636363636)(227.671717171717,-8.54545454545455)(223.939393939394,-8.57575757575757)(211.498316498317,-8.72727272727273)(209.010101010101,-8.75757575757576)(201.545454545455,-8.72727272727273)(194.080808080808,-8.68181818181818)(179.151515151515,-8.65909090909091)(166.710437710438,-8.54545454545455)(164.222222222222,-8.45454545454545)(160.489898989899,-8.36363636363636)(164.222222222222,-8.33333333333333)};

\addplot [fill=white,draw=none,forget plot] coordinates{ (388.161616161616,-8.31818181818182)(380.69696969697,-8.36363636363636)(388.161616161616,-8.40909090909091)(391.893939393939,-8.36363636363636)(388.161616161616,-8.31818181818182)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091)(119.434343434343,-8.36363636363636)(791.252525252525,-8.72727272727273)(627.030303030303,-7.63636363636364)(1224.20202020202,-7.81818181818182)(791.252525252525,-9.09090909090909)(1089.83838383838,-10.1818181818182)(806.181818181818,-8.18181818181818)(641.959595959596,-8)(821.111111111111,-8)(940.545454545455,-7.27272727272727)(1030.12121212121,-7.27272727272727)(403.090909090909,-8.36363636363636)(1418.28282828283,-10)(283.656565656566,-8.18181818181818)(268.727272727273,-8)(477.737373737374,-7.45454545454546)(1224.20202020202,-10)(1209.27272727273,-10)(1283.91919191919,-10)(134.363636363636,-8.54545454545455)(134.363636363636,-8.72727272727273)(791.252525252525,-8.36363636363636)(447.878787878788,-8.72727272727273)(955.474747474747,-7.27272727272727)(522.525252525253,-7.27272727272727)(268.727272727273,-8.72727272727273)(776.323232323232,-8.72727272727273)(627.030303030303,-8.54545454545455)(1209.27272727273,-7.81818181818182)(1448.14141414141,-9.81818181818182)(880.828282828283,-9.81818181818182)(253.79797979798,-8.72727272727273)(895.757575757576,-7.45454545454546)(149.292929292929,-8)(462.808080808081,-8.90909090909091)(298.585858585859,-8.36363636363636)(403.090909090909,-8)(388.161616161616,-8.18181818181818)(1074.90909090909,-10.1818181818182)(432.949494949495,-8.72727272727273) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_220.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.00008294006,-8.72727272727273)(1478.00033175469,-8.90909090909091)(1478.00066349464,-9.09090909090909)(1478.00058056104,-9.27272727272727)(1478.00049762651,-9.45454545454546)(1478.00041469106,-9.63636363636364)(1478.00041469106,-9.81818181818182)(1478.0002488174,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.93181818181818)(1478.00029027891,-9.09090909090909)(1478.00020734323,-9.27272727272727)(1478.00012440663,-9.45454545454546)(1478.00004146911,-9.63636363636364)(1478.00004146911,-9.81818181818182)(1478,-9.86363636363636)(1463.07070707071,-9.90909090909091)(1451.87373737374,-10)(1448.14141414141,-10.030303030303)(1433.21212121212,-10.0909090909091)(1418.28282828283,-10.1272727272727)(1407.08585858586,-10.1818181818182)(1403.35353535354,-10.2272727272727)(1388.42424242424,-10.2954545454545)(1373.49494949495,-10.3484848484848)(1358.56565656566,-10.3090909090909)(1343.63636363636,-10.2954545454545)(1328.70707070707,-10.2121212121212)(1313.77777777778,-10.2727272727273)(1298.84848484848,-10.2954545454545)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2045454545455)(1261.52525252525,-10.1818181818182)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1666666666667)(1216.73737373737,-10.1818181818182)(1209.27272727273,-10.2045454545455)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2954545454545)(1164.48484848485,-10.2121212121212)(1149.55555555556,-10.2121212121212)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.2121212121212)(1104.76767676768,-10.2045454545455)(1089.83838383838,-10.2)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1056.24747474747,-10.3636363636364)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2727272727273)(1000.26262626263,-10.2045454545455)(985.333333333333,-10.2121212121212)(970.40404040404,-10.2727272727273)(955.474747474748,-10.25)(944.277777777778,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0545454545455)(895.757575757576,-10.0909090909091)(880.828282828283,-10.030303030303)(873.363636363636,-10)(865.89898989899,-9.98484848484848)(850.969696969697,-9.84090909090909)(843.505050505051,-9.81818181818182)(836.040404040404,-9.78787878787879)(826.709595959596,-9.63636363636364)(821.111111111111,-9.54545454545455)(806.181818181818,-9.5)(798.717171717172,-9.45454545454546)(791.252525252525,-9.43181818181818)(776.323232323232,-9.36363636363636)(770.724747474747,-9.27272727272727)(768.858585858586,-9.09090909090909)(766.992424242424,-8.90909090909091)(765.126262626263,-8.72727272727273)(763.260101010101,-8.54545454545455)(768.858585858586,-8.36363636363636)(776.323232323232,-8.22727272727273)(778.189393939394,-8.18181818181818)(791.252525252525,-8.05454545454545)(802.449494949495,-8)(806.181818181818,-7.98181818181818)(821.111111111111,-7.92424242424242)(831.561616161616,-7.81818181818182)(836.040404040404,-7.72727272727273)(843.505050505051,-7.63636363636364)(850.969696969697,-7.54545454545455)(858.434343434343,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.37878787878788)(895.757575757576,-7.28787878787879)(910.686868686869,-7.28787878787879)(914.419191919192,-7.27272727272727)(925.616161616162,-7.20454545454546)(940.545454545455,-7.15909090909091)(955.474747474747,-7.10606060606061)(970.40404040404,-7.10606060606061)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1007.72727272727,-7.09090909090909)(1015.19191919192,-7.06818181818182)(1022.65656565657,-7.09090909090909)(1030.12121212121,-7.10606060606061)(1045.05050505051,-7.13636363636364)(1059.9797979798,-7.13636363636364)(1074.90909090909,-7.20454545454546)(1089.83838383838,-7.25)(1092.3265993266,-7.27272727272727)(1104.76767676768,-7.42424242424243)(1112.23232323232,-7.45454545454546)(1119.69696969697,-7.46969696969697)(1134.62626262626,-7.56060606060606)(1149.55555555556,-7.58181818181818)(1164.48484848485,-7.61363636363636)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.65151515151515)(1194.34343434343,-7.65151515151515)(1209.27272727273,-7.68181818181818)(1224.20202020202,-7.65151515151515)(1239.13131313131,-7.65151515151515)(1242.86363636364,-7.63636363636364)(1254.06060606061,-7.59090909090909)(1268.9898989899,-7.59090909090909)(1283.91919191919,-7.61818181818182)(1291.38383838384,-7.63636363636364)(1298.84848484848,-7.65909090909091)(1313.77777777778,-7.72727272727273)(1328.70707070707,-7.70454545454546)(1343.63636363636,-7.78787878787879)(1358.56565656566,-7.79545454545455)(1361.05387205387,-7.81818181818182)(1371.62878787879,-8)(1373.49494949495,-8.09090909090909)(1380.9595959596,-8.18181818181818)(1388.42424242424,-8.27272727272727)(1395.88888888889,-8.36363636363636)(1403.35353535354,-8.39393939393939)(1418.28282828283,-8.47727272727273)(1433.21212121212,-8.52272727272727)(1435.70033670034,-8.54545454545455)(1448.14141414141,-8.65909090909091)(1455.60606060606,-8.72727272727273)(1463.07070707071,-8.86363636363636)(1470.53535353535,-8.90909090909091)(1478,-8.93181818181818)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.38636363636364)(1438.81060606061,-9.45454545454546)(1435.07828282828,-9.63636363636364)(1433.21212121212,-9.66666666666667)(1418.28282828283,-9.76363636363636)(1403.35353535354,-9.79545454545455)(1400.86531986532,-9.81818181818182)(1388.42424242424,-9.96969696969697)(1385.93602693603,-10)(1373.49494949495,-10.0757575757576)(1358.56565656566,-10.0151515151515)(1351.10101010101,-10)(1343.63636363636,-9.96969696969697)(1328.70707070707,-9.88636363636364)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.96969696969697)(1283.91919191919,-9.97727272727273)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.89393939393939)(1239.13131313131,-9.83333333333333)(1224.20202020202,-9.89393939393939)(1209.27272727273,-9.90909090909091)(1194.34343434343,-9.97727272727273)(1179.41414141414,-9.96969696969697)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.88636363636364)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.88636363636364)(1104.76767676768,-9.90909090909091)(1089.83838383838,-9.92424242424243)(1077.39730639731,-10)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1017.68013468013,-10)(1015.19191919192,-9.97727272727273)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.88636363636364)(970.40404040404,-9.90909090909091)(955.474747474748,-9.93181818181818)(940.545454545455,-9.87272727272727)(925.616161616162,-9.83333333333333)(921.883838383838,-9.81818181818182)(910.686868686869,-9.76363636363636)(895.757575757576,-9.79545454545455)(880.828282828283,-9.70454545454546)(865.89898989899,-9.69090909090909)(861.420202020202,-9.63636363636364)(850.969696969697,-9.50909090909091)(845.371212121212,-9.45454545454546)(836.040404040404,-9.3030303030303)(834.174242424242,-9.27272727272727)(821.111111111111,-9.11363636363636)(818.622895622896,-9.09090909090909)(806.181818181818,-8.97727272727273)(801.70303030303,-8.90909090909091)(804.688888888889,-8.72727272727273)(796.85101010101,-8.54545454545455)(800.583333333333,-8.36363636363636)(806.181818181818,-8.29545454545455)(821.111111111111,-8.2)(824.843434343434,-8.18181818181818)(836.040404040404,-8.11363636363636)(848.481481481482,-8)(850.969696969697,-7.96969696969697)(858.434343434343,-7.81818181818182)(865.89898989899,-7.72727272727273)(880.828282828283,-7.69090909090909)(888.292929292929,-7.63636363636364)(895.757575757576,-7.58181818181818)(910.686868686869,-7.61363636363636)(925.616161616162,-7.52272727272727)(940.545454545455,-7.48484848484849)(943.03367003367,-7.45454545454546)(955.474747474747,-7.37878787878788)(970.40404040404,-7.37878787878788)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1015.19191919192,-7.36363636363636)(1030.12121212121,-7.4)(1045.05050505051,-7.43636363636364)(1059.9797979798,-7.40909090909091)(1065.57828282828,-7.45454545454546)(1074.90909090909,-7.56818181818182)(1089.83838383838,-7.61818181818182)(1092.3265993266,-7.63636363636364)(1104.76767676768,-7.75)(1119.69696969697,-7.79545454545455)(1127.16161616162,-7.81818181818182)(1134.62626262626,-7.83636363636364)(1149.55555555556,-7.87272727272727)(1164.48484848485,-7.90909090909091)(1179.41414141414,-7.94545454545455)(1194.34343434343,-7.92424242424242)(1209.27272727273,-7.95454545454546)(1224.20202020202,-7.92424242424242)(1239.13131313131,-7.92424242424242)(1254.06060606061,-7.86363636363636)(1268.9898989899,-7.89393939393939)(1283.91919191919,-7.95454545454546)(1298.84848484848,-7.98484848484848)(1301.3367003367,-8)(1313.77777777778,-8.15151515151515)(1328.70707070707,-8.09090909090909)(1334.30555555556,-8.18181818181818)(1343.63636363636,-8.33333333333333)(1346.12457912458,-8.36363636363636)(1358.56565656566,-8.51515151515152)(1360.43181818182,-8.54545454545455)(1373.49494949495,-8.67272727272727)(1379.09343434343,-8.72727272727273)(1388.42424242424,-8.84090909090909)(1399.62121212121,-8.90909090909091)(1403.35353535354,-8.95454545454546)(1418.28282828283,-9.04545454545455)(1420.14898989899,-9.09090909090909)(1425.74747474747,-9.27272727272727)(1433.21212121212,-9.38636363636364)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-7.77272727272727)(85.8434343434344,-7.63636363636364)(89.5757575757576,-7.60606060606061)(104.505050505051,-7.54545454545455)(119.434343434343,-7.48484848484849)(126.89898989899,-7.45454545454546)(134.363636363636,-7.42424242424243)(149.292929292929,-7.36363636363636)(160.489898989899,-7.45454545454546)(164.222222222222,-7.5)(179.151515151515,-7.59090909090909)(182.883838383838,-7.63636363636364)(194.080808080808,-7.72727272727273)(209.010101010101,-7.65909090909091)(216.474747474747,-7.63636363636364)(223.939393939394,-7.59090909090909)(238.868686868687,-7.54545454545455)(253.79797979798,-7.54545454545455)(268.727272727273,-7.60606060606061)(276.191919191919,-7.63636363636364)(283.656565656566,-7.68181818181818)(298.585858585859,-7.72727272727273)(313.515151515152,-7.72727272727273)(324.712121212121,-7.81818181818182)(328.444444444444,-7.84848484848485)(343.373737373737,-7.84848484848485)(358.30303030303,-7.86363636363636)(360.791245791246,-7.81818181818182)(373.232323232323,-7.66666666666667)(388.161616161616,-7.65909090909091)(403.090909090909,-7.65909090909091)(406.823232323232,-7.63636363636364)(414.287878787879,-7.45454545454546)(418.020202020202,-7.43181818181818)(432.949494949495,-7.36363636363636)(447.878787878788,-7.32727272727273)(459.075757575758,-7.27272727272727)(462.808080808081,-7.24242424242424)(477.737373737374,-7.18181818181818)(492.666666666667,-7.15909090909091)(507.59595959596,-7.24242424242424)(515.060606060606,-7.27272727272727)(522.525252525253,-7.28787878787879)(537.454545454546,-7.28787878787879)(541.186868686869,-7.27272727272727)(552.383838383838,-7.21818181818182)(567.313131313131,-7.20454545454546)(582.242424242424,-7.15909090909091)(597.171717171717,-7.22727272727273)(612.10101010101,-7.24242424242424)(615.833333333333,-7.27272727272727)(627.030303030303,-7.36363636363636)(638.227272727273,-7.45454545454546)(641.959595959596,-7.5)(656.888888888889,-7.59090909090909)(660.621212121212,-7.63636363636364)(671.818181818182,-7.77272727272727)(674.306397306397,-7.81818181818182)(679.282828282828,-8)(679.282828282828,-8.18181818181818)(679.282828282828,-8.36363636363636)(671.818181818182,-8.5)(664.353535353535,-8.54545454545455)(656.888888888889,-8.59090909090909)(641.959595959596,-8.59090909090909)(627.030303030303,-8.68181818181818)(619.565656565657,-8.72727272727273)(612.10101010101,-8.81818181818182)(604.636363636364,-8.90909090909091)(597.171717171717,-8.93939393939394)(582.242424242424,-9.03636363636364)(571.045454545455,-9.09090909090909)(567.313131313131,-9.11363636363636)(552.383838383838,-9.16666666666667)(537.454545454546,-9.22727272727273)(522.525252525253,-9.25757575757576)(507.59595959596,-9.25757575757576)(492.666666666667,-9.25757575757576)(477.737373737374,-9.22727272727273)(462.808080808081,-9.21818181818182)(447.878787878788,-9.11363636363636)(445.390572390572,-9.09090909090909)(432.949494949495,-8.93939393939394)(429.217171717172,-8.90909090909091)(418.020202020202,-8.84090909090909)(403.090909090909,-8.81818181818182)(391.893939393939,-8.72727272727273)(388.161616161616,-8.63636363636364)(373.232323232323,-8.59090909090909)(358.30303030303,-8.63636363636364)(343.373737373737,-8.63636363636364)(328.444444444444,-8.6969696969697)(324.712121212121,-8.72727272727273)(313.515151515152,-8.79545454545455)(298.585858585859,-8.87878787878788)(283.656565656566,-8.88636363636364)(281.16835016835,-8.90909090909091)(268.727272727273,-9.06060606060606)(261.262626262626,-9.09090909090909)(253.79797979798,-9.12121212121212)(238.868686868687,-9.22727272727273)(231.40404040404,-9.27272727272727)(223.939393939394,-9.3030303030303)(209.010101010101,-9.36363636363636)(194.080808080808,-9.3030303030303)(186.616161616162,-9.27272727272727)(179.151515151515,-9.22727272727273)(173.55303030303,-9.09090909090909)(164.222222222222,-8.93939393939394)(149.292929292929,-8.93939393939394)(145.560606060606,-8.90909090909091)(134.363636363636,-8.85454545454546)(119.434343434343,-8.79545454545455)(111.969696969697,-8.72727272727273)(106.993265993266,-8.54545454545455)(104.505050505051,-8.45454545454545)(100.772727272727,-8.36363636363636)(89.5757575757576,-8.27272727272727)(82.1111111111111,-8.18181818181818)(74.6464646464647,-8.04545454545455)(72.1582491582492,-8)(72.1582491582492,-7.81818181818182)(74.6464646464647,-7.77272727272727)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.72727272727273)(459.075757575758,-7.63636363636364)(462.808080808081,-7.61363636363636)(477.737373737374,-7.60606060606061)(492.666666666667,-7.48484848484849)(507.59595959596,-7.56818181818182)(522.525252525253,-7.58181818181818)(537.454545454546,-7.56060606060606)(552.383838383838,-7.50909090909091)(567.313131313131,-7.52272727272727)(582.242424242424,-7.54545454545455)(589.707070707071,-7.63636363636364)(597.171717171717,-7.70454545454546)(606.502525252525,-7.81818181818182)(612.10101010101,-7.95454545454546)(615.833333333333,-8)(623.29797979798,-8.18181818181818)(612.10101010101,-8.25)(602.770202020202,-8.36363636363636)(597.171717171717,-8.45454545454545)(589.707070707071,-8.54545454545455)(582.242424242424,-8.63636363636364)(576.643939393939,-8.72727272727273)(567.313131313131,-8.81818181818182)(552.383838383838,-8.89090909090909)(548.651515151515,-8.90909090909091)(537.454545454546,-8.95454545454546)(522.525252525253,-8.98484848484848)(507.59595959596,-8.98484848484848)(492.666666666667,-8.98484848484848)(477.737373737374,-8.92727272727273)(470.272727272727,-8.90909090909091)(462.808080808081,-8.86363636363636)(457.209595959596,-8.72727272727273)(453.477272727273,-8.54545454545455)(447.878787878788,-8.45454545454545)(436.681818181818,-8.36363636363636)(435.43771043771,-8.18181818181818)(438.54797979798,-8)(440.414141414141,-7.81818181818182)(447.878787878788,-7.72727272727273)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (477.737373737374,-14.6818181818182)(488.934343434343,-14.5454545454545)(492.666666666667,-14.5151515151515)(507.59595959596,-14.3939393939394)(515.060606060606,-14.3636363636364)(522.525252525253,-14.3333333333333)(537.454545454546,-14.2727272727273)(552.383838383838,-14.2727272727273)(567.313131313131,-14.2727272727273)(582.242424242424,-14.2727272727273)(597.171717171717,-14.2727272727273)(612.10101010101,-14.2727272727273)(627.030303030303,-14.2727272727273)(641.959595959596,-14.2727272727273)(656.888888888889,-14.2727272727273)(671.818181818182,-14.2727272727273)(686.747474747475,-14.3181818181818)(690.479797979798,-14.3636363636364)(690.479797979798,-14.5454545454545)(686.747474747475,-14.5757575757576)(671.818181818182,-14.6969696969697)(664.353535353535,-14.7272727272727)(656.888888888889,-14.7575757575758)(641.959595959596,-14.8787878787879)(634.494949494949,-14.9090909090909)(627.030303030303,-14.9393939393939)(612.10101010101,-15.0606060606061)(604.636363636364,-15.0909090909091)(597.171717171717,-15.1212121212121)(582.242424242424,-15.1818181818182)(567.313131313131,-15.2424242424242)(559.848484848485,-15.2727272727273)(552.383838383838,-15.3030303030303)(537.454545454546,-15.3636363636364)(522.525252525253,-15.3636363636364)(507.59595959596,-15.3636363636364)(492.666666666667,-15.3030303030303)(488.934343434343,-15.2727272727273)(477.737373737374,-15.1363636363636)(475.249158249158,-15.0909090909091)(470.272727272727,-14.9090909090909)(475.249158249158,-14.7272727272727)(477.737373737374,-14.6818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (164.222222222222,-8.33333333333333)(176.6632996633,-8.18181818181818)(179.151515151515,-8.15909090909091)(194.080808080808,-8.12727272727273)(209.010101010101,-8.12727272727273)(220.207070707071,-8.18181818181818)(223.939393939394,-8.22727272727273)(229.537878787879,-8.36363636363636)(227.671717171717,-8.54545454545455)(223.939393939394,-8.57575757575757)(211.498316498317,-8.72727272727273)(209.010101010101,-8.75757575757576)(201.545454545455,-8.72727272727273)(194.080808080808,-8.68181818181818)(179.151515151515,-8.65909090909091)(166.710437710438,-8.54545454545455)(164.222222222222,-8.45454545454545)(160.489898989899,-8.36363636363636)(164.222222222222,-8.33333333333333)};

\addplot [fill=white,draw=none,forget plot] coordinates{ (388.161616161616,-8.31818181818182)(380.69696969697,-8.36363636363636)(388.161616161616,-8.45454545454545)(391.893939393939,-8.36363636363636)(388.161616161616,-8.31818181818182)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091)(119.434343434343,-8.36363636363636)(791.252525252525,-8.72727272727273)(627.030303030303,-7.63636363636364)(1224.20202020202,-7.81818181818182)(791.252525252525,-9.09090909090909)(1089.83838383838,-10.1818181818182)(806.181818181818,-8.18181818181818)(641.959595959596,-8)(821.111111111111,-8)(940.545454545455,-7.27272727272727)(1030.12121212121,-7.27272727272727)(403.090909090909,-8.36363636363636)(1418.28282828283,-10)(283.656565656566,-8.18181818181818)(268.727272727273,-8)(477.737373737374,-7.45454545454546)(1224.20202020202,-10)(1209.27272727273,-10)(1283.91919191919,-10)(134.363636363636,-8.54545454545455)(134.363636363636,-8.72727272727273)(791.252525252525,-8.36363636363636)(447.878787878788,-8.72727272727273)(955.474747474747,-7.27272727272727)(522.525252525253,-7.27272727272727)(268.727272727273,-8.72727272727273)(776.323232323232,-8.72727272727273)(627.030303030303,-8.54545454545455)(1209.27272727273,-7.81818181818182)(1448.14141414141,-9.81818181818182)(880.828282828283,-9.81818181818182)(253.79797979798,-8.72727272727273)(895.757575757576,-7.45454545454546)(149.292929292929,-8)(462.808080808081,-8.90909090909091)(298.585858585859,-8.36363636363636)(403.090909090909,-8)(388.161616161616,-8.18181818181818)(1074.90909090909,-10.1818181818182)(432.949494949495,-8.72727272727273)(1268.9898989899,-7.81818181818182)(119.434343434343,-8.54545454545455)(1283.91919191919,-7.81818181818182)(149.292929292929,-8.90909090909091)(298.585858585859,-8.18181818181818)(1194.34343434343,-10)(1388.42424242424,-10)(1343.63636363636,-10.1818181818182)(283.656565656566,-8.54545454545455)(1463.07070707071,-9.27272727272727)(836.040404040404,-7.81818181818182)(238.868686868687,-8)(552.383838383838,-8.90909090909091)(522.525252525253,-9.09090909090909)(507.59595959596,-9.09090909090909)(537.454545454546,-9.09090909090909)(492.666666666667,-9.09090909090909)(1478,-9.45454545454546)(641.959595959596,-8.54545454545455)(1343.63636363636,-8) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_240.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.00008294006,-8.72727272727273)(1478.00033175469,-8.90909090909091)(1478.00066349464,-9.09090909090909)(1478.00058056104,-9.27272727272727)(1478.00049762651,-9.45454545454546)(1478.00041469106,-9.63636363636364)(1478.00041469106,-9.81818181818182)(1478.0002488174,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.93181818181818)(1478.00029027891,-9.09090909090909)(1478.00020734323,-9.27272727272727)(1478.00012440663,-9.45454545454546)(1478.00004146911,-9.63636363636364)(1478.00004146911,-9.81818181818182)(1478,-9.86363636363636)(1463.07070707071,-9.90909090909091)(1451.87373737374,-10)(1448.14141414141,-10.030303030303)(1433.21212121212,-10.0909090909091)(1418.28282828283,-10.1272727272727)(1407.08585858586,-10.1818181818182)(1403.35353535354,-10.2272727272727)(1388.42424242424,-10.2954545454545)(1373.49494949495,-10.3484848484848)(1358.56565656566,-10.3090909090909)(1343.63636363636,-10.2954545454545)(1328.70707070707,-10.2121212121212)(1313.77777777778,-10.2727272727273)(1298.84848484848,-10.2954545454545)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2045454545455)(1261.52525252525,-10.1818181818182)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1666666666667)(1216.73737373737,-10.1818181818182)(1209.27272727273,-10.2045454545455)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2954545454545)(1164.48484848485,-10.2121212121212)(1149.55555555556,-10.2121212121212)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.2121212121212)(1104.76767676768,-10.2045454545455)(1089.83838383838,-10.2)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1056.24747474747,-10.3636363636364)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2727272727273)(1000.26262626263,-10.2045454545455)(985.333333333333,-10.2121212121212)(970.40404040404,-10.2727272727273)(955.474747474748,-10.25)(944.277777777778,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0545454545455)(895.757575757576,-10.0909090909091)(880.828282828283,-10.030303030303)(877.09595959596,-10)(865.89898989899,-9.95454545454546)(852.462626262626,-9.81818181818182)(850.969696969697,-9.8030303030303)(836.040404040404,-9.75)(821.111111111111,-9.65909090909091)(813.646464646465,-9.63636363636364)(806.181818181818,-9.59090909090909)(798.717171717172,-9.45454545454546)(791.252525252525,-9.4)(778.189393939394,-9.27272727272727)(778.811447811448,-9.09090909090909)(776.323232323232,-9.06060606060606)(766.992424242424,-8.90909090909091)(765.126262626263,-8.72727272727273)(763.260101010101,-8.54545454545455)(768.858585858586,-8.36363636363636)(776.323232323232,-8.22727272727273)(778.189393939394,-8.18181818181818)(791.252525252525,-8.05454545454545)(802.449494949495,-8)(806.181818181818,-7.98181818181818)(821.111111111111,-7.89393939393939)(828.575757575758,-7.81818181818182)(836.040404040404,-7.70454545454546)(843.505050505051,-7.63636363636364)(850.969696969697,-7.54545454545455)(858.434343434343,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.37878787878788)(895.757575757576,-7.28787878787879)(910.686868686869,-7.28787878787879)(914.419191919192,-7.27272727272727)(925.616161616162,-7.20454545454546)(940.545454545455,-7.15909090909091)(955.474747474747,-7.10606060606061)(970.40404040404,-7.10606060606061)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.10606060606061)(1030.12121212121,-7.16666666666667)(1045.05050505051,-7.1969696969697)(1059.9797979798,-7.1969696969697)(1074.90909090909,-7.25)(1082.37373737374,-7.27272727272727)(1089.83838383838,-7.29090909090909)(1104.76767676768,-7.36363636363636)(1119.69696969697,-7.42424242424243)(1122.18518518519,-7.45454545454546)(1134.62626262626,-7.53030303030303)(1149.55555555556,-7.58181818181818)(1164.48484848485,-7.61363636363636)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.65151515151515)(1194.34343434343,-7.65151515151515)(1209.27272727273,-7.68181818181818)(1224.20202020202,-7.65151515151515)(1239.13131313131,-7.65151515151515)(1242.86363636364,-7.63636363636364)(1254.06060606061,-7.59090909090909)(1268.9898989899,-7.59090909090909)(1283.91919191919,-7.61818181818182)(1291.38383838384,-7.63636363636364)(1298.84848484848,-7.65454545454546)(1313.77777777778,-7.72727272727273)(1328.70707070707,-7.70454545454546)(1343.63636363636,-7.78787878787879)(1358.56565656566,-7.79545454545455)(1361.05387205387,-7.81818181818182)(1367.89646464646,-8)(1372.00202020202,-8.18181818181818)(1373.49494949495,-8.22727272727273)(1384.69191919192,-8.36363636363636)(1388.42424242424,-8.39393939393939)(1403.35353535354,-8.39393939393939)(1418.28282828283,-8.47727272727273)(1433.21212121212,-8.52272727272727)(1435.70033670034,-8.54545454545455)(1448.14141414141,-8.65909090909091)(1455.60606060606,-8.72727272727273)(1463.07070707071,-8.86363636363636)(1470.53535353535,-8.90909090909091)(1478,-8.93181818181818)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.38636363636364)(1438.81060606061,-9.45454545454546)(1435.07828282828,-9.63636363636364)(1433.21212121212,-9.66666666666667)(1418.28282828283,-9.76363636363636)(1403.35353535354,-9.79545454545455)(1400.86531986532,-9.81818181818182)(1388.42424242424,-9.96969696969697)(1385.93602693603,-10)(1373.49494949495,-10.0757575757576)(1358.56565656566,-10.0151515151515)(1351.10101010101,-10)(1343.63636363636,-9.96969696969697)(1328.70707070707,-9.88636363636364)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.96969696969697)(1283.91919191919,-9.97727272727273)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.89393939393939)(1239.13131313131,-9.83333333333333)(1224.20202020202,-9.89393939393939)(1209.27272727273,-9.90909090909091)(1194.34343434343,-9.97727272727273)(1179.41414141414,-9.96969696969697)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.88636363636364)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.88636363636364)(1104.76767676768,-9.90909090909091)(1089.83838383838,-9.92424242424243)(1077.39730639731,-10)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1017.68013468013,-10)(1015.19191919192,-9.97727272727273)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.88636363636364)(970.40404040404,-9.90909090909091)(955.474747474748,-9.93181818181818)(940.545454545455,-9.87272727272727)(925.616161616162,-9.83333333333333)(921.883838383838,-9.81818181818182)(910.686868686869,-9.76363636363636)(895.757575757576,-9.79545454545455)(880.828282828283,-9.70454545454546)(865.89898989899,-9.65454545454546)(864.032828282828,-9.63636363636364)(850.969696969697,-9.53030303030303)(838.528619528619,-9.45454545454546)(836.040404040404,-9.42424242424243)(821.111111111111,-9.29090909090909)(818.622895622896,-9.27272727272727)(811.780303030303,-9.09090909090909)(806.181818181818,-9.02272727272727)(798.717171717172,-8.90909090909091)(804.688888888889,-8.72727272727273)(796.85101010101,-8.54545454545455)(800.583333333333,-8.36363636363636)(806.181818181818,-8.29545454545455)(818.622895622896,-8.18181818181818)(821.111111111111,-8.16666666666667)(836.040404040404,-8.06818181818182)(843.505050505051,-8)(850.969696969697,-7.90909090909091)(856.568181818182,-7.81818181818182)(865.89898989899,-7.72727272727273)(880.828282828283,-7.69090909090909)(888.292929292929,-7.63636363636364)(895.757575757576,-7.58181818181818)(910.686868686869,-7.61363636363636)(925.616161616162,-7.52272727272727)(940.545454545455,-7.48484848484849)(943.03367003367,-7.45454545454546)(955.474747474747,-7.37878787878788)(970.40404040404,-7.37878787878788)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1015.19191919192,-7.37878787878788)(1030.12121212121,-7.43939393939394)(1037.58585858586,-7.45454545454546)(1045.05050505051,-7.47272727272727)(1059.9797979798,-7.47272727272727)(1074.90909090909,-7.54545454545455)(1089.83838383838,-7.59090909090909)(1101.03535353535,-7.63636363636364)(1104.76767676768,-7.65909090909091)(1119.69696969697,-7.75)(1134.62626262626,-7.8030303030303)(1138.35858585859,-7.81818181818182)(1149.55555555556,-7.87272727272727)(1164.48484848485,-7.90909090909091)(1179.41414141414,-7.94545454545455)(1194.34343434343,-7.92424242424242)(1209.27272727273,-7.95454545454546)(1224.20202020202,-7.92424242424242)(1239.13131313131,-7.92424242424242)(1254.06060606061,-7.86363636363636)(1268.9898989899,-7.86363636363636)(1283.91919191919,-7.92424242424242)(1298.84848484848,-7.95454545454546)(1306.31313131313,-8)(1313.77777777778,-8.09090909090909)(1328.70707070707,-8.03030303030303)(1338.03787878788,-8.18181818181818)(1343.63636363636,-8.27272727272727)(1348.11515151515,-8.36363636363636)(1358.56565656566,-8.52272727272727)(1360.43181818182,-8.54545454545455)(1373.49494949495,-8.67272727272727)(1379.09343434343,-8.72727272727273)(1388.42424242424,-8.84090909090909)(1399.62121212121,-8.90909090909091)(1403.35353535354,-8.95454545454546)(1418.28282828283,-9.04545454545455)(1420.14898989899,-9.09090909090909)(1425.74747474747,-9.27272727272727)(1433.21212121212,-9.38636363636364)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (89.5757575757576,-7.86363636363636)(93.3080808080808,-7.81818181818182)(104.505050505051,-7.68181818181818)(111.969696969697,-7.63636363636364)(119.434343434343,-7.60606060606061)(134.363636363636,-7.59090909090909)(149.292929292929,-7.59090909090909)(156.757575757576,-7.63636363636364)(164.222222222222,-7.66666666666667)(179.151515151515,-7.65909090909091)(194.080808080808,-7.72727272727273)(209.010101010101,-7.65909090909091)(216.474747474747,-7.63636363636364)(223.939393939394,-7.59090909090909)(238.868686868687,-7.54545454545455)(253.79797979798,-7.60606060606061)(261.262626262626,-7.63636363636364)(268.727272727273,-7.66666666666667)(283.656565656566,-7.77272727272727)(298.585858585859,-7.72727272727273)(313.515151515152,-7.72727272727273)(324.712121212121,-7.81818181818182)(328.444444444444,-7.84848484848485)(343.373737373737,-7.84848484848485)(358.30303030303,-7.86363636363636)(360.169191919192,-7.81818181818182)(373.232323232323,-7.65909090909091)(388.161616161616,-7.65454545454546)(403.090909090909,-7.69090909090909)(414.287878787879,-7.63636363636364)(418.020202020202,-7.54545454545455)(420.508417508418,-7.45454545454546)(432.949494949495,-7.34090909090909)(447.878787878788,-7.28787878787879)(451.611111111111,-7.27272727272727)(462.808080808081,-7.20454545454546)(477.737373737374,-7.11363636363636)(485.20202020202,-7.09090909090909)(492.666666666667,-7.07272727272727)(500.131313131313,-7.09090909090909)(507.59595959596,-7.10606060606061)(522.525252525253,-7.16666666666667)(537.454545454546,-7.22727272727273)(552.383838383838,-7.16666666666667)(567.313131313131,-7.20454545454546)(582.242424242424,-7.15909090909091)(594.683501683502,-7.27272727272727)(597.171717171717,-7.28787878787879)(604.636363636364,-7.27272727272727)(612.10101010101,-7.24242424242424)(615.833333333333,-7.27272727272727)(627.030303030303,-7.36363636363636)(638.227272727273,-7.45454545454546)(641.959595959596,-7.5)(653.156565656566,-7.63636363636364)(656.888888888889,-7.66666666666667)(669.329966329966,-7.81818181818182)(671.818181818182,-7.90909090909091)(674.306397306397,-8)(679.282828282828,-8.18181818181818)(674.306397306397,-8.36363636363636)(671.818181818182,-8.40909090909091)(656.888888888889,-8.51515151515152)(649.424242424242,-8.54545454545455)(641.959595959596,-8.59090909090909)(627.030303030303,-8.68181818181818)(619.565656565657,-8.72727272727273)(612.10101010101,-8.81818181818182)(604.636363636364,-8.90909090909091)(597.171717171717,-8.93939393939394)(582.242424242424,-9.03636363636364)(571.045454545455,-9.09090909090909)(567.313131313131,-9.11363636363636)(552.383838383838,-9.16666666666667)(537.454545454546,-9.22727272727273)(522.525252525253,-9.25757575757576)(507.59595959596,-9.25757575757576)(492.666666666667,-9.25757575757576)(477.737373737374,-9.22727272727273)(462.808080808081,-9.21818181818182)(447.878787878788,-9.11363636363636)(445.390572390572,-9.09090909090909)(432.949494949495,-8.93939393939394)(429.217171717172,-8.90909090909091)(418.020202020202,-8.84090909090909)(403.090909090909,-8.81818181818182)(391.893939393939,-8.72727272727273)(388.161616161616,-8.63636363636364)(373.232323232323,-8.59090909090909)(358.30303030303,-8.63636363636364)(343.373737373737,-8.63636363636364)(328.444444444444,-8.6969696969697)(324.712121212121,-8.72727272727273)(313.515151515152,-8.79545454545455)(298.585858585859,-8.87878787878788)(283.656565656566,-8.88636363636364)(281.16835016835,-8.90909090909091)(268.727272727273,-9.06060606060606)(261.262626262626,-9.09090909090909)(253.79797979798,-9.12121212121212)(238.868686868687,-9.22727272727273)(231.40404040404,-9.27272727272727)(223.939393939394,-9.3030303030303)(209.010101010101,-9.36363636363636)(194.080808080808,-9.3030303030303)(186.616161616162,-9.27272727272727)(179.151515151515,-9.22727272727273)(173.55303030303,-9.09090909090909)(164.222222222222,-8.93939393939394)(149.292929292929,-8.93939393939394)(145.560606060606,-8.90909090909091)(134.363636363636,-8.85454545454546)(119.434343434343,-8.79545454545455)(111.969696969697,-8.72727272727273)(106.371212121212,-8.54545454545455)(104.505050505051,-8.45454545454545)(100.772727272727,-8.36363636363636)(89.5757575757576,-8.22727272727273)(87.0875420875421,-8.18181818181818)(82.1111111111111,-8)(89.5757575757576,-7.86363636363636)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (432.949494949495,-8.09090909090909)(434.815656565657,-8)(437.428282828283,-7.81818181818182)(446.012626262626,-7.63636363636364)(447.878787878788,-7.61363636363636)(462.808080808081,-7.52272727272727)(474.005050505051,-7.45454545454546)(477.737373737374,-7.43939393939394)(492.666666666667,-7.34848484848485)(507.59595959596,-7.37878787878788)(522.525252525253,-7.43939393939394)(526.257575757576,-7.45454545454546)(537.454545454546,-7.5)(548.651515151515,-7.45454545454546)(552.383838383838,-7.43939393939394)(556.116161616162,-7.45454545454546)(567.313131313131,-7.52272727272727)(582.242424242424,-7.48484848484849)(594.683501683502,-7.63636363636364)(597.171717171717,-7.65909090909091)(610.234848484849,-7.81818181818182)(612.10101010101,-7.90909090909091)(615.833333333333,-8)(623.29797979798,-8.18181818181818)(612.10101010101,-8.25)(602.770202020202,-8.36363636363636)(597.171717171717,-8.45454545454545)(589.707070707071,-8.54545454545455)(582.242424242424,-8.63636363636364)(576.643939393939,-8.72727272727273)(567.313131313131,-8.81818181818182)(552.383838383838,-8.89090909090909)(548.651515151515,-8.90909090909091)(537.454545454546,-8.95454545454546)(522.525252525253,-8.98484848484848)(507.59595959596,-8.98484848484848)(492.666666666667,-8.98484848484848)(477.737373737374,-8.92727272727273)(470.272727272727,-8.90909090909091)(462.808080808081,-8.86363636363636)(457.209595959596,-8.72727272727273)(453.477272727273,-8.54545454545455)(447.878787878788,-8.45454545454545)(436.681818181818,-8.36363636363636)(432.949494949495,-8.27272727272727)(430.461279461279,-8.18181818181818)(432.949494949495,-8.09090909090909)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (164.222222222222,-8.31818181818182)(171.686868686869,-8.18181818181818)(179.151515151515,-8.11363636363636)(194.080808080808,-8.12727272727273)(209.010101010101,-8.12727272727273)(220.207070707071,-8.18181818181818)(223.939393939394,-8.22727272727273)(229.537878787879,-8.36363636363636)(227.671717171717,-8.54545454545455)(223.939393939394,-8.57575757575757)(211.498316498317,-8.72727272727273)(209.010101010101,-8.75757575757576)(201.545454545455,-8.72727272727273)(194.080808080808,-8.68181818181818)(179.151515151515,-8.65909090909091)(166.710437710438,-8.54545454545455)(164.222222222222,-8.45454545454545)(160.489898989899,-8.36363636363636)(164.222222222222,-8.31818181818182)};

\addplot [fill=white,draw=none,forget plot] coordinates{ (388.161616161616,-8.33333333333333)(380.69696969697,-8.36363636363636)(388.161616161616,-8.45454545454545)(391.893939393939,-8.36363636363636)(388.161616161616,-8.33333333333333)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091)(119.434343434343,-8.36363636363636)(791.252525252525,-8.72727272727273)(627.030303030303,-7.63636363636364)(1224.20202020202,-7.81818181818182)(791.252525252525,-9.09090909090909)(1089.83838383838,-10.1818181818182)(806.181818181818,-8.18181818181818)(641.959595959596,-8)(821.111111111111,-8)(940.545454545455,-7.27272727272727)(1030.12121212121,-7.27272727272727)(403.090909090909,-8.36363636363636)(1418.28282828283,-10)(283.656565656566,-8.18181818181818)(268.727272727273,-8)(477.737373737374,-7.45454545454546)(1224.20202020202,-10)(1209.27272727273,-10)(1283.91919191919,-10)(134.363636363636,-8.54545454545455)(134.363636363636,-8.72727272727273)(791.252525252525,-8.36363636363636)(447.878787878788,-8.72727272727273)(955.474747474747,-7.27272727272727)(522.525252525253,-7.27272727272727)(268.727272727273,-8.72727272727273)(776.323232323232,-8.72727272727273)(627.030303030303,-8.54545454545455)(1209.27272727273,-7.81818181818182)(1448.14141414141,-9.81818181818182)(880.828282828283,-9.81818181818182)(253.79797979798,-8.72727272727273)(895.757575757576,-7.45454545454546)(149.292929292929,-8)(462.808080808081,-8.90909090909091)(298.585858585859,-8.36363636363636)(403.090909090909,-8)(388.161616161616,-8.18181818181818)(1074.90909090909,-10.1818181818182)(432.949494949495,-8.72727272727273)(1268.9898989899,-7.81818181818182)(119.434343434343,-8.54545454545455)(1283.91919191919,-7.81818181818182)(149.292929292929,-8.90909090909091)(298.585858585859,-8.18181818181818)(1194.34343434343,-10)(1388.42424242424,-10)(1343.63636363636,-10.1818181818182)(283.656565656566,-8.54545454545455)(1463.07070707071,-9.27272727272727)(836.040404040404,-7.81818181818182)(238.868686868687,-8)(552.383838383838,-8.90909090909091)(522.525252525253,-9.09090909090909)(507.59595959596,-9.09090909090909)(537.454545454546,-9.09090909090909)(492.666666666667,-9.09090909090909)(1478,-9.45454545454546)(641.959595959596,-8.54545454545455)(1343.63636363636,-8)(1045.05050505051,-7.27272727272727)(1119.69696969697,-7.63636363636364)(418.020202020202,-7.63636363636364)(119.434343434343,-8)(836.040404040404,-8)(134.363636363636,-8.18181818181818)(164.222222222222,-8)(806.181818181818,-9.45454545454546)(791.252525252525,-9.27272727272727)(850.969696969697,-9.81818181818182)(283.656565656566,-8.36363636363636)(388.161616161616,-8)(1373.49494949495,-8.18181818181818)(134.363636363636,-8.36363636363636)(671.818181818182,-14.3636363636364)(507.59595959596,-7.27272727272727)(567.313131313131,-7.27272727272727)(582.242424242424,-7.27272727272727)(447.878787878788,-7.45454545454546)(492.666666666667,-7.27272727272727) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_260.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.00008294006,-8.72727272727273)(1478.00016587919,-8.90909090909091)(1478.00049762651,-9.09090909090909)(1478.00041469106,-9.27272727272727)(1478.00049762651,-9.45454545454546)(1478.0002488174,-9.63636363636364)(1478.0002488174,-9.81818181818182)(1478.00008294006,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-9.02272727272727)(1478.00012440663,-9.09090909090909)(1478.00004146911,-9.27272727272727)(1478.00012440663,-9.45454545454546)(1478,-9.54545454545455)(1463.07070707071,-9.59090909090909)(1461.57777777778,-9.63636363636364)(1463.07070707071,-9.72727272727273)(1466.80303030303,-9.81818181818182)(1463.07070707071,-9.84848484848485)(1450.62962962963,-10)(1448.14141414141,-10.030303030303)(1433.21212121212,-10.0909090909091)(1418.28282828283,-10.1272727272727)(1407.08585858586,-10.1818181818182)(1403.35353535354,-10.2272727272727)(1388.42424242424,-10.2954545454545)(1373.49494949495,-10.3484848484848)(1358.56565656566,-10.3090909090909)(1343.63636363636,-10.2954545454545)(1328.70707070707,-10.2121212121212)(1313.77777777778,-10.2727272727273)(1298.84848484848,-10.2954545454545)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2045454545455)(1261.52525252525,-10.1818181818182)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1666666666667)(1216.73737373737,-10.1818181818182)(1209.27272727273,-10.2045454545455)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2954545454545)(1164.48484848485,-10.2121212121212)(1149.55555555556,-10.2121212121212)(1134.62626262626,-10.2727272727273)(1119.69696969697,-10.2954545454545)(1104.76767676768,-10.2727272727273)(1089.83838383838,-10.2272727272727)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1056.24747474747,-10.3636363636364)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2727272727273)(1000.26262626263,-10.2045454545455)(985.333333333333,-10.2121212121212)(970.40404040404,-10.2954545454545)(955.474747474747,-10.2727272727273)(940.545454545455,-10.2045454545455)(938.057239057239,-10.1818181818182)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0545454545455)(895.757575757576,-10.0909090909091)(880.828282828283,-10.030303030303)(877.09595959596,-10)(865.89898989899,-9.95454545454546)(852.462626262626,-9.81818181818182)(850.969696969697,-9.8030303030303)(836.040404040404,-9.75)(821.111111111111,-9.65909090909091)(813.646464646465,-9.63636363636364)(806.181818181818,-9.59090909090909)(798.717171717172,-9.45454545454546)(791.252525252525,-9.4)(778.189393939394,-9.27272727272727)(778.811447811448,-9.09090909090909)(776.323232323232,-9.06060606060606)(766.992424242424,-8.90909090909091)(765.126262626263,-8.72727272727273)(763.260101010101,-8.54545454545455)(768.858585858586,-8.36363636363636)(776.323232323232,-8.22727272727273)(778.189393939394,-8.18181818181818)(791.252525252525,-8.05454545454545)(802.449494949495,-8)(806.181818181818,-7.98181818181818)(821.111111111111,-7.89393939393939)(828.575757575758,-7.81818181818182)(836.040404040404,-7.70454545454546)(843.505050505051,-7.63636363636364)(850.969696969697,-7.54545454545455)(858.434343434343,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.37878787878788)(895.757575757576,-7.28787878787879)(910.686868686869,-7.28787878787879)(914.419191919192,-7.27272727272727)(925.616161616162,-7.20454545454546)(940.545454545455,-7.15909090909091)(955.474747474747,-7.10606060606061)(970.40404040404,-7.10606060606061)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.10606060606061)(1030.12121212121,-7.16666666666667)(1045.05050505051,-7.1969696969697)(1059.9797979798,-7.1969696969697)(1074.90909090909,-7.25)(1082.37373737374,-7.27272727272727)(1089.83838383838,-7.29090909090909)(1104.76767676768,-7.36363636363636)(1119.69696969697,-7.42424242424243)(1122.18518518519,-7.45454545454546)(1134.62626262626,-7.53030303030303)(1149.55555555556,-7.61818181818182)(1157.0202020202,-7.63636363636364)(1164.48484848485,-7.65151515151515)(1179.41414141414,-7.68181818181818)(1194.34343434343,-7.65151515151515)(1209.27272727273,-7.68181818181818)(1224.20202020202,-7.65151515151515)(1239.13131313131,-7.65151515151515)(1242.86363636364,-7.63636363636364)(1254.06060606061,-7.59090909090909)(1268.9898989899,-7.59090909090909)(1283.91919191919,-7.59090909090909)(1295.11616161616,-7.63636363636364)(1298.84848484848,-7.65151515151515)(1313.77777777778,-7.70454545454546)(1328.70707070707,-7.75)(1343.63636363636,-7.78787878787879)(1358.56565656566,-7.79545454545455)(1361.05387205387,-7.81818181818182)(1367.89646464646,-8)(1372.00202020202,-8.18181818181818)(1373.49494949495,-8.21212121212121)(1388.42424242424,-8.31818181818182)(1395.88888888889,-8.36363636363636)(1403.35353535354,-8.38636363636364)(1418.28282828283,-8.51515151515152)(1425.74747474747,-8.54545454545455)(1433.21212121212,-8.57575757575757)(1445.6531986532,-8.72727272727273)(1448.14141414141,-8.75757575757576)(1457.47222222222,-8.90909090909091)(1463.07070707071,-9.04545454545455)(1478,-9.02272727272727)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.40909090909091)(1435.07828282828,-9.45454545454546)(1433.21212121212,-9.54545454545455)(1431.34595959596,-9.63636363636364)(1418.28282828283,-9.76363636363636)(1403.35353535354,-9.79545454545455)(1400.86531986532,-9.81818181818182)(1388.42424242424,-9.96969696969697)(1385.93602693603,-10)(1373.49494949495,-10.0757575757576)(1358.56565656566,-10.0151515151515)(1351.10101010101,-10)(1343.63636363636,-9.96969696969697)(1328.70707070707,-9.88636363636364)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.96969696969697)(1283.91919191919,-9.97727272727273)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.89393939393939)(1239.13131313131,-9.83333333333333)(1224.20202020202,-9.89393939393939)(1209.27272727273,-9.90909090909091)(1194.34343434343,-9.97727272727273)(1179.41414141414,-9.96969696969697)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.88636363636364)(1134.62626262626,-9.90909090909091)(1119.69696969697,-9.96969696969697)(1104.76767676768,-9.97727272727273)(1089.83838383838,-9.95454545454546)(1078.64141414141,-10)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1017.68013468013,-10)(1015.19191919192,-9.97727272727273)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.88636363636364)(970.40404040404,-9.96969696969697)(955.474747474747,-9.97727272727273)(940.545454545455,-9.90909090909091)(925.616161616162,-9.83333333333333)(921.883838383838,-9.81818181818182)(910.686868686869,-9.76363636363636)(895.757575757576,-9.79545454545455)(880.828282828283,-9.70454545454546)(865.89898989899,-9.65454545454546)(864.032828282828,-9.63636363636364)(850.969696969697,-9.53030303030303)(838.528619528619,-9.45454545454546)(836.040404040404,-9.42424242424243)(821.111111111111,-9.29090909090909)(818.622895622896,-9.27272727272727)(811.780303030303,-9.09090909090909)(806.181818181818,-9.02272727272727)(798.717171717172,-8.90909090909091)(804.688888888889,-8.72727272727273)(796.85101010101,-8.54545454545455)(800.583333333333,-8.36363636363636)(806.181818181818,-8.29545454545455)(818.622895622896,-8.18181818181818)(821.111111111111,-8.16666666666667)(836.040404040404,-8.06818181818182)(843.505050505051,-8)(850.969696969697,-7.90909090909091)(856.568181818182,-7.81818181818182)(865.89898989899,-7.72727272727273)(880.828282828283,-7.69090909090909)(888.292929292929,-7.63636363636364)(895.757575757576,-7.58181818181818)(910.686868686869,-7.61363636363636)(925.616161616162,-7.52272727272727)(940.545454545455,-7.48484848484849)(943.03367003367,-7.45454545454546)(955.474747474747,-7.37878787878788)(970.40404040404,-7.37878787878788)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1015.19191919192,-7.37878787878788)(1030.12121212121,-7.43939393939394)(1037.58585858586,-7.45454545454546)(1045.05050505051,-7.47272727272727)(1059.9797979798,-7.47272727272727)(1074.90909090909,-7.54545454545455)(1089.83838383838,-7.59090909090909)(1101.03535353535,-7.63636363636364)(1104.76767676768,-7.65909090909091)(1119.69696969697,-7.75)(1134.62626262626,-7.8030303030303)(1137.11447811448,-7.81818181818182)(1149.55555555556,-7.89393939393939)(1164.48484848485,-7.92424242424242)(1179.41414141414,-7.95454545454546)(1194.34343434343,-7.92424242424242)(1209.27272727273,-7.95454545454546)(1224.20202020202,-7.92424242424242)(1239.13131313131,-7.92424242424242)(1254.06060606061,-7.86363636363636)(1268.9898989899,-7.86363636363636)(1283.91919191919,-7.86363636363636)(1298.84848484848,-7.92424242424242)(1311.28956228956,-8)(1313.77777777778,-8.03030303030303)(1328.70707070707,-8.06818181818182)(1338.03787878788,-8.18181818181818)(1343.63636363636,-8.27272727272727)(1349.23484848485,-8.36363636363636)(1358.56565656566,-8.47727272727273)(1366.0303030303,-8.54545454545455)(1373.49494949495,-8.6)(1388.42424242424,-8.70909090909091)(1392.15656565657,-8.72727272727273)(1403.35353535354,-8.79545454545455)(1418.28282828283,-8.89090909090909)(1420.14898989899,-8.90909090909091)(1426.99158249158,-9.09090909090909)(1429.4797979798,-9.27272727272727)(1433.21212121212,-9.40909090909091)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (89.5757575757576,-7.86363636363636)(93.3080808080808,-7.81818181818182)(104.505050505051,-7.68181818181818)(111.969696969697,-7.63636363636364)(119.434343434343,-7.60606060606061)(134.363636363636,-7.59090909090909)(149.292929292929,-7.59090909090909)(156.757575757576,-7.63636363636364)(164.222222222222,-7.66666666666667)(179.151515151515,-7.65909090909091)(194.080808080808,-7.72727272727273)(209.010101010101,-7.70454545454546)(223.939393939394,-7.66666666666667)(231.40404040404,-7.63636363636364)(238.868686868687,-7.59090909090909)(253.79797979798,-7.60606060606061)(261.262626262626,-7.63636363636364)(268.727272727273,-7.66666666666667)(283.656565656566,-7.77272727272727)(298.585858585859,-7.72727272727273)(313.515151515152,-7.72727272727273)(324.712121212121,-7.81818181818182)(328.444444444444,-7.84848484848485)(343.373737373737,-7.84848484848485)(358.30303030303,-7.86363636363636)(360.169191919192,-7.81818181818182)(373.232323232323,-7.65909090909091)(388.161616161616,-7.65454545454546)(403.090909090909,-7.69090909090909)(414.287878787879,-7.63636363636364)(418.020202020202,-7.54545454545455)(420.508417508418,-7.45454545454546)(432.949494949495,-7.34090909090909)(447.878787878788,-7.28787878787879)(455.343434343434,-7.27272727272727)(462.808080808081,-7.25)(477.737373737374,-7.15909090909091)(492.666666666667,-7.10606060606061)(507.59595959596,-7.10606060606061)(522.525252525253,-7.16666666666667)(537.454545454546,-7.22727272727273)(552.383838383838,-7.16666666666667)(567.313131313131,-7.20454545454546)(582.242424242424,-7.15909090909091)(594.683501683502,-7.27272727272727)(597.171717171717,-7.28787878787879)(604.636363636364,-7.27272727272727)(612.10101010101,-7.24242424242424)(615.833333333333,-7.27272727272727)(627.030303030303,-7.36363636363636)(638.227272727273,-7.45454545454546)(641.959595959596,-7.48484848484849)(654.400673400673,-7.63636363636364)(656.888888888889,-7.66666666666667)(669.329966329966,-7.81818181818182)(671.818181818182,-7.90909090909091)(674.306397306397,-8)(679.282828282828,-8.18181818181818)(674.306397306397,-8.36363636363636)(671.818181818182,-8.40909090909091)(656.888888888889,-8.51515151515152)(641.959595959596,-8.51515151515152)(634.494949494949,-8.54545454545455)(627.030303030303,-8.59090909090909)(615.833333333333,-8.72727272727273)(612.10101010101,-8.81818181818182)(608.368686868687,-8.90909090909091)(597.171717171717,-9)(582.242424242424,-9.07272727272727)(567.313131313131,-9.07575757575758)(563.580808080808,-9.09090909090909)(552.383838383838,-9.13636363636364)(537.454545454546,-9.1969696969697)(522.525252525253,-9.25757575757576)(507.59595959596,-9.25757575757576)(492.666666666667,-9.25757575757576)(477.737373737374,-9.22727272727273)(462.808080808081,-9.21818181818182)(447.878787878788,-9.11363636363636)(445.390572390572,-9.09090909090909)(432.949494949495,-8.93939393939394)(429.217171717172,-8.90909090909091)(418.020202020202,-8.81818181818182)(406.823232323232,-8.72727272727273)(403.090909090909,-8.63636363636364)(400.602693602694,-8.54545454545455)(403.090909090909,-8.45454545454545)(404.957070707071,-8.36363636363636)(403.090909090909,-8.33333333333333)(388.161616161616,-8.23636363636364)(373.232323232323,-8.29545454545455)(362.035353535354,-8.36363636363636)(358.30303030303,-8.40909090909091)(343.373737373737,-8.51515151515152)(335.909090909091,-8.54545454545455)(328.444444444444,-8.57575757575757)(316.003367003367,-8.72727272727273)(313.515151515152,-8.75)(298.585858585859,-8.75757575757576)(283.656565656566,-8.84090909090909)(272.459595959596,-8.90909090909091)(268.727272727273,-8.93939393939394)(253.79797979798,-9.04545454545455)(238.868686868687,-9.06060606060606)(235.136363636364,-9.09090909090909)(223.939393939394,-9.18181818181818)(209.010101010101,-9.20454545454546)(194.080808080808,-9.20454545454546)(179.151515151515,-9.13636363636364)(176.6632996633,-9.09090909090909)(164.222222222222,-8.97727272727273)(149.292929292929,-8.97727272727273)(138.09595959596,-8.90909090909091)(134.363636363636,-8.89090909090909)(119.434343434343,-8.79545454545455)(111.969696969697,-8.72727272727273)(106.371212121212,-8.54545454545455)(104.505050505051,-8.45454545454545)(100.772727272727,-8.36363636363636)(89.5757575757576,-8.22727272727273)(87.0875420875421,-8.18181818181818)(82.1111111111111,-8)(89.5757575757576,-7.86363636363636)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (432.949494949495,-8.09090909090909)(434.815656565657,-8)(437.428282828283,-7.81818181818182)(446.012626262626,-7.63636363636364)(447.878787878788,-7.61363636363636)(462.808080808081,-7.54545454545455)(477.737373737374,-7.48484848484849)(480.225589225589,-7.45454545454546)(492.666666666667,-7.37878787878788)(507.59595959596,-7.37878787878788)(522.525252525253,-7.43939393939394)(526.257575757576,-7.45454545454546)(537.454545454546,-7.5)(548.651515151515,-7.45454545454546)(552.383838383838,-7.43939393939394)(556.116161616162,-7.45454545454546)(567.313131313131,-7.52272727272727)(582.242424242424,-7.48484848484849)(594.683501683502,-7.63636363636364)(597.171717171717,-7.65909090909091)(612.10101010101,-7.77272727272727)(614.589225589226,-7.81818181818182)(623.29797979798,-8)(623.29797979798,-8.18181818181818)(612.10101010101,-8.25)(602.770202020202,-8.36363636363636)(597.171717171717,-8.45454545454545)(589.707070707071,-8.54545454545455)(582.242424242424,-8.68181818181818)(579.754208754209,-8.72727272727273)(567.313131313131,-8.8030303030303)(552.383838383838,-8.86363636363636)(541.186868686869,-8.90909090909091)(537.454545454546,-8.92424242424242)(522.525252525253,-8.98484848484848)(507.59595959596,-8.98484848484848)(492.666666666667,-8.98484848484848)(477.737373737374,-8.92727272727273)(470.272727272727,-8.90909090909091)(462.808080808081,-8.86363636363636)(457.209595959596,-8.72727272727273)(453.477272727273,-8.54545454545455)(447.878787878788,-8.45454545454545)(436.681818181818,-8.36363636363636)(432.949494949495,-8.27272727272727)(431.083333333333,-8.18181818181818)(432.949494949495,-8.09090909090909)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (149.292929292929,-8.5)(160.489898989899,-8.36363636363636)(164.222222222222,-8.31818181818182)(171.686868686869,-8.18181818181818)(179.151515151515,-8.11363636363636)(194.080808080808,-8.12727272727273)(209.010101010101,-8.10606060606061)(223.939393939394,-8.16363636363636)(231.40404040404,-8.18181818181818)(233.270202020202,-8.36363636363636)(223.939393939394,-8.51515151515152)(221.451178451178,-8.54545454545455)(210.876262626263,-8.72727272727273)(209.010101010101,-8.75757575757576)(201.545454545455,-8.72727272727273)(194.080808080808,-8.68181818181818)(179.151515151515,-8.65909090909091)(164.222222222222,-8.56363636363636)(149.292929292929,-8.56818181818182)(146.804713804714,-8.54545454545455)(149.292929292929,-8.5)};

\addplot [fill=white,draw=none,forget plot] coordinates{ (1463.07070707071,-9.18181818181818)(1461.57777777778,-9.27272727272727)(1463.07070707071,-9.31818181818182)(1470.53535353535,-9.27272727272727)(1463.07070707071,-9.18181818181818)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091)(119.434343434343,-8.36363636363636)(791.252525252525,-8.72727272727273)(627.030303030303,-7.63636363636364)(1224.20202020202,-7.81818181818182)(791.252525252525,-9.09090909090909)(1089.83838383838,-10.1818181818182)(806.181818181818,-8.18181818181818)(641.959595959596,-8)(821.111111111111,-8)(940.545454545455,-7.27272727272727)(1030.12121212121,-7.27272727272727)(403.090909090909,-8.36363636363636)(1418.28282828283,-10)(283.656565656566,-8.18181818181818)(268.727272727273,-8)(477.737373737374,-7.45454545454546)(1224.20202020202,-10)(1209.27272727273,-10)(1283.91919191919,-10)(134.363636363636,-8.54545454545455)(134.363636363636,-8.72727272727273)(791.252525252525,-8.36363636363636)(447.878787878788,-8.72727272727273)(955.474747474747,-7.27272727272727)(522.525252525253,-7.27272727272727)(268.727272727273,-8.72727272727273)(776.323232323232,-8.72727272727273)(627.030303030303,-8.54545454545455)(1209.27272727273,-7.81818181818182)(1448.14141414141,-9.81818181818182)(880.828282828283,-9.81818181818182)(253.79797979798,-8.72727272727273)(895.757575757576,-7.45454545454546)(149.292929292929,-8)(462.808080808081,-8.90909090909091)(298.585858585859,-8.36363636363636)(403.090909090909,-8)(388.161616161616,-8.18181818181818)(1074.90909090909,-10.1818181818182)(432.949494949495,-8.72727272727273)(1268.9898989899,-7.81818181818182)(119.434343434343,-8.54545454545455)(1283.91919191919,-7.81818181818182)(149.292929292929,-8.90909090909091)(298.585858585859,-8.18181818181818)(1194.34343434343,-10)(1388.42424242424,-10)(1343.63636363636,-10.1818181818182)(283.656565656566,-8.54545454545455)(1463.07070707071,-9.27272727272727)(836.040404040404,-7.81818181818182)(238.868686868687,-8)(552.383838383838,-8.90909090909091)(522.525252525253,-9.09090909090909)(507.59595959596,-9.09090909090909)(537.454545454546,-9.09090909090909)(492.666666666667,-9.09090909090909)(1478,-9.45454545454546)(641.959595959596,-8.54545454545455)(1343.63636363636,-8)(1045.05050505051,-7.27272727272727)(1119.69696969697,-7.63636363636364)(418.020202020202,-7.63636363636364)(119.434343434343,-8)(836.040404040404,-8)(134.363636363636,-8.18181818181818)(164.222222222222,-8)(806.181818181818,-9.45454545454546)(791.252525252525,-9.27272727272727)(850.969696969697,-9.81818181818182)(283.656565656566,-8.36363636363636)(388.161616161616,-8)(1373.49494949495,-8.18181818181818)(134.363636363636,-8.36363636363636)(671.818181818182,-14.3636363636364)(507.59595959596,-7.27272727272727)(567.313131313131,-7.27272727272727)(582.242424242424,-7.27272727272727)(447.878787878788,-7.45454545454546)(492.666666666667,-7.27272727272727)(1298.84848484848,-7.81818181818182)(597.171717171717,-8.90909090909091)(552.383838383838,-9.09090909090909)(627.030303030303,-8.72727272727273)(627.030303030303,-7.81818181818182)(955.474747474747,-10)(1119.69696969697,-10.1818181818182)(1313.77777777778,-7.81818181818182)(149.292929292929,-8.72727272727273)(1164.48484848485,-7.63636363636364)(1448.14141414141,-9.45454545454546)(1433.21212121212,-9.09090909090909)(1433.21212121212,-8.72727272727273)(1448.14141414141,-8.90909090909091)(403.090909090909,-8.54545454545455)(403.090909090909,-8.18181818181818)(477.737373737374,-7.27272727272727)(238.868686868687,-8.72727272727273)(268.727272727273,-8.18181818181818)(223.939393939394,-7.81818181818182) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_280.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.00008294006,-8.72727272727273)(1478.00016587919,-8.90909090909091)(1478.00049762651,-9.09090909090909)(1478.00041469106,-9.27272727272727)(1478.00049762651,-9.45454545454546)(1478.0002488174,-9.63636363636364)(1478.0002488174,-9.81818181818182)(1478.00008294006,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-9.02272727272727)(1478.00012440663,-9.09090909090909)(1478.00004146911,-9.27272727272727)(1478.00012440663,-9.45454545454546)(1478,-9.54545454545455)(1463.07070707071,-9.59090909090909)(1461.57777777778,-9.63636363636364)(1463.07070707071,-9.72727272727273)(1466.80303030303,-9.81818181818182)(1463.07070707071,-9.84848484848485)(1450.62962962963,-10)(1448.14141414141,-10.030303030303)(1433.21212121212,-10.030303030303)(1418.28282828283,-10.0909090909091)(1403.35353535354,-10.1636363636364)(1399.62121212121,-10.1818181818182)(1388.42424242424,-10.25)(1373.49494949495,-10.3181818181818)(1358.56565656566,-10.2727272727273)(1343.63636363636,-10.25)(1332.43939393939,-10.1818181818182)(1328.70707070707,-10.1666666666667)(1321.24242424242,-10.1818181818182)(1313.77777777778,-10.2121212121212)(1298.84848484848,-10.2954545454545)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2045454545455)(1261.52525252525,-10.1818181818182)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1666666666667)(1216.73737373737,-10.1818181818182)(1209.27272727273,-10.2045454545455)(1194.34343434343,-10.2878787878788)(1179.41414141414,-10.3090909090909)(1164.48484848485,-10.25)(1153.28787878788,-10.1818181818182)(1149.55555555556,-10.1666666666667)(1142.09090909091,-10.1818181818182)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.25)(1104.76767676768,-10.2727272727273)(1089.83838383838,-10.2272727272727)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1056.24747474747,-10.3636363636364)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2727272727273)(1002.75084175084,-10.1818181818182)(1000.26262626263,-10.1666666666667)(985.333333333333,-10.1666666666667)(977.868686868687,-10.1818181818182)(970.40404040404,-10.2045454545455)(955.474747474747,-10.2363636363636)(944.277777777778,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0545454545455)(895.757575757576,-10.0909090909091)(880.828282828283,-10.030303030303)(877.09595959596,-10)(865.89898989899,-9.95454545454546)(852.462626262626,-9.81818181818182)(850.969696969697,-9.8030303030303)(836.040404040404,-9.70454545454546)(824.843434343434,-9.63636363636364)(821.111111111111,-9.61363636363636)(806.181818181818,-9.5)(802.449494949495,-9.45454545454546)(791.252525252525,-9.4)(778.189393939394,-9.27272727272727)(778.811447811448,-9.09090909090909)(776.323232323232,-9.06060606060606)(766.992424242424,-8.90909090909091)(772.590909090909,-8.72727272727273)(766.992424242424,-8.54545454545455)(773.835016835017,-8.36363636363636)(776.323232323232,-8.27272727272727)(778.189393939394,-8.18181818181818)(791.252525252525,-8.05454545454545)(802.449494949495,-8)(806.181818181818,-7.98181818181818)(821.111111111111,-7.89393939393939)(828.575757575758,-7.81818181818182)(836.040404040404,-7.70454545454546)(843.505050505051,-7.63636363636364)(850.969696969697,-7.54545454545455)(858.434343434343,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.37878787878788)(895.757575757576,-7.28787878787879)(910.686868686869,-7.28787878787879)(914.419191919192,-7.27272727272727)(925.616161616162,-7.20454545454546)(940.545454545455,-7.15909090909091)(955.474747474747,-7.10606060606061)(970.40404040404,-7.10606060606061)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.10606060606061)(1030.12121212121,-7.16666666666667)(1045.05050505051,-7.1969696969697)(1059.9797979798,-7.1969696969697)(1074.90909090909,-7.25)(1082.37373737374,-7.27272727272727)(1089.83838383838,-7.29090909090909)(1104.76767676768,-7.36363636363636)(1119.69696969697,-7.42424242424243)(1122.18518518519,-7.45454545454546)(1134.62626262626,-7.53030303030303)(1149.55555555556,-7.61818181818182)(1157.0202020202,-7.63636363636364)(1164.48484848485,-7.65151515151515)(1179.41414141414,-7.68181818181818)(1194.34343434343,-7.65151515151515)(1209.27272727273,-7.68181818181818)(1224.20202020202,-7.65151515151515)(1239.13131313131,-7.65151515151515)(1242.86363636364,-7.63636363636364)(1254.06060606061,-7.59090909090909)(1268.9898989899,-7.59090909090909)(1283.91919191919,-7.59090909090909)(1295.11616161616,-7.63636363636364)(1298.84848484848,-7.65151515151515)(1313.77777777778,-7.70454545454546)(1328.70707070707,-7.75)(1343.63636363636,-7.78787878787879)(1358.56565656566,-7.79545454545455)(1361.05387205387,-7.81818181818182)(1367.89646464646,-8)(1373.49494949495,-8.13636363636364)(1377.22727272727,-8.18181818181818)(1388.42424242424,-8.31818181818182)(1392.15656565657,-8.36363636363636)(1403.35353535354,-8.43181818181818)(1415.79461279461,-8.54545454545455)(1418.28282828283,-8.56818181818182)(1433.21212121212,-8.63636363636364)(1444.40909090909,-8.72727272727273)(1448.14141414141,-8.75757575757576)(1457.47222222222,-8.90909090909091)(1463.07070707071,-9.04545454545455)(1478,-9.02272727272727)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.40909090909091)(1435.07828282828,-9.45454545454546)(1433.21212121212,-9.54545454545455)(1431.34595959596,-9.63636363636364)(1418.28282828283,-9.76363636363636)(1403.35353535354,-9.79545454545455)(1400.86531986532,-9.81818181818182)(1388.42424242424,-9.93181818181818)(1380.9595959596,-10)(1373.49494949495,-10.0454545454545)(1362.29797979798,-10)(1358.56565656566,-9.97727272727273)(1343.63636363636,-9.93181818181818)(1328.70707070707,-9.87272727272727)(1313.77777777778,-9.88636363636364)(1298.84848484848,-9.96969696969697)(1283.91919191919,-9.97727272727273)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.89393939393939)(1239.13131313131,-9.83333333333333)(1224.20202020202,-9.89393939393939)(1209.27272727273,-9.90909090909091)(1196.83164983165,-10)(1194.34343434343,-10.0151515151515)(1179.41414141414,-10.0151515151515)(1175.68181818182,-10)(1164.48484848485,-9.93181818181818)(1149.55555555556,-9.87272727272727)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.93181818181818)(1104.76767676768,-9.97727272727273)(1089.83838383838,-9.95454545454546)(1078.64141414141,-10)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1017.68013468013,-10)(1015.19191919192,-9.97727272727273)(1000.26262626263,-9.89393939393939)(985.333333333333,-9.87272727272727)(970.40404040404,-9.90909090909091)(955.474747474747,-9.94545454545455)(940.545454545455,-9.89393939393939)(925.616161616162,-9.83333333333333)(921.883838383838,-9.81818181818182)(910.686868686869,-9.76363636363636)(895.757575757576,-9.79545454545455)(880.828282828283,-9.70454545454546)(865.89898989899,-9.65454545454546)(864.032828282828,-9.63636363636364)(850.969696969697,-9.53030303030303)(841.638888888889,-9.45454545454546)(836.040404040404,-9.38636363636364)(821.111111111111,-9.28787878787879)(818.622895622896,-9.27272727272727)(811.780303030303,-9.09090909090909)(806.181818181818,-9.02272727272727)(798.717171717172,-8.90909090909091)(804.93771043771,-8.72727272727273)(798.717171717172,-8.54545454545455)(801.70303030303,-8.36363636363636)(806.181818181818,-8.29545454545455)(818.622895622896,-8.18181818181818)(821.111111111111,-8.16666666666667)(836.040404040404,-8.06818181818182)(843.505050505051,-8)(850.969696969697,-7.90909090909091)(856.568181818182,-7.81818181818182)(865.89898989899,-7.72727272727273)(880.828282828283,-7.69090909090909)(888.292929292929,-7.63636363636364)(895.757575757576,-7.58181818181818)(910.686868686869,-7.61363636363636)(925.616161616162,-7.52272727272727)(940.545454545455,-7.48484848484849)(943.03367003367,-7.45454545454546)(955.474747474747,-7.37878787878788)(970.40404040404,-7.37878787878788)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1015.19191919192,-7.37878787878788)(1030.12121212121,-7.43939393939394)(1037.58585858586,-7.45454545454546)(1045.05050505051,-7.47272727272727)(1059.9797979798,-7.47272727272727)(1074.90909090909,-7.54545454545455)(1089.83838383838,-7.59090909090909)(1101.03535353535,-7.63636363636364)(1104.76767676768,-7.65909090909091)(1119.69696969697,-7.75)(1134.62626262626,-7.8030303030303)(1137.11447811448,-7.81818181818182)(1149.55555555556,-7.89393939393939)(1164.48484848485,-7.92424242424242)(1179.41414141414,-7.95454545454546)(1194.34343434343,-7.92424242424242)(1209.27272727273,-7.95454545454546)(1224.20202020202,-7.92424242424242)(1239.13131313131,-7.92424242424242)(1254.06060606061,-7.86363636363636)(1268.9898989899,-7.86363636363636)(1283.91919191919,-7.86363636363636)(1298.84848484848,-7.92424242424242)(1311.28956228956,-8)(1313.77777777778,-8.03030303030303)(1328.70707070707,-8.06818181818182)(1341.14814814815,-8.18181818181818)(1343.63636363636,-8.21212121212121)(1352.96717171717,-8.36363636363636)(1358.56565656566,-8.43181818181818)(1371.00673400673,-8.54545454545455)(1373.49494949495,-8.56818181818182)(1388.42424242424,-8.70909090909091)(1390.91245791246,-8.72727272727273)(1403.35353535354,-8.81818181818182)(1418.28282828283,-8.89393939393939)(1420.14898989899,-8.90909090909091)(1426.99158249158,-9.09090909090909)(1429.4797979798,-9.27272727272727)(1433.21212121212,-9.40909090909091)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (89.5757575757576,-7.95454545454546)(104.505050505051,-7.86363636363636)(108.237373737374,-7.81818181818182)(119.434343434343,-7.72727272727273)(130.631313131313,-7.81818181818182)(134.363636363636,-7.90909090909091)(138.09595959596,-7.81818181818182)(149.292929292929,-7.75)(164.222222222222,-7.79545454545455)(179.151515151515,-7.72727272727273)(194.080808080808,-7.75)(209.010101010101,-7.70454545454546)(223.939393939394,-7.72727272727273)(238.868686868687,-7.70454545454546)(253.79797979798,-7.77272727272727)(268.727272727273,-7.77272727272727)(276.191919191919,-7.81818181818182)(283.656565656566,-7.84090909090909)(291.121212121212,-7.81818181818182)(298.585858585859,-7.77272727272727)(313.515151515152,-7.72727272727273)(324.712121212121,-7.81818181818182)(328.444444444444,-7.84848484848485)(343.373737373737,-7.84848484848485)(358.30303030303,-7.86363636363636)(360.169191919192,-7.81818181818182)(373.232323232323,-7.65909090909091)(388.161616161616,-7.65454545454546)(403.090909090909,-7.69090909090909)(410.555555555556,-7.63636363636364)(415.531986531986,-7.45454545454546)(418.020202020202,-7.42424242424243)(432.949494949495,-7.29545454545455)(440.414141414141,-7.27272727272727)(447.878787878788,-7.25)(462.808080808081,-7.25)(477.737373737374,-7.15909090909091)(492.666666666667,-7.10606060606061)(507.59595959596,-7.10606060606061)(522.525252525253,-7.16666666666667)(537.454545454546,-7.22727272727273)(552.383838383838,-7.16666666666667)(567.313131313131,-7.20454545454546)(582.242424242424,-7.20454545454546)(589.707070707071,-7.27272727272727)(597.171717171717,-7.31818181818182)(612.10101010101,-7.29545454545455)(627.030303030303,-7.36363636363636)(638.227272727273,-7.45454545454546)(641.959595959596,-7.48484848484849)(654.400673400673,-7.63636363636364)(656.888888888889,-7.68181818181818)(664.353535353535,-7.81818181818182)(671.818181818182,-7.95454545454546)(674.306397306397,-8)(675.550505050505,-8.18181818181818)(674.306397306397,-8.36363636363636)(671.818181818182,-8.39393939393939)(656.888888888889,-8.47727272727273)(641.959595959596,-8.47727272727273)(630.762626262626,-8.54545454545455)(627.030303030303,-8.59090909090909)(615.833333333333,-8.72727272727273)(612.10101010101,-8.81818181818182)(608.368686868687,-8.90909090909091)(597.171717171717,-9)(582.242424242424,-9.07272727272727)(567.313131313131,-9.07575757575758)(563.580808080808,-9.09090909090909)(552.383838383838,-9.13636363636364)(537.454545454546,-9.1969696969697)(522.525252525253,-9.25757575757576)(507.59595959596,-9.25757575757576)(492.666666666667,-9.25757575757576)(477.737373737374,-9.22727272727273)(462.808080808081,-9.21818181818182)(447.878787878788,-9.11363636363636)(445.390572390572,-9.09090909090909)(432.949494949495,-8.93939393939394)(430.461279461279,-8.90909090909091)(418.020202020202,-8.79545454545455)(410.555555555556,-8.72727272727273)(410.555555555556,-8.54545454545455)(407.569696969697,-8.36363636363636)(403.090909090909,-8.27272727272727)(388.161616161616,-8.23636363636364)(373.232323232323,-8.29545454545455)(362.035353535354,-8.36363636363636)(358.30303030303,-8.40909090909091)(343.373737373737,-8.45454545454545)(328.444444444444,-8.51515151515152)(324.712121212121,-8.54545454545455)(313.515151515152,-8.68181818181818)(306.050505050505,-8.72727272727273)(298.585858585859,-8.75757575757576)(283.656565656566,-8.84090909090909)(268.727272727273,-8.86363636363636)(264.99494949495,-8.90909090909091)(253.79797979798,-9.04545454545455)(238.868686868687,-9.06060606060606)(236.380471380471,-9.09090909090909)(223.939393939394,-9.20454545454546)(209.010101010101,-9.20454545454546)(194.080808080808,-9.20454545454546)(179.151515151515,-9.13636363636364)(176.6632996633,-9.09090909090909)(164.222222222222,-8.97727272727273)(149.292929292929,-8.97727272727273)(138.09595959596,-8.90909090909091)(134.363636363636,-8.89090909090909)(119.434343434343,-8.79545454545455)(111.969696969697,-8.72727272727273)(106.371212121212,-8.54545454545455)(104.505050505051,-8.45454545454545)(100.772727272727,-8.36363636363636)(89.5757575757576,-8.22727272727273)(87.0875420875421,-8.18181818181818)(87.0875420875421,-8)(89.5757575757576,-7.95454545454546)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.56818181818182)(462.808080808081,-7.54545454545455)(477.737373737374,-7.48484848484849)(480.225589225589,-7.45454545454546)(492.666666666667,-7.37878787878788)(507.59595959596,-7.37878787878788)(522.525252525253,-7.43939393939394)(526.257575757576,-7.45454545454546)(537.454545454546,-7.5)(548.651515151515,-7.45454545454546)(552.383838383838,-7.43939393939394)(556.116161616162,-7.45454545454546)(567.313131313131,-7.52272727272727)(582.242424242424,-7.52272727272727)(597.171717171717,-7.61818181818182)(604.636363636364,-7.63636363636364)(612.10101010101,-7.68181818181818)(619.565656565657,-7.81818181818182)(627.030303030303,-7.95454545454546)(629.518518518518,-8)(627.030303030303,-8.09090909090909)(623.29797979798,-8.18181818181818)(612.10101010101,-8.25)(602.770202020202,-8.36363636363636)(597.171717171717,-8.45454545454545)(589.707070707071,-8.54545454545455)(582.242424242424,-8.68181818181818)(579.754208754209,-8.72727272727273)(567.313131313131,-8.8030303030303)(552.383838383838,-8.86363636363636)(541.186868686869,-8.90909090909091)(537.454545454546,-8.92424242424242)(522.525252525253,-8.98484848484848)(507.59595959596,-8.98484848484848)(492.666666666667,-8.98484848484848)(477.737373737374,-8.92727272727273)(470.272727272727,-8.90909090909091)(462.808080808081,-8.86363636363636)(455.343434343434,-8.72727272727273)(450.367003367003,-8.54545454545455)(447.878787878788,-8.51515151515152)(435.43771043771,-8.36363636363636)(434.815656565657,-8.18181818181818)(434.815656565657,-8)(437.428282828283,-7.81818181818182)(442.280303030303,-7.63636363636364)(447.878787878788,-7.56818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (149.292929292929,-8.5)(160.489898989899,-8.36363636363636)(164.222222222222,-8.27272727272727)(166.710437710438,-8.18181818181818)(179.151515151515,-8.09090909090909)(194.080808080808,-8.10606060606061)(209.010101010101,-8.10606060606061)(223.939393939394,-8.16363636363636)(231.40404040404,-8.18181818181818)(237.002525252525,-8.36363636363636)(227.671717171717,-8.54545454545455)(223.939393939394,-8.59090909090909)(212.742424242424,-8.72727272727273)(209.010101010101,-8.75757575757576)(201.545454545455,-8.72727272727273)(194.080808080808,-8.68181818181818)(179.151515151515,-8.65909090909091)(164.222222222222,-8.56363636363636)(149.292929292929,-8.56818181818182)(146.804713804714,-8.54545454545455)(149.292929292929,-8.5)};

\addplot [fill=white,draw=none,forget plot] coordinates{ (1463.07070707071,-9.18181818181818)(1461.57777777778,-9.27272727272727)(1463.07070707071,-9.31818181818182)(1470.53535353535,-9.27272727272727)(1463.07070707071,-9.18181818181818)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091)(119.434343434343,-8.36363636363636)(791.252525252525,-8.72727272727273)(627.030303030303,-7.63636363636364)(1224.20202020202,-7.81818181818182)(791.252525252525,-9.09090909090909)(1089.83838383838,-10.1818181818182)(806.181818181818,-8.18181818181818)(641.959595959596,-8)(821.111111111111,-8)(940.545454545455,-7.27272727272727)(1030.12121212121,-7.27272727272727)(403.090909090909,-8.36363636363636)(1418.28282828283,-10)(283.656565656566,-8.18181818181818)(268.727272727273,-8)(477.737373737374,-7.45454545454546)(1224.20202020202,-10)(1209.27272727273,-10)(1283.91919191919,-10)(134.363636363636,-8.54545454545455)(134.363636363636,-8.72727272727273)(791.252525252525,-8.36363636363636)(447.878787878788,-8.72727272727273)(955.474747474747,-7.27272727272727)(522.525252525253,-7.27272727272727)(268.727272727273,-8.72727272727273)(776.323232323232,-8.72727272727273)(627.030303030303,-8.54545454545455)(1209.27272727273,-7.81818181818182)(1448.14141414141,-9.81818181818182)(880.828282828283,-9.81818181818182)(253.79797979798,-8.72727272727273)(895.757575757576,-7.45454545454546)(149.292929292929,-8)(462.808080808081,-8.90909090909091)(298.585858585859,-8.36363636363636)(403.090909090909,-8)(388.161616161616,-8.18181818181818)(1074.90909090909,-10.1818181818182)(432.949494949495,-8.72727272727273)(1268.9898989899,-7.81818181818182)(119.434343434343,-8.54545454545455)(1283.91919191919,-7.81818181818182)(149.292929292929,-8.90909090909091)(298.585858585859,-8.18181818181818)(1194.34343434343,-10)(1388.42424242424,-10)(1343.63636363636,-10.1818181818182)(283.656565656566,-8.54545454545455)(1463.07070707071,-9.27272727272727)(836.040404040404,-7.81818181818182)(238.868686868687,-8)(552.383838383838,-8.90909090909091)(522.525252525253,-9.09090909090909)(507.59595959596,-9.09090909090909)(537.454545454546,-9.09090909090909)(492.666666666667,-9.09090909090909)(1478,-9.45454545454546)(641.959595959596,-8.54545454545455)(1343.63636363636,-8)(1045.05050505051,-7.27272727272727)(1119.69696969697,-7.63636363636364)(418.020202020202,-7.63636363636364)(119.434343434343,-8)(836.040404040404,-8)(134.363636363636,-8.18181818181818)(164.222222222222,-8)(806.181818181818,-9.45454545454546)(791.252525252525,-9.27272727272727)(850.969696969697,-9.81818181818182)(283.656565656566,-8.36363636363636)(388.161616161616,-8)(1373.49494949495,-8.18181818181818)(134.363636363636,-8.36363636363636)(671.818181818182,-14.3636363636364)(507.59595959596,-7.27272727272727)(567.313131313131,-7.27272727272727)(582.242424242424,-7.27272727272727)(447.878787878788,-7.45454545454546)(492.666666666667,-7.27272727272727)(1298.84848484848,-7.81818181818182)(597.171717171717,-8.90909090909091)(552.383838383838,-9.09090909090909)(627.030303030303,-8.72727272727273)(627.030303030303,-7.81818181818182)(955.474747474747,-10)(1119.69696969697,-10.1818181818182)(1313.77777777778,-7.81818181818182)(149.292929292929,-8.72727272727273)(1164.48484848485,-7.63636363636364)(1448.14141414141,-9.45454545454546)(1433.21212121212,-9.09090909090909)(1433.21212121212,-8.72727272727273)(1448.14141414141,-8.90909090909091)(403.090909090909,-8.54545454545455)(403.090909090909,-8.18181818181818)(477.737373737374,-7.27272727272727)(238.868686868687,-8.72727272727273)(268.727272727273,-8.18181818181818)(223.939393939394,-7.81818181818182)(656.888888888889,-8.18181818181818)(656.888888888889,-8)(776.323232323232,-8.54545454545455)(283.656565656566,-8)(1328.70707070707,-10.1818181818182)(432.949494949495,-8.54545454545455)(1418.28282828283,-8.54545454545455)(656.888888888889,-8.36363636363636)(1134.62626262626,-10.1818181818182)(418.020202020202,-8.36363636363636)(1179.41414141414,-10)(432.949494949495,-7.45454545454546)(179.151515151515,-8)(179.151515151515,-7.81818181818182)(1373.49494949495,-10.1818181818182)(597.171717171717,-7.27272727272727)(985.333333333333,-10.1818181818182)(238.868686868687,-8.90909090909091)(253.79797979798,-8.90909090909091)(821.111111111111,-9.63636363636364) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_300.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478.00033175469,-9.09090909090909)(1478.00033175469,-9.27272727272727)(1478.00033175469,-9.45454545454546)(1478.00008294006,-9.63636363636364)(1478.00008294006,-9.81818181818182)(1478.00008294006,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1463.07070707071,-9.40909090909091)(1470.53535353535,-9.45454545454546)(1463.07070707071,-9.5)(1459.33838383838,-9.63636363636364)(1458.59191919192,-9.81818181818182)(1448.14141414141,-9.97727272727273)(1433.21212121212,-9.98484848484848)(1430.72390572391,-10)(1418.28282828283,-10.0909090909091)(1403.35353535354,-10.1636363636364)(1399.62121212121,-10.1818181818182)(1388.42424242424,-10.25)(1373.49494949495,-10.3181818181818)(1358.56565656566,-10.2727272727273)(1343.63636363636,-10.25)(1336.17171717172,-10.1818181818182)(1328.70707070707,-10.1363636363636)(1317.5101010101,-10.1818181818182)(1313.77777777778,-10.2045454545455)(1298.84848484848,-10.2727272727273)(1283.91919191919,-10.2878787878788)(1268.9898989899,-10.2045454545455)(1261.52525252525,-10.1818181818182)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1666666666667)(1216.73737373737,-10.1818181818182)(1209.27272727273,-10.2045454545455)(1194.34343434343,-10.2878787878788)(1179.41414141414,-10.3090909090909)(1164.48484848485,-10.25)(1153.28787878788,-10.1818181818182)(1149.55555555556,-10.1666666666667)(1142.09090909091,-10.1818181818182)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.25)(1104.76767676768,-10.2727272727273)(1089.83838383838,-10.2272727272727)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1056.24747474747,-10.3636363636364)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2878787878788)(1000.26262626263,-10.2)(985.333333333333,-10.2363636363636)(970.40404040404,-10.2363636363636)(955.474747474747,-10.2575757575758)(943.03367003367,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0181818181818)(895.757575757576,-10.0545454545455)(884.560606060606,-10)(880.828282828283,-9.98484848484848)(865.89898989899,-9.95454545454546)(852.462626262626,-9.81818181818182)(850.969696969697,-9.8030303030303)(836.040404040404,-9.70454545454546)(824.843434343434,-9.63636363636364)(821.111111111111,-9.61363636363636)(806.181818181818,-9.5)(802.449494949495,-9.45454545454546)(791.252525252525,-9.4)(778.189393939394,-9.27272727272727)(778.811447811448,-9.09090909090909)(776.323232323232,-9.06060606060606)(766.992424242424,-8.90909090909091)(772.590909090909,-8.72727272727273)(766.992424242424,-8.54545454545455)(773.835016835017,-8.36363636363636)(776.323232323232,-8.27272727272727)(778.189393939394,-8.18181818181818)(791.252525252525,-8.05454545454545)(802.449494949495,-8)(806.181818181818,-7.98181818181818)(821.111111111111,-7.89393939393939)(828.575757575758,-7.81818181818182)(836.040404040404,-7.70454545454546)(843.505050505051,-7.63636363636364)(850.969696969697,-7.54545454545455)(858.434343434343,-7.45454545454546)(865.89898989899,-7.4)(880.828282828283,-7.37878787878788)(895.757575757576,-7.31818181818182)(910.686868686869,-7.34848484848485)(925.616161616162,-7.28787878787879)(929.348484848485,-7.27272727272727)(940.545454545455,-7.20454545454546)(955.474747474747,-7.10606060606061)(970.40404040404,-7.10606060606061)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.10606060606061)(1030.12121212121,-7.16666666666667)(1045.05050505051,-7.1969696969697)(1059.9797979798,-7.1969696969697)(1074.90909090909,-7.25)(1082.37373737374,-7.27272727272727)(1089.83838383838,-7.29090909090909)(1104.76767676768,-7.36363636363636)(1119.69696969697,-7.42424242424243)(1122.18518518519,-7.45454545454546)(1134.62626262626,-7.53030303030303)(1149.55555555556,-7.61818181818182)(1157.0202020202,-7.63636363636364)(1164.48484848485,-7.65151515151515)(1179.41414141414,-7.68181818181818)(1194.34343434343,-7.65151515151515)(1209.27272727273,-7.68181818181818)(1224.20202020202,-7.65151515151515)(1239.13131313131,-7.65151515151515)(1242.86363636364,-7.63636363636364)(1254.06060606061,-7.59090909090909)(1268.9898989899,-7.59090909090909)(1283.91919191919,-7.59090909090909)(1295.11616161616,-7.63636363636364)(1298.84848484848,-7.65151515151515)(1313.77777777778,-7.75)(1328.70707070707,-7.79545454545455)(1343.63636363636,-7.79545454545455)(1358.56565656566,-7.76363636363636)(1366.0303030303,-7.81818181818182)(1369.01616161616,-8)(1373.49494949495,-8.13636363636364)(1377.22727272727,-8.18181818181818)(1388.42424242424,-8.27272727272727)(1399.62121212121,-8.36363636363636)(1403.35353535354,-8.37878787878788)(1418.28282828283,-8.47727272727273)(1423.88131313131,-8.54545454545455)(1433.21212121212,-8.65909090909091)(1438.81060606061,-8.72727272727273)(1446.89730639731,-8.90909090909091)(1448.14141414141,-8.93181818181818)(1458.59191919192,-9.09090909090909)(1458.59191919192,-9.27272727272727)(1463.07070707071,-9.40909090909091)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.40909090909091)(1435.07828282828,-9.45454545454546)(1433.21212121212,-9.54545454545455)(1431.34595959596,-9.63636363636364)(1418.28282828283,-9.76363636363636)(1403.35353535354,-9.79545454545455)(1400.86531986532,-9.81818181818182)(1388.42424242424,-9.93181818181818)(1380.9595959596,-10)(1373.49494949495,-10.0454545454545)(1362.29797979798,-10)(1358.56565656566,-9.97727272727273)(1343.63636363636,-9.93181818181818)(1328.70707070707,-9.86363636363636)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.97727272727273)(1291.38383838384,-10)(1283.91919191919,-10.0151515151515)(1281.43097643098,-10)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.89393939393939)(1239.13131313131,-9.83333333333333)(1224.20202020202,-9.89393939393939)(1209.27272727273,-9.90909090909091)(1196.83164983165,-10)(1194.34343434343,-10.0151515151515)(1179.41414141414,-10.0151515151515)(1175.68181818182,-10)(1164.48484848485,-9.93181818181818)(1149.55555555556,-9.87272727272727)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.93181818181818)(1104.76767676768,-9.97727272727273)(1089.83838383838,-9.95454545454546)(1078.64141414141,-10)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0151515151515)(1012.7037037037,-10)(1000.26262626263,-9.92424242424243)(985.333333333333,-9.94545454545455)(970.40404040404,-9.94545454545455)(955.474747474747,-9.98181818181818)(940.545454545455,-9.89393939393939)(925.616161616162,-9.83333333333333)(923.127946127946,-9.81818181818182)(910.686868686869,-9.74242424242424)(895.757575757576,-9.76363636363636)(880.828282828283,-9.69090909090909)(865.89898989899,-9.65454545454546)(864.032828282828,-9.63636363636364)(850.969696969697,-9.53030303030303)(841.638888888889,-9.45454545454546)(836.040404040404,-9.38636363636364)(821.111111111111,-9.28787878787879)(818.622895622896,-9.27272727272727)(811.780303030303,-9.09090909090909)(806.181818181818,-9.02272727272727)(798.717171717172,-8.90909090909091)(804.93771043771,-8.72727272727273)(798.717171717172,-8.54545454545455)(801.70303030303,-8.36363636363636)(806.181818181818,-8.29545454545455)(818.622895622896,-8.18181818181818)(821.111111111111,-8.16666666666667)(836.040404040404,-8.06818181818182)(843.505050505051,-8)(850.969696969697,-7.90909090909091)(856.568181818182,-7.81818181818182)(865.89898989899,-7.72727272727273)(880.828282828283,-7.69090909090909)(888.292929292929,-7.63636363636364)(895.757575757576,-7.59090909090909)(910.686868686869,-7.62121212121212)(925.616161616162,-7.56060606060606)(940.545454545455,-7.52272727272727)(946.143939393939,-7.45454545454546)(955.474747474747,-7.37878787878788)(970.40404040404,-7.37878787878788)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1015.19191919192,-7.37878787878788)(1030.12121212121,-7.43939393939394)(1037.58585858586,-7.45454545454546)(1045.05050505051,-7.47272727272727)(1059.9797979798,-7.47272727272727)(1074.90909090909,-7.54545454545455)(1089.83838383838,-7.59090909090909)(1101.03535353535,-7.63636363636364)(1104.76767676768,-7.65909090909091)(1119.69696969697,-7.75)(1134.62626262626,-7.8030303030303)(1137.11447811448,-7.81818181818182)(1149.55555555556,-7.89393939393939)(1164.48484848485,-7.92424242424242)(1179.41414141414,-7.95454545454546)(1194.34343434343,-7.92424242424242)(1209.27272727273,-7.95454545454546)(1224.20202020202,-7.92424242424242)(1239.13131313131,-7.92424242424242)(1254.06060606061,-7.86363636363636)(1268.9898989899,-7.86363636363636)(1283.91919191919,-7.86363636363636)(1298.84848484848,-7.92424242424242)(1308.17929292929,-8)(1313.77777777778,-8.06818181818182)(1328.70707070707,-8.09090909090909)(1343.63636363636,-8.16363636363636)(1346.12457912458,-8.18181818181818)(1352.96717171717,-8.36363636363636)(1358.56565656566,-8.43181818181818)(1373.49494949495,-8.53030303030303)(1377.22727272727,-8.54545454545455)(1388.42424242424,-8.61363636363636)(1403.35353535354,-8.70454545454545)(1405.2196969697,-8.72727272727273)(1418.28282828283,-8.83333333333333)(1424.50336700337,-8.90909090909091)(1429.4797979798,-9.09090909090909)(1429.4797979798,-9.27272727272727)(1433.21212121212,-9.40909090909091)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (388.161616161616,-7.79545454545455)(403.090909090909,-7.74242424242424)(416.15404040404,-7.63636363636364)(418.020202020202,-7.54545454545455)(419.886363636364,-7.45454545454546)(432.949494949495,-7.29545454545455)(440.414141414141,-7.27272727272727)(447.878787878788,-7.25)(462.808080808081,-7.25)(477.737373737374,-7.15909090909091)(492.666666666667,-7.10606060606061)(507.59595959596,-7.10606060606061)(522.525252525253,-7.16666666666667)(537.454545454546,-7.22727272727273)(552.383838383838,-7.16666666666667)(567.313131313131,-7.20454545454546)(582.242424242424,-7.20454545454546)(589.707070707071,-7.27272727272727)(597.171717171717,-7.31818181818182)(612.10101010101,-7.29545454545455)(625.164141414141,-7.45454545454546)(627.030303030303,-7.48484848484849)(639.47138047138,-7.63636363636364)(641.959595959596,-7.68181818181818)(653.156565656566,-7.81818181818182)(656.888888888889,-7.83636363636364)(671.818181818182,-7.96969696969697)(674.306397306397,-8)(675.550505050505,-8.18181818181818)(674.306397306397,-8.36363636363636)(671.818181818182,-8.39393939393939)(656.888888888889,-8.47727272727273)(641.959595959596,-8.47727272727273)(630.762626262626,-8.54545454545455)(627.030303030303,-8.59090909090909)(615.833333333333,-8.72727272727273)(612.10101010101,-8.81818181818182)(608.368686868687,-8.90909090909091)(597.171717171717,-9)(582.242424242424,-9.07272727272727)(567.313131313131,-9.07575757575758)(563.580808080808,-9.09090909090909)(552.383838383838,-9.13636363636364)(537.454545454546,-9.1969696969697)(522.525252525253,-9.25757575757576)(507.59595959596,-9.25757575757576)(492.666666666667,-9.25757575757576)(477.737373737374,-9.22727272727273)(462.808080808081,-9.21818181818182)(447.878787878788,-9.11363636363636)(445.390572390572,-9.09090909090909)(432.949494949495,-8.93939393939394)(430.461279461279,-8.90909090909091)(418.020202020202,-8.79545454545455)(410.555555555556,-8.72727272727273)(410.555555555556,-8.54545454545455)(410.555555555556,-8.36363636363636)(403.090909090909,-8.25)(391.893939393939,-8.18181818181818)(388.161616161616,-8.09090909090909)(384.429292929293,-8)(384.429292929293,-7.81818181818182)(388.161616161616,-7.79545454545455)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (89.5757575757576,-8.09090909090909)(97.040404040404,-8)(104.505050505051,-7.95454545454546)(115.70202020202,-7.81818181818182)(119.434343434343,-7.77272727272727)(126.89898989899,-7.81818181818182)(134.363636363636,-7.90909090909091)(141.828282828283,-7.81818181818182)(149.292929292929,-7.79545454545455)(156.757575757576,-7.81818181818182)(164.222222222222,-7.83636363636364)(171.686868686869,-7.81818181818182)(179.151515151515,-7.8)(194.080808080808,-7.8)(209.010101010101,-7.8)(223.939393939394,-7.79545454545455)(238.868686868687,-7.75)(253.79797979798,-7.77272727272727)(261.262626262626,-7.81818181818182)(268.727272727273,-7.83636363636364)(283.656565656566,-7.93181818181818)(298.585858585859,-7.96969696969697)(306.050505050505,-8)(313.515151515152,-8.04545454545455)(328.444444444444,-8.04545454545455)(335.909090909091,-8.18181818181818)(335.909090909091,-8.36363636363636)(328.444444444444,-8.45454545454545)(320.979797979798,-8.54545454545455)(313.515151515152,-8.68181818181818)(306.050505050505,-8.72727272727273)(298.585858585859,-8.75757575757576)(283.656565656566,-8.84090909090909)(268.727272727273,-8.86363636363636)(264.99494949495,-8.90909090909091)(253.79797979798,-9.04545454545455)(238.868686868687,-9.06060606060606)(236.380471380471,-9.09090909090909)(223.939393939394,-9.20454545454546)(209.010101010101,-9.20454545454546)(194.080808080808,-9.20454545454546)(179.151515151515,-9.13636363636364)(176.6632996633,-9.09090909090909)(164.222222222222,-8.97727272727273)(149.292929292929,-8.97727272727273)(138.09595959596,-8.90909090909091)(134.363636363636,-8.89090909090909)(119.434343434343,-8.79545454545455)(111.969696969697,-8.72727272727273)(104.505050505051,-8.59090909090909)(102.016835016835,-8.54545454545455)(93.3080808080808,-8.36363636363636)(89.5757575757576,-8.27272727272727)(87.709595959596,-8.18181818181818)(89.5757575757576,-8.09090909090909)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.56818181818182)(462.808080808081,-7.54545454545455)(477.737373737374,-7.48484848484849)(480.225589225589,-7.45454545454546)(492.666666666667,-7.37878787878788)(507.59595959596,-7.37878787878788)(522.525252525253,-7.43939393939394)(526.257575757576,-7.45454545454546)(537.454545454546,-7.5)(548.651515151515,-7.45454545454546)(552.383838383838,-7.43939393939394)(556.116161616162,-7.45454545454546)(567.313131313131,-7.52272727272727)(582.242424242424,-7.52272727272727)(597.171717171717,-7.61818181818182)(604.636363636364,-7.63636363636364)(612.10101010101,-7.68181818181818)(617.699494949495,-7.81818181818182)(627.030303030303,-7.96969696969697)(629.518518518518,-8)(627.030303030303,-8.09090909090909)(623.29797979798,-8.18181818181818)(612.10101010101,-8.25)(602.770202020202,-8.36363636363636)(597.171717171717,-8.45454545454545)(589.707070707071,-8.54545454545455)(582.242424242424,-8.68181818181818)(579.754208754209,-8.72727272727273)(567.313131313131,-8.8030303030303)(552.383838383838,-8.86363636363636)(541.186868686869,-8.90909090909091)(537.454545454546,-8.92424242424242)(522.525252525253,-8.98484848484848)(507.59595959596,-8.98484848484848)(492.666666666667,-8.98484848484848)(477.737373737374,-8.92727272727273)(470.272727272727,-8.90909090909091)(462.808080808081,-8.86363636363636)(455.343434343434,-8.72727272727273)(450.367003367003,-8.54545454545455)(447.878787878788,-8.51515151515152)(438.54797979798,-8.36363636363636)(434.815656565657,-8.18181818181818)(434.815656565657,-8)(434.815656565657,-7.81818181818182)(442.280303030303,-7.63636363636364)(447.878787878788,-7.56818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (149.292929292929,-8.27272727272727)(153.025252525253,-8.18181818181818)(164.222222222222,-8.13636363636364)(179.151515151515,-8.07575757575757)(194.080808080808,-8.07575757575757)(209.010101010101,-8.07575757575757)(223.939393939394,-8.09090909090909)(238.868686868687,-8.15151515151515)(242.60101010101,-8.18181818181818)(253.79797979798,-8.31818181818182)(257.530303030303,-8.36363636363636)(253.79797979798,-8.39393939393939)(238.868686868687,-8.40909090909091)(227.671717171717,-8.54545454545455)(223.939393939394,-8.59090909090909)(212.742424242424,-8.72727272727273)(209.010101010101,-8.75757575757576)(201.545454545455,-8.72727272727273)(194.080808080808,-8.68181818181818)(179.151515151515,-8.65909090909091)(164.222222222222,-8.59090909090909)(149.292929292929,-8.6)(141.828282828283,-8.54545454545455)(147.426767676768,-8.36363636363636)(149.292929292929,-8.27272727272727)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091)(119.434343434343,-8.36363636363636)(791.252525252525,-8.72727272727273)(627.030303030303,-7.63636363636364)(1224.20202020202,-7.81818181818182)(791.252525252525,-9.09090909090909)(1089.83838383838,-10.1818181818182)(806.181818181818,-8.18181818181818)(641.959595959596,-8)(821.111111111111,-8)(940.545454545455,-7.27272727272727)(1030.12121212121,-7.27272727272727)(403.090909090909,-8.36363636363636)(1418.28282828283,-10)(283.656565656566,-8.18181818181818)(268.727272727273,-8)(477.737373737374,-7.45454545454546)(1224.20202020202,-10)(1209.27272727273,-10)(1283.91919191919,-10)(134.363636363636,-8.54545454545455)(134.363636363636,-8.72727272727273)(791.252525252525,-8.36363636363636)(447.878787878788,-8.72727272727273)(955.474747474747,-7.27272727272727)(522.525252525253,-7.27272727272727)(268.727272727273,-8.72727272727273)(776.323232323232,-8.72727272727273)(627.030303030303,-8.54545454545455)(1209.27272727273,-7.81818181818182)(1448.14141414141,-9.81818181818182)(880.828282828283,-9.81818181818182)(253.79797979798,-8.72727272727273)(895.757575757576,-7.45454545454546)(149.292929292929,-8)(462.808080808081,-8.90909090909091)(298.585858585859,-8.36363636363636)(403.090909090909,-8)(388.161616161616,-8.18181818181818)(1074.90909090909,-10.1818181818182)(432.949494949495,-8.72727272727273)(1268.9898989899,-7.81818181818182)(119.434343434343,-8.54545454545455)(1283.91919191919,-7.81818181818182)(149.292929292929,-8.90909090909091)(298.585858585859,-8.18181818181818)(1194.34343434343,-10)(1388.42424242424,-10)(1343.63636363636,-10.1818181818182)(283.656565656566,-8.54545454545455)(1463.07070707071,-9.27272727272727)(836.040404040404,-7.81818181818182)(238.868686868687,-8)(552.383838383838,-8.90909090909091)(522.525252525253,-9.09090909090909)(507.59595959596,-9.09090909090909)(537.454545454546,-9.09090909090909)(492.666666666667,-9.09090909090909)(1478,-9.45454545454546)(641.959595959596,-8.54545454545455)(1343.63636363636,-8)(1045.05050505051,-7.27272727272727)(1119.69696969697,-7.63636363636364)(418.020202020202,-7.63636363636364)(119.434343434343,-8)(836.040404040404,-8)(134.363636363636,-8.18181818181818)(164.222222222222,-8)(806.181818181818,-9.45454545454546)(791.252525252525,-9.27272727272727)(850.969696969697,-9.81818181818182)(283.656565656566,-8.36363636363636)(388.161616161616,-8)(1373.49494949495,-8.18181818181818)(134.363636363636,-8.36363636363636)(671.818181818182,-14.3636363636364)(507.59595959596,-7.27272727272727)(567.313131313131,-7.27272727272727)(582.242424242424,-7.27272727272727)(447.878787878788,-7.45454545454546)(492.666666666667,-7.27272727272727)(1298.84848484848,-7.81818181818182)(597.171717171717,-8.90909090909091)(552.383838383838,-9.09090909090909)(627.030303030303,-8.72727272727273)(627.030303030303,-7.81818181818182)(955.474747474747,-10)(1119.69696969697,-10.1818181818182)(1313.77777777778,-7.81818181818182)(149.292929292929,-8.72727272727273)(1164.48484848485,-7.63636363636364)(1448.14141414141,-9.45454545454546)(1433.21212121212,-9.09090909090909)(1433.21212121212,-8.72727272727273)(1448.14141414141,-8.90909090909091)(403.090909090909,-8.54545454545455)(403.090909090909,-8.18181818181818)(477.737373737374,-7.27272727272727)(238.868686868687,-8.72727272727273)(268.727272727273,-8.18181818181818)(223.939393939394,-7.81818181818182)(656.888888888889,-8.18181818181818)(656.888888888889,-8)(776.323232323232,-8.54545454545455)(283.656565656566,-8)(1328.70707070707,-10.1818181818182)(432.949494949495,-8.54545454545455)(1418.28282828283,-8.54545454545455)(656.888888888889,-8.36363636363636)(1134.62626262626,-10.1818181818182)(418.020202020202,-8.36363636363636)(1179.41414141414,-10)(432.949494949495,-7.45454545454546)(179.151515151515,-8)(179.151515151515,-7.81818181818182)(1373.49494949495,-10.1818181818182)(597.171717171717,-7.27272727272727)(985.333333333333,-10.1818181818182)(238.868686868687,-8.90909090909091)(253.79797979798,-8.90909090909091)(821.111111111111,-9.63636363636364)(403.090909090909,-7.63636363636364)(418.020202020202,-8.18181818181818)(418.020202020202,-8)(641.959595959596,-7.63636363636364)(104.505050505051,-8.18181818181818)(104.505050505051,-8.36363636363636)(104.505050505051,-8)(89.5757575757576,-8.18181818181818)(1358.56565656566,-8)(209.010101010101,-8)(164.222222222222,-7.81818181818182)(1298.84848484848,-10)(1313.77777777778,-10.1818181818182)(970.40404040404,-10)(895.757575757576,-10)(1463.07070707071,-9.09090909090909)(925.616161616162,-7.27272727272727)(1403.35353535354,-8.36363636363636)(1388.42424242424,-8.18181818181818)(1328.70707070707,-7.81818181818182) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_320.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478.00016587919,-9.09090909090909)(1478.00016587919,-9.27272727272727)(1478.00016587919,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1448.14141414141,-8.93181818181818)(1456.85016835017,-9.09090909090909)(1456.85016835017,-9.27272727272727)(1461.8265993266,-9.45454545454546)(1456.85016835017,-9.63636363636364)(1455.60606060606,-9.81818181818182)(1448.14141414141,-9.93181818181818)(1433.21212121212,-9.95454545454546)(1422.01515151515,-10)(1418.28282828283,-10.0227272727273)(1403.35353535354,-10.1136363636364)(1392.15656565657,-10.1818181818182)(1388.42424242424,-10.2045454545455)(1373.49494949495,-10.3181818181818)(1358.56565656566,-10.2727272727273)(1343.63636363636,-10.25)(1336.17171717172,-10.1818181818182)(1328.70707070707,-10.1363636363636)(1321.24242424242,-10.1818181818182)(1313.77777777778,-10.25)(1298.84848484848,-10.3090909090909)(1283.91919191919,-10.3181818181818)(1268.9898989899,-10.2045454545455)(1261.52525252525,-10.1818181818182)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1666666666667)(1209.27272727273,-10.1666666666667)(1206.78451178451,-10.1818181818182)(1194.34343434343,-10.2575757575758)(1179.41414141414,-10.25)(1164.48484848485,-10.2121212121212)(1160.75252525253,-10.1818181818182)(1149.55555555556,-10.1363636363636)(1138.35858585859,-10.1818181818182)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.25)(1104.76767676768,-10.2727272727273)(1089.83838383838,-10.2272727272727)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1056.24747474747,-10.3636363636364)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2878787878788)(1000.26262626263,-10.2)(985.333333333333,-10.2363636363636)(970.40404040404,-10.2363636363636)(955.474747474747,-10.2575757575758)(943.03367003367,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0454545454545)(895.757575757576,-10.0757575757576)(880.828282828283,-10.0227272727273)(877.09595959596,-10)(865.89898989899,-9.95454545454546)(852.462626262626,-9.81818181818182)(850.969696969697,-9.8030303030303)(836.040404040404,-9.70454545454546)(824.843434343434,-9.63636363636364)(821.111111111111,-9.61363636363636)(808.04797979798,-9.45454545454546)(806.181818181818,-9.43939393939394)(791.252525252525,-9.37878787878788)(778.189393939394,-9.27272727272727)(778.189393939394,-9.09090909090909)(776.323232323232,-9.04545454545455)(770.724747474747,-8.90909090909091)(776.323232323232,-8.84090909090909)(782.543771043771,-8.72727272727273)(776.323232323232,-8.57575757575757)(774.457070707071,-8.54545454545455)(776.323232323232,-8.45454545454545)(777.56734006734,-8.36363636363636)(778.189393939394,-8.18181818181818)(791.252525252525,-8.05454545454545)(802.449494949495,-8)(806.181818181818,-7.98181818181818)(821.111111111111,-7.89393939393939)(830.441919191919,-7.81818181818182)(836.040404040404,-7.75)(850.969696969697,-7.65151515151515)(852.462626262626,-7.63636363636364)(863.410774410775,-7.45454545454546)(865.89898989899,-7.43181818181818)(880.828282828283,-7.37878787878788)(895.757575757576,-7.31818181818182)(910.686868686869,-7.34848484848485)(925.616161616162,-7.28787878787879)(929.348484848485,-7.27272727272727)(940.545454545455,-7.20454545454546)(955.474747474747,-7.10606060606061)(970.40404040404,-7.10606060606061)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.10606060606061)(1030.12121212121,-7.16666666666667)(1045.05050505051,-7.22727272727273)(1059.9797979798,-7.22727272727273)(1071.17676767677,-7.27272727272727)(1074.90909090909,-7.28787878787879)(1089.83838383838,-7.29090909090909)(1104.76767676768,-7.36363636363636)(1119.69696969697,-7.42424242424243)(1122.18518518519,-7.45454545454546)(1134.62626262626,-7.53030303030303)(1149.55555555556,-7.59090909090909)(1164.48484848485,-7.61818181818182)(1179.41414141414,-7.61818181818182)(1194.34343434343,-7.61818181818182)(1201.80808080808,-7.63636363636364)(1209.27272727273,-7.65151515151515)(1224.20202020202,-7.65151515151515)(1239.13131313131,-7.65151515151515)(1242.86363636364,-7.63636363636364)(1254.06060606061,-7.59090909090909)(1268.9898989899,-7.59090909090909)(1283.91919191919,-7.59090909090909)(1295.11616161616,-7.63636363636364)(1298.84848484848,-7.65151515151515)(1313.77777777778,-7.75)(1328.70707070707,-7.79545454545455)(1343.63636363636,-7.79545454545455)(1358.56565656566,-7.76363636363636)(1366.0303030303,-7.81818181818182)(1369.01616161616,-8)(1373.49494949495,-8.13636363636364)(1377.22727272727,-8.18181818181818)(1388.42424242424,-8.27272727272727)(1399.62121212121,-8.36363636363636)(1403.35353535354,-8.37878787878788)(1418.28282828283,-8.47727272727273)(1423.88131313131,-8.54545454545455)(1433.21212121212,-8.65909090909091)(1438.81060606061,-8.72727272727273)(1446.89730639731,-8.90909090909091)(1448.14141414141,-8.93181818181818)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.40909090909091)(1435.07828282828,-9.45454545454546)(1433.21212121212,-9.5)(1427.61363636364,-9.63636363636364)(1418.28282828283,-9.72727272727273)(1403.35353535354,-9.75)(1397.75505050505,-9.81818181818182)(1388.42424242424,-9.90909090909091)(1379.09343434343,-10)(1373.49494949495,-10.0454545454545)(1362.29797979798,-10)(1358.56565656566,-9.97727272727273)(1343.63636363636,-9.93181818181818)(1328.70707070707,-9.86363636363636)(1313.77777777778,-9.93181818181818)(1302.58080808081,-10)(1298.84848484848,-10.0151515151515)(1283.91919191919,-10.0454545454545)(1278.32070707071,-10)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.89393939393939)(1239.13131313131,-9.83333333333333)(1224.20202020202,-9.89393939393939)(1209.27272727273,-9.89393939393939)(1194.34343434343,-9.98181818181818)(1179.41414141414,-9.93181818181818)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.83636363636364)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.93181818181818)(1104.76767676768,-9.97727272727273)(1089.83838383838,-9.95454545454546)(1078.64141414141,-10)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0151515151515)(1012.7037037037,-10)(1000.26262626263,-9.92424242424243)(985.333333333333,-9.94545454545455)(970.40404040404,-9.94545454545455)(955.474747474747,-9.98181818181818)(940.545454545455,-9.89393939393939)(925.616161616162,-9.83333333333333)(921.883838383838,-9.81818181818182)(910.686868686869,-9.77272727272727)(895.757575757576,-9.8)(880.828282828283,-9.72727272727273)(865.89898989899,-9.65454545454546)(864.032828282828,-9.63636363636364)(850.969696969697,-9.53030303030303)(841.638888888889,-9.45454545454546)(836.040404040404,-9.38636363636364)(821.111111111111,-9.28787878787879)(819.244949494949,-9.27272727272727)(811.780303030303,-9.09090909090909)(806.181818181818,-9.02272727272727)(796.85101010101,-8.90909090909091)(804.93771043771,-8.72727272727273)(798.717171717172,-8.54545454545455)(801.70303030303,-8.36363636363636)(806.181818181818,-8.29545454545455)(818.622895622896,-8.18181818181818)(821.111111111111,-8.16666666666667)(836.040404040404,-8.06818181818182)(847.237373737374,-8)(850.969696969697,-7.97727272727273)(864.032828282828,-7.81818181818182)(865.89898989899,-7.8)(880.828282828283,-7.72727272727273)(890.159090909091,-7.63636363636364)(895.757575757576,-7.59090909090909)(910.686868686869,-7.62121212121212)(925.616161616162,-7.56060606060606)(940.545454545455,-7.52272727272727)(946.143939393939,-7.45454545454546)(955.474747474747,-7.37878787878788)(970.40404040404,-7.37878787878788)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1015.19191919192,-7.37878787878788)(1030.12121212121,-7.43939393939394)(1033.85353535354,-7.45454545454546)(1045.05050505051,-7.5)(1059.9797979798,-7.5)(1074.90909090909,-7.56060606060606)(1089.83838383838,-7.59090909090909)(1101.03535353535,-7.63636363636364)(1104.76767676768,-7.65909090909091)(1119.69696969697,-7.75)(1134.62626262626,-7.8030303030303)(1138.35858585859,-7.81818181818182)(1149.55555555556,-7.86363636363636)(1164.48484848485,-7.89393939393939)(1179.41414141414,-7.89393939393939)(1194.34343434343,-7.89393939393939)(1209.27272727273,-7.92424242424242)(1224.20202020202,-7.92424242424242)(1239.13131313131,-7.92424242424242)(1254.06060606061,-7.86363636363636)(1268.9898989899,-7.86363636363636)(1283.91919191919,-7.86363636363636)(1298.84848484848,-7.92424242424242)(1308.17929292929,-8)(1313.77777777778,-8.06818181818182)(1328.70707070707,-8.09090909090909)(1343.63636363636,-8.16363636363636)(1346.12457912458,-8.18181818181818)(1352.96717171717,-8.36363636363636)(1358.56565656566,-8.43181818181818)(1373.49494949495,-8.53030303030303)(1377.22727272727,-8.54545454545455)(1388.42424242424,-8.61363636363636)(1403.35353535354,-8.70454545454545)(1405.2196969697,-8.72727272727273)(1418.28282828283,-8.83333333333333)(1424.50336700337,-8.90909090909091)(1429.4797979798,-9.09090909090909)(1429.4797979798,-9.27272727272727)(1433.21212121212,-9.40909090909091)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (403.090909090909,-7.77272727272727)(416.527272727273,-7.63636363636364)(418.020202020202,-7.54545454545455)(419.886363636364,-7.45454545454546)(432.949494949495,-7.29545454545455)(440.414141414141,-7.27272727272727)(447.878787878788,-7.25)(462.808080808081,-7.25)(477.737373737374,-7.15909090909091)(492.666666666667,-7.10606060606061)(507.59595959596,-7.10606060606061)(522.525252525253,-7.16666666666667)(537.454545454546,-7.22727272727273)(552.383838383838,-7.16666666666667)(567.313131313131,-7.20454545454546)(582.242424242424,-7.20454545454546)(589.707070707071,-7.27272727272727)(597.171717171717,-7.31818181818182)(612.10101010101,-7.34090909090909)(621.431818181818,-7.45454545454546)(627.030303030303,-7.54545454545455)(634.494949494949,-7.63636363636364)(641.959595959596,-7.72727272727273)(653.156565656566,-7.81818181818182)(656.888888888889,-7.83636363636364)(671.818181818182,-7.96969696969697)(674.306397306397,-8)(675.550505050505,-8.18181818181818)(674.306397306397,-8.36363636363636)(671.818181818182,-8.39393939393939)(656.888888888889,-8.47727272727273)(641.959595959596,-8.47727272727273)(630.762626262626,-8.54545454545455)(627.030303030303,-8.57575757575757)(614.589225589226,-8.72727272727273)(612.10101010101,-8.81818181818182)(608.368686868687,-8.90909090909091)(597.171717171717,-8.97727272727273)(582.242424242424,-9.07575757575758)(567.313131313131,-9.07575757575758)(563.580808080808,-9.09090909090909)(552.383838383838,-9.13636363636364)(537.454545454546,-9.1969696969697)(522.525252525253,-9.25757575757576)(507.59595959596,-9.25757575757576)(492.666666666667,-9.25757575757576)(477.737373737374,-9.22727272727273)(462.808080808081,-9.20454545454546)(453.477272727273,-9.09090909090909)(447.878787878788,-9)(440.414141414141,-8.90909090909091)(432.949494949495,-8.85454545454546)(418.020202020202,-8.75)(414.287878787879,-8.72727272727273)(408.689393939394,-8.54545454545455)(409.311447811448,-8.36363636363636)(403.090909090909,-8.25)(391.893939393939,-8.18181818181818)(391.893939393939,-8)(391.893939393939,-7.81818181818182)(403.090909090909,-7.77272727272727)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (432.949494949495,-8.09090909090909)(434.815656565657,-8)(434.815656565657,-7.81818181818182)(442.280303030303,-7.63636363636364)(447.878787878788,-7.56818181818182)(462.808080808081,-7.54545454545455)(477.737373737374,-7.48484848484849)(480.225589225589,-7.45454545454546)(492.666666666667,-7.37878787878788)(507.59595959596,-7.37878787878788)(522.525252525253,-7.43939393939394)(526.257575757576,-7.45454545454546)(537.454545454546,-7.5)(548.651515151515,-7.45454545454546)(552.383838383838,-7.43939393939394)(556.116161616162,-7.45454545454546)(567.313131313131,-7.52272727272727)(582.242424242424,-7.52272727272727)(597.171717171717,-7.61818181818182)(600.90404040404,-7.63636363636364)(612.10101010101,-7.72727272727273)(617.699494949495,-7.81818181818182)(627.030303030303,-7.96969696969697)(629.518518518518,-8)(627.030303030303,-8.09090909090909)(623.29797979798,-8.18181818181818)(612.10101010101,-8.25)(602.770202020202,-8.36363636363636)(597.171717171717,-8.5)(594.683501683502,-8.54545454545455)(583.735353535354,-8.72727272727273)(582.242424242424,-8.75)(567.313131313131,-8.8030303030303)(552.383838383838,-8.86363636363636)(541.186868686869,-8.90909090909091)(537.454545454546,-8.92424242424242)(522.525252525253,-8.98484848484848)(507.59595959596,-8.98484848484848)(492.666666666667,-8.98484848484848)(477.737373737374,-8.92727272727273)(474.005050505051,-8.90909090909091)(462.808080808081,-8.77272727272727)(460.941919191919,-8.72727272727273)(447.878787878788,-8.56818181818182)(444.146464646465,-8.54545454545455)(434.815656565657,-8.36363636363636)(432.949494949495,-8.27272727272727)(431.083333333333,-8.18181818181818)(432.949494949495,-8.09090909090909)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (89.5757575757576,-8.09090909090909)(97.040404040404,-8)(104.505050505051,-7.95454545454546)(115.70202020202,-7.81818181818182)(119.434343434343,-7.77272727272727)(126.89898989899,-7.81818181818182)(134.363636363636,-7.90909090909091)(141.828282828283,-7.81818181818182)(149.292929292929,-7.79545454545455)(156.757575757576,-7.81818181818182)(164.222222222222,-7.83636363636364)(167.954545454545,-7.81818181818182)(179.151515151515,-7.77272727272727)(194.080808080808,-7.77272727272727)(209.010101010101,-7.77272727272727)(220.207070707071,-7.81818181818182)(223.939393939394,-7.83333333333333)(238.868686868687,-7.84090909090909)(253.79797979798,-7.93181818181818)(268.727272727273,-7.93181818181818)(279.924242424242,-8)(283.656565656566,-8.02272727272727)(298.585858585859,-8.13636363636364)(300.45202020202,-8.18181818181818)(307.916666666667,-8.36363636363636)(298.585858585859,-8.51515151515152)(296.719696969697,-8.54545454545455)(286.144781144781,-8.72727272727273)(283.656565656566,-8.75)(268.727272727273,-8.77272727272727)(261.262626262626,-8.90909090909091)(253.79797979798,-9.04545454545455)(238.868686868687,-9.06818181818182)(236.380471380471,-9.09090909090909)(223.939393939394,-9.20454545454546)(209.010101010101,-9.20454545454546)(194.080808080808,-9.20454545454546)(181.639730639731,-9.09090909090909)(179.151515151515,-9.06818181818182)(164.222222222222,-8.93181818181818)(156.757575757576,-8.90909090909091)(149.292929292929,-8.89090909090909)(134.363636363636,-8.81818181818182)(121.922558922559,-8.72727272727273)(119.434343434343,-8.70454545454545)(106.371212121212,-8.54545454545455)(104.505050505051,-8.5)(93.3080808080808,-8.36363636363636)(89.5757575757576,-8.27272727272727)(87.709595959596,-8.18181818181818)(89.5757575757576,-8.09090909090909)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (149.292929292929,-8.27272727272727)(153.025252525253,-8.18181818181818)(164.222222222222,-8.13636363636364)(179.151515151515,-8.04545454545455)(194.080808080808,-8.04545454545455)(209.010101010101,-8.04545454545455)(223.939393939394,-8.10606060606061)(236.380471380471,-8.18181818181818)(237.375757575758,-8.36363636363636)(235.136363636364,-8.54545454545455)(223.939393939394,-8.68181818181818)(220.207070707071,-8.72727272727273)(209.010101010101,-8.81818181818182)(197.813131313131,-8.72727272727273)(194.080808080808,-8.68181818181818)(179.151515151515,-8.65909090909091)(164.222222222222,-8.59090909090909)(149.292929292929,-8.59090909090909)(143.694444444444,-8.54545454545455)(147.426767676768,-8.36363636363636)(149.292929292929,-8.27272727272727)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091)(119.434343434343,-8.36363636363636)(791.252525252525,-8.72727272727273)(627.030303030303,-7.63636363636364)(1224.20202020202,-7.81818181818182)(791.252525252525,-9.09090909090909)(1089.83838383838,-10.1818181818182)(806.181818181818,-8.18181818181818)(641.959595959596,-8)(821.111111111111,-8)(940.545454545455,-7.27272727272727)(1030.12121212121,-7.27272727272727)(403.090909090909,-8.36363636363636)(1418.28282828283,-10)(283.656565656566,-8.18181818181818)(268.727272727273,-8)(477.737373737374,-7.45454545454546)(1224.20202020202,-10)(1209.27272727273,-10)(1283.91919191919,-10)(134.363636363636,-8.54545454545455)(134.363636363636,-8.72727272727273)(791.252525252525,-8.36363636363636)(447.878787878788,-8.72727272727273)(955.474747474747,-7.27272727272727)(522.525252525253,-7.27272727272727)(268.727272727273,-8.72727272727273)(776.323232323232,-8.72727272727273)(627.030303030303,-8.54545454545455)(1209.27272727273,-7.81818181818182)(1448.14141414141,-9.81818181818182)(880.828282828283,-9.81818181818182)(253.79797979798,-8.72727272727273)(895.757575757576,-7.45454545454546)(149.292929292929,-8)(462.808080808081,-8.90909090909091)(298.585858585859,-8.36363636363636)(403.090909090909,-8)(388.161616161616,-8.18181818181818)(1074.90909090909,-10.1818181818182)(432.949494949495,-8.72727272727273)(1268.9898989899,-7.81818181818182)(119.434343434343,-8.54545454545455)(1283.91919191919,-7.81818181818182)(149.292929292929,-8.90909090909091)(298.585858585859,-8.18181818181818)(1194.34343434343,-10)(1388.42424242424,-10)(1343.63636363636,-10.1818181818182)(283.656565656566,-8.54545454545455)(1463.07070707071,-9.27272727272727)(836.040404040404,-7.81818181818182)(238.868686868687,-8)(552.383838383838,-8.90909090909091)(522.525252525253,-9.09090909090909)(507.59595959596,-9.09090909090909)(537.454545454546,-9.09090909090909)(492.666666666667,-9.09090909090909)(1478,-9.45454545454546)(641.959595959596,-8.54545454545455)(1343.63636363636,-8)(1045.05050505051,-7.27272727272727)(1119.69696969697,-7.63636363636364)(418.020202020202,-7.63636363636364)(119.434343434343,-8)(836.040404040404,-8)(134.363636363636,-8.18181818181818)(164.222222222222,-8)(806.181818181818,-9.45454545454546)(791.252525252525,-9.27272727272727)(850.969696969697,-9.81818181818182)(283.656565656566,-8.36363636363636)(388.161616161616,-8)(1373.49494949495,-8.18181818181818)(134.363636363636,-8.36363636363636)(671.818181818182,-14.3636363636364)(507.59595959596,-7.27272727272727)(567.313131313131,-7.27272727272727)(582.242424242424,-7.27272727272727)(447.878787878788,-7.45454545454546)(492.666666666667,-7.27272727272727)(1298.84848484848,-7.81818181818182)(597.171717171717,-8.90909090909091)(552.383838383838,-9.09090909090909)(627.030303030303,-8.72727272727273)(627.030303030303,-7.81818181818182)(955.474747474747,-10)(1119.69696969697,-10.1818181818182)(1313.77777777778,-7.81818181818182)(149.292929292929,-8.72727272727273)(1164.48484848485,-7.63636363636364)(1448.14141414141,-9.45454545454546)(1433.21212121212,-9.09090909090909)(1433.21212121212,-8.72727272727273)(1448.14141414141,-8.90909090909091)(403.090909090909,-8.54545454545455)(403.090909090909,-8.18181818181818)(477.737373737374,-7.27272727272727)(238.868686868687,-8.72727272727273)(268.727272727273,-8.18181818181818)(223.939393939394,-7.81818181818182)(656.888888888889,-8.18181818181818)(656.888888888889,-8)(776.323232323232,-8.54545454545455)(283.656565656566,-8)(1328.70707070707,-10.1818181818182)(432.949494949495,-8.54545454545455)(1418.28282828283,-8.54545454545455)(656.888888888889,-8.36363636363636)(1134.62626262626,-10.1818181818182)(418.020202020202,-8.36363636363636)(1179.41414141414,-10)(432.949494949495,-7.45454545454546)(179.151515151515,-8)(179.151515151515,-7.81818181818182)(1373.49494949495,-10.1818181818182)(597.171717171717,-7.27272727272727)(985.333333333333,-10.1818181818182)(238.868686868687,-8.90909090909091)(253.79797979798,-8.90909090909091)(821.111111111111,-9.63636363636364)(403.090909090909,-7.63636363636364)(418.020202020202,-8.18181818181818)(418.020202020202,-8)(641.959595959596,-7.63636363636364)(104.505050505051,-8.18181818181818)(104.505050505051,-8.36363636363636)(104.505050505051,-8)(89.5757575757576,-8.18181818181818)(1358.56565656566,-8)(209.010101010101,-8)(164.222222222222,-7.81818181818182)(1298.84848484848,-10)(1313.77777777778,-10.1818181818182)(970.40404040404,-10)(895.757575757576,-10)(1463.07070707071,-9.09090909090909)(925.616161616162,-7.27272727272727)(1403.35353535354,-8.36363636363636)(1388.42424242424,-8.18181818181818)(1328.70707070707,-7.81818181818182)(612.10101010101,-8.90909090909091)(447.878787878788,-8.90909090909091)(1059.9797979798,-7.27272727272727)(1418.28282828283,-9.81818181818182)(1194.34343434343,-7.81818181818182)(432.949494949495,-8.36363636363636)(627.030303030303,-7.45454545454546)(283.656565656566,-8.72727272727273)(119.434343434343,-8.72727272727273)(597.171717171717,-8.72727272727273)(238.868686868687,-7.81818181818182)(194.080808080808,-8)(776.323232323232,-9.09090909090909)(865.89898989899,-7.81818181818182)(761.393939393939,-8.72727272727273)(1298.84848484848,-10.1818181818182)(1164.48484848485,-10)(313.515151515152,-8.36363636363636)(253.79797979798,-8.18181818181818)(223.939393939394,-8.72727272727273) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_340.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478.00016587919,-9.09090909090909)(1478.00016587919,-9.27272727272727)(1478.00016587919,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1448.14141414141,-8.93181818181818)(1456.85016835017,-9.09090909090909)(1456.85016835017,-9.27272727272727)(1461.8265993266,-9.45454545454546)(1456.85016835017,-9.63636363636364)(1453.7398989899,-9.81818181818182)(1448.14141414141,-9.88636363636364)(1433.21212121212,-9.92424242424243)(1418.28282828283,-9.98484848484848)(1415.79461279461,-10)(1403.35353535354,-10.1136363636364)(1392.15656565657,-10.1818181818182)(1388.42424242424,-10.2045454545455)(1373.49494949495,-10.3181818181818)(1358.56565656566,-10.2727272727273)(1343.63636363636,-10.25)(1336.17171717172,-10.1818181818182)(1328.70707070707,-10.1363636363636)(1321.24242424242,-10.1818181818182)(1313.77777777778,-10.25)(1298.84848484848,-10.2727272727273)(1283.91919191919,-10.2878787878788)(1270.85606060606,-10.1818181818182)(1268.9898989899,-10.1666666666667)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1666666666667)(1209.27272727273,-10.1666666666667)(1205.5404040404,-10.1818181818182)(1194.34343434343,-10.2272727272727)(1183.14646464646,-10.1818181818182)(1179.41414141414,-10.1666666666667)(1164.48484848485,-10.1666666666667)(1149.55555555556,-10.1363636363636)(1142.09090909091,-10.1818181818182)(1134.62626262626,-10.25)(1119.69696969697,-10.25)(1104.76767676768,-10.2727272727273)(1089.83838383838,-10.2272727272727)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1056.24747474747,-10.3636363636364)(1045.05050505051,-10.4090909090909)(1033.85353535354,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2878787878788)(1000.26262626263,-10.2)(985.333333333333,-10.2)(970.40404040404,-10.2)(955.474747474747,-10.2272727272727)(944.277777777778,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0454545454545)(895.757575757576,-10.0757575757576)(880.828282828283,-10.0227272727273)(877.09595959596,-10)(865.89898989899,-9.95454545454546)(852.462626262626,-9.81818181818182)(850.969696969697,-9.8030303030303)(836.040404040404,-9.70454545454546)(824.843434343434,-9.63636363636364)(821.111111111111,-9.61363636363636)(808.04797979798,-9.45454545454546)(806.181818181818,-9.43939393939394)(791.252525252525,-9.37878787878788)(778.189393939394,-9.27272727272727)(778.189393939394,-9.09090909090909)(776.323232323232,-9.04545454545455)(770.724747474747,-8.90909090909091)(776.323232323232,-8.84090909090909)(782.543771043771,-8.72727272727273)(776.323232323232,-8.57575757575757)(774.457070707071,-8.54545454545455)(776.323232323232,-8.5)(780.055555555556,-8.36363636363636)(781.921717171717,-8.18181818181818)(791.252525252525,-8.09090909090909)(806.181818181818,-8.01515151515152)(808.04797979798,-8)(821.111111111111,-7.89393939393939)(830.441919191919,-7.81818181818182)(836.040404040404,-7.75)(850.969696969697,-7.65151515151515)(852.462626262626,-7.63636363636364)(863.410774410775,-7.45454545454546)(865.89898989899,-7.43181818181818)(880.828282828283,-7.37878787878788)(895.757575757576,-7.31818181818182)(910.686868686869,-7.34848484848485)(925.616161616162,-7.28787878787879)(929.348484848485,-7.27272727272727)(940.545454545455,-7.20454545454546)(955.474747474747,-7.10606060606061)(970.40404040404,-7.10606060606061)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.10606060606061)(1030.12121212121,-7.16666666666667)(1045.05050505051,-7.22727272727273)(1059.9797979798,-7.22727272727273)(1071.17676767677,-7.27272727272727)(1074.90909090909,-7.28787878787879)(1089.83838383838,-7.28787878787879)(1104.76767676768,-7.34848484848485)(1119.69696969697,-7.38636363636364)(1125.29545454545,-7.45454545454546)(1134.62626262626,-7.53030303030303)(1149.55555555556,-7.59090909090909)(1164.48484848485,-7.61818181818182)(1179.41414141414,-7.61818181818182)(1194.34343434343,-7.61818181818182)(1201.80808080808,-7.63636363636364)(1209.27272727273,-7.65151515151515)(1224.20202020202,-7.65151515151515)(1239.13131313131,-7.65151515151515)(1242.86363636364,-7.63636363636364)(1254.06060606061,-7.59090909090909)(1268.9898989899,-7.59090909090909)(1283.91919191919,-7.59090909090909)(1295.11616161616,-7.63636363636364)(1298.84848484848,-7.65151515151515)(1313.77777777778,-7.75)(1328.70707070707,-7.79545454545455)(1343.63636363636,-7.79545454545455)(1358.56565656566,-7.79545454545455)(1361.05387205387,-7.81818181818182)(1366.0303030303,-8)(1372.25084175084,-8.18181818181818)(1373.49494949495,-8.20454545454546)(1388.42424242424,-8.29545454545455)(1399.62121212121,-8.36363636363636)(1403.35353535354,-8.37878787878788)(1418.28282828283,-8.47727272727273)(1423.88131313131,-8.54545454545455)(1433.21212121212,-8.65909090909091)(1438.81060606061,-8.72727272727273)(1446.89730639731,-8.90909090909091)(1448.14141414141,-8.93181818181818)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.40909090909091)(1435.07828282828,-9.45454545454546)(1433.21212121212,-9.5)(1427.61363636364,-9.63636363636364)(1418.28282828283,-9.71212121212121)(1403.35353535354,-9.75)(1397.75505050505,-9.81818181818182)(1388.42424242424,-9.90909090909091)(1379.09343434343,-10)(1373.49494949495,-10.0454545454545)(1362.29797979798,-10)(1358.56565656566,-9.97727272727273)(1343.63636363636,-9.93181818181818)(1328.70707070707,-9.86363636363636)(1313.77777777778,-9.93181818181818)(1298.84848484848,-9.97727272727273)(1291.38383838384,-10)(1283.91919191919,-10.0151515151515)(1282.05303030303,-10)(1268.9898989899,-9.89393939393939)(1254.06060606061,-9.89393939393939)(1239.13131313131,-9.83333333333333)(1224.20202020202,-9.89393939393939)(1209.27272727273,-9.89393939393939)(1194.34343434343,-9.95454545454546)(1179.41414141414,-9.89393939393939)(1164.48484848485,-9.89393939393939)(1149.55555555556,-9.86363636363636)(1134.62626262626,-9.93181818181818)(1119.69696969697,-9.93181818181818)(1104.76767676768,-9.97727272727273)(1089.83838383838,-9.95454545454546)(1078.64141414141,-10)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.1363636363636)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0151515151515)(1012.7037037037,-10)(1000.26262626263,-9.92424242424243)(985.333333333333,-9.92424242424243)(970.40404040404,-9.92424242424243)(955.474747474747,-9.95454545454546)(940.545454545455,-9.89393939393939)(925.616161616162,-9.83333333333333)(921.883838383838,-9.81818181818182)(910.686868686869,-9.77272727272727)(895.757575757576,-9.8)(880.828282828283,-9.72727272727273)(865.89898989899,-9.65454545454546)(864.032828282828,-9.63636363636364)(850.969696969697,-9.53030303030303)(841.638888888889,-9.45454545454546)(836.040404040404,-9.38636363636364)(821.111111111111,-9.28787878787879)(819.244949494949,-9.27272727272727)(811.780303030303,-9.09090909090909)(806.181818181818,-9.02272727272727)(796.85101010101,-8.90909090909091)(804.93771043771,-8.72727272727273)(798.717171717172,-8.54545454545455)(804.688888888889,-8.36363636363636)(806.181818181818,-8.34090909090909)(819.244949494949,-8.18181818181818)(821.111111111111,-8.16666666666667)(836.040404040404,-8.06818181818182)(847.237373737374,-8)(850.969696969697,-7.97727272727273)(864.032828282828,-7.81818181818182)(865.89898989899,-7.8)(880.828282828283,-7.72727272727273)(890.159090909091,-7.63636363636364)(895.757575757576,-7.59090909090909)(910.686868686869,-7.62121212121212)(925.616161616162,-7.56060606060606)(940.545454545455,-7.52272727272727)(946.143939393939,-7.45454545454546)(955.474747474747,-7.37878787878788)(970.40404040404,-7.37878787878788)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1015.19191919192,-7.37878787878788)(1030.12121212121,-7.43939393939394)(1033.85353535354,-7.45454545454546)(1045.05050505051,-7.5)(1059.9797979798,-7.5)(1074.90909090909,-7.56060606060606)(1089.83838383838,-7.56060606060606)(1104.76767676768,-7.62121212121212)(1108.5,-7.63636363636364)(1119.69696969697,-7.70454545454546)(1134.62626262626,-7.8030303030303)(1138.35858585859,-7.81818181818182)(1149.55555555556,-7.86363636363636)(1164.48484848485,-7.89393939393939)(1179.41414141414,-7.89393939393939)(1194.34343434343,-7.89393939393939)(1209.27272727273,-7.92424242424242)(1224.20202020202,-7.92424242424242)(1239.13131313131,-7.92424242424242)(1254.06060606061,-7.86363636363636)(1268.9898989899,-7.86363636363636)(1283.91919191919,-7.86363636363636)(1298.84848484848,-7.92424242424242)(1308.17929292929,-8)(1313.77777777778,-8.06818181818182)(1328.70707070707,-8.09090909090909)(1343.63636363636,-8.16363636363636)(1345.50252525253,-8.18181818181818)(1352.96717171717,-8.36363636363636)(1358.56565656566,-8.43181818181818)(1373.49494949495,-8.53030303030303)(1377.22727272727,-8.54545454545455)(1388.42424242424,-8.61363636363636)(1403.35353535354,-8.70454545454545)(1405.2196969697,-8.72727272727273)(1418.28282828283,-8.83333333333333)(1424.50336700337,-8.90909090909091)(1429.4797979798,-9.09090909090909)(1429.4797979798,-9.27272727272727)(1433.21212121212,-9.40909090909091)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (403.090909090909,-7.77272727272727)(414.287878787879,-7.63636363636364)(418.020202020202,-7.5)(419.886363636364,-7.45454545454546)(432.949494949495,-7.29545454545455)(447.878787878788,-7.28787878787879)(462.808080808081,-7.28787878787879)(466.540404040404,-7.27272727272727)(477.737373737374,-7.20454545454546)(492.666666666667,-7.10606060606061)(507.59595959596,-7.10606060606061)(522.525252525253,-7.16666666666667)(537.454545454546,-7.22727272727273)(552.383838383838,-7.16666666666667)(567.313131313131,-7.20454545454546)(582.242424242424,-7.20454545454546)(587.840909090909,-7.27272727272727)(597.171717171717,-7.34848484848485)(612.10101010101,-7.38636363636364)(617.699494949495,-7.45454545454546)(627.030303030303,-7.56818181818182)(632.628787878788,-7.63636363636364)(641.959595959596,-7.75)(647.558080808081,-7.81818181818182)(656.888888888889,-7.93181818181818)(662.487373737374,-8)(662.487373737374,-8.18181818181818)(660.621212121212,-8.36363636363636)(656.888888888889,-8.38636363636364)(641.959595959596,-8.5)(634.494949494949,-8.54545454545455)(627.030303030303,-8.61363636363636)(617.699494949495,-8.72727272727273)(612.10101010101,-8.86363636363636)(608.368686868687,-8.90909090909091)(597.171717171717,-8.97727272727273)(582.242424242424,-9.07575757575758)(567.313131313131,-9.07575757575758)(563.580808080808,-9.09090909090909)(552.383838383838,-9.13636363636364)(537.454545454546,-9.1969696969697)(522.525252525253,-9.25757575757576)(507.59595959596,-9.25757575757576)(492.666666666667,-9.25757575757576)(477.737373737374,-9.1969696969697)(462.808080808081,-9.15909090909091)(457.209595959596,-9.09090909090909)(449.122895622896,-8.90909090909091)(447.878787878788,-8.89393939393939)(432.949494949495,-8.83333333333333)(419.886363636364,-8.72727272727273)(418.020202020202,-8.68181818181818)(412.421717171717,-8.54545454545455)(409.311447811448,-8.36363636363636)(403.090909090909,-8.25)(391.893939393939,-8.18181818181818)(391.893939393939,-8)(391.893939393939,-7.81818181818182)(403.090909090909,-7.77272727272727)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (432.949494949495,-7.77272727272727)(438.54797979798,-7.63636363636364)(447.878787878788,-7.56060606060606)(462.808080808081,-7.56060606060606)(477.737373737374,-7.52272727272727)(483.335858585859,-7.45454545454546)(492.666666666667,-7.37878787878788)(507.59595959596,-7.37878787878788)(522.525252525253,-7.43939393939394)(526.257575757576,-7.45454545454546)(537.454545454546,-7.5)(548.651515151515,-7.45454545454546)(552.383838383838,-7.43939393939394)(556.116161616162,-7.45454545454546)(567.313131313131,-7.52272727272727)(582.242424242424,-7.52272727272727)(597.171717171717,-7.62121212121212)(600.90404040404,-7.63636363636364)(612.10101010101,-7.70454545454546)(621.431818181818,-7.81818181818182)(627.030303030303,-7.88636363636364)(636.361111111111,-8)(636.361111111111,-8.18181818181818)(627.030303030303,-8.29545454545455)(615.833333333333,-8.36363636363636)(612.10101010101,-8.38636363636364)(599.037878787879,-8.54545454545455)(597.171717171717,-8.56818181818182)(584.108585858586,-8.72727272727273)(582.242424242424,-8.75)(567.313131313131,-8.8030303030303)(552.383838383838,-8.86363636363636)(541.186868686869,-8.90909090909091)(537.454545454546,-8.92424242424242)(522.525252525253,-8.98484848484848)(507.59595959596,-8.98484848484848)(492.666666666667,-8.98484848484848)(483.335858585859,-8.90909090909091)(477.737373737374,-8.84090909090909)(462.808080808081,-8.75)(460.941919191919,-8.72727272727273)(447.878787878788,-8.56818181818182)(444.146464646465,-8.54545454545455)(432.949494949495,-8.40909090909091)(431.705387205387,-8.36363636363636)(431.083333333333,-8.18181818181818)(431.083333333333,-8)(431.083333333333,-7.81818181818182)(432.949494949495,-7.77272727272727)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (89.5757575757576,-8.13636363636364)(104.505050505051,-8.13636363636364)(119.434343434343,-8.02272727272727)(134.363636363636,-8.06818181818182)(139.962121212121,-8)(149.292929292929,-7.84848484848485)(164.222222222222,-7.83636363636364)(167.954545454545,-7.81818181818182)(179.151515151515,-7.77272727272727)(194.080808080808,-7.77272727272727)(209.010101010101,-7.77272727272727)(220.207070707071,-7.81818181818182)(223.939393939394,-7.83333333333333)(238.868686868687,-7.84090909090909)(253.79797979798,-7.93181818181818)(268.727272727273,-7.93181818181818)(279.924242424242,-8)(283.656565656566,-8.02272727272727)(296.719696969697,-8.18181818181818)(298.585858585859,-8.22727272727273)(304.184343434343,-8.36363636363636)(298.585858585859,-8.5)(296.719696969697,-8.54545454545455)(286.144781144781,-8.72727272727273)(283.656565656566,-8.75)(268.727272727273,-8.77272727272727)(257.530303030303,-8.90909090909091)(253.79797979798,-8.95454545454546)(238.868686868687,-8.97727272727273)(229.537878787879,-9.09090909090909)(223.939393939394,-9.15909090909091)(209.010101010101,-9.15909090909091)(194.080808080808,-9.15909090909091)(188.482323232323,-9.09090909090909)(179.151515151515,-8.97727272727273)(167.954545454545,-8.90909090909091)(164.222222222222,-8.89090909090909)(149.292929292929,-8.89090909090909)(134.363636363636,-8.81818181818182)(121.922558922559,-8.72727272727273)(119.434343434343,-8.70454545454545)(106.371212121212,-8.54545454545455)(104.505050505051,-8.5)(93.3080808080808,-8.36363636363636)(89.5757575757576,-8.27272727272727)(87.709595959596,-8.18181818181818)(89.5757575757576,-8.13636363636364)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (149.292929292929,-8.27272727272727)(153.025252525253,-8.18181818181818)(164.222222222222,-8.13636363636364)(179.151515151515,-8.04545454545455)(194.080808080808,-8.04545454545455)(209.010101010101,-8.04545454545455)(223.939393939394,-8.10606060606061)(238.868686868687,-8.16666666666667)(242.60101010101,-8.18181818181818)(253.79797979798,-8.31818181818182)(257.530303030303,-8.36363636363636)(253.79797979798,-8.40909090909091)(242.60101010101,-8.54545454545455)(238.868686868687,-8.56818181818182)(225.805555555556,-8.72727272727273)(223.939393939394,-8.75)(209.010101010101,-8.84090909090909)(194.080808080808,-8.75)(190.348484848485,-8.72727272727273)(179.151515151515,-8.65909090909091)(164.222222222222,-8.59090909090909)(149.292929292929,-8.59090909090909)(143.694444444444,-8.54545454545455)(147.426767676768,-8.36363636363636)(149.292929292929,-8.27272727272727)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091)(119.434343434343,-8.36363636363636)(791.252525252525,-8.72727272727273)(627.030303030303,-7.63636363636364)(1224.20202020202,-7.81818181818182)(791.252525252525,-9.09090909090909)(1089.83838383838,-10.1818181818182)(806.181818181818,-8.18181818181818)(641.959595959596,-8)(821.111111111111,-8)(940.545454545455,-7.27272727272727)(1030.12121212121,-7.27272727272727)(403.090909090909,-8.36363636363636)(1418.28282828283,-10)(283.656565656566,-8.18181818181818)(268.727272727273,-8)(477.737373737374,-7.45454545454546)(1224.20202020202,-10)(1209.27272727273,-10)(1283.91919191919,-10)(134.363636363636,-8.54545454545455)(134.363636363636,-8.72727272727273)(791.252525252525,-8.36363636363636)(447.878787878788,-8.72727272727273)(955.474747474747,-7.27272727272727)(522.525252525253,-7.27272727272727)(268.727272727273,-8.72727272727273)(776.323232323232,-8.72727272727273)(627.030303030303,-8.54545454545455)(1209.27272727273,-7.81818181818182)(1448.14141414141,-9.81818181818182)(880.828282828283,-9.81818181818182)(253.79797979798,-8.72727272727273)(895.757575757576,-7.45454545454546)(149.292929292929,-8)(462.808080808081,-8.90909090909091)(298.585858585859,-8.36363636363636)(403.090909090909,-8)(388.161616161616,-8.18181818181818)(1074.90909090909,-10.1818181818182)(432.949494949495,-8.72727272727273)(1268.9898989899,-7.81818181818182)(119.434343434343,-8.54545454545455)(1283.91919191919,-7.81818181818182)(149.292929292929,-8.90909090909091)(298.585858585859,-8.18181818181818)(1194.34343434343,-10)(1388.42424242424,-10)(1343.63636363636,-10.1818181818182)(283.656565656566,-8.54545454545455)(1463.07070707071,-9.27272727272727)(836.040404040404,-7.81818181818182)(238.868686868687,-8)(552.383838383838,-8.90909090909091)(522.525252525253,-9.09090909090909)(507.59595959596,-9.09090909090909)(537.454545454546,-9.09090909090909)(492.666666666667,-9.09090909090909)(1478,-9.45454545454546)(641.959595959596,-8.54545454545455)(1343.63636363636,-8)(1045.05050505051,-7.27272727272727)(1119.69696969697,-7.63636363636364)(418.020202020202,-7.63636363636364)(119.434343434343,-8)(836.040404040404,-8)(134.363636363636,-8.18181818181818)(164.222222222222,-8)(806.181818181818,-9.45454545454546)(791.252525252525,-9.27272727272727)(850.969696969697,-9.81818181818182)(283.656565656566,-8.36363636363636)(388.161616161616,-8)(1373.49494949495,-8.18181818181818)(134.363636363636,-8.36363636363636)(671.818181818182,-14.3636363636364)(507.59595959596,-7.27272727272727)(567.313131313131,-7.27272727272727)(582.242424242424,-7.27272727272727)(447.878787878788,-7.45454545454546)(492.666666666667,-7.27272727272727)(1298.84848484848,-7.81818181818182)(597.171717171717,-8.90909090909091)(552.383838383838,-9.09090909090909)(627.030303030303,-8.72727272727273)(627.030303030303,-7.81818181818182)(955.474747474747,-10)(1119.69696969697,-10.1818181818182)(1313.77777777778,-7.81818181818182)(149.292929292929,-8.72727272727273)(1164.48484848485,-7.63636363636364)(1448.14141414141,-9.45454545454546)(1433.21212121212,-9.09090909090909)(1433.21212121212,-8.72727272727273)(1448.14141414141,-8.90909090909091)(403.090909090909,-8.54545454545455)(403.090909090909,-8.18181818181818)(477.737373737374,-7.27272727272727)(238.868686868687,-8.72727272727273)(268.727272727273,-8.18181818181818)(223.939393939394,-7.81818181818182)(656.888888888889,-8.18181818181818)(656.888888888889,-8)(776.323232323232,-8.54545454545455)(283.656565656566,-8)(1328.70707070707,-10.1818181818182)(432.949494949495,-8.54545454545455)(1418.28282828283,-8.54545454545455)(656.888888888889,-8.36363636363636)(1134.62626262626,-10.1818181818182)(418.020202020202,-8.36363636363636)(1179.41414141414,-10)(432.949494949495,-7.45454545454546)(179.151515151515,-8)(179.151515151515,-7.81818181818182)(1373.49494949495,-10.1818181818182)(597.171717171717,-7.27272727272727)(985.333333333333,-10.1818181818182)(238.868686868687,-8.90909090909091)(253.79797979798,-8.90909090909091)(821.111111111111,-9.63636363636364)(403.090909090909,-7.63636363636364)(418.020202020202,-8.18181818181818)(418.020202020202,-8)(641.959595959596,-7.63636363636364)(104.505050505051,-8.18181818181818)(104.505050505051,-8.36363636363636)(104.505050505051,-8)(89.5757575757576,-8.18181818181818)(1358.56565656566,-8)(209.010101010101,-8)(164.222222222222,-7.81818181818182)(1298.84848484848,-10)(1313.77777777778,-10.1818181818182)(970.40404040404,-10)(895.757575757576,-10)(1463.07070707071,-9.09090909090909)(925.616161616162,-7.27272727272727)(1403.35353535354,-8.36363636363636)(1388.42424242424,-8.18181818181818)(1328.70707070707,-7.81818181818182)(612.10101010101,-8.90909090909091)(447.878787878788,-8.90909090909091)(1059.9797979798,-7.27272727272727)(1418.28282828283,-9.81818181818182)(1194.34343434343,-7.81818181818182)(432.949494949495,-8.36363636363636)(627.030303030303,-7.45454545454546)(283.656565656566,-8.72727272727273)(119.434343434343,-8.72727272727273)(597.171717171717,-8.72727272727273)(238.868686868687,-7.81818181818182)(194.080808080808,-8)(776.323232323232,-9.09090909090909)(865.89898989899,-7.81818181818182)(761.393939393939,-8.72727272727273)(1298.84848484848,-10.1818181818182)(1164.48484848485,-10)(313.515151515152,-8.36363636363636)(253.79797979798,-8.18181818181818)(223.939393939394,-8.72727272727273)(462.808080808081,-8.72727272727273)(627.030303030303,-8.36363636363636)(656.888888888889,-7.81818181818182)(627.030303030303,-8)(1149.55555555556,-10)(1283.91919191919,-10.1818181818182)(209.010101010101,-9.09090909090909)(194.080808080808,-9.09090909090909)(223.939393939394,-9.09090909090909)(447.878787878788,-8.54545454545455)(134.363636363636,-7.81818181818182)(462.808080808081,-7.27272727272727)(1433.21212121212,-10)(432.949494949495,-7.81818181818182)(970.40404040404,-10.1818181818182)(1104.76767676768,-7.63636363636364)(253.79797979798,-8.36363636363636)(641.959595959596,-8.72727272727273)(462.808080808081,-9.09090909090909)(1373.49494949495,-8) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_354.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1448.14141414141,-9.04545454545455)(1450.62962962963,-9.09090909090909)(1455.60606060606,-9.27272727272727)(1450.62962962963,-9.45454545454546)(1448.14141414141,-9.5)(1440.67676767677,-9.63636363636364)(1433.21212121212,-9.72727272727273)(1422.01515151515,-9.81818181818182)(1418.28282828283,-9.84848484848485)(1403.35353535354,-9.96969696969697)(1395.88888888889,-10)(1388.42424242424,-10.030303030303)(1373.49494949495,-10.0909090909091)(1358.56565656566,-10.0909090909091)(1343.63636363636,-10.0909090909091)(1328.70707070707,-10.0909090909091)(1313.77777777778,-10.0909090909091)(1298.84848484848,-10.0909090909091)(1283.91919191919,-10.0909090909091)(1268.9898989899,-10.0909090909091)(1254.06060606061,-10.0909090909091)(1239.13131313131,-10.0909090909091)(1224.20202020202,-10.0909090909091)(1209.27272727273,-10.0909090909091)(1194.34343434343,-10.0909090909091)(1179.41414141414,-10.0909090909091)(1164.48484848485,-10.0909090909091)(1149.55555555556,-10.0909090909091)(1134.62626262626,-10.0909090909091)(1119.69696969697,-10.0909090909091)(1104.76767676768,-10.0909090909091)(1089.83838383838,-10.0909090909091)(1074.90909090909,-10.0909090909091)(1059.9797979798,-10.0909090909091)(1045.05050505051,-10.0909090909091)(1030.12121212121,-10.0909090909091)(1015.19191919192,-10.0909090909091)(1000.26262626263,-10.0909090909091)(985.333333333333,-10.0909090909091)(970.40404040404,-10.0909090909091)(955.474747474747,-10.0909090909091)(940.545454545455,-10.030303030303)(933.080808080808,-10)(925.616161616162,-9.96969696969697)(910.686868686869,-9.90909090909091)(895.757575757576,-9.90909090909091)(880.828282828283,-9.84848484848485)(873.363636363636,-9.81818181818182)(865.89898989899,-9.78787878787879)(850.969696969697,-9.72727272727273)(836.040404040404,-9.66666666666667)(832.308080808081,-9.63636363636364)(821.111111111111,-9.54545454545455)(813.646464646465,-9.45454545454546)(806.181818181818,-9.36363636363636)(798.717171717172,-9.27272727272727)(791.252525252525,-9.13636363636364)(788.76430976431,-9.09090909090909)(783.787878787879,-8.90909090909091)(783.787878787879,-8.72727272727273)(788.76430976431,-8.54545454545455)(791.252525252525,-8.5)(798.717171717172,-8.36363636363636)(806.181818181818,-8.27272727272727)(813.646464646465,-8.18181818181818)(821.111111111111,-8.09090909090909)(832.308080808081,-8)(836.040404040404,-7.96969696969697)(850.969696969697,-7.84848484848485)(854.70202020202,-7.81818181818182)(865.89898989899,-7.72727272727273)(877.09595959596,-7.63636363636364)(880.828282828283,-7.60606060606061)(895.757575757576,-7.48484848484849)(903.222222222222,-7.45454545454546)(910.686868686869,-7.42424242424243)(925.616161616162,-7.36363636363636)(940.545454545455,-7.36363636363636)(955.474747474747,-7.3030303030303)(962.939393939394,-7.27272727272727)(970.40404040404,-7.24242424242424)(985.333333333333,-7.18181818181818)(1000.26262626263,-7.18181818181818)(1015.19191919192,-7.24242424242424)(1022.65656565657,-7.27272727272727)(1030.12121212121,-7.3030303030303)(1045.05050505051,-7.36363636363636)(1059.9797979798,-7.36363636363636)(1074.90909090909,-7.42424242424243)(1082.37373737374,-7.45454545454546)(1089.83838383838,-7.48484848484849)(1104.76767676768,-7.54545454545455)(1119.69696969697,-7.54545454545455)(1134.62626262626,-7.60606060606061)(1142.09090909091,-7.63636363636364)(1149.55555555556,-7.66666666666667)(1164.48484848485,-7.72727272727273)(1179.41414141414,-7.72727272727273)(1194.34343434343,-7.72727272727273)(1209.27272727273,-7.72727272727273)(1224.20202020202,-7.72727272727273)(1239.13131313131,-7.72727272727273)(1254.06060606061,-7.72727272727273)(1268.9898989899,-7.72727272727273)(1283.91919191919,-7.78787878787879)(1291.38383838384,-7.81818181818182)(1298.84848484848,-7.84848484848485)(1313.77777777778,-7.90909090909091)(1328.70707070707,-7.90909090909091)(1343.63636363636,-7.96969696969697)(1347.36868686869,-8)(1358.56565656566,-8.09090909090909)(1369.76262626263,-8.18181818181818)(1373.49494949495,-8.21212121212121)(1388.42424242424,-8.33333333333333)(1392.15656565657,-8.36363636363636)(1403.35353535354,-8.45454545454545)(1410.81818181818,-8.54545454545455)(1418.28282828283,-8.63636363636364)(1425.74747474747,-8.72727272727273)(1433.21212121212,-8.81818181818182)(1440.67676767677,-8.90909090909091)(1448.14141414141,-9.04545454545455)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (418.020202020202,-7.77272727272727)(429.217171717172,-7.63636363636364)(432.949494949495,-7.60606060606061)(447.878787878788,-7.48484848484849)(455.343434343434,-7.45454545454546)(462.808080808081,-7.42424242424243)(477.737373737374,-7.36363636363636)(492.666666666667,-7.3030303030303)(500.131313131313,-7.27272727272727)(507.59595959596,-7.24242424242424)(522.525252525253,-7.18181818181818)(537.454545454546,-7.18181818181818)(552.383838383838,-7.24242424242424)(559.848484848485,-7.27272727272727)(567.313131313131,-7.3030303030303)(582.242424242424,-7.36363636363636)(597.171717171717,-7.42424242424243)(600.90404040404,-7.45454545454546)(612.10101010101,-7.54545454545455)(619.565656565657,-7.63636363636364)(627.030303030303,-7.77272727272727)(629.518518518518,-7.81818181818182)(639.47138047138,-8)(639.47138047138,-8.18181818181818)(639.47138047138,-8.36363636363636)(629.518518518518,-8.54545454545455)(627.030303030303,-8.59090909090909)(615.833333333333,-8.72727272727273)(612.10101010101,-8.75757575757576)(597.171717171717,-8.87878787878788)(589.707070707071,-8.90909090909091)(582.242424242424,-8.93939393939394)(567.313131313131,-9)(552.383838383838,-9)(537.454545454546,-9)(522.525252525253,-9)(507.59595959596,-9)(492.666666666667,-9)(477.737373737374,-8.93939393939394)(470.272727272727,-8.90909090909091)(462.808080808081,-8.87878787878788)(447.878787878788,-8.75757575757576)(444.146464646465,-8.72727272727273)(432.949494949495,-8.63636363636364)(425.484848484849,-8.54545454545455)(418.020202020202,-8.40909090909091)(415.531986531986,-8.36363636363636)(410.555555555556,-8.18181818181818)(410.555555555556,-8)(415.531986531986,-7.81818181818182)(418.020202020202,-7.77272727272727)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (134.363636363636,-8.13636363636364)(145.560606060606,-8)(149.292929292929,-7.96969696969697)(164.222222222222,-7.90909090909091)(179.151515151515,-7.90909090909091)(194.080808080808,-7.90909090909091)(209.010101010101,-7.90909090909091)(223.939393939394,-7.96969696969697)(231.40404040404,-8)(238.868686868687,-8.03030303030303)(253.79797979798,-8.09090909090909)(264.99494949495,-8.18181818181818)(268.727272727273,-8.22727272727273)(276.191919191919,-8.36363636363636)(271.215488215488,-8.54545454545455)(268.727272727273,-8.59090909090909)(257.530303030303,-8.72727272727273)(253.79797979798,-8.75757575757576)(238.868686868687,-8.81818181818182)(223.939393939394,-8.81818181818182)(209.010101010101,-8.81818181818182)(194.080808080808,-8.81818181818182)(179.151515151515,-8.81818181818182)(164.222222222222,-8.75757575757576)(156.757575757576,-8.72727272727273)(149.292929292929,-8.6969696969697)(136.851851851852,-8.54545454545455)(134.363636363636,-8.5)(126.89898989899,-8.36363636363636)(131.875420875421,-8.18181818181818)(134.363636363636,-8.13636363636364)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636)(373.232323232323,-8.18181818181818)(791.252525252525,-8.90909090909091)(582.242424242424,-8.72727272727273)(1179.41414141414,-7.63636363636364)(1059.9797979798,-10.1818181818182)(567.313131313131,-8.90909090909091)(1448.14141414141,-9.09090909090909)(880.828282828283,-7.63636363636364)(641.959595959596,-7.81818181818182)(477.737373737374,-8.90909090909091)(1254.06060606061,-10)(1239.13131313131,-10)(552.383838383838,-7.45454545454546)(850.969696969697,-9.63636363636364)(1149.55555555556,-7.63636363636364)(1059.9797979798,-7.45454545454546)(985.333333333333,-7.27272727272727)(597.171717171717,-7.45454545454546)(552.383838383838,-7.27272727272727)(403.090909090909,-7.81818181818182)(432.949494949495,-3.27272727272727)(194.080808080808,-8.36363636363636)(194.080808080808,-8.54545454545455)(1045.05050505051,-10.1818181818182)(1313.77777777778,-8)(1373.49494949495,-10)(1448.14141414141,-9.63636363636364)(1000.26262626263,-10.1818181818182)(582.242424242424,-8.90909090909091)(134.363636363636,-8)(44.7878787878788,-7.63636363636364)(179.151515151515,-8.18181818181818)(164.222222222222,-8.36363636363636)(223.939393939394,-8)(179.151515151515,-8.54545454545455)(179.151515151515,-8.72727272727273)(149.292929292929,-7.81818181818182)(119.434343434343,-8.18181818181818)(253.79797979798,-8)(209.010101010101,-7.81818181818182)(253.79797979798,-8.54545454545455)(418.020202020202,-8.54545454545455)(791.252525252525,-8.54545454545455)(850.969696969697,-7.81818181818182)(612.10101010101,-7.45454545454546)(806.181818181818,-9.27272727272727)(1239.13131313131,-7.81818181818182)(1478,-18)(940.545454545455,-10)(612.10101010101,-8.72727272727273)(1268.9898989899,-10)(641.959595959596,-8.36363636363636)(1433.21212121212,-9.81818181818182)(1463.07070707071,-9.63636363636364)(418.020202020202,-7.81818181818182)(1403.35353535354,-8.54545454545455)(1433.21212121212,-8.90909090909091)(164.222222222222,-8.54545454545455)(836.040404040404,-9.63636363636364)(447.878787878788,-7.63636363636364)(537.454545454546,-7.27272727272727)(268.727272727273,-8.36363636363636)(194.080808080808,-7.81818181818182)(268.727272727273,-8.54545454545455)(1134.62626262626,-7.63636363636364)(910.686868686869,-7.45454545454546)(970.40404040404,-7.27272727272727)(1000.26262626263,-7.27272727272727)(1015.19191919192,-7.27272727272727)(1015.19191919192,-7.09090909090909)(1358.56565656566,-8.18181818181818)(388.161616161616,-8.36363636363636)(492.666666666667,-8.90909090909091)(194.080808080808,-8.72727272727273)(194.080808080808,-8.90909090909091)(164.222222222222,-8.72727272727273)(179.151515151515,-8.90909090909091)(209.010101010101,-8.90909090909091)(164.222222222222,-8.90909090909091)(223.939393939394,-8.90909090909091)(119.434343434343,-8.36363636363636)(791.252525252525,-8.72727272727273)(627.030303030303,-7.63636363636364)(1224.20202020202,-7.81818181818182)(791.252525252525,-9.09090909090909)(1089.83838383838,-10.1818181818182)(806.181818181818,-8.18181818181818)(641.959595959596,-8)(821.111111111111,-8)(940.545454545455,-7.27272727272727)(1030.12121212121,-7.27272727272727)(403.090909090909,-8.36363636363636)(1418.28282828283,-10)(283.656565656566,-8.18181818181818)(268.727272727273,-8)(477.737373737374,-7.45454545454546)(1224.20202020202,-10)(1209.27272727273,-10)(1283.91919191919,-10)(134.363636363636,-8.54545454545455)(134.363636363636,-8.72727272727273)(791.252525252525,-8.36363636363636)(447.878787878788,-8.72727272727273)(955.474747474747,-7.27272727272727)(522.525252525253,-7.27272727272727)(268.727272727273,-8.72727272727273)(776.323232323232,-8.72727272727273)(627.030303030303,-8.54545454545455)(1209.27272727273,-7.81818181818182)(1448.14141414141,-9.81818181818182)(880.828282828283,-9.81818181818182)(253.79797979798,-8.72727272727273)(895.757575757576,-7.45454545454546)(149.292929292929,-8)(462.808080808081,-8.90909090909091)(298.585858585859,-8.36363636363636)(403.090909090909,-8)(388.161616161616,-8.18181818181818)(1074.90909090909,-10.1818181818182)(432.949494949495,-8.72727272727273)(1268.9898989899,-7.81818181818182)(119.434343434343,-8.54545454545455)(1283.91919191919,-7.81818181818182)(149.292929292929,-8.90909090909091)(298.585858585859,-8.18181818181818)(1194.34343434343,-10)(1388.42424242424,-10)(1343.63636363636,-10.1818181818182)(283.656565656566,-8.54545454545455)(1463.07070707071,-9.27272727272727)(836.040404040404,-7.81818181818182)(238.868686868687,-8)(552.383838383838,-8.90909090909091)(522.525252525253,-9.09090909090909)(507.59595959596,-9.09090909090909)(537.454545454546,-9.09090909090909)(492.666666666667,-9.09090909090909)(1478,-9.45454545454546)(641.959595959596,-8.54545454545455)(1343.63636363636,-8)(1045.05050505051,-7.27272727272727)(1119.69696969697,-7.63636363636364)(418.020202020202,-7.63636363636364)(119.434343434343,-8)(836.040404040404,-8)(134.363636363636,-8.18181818181818)(164.222222222222,-8)(806.181818181818,-9.45454545454546)(791.252525252525,-9.27272727272727)(850.969696969697,-9.81818181818182)(283.656565656566,-8.36363636363636)(388.161616161616,-8)(1373.49494949495,-8.18181818181818)(134.363636363636,-8.36363636363636)(671.818181818182,-14.3636363636364)(507.59595959596,-7.27272727272727)(567.313131313131,-7.27272727272727)(582.242424242424,-7.27272727272727)(447.878787878788,-7.45454545454546)(492.666666666667,-7.27272727272727)(1298.84848484848,-7.81818181818182)(597.171717171717,-8.90909090909091)(552.383838383838,-9.09090909090909)(627.030303030303,-8.72727272727273)(627.030303030303,-7.81818181818182)(955.474747474747,-10)(1119.69696969697,-10.1818181818182)(1313.77777777778,-7.81818181818182)(149.292929292929,-8.72727272727273)(1164.48484848485,-7.63636363636364)(1448.14141414141,-9.45454545454546)(1433.21212121212,-9.09090909090909)(1433.21212121212,-8.72727272727273)(1448.14141414141,-8.90909090909091)(403.090909090909,-8.54545454545455)(403.090909090909,-8.18181818181818)(477.737373737374,-7.27272727272727)(238.868686868687,-8.72727272727273)(268.727272727273,-8.18181818181818)(223.939393939394,-7.81818181818182)(656.888888888889,-8.18181818181818)(656.888888888889,-8)(776.323232323232,-8.54545454545455)(283.656565656566,-8)(1328.70707070707,-10.1818181818182)(432.949494949495,-8.54545454545455)(1418.28282828283,-8.54545454545455)(656.888888888889,-8.36363636363636)(1134.62626262626,-10.1818181818182)(418.020202020202,-8.36363636363636)(1179.41414141414,-10)(432.949494949495,-7.45454545454546)(179.151515151515,-8)(179.151515151515,-7.81818181818182)(1373.49494949495,-10.1818181818182)(597.171717171717,-7.27272727272727)(985.333333333333,-10.1818181818182)(238.868686868687,-8.90909090909091)(253.79797979798,-8.90909090909091)(821.111111111111,-9.63636363636364)(403.090909090909,-7.63636363636364)(418.020202020202,-8.18181818181818)(418.020202020202,-8)(641.959595959596,-7.63636363636364)(104.505050505051,-8.18181818181818)(104.505050505051,-8.36363636363636)(104.505050505051,-8)(89.5757575757576,-8.18181818181818)(1358.56565656566,-8)(209.010101010101,-8)(164.222222222222,-7.81818181818182)(1298.84848484848,-10)(1313.77777777778,-10.1818181818182)(970.40404040404,-10)(895.757575757576,-10)(1463.07070707071,-9.09090909090909)(925.616161616162,-7.27272727272727)(1403.35353535354,-8.36363636363636)(1388.42424242424,-8.18181818181818)(1328.70707070707,-7.81818181818182)(612.10101010101,-8.90909090909091)(447.878787878788,-8.90909090909091)(1059.9797979798,-7.27272727272727)(1418.28282828283,-9.81818181818182)(1194.34343434343,-7.81818181818182)(432.949494949495,-8.36363636363636)(627.030303030303,-7.45454545454546)(283.656565656566,-8.72727272727273)(119.434343434343,-8.72727272727273)(597.171717171717,-8.72727272727273)(238.868686868687,-7.81818181818182)(194.080808080808,-8)(776.323232323232,-9.09090909090909)(865.89898989899,-7.81818181818182)(761.393939393939,-8.72727272727273)(1298.84848484848,-10.1818181818182)(1164.48484848485,-10)(313.515151515152,-8.36363636363636)(253.79797979798,-8.18181818181818)(223.939393939394,-8.72727272727273)(462.808080808081,-8.72727272727273)(627.030303030303,-8.36363636363636)(656.888888888889,-7.81818181818182)(627.030303030303,-8)(1149.55555555556,-10)(1283.91919191919,-10.1818181818182)(209.010101010101,-9.09090909090909)(194.080808080808,-9.09090909090909)(223.939393939394,-9.09090909090909)(447.878787878788,-8.54545454545455)(134.363636363636,-7.81818181818182)(462.808080808081,-7.27272727272727)(1433.21212121212,-10)(432.949494949495,-7.81818181818182)(970.40404040404,-10.1818181818182)(1104.76767676768,-7.63636363636364)(253.79797979798,-8.36363636363636)(641.959595959596,-8.72727272727273)(462.808080808081,-9.09090909090909)(1373.49494949495,-8)(1134.62626262626,-10)(1343.63636363636,-10)(1119.69696969697,-10)(149.292929292929,-8.54545454545455)(149.292929292929,-8.18181818181818)(268.727272727273,-8.90909090909091)(1179.41414141414,-7.81818181818182)(89.5757575757576,-8)(985.333333333333,-10)(656.888888888889,-8.54545454545455)(1388.42424242424,-10.1818181818182)(776.323232323232,-8.36363636363636)(880.828282828283,-7.45454545454546)(1343.63636363636,-7.81818181818182) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_40.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478.0002488174,-8.54545454545455)(1478.00049762651,-8.72727272727273)(1478.00074642733,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00074642733,-9.27272727272727)(1478.00074642733,-9.45454545454546)(1478.00074642733,-9.63636363636364)(1478.00074642733,-9.81818181818182)(1478.00058056104,-10)(1478.00033175469,-10.1818181818182)(1478.00008294006,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478.0002488174,-17.4545454545455)(1478.00049762651,-17.6363636363636)(1478.00074642733,-17.8181818181818)(1478.00074642733,-18)(1478,-18.0000090904546)(1463.07070707071,-18.0000090904546)(1448.14141414141,-18.0000090904546)(1433.21212121212,-18.0000090904546)(1418.28282828283,-18.0000090904546)(1403.35353535354,-18.000008080449)(1388.42424242424,-18.0000070704321)(1373.49494949495,-18.0000040403143)(1358.56565656566,-18.0000020201796)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(-0.000248817401863321,-8)(-0.000497626510092015,-7.81818181818182)(-0.000746427325097138,-7.63636363636364)(-0.000746427325097138,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000497626510092015,-7.09090909090909)(-0.000248817401863321,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(-0.000248817401863321,-3.81818181818182)(-0.000497626510092015,-3.63636363636364)(-0.000746427325097138,-3.45454545454546)(-0.000746427325097138,-3.27272727272727)(-0.000746427325097138,-3.09090909090909)(-0.000497626510092015,-2.90909090909091)(-0.000248817401863321,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-7)(14.9292929292929,-7)(29.8585858585859,-7)(44.7878787878788,-7)(59.7171717171717,-7)(74.6464646464647,-7)(89.5757575757576,-7)(104.505050505051,-6.93939393939394)(111.969696969697,-6.90909090909091)(119.434343434343,-6.87878787878788)(134.363636363636,-6.81818181818182)(149.292929292929,-6.75757575757576)(156.757575757576,-6.72727272727273)(164.222222222222,-6.6969696969697)(179.151515151515,-6.63636363636364)(194.080808080808,-6.57575757575758)(201.545454545455,-6.54545454545455)(209.010101010101,-6.51515151515151)(223.939393939394,-6.45454545454545)(238.868686868687,-6.45454545454545)(253.79797979798,-6.51515151515151)(261.262626262626,-6.54545454545455)(268.727272727273,-6.57575757575758)(283.656565656566,-6.6969696969697)(287.388888888889,-6.72727272727273)(298.585858585859,-6.81818181818182)(309.782828282828,-6.90909090909091)(313.515151515152,-6.93939393939394)(328.444444444444,-7.06060606060606)(335.909090909091,-7.09090909090909)(343.373737373737,-7.12121212121212)(358.30303030303,-7.18181818181818)(373.232323232323,-7.24242424242424)(380.69696969697,-7.27272727272727)(388.161616161616,-7.3030303030303)(403.090909090909,-7.36363636363636)(418.020202020202,-7.36363636363636)(432.949494949495,-7.3030303030303)(440.414141414141,-7.27272727272727)(447.878787878788,-7.24242424242424)(462.808080808081,-7.18181818181818)(477.737373737374,-7.18181818181818)(492.666666666667,-7.18181818181818)(507.59595959596,-7.18181818181818)(522.525252525253,-7.18181818181818)(537.454545454546,-7.18181818181818)(552.383838383838,-7.18181818181818)(567.313131313131,-7.18181818181818)(582.242424242424,-7.18181818181818)(597.171717171717,-7.18181818181818)(612.10101010101,-7.18181818181818)(627.030303030303,-7.18181818181818)(641.959595959596,-7.18181818181818)(656.888888888889,-7.24242424242424)(664.353535353535,-7.27272727272727)(671.818181818182,-7.3030303030303)(686.747474747475,-7.36363636363636)(701.676767676768,-7.36363636363636)(716.606060606061,-7.36363636363636)(731.535353535354,-7.36363636363636)(746.464646464646,-7.42424242424243)(753.929292929293,-7.45454545454546)(761.393939393939,-7.48484848484849)(776.323232323232,-7.54545454545455)(791.252525252525,-7.48484848484849)(798.717171717172,-7.45454545454546)(806.181818181818,-7.42424242424243)(821.111111111111,-7.36363636363636)(836.040404040404,-7.36363636363636)(850.969696969697,-7.34090909090909)(865.89898989899,-7.34090909090909)(880.828282828283,-7.34090909090909)(895.757575757576,-7.3030303030303)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(925.616161616162,-7.18181818181818)(940.545454545455,-7.18181818181818)(955.474747474747,-7.18181818181818)(970.40404040404,-7.18181818181818)(985.333333333333,-7.18181818181818)(1000.26262626263,-7.12121212121212)(1007.72727272727,-7.09090909090909)(1015.19191919192,-7.06060606060606)(1030.12121212121,-7)(1045.05050505051,-7)(1059.9797979798,-7)(1074.90909090909,-7)(1089.83838383838,-7)(1104.76767676768,-7)(1119.69696969697,-7)(1134.62626262626,-7)(1149.55555555556,-7.06060606060606)(1157.0202020202,-7.09090909090909)(1164.48484848485,-7.12121212121212)(1179.41414141414,-7.18181818181818)(1194.34343434343,-7.18181818181818)(1209.27272727273,-7.24242424242424)(1216.73737373737,-7.27272727272727)(1224.20202020202,-7.31818181818182)(1239.13131313131,-7.36363636363636)(1254.06060606061,-7.36363636363636)(1268.9898989899,-7.42424242424243)(1276.45454545455,-7.45454545454546)(1283.91919191919,-7.48484848484849)(1298.84848484848,-7.60606060606061)(1313.77777777778,-7.60606060606061)(1321.24242424242,-7.63636363636364)(1328.70707070707,-7.66666666666667)(1343.63636363636,-7.66666666666667)(1358.56565656566,-7.78787878787879)(1366.0303030303,-7.81818181818182)(1373.49494949495,-7.84848484848485)(1388.42424242424,-7.96969696969697)(1392.15656565657,-8)(1403.35353535354,-8.09090909090909)(1414.5505050505,-8.18181818181818)(1418.28282828283,-8.21212121212121)(1433.21212121212,-8.33333333333333)(1436.94444444444,-8.36363636363636)(1448.14141414141,-8.45454545454545)(1459.33838383838,-8.54545454545455)(1463.07070707071,-8.57575757575757)(1478,-8.63636363636364)(1478.00012440663,-8.72727272727273)(1478.00037321366,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00037321366,-9.27272727272727)(1478.00037321366,-9.45454545454546)(1478.00037321366,-9.63636363636364)(1478.00037321366,-9.81818181818182)(1478.00020734323,-10)(1478,-10.1515151515152)(1470.53535353535,-10.1818181818182)(1463.07070707071,-10.2121212121212)(1448.14141414141,-10.3333333333333)(1440.67676767677,-10.3636363636364)(1433.21212121212,-10.3939393939394)(1418.28282828283,-10.4545454545455)(1403.35353535354,-10.5151515151515)(1395.88888888889,-10.5454545454545)(1388.42424242424,-10.5757575757576)(1373.49494949495,-10.6969696969697)(1366.0303030303,-10.7272727272727)(1358.56565656566,-10.7575757575758)(1343.63636363636,-10.8181818181818)(1328.70707070707,-10.8181818181818)(1313.77777777778,-10.8181818181818)(1298.84848484848,-10.8181818181818)(1283.91919191919,-10.8181818181818)(1268.9898989899,-10.7575757575758)(1265.25757575758,-10.7272727272727)(1254.06060606061,-10.6363636363636)(1239.13131313131,-10.5757575757576)(1224.20202020202,-10.5757575757576)(1209.27272727273,-10.6363636363636)(1194.34343434343,-10.6363636363636)(1179.41414141414,-10.6363636363636)(1164.48484848485,-10.6363636363636)(1149.55555555556,-10.5909090909091)(1134.62626262626,-10.5909090909091)(1119.69696969697,-10.5909090909091)(1104.76767676768,-10.6363636363636)(1089.83838383838,-10.6363636363636)(1074.90909090909,-10.6363636363636)(1059.9797979798,-10.5757575757576)(1052.51515151515,-10.5454545454545)(1045.05050505051,-10.5151515151515)(1030.12121212121,-10.4090909090909)(1015.19191919192,-10.4090909090909)(1000.26262626263,-10.4090909090909)(985.333333333333,-10.4545454545455)(970.40404040404,-10.4545454545455)(955.474747474747,-10.3939393939394)(948.010101010101,-10.3636363636364)(940.545454545455,-10.3333333333333)(925.616161616162,-10.2727272727273)(910.686868686869,-10.2727272727273)(895.757575757576,-10.2121212121212)(888.292929292929,-10.1818181818182)(880.828282828283,-10.1515151515152)(865.89898989899,-10.0909090909091)(850.969696969697,-10.0909090909091)(836.040404040404,-10.030303030303)(828.575757575758,-10)(821.111111111111,-9.96969696969697)(806.181818181818,-9.84848484848485)(798.717171717172,-9.81818181818182)(791.252525252525,-9.78787878787879)(776.323232323232,-9.66666666666667)(768.858585858586,-9.63636363636364)(761.393939393939,-9.60606060606061)(746.464646464646,-9.54545454545455)(731.535353535354,-9.48484848484848)(724.070707070707,-9.45454545454546)(716.606060606061,-9.42424242424243)(701.676767676768,-9.36363636363636)(686.747474747475,-9.36363636363636)(671.818181818182,-9.36363636363636)(656.888888888889,-9.3030303030303)(641.959595959596,-9.3030303030303)(627.030303030303,-9.3030303030303)(612.10101010101,-9.36363636363636)(597.171717171717,-9.36363636363636)(582.242424242424,-9.36363636363636)(567.313131313131,-9.36363636363636)(552.383838383838,-9.36363636363636)(537.454545454546,-9.36363636363636)(522.525252525253,-9.42424242424243)(515.060606060606,-9.45454545454546)(507.59595959596,-9.48484848484848)(492.666666666667,-9.54545454545455)(477.737373737374,-9.54545454545455)(462.808080808081,-9.54545454545455)(447.878787878788,-9.54545454545455)(432.949494949495,-9.54545454545455)(418.020202020202,-9.48484848484848)(410.555555555556,-9.45454545454546)(403.090909090909,-9.42424242424243)(388.161616161616,-9.36363636363636)(373.232323232323,-9.36363636363636)(358.30303030303,-9.31818181818182)(343.373737373737,-9.31818181818182)(328.444444444444,-9.31818181818182)(313.515151515152,-9.36363636363636)(298.585858585859,-9.36363636363636)(283.656565656566,-9.36363636363636)(268.727272727273,-9.42424242424243)(261.262626262626,-9.45454545454546)(253.79797979798,-9.48484848484848)(238.868686868687,-9.54545454545455)(223.939393939394,-9.60606060606061)(216.474747474747,-9.63636363636364)(209.010101010101,-9.66666666666667)(194.080808080808,-9.72727272727273)(179.151515151515,-9.72727272727273)(164.222222222222,-9.72727272727273)(149.292929292929,-9.72727272727273)(134.363636363636,-9.66666666666667)(130.631313131313,-9.63636363636364)(119.434343434343,-9.5)(116.946127946128,-9.45454545454546)(111.969696969697,-9.27272727272727)(111.969696969697,-9.09090909090909)(111.969696969697,-8.90909090909091)(111.969696969697,-8.72727272727273)(106.993265993266,-8.54545454545455)(104.505050505051,-8.5)(97.040404040404,-8.36363636363636)(89.5757575757576,-8.27272727272727)(78.3787878787879,-8.18181818181818)(74.6464646464647,-8.15151515151515)(59.7171717171717,-8.09090909090909)(44.7878787878788,-8.03030303030303)(37.3232323232323,-8)(29.8585858585859,-7.96969696969697)(14.9292929292929,-7.90909090909091)(0,-7.90909090909091)(-0.000124406627521346,-7.81818181818182)(-0.000373213662548569,-7.63636363636364)(-0.000373213662548569,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000124406627521346,-7.09090909090909)(0,-7)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-2.81818181818182)(14.9292929292929,-2.81818181818182)(29.8585858585859,-2.81818181818182)(44.7878787878788,-2.81818181818182)(59.7171717171717,-2.81818181818182)(74.6464646464647,-2.81818181818182)(89.5757575757576,-2.75757575757576)(97.040404040404,-2.72727272727273)(104.505050505051,-2.6969696969697)(119.434343434343,-2.63636363636364)(134.363636363636,-2.63636363636364)(149.292929292929,-2.63636363636364)(164.222222222222,-2.57575757575758)(171.686868686869,-2.54545454545455)(179.151515151515,-2.51515151515151)(194.080808080808,-2.45454545454545)(209.010101010101,-2.39393939393939)(216.474747474747,-2.36363636363636)(223.939393939394,-2.33333333333333)(238.868686868687,-2.27272727272727)(253.79797979798,-2.21212121212121)(261.262626262626,-2.18181818181818)(268.727272727273,-2.15151515151515)(283.656565656566,-2.09090909090909)(298.585858585859,-2.03030303030303)(306.050505050505,-2)(313.515151515152,-1.96969696969697)(328.444444444444,-1.90909090909091)(343.373737373737,-1.84848484848485)(350.838383838384,-1.81818181818182)(358.30303030303,-1.78787878787879)(373.232323232323,-1.72727272727273)(388.161616161616,-1.72727272727273)(403.090909090909,-1.72727272727273)(418.020202020202,-1.72727272727273)(432.949494949495,-1.72727272727273)(447.878787878788,-1.72727272727273)(462.808080808081,-1.72727272727273)(477.737373737374,-1.78787878787879)(485.20202020202,-1.81818181818182)(492.666666666667,-1.84848484848485)(507.59595959596,-1.90909090909091)(522.525252525253,-1.96969696969697)(526.257575757576,-2)(537.454545454546,-2.09090909090909)(548.651515151515,-2.18181818181818)(552.383838383838,-2.21212121212121)(567.313131313131,-2.33333333333333)(571.045454545455,-2.36363636363636)(582.242424242424,-2.45454545454545)(589.707070707071,-2.54545454545455)(597.171717171717,-2.63636363636364)(604.636363636364,-2.72727272727273)(612.10101010101,-2.81818181818182)(619.565656565657,-2.90909090909091)(627.030303030303,-3.04545454545455)(629.518518518518,-3.09090909090909)(634.494949494949,-3.27272727272727)(629.518518518518,-3.45454545454546)(627.030303030303,-3.5)(615.833333333333,-3.63636363636364)(612.10101010101,-3.66666666666667)(597.171717171717,-3.78787878787879)(589.707070707071,-3.81818181818182)(582.242424242424,-3.84848484848485)(567.313131313131,-3.90909090909091)(552.383838383838,-3.96969696969697)(544.919191919192,-4)(537.454545454546,-4.03030303030303)(522.525252525253,-4.09090909090909)(507.59595959596,-4.15151515151515)(500.131313131313,-4.18181818181818)(492.666666666667,-4.21212121212121)(477.737373737374,-4.27272727272727)(462.808080808081,-4.27272727272727)(447.878787878788,-4.33333333333333)(440.414141414141,-4.36363636363636)(432.949494949495,-4.39393939393939)(418.020202020202,-4.45454545454545)(403.090909090909,-4.45454545454545)(388.161616161616,-4.51515151515151)(380.69696969697,-4.54545454545455)(373.232323232323,-4.57575757575758)(358.30303030303,-4.63636363636364)(343.373737373737,-4.63636363636364)(328.444444444444,-4.63636363636364)(313.515151515152,-4.6969696969697)(306.050505050505,-4.72727272727273)(298.585858585859,-4.75757575757576)(283.656565656566,-4.75757575757576)(276.191919191919,-4.72727272727273)(268.727272727273,-4.6969696969697)(253.79797979798,-4.63636363636364)(238.868686868687,-4.63636363636364)(223.939393939394,-4.57575757575758)(216.474747474747,-4.54545454545455)(209.010101010101,-4.51515151515151)(194.080808080808,-4.39393939393939)(186.616161616162,-4.36363636363636)(179.151515151515,-4.33333333333333)(164.222222222222,-4.21212121212121)(156.757575757576,-4.18181818181818)(149.292929292929,-4.15151515151515)(134.363636363636,-4.09090909090909)(119.434343434343,-4.03030303030303)(111.969696969697,-4)(104.505050505051,-3.96969696969697)(89.5757575757576,-3.90909090909091)(74.6464646464647,-3.84848484848485)(67.1818181818182,-3.81818181818182)(59.7171717171717,-3.78787878787879)(44.7878787878788,-3.72727272727273)(29.8585858585859,-3.72727272727273)(14.9292929292929,-3.72727272727273)(0,-3.72727272727273)(-0.000124406627521346,-3.63636363636364)(-0.000373213662548569,-3.45454545454546)(-0.000373213662548569,-3.27272727272727)(-0.000373213662548569,-3.09090909090909)(-0.000124406627521346,-2.90909090909091)(0,-2.81818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1343.63636363636,-9.18181818181818)(1346.12457912458,-9.27272727272727)(1343.63636363636,-9.36363636363636)(1341.14814814815,-9.45454545454546)(1328.70707070707,-9.60606060606061)(1321.24242424242,-9.63636363636364)(1313.77777777778,-9.66666666666667)(1298.84848484848,-9.72727272727273)(1283.91919191919,-9.72727272727273)(1268.9898989899,-9.72727272727273)(1254.06060606061,-9.78787878787879)(1246.59595959596,-9.81818181818182)(1239.13131313131,-9.84848484848485)(1224.20202020202,-9.90909090909091)(1209.27272727273,-9.90909090909091)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.90909090909091)(1149.55555555556,-9.90909090909091)(1134.62626262626,-9.90909090909091)(1119.69696969697,-9.90909090909091)(1104.76767676768,-9.90909090909091)(1089.83838383838,-9.90909090909091)(1074.90909090909,-9.90909090909091)(1059.9797979798,-9.90909090909091)(1045.05050505051,-9.90909090909091)(1030.12121212121,-9.88636363636364)(1015.19191919192,-9.84090909090909)(1007.72727272727,-9.81818181818182)(1000.26262626263,-9.78787878787879)(985.333333333333,-9.72727272727273)(970.40404040404,-9.72727272727273)(955.474747474747,-9.72727272727273)(940.545454545455,-9.72727272727273)(925.616161616162,-9.66666666666667)(918.151515151515,-9.63636363636364)(910.686868686869,-9.60606060606061)(895.757575757576,-9.54545454545455)(880.828282828283,-9.48484848484848)(865.89898989899,-9.48484848484848)(862.166666666667,-9.45454545454546)(850.969696969697,-9.36363636363636)(836.040404040404,-9.3030303030303)(833.552188552189,-9.27272727272727)(821.111111111111,-9.12121212121212)(817.378787878788,-9.09090909090909)(806.181818181818,-8.95454545454546)(803.693602693603,-8.90909090909091)(798.717171717172,-8.72727272727273)(798.717171717172,-8.54545454545455)(806.181818181818,-8.40909090909091)(808.670033670034,-8.36363636363636)(821.111111111111,-8.21212121212121)(824.843434343434,-8.18181818181818)(836.040404040404,-8.09090909090909)(847.237373737374,-8)(850.969696969697,-7.95454545454546)(865.89898989899,-7.86363636363636)(873.363636363636,-7.81818181818182)(880.828282828283,-7.78787878787879)(895.757575757576,-7.78787878787879)(910.686868686869,-7.72727272727273)(925.616161616162,-7.72727272727273)(940.545454545455,-7.72727272727273)(955.474747474747,-7.72727272727273)(970.40404040404,-7.72727272727273)(985.333333333333,-7.66666666666667)(1000.26262626263,-7.66666666666667)(1015.19191919192,-7.66666666666667)(1030.12121212121,-7.72727272727273)(1045.05050505051,-7.72727272727273)(1059.9797979798,-7.72727272727273)(1074.90909090909,-7.75)(1089.83838383838,-7.75)(1104.76767676768,-7.75)(1119.69696969697,-7.78787878787879)(1127.16161616162,-7.81818181818182)(1134.62626262626,-7.84848484848485)(1149.55555555556,-7.90909090909091)(1164.48484848485,-7.90909090909091)(1179.41414141414,-7.96969696969697)(1186.87878787879,-8)(1194.34343434343,-8.03030303030303)(1209.27272727273,-8.09090909090909)(1224.20202020202,-8.09090909090909)(1239.13131313131,-8.15151515151515)(1246.59595959596,-8.18181818181818)(1254.06060606061,-8.21212121212121)(1268.9898989899,-8.33333333333333)(1272.72222222222,-8.36363636363636)(1283.91919191919,-8.45454545454545)(1295.11616161616,-8.54545454545455)(1298.84848484848,-8.57575757575757)(1313.77777777778,-8.6969696969697)(1317.5101010101,-8.72727272727273)(1328.70707070707,-8.86363636363636)(1331.19528619529,-8.90909090909091)(1341.14814814815,-9.09090909090909)(1343.63636363636,-9.18181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (462.808080808081,-14.6818181818182)(470.272727272727,-14.5454545454545)(477.737373737374,-14.4545454545455)(488.934343434343,-14.3636363636364)(492.666666666667,-14.3333333333333)(507.59595959596,-14.2727272727273)(522.525252525253,-14.2727272727273)(537.454545454546,-14.2727272727273)(552.383838383838,-14.2727272727273)(567.313131313131,-14.2727272727273)(582.242424242424,-14.2727272727273)(597.171717171717,-14.2727272727273)(612.10101010101,-14.2727272727273)(627.030303030303,-14.2727272727273)(641.959595959596,-14.2727272727273)(656.888888888889,-14.2727272727273)(671.818181818182,-14.2727272727273)(686.747474747475,-14.3181818181818)(690.479797979798,-14.3636363636364)(690.479797979798,-14.5454545454545)(686.747474747475,-14.5757575757576)(671.818181818182,-14.6969696969697)(664.353535353535,-14.7272727272727)(656.888888888889,-14.7575757575758)(641.959595959596,-14.8787878787879)(634.494949494949,-14.9090909090909)(627.030303030303,-14.9393939393939)(612.10101010101,-15.0606060606061)(604.636363636364,-15.0909090909091)(597.171717171717,-15.1212121212121)(582.242424242424,-15.1818181818182)(567.313131313131,-15.2424242424242)(559.848484848485,-15.2727272727273)(552.383838383838,-15.3030303030303)(537.454545454546,-15.3636363636364)(522.525252525253,-15.3636363636364)(507.59595959596,-15.3636363636364)(492.666666666667,-15.3636363636364)(477.737373737374,-15.3030303030303)(474.005050505051,-15.2727272727273)(462.808080808081,-15.1363636363636)(460.319865319865,-15.0909090909091)(455.343434343434,-14.9090909090909)(460.319865319865,-14.7272727272727)(462.808080808081,-14.6818181818182)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-17.5454545454545)(1478.00012440663,-17.6363636363636)(1478.00037321366,-17.8181818181818)(1478.00037321366,-18)(1478,-18.0000045452273)(1463.07070707071,-18.0000045452273)(1448.14141414141,-18.0000045452273)(1433.21212121212,-18.0000045452273)(1418.28282828283,-18.0000045452273)(1403.35353535354,-18.0000035351964)(1388.42424242424,-18.0000025251543)(1375.98316498317,-18)(1388.42424242424,-17.8484848484848)(1395.88888888889,-17.8181818181818)(1403.35353535354,-17.7878787878788)(1418.28282828283,-17.7272727272727)(1433.21212121212,-17.7272727272727)(1448.14141414141,-17.6666666666667)(1455.60606060606,-17.6363636363636)(1463.07070707071,-17.6060606060606)(1478,-17.5454545454545)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_60.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478.0002488174,-8.54545454545455)(1478.00049762651,-8.72727272727273)(1478.00074642733,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00074642733,-9.27272727272727)(1478.00074642733,-9.45454545454546)(1478.00074642733,-9.63636363636364)(1478.00074642733,-9.81818181818182)(1478.00058056104,-10)(1478.00033175469,-10.1818181818182)(1478.00008294006,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478.0002488174,-17.4545454545455)(1478.00049762651,-17.6363636363636)(1478.00074642733,-17.8181818181818)(1478.00074642733,-18)(1478,-18.0000090904546)(1463.07070707071,-18.0000090904546)(1448.14141414141,-18.0000090904546)(1433.21212121212,-18.0000090904546)(1418.28282828283,-18.0000090904546)(1403.35353535354,-18.000008080449)(1388.42424242424,-18.0000070704321)(1373.49494949495,-18.0000040403143)(1358.56565656566,-18.0000020201796)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(-0.000248817401863321,-8)(-0.000497626510092015,-7.81818181818182)(-0.000746427325097138,-7.63636363636364)(-0.000746427325097138,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000497626510092015,-7.09090909090909)(-0.000248817401863321,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(-0.000248817401863321,-3.81818181818182)(-0.000497626510092015,-3.63636363636364)(-0.000746427325097138,-3.45454545454546)(-0.000746427325097138,-3.27272727272727)(-0.000746427325097138,-3.09090909090909)(-0.000497626510092015,-2.90909090909091)(-0.000248817401863321,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-7)(14.9292929292929,-7)(29.8585858585859,-7)(44.7878787878788,-7)(59.7171717171717,-7)(74.6464646464647,-7)(89.5757575757576,-7)(104.505050505051,-7)(119.434343434343,-7)(134.363636363636,-7)(149.292929292929,-7)(164.222222222222,-7.06060606060606)(171.686868686869,-7.09090909090909)(179.151515151515,-7.12121212121212)(194.080808080808,-7.18181818181818)(209.010101010101,-7.18181818181818)(223.939393939394,-7.18181818181818)(238.868686868687,-7.18181818181818)(253.79797979798,-7.24242424242424)(261.262626262626,-7.27272727272727)(268.727272727273,-7.3030303030303)(283.656565656566,-7.36363636363636)(298.585858585859,-7.36363636363636)(313.515151515152,-7.36363636363636)(328.444444444444,-7.36363636363636)(343.373737373737,-7.36363636363636)(358.30303030303,-7.36363636363636)(373.232323232323,-7.36363636363636)(388.161616161616,-7.36363636363636)(403.090909090909,-7.36363636363636)(418.020202020202,-7.36363636363636)(432.949494949495,-7.3030303030303)(440.414141414141,-7.27272727272727)(447.878787878788,-7.24242424242424)(462.808080808081,-7.18181818181818)(477.737373737374,-7.18181818181818)(492.666666666667,-7.18181818181818)(507.59595959596,-7.18181818181818)(522.525252525253,-7.18181818181818)(537.454545454546,-7.18181818181818)(552.383838383838,-7.15909090909091)(567.313131313131,-7.18181818181818)(582.242424242424,-7.18181818181818)(597.171717171717,-7.22727272727273)(612.10101010101,-7.18181818181818)(627.030303030303,-7.18181818181818)(641.959595959596,-7.18181818181818)(656.888888888889,-7.24242424242424)(664.353535353535,-7.27272727272727)(671.818181818182,-7.3030303030303)(686.747474747475,-7.36363636363636)(701.676767676768,-7.42424242424243)(709.141414141414,-7.45454545454546)(716.606060606061,-7.48484848484849)(731.535353535354,-7.54545454545455)(746.464646464646,-7.60606060606061)(761.393939393939,-7.60606060606061)(768.858585858586,-7.63636363636364)(776.323232323232,-7.66666666666667)(783.787878787879,-7.63636363636364)(791.252525252525,-7.59090909090909)(806.181818181818,-7.59090909090909)(821.111111111111,-7.54545454545455)(836.040404040404,-7.48484848484849)(839.772727272727,-7.45454545454546)(850.969696969697,-7.38636363636364)(865.89898989899,-7.34090909090909)(880.828282828283,-7.34090909090909)(895.757575757576,-7.3030303030303)(910.686868686869,-7.3030303030303)(918.151515151515,-7.27272727272727)(925.616161616162,-7.22727272727273)(940.545454545455,-7.22727272727273)(955.474747474747,-7.18181818181818)(970.40404040404,-7.18181818181818)(985.333333333333,-7.18181818181818)(1000.26262626263,-7.12121212121212)(1007.72727272727,-7.09090909090909)(1015.19191919192,-7.06060606060606)(1030.12121212121,-7)(1045.05050505051,-7)(1059.9797979798,-7)(1074.90909090909,-7)(1089.83838383838,-7.06060606060606)(1097.30303030303,-7.09090909090909)(1104.76767676768,-7.12121212121212)(1119.69696969697,-7.15909090909091)(1134.62626262626,-7.24242424242424)(1142.09090909091,-7.27272727272727)(1149.55555555556,-7.3030303030303)(1164.48484848485,-7.36363636363636)(1179.41414141414,-7.40909090909091)(1186.87878787879,-7.45454545454546)(1194.34343434343,-7.48484848484849)(1209.27272727273,-7.54545454545455)(1224.20202020202,-7.54545454545455)(1239.13131313131,-7.54545454545455)(1254.06060606061,-7.54545454545455)(1268.9898989899,-7.54545454545455)(1283.91919191919,-7.54545454545455)(1298.84848484848,-7.60606060606061)(1306.31313131313,-7.63636363636364)(1313.77777777778,-7.66666666666667)(1328.70707070707,-7.72727272727273)(1343.63636363636,-7.72727272727273)(1358.56565656566,-7.78787878787879)(1366.0303030303,-7.81818181818182)(1373.49494949495,-7.84848484848485)(1388.42424242424,-7.96969696969697)(1392.15656565657,-8)(1403.35353535354,-8.09090909090909)(1414.5505050505,-8.18181818181818)(1418.28282828283,-8.21212121212121)(1433.21212121212,-8.33333333333333)(1436.94444444444,-8.36363636363636)(1448.14141414141,-8.45454545454545)(1459.33838383838,-8.54545454545455)(1463.07070707071,-8.57575757575757)(1478,-8.63636363636364)(1478.00012440663,-8.72727272727273)(1478.00037321366,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00037321366,-9.27272727272727)(1478.00037321366,-9.45454545454546)(1478.00037321366,-9.63636363636364)(1478.00037321366,-9.81818181818182)(1478.00020734323,-10)(1478,-10.1515151515152)(1470.53535353535,-10.1818181818182)(1463.07070707071,-10.2121212121212)(1448.14141414141,-10.3333333333333)(1440.67676767677,-10.3636363636364)(1433.21212121212,-10.3939393939394)(1418.28282828283,-10.4545454545455)(1403.35353535354,-10.5151515151515)(1395.88888888889,-10.5454545454545)(1388.42424242424,-10.5757575757576)(1373.49494949495,-10.6969696969697)(1366.0303030303,-10.7272727272727)(1358.56565656566,-10.7575757575758)(1343.63636363636,-10.8181818181818)(1328.70707070707,-10.8181818181818)(1313.77777777778,-10.8181818181818)(1298.84848484848,-10.8181818181818)(1283.91919191919,-10.7575757575758)(1276.45454545455,-10.7272727272727)(1268.9898989899,-10.6969696969697)(1254.06060606061,-10.5757575757576)(1239.13131313131,-10.5757575757576)(1224.20202020202,-10.5757575757576)(1209.27272727273,-10.6363636363636)(1194.34343434343,-10.6363636363636)(1179.41414141414,-10.6363636363636)(1164.48484848485,-10.6363636363636)(1149.55555555556,-10.5909090909091)(1134.62626262626,-10.5909090909091)(1119.69696969697,-10.5909090909091)(1104.76767676768,-10.5757575757576)(1097.30303030303,-10.5454545454545)(1089.83838383838,-10.5151515151515)(1074.90909090909,-10.4545454545455)(1059.9797979798,-10.4545454545455)(1045.05050505051,-10.4772727272727)(1030.12121212121,-10.4545454545455)(1015.19191919192,-10.4545454545455)(1000.26262626263,-10.4090909090909)(985.333333333333,-10.3939393939394)(977.868686868687,-10.3636363636364)(970.40404040404,-10.3333333333333)(955.474747474747,-10.2727272727273)(940.545454545455,-10.2727272727273)(929.348484848485,-10.1818181818182)(925.616161616162,-10.1515151515152)(910.686868686869,-10.0909090909091)(895.757575757576,-10.030303030303)(880.828282828283,-10.0454545454545)(873.363636363636,-10)(865.89898989899,-9.96969696969697)(850.969696969697,-9.90909090909091)(836.040404040404,-9.90909090909091)(821.111111111111,-9.84848484848485)(813.646464646465,-9.81818181818182)(806.181818181818,-9.78787878787879)(791.252525252525,-9.66666666666667)(787.520202020202,-9.63636363636364)(776.323232323232,-9.54545454545455)(768.858585858586,-9.45454545454546)(761.393939393939,-9.36363636363636)(753.929292929293,-9.27272727272727)(746.464646464646,-9.18181818181818)(739,-9.09090909090909)(731.535353535354,-9)(724.070707070707,-8.90909090909091)(716.606060606061,-8.81818181818182)(705.409090909091,-8.72727272727273)(701.676767676768,-8.6969696969697)(686.747474747475,-8.6969696969697)(679.282828282828,-8.72727272727273)(671.818181818182,-8.75757575757576)(656.888888888889,-8.81818181818182)(641.959595959596,-8.81818181818182)(627.030303030303,-8.87878787878788)(619.565656565657,-8.90909090909091)(612.10101010101,-8.93939393939394)(597.171717171717,-9)(582.242424242424,-9)(567.313131313131,-9.06060606060606)(559.848484848485,-9.09090909090909)(552.383838383838,-9.12121212121212)(537.454545454546,-9.18181818181818)(522.525252525253,-9.20454545454546)(507.59595959596,-9.20454545454546)(492.666666666667,-9.25)(477.737373737374,-9.24242424242424)(462.808080808081,-9.24242424242424)(447.878787878788,-9.18181818181818)(436.681818181818,-9.09090909090909)(432.949494949495,-9.06060606060606)(418.020202020202,-9)(403.090909090909,-8.93939393939394)(388.161616161616,-9)(373.232323232323,-9)(358.30303030303,-9)(343.373737373737,-9)(328.444444444444,-9)(313.515151515152,-9)(298.585858585859,-9.06060606060606)(291.121212121212,-9.09090909090909)(283.656565656566,-9.12121212121212)(268.727272727273,-9.24242424242424)(264.99494949495,-9.27272727272727)(253.79797979798,-9.36363636363636)(242.60101010101,-9.45454545454546)(238.868686868687,-9.48484848484848)(223.939393939394,-9.54545454545455)(209.010101010101,-9.60606060606061)(201.545454545455,-9.63636363636364)(194.080808080808,-9.66666666666667)(179.151515151515,-9.72727272727273)(164.222222222222,-9.72727272727273)(149.292929292929,-9.66666666666667)(145.560606060606,-9.63636363636364)(134.363636363636,-9.5)(131.875420875421,-9.45454545454546)(126.89898989899,-9.27272727272727)(121.922558922559,-9.09090909090909)(119.434343434343,-9)(116.946127946128,-8.90909090909091)(111.969696969697,-8.72727272727273)(106.993265993266,-8.54545454545455)(104.505050505051,-8.5)(97.040404040404,-8.36363636363636)(89.5757575757576,-8.27272727272727)(78.3787878787879,-8.18181818181818)(74.6464646464647,-8.15151515151515)(59.7171717171717,-8.09090909090909)(44.7878787878788,-8.03030303030303)(37.3232323232323,-8)(29.8585858585859,-7.96969696969697)(14.9292929292929,-7.90909090909091)(0,-7.90909090909091)(-0.000124406627521346,-7.81818181818182)(-0.000373213662548569,-7.63636363636364)(-0.000373213662548569,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000124406627521346,-7.09090909090909)(0,-7)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1388.42424242424,-9.22727272727273)(1390.91245791246,-9.27272727272727)(1395.88888888889,-9.45454545454546)(1388.42424242424,-9.59090909090909)(1385.93602693603,-9.63636363636364)(1375.98316498317,-9.81818181818182)(1373.49494949495,-9.86363636363636)(1358.56565656566,-9.95454545454546)(1351.10101010101,-10)(1343.63636363636,-10.030303030303)(1339.90404040404,-10)(1328.70707070707,-9.90909090909091)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.90909090909091)(1283.91919191919,-9.90909090909091)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.90909090909091)(1239.13131313131,-9.90909090909091)(1224.20202020202,-9.90909090909091)(1209.27272727273,-9.90909090909091)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.90909090909091)(1149.55555555556,-9.90909090909091)(1134.62626262626,-9.90909090909091)(1119.69696969697,-9.90909090909091)(1104.76767676768,-9.90909090909091)(1089.83838383838,-9.90909090909091)(1074.90909090909,-9.90909090909091)(1059.9797979798,-9.90909090909091)(1045.05050505051,-9.95454545454546)(1030.12121212121,-9.90909090909091)(1015.19191919192,-9.90909090909091)(1000.26262626263,-9.88636363636364)(985.333333333333,-9.90909090909091)(970.40404040404,-9.90909090909091)(955.474747474747,-9.84848484848485)(948.010101010101,-9.81818181818182)(940.545454545455,-9.78787878787879)(925.616161616162,-9.70454545454546)(910.686868686869,-9.70454545454546)(895.757575757576,-9.65909090909091)(892.025252525252,-9.63636363636364)(880.828282828283,-9.56818181818182)(865.89898989899,-9.52272727272727)(854.70202020202,-9.45454545454546)(850.969696969697,-9.42424242424243)(836.040404040404,-9.3030303030303)(833.552188552189,-9.27272727272727)(821.111111111111,-9.12121212121212)(817.378787878788,-9.09090909090909)(806.181818181818,-8.95454545454546)(804.315656565657,-8.90909090909091)(800.583333333333,-8.72727272727273)(798.717171717172,-8.54545454545455)(806.181818181818,-8.40909090909091)(808.670033670034,-8.36363636363636)(821.111111111111,-8.21212121212121)(824.843434343434,-8.18181818181818)(836.040404040404,-8.09090909090909)(847.237373737374,-8)(850.969696969697,-7.95454545454546)(865.89898989899,-7.86363636363636)(873.363636363636,-7.81818181818182)(880.828282828283,-7.78787878787879)(895.757575757576,-7.78787878787879)(910.686868686869,-7.75)(925.616161616162,-7.75)(940.545454545455,-7.75)(955.474747474747,-7.66666666666667)(962.939393939394,-7.63636363636364)(970.40404040404,-7.60606060606061)(985.333333333333,-7.54545454545455)(1000.26262626263,-7.54545454545455)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.54545454545455)(1059.9797979798,-7.60606060606061)(1063.71212121212,-7.63636363636364)(1074.90909090909,-7.70454545454546)(1089.83838383838,-7.72727272727273)(1104.76767676768,-7.72727272727273)(1119.69696969697,-7.68181818181818)(1134.62626262626,-7.72727272727273)(1149.55555555556,-7.78787878787879)(1157.0202020202,-7.81818181818182)(1164.48484848485,-7.84848484848485)(1179.41414141414,-7.93181818181818)(1194.34343434343,-7.94545454545455)(1209.27272727273,-7.98181818181818)(1216.73737373737,-8)(1224.20202020202,-8.03030303030303)(1239.13131313131,-8.09090909090909)(1254.06060606061,-8.09090909090909)(1268.9898989899,-8.15151515151515)(1276.45454545455,-8.18181818181818)(1283.91919191919,-8.21212121212121)(1298.84848484848,-8.33333333333333)(1306.31313131313,-8.36363636363636)(1313.77777777778,-8.39393939393939)(1328.70707070707,-8.5)(1332.43939393939,-8.54545454545455)(1343.63636363636,-8.63636363636364)(1351.10101010101,-8.72727272727273)(1358.56565656566,-8.81818181818182)(1366.0303030303,-8.90909090909091)(1373.49494949495,-9)(1380.9595959596,-9.09090909090909)(1388.42424242424,-9.22727272727273)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-2.81818181818182)(14.9292929292929,-2.81818181818182)(29.8585858585859,-2.81818181818182)(44.7878787878788,-2.81818181818182)(59.7171717171717,-2.81818181818182)(74.6464646464647,-2.81818181818182)(89.5757575757576,-2.81818181818182)(104.505050505051,-2.81818181818182)(119.434343434343,-2.81818181818182)(134.363636363636,-2.81818181818182)(149.292929292929,-2.75757575757576)(156.757575757576,-2.72727272727273)(164.222222222222,-2.6969696969697)(179.151515151515,-2.63636363636364)(194.080808080808,-2.57575757575758)(201.545454545455,-2.54545454545455)(209.010101010101,-2.51515151515151)(223.939393939394,-2.45454545454545)(238.868686868687,-2.45454545454545)(253.79797979798,-2.39393939393939)(261.262626262626,-2.36363636363636)(268.727272727273,-2.33333333333333)(283.656565656566,-2.27272727272727)(298.585858585859,-2.21212121212121)(306.050505050505,-2.18181818181818)(313.515151515152,-2.15151515151515)(328.444444444444,-2.09090909090909)(343.373737373737,-2.03030303030303)(350.838383838384,-2)(358.30303030303,-1.96969696969697)(373.232323232323,-1.90909090909091)(388.161616161616,-1.90909090909091)(403.090909090909,-1.90909090909091)(418.020202020202,-1.90909090909091)(432.949494949495,-1.90909090909091)(447.878787878788,-1.90909090909091)(462.808080808081,-1.90909090909091)(477.737373737374,-1.90909090909091)(492.666666666667,-1.96969696969697)(500.131313131313,-2)(507.59595959596,-2.03030303030303)(522.525252525253,-2.15151515151515)(526.257575757576,-2.18181818181818)(537.454545454546,-2.27272727272727)(548.651515151515,-2.36363636363636)(552.383838383838,-2.39393939393939)(567.313131313131,-2.51515151515151)(571.045454545455,-2.54545454545455)(582.242424242424,-2.68181818181818)(584.73063973064,-2.72727272727273)(594.683501683502,-2.90909090909091)(597.171717171717,-3)(599.659932659933,-3.09090909090909)(599.659932659933,-3.27272727272727)(597.171717171717,-3.31818181818182)(589.707070707071,-3.45454545454546)(582.242424242424,-3.54545454545455)(571.045454545455,-3.63636363636364)(567.313131313131,-3.66666666666667)(552.383838383838,-3.78787878787879)(544.919191919192,-3.81818181818182)(537.454545454546,-3.84848484848485)(522.525252525253,-3.90909090909091)(507.59595959596,-3.90909090909091)(492.666666666667,-3.90909090909091)(477.737373737374,-3.96969696969697)(470.272727272727,-4)(462.808080808081,-4.03030303030303)(447.878787878788,-4.09090909090909)(432.949494949495,-4.09090909090909)(418.020202020202,-4.09090909090909)(403.090909090909,-4.09090909090909)(388.161616161616,-4.15151515151515)(380.69696969697,-4.18181818181818)(373.232323232323,-4.21212121212121)(358.30303030303,-4.27272727272727)(343.373737373737,-4.27272727272727)(328.444444444444,-4.27272727272727)(313.515151515152,-4.27272727272727)(298.585858585859,-4.27272727272727)(283.656565656566,-4.27272727272727)(268.727272727273,-4.27272727272727)(253.79797979798,-4.27272727272727)(238.868686868687,-4.21212121212121)(231.40404040404,-4.18181818181818)(223.939393939394,-4.15151515151515)(209.010101010101,-4.09090909090909)(194.080808080808,-4.09090909090909)(179.151515151515,-4.03030303030303)(171.686868686869,-4)(164.222222222222,-3.96969696969697)(149.292929292929,-3.90909090909091)(134.363636363636,-3.84848484848485)(126.89898989899,-3.81818181818182)(119.434343434343,-3.78787878787879)(104.505050505051,-3.72727272727273)(89.5757575757576,-3.72727272727273)(74.6464646464647,-3.72727272727273)(59.7171717171717,-3.72727272727273)(44.7878787878788,-3.72727272727273)(29.8585858585859,-3.72727272727273)(14.9292929292929,-3.72727272727273)(0,-3.72727272727273)(-0.000124406627521346,-3.63636363636364)(-0.000373213662548569,-3.45454545454546)(-0.000373213662548569,-3.27272727272727)(-0.000373213662548569,-3.09090909090909)(-0.000124406627521346,-2.90909090909091)(0,-2.81818181818182)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (462.808080808081,-14.6818181818182)(470.272727272727,-14.5454545454545)(477.737373737374,-14.4545454545455)(488.934343434343,-14.3636363636364)(492.666666666667,-14.3333333333333)(507.59595959596,-14.2727272727273)(522.525252525253,-14.2727272727273)(537.454545454546,-14.2727272727273)(552.383838383838,-14.2727272727273)(567.313131313131,-14.2727272727273)(582.242424242424,-14.2727272727273)(597.171717171717,-14.2727272727273)(612.10101010101,-14.2727272727273)(627.030303030303,-14.2727272727273)(641.959595959596,-14.2727272727273)(656.888888888889,-14.2727272727273)(671.818181818182,-14.2727272727273)(686.747474747475,-14.3181818181818)(690.479797979798,-14.3636363636364)(690.479797979798,-14.5454545454545)(686.747474747475,-14.5757575757576)(671.818181818182,-14.6969696969697)(664.353535353535,-14.7272727272727)(656.888888888889,-14.7575757575758)(641.959595959596,-14.8787878787879)(634.494949494949,-14.9090909090909)(627.030303030303,-14.9393939393939)(612.10101010101,-15.0606060606061)(604.636363636364,-15.0909090909091)(597.171717171717,-15.1212121212121)(582.242424242424,-15.1818181818182)(567.313131313131,-15.2424242424242)(559.848484848485,-15.2727272727273)(552.383838383838,-15.3030303030303)(537.454545454546,-15.3636363636364)(522.525252525253,-15.3636363636364)(507.59595959596,-15.3636363636364)(492.666666666667,-15.3636363636364)(477.737373737374,-15.3030303030303)(474.005050505051,-15.2727272727273)(462.808080808081,-15.1363636363636)(460.319865319865,-15.0909090909091)(455.343434343434,-14.9090909090909)(460.319865319865,-14.7272727272727)(462.808080808081,-14.6818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (462.808080808081,-7.95454545454546)(474.005050505051,-7.81818181818182)(477.737373737374,-7.78787878787879)(492.666666666667,-7.72727272727273)(507.59595959596,-7.72727272727273)(522.525252525253,-7.72727272727273)(537.454545454546,-7.72727272727273)(552.383838383838,-7.77272727272727)(556.116161616162,-7.81818181818182)(567.313131313131,-7.95454545454546)(569.801346801347,-8)(567.313131313131,-8.09090909090909)(563.580808080808,-8.18181818181818)(552.383838383838,-8.27272727272727)(537.454545454546,-8.33333333333333)(529.989898989899,-8.36363636363636)(522.525252525253,-8.39393939393939)(507.59595959596,-8.45454545454545)(492.666666666667,-8.45454545454545)(477.737373737374,-8.45454545454545)(466.540404040404,-8.36363636363636)(462.808080808081,-8.31818181818182)(455.343434343434,-8.18181818181818)(460.319865319865,-8)(462.808080808081,-7.95454545454546)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-17.5454545454545)(1478.00012440663,-17.6363636363636)(1478.00037321366,-17.8181818181818)(1478.00037321366,-18)(1478,-18.0000045452273)(1463.07070707071,-18.0000045452273)(1448.14141414141,-18.0000045452273)(1433.21212121212,-18.0000045452273)(1418.28282828283,-18.0000045452273)(1403.35353535354,-18.0000035351964)(1388.42424242424,-18.0000025251543)(1375.98316498317,-18)(1388.42424242424,-17.8484848484848)(1395.88888888889,-17.8181818181818)(1403.35353535354,-17.7878787878788)(1418.28282828283,-17.7272727272727)(1433.21212121212,-17.7272727272727)(1448.14141414141,-17.6666666666667)(1455.60606060606,-17.6363636363636)(1463.07070707071,-17.6060606060606)(1478,-17.5454545454545)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/limno_bgape_class_80.tex
LSE algorithm

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478.0002488174,-8.54545454545455)(1478.00049762651,-8.72727272727273)(1478.00074642733,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00066349464,-9.27272727272727)(1478.00066349464,-9.45454545454546)(1478.00066349464,-9.63636363636364)(1478.00074642733,-9.81818181818182)(1478.00049762651,-10)(1478.0002488174,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478.0002488174,-17.4545454545455)(1478.00049762651,-17.6363636363636)(1478.00074642733,-17.8181818181818)(1478.00074642733,-18)(1478,-18.0000090904546)(1463.07070707071,-18.0000090904546)(1448.14141414141,-18.0000090904546)(1433.21212121212,-18.0000090904546)(1418.28282828283,-18.0000090904546)(1403.35353535354,-18.000008080449)(1388.42424242424,-18.0000070704321)(1373.49494949495,-18.0000040403143)(1358.56565656566,-18.0000020201796)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(-0.000248817401863321,-8)(-0.000497626510092015,-7.81818181818182)(-0.000746427325097138,-7.63636363636364)(-0.000746427325097138,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000497626510092015,-7.09090909090909)(-0.000248817401863321,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(-0.000248817401863321,-3.81818181818182)(-0.000497626510092015,-3.63636363636364)(-0.000746427325097138,-3.45454545454546)(-0.000746427325097138,-3.27272727272727)(-0.000746427325097138,-3.09090909090909)(-0.000497626510092015,-2.90909090909091)(-0.000248817401863321,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-7)(14.9292929292929,-7)(29.8585858585859,-7)(44.7878787878788,-7)(59.7171717171717,-7)(74.6464646464647,-7)(89.5757575757576,-7)(104.505050505051,-7)(119.434343434343,-7)(134.363636363636,-7)(149.292929292929,-7)(164.222222222222,-7.06060606060606)(171.686868686869,-7.09090909090909)(179.151515151515,-7.12121212121212)(194.080808080808,-7.18181818181818)(209.010101010101,-7.18181818181818)(223.939393939394,-7.18181818181818)(238.868686868687,-7.18181818181818)(253.79797979798,-7.24242424242424)(261.262626262626,-7.27272727272727)(268.727272727273,-7.3030303030303)(283.656565656566,-7.36363636363636)(298.585858585859,-7.36363636363636)(313.515151515152,-7.36363636363636)(328.444444444444,-7.36363636363636)(343.373737373737,-7.36363636363636)(358.30303030303,-7.36363636363636)(373.232323232323,-7.36363636363636)(388.161616161616,-7.36363636363636)(403.090909090909,-7.36363636363636)(418.020202020202,-7.34090909090909)(432.949494949495,-7.29545454545455)(447.878787878788,-7.29545454545455)(455.343434343434,-7.27272727272727)(462.808080808081,-7.22727272727273)(477.737373737374,-7.22727272727273)(492.666666666667,-7.18181818181818)(507.59595959596,-7.18181818181818)(522.525252525253,-7.18181818181818)(537.454545454546,-7.18181818181818)(552.383838383838,-7.15909090909091)(567.313131313131,-7.18181818181818)(582.242424242424,-7.18181818181818)(597.171717171717,-7.22727272727273)(612.10101010101,-7.18181818181818)(627.030303030303,-7.18181818181818)(641.959595959596,-7.18181818181818)(656.888888888889,-7.24242424242424)(660.621212121212,-7.27272727272727)(671.818181818182,-7.36363636363636)(679.282828282828,-7.45454545454546)(686.747474747475,-7.54545454545455)(694.212121212121,-7.63636363636364)(699.188552188552,-7.81818181818182)(701.676767676768,-7.86363636363636)(712.873737373737,-8)(716.606060606061,-8.04545454545455)(731.535353535354,-8.09090909090909)(746.464646464646,-8.09090909090909)(761.393939393939,-8.09090909090909)(776.323232323232,-8.03030303030303)(791.252525252525,-8.02272727272727)(793.740740740741,-8)(806.181818181818,-7.88636363636364)(817.378787878788,-7.81818181818182)(821.111111111111,-7.77272727272727)(832.308080808081,-7.63636363636364)(836.040404040404,-7.60606060606061)(850.969696969697,-7.48484848484849)(858.434343434343,-7.45454545454546)(865.89898989899,-7.43181818181818)(880.828282828283,-7.38636363636364)(895.757575757576,-7.3030303030303)(910.686868686869,-7.3030303030303)(914.419191919192,-7.27272727272727)(925.616161616162,-7.18181818181818)(940.545454545455,-7.18181818181818)(955.474747474748,-7.15909090909091)(970.40404040404,-7.18181818181818)(985.333333333333,-7.18181818181818)(1000.26262626263,-7.12121212121212)(1007.72727272727,-7.09090909090909)(1015.19191919192,-7.06060606060606)(1030.12121212121,-7)(1045.05050505051,-7)(1059.9797979798,-7)(1074.90909090909,-7.06060606060606)(1082.37373737374,-7.09090909090909)(1089.83838383838,-7.11363636363636)(1104.76767676768,-7.18181818181818)(1119.69696969697,-7.20454545454546)(1130.89393939394,-7.27272727272727)(1134.62626262626,-7.3030303030303)(1149.55555555556,-7.36363636363636)(1164.48484848485,-7.36363636363636)(1179.41414141414,-7.40909090909091)(1183.14646464646,-7.45454545454546)(1194.34343434343,-7.54545454545455)(1209.27272727273,-7.60606060606061)(1224.20202020202,-7.60606060606061)(1239.13131313131,-7.52272727272727)(1254.06060606061,-7.52272727272727)(1268.9898989899,-7.52272727272727)(1283.91919191919,-7.54545454545455)(1298.84848484848,-7.60606060606061)(1306.31313131313,-7.63636363636364)(1313.77777777778,-7.68181818181818)(1328.70707070707,-7.77272727272727)(1343.63636363636,-7.77272727272727)(1358.56565656566,-7.78787878787879)(1366.0303030303,-7.81818181818182)(1373.49494949495,-7.84848484848485)(1388.42424242424,-7.96969696969697)(1392.15656565657,-8)(1403.35353535354,-8.13636363636364)(1410.81818181818,-8.18181818181818)(1418.28282828283,-8.21212121212121)(1433.21212121212,-8.33333333333333)(1436.94444444444,-8.36363636363636)(1448.14141414141,-8.45454545454545)(1459.33838383838,-8.54545454545455)(1463.07070707071,-8.57575757575757)(1478,-8.63636363636364)(1478.00012440663,-8.72727272727273)(1478.00037321366,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00029027891,-9.27272727272727)(1478.00029027891,-9.45454545454546)(1478.00029027891,-9.63636363636364)(1478.00037321366,-9.81818181818182)(1478.00012440663,-10)(1478,-10.0909090909091)(1463.07070707071,-10.0909090909091)(1448.14141414141,-10.1515151515152)(1440.67676767677,-10.1818181818182)(1433.21212121212,-10.2121212121212)(1418.28282828283,-10.2272727272727)(1403.35353535354,-10.2272727272727)(1388.42424242424,-10.2272727272727)(1373.49494949495,-10.3409090909091)(1358.56565656566,-10.3409090909091)(1343.63636363636,-10.3409090909091)(1328.70707070707,-10.2727272727273)(1313.77777777778,-10.2727272727273)(1298.84848484848,-10.2727272727273)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2727272727273)(1254.06060606061,-10.2727272727273)(1239.13131313131,-10.2727272727273)(1224.20202020202,-10.2727272727273)(1209.27272727273,-10.2727272727273)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.2121212121212)(1149.55555555556,-10.2121212121212)(1134.62626262626,-10.2121212121212)(1119.69696969697,-10.2121212121212)(1104.76767676768,-10.2727272727273)(1089.83838383838,-10.3333333333333)(1086.10606060606,-10.3636363636364)(1074.90909090909,-10.4545454545455)(1059.9797979798,-10.4545454545455)(1045.05050505051,-10.4772727272727)(1030.12121212121,-10.4545454545455)(1015.19191919192,-10.3939393939394)(1011.4595959596,-10.3636363636364)(1000.26262626263,-10.2727272727273)(985.333333333333,-10.2727272727273)(970.40404040404,-10.2727272727273)(955.474747474747,-10.2727272727273)(944.277777777778,-10.1818181818182)(940.545454545455,-10.1590909090909)(925.616161616162,-10.030303030303)(918.151515151515,-10)(910.686868686869,-9.98484848484848)(903.222222222222,-10)(895.757575757576,-10.030303030303)(888.292929292929,-10)(880.828282828283,-9.97727272727273)(865.89898989899,-9.90909090909091)(850.969696969697,-9.84848484848485)(836.040404040404,-9.84848484848485)(828.575757575758,-9.81818181818182)(821.111111111111,-9.77272727272727)(809.914141414141,-9.63636363636364)(806.181818181818,-9.60606060606061)(791.252525252525,-9.54545454545455)(783.787878787879,-9.45454545454546)(776.323232323232,-9.36363636363636)(768.858585858586,-9.27272727272727)(761.393939393939,-9.13636363636364)(757.661616161616,-9.09090909090909)(746.464646464646,-8.95454545454546)(743.976430976431,-8.90909090909091)(731.535353535354,-8.75757575757576)(727.80303030303,-8.72727272727273)(716.606060606061,-8.63636363636364)(701.676767676768,-8.63636363636364)(686.747474747475,-8.63636363636364)(671.818181818182,-8.6969696969697)(664.353535353535,-8.72727272727273)(656.888888888889,-8.75757575757576)(641.959595959596,-8.81818181818182)(627.030303030303,-8.87878787878788)(619.565656565657,-8.90909090909091)(612.10101010101,-8.93939393939394)(597.171717171717,-9)(582.242424242424,-9)(567.313131313131,-9.06818181818182)(559.848484848485,-9.09090909090909)(552.383838383838,-9.12121212121212)(537.454545454546,-9.18181818181818)(522.525252525253,-9.20454545454546)(507.59595959596,-9.20454545454546)(492.666666666667,-9.25)(477.737373737374,-9.24242424242424)(462.808080808081,-9.18181818181818)(451.611111111111,-9.09090909090909)(447.878787878788,-9.06060606060606)(432.949494949495,-8.93939393939394)(418.020202020202,-8.93939393939394)(410.555555555556,-8.90909090909091)(403.090909090909,-8.86363636363636)(388.161616161616,-8.86363636363636)(373.232323232323,-8.77272727272727)(358.30303030303,-8.81818181818182)(343.373737373737,-8.81818181818182)(328.444444444444,-8.81818181818182)(313.515151515152,-8.84090909090909)(298.585858585859,-8.88636363636364)(294.853535353535,-8.90909090909091)(283.656565656566,-9)(272.459595959596,-9.09090909090909)(268.727272727273,-9.12121212121212)(253.79797979798,-9.24242424242424)(250.065656565657,-9.27272727272727)(238.868686868687,-9.36363636363636)(227.671717171717,-9.45454545454546)(223.939393939394,-9.48484848484848)(209.010101010101,-9.60606060606061)(201.545454545455,-9.63636363636364)(194.080808080808,-9.66666666666667)(179.151515151515,-9.72727272727273)(164.222222222222,-9.72727272727273)(149.292929292929,-9.66666666666667)(145.560606060606,-9.63636363636364)(134.363636363636,-9.5)(131.875420875421,-9.45454545454546)(126.89898989899,-9.27272727272727)(121.922558922559,-9.09090909090909)(119.434343434343,-9)(116.946127946128,-8.90909090909091)(111.969696969697,-8.72727272727273)(106.993265993266,-8.54545454545455)(104.505050505051,-8.5)(97.040404040404,-8.36363636363636)(89.5757575757576,-8.27272727272727)(78.3787878787879,-8.18181818181818)(74.6464646464647,-8.15151515151515)(59.7171717171717,-8.09090909090909)(44.7878787878788,-8.03030303030303)(37.3232323232323,-8)(29.8585858585859,-7.96969696969697)(14.9292929292929,-7.90909090909091)(0,-7.90909090909091)(-0.000124406627521346,-7.81818181818182)(-0.000373213662548569,-7.63636363636364)(-0.000373213662548569,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000124406627521346,-7.09090909090909)(0,-7)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-9)(1407.08585858586,-9.09090909090909)(1414.5505050505,-9.27272727272727)(1410.81818181818,-9.45454545454546)(1403.35353535354,-9.5)(1392.15656565657,-9.63636363636364)(1388.42424242424,-9.65909090909091)(1375.36111111111,-9.81818181818182)(1373.49494949495,-9.86363636363636)(1358.56565656566,-9.95454545454546)(1351.10101010101,-10)(1343.63636363636,-10.0151515151515)(1339.90404040404,-10)(1328.70707070707,-9.90909090909091)(1313.77777777778,-9.90909090909091)(1298.84848484848,-9.90909090909091)(1283.91919191919,-9.90909090909091)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.90909090909091)(1239.13131313131,-9.90909090909091)(1224.20202020202,-9.90909090909091)(1209.27272727273,-9.90909090909091)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.88636363636364)(1149.55555555556,-9.88636363636364)(1134.62626262626,-9.88636363636364)(1119.69696969697,-9.88636363636364)(1104.76767676768,-9.88636363636364)(1089.83838383838,-9.88636363636364)(1074.90909090909,-9.90909090909091)(1059.9797979798,-9.90909090909091)(1045.05050505051,-9.95454545454546)(1030.12121212121,-9.90909090909091)(1015.19191919192,-9.90909090909091)(1000.26262626263,-9.88636363636364)(985.333333333333,-9.90909090909091)(970.40404040404,-9.90909090909091)(955.474747474747,-9.84848484848485)(951.742424242424,-9.81818181818182)(940.545454545455,-9.75)(925.616161616162,-9.69090909090909)(910.686868686869,-9.69090909090909)(895.757575757576,-9.65909090909091)(892.025252525252,-9.63636363636364)(880.828282828283,-9.56818181818182)(865.89898989899,-9.52272727272727)(854.70202020202,-9.45454545454546)(850.969696969697,-9.42424242424243)(838.528619528619,-9.27272727272727)(836.040404040404,-9.24242424242424)(821.111111111111,-9.11363636363636)(817.378787878788,-9.09090909090909)(806.181818181818,-8.95454545454546)(804.315656565657,-8.90909090909091)(800.583333333333,-8.72727272727273)(798.717171717172,-8.54545454545455)(803.693602693603,-8.36363636363636)(806.181818181818,-8.33333333333333)(821.111111111111,-8.20454545454546)(823.599326599327,-8.18181818181818)(836.040404040404,-8.03030303030303)(843.505050505051,-8)(850.969696969697,-7.95454545454546)(865.89898989899,-7.86363636363636)(873.363636363636,-7.81818181818182)(880.828282828283,-7.79545454545455)(895.757575757576,-7.78787878787879)(910.686868686869,-7.75)(925.616161616162,-7.72727272727273)(940.545454545455,-7.66666666666667)(944.277777777778,-7.63636363636364)(955.474747474747,-7.54545454545455)(970.40404040404,-7.54545454545455)(985.333333333333,-7.54545454545455)(1000.26262626263,-7.54545454545455)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.54545454545455)(1059.9797979798,-7.48484848484849)(1074.90909090909,-7.60606060606061)(1089.83838383838,-7.60606060606061)(1093.57070707071,-7.63636363636364)(1104.76767676768,-7.72727272727273)(1119.69696969697,-7.68181818181818)(1134.62626262626,-7.72727272727273)(1149.55555555556,-7.78787878787879)(1157.0202020202,-7.81818181818182)(1164.48484848485,-7.84848484848485)(1179.41414141414,-7.93181818181818)(1194.34343434343,-7.94545454545455)(1209.27272727273,-7.94545454545455)(1224.20202020202,-7.93181818181818)(1239.13131313131,-7.90909090909091)(1254.06060606061,-7.96969696969697)(1261.52525252525,-8)(1268.9898989899,-8.04545454545455)(1283.91919191919,-8.09090909090909)(1298.84848484848,-8.15151515151515)(1302.58080808081,-8.18181818181818)(1313.77777777778,-8.25)(1328.70707070707,-8.29545454545455)(1339.90404040404,-8.36363636363636)(1343.63636363636,-8.40909090909091)(1351.10101010101,-8.54545454545455)(1358.56565656566,-8.61363636363636)(1373.49494949495,-8.70909090909091)(1377.22727272727,-8.72727272727273)(1388.42424242424,-8.81818181818182)(1399.62121212121,-8.90909090909091)(1403.35353535354,-9)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-2.81818181818182)(14.9292929292929,-2.81818181818182)(29.8585858585859,-2.81818181818182)(44.7878787878788,-2.81818181818182)(59.7171717171717,-2.81818181818182)(74.6464646464647,-2.81818181818182)(89.5757575757576,-2.81818181818182)(104.505050505051,-2.81818181818182)(119.434343434343,-2.81818181818182)(134.363636363636,-2.81818181818182)(149.292929292929,-2.75757575757576)(156.757575757576,-2.72727272727273)(164.222222222222,-2.6969696969697)(179.151515151515,-2.63636363636364)(194.080808080808,-2.57575757575758)(201.545454545455,-2.54545454545455)(209.010101010101,-2.51515151515151)(223.939393939394,-2.45454545454545)(238.868686868687,-2.45454545454545)(253.79797979798,-2.39393939393939)(261.262626262626,-2.36363636363636)(268.727272727273,-2.33333333333333)(283.656565656566,-2.27272727272727)(298.585858585859,-2.21212121212121)(306.050505050505,-2.18181818181818)(313.515151515152,-2.15151515151515)(328.444444444444,-2.09090909090909)(343.373737373737,-2.03030303030303)(350.838383838384,-2)(358.30303030303,-1.96969696969697)(373.232323232323,-1.90909090909091)(388.161616161616,-1.90909090909091)(403.090909090909,-1.90909090909091)(418.020202020202,-1.90909090909091)(432.949494949495,-1.90909090909091)(447.878787878788,-1.90909090909091)(462.808080808081,-1.90909090909091)(477.737373737374,-1.90909090909091)(492.666666666667,-1.96969696969697)(500.131313131313,-2)(507.59595959596,-2.03030303030303)(522.525252525253,-2.15151515151515)(526.257575757576,-2.18181818181818)(537.454545454546,-2.27272727272727)(548.651515151515,-2.36363636363636)(552.383838383838,-2.39393939393939)(567.313131313131,-2.51515151515151)(571.045454545455,-2.54545454545455)(582.242424242424,-2.68181818181818)(584.73063973064,-2.72727272727273)(594.683501683502,-2.90909090909091)(597.171717171717,-3)(599.659932659933,-3.09090909090909)(599.659932659933,-3.27272727272727)(597.171717171717,-3.31818181818182)(589.707070707071,-3.45454545454546)(582.242424242424,-3.54545454545455)(571.045454545455,-3.63636363636364)(567.313131313131,-3.66666666666667)(552.383838383838,-3.78787878787879)(544.919191919192,-3.81818181818182)(537.454545454546,-3.84848484848485)(522.525252525253,-3.90909090909091)(507.59595959596,-3.90909090909091)(492.666666666667,-3.90909090909091)(477.737373737374,-3.96969696969697)(470.272727272727,-4)(462.808080808081,-4.03030303030303)(447.878787878788,-4.09090909090909)(432.949494949495,-4.09090909090909)(418.020202020202,-4.09090909090909)(403.090909090909,-4.09090909090909)(388.161616161616,-4.15151515151515)(380.69696969697,-4.18181818181818)(373.232323232323,-4.21212121212121)(358.30303030303,-4.27272727272727)(343.373737373737,-4.27272727272727)(328.444444444444,-4.27272727272727)(313.515151515152,-4.27272727272727)(298.585858585859,-4.27272727272727)(283.656565656566,-4.27272727272727)(268.727272727273,-4.27272727272727)(253.79797979798,-4.27272727272727)(238.868686868687,-4.21212121212121)(231.40404040404,-4.18181818181818)(223.939393939394,-4.15151515151515)(209.010101010101,-4.09090909090909)(194.080808080808,-4.09090909090909)(179.151515151515,-4.03030303030303)(171.686868686869,-4)(164.222222222222,-3.96969696969697)(149.292929292929,-3.90909090909091)(134.363636363636,-3.84848484848485)(126.89898989899,-3.81818181818182)(119.434343434343,-3.78787878787879)(104.505050505051,-3.72727272727273)(89.5757575757576,-3.72727272727273)(74.6464646464647,-3.72727272727273)(59.7171717171717,-3.72727272727273)(44.7878787878788,-3.72727272727273)(29.8585858585859,-3.72727272727273)(14.9292929292929,-3.72727272727273)(0,-3.72727272727273)(-0.000124406627521346,-3.63636363636364)(-0.000373213662548569,-3.45454545454546)(-0.000373213662548569,-3.27272727272727)(-0.000373213662548569,-3.09090909090909)(-0.000124406627521346,-2.90909090909091)(0,-2.81818181818182)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (462.808080808081,-14.6818181818182)(470.272727272727,-14.5454545454545)(477.737373737374,-14.4545454545455)(488.934343434343,-14.3636363636364)(492.666666666667,-14.3333333333333)(507.59595959596,-14.2727272727273)(522.525252525253,-14.2727272727273)(537.454545454546,-14.2727272727273)(552.383838383838,-14.2727272727273)(567.313131313131,-14.2727272727273)(582.242424242424,-14.2727272727273)(597.171717171717,-14.2727272727273)(612.10101010101,-14.2727272727273)(627.030303030303,-14.2727272727273)(641.959595959596,-14.2727272727273)(656.888888888889,-14.2727272727273)(671.818181818182,-14.2727272727273)(686.747474747475,-14.3181818181818)(690.479797979798,-14.3636363636364)(690.479797979798,-14.5454545454545)(686.747474747475,-14.5757575757576)(671.818181818182,-14.6969696969697)(664.353535353535,-14.7272727272727)(656.888888888889,-14.7575757575758)(641.959595959596,-14.8787878787879)(634.494949494949,-14.9090909090909)(627.030303030303,-14.9393939393939)(612.10101010101,-15.0606060606061)(604.636363636364,-15.0909090909091)(597.171717171717,-15.1212121212121)(582.242424242424,-15.1818181818182)(567.313131313131,-15.2424242424242)(559.848484848485,-15.2727272727273)(552.383838383838,-15.3030303030303)(537.454545454546,-15.3636363636364)(522.525252525253,-15.3636363636364)(507.59595959596,-15.3636363636364)(492.666666666667,-15.3636363636364)(477.737373737374,-15.3030303030303)(474.005050505051,-15.2727272727273)(462.808080808081,-15.1363636363636)(460.319865319865,-15.0909090909091)(455.343434343434,-14.9090909090909)(460.319865319865,-14.7272727272727)(462.808080808081,-14.6818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (462.808080808081,-7.95454545454546)(474.005050505051,-7.81818181818182)(477.737373737374,-7.79545454545455)(492.666666666667,-7.72727272727273)(507.59595959596,-7.72727272727273)(522.525252525253,-7.72727272727273)(537.454545454546,-7.72727272727273)(552.383838383838,-7.68181818181818)(567.313131313131,-7.72727272727273)(578.510101010101,-7.81818181818182)(582.242424242424,-7.86363636363636)(589.707070707071,-8)(584.73063973064,-8.18181818181818)(582.242424242424,-8.21212121212121)(569.801346801347,-8.36363636363636)(567.313131313131,-8.40909090909091)(552.383838383838,-8.5)(537.454545454546,-8.5)(522.525252525253,-8.45454545454545)(507.59595959596,-8.45454545454545)(492.666666666667,-8.45454545454545)(477.737373737374,-8.45454545454545)(466.540404040404,-8.36363636363636)(462.808080808081,-8.31818181818182)(455.343434343434,-8.18181818181818)(460.319865319865,-8)(462.808080808081,-7.95454545454546)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-17.5454545454545)(1478.00012440663,-17.6363636363636)(1478.00037321366,-17.8181818181818)(1478.00037321366,-18)(1478,-18.0000045452273)(1463.07070707071,-18.0000045452273)(1448.14141414141,-18.0000045452273)(1433.21212121212,-18.0000045452273)(1418.28282828283,-18.0000045452273)(1403.35353535354,-18.0000035351964)(1388.42424242424,-18.0000025251543)(1375.98316498317,-18)(1388.42424242424,-17.8484848484848)(1395.88888888889,-17.8181818181818)(1403.35353535354,-17.7878787878788)(1418.28282828283,-17.7272727272727)(1433.21212121212,-17.7272727272727)(1448.14141414141,-17.6666666666667)(1455.60606060606,-17.6363636363636)(1463.07070707071,-17.6060606060606)(1478,-17.5454545454545)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (1358.56565656566,-4.54545454545455)(0,-18)(0,0)(1478,-14.7272727272727)(0,-8.72727272727273)(477.737373737374,-9.09090909090909)(432.949494949495,-6.90909090909091)(358.30303030303,-11.2727272727273)(806.181818181818,-8.72727272727273)(895.757575757576,-10.5454545454545)(836.040404040404,-7.09090909090909)(1164.48484848485,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1313.77777777778,-7.63636363636364)(1239.13131313131,-10.5454545454545)(1089.83838383838,-7.45454545454546)(0,-5.81818181818182)(656.888888888889,-9.63636363636364)(298.585858585859,-8.54545454545455)(567.313131313131,-8.18181818181818)(1015.19191919192,-10.1818181818182)(1478,-8.36363636363636)(910.686868686869,0)(880.828282828283,-18)(1478,-10.5454545454545)(343.373737373737,-8)(850.969696969697,-9.45454545454546)(701.676767676768,-8)(343.373737373737,-9.09090909090909)(1000.26262626263,-7.63636363636364)(1358.56565656566,-10)(179.151515151515,-7.63636363636364)(1209.27272727273,-7.63636363636364)(1373.49494949495,-8.36363636363636)(477.737373737374,-7.81818181818182)(0,-13.2727272727273)(865.89898989899,-7.63636363636364)(1134.62626262626,-10.3636363636364)(1478,0)(701.676767676768,-8.72727272727273)(1433.21212121212,-9.63636363636364)(552.383838383838,-7.81818181818182)(567.313131313131,-7.45454545454546)(865.89898989899,-9.81818181818182)(507.59595959596,-8.90909090909091)(343.373737373737,-7.81818181818182)(791.252525252525,-7.81818181818182)(1030.12121212121,-10.1818181818182)(1104.76767676768,-7.45454545454546)(1343.63636363636,-8.18181818181818)(1358.56565656566,-10.1818181818182)(925.616161616162,-7.45454545454546)(1448.14141414141,-9.27272727272727)(418.020202020202,-8.90909090909091)(612.10101010101,-7.63636363636364)(776.323232323232,-8.90909090909091)(597.171717171717,-8.54545454545455)(910.686868686869,-10)(1194.34343434343,-7.63636363636364)(582.242424242424,-7.45454545454546)(432.949494949495,-7.63636363636364)(806.181818181818,-8)(1268.9898989899,-10.3636363636364)(1149.55555555556,-10.1818181818182)(1418.28282828283,-8.72727272727273)(1463.07070707071,-9.45454545454546)(821.111111111111,-9.45454545454546)(1254.06060606061,-7.81818181818182)(940.545454545455,-7.45454545454546)(1104.76767676768,-10.1818181818182)(388.161616161616,-8.54545454545455)(821.111111111111,-8.18181818181818)(552.383838383838,-8.72727272727273)(462.808080808081,-7.45454545454546)(1328.70707070707,-8)(1403.35353535354,-10)(925.616161616162,-10)(1074.90909090909,-7.45454545454546)(641.959595959596,-8.18181818181818)(1388.42424242424,-8.36363636363636) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-19 figurefactory/files/voned_cl_41_amb_1.tex
LSE algorithm

--- 2013-03-19 figurefactory/files/voned_cl_41.tex
@@
 
+\addplot [
+color=black,
+solid,
+line width=1.5pt,
+mark=-,
+mark size=3pt,
+forget plot
+]
+coordinates{
+ (1.23,0.0268)(1.23,1.9195)
+};
+
+\addplot [
+color=yellow,
+solid,
+line width=4pt,
+forget plot
+]
+coordinates{
+ (1.23,1.2)(1.23,1.9195)
+};
+
+\addplot [
+color=black,
+solid,
+line width=1.5pt,
+mark=-,
+mark size=3pt,
+forget plot
+]
+coordinates{
+ (0.23,0.9288)(0.23,3.8259)
+};
+
 \end{axis}

### 2013-03-19 msthpres.tex
LSE algorithm

@@
 \usepackage[T1]{fontenc}
+
+%%
+\usepackage{xspace}
+\usepackage{msthpres}
+\newcommand{\gpucb}{\textsf{GP-UCB}\xspace}
+\newcommand{\gpbucb}{\textsf{GP-BUCB}\xspace}
+\newcommand{\acl}{\textsf{LSE}\xspace}
+\newcommand{\fullacl}{Level Set Estimation\xspace}
+\newcommand{\iacl}{\textsf{LSE\textsubscript{imp}}\xspace}
+\newcommand{\bacl}{\textsf{LSE\textsubscript{batch}}\xspace}
+\newcommand{\ibacl}{\textsf{LSE\textsubscript{imp-batch}}\xspace}
+\newcommand{\str}{\textsf{STR}\xspace}
+\newcommand{\istr}{\textsf{STR\textsubscript{imp}}\xspace}
+\newcommand{\bstr}{\textsf{STR\textsubscript{batch}}\xspace}
+\newcommand{\rstr}{\textsf{STR\textsubscript{rank}}\xspace}
+\newcommand{\var}{\textsf{VAR}\xspace}
+%%
 
@@
 \vspace{0.3em}
-\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<16->{\Large\color{green!70!black}\checkmark}
+\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<24->{\Large\color{green!70!black}\checkmark}
+\uncover<16->{
+\begin{itemize}
+\item<16-> Pick among the yet unclassified.
+\item<17-> Doesn't really matter which!\\
+           \uncover<18->{(e.g. max. variance, }\uncover<19->{max. ambiguity}\uncover<23->{, or even random)}
+\end{itemize}}
 \end{enumerate}
@@
 \includegraphics<12>[width=3.5in]{figures/voned_cl_40}
-\includegraphics<13->[width=3.5in]{figures/voned_cl_41}
+\includegraphics<13-19>[width=3.5in]{figures/voned_cl_41}
+\includegraphics<20>[width=3.5in]{figures/voned_cl_41_amb_0}
+\includegraphics<21>[width=3.5in]{figures/voned_cl_41_amb_1}
+\includegraphics<22->[width=3.5in]{figures/voned_cl_41_amb_2}
+\end{center}
+\end{frame}
+
+\definecolor{c1}{RGB}{255,255,255}
+\definecolor{c2}{RGB}{27,161,226}
+\definecolor{c6}{RGB}{140,191,38}
+\definecolor{c4}{RGB}{240,150,9}
+\definecolor{c5}{RGB}{255,255,255}
+\definecolor{c3}{RGB}{230,113,184}
+%\colorlet{c1}{cyan}
+%\colorlet{c2}{magenta}
+%\colorlet{c3}{red}
+%\colorlet{c4}{green}
+%\colorlet{c5}{yellow}
+
+\begin{frame}
+\begin{columns}[t]
+\column{0.5\textwidth}
+{\footnotesize
+\begin{algorithmic}[1]
+  \REQUIRE sample set $D$, GP prior ($\mu_0 = 0$, $k$, $\sigma_0$),\\
+           \hspace{1.35em}threshold value $h$, accuracy parameter $\epsilon$
+  \ENSURE predicted sets $\hat{H}$, $\hat{L}$
+  \uncover<2->{
+  \CSTATE{c1}$H_0 \gets \varnothing$,\enskip $L_0 \gets \varnothing$,\enskip $U_0 \gets D$ \label{lin:init1}
+  %\LET{$H_0$}{$\varnothing$} \label{lin:init1}
+  %\LET{$L_0$}{$\varnothing$}
+  %\LET{$U_0$}{$D$}
+  \CLET{c1}{$C_0(\*x)$}{$\mathbb{R}$, for all $\*x \in D$} \label{lin:init2}
+  \CLET{c1}{$t$}{1}
+  }
+  \uncover<3->{
+  \CWHILE{c6}{$U_{t-1} \neq \varnothing$}
+    \CSTATE{c6}$H_t \gets H_{t-1}$,\enskip $L_t \gets L_{t-1}$,\enskip $U_t \gets U_{t-1}$
+    }
+    %\LET{$H_t$}{$H_{t-1}$}
+    %\LET{$L_t$}{$L_{t-1}$}
+    %\LET{$U_t$}{$U_{t-1}$}
+    \uncover<4->{
+    \CFORALL{c2}{$\*x \in U_{t-1}$}
+      \CLET{c2}{$C_{t}(\*x)$}{$C_{t-1}(\*x) \cap Q_t(\*x)$} \label{lin:upd}
+      \CIF{c2}{$\min(C_t(\*x)) + \epsilon > h$} \label{lin:class1}
+        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
+        \CLET{c2}{$H_t$}{$H_t \cup \{\*x\}$} 
+      \CELSIF{c2}{$\max(C_t(\*x)) - \epsilon \leq h$} \label{lin:classr2}
+        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
+        \CLET{c2}{$L_t$}{$L_t \cup \{\*x\}$}
+      \CENDIF{c2} \label{lin:class2}
+    \CENDFOR{c2}
+    }
+    \uncover<5->{
+    \CLET{c3}{$\*x_t$}{$\argmax_{\*x \in U_t}(a_t(\*x))$} \label{lin:sel1}
+    \CLET{c3}{$y_t$}{$f(\*x_t) + n_t$} \label{lin:sel2}
+    }
+    \uncover<6->{
+    \CSTATE{c4}Compute $\mu_t(\*x)$ and $\sigma_t(\*x)$, for all $\*x \in U_t$ \label{lin:inf}
+    }
+    \uncover<3->{
+    \CLET{c6}{$t$}{$t + 1$}
+  \CENDWHILE{c6}
+  }
+  \uncover<2->{
+  \CLET{c5}{$\hat{H}$}{$H_{t-1}$} \label{lin:ret1}
+  \CLET{c5}{$\hat{L}$}{$L_{t-1}$} \label{lin:ret2}
+  }
+\end{algorithmic}
+}
+\column{0.5\textwidth}
+\begin{center}
+The Level Set Estimation (\acl) algorithm
+\end{center}
+\only<3-6>{\vspace{34pt}$\leftarrow$ {\small loop until all points have been classified\\}\vspace{40pt}}
+\only<4-6>{$\leftarrow$ {\small classify\\}\vspace{52pt}}
+\only<5-6>{$\leftarrow$ {\small select max. ambiguity point\\}\vspace{3pt}}
+\only<6>{$\leftarrow$ {\small update GP estimate}}
+\only<7->{
+\vspace{3pt}
+\begin{itemize}
+\only<7->{
+\item Monotonicity of
+\begin{enumerate}
+\item confidence intervals
+\item classification
+\end{enumerate}
+}
+\vspace{0em}
+\only<8->{
+\item Relaxed classification rules by an accuracy parameter $\epsilon$\\
+      (trades off sampling cost for accuracy)
+}
+\end{itemize}
+}
+\begin{center}
+\includegraphics<8->[width=2in]{figures/voned_cl_41_eps}
+\end{center}
+\end{columns}
+\end{frame}
+
+\begin{frame}
+\begin{center}
+\includegraphics<1->[width=4in]{figures/limno_bgape_ls}\\
+
+\only<1>{\color{white}\small{$t = 0$\\}}
+\only<2>{\small{$t = 0$\\}}
+\only<3>{\small{$t = 20$\\}}
+\only<4>{\small{$t = 40$\\}}
+\only<5>{\small{$t = 60$\\}}
+\only<6>{\small{$t = 80$\\}}
+\only<7>{\small{$t = 100$\\}}
+\only<8>{\small{$t = 120$\\}}
+\only<9>{\small{$t = 140$\\}}
+\only<10>{\small{$t = 160$\\}}
+\only<11>{\small{$t = 180$\\}}
+\only<12>{\small{$t = 200$\\}}
+%\only<13>{\small{$t = 220$\\}}
+%\only<14>{\small{$t = 240$\\}}
+\only<13>{\small{$t = 260$\\}}
+%\only<16>{\small{$t = 280$\\}}
+%\only<17>{\small{$t = 300$\\}}
+%\only<18>{\small{$t = 320$\\}}
+%\only<19>{\small{$t = 340$\\}}
+\only<14>{\small{$t = 354$\\}}
+
+\hspace{-1.9em}
+\color{white}
+\includegraphics<1>[draft,width=3.78in]{figures/limno_bgape_class_20}
+\color{black}
+\includegraphics<2>[width=3.78in]{figures/limno_bgape_class_0}
+\includegraphics<3>[width=3.78in]{figures/limno_bgape_class_20}
+\includegraphics<4>[width=3.78in]{figures/limno_bgape_class_40}
+\includegraphics<5>[width=3.78in]{figures/limno_bgape_class_60}
+\includegraphics<6>[width=3.78in]{figures/limno_bgape_class_80}
+\includegraphics<7>[width=3.78in]{figures/limno_bgape_class_100}
+\includegraphics<8>[width=3.78in]{figures/limno_bgape_class_120}
+\includegraphics<9>[width=3.78in]{figures/limno_bgape_class_140}
+\includegraphics<10>[width=3.78in]{figures/limno_bgape_class_160}
+\includegraphics<11>[width=3.78in]{figures/limno_bgape_class_180}
+\includegraphics<12>[width=3.78in]{figures/limno_bgape_class_200}
+%\includegraphics<13>[width=3.78in]{figures/limno_bgape_class_220}
+%\includegraphics<14>[width=3.78in]{figures/limno_bgape_class_240}
+\includegraphics<13>[width=3.78in]{figures/limno_bgape_class_260}
+%\includegraphics<16>[width=3.78in]{figures/limno_bgape_class_280}
+%\includegraphics<17>[width=3.78in]{figures/limno_bgape_class_300}
+%\includegraphics<18>[width=3.78in]{figures/limno_bgape_class_320}
+%\includegraphics<19>[width=3.78in]{figures/limno_bgape_class_340}
+\includegraphics<14>[width=3.78in]{figures/limno_bgape_class_354}
 \end{center}

### 2013-03-20 figurefactory/files/ev_bgape_eps.tex
LSE theory and experiments

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{mycolor1}{rgb}{1,0.04,0}
\definecolor{mycolor2}{rgb}{1,0.08,0}
\definecolor{mycolor3}{rgb}{1,0.12,0}
\definecolor{mycolor4}{rgb}{1,0.16,0}
\definecolor{mycolor5}{rgb}{1,0.2,0}
\definecolor{mycolor6}{rgb}{1,0.24,0}
\definecolor{mycolor7}{rgb}{1,0.28,0}
\definecolor{mycolor8}{rgb}{1,0.32,0}
\definecolor{mycolor9}{rgb}{1,0.36,0}
\definecolor{mycolor10}{rgb}{1,0.4,0}
\definecolor{mycolor11}{rgb}{1,0.44,0}
\definecolor{mycolor12}{rgb}{1,0.48,0}
\definecolor{mycolor13}{rgb}{1,0.52,0}
\definecolor{mycolor14}{rgb}{1,0.56,0}
\definecolor{mycolor15}{rgb}{1,0.6,0}
\definecolor{mycolor16}{rgb}{1,0.68,0}
\definecolor{mycolor17}{rgb}{1,0.72,0}
\definecolor{mycolor18}{rgb}{1,0.76,0}
\definecolor{mycolor19}{rgb}{1,0.84,0}
\definecolor{mycolor20}{rgb}{1,0.88,0}
\definecolor{mycolor21}{rgb}{1,0.96,0}
\definecolor{mycolor22}{rgb}{1,1,0}
\definecolor{mycolor23}{rgb}{0.92,1,0.08}
\definecolor{mycolor24}{rgb}{0.84,1,0.16}
\definecolor{mycolor25}{rgb}{0.76,1,0.24}
\definecolor{mycolor26}{rgb}{0.68,1,0.32}
\definecolor{mycolor27}{rgb}{0.6,1,0.4}
\definecolor{mycolor28}{rgb}{0.52,1,0.48}
\definecolor{mycolor29}{rgb}{0.44,1,0.56}
\definecolor{mycolor30}{rgb}{0.36,1,0.64}
\definecolor{mycolor31}{rgb}{0.24,1,0.76}
\definecolor{mycolor32}{rgb}{0.16,1,0.84}
\definecolor{mycolor33}{rgb}{0.04,1,0.96}
\definecolor{mycolor34}{rgb}{0,0.92,1}
\definecolor{mycolor35}{rgb}{0,0.8,1}
\definecolor{mycolor36}{rgb}{0,0.68,1}
\definecolor{mycolor37}{rgb}{0,0.56,1}
\definecolor{mycolor38}{rgb}{0,0.44,1}
\definecolor{mycolor39}{rgb}{0,0.28,1}
\definecolor{mycolor40}{rgb}{0,0.12,1}
\definecolor{mycolor41}{rgb}{0,0.52,1}
\definecolor{mycolor42}{rgb}{0,0.48,1}
\definecolor{mycolor43}{rgb}{0,0.4,1}
\definecolor{mycolor44}{rgb}{0,0.36,1}
\definecolor{mycolor45}{rgb}{0,0.32,1}
\definecolor{mycolor46}{rgb}{0,0.24,1}
\definecolor{mycolor47}{rgb}{0,0.2,1}
\definecolor{mycolor48}{rgb}{0,0.16,1}
\definecolor{mycolor49}{rgb}{0,0.08,1}
\definecolor{mycolor50}{rgb}{0,0.04,1}
\definecolor{mycolor51}{rgb}{1,0.64,0}
\definecolor{mycolor52}{rgb}{0.96,1,0.04}
\definecolor{mycolor53}{rgb}{0.88,1,0.12}
\definecolor{mycolor54}{rgb}{0.8,1,0.2}
\definecolor{mycolor55}{rgb}{0.72,1,0.28}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-6pt},
ylabel shift={-4pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=400,
xlabel={Samples},
ymin=0.5, ymax=1,
ylabel={$F_1$-score},
name=plot1,
axis lines*=left,
colormap={mymap}{[1pt] rgb(0pt)=(0.5,0,0); rgb(8pt)=(1,0,0); rgb(24pt)=(1,1,0); rgb(40pt)=(0,1,1); rgb(56pt)=(0,0,1); rgb(63pt)=(0,0,0.5625)},
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.06, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
tickwidth=0.1cm,
colorbar/width=0.15cm,
point meta min=0,
point meta max=2
]

\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (294,0.930862437633642) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (352,0.974216027874564) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (308,0.960111966410077) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (258,0.885196374622356) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.942997888810697) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (350,0.965034965034965) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (281,0.945454545454545) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (360,0.974107767669699) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (298,0.951219512195122) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (305,0.972515856236786) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (230,0.867078825347759) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (226,0.878971255673222) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (316,0.953439888811675) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (214,0.876712328767123) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (276,0.956951305575159) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (286,0.947220267417312) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (286,0.952843273231623) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (285,0.961884961884962) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (189,0.879818594104308) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (261,0.945404284727021) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (233,0.951269732326699) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (195,0.896860986547085) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (251,0.963838664812239) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (186,0.926898509581263) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (213,0.952247191011236) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (159,0.877488514548239) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (195,0.936319104268719) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (190,0.939958592132505) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (175,0.913105413105413) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (128,0.86697247706422) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (135,0.856278366111951) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (143,0.917018284106892) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (108,0.862147753236862) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (102,0.842105263157895) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (121,0.922865013774105) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (92,0.908821349147517) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (98,0.864216054013503) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (99,0.885409252669039) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (82,0.849438202247191) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (85,0.930428671820098) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (70,0.879219804951238) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.874243443174176) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.883755588673621) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.815052041633307) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.85912560721721) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (52,0.851851851851852) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.823275862068965) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.803951367781155) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.834905660377358) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.847107438016529) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.789259560618389) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.832298136645963) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.858564321250888) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.859408795962509) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.813404417364813) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.771747211895911) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.78893280632411) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.769230769230769) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.763840224246671) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.776377952755905) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.760746147607461) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.760655737704918) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.768333333333333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.784873949579832) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.73195020746888) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.728129205921938) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.745874587458746) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.766265060240964) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (355,0.966433566433566) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (372,0.970159611380985) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (364,0.962095106822881) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (354,0.967877094972067) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (330,0.964754664823773) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (327,0.968728283530229) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (371,0.966461327857632) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (331,0.964509394572025) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (237,0.881559220389805) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (353,0.959666203059805) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (301,0.944793850454228) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (325,0.959778085991678) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (325,0.948986722571628) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (280,0.945086705202312) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (221,0.874536005939124) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (226,0.928011404133999) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (266,0.946938775510204) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (200,0.933914306463326) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (166,0.919540229885057) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (183,0.907246376811594) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (187,0.877643504531722) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (215,0.945908460471567) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (230,0.948251748251748) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (226,0.953179594689029) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (213,0.938186813186813) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (184,0.943181818181818) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (147,0.907246376811594) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (176,0.936140350877193) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (165,0.929190751445086) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (160,0.929235167977126) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (163,0.950102529049897) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (168,0.930679478380233) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (133,0.917915774446823) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (114,0.881638846737481) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (119,0.930826057756884) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (80,0.818110850897736) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (86,0.876371616678859) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (80,0.867415730337079) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (94,0.93183415319747) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.905606813342796) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (75,0.899470899470899) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.90146750524109) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.830135039090263) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.85348506401138) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.829268292682927) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.820705176294073) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.845814977973568) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.836473247927656) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.833333333333333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.835481425322214) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.813008130081301) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.845986984815618) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.852805280528053) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.810566037735849) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.802684563758389) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.81413612565445) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.817219477769936) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.814555633310007) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.789515488482923) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.79409594095941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.769356153219234) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.79288256227758) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.776957163958641) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.724842767295597) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.789598108747045) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.763212079615649) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.819464033850493) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.54728370221328) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (387,0.95859649122807) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (348,0.961702127659574) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (275,0.876233864844343) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (286,0.932559825960841) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (358,0.965034965034965) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (283,0.946191474493361) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (263,0.92463768115942) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.956829440905874) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (314,0.954766875434934) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (323,0.953389830508474) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (263,0.926300578034682) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (329,0.96056338028169) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.959056210964608) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (299,0.960339943342776) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (308,0.957182320441989) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (285,0.954321855235418) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (247,0.953191489361702) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (204,0.918681318681319) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (258,0.940925266903915) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (186,0.876795162509448) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (247,0.947001394700139) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (203,0.924652523774689) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (187,0.917888563049853) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (213,0.952112676056338) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (230,0.948936170212766) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (207,0.938628158844765) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (194,0.944674965421853) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (148,0.921511627906977) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (166,0.92600422832981) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (137,0.879939209726444) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (182,0.944979367262723) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (149,0.905109489051095) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (129,0.913868613138686) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (132,0.937588652482269) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (121,0.90050107372942) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (97,0.841221374045801) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (93,0.853374709076804) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (88,0.843822843822844) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (89,0.921052631578947) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.885838150289017) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.884241971620612) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.903724525650035) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.863768115942029) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.875280059746079) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.877167630057803) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (60,0.844137931034483) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (56,0.888730385164051) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.869433962264151) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.818722139673105) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.875524475524475) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.840245775729647) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.825590251332825) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.813559322033898) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.79126213592233) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.809160305343511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.802896218825422) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.805687203791469) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.7808) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.786610878661088) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.764350453172205) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.78475935828877) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.785046728971962) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.788083953960731) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.811755361397935) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.696673189823875) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.806646525679758) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.788888888888889) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.785829307568438) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (374,0.962649753347428) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (338,0.97194950911641) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (345,0.963380281690141) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (362,0.956645344705046) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (365,0.968197879858657) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (340,0.962754743499649) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (343,0.959212376933896) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (334,0.959497206703911) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (247,0.933621933621934) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (296,0.926007326007326) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (266,0.942628903413217) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (283,0.93371757925072) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (313,0.960839160839161) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (244,0.938040345821326) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (283,0.961379310344827) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (255,0.934296028880866) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (232,0.935740072202166) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (235,0.951983298538622) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (204,0.880061115355233) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (259,0.941761363636364) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (218,0.897744360902256) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (275,0.964260686755431) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.903846153846154) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (195,0.938804895608351) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (233,0.956036287508723) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (172,0.923076923076923) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (210,0.961779013203613) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (181,0.909479686386315) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (188,0.949224259520451) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (169,0.950071326676177) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (171,0.96078431372549) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (161,0.945736434108527) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (148,0.936376210235131) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (146,0.935817805383023) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (116,0.925631768953068) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (105,0.914487632508834) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (94,0.90961262553802) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (97,0.905003625815808) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (90,0.895774647887324) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (90,0.900808229243203) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.836573074154068) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (75,0.835666912306559) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.853675945753034) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.884798909338787) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.823346303501945) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.831426392067124) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.826291079812207) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.839524517087667) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.826706676669167) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.843465045592705) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.813450760608487) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.804705882352941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.808176100628931) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.793774319066148) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.810879190385832) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.82641252552757) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.805194805194805) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.813559322033898) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.761835396941005) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.810727969348659) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.809930178432894) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.793080505655356) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.822238478419898) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.805890227576974) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.789350039154268) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.785581106277191) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.759136212624585) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.766476810414971) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (343,0.964234620886981) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.954220314735336) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (311,0.936635105608157) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (306,0.967329545454545) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (307,0.94201861130995) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (336,0.94592645998558) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (323,0.960507757404795) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (262,0.938271604938271) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (251,0.917325664989216) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (314,0.954022988505747) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (287,0.94608195542775) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (287,0.946280991735537) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (247,0.941007194244604) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (290,0.961918194640338) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (283,0.950819672131147) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (291,0.962078651685393) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (231,0.933235509904622) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (231,0.929824561403509) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (209,0.918639053254438) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (286,0.951902368987796) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (233,0.953439888811675) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (262,0.957142857142857) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (236,0.948699929725931) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (249,0.957507082152974) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (178,0.886706948640483) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (168,0.920704845814978) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (160,0.924198250728863) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (180,0.930635838150289) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (163,0.930664760543245) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (143,0.92557111274871) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (162,0.932871972318339) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (138,0.920634920634921) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (139,0.943342776203966) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (134,0.928208846990573) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (100,0.864446165762975) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (101,0.841221374045801) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (101,0.869629629629629) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (89,0.893862815884476) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (84,0.901387874360847) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (81,0.874051593323217) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.913528591352859) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (77,0.897079276773296) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (60,0.880239520958084) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.87832973362131) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.797720797720798) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.88) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.814132104454685) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.796516231195566) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.890921885995777) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.872135994087213) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.832535885167464) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.827862289831865) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.880056777856636) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.81037037037037) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.81259842519685) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.778089887640449) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.791666666666667) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.809523809523809) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.84012539184953) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.811614730878187) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.827169811320755) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.815450643776824) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.843490304709141) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.733676975945017) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.817365269461078) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.76030534351145) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.503267973856209) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.701214574898785) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (350,0.964936886395512) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (269,0.885022692889561) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (360,0.967559943582511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (248,0.885196374622356) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (202,0.900221729490022) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (333,0.96575821104123) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (352,0.963687150837989) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (302,0.963585434173669) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (323,0.959717314487632) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (246,0.951167728237792) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (217,0.929248723559446) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (268,0.934971098265896) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (256,0.940841054882395) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (331,0.97071129707113) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (269,0.972554539057002) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (284,0.960334029227557) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (280,0.962237762237762) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (274,0.955602536997886) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (220,0.925952552120776) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (220,0.932374100719424) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (217,0.946695095948827) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (238,0.965901183020181) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (163,0.884498480243161) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (218,0.948699929725931) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (207,0.946022727272727) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (198,0.951236749116608) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (194,0.942512420156139) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (154,0.934876989869754) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (154,0.944323933477946) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (190,0.956583629893238) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (168,0.952447552447552) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (117,0.893961708394698) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (93,0.894930198383541) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (123,0.915523465703971) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (102,0.867017280240421) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (103,0.888272033310201) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (92,0.869899923017706) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (96,0.913597733711048) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.840513983371126) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.824561403508772) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.884502923976608) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (72,0.895144264602393) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (75,0.885072655217966) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.876534296028881) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.888106966924701) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.847250509164969) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.801872074882995) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.851421188630491) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.802873104549082) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.834258524980174) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.814927646610815) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.861493836113125) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.818466353677621) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.833222591362126) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.804861580013504) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.828685258964143) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.773712737127371) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.767326732673267) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.809005083514887) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.774603174603175) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.7859375) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.804012345679012) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.802666666666667) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.749022673964034) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.724046140195208) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.689313517338995) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.725352112676056) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.414866032843561) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (279,0.928930366116296) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (356,0.954577218728162) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (362,0.955369595536959) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (357,0.955801104972376) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (385,0.956224350205198) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (309,0.938833570412518) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (300,0.944405348346235) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (274,0.926164874551971) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (329,0.945224719101123) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (299,0.931929824561403) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (355,0.956461644782308) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (257,0.924177396280401) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (335,0.955431754874652) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (266,0.935988620199146) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.949480968858131) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (262,0.957550452331246) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (281,0.948824343015214) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (298,0.96551724137931) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (249,0.943213296398892) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (234,0.941836019621584) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (256,0.948311509303928) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (254,0.942657342657343) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (192,0.868035190615836) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (228,0.943632567849687) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (178,0.923516797712652) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (212,0.923076923076923) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (161,0.922190201729106) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (181,0.922859164897381) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (186,0.947960618846695) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (151,0.915645277577505) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (148,0.865470852017937) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (139,0.928923293455313) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (143,0.92) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (144,0.934886908841672) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (105,0.888888888888889) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (98,0.889374090247453) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (108,0.930327868852459) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (90,0.908037653874004) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (84,0.893430656934307) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (69,0.835463258785942) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (71,0.887060583395662) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.816358024691358) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.858433734939759) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (60,0.831360946745562) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (58,0.821939586645469) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.836193447737909) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.84692417739628) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.802091112770724) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.794952681388013) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.78975131876413) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.795509222133119) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.838056680161943) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.802996254681648) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.825816485225505) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.836532097948378) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.781542898341745) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.811111111111111) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.806842480399144) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.813507290867229) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.817610062893082) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.768) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.802278275020342) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.782546494992847) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.810483870967742) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.764627659574468) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.772486772486773) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.757249378624689) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.081180811808118) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (348,0.959326788218794) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (359,0.961864406779661) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (378,0.968242766407904) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (364,0.959660297239915) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (304,0.951977401129943) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (350,0.960227272727273) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (314,0.948884089272858) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (268,0.93644996347699) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.955903271692745) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (246,0.932748538011696) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (230,0.928571428571428) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (290,0.959553695955369) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (195,0.923976608187134) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (316,0.963752665245202) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (299,0.96113074204947) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (249,0.941092973740241) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.878533231474408) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (237,0.934105720492397) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (237,0.936727272727273) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (187,0.878347360367253) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (265,0.9593837535014) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (235,0.952313167259786) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (218,0.941595441595441) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (206,0.934936350777935) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (164,0.877566539923954) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.949681077250177) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (174,0.92836676217765) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (204,0.946695095948827) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (142,0.859714928732183) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (134,0.922302158273381) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (173,0.940677966101695) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (156,0.933428775948461) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (152,0.934191702432046) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (88,0.83015873015873) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (112,0.896151053013798) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (92,0.881670533642691) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (112,0.935805991440799) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (78,0.892512972572276) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (90,0.915679442508711) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (77,0.897168405365127) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.881458966565349) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.883211678832117) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.877840909090909) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.898509581263307) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.861731843575419) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.871259568545581) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.869318181818182) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.847430830039526) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.814756671899529) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.814814814814815) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.800656275635767) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.795819935691318) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.813688212927757) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.845605700712589) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.831967213114754) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.821917808219178) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.808444096950743) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.7936) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.789712556732224) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.778435239973701) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.793650793650794) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.79874213836478) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.819007686932215) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.785333333333333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.782292298362644) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.717832957110609) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.805946791862285) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.70697012802276) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (324,0.965322009907997) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (344,0.954967834167262) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (306,0.952116585704372) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (380,0.961702127659574) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (294,0.959603118355776) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (254,0.928312816799421) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (324,0.96218487394958) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (309,0.947444204463643) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.96011396011396) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (275,0.951359084406295) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (293,0.950749464668094) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (298,0.955523672883788) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (291,0.959603118355776) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (289,0.951236749116608) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (296,0.950634696755994) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (203,0.870109546165884) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (251,0.941672522839072) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (198,0.878274268104776) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (226,0.920883820384889) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (246,0.947519769949676) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (170,0.910029498525074) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (228,0.952924393723252) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (223,0.951841359773371) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (249,0.956583629893238) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (158,0.87024087024087) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (202,0.954738330975955) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (148,0.860182370820669) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (184,0.915032679738562) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (137,0.860046911649726) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (160,0.926007326007326) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (131,0.861154446177847) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (138,0.861989205859676) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (133,0.92138133725202) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (117,0.922855082912761) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (111,0.903597122302158) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (92,0.902616279069767) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (109,0.928923293455313) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (93,0.892392049348869) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (98,0.935323383084577) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.899042004421518) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (83,0.923829489867226) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.886750555144337) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (70,0.880116959064327) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.867292225201072) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (60,0.865609924190214) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.815642458100559) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.799365582870737) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.824742268041237) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.819512195121951) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.819018404907975) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.82648401826484) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.783387622149837) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.795962509012257) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.773246329526917) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.819334389857369) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.738095238095238) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.78010878010878) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.771565495207668) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.754601226993865) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.773480662983425) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.723842195540309) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.788663967611336) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.773584905660377) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.727117194183062) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.770359501100513) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.755212355212355) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.718446601941747) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.673060156931125) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (325,0.95591322603219) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (302,0.952654232424677) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (309,0.958512160228898) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (299,0.955287437899219) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (283,0.954415954415954) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (332,0.968421052631579) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (327,0.972593113141251) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.97191011235955) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (337,0.957887223411849) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (256,0.941944847605225) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (280,0.958185683912119) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (299,0.951029098651526) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (232,0.877030162412993) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (222,0.945165945165945) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (198,0.880860876249039) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (257,0.947444204463643) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (204,0.871439568899153) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (303,0.969187675070028) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (204,0.937226277372263) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (259,0.961294862772695) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (191,0.940493468795356) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (209,0.935272727272727) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (164,0.909090909090909) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (227,0.950508474576271) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (185,0.932851985559567) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (164,0.875576036866359) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (195,0.951305575158786) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (201,0.951497860199715) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (140,0.881996974281392) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (146,0.950980392156863) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (179,0.958827634333566) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (122,0.932153392330383) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (115,0.865900383141762) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (138,0.929264909847434) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (107,0.896408839779005) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (107,0.909336941813261) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.869961977186312) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (80,0.860700389105058) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (84,0.86969696969697) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.80521597392013) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.89900426742532) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (75,0.892957746478873) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (78,0.902571041948579) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.85949177877429) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.88967468175389) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.877611940298507) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.860973888496824) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.829975825946817) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.885174418604651) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.811945117029863) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.838709677419355) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.835409836065574) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.80250347705146) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.804043545878694) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.805673758865248) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.775038520801233) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.799139167862267) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.7546875) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.783258594917788) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.812089356110381) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.790844514601421) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.798069187449718) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.750402576489533) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.766584766584767) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.70631970260223) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.741100323624595) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.820405310971349) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.694850115295926) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.659279778393352) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.750405186385737) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.701298701298701) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.794076163610719) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.656502242152466) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.79048349961627) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.804532577903683) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.789808917197452) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.758827948910593) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.772635814889336) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.732796032238066) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.807417974322396) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.758152173913043) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.779639175257732) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.795505617977528) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.764754779717373) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.765809589993051) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.618556701030928) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.8140625) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.779050736497545) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.399612027158099) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.734463276836158) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.760072158749248) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (6,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.816816816816817) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.645510835913313) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.804580152671756) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (2,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.76523151909017) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.782808902532617) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.7) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.795768917819365) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.781575037147102) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.785104732350659) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.593448940269749) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.783402489626556) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.749190938511327) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.73890142964635) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.0355329949238578) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.746498599439776) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.768066070199587) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.233009708737864) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.771929824561403) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.689100219458669) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.76663993584603) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.262008733624454) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.740207833733013) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.794871794871795) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.207142857142857) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.797404470079308) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.763665594855305) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.783333333333333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.779527559055118) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.227657572906867) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.761666666666667) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (4,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (7,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.800963081861958) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.236509758897819) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.782138024357239) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.782973621103117) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.770653514180025) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.790960451977401) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.78499106611078) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.75583596214511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.790289952798382) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.774193548387097) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.72264631043257) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.76103714085494) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.763432237369687) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.782475019215988) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.730407523510972) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.773790951638065) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.761982128350934) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.783053323593864) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.788710907704043) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.689165186500888) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.772525849335303) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.76969696969697) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.758314855875831) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.724884080370943) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.651079136690647) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.764423076923077) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.774355751099937) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (3,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.795969773299748) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.708588957055215) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.762096774193548) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.762198888202594) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.766025641025641) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.740412979351032) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.762996941896024) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.637873754152824) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.568627450980392) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.801925722145804) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.778235779060181) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.456404736275565) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.790863668807994) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.774007220216606) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.778894472361809) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.706779661016949) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.758990053557766) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.746347941567065) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.726739926739927) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.758139534883721) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.702113156100886) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.738664468260511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.793674698795181) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.759656652360515) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.210161662817552) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (5,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.790123456790123) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.781542898341745) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.516765285996055) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.671197960917587) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.748224151539068) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.701505757307352) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.744479495268139) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.806451612903226) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.776200135226504) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.782215523737754) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.744279946164199) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.775055679287305) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.800936768149883) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.797822706065319) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.785714285714286) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.822794691647151) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.791354945968412) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.775572519083969) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.699846860643185) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.734864300626305) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.668453976764969) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.798732171156894) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.713804713804714) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.780162842339008) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.750773993808049) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.780373831775701) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.73195020746888) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.795144157814871) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.747813411078717) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.743071161048689) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.77602523659306) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.771641791044776) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.700087950747581) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.804628999319265) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.748172757475083) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.786301369863013) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.774522292993631) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.777609682299546) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.789559543230016) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.788310762651461) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.744645799011532) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.811819595645412) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.777847702957835) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.673862760215883) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.765498652291105) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.611913357400722) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.757692307692308) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.797101449275362) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.804511278195489) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.780285035629454) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.0408163265306122) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.760104302477184) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.819672131147541) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (6,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.741312741312741) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.680456490727532) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.654418197725284) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.746172441579371) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.783279742765273) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.703216374269006) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.72249822569198) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (3,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.597320724980299) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.673196794300979) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.760330578512396) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.71701244813278) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.706355591311344) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.759316770186335) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.778294573643411) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.723646723646724) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.691455696202532) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.778248587570621) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.790697674418605) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.783634933123525) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.225058004640371) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.755555555555556) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.746196957566053) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.75984555984556) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.775732788002726) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.8) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.799467021985343) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.735372340425532) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.687105500450857) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.756134969325153) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.743388134381701) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.70028818443804) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.800623052959501) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.783171521035599) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.234866828087167) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (6,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.742351046698873) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.792971734148205) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (2,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.776906628652887) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.78129713423831) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.768768768768769) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.817864619678995) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.783004552352048) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.784167289021658) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.792805755395683) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.792421746293245) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.747051114023591) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.816434724983433) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.00262467191601047) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.779761904761905) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.258064516129032) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.807692307692308) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.808629088378566) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.800528401585205) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.757062146892655) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.703894195444526) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.694262890341322) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.802387267904509) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.751219512195122) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.766905330151153) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.664383561643836) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.748019017432647) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.717391304347826) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.754448398576512) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.35361216730038) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (4,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.795902285263987) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.73663101604278) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.793313069908815) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.75) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.755656108597285) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.776595744680851) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.78726483357453) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.736220472440945) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.76499647141849) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.768051118210863) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.666666666666667) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.76602086438152) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.695652173913043) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.626262626262626) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.785813630041725) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.708404802744425) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.629294755877034) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.802575107296137) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.789799072642967) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.619961612284069) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.713906111603189) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.783699059561129) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.779179810725552) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.670999187652315) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.428321678321678) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (6,0.56007226738934) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.633943427620632) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.75085910652921) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.765349032800673) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.779179810725552) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (2,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.784682080924855) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.774860779634049) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.780373831775701) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.244705882352941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.785763175906913) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.837570621468926) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.7601246105919) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.784067085953878) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.762811127379209) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.776432606941081) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.753911806543385) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.744379683597002) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.748858447488584) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.710108604845447) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.723051409618574) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.775181305398872) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.800929512006197) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.726307808946171) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.743791641429437) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.712005551700208) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.763969974979149) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.793650793650794) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.733113673805601) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (6,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (6,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (7,0.702362204724409) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.655021834061135) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.72210953346856) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (7,0.686119873817035) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.770338372930165) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.788990825688073) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.799222797927461) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.732888146911519) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.768601798855274) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.80835734870317) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.750147666863556) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.796502384737679) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.780766096169519) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.275334608030593) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.767203513909224) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.754047802621434) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.748137108792846) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.0344827586206896) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.755020080321285) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.76253081347576) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.80253766851705) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.771293375394322) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.544268406337372) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.743790849673202) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.239651416122004) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.757695343330702) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.654993514915694) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.768979591836735) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (6,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.782407407407407) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (4,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.241918665276329) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.754613807245386) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.78587528174305) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.736842105263158) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.741827885256838) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.758620689655172) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.776173285198556) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.791192103264996) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.749185667752443) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.787037037037037) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.71850699844479) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.778635778635778) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.745198463508322) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.774877650897227) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.786499215070643) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.700348432055749) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.753462603878116) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.792626728110599) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.741176470588235) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.765957446808511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.658008658008658) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.7765625) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.795050270688322) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.555133079847909) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.674740484429066) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.685673556664291) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.782824112303881) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.538314176245211) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.752365930599369) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.707638279192274) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (3,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (4,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.701612903225806) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.708487084870849) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.76875) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.618410700236035) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.154440154440154) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.803559206023272) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.768802228412256) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.707070707070707) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.705693664795509) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.792251169004676) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.747268754552076) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.776588151320485) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.766265060240964) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.163265306122449) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.579512195121951) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.742808798646362) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.715702479338843) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.73938679245283) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.80327868852459) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.769945778466305) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.787923416789396) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.600749063670412) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.748376623376623) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.622540250447227) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.707350901525659) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.778501628664495) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.767616191904048) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.783748361730013) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.785150078988941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.778123057799875) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.699236641221374) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.796795338674435) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.764617691154423) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.745791245791246) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.815028901734104) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.784883720930232) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.784711388455538) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.754426481909161) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.755795981452859) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.812742812742813) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.673497267759563) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.761437908496732) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.461095100864553) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.774668630338733) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.759148936170213) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.774395003903201) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.783608914450036) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.757939308398024) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.687631027253669) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.718964204112719) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.722778891115564) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.793243243243243) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.750716332378223) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.76459741856177) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (7,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.739656269891788) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.746395250212044) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.767284991568297) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (3,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.798223350253807) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.770580296896086) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.788355625491739) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.729684908789386) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.709849157054126) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.803459119496855) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.753898305084746) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.785658612626656) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.55378858746492) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.792452830188679) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.689908256880734) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.771604938271605) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.807888970051132) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.24896265560166) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.803041825095057) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.8125) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.724003127443315) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.768353528153956) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.754257907542579) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.751152073732719) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.711920529801324) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.773333333333333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.765990639625585) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.247058823529412) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.743548387096774) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.746177370030581) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.650392327811683) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.693706293706294) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (4,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.610915492957747) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.808646917534027) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.8218966846569) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.734099616858237) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.769911504424779) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.753184713375796) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.722488038277512) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.765990639625585) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.799199466310874) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.761389961389961) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.747336377473364) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.784810126582278) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.796570537802026) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.791758646063282) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.253521126760563) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.705432287681714) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.790584415584416) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.564727954971857) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.608775137111517) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.736022646850672) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.787456445993031) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.798114689709348) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.780337941628264) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.792018419033001) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (7,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.11070110701107) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (7,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.772200772200772) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.171683389074693) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (5,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.749797570850202) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.736688548504741) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.780790085205267) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.796758946657664) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.731966590736522) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.745393634840871) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.800959232613909) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.754349338900487) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.731297709923664) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.682512733446519) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.761020881670533) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.782870022539444) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.670618120237087) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.569811320754717) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.654594232059021) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.796403339755941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.771084337349397) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.0164609053497942) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.729751403368083) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.72) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.753558052434457) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.713656387665198) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.772655007949125) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.732336956521739) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.781666666666667) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.762043795620438) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.738284066330209) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.716917922948074) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (3,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.692116182572614) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.774531835205992) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.746987951807229) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.716862745098039) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.652766639935846) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.749521988527725) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.789259560618389) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.770949720670391) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.708383961117861) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.792511700468019) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.697916666666667) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.695876288659794) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.727420667209113) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.747044917257683) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.762225969645868) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.77491961414791) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.752040175768989) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.767019667170953) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.790697674418605) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.75642965204236) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (6,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.788519637462236) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.774821544451655) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.240252897787144) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.696110744891233) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.759247242050616) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.772264631043257) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (4,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.65300727032386) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.790629575402635) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.259593679458239) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.755277560594214) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.765543071161049) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.762805358550039) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.746590093323762) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.822342901474011) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.711356466876972) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.793478260869565) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.634275618374558) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.650709219858156) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.773680404916847) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.73394495412844) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.515410958904109) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.754978354978355) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.773448773448773) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.768020969855832) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.786707882534776) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.722662440570523) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.766638584667228) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.72477693891558) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.734987990392314) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.786254295532646) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.641095890410959) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.806318681318681) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.779794790844515) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.727149627623561) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.799061767005473) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (3,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.811428571428571) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.758718861209964) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.831444759206799) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.786479802143446) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.756756756756757) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.760224538893344) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.799682034976153) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.705882352941176) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.764468371467025) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.756159728122345) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.755134281200632) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.758169934640523) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.74591381872214) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.755852842809364) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.785657370517928) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.786567164179104) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.611218568665377) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.752857142857143) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.756602426837973) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.697961704756022) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.802884615384615) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.765306122448979) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.749058025621703) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.79053583855254) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.798771121351766) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.800316957210777) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.643799472295514) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.763369963369963) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.738001573564123) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (4,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (302,0.935897435897436) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (262,0.930594900849858) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (373,0.958133150308854) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (383,0.970954356846473) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (309,0.916850625459897) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (283,0.943396226415094) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (323,0.95676429567643) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (254,0.932107496463932) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (299,0.959112959112959) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (308,0.961379310344827) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (248,0.938571428571429) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (286,0.963215258855586) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (303,0.969529085872576) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (295,0.954102920723227) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (207,0.884498480243161) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (235,0.92867332382311) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (221,0.906020558002937) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (243,0.952249134948097) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (235,0.949035812672176) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (236,0.954102920723227) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (183,0.924608819345661) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (198,0.946191474493361) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (206,0.939118264520644) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (163,0.92264017033357) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (171,0.922970159611381) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (137,0.887397464578673) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (145,0.943262411347518) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (144,0.926058865757358) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (136,0.919212491513917) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (109,0.902015288394718) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (102,0.857566765578635) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (113,0.949080622347949) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.831913245546088) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.894183601962158) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.891061452513967) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.84299674267101) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.841710427606902) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.873280231716148) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.874743326488706) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (56,0.830838323353293) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.822840409956076) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.857571214392803) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.821165438713999) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.843235504652827) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.838805970149254) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.804444444444444) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.798737174427782) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.807782101167315) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.747307373653687) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (329,0.950980392156863) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (349,0.960553633217993) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (338,0.949057920446615) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (262,0.934782608695652) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (279,0.935028248587571) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (347,0.958333333333333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (357,0.970588235294118) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (275,0.945280437756498) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (214,0.8763197586727) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (236,0.935553946415641) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (292,0.954577218728162) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (329,0.971468336812804) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (255,0.946991404011461) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (281,0.959889349930844) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (274,0.940308517773306) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (188,0.919793966151582) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (228,0.918918918918919) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (237,0.94468085106383) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (235,0.945195729537366) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (209,0.948033707865168) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (241,0.954929577464789) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (174,0.922068463219228) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (172,0.924198250728863) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (180,0.925435540069686) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (175,0.954293628808864) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (159,0.929824561403509) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (136,0.870552611657835) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (121,0.87175572519084) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (153,0.92494639027877) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (112,0.82992125984252) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (121,0.915351506456241) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (133,0.922764227642276) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (96,0.917547568710359) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (91,0.894508670520231) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (78,0.854802680565897) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (80,0.914862914862915) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.863204096561814) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.893995552260934) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (58,0.850691915513474) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (60,0.888888888888889) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (56,0.849315068493151) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.825019794140934) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.848845867460908) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.77502001601281) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.830788804071247) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.784988272087568) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.819858156028369) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.822373393801965) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.832572298325723) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.823693379790941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (360,0.958654519971969) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (355,0.953405017921147) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (357,0.962025316455696) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (289,0.934497816593886) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (269,0.86910197869102) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (317,0.948611111111111) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.953910614525139) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (259,0.875384615384615) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (292,0.945583038869258) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (300,0.950175438596491) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (278,0.948336871903751) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (258,0.932489451476793) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.957805907172996) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (300,0.963493199713672) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (318,0.964210526315789) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (238,0.927641099855282) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (287,0.956036287508723) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (222,0.921511627906977) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.925764192139738) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (257,0.953323903818953) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (221,0.939265536723164) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (215,0.927234927234927) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (176,0.914705882352941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (203,0.947368421052632) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (158,0.920245398773006) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (148,0.911917098445596) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (169,0.922749822820695) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (151,0.90028901734104) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (165,0.930914166085136) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (136,0.914893617021276) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (137,0.912398921832884) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (101,0.922413793103448) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (101,0.89900426742532) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (100,0.926359256710254) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (86,0.888571428571428) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (73,0.86046511627907) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.822981366459627) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (78,0.875714285714286) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (72,0.884917798427448) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.909732016925247) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.86377245508982) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.893124574540504) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.795811518324607) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.866176470588235) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.825278810408922) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.839319470699433) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.814390842191333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.791124713083397) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.85878962536023) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.811361981063365) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (361,0.961990324809951) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (400,0.974180041870202) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (384,0.973121984838043) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (356,0.973756906077348) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (357,0.975103734439834) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (338,0.962025316455696) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (369,0.973463687150838) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (234,0.890566037735849) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (272,0.964459930313589) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (340,0.969739619985925) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (299,0.964607911172797) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (297,0.970954356846473) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (307,0.970034843205575) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (291,0.966850828729282) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (273,0.969571230982019) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (286,0.97464016449623) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (224,0.943078004216444) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (264,0.967474048442907) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (234,0.961618981158409) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (237,0.957627118644068) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (205,0.967559943582511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (212,0.934579439252336) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (184,0.953103448275862) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (188,0.936886395511921) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (168,0.952908587257618) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (126,0.870769230769231) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (120,0.879154078549849) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (147,0.952836637047163) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (147,0.93408929836995) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (130,0.930808448652586) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (119,0.912778904665314) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (99,0.91399416909621) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (116,0.922330097087379) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.871064467766117) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (86,0.901387874360847) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (85,0.88626907073509) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (72,0.890792291220557) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.868827160493827) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.844514601420679) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.843226788432268) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.858630952380952) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.869446343130553) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.837430610626487) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.853087295954578) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.821917808219178) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.802241793434748) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.827933765298776) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.842654735272185) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.816577129700691) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.814296814296814) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (336,0.957431960921144) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (344,0.953310104529617) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (317,0.956645344705046) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (375,0.963066202090592) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (340,0.960283687943262) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (244,0.882175226586103) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (353,0.966480446927374) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (322,0.959774170783345) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.958017894012388) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (292,0.958066808813077) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (304,0.964838255977496) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (297,0.950608446671439) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (228,0.878012048192771) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (255,0.940406976744186) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (287,0.964985994397759) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (264,0.963117606123869) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (223,0.93915533285612) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (183,0.925872093023256) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (266,0.949856733524355) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (247,0.951856946354883) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (219,0.927075812274368) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.946206896551724) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (179,0.928312816799421) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (192,0.944793850454228) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (178,0.955096222380613) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (178,0.926724137931034) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (178,0.929618768328446) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (161,0.935574229691877) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (155,0.952249134948097) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (121,0.912152269399707) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (119,0.910791366906475) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (90,0.836335160532498) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (97,0.900293255131965) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (88,0.896746817538897) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (84,0.905011219147345) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (77,0.850152905198777) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.887943262411347) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (67,0.882058613295211) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (73,0.902404526166902) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.871794871794872) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.820109976433621) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.853582554517134) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.836781609195402) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.839452843772498) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.819314641744548) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.808208366219416) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.824727272727273) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.791967871485944) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.81650700073692) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.792297111416781) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (380,0.967428967428967) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (354,0.970446735395189) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (295,0.965948575399583) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (267,0.92790863668808) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (367,0.964754664823773) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (313,0.948682385575589) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (259,0.881608339538347) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (349,0.965469613259669) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (329,0.955570745044429) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (313,0.965181058495822) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (294,0.962131837307153) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (304,0.95807560137457) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (223,0.880418535127055) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (228,0.881688018085908) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (287,0.95807560137457) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (222,0.931623931623932) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (264,0.942934782608695) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (208,0.926690391459075) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (205,0.879761015683346) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (239,0.935135135135135) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (179,0.882572924457741) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (201,0.926375982844889) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (160,0.869179600886918) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (165,0.875748502994012) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (161,0.92972972972973) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (176,0.946116165150455) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (186,0.947079037800687) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (152,0.918497519489723) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (163,0.951523545706371) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (111,0.88138030194105) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (124,0.917142857142857) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (112,0.902266288951841) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (96,0.864253393665158) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (86,0.919945725915875) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (83,0.88569374550683) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (88,0.918518518518518) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (75,0.856512141280353) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (73,0.896232650363516) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.885359116022099) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.842911877394636) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (52,0.853658536585366) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.870481927710843) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.875636363636364) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.84558327714093) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.856948228882834) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.843326885880077) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.811102544333076) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.832151300236407) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.776772247360482) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.862800565770863) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (288,0.893129770992366) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (316,0.942266571632217) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (380,0.973163841807909) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (368,0.976256983240223) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (359,0.968332160450387) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (240,0.891603053435114) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (322,0.962290502793296) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (335,0.966386554621849) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (340,0.968287526427061) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (342,0.977591036414566) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (273,0.967247386759582) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (293,0.971187631763879) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (303,0.977746870653685) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (255,0.9593837535014) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (250,0.936344969199179) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (227,0.93768115942029) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (290,0.968011126564673) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (189,0.893262679788039) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (264,0.960111966410077) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (191,0.93103448275862) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (232,0.956276445698166) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (132,0.856477889837083) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (177,0.927745664739884) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (205,0.958479943701618) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (175,0.93768115942029) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (134,0.882664647993944) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (127,0.925872093023256) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (151,0.913169319826339) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (122,0.906724511930586) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (142,0.93173821252639) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (109,0.858461538461538) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (121,0.909708078750849) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (85,0.884241971620612) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (89,0.900785153461813) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.896451846488052) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (84,0.894623655913978) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.853435114503817) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.832558139534884) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.835886214442013) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.866914498141264) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.852281515854602) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.858654572940287) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.829411764705882) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.862637362637362) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.804453723034099) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.809220985691574) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.811361981063365) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.888059701492537) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.826830937713894) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.823620823620824) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (363,0.963380281690141) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (343,0.967651195499297) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (363,0.963276836158192) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (352,0.967109867039888) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (232,0.87044220325834) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (231,0.867132867132867) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (349,0.962702322308233) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (344,0.96629213483146) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (339,0.97752808988764) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (285,0.940836940836941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (288,0.959887403237157) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (219,0.868421052631579) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (247,0.934687953555878) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (291,0.946554149085794) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (272,0.938775510204082) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (259,0.950749464668094) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (245,0.927641099855282) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (195,0.92882818116463) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (242,0.945351312987935) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (189,0.873174481168332) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (169,0.86910197869102) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (178,0.917510853835022) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (203,0.936139332365747) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (185,0.942737430167598) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (176,0.919308357348703) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (179,0.941342756183746) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (128,0.910384068278805) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (156,0.942172073342736) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (144,0.943632567849687) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (115,0.921052631578947) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (119,0.87832973362131) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (98,0.871910112359551) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (101,0.911485003657644) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (75,0.838862559241706) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.924285714285714) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (73,0.884588804422944) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (69,0.877037037037037) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.883227176220807) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.85439763488544) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (58,0.87598944591029) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.819466248037676) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.836003051106026) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.856711915535445) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.786011656952539) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.808340016038492) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.838810641627543) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.87454677302393) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.784345047923323) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.805212620027435) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.752553024351925) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (395,0.962251201098147) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (281,0.934296028880866) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (381,0.963673749143249) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (331,0.949128919860627) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (316,0.937238493723849) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (271,0.937544867193108) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (252,0.878877400295421) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (287,0.937845303867403) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (357,0.96986301369863) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (312,0.960055096418733) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (301,0.9648033126294) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (302,0.950105411103303) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (323,0.964137931034483) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (272,0.9637234770705) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (294,0.954607977991747) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (260,0.939353099730458) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (259,0.962042788129744) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (225,0.929336188436831) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (269,0.953232462173315) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.938833570412518) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (230,0.943189596167009) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (186,0.884241971620612) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (171,0.919540229885057) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (169,0.908296943231441) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (186,0.934871099050203) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (183,0.95407813570939) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (137,0.883582089552239) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (151,0.941828254847645) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (130,0.91027496382055) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (152,0.907518296739854) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (117,0.909698996655518) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (118,0.886111111111111) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (99,0.913454545454545) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (106,0.891628812459442) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.875798438608942) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (82,0.887142857142857) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.877840909090909) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.888230940044412) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.885793871866295) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.808868501529052) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.825) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.860411899313501) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.836913285600636) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.874285714285714) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.791862284820031) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.827208756841282) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.793242156074014) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.859479553903346) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.799363057324841) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.809266409266409) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (281,0.930935251798561) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (321,0.952646239554317) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (387,0.962131837307153) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (248,0.877458396369138) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (372,0.963117606123869) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (325,0.957805907172996) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (312,0.951135581555402) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (316,0.955182072829132) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (357,0.96) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (226,0.873369148119724) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (308,0.96455872133426) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (313,0.9721059972106) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (317,0.963636363636364) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (279,0.95049504950495) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (207,0.876438986953185) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (278,0.963380281690141) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (223,0.904129793510324) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (256,0.96140350877193) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (235,0.945659844742413) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (239,0.954732510288066) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (177,0.874905231235785) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (179,0.857798165137615) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (220,0.959212376933896) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (171,0.925287356321839) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (192,0.956036287508723) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (152,0.909752547307132) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (175,0.95575221238938) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (144,0.929394812680115) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (136,0.922651933701657) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (137,0.943342776203966) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (110,0.861132660977502) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (111,0.91114245416079) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (107,0.90144727773949) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (100,0.899786780383795) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (91,0.858571428571429) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.839694656488549) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (71,0.821321321321321) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.898813677599442) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (58,0.857988165680473) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.852897473997028) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.884968242766408) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.816064257028112) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.857798165137615) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.833212996389892) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.824508320726172) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.835666912306559) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.841622035195103) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.827823691460055) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.793388429752066) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.806826997672614) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-20 figurefactory/files/ev_chl_eps.tex
LSE theory and experiments

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{mycolor1}{rgb}{1,0.04,0}
\definecolor{mycolor2}{rgb}{1,0.08,0}
\definecolor{mycolor3}{rgb}{1,0.12,0}
\definecolor{mycolor4}{rgb}{1,0.16,0}
\definecolor{mycolor5}{rgb}{1,0.2,0}
\definecolor{mycolor6}{rgb}{1,0.24,0}
\definecolor{mycolor7}{rgb}{1,0.28,0}
\definecolor{mycolor8}{rgb}{1,0.32,0}
\definecolor{mycolor9}{rgb}{1,0.36,0}
\definecolor{mycolor10}{rgb}{1,0.4,0}
\definecolor{mycolor11}{rgb}{1,0.44,0}
\definecolor{mycolor12}{rgb}{1,0.48,0}
\definecolor{mycolor13}{rgb}{1,0.52,0}
\definecolor{mycolor14}{rgb}{1,0.56,0}
\definecolor{mycolor15}{rgb}{1,0.6,0}
\definecolor{mycolor16}{rgb}{1,0.64,0}
\definecolor{mycolor17}{rgb}{1,0.68,0}
\definecolor{mycolor18}{rgb}{1,0.72,0}
\definecolor{mycolor19}{rgb}{1,0.76,0}
\definecolor{mycolor20}{rgb}{1,0.8,0}
\definecolor{mycolor21}{rgb}{1,0.84,0}
\definecolor{mycolor22}{rgb}{1,0.88,0}
\definecolor{mycolor23}{rgb}{1,0.92,0}
\definecolor{mycolor24}{rgb}{1,0.96,0}
\definecolor{mycolor25}{rgb}{1,1,0}
\definecolor{mycolor26}{rgb}{0.96,1,0.04}
\definecolor{mycolor27}{rgb}{0.92,1,0.08}
\definecolor{mycolor28}{rgb}{0.88,1,0.12}
\definecolor{mycolor29}{rgb}{0.84,1,0.16}
\definecolor{mycolor30}{rgb}{0.76,1,0.24}
\definecolor{mycolor31}{rgb}{0.72,1,0.28}
\definecolor{mycolor32}{rgb}{0.68,1,0.32}
\definecolor{mycolor33}{rgb}{0.64,1,0.36}
\definecolor{mycolor34}{rgb}{0.56,1,0.44}
\definecolor{mycolor35}{rgb}{0.52,1,0.48}
\definecolor{mycolor36}{rgb}{0.48,1,0.52}
\definecolor{mycolor37}{rgb}{0.4,1,0.6}
\definecolor{mycolor38}{rgb}{0.36,1,0.64}
\definecolor{mycolor39}{rgb}{0.28,1,0.72}
\definecolor{mycolor40}{rgb}{0.24,1,0.76}
\definecolor{mycolor41}{rgb}{0.16,1,0.84}
\definecolor{mycolor42}{rgb}{0.12,1,0.88}
\definecolor{mycolor43}{rgb}{0.04,1,0.96}
\definecolor{mycolor44}{rgb}{0,0.96,1}
\definecolor{mycolor45}{rgb}{0,0.92,1}
\definecolor{mycolor46}{rgb}{0,0.84,1}
\definecolor{mycolor47}{rgb}{0,0.76,1}
\definecolor{mycolor48}{rgb}{0,0.68,1}
\definecolor{mycolor49}{rgb}{0,0.6,1}
\definecolor{mycolor50}{rgb}{0,0.52,1}
\definecolor{mycolor51}{rgb}{0,0.44,1}
\definecolor{mycolor52}{rgb}{0,0.36,1}
\definecolor{mycolor53}{rgb}{0,0.28,1}
\definecolor{mycolor54}{rgb}{0,0.16,1}
\definecolor{mycolor55}{rgb}{0,0.08,1}
\definecolor{mycolor56}{rgb}{0.44,1,0.56}
\definecolor{mycolor57}{rgb}{0.32,1,0.68}
\definecolor{mycolor58}{rgb}{0.2,1,0.8}
\definecolor{mycolor59}{rgb}{0.08,1,0.92}
\definecolor{mycolor60}{rgb}{0,1,1}
\definecolor{mycolor61}{rgb}{0,0.88,1}
\definecolor{mycolor62}{rgb}{0,0.8,1}
\definecolor{mycolor63}{rgb}{0,0.72,1}
\definecolor{mycolor64}{rgb}{0,0.64,1}
\definecolor{mycolor65}{rgb}{0,0.56,1}
\definecolor{mycolor66}{rgb}{0,0.48,1}
\definecolor{mycolor67}{rgb}{0,0.4,1}
\definecolor{mycolor68}{rgb}{0,0.32,1}
\definecolor{mycolor69}{rgb}{0,0.24,1}
\definecolor{mycolor70}{rgb}{0,0.2,1}
\definecolor{mycolor71}{rgb}{0,0.12,1}
\definecolor{mycolor72}{rgb}{0,0.04,1}
\definecolor{mycolor73}{rgb}{0,0,0.56}
\definecolor{mycolor74}{rgb}{0.8,1,0.2}
\definecolor{mycolor75}{rgb}{0.6,1,0.4}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-6pt},
ylabel shift={-4pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=400,
xlabel={Samples},
ymin=0.5, ymax=1,
ylabel={$F_1$-score},
name=plot1,
axis lines*=left,
colormap={mymap}{[1pt] rgb(0pt)=(0.5,0,0); rgb(8pt)=(1,0,0); rgb(24pt)=(1,1,0); rgb(40pt)=(0,1,1); rgb(56pt)=(0,0,1); rgb(63pt)=(0,0,0.5625)},
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.06, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
tickwidth=0.1cm,
colorbar/width=0.15cm,
point meta min=0,
point meta max=1
]

\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (383,0.920627376425855) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (365,0.954618015963512) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (357,0.919687277896233) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (360,0.927679623085983) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (317,0.932016536518144) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.924838940586972) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (276,0.933055362520269) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (270,0.913882352941176) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (259,0.932475884244373) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (266,0.92346471127406) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (243,0.926806526806527) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (236,0.949767441860465) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (224,0.914419695193435) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (212,0.926267281105991) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (213,0.930856067732832) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (202,0.890752387607733) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (185,0.933861201676758) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (176,0.937427308676436) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (171,0.922470433639947) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (154,0.904059877523248) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (160,0.916763273823325) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (141,0.884670147128619) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (139,0.922135968007528) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (124,0.886009224687019) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (129,0.868557919621749) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (114,0.913023884632717) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (108,0.878591288229842) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (108,0.899885974914481) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (102,0.878853046594982) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (102,0.854586129753915) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.820249449743213) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (88,0.897721989772199) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.915261659732866) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (85,0.888432580424367) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (78,0.862354892205638) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (72,0.874582312319002) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.806558935361217) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (71,0.793864745526377) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.89149560117302) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.843316889828517) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.84857973607694) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.827240143369175) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (60,0.813210379583959) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (52,0.877560309512972) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.851585623678647) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.83169673441425) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.704498269896194) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.809187279151943) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.689636313918512) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.801229508196721) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.715773809523809) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.809985458070771) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.84080445844439) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.747091552857865) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.856391875746714) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.796696814785686) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.855006796556411) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.811505507955936) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.8166627441751) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.782567947516401) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.774969915764139) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.816287425149701) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.772799636115533) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.765501165501165) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.800239234449761) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.734396996715157) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.649639423076923) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.827707919699978) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.599538372763993) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.533975903614458) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.769065981148243) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.768549280177187) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.802575107296137) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.672905331882481) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.696956889264581) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.58615221987315) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.621519584709769) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.777078651685393) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.697664543524416) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.486176836861768) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.684233449477352) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.753533568904594) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.527763627101375) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.721542608335061) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.702539602715615) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.659987856709168) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!60!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.665330661322645) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.503211393465512) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (6,0.329348245275742) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.816740960871718) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.780425313861132) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.752901353965184) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.790649884407912) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor56,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.578715056400196) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor56,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.605374077976818) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.739073540957864) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.746866065537717) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.665319525132609) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.66875) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor57,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.840089086859688) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.5657469550087) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.772897815051865) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.606294536817102) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.803651194406681) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor58,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.751927437641723) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor58,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.87147766323024) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.581502576620559) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.545933014354067) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.846911800048065) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor59,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.717948717948718) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor59,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.56657567485593) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.712) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.693888588426176) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor60,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.692395005675369) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.809546092653252) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.694828469022017) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.513928368391131) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.727987764911514) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor61,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.669603524229075) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.753276792598304) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.702082447938801) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor62,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.632636437686668) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.684998772403634) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.355127322780454) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor63,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.644655847789591) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.539637599093998) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.467532467532467) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor64,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.324404761904762) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.680245291283399) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.700901393062005) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor65,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.658042744656918) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.718541574032903) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.768842105263158) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor66,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.618575851393189) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.788557806912992) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor67,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.593739916101968) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor67,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.655133295519002) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.589428723972237) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor68,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.668627450980392) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.543239227340267) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.622902561083309) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor69,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.544344286129689) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor70,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.57837528604119) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.574266574266574) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor71,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.630492323980942) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor71,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.715287517531557) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.680589022757697) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor72,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.641860465116279) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.780365296803653) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.611721611721612) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.584743057772103) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.669121514992109) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.676288659793814) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.170266836086404) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.41851616994293) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.692734478203434) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.638255698711596) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.297386823702613) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!64!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.437275985663082) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!60!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.534194698151036) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor73,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.54445165476963) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.317921283912877) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.592728383745799) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.427279053583855) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.494597839135654) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.586343394359228) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.809259259259259) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.763672854992474) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.6855693868142) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.611425630468348) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor56,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.779730740463725) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor56,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.743899851474645) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.819678714859438) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.840132827324478) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.729564863765758) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.693003144654088) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor57,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.803216439580076) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.392037786774629) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.697445512069369) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.652960118900173) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.78) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor58,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.615985576923077) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor58,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.774031202818319) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.756616257088847) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.83106449453247) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.758706467661691) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor59,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.744228157537347) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor59,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.731303288672351) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.594059405940594) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.693709327548807) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor60,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.643767313019391) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.586734693877551) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.580510992275698) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.703553299492386) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.64476821192053) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor61,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.658665922411387) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.647314949201741) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.718332442544094) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor62,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.808384417638916) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.681485649971863) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.604446616173955) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor63,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.43978349120433) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.678554886521538) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.445234708392603) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor64,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.521162672106068) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.793095616625028) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.706996770721206) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor65,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.802838766910623) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.205088062622309) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.810042633822833) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor66,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.72569688451628) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.58434026099565) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor67,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.604332327940773) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor67,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.787039106145251) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.519722975007528) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor68,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.381634646694888) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.613044599123485) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.628063560463237) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor69,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.724870017331022) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor70,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.555399719495091) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.663329820864067) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor71,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.618096357226792) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor71,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.333671742808799) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.713962574542463) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor72,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.61759029500965) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.447385003150599) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.394671107410491) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.687603305785124) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.605599104143337) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.661727133367399) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.520259820600062) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.315201192250373) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.640275387263339) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.652136994056043) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.663863337713535) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!64!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.378052283826487) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!60!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.572074618428491) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor73,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.523722627737226) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.688920454545454) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.229361225252148) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (5,0.274867122247532) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.462440659033789) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.509664292980671) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.796888141295206) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.763816925734024) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.818261633011413) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.73870636550308) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor56,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.839582344565733) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor56,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.809427609427609) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.779917469050894) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.841784037558685) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.753956834532374) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.735879259089869) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor57,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.822724161533196) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.602597402597402) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.793499043977055) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.83207039843559) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.723041474654378) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor58,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.810580204778157) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor58,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.702300720427609) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.76307295029051) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.790393933010322) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.622570194384449) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor59,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.762422047877691) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor59,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.642542787286063) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.692270992366412) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.715997915581032) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor60,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.764863828154967) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.660366552119129) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.444444444444444) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.758252427184466) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.791684711996535) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor61,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.708605664488017) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.293010752688172) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.604067985511284) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor62,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.108061002178649) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.79496317415063) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.41096817874069) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor63,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.37992590097676) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.599163179916318) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.642300456866434) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor64,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.697699304440877) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.533501896333755) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.77087114337568) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor65,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.597621119814331) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.674875556719937) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.439812096300646) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor66,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.705913272010512) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.602993197278911) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor67,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.695475113122172) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor67,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.642878207018579) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.665593129361245) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor68,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.814687567103285) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.667370644139387) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.613364595545135) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor69,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.67652572380754) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor70,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.448130081300813) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.614322691975841) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor71,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.375272727272727) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor71,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.49875173370319) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.432941176470588) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor72,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.568326271186441) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.638865004299226) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.628442663995994) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.281635802469136) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.566705336426914) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.286647314949202) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.177723177723178) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.497709923664122) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.66155950752394) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.348736462093863) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.680682661390057) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!64!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.637261990841166) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!60!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.56555590158829) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor73,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.703451882845188) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.240480961923848) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.282677391554151) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (8,0.659445843828715) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (4,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (6,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.796187683284457) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.658215010141988) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.809181544168792) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.834630350194552) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor56,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.77797434763379) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor56,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.804736587723538) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.730873978707601) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.838006952491309) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.827505827505827) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.732490272373541) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor57,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.668514176081859) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.83093447905478) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.682313892840208) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.752908329455561) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.680164018452076) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor58,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (26,0.766307541625857) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor58,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.7337957426453) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.810680779408227) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.665826612903226) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.77572793954212) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor59,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.688967971530249) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor59,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.81453634085213) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (25,0.611478444855858) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.765874939408628) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor60,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (23,0.645833333333333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.75971515768057) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.700170035896467) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.712065136935603) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.699408588326048) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor61,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (24,0.770192085165471) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.551943290149108) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.763976506417228) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor62,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (22,0.806384976525822) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.804878048780488) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.667990293403927) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor63,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (21,0.684081632653061) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.628804347826087) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (20,0.731782945736434) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor64,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.678260869565217) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.689445048966267) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.724023825281271) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor65,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.720123361603701) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (18,0.676339285714285) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.543382997370727) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor66,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.559206798866855) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (19,0.688484251968504) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor67,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.689798750867453) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor67,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.681792073520965) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.791161178509532) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor68,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (16,0.659885237350026) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.34565560821485) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.628371089536138) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor69,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.603129445234708) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor70,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.423952095808383) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (17,0.708926875593542) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor71,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (14,0.761444771104578) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor71,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.58952849291293) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.670391061452514) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor72,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.713216957605985) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.415430267062314) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (15,0.531341534856473) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.390929415522197) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (13,0.657091561938959) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.0748663101604278) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!80!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (12,0.323261740080087) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!76!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.242321970975363) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!72!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.45557963163597) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!68!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.700075169130544) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!64!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.620746887966805) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!60!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (9,0.596015015882183) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor73,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.225817555938038) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.608452280996362) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (10,0.555043227665706) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (11,0.773273579140354) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (5,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (3,0) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (394,0.952903520804755) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (400,0.950011412919425) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (376,0.964441385638908) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (342,0.952315134761575) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (363,0.953930781572313) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (360,0.951876583007138) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (321,0.939543636791343) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (329,0.931759149940968) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (307,0.931932171005493) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (323,0.955012559945193) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (288,0.938938468764678) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (276,0.946866485013624) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (278,0.948168624740843) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (271,0.933486766398159) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (266,0.941577631279836) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (260,0.955203619909502) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (242,0.942592592592592) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (257,0.9446104343829) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (232,0.945995423340961) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (237,0.92283882378952) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (224,0.954745880714783) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (218,0.941479400749063) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (193,0.926126976634411) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (200,0.929334242217678) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (192,0.908125577100646) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (189,0.906093189964158) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (180,0.919384902143523) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (164,0.892163429336905) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (168,0.913156036714521) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (167,0.923112338858195) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (149,0.88504753673293) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (149,0.921514312096029) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (156,0.918466898954704) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (139,0.911363110391113) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (139,0.920341722465943) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (133,0.917223887479825) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (139,0.915866483767718) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (108,0.899374097255657) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (125,0.921731123388582) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (111,0.878522377456784) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (114,0.89873417721519) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (101,0.894033412887828) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (109,0.905942910622368) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (105,0.912200684150513) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (104,0.880537580886013) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (100,0.902199344875994) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (99,0.92507068803016) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (99,0.883901992214335) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.907118644067797) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (94,0.930178612850847) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (85,0.880158905318914) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (85,0.881091617933723) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (82,0.898850035203004) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (77,0.792304126101066) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.880568720379147) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.857019251568246) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.880762411347518) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (70,0.917994917994918) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.887558216899534) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (69,0.889949868703748) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.896680691912108) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.85852534562212) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.872617387261739) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.836189170664839) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.737826685006877) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (56,0.819440815259995) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.805837894188168) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.863237139272271) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.875623960066556) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.873100983020554) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.832384253528101) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.834539089848308) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.76730869338886) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.814760508308895) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.852720236740269) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.825171516441921) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.81019955654102) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.900023747328426) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.854397950469684) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.845379688929552) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.872364039955605) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.724239450441609) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.847392144236961) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.735991379310345) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.736179529282977) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.853647058823529) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.842877425461429) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.827407581822463) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.812372071867182) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.813519813519813) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.742579600647598) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.760679611650485) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.769528978484202) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.678711704634721) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.79477069931521) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.770513383062747) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.636017410228509) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (396,0.952712100139082) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (392,0.947614593077643) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (392,0.936249418334109) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (397,0.945989427717766) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (376,0.948060784758449) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (373,0.952710495963091) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (349,0.937049941927991) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (368,0.939024390243902) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (354,0.953697304768486) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (315,0.956302905513612) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (303,0.899073622623111) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (327,0.933174224343675) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (295,0.940575673166202) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (295,0.93886058360352) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (300,0.922497055359246) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (293,0.896750902527076) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (261,0.921972235519387) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (269,0.93308463511308) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (247,0.930308699719364) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (252,0.939981949458484) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (230,0.867843511450382) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (252,0.848318804483188) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (225,0.886192671681631) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (218,0.92644044636757) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (212,0.893278728017345) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (192,0.923356009070295) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (201,0.938009049773756) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (189,0.914433474377057) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (186,0.930389727416085) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (183,0.91874859329282) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (176,0.918955123911587) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (176,0.913441238564391) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (162,0.908678903240426) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (151,0.85012285012285) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (140,0.916628701594533) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (151,0.890788224121557) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (149,0.878963202962277) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (133,0.869397383658589) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (138,0.901322923443938) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (134,0.874090407938258) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (127,0.884851344974044) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (125,0.881990521327014) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (115,0.847767086109055) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (116,0.919582008178101) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (113,0.877152163797115) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (109,0.905454545454545) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (107,0.904587155963303) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (96,0.788807785888078) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (90,0.870774497218656) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (93,0.911121239744758) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (86,0.830568124685772) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (90,0.859353023909986) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.882057989971659) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (85,0.908190819081908) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (88,0.901736745886654) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.864637465973769) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (77,0.893464637421665) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.817712177121771) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (73,0.878242580042066) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (72,0.831455169034787) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (69,0.865523241362168) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.842843779232928) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.874828060522696) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.88711943793911) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.84228684080828) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.848019801980198) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (58,0.837431367868226) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.885245901639344) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.824888050907377) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.862811517057827) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.830261881668283) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.84761045987376) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.84503127171647) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.824973544973545) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.84503745318352) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.875670404680644) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.787304837471206) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.823614457831325) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.794488001900689) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.854377880184332) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.689564068692206) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.877663079288381) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.838980954736582) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.879907621247113) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.883087907184293) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.829443447037702) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.801331853496115) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.819965234666004) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.844422211105553) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.82573849324479) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.819451371571072) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.764828303850156) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.743595999024152) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.821473790833122) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.778629395852119) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.720295202952029) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.66336361134049) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.805212939259949) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.752428334517887) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (397,0.934160305343511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (397,0.94524089306698) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (367,0.929148834997622) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (367,0.947294448348559) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (389,0.933301458283528) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (379,0.93422880963409) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (364,0.945616502578528) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (337,0.933944069431051) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (323,0.947319347319347) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (352,0.927371658386562) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (334,0.918444760550024) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (309,0.942599620493359) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (298,0.940340909090909) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (299,0.915570437694331) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (277,0.934536201711774) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (274,0.928488775746355) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (274,0.940456578018357) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (273,0.932895354293759) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (260,0.926910299003322) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (241,0.929078014184397) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (235,0.942850478189876) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (225,0.935612268789511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (218,0.916131989000917) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (227,0.888836662749706) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.885599598595083) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.935409986257444) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (196,0.910611854684512) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (190,0.902900982977703) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (169,0.89730241362991) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (186,0.915159944367177) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (158,0.908758289503773) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (162,0.886347390993567) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (164,0.90384167636787) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (151,0.902107728337237) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (155,0.824947832135404) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (142,0.940032414910859) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (140,0.876129978011239) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (133,0.890436397400186) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (129,0.923581809657759) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (130,0.904063476797307) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (133,0.924432081594808) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (117,0.890865384615385) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (121,0.886433106042793) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (114,0.887542413960252) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (115,0.868705882352941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (105,0.878974845752254) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (105,0.866553644950351) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (102,0.897697602658438) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (106,0.897867564534231) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (100,0.869216241737488) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (94,0.854842529007814) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (83,0.880474452554744) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (88,0.871479289940828) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (91,0.862068965517241) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (81,0.823916898910565) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (81,0.87471317117944) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (75,0.907271839921913) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (70,0.888687372477896) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (75,0.850431447746884) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.86952675807165) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.847666971637694) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (72,0.773658283640135) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (67,0.878610108303249) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (69,0.883764705882353) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.887003126395712) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.860380998312033) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.879873073436083) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.740056022408963) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.848177203507153) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.852720918622067) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.788466318667661) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (52,0.776524741081703) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.802967083912842) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.807327001356852) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.74825550187869) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.808443745789355) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.859515570934256) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.800415368639668) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.839123699933613) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.85170429393537) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.852880422308928) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.788147007889167) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.670103092783505) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.831607384061234) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.769647696476965) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.820658611703388) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.736505032021958) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.838047445255474) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.827401267674305) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.841885302995124) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.732270732270732) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.812539987204094) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.77541843617287) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.814403200711269) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.702660406885759) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.717720751667003) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.749895963379109) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.833855799373041) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.771508603441377) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (378,0.942979490646833) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (381,0.943245778611632) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (380,0.94035257184255) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (383,0.962669155389641) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (331,0.925541941564562) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (324,0.938212927756654) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (309,0.954211150652432) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (308,0.956339990710636) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (320,0.943022694350555) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (301,0.954808806488992) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (304,0.932391048292108) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (281,0.922196796338673) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (249,0.926408942710759) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (282,0.927337278106509) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (268,0.926519076778144) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (241,0.924154025670945) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (227,0.937823834196891) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (230,0.912776991984913) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (223,0.926325668700141) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (212,0.910007199424046) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (218,0.913730255164034) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.937013446567587) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (212,0.938219403335682) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (207,0.917582417582417) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (191,0.894787183165949) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (177,0.914111865200094) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (165,0.914821944177093) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (176,0.9206206431302) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (161,0.903480622068625) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (167,0.887135341941655) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (148,0.920459770114942) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (158,0.915129151291513) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (158,0.856050955414013) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (143,0.940582702454691) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (139,0.893748514380794) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (138,0.891955098222638) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (129,0.912106135986733) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (118,0.910209662716499) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (119,0.893617021276596) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (111,0.910199296600234) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (109,0.888345956511116) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (111,0.908580780921206) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (118,0.85981724983285) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (102,0.807237999497361) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (101,0.920968478757423) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (94,0.905616406432067) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (94,0.909007981755986) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (93,0.871028923660503) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (94,0.892279662946937) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (89,0.87518573551263) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (80,0.888736263736264) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (80,0.834558004898686) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (75,0.892543365622888) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.871602624179944) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (73,0.920446774561204) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (72,0.841117108659939) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.88423058599333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.750309329373917) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.819299044151115) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.869031975470872) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.85938242280285) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.872703412073491) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (58,0.801672903367818) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (58,0.895564421497301) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (56,0.824200913242009) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.842509603072983) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.868368479467258) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.750543478260869) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.84572864321608) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.865376344086021) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.849712313003452) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.818655420491193) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.82167530224525) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.787552070570938) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.764059753954306) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.780626780626781) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.837742504409171) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.796061269146608) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.840107190710138) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.844711872251794) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.771172825338535) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.826396872844332) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.782767266925005) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.793881644934804) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.758937198067633) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.804933299773471) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.816696914700544) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.858898398068905) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.750996015936255) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.766917293233083) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.865286236297198) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.814657008947593) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.683255572835666) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.889537494387068) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.70027397260274) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.710260499734184) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (359,0.938007894125842) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (373,0.929148396030464) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (373,0.930340199028003) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (365,0.943217665615142) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (351,0.934422509643749) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (326,0.938672768878719) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (330,0.943181818181818) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (314,0.917971488665576) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (298,0.927476549988561) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (280,0.927379341452413) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (275,0.939483900433889) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (277,0.919571656413762) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (282,0.903471231573942) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (279,0.936288088642659) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (259,0.926994141505182) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (238,0.910505836575875) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (251,0.93389395001168) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (222,0.89699472356045) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (196,0.922896097790315) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (212,0.929571106094808) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (206,0.941471191072649) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (209,0.915285880980163) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (187,0.937081659973226) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (169,0.891990846681922) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (173,0.928407526388251) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (179,0.935153583617747) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (175,0.893796992481203) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (159,0.896208530805687) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (164,0.891215293582157) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (144,0.894282380396733) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (160,0.906091928744227) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (147,0.896969696969697) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (152,0.902559286217422) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (135,0.926115241635688) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (128,0.910437398750289) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (129,0.884047786366831) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (123,0.919790956600773) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (116,0.889611797874648) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (118,0.894700300856283) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (107,0.862725940400586) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (107,0.89745323416723) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (111,0.875083500334001) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (102,0.917658035922556) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (99,0.877098723975823) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (91,0.900353356890459) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (91,0.861282660332542) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (88,0.864287338031371) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (90,0.864826941066417) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (84,0.90782686701054) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.827603513174404) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.876328283970156) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (78,0.816810877626699) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (71,0.852161100196464) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.876665022200296) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.892138063279003) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.852275379229872) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (69,0.80523890371089) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (69,0.89031971580817) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.838799720865318) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.879193056532958) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (58,0.869746923612723) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.859432531947152) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.855797263960529) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.861531190926276) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.877043673012318) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.830406757057124) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.823343135037322) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.815963511972634) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.80306905370844) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.886635944700461) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.821601661666282) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.864347420032687) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.852624643092466) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.806205250596659) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.832639059054153) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.864088909469785) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.838546458141674) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.841983317886932) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.810797782598216) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.859231313369488) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.729853259562184) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.824464561713402) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.766083312792704) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.815245478036176) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.61463133640553) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.796529284164859) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.747038037829973) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.837807854448635) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.774766962930847) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.862701252236136) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.838320575272558) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.796355577443979) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.837251769002511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.723449903454194) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (390,0.943111720356409) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (394,0.941344098788886) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (363,0.956684617185671) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (388,0.913378248315688) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (356,0.943857176415316) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (338,0.944365865157944) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (341,0.942908926144087) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (339,0.923076923076923) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (282,0.941947142534448) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (288,0.934869503879614) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (300,0.948609146628948) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (289,0.948664343786295) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (292,0.927440321437012) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (263,0.919101666264187) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (260,0.939753431030472) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (261,0.931168201648085) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (239,0.930678819860878) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (238,0.925429310750411) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (226,0.950766372503483) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (223,0.939647168059424) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (238,0.919540229885057) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (216,0.908223534756929) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (198,0.930068283494231) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (190,0.927849264705882) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (186,0.926075588305205) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (190,0.932804479701353) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (176,0.901950975487744) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (165,0.94096025729382) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (168,0.936338289962825) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (165,0.925866421849897) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (153,0.918179674605046) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (151,0.889051450865642) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (147,0.93466172381835) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (146,0.912822878228782) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (127,0.92406264831514) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (129,0.87672514619883) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (132,0.890973036342321) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (125,0.905815279361459) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (110,0.889400921658986) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (112,0.865304226660474) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (118,0.910045335242186) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (116,0.897238569488456) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (110,0.854803756320732) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (107,0.90625) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (97,0.903271692745377) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (101,0.913876702839991) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (91,0.88991888760139) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (95,0.865896771152486) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (93,0.901109275430729) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (90,0.901492537313433) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (86,0.852832055404403) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (89,0.858653183176281) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (82,0.858048780487805) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (80,0.869932852524248) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.889090496711272) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (78,0.896317829457364) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (77,0.892119009766069) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.856290174471993) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (71,0.890079180251514) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.726404494382022) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (67,0.905402325051288) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.826590962857819) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.88936678614098) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.838297872340425) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.797135032652201) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.848924341310128) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.885818181818182) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.880097087378641) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.832529867952211) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.850841830685321) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.820338983050847) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.67741935483871) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.855822143957737) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.835058993498676) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.815170008718396) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.865622809067539) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.833570412517781) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.807608957380207) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.785352927005541) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.833264033264033) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.862557077625571) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.778743481499876) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.818950177935943) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.807204803202135) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.835551545228965) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.778224852071006) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.744557016598405) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.73802669458257) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.75384214639229) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.847930283224401) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.842250287026406) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.838967136150235) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.822881761608425) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.7851966873706) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.720473192138905) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.758868074930251) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (383,0.951429868361325) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (382,0.935750344194585) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (371,0.949725776965265) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (344,0.944087992667278) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (392,0.955411054342778) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (361,0.949798296727925) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (354,0.954296160877514) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (326,0.907050500121981) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (321,0.947368421052631) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (293,0.935015472506546) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (308,0.94629963898917) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (328,0.937470835277648) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (288,0.93393536121673) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (285,0.949372967951695) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (258,0.926022216969983) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (252,0.913256955810147) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (250,0.943482224247949) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (251,0.932195353247985) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (227,0.941825707059094) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (230,0.940886699507389) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (219,0.920431093785829) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (203,0.929538030797947) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (200,0.941863180014009) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (208,0.934316991908615) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (204,0.903396771862202) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (193,0.892315104794025) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (177,0.875905118601748) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (163,0.898557158712541) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (178,0.936907788305986) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (170,0.912552891396333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (159,0.91599045346062) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (144,0.922380629101607) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (145,0.910709987966306) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (151,0.910662824207493) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (134,0.91804788213628) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (136,0.903957528957529) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (130,0.904576436222006) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (133,0.9032410693163) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (126,0.910507569011576) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (121,0.871679197994987) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (111,0.899589228662711) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (105,0.90691908947487) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (108,0.882266731802638) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (111,0.909937165464277) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (104,0.898093359631821) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (103,0.898517145505097) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (91,0.90556453474948) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (89,0.873345935727788) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (90,0.860771184483953) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (92,0.87972972972973) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (89,0.912517449976733) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (82,0.867244205104191) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (77,0.860787824529991) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.8750598372427) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (73,0.881859573448358) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.850269784172662) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (72,0.862982273201251) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (73,0.854074247023114) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (72,0.809160305343511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.898933704218822) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.827188940092166) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.857617465590887) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (62,0.86075378018506) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (60,0.837376460017969) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (60,0.799814643188137) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (58,0.876528410453129) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (56,0.822458270106221) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.752043596730245) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.879429250891795) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (52,0.792210993344836) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.900909302867801) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.822479928635147) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.87355801854784) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (47,0.844191343963554) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.799615107048352) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.857925993604385) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.836230110159119) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.840919133893062) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.823117338003503) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.832502708559047) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.800888230940044) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.843180808529542) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.776632302405498) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.866138265081462) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.796213515645543) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.770543331836551) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.718188530642382) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.834423117485762) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.753682072117826) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.803141875306824) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.638873550524572) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.759153175591532) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.759052652182423) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.830610134436401) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.742883170120701) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.800578034682081) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.714539795464651) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (387,0.933061039255729) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (367,0.930166270783848) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (393,0.950263580105432) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (386,0.941776849918812) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (371,0.94829584975655) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (327,0.90861494526416) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (333,0.934071222329163) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (312,0.940333024976873) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (319,0.952755905511811) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (291,0.928819846974264) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (320,0.924105011933174) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (286,0.937973484848485) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (306,0.946532804109269) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (278,0.946003301108229) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (267,0.92492351141445) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (256,0.944150769937945) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (261,0.943794448267951) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (243,0.917827967323402) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (229,0.936320754716981) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (233,0.917488573490498) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (237,0.907488986784141) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (223,0.943184475099369) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (212,0.927693761814745) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (203,0.945964589560819) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.930276087973795) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (189,0.900637243332546) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (182,0.923324150596878) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (189,0.910302165120152) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (174,0.916034046468829) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (171,0.907547602661161) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (156,0.933886201336098) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (157,0.9039780521262) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (150,0.889532293986637) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (158,0.888785046728972) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (141,0.932767478222024) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (139,0.891423140888572) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (137,0.877201332698715) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (136,0.886715955163367) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (133,0.882861819032032) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (115,0.899142128448875) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (121,0.905923344947735) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (115,0.85835493754419) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (111,0.892103391036282) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (107,0.859504132231405) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (100,0.819444444444444) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (106,0.848375451263538) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (94,0.841389728096677) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (96,0.858062918008422) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (94,0.866728366496992) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (94,0.904174573055028) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (91,0.883874000940291) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (84,0.854593682179889) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (83,0.906145995118704) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (87,0.89874593590339) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (80,0.867531264474293) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (71,0.871425545435289) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (74,0.886390255329117) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.787721573713791) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (71,0.845849802371542) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.826116221673771) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.891566265060241) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.833047315518509) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.883359963478658) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.786316776007498) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.839675914559293) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.829219645973573) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (52,0.841117216117216) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.824148296593186) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (52,0.837520165936852) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.877200902934537) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.863420158550396) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.736785904965296) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.851279788172992) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.741027627162406) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.697504906083544) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.754951085659747) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.815701292484442) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (44,0.691448216587881) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.840065374737333) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.829336437718277) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (42,0.724161533196441) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.858744394618834) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.795233463035019) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.766457023060796) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.816364054240404) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.788235294117647) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.763184584178499) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.680154972018941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.794871794871795) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.747634875990795) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.821968815452641) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.814132104454685) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (29,0.680098012523822) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.651342850229857) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.63776918829376) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.836888888888889) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.75130507412821) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (392,0.939098093909809) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (379,0.957686882933709) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (371,0.924756154203437) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (383,0.942587041733917) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (397,0.947464180122811) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (356,0.929844871498032) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (352,0.957913998170174) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (360,0.937442502299908) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (335,0.945193171608266) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (352,0.939683952815491) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (312,0.946127167630058) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (320,0.93780573025856) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (275,0.948735169017237) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (298,0.936179981634527) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (272,0.925908881730327) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (281,0.928959276018099) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (266,0.942338617045716) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (252,0.916311420237828) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (262,0.943153049482163) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (240,0.933608058608059) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (222,0.939130434782609) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (220,0.925796696906257) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (206,0.908452353078904) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (211,0.931767833407178) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (222,0.901987979657882) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (200,0.928455661032646) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (196,0.928901200369344) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (181,0.935962877030162) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (162,0.912796208530806) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (167,0.936327853669831) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (172,0.914111865200094) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (167,0.932306995698438) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (160,0.931144550843593) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (154,0.917685794920038) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (156,0.91789667896679) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (143,0.93822573153739) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (135,0.930113768284188) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (120,0.901171788635861) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (135,0.910498747437941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (127,0.875512995896033) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (120,0.927276795703737) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (129,0.880533079485959) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (119,0.942141230068337) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (110,0.908587257617728) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (112,0.897986577181208) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (104,0.893064876957494) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (104,0.853658536585366) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (98,0.881488286632981) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (102,0.921433657726086) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (96,0.911570811548079) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (82,0.877422164162856) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (80,0.893617021276596) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (83,0.923837339923613) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (81,0.844239631336405) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (81,0.886069889899473) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.85734496580995) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (78,0.866697631212262) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (79,0.874169251218431) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.852757793764988) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.872311212814645) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.845542427497315) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (61,0.830812854442344) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (60,0.818329090488313) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (66,0.821681864235056) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (64,0.898277082841633) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (56,0.852543464262717) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.843390467245832) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.864185826025124) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.740112994350282) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (52,0.880052436093511) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (54,0.853464419475655) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (56,0.828899194532585) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (52,0.838430050565856) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.855004677268475) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (48,0.867371456030754) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.836273179556761) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.861166116611661) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.83525656764056) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.712680577849117) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.773505333664103) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.811254980079681) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.803274494755692) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.784564272936366) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.821192052980132) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.850057937427578) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.797594263243118) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.808585194918966) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.825700615174299) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.703475474488538) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (34,0.834313085129545) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.808871168701719) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.83205930044012) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.510006455777921) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.83009814612868) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.766931340495096) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (31,0.854600796066495) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (28,0.694024108745832) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.805599458116956) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (395,0.949461862423959) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (400,0.940305635148042) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (399,0.951202749140893) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (376,0.94974406700791) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (374,0.957481038841646) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (388,0.946094106898127) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (355,0.954766875434934) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (348,0.945183111733147) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (325,0.934083978418954) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (337,0.948700253048079) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (315,0.935748792270531) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (303,0.93956934475573) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (309,0.926012098650535) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (290,0.946436888681882) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (284,0.94877096255456) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (285,0.932323710364411) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (283,0.881557085212438) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (267,0.926106092193653) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (240,0.91988821611551) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (242,0.936298355339356) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (242,0.944292237442922) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=red,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (220,0.948069852941176) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (231,0.894094680331869) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (215,0.910953891192974) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (207,0.929101019462465) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (185,0.932905885046943) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (191,0.919963201471941) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (176,0.931339225016995) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (183,0.833289577316881) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (173,0.870991432068543) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (177,0.909341923607915) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (153,0.891376846117198) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (148,0.924608819345661) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (146,0.904174573055028) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (157,0.922968859751814) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (143,0.905770635500365) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (141,0.900096061479347) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (126,0.899784740492705) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (134,0.893432764012509) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (129,0.908745247148289) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (133,0.893189964157706) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (125,0.900207421064761) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (123,0.886419204267615) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (108,0.929667812142039) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (110,0.920957542908762) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (96,0.905677655677656) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (98,0.88590899098703) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (98,0.861262112975656) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (92,0.853032845840326) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (91,0.913465987968533) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (89,0.91643059490085) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (92,0.837742917349567) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (86,0.878060153882024) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (82,0.901427913403961) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (78,0.838621940163191) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (73,0.877507670521595) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (76,0.874259102455546) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (81,0.865921787709497) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (70,0.828997221520586) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (65,0.831875147789075) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (68,0.882807327300816) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.850534584333406) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (63,0.86932804363997) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (56,0.824389225307997) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (60,0.864516129032258) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (59,0.878966455122393) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.79732165851146) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (55,0.808812729498164) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (57,0.802688430148824) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (51,0.868092691622103) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (49,0.835748792270531) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (53,0.806613226452906) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.88034188034188) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.779572694111516) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (50,0.84643179765131) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (45,0.825348432055749) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.795289499509323) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.856514084507042) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (40,0.805523051720103) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (46,0.726723427629772) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (43,0.80864040660737) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (41,0.807138249838744) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.873322720036388) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (37,0.824190064794816) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (38,0.831571529245948) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (39,0.828000775644754) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.834297520661157) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.774317201724964) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (36,0.826616682286785) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.708015768725361) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (32,0.739744155271283) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.73972602739726) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (35,0.720064291454594) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.735064280312579) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (33,0.800338051975491) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.777827248441674) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (30,0.638319672131147) 
};
\addplot [
color=blue,
mark size=1.3pt,
only marks,
mark=*,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
forget plot
]
coordinates{
 (27,0.785007808433108) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-20 figurefactory/files/limno_bgape_str_class_400.tex
LSE theory and experiments

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (1478,0)(1478,-0.181818181818182)(1478,-0.363636363636364)(1478,-0.545454545454545)(1478,-0.727272727272727)(1478,-0.909090909090909)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454545)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454545)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454545)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454545)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454545)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454545)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.909090909090909)(0,-0.727272727272727)(0,-0.545454545454545)(0,-0.363636363636364)(0,-0.181818181818182)(0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (574.777777777778,-7.27272727272727)(582.242424242424,-7.3030303030303)(597.171717171717,-7.42424242424242)(600.90404040404,-7.45454545454545)(612.10101010101,-7.54545454545455)(619.565656565657,-7.63636363636364)(627.030303030303,-7.77272727272727)(629.518518518518,-7.81818181818182)(634.494949494949,-8)(634.494949494949,-8.18181818181818)(629.518518518518,-8.36363636363636)(627.030303030303,-8.40909090909091)(619.565656565657,-8.54545454545455)(612.10101010101,-8.63636363636364)(604.636363636364,-8.72727272727273)(597.171717171717,-8.81818181818182)(585.974747474747,-8.90909090909091)(582.242424242424,-8.93939393939394)(567.313131313131,-9.06060606060606)(559.848484848485,-9.09090909090909)(552.383838383838,-9.12121212121212)(537.454545454546,-9.18181818181818)(522.525252525253,-9.18181818181818)(507.59595959596,-9.18181818181818)(492.666666666667,-9.12121212121212)(485.20202020202,-9.09090909090909)(477.737373737374,-9.06060606060606)(462.808080808081,-8.93939393939394)(459.075757575758,-8.90909090909091)(447.878787878788,-8.77272727272727)(445.390572390572,-8.72727272727273)(435.43771043771,-8.54545454545455)(432.949494949495,-8.45454545454545)(430.461279461279,-8.36363636363636)(420.508417508418,-8.18181818181818)(418.020202020202,-8.09090909090909)(415.531986531986,-8)(415.531986531986,-7.81818181818182)(418.020202020202,-7.77272727272727)(425.484848484849,-7.63636363636364)(432.949494949495,-7.54545454545455)(444.146464646465,-7.45454545454545)(447.878787878788,-7.42424242424242)(462.808080808081,-7.36363636363636)(477.737373737374,-7.3030303030303)(485.20202020202,-7.27272727272727)(492.666666666667,-7.24242424242424)(507.59595959596,-7.18181818181818)(522.525252525253,-7.18181818181818)(537.454545454546,-7.18181818181818)(552.383838383838,-7.18181818181818)(567.313131313131,-7.24242424242424)(574.777777777778,-7.27272727272727)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (231.40404040404,-7.81818181818182)(238.868686868687,-7.84848484848485)(253.79797979798,-7.90909090909091)(268.727272727273,-7.96969696969697)(272.459595959596,-8)(283.656565656566,-8.13636363636364)(286.144781144781,-8.18181818181818)(286.144781144781,-8.36363636363636)(283.656565656566,-8.40909090909091)(276.191919191919,-8.54545454545455)(268.727272727273,-8.63636363636364)(257.530303030303,-8.72727272727273)(253.79797979798,-8.75757575757576)(238.868686868687,-8.81818181818182)(223.939393939394,-8.81818181818182)(209.010101010101,-8.81818181818182)(194.080808080808,-8.81818181818182)(179.151515151515,-8.75757575757576)(171.686868686869,-8.72727272727273)(164.222222222222,-8.6969696969697)(149.292929292929,-8.57575757575757)(145.560606060606,-8.54545454545455)(134.363636363636,-8.45454545454545)(126.89898989899,-8.36363636363636)(119.434343434343,-8.22727272727273)(116.946127946128,-8.18181818181818)(119.434343434343,-8.09090909090909)(121.922558922559,-8)(134.363636363636,-7.84848484848485)(141.828282828283,-7.81818181818182)(149.292929292929,-7.78787878787879)(164.222222222222,-7.72727272727273)(179.151515151515,-7.72727272727273)(194.080808080808,-7.72727272727273)(209.010101010101,-7.72727272727273)(223.939393939394,-7.78787878787879)(231.40404040404,-7.81818181818182)};

\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (821.111111111111,-13.6363636363636)(1224.20202020202,-3.27272727272727)(0,-18)(0,-8)(0,-6)(253.79797979798,-8.90909090909091)(104.505050505051,-10.1818181818182)(388.161616161616,-7.63636363636364)(492.666666666667,-8.90909090909091)(209.010101010101,-7.63636363636364)(656.888888888889,-7.81818181818182)(388.161616161616,-9.27272727272727)(507.59595959596,-8)(507.59595959596,-7.27272727272727)(567.313131313131,-8.72727272727273)(612.10101010101,-8.90909090909091)(238.868686868687,-8.54545454545455)(552.383838383838,-7.27272727272727)(418.020202020202,-7.27272727272727)(209.010101010101,-8.36363636363636)(89.5757575757576,-8.54545454545455)(134.363636363636,-8)(119.434343434343,-8.72727272727273)(328.444444444444,-7.63636363636364)(119.434343434343,-7.81818181818182)(89.5757575757576,-7.63636363636364)(627.030303030303,-8.18181818181818)(477.737373737374,-9.09090909090909)(537.454545454546,-7.27272727272727)(223.939393939394,-8.90909090909091)(462.808080808081,-9.09090909090909)(74.6464646464647,-7.63636363636364)(194.080808080808,-7.63636363636364)(597.171717171717,-7.45454545454545)(612.10101010101,-7.27272727272727)(612.10101010101,-8.54545454545455)(194.080808080808,-8.90909090909091)(343.373737373737,-8.90909090909091)(477.737373737374,-7.27272727272727)(597.171717171717,-7.27272727272727)(373.232323232323,-7.63636363636364)(89.5757575757576,-8.36363636363636)(567.313131313131,-8.90909090909091)(522.525252525253,-9.09090909090909)(567.313131313131,-9.09090909090909)(328.444444444444,-8.90909090909091)(627.030303030303,-7.81818181818182)(388.161616161616,-8.90909090909091)(313.515151515152,-7.81818181818182)(223.939393939394,-7.63636363636364)(119.434343434343,-7.63636363636364)(582.242424242424,-9.09090909090909)(627.030303030303,-8.36363636363636)(462.808080808081,-7.27272727272727)(403.090909090909,-8.90909090909091)(358.30303030303,-8.72727272727273)(149.292929292929,-8.72727272727273)(388.161616161616,-8.72727272727273)(328.444444444444,-7.81818181818182)(238.868686868687,-7.63636363636364)(358.30303030303,-8.54545454545455)(612.10101010101,-8.72727272727273)(582.242424242424,-7.27272727272727)(373.232323232323,-8.54545454545455)(373.232323232323,-8.36363636363636)(627.030303030303,-8)(388.161616161616,-8.36363636363636)(432.949494949495,-8.54545454545455)(432.949494949495,-7.45454545454545)(597.171717171717,-8.90909090909091)(313.515151515152,-8.36363636363636)(104.505050505051,-7.63636363636364)(74.6464646464647,-8)(134.363636363636,-8.54545454545455)(238.868686868687,-8.72727272727273)(522.525252525253,-7.09090909090909)(298.585858585859,-7.81818181818182)(403.090909090909,-7.63636363636364)(447.878787878788,-8.72727272727273)(492.666666666667,-9.09090909090909)(552.383838383838,-9.09090909090909)(209.010101010101,-8.72727272727273)(104.505050505051,-8.18181818181818)(179.151515151515,-8.72727272727273)(627.030303030303,-8.54545454545455)(388.161616161616,-8.18181818181818)(298.585858585859,-8.54545454545455)(283.656565656566,-7.81818181818182)(298.585858585859,-8.36363636363636)(164.222222222222,-7.45454545454545)(388.161616161616,-7.81818181818182)(388.161616161616,-8)(418.020202020202,-8.36363636363636)(537.454545454546,-9.27272727272727)(552.383838383838,-9.27272727272727)(432.949494949495,-8.36363636363636)(89.5757575757576,-8)(119.434343434343,-8.36363636363636)(104.505050505051,-8.36363636363636)(298.585858585859,-8.18181818181818)(567.313131313131,-7.27272727272727)(403.090909090909,-8)(179.151515151515,-7.45454545454545)(507.59595959596,-9.09090909090909)(627.030303030303,-7.63636363636364)(612.10101010101,-7.45454545454545)(418.020202020202,-7.63636363636364)(89.5757575757576,-8.18181818181818)(268.727272727273,-7.81818181818182)(403.090909090909,-7.81818181818182)(164.222222222222,-8.72727272727273)(253.79797979798,-8.72727272727273)(283.656565656566,-8.54545454545455)(447.878787878788,-7.27272727272727)(298.585858585859,-8)(134.363636363636,-7.63636363636364)(104.505050505051,-7.81818181818182)(492.666666666667,-7.27272727272727)(209.010101010101,-8.90909090909091)(418.020202020202,-8.18181818181818)(119.434343434343,-8.54545454545455)(641.959595959596,-8)(641.959595959596,-8.18181818181818)(477.737373737374,-8.90909090909091)(641.959595959596,-7.81818181818182)(89.5757575757576,-7.81818181818182)(268.727272727273,-8.72727272727273)(283.656565656566,-8)(462.808080808081,-8.90909090909091)(447.878787878788,-7.45454545454545)(418.020202020202,-7.81818181818182)(432.949494949495,-7.63636363636364)(462.808080808081,-7.45454545454545)(522.525252525253,-7.27272727272727)(418.020202020202,-8)(432.949494949495,-8.18181818181818)(432.949494949495,-7.81818181818182)(253.79797979798,-7.63636363636364)(149.292929292929,-7.63636363636364)(179.151515151515,-7.63636363636364)(164.222222222222,-7.63636363636364)(253.79797979798,-7.81818181818182)(283.656565656566,-8.36363636363636)(447.878787878788,-8.54545454545455)(522.525252525253,-9.27272727272727)(641.959595959596,-8.36363636363636)(238.868686868687,-7.81818181818182)(432.949494949495,-8)(104.505050505051,-8)(238.868686868687,-8.90909090909091)(283.656565656566,-8.18181818181818)(582.242424242424,-8.90909090909091)(447.878787878788,-7.63636363636364)(268.727272727273,-8.54545454545455)(552.383838383838,-7.09090909090909)(537.454545454546,-7.09090909090909)(462.808080808081,-8.72727272727273)(447.878787878788,-8.90909090909091)(627.030303030303,-7.45454545454545)(537.454545454546,-9.09090909090909)(134.363636363636,-7.81818181818182)(612.10101010101,-7.63636363636364)(313.515151515152,-8.18181818181818)(627.030303030303,-8.72727272727273)(477.737373737374,-7.45454545454545)(194.080808080808,-8.72727272727273)(223.939393939394,-8.72727272727273)(313.515151515152,-8)(268.727272727273,-8)(597.171717171717,-8.72727272727273)(223.939393939394,-7.81818181818182)(567.313131313131,-7.09090909090909)(507.59595959596,-9.27272727272727)(447.878787878788,-8.36363636363636)(432.949494949495,-8.72727272727273)(149.292929292929,-8.54545454545455)(567.313131313131,-9.27272727272727)(283.656565656566,-8.72727272727273)(582.242424242424,-7.45454545454545)(492.666666666667,-9.27272727272727)(403.090909090909,-8.18181818181818)(119.434343434343,-8)(268.727272727273,-7.63636363636364)(74.6464646464647,-8.18181818181818)(597.171717171717,-9.09090909090909)(268.727272727273,-8.36363636363636)(134.363636363636,-8.72727272727273)(104.505050505051,-8.54545454545455)(179.151515151515,-8.90909090909091)(447.878787878788,-7.81818181818182)(507.59595959596,-7.09090909090909)(612.10101010101,-8.36363636363636)(209.010101010101,-7.81818181818182)(328.444444444444,-8.18181818181818)(268.727272727273,-8.18181818181818)(418.020202020202,-8.54545454545455)(74.6464646464647,-7.81818181818182)(612.10101010101,-7.81818181818182)(641.959595959596,-7.63636363636364)(328.444444444444,-8)(462.808080808081,-8.54545454545455)(403.090909090909,-8.36363636363636)(253.79797979798,-8.54545454545455)(149.292929292929,-7.81818181818182)(194.080808080808,-7.81818181818182)(253.79797979798,-8)(164.222222222222,-7.81818181818182)(179.151515151515,-7.81818181818182)(119.434343434343,-8.18181818181818)(134.363636363636,-8.36363636363636)(418.020202020202,-7.45454545454545)(492.666666666667,-7.09090909090909)(164.222222222222,-8.90909090909091)(164.222222222222,-8.54545454545455)(373.232323232323,-7.81818181818182)(313.515151515152,-8.54545454545455)(373.232323232323,-8)(268.727272727273,-8.90909090909091)(298.585858585859,-8.72727272727273)(238.868686868687,-8)(59.7171717171717,-8)(134.363636363636,-8.18181818181818)(328.444444444444,-8.36363636363636)(477.737373737374,-9.27272727272727)(432.949494949495,-7.27272727272727)(403.090909090909,-7.45454545454545)(477.737373737374,-7.09090909090909)(462.808080808081,-7.09090909090909)(447.878787878788,-7.09090909090909)(283.656565656566,-7.63636363636364)(432.949494949495,-8.90909090909091)(447.878787878788,-8.18181818181818)(388.161616161616,-7.45454545454545)(612.10101010101,-8.18181818181818)(343.373737373737,-8)(358.30303030303,-7.81818181818182)(343.373737373737,-7.81818181818182)(582.242424242424,-7.09090909090909)(597.171717171717,-7.63636363636364)(567.313131313131,-7.45454545454545)(253.79797979798,-8.18181818181818)(477.737373737374,-8.72727272727273)(149.292929292929,-8)(149.292929292929,-8.36363636363636)(223.939393939394,-8)(253.79797979798,-8.36363636363636)(283.656565656566,-8.90909090909091)(358.30303030303,-8)(641.959595959596,-8.54545454545455)(179.151515151515,-8.54545454545455)(343.373737373737,-8.18181818181818)(447.878787878788,-8)(447.878787878788,-9.09090909090909)(149.292929292929,-7.45454545454545)(403.090909090909,-7.27272727272727)(358.30303030303,-7.63636363636364)(373.232323232323,-7.45454545454545)(612.10101010101,-8)(656.888888888889,-8)(164.222222222222,-8)(298.585858585859,-7.63636363636364)(74.6464646464647,-8.36363636363636)(492.666666666667,-7.45454545454545)(552.383838383838,-8.90909090909091)(507.59595959596,-8.90909090909091)(582.242424242424,-8.72727272727273)(418.020202020202,-8.72727272727273)(209.010101010101,-8)(373.232323232323,-8.18181818181818)(149.292929292929,-8.18181818181818)(179.151515151515,-8)(194.080808080808,-8)(343.373737373737,-7.63636363636364)(313.515151515152,-7.63636363636364)(656.888888888889,-8.18181818181818)(134.363636363636,-7.45454545454545)(119.434343434343,-7.45454545454545)(388.161616161616,-7.27272727272727)(358.30303030303,-7.45454545454545)(223.939393939394,-8.54545454545455)(358.30303030303,-8.18181818181818)(403.090909090909,-8.54545454545455)(432.949494949495,-7.09090909090909)(462.808080808081,-7.63636363636364)(238.868686868687,-8.18181818181818)(194.080808080808,-8.54545454545455)(597.171717171717,-8.54545454545455)(164.222222222222,-8.36363636363636)(164.222222222222,-8.18181818181818)(209.010101010101,-8.54545454545455)(238.868686868687,-8.36363636363636)(194.080808080808,-7.45454545454545)(462.808080808081,-8.36363636363636)(223.939393939394,-9.09090909090909)(343.373737373737,-7.45454545454545)(522.525252525253,-9.45454545454546)(223.939393939394,-8.18181818181818)(462.808080808081,-9.27272727272727)(343.373737373737,-8.36363636363636)(59.7171717171717,-7.81818181818182)(328.444444444444,-8.54545454545455)(179.151515151515,-8.18181818181818)(179.151515151515,-8.36363636363636)(522.525252525253,-8.90909090909091)(537.454545454546,-8.90909090909091)(462.808080808081,-8.18181818181818)(641.959595959596,-7.45454545454545)(627.030303030303,-7.27272727272727)(656.888888888889,-7.63636363636364)(597.171717171717,-7.09090909090909)(612.10101010101,-7.09090909090909)(641.959595959596,-7.27272727272727)(507.59595959596,-7.45454545454545)(552.383838383838,-7.45454545454545)(462.808080808081,-7.81818181818182)(522.525252525253,-7.45454545454545)(537.454545454546,-7.45454545454545)(477.737373737374,-7.63636363636364)(418.020202020202,-7.09090909090909)(582.242424242424,-9.27272727272727)(627.030303030303,-8.90909090909091)(492.666666666667,-8.72727272727273)(358.30303030303,-8.36363636363636)(537.454545454546,-9.45454545454546)(313.515151515152,-8.72727272727273)(209.010101010101,-8.18181818181818)(223.939393939394,-8.36363636363636)(194.080808080808,-8.18181818181818)(477.737373737374,-8.54545454545455)(149.292929292929,-8.90909090909091)(209.010101010101,-7.45454545454545)(656.888888888889,-7.45454545454545)(507.59595959596,-9.45454545454546)(552.383838383838,-9.45454545454546)(104.505050505051,-7.45454545454545)(89.5757575757576,-7.45454545454545)(223.939393939394,-7.45454545454545)(328.444444444444,-7.45454545454545)(238.868686868687,-7.45454545454545)(194.080808080808,-8.36363636363636)(492.666666666667,-9.45454545454546)(537.454545454546,-6.90909090909091)(522.525252525253,-6.90909090909091)(552.383838383838,-6.90909090909091)(507.59595959596,-6.90909090909091)(567.313131313131,-6.90909090909091)(567.313131313131,-4.72727272727273)(492.666666666667,-6.90909090909091)(462.808080808081,-8)(388.161616161616,-8.54545454545455)(343.373737373737,-8.54545454545455)(403.090909090909,-8.72727272727273)(104.505050505051,-8.72727272727273)(59.7171717171717,-7.63636363636364)(656.888888888889,-8.36363636363636)(582.242424242424,-7.63636363636364)(597.171717171717,-7.81818181818182)(238.868686868687,-9.09090909090909)(209.010101010101,-9.09090909090909)(253.79797979798,-9.09090909090909)(194.080808080808,-9.09090909090909)(298.585858585859,-8.90909090909091)(268.727272727273,-9.09090909090909)(418.020202020202,-8.90909090909091)(597.171717171717,-8.36363636363636)(582.242424242424,-6.90909090909091)(627.030303030303,-7.09090909090909)(328.444444444444,-8.72727272727273)(612.10101010101,-9.09090909090909)(373.232323232323,-7.27272727272727)(432.949494949495,-9.09090909090909)(492.666666666667,-7.63636363636364)(477.737373737374,-6.90909090909091)(313.515151515152,-8.90909090909091)(283.656565656566,-9.09090909090909)(179.151515151515,-9.09090909090909)(582.242424242424,-8.54545454545455)(597.171717171717,-8)(313.515151515152,-7.45454545454545)(134.363636363636,-8.90909090909091)(447.878787878788,-9.27272727272727)(343.373737373737,-8.72727272727273)(477.737373737374,-9.45454545454546)(477.737373737374,-7.81818181818182)(641.959595959596,-8.72727272727273)(298.585858585859,-7.45454545454545)(253.79797979798,-7.45454545454545)(283.656565656566,-7.45454545454545)(59.7171717171717,-8.18181818181818)(567.313131313131,-7.63636363636364)(597.171717171717,-8.18181818181818)(477.737373737374,-8.36363636363636)(462.808080808081,-6.90909090909091)(507.59595959596,-7.63636363636364)(507.59595959596,-8.72727272727273)(597.171717171717,-6.90909090909091)(298.585858585859,-9.09090909090909)(552.383838383838,-8.72727272727273)(418.020202020202,-9.09090909090909)(373.232323232323,-8.72727272727273) 
};

\end{axis}
\end{tikzpicture}%

### 2013-03-20 figurefactory/files/limno_bgape_var_class_400.tex
LSE theory and experiments

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (1478,0)(1478,-0.181818181818182)(1478,-0.363636363636364)(1478,-0.545454545454545)(1478,-0.727272727272727)(1478,-0.909090909090909)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454545)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454545)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454545)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478.00016587919,-9.09090909090909)(1478.00033175469,-9.27272727272727)(1478.00033175469,-9.45454545454546)(1478.00016587919,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454545)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454545)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454545)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.909090909090909)(0,-0.727272727272727)(0,-0.545454545454545)(0,-0.363636363636364)(0,-0.181818181818182)(0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1216.73737373737,-7.63636363636364)(1224.20202020202,-7.66666666666667)(1239.13131313131,-7.72727272727273)(1254.06060606061,-7.72727272727273)(1268.9898989899,-7.72727272727273)(1283.91919191919,-7.78787878787879)(1291.38383838384,-7.81818181818182)(1298.84848484848,-7.84848484848485)(1313.77777777778,-7.90909090909091)(1328.70707070707,-7.96969696969697)(1336.17171717172,-8)(1343.63636363636,-8.03030303030303)(1358.56565656566,-8.15151515151515)(1362.29797979798,-8.18181818181818)(1373.49494949495,-8.27272727272727)(1384.69191919192,-8.36363636363636)(1388.42424242424,-8.39393939393939)(1403.35353535354,-8.51515151515152)(1407.08585858586,-8.54545454545455)(1418.28282828283,-8.63636363636364)(1425.74747474747,-8.72727272727273)(1433.21212121212,-8.81818181818182)(1440.67676767677,-8.90909090909091)(1448.14141414141,-9)(1455.60606060606,-9.09090909090909)(1463.07070707071,-9.22727272727273)(1465.55892255892,-9.27272727272727)(1465.55892255892,-9.45454545454546)(1463.07070707071,-9.5)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.72727272727273)(1436.94444444444,-9.81818181818182)(1433.21212121212,-9.84848484848485)(1418.28282828283,-9.96969696969697)(1410.81818181818,-10)(1403.35353535354,-10.030303030303)(1388.42424242424,-10.0909090909091)(1373.49494949495,-10.0909090909091)(1358.56565656566,-10.0909090909091)(1343.63636363636,-10.0909090909091)(1328.70707070707,-10.0909090909091)(1313.77777777778,-10.0909090909091)(1298.84848484848,-10.0909090909091)(1283.91919191919,-10.0909090909091)(1268.9898989899,-10.0909090909091)(1254.06060606061,-10.0909090909091)(1239.13131313131,-10.0909090909091)(1224.20202020202,-10.0909090909091)(1209.27272727273,-10.0909090909091)(1194.34343434343,-10.0909090909091)(1179.41414141414,-10.0909090909091)(1164.48484848485,-10.0909090909091)(1149.55555555556,-10.0909090909091)(1134.62626262626,-10.0909090909091)(1119.69696969697,-10.0909090909091)(1104.76767676768,-10.0909090909091)(1089.83838383838,-10.0909090909091)(1074.90909090909,-10.0909090909091)(1059.9797979798,-10.0909090909091)(1045.05050505051,-10.0909090909091)(1030.12121212121,-10.0909090909091)(1015.19191919192,-10.0909090909091)(1000.26262626263,-10.0909090909091)(985.333333333333,-10.0909090909091)(970.40404040404,-10.030303030303)(962.939393939394,-10)(955.474747474747,-9.96969696969697)(940.545454545455,-9.90909090909091)(925.616161616162,-9.90909090909091)(910.686868686869,-9.84848484848485)(903.222222222222,-9.81818181818182)(895.757575757576,-9.78787878787879)(880.828282828283,-9.72727272727273)(865.89898989899,-9.66666666666667)(858.434343434343,-9.63636363636364)(850.969696969697,-9.60606060606061)(836.040404040404,-9.48484848484848)(832.308080808081,-9.45454545454546)(821.111111111111,-9.36363636363636)(813.646464646465,-9.27272727272727)(806.181818181818,-9.18181818181818)(798.717171717172,-9.09090909090909)(791.252525252525,-9)(783.787878787879,-8.90909090909091)(776.323232323232,-8.77272727272727)(773.835016835017,-8.72727272727273)(773.835016835017,-8.54545454545455)(776.323232323232,-8.45454545454545)(778.811447811448,-8.36363636363636)(791.252525252525,-8.21212121212121)(793.740740740741,-8.18181818181818)(806.181818181818,-8.03030303030303)(813.646464646465,-8)(821.111111111111,-7.96969696969697)(836.040404040404,-7.84848484848485)(843.505050505051,-7.81818181818182)(850.969696969697,-7.78787878787879)(865.89898989899,-7.72727272727273)(880.828282828283,-7.66666666666667)(888.292929292929,-7.63636363636364)(895.757575757576,-7.60606060606061)(910.686868686869,-7.54545454545455)(925.616161616162,-7.54545454545455)(940.545454545455,-7.54545454545455)(955.474747474747,-7.54545454545455)(970.40404040404,-7.54545454545455)(985.333333333333,-7.54545454545455)(1000.26262626263,-7.54545454545455)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.54545454545455)(1059.9797979798,-7.54545454545455)(1074.90909090909,-7.54545454545455)(1089.83838383838,-7.54545454545455)(1104.76767676768,-7.54545454545455)(1119.69696969697,-7.54545454545455)(1134.62626262626,-7.54545454545455)(1149.55555555556,-7.54545454545455)(1164.48484848485,-7.54545454545455)(1179.41414141414,-7.54545454545455)(1194.34343434343,-7.54545454545455)(1209.27272727273,-7.60606060606061)(1216.73737373737,-7.63636363636364)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (559.848484848485,-7.45454545454545)(567.313131313131,-7.48484848484848)(582.242424242424,-7.60606060606061)(585.974747474747,-7.63636363636364)(597.171717171717,-7.77272727272727)(599.659932659933,-7.81818181818182)(609.612794612795,-8)(609.612794612795,-8.18181818181818)(604.636363636364,-8.36363636363636)(597.171717171717,-8.45454545454545)(585.974747474747,-8.54545454545455)(582.242424242424,-8.57575757575757)(567.313131313131,-8.63636363636364)(552.383838383838,-8.63636363636364)(537.454545454546,-8.63636363636364)(522.525252525253,-8.63636363636364)(507.59595959596,-8.63636363636364)(492.666666666667,-8.63636363636364)(477.737373737374,-8.63636363636364)(462.808080808081,-8.63636363636364)(447.878787878788,-8.63636363636364)(432.949494949495,-8.63636363636364)(418.020202020202,-8.63636363636364)(403.090909090909,-8.63636363636364)(388.161616161616,-8.57575757575757)(380.69696969697,-8.54545454545455)(373.232323232323,-8.51515151515152)(358.30303030303,-8.45454545454545)(343.373737373737,-8.45454545454545)(328.444444444444,-8.45454545454545)(313.515151515152,-8.45454545454545)(298.585858585859,-8.45454545454545)(283.656565656566,-8.45454545454545)(268.727272727273,-8.51515151515152)(261.262626262626,-8.54545454545455)(253.79797979798,-8.57575757575757)(238.868686868687,-8.57575757575757)(231.40404040404,-8.54545454545455)(223.939393939394,-8.51515151515152)(209.010101010101,-8.45454545454545)(194.080808080808,-8.39393939393939)(190.348484848485,-8.36363636363636)(179.151515151515,-8.22727272727273)(176.6632996633,-8.18181818181818)(179.151515151515,-8.09090909090909)(182.883838383838,-8)(194.080808080808,-7.90909090909091)(209.010101010101,-7.90909090909091)(223.939393939394,-7.90909090909091)(238.868686868687,-7.90909090909091)(253.79797979798,-7.90909090909091)(268.727272727273,-7.90909090909091)(283.656565656566,-7.90909090909091)(298.585858585859,-7.90909090909091)(313.515151515152,-7.90909090909091)(328.444444444444,-7.90909090909091)(343.373737373737,-7.90909090909091)(358.30303030303,-7.84848484848485)(365.767676767677,-7.81818181818182)(373.232323232323,-7.78787878787879)(388.161616161616,-7.66666666666667)(395.626262626263,-7.63636363636364)(403.090909090909,-7.60606060606061)(418.020202020202,-7.54545454545455)(432.949494949495,-7.48484848484848)(440.414141414141,-7.45454545454545)(447.878787878788,-7.42424242424242)(462.808080808081,-7.36363636363636)(477.737373737374,-7.36363636363636)(492.666666666667,-7.36363636363636)(507.59595959596,-7.36363636363636)(522.525252525253,-7.36363636363636)(537.454545454546,-7.36363636363636)(552.383838383838,-7.42424242424242)(559.848484848485,-7.45454545454545)};

\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (477.737373737374,-17.4545454545455)(1478,0)(0,-5.81818181818182)(1478,-10.1818181818182)(1478,-18)(418.020202020202,0)(0,-12.1818181818182)(940.545454545455,-5.45454545454545)(791.252525252525,-12.1818181818182)(1478,-4.72727272727273)(0,-18)(1478,-14.1818181818182)(462.808080808081,-8.54545454545455)(0,-1.81818181818182)(940.545454545455,-1.27272727272727)(970.40404040404,-18)(462.808080808081,-4)(1015.19191919192,-8.90909090909091)(358.30303030303,-14.3636363636364)(0,-9.09090909090909)(985.333333333333,-14.9090909090909)(1478,-7.45454545454545)(0,-15.2727272727273)(0,0)(388.161616161616,-11.2727272727273)(1194.34343434343,-12.1818181818182)(1283.91919191919,-2.54545454545455)(567.313131313131,-6.36363636363636)(1134.62626262626,0)(1283.91919191919,-16.1818181818182)(731.535353535354,0)(671.818181818182,-15.4545454545455)(776.323232323232,-3.27272727272727)(731.535353535354,-9.81818181818182)(358.30303030303,-2)(0,-3.81818181818182)(1209.27272727273,-6.54545454545455)(238.868686868687,-6.90909090909091)(1478,-12.1818181818182)(1478,-2.18181818181818)(223.939393939394,-16.5454545454545)(821.111111111111,-7.45454545454545)(716.606060606061,-18)(1149.55555555556,-4.18181818181818)(582.242424242424,-13.2727272727273)(1179.41414141414,-10.3636363636364)(1224.20202020202,-18)(209.010101010101,-10)(238.868686868687,-4.90909090909091)(268.727272727273,-18)(627.030303030303,-1.63636363636364)(1478,-16.1818181818182)(194.080808080808,-13.0909090909091)(1283.91919191919,-8.54545454545455)(1209.27272727273,-14)(0,-7.45454545454545)(910.686868686869,-16.5454545454545)(0,-13.8181818181818)(209.010101010101,0)(940.545454545455,-13.2727272727273)(955.474747474747,-10.9090909090909)(0,-10.7272727272727)(701.676767676768,-4.90909090909091)(1015.19191919192,-2.90909090909091)(194.080808080808,-3.09090909090909)(1283.91919191919,-1.09090909090909)(1478,-6)(597.171717171717,-11.0909090909091)(0,-16.7272727272727)(447.878787878788,-15.8181818181818)(223.939393939394,-8.36363636363636)(1030.12121212121,-7.27272727272727)(1478,-8.90909090909091)(925.616161616162,0)(761.393939393939,-14.1818181818182)(1478,-3.45454545454545)(462.808080808081,-9.81818181818182)(671.818181818182,-8.36363636363636)(1283.91919191919,-5.09090909090909)(179.151515151515,-1.27272727272727)(179.151515151515,-14.9090909090909)(403.090909090909,-5.63636363636364)(1104.76767676768,-16.5454545454545)(194.080808080808,-11.6363636363636)(403.090909090909,-12.7272727272727)(686.747474747475,-16.7272727272727)(552.383838383838,-2.90909090909091)(1343.63636363636,-11.0909090909091)(1313.77777777778,0)(925.616161616162,-4.18181818181818)(432.949494949495,-7.27272727272727)(1358.56565656566,-13.0909090909091)(1313.77777777778,-15.0909090909091)(776.323232323232,-6.18181818181818)(1478,-1.09090909090909)(1119.69696969697,-1.63636363636364)(567.313131313131,0)(522.525252525253,-18)(806.181818181818,-2)(1015.19191919192,-12.1818181818182)(537.454545454546,-14.5454545454545)(850.969696969697,-8.90909090909091)(447.878787878788,-1.09090909090909)(0,-4.72727272727273)(1358.56565656566,-17.2727272727273)(1104.76767676768,-5.63636363636364)(1313.77777777778,-7.27272727272727)(0,-2.72727272727273)(1313.77777777778,-3.81818181818182)(1313.77777777778,-9.63636363636364)(149.292929292929,-6)(134.363636363636,-18)(791.252525252525,-10.9090909090909)(1478,-15.2727272727273)(597.171717171717,-12.1818181818182)(1134.62626262626,-15.2727272727273)(836.040404040404,-15.4545454545455)(313.515151515152,-3.63636363636364)(0,-0.909090909090909)(1134.62626262626,-8.18181818181818)(552.383838383838,-4.90909090909091)(1478,-11.2727272727273)(1000.26262626263,-10)(627.030303030303,-7.27272727272727)(1089.83838383838,-13.4545454545455)(1478,-13.2727272727273)(761.393939393939,-0.909090909090909)(836.040404040404,-18)(1104.76767676768,-18)(313.515151515152,-9.27272727272727)(373.232323232323,-16.7272727272727)(1478,-17.0909090909091)(656.888888888889,-3.81818181818182)(89.5757575757576,-8.18181818181818)(134.363636363636,-4.18181818181818)(597.171717171717,-9.45454545454546)(298.585858585859,-15.4545454545455)(761.393939393939,-13.0909090909091)(0,-9.81818181818182)(940.545454545455,-6.54545454545455)(0,-12.9090909090909)(0,-6.72727272727273)(1119.69696969697,-11.2727272727273)(1149.55555555556,-3.09090909090909)(164.222222222222,-14)(1343.63636363636,-6)(104.505050505051,-16)(164.222222222222,-2.18181818181818)(1343.63636363636,-18)(373.232323232323,-18)(149.292929292929,-10.7272727272727)(567.313131313131,-16.3636363636364)(298.585858585859,-0.727272727272727)(1149.55555555556,-9.27272727272727)(1074.90909090909,-0.727272727272727)(418.020202020202,-2.72727272727273)(403.090909090909,-13.6363636363636)(343.373737373737,-10.5454545454545)(1478,-8.18181818181818)(119.434343434343,0)(910.686868686869,-14.1818181818182)(1328.70707070707,-12.1818181818182)(343.373737373737,-6.36363636363636)(910.686868686869,-2.54545454545455)(925.616161616162,-8)(0,-11.4545454545455)(0,-14.5454545454545)(298.585858585859,-12.1818181818182)(821.111111111111,-4.72727272727273)(821.111111111111,-17.0909090909091)(1478,-6.72727272727273)(134.363636363636,-17.0909090909091)(328.444444444444,-7.81818181818182)(1194.34343434343,-17.0909090909091)(1343.63636363636,-14.1818181818182)(1045.05050505051,-4.54545454545455)(134.363636363636,-9.27272727272727)(0,-8.36363636363636)(1358.56565656566,-1.81818181818182)(671.818181818182,-2.54545454545455)(373.232323232323,-4.72727272727273)(582.242424242424,-0.909090909090909)(1000.26262626263,-15.8181818181818)(865.89898989899,-9.81818181818182)(134.363636363636,-7.27272727272727)(656.888888888889,-5.81818181818182)(1015.19191919192,0)(895.757575757576,-11.8181818181818)(1478,-2.90909090909091)(627.030303030303,-18)(477.737373737374,-11.8181818181818)(0,-16)(1015.19191919192,-17.0909090909091)(582.242424242424,-10.3636363636364)(641.959595959596,-14.1818181818182)(1478,-5.27272727272727)(328.444444444444,0)(1478,-9.63636363636364)(119.434343434343,-12.3636363636364)(821.111111111111,0)(1463.07070707071,0)(1209.27272727273,-13.0909090909091)(1164.48484848485,-7.27272727272727)(0,-17.4545454545455)(552.383838383838,-8)(1089.83838383838,-14.3636363636364)(1239.13131313131,0)(119.434343434343,-5.27272727272727)(1478,-4.18181818181818)(477.737373737374,-15.0909090909091)(701.676767676768,-11.6363636363636)(507.59595959596,-2)(1074.90909090909,-2.18181818181818)(1328.70707070707,-10.3636363636364)(910.686868686869,-3.45454545454545)(1343.63636363636,-8)(1463.07070707071,-18)(731.535353535354,-7.09090909090909)(0,-3.27272727272727)(1059.9797979798,-6.36363636363636)(776.323232323232,-16)(1328.70707070707,-4.54545454545455)(761.393939393939,-8.54545454545455)(1343.63636363636,-3.09090909090909)(14.9292929292929,0)(283.656565656566,-13.4545454545455)(1478,-14.7272727272727)(1478,-0.909090909090909)(1373.49494949495,-16)(104.505050505051,-0.909090909090909)(627.030303030303,0)(1179.41414141414,-5.27272727272727)(283.656565656566,-17.2727272727273)(1478,-12.7272727272727)(283.656565656566,-2.54545454545455)(597.171717171717,-17.0909090909091)(477.737373737374,-6.36363636363636)(1239.13131313131,-11.2727272727273)(0,-5.27272727272727)(880.828282828283,-0.909090909090909)(268.727272727273,-5.81818181818182)(1478,-10.9090909090909)(836.040404040404,-5.63636363636364)(1179.41414141414,-15.8181818181818)(1194.34343434343,-1.09090909090909)(552.383838383838,-3.81818181818182)(1059.9797979798,-12.7272727272727)(776.323232323232,-14.9090909090909)(14.9292929292929,-18)(388.161616161616,-8.90909090909091)(507.59595959596,-12.9090909090909)(865.89898989899,-12.9090909090909)(477.737373737374,-10.7272727272727)(1074.90909090909,-10.3636363636364)(134.363636363636,-3.45454545454545)(761.393939393939,-4)(1358.56565656566,-0.727272727272727)(1059.9797979798,-3.63636363636364)(194.080808080808,-15.6363636363636)(1358.56565656566,-9.09090909090909)(298.585858585859,-1.45454545454545)(925.616161616162,-18)(253.79797979798,-11.0909090909091)(716.606060606061,-10.5454545454545)(0,-2)(1478,-16.7272727272727)(671.818181818182,-12.9090909090909)(1358.56565656566,-6.72727272727273)(522.525252525253,-5.45454545454545)(597.171717171717,-15.4545454545455)(1209.27272727273,-2.18181818181818)(0,-13.4545454545455)(0,-10.1818181818182)(582.242424242424,-8.90909090909091)(268.727272727273,-4.18181818181818)(1030.12121212121,-8.18181818181818)(477.737373737374,0)(1478,-1.81818181818182)(1224.20202020202,-14.7272727272727)(179.151515151515,-18)(283.656565656566,-14.5454545454545)(0,-6.36363636363636)(731.535353535354,-1.63636363636364)(970.40404040404,-1.81818181818182)(104.505050505051,-14.5454545454545)(432.949494949495,-18)(1030.12121212121,-11.4545454545455)(880.828282828283,-6.90909090909091)(1119.69696969697,-18)(492.666666666667,-14)(358.30303030303,-16)(1298.84848484848,-16.9090909090909)(1224.20202020202,-3.63636363636364)(104.505050505051,-11.4545454545455)(403.090909090909,-3.27272727272727)(1000.26262626263,-5.09090909090909)(1194.34343434343,-9.45454545454546)(880.828282828283,-10.5454545454545)(343.373737373737,-10)(0,-7.81818181818182)(1478,-13.8181818181818)(134.363636363636,-6.54545454545455)(119.434343434343,-13.2727272727273)(0,-4.36363636363636)(955.474747474747,-9.27272727272727)(238.868686868687,-7.63636363636364)(507.59595959596,-7.27272727272727)(477.737373737374,-16.7272727272727)(0,-1.09090909090909)(194.080808080808,-8.90909090909091)(1313.77777777778,-13.4545454545455)(1239.13131313131,-6)(1298.84848484848,-18)(1000.26262626263,-14)(746.464646464646,-17.2727272727273)(104.505050505051,-2.36363636363636)(1478,-11.8181818181818)(776.323232323232,-2.72727272727273)(1209.27272727273,-8)(1478,-15.6363636363636)(731.535353535354,-9.27272727272727)(119.434343434343,-10)(925.616161616162,-15.4545454545455)(821.111111111111,-13.8181818181818)(1358.56565656566,0)(1373.49494949495,-5.27272727272727)(1478,-7.81818181818182)(0,-16.9090909090909)(671.818181818182,-0.727272727272727)(1104.76767676768,0)(283.656565656566,-12.5454545454545)(432.949494949495,-0.909090909090909)(0,-15.0909090909091)(627.030303030303,-4.54545454545455)(238.868686868687,0)(1343.63636363636,-11.8181818181818)(746.464646464646,-7.81818181818182)(1478,-6.36363636363636)(940.545454545455,-17.0909090909091)(671.818181818182,-6.54545454545455)(0,-12)(0,-8.90909090909091)(776.323232323232,-18)(432.949494949495,-4.72727272727273)(1478,-9.09090909090909)(403.090909090909,-8)(1358.56565656566,-15.0909090909091)(627.030303030303,-3.09090909090909)(1478,-3.81818181818182)(343.373737373737,-6.90909090909091)(880.828282828283,0)(836.040404040404,-11.4545454545455)(418.020202020202,-12)(1015.19191919192,-0.909090909090909)(1149.55555555556,-12.1818181818182)(388.161616161616,-15.0909090909091)(1194.34343434343,-4.54545454545455)(134.363636363636,-4.72727272727273)(656.888888888889,-14.7272727272727)(1119.69696969697,-17.0909090909091)(582.242424242424,-11.6363636363636)(597.171717171717,-18)(731.535353535354,-5.45454545454545)(1059.9797979798,-16)(492.666666666667,-9.45454545454546)(1373.49494949495,-2.54545454545455)(134.363636363636,-16.7272727272727)(686.747474747475,-16.1818181818182)(985.333333333333,-6)(552.383838383838,-2)(880.828282828283,-8.18181818181818)(940.545454545455,-12.5454545454545)(671.818181818182,-13.6363636363636)(1478,-10.3636363636364)(1104.76767676768,-6.90909090909091)(0,-10.9090909090909)(298.585858585859,-5.27272727272727)(1478,-17.4545454545455)(1239.13131313131,-10.5454545454545)(880.828282828283,-4.54545454545455)(179.151515151515,-0.727272727272727)(1074.90909090909,-9.45454545454546)(716.606060606061,0)(313.515151515152,-18)(701.676767676768,-12.3636363636364)(880.828282828283,-14.7272727272727)(850.969696969697,-16.1818181818182)(1478,-5.45454545454545)(0,-15.8181818181818)(1283.91919191919,-1.63636363636364)(1149.55555555556,-2.72727272727273)(0,-0.181818181818182)(1089.83838383838,-14.9090909090909)(1373.49494949495,-4)(1030.12121212121,-18)(1478,-0.181818181818182)(865.89898989899,-1.81818181818182)(0,-2.90909090909091)(0,-14.1818181818182)(358.30303030303,-17.0909090909091) 
};

\end{axis}
\end{tikzpicture}%

### 2013-03-20 figurefactory/proof.tex
LSE theory and experiments

\documentclass{minimal}

\usepackage{libertine}

\usepackage{tikz}
\usepackage{xspace}
\usepackage{makecell}
\usepackage{amsmath}

\newcommand{\acl}{\textsf{LSE}\xspace}

\usetikzlibrary{arrows,positioning,shapes,fit}
\tikzset{
    %Define standard arrow tip
    >=stealth',
    %Define style for boxes
    st/.style={
           rectangle,
           %rounded corners,
           draw=black, very thick,
           %text width=6.5em,
           minimum height=2em,
           text centered},
    % Define arrow style
    pil/.style={
           ->,
           thick,
           shorten <=2pt,
           shorten >=2pt,}
}

\begin{document}
\hspace{-8em}
\begin{tikzpicture}[node distance=1cm, auto,]
 %nodes
 \node[st] (conv) {Convergence of \acl};

 \node[st,below=3em of conv] (clas) {All points in $D$ have been classified}
   edge[pil] (conv);

 \node[st,text width=14em,below=3em of clas] (amb)
 {\makecell[c]
   {Conf. intervals ($\Leftrightarrow$ ambiguities)\\
    get small enough ($<2\epsilon$):\\[0.5em]
    $a_t(\*x_t) \sim \mathcal{O}\left(\sqrt{\displaystyle\frac{\beta_t\gamma_t}{t}}\right)$
   }
 } edge[pil] (clas);

 \node[st,draw=none,below=3em of amb] (dummy) {};

 \node[st,left=2em of amb] (t0) {Monotonicity}
   edge[pil] (amb);
 \node[st,left=3em of dummy] (t1) {Samples ($t$)}
   edge[pil] (amb);
 \node[st,right=1em of t1] (t2) {Kernel ($k$)}
   edge[pil] (amb);
 \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
   edge[pil] (amb);
 \node[st,right=3em of t3] (t4) {$\beta_t$}
   edge[pil] (amb);

 \node[draw=black,densely dotted,line width=0.7pt,fit=(t1)(t3)] (fit1) {};

 \node[st,below=3em of fit1] (gamma)
 {\makecell[c]
   {Quantify by max. information gain (Srinivas \emph{et al.}, 2010):\\[0.5em]
    $\gamma_t = \max_{\*y_t} I(\*y_{1:t}; f)$\\[0.5em]
    For SE kernel $\gamma_t \sim \mathcal{O}\left((\log t)^{d+1}\right)$
   }
 } edge[pil] (fit1);

 \node[st,right=8em of conv] (acc) {Solution accuracy};

 \node[st,below=3em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
   edge[pil] (acc);

 \node[st,right=2em of loss] (rules) {Classification rules}
   edge[pil] (loss);

 \node[st,below=3em of loss] (est) {Correctly estimate $f$ w.h.p.}
   edge[pil] (loss);

 \node[st,right=2em of est] (delta) {$\delta$}
   edge[pil] (est);

 \node[st,below=3em of est] (large) {Conf. intervals are large enough}
   edge[pil] (est)
   edge[pil,<-] (t4);

 \node[st,right=1.5em of clas] (eps) {$\epsilon$}
   edge[pil] (amb)
   edge[pil] (loss);
\end{tikzpicture}
\end{document}

### 2013-03-20 msthpres.tex
LSE theory and experiments

@@
-\documentclass[10pt]{beamer}
+\documentclass[10pt,mathserif,serif]{beamer}
+%\documentclass[10pt,mathserif,serif,draft, handout]{beamer}
 
@@
 \setbeamertemplate{section in toc}{$\circ$ \inserttocsection}
+\setbeamertemplate{subsection in toc}{\hspace{1em}{\footnotesize$\circ$} \inserttocsubsection}
 \setbeamertemplate{itemize item}{\scriptsize\raise1.25pt\hbox{\donotcoloroutermaths$\blacktriangleright$}}
@@
 
+\usepackage{fontspec}
+\setmainfont[Mapping=tex-text]{Linux Libertine}
+%\setsansfont{Myriad Pro}
+%\setmonofont[Scale=0.9]{Consolas}
 \usepackage[english]{babel}
-\usepackage[latin1]{inputenc}
-\usepackage{libertine}
-\usepackage[T1]{fontenc}
+%\usepackage[latin1]{inputenc}
+%\usepackage{libertine}
+%\usepackage[T1]{fontenc}
 
@@
 \usepackage{xspace}
+\usepackage{makecell}
 \usepackage{msthpres}
@@
 %%
+
+\usepackage{tikz}
+\usetikzlibrary{arrows,positioning,shapes,fit}
+\tikzset{
+    %Define standard arrow tip
+    >=stealth',
+    %Define style for boxes
+    st/.style={
+           rectangle,
+           %rounded corners,
+           draw=black, thick,
+           %text width=6.5em,
+           minimum height=2em,
+           text centered},
+    % Define arrow style
+    pil/.style={
+           ->,
+           semithick,
+           shorten <=2pt,
+           shorten >=2pt,}
+}
 
@@
 
-\section{Motivation and Background}
+\section{Motivation and background}
 
@@
 \item<4-> More importantly: they provide \textbf{variance estimates}!\\
-          Construct confidence intervals: $Q_t(\*x) = \left[\mu_{t-1}(\*x) \pm \beta_t \sigma_{t-1}(\*x)\right]$
+          Construct confidence intervals: $Q_t(\*x) = \left[\mu_{t-1}(\*x) \pm \beta_t^{1/2} \sigma_{t-1}(\*x)\right]$
 \end{itemize}
@@
 
+\section{The LSE algorithm}
 \definecolor{c1}{RGB}{255,255,255}
@@
 
-\section{The LSE algorithm}
+\subsection*{Theoretical analysis}
+\begin{frame}
+How do we judge the ``accuracy'' of a solution $(\hat{H}, \hat{L})$?
+\uncover<2->{
+\begin{definition}[Misclassification loss]
+%\begin{align*}
+$\ell_h(\*x) = \twopartdef{\max\{0, f(\*x) - h\}}{\*x\in \hat{L}}{\max\{0, h - f(\*x)\}}{\*x\in \hat{H}}$
+%\end{align*}
+\end{definition}
+\begin{center}
+\includegraphics[width=3.5in]{figures/misclass}
+\end{center}
+}
+\end{frame}
 
 \begin{frame}
+\footnotesize
+\begin{tikzpicture}[node distance=1cm, auto,]
+ \uncover<1->{
+ \node[st] (conv) {Convergence};
+ }
+
+ \uncover<3->{
+ \node[st,below=3em of conv] (clas) {All points in $D$ have been classified}
+   edge[pil] (conv);
+ }
+
+ \uncover<4->{
+ \node[st,text width=14em,below=3em of clas] (amb)
+ {\makecell[c]
+   {Conf. intervals ($\Leftrightarrow$ ambiguities)\\
+    get small enough ($<2\epsilon$)\uncover<12->{:\\[0.5em]
+    $a_t(\*x_t) \sim \mathcal{O}\left(\sqrt{\displaystyle\frac{\beta_t\gamma_t}{t}}\right)$
+    }
+   }
+ } edge[pil] (clas);
+
+ \uncover<4->{ 
+ \node[st,right=1.5em of clas] (eps) {$\epsilon$}
+   edge[pil] (amb);
+ }
+
+ \uncover<18->{ 
+ \node[st,right=1.5em of clas,fill=c6] (eps) {$\epsilon$}
+   edge[pil] (amb);
+ }
+
+ \node[st,draw=none,below=3em of amb] (dummy) {};
+ }
+
+ \uncover<11->{
+ \node[st,left=2em of amb] (t0) {Monotonicity}
+   edge[pil] (amb);
+ }
+
+ \uncover<5->{
+ \node[st,left=3em of dummy] (t1) {Samples ($t$)}
+   edge[pil] (amb);
+ }
+
+ \uncover<6->{
+ \node[st,right=1em of t1] (t2) {Kernel ($k$)}
+   edge[pil] (amb);
+ }
+
+ \uncover<7->{
+ \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
+   edge[pil] (amb);
+ }
+
+ \uncover<8->{
+ \node[st,right=3em of t3] (t4) {$\beta_t$}
+   edge[pil] (amb);
+ }
+
+ \uncover<18->{
+ \node[st,right=3em of t3,fill=c6] (t4) {$\beta_t$}
+   edge[pil] (amb);
+ }
+
+ \uncover<9->{
+ \node[draw=black,densely dotted,line width=0.7pt,fit=(t1)(t3)] (fit1) {};}
+
+ \uncover<9->{
+ \node[st,below=3em of fit1] (gamma)
+ {\makecell[c]
+   {Quantify by max. information gain (Srinivas \emph{et al.}, 2010):\\[0.5em]
+    $\gamma_t = \max_{\*y_t} I(\*y_{1:t}; f)$\uncover<10->{\\[0.5em]
+    For SE kernel $\gamma_t \sim \mathcal{O}\left((\log t)^{d+1}\right)$
+    }
+   }
+ } edge[pil] (fit1);
+ }
+
+ \uncover<2->{
+ \node[st,right=9em of conv] (acc) {Solution accuracy};
+ }
+
+ \uncover<14->{
+ \node[st,below=3em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
+   edge[pil] (acc)
+   edge[pil,<-] (eps);
+ }
+
+ \uncover<15->{
+ \node[st,right=2em of loss] (rules) {Class. rules}
+   edge[pil] (loss);
+ }
+
+ \uncover<16->{ 
+ \node[st,below=3em of loss] (est) {Correctly estimate $f$ w.h.p.}
+   edge[pil] (loss);
+ }
+
+ \uncover<16->{ 
+ \node[st,right=2em of est] (delta) {$\delta$}
+   edge[pil] (est);
+ }
+
+ \uncover<17->{
+ \node[st,below=3em of est] (large) {Conf. intervals are large enough}
+   edge[pil] (est)
+   edge[pil,<-] (t4);
+ }
+\end{tikzpicture}
+\end{frame}
+
+\begin{frame}
+\begin{theorem}[Convergence of \acl]
+\label{thm:acl}
+For any $h\in\mathbb{R}$, $\delta \in (0, 1)$, and $\epsilon > 0$,
+if $\beta_t = 2\log(|D|\pi^2 t^2/(6\delta))$, \acl terminates after
+at most $T$ iterations, where $T$ is the smallest positive integer
+satisfying
+\begin{align*}
+\frac{T}{\beta_T \gamma_T} \geq \frac{C_1}{4\epsilon^2},
+%T/(\beta_T \gamma_T) \geq C_1/(4\epsilon^2),
+\end{align*}
+where $C_1 = 8 / \log(1 + \sigma^{-2})$.
+
+Furthermore, with probability at least $1-\delta$, the algorithm returns
+an $\epsilon$-accurate solution, that is
+\begin{align*}
+\Pr\left\{\max_{\*x\in D}\ell_h(\*x) \leq \epsilon\right\} \geq 1 - \delta.
+\end{align*}
+\end{theorem}
+\end{frame}
+
+\subsection*{Results}
+\begin{frame}
+\begin{center}
+{\large Experiments}
+\end{center}
 \begin{enumerate}
-\item bla
+\item \acl
+\item<2-> Maximum variance sampling:
+\vspace{-0.5em}
+\begin{align*}
+\*x_t = \argmax_{\*x\in D} \sigma_{t-1}(\*x)
+\end{align*}
+\item<3-> ``Straddle'' heuristic (Bryan \emph{et al.}, 2005):
+\vspace{-0.5em}
+\begin{align*}
+\*x_t &= \argmax_{\*x\in D} 1.96\sigma_{t-1}(\*x)-|\mu_{t-1}(\*x) - h|\\
+&\approx \argmax_{\*x\in D} a_{t-1}(\*x) \tag{for $\beta_t = 1.96$}
+\end{align*}
 \end{enumerate}
@@
 
-\section{Extensions}
+\begin{frame}
+\begin{center}
+\hspace{4pt}\includegraphics<1->[width=4in]{figures/limno_chl_ls}\\[0.5em]
+\uncover<2->{\includegraphics[width=2.3in]{figures/ev_chl_seq}}
+\uncover<3>{\includegraphics[width=2.3in]{figures/ev_chl_eps}}
+\end{center}
+\end{frame}
 
 \begin{frame}
-\begin{enumerate}
-\item bla
-\end{enumerate}
+\begin{center}
+\includegraphics<1->[width=4in]{figures/limno_bgape_ls}\\[0.5em]
+\color{white}
+\only<1>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_seq}}
+\color{black}
+\only<2-4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq}}
+\color{white}
+\only<2>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_eps}}
+\color{black}
+\only<3>{\includegraphics[width=2.3in]{figures/ev_bgape_eps}}
+\only<4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq_str_sc}}
+\only<5>{\includegraphics[width=4in]{figures/limno_bgape_class_354}}
+\only<6>{\includegraphics[width=4in]{figures/limno_bgape_str_class_400}}
+\only<7>{\includegraphics[width=4in]{figures/limno_bgape_var_class_400}}
+\end{center}
 \end{frame}
 
-\section{Results}
+\section{Extensions}
 
@@
 
-%\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
-%  % - A title should summarize the slide in an understandable fashion
-%  %   for anyone how does not follow everything on the slide itself.
-%
-%  \begin{itemize}
-%  \item
-%    Use \texttt{itemize} a lot.
-%  \item
-%    Use very short sentences or short phrases.
-%  \end{itemize}
-%\end{frame}
-%
-%\begin{frame}{Make Titles Informative.}
-%
-%  You can create overlays\dots
-%  \begin{itemize}
-%  \item using the \texttt{pause} command:
-%    \begin{itemize}
-%    \item
-%      First item.
-%      \pause
-%    \item    
-%      Second item.
-%    \end{itemize}
-%  \item
-%    using overlay specifications:
-%    \begin{itemize}
-%    \item<3->
-%      First item.
-%    \item<4->
-%      Second item.
-%    \end{itemize}
-%  \item
-%    using the general \texttt{uncover} command:
-%    \begin{itemize}
-%      \uncover<5->{\item
-%        First item.}
-%      \uncover<6->{\item
-%        Second item.}
-%    \end{itemize}
-%  \end{itemize}
-%\end{frame}
-
-%\begin{frame}{Summary}
-%
-%  % Keep the summary *very short*.
-%  \begin{itemize}
-%  \item
-%    The \alert{first main message} of your talk in one or two lines.
-%  \item
-%    The \alert{second main message} of your talk in one or two lines.
-%  \item
-%    Perhaps a \alert{third message}, but not more than that.
-%  \end{itemize}
-%  
-%  % The following outlook is optional.
-%  \vskip0pt plus.5fill
-%  \begin{itemize}
-%  \item
-%    Outlook
-%    \begin{itemize}
-%    \item
-%      Something you haven't solved.
-%    \item
-%      Something else you haven't solved.
-%    \end{itemize}
-%  \end{itemize}
-%\end{frame}
-
 \end{document}

### 2013-03-21 msthpres.tex
Various fixes

@@
 \vspace{0.2in}
+\only<1>{
 \includegraphics[width=2in]{figures/manual.jpg}\\[-0.5em]
-{\tiny (Source: www.limnobotics.ch)}
+{\tiny (Source: www.limnobotics.ch)}}
+\only<2>{
+\includegraphics[width=4in]{figures/boat.jpg}\\[-0.5em]
+{\tiny (Source: www.limnobotics.ch)}}
+\only<3>{
+\includegraphics[width=4in]{figures/lake.png}\\[-0.5em]
+{\tiny (Source: www.limnobotics.ch)}}
 \end{center}
@@
 \vspace{0.2in}
-\includegraphics[width=4in]{figures/boat.jpg}\\[-0.5em]
-{\tiny (Source: www.limnobotics.ch)}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\begin{center}
-\vspace{0.2in}
-\includegraphics[width=4in]{figures/lake.png}\\[-0.5em]
-{\tiny (Source: www.limnobotics.ch)}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\begin{center}
-\vspace{0.2in}
-\includegraphics[width=4.7in]{figures/limno_bgape_sc}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\begin{center}
-\vspace{0.2in}
-\includegraphics[width=4.7in]{figures/limno_bgape}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\begin{center}
-\vspace{0.2in}
-\includegraphics[width=4.7in]{figures/limno_bgape_ls}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\begin{center}
-\vspace{0.2in}
-\hspace{-2em}\includegraphics[width=4.45in]{figures/limno_bgape_cl}
+\includegraphics<1>[width=4.7in]{figures/limno_bgape_sc}
+\includegraphics<2>[width=4.7in]{figures/limno_bgape}
+\includegraphics<3>[width=4.7in]{figures/limno_bgape_ls}
+\only<4>{\hspace{-2em}\includegraphics[width=4.45in]{figures/limno_bgape_cl}}
 \end{center}
@@
 \only<4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq_str_sc}}
-\only<5>{\includegraphics[width=4in]{figures/limno_bgape_class_354}}
-\only<6>{\includegraphics[width=4in]{figures/limno_bgape_str_class_400}}
-\only<7>{\includegraphics[width=4in]{figures/limno_bgape_var_class_400}}
+\only<5>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_class_354}}
+\only<6>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_str_class_400}}
+\only<7>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_var_class_400}}
 \end{center}

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_100.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
% 
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478.00005529347,-8.36363636363636)(1478.00022117143,-8.54545454545455)(1478.00027646327,-8.72727272727273)(1478.00038704571,-8.90909090909091)(1478.00038704571,-9.09090909090909)(1478.00049762651,-9.27272727272727)(1478.00038704571,-9.45454545454546)(1478.00038704571,-9.63636363636364)(1478.00038704571,-9.81818181818182)(1478.00038704571,-10)(1478.00022117143,-10.1818181818182)(1478.00005529347,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.63636363636364)(1478.00002764633,-8.72727272727273)(1478.00013823061,-8.90909090909091)(1478.00013823061,-9.09090909090909)(1478.00024881326,-9.27272727272727)(1478.00013823061,-9.45454545454546)(1478.00013823061,-9.63636363636364)(1478.00013823061,-9.81818181818182)(1478.00013823061,-10)(1478,-10.1515151515152)(1470.53535353535,-10.1818181818182)(1463.07070707071,-10.2121212121212)(1448.14141414141,-10.3333333333333)(1440.67676767677,-10.3636363636364)(1433.21212121212,-10.3939393939394)(1418.28282828283,-10.4545454545455)(1403.35353535354,-10.5151515151515)(1395.88888888889,-10.5454545454545)(1388.42424242424,-10.5757575757576)(1373.49494949495,-10.6363636363636)(1358.56565656566,-10.6363636363636)(1343.63636363636,-10.6363636363636)(1328.70707070707,-10.6363636363636)(1313.77777777778,-10.6363636363636)(1298.84848484848,-10.6363636363636)(1283.91919191919,-10.6363636363636)(1268.9898989899,-10.6363636363636)(1254.06060606061,-10.6363636363636)(1239.13131313131,-10.6363636363636)(1224.20202020202,-10.6363636363636)(1209.27272727273,-10.6363636363636)(1194.34343434343,-10.6363636363636)(1179.41414141414,-10.6363636363636)(1164.48484848485,-10.6363636363636)(1149.55555555556,-10.6363636363636)(1134.62626262626,-10.6363636363636)(1119.69696969697,-10.6363636363636)(1104.76767676768,-10.6363636363636)(1089.83838383838,-10.6363636363636)(1074.90909090909,-10.6363636363636)(1059.9797979798,-10.6363636363636)(1045.05050505051,-10.6363636363636)(1030.12121212121,-10.6363636363636)(1015.19191919192,-10.6363636363636)(1000.26262626263,-10.6363636363636)(985.333333333333,-10.6363636363636)(970.40404040404,-10.5757575757576)(962.939393939394,-10.5454545454545)(955.474747474747,-10.5151515151515)(940.545454545455,-10.4545454545455)(925.616161616162,-10.4090909090909)(918.151515151515,-10.3636363636364)(910.686868686869,-10.3333333333333)(895.757575757576,-10.2727272727273)(880.828282828283,-10.2727272727273)(865.89898989899,-10.2121212121212)(858.434343434343,-10.1818181818182)(850.969696969697,-10.1515151515152)(836.040404040404,-10.030303030303)(832.308080808081,-10)(821.111111111111,-9.90909090909091)(813.646464646465,-9.81818181818182)(806.181818181818,-9.72727272727273)(798.717171717172,-9.63636363636364)(791.252525252525,-9.54545454545455)(780.055555555556,-9.45454545454546)(776.323232323232,-9.42424242424243)(761.393939393939,-9.3030303030303)(753.929292929293,-9.27272727272727)(746.464646464646,-9.24242424242424)(731.535353535354,-9.12121212121212)(724.070707070707,-9.09090909090909)(716.606060606061,-9.06060606060606)(701.676767676768,-9)(686.747474747475,-9)(671.818181818182,-9.06060606060606)(664.353535353535,-9.09090909090909)(656.888888888889,-9.12121212121212)(641.959595959596,-9.18181818181818)(627.030303030303,-9.18181818181818)(612.10101010101,-9.18181818181818)(597.171717171717,-9.24242424242424)(589.707070707071,-9.27272727272727)(582.242424242424,-9.3030303030303)(567.313131313131,-9.36363636363636)(552.383838383838,-9.36363636363636)(537.454545454546,-9.36363636363636)(522.525252525253,-9.36363636363636)(507.59595959596,-9.36363636363636)(492.666666666667,-9.36363636363636)(477.737373737374,-9.36363636363636)(462.808080808081,-9.36363636363636)(447.878787878788,-9.36363636363636)(432.949494949495,-9.36363636363636)(418.020202020202,-9.36363636363636)(403.090909090909,-9.36363636363636)(388.161616161616,-9.36363636363636)(373.232323232323,-9.36363636363636)(358.30303030303,-9.36363636363636)(343.373737373737,-9.36363636363636)(328.444444444444,-9.36363636363636)(313.515151515152,-9.36363636363636)(298.585858585859,-9.36363636363636)(283.656565656566,-9.36363636363636)(268.727272727273,-9.36363636363636)(253.79797979798,-9.36363636363636)(238.868686868687,-9.38636363636364)(223.939393939394,-9.34090909090909)(209.010101010101,-9.29545454545455)(205.277777777778,-9.27272727272727)(194.080808080808,-9.18181818181818)(179.151515151515,-9.18181818181818)(164.222222222222,-9.12121212121212)(160.489898989899,-9.09090909090909)(149.292929292929,-9)(138.09595959596,-8.90909090909091)(134.363636363636,-8.88636363636364)(119.434343434343,-8.84090909090909)(104.505050505051,-8.79545454545455)(97.040404040404,-8.72727272727273)(89.5757575757576,-8.63636363636364)(78.3787878787879,-8.54545454545455)(74.6464646464647,-8.51515151515152)(59.7171717171717,-8.39393939393939)(55.9848484848485,-8.36363636363636)(44.7878787878788,-8.27272727272727)(37.3232323232323,-8.18181818181818)(29.8585858585859,-8.04545454545455)(27.3703703703704,-8)(22.3939393939394,-7.81818181818182)(22.3939393939394,-7.63636363636364)(27.3703703703704,-7.45454545454546)(29.8585858585859,-7.40909090909091)(37.3232323232323,-7.27272727272727)(44.7878787878788,-7.18181818181818)(55.9848484848485,-7.09090909090909)(59.7171717171717,-7.06060606060606)(74.6464646464647,-7)(89.5757575757576,-7)(104.505050505051,-7)(119.434343434343,-7)(134.363636363636,-7)(149.292929292929,-7)(164.222222222222,-7)(179.151515151515,-7)(194.080808080808,-7)(209.010101010101,-7)(223.939393939394,-7)(238.868686868687,-7.04545454545455)(253.79797979798,-7.04545454545455)(261.262626262626,-7.09090909090909)(268.727272727273,-7.12121212121212)(283.656565656566,-7.12121212121212)(298.585858585859,-7.18181818181818)(313.515151515152,-7.12121212121212)(320.979797979798,-7.09090909090909)(328.444444444444,-7.06060606060606)(343.373737373737,-7)(358.30303030303,-7)(373.232323232323,-6.95454545454546)(380.69696969697,-6.90909090909091)(388.161616161616,-6.87878787878788)(403.090909090909,-6.81818181818182)(418.020202020202,-6.81818181818182)(432.949494949495,-6.75757575757576)(447.878787878788,-6.75757575757576)(455.343434343434,-6.72727272727273)(462.808080808081,-6.6969696969697)(477.737373737374,-6.6969696969697)(492.666666666667,-6.63636363636364)(507.59595959596,-6.63636363636364)(522.525252525253,-6.63636363636364)(537.454545454546,-6.63636363636364)(552.383838383838,-6.63636363636364)(567.313131313131,-6.6969696969697)(574.777777777778,-6.72727272727273)(582.242424242424,-6.75757575757576)(597.171717171717,-6.81818181818182)(612.10101010101,-6.87878787878788)(619.565656565657,-6.90909090909091)(627.030303030303,-6.93939393939394)(641.959595959596,-7.06060606060606)(649.424242424242,-7.09090909090909)(656.888888888889,-7.12121212121212)(671.818181818182,-7.24242424242424)(675.550505050505,-7.27272727272727)(686.747474747475,-7.36363636363636)(697.944444444444,-7.45454545454546)(701.676767676768,-7.48484848484849)(716.606060606061,-7.54545454545455)(731.535353535354,-7.60606060606061)(739,-7.63636363636364)(746.464646464646,-7.66666666666667)(761.393939393939,-7.72727272727273)(776.323232323232,-7.72727272727273)(791.252525252525,-7.72727272727273)(806.181818181818,-7.72727272727273)(821.111111111111,-7.66666666666667)(828.575757575758,-7.63636363636364)(836.040404040404,-7.60606060606061)(850.969696969697,-7.48484848484849)(858.434343434343,-7.45454545454546)(865.89898989899,-7.42424242424243)(878.340067340067,-7.27272727272727)(880.828282828283,-7.24242424242424)(895.757575757576,-7.18181818181818)(910.686868686869,-7.12121212121212)(925.616161616162,-7.12121212121212)(933.080808080808,-7.09090909090909)(940.545454545455,-7.06060606060606)(955.474747474747,-7)(970.40404040404,-6.97727272727273)(985.333333333333,-6.97727272727273)(1000.26262626263,-6.97727272727273)(1015.19191919192,-7)(1030.12121212121,-7)(1045.05050505051,-7)(1059.9797979798,-7)(1074.90909090909,-7)(1089.83838383838,-7)(1104.76767676768,-7)(1119.69696969697,-7)(1134.62626262626,-7)(1149.55555555556,-7.06060606060606)(1157.0202020202,-7.09090909090909)(1164.48484848485,-7.12121212121212)(1179.41414141414,-7.18181818181818)(1194.34343434343,-7.18181818181818)(1209.27272727273,-7.18181818181818)(1224.20202020202,-7.18181818181818)(1239.13131313131,-7.18181818181818)(1254.06060606061,-7.18181818181818)(1268.9898989899,-7.18181818181818)(1283.91919191919,-7.24242424242424)(1291.38383838384,-7.27272727272727)(1298.84848484848,-7.3030303030303)(1313.77777777778,-7.36363636363636)(1328.70707070707,-7.36363636363636)(1343.63636363636,-7.42424242424243)(1351.10101010101,-7.45454545454546)(1358.56565656566,-7.48484848484849)(1373.49494949495,-7.60606060606061)(1377.22727272727,-7.63636363636364)(1388.42424242424,-7.72727272727273)(1399.62121212121,-7.81818181818182)(1403.35353535354,-7.84848484848485)(1418.28282828283,-7.96969696969697)(1422.01515151515,-8)(1433.21212121212,-8.09090909090909)(1440.67676767677,-8.18181818181818)(1448.14141414141,-8.27272727272727)(1455.60606060606,-8.36363636363636)(1463.07070707071,-8.45454545454545)(1474.26767676768,-8.54545454545455)(1478,-8.63636363636364)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1388.42424242424,-8.95454545454546)(1392.15656565657,-9.09090909090909)(1392.15656565657,-9.27272727272727)(1388.42424242424,-9.40909090909091)(1386.93131313131,-9.45454545454546)(1375.98316498317,-9.63636363636364)(1373.49494949495,-9.66666666666667)(1358.56565656566,-9.8)(1356.07744107744,-9.81818181818182)(1343.63636363636,-9.89393939393939)(1328.70707070707,-9.92424242424243)(1313.77777777778,-9.98484848484848)(1306.31313131313,-10)(1298.84848484848,-10.0181818181818)(1283.91919191919,-10.0454545454545)(1268.9898989899,-10.0454545454545)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.0757575757576)(1224.20202020202,-10.0757575757576)(1209.27272727273,-10.0454545454545)(1194.34343434343,-10.0454545454545)(1179.41414141414,-10.0454545454545)(1164.48484848485,-10.0454545454545)(1149.55555555556,-10.0454545454545)(1134.62626262626,-10.0454545454545)(1119.69696969697,-10.0454545454545)(1104.76767676768,-10.0757575757576)(1089.83838383838,-10.1060606060606)(1074.90909090909,-10.1363636363636)(1059.9797979798,-10.1363636363636)(1045.05050505051,-10.0909090909091)(1030.12121212121,-10.0545454545455)(1015.19191919192,-10.0181818181818)(1000.26262626263,-10.0454545454545)(985.333333333333,-10.0454545454545)(970.40404040404,-10.0454545454545)(959.207070707071,-10)(955.474747474747,-9.98484848484848)(940.545454545455,-9.92424242424243)(925.616161616162,-9.85714285714286)(914.419191919192,-9.81818181818182)(910.686868686869,-9.8030303030303)(895.757575757576,-9.74242424242424)(882.694444444444,-9.63636363636364)(880.828282828283,-9.62121212121212)(865.89898989899,-9.54545454545455)(856.568181818182,-9.45454545454546)(850.969696969697,-9.38636363636364)(841.638888888889,-9.27272727272727)(836.040404040404,-9.13636363636364)(834.547474747475,-9.09090909090909)(832.308080808081,-8.90909090909091)(832.308080808081,-8.72727272727273)(836.040404040404,-8.59090909090909)(837.284511784512,-8.54545454545455)(845.371212121212,-8.36363636363636)(850.969696969697,-8.29545454545455)(860.300505050505,-8.18181818181818)(865.89898989899,-8.11363636363636)(875.229797979798,-8)(880.828282828283,-7.93181818181818)(895.757575757576,-7.83333333333333)(898.245791245791,-7.81818181818182)(910.686868686869,-7.74242424242424)(925.616161616162,-7.69090909090909)(936.813131313131,-7.63636363636364)(940.545454545455,-7.61818181818182)(955.474747474747,-7.59090909090909)(970.40404040404,-7.54545454545455)(985.333333333333,-7.50909090909091)(1000.26262626263,-7.47272727272727)(1015.19191919192,-7.53030303030303)(1030.12121212121,-7.56060606060606)(1045.05050505051,-7.59090909090909)(1059.9797979798,-7.59090909090909)(1074.90909090909,-7.59090909090909)(1089.83838383838,-7.59090909090909)(1104.76767676768,-7.59090909090909)(1119.69696969697,-7.59090909090909)(1134.62626262626,-7.61818181818182)(1149.55555555556,-7.61818181818182)(1153.28787878788,-7.63636363636364)(1164.48484848485,-7.68181818181818)(1179.41414141414,-7.71212121212121)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.77272727272727)(1224.20202020202,-7.77272727272727)(1239.13131313131,-7.77272727272727)(1254.06060606061,-7.79545454545455)(1257.79292929293,-7.81818181818182)(1268.9898989899,-7.87272727272727)(1283.91919191919,-7.94545454545455)(1295.11616161616,-8)(1298.84848484848,-8.01515151515152)(1313.77777777778,-8.07575757575757)(1326.84090909091,-8.18181818181818)(1328.70707070707,-8.1969696969697)(1343.63636363636,-8.25)(1352.96717171717,-8.36363636363636)(1358.56565656566,-8.43181818181818)(1367.89646464646,-8.54545454545455)(1373.49494949495,-8.63636363636364)(1379.09343434343,-8.72727272727273)(1387.18013468013,-8.90909090909091)(1388.42424242424,-8.95454545454546)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1358.56565656566,-8.79545454545455)(1364.7861952862,-8.90909090909091)(1369.76262626263,-9.09090909090909)(1367.27441077441,-9.27272727272727)(1362.29797979798,-9.45454545454546)(1358.56565656566,-9.5)(1343.63636363636,-9.58181818181818)(1332.43939393939,-9.63636363636364)(1328.70707070707,-9.65151515151515)(1313.77777777778,-9.71212121212121)(1298.84848484848,-9.74242424242424)(1283.91919191919,-9.77272727272727)(1268.9898989899,-9.77272727272727)(1254.06060606061,-9.77272727272727)(1239.13131313131,-9.77272727272727)(1224.20202020202,-9.77272727272727)(1209.27272727273,-9.77272727272727)(1194.34343434343,-9.77272727272727)(1179.41414141414,-9.77272727272727)(1164.48484848485,-9.77272727272727)(1149.55555555556,-9.77272727272727)(1134.62626262626,-9.74242424242424)(1119.69696969697,-9.74242424242424)(1104.76767676768,-9.76363636363636)(1093.57070707071,-9.81818181818182)(1089.83838383838,-9.83333333333333)(1074.90909090909,-9.86363636363636)(1059.9797979798,-9.86363636363636)(1048.78282828283,-9.81818181818182)(1045.05050505051,-9.79545454545455)(1030.12121212121,-9.76363636363636)(1015.19191919192,-9.74242424242424)(1000.26262626263,-9.77272727272727)(985.333333333333,-9.77272727272727)(970.40404040404,-9.77272727272727)(955.474747474747,-9.71212121212121)(940.545454545455,-9.65151515151515)(936.813131313131,-9.63636363636364)(925.616161616162,-9.59090909090909)(910.686868686869,-9.53030303030303)(895.757575757576,-9.46969696969697)(893.891414141414,-9.45454545454546)(880.828282828283,-9.34848484848485)(868.387205387205,-9.27272727272727)(865.89898989899,-9.25)(857.190235690236,-9.09090909090909)(854.70202020202,-8.90909090909091)(854.70202020202,-8.72727272727273)(859.678451178451,-8.54545454545455)(865.89898989899,-8.43181818181818)(871.497474747475,-8.36363636363636)(880.828282828283,-8.25)(886.426767676768,-8.18181818181818)(895.757575757576,-8.10606060606061)(910.686868686869,-8.01818181818182)(918.151515151515,-8)(925.616161616162,-7.98484848484848)(940.545454545455,-7.92424242424242)(955.474747474747,-7.89393939393939)(970.40404040404,-7.83636363636364)(977.868686868687,-7.81818181818182)(985.333333333333,-7.8030303030303)(1000.26262626263,-7.77272727272727)(1015.19191919192,-7.8030303030303)(1022.65656565657,-7.81818181818182)(1030.12121212121,-7.83636363636364)(1045.05050505051,-7.86363636363636)(1059.9797979798,-7.87272727272727)(1074.90909090909,-7.87272727272727)(1089.83838383838,-7.87272727272727)(1104.76767676768,-7.86363636363636)(1119.69696969697,-7.86363636363636)(1134.62626262626,-7.89393939393939)(1149.55555555556,-7.89393939393939)(1164.48484848485,-7.95454545454546)(1179.41414141414,-7.98484848484848)(1183.14646464646,-8)(1194.34343434343,-8.04545454545455)(1209.27272727273,-8.04545454545455)(1224.20202020202,-8.04545454545455)(1239.13131313131,-8.05454545454545)(1254.06060606061,-8.12727272727273)(1265.25757575758,-8.18181818181818)(1268.9898989899,-8.20454545454546)(1283.91919191919,-8.22727272727273)(1298.84848484848,-8.28787878787879)(1313.77777777778,-8.34848484848485)(1315.64393939394,-8.36363636363636)(1328.70707070707,-8.46969696969697)(1341.14814814815,-8.54545454545455)(1343.63636363636,-8.57575757575757)(1352.96717171717,-8.72727272727273)(1358.56565656566,-8.79545454545455)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_120.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478.00005529347,-8.36363636363636)(1478.00022117143,-8.54545454545455)(1478.00027646327,-8.72727272727273)(1478.00027646327,-8.90909090909091)(1478.00027646327,-9.09090909090909)(1478.00038704571,-9.27272727272727)(1478.00038704571,-9.45454545454546)(1478.00038704571,-9.63636363636364)(1478.00027646327,-9.81818181818182)(1478.00022117143,-10)(1478.00005529347,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.63636363636364)(1478.00002764633,-8.72727272727273)(1478.00002764633,-8.90909090909091)(1478.00002764633,-9.09090909090909)(1478.00013823061,-9.27272727272727)(1478.00013823061,-9.45454545454546)(1478.00013823061,-9.63636363636364)(1478.00002764633,-9.81818181818182)(1478,-9.90909090909091)(1470.53535353535,-10)(1463.07070707071,-10.030303030303)(1448.14141414141,-10.1515151515152)(1440.67676767677,-10.1818181818182)(1433.21212121212,-10.2121212121212)(1418.28282828283,-10.3333333333333)(1410.81818181818,-10.3636363636364)(1403.35353535354,-10.3939393939394)(1388.42424242424,-10.4545454545455)(1373.49494949495,-10.5151515151515)(1366.0303030303,-10.5454545454545)(1358.56565656566,-10.5757575757576)(1343.63636363636,-10.6363636363636)(1328.70707070707,-10.6363636363636)(1313.77777777778,-10.6363636363636)(1298.84848484848,-10.6363636363636)(1283.91919191919,-10.6363636363636)(1268.9898989899,-10.6363636363636)(1254.06060606061,-10.6363636363636)(1239.13131313131,-10.6363636363636)(1224.20202020202,-10.6363636363636)(1209.27272727273,-10.5757575757576)(1194.34343434343,-10.5757575757576)(1179.41414141414,-10.5757575757576)(1164.48484848485,-10.6363636363636)(1149.55555555556,-10.6363636363636)(1134.62626262626,-10.6363636363636)(1119.69696969697,-10.6363636363636)(1104.76767676768,-10.6363636363636)(1089.83838383838,-10.6363636363636)(1074.90909090909,-10.6363636363636)(1059.9797979798,-10.6363636363636)(1045.05050505051,-10.6363636363636)(1030.12121212121,-10.6363636363636)(1015.19191919192,-10.6363636363636)(1000.26262626263,-10.6363636363636)(985.333333333333,-10.6363636363636)(970.40404040404,-10.5757575757576)(962.939393939394,-10.5454545454545)(955.474747474747,-10.5151515151515)(940.545454545455,-10.4545454545455)(925.616161616162,-10.4090909090909)(918.151515151515,-10.3636363636364)(910.686868686869,-10.3333333333333)(895.757575757576,-10.2727272727273)(880.828282828283,-10.2121212121212)(873.363636363636,-10.1818181818182)(865.89898989899,-10.1515151515152)(850.969696969697,-10.030303030303)(843.505050505051,-10)(836.040404040404,-9.96969696969697)(821.111111111111,-9.84848484848485)(817.378787878788,-9.81818181818182)(806.181818181818,-9.72727272727273)(798.717171717172,-9.63636363636364)(791.252525252525,-9.54545454545455)(780.055555555556,-9.45454545454546)(776.323232323232,-9.42424242424243)(761.393939393939,-9.3030303030303)(753.929292929293,-9.27272727272727)(746.464646464646,-9.24242424242424)(731.535353535354,-9.12121212121212)(724.070707070707,-9.09090909090909)(716.606060606061,-9.06060606060606)(701.676767676768,-9)(686.747474747475,-9)(671.818181818182,-9.06060606060606)(664.353535353535,-9.09090909090909)(656.888888888889,-9.12121212121212)(641.959595959596,-9.18181818181818)(627.030303030303,-9.18181818181818)(612.10101010101,-9.18181818181818)(597.171717171717,-9.24242424242424)(589.707070707071,-9.27272727272727)(582.242424242424,-9.3030303030303)(567.313131313131,-9.36363636363636)(552.383838383838,-9.42424242424243)(537.454545454546,-9.42424242424243)(522.525252525253,-9.42424242424243)(507.59595959596,-9.36363636363636)(492.666666666667,-9.36363636363636)(477.737373737374,-9.36363636363636)(462.808080808081,-9.36363636363636)(447.878787878788,-9.36363636363636)(432.949494949495,-9.36363636363636)(418.020202020202,-9.36363636363636)(403.090909090909,-9.36363636363636)(388.161616161616,-9.3030303030303)(380.69696969697,-9.27272727272727)(373.232323232323,-9.24242424242424)(358.30303030303,-9.18181818181818)(343.373737373737,-9.18181818181818)(328.444444444444,-9.18181818181818)(313.515151515152,-9.18181818181818)(298.585858585859,-9.18181818181818)(283.656565656566,-9.18181818181818)(268.727272727273,-9.18181818181818)(253.79797979798,-9.18181818181818)(238.868686868687,-9.24242424242424)(223.939393939394,-9.24242424242424)(209.010101010101,-9.24242424242424)(194.080808080808,-9.18181818181818)(179.151515151515,-9.18181818181818)(164.222222222222,-9.12121212121212)(160.489898989899,-9.09090909090909)(149.292929292929,-9)(138.09595959596,-8.90909090909091)(134.363636363636,-8.88636363636364)(119.434343434343,-8.84090909090909)(104.505050505051,-8.79545454545455)(97.040404040404,-8.72727272727273)(89.5757575757576,-8.63636363636364)(78.3787878787879,-8.54545454545455)(74.6464646464647,-8.51515151515152)(59.7171717171717,-8.39393939393939)(55.9848484848485,-8.36363636363636)(44.7878787878788,-8.22727272727273)(42.2996632996633,-8.18181818181818)(37.3232323232323,-8)(37.3232323232323,-7.81818181818182)(37.3232323232323,-7.63636363636364)(42.2996632996633,-7.45454545454546)(44.7878787878788,-7.40909090909091)(55.9848484848485,-7.27272727272727)(59.7171717171717,-7.24242424242424)(74.6464646464647,-7.18181818181818)(89.5757575757576,-7.18181818181818)(104.505050505051,-7.18181818181818)(119.434343434343,-7.12121212121212)(134.363636363636,-7.12121212121212)(149.292929292929,-7.12121212121212)(164.222222222222,-7.18181818181818)(179.151515151515,-7.18181818181818)(194.080808080808,-7.18181818181818)(209.010101010101,-7.18181818181818)(223.939393939394,-7.18181818181818)(238.868686868687,-7.24242424242424)(246.333333333333,-7.27272727272727)(253.79797979798,-7.3030303030303)(268.727272727273,-7.36363636363636)(283.656565656566,-7.36363636363636)(298.585858585859,-7.36363636363636)(313.515151515152,-7.36363636363636)(328.444444444444,-7.36363636363636)(343.373737373737,-7.3030303030303)(350.838383838384,-7.27272727272727)(358.30303030303,-7.24242424242424)(373.232323232323,-7.18181818181818)(384.429292929293,-7.09090909090909)(388.161616161616,-7.04545454545455)(399.358585858586,-6.90909090909091)(403.090909090909,-6.87878787878788)(418.020202020202,-6.81818181818182)(432.949494949495,-6.75757575757576)(447.878787878788,-6.75757575757576)(455.343434343434,-6.72727272727273)(462.808080808081,-6.6969696969697)(477.737373737374,-6.6969696969697)(492.666666666667,-6.63636363636364)(507.59595959596,-6.63636363636364)(522.525252525253,-6.63636363636364)(537.454545454546,-6.63636363636364)(552.383838383838,-6.6969696969697)(559.848484848485,-6.72727272727273)(567.313131313131,-6.75757575757576)(582.242424242424,-6.81818181818182)(597.171717171717,-6.87878787878788)(604.636363636364,-6.90909090909091)(612.10101010101,-6.93939393939394)(627.030303030303,-7.06060606060606)(634.494949494949,-7.09090909090909)(641.959595959596,-7.12121212121212)(656.888888888889,-7.24242424242424)(664.353535353535,-7.27272727272727)(671.818181818182,-7.3030303030303)(686.747474747475,-7.42424242424243)(694.212121212121,-7.45454545454546)(701.676767676768,-7.48484848484849)(716.606060606061,-7.60606060606061)(724.070707070707,-7.63636363636364)(731.535353535354,-7.66666666666667)(746.464646464646,-7.72727272727273)(761.393939393939,-7.72727272727273)(776.323232323232,-7.72727272727273)(791.252525252525,-7.72727272727273)(806.181818181818,-7.72727272727273)(821.111111111111,-7.66666666666667)(828.575757575758,-7.63636363636364)(836.040404040404,-7.60606060606061)(850.969696969697,-7.48484848484849)(858.434343434343,-7.45454545454546)(865.89898989899,-7.42424242424243)(878.340067340067,-7.27272727272727)(880.828282828283,-7.24242424242424)(895.757575757576,-7.18181818181818)(910.686868686869,-7.12121212121212)(925.616161616162,-7.18181818181818)(940.545454545455,-7.12121212121212)(948.010101010101,-7.09090909090909)(955.474747474747,-7.06060606060606)(970.40404040404,-6.97727272727273)(985.333333333333,-6.97727272727273)(1000.26262626263,-6.97727272727273)(1015.19191919192,-7)(1030.12121212121,-7)(1045.05050505051,-7)(1059.9797979798,-7)(1074.90909090909,-7)(1089.83838383838,-7)(1104.76767676768,-7.06060606060606)(1112.23232323232,-7.09090909090909)(1119.69696969697,-7.12121212121212)(1134.62626262626,-7.18181818181818)(1149.55555555556,-7.18181818181818)(1164.48484848485,-7.18181818181818)(1179.41414141414,-7.18181818181818)(1194.34343434343,-7.18181818181818)(1209.27272727273,-7.18181818181818)(1224.20202020202,-7.18181818181818)(1239.13131313131,-7.18181818181818)(1254.06060606061,-7.18181818181818)(1268.9898989899,-7.24242424242424)(1276.45454545455,-7.27272727272727)(1283.91919191919,-7.29545454545455)(1298.84848484848,-7.36363636363636)(1313.77777777778,-7.36363636363636)(1328.70707070707,-7.36363636363636)(1343.63636363636,-7.42424242424243)(1351.10101010101,-7.45454545454546)(1358.56565656566,-7.48484848484849)(1373.49494949495,-7.60606060606061)(1377.22727272727,-7.63636363636364)(1388.42424242424,-7.72727272727273)(1399.62121212121,-7.81818181818182)(1403.35353535354,-7.84848484848485)(1418.28282828283,-7.96969696969697)(1422.01515151515,-8)(1433.21212121212,-8.09090909090909)(1440.67676767677,-8.18181818181818)(1448.14141414141,-8.27272727272727)(1455.60606060606,-8.36363636363636)(1463.07070707071,-8.45454545454545)(1474.26767676768,-8.54545454545455)(1478,-8.63636363636364)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-8.86363636363636)(1405.84175084175,-8.90909090909091)(1410.81818181818,-9.09090909090909)(1405.84175084175,-9.27272727272727)(1403.35353535354,-9.31818181818182)(1397.75505050505,-9.45454545454546)(1388.42424242424,-9.56818181818182)(1380.9595959596,-9.63636363636364)(1373.49494949495,-9.72727272727273)(1366.0303030303,-9.81818181818182)(1358.56565656566,-9.88636363636364)(1343.63636363636,-9.94545454545455)(1328.70707070707,-9.95454545454546)(1317.5101010101,-10)(1313.77777777778,-10.0227272727273)(1298.84848484848,-10.0909090909091)(1283.91919191919,-10.1363636363636)(1268.9898989899,-10.1363636363636)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1666666666667)(1224.20202020202,-10.1666666666667)(1209.27272727273,-10.1363636363636)(1194.34343434343,-10.1272727272727)(1179.41414141414,-10.1272727272727)(1164.48484848485,-10.1272727272727)(1149.55555555556,-10.1363636363636)(1134.62626262626,-10.1363636363636)(1119.69696969697,-10.1363636363636)(1104.76767676768,-10.1363636363636)(1089.83838383838,-10.1363636363636)(1074.90909090909,-10.1363636363636)(1059.9797979798,-10.1363636363636)(1045.05050505051,-10.1272727272727)(1030.12121212121,-10.1272727272727)(1015.19191919192,-10.1272727272727)(1000.26262626263,-10.1363636363636)(985.333333333333,-10.1060606060606)(970.40404040404,-10.0545454545455)(959.207070707071,-10)(955.474747474747,-9.98484848484848)(940.545454545455,-9.95454545454546)(925.616161616162,-9.89393939393939)(910.686868686869,-9.83636363636364)(908.198653198653,-9.81818181818182)(895.757575757576,-9.72727272727273)(880.828282828283,-9.65909090909091)(878.340067340067,-9.63636363636364)(865.89898989899,-9.52272727272727)(858.434343434343,-9.45454545454546)(850.969696969697,-9.36363636363636)(845.371212121212,-9.27272727272727)(840.519191919192,-9.09090909090909)(839.772727272727,-8.90909090909091)(839.772727272727,-8.72727272727273)(843.505050505051,-8.54545454545455)(849.103535353535,-8.36363636363636)(850.969696969697,-8.33333333333333)(863.410774410775,-8.18181818181818)(865.89898989899,-8.15151515151515)(878.340067340067,-8)(880.828282828283,-7.97727272727273)(895.757575757576,-7.83636363636364)(898.245791245791,-7.81818181818182)(910.686868686869,-7.72727272727273)(925.616161616162,-7.69090909090909)(936.813131313131,-7.63636363636364)(940.545454545455,-7.61363636363636)(955.474747474747,-7.54545454545455)(970.40404040404,-7.47272727272727)(985.333333333333,-7.47272727272727)(1000.26262626263,-7.47272727272727)(1015.19191919192,-7.5)(1030.12121212121,-7.5)(1045.05050505051,-7.5)(1059.9797979798,-7.5)(1074.90909090909,-7.50909090909091)(1089.83838383838,-7.56818181818182)(1101.03535353535,-7.63636363636364)(1104.76767676768,-7.65151515151515)(1119.69696969697,-7.68181818181818)(1134.62626262626,-7.68181818181818)(1149.55555555556,-7.68181818181818)(1164.48484848485,-7.68181818181818)(1179.41414141414,-7.68181818181818)(1194.34343434343,-7.68181818181818)(1209.27272727273,-7.68181818181818)(1224.20202020202,-7.71212121212121)(1239.13131313131,-7.76363636363636)(1254.06060606061,-7.79545454545455)(1261.52525252525,-7.81818181818182)(1268.9898989899,-7.83636363636364)(1283.91919191919,-7.83636363636364)(1298.84848484848,-7.90909090909091)(1313.77777777778,-7.97727272727273)(1316.26599326599,-8)(1328.70707070707,-8.09090909090909)(1343.63636363636,-8.15909090909091)(1346.12457912458,-8.18181818181818)(1358.56565656566,-8.29545454545455)(1366.0303030303,-8.36363636363636)(1373.49494949495,-8.43181818181818)(1382.82575757576,-8.54545454545455)(1388.42424242424,-8.61363636363636)(1397.75505050505,-8.72727272727273)(1403.35353535354,-8.86363636363636)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1373.49494949495,-9)(1377.22727272727,-9.09090909090909)(1373.49494949495,-9.18181818181818)(1371.00673400673,-9.27272727272727)(1360.43181818182,-9.45454545454546)(1358.56565656566,-9.47727272727273)(1343.63636363636,-9.60606060606061)(1339.90404040404,-9.63636363636364)(1328.70707070707,-9.68181818181818)(1313.77777777778,-9.72727272727273)(1298.84848484848,-9.79545454545455)(1295.11616161616,-9.81818181818182)(1283.91919191919,-9.86363636363636)(1268.9898989899,-9.86363636363636)(1254.06060606061,-9.87272727272727)(1239.13131313131,-9.87272727272727)(1224.20202020202,-9.87272727272727)(1209.27272727273,-9.86363636363636)(1194.34343434343,-9.83333333333333)(1179.41414141414,-9.83333333333333)(1164.48484848485,-9.83333333333333)(1149.55555555556,-9.86363636363636)(1134.62626262626,-9.83636363636364)(1119.69696969697,-9.83636363636364)(1104.76767676768,-9.83636363636364)(1089.83838383838,-9.86363636363636)(1074.90909090909,-9.86363636363636)(1059.9797979798,-9.86363636363636)(1045.05050505051,-9.83333333333333)(1030.12121212121,-9.83333333333333)(1015.19191919192,-9.83333333333333)(1000.26262626263,-9.86363636363636)(985.333333333333,-9.83333333333333)(981.60101010101,-9.81818181818182)(970.40404040404,-9.76363636363636)(955.474747474747,-9.71212121212121)(940.545454545455,-9.68181818181818)(929.348484848485,-9.63636363636364)(925.616161616162,-9.61363636363636)(910.686868686869,-9.54545454545455)(898.245791245791,-9.45454545454546)(895.757575757576,-9.43181818181818)(880.828282828283,-9.32727272727273)(875.229797979798,-9.27272727272727)(865.89898989899,-9.12121212121212)(864.654882154882,-9.09090909090909)(862.166666666667,-8.90909090909091)(862.166666666667,-8.72727272727273)(865.89898989899,-8.59090909090909)(867.765151515152,-8.54545454545455)(876.349494949495,-8.36363636363636)(880.828282828283,-8.30909090909091)(893.891414141414,-8.18181818181818)(895.757575757576,-8.16363636363636)(910.686868686869,-8.02272727272727)(918.151515151515,-8)(925.616161616162,-7.98484848484848)(940.545454545455,-7.94545454545455)(955.474747474748,-7.88636363636364)(962.939393939394,-7.81818181818182)(970.40404040404,-7.77272727272727)(985.333333333333,-7.77272727272727)(1000.26262626263,-7.77272727272727)(1015.19191919192,-7.77272727272727)(1030.12121212121,-7.77272727272727)(1045.05050505051,-7.77272727272727)(1059.9797979798,-7.77272727272727)(1074.90909090909,-7.8030303030303)(1078.64141414141,-7.81818181818182)(1089.83838383838,-7.90909090909091)(1104.76767676768,-7.94545454545455)(1119.69696969697,-7.95454545454546)(1134.62626262626,-7.95454545454546)(1149.55555555556,-7.95454545454546)(1164.48484848485,-7.95454545454546)(1179.41414141414,-7.95454545454546)(1194.34343434343,-7.95454545454546)(1209.27272727273,-7.95454545454546)(1224.20202020202,-7.98484848484848)(1227.93434343434,-8)(1239.13131313131,-8.06818181818182)(1254.06060606061,-8.12727272727273)(1268.9898989899,-8.16363636363636)(1283.91919191919,-8.13636363636364)(1295.11616161616,-8.18181818181818)(1298.84848484848,-8.20454545454546)(1313.77777777778,-8.27272727272727)(1326.21885521886,-8.36363636363636)(1328.70707070707,-8.38636363636364)(1343.63636363636,-8.49090909090909)(1349.23484848485,-8.54545454545455)(1358.56565656566,-8.6969696969697)(1360.43181818182,-8.72727272727273)(1371.00673400673,-8.90909090909091)(1373.49494949495,-9)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (492.666666666667,-7.95454545454546)(503.863636363636,-7.81818181818182)(507.59595959596,-7.78787878787879)(522.525252525253,-7.72727272727273)(537.454545454546,-7.78787878787879)(541.186868686869,-7.81818181818182)(552.383838383838,-7.90909090909091)(559.848484848485,-8)(567.313131313131,-8.13636363636364)(569.801346801347,-8.18181818181818)(567.313131313131,-8.27272727272727)(563.580808080808,-8.36363636363636)(552.383838383838,-8.45454545454545)(537.454545454546,-8.45454545454545)(522.525252525253,-8.45454545454545)(507.59595959596,-8.39393939393939)(503.863636363636,-8.36363636363636)(492.666666666667,-8.22727272727273)(488.934343434343,-8.18181818181818)(488.934343434343,-8)(492.666666666667,-7.95454545454546)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_140.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478.00005529347,-8.36363636363636)(1478.00011058654,-8.54545454545455)(1478.00016587919,-8.72727272727273)(1478.00016587919,-8.90909090909091)(1478.00027646327,-9.09090909090909)(1478.00038704571,-9.27272727272727)(1478.00038704571,-9.45454545454546)(1478.00027646327,-9.63636363636364)(1478.00011058654,-9.81818181818182)(1478.00005529347,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-9.04545454545455)(1478.00002764633,-9.09090909090909)(1478.00013823061,-9.27272727272727)(1478.00013823061,-9.45454545454546)(1478.00002764633,-9.63636363636364)(1478,-9.66666666666667)(1465.55892255892,-9.81818181818182)(1463.07070707071,-9.86363636363636)(1455.60606060606,-10)(1448.14141414141,-10.0909090909091)(1436.94444444444,-10.1818181818182)(1433.21212121212,-10.2121212121212)(1418.28282828283,-10.2727272727273)(1403.35353535354,-10.3333333333333)(1395.88888888889,-10.3636363636364)(1388.42424242424,-10.3939393939394)(1373.49494949495,-10.4545454545455)(1358.56565656566,-10.4545454545455)(1343.63636363636,-10.5151515151515)(1336.17171717172,-10.5454545454545)(1328.70707070707,-10.5757575757576)(1313.77777777778,-10.6363636363636)(1298.84848484848,-10.6363636363636)(1283.91919191919,-10.6363636363636)(1268.9898989899,-10.6363636363636)(1254.06060606061,-10.6363636363636)(1239.13131313131,-10.6363636363636)(1224.20202020202,-10.6363636363636)(1209.27272727273,-10.5757575757576)(1194.34343434343,-10.5757575757576)(1186.87878787879,-10.5454545454545)(1179.41414141414,-10.5151515151515)(1164.48484848485,-10.5151515151515)(1149.55555555556,-10.4545454545455)(1134.62626262626,-10.4545454545455)(1119.69696969697,-10.4545454545455)(1104.76767676768,-10.4090909090909)(1089.83838383838,-10.4090909090909)(1074.90909090909,-10.4090909090909)(1059.9797979798,-10.4545454545455)(1045.05050505051,-10.4545454545455)(1030.12121212121,-10.4545454545455)(1015.19191919192,-10.4545454545455)(1000.26262626263,-10.4545454545455)(985.333333333333,-10.4545454545455)(970.40404040404,-10.4545454545455)(955.474747474747,-10.3939393939394)(948.010101010101,-10.3636363636364)(940.545454545455,-10.3333333333333)(925.616161616162,-10.2121212121212)(910.686868686869,-10.2121212121212)(903.222222222222,-10.1818181818182)(895.757575757576,-10.1515151515152)(880.828282828283,-10.1515151515152)(865.89898989899,-10.0909090909091)(850.969696969697,-10.030303030303)(843.505050505051,-10)(836.040404040404,-9.96969696969697)(821.111111111111,-9.84848484848485)(817.378787878788,-9.81818181818182)(806.181818181818,-9.72727272727273)(798.717171717172,-9.63636363636364)(791.252525252525,-9.54545454545455)(783.787878787879,-9.45454545454546)(776.323232323232,-9.36363636363636)(765.126262626263,-9.27272727272727)(761.393939393939,-9.24242424242424)(746.464646464646,-9.12121212121212)(739,-9.09090909090909)(731.535353535354,-9.06060606060606)(716.606060606061,-9)(701.676767676768,-9)(686.747474747475,-9)(671.818181818182,-9)(656.888888888889,-9.06060606060606)(649.424242424242,-9.09090909090909)(641.959595959596,-9.12121212121212)(627.030303030303,-9.18181818181818)(612.10101010101,-9.18181818181818)(597.171717171717,-9.18181818181818)(582.242424242424,-9.24242424242424)(574.777777777778,-9.27272727272727)(567.313131313131,-9.3030303030303)(552.383838383838,-9.42424242424243)(537.454545454546,-9.42424242424243)(522.525252525253,-9.42424242424243)(507.59595959596,-9.36363636363636)(492.666666666667,-9.36363636363636)(477.737373737374,-9.36363636363636)(462.808080808081,-9.36363636363636)(447.878787878788,-9.3030303030303)(440.414141414141,-9.27272727272727)(432.949494949495,-9.24242424242424)(418.020202020202,-9.18181818181818)(403.090909090909,-9.18181818181818)(388.161616161616,-9.12121212121212)(380.69696969697,-9.09090909090909)(373.232323232323,-9.06060606060606)(358.30303030303,-9)(343.373737373737,-8.95454545454546)(328.444444444444,-8.95454545454546)(313.515151515152,-9.04545454545455)(306.050505050505,-9.09090909090909)(298.585858585859,-9.12121212121212)(283.656565656566,-9.18181818181818)(268.727272727273,-9.18181818181818)(253.79797979798,-9.18181818181818)(238.868686868687,-9.24242424242424)(223.939393939394,-9.24242424242424)(209.010101010101,-9.24242424242424)(194.080808080808,-9.18181818181818)(179.151515151515,-9.24242424242424)(164.222222222222,-9.18181818181818)(153.025252525253,-9.09090909090909)(149.292929292929,-9.06060606060606)(136.851851851852,-8.90909090909091)(134.363636363636,-8.88636363636364)(119.434343434343,-8.84090909090909)(104.505050505051,-8.79545454545455)(97.040404040404,-8.72727272727273)(89.5757575757576,-8.63636363636364)(82.1111111111111,-8.54545454545455)(74.6464646464647,-8.45454545454545)(67.1818181818182,-8.36363636363636)(59.7171717171717,-8.27272727272727)(52.2525252525253,-8.18181818181818)(44.7878787878788,-8.04545454545455)(42.2996632996633,-8)(37.3232323232323,-7.81818181818182)(42.2996632996633,-7.63636363636364)(44.7878787878788,-7.59090909090909)(52.2525252525253,-7.45454545454546)(59.7171717171717,-7.36363636363636)(70.9141414141414,-7.27272727272727)(74.6464646464647,-7.24242424242424)(89.5757575757576,-7.18181818181818)(104.505050505051,-7.18181818181818)(119.434343434343,-7.18181818181818)(134.363636363636,-7.18181818181818)(149.292929292929,-7.18181818181818)(164.222222222222,-7.18181818181818)(179.151515151515,-7.18181818181818)(194.080808080808,-7.18181818181818)(209.010101010101,-7.24242424242424)(216.474747474747,-7.27272727272727)(223.939393939394,-7.3030303030303)(238.868686868687,-7.36363636363636)(253.79797979798,-7.36363636363636)(268.727272727273,-7.42424242424243)(276.191919191919,-7.45454545454546)(283.656565656566,-7.48484848484849)(298.585858585859,-7.54545454545455)(313.515151515152,-7.54545454545455)(328.444444444444,-7.48484848484849)(335.909090909091,-7.45454545454546)(343.373737373737,-7.42424242424243)(358.30303030303,-7.36363636363636)(373.232323232323,-7.36363636363636)(388.161616161616,-7.3030303030303)(391.893939393939,-7.27272727272727)(403.090909090909,-7.18181818181818)(414.287878787879,-7.09090909090909)(418.020202020202,-7.06060606060606)(432.949494949495,-7)(447.878787878788,-6.93939393939394)(455.343434343434,-6.90909090909091)(462.808080808081,-6.87878787878788)(477.737373737374,-6.81818181818182)(492.666666666667,-6.81818181818182)(507.59595959596,-6.81818181818182)(522.525252525253,-6.81818181818182)(537.454545454546,-6.81818181818182)(552.383838383838,-6.81818181818182)(567.313131313131,-6.87878787878788)(574.777777777778,-6.90909090909091)(582.242424242424,-6.93939393939394)(597.171717171717,-7)(612.10101010101,-7.06060606060606)(627.030303030303,-7.06818181818182)(630.762626262626,-7.09090909090909)(641.959595959596,-7.18181818181818)(653.156565656566,-7.27272727272727)(656.888888888889,-7.3030303030303)(669.329966329966,-7.45454545454546)(671.818181818182,-7.48484848484849)(686.747474747475,-7.60606060606061)(690.479797979798,-7.63636363636364)(701.676767676768,-7.72727272727273)(712.873737373737,-7.81818181818182)(716.606060606061,-7.84848484848485)(731.535353535354,-7.90909090909091)(746.464646464646,-7.90909090909091)(761.393939393939,-7.90909090909091)(776.323232323232,-7.90909090909091)(791.252525252525,-7.84848484848485)(798.717171717172,-7.81818181818182)(806.181818181818,-7.78787878787879)(821.111111111111,-7.66666666666667)(828.575757575758,-7.63636363636364)(836.040404040404,-7.60606060606061)(850.969696969697,-7.48484848484849)(858.434343434343,-7.45454545454546)(865.89898989899,-7.42424242424243)(878.340067340067,-7.27272727272727)(880.828282828283,-7.24242424242424)(895.757575757576,-7.18181818181818)(910.686868686869,-7.12121212121212)(925.616161616162,-7.18181818181818)(940.545454545455,-7.12121212121212)(948.010101010101,-7.09090909090909)(955.474747474747,-7.06060606060606)(970.40404040404,-6.97727272727273)(985.333333333333,-6.97727272727273)(1000.26262626263,-6.97727272727273)(1015.19191919192,-7)(1030.12121212121,-7)(1045.05050505051,-7)(1059.9797979798,-7.06060606060606)(1067.44444444444,-7.09090909090909)(1074.90909090909,-7.12121212121212)(1089.83838383838,-7.18181818181818)(1104.76767676768,-7.18181818181818)(1119.69696969697,-7.18181818181818)(1134.62626262626,-7.18181818181818)(1149.55555555556,-7.24242424242424)(1157.0202020202,-7.27272727272727)(1164.48484848485,-7.3030303030303)(1179.41414141414,-7.36363636363636)(1194.34343434343,-7.36363636363636)(1209.27272727273,-7.36363636363636)(1224.20202020202,-7.36363636363636)(1239.13131313131,-7.36363636363636)(1254.06060606061,-7.34090909090909)(1268.9898989899,-7.34090909090909)(1283.91919191919,-7.34090909090909)(1298.84848484848,-7.36363636363636)(1313.77777777778,-7.36363636363636)(1328.70707070707,-7.42424242424243)(1336.17171717172,-7.45454545454546)(1343.63636363636,-7.48484848484849)(1358.56565656566,-7.60606060606061)(1366.0303030303,-7.63636363636364)(1373.49494949495,-7.66666666666667)(1388.42424242424,-7.78787878787879)(1395.88888888889,-7.81818181818182)(1403.35353535354,-7.84848484848485)(1418.28282828283,-7.96969696969697)(1422.01515151515,-8)(1433.21212121212,-8.09090909090909)(1440.67676767677,-8.18181818181818)(1448.14141414141,-8.27272727272727)(1455.60606060606,-8.36363636363636)(1463.07070707071,-8.5)(1465.55892255892,-8.54545454545455)(1470.53535353535,-8.72727272727273)(1470.53535353535,-8.90909090909091)(1478,-9.04545454545455)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-8.86363636363636)(1405.84175084175,-8.90909090909091)(1410.81818181818,-9.09090909090909)(1410.81818181818,-9.27272727272727)(1405.84175084175,-9.45454545454546)(1403.35353535354,-9.5)(1392.15656565657,-9.63636363636364)(1388.42424242424,-9.68181818181818)(1377.22727272727,-9.81818181818182)(1373.49494949495,-9.84848484848485)(1358.56565656566,-9.90909090909091)(1343.63636363636,-9.93181818181818)(1328.70707070707,-9.98181818181818)(1321.24242424242,-10)(1313.77777777778,-10.030303030303)(1298.84848484848,-10.0909090909091)(1283.91919191919,-10.1136363636364)(1268.9898989899,-10.1272727272727)(1254.06060606061,-10.1666666666667)(1239.13131313131,-10.1666666666667)(1224.20202020202,-10.1666666666667)(1209.27272727273,-10.1363636363636)(1194.34343434343,-10.1272727272727)(1179.41414141414,-10.1272727272727)(1164.48484848485,-10.1272727272727)(1149.55555555556,-10.1363636363636)(1134.62626262626,-10.1363636363636)(1119.69696969697,-10.1363636363636)(1104.76767676768,-10.1060606060606)(1089.83838383838,-10.1060606060606)(1074.90909090909,-10.1060606060606)(1059.9797979798,-10.1363636363636)(1045.05050505051,-10.1272727272727)(1030.12121212121,-10.1136363636364)(1015.19191919192,-10.0909090909091)(1000.26262626263,-10.0909090909091)(985.333333333333,-10.0909090909091)(970.40404040404,-10.030303030303)(962.939393939394,-10)(955.474747474747,-9.98484848484848)(940.545454545455,-9.94545454545455)(925.616161616162,-9.87272727272727)(914.419191919192,-9.81818181818182)(910.686868686869,-9.8)(895.757575757576,-9.75)(880.828282828283,-9.66666666666667)(877.09595959596,-9.63636363636364)(865.89898989899,-9.54545454545455)(858.434343434343,-9.45454545454546)(850.969696969697,-9.36363636363636)(843.505050505051,-9.27272727272727)(836.040404040404,-9.13636363636364)(833.552188552189,-9.09090909090909)(828.575757575758,-8.90909090909091)(833.552188552189,-8.72727272727273)(836.040404040404,-8.63636363636364)(837.906565656566,-8.54545454545455)(848.481481481482,-8.36363636363636)(850.969696969697,-8.31818181818182)(856.568181818182,-8.18181818181818)(865.89898989899,-8.06818181818182)(871.497474747475,-8)(880.828282828283,-7.88636363636364)(892.025252525252,-7.81818181818182)(895.757575757576,-7.78787878787879)(910.686868686869,-7.70454545454546)(925.616161616162,-7.65909090909091)(929.348484848485,-7.63636363636364)(940.545454545455,-7.56818181818182)(955.474747474747,-7.50909090909091)(970.40404040404,-7.47272727272727)(985.333333333333,-7.47272727272727)(1000.26262626263,-7.47272727272727)(1015.19191919192,-7.5)(1030.12121212121,-7.5)(1045.05050505051,-7.50909090909091)(1059.9797979798,-7.52272727272727)(1074.90909090909,-7.54545454545455)(1089.83838383838,-7.60606060606061)(1097.30303030303,-7.63636363636364)(1104.76767676768,-7.65151515151515)(1119.69696969697,-7.68181818181818)(1134.62626262626,-7.68181818181818)(1149.55555555556,-7.68181818181818)(1164.48484848485,-7.69090909090909)(1179.41414141414,-7.70454545454546)(1194.34343434343,-7.72727272727273)(1209.27272727273,-7.72727272727273)(1224.20202020202,-7.72727272727273)(1239.13131313131,-7.72727272727273)(1254.06060606061,-7.72727272727273)(1268.9898989899,-7.78787878787879)(1276.45454545455,-7.81818181818182)(1283.91919191919,-7.84090909090909)(1298.84848484848,-7.88636363636364)(1313.77777777778,-7.96969696969697)(1321.24242424242,-8)(1328.70707070707,-8.02272727272727)(1343.63636363636,-8.15151515151515)(1347.36868686869,-8.18181818181818)(1358.56565656566,-8.25)(1367.89646464646,-8.36363636363636)(1373.49494949495,-8.43181818181818)(1382.82575757576,-8.54545454545455)(1388.42424242424,-8.63636363636364)(1395.88888888889,-8.72727272727273)(1403.35353535354,-8.86363636363636)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1358.56565656566,-8.81818181818182)(1361.05387205387,-8.90909090909091)(1361.05387205387,-9.09090909090909)(1361.05387205387,-9.27272727272727)(1358.56565656566,-9.31818181818182)(1351.10101010101,-9.45454545454546)(1343.63636363636,-9.54545454545455)(1332.43939393939,-9.63636363636364)(1328.70707070707,-9.65454545454546)(1313.77777777778,-9.70454545454546)(1298.84848484848,-9.72727272727273)(1283.91919191919,-9.78787878787879)(1276.45454545455,-9.81818181818182)(1268.9898989899,-9.83333333333333)(1254.06060606061,-9.87272727272727)(1239.13131313131,-9.87272727272727)(1224.20202020202,-9.87272727272727)(1209.27272727273,-9.86363636363636)(1194.34343434343,-9.83333333333333)(1179.41414141414,-9.83333333333333)(1164.48484848485,-9.83333333333333)(1149.55555555556,-9.86363636363636)(1134.62626262626,-9.83636363636364)(1119.69696969697,-9.83636363636364)(1104.76767676768,-9.83333333333333)(1089.83838383838,-9.85714285714286)(1074.90909090909,-9.85714285714286)(1059.9797979798,-9.86363636363636)(1045.05050505051,-9.83333333333333)(1037.58585858586,-9.81818181818182)(1030.12121212121,-9.78787878787879)(1015.19191919192,-9.72727272727273)(1000.26262626263,-9.72727272727273)(985.333333333333,-9.72727272727273)(970.40404040404,-9.70454545454546)(955.474747474747,-9.69090909090909)(940.545454545455,-9.65151515151515)(936.813131313131,-9.63636363636364)(925.616161616162,-9.54545454545455)(914.419191919192,-9.45454545454546)(910.686868686869,-9.42424242424243)(895.757575757576,-9.36363636363636)(888.292929292929,-9.27272727272727)(880.828282828283,-9.18181818181818)(873.363636363636,-9.09090909090909)(865.89898989899,-8.95454545454546)(863.410774410775,-8.90909090909091)(864.032828282828,-8.72727272727273)(865.89898989899,-8.63636363636364)(868.387205387205,-8.54545454545455)(878.962121212121,-8.36363636363636)(880.828282828283,-8.33333333333333)(893.26936026936,-8.18181818181818)(895.757575757576,-8.15909090909091)(910.686868686869,-8.03030303030303)(925.616161616162,-8.03030303030303)(929.348484848485,-8)(940.545454545455,-7.93181818181818)(955.474747474747,-7.84848484848485)(962.939393939394,-7.81818181818182)(970.40404040404,-7.8)(985.333333333333,-7.8)(1000.26262626263,-7.8)(1015.19191919192,-7.77272727272727)(1030.12121212121,-7.77272727272727)(1045.05050505051,-7.8030303030303)(1052.51515151515,-7.81818181818182)(1059.9797979798,-7.86363636363636)(1074.90909090909,-7.95454545454546)(1089.83838383838,-7.96969696969697)(1104.76767676768,-7.94545454545455)(1119.69696969697,-7.95454545454546)(1134.62626262626,-7.95454545454546)(1149.55555555556,-7.95454545454546)(1164.48484848485,-7.98484848484848)(1171.94949494949,-8)(1179.41414141414,-8.03030303030303)(1194.34343434343,-8.09090909090909)(1209.27272727273,-8.09090909090909)(1224.20202020202,-8.09090909090909)(1239.13131313131,-8.13636363636364)(1254.06060606061,-8.15151515151515)(1268.9898989899,-8.15909090909091)(1283.91919191919,-8.16666666666667)(1291.38383838384,-8.18181818181818)(1298.84848484848,-8.21212121212121)(1313.77777777778,-8.34090909090909)(1321.24242424242,-8.36363636363636)(1328.70707070707,-8.39393939393939)(1343.63636363636,-8.52272727272727)(1346.12457912458,-8.54545454545455)(1356.07744107744,-8.72727272727273)(1358.56565656566,-8.81818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (492.666666666667,-7.95454545454546)(507.59595959596,-7.84090909090909)(515.060606060606,-7.81818181818182)(522.525252525253,-7.78787878787879)(529.989898989899,-7.81818181818182)(537.454545454546,-7.84090909090909)(552.383838383838,-7.90909090909091)(559.848484848485,-8)(567.313131313131,-8.13636363636364)(569.801346801347,-8.18181818181818)(567.313131313131,-8.27272727272727)(563.580808080808,-8.36363636363636)(552.383838383838,-8.45454545454545)(537.454545454546,-8.45454545454545)(522.525252525253,-8.45454545454545)(507.59595959596,-8.39393939393939)(503.863636363636,-8.36363636363636)(492.666666666667,-8.22727272727273)(488.934343434343,-8.18181818181818)(488.934343434343,-8)(492.666666666667,-7.95454545454546)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_160.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
% 
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.00005529347,-8.72727272727273)(1478.00011058654,-8.90909090909091)(1478.00027646327,-9.09090909090909)(1478.00027646327,-9.27272727272727)(1478.00027646327,-9.45454545454546)(1478.00016587919,-9.63636363636364)(1478.00011058654,-9.81818181818182)(1478.00005529347,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-9.06060606060606)(1478.00002764633,-9.09090909090909)(1478.00002764633,-9.27272727272727)(1478.00002764633,-9.45454545454546)(1478,-9.5)(1470.53535353535,-9.63636363636364)(1465.55892255892,-9.81818181818182)(1463.07070707071,-9.86363636363636)(1451.87373737374,-10)(1448.14141414141,-10.030303030303)(1433.21212121212,-10.1515151515152)(1425.74747474747,-10.1818181818182)(1418.28282828283,-10.2121212121212)(1403.35353535354,-10.2727272727273)(1388.42424242424,-10.3409090909091)(1380.9595959596,-10.3636363636364)(1373.49494949495,-10.3939393939394)(1358.56565656566,-10.4545454545455)(1343.63636363636,-10.4545454545455)(1328.70707070707,-10.4545454545455)(1313.77777777778,-10.4545454545455)(1298.84848484848,-10.4545454545455)(1283.91919191919,-10.4545454545455)(1268.9898989899,-10.4545454545455)(1254.06060606061,-10.4772727272727)(1239.13131313131,-10.4772727272727)(1224.20202020202,-10.4772727272727)(1209.27272727273,-10.4545454545455)(1194.34343434343,-10.4545454545455)(1179.41414141414,-10.4545454545455)(1164.48484848485,-10.4545454545455)(1149.55555555556,-10.4545454545455)(1134.62626262626,-10.4545454545455)(1119.69696969697,-10.4545454545455)(1104.76767676768,-10.4090909090909)(1089.83838383838,-10.4090909090909)(1074.90909090909,-10.4090909090909)(1059.9797979798,-10.4545454545455)(1045.05050505051,-10.4545454545455)(1030.12121212121,-10.4545454545455)(1015.19191919192,-10.4545454545455)(1000.26262626263,-10.4545454545455)(985.333333333333,-10.4545454545455)(970.40404040404,-10.3939393939394)(962.939393939394,-10.3636363636364)(955.474747474747,-10.3409090909091)(940.545454545455,-10.2727272727273)(925.616161616162,-10.2121212121212)(918.151515151515,-10.1818181818182)(910.686868686869,-10.1590909090909)(895.757575757576,-10.0909090909091)(880.828282828283,-10.0909090909091)(865.89898989899,-10.030303030303)(858.434343434343,-10)(850.969696969697,-9.96969696969697)(836.040404040404,-9.84848484848485)(828.575757575758,-9.81818181818182)(821.111111111111,-9.78787878787879)(806.181818181818,-9.66666666666667)(802.449494949495,-9.63636363636364)(791.252525252525,-9.54545454545455)(783.787878787879,-9.45454545454546)(776.323232323232,-9.36363636363636)(765.126262626263,-9.27272727272727)(761.393939393939,-9.24242424242424)(746.464646464646,-9.12121212121212)(742.732323232323,-9.09090909090909)(731.535353535354,-9.02272727272727)(716.606060606061,-8.93181818181818)(709.141414141414,-8.90909090909091)(701.676767676768,-8.87878787878788)(686.747474747475,-8.87878787878788)(679.282828282828,-8.90909090909091)(671.818181818182,-8.93939393939394)(656.888888888889,-9)(641.959595959596,-9.06060606060606)(634.494949494949,-9.09090909090909)(627.030303030303,-9.12121212121212)(612.10101010101,-9.18181818181818)(597.171717171717,-9.18181818181818)(582.242424242424,-9.24242424242424)(574.777777777778,-9.27272727272727)(567.313131313131,-9.3030303030303)(552.383838383838,-9.42424242424243)(537.454545454546,-9.42424242424243)(522.525252525253,-9.42424242424243)(507.59595959596,-9.42424242424243)(492.666666666667,-9.42424242424243)(477.737373737374,-9.42424242424243)(462.808080808081,-9.36363636363636)(447.878787878788,-9.3030303030303)(440.414141414141,-9.27272727272727)(432.949494949495,-9.24242424242424)(418.020202020202,-9.18181818181818)(403.090909090909,-9.12121212121212)(395.626262626263,-9.09090909090909)(388.161616161616,-9.04545454545455)(373.232323232323,-9)(358.30303030303,-9)(343.373737373737,-8.95454545454546)(328.444444444444,-8.95454545454546)(313.515151515152,-8.95454545454546)(298.585858585859,-9)(283.656565656566,-9.06060606060606)(268.727272727273,-9.06060606060606)(261.262626262626,-9.09090909090909)(253.79797979798,-9.12121212121212)(238.868686868687,-9.18181818181818)(223.939393939394,-9.24242424242424)(209.010101010101,-9.24242424242424)(194.080808080808,-9.18181818181818)(179.151515151515,-9.24242424242424)(164.222222222222,-9.18181818181818)(153.025252525253,-9.09090909090909)(149.292929292929,-9.06060606060606)(136.851851851852,-8.90909090909091)(134.363636363636,-8.88636363636364)(119.434343434343,-8.84090909090909)(104.505050505051,-8.79545454545455)(97.040404040404,-8.72727272727273)(89.5757575757576,-8.63636363636364)(82.1111111111111,-8.54545454545455)(74.6464646464647,-8.45454545454545)(67.1818181818182,-8.36363636363636)(59.7171717171717,-8.22727272727273)(57.2289562289562,-8.18181818181818)(52.2525252525253,-8)(52.2525252525253,-7.81818181818182)(57.2289562289562,-7.63636363636364)(59.7171717171717,-7.59090909090909)(70.9141414141414,-7.45454545454546)(74.6464646464647,-7.42424242424243)(89.5757575757576,-7.36363636363636)(104.505050505051,-7.3030303030303)(111.969696969697,-7.27272727272727)(119.434343434343,-7.24242424242424)(134.363636363636,-7.18181818181818)(149.292929292929,-7.18181818181818)(164.222222222222,-7.18181818181818)(179.151515151515,-7.24242424242424)(186.616161616162,-7.27272727272727)(194.080808080808,-7.29545454545455)(209.010101010101,-7.36363636363636)(223.939393939394,-7.36363636363636)(238.868686868687,-7.36363636363636)(253.79797979798,-7.36363636363636)(268.727272727273,-7.42424242424243)(276.191919191919,-7.45454545454546)(283.656565656566,-7.48484848484849)(298.585858585859,-7.54545454545455)(313.515151515152,-7.54545454545455)(328.444444444444,-7.48484848484849)(335.909090909091,-7.45454545454546)(343.373737373737,-7.42424242424243)(358.30303030303,-7.36363636363636)(373.232323232323,-7.36363636363636)(388.161616161616,-7.3030303030303)(395.626262626263,-7.27272727272727)(403.090909090909,-7.24242424242424)(418.020202020202,-7.12121212121212)(425.484848484849,-7.09090909090909)(432.949494949495,-7.06060606060606)(447.878787878788,-6.93939393939394)(455.343434343434,-6.90909090909091)(462.808080808081,-6.87878787878788)(477.737373737374,-6.81818181818182)(492.666666666667,-6.81818181818182)(507.59595959596,-6.81818181818182)(522.525252525253,-6.81818181818182)(537.454545454546,-6.81818181818182)(552.383838383838,-6.81818181818182)(567.313131313131,-6.87878787878788)(574.777777777778,-6.90909090909091)(582.242424242424,-6.93939393939394)(597.171717171717,-7)(612.10101010101,-7.06060606060606)(627.030303030303,-7.06818181818182)(630.762626262626,-7.09090909090909)(641.959595959596,-7.18181818181818)(653.156565656566,-7.27272727272727)(656.888888888889,-7.3030303030303)(669.329966329966,-7.45454545454546)(671.818181818182,-7.48484848484849)(684.259259259259,-7.63636363636364)(686.747474747475,-7.66666666666667)(701.676767676768,-7.78787878787879)(705.409090909091,-7.81818181818182)(716.606060606061,-7.90909090909091)(731.535353535354,-7.90909090909091)(746.464646464646,-7.90909090909091)(761.393939393939,-7.90909090909091)(776.323232323232,-7.90909090909091)(791.252525252525,-7.84848484848485)(798.717171717172,-7.81818181818182)(806.181818181818,-7.78787878787879)(821.111111111111,-7.66666666666667)(828.575757575758,-7.63636363636364)(836.040404040404,-7.60606060606061)(850.969696969697,-7.54545454545455)(865.89898989899,-7.48484848484849)(868.387205387205,-7.45454545454546)(880.828282828283,-7.3030303030303)(884.560606060606,-7.27272727272727)(895.757575757576,-7.18181818181818)(910.686868686869,-7.12121212121212)(925.616161616162,-7.18181818181818)(940.545454545455,-7.18181818181818)(955.474747474747,-7.12121212121212)(959.207070707071,-7.09090909090909)(970.40404040404,-7.02272727272727)(985.333333333333,-6.97727272727273)(1000.26262626263,-6.97727272727273)(1015.19191919192,-7.06060606060606)(1022.65656565657,-7.09090909090909)(1030.12121212121,-7.12121212121212)(1045.05050505051,-7.18181818181818)(1059.9797979798,-7.18181818181818)(1074.90909090909,-7.18181818181818)(1089.83838383838,-7.18181818181818)(1104.76767676768,-7.18181818181818)(1119.69696969697,-7.18181818181818)(1134.62626262626,-7.24242424242424)(1142.09090909091,-7.27272727272727)(1149.55555555556,-7.3030303030303)(1164.48484848485,-7.36363636363636)(1179.41414141414,-7.36363636363636)(1194.34343434343,-7.36363636363636)(1209.27272727273,-7.36363636363636)(1224.20202020202,-7.36363636363636)(1239.13131313131,-7.36363636363636)(1254.06060606061,-7.34090909090909)(1268.9898989899,-7.34090909090909)(1283.91919191919,-7.34090909090909)(1298.84848484848,-7.36363636363636)(1313.77777777778,-7.42424242424243)(1321.24242424242,-7.45454545454546)(1328.70707070707,-7.48484848484849)(1343.63636363636,-7.54545454545455)(1358.56565656566,-7.60606060606061)(1366.0303030303,-7.63636363636364)(1373.49494949495,-7.66666666666667)(1388.42424242424,-7.78787878787879)(1392.15656565657,-7.81818181818182)(1403.35353535354,-7.90909090909091)(1410.81818181818,-8)(1418.28282828283,-8.09090909090909)(1425.74747474747,-8.18181818181818)(1433.21212121212,-8.27272727272727)(1440.67676767677,-8.36363636363636)(1448.14141414141,-8.5)(1450.62962962963,-8.54545454545455)(1460.58249158249,-8.72727272727273)(1463.07070707071,-8.81818181818182)(1465.55892255892,-8.90909090909091)(1478,-9.06060606060606)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-8.86363636363636)(1405.84175084175,-8.90909090909091)(1410.81818181818,-9.09090909090909)(1410.81818181818,-9.27272727272727)(1405.84175084175,-9.45454545454546)(1403.35353535354,-9.5)(1395.88888888889,-9.63636363636364)(1388.42424242424,-9.77272727272727)(1384.69191919192,-9.81818181818182)(1373.49494949495,-9.90909090909091)(1358.56565656566,-9.96969696969697)(1343.63636363636,-9.96969696969697)(1336.17171717172,-10)(1328.70707070707,-10.030303030303)(1313.77777777778,-10.0909090909091)(1298.84848484848,-10.0909090909091)(1283.91919191919,-10.0909090909091)(1268.9898989899,-10.0909090909091)(1254.06060606061,-10.1515151515152)(1239.13131313131,-10.1515151515152)(1224.20202020202,-10.1515151515152)(1209.27272727273,-10.0909090909091)(1194.34343434343,-10.0909090909091)(1179.41414141414,-10.0909090909091)(1164.48484848485,-10.0909090909091)(1149.55555555556,-10.0909090909091)(1134.62626262626,-10.0909090909091)(1119.69696969697,-10.0909090909091)(1104.76767676768,-10.030303030303)(1089.83838383838,-10.030303030303)(1074.90909090909,-10.030303030303)(1059.9797979798,-10.0909090909091)(1045.05050505051,-10.0909090909091)(1030.12121212121,-10.0909090909091)(1015.19191919192,-10.0909090909091)(1000.26262626263,-10.0909090909091)(985.333333333333,-10.0909090909091)(970.40404040404,-10.0227272727273)(962.939393939394,-10)(955.474747474747,-9.97727272727273)(940.545454545455,-9.90909090909091)(925.616161616162,-9.84090909090909)(918.151515151515,-9.81818181818182)(910.686868686869,-9.79545454545455)(895.757575757576,-9.72727272727273)(880.828282828283,-9.66666666666667)(877.09595959596,-9.63636363636364)(865.89898989899,-9.54545454545455)(858.434343434343,-9.45454545454546)(850.969696969697,-9.36363636363636)(843.505050505051,-9.27272727272727)(836.040404040404,-9.13636363636364)(833.552188552189,-9.09090909090909)(828.575757575758,-8.90909090909091)(828.575757575758,-8.72727272727273)(833.552188552189,-8.54545454545455)(836.040404040404,-8.45454545454545)(838.528619528619,-8.36363636363636)(848.481481481482,-8.18181818181818)(850.969696969697,-8.13636363636364)(862.166666666667,-8)(865.89898989899,-7.96969696969697)(880.828282828283,-7.84848484848485)(888.292929292929,-7.81818181818182)(895.757575757576,-7.78787878787879)(910.686868686869,-7.65909090909091)(918.151515151515,-7.63636363636364)(925.616161616162,-7.60606060606061)(940.545454545455,-7.54545454545455)(955.474747474748,-7.52272727272727)(970.40404040404,-7.47727272727273)(985.333333333333,-7.47272727272727)(1000.26262626263,-7.47272727272727)(1015.19191919192,-7.5)(1030.12121212121,-7.50909090909091)(1045.05050505051,-7.52272727272727)(1059.9797979798,-7.54545454545455)(1074.90909090909,-7.54545454545455)(1089.83838383838,-7.60606060606061)(1097.30303030303,-7.63636363636364)(1104.76767676768,-7.65151515151515)(1119.69696969697,-7.68181818181818)(1134.62626262626,-7.69090909090909)(1149.55555555556,-7.70454545454546)(1164.48484848485,-7.72727272727273)(1179.41414141414,-7.72727272727273)(1194.34343434343,-7.72727272727273)(1209.27272727273,-7.72727272727273)(1224.20202020202,-7.72727272727273)(1239.13131313131,-7.72727272727273)(1254.06060606061,-7.72727272727273)(1268.9898989899,-7.78787878787879)(1276.45454545455,-7.81818181818182)(1283.91919191919,-7.86363636363636)(1298.84848484848,-7.90909090909091)(1313.77777777778,-7.96969696969697)(1321.24242424242,-8)(1328.70707070707,-8.03030303030303)(1343.63636363636,-8.15151515151515)(1347.36868686869,-8.18181818181818)(1358.56565656566,-8.27272727272727)(1366.0303030303,-8.36363636363636)(1373.49494949495,-8.45454545454545)(1380.9595959596,-8.54545454545455)(1388.42424242424,-8.63636363636364)(1395.88888888889,-8.72727272727273)(1403.35353535354,-8.86363636363636)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1343.63636363636,-8.86363636363636)(1346.12457912458,-8.90909090909091)(1351.10101010101,-9.09090909090909)(1346.12457912458,-9.27272727272727)(1343.63636363636,-9.31818181818182)(1332.43939393939,-9.45454545454546)(1328.70707070707,-9.48484848484848)(1313.77777777778,-9.60606060606061)(1306.31313131313,-9.63636363636364)(1298.84848484848,-9.66666666666667)(1283.91919191919,-9.72727272727273)(1268.9898989899,-9.68181818181818)(1254.06060606061,-9.68181818181818)(1239.13131313131,-9.68181818181818)(1224.20202020202,-9.72727272727273)(1209.27272727273,-9.72727272727273)(1194.34343434343,-9.72727272727273)(1179.41414141414,-9.72727272727273)(1164.48484848485,-9.72727272727273)(1149.55555555556,-9.72727272727273)(1134.62626262626,-9.66666666666667)(1119.69696969697,-9.66666666666667)(1104.76767676768,-9.66666666666667)(1089.83838383838,-9.72727272727273)(1074.90909090909,-9.72727272727273)(1059.9797979798,-9.72727272727273)(1045.05050505051,-9.72727272727273)(1030.12121212121,-9.72727272727273)(1015.19191919192,-9.72727272727273)(1000.26262626263,-9.72727272727273)(985.333333333333,-9.72727272727273)(970.40404040404,-9.65909090909091)(962.939393939394,-9.63636363636364)(955.474747474747,-9.60606060606061)(940.545454545455,-9.5)(933.080808080808,-9.45454545454546)(925.616161616162,-9.42424242424243)(910.686868686869,-9.36363636363636)(895.757575757576,-9.3030303030303)(892.025252525252,-9.27272727272727)(880.828282828283,-9.13636363636364)(878.340067340067,-9.09090909090909)(873.363636363636,-8.90909090909091)(873.363636363636,-8.72727272727273)(878.340067340067,-8.54545454545455)(880.828282828283,-8.5)(892.025252525252,-8.36363636363636)(895.757575757576,-8.31818181818182)(903.222222222222,-8.18181818181818)(910.686868686869,-8.09090909090909)(925.616161616162,-8.03030303030303)(933.080808080808,-8)(940.545454545455,-7.96969696969697)(955.474747474747,-7.90909090909091)(970.40404040404,-7.84848484848485)(977.868686868687,-7.81818181818182)(985.333333333333,-7.8)(1000.26262626263,-7.8)(1015.19191919192,-7.77272727272727)(1030.12121212121,-7.8030303030303)(1037.58585858586,-7.81818181818182)(1045.05050505051,-7.84848484848485)(1059.9797979798,-7.95454545454546)(1074.90909090909,-7.95454545454546)(1089.83838383838,-7.96969696969697)(1104.76767676768,-7.94545454545455)(1119.69696969697,-7.95454545454546)(1134.62626262626,-7.98484848484848)(1142.09090909091,-8)(1149.55555555556,-8.03030303030303)(1164.48484848485,-8.09090909090909)(1179.41414141414,-8.09090909090909)(1194.34343434343,-8.09090909090909)(1209.27272727273,-8.09090909090909)(1224.20202020202,-8.09090909090909)(1239.13131313131,-8.13636363636364)(1246.59595959596,-8.18181818181818)(1254.06060606061,-8.21212121212121)(1268.9898989899,-8.27272727272727)(1283.91919191919,-8.27272727272727)(1298.84848484848,-8.33333333333333)(1302.58080808081,-8.36363636363636)(1313.77777777778,-8.45454545454545)(1321.24242424242,-8.54545454545455)(1328.70707070707,-8.63636363636364)(1336.17171717172,-8.72727272727273)(1343.63636363636,-8.86363636363636)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (462.808080808081,-7.95454545454546)(474.005050505051,-7.81818181818182)(477.737373737374,-7.78787878787879)(492.666666666667,-7.72727272727273)(507.59595959596,-7.78787878787879)(522.525252525253,-7.72727272727273)(537.454545454546,-7.72727272727273)(552.383838383838,-7.66666666666667)(567.313131313131,-7.78787878787879)(571.045454545455,-7.81818181818182)(582.242424242424,-7.90909090909091)(589.707070707071,-8)(597.171717171717,-8.13636363636364)(599.659932659933,-8.18181818181818)(599.659932659933,-8.36363636363636)(597.171717171717,-8.40909090909091)(585.974747474747,-8.54545454545455)(582.242424242424,-8.57575757575757)(567.313131313131,-8.63636363636364)(552.383838383838,-8.6969696969697)(544.919191919192,-8.72727272727273)(537.454545454546,-8.75757575757576)(522.525252525253,-8.75757575757576)(515.060606060606,-8.72727272727273)(507.59595959596,-8.6969696969697)(492.666666666667,-8.57575757575757)(485.20202020202,-8.54545454545455)(477.737373737374,-8.52272727272727)(462.808080808081,-8.45454545454545)(455.343434343434,-8.36363636363636)(450.367003367003,-8.18181818181818)(460.319865319865,-8)(462.808080808081,-7.95454545454546)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_180.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.00005529347,-8.72727272727273)(1478.00011058654,-8.90909090909091)(1478.00016587919,-9.09090909090909)(1478.00016587919,-9.27272727272727)(1478.00016587919,-9.45454545454546)(1478.00016587919,-9.63636363636364)(1478.00011058654,-9.81818181818182)(1478.00005529347,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1463.07070707071,-8.86363636363636)(1465.55892255892,-8.90909090909091)(1470.53535353535,-9.09090909090909)(1470.53535353535,-9.27272727272727)(1470.53535353535,-9.45454545454546)(1470.53535353535,-9.63636363636364)(1465.55892255892,-9.81818181818182)(1463.07070707071,-9.86363636363636)(1451.87373737374,-10)(1448.14141414141,-10.030303030303)(1433.21212121212,-10.1515151515152)(1425.74747474747,-10.1818181818182)(1418.28282828283,-10.2121212121212)(1403.35353535354,-10.2727272727273)(1392.15656565657,-10.3636363636364)(1388.42424242424,-10.3939393939394)(1373.49494949495,-10.4545454545455)(1358.56565656566,-10.5151515151515)(1343.63636363636,-10.4545454545455)(1328.70707070707,-10.4545454545455)(1313.77777777778,-10.4545454545455)(1298.84848484848,-10.4545454545455)(1283.91919191919,-10.4545454545455)(1268.9898989899,-10.4545454545455)(1254.06060606061,-10.4772727272727)(1239.13131313131,-10.4772727272727)(1224.20202020202,-10.4772727272727)(1209.27272727273,-10.4545454545455)(1194.34343434343,-10.4545454545455)(1179.41414141414,-10.4545454545455)(1164.48484848485,-10.4545454545455)(1149.55555555556,-10.3939393939394)(1134.62626262626,-10.3939393939394)(1127.16161616162,-10.3636363636364)(1119.69696969697,-10.3484848484848)(1104.76767676768,-10.3181818181818)(1089.83838383838,-10.2878787878788)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3181818181818)(1045.05050505051,-10.3181818181818)(1030.12121212121,-10.3181818181818)(1015.19191919192,-10.3181818181818)(1000.26262626263,-10.3181818181818)(985.333333333333,-10.2878787878788)(970.40404040404,-10.2727272727273)(955.474747474748,-10.25)(940.545454545455,-10.2727272727273)(925.616161616162,-10.2121212121212)(918.151515151515,-10.1818181818182)(910.686868686869,-10.1590909090909)(895.757575757576,-10.0909090909091)(880.828282828283,-10.030303030303)(873.363636363636,-10)(865.89898989899,-9.97727272727273)(850.969696969697,-9.84848484848485)(843.505050505051,-9.81818181818182)(836.040404040404,-9.79545454545455)(821.111111111111,-9.66666666666667)(813.646464646465,-9.63636363636364)(806.181818181818,-9.60606060606061)(791.252525252525,-9.48484848484848)(787.520202020202,-9.45454545454546)(776.323232323232,-9.36363636363636)(768.858585858586,-9.27272727272727)(761.393939393939,-9.18181818181818)(753.929292929293,-9.09090909090909)(746.464646464646,-9)(731.535353535354,-8.93181818181818)(724.070707070707,-8.90909090909091)(716.606060606061,-8.87878787878788)(701.676767676768,-8.87878787878788)(686.747474747475,-8.81818181818182)(671.818181818182,-8.87878787878788)(664.353535353535,-8.90909090909091)(656.888888888889,-8.93939393939394)(641.959595959596,-9.06060606060606)(634.494949494949,-9.09090909090909)(627.030303030303,-9.12121212121212)(612.10101010101,-9.18181818181818)(597.171717171717,-9.18181818181818)(582.242424242424,-9.18181818181818)(567.313131313131,-9.24242424242424)(563.580808080808,-9.27272727272727)(552.383838383838,-9.36363636363636)(537.454545454546,-9.42424242424243)(522.525252525253,-9.42424242424243)(507.59595959596,-9.42424242424243)(492.666666666667,-9.42424242424243)(477.737373737374,-9.42424242424243)(462.808080808081,-9.36363636363636)(447.878787878788,-9.3030303030303)(440.414141414141,-9.27272727272727)(432.949494949495,-9.24242424242424)(418.020202020202,-9.18181818181818)(403.090909090909,-9.12121212121212)(395.626262626263,-9.09090909090909)(388.161616161616,-9.04545454545455)(373.232323232323,-9)(358.30303030303,-9)(343.373737373737,-8.95454545454546)(328.444444444444,-8.95454545454546)(313.515151515152,-8.95454545454546)(298.585858585859,-9)(283.656565656566,-9)(268.727272727273,-9)(253.79797979798,-9.06060606060606)(250.065656565657,-9.09090909090909)(238.868686868687,-9.18181818181818)(223.939393939394,-9.24242424242424)(209.010101010101,-9.24242424242424)(194.080808080808,-9.18181818181818)(179.151515151515,-9.24242424242424)(164.222222222222,-9.18181818181818)(153.025252525253,-9.09090909090909)(149.292929292929,-9.06060606060606)(136.851851851852,-8.90909090909091)(134.363636363636,-8.88636363636364)(119.434343434343,-8.88636363636364)(104.505050505051,-8.84090909090909)(92.0639730639731,-8.72727272727273)(89.5757575757576,-8.6969696969697)(80.2449494949495,-8.54545454545455)(74.6464646464647,-8.45454545454545)(67.1818181818182,-8.36363636363636)(59.7171717171717,-8.22727272727273)(57.2289562289562,-8.18181818181818)(57.2289562289562,-8)(59.7171717171717,-7.90909090909091)(62.2053872053872,-7.81818181818182)(74.6464646464647,-7.66666666666667)(78.3787878787879,-7.63636363636364)(89.5757575757576,-7.5)(97.040404040404,-7.45454545454546)(104.505050505051,-7.42424242424243)(119.434343434343,-7.36363636363636)(134.363636363636,-7.36363636363636)(149.292929292929,-7.36363636363636)(164.222222222222,-7.34090909090909)(179.151515151515,-7.34090909090909)(194.080808080808,-7.34090909090909)(209.010101010101,-7.36363636363636)(223.939393939394,-7.36363636363636)(238.868686868687,-7.36363636363636)(253.79797979798,-7.36363636363636)(268.727272727273,-7.42424242424243)(276.191919191919,-7.45454545454546)(283.656565656566,-7.47727272727273)(298.585858585859,-7.52272727272727)(313.515151515152,-7.54545454545455)(328.444444444444,-7.48484848484849)(335.909090909091,-7.45454545454546)(343.373737373737,-7.42424242424243)(358.30303030303,-7.36363636363636)(373.232323232323,-7.36363636363636)(388.161616161616,-7.3030303030303)(395.626262626263,-7.27272727272727)(403.090909090909,-7.24242424242424)(418.020202020202,-7.12121212121212)(425.484848484849,-7.09090909090909)(432.949494949495,-7.06060606060606)(447.878787878788,-7)(462.808080808081,-7)(477.737373737374,-7)(492.666666666667,-7)(507.59595959596,-6.97727272727273)(522.525252525253,-6.97727272727273)(537.454545454546,-6.97727272727273)(552.383838383838,-7)(567.313131313131,-7)(582.242424242424,-7)(597.171717171717,-7.06060606060606)(604.636363636364,-7.09090909090909)(612.10101010101,-7.12121212121212)(627.030303030303,-7.12121212121212)(641.959595959596,-7.18181818181818)(653.156565656566,-7.27272727272727)(656.888888888889,-7.3030303030303)(666.219696969697,-7.45454545454546)(671.818181818182,-7.54545454545455)(679.282828282828,-7.63636363636364)(686.747474747475,-7.72727272727273)(694.212121212121,-7.81818181818182)(701.676767676768,-7.90909090909091)(712.873737373737,-8)(716.606060606061,-8.03030303030303)(731.535353535354,-8.09090909090909)(746.464646464646,-8.13636363636364)(761.393939393939,-8.04545454545455)(768.858585858586,-8)(776.323232323232,-7.96969696969697)(791.252525252525,-7.90909090909091)(806.181818181818,-7.84848484848485)(809.914141414141,-7.81818181818182)(821.111111111111,-7.72727272727273)(832.308080808081,-7.63636363636364)(836.040404040404,-7.60606060606061)(850.969696969697,-7.54545454545455)(865.89898989899,-7.48484848484849)(868.387205387205,-7.45454545454546)(880.828282828283,-7.3030303030303)(884.560606060606,-7.27272727272727)(895.757575757576,-7.18181818181818)(910.686868686869,-7.12121212121212)(925.616161616162,-7.18181818181818)(940.545454545455,-7.18181818181818)(955.474747474747,-7.18181818181818)(970.40404040404,-7.12121212121212)(985.333333333333,-7.12121212121212)(1000.26262626263,-7.12121212121212)(1015.19191919192,-7.18181818181818)(1030.12121212121,-7.18181818181818)(1045.05050505051,-7.18181818181818)(1059.9797979798,-7.18181818181818)(1074.90909090909,-7.18181818181818)(1089.83838383838,-7.18181818181818)(1104.76767676768,-7.12121212121212)(1119.69696969697,-7.18181818181818)(1134.62626262626,-7.24242424242424)(1138.35858585859,-7.27272727272727)(1149.55555555556,-7.36363636363636)(1164.48484848485,-7.36363636363636)(1179.41414141414,-7.36363636363636)(1194.34343434343,-7.36363636363636)(1209.27272727273,-7.36363636363636)(1224.20202020202,-7.36363636363636)(1239.13131313131,-7.36363636363636)(1254.06060606061,-7.34090909090909)(1268.9898989899,-7.34090909090909)(1283.91919191919,-7.34090909090909)(1298.84848484848,-7.42424242424243)(1306.31313131313,-7.45454545454546)(1313.77777777778,-7.48484848484849)(1328.70707070707,-7.54545454545455)(1343.63636363636,-7.54545454545455)(1358.56565656566,-7.60606060606061)(1362.29797979798,-7.63636363636364)(1373.49494949495,-7.70454545454546)(1385.93602693603,-7.81818181818182)(1388.42424242424,-7.84848484848485)(1400.86531986532,-8)(1403.35353535354,-8.03030303030303)(1412.68434343434,-8.18181818181818)(1418.28282828283,-8.27272727272727)(1425.74747474747,-8.36363636363636)(1433.21212121212,-8.45454545454545)(1440.67676767677,-8.54545454545455)(1448.14141414141,-8.63636363636364)(1455.60606060606,-8.72727272727273)(1463.07070707071,-8.86363636363636)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-8.86363636363636)(1405.84175084175,-8.90909090909091)(1410.81818181818,-9.09090909090909)(1410.81818181818,-9.27272727272727)(1405.84175084175,-9.45454545454546)(1403.35353535354,-9.5)(1395.88888888889,-9.63636363636364)(1388.42424242424,-9.77272727272727)(1384.69191919192,-9.81818181818182)(1373.49494949495,-9.90909090909091)(1358.56565656566,-9.96969696969697)(1343.63636363636,-9.96969696969697)(1336.17171717172,-10)(1328.70707070707,-10.030303030303)(1313.77777777778,-10.0909090909091)(1298.84848484848,-10.0909090909091)(1283.91919191919,-10.0909090909091)(1268.9898989899,-10.0909090909091)(1254.06060606061,-10.1515151515152)(1239.13131313131,-10.1515151515152)(1224.20202020202,-10.1515151515152)(1209.27272727273,-10.0909090909091)(1194.34343434343,-10.0909090909091)(1179.41414141414,-10.0909090909091)(1164.48484848485,-10.0909090909091)(1149.55555555556,-10.0681818181818)(1134.62626262626,-10.0681818181818)(1119.69696969697,-10.0545454545455)(1104.76767676768,-10.0181818181818)(1089.83838383838,-10.0151515151515)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0454545454545)(1045.05050505051,-10.0454545454545)(1030.12121212121,-10.0454545454545)(1015.19191919192,-10.0454545454545)(1000.26262626263,-10.0454545454545)(985.333333333333,-10.0151515151515)(977.868686868687,-10)(970.40404040404,-9.97727272727273)(955.474747474748,-9.93181818181818)(940.545454545455,-9.90909090909091)(925.616161616162,-9.84090909090909)(918.151515151515,-9.81818181818182)(910.686868686869,-9.79545454545455)(895.757575757576,-9.72727272727273)(880.828282828283,-9.65909090909091)(873.363636363636,-9.63636363636364)(865.89898989899,-9.60606060606061)(850.969696969697,-9.47727272727273)(847.237373737374,-9.45454545454546)(836.040404040404,-9.31818181818182)(833.552188552189,-9.27272727272727)(823.599326599327,-9.09090909090909)(821.111111111111,-9)(818.622895622896,-8.90909090909091)(819.244949494949,-8.72727272727273)(821.111111111111,-8.63636363636364)(823.599326599327,-8.54545454545455)(833.552188552189,-8.36363636363636)(836.040404040404,-8.31818181818182)(843.505050505051,-8.18181818181818)(850.969696969697,-8.09090909090909)(862.166666666667,-8)(865.89898989899,-7.96969696969697)(880.828282828283,-7.84848484848485)(888.292929292929,-7.81818181818182)(895.757575757576,-7.78787878787879)(910.686868686869,-7.65909090909091)(918.151515151515,-7.63636363636364)(925.616161616162,-7.60606060606061)(940.545454545455,-7.54545454545455)(955.474747474747,-7.54545454545455)(970.40404040404,-7.5)(985.333333333333,-7.5)(1000.26262626263,-7.5)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.54545454545455)(1059.9797979798,-7.54545454545455)(1074.90909090909,-7.54545454545455)(1089.83838383838,-7.54545454545455)(1104.76767676768,-7.59090909090909)(1112.23232323232,-7.63636363636364)(1119.69696969697,-7.66666666666667)(1134.62626262626,-7.72727272727273)(1149.55555555556,-7.72727272727273)(1164.48484848485,-7.72727272727273)(1179.41414141414,-7.72727272727273)(1194.34343434343,-7.72727272727273)(1209.27272727273,-7.72727272727273)(1224.20202020202,-7.72727272727273)(1239.13131313131,-7.72727272727273)(1254.06060606061,-7.66666666666667)(1268.9898989899,-7.72727272727273)(1283.91919191919,-7.78787878787879)(1287.65151515152,-7.81818181818182)(1298.84848484848,-7.90909090909091)(1313.77777777778,-7.96969696969697)(1321.24242424242,-8)(1328.70707070707,-8.03030303030303)(1343.63636363636,-8.15151515151515)(1347.36868686869,-8.18181818181818)(1358.56565656566,-8.27272727272727)(1366.0303030303,-8.36363636363636)(1373.49494949495,-8.45454545454545)(1380.9595959596,-8.54545454545455)(1388.42424242424,-8.63636363636364)(1395.88888888889,-8.72727272727273)(1403.35353535354,-8.86363636363636)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1343.63636363636,-8.86363636363636)(1346.12457912458,-8.90909090909091)(1351.10101010101,-9.09090909090909)(1346.12457912458,-9.27272727272727)(1343.63636363636,-9.31818181818182)(1332.43939393939,-9.45454545454546)(1328.70707070707,-9.48484848484848)(1313.77777777778,-9.54545454545455)(1298.84848484848,-9.60606060606061)(1291.38383838384,-9.63636363636364)(1283.91919191919,-9.66666666666667)(1268.9898989899,-9.68181818181818)(1254.06060606061,-9.68181818181818)(1239.13131313131,-9.68181818181818)(1224.20202020202,-9.72727272727273)(1209.27272727273,-9.72727272727273)(1194.34343434343,-9.72727272727273)(1179.41414141414,-9.72727272727273)(1164.48484848485,-9.72727272727273)(1149.55555555556,-9.72727272727273)(1134.62626262626,-9.66666666666667)(1119.69696969697,-9.66666666666667)(1104.76767676768,-9.66666666666667)(1089.83838383838,-9.72727272727273)(1074.90909090909,-9.72727272727273)(1059.9797979798,-9.72727272727273)(1045.05050505051,-9.72727272727273)(1030.12121212121,-9.72727272727273)(1015.19191919192,-9.66666666666667)(1007.72727272727,-9.63636363636364)(1000.26262626263,-9.59090909090909)(985.333333333333,-9.5)(970.40404040404,-9.54545454545455)(955.474747474747,-9.54545454545455)(940.545454545455,-9.5)(933.080808080808,-9.45454545454546)(925.616161616162,-9.42424242424243)(910.686868686869,-9.36363636363636)(895.757575757576,-9.3030303030303)(892.025252525252,-9.27272727272727)(883.316498316498,-9.09090909090909)(880.828282828283,-9)(878.340067340067,-8.90909090909091)(878.340067340067,-8.72727272727273)(878.340067340067,-8.54545454545455)(880.828282828283,-8.5)(892.025252525252,-8.36363636363636)(895.757575757576,-8.31818181818182)(903.222222222222,-8.18181818181818)(910.686868686869,-8.09090909090909)(925.616161616162,-8.03030303030303)(933.080808080808,-8)(940.545454545455,-7.96969696969697)(955.474747474747,-7.96969696969697)(970.40404040404,-7.96969696969697)(985.333333333333,-7.96969696969697)(1000.26262626263,-7.96969696969697)(1015.19191919192,-7.90909090909091)(1030.12121212121,-7.90909090909091)(1045.05050505051,-7.90909090909091)(1059.9797979798,-7.95454545454546)(1074.90909090909,-7.95454545454546)(1082.37373737374,-8)(1089.83838383838,-8.03030303030303)(1104.76767676768,-8.03030303030303)(1119.69696969697,-8.09090909090909)(1134.62626262626,-8.09090909090909)(1149.55555555556,-8.15151515151515)(1164.48484848485,-8.15151515151515)(1179.41414141414,-8.15151515151515)(1194.34343434343,-8.09090909090909)(1209.27272727273,-8.09090909090909)(1224.20202020202,-8.15151515151515)(1227.93434343434,-8.18181818181818)(1239.13131313131,-8.27272727272727)(1254.06060606061,-8.33333333333333)(1268.9898989899,-8.33333333333333)(1283.91919191919,-8.33333333333333)(1291.38383838384,-8.36363636363636)(1298.84848484848,-8.39393939393939)(1313.77777777778,-8.51515151515152)(1317.5101010101,-8.54545454545455)(1328.70707070707,-8.63636363636364)(1336.17171717172,-8.72727272727273)(1343.63636363636,-8.86363636363636)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-8.04545454545455)(450.367003367003,-8)(462.808080808081,-7.84848484848485)(470.272727272727,-7.81818181818182)(477.737373737374,-7.78787878787879)(492.666666666667,-7.66666666666667)(507.59595959596,-7.72727272727273)(522.525252525253,-7.66666666666667)(537.454545454546,-7.66666666666667)(544.919191919192,-7.63636363636364)(552.383838383838,-7.60606060606061)(556.116161616162,-7.63636363636364)(567.313131313131,-7.72727272727273)(574.777777777778,-7.81818181818182)(582.242424242424,-7.90909090909091)(589.707070707071,-8)(597.171717171717,-8.13636363636364)(599.659932659933,-8.18181818181818)(599.659932659933,-8.36363636363636)(597.171717171717,-8.40909090909091)(585.974747474747,-8.54545454545455)(582.242424242424,-8.57575757575757)(567.313131313131,-8.63636363636364)(552.383838383838,-8.6969696969697)(544.919191919192,-8.72727272727273)(537.454545454546,-8.75757575757576)(522.525252525253,-8.75757575757576)(515.060606060606,-8.72727272727273)(507.59595959596,-8.6969696969697)(492.666666666667,-8.57575757575757)(485.20202020202,-8.54545454545455)(477.737373737374,-8.52272727272727)(462.808080808081,-8.47727272727273)(450.367003367003,-8.36363636363636)(447.878787878788,-8.31818181818182)(440.414141414141,-8.18181818181818)(447.878787878788,-8.04545454545455)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_20.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,3.30572501897308e-06)(283.656565656566,8.2640871684445e-06)(298.585858585859,1.32221788827669e-05)(313.515151515152,1.48748160261842e-05)(328.444444444444,1.48748160261842e-05)(343.373737373737,1.48748160261842e-05)(358.30303030303,1.48748160261842e-05)(373.232323232323,1.48748160261842e-05)(388.161616161616,1.48748160261842e-05)(403.090909090909,1.48748160261842e-05)(418.020202020202,1.48748160261842e-05)(432.949494949495,1.48748160261842e-05)(447.878787878788,1.48748160261842e-05)(462.808080808081,1.48748160261842e-05)(477.737373737374,1.48748160261842e-05)(492.666666666667,1.48748160261842e-05)(507.59595959596,1.48748160261842e-05)(522.525252525253,1.48748160261842e-05)(537.454545454546,1.48748160261842e-05)(552.383838383838,1.48748160261842e-05)(567.313131313131,1.48748160261842e-05)(582.242424242424,1.48748160261842e-05)(597.171717171717,1.48748160261842e-05)(612.10101010101,1.48748160261842e-05)(627.030303030303,1.48748160261842e-05)(641.959595959596,1.48748160261842e-05)(656.888888888889,9.91681445518895e-06)(671.818181818182,4.95854245421226e-06)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478.00040715143,-1.27272727272727)(1478.00081428065,-1.45454545454545)(1478.00122138767,-1.63636363636364)(1478.00122138767,-1.81818181818182)(1478.00122138767,-2)(1478.00122138767,-2.18181818181818)(1478.00122138767,-2.36363636363636)(1478.00122138767,-2.54545454545455)(1478.00122138767,-2.72727272727273)(1478.00122138767,-2.90909090909091)(1478.00122138767,-3.09090909090909)(1478.00081428065,-3.27272727272727)(1478.00040715143,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00054286364,-4.18181818181818)(1478.00054286364,-4.36363636363636)(1478.00054286364,-4.54545454545455)(1478.00040715143,-4.72727272727273)(1478.00081428065,-4.90909090909091)(1478.00122138767,-5.09090909090909)(1478.00122138767,-5.27272727272727)(1478.00122138767,-5.45454545454546)(1478.00122138767,-5.63636363636364)(1478.00122138767,-5.81818181818182)(1478.00122138767,-6)(1478.00122138767,-6.18181818181818)(1478.00122138767,-6.36363636363636)(1478.00122138767,-6.54545454545455)(1478.00122138767,-6.72727272727273)(1478.00122138767,-6.90909090909091)(1478.00122138767,-7.09090909090909)(1478.00122138767,-7.27272727272727)(1478.00122138767,-7.45454545454546)(1478.00122138767,-7.63636363636364)(1478.00122138767,-7.81818181818182)(1478.00122138767,-8)(1478.00122138767,-8.18181818181818)(1478.00122138767,-8.36363636363636)(1478.00122138767,-8.54545454545455)(1478.00122138767,-8.72727272727273)(1478.00122138767,-8.90909090909091)(1478.00122138767,-9.09090909090909)(1478.00122138767,-9.27272727272727)(1478.00122138767,-9.45454545454546)(1478.00122138767,-9.63636363636364)(1478.00122138767,-9.81818181818182)(1478.00122138767,-10)(1478.00122138767,-10.1818181818182)(1478.00122138767,-10.3636363636364)(1478.00122138767,-10.5454545454545)(1478.00149278002,-10.7272727272727)(1478.00149278002,-10.9090909090909)(1478.00149278002,-11.0909090909091)(1478.00122138767,-11.2727272727273)(1478.00122138767,-11.4545454545455)(1478.00122138767,-11.6363636363636)(1478.00122138767,-11.8181818181818)(1478.00122138767,-12)(1478.00122138767,-12.1818181818182)(1478.00122138767,-12.3636363636364)(1478.00122138767,-12.5454545454545)(1478.00122138767,-12.7272727272727)(1478.00122138767,-12.9090909090909)(1478.00122138767,-13.0909090909091)(1478.00081428065,-13.2727272727273)(1478.00040715143,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(-0.000407151430307532,-16.7272727272727)(-0.000814280653561821,-16.5454545454545)(-0.0012213876715861,-16.3636363636364)(-0.0012213876715861,-16.1818181818182)(-0.0012213876715861,-16)(-0.0012213876715861,-15.8181818181818)(-0.0012213876715861,-15.6363636363636)(-0.0012213876715861,-15.4545454545455)(-0.0012213876715861,-15.2727272727273)(-0.0012213876715861,-15.0909090909091)(-0.0012213876715861,-14.9090909090909)(-0.0012213876715861,-14.7272727272727)(-0.000814280653561821,-14.5454545454545)(-0.000407151430307532,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(-0.000407151430307532,-12.5454545454545)(-0.000814280653561821,-12.3636363636364)(-0.0012213876715861,-12.1818181818182)(-0.0012213876715861,-12)(-0.0012213876715861,-11.8181818181818)(-0.0012213876715861,-11.6363636363636)(-0.0012213876715861,-11.4545454545455)(-0.0012213876715861,-11.2727272727273)(-0.0012213876715861,-11.0909090909091)(-0.0012213876715861,-10.9090909090909)(-0.0012213876715861,-10.7272727272727)(-0.0012213876715861,-10.5454545454545)(-0.0012213876715861,-10.3636363636364)(-0.0012213876715861,-10.1818181818182)(-0.0012213876715861,-10)(-0.0012213876715861,-9.81818181818182)(-0.0012213876715861,-9.63636363636364)(-0.0012213876715861,-9.45454545454546)(-0.0012213876715861,-9.27272727272727)(-0.0012213876715861,-9.09090909090909)(-0.0012213876715861,-8.90909090909091)(-0.00149278001492805,-8.72727272727273)(-0.00149278001492805,-8.54545454545455)(-0.00149278001492805,-8.36363636363636)(-0.0012213876715861,-8.18181818181818)(-0.0012213876715861,-8)(-0.0012213876715861,-7.81818181818182)(-0.0012213876715861,-7.63636363636364)(-0.0012213876715861,-7.45454545454546)(-0.0012213876715861,-7.27272727272727)(-0.0012213876715861,-7.09090909090909)(-0.0012213876715861,-6.90909090909091)(-0.0012213876715861,-6.72727272727273)(-0.0012213876715861,-6.54545454545455)(-0.0012213876715861,-6.36363636363636)(-0.0012213876715861,-6.18181818181818)(-0.0012213876715861,-6)(-0.0012213876715861,-5.81818181818182)(-0.0012213876715861,-5.63636363636364)(-0.000814280653561821,-5.45454545454546)(-0.000407151430307532,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-5.36363636363636)(14.9292929292929,-5.36363636363636)(29.8585858585859,-5.36363636363636)(44.7878787878788,-5.3030303030303)(52.2525252525253,-5.27272727272727)(59.7171717171717,-5.24242424242424)(74.6464646464647,-5.18181818181818)(89.5757575757576,-5.18181818181818)(104.505050505051,-5.12121212121212)(111.969696969697,-5.09090909090909)(119.434343434343,-5.06060606060606)(134.363636363636,-4.93939393939394)(141.828282828283,-4.90909090909091)(149.292929292929,-4.87878787878788)(164.222222222222,-4.75757575757576)(167.954545454545,-4.72727272727273)(179.151515151515,-4.63636363636364)(190.348484848485,-4.54545454545455)(194.080808080808,-4.51515151515151)(209.010101010101,-4.39393939393939)(212.742424242424,-4.36363636363636)(223.939393939394,-4.27272727272727)(235.136363636364,-4.18181818181818)(238.868686868687,-4.15151515151515)(253.79797979798,-4.03030303030303)(261.262626262626,-4)(268.727272727273,-3.96969696969697)(283.656565656566,-3.84848484848485)(291.121212121212,-3.81818181818182)(298.585858585859,-3.78787878787879)(313.515151515152,-3.72727272727273)(328.444444444444,-3.72727272727273)(343.373737373737,-3.72727272727273)(358.30303030303,-3.72727272727273)(373.232323232323,-3.72727272727273)(388.161616161616,-3.72727272727273)(403.090909090909,-3.72727272727273)(418.020202020202,-3.72727272727273)(432.949494949495,-3.72727272727273)(447.878787878788,-3.72727272727273)(462.808080808081,-3.72727272727273)(477.737373737374,-3.72727272727273)(492.666666666667,-3.72727272727273)(507.59595959596,-3.72727272727273)(522.525252525253,-3.72727272727273)(537.454545454546,-3.72727272727273)(552.383838383838,-3.72727272727273)(567.313131313131,-3.72727272727273)(582.242424242424,-3.72727272727273)(597.171717171717,-3.72727272727273)(612.10101010101,-3.72727272727273)(627.030303030303,-3.72727272727273)(641.959595959596,-3.72727272727273)(656.888888888889,-3.72727272727273)(671.818181818182,-3.66666666666667)(679.282828282828,-3.63636363636364)(686.747474747475,-3.60606060606061)(701.676767676768,-3.54545454545455)(716.606060606061,-3.54545454545455)(731.535353535354,-3.54545454545455)(746.464646464646,-3.54545454545455)(761.393939393939,-3.60606060606061)(768.858585858586,-3.63636363636364)(776.323232323232,-3.66666666666667)(791.252525252525,-3.72727272727273)(806.181818181818,-3.72727272727273)(821.111111111111,-3.78787878787879)(828.575757575758,-3.81818181818182)(836.040404040404,-3.84848484848485)(850.969696969697,-3.96969696969697)(858.434343434343,-4)(865.89898989899,-4.03030303030303)(880.828282828283,-4.09090909090909)(895.757575757576,-4.15151515151515)(903.222222222222,-4.18181818181818)(910.686868686869,-4.21212121212121)(925.616161616162,-4.27272727272727)(940.545454545455,-4.27272727272727)(955.474747474747,-4.27272727272727)(970.40404040404,-4.27272727272727)(985.333333333333,-4.27272727272727)(1000.26262626263,-4.27272727272727)(1015.19191919192,-4.27272727272727)(1030.12121212121,-4.27272727272727)(1045.05050505051,-4.27272727272727)(1059.9797979798,-4.27272727272727)(1074.90909090909,-4.27272727272727)(1089.83838383838,-4.27272727272727)(1104.76767676768,-4.27272727272727)(1119.69696969697,-4.27272727272727)(1134.62626262626,-4.27272727272727)(1149.55555555556,-4.21212121212121)(1157.0202020202,-4.18181818181818)(1164.48484848485,-4.15151515151515)(1179.41414141414,-4.09090909090909)(1194.34343434343,-4.09090909090909)(1209.27272727273,-4.03030303030303)(1216.73737373737,-4)(1224.20202020202,-3.96969696969697)(1239.13131313131,-3.90909090909091)(1254.06060606061,-3.90909090909091)(1268.9898989899,-3.90909090909091)(1283.91919191919,-3.90909090909091)(1298.84848484848,-3.90909090909091)(1313.77777777778,-3.96969696969697)(1321.24242424242,-4)(1328.70707070707,-4.03030303030303)(1343.63636363636,-4.15151515151515)(1347.36868686869,-4.18181818181818)(1358.56565656566,-4.27272727272727)(1369.76262626263,-4.36363636363636)(1373.49494949495,-4.39393939393939)(1388.42424242424,-4.51515151515151)(1395.88888888889,-4.54545454545455)(1403.35353535354,-4.57575757575758)(1418.28282828283,-4.63636363636364)(1433.21212121212,-4.6969696969697)(1440.67676767677,-4.72727272727273)(1448.14141414141,-4.75757575757576)(1463.07070707071,-4.81818181818182)(1478,-4.81818181818182)(1478.00020357016,-4.90909090909091)(1478.00061069384,-5.09090909090909)(1478.00061069384,-5.27272727272727)(1478.00061069384,-5.45454545454546)(1478.00061069384,-5.63636363636364)(1478.00061069384,-5.81818181818182)(1478.00061069384,-6)(1478.00061069384,-6.18181818181818)(1478.00061069384,-6.36363636363636)(1478.00061069384,-6.54545454545455)(1478.00061069384,-6.72727272727273)(1478.00061069384,-6.90909090909091)(1478.00061069384,-7.09090909090909)(1478.00061069384,-7.27272727272727)(1478.00061069384,-7.45454545454546)(1478.00061069384,-7.63636363636364)(1478.00061069384,-7.81818181818182)(1478.00061069384,-8)(1478.00061069384,-8.18181818181818)(1478.00061069384,-8.36363636363636)(1478.00061069384,-8.54545454545455)(1478.00061069384,-8.72727272727273)(1478.00061069384,-8.90909090909091)(1478.00061069384,-9.09090909090909)(1478.00061069384,-9.27272727272727)(1478.00061069384,-9.45454545454546)(1478.00061069384,-9.63636363636364)(1478.00061069384,-9.81818181818182)(1478.00061069384,-10)(1478.00061069384,-10.1818181818182)(1478.00061069384,-10.3636363636364)(1478.00061069384,-10.5454545454545)(1478.00088209728,-10.7272727272727)(1478.00088209728,-10.9090909090909)(1478.00088209728,-11.0909090909091)(1478.00061069384,-11.2727272727273)(1478.00061069384,-11.4545454545455)(1478.00061069384,-11.6363636363636)(1478.00061069384,-11.8181818181818)(1478.00061069384,-12)(1478.00061069384,-12.1818181818182)(1478.00061069384,-12.3636363636364)(1478.00061069384,-12.5454545454545)(1478.00061069384,-12.7272727272727)(1478.00061069384,-12.9090909090909)(1478.00061069384,-13.0909090909091)(1478.00020357016,-13.2727272727273)(1478,-13.3636363636364)(1463.07070707071,-13.3636363636364)(1448.14141414141,-13.3636363636364)(1433.21212121212,-13.3636363636364)(1418.28282828283,-13.3636363636364)(1403.35353535354,-13.4242424242424)(1395.88888888889,-13.4545454545455)(1388.42424242424,-13.4848484848485)(1373.49494949495,-13.6060606060606)(1366.0303030303,-13.6363636363636)(1358.56565656566,-13.6666666666667)(1343.63636363636,-13.7878787878788)(1339.90404040404,-13.8181818181818)(1328.70707070707,-13.9090909090909)(1317.5101010101,-14)(1313.77777777778,-14.030303030303)(1298.84848484848,-14.1515151515152)(1295.11616161616,-14.1818181818182)(1283.91919191919,-14.3181818181818)(1281.43097643098,-14.3636363636364)(1271.47811447811,-14.5454545454545)(1268.9898989899,-14.6363636363636)(1266.50168350168,-14.7272727272727)(1256.54882154882,-14.9090909090909)(1254.06060606061,-15)(1251.57239057239,-15.0909090909091)(1246.59595959596,-15.2727272727273)(1241.61952861953,-15.4545454545455)(1239.13131313131,-15.5)(1231.66666666667,-15.6363636363636)(1224.20202020202,-15.7272727272727)(1213.00505050505,-15.8181818181818)(1209.27272727273,-15.8484848484848)(1194.34343434343,-15.9090909090909)(1179.41414141414,-15.9090909090909)(1164.48484848485,-15.9090909090909)(1149.55555555556,-15.9090909090909)(1134.62626262626,-15.8484848484848)(1127.16161616162,-15.8181818181818)(1119.69696969697,-15.7878787878788)(1104.76767676768,-15.6666666666667)(1097.30303030303,-15.6363636363636)(1089.83838383838,-15.6060606060606)(1077.39730639731,-15.4545454545455)(1074.90909090909,-15.4242424242424)(1062.46801346801,-15.2727272727273)(1059.9797979798,-15.2272727272727)(1052.51515151515,-15.0909090909091)(1045.05050505051,-15)(1037.58585858586,-14.9090909090909)(1030.12121212121,-14.8181818181818)(1022.65656565657,-14.7272727272727)(1015.19191919192,-14.6363636363636)(1003.99494949495,-14.5454545454545)(1000.26262626263,-14.5151515151515)(985.333333333333,-14.3939393939394)(981.60101010101,-14.3636363636364)(970.40404040404,-14.2727272727273)(959.207070707071,-14.1818181818182)(955.474747474747,-14.1515151515152)(940.545454545455,-14.030303030303)(933.080808080808,-14)(925.616161616162,-13.969696969697)(910.686868686869,-13.9090909090909)(895.757575757576,-13.8484848484849)(888.292929292929,-13.8181818181818)(880.828282828283,-13.7878787878788)(865.89898989899,-13.7272727272727)(850.969696969697,-13.7272727272727)(836.040404040404,-13.6666666666667)(828.575757575758,-13.6363636363636)(821.111111111111,-13.6060606060606)(806.181818181818,-13.5454545454545)(791.252525252525,-13.5454545454545)(776.323232323232,-13.5454545454545)(761.393939393939,-13.5454545454545)(746.464646464646,-13.5454545454545)(731.535353535354,-13.6060606060606)(724.070707070707,-13.6363636363636)(716.606060606061,-13.6666666666667)(701.676767676768,-13.7272727272727)(686.747474747475,-13.7272727272727)(671.818181818182,-13.7878787878788)(668.085858585859,-13.8181818181818)(656.888888888889,-13.9090909090909)(645.691919191919,-14)(641.959595959596,-14.030303030303)(627.030303030303,-14.1515151515152)(623.29797979798,-14.1818181818182)(612.10101010101,-14.2727272727273)(604.636363636364,-14.3636363636364)(597.171717171717,-14.5)(594.683501683502,-14.5454545454545)(584.73063973064,-14.7272727272727)(582.242424242424,-14.8181818181818)(579.754208754209,-14.9090909090909)(569.801346801347,-15.0909090909091)(567.313131313131,-15.1818181818182)(564.824915824916,-15.2727272727273)(559.848484848485,-15.4545454545455)(554.872053872054,-15.6363636363636)(552.383838383838,-15.7272727272727)(549.895622895623,-15.8181818181818)(539.942760942761,-16)(537.454545454546,-16.0454545454545)(529.989898989899,-16.1818181818182)(522.525252525253,-16.2727272727273)(511.328282828283,-16.3636363636364)(507.59595959596,-16.3939393939394)(492.666666666667,-16.5151515151515)(485.20202020202,-16.5454545454545)(477.737373737374,-16.5757575757576)(462.808080808081,-16.6969696969697)(459.075757575758,-16.7272727272727)(447.878787878788,-16.8181818181818)(436.681818181818,-16.9090909090909)(432.949494949495,-16.9393939393939)(418.020202020202,-17.0606060606061)(410.555555555556,-17.0909090909091)(403.090909090909,-17.1212121212121)(388.161616161616,-17.2424242424242)(384.429292929293,-17.2727272727273)(373.232323232323,-17.3636363636364)(362.035353535354,-17.4545454545455)(358.30303030303,-17.4848484848485)(343.373737373737,-17.6060606060606)(335.909090909091,-17.6363636363636)(328.444444444444,-17.6666666666667)(313.515151515152,-17.7272727272727)(298.585858585859,-17.7272727272727)(283.656565656566,-17.6666666666667)(276.191919191919,-17.6363636363636)(268.727272727273,-17.6060606060606)(253.79797979798,-17.4848484848485)(246.333333333333,-17.4545454545455)(238.868686868687,-17.4242424242424)(223.939393939394,-17.3030303030303)(216.474747474747,-17.2727272727273)(209.010101010101,-17.2424242424242)(194.080808080808,-17.1212121212121)(186.616161616162,-17.0909090909091)(179.151515151515,-17.0606060606061)(164.222222222222,-17)(149.292929292929,-16.9393939393939)(141.828282828283,-16.9090909090909)(134.363636363636,-16.8787878787879)(119.434343434343,-16.8181818181818)(104.505050505051,-16.7575757575758)(97.040404040404,-16.7272727272727)(89.5757575757576,-16.6969696969697)(74.6464646464647,-16.6363636363636)(59.7171717171717,-16.6363636363636)(44.7878787878788,-16.6363636363636)(29.8585858585859,-16.6363636363636)(14.9292929292929,-16.6363636363636)(0,-16.6363636363636)(-0.000203570163392941,-16.5454545454545)(-0.000610693835794708,-16.3636363636364)(-0.000610693835794708,-16.1818181818182)(-0.000610693835794708,-16)(-0.000610693835794708,-15.8181818181818)(-0.000610693835794708,-15.6363636363636)(-0.000610693835794708,-15.4545454545455)(-0.000610693835794708,-15.2727272727273)(-0.000610693835794708,-15.0909090909091)(-0.000610693835794708,-14.9090909090909)(-0.000610693835794708,-14.7272727272727)(-0.000203570163392941,-14.5454545454545)(0,-14.4545454545455)(14.9292929292929,-14.4545454545455)(29.8585858585859,-14.4545454545455)(44.7878787878788,-14.3939393939394)(52.2525252525253,-14.3636363636364)(59.7171717171717,-14.3333333333333)(74.6464646464647,-14.2727272727273)(89.5757575757576,-14.2121212121212)(93.3080808080808,-14.1818181818182)(104.505050505051,-14.0909090909091)(111.969696969697,-14)(119.434343434343,-13.9090909090909)(126.89898989899,-13.8181818181818)(134.363636363636,-13.6818181818182)(136.851851851852,-13.6363636363636)(141.828282828283,-13.4545454545455)(136.851851851852,-13.2727272727273)(134.363636363636,-13.2272727272727)(126.89898989899,-13.0909090909091)(119.434343434343,-13)(111.969696969697,-12.9090909090909)(104.505050505051,-12.8181818181818)(93.3080808080808,-12.7272727272727)(89.5757575757576,-12.6969696969697)(74.6464646464647,-12.6363636363636)(59.7171717171717,-12.5757575757576)(52.2525252525253,-12.5454545454545)(44.7878787878788,-12.5151515151515)(29.8585858585859,-12.4545454545455)(14.9292929292929,-12.4545454545455)(0,-12.4545454545455)(-0.000203570163392941,-12.3636363636364)(-0.000610693835794708,-12.1818181818182)(-0.000610693835794708,-12)(-0.000610693835794708,-11.8181818181818)(-0.000610693835794708,-11.6363636363636)(-0.000610693835794708,-11.4545454545455)(-0.000610693835794708,-11.2727272727273)(-0.000610693835794708,-11.0909090909091)(-0.000610693835794708,-10.9090909090909)(-0.000610693835794708,-10.7272727272727)(-0.000610693835794708,-10.5454545454545)(-0.000610693835794708,-10.3636363636364)(-0.000610693835794708,-10.1818181818182)(-0.000610693835794708,-10)(-0.000610693835794708,-9.81818181818182)(-0.000610693835794708,-9.63636363636364)(-0.000610693835794708,-9.45454545454546)(-0.000610693835794708,-9.27272727272727)(-0.000610693835794708,-9.09090909090909)(-0.000610693835794708,-8.90909090909091)(-0.000882097281547789,-8.72727272727273)(-0.000882097281547789,-8.54545454545455)(-0.000882097281547789,-8.36363636363636)(-0.000610693835794708,-8.18181818181818)(-0.000610693835794708,-8)(-0.000610693835794708,-7.81818181818182)(-0.000610693835794708,-7.63636363636364)(-0.000610693835794708,-7.45454545454546)(-0.000610693835794708,-7.27272727272727)(-0.000610693835794708,-7.09090909090909)(-0.000610693835794708,-6.90909090909091)(-0.000610693835794708,-6.72727272727273)(-0.000610693835794708,-6.54545454545455)(-0.000610693835794708,-6.36363636363636)(-0.000610693835794708,-6.18181818181818)(-0.000610693835794708,-6)(-0.000610693835794708,-5.81818181818182)(-0.000610693835794708,-5.63636363636364)(-0.000203570163392941,-5.45454545454546)(0,-5.36363636363636)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-1.36363636363636)(1478.00020357016,-1.45454545454545)(1478.00061069384,-1.63636363636364)(1478.00061069384,-1.81818181818182)(1478.00061069384,-2)(1478.00061069384,-2.18181818181818)(1478.00061069384,-2.36363636363636)(1478.00061069384,-2.54545454545455)(1478.00061069384,-2.72727272727273)(1478.00061069384,-2.90909090909091)(1478.00061069384,-3.09090909090909)(1478.00020357016,-3.27272727272727)(1478,-3.36363636363636)(1463.07070707071,-3.36363636363636)(1448.14141414141,-3.3030303030303)(1440.67676767677,-3.27272727272727)(1433.21212121212,-3.24242424242424)(1418.28282828283,-3.18181818181818)(1403.35353535354,-3.18181818181818)(1388.42424242424,-3.18181818181818)(1373.49494949495,-3.18181818181818)(1358.56565656566,-3.18181818181818)(1343.63636363636,-3.18181818181818)(1328.70707070707,-3.12121212121212)(1321.24242424242,-3.09090909090909)(1313.77777777778,-3.06060606060606)(1298.84848484848,-2.93939393939394)(1295.11616161616,-2.90909090909091)(1283.91919191919,-2.77272727272727)(1281.43097643098,-2.72727272727273)(1271.47811447811,-2.54545454545455)(1268.9898989899,-2.5)(1261.52525252525,-2.36363636363636)(1254.06060606061,-2.22727272727273)(1251.57239057239,-2.18181818181818)(1241.61952861953,-2)(1239.13131313131,-1.90909090909091)(1236.6430976431,-1.81818181818182)(1236.6430976431,-1.63636363636364)(1239.13131313131,-1.59090909090909)(1250.32828282828,-1.45454545454545)(1254.06060606061,-1.42424242424242)(1268.9898989899,-1.36363636363636)(1283.91919191919,-1.36363636363636)(1298.84848484848,-1.36363636363636)(1313.77777777778,-1.36363636363636)(1328.70707070707,-1.36363636363636)(1343.63636363636,-1.36363636363636)(1358.56565656566,-1.36363636363636)(1373.49494949495,-1.36363636363636)(1388.42424242424,-1.36363636363636)(1403.35353535354,-1.36363636363636)(1418.28282828283,-1.36363636363636)(1433.21212121212,-1.36363636363636)(1448.14141414141,-1.36363636363636)(1463.07070707071,-1.36363636363636)(1478,-1.36363636363636)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (283.656565656566,8.26408717619588e-07)(298.585858585859,5.78470326217944e-06)(313.515151515152,7.4374080130921e-06)(328.444444444444,7.4374080130921e-06)(343.373737373737,7.4374080130921e-06)(358.30303030303,7.4374080130921e-06)(373.232323232323,7.4374080130921e-06)(388.161616161616,7.4374080130921e-06)(403.090909090909,7.4374080130921e-06)(418.020202020202,7.4374080130921e-06)(432.949494949495,7.4374080130921e-06)(447.878787878788,7.4374080130921e-06)(462.808080808081,7.4374080130921e-06)(477.737373737374,7.4374080130921e-06)(492.666666666667,7.4374080130921e-06)(507.59595959596,7.4374080130921e-06)(522.525252525253,7.4374080130921e-06)(537.454545454546,7.4374080130921e-06)(552.383838383838,7.4374080130921e-06)(567.313131313131,7.4374080130921e-06)(582.242424242424,7.4374080130921e-06)(597.171717171717,7.4374080130921e-06)(612.10101010101,7.4374080130921e-06)(627.030303030303,7.4374080130921e-06)(641.959595959596,7.4374080130921e-06)(656.888888888889,2.47920361444319e-06)(664.353535353535,0)(659.377104377104,-0.181818181818183)(656.888888888889,-0.227272727272728)(649.424242424242,-0.363636363636363)(641.959595959596,-0.454545454545455)(634.494949494949,-0.545454545454547)(627.030303030303,-0.636363636363637)(615.833333333333,-0.727272727272727)(612.10101010101,-0.757575757575758)(597.171717171717,-0.818181818181818)(582.242424242424,-0.818181818181818)(567.313131313131,-0.878787878787879)(559.848484848485,-0.90909090909091)(552.383838383838,-0.939393939393941)(537.454545454546,-1)(522.525252525253,-1)(507.59595959596,-1)(492.666666666667,-1)(477.737373737374,-1)(462.808080808081,-1)(447.878787878788,-1)(432.949494949495,-1)(418.020202020202,-1)(403.090909090909,-1)(388.161616161616,-1)(373.232323232323,-1)(358.30303030303,-1)(343.373737373737,-0.939393939393941)(339.641414141414,-0.90909090909091)(328.444444444444,-0.818181818181818)(320.979797979798,-0.727272727272727)(313.515151515152,-0.590909090909092)(311.026936026936,-0.545454545454547)(301.074074074074,-0.363636363636363)(298.585858585859,-0.318181818181818)(291.121212121212,-0.181818181818183)(283.656565656566,-0.0454545454545459)(281.16835016835,0)(283.656565656566,8.26408717619588e-07)};

\addplot [fill=locol,draw=none,forget plot] coordinates{ (641.959595959596,-10.6363636363636)(634.494949494949,-10.7272727272727)(629.518518518518,-10.9090909090909)(638.227272727273,-11.0909090909091)(641.959595959596,-11.1212121212121)(656.888888888889,-11.2424242424242)(664.353535353535,-11.2727272727273)(671.818181818182,-11.3030303030303)(686.747474747475,-11.3030303030303)(694.212121212121,-11.2727272727273)(701.676767676768,-11.2424242424242)(716.606060606061,-11.1212121212121)(720.338383838384,-11.0909090909091)(731.535353535354,-10.9545454545455)(734.023569023569,-10.9090909090909)(731.535353535354,-10.8181818181818)(729.047138047138,-10.7272727272727)(716.606060606061,-10.5757575757576)(709.141414141414,-10.5454545454545)(701.676767676768,-10.5151515151515)(686.747474747475,-10.4545454545455)(671.818181818182,-10.4545454545455)(656.888888888889,-10.5151515151515)(653.156565656566,-10.5454545454545)(641.959595959596,-10.6363636363636)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_200.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478.00005529347,-8.90909090909091)(1478.00011058654,-9.09090909090909)(1478.00016587919,-9.27272727272727)(1478.00016587919,-9.45454545454546)(1478.00011058654,-9.63636363636364)(1478.00005529347,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1463.07070707071,-9.04545454545455)(1465.55892255892,-9.09090909090909)(1470.53535353535,-9.27272727272727)(1470.53535353535,-9.45454545454546)(1465.55892255892,-9.63636363636364)(1463.07070707071,-9.68181818181818)(1455.60606060606,-9.81818181818182)(1448.14141414141,-9.90909090909091)(1436.94444444444,-10)(1433.21212121212,-10.030303030303)(1418.28282828283,-10.1515151515152)(1410.81818181818,-10.1818181818182)(1403.35353535354,-10.2121212121212)(1390.91245791246,-10.3636363636364)(1388.42424242424,-10.3939393939394)(1373.49494949495,-10.3939393939394)(1358.56565656566,-10.3939393939394)(1354.83333333333,-10.3636363636364)(1343.63636363636,-10.2954545454545)(1328.70707070707,-10.3090909090909)(1313.77777777778,-10.3181818181818)(1298.84848484848,-10.3181818181818)(1283.91919191919,-10.3181818181818)(1268.9898989899,-10.3181818181818)(1254.06060606061,-10.3484848484848)(1239.13131313131,-10.3484848484848)(1224.20202020202,-10.3484848484848)(1209.27272727273,-10.3181818181818)(1194.34343434343,-10.3181818181818)(1179.41414141414,-10.3181818181818)(1164.48484848485,-10.3181818181818)(1149.55555555556,-10.3181818181818)(1134.62626262626,-10.3181818181818)(1119.69696969697,-10.3181818181818)(1104.76767676768,-10.2878787878788)(1089.83838383838,-10.2878787878788)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3181818181818)(1045.05050505051,-10.3181818181818)(1030.12121212121,-10.3181818181818)(1015.19191919192,-10.3181818181818)(1000.26262626263,-10.3181818181818)(985.333333333333,-10.2878787878788)(970.40404040404,-10.2727272727273)(955.474747474747,-10.2045454545455)(948.010101010101,-10.1818181818182)(940.545454545455,-10.1666666666667)(925.616161616162,-10.1272727272727)(910.686868686869,-10.1136363636364)(895.757575757576,-10.030303030303)(888.292929292929,-10)(880.828282828283,-9.98181818181818)(865.89898989899,-9.88636363636364)(854.70202020202,-9.81818181818182)(850.969696969697,-9.8)(836.040404040404,-9.70454545454546)(828.575757575758,-9.63636363636364)(821.111111111111,-9.56818181818182)(808.670033670034,-9.45454545454546)(806.181818181818,-9.42424242424243)(791.252525252525,-9.3030303030303)(787.520202020202,-9.27272727272727)(776.323232323232,-9.13636363636364)(773.835016835017,-9.09090909090909)(763.882154882155,-8.90909090909091)(761.393939393939,-8.81818181818182)(758.905723905724,-8.72727272727273)(758.905723905724,-8.54545454545455)(761.393939393939,-8.5)(772.590909090909,-8.36363636363636)(776.323232323232,-8.31818181818182)(783.787878787879,-8.18181818181818)(791.252525252525,-8.09090909090909)(798.717171717172,-8)(806.181818181818,-7.90909090909091)(817.378787878788,-7.81818181818182)(821.111111111111,-7.78787878787879)(836.040404040404,-7.66666666666667)(843.505050505051,-7.63636363636364)(850.969696969697,-7.60606060606061)(865.89898989899,-7.48484848484849)(868.387205387205,-7.45454545454546)(880.828282828283,-7.3030303030303)(888.292929292929,-7.27272727272727)(895.757575757576,-7.24242424242424)(910.686868686869,-7.18181818181818)(925.616161616162,-7.24242424242424)(940.545454545455,-7.18181818181818)(955.474747474747,-7.18181818181818)(970.40404040404,-7.12121212121212)(985.333333333333,-7.12121212121212)(1000.26262626263,-7.12121212121212)(1015.19191919192,-7.18181818181818)(1030.12121212121,-7.18181818181818)(1045.05050505051,-7.18181818181818)(1059.9797979798,-7.18181818181818)(1074.90909090909,-7.18181818181818)(1089.83838383838,-7.24242424242424)(1104.76767676768,-7.18181818181818)(1119.69696969697,-7.24242424242424)(1134.62626262626,-7.24242424242424)(1138.35858585859,-7.27272727272727)(1149.55555555556,-7.36363636363636)(1164.48484848485,-7.36363636363636)(1179.41414141414,-7.36363636363636)(1194.34343434343,-7.40909090909091)(1209.27272727273,-7.40909090909091)(1216.73737373737,-7.45454545454546)(1224.20202020202,-7.46969696969697)(1239.13131313131,-7.46969696969697)(1254.06060606061,-7.46969696969697)(1268.9898989899,-7.47272727272727)(1283.91919191919,-7.47727272727273)(1298.84848484848,-7.54545454545455)(1313.77777777778,-7.54545454545455)(1328.70707070707,-7.54545454545455)(1343.63636363636,-7.60606060606061)(1351.10101010101,-7.63636363636364)(1358.56565656566,-7.66666666666667)(1373.49494949495,-7.75)(1384.69191919192,-7.81818181818182)(1388.42424242424,-7.84848484848485)(1400.86531986532,-8)(1403.35353535354,-8.03030303030303)(1412.68434343434,-8.18181818181818)(1418.28282828283,-8.27272727272727)(1425.74747474747,-8.36363636363636)(1433.21212121212,-8.5)(1435.70033670034,-8.54545454545455)(1445.6531986532,-8.72727272727273)(1448.14141414141,-8.77272727272727)(1455.60606060606,-8.90909090909091)(1463.07070707071,-9.04545454545455)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-8.86363636363636)(1405.84175084175,-8.90909090909091)(1410.81818181818,-9.09090909090909)(1410.81818181818,-9.27272727272727)(1410.81818181818,-9.45454545454546)(1405.84175084175,-9.63636363636364)(1403.35353535354,-9.68181818181818)(1395.88888888889,-9.81818181818182)(1388.42424242424,-9.90909090909091)(1373.49494949495,-9.96969696969697)(1358.56565656566,-9.96969696969697)(1343.63636363636,-9.96969696969697)(1336.17171717172,-10)(1328.70707070707,-10.0151515151515)(1313.77777777778,-10.0454545454545)(1298.84848484848,-10.0454545454545)(1283.91919191919,-10.0454545454545)(1268.9898989899,-10.0454545454545)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.0757575757576)(1224.20202020202,-10.0757575757576)(1209.27272727273,-10.0454545454545)(1194.34343434343,-10.0454545454545)(1179.41414141414,-10.0454545454545)(1164.48484848485,-10.0454545454545)(1149.55555555556,-10.0454545454545)(1134.62626262626,-10.0454545454545)(1119.69696969697,-10.0454545454545)(1104.76767676768,-10.0151515151515)(1089.83838383838,-10.0151515151515)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0454545454545)(1045.05050505051,-10.0454545454545)(1030.12121212121,-10.0454545454545)(1015.19191919192,-10.0454545454545)(1000.26262626263,-10.0454545454545)(985.333333333333,-10.0151515151515)(977.868686868687,-10)(970.40404040404,-9.97727272727273)(955.474747474747,-9.90909090909091)(940.545454545455,-9.87272727272727)(925.616161616162,-9.83333333333333)(918.151515151515,-9.81818181818182)(910.686868686869,-9.78787878787879)(895.757575757576,-9.70454545454546)(880.828282828283,-9.65454545454546)(877.09595959596,-9.63636363636364)(865.89898989899,-9.56818181818182)(850.969696969697,-9.47272727272727)(848.481481481482,-9.45454545454546)(836.040404040404,-9.3030303030303)(834.174242424242,-9.27272727272727)(823.599326599327,-9.09090909090909)(821.111111111111,-9)(818.622895622896,-8.90909090909091)(819.244949494949,-8.72727272727273)(819.244949494949,-8.54545454545455)(821.111111111111,-8.5)(828.575757575758,-8.36363636363636)(836.040404040404,-8.22727272727273)(839.772727272727,-8.18181818181818)(850.969696969697,-8.09090909090909)(862.166666666667,-8)(865.89898989899,-7.96969696969697)(880.828282828283,-7.84848484848485)(888.292929292929,-7.81818181818182)(895.757575757576,-7.78787878787879)(910.686868686869,-7.66666666666667)(918.151515151515,-7.63636363636364)(925.616161616162,-7.61363636363636)(940.545454545455,-7.54545454545455)(955.474747474747,-7.54545454545455)(970.40404040404,-7.5)(985.333333333333,-7.5)(1000.26262626263,-7.5)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.54545454545455)(1059.9797979798,-7.54545454545455)(1074.90909090909,-7.54545454545455)(1089.83838383838,-7.56818181818182)(1104.76767676768,-7.60606060606061)(1112.23232323232,-7.63636363636364)(1119.69696969697,-7.66666666666667)(1134.62626262626,-7.72727272727273)(1149.55555555556,-7.72727272727273)(1164.48484848485,-7.72727272727273)(1179.41414141414,-7.72727272727273)(1194.34343434343,-7.78787878787879)(1209.27272727273,-7.78787878787879)(1224.20202020202,-7.79545454545455)(1239.13131313131,-7.76363636363636)(1254.06060606061,-7.74242424242424)(1268.9898989899,-7.77272727272727)(1283.91919191919,-7.8030303030303)(1287.65151515152,-7.81818181818182)(1298.84848484848,-7.90909090909091)(1313.77777777778,-7.90909090909091)(1328.70707070707,-7.96969696969697)(1332.43939393939,-8)(1343.63636363636,-8.09090909090909)(1354.83333333333,-8.18181818181818)(1358.56565656566,-8.21212121212121)(1371.00673400673,-8.36363636363636)(1373.49494949495,-8.39393939393939)(1385.93602693603,-8.54545454545455)(1388.42424242424,-8.59090909090909)(1395.88888888889,-8.72727272727273)(1403.35353535354,-8.86363636363636)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-7.95454545454546)(85.8434343434344,-7.81818181818182)(89.5757575757576,-7.78787878787879)(104.505050505051,-7.66666666666667)(106.993265993266,-7.63636363636364)(116.946127946128,-7.45454545454546)(119.434343434343,-7.42424242424243)(134.363636363636,-7.36363636363636)(149.292929292929,-7.3030303030303)(164.222222222222,-7.34090909090909)(179.151515151515,-7.34090909090909)(194.080808080808,-7.34090909090909)(209.010101010101,-7.36363636363636)(223.939393939394,-7.42424242424243)(231.40404040404,-7.45454545454546)(238.868686868687,-7.48484848484849)(253.79797979798,-7.54545454545455)(268.727272727273,-7.52272727272727)(283.656565656566,-7.52272727272727)(298.585858585859,-7.52272727272727)(313.515151515152,-7.54545454545455)(328.444444444444,-7.54545454545455)(343.373737373737,-7.54545454545455)(358.30303030303,-7.54545454545455)(373.232323232323,-7.52272727272727)(388.161616161616,-7.47727272727273)(395.626262626263,-7.45454545454546)(403.090909090909,-7.42424242424243)(418.020202020202,-7.3030303030303)(425.484848484849,-7.27272727272727)(432.949494949495,-7.24242424242424)(447.878787878788,-7.18181818181818)(462.808080808081,-7.18181818181818)(477.737373737374,-7.12121212121212)(485.20202020202,-7.09090909090909)(492.666666666667,-7.06060606060606)(507.59595959596,-6.97727272727273)(522.525252525253,-6.97727272727273)(537.454545454546,-7.02272727272727)(548.651515151515,-7.09090909090909)(552.383838383838,-7.12121212121212)(567.313131313131,-7.18181818181818)(582.242424242424,-7.18181818181818)(597.171717171717,-7.24242424242424)(604.636363636364,-7.27272727272727)(612.10101010101,-7.3030303030303)(627.030303030303,-7.3030303030303)(641.959595959596,-7.40909090909091)(645.691919191919,-7.45454545454546)(644.447811447811,-7.63636363636364)(656.888888888889,-7.78787878787879)(660.621212121212,-7.81818181818182)(671.818181818182,-7.90909090909091)(679.282828282828,-8)(686.747474747475,-8.13636363636364)(689.23569023569,-8.18181818181818)(689.23569023569,-8.36363636363636)(686.747474747475,-8.40909090909091)(675.550505050505,-8.54545454545455)(671.818181818182,-8.59090909090909)(664.353535353535,-8.72727272727273)(656.888888888889,-8.81818181818182)(645.691919191919,-8.90909090909091)(641.959595959596,-8.93939393939394)(627.030303030303,-9)(612.10101010101,-9.06060606060606)(604.636363636364,-9.09090909090909)(597.171717171717,-9.12121212121212)(582.242424242424,-9.18181818181818)(567.313131313131,-9.18181818181818)(556.116161616162,-9.27272727272727)(552.383838383838,-9.3030303030303)(537.454545454546,-9.36363636363636)(522.525252525253,-9.42424242424243)(507.59595959596,-9.42424242424243)(492.666666666667,-9.36363636363636)(477.737373737374,-9.3030303030303)(474.005050505051,-9.27272727272727)(462.808080808081,-9.18181818181818)(447.878787878788,-9.12121212121212)(440.414141414141,-9.09090909090909)(432.949494949495,-9.06060606060606)(420.508417508418,-8.90909090909091)(418.020202020202,-8.87878787878788)(403.090909090909,-8.81818181818182)(388.161616161616,-8.75757575757576)(373.232323232323,-8.81818181818182)(358.30303030303,-8.81818181818182)(343.373737373737,-8.75757575757576)(328.444444444444,-8.75757575757576)(313.515151515152,-8.79545454545455)(298.585858585859,-8.88636363636364)(291.121212121212,-8.90909090909091)(283.656565656566,-8.93939393939394)(268.727272727273,-9)(253.79797979798,-9)(242.60101010101,-9.09090909090909)(238.868686868687,-9.12121212121212)(223.939393939394,-9.18181818181818)(209.010101010101,-9.24242424242424)(194.080808080808,-9.24242424242424)(186.616161616162,-9.27272727272727)(179.151515151515,-9.29090909090909)(171.686868686869,-9.27272727272727)(164.222222222222,-9.24242424242424)(151.781144781145,-9.09090909090909)(149.292929292929,-9.06060606060606)(136.851851851852,-8.90909090909091)(134.363636363636,-8.88636363636364)(119.434343434343,-8.88636363636364)(104.505050505051,-8.84090909090909)(92.0639730639731,-8.72727272727273)(89.5757575757576,-8.6969696969697)(80.2449494949495,-8.54545454545455)(74.6464646464647,-8.40909090909091)(72.1582491582492,-8.36363636363636)(67.1818181818182,-8.18181818181818)(72.1582491582492,-8)(74.6464646464647,-7.95454545454546)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1313.77777777778,-9)(1316.26599326599,-9.09090909090909)(1313.77777777778,-9.13636363636364)(1302.58080808081,-9.27272727272727)(1298.84848484848,-9.3030303030303)(1283.91919191919,-9.36363636363636)(1268.9898989899,-9.36363636363636)(1254.06060606061,-9.42424242424243)(1246.59595959596,-9.45454545454546)(1239.13131313131,-9.48484848484848)(1224.20202020202,-9.54545454545455)(1209.27272727273,-9.5)(1194.34343434343,-9.5)(1179.41414141414,-9.5)(1164.48484848485,-9.54545454545455)(1149.55555555556,-9.54545454545455)(1134.62626262626,-9.54545454545455)(1119.69696969697,-9.54545454545455)(1104.76767676768,-9.54545454545455)(1089.83838383838,-9.48484848484848)(1074.90909090909,-9.48484848484848)(1059.9797979798,-9.48484848484848)(1045.05050505051,-9.54545454545455)(1030.12121212121,-9.54545454545455)(1015.19191919192,-9.5)(1000.26262626263,-9.5)(985.333333333333,-9.5)(970.40404040404,-9.54545454545455)(955.474747474747,-9.48484848484848)(951.742424242424,-9.45454545454546)(940.545454545455,-9.36363636363636)(929.348484848485,-9.27272727272727)(925.616161616162,-9.24242424242424)(910.686868686869,-9.12121212121212)(906.954545454546,-9.09090909090909)(895.757575757576,-8.95454545454546)(893.26936026936,-8.90909090909091)(892.025252525252,-8.72727272727273)(895.757575757576,-8.63636363636364)(898.245791245791,-8.54545454545455)(908.198653198653,-8.36363636363636)(910.686868686869,-8.31818181818182)(921.883838383838,-8.18181818181818)(925.616161616162,-8.15151515151515)(940.545454545455,-8.03030303030303)(948.010101010101,-8)(955.474747474747,-7.96969696969697)(970.40404040404,-7.96969696969697)(985.333333333333,-7.96969696969697)(992.79797979798,-8)(1000.26262626263,-8.03030303030303)(1007.72727272727,-8)(1015.19191919192,-7.96969696969697)(1030.12121212121,-7.96969696969697)(1045.05050505051,-7.90909090909091)(1059.9797979798,-7.95454545454546)(1067.44444444444,-8)(1074.90909090909,-8.03030303030303)(1089.83838383838,-8.09090909090909)(1104.76767676768,-8.09090909090909)(1119.69696969697,-8.09090909090909)(1134.62626262626,-8.15151515151515)(1142.09090909091,-8.18181818181818)(1149.55555555556,-8.22727272727273)(1164.48484848485,-8.31818181818182)(1179.41414141414,-8.31818181818182)(1194.34343434343,-8.27272727272727)(1209.27272727273,-8.27272727272727)(1224.20202020202,-8.27272727272727)(1239.13131313131,-8.33333333333333)(1246.59595959596,-8.36363636363636)(1254.06060606061,-8.39393939393939)(1268.9898989899,-8.45454545454545)(1280.18686868687,-8.54545454545455)(1283.91919191919,-8.57575757575757)(1298.84848484848,-8.6969696969697)(1301.3367003367,-8.72727272727273)(1311.28956228956,-8.90909090909091)(1313.77777777778,-9)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-8.04545454545455)(450.367003367003,-8)(462.808080808081,-7.88636363636364)(474.005050505051,-7.81818181818182)(477.737373737374,-7.78787878787879)(492.666666666667,-7.66666666666667)(507.59595959596,-7.72727272727273)(522.525252525253,-7.66666666666667)(537.454545454546,-7.66666666666667)(544.919191919192,-7.63636363636364)(552.383838383838,-7.60606060606061)(556.116161616162,-7.63636363636364)(567.313131313131,-7.72727272727273)(574.777777777778,-7.81818181818182)(582.242424242424,-7.90909090909091)(589.707070707071,-8)(597.171717171717,-8.13636363636364)(599.659932659933,-8.18181818181818)(600.90404040404,-8.36363636363636)(597.171717171717,-8.40909090909091)(585.974747474747,-8.54545454545455)(582.242424242424,-8.57575757575757)(567.313131313131,-8.63636363636364)(552.383838383838,-8.6969696969697)(544.919191919192,-8.72727272727273)(537.454545454546,-8.75757575757576)(522.525252525253,-8.75757575757576)(515.060606060606,-8.72727272727273)(507.59595959596,-8.6969696969697)(492.666666666667,-8.57575757575757)(485.20202020202,-8.54545454545455)(477.737373737374,-8.52272727272727)(462.808080808081,-8.47727272727273)(450.367003367003,-8.36363636363636)(447.878787878788,-8.31818181818182)(440.414141414141,-8.18181818181818)(447.878787878788,-8.04545454545455)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_220.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478.00005529347,-9.09090909090909)(1478.00011058654,-9.27272727272727)(1478.00011058654,-9.45454545454546)(1478.00005529347,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1463.07070707071,-9.18181818181818)(1465.55892255892,-9.27272727272727)(1465.55892255892,-9.45454545454546)(1463.07070707071,-9.54545454545455)(1460.58249158249,-9.63636363636364)(1448.14141414141,-9.78787878787879)(1445.6531986532,-9.81818181818182)(1433.21212121212,-9.96969696969697)(1429.4797979798,-10)(1418.28282828283,-10.0909090909091)(1407.08585858586,-10.1818181818182)(1403.35353535354,-10.2121212121212)(1390.91245791246,-10.3636363636364)(1388.42424242424,-10.3939393939394)(1373.49494949495,-10.3939393939394)(1358.56565656566,-10.3939393939394)(1354.83333333333,-10.3636363636364)(1343.63636363636,-10.2954545454545)(1328.70707070707,-10.3090909090909)(1313.77777777778,-10.3181818181818)(1298.84848484848,-10.3181818181818)(1283.91919191919,-10.3181818181818)(1268.9898989899,-10.3181818181818)(1254.06060606061,-10.3484848484848)(1239.13131313131,-10.3484848484848)(1224.20202020202,-10.3484848484848)(1209.27272727273,-10.3181818181818)(1194.34343434343,-10.3181818181818)(1179.41414141414,-10.3484848484848)(1164.48484848485,-10.3484848484848)(1149.55555555556,-10.3484848484848)(1134.62626262626,-10.3181818181818)(1119.69696969697,-10.3181818181818)(1104.76767676768,-10.2878787878788)(1089.83838383838,-10.2878787878788)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1045.05050505051,-10.3484848484848)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.3181818181818)(1000.26262626263,-10.3181818181818)(985.333333333333,-10.2878787878788)(970.40404040404,-10.2363636363636)(962.939393939394,-10.1818181818182)(955.474747474747,-10.1363636363636)(940.545454545455,-10.1060606060606)(925.616161616162,-10.0909090909091)(910.686868686869,-10.0681818181818)(899.489898989899,-10)(895.757575757576,-9.98484848484848)(880.828282828283,-9.94545454545455)(865.89898989899,-9.88636363636364)(854.70202020202,-9.81818181818182)(850.969696969697,-9.8)(836.040404040404,-9.70454545454546)(828.575757575758,-9.63636363636364)(821.111111111111,-9.56818181818182)(808.670033670034,-9.45454545454546)(806.181818181818,-9.43181818181818)(793.118686868687,-9.27272727272727)(791.252525252525,-9.24242424242424)(778.811447811448,-9.09090909090909)(776.323232323232,-9)(773.835016835017,-8.90909090909091)(772.590909090909,-8.72727272727273)(772.590909090909,-8.54545454545455)(776.323232323232,-8.45454545454545)(778.811447811448,-8.36363636363636)(783.787878787879,-8.18181818181818)(791.252525252525,-8.09090909090909)(798.717171717172,-8)(806.181818181818,-7.90909090909091)(817.378787878788,-7.81818181818182)(821.111111111111,-7.78787878787879)(836.040404040404,-7.66666666666667)(843.505050505051,-7.63636363636364)(850.969696969697,-7.60606060606061)(865.89898989899,-7.47727272727273)(868.387205387205,-7.45454545454546)(880.828282828283,-7.3030303030303)(888.292929292929,-7.27272727272727)(895.757575757576,-7.24242424242424)(910.686868686869,-7.24242424242424)(918.151515151515,-7.27272727272727)(925.616161616162,-7.29090909090909)(933.080808080808,-7.27272727272727)(940.545454545455,-7.24242424242424)(955.474747474747,-7.18181818181818)(970.40404040404,-7.12121212121212)(985.333333333333,-7.12121212121212)(1000.26262626263,-7.12121212121212)(1015.19191919192,-7.22727272727273)(1030.12121212121,-7.22727272727273)(1045.05050505051,-7.22727272727273)(1059.9797979798,-7.24242424242424)(1067.44444444444,-7.27272727272727)(1074.90909090909,-7.28787878787879)(1089.83838383838,-7.31818181818182)(1101.03535353535,-7.27272727272727)(1104.76767676768,-7.24242424242424)(1119.69696969697,-7.24242424242424)(1134.62626262626,-7.24242424242424)(1138.35858585859,-7.27272727272727)(1149.55555555556,-7.36363636363636)(1164.48484848485,-7.36363636363636)(1179.41414141414,-7.3030303030303)(1194.34343434343,-7.31818181818182)(1209.27272727273,-7.31818181818182)(1220.4696969697,-7.45454545454546)(1224.20202020202,-7.46969696969697)(1239.13131313131,-7.46969696969697)(1254.06060606061,-7.46969696969697)(1268.9898989899,-7.47272727272727)(1283.91919191919,-7.47727272727273)(1298.84848484848,-7.54545454545455)(1313.77777777778,-7.54545454545455)(1328.70707070707,-7.60606060606061)(1336.17171717172,-7.63636363636364)(1343.63636363636,-7.65909090909091)(1358.56565656566,-7.78787878787879)(1373.49494949495,-7.79545454545455)(1377.22727272727,-7.81818181818182)(1388.42424242424,-7.90909090909091)(1399.62121212121,-8)(1403.35353535354,-8.03030303030303)(1412.68434343434,-8.18181818181818)(1418.28282828283,-8.31818181818182)(1420.77104377104,-8.36363636363636)(1431.34595959596,-8.54545454545455)(1433.21212121212,-8.59090909090909)(1440.67676767677,-8.72727272727273)(1448.14141414141,-8.86363636363636)(1450.62962962963,-8.90909090909091)(1460.58249158249,-9.09090909090909)(1463.07070707071,-9.18181818181818)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-8.77272727272727)(1410.81818181818,-8.90909090909091)(1410.81818181818,-9.09090909090909)(1410.81818181818,-9.27272727272727)(1410.81818181818,-9.45454545454546)(1405.84175084175,-9.63636363636364)(1403.35353535354,-9.68181818181818)(1395.88888888889,-9.81818181818182)(1388.42424242424,-9.90909090909091)(1373.49494949495,-9.96969696969697)(1358.56565656566,-9.96969696969697)(1343.63636363636,-9.96969696969697)(1336.17171717172,-10)(1328.70707070707,-10.0151515151515)(1313.77777777778,-10.0454545454545)(1298.84848484848,-10.0454545454545)(1283.91919191919,-10.0454545454545)(1268.9898989899,-10.0454545454545)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.0757575757576)(1224.20202020202,-10.0757575757576)(1209.27272727273,-10.0454545454545)(1194.34343434343,-10.0454545454545)(1179.41414141414,-10.0757575757576)(1164.48484848485,-10.0757575757576)(1149.55555555556,-10.0757575757576)(1134.62626262626,-10.0454545454545)(1119.69696969697,-10.0454545454545)(1104.76767676768,-10.0151515151515)(1089.83838383838,-10.0151515151515)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.0757575757576)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0454545454545)(1000.26262626263,-10.0454545454545)(985.333333333333,-10.0151515151515)(981.60101010101,-10)(970.40404040404,-9.94545454545455)(955.474747474747,-9.86363636363636)(940.545454545455,-9.83333333333333)(933.080808080808,-9.81818181818182)(925.616161616162,-9.79545454545455)(910.686868686869,-9.75)(895.757575757576,-9.69090909090909)(880.828282828283,-9.65151515151515)(877.09595959596,-9.63636363636364)(865.89898989899,-9.56818181818182)(850.969696969697,-9.47272727272727)(848.481481481482,-9.45454545454546)(836.040404040404,-9.34090909090909)(830.441919191919,-9.27272727272727)(821.111111111111,-9.12121212121212)(818.622895622896,-9.09090909090909)(813.646464646465,-8.90909090909091)(819.244949494949,-8.72727272727273)(819.244949494949,-8.54545454545455)(821.111111111111,-8.5)(828.575757575758,-8.36363636363636)(836.040404040404,-8.22727272727273)(839.772727272727,-8.18181818181818)(850.969696969697,-8.09090909090909)(858.434343434343,-8)(865.89898989899,-7.90909090909091)(877.09595959596,-7.81818181818182)(880.828282828283,-7.79545454545455)(895.757575757576,-7.72727272727273)(910.686868686869,-7.66666666666667)(918.151515151515,-7.63636363636364)(925.616161616162,-7.61818181818182)(940.545454545455,-7.56818181818182)(955.474747474747,-7.54545454545455)(970.40404040404,-7.5)(985.333333333333,-7.5)(1000.26262626263,-7.5)(1015.19191919192,-7.60606060606061)(1030.12121212121,-7.60606060606061)(1045.05050505051,-7.60606060606061)(1059.9797979798,-7.56818181818182)(1074.90909090909,-7.58181818181818)(1089.83838383838,-7.59090909090909)(1104.76767676768,-7.61363636363636)(1112.23232323232,-7.63636363636364)(1119.69696969697,-7.66666666666667)(1134.62626262626,-7.72727272727273)(1149.55555555556,-7.72727272727273)(1164.48484848485,-7.72727272727273)(1179.41414141414,-7.68181818181818)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.77272727272727)(1224.20202020202,-7.79545454545455)(1239.13131313131,-7.76363636363636)(1254.06060606061,-7.74242424242424)(1268.9898989899,-7.77272727272727)(1283.91919191919,-7.8030303030303)(1287.65151515152,-7.81818181818182)(1298.84848484848,-7.90909090909091)(1313.77777777778,-7.90909090909091)(1328.70707070707,-7.97727272727273)(1332.43939393939,-8)(1343.63636363636,-8.09090909090909)(1354.83333333333,-8.18181818181818)(1358.56565656566,-8.21212121212121)(1371.00673400673,-8.36363636363636)(1373.49494949495,-8.39393939393939)(1388.42424242424,-8.51515151515152)(1390.91245791246,-8.54545454545455)(1400.86531986532,-8.72727272727273)(1403.35353535354,-8.77272727272727)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-7.95454545454546)(85.8434343434344,-7.81818181818182)(89.5757575757576,-7.78787878787879)(104.505050505051,-7.66666666666667)(106.993265993266,-7.63636363636364)(116.946127946128,-7.45454545454546)(119.434343434343,-7.42424242424243)(134.363636363636,-7.36363636363636)(149.292929292929,-7.3030303030303)(164.222222222222,-7.34090909090909)(179.151515151515,-7.34090909090909)(194.080808080808,-7.34090909090909)(209.010101010101,-7.36363636363636)(223.939393939394,-7.42424242424243)(231.40404040404,-7.45454545454546)(238.868686868687,-7.48484848484849)(253.79797979798,-7.54545454545455)(268.727272727273,-7.52272727272727)(283.656565656566,-7.56818181818182)(298.585858585859,-7.61363636363636)(302.318181818182,-7.63636363636364)(313.515151515152,-7.72727272727273)(328.444444444444,-7.77272727272727)(343.373737373737,-7.77272727272727)(358.30303030303,-7.68181818181818)(362.035353535354,-7.63636363636364)(373.232323232323,-7.56818181818182)(388.161616161616,-7.47727272727273)(395.626262626263,-7.45454545454546)(403.090909090909,-7.42424242424243)(418.020202020202,-7.36363636363636)(432.949494949495,-7.31818181818182)(440.414141414141,-7.27272727272727)(447.878787878788,-7.24242424242424)(462.808080808081,-7.18181818181818)(477.737373737374,-7.18181818181818)(492.666666666667,-7.12121212121212)(496.39898989899,-7.09090909090909)(507.59595959596,-7.02272727272727)(522.525252525253,-6.97727272727273)(537.454545454546,-7.02272727272727)(548.651515151515,-7.09090909090909)(552.383838383838,-7.12121212121212)(567.313131313131,-7.18181818181818)(582.242424242424,-7.18181818181818)(597.171717171717,-7.24242424242424)(604.636363636364,-7.27272727272727)(612.10101010101,-7.3030303030303)(627.030303030303,-7.3030303030303)(641.959595959596,-7.40909090909091)(645.691919191919,-7.45454545454546)(641.959595959596,-7.54545454545455)(639.47138047138,-7.63636363636364)(641.959595959596,-7.68181818181818)(649.424242424242,-7.81818181818182)(654.400673400673,-8)(656.888888888889,-8.04545454545455)(664.353535353535,-8.18181818181818)(664.353535353535,-8.36363636363636)(664.353535353535,-8.54545454545455)(656.888888888889,-8.68181818181818)(655.022727272727,-8.72727272727273)(641.959595959596,-8.88636363636364)(634.494949494949,-8.90909090909091)(627.030303030303,-8.93939393939394)(612.10101010101,-9.06060606060606)(604.636363636364,-9.09090909090909)(597.171717171717,-9.12121212121212)(582.242424242424,-9.18181818181818)(567.313131313131,-9.18181818181818)(556.116161616162,-9.27272727272727)(552.383838383838,-9.3030303030303)(537.454545454546,-9.36363636363636)(522.525252525253,-9.36363636363636)(507.59595959596,-9.36363636363636)(492.666666666667,-9.3030303030303)(477.737373737374,-9.3030303030303)(474.005050505051,-9.27272727272727)(462.808080808081,-9.18181818181818)(447.878787878788,-9.12121212121212)(440.414141414141,-9.09090909090909)(432.949494949495,-9.06060606060606)(420.508417508418,-8.90909090909091)(418.020202020202,-8.87878787878788)(403.090909090909,-8.81818181818182)(388.161616161616,-8.75757575757576)(373.232323232323,-8.75757575757576)(365.767676767677,-8.72727272727273)(358.30303030303,-8.6969696969697)(343.373737373737,-8.63636363636364)(328.444444444444,-8.6969696969697)(324.712121212121,-8.72727272727273)(313.515151515152,-8.79545454545455)(298.585858585859,-8.84090909090909)(283.656565656566,-8.88636363636364)(276.191919191919,-8.90909090909091)(268.727272727273,-8.93939393939394)(253.79797979798,-9)(242.60101010101,-9.09090909090909)(238.868686868687,-9.12121212121212)(223.939393939394,-9.18181818181818)(209.010101010101,-9.24242424242424)(194.080808080808,-9.24242424242424)(186.616161616162,-9.27272727272727)(179.151515151515,-9.29090909090909)(171.686868686869,-9.27272727272727)(164.222222222222,-9.24242424242424)(151.781144781145,-9.09090909090909)(149.292929292929,-9.06060606060606)(136.851851851852,-8.90909090909091)(134.363636363636,-8.88636363636364)(119.434343434343,-8.88636363636364)(104.505050505051,-8.81818181818182)(97.040404040404,-8.72727272727273)(89.5757575757576,-8.63636363636364)(83.9772727272727,-8.54545454545455)(77.1346801346801,-8.36363636363636)(74.6464646464647,-8.31818181818182)(67.1818181818182,-8.18181818181818)(72.1582491582492,-8)(74.6464646464647,-7.95454545454546)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1313.77777777778,-9)(1316.26599326599,-9.09090909090909)(1313.77777777778,-9.13636363636364)(1302.58080808081,-9.27272727272727)(1298.84848484848,-9.3030303030303)(1283.91919191919,-9.36363636363636)(1268.9898989899,-9.36363636363636)(1254.06060606061,-9.42424242424243)(1246.59595959596,-9.45454545454546)(1239.13131313131,-9.48484848484848)(1224.20202020202,-9.54545454545455)(1209.27272727273,-9.5)(1201.80808080808,-9.45454545454546)(1194.34343434343,-9.42424242424243)(1179.41414141414,-9.42424242424243)(1171.94949494949,-9.45454545454546)(1164.48484848485,-9.5)(1149.55555555556,-9.54545454545455)(1134.62626262626,-9.54545454545455)(1119.69696969697,-9.54545454545455)(1104.76767676768,-9.54545454545455)(1089.83838383838,-9.48484848484848)(1074.90909090909,-9.48484848484848)(1059.9797979798,-9.48484848484848)(1045.05050505051,-9.54545454545455)(1030.12121212121,-9.54545454545455)(1015.19191919192,-9.5)(1000.26262626263,-9.5)(985.333333333333,-9.5)(970.40404040404,-9.48484848484848)(962.939393939394,-9.45454545454546)(955.474747474747,-9.42424242424243)(940.545454545455,-9.3030303030303)(933.080808080808,-9.27272727272727)(925.616161616162,-9.24242424242424)(910.686868686869,-9.12121212121212)(906.954545454546,-9.09090909090909)(895.757575757576,-8.95454545454546)(893.26936026936,-8.90909090909091)(892.025252525252,-8.72727272727273)(895.757575757576,-8.63636363636364)(898.245791245791,-8.54545454545455)(910.686868686869,-8.39393939393939)(914.419191919192,-8.36363636363636)(925.616161616162,-8.22727272727273)(929.348484848485,-8.18181818181818)(940.545454545455,-8.09090909090909)(951.742424242424,-8)(955.474747474747,-7.96969696969697)(970.40404040404,-7.96969696969697)(985.333333333333,-7.96969696969697)(992.79797979798,-8)(1000.26262626263,-8.03030303030303)(1007.72727272727,-8)(1015.19191919192,-7.96969696969697)(1030.12121212121,-7.96969696969697)(1045.05050505051,-7.90909090909091)(1056.24747474747,-8)(1059.9797979798,-8.03030303030303)(1074.90909090909,-8.09090909090909)(1089.83838383838,-8.15151515151515)(1104.76767676768,-8.09090909090909)(1119.69696969697,-8.09090909090909)(1134.62626262626,-8.15151515151515)(1142.09090909091,-8.18181818181818)(1149.55555555556,-8.22727272727273)(1164.48484848485,-8.31818181818182)(1179.41414141414,-8.31818181818182)(1194.34343434343,-8.27272727272727)(1209.27272727273,-8.33333333333333)(1224.20202020202,-8.33333333333333)(1231.66666666667,-8.36363636363636)(1239.13131313131,-8.39393939393939)(1254.06060606061,-8.39393939393939)(1268.9898989899,-8.45454545454545)(1280.18686868687,-8.54545454545455)(1283.91919191919,-8.57575757575757)(1298.84848484848,-8.6969696969697)(1301.3367003367,-8.72727272727273)(1311.28956228956,-8.90909090909091)(1313.77777777778,-9)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-8.04545454545455)(450.367003367003,-8)(462.808080808081,-7.88636363636364)(474.005050505051,-7.81818181818182)(477.737373737374,-7.78787878787879)(492.666666666667,-7.66666666666667)(507.59595959596,-7.72727272727273)(522.525252525253,-7.66666666666667)(537.454545454546,-7.66666666666667)(544.919191919192,-7.63636363636364)(552.383838383838,-7.60606060606061)(559.848484848485,-7.63636363636364)(567.313131313131,-7.66666666666667)(579.754208754209,-7.81818181818182)(582.242424242424,-7.84848484848485)(594.683501683502,-8)(597.171717171717,-8.09090909090909)(599.659932659933,-8.18181818181818)(600.90404040404,-8.36363636363636)(597.171717171717,-8.40909090909091)(585.974747474747,-8.54545454545455)(582.242424242424,-8.57575757575757)(567.313131313131,-8.6969696969697)(559.848484848485,-8.72727272727273)(552.383838383838,-8.75757575757576)(537.454545454546,-8.81818181818182)(522.525252525253,-8.81818181818182)(507.59595959596,-8.75757575757576)(503.863636363636,-8.72727272727273)(492.666666666667,-8.63636363636364)(481.469696969697,-8.54545454545455)(477.737373737374,-8.52272727272727)(462.808080808081,-8.47727272727273)(450.367003367003,-8.36363636363636)(447.878787878788,-8.31818181818182)(440.414141414141,-8.18181818181818)(447.878787878788,-8.04545454545455)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_240.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1448.14141414141,-8.86363636363636)(1450.62962962963,-8.90909090909091)(1455.60606060606,-9.09090909090909)(1455.60606060606,-9.27272727272727)(1455.60606060606,-9.45454545454546)(1450.62962962963,-9.63636363636364)(1448.14141414141,-9.68181818181818)(1440.67676767677,-9.81818181818182)(1433.21212121212,-9.90909090909091)(1422.01515151515,-10)(1418.28282828283,-10.030303030303)(1403.35353535354,-10.1590909090909)(1401.48737373737,-10.1818181818182)(1388.42424242424,-10.3409090909091)(1380.9595959596,-10.3636363636364)(1373.49494949495,-10.3939393939394)(1358.56565656566,-10.3939393939394)(1354.83333333333,-10.3636363636364)(1343.63636363636,-10.2954545454545)(1328.70707070707,-10.3090909090909)(1313.77777777778,-10.2878787878788)(1298.84848484848,-10.2878787878788)(1283.91919191919,-10.2878787878788)(1268.9898989899,-10.3181818181818)(1254.06060606061,-10.3484848484848)(1239.13131313131,-10.3484848484848)(1224.20202020202,-10.3484848484848)(1209.27272727273,-10.3181818181818)(1194.34343434343,-10.3181818181818)(1179.41414141414,-10.3484848484848)(1164.48484848485,-10.3484848484848)(1149.55555555556,-10.3484848484848)(1134.62626262626,-10.3181818181818)(1119.69696969697,-10.3181818181818)(1104.76767676768,-10.2878787878788)(1089.83838383838,-10.2878787878788)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1045.05050505051,-10.3484848484848)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.3181818181818)(1000.26262626263,-10.3181818181818)(985.333333333333,-10.2878787878788)(970.40404040404,-10.2363636363636)(962.939393939394,-10.1818181818182)(955.474747474747,-10.1363636363636)(940.545454545455,-10.1060606060606)(925.616161616162,-10.0909090909091)(910.686868686869,-10.0681818181818)(899.489898989899,-10)(895.757575757576,-9.98484848484848)(880.828282828283,-9.94545454545455)(865.89898989899,-9.88636363636364)(854.70202020202,-9.81818181818182)(850.969696969697,-9.8)(836.040404040404,-9.70454545454546)(828.575757575758,-9.63636363636364)(821.111111111111,-9.56818181818182)(811.780303030303,-9.45454545454546)(806.181818181818,-9.38636363636364)(796.85101010101,-9.27272727272727)(791.252525252525,-9.18181818181818)(783.787878787879,-9.09090909090909)(776.323232323232,-8.95454545454546)(773.835016835017,-8.90909090909091)(772.590909090909,-8.72727272727273)(772.590909090909,-8.54545454545455)(776.323232323232,-8.45454545454545)(778.811447811448,-8.36363636363636)(783.787878787879,-8.18181818181818)(791.252525252525,-8.09090909090909)(802.449494949495,-8)(806.181818181818,-7.96969696969697)(821.111111111111,-7.90909090909091)(832.308080808081,-7.81818181818182)(836.040404040404,-7.78787878787879)(850.969696969697,-7.65909090909091)(853.457912457912,-7.63636363636364)(865.89898989899,-7.52272727272727)(873.363636363636,-7.45454545454546)(880.828282828283,-7.36363636363636)(895.757575757576,-7.29545454545455)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(914.419191919192,-7.27272727272727)(925.616161616162,-7.31818181818182)(940.545454545455,-7.28787878787879)(948.010101010101,-7.27272727272727)(955.474747474747,-7.24242424242424)(970.40404040404,-7.12121212121212)(985.333333333333,-7.12121212121212)(1000.26262626263,-7.12121212121212)(1015.19191919192,-7.22727272727273)(1030.12121212121,-7.22727272727273)(1037.58585858586,-7.27272727272727)(1045.05050505051,-7.28787878787879)(1059.9797979798,-7.28787878787879)(1074.90909090909,-7.31818181818182)(1089.83838383838,-7.31818181818182)(1101.03535353535,-7.27272727272727)(1104.76767676768,-7.24242424242424)(1119.69696969697,-7.24242424242424)(1134.62626262626,-7.24242424242424)(1138.35858585859,-7.27272727272727)(1149.55555555556,-7.36363636363636)(1164.48484848485,-7.36363636363636)(1179.41414141414,-7.3030303030303)(1194.34343434343,-7.31818181818182)(1209.27272727273,-7.40909090909091)(1213.00505050505,-7.45454545454546)(1224.20202020202,-7.5)(1239.13131313131,-7.5)(1254.06060606061,-7.46969696969697)(1268.9898989899,-7.46969696969697)(1283.91919191919,-7.47272727272727)(1298.84848484848,-7.52272727272727)(1313.77777777778,-7.54545454545455)(1328.70707070707,-7.60606060606061)(1336.17171717172,-7.63636363636364)(1343.63636363636,-7.65909090909091)(1358.56565656566,-7.78787878787879)(1373.49494949495,-7.79545454545455)(1377.22727272727,-7.81818181818182)(1388.42424242424,-7.88636363636364)(1403.35353535354,-7.96969696969697)(1405.84175084175,-8)(1416.41666666667,-8.18181818181818)(1418.28282828283,-8.22727272727273)(1423.88131313131,-8.36363636363636)(1431.34595959596,-8.54545454545455)(1433.21212121212,-8.59090909090909)(1440.67676767677,-8.72727272727273)(1448.14141414141,-8.86363636363636)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-8.68181818181818)(1405.2196969697,-8.72727272727273)(1410.81818181818,-8.90909090909091)(1415.79461279461,-9.09090909090909)(1415.79461279461,-9.27272727272727)(1415.79461279461,-9.45454545454546)(1405.84175084175,-9.63636363636364)(1403.35353535354,-9.68181818181818)(1395.88888888889,-9.81818181818182)(1388.42424242424,-9.88636363636364)(1373.49494949495,-9.96969696969697)(1358.56565656566,-9.96969696969697)(1343.63636363636,-9.96969696969697)(1336.17171717172,-10)(1328.70707070707,-10.0151515151515)(1313.77777777778,-10.0151515151515)(1298.84848484848,-10.0151515151515)(1283.91919191919,-10.0151515151515)(1268.9898989899,-10.0454545454545)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.0757575757576)(1224.20202020202,-10.0757575757576)(1209.27272727273,-10.0454545454545)(1194.34343434343,-10.0454545454545)(1179.41414141414,-10.0757575757576)(1164.48484848485,-10.0757575757576)(1149.55555555556,-10.0757575757576)(1134.62626262626,-10.0454545454545)(1119.69696969697,-10.0454545454545)(1104.76767676768,-10.0151515151515)(1089.83838383838,-10.0151515151515)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.0757575757576)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0454545454545)(1000.26262626263,-10.0454545454545)(985.333333333333,-10.0151515151515)(981.60101010101,-10)(970.40404040404,-9.94545454545455)(955.474747474747,-9.86363636363636)(940.545454545455,-9.83333333333333)(933.080808080808,-9.81818181818182)(925.616161616162,-9.79545454545455)(910.686868686869,-9.75)(895.757575757576,-9.69090909090909)(880.828282828283,-9.65151515151515)(877.09595959596,-9.63636363636364)(865.89898989899,-9.56818181818182)(850.969696969697,-9.47272727272727)(848.481481481482,-9.45454545454546)(836.040404040404,-9.34090909090909)(830.441919191919,-9.27272727272727)(821.111111111111,-9.12121212121212)(819.244949494949,-9.09090909090909)(813.646464646465,-8.90909090909091)(815.512626262626,-8.72727272727273)(815.512626262626,-8.54545454545455)(821.111111111111,-8.40909090909091)(823.599326599327,-8.36363636363636)(836.040404040404,-8.21212121212121)(839.772727272727,-8.18181818181818)(850.969696969697,-8.11363636363636)(860.300505050505,-8)(865.89898989899,-7.90909090909091)(877.09595959596,-7.81818181818182)(880.828282828283,-7.8)(895.757575757576,-7.70454545454546)(906.954545454546,-7.63636363636364)(910.686868686869,-7.61363636363636)(925.616161616162,-7.59090909090909)(940.545454545455,-7.58181818181818)(955.474747474748,-7.56818181818182)(970.40404040404,-7.5)(985.333333333333,-7.5)(1000.26262626263,-7.5)(1015.19191919192,-7.60606060606061)(1030.12121212121,-7.60606060606061)(1045.05050505051,-7.61363636363636)(1059.9797979798,-7.58181818181818)(1074.90909090909,-7.59090909090909)(1089.83838383838,-7.59090909090909)(1104.76767676768,-7.61363636363636)(1112.23232323232,-7.63636363636364)(1119.69696969697,-7.66666666666667)(1134.62626262626,-7.72727272727273)(1149.55555555556,-7.72727272727273)(1164.48484848485,-7.72727272727273)(1179.41414141414,-7.68181818181818)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.78787878787879)(1224.20202020202,-7.8)(1239.13131313131,-7.77272727272727)(1254.06060606061,-7.74242424242424)(1268.9898989899,-7.74242424242424)(1283.91919191919,-7.77272727272727)(1295.11616161616,-7.81818181818182)(1298.84848484848,-7.84848484848485)(1313.77777777778,-7.90909090909091)(1328.70707070707,-7.97727272727273)(1336.17171717172,-8)(1343.63636363636,-8.03030303030303)(1358.56565656566,-8.15909090909091)(1366.0303030303,-8.18181818181818)(1373.49494949495,-8.22727272727273)(1384.69191919192,-8.36363636363636)(1388.42424242424,-8.40909090909091)(1395.88888888889,-8.54545454545455)(1403.35353535354,-8.68181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-7.95454545454546)(85.8434343434344,-7.81818181818182)(89.5757575757576,-7.78787878787879)(104.505050505051,-7.66666666666667)(106.993265993266,-7.63636363636364)(116.946127946128,-7.45454545454546)(119.434343434343,-7.42424242424243)(134.363636363636,-7.36363636363636)(149.292929292929,-7.3030303030303)(164.222222222222,-7.34090909090909)(179.151515151515,-7.34090909090909)(194.080808080808,-7.38636363636364)(205.277777777778,-7.45454545454546)(209.010101010101,-7.48484848484849)(223.939393939394,-7.54545454545455)(238.868686868687,-7.54545454545455)(253.79797979798,-7.60606060606061)(268.727272727273,-7.61363636363636)(276.191919191919,-7.63636363636364)(283.656565656566,-7.66666666666667)(298.585858585859,-7.66666666666667)(313.515151515152,-7.72727272727273)(328.444444444444,-7.77272727272727)(343.373737373737,-7.77272727272727)(354.570707070707,-7.63636363636364)(358.30303030303,-7.60606060606061)(373.232323232323,-7.52272727272727)(388.161616161616,-7.47727272727273)(403.090909090909,-7.47727272727273)(410.555555555556,-7.45454545454546)(418.020202020202,-7.42424242424243)(432.949494949495,-7.31818181818182)(440.414141414141,-7.27272727272727)(447.878787878788,-7.24242424242424)(462.808080808081,-7.18181818181818)(477.737373737374,-7.18181818181818)(492.666666666667,-7.12121212121212)(496.39898989899,-7.09090909090909)(507.59595959596,-7.02272727272727)(522.525252525253,-7.02272727272727)(537.454545454546,-7.06818181818182)(541.186868686869,-7.09090909090909)(552.383838383838,-7.18181818181818)(567.313131313131,-7.18181818181818)(582.242424242424,-7.24242424242424)(589.707070707071,-7.27272727272727)(597.171717171717,-7.3030303030303)(612.10101010101,-7.42424242424243)(627.030303030303,-7.36363636363636)(638.227272727273,-7.45454545454546)(634.494949494949,-7.63636363636364)(641.959595959596,-7.72727272727273)(649.424242424242,-7.81818181818182)(654.400673400673,-8)(656.888888888889,-8.09090909090909)(659.377104377104,-8.18181818181818)(659.377104377104,-8.36363636363636)(659.377104377104,-8.54545454545455)(656.888888888889,-8.63636363636364)(655.39595959596,-8.72727272727273)(644.447811447811,-8.90909090909091)(641.959595959596,-8.93939393939394)(627.030303030303,-9)(615.833333333333,-9.09090909090909)(612.10101010101,-9.11363636363636)(597.171717171717,-9.12121212121212)(582.242424242424,-9.18181818181818)(567.313131313131,-9.18181818181818)(556.116161616162,-9.27272727272727)(552.383838383838,-9.3030303030303)(537.454545454546,-9.3030303030303)(522.525252525253,-9.3030303030303)(507.59595959596,-9.3030303030303)(492.666666666667,-9.3030303030303)(477.737373737374,-9.3030303030303)(475.249158249158,-9.27272727272727)(462.808080808081,-9.12121212121212)(455.343434343434,-9.09090909090909)(447.878787878788,-9.06060606060606)(432.949494949495,-9)(421.752525252525,-8.90909090909091)(418.020202020202,-8.87878787878788)(403.090909090909,-8.81818181818182)(391.893939393939,-8.72727272727273)(388.161616161616,-8.6969696969697)(373.232323232323,-8.6969696969697)(358.30303030303,-8.63636363636364)(343.373737373737,-8.63636363636364)(328.444444444444,-8.63636363636364)(313.515151515152,-8.6969696969697)(306.050505050505,-8.72727272727273)(298.585858585859,-8.75)(283.656565656566,-8.79545454545455)(268.727272727273,-8.87878787878788)(261.262626262626,-8.90909090909091)(253.79797979798,-8.93939393939394)(241.356902356902,-9.09090909090909)(238.868686868687,-9.12121212121212)(223.939393939394,-9.12121212121212)(209.010101010101,-9.12121212121212)(194.080808080808,-9.12121212121212)(179.151515151515,-9.24242424242424)(164.222222222222,-9.24242424242424)(151.781144781145,-9.09090909090909)(149.292929292929,-9.06060606060606)(136.851851851852,-8.90909090909091)(134.363636363636,-8.88636363636364)(119.434343434343,-8.88636363636364)(104.505050505051,-8.81818181818182)(97.040404040404,-8.72727272727273)(89.5757575757576,-8.59090909090909)(87.709595959596,-8.54545454545455)(82.1111111111111,-8.36363636363636)(74.6464646464647,-8.22727272727273)(72.1582491582492,-8.18181818181818)(72.1582491582492,-8)(74.6464646464647,-7.95454545454546)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1298.84848484848,-8.81818181818182)(1301.3367003367,-8.90909090909091)(1301.3367003367,-9.09090909090909)(1298.84848484848,-9.13636363636364)(1287.65151515152,-9.27272727272727)(1283.91919191919,-9.3030303030303)(1268.9898989899,-9.36363636363636)(1254.06060606061,-9.36363636363636)(1239.13131313131,-9.42424242424243)(1231.66666666667,-9.45454545454546)(1224.20202020202,-9.48484848484848)(1209.27272727273,-9.5)(1201.80808080808,-9.45454545454546)(1194.34343434343,-9.42424242424243)(1179.41414141414,-9.42424242424243)(1171.94949494949,-9.45454545454546)(1164.48484848485,-9.5)(1149.55555555556,-9.54545454545455)(1134.62626262626,-9.54545454545455)(1119.69696969697,-9.48484848484848)(1104.76767676768,-9.48484848484848)(1097.30303030303,-9.45454545454546)(1089.83838383838,-9.40909090909091)(1082.37373737374,-9.45454545454546)(1074.90909090909,-9.48484848484848)(1059.9797979798,-9.48484848484848)(1045.05050505051,-9.54545454545455)(1030.12121212121,-9.54545454545455)(1015.19191919192,-9.5)(1000.26262626263,-9.5)(985.333333333333,-9.5)(970.40404040404,-9.48484848484848)(966.671717171717,-9.45454545454546)(955.474747474747,-9.36363636363636)(944.277777777778,-9.27272727272727)(940.545454545455,-9.22727272727273)(925.616161616162,-9.18181818181818)(910.686868686869,-9.12121212121212)(906.954545454546,-9.09090909090909)(895.757575757576,-8.95454545454546)(893.26936026936,-8.90909090909091)(892.025252525252,-8.72727272727273)(895.757575757576,-8.63636363636364)(898.245791245791,-8.54545454545455)(910.686868686869,-8.39393939393939)(914.419191919192,-8.36363636363636)(925.616161616162,-8.22727272727273)(929.348484848485,-8.18181818181818)(940.545454545455,-8.09090909090909)(951.742424242424,-8)(955.474747474747,-7.96969696969697)(970.40404040404,-7.96969696969697)(985.333333333333,-7.96969696969697)(992.79797979798,-8)(1000.26262626263,-8.03030303030303)(1007.72727272727,-8)(1015.19191919192,-7.96969696969697)(1030.12121212121,-7.96969696969697)(1045.05050505051,-7.96969696969697)(1048.78282828283,-8)(1059.9797979798,-8.09090909090909)(1074.90909090909,-8.15151515151515)(1082.37373737374,-8.18181818181818)(1089.83838383838,-8.21212121212121)(1104.76767676768,-8.21212121212121)(1119.69696969697,-8.27272727272727)(1134.62626262626,-8.27272727272727)(1149.55555555556,-8.31818181818182)(1164.48484848485,-8.31818181818182)(1179.41414141414,-8.31818181818182)(1194.34343434343,-8.27272727272727)(1209.27272727273,-8.33333333333333)(1224.20202020202,-8.33333333333333)(1231.66666666667,-8.36363636363636)(1239.13131313131,-8.39393939393939)(1254.06060606061,-8.39393939393939)(1268.9898989899,-8.45454545454545)(1280.18686868687,-8.54545454545455)(1283.91919191919,-8.57575757575757)(1296.36026936027,-8.72727272727273)(1298.84848484848,-8.81818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-8.03030303030303)(450.367003367003,-8)(462.808080808081,-7.88636363636364)(474.005050505051,-7.81818181818182)(477.737373737374,-7.78787878787879)(492.666666666667,-7.66666666666667)(507.59595959596,-7.72727272727273)(522.525252525253,-7.66666666666667)(537.454545454546,-7.66666666666667)(544.919191919192,-7.63636363636364)(552.383838383838,-7.60606060606061)(559.848484848485,-7.63636363636364)(567.313131313131,-7.66666666666667)(579.754208754209,-7.81818181818182)(582.242424242424,-7.84848484848485)(594.683501683502,-8)(597.171717171717,-8.09090909090909)(599.659932659933,-8.18181818181818)(600.90404040404,-8.36363636363636)(597.171717171717,-8.40909090909091)(589.707070707071,-8.54545454545455)(582.242424242424,-8.63636363636364)(571.045454545455,-8.72727272727273)(567.313131313131,-8.75757575757576)(552.383838383838,-8.81818181818182)(537.454545454546,-8.81818181818182)(522.525252525253,-8.81818181818182)(507.59595959596,-8.81818181818182)(496.39898989899,-8.72727272727273)(492.666666666667,-8.6969696969697)(477.737373737374,-8.57575757575757)(474.005050505051,-8.54545454545455)(462.808080808081,-8.47727272727273)(447.878787878788,-8.40909090909091)(444.146464646465,-8.36363636363636)(435.43771043771,-8.18181818181818)(447.878787878788,-8.03030303030303)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (149.292929292929,-8.13636363636364)(164.222222222222,-8.09090909090909)(179.151515151515,-8.09090909090909)(194.080808080808,-8.09090909090909)(205.277777777778,-8.18181818181818)(209.010101010101,-8.27272727272727)(212.742424242424,-8.36363636363636)(209.010101010101,-8.40909090909091)(197.813131313131,-8.54545454545455)(194.080808080808,-8.57575757575757)(179.151515151515,-8.63636363636364)(164.222222222222,-8.57575757575757)(160.489898989899,-8.54545454545455)(149.292929292929,-8.40909090909091)(145.560606060606,-8.36363636363636)(145.560606060606,-8.18181818181818)(149.292929292929,-8.13636363636364)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182)(373.232323232323,-7.63636363636364)(1313.77777777778,-9.09090909090909)(1015.19191919192,-9.09090909090909)(194.080808080808,-9.09090909090909)(627.030303030303,-8.90909090909091)(223.939393939394,-7.45454545454546)(1104.76767676768,-8.18181818181818)(940.545454545455,-7.27272727272727)(1403.35353535354,-8.18181818181818)(134.363636363636,-8)(432.949494949495,-8.36363636363636)(1059.9797979798,-7.27272727272727)(836.040404040404,-7.81818181818182)(1298.84848484848,-10.1818181818182)(791.252525252525,-9.27272727272727)(1418.28282828283,-9.27272727272727)(940.545454545455,-9.27272727272727)(1104.76767676768,-9.45454545454546)(298.585858585859,-8.72727272727273)(597.171717171717,-7.27272727272727) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_260.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1448.14141414141,-8.86363636363636)(1450.62962962963,-8.90909090909091)(1455.60606060606,-9.09090909090909)(1455.60606060606,-9.27272727272727)(1455.60606060606,-9.45454545454546)(1450.62962962963,-9.63636363636364)(1448.14141414141,-9.68181818181818)(1440.67676767677,-9.81818181818182)(1433.21212121212,-9.90909090909091)(1422.01515151515,-10)(1418.28282828283,-10.030303030303)(1403.35353535354,-10.1136363636364)(1397.75505050505,-10.1818181818182)(1388.42424242424,-10.2954545454545)(1373.49494949495,-10.3409090909091)(1366.0303030303,-10.3636363636364)(1358.56565656566,-10.3939393939394)(1354.83333333333,-10.3636363636364)(1343.63636363636,-10.2954545454545)(1328.70707070707,-10.3090909090909)(1313.77777777778,-10.2878787878788)(1298.84848484848,-10.2878787878788)(1283.91919191919,-10.2878787878788)(1268.9898989899,-10.3181818181818)(1254.06060606061,-10.3484848484848)(1239.13131313131,-10.3484848484848)(1224.20202020202,-10.3484848484848)(1209.27272727273,-10.3181818181818)(1194.34343434343,-10.3181818181818)(1179.41414141414,-10.3484848484848)(1164.48484848485,-10.3484848484848)(1149.55555555556,-10.3484848484848)(1134.62626262626,-10.2878787878788)(1119.69696969697,-10.2878787878788)(1104.76767676768,-10.2575757575758)(1089.83838383838,-10.2878787878788)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.3484848484848)(1045.05050505051,-10.3484848484848)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.3181818181818)(1000.26262626263,-10.2878787878788)(985.333333333333,-10.2575757575758)(970.40404040404,-10.2)(966.671717171717,-10.1818181818182)(955.474747474747,-10.1363636363636)(940.545454545455,-10.1060606060606)(925.616161616162,-10.0909090909091)(910.686868686869,-10.0681818181818)(899.489898989899,-10)(895.757575757576,-9.98484848484848)(880.828282828283,-9.90909090909091)(865.89898989899,-9.84090909090909)(862.166666666667,-9.81818181818182)(850.969696969697,-9.76363636363636)(836.040404040404,-9.70454545454546)(828.575757575758,-9.63636363636364)(821.111111111111,-9.56818181818182)(811.780303030303,-9.45454545454546)(806.181818181818,-9.38636363636364)(796.85101010101,-9.27272727272727)(791.252525252525,-9.18181818181818)(783.787878787879,-9.09090909090909)(776.323232323232,-8.95454545454546)(773.835016835017,-8.90909090909091)(765.126262626263,-8.72727272727273)(772.590909090909,-8.54545454545455)(776.323232323232,-8.45454545454545)(778.811447811448,-8.36363636363636)(788.76430976431,-8.18181818181818)(791.252525252525,-8.13636363636364)(802.449494949495,-8)(806.181818181818,-7.96969696969697)(821.111111111111,-7.88636363636364)(828.575757575758,-7.81818181818182)(836.040404040404,-7.75)(850.969696969697,-7.65454545454546)(853.457912457912,-7.63636363636364)(865.89898989899,-7.52272727272727)(873.363636363636,-7.45454545454546)(880.828282828283,-7.36363636363636)(895.757575757576,-7.29545454545455)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(914.419191919192,-7.27272727272727)(925.616161616162,-7.31818181818182)(940.545454545455,-7.28787878787879)(944.277777777778,-7.27272727272727)(955.474747474748,-7.20454545454546)(970.40404040404,-7.10909090909091)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.15909090909091)(1030.12121212121,-7.18181818181818)(1041.31818181818,-7.27272727272727)(1045.05050505051,-7.28787878787879)(1059.9797979798,-7.28787878787879)(1074.90909090909,-7.31818181818182)(1089.83838383838,-7.31818181818182)(1101.03535353535,-7.27272727272727)(1104.76767676768,-7.24242424242424)(1119.69696969697,-7.24242424242424)(1134.62626262626,-7.24242424242424)(1138.35858585859,-7.27272727272727)(1149.55555555556,-7.32727272727273)(1164.48484848485,-7.29545454545455)(1171.94949494949,-7.27272727272727)(1179.41414141414,-7.25454545454546)(1186.87878787879,-7.27272727272727)(1194.34343434343,-7.31818181818182)(1205.5404040404,-7.45454545454546)(1209.27272727273,-7.46969696969697)(1224.20202020202,-7.53030303030303)(1239.13131313131,-7.5)(1254.06060606061,-7.46969696969697)(1268.9898989899,-7.46969696969697)(1283.91919191919,-7.46969696969697)(1298.84848484848,-7.50909090909091)(1313.77777777778,-7.52272727272727)(1328.70707070707,-7.60606060606061)(1336.17171717172,-7.63636363636364)(1343.63636363636,-7.65454545454546)(1358.56565656566,-7.75)(1373.49494949495,-7.79545454545455)(1377.22727272727,-7.81818181818182)(1388.42424242424,-7.88636363636364)(1403.35353535354,-7.96969696969697)(1405.84175084175,-8)(1412.68434343434,-8.18181818181818)(1418.28282828283,-8.31818181818182)(1420.14898989899,-8.36363636363636)(1427.61363636364,-8.54545454545455)(1433.21212121212,-8.63636363636364)(1440.67676767677,-8.72727272727273)(1448.14141414141,-8.86363636363636)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1418.28282828283,-9)(1420.77104377104,-9.09090909090909)(1420.77104377104,-9.27272727272727)(1418.28282828283,-9.36363636363636)(1415.79461279461,-9.45454545454546)(1405.84175084175,-9.63636363636364)(1403.35353535354,-9.68181818181818)(1395.88888888889,-9.81818181818182)(1388.42424242424,-9.87272727272727)(1373.49494949495,-9.93181818181818)(1358.56565656566,-9.96969696969697)(1343.63636363636,-9.96969696969697)(1336.17171717172,-10)(1328.70707070707,-10.0151515151515)(1313.77777777778,-10.0151515151515)(1298.84848484848,-10.0151515151515)(1283.91919191919,-10.0151515151515)(1268.9898989899,-10.0454545454545)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.0757575757576)(1224.20202020202,-10.0757575757576)(1209.27272727273,-10.0454545454545)(1194.34343434343,-10.0454545454545)(1179.41414141414,-10.0757575757576)(1164.48484848485,-10.0757575757576)(1149.55555555556,-10.0757575757576)(1134.62626262626,-10.0151515151515)(1119.69696969697,-10.0151515151515)(1112.23232323232,-10)(1104.76767676768,-9.98181818181818)(1097.30303030303,-10)(1089.83838383838,-10.0151515151515)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0757575757576)(1045.05050505051,-10.0757575757576)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0454545454545)(1000.26262626263,-10.0151515151515)(992.79797979798,-10)(985.333333333333,-9.98181818181818)(970.40404040404,-9.92424242424243)(955.474747474747,-9.86363636363636)(940.545454545455,-9.83333333333333)(933.080808080808,-9.81818181818182)(925.616161616162,-9.79545454545455)(910.686868686869,-9.75)(895.757575757576,-9.69090909090909)(884.560606060606,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.54545454545455)(850.969696969697,-9.46969696969697)(848.481481481482,-9.45454545454546)(836.040404040404,-9.34090909090909)(830.441919191919,-9.27272727272727)(821.111111111111,-9.12121212121212)(819.244949494949,-9.09090909090909)(813.646464646465,-8.90909090909091)(815.512626262626,-8.72727272727273)(815.512626262626,-8.54545454545455)(819.244949494949,-8.36363636363636)(821.111111111111,-8.31818181818182)(828.575757575758,-8.18181818181818)(836.040404040404,-8.12727272727273)(850.969696969697,-8.02272727272727)(853.457912457912,-8)(865.89898989899,-7.84848484848485)(873.363636363636,-7.81818181818182)(880.828282828283,-7.8)(895.757575757576,-7.70454545454546)(906.954545454546,-7.63636363636364)(910.686868686869,-7.61363636363636)(925.616161616162,-7.59090909090909)(940.545454545455,-7.58181818181818)(955.474747474748,-7.52272727272727)(962.939393939394,-7.45454545454546)(970.40404040404,-7.40909090909091)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1012.7037037037,-7.45454545454546)(1015.19191919192,-7.48484848484849)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.61363636363636)(1059.9797979798,-7.58181818181818)(1074.90909090909,-7.59090909090909)(1089.83838383838,-7.59090909090909)(1104.76767676768,-7.56818181818182)(1119.69696969697,-7.56818181818182)(1134.62626262626,-7.56818181818182)(1149.55555555556,-7.62121212121212)(1164.48484848485,-7.62121212121212)(1179.41414141414,-7.62121212121212)(1183.14646464646,-7.63636363636364)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.79545454545455)(1224.20202020202,-7.8030303030303)(1239.13131313131,-7.77272727272727)(1254.06060606061,-7.74242424242424)(1268.9898989899,-7.74242424242424)(1283.91919191919,-7.74242424242424)(1298.84848484848,-7.8030303030303)(1306.31313131313,-7.81818181818182)(1313.77777777778,-7.84848484848485)(1328.70707070707,-7.93181818181818)(1343.63636363636,-7.98181818181818)(1346.12457912458,-8)(1358.56565656566,-8.11363636363636)(1369.76262626263,-8.18181818181818)(1373.49494949495,-8.22727272727273)(1384.69191919192,-8.36363636363636)(1388.42424242424,-8.40909090909091)(1394.02272727273,-8.54545454545455)(1403.35353535354,-8.6969696969697)(1405.2196969697,-8.72727272727273)(1415.79461279461,-8.90909090909091)(1418.28282828283,-9)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (89.5757575757576,-7.86363636363636)(92.0639730639731,-7.81818181818182)(104.505050505051,-7.66666666666667)(106.993265993266,-7.63636363636364)(116.946127946128,-7.45454545454546)(119.434343434343,-7.42424242424243)(134.363636363636,-7.42424242424243)(149.292929292929,-7.36363636363636)(164.222222222222,-7.43181818181818)(179.151515151515,-7.43181818181818)(186.616161616162,-7.45454545454546)(194.080808080808,-7.48484848484849)(209.010101010101,-7.54545454545455)(223.939393939394,-7.60606060606061)(231.40404040404,-7.63636363636364)(238.868686868687,-7.66666666666667)(253.79797979798,-7.72727272727273)(268.727272727273,-7.66666666666667)(283.656565656566,-7.72727272727273)(298.585858585859,-7.78787878787879)(302.318181818182,-7.81818181818182)(313.515151515152,-7.90909090909091)(328.444444444444,-7.96969696969697)(335.909090909091,-8)(343.373737373737,-8.03030303030303)(350.838383838384,-8)(355.814814814815,-7.81818181818182)(358.30303030303,-7.77272727272727)(365.767676767677,-7.63636363636364)(373.232323232323,-7.54545454545455)(388.161616161616,-7.47727272727273)(403.090909090909,-7.47727272727273)(410.555555555556,-7.45454545454546)(418.020202020202,-7.42424242424243)(432.949494949495,-7.40909090909091)(447.878787878788,-7.31818181818182)(455.343434343434,-7.27272727272727)(462.808080808081,-7.24242424242424)(477.737373737374,-7.18181818181818)(492.666666666667,-7.18181818181818)(507.59595959596,-7.12121212121212)(522.525252525253,-7.12121212121212)(537.454545454546,-7.12121212121212)(552.383838383838,-7.18181818181818)(567.313131313131,-7.18181818181818)(582.242424242424,-7.24242424242424)(589.707070707071,-7.27272727272727)(597.171717171717,-7.3030303030303)(612.10101010101,-7.42424242424243)(627.030303030303,-7.40909090909091)(630.762626262626,-7.45454545454546)(629.518518518518,-7.63636363636364)(641.959595959596,-7.78787878787879)(644.447811447811,-7.81818181818182)(654.400673400673,-8)(656.888888888889,-8.09090909090909)(659.377104377104,-8.18181818181818)(659.377104377104,-8.36363636363636)(656.888888888889,-8.45454545454545)(655.022727272727,-8.54545454545455)(652.410101010101,-8.72727272727273)(641.959595959596,-8.88636363636364)(638.227272727273,-8.90909090909091)(627.030303030303,-9)(615.833333333333,-9.09090909090909)(612.10101010101,-9.11363636363636)(597.171717171717,-9.12121212121212)(582.242424242424,-9.18181818181818)(567.313131313131,-9.18181818181818)(556.116161616162,-9.27272727272727)(552.383838383838,-9.3030303030303)(537.454545454546,-9.3030303030303)(522.525252525253,-9.3030303030303)(507.59595959596,-9.3030303030303)(492.666666666667,-9.3030303030303)(485.20202020202,-9.27272727272727)(477.737373737374,-9.24242424242424)(465.296296296296,-9.09090909090909)(462.808080808081,-9.04545454545455)(447.878787878788,-9)(432.949494949495,-8.93939393939394)(429.217171717172,-8.90909090909091)(418.020202020202,-8.81818181818182)(406.823232323232,-8.72727272727273)(403.090909090909,-8.6969696969697)(388.161616161616,-8.63636363636364)(373.232323232323,-8.63636363636364)(358.30303030303,-8.57575757575757)(343.373737373737,-8.57575757575757)(328.444444444444,-8.57575757575757)(313.515151515152,-8.6969696969697)(306.050505050505,-8.72727272727273)(298.585858585859,-8.75)(283.656565656566,-8.79545454545455)(268.727272727273,-8.87878787878788)(261.262626262626,-8.90909090909091)(253.79797979798,-8.93939393939394)(241.356902356902,-9.09090909090909)(238.868686868687,-9.12121212121212)(223.939393939394,-9.12121212121212)(209.010101010101,-9.12121212121212)(194.080808080808,-9.12121212121212)(179.151515151515,-9.24242424242424)(164.222222222222,-9.24242424242424)(151.781144781145,-9.09090909090909)(149.292929292929,-9.06060606060606)(139.962121212121,-8.90909090909091)(134.363636363636,-8.85454545454546)(119.434343434343,-8.84090909090909)(104.505050505051,-8.75757575757576)(100.772727272727,-8.72727272727273)(89.5757575757576,-8.59090909090909)(87.709595959596,-8.54545454545455)(82.1111111111111,-8.36363636363636)(77.1346801346801,-8.18181818181818)(78.3787878787879,-8)(89.5757575757576,-7.86363636363636)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1298.84848484848,-8.81818181818182)(1301.3367003367,-8.90909090909091)(1301.3367003367,-9.09090909090909)(1298.84848484848,-9.13636363636364)(1287.65151515152,-9.27272727272727)(1283.91919191919,-9.3030303030303)(1268.9898989899,-9.36363636363636)(1254.06060606061,-9.36363636363636)(1239.13131313131,-9.36363636363636)(1224.20202020202,-9.42424242424243)(1209.27272727273,-9.42424242424243)(1194.34343434343,-9.42424242424243)(1179.41414141414,-9.42424242424243)(1171.94949494949,-9.45454545454546)(1164.48484848485,-9.5)(1149.55555555556,-9.54545454545455)(1134.62626262626,-9.54545454545455)(1119.69696969697,-9.48484848484848)(1104.76767676768,-9.48484848484848)(1097.30303030303,-9.45454545454546)(1089.83838383838,-9.40909090909091)(1082.37373737374,-9.45454545454546)(1074.90909090909,-9.48484848484848)(1059.9797979798,-9.48484848484848)(1045.05050505051,-9.54545454545455)(1030.12121212121,-9.54545454545455)(1015.19191919192,-9.5)(1000.26262626263,-9.5)(985.333333333333,-9.5)(970.40404040404,-9.48484848484848)(966.671717171717,-9.45454545454546)(955.474747474747,-9.36363636363636)(944.277777777778,-9.27272727272727)(940.545454545455,-9.22727272727273)(925.616161616162,-9.18181818181818)(910.686868686869,-9.12121212121212)(906.954545454546,-9.09090909090909)(895.757575757576,-8.95454545454546)(893.26936026936,-8.90909090909091)(892.025252525252,-8.72727272727273)(895.757575757576,-8.63636363636364)(898.245791245791,-8.54545454545455)(910.686868686869,-8.39393939393939)(914.419191919192,-8.36363636363636)(925.616161616162,-8.22727272727273)(933.080808080808,-8.18181818181818)(940.545454545455,-8.15151515151515)(955.474747474747,-8.03030303030303)(970.40404040404,-8.03030303030303)(977.868686868687,-8)(985.333333333333,-7.96969696969697)(992.79797979798,-8)(1000.26262626263,-8.03030303030303)(1007.72727272727,-8)(1015.19191919192,-7.96969696969697)(1030.12121212121,-7.96969696969697)(1045.05050505051,-7.96969696969697)(1048.78282828283,-8)(1059.9797979798,-8.09090909090909)(1074.90909090909,-8.15151515151515)(1082.37373737374,-8.18181818181818)(1089.83838383838,-8.21212121212121)(1104.76767676768,-8.21212121212121)(1119.69696969697,-8.27272727272727)(1134.62626262626,-8.27272727272727)(1149.55555555556,-8.31818181818182)(1164.48484848485,-8.31818181818182)(1179.41414141414,-8.31818181818182)(1194.34343434343,-8.27272727272727)(1209.27272727273,-8.33333333333333)(1224.20202020202,-8.33333333333333)(1231.66666666667,-8.36363636363636)(1239.13131313131,-8.40909090909091)(1254.06060606061,-8.40909090909091)(1268.9898989899,-8.45454545454545)(1280.18686868687,-8.54545454545455)(1283.91919191919,-8.57575757575757)(1296.36026936027,-8.72727272727273)(1298.84848484848,-8.81818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.90909090909091)(459.075757575758,-7.81818181818182)(462.808080808081,-7.78787878787879)(477.737373737374,-7.66666666666667)(485.20202020202,-7.63636363636364)(492.666666666667,-7.60606060606061)(500.131313131313,-7.63636363636364)(507.59595959596,-7.66666666666667)(522.525252525253,-7.66666666666667)(537.454545454546,-7.66666666666667)(544.919191919192,-7.63636363636364)(552.383838383838,-7.60606060606061)(559.848484848485,-7.63636363636364)(567.313131313131,-7.66666666666667)(582.242424242424,-7.78787878787879)(585.974747474747,-7.81818181818182)(597.171717171717,-7.95454545454546)(599.659932659933,-8)(604.636363636364,-8.18181818181818)(608.368686868687,-8.36363636363636)(600.90404040404,-8.54545454545455)(597.171717171717,-8.59090909090909)(585.974747474747,-8.72727272727273)(582.242424242424,-8.75757575757576)(567.313131313131,-8.81818181818182)(552.383838383838,-8.81818181818182)(537.454545454546,-8.81818181818182)(522.525252525253,-8.81818181818182)(507.59595959596,-8.81818181818182)(496.39898989899,-8.72727272727273)(492.666666666667,-8.6969696969697)(477.737373737374,-8.63636363636364)(466.540404040404,-8.54545454545455)(462.808080808081,-8.52272727272727)(447.878787878788,-8.5)(440.414141414141,-8.36363636363636)(435.43771043771,-8.18181818181818)(440.414141414141,-8)(447.878787878788,-7.90909090909091)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (134.363636363636,-8.04545454545455)(138.09595959596,-8)(149.292929292929,-7.90909090909091)(164.222222222222,-7.86363636363636)(179.151515151515,-7.95454545454546)(186.616161616162,-8)(194.080808080808,-8.03030303030303)(206.521885521886,-8.18181818181818)(209.010101010101,-8.22727272727273)(220.207070707071,-8.36363636363636)(209.010101010101,-8.5)(205.277777777778,-8.54545454545455)(194.080808080808,-8.63636363636364)(179.151515151515,-8.63636363636364)(164.222222222222,-8.63636363636364)(149.292929292929,-8.56818181818182)(145.560606060606,-8.54545454545455)(134.363636363636,-8.45454545454545)(126.89898989899,-8.36363636363636)(126.89898989899,-8.18181818181818)(134.363636363636,-8.04545454545455)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182)(373.232323232323,-7.63636363636364)(1313.77777777778,-9.09090909090909)(1015.19191919192,-9.09090909090909)(194.080808080808,-9.09090909090909)(627.030303030303,-8.90909090909091)(223.939393939394,-7.45454545454546)(1104.76767676768,-8.18181818181818)(940.545454545455,-7.27272727272727)(1403.35353535354,-8.18181818181818)(134.363636363636,-8)(432.949494949495,-8.36363636363636)(1059.9797979798,-7.27272727272727)(836.040404040404,-7.81818181818182)(1298.84848484848,-10.1818181818182)(791.252525252525,-9.27272727272727)(1418.28282828283,-9.27272727272727)(940.545454545455,-9.27272727272727)(1104.76767676768,-9.45454545454546)(298.585858585859,-8.72727272727273)(597.171717171717,-7.27272727272727)(447.878787878788,-7.27272727272727)(1298.84848484848,-7.81818181818182)(985.333333333333,-10.1818181818182)(74.6464646464647,-8)(1239.13131313131,-8.72727272727273)(462.808080808081,-9.09090909090909)(1119.69696969697,-10.1818181818182)(776.323232323232,-8.54545454545455)(1000.26262626263,-8.54545454545455)(1388.42424242424,-10.1818181818182)(1179.41414141414,-7.45454545454546)(298.585858585859,-7.81818181818182)(119.434343434343,-8.72727272727273)(865.89898989899,-9.81818181818182)(656.888888888889,-8.72727272727273)(149.292929292929,-7.45454545454546)(1418.28282828283,-8.36363636363636)(955.474747474747,-8)(1224.20202020202,-9.45454545454546)(447.878787878788,-7.81818181818182) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_280.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1448.14141414141,-9)(1450.62962962963,-9.09090909090909)(1455.60606060606,-9.27272727272727)(1460.58249158249,-9.45454545454546)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.77272727272727)(1445.6531986532,-9.81818181818182)(1433.21212121212,-9.93181818181818)(1422.01515151515,-10)(1418.28282828283,-10.030303030303)(1403.35353535354,-10.1136363636364)(1397.75505050505,-10.1818181818182)(1388.42424242424,-10.2954545454545)(1373.49494949495,-10.3409090909091)(1366.0303030303,-10.3636363636364)(1358.56565656566,-10.3939393939394)(1354.83333333333,-10.3636363636364)(1343.63636363636,-10.2954545454545)(1328.70707070707,-10.3090909090909)(1313.77777777778,-10.2878787878788)(1298.84848484848,-10.2878787878788)(1283.91919191919,-10.2878787878788)(1268.9898989899,-10.3181818181818)(1254.06060606061,-10.3484848484848)(1246.59595959596,-10.3636363636364)(1239.13131313131,-10.3818181818182)(1224.20202020202,-10.3818181818182)(1216.73737373737,-10.3636363636364)(1209.27272727273,-10.3484848484848)(1194.34343434343,-10.3181818181818)(1179.41414141414,-10.3484848484848)(1164.48484848485,-10.3484848484848)(1149.55555555556,-10.3484848484848)(1134.62626262626,-10.2878787878788)(1119.69696969697,-10.2878787878788)(1104.76767676768,-10.2575757575758)(1089.83838383838,-10.2878787878788)(1074.90909090909,-10.3181818181818)(1063.71212121212,-10.3636363636364)(1059.9797979798,-10.3818181818182)(1045.05050505051,-10.3818181818182)(1037.58585858586,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.3181818181818)(1000.26262626263,-10.2878787878788)(985.333333333333,-10.2575757575758)(970.40404040404,-10.2)(966.671717171717,-10.1818181818182)(955.474747474747,-10.1363636363636)(940.545454545455,-10.1060606060606)(925.616161616162,-10.1363636363636)(910.686868686869,-10.1272727272727)(895.757575757576,-10.0681818181818)(890.159090909091,-10)(880.828282828283,-9.90909090909091)(865.89898989899,-9.84090909090909)(862.166666666667,-9.81818181818182)(850.969696969697,-9.76363636363636)(836.040404040404,-9.70454545454546)(828.575757575758,-9.63636363636364)(821.111111111111,-9.56818181818182)(811.780303030303,-9.45454545454546)(806.181818181818,-9.38636363636364)(796.85101010101,-9.27272727272727)(791.252525252525,-9.18181818181818)(783.787878787879,-9.09090909090909)(776.323232323232,-8.95454545454546)(773.835016835017,-8.90909090909091)(765.126262626263,-8.72727272727273)(772.590909090909,-8.54545454545455)(776.323232323232,-8.5)(783.787878787879,-8.36363636363636)(791.252525252525,-8.27272727272727)(796.85101010101,-8.18181818181818)(806.181818181818,-8.06818181818182)(813.646464646465,-8)(821.111111111111,-7.93181818181818)(833.552188552189,-7.81818181818182)(836.040404040404,-7.79545454545455)(850.969696969697,-7.69090909090909)(858.434343434343,-7.63636363636364)(865.89898989899,-7.56818181818182)(875.229797979798,-7.45454545454546)(880.828282828283,-7.36363636363636)(895.757575757576,-7.29545454545455)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(914.419191919192,-7.27272727272727)(925.616161616162,-7.31818181818182)(940.545454545455,-7.31818181818182)(951.742424242424,-7.27272727272727)(955.474747474747,-7.25)(970.40404040404,-7.14545454545455)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.15909090909091)(1030.12121212121,-7.24242424242424)(1033.85353535354,-7.27272727272727)(1045.05050505051,-7.31818181818182)(1059.9797979798,-7.31818181818182)(1074.90909090909,-7.31818181818182)(1089.83838383838,-7.31818181818182)(1101.03535353535,-7.27272727272727)(1104.76767676768,-7.24242424242424)(1119.69696969697,-7.24242424242424)(1134.62626262626,-7.24242424242424)(1138.35858585859,-7.27272727272727)(1149.55555555556,-7.32727272727273)(1164.48484848485,-7.29545454545455)(1171.94949494949,-7.27272727272727)(1179.41414141414,-7.25454545454546)(1186.87878787879,-7.27272727272727)(1194.34343434343,-7.31818181818182)(1205.5404040404,-7.45454545454546)(1209.27272727273,-7.46969696969697)(1224.20202020202,-7.53030303030303)(1239.13131313131,-7.5)(1254.06060606061,-7.46969696969697)(1268.9898989899,-7.46969696969697)(1283.91919191919,-7.46969696969697)(1298.84848484848,-7.5)(1313.77777777778,-7.54545454545455)(1328.70707070707,-7.61363636363636)(1332.43939393939,-7.63636363636364)(1343.63636363636,-7.69090909090909)(1358.56565656566,-7.75)(1373.49494949495,-7.79545454545455)(1377.22727272727,-7.81818181818182)(1388.42424242424,-7.88636363636364)(1403.35353535354,-7.96969696969697)(1405.84175084175,-8)(1412.68434343434,-8.18181818181818)(1418.28282828283,-8.31818181818182)(1420.14898989899,-8.36363636363636)(1427.61363636364,-8.54545454545455)(1433.21212121212,-8.68181818181818)(1435.70033670034,-8.72727272727273)(1446.27525252525,-8.90909090909091)(1448.14141414141,-9)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1418.28282828283,-9)(1420.14898989899,-9.09090909090909)(1420.77104377104,-9.27272727272727)(1418.28282828283,-9.36363636363636)(1415.79461279461,-9.45454545454546)(1405.84175084175,-9.63636363636364)(1403.35353535354,-9.68181818181818)(1395.88888888889,-9.81818181818182)(1388.42424242424,-9.87272727272727)(1373.49494949495,-9.93181818181818)(1358.56565656566,-9.96969696969697)(1343.63636363636,-9.96969696969697)(1336.17171717172,-10)(1328.70707070707,-10.0151515151515)(1313.77777777778,-10.0151515151515)(1298.84848484848,-10.0151515151515)(1283.91919191919,-10.0151515151515)(1268.9898989899,-10.0454545454545)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1060606060606)(1209.27272727273,-10.0757575757576)(1194.34343434343,-10.0454545454545)(1179.41414141414,-10.0757575757576)(1164.48484848485,-10.0757575757576)(1149.55555555556,-10.0757575757576)(1134.62626262626,-10.0151515151515)(1119.69696969697,-10.0151515151515)(1112.23232323232,-10)(1104.76767676768,-9.98181818181818)(1097.30303030303,-10)(1089.83838383838,-10.0151515151515)(1074.90909090909,-10.0454545454545)(1059.9797979798,-10.1060606060606)(1045.05050505051,-10.1060606060606)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0454545454545)(1000.26262626263,-10.0151515151515)(992.79797979798,-10)(985.333333333333,-9.98181818181818)(970.40404040404,-9.92424242424243)(955.474747474747,-9.86363636363636)(940.545454545455,-9.83333333333333)(925.616161616162,-9.86363636363636)(910.686868686869,-9.83333333333333)(906.954545454546,-9.81818181818182)(895.757575757576,-9.75)(883.316498316498,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.54545454545455)(850.969696969697,-9.46969696969697)(848.481481481482,-9.45454545454546)(836.040404040404,-9.34090909090909)(830.441919191919,-9.27272727272727)(821.111111111111,-9.12121212121212)(819.244949494949,-9.09090909090909)(808.670033670034,-8.90909090909091)(811.780303030303,-8.72727272727273)(811.780303030303,-8.54545454545455)(819.618181818182,-8.36363636363636)(821.111111111111,-8.33333333333333)(830.441919191919,-8.18181818181818)(836.040404040404,-8.12727272727273)(850.969696969697,-8.02272727272727)(853.457912457912,-8)(865.89898989899,-7.88636363636364)(877.09595959596,-7.81818181818182)(880.828282828283,-7.8)(895.757575757576,-7.70454545454546)(906.954545454546,-7.63636363636364)(910.686868686869,-7.61363636363636)(925.616161616162,-7.59090909090909)(940.545454545455,-7.59090909090909)(955.474747474747,-7.54545454545455)(967.915824915825,-7.45454545454546)(970.40404040404,-7.43939393939394)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1012.7037037037,-7.45454545454546)(1015.19191919192,-7.48484848484849)(1030.12121212121,-7.56818181818182)(1045.05050505051,-7.61818181818182)(1059.9797979798,-7.59090909090909)(1074.90909090909,-7.59090909090909)(1089.83838383838,-7.59090909090909)(1104.76767676768,-7.56818181818182)(1119.69696969697,-7.56818181818182)(1134.62626262626,-7.56818181818182)(1149.55555555556,-7.62121212121212)(1164.48484848485,-7.62121212121212)(1179.41414141414,-7.62121212121212)(1183.14646464646,-7.63636363636364)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.79545454545455)(1224.20202020202,-7.8030303030303)(1239.13131313131,-7.77272727272727)(1254.06060606061,-7.74242424242424)(1268.9898989899,-7.74242424242424)(1283.91919191919,-7.74242424242424)(1298.84848484848,-7.77272727272727)(1310.04545454545,-7.81818181818182)(1313.77777777778,-7.84090909090909)(1328.70707070707,-7.90909090909091)(1343.63636363636,-7.98484848484848)(1346.12457912458,-8)(1358.56565656566,-8.11363636363636)(1369.76262626263,-8.18181818181818)(1373.49494949495,-8.22727272727273)(1384.69191919192,-8.36363636363636)(1388.42424242424,-8.40909090909091)(1394.02272727273,-8.54545454545455)(1403.35353535354,-8.6969696969697)(1405.2196969697,-8.72727272727273)(1415.79461279461,-8.90909090909091)(1418.28282828283,-9)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (358.30303030303,-7.77272727272727)(365.767676767677,-7.63636363636364)(373.232323232323,-7.54545454545455)(388.161616161616,-7.47727272727273)(403.090909090909,-7.47727272727273)(410.555555555556,-7.45454545454546)(418.020202020202,-7.42424242424243)(432.949494949495,-7.40909090909091)(447.878787878788,-7.31818181818182)(455.343434343434,-7.27272727272727)(462.808080808081,-7.24242424242424)(477.737373737374,-7.18181818181818)(492.666666666667,-7.18181818181818)(507.59595959596,-7.12121212121212)(522.525252525253,-7.12121212121212)(537.454545454546,-7.12121212121212)(552.383838383838,-7.18181818181818)(567.313131313131,-7.12121212121212)(582.242424242424,-7.18181818181818)(597.171717171717,-7.24242424242424)(599.659932659933,-7.27272727272727)(612.10101010101,-7.42424242424243)(627.030303030303,-7.40909090909091)(630.762626262626,-7.45454545454546)(629.518518518518,-7.63636363636364)(641.959595959596,-7.78787878787879)(644.447811447811,-7.81818181818182)(654.400673400673,-8)(656.888888888889,-8.09090909090909)(659.377104377104,-8.18181818181818)(659.377104377104,-8.36363636363636)(656.888888888889,-8.45454545454545)(655.022727272727,-8.54545454545455)(652.410101010101,-8.72727272727273)(641.959595959596,-8.88636363636364)(638.227272727273,-8.90909090909091)(627.030303030303,-9)(612.10101010101,-9.06060606060606)(597.171717171717,-9.06818181818182)(589.707070707071,-9.09090909090909)(582.242424242424,-9.12121212121212)(567.313131313131,-9.18181818181818)(556.116161616162,-9.27272727272727)(552.383838383838,-9.3030303030303)(537.454545454546,-9.3030303030303)(522.525252525253,-9.3030303030303)(507.59595959596,-9.3030303030303)(492.666666666667,-9.3030303030303)(485.20202020202,-9.27272727272727)(477.737373737374,-9.24242424242424)(465.296296296296,-9.09090909090909)(462.808080808081,-9.04545454545455)(447.878787878788,-9)(432.949494949495,-8.93939393939394)(429.217171717172,-8.90909090909091)(418.020202020202,-8.81818181818182)(406.823232323232,-8.72727272727273)(403.090909090909,-8.6969696969697)(388.161616161616,-8.57575757575757)(384.429292929293,-8.54545454545455)(373.232323232323,-8.40909090909091)(370.744107744108,-8.36363636363636)(360.791245791246,-8.18181818181818)(360.169191919192,-8)(358.30303030303,-7.90909090909091)(356.436868686869,-7.81818181818182)(358.30303030303,-7.77272727272727)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1283.91919191919,-8.68181818181818)(1286.40740740741,-8.72727272727273)(1291.38383838384,-8.90909090909091)(1286.40740740741,-9.09090909090909)(1283.91919191919,-9.13636363636364)(1272.72222222222,-9.27272727272727)(1268.9898989899,-9.3030303030303)(1254.06060606061,-9.36363636363636)(1239.13131313131,-9.36363636363636)(1224.20202020202,-9.42424242424243)(1209.27272727273,-9.42424242424243)(1194.34343434343,-9.42424242424243)(1179.41414141414,-9.42424242424243)(1171.94949494949,-9.45454545454546)(1164.48484848485,-9.5)(1149.55555555556,-9.54545454545455)(1134.62626262626,-9.54545454545455)(1119.69696969697,-9.48484848484848)(1104.76767676768,-9.48484848484848)(1097.30303030303,-9.45454545454546)(1089.83838383838,-9.40909090909091)(1082.37373737374,-9.45454545454546)(1074.90909090909,-9.48484848484848)(1059.9797979798,-9.48484848484848)(1045.05050505051,-9.48484848484848)(1030.12121212121,-9.48484848484848)(1022.65656565657,-9.45454545454546)(1015.19191919192,-9.40909090909091)(1007.72727272727,-9.45454545454546)(1000.26262626263,-9.5)(985.333333333333,-9.5)(970.40404040404,-9.48484848484848)(966.671717171717,-9.45454545454546)(955.474747474747,-9.36363636363636)(944.277777777778,-9.27272727272727)(940.545454545455,-9.22727272727273)(925.616161616162,-9.18181818181818)(910.686868686869,-9.12121212121212)(906.954545454546,-9.09090909090909)(898.245791245791,-8.90909090909091)(898.245791245791,-8.72727272727273)(903.222222222222,-8.54545454545455)(910.686868686869,-8.40909090909091)(914.419191919192,-8.36363636363636)(925.616161616162,-8.22727272727273)(933.080808080808,-8.18181818181818)(940.545454545455,-8.15151515151515)(955.474747474747,-8.03030303030303)(970.40404040404,-8.03030303030303)(977.868686868687,-8)(985.333333333333,-7.96969696969697)(992.79797979798,-8)(1000.26262626263,-8.03030303030303)(1007.72727272727,-8)(1015.19191919192,-7.96969696969697)(1022.65656565657,-8)(1030.12121212121,-8.04545454545455)(1045.05050505051,-8.04545454545455)(1059.9797979798,-8.15151515151515)(1074.90909090909,-8.15151515151515)(1082.37373737374,-8.18181818181818)(1089.83838383838,-8.22727272727273)(1104.76767676768,-8.22727272727273)(1119.69696969697,-8.31818181818182)(1134.62626262626,-8.27272727272727)(1149.55555555556,-8.31818181818182)(1164.48484848485,-8.31818181818182)(1179.41414141414,-8.31818181818182)(1194.34343434343,-8.27272727272727)(1209.27272727273,-8.33333333333333)(1224.20202020202,-8.33333333333333)(1231.66666666667,-8.36363636363636)(1239.13131313131,-8.40909090909091)(1254.06060606061,-8.40909090909091)(1268.9898989899,-8.51515151515152)(1272.72222222222,-8.54545454545455)(1283.91919191919,-8.68181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (89.5757575757576,-7.86363636363636)(92.0639730639731,-7.81818181818182)(104.505050505051,-7.66666666666667)(106.993265993266,-7.63636363636364)(116.946127946128,-7.45454545454546)(119.434343434343,-7.42424242424243)(134.363636363636,-7.42424242424243)(149.292929292929,-7.36363636363636)(164.222222222222,-7.43181818181818)(179.151515151515,-7.43181818181818)(186.616161616162,-7.45454545454546)(194.080808080808,-7.48484848484849)(209.010101010101,-7.54545454545455)(223.939393939394,-7.60606060606061)(231.40404040404,-7.63636363636364)(238.868686868687,-7.66666666666667)(253.79797979798,-7.72727272727273)(268.727272727273,-7.66666666666667)(283.656565656566,-7.72727272727273)(294.853535353535,-7.81818181818182)(298.585858585859,-7.84848484848485)(307.916666666667,-8)(313.515151515152,-8.13636363636364)(316.003367003367,-8.18181818181818)(319.113636363636,-8.36363636363636)(313.515151515152,-8.5)(311.026936026936,-8.54545454545455)(298.585858585859,-8.6969696969697)(294.853535353535,-8.72727272727273)(283.656565656566,-8.79545454545455)(268.727272727273,-8.87878787878788)(261.262626262626,-8.90909090909091)(253.79797979798,-8.93939393939394)(241.356902356902,-9.09090909090909)(238.868686868687,-9.12121212121212)(223.939393939394,-9.12121212121212)(209.010101010101,-9.12121212121212)(194.080808080808,-9.12121212121212)(179.151515151515,-9.24242424242424)(164.222222222222,-9.24242424242424)(151.781144781145,-9.09090909090909)(149.292929292929,-9.06060606060606)(139.962121212121,-8.90909090909091)(134.363636363636,-8.85454545454546)(119.434343434343,-8.84090909090909)(104.505050505051,-8.75757575757576)(100.772727272727,-8.72727272727273)(89.5757575757576,-8.59090909090909)(87.709595959596,-8.54545454545455)(82.1111111111111,-8.36363636363636)(77.1346801346801,-8.18181818181818)(78.3787878787879,-8)(89.5757575757576,-7.86363636363636)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.90909090909091)(455.343434343434,-7.81818181818182)(462.808080808081,-7.72727272727273)(474.005050505051,-7.63636363636364)(477.737373737374,-7.60606060606061)(492.666666666667,-7.54545454545455)(503.863636363636,-7.63636363636364)(507.59595959596,-7.66666666666667)(522.525252525253,-7.66666666666667)(537.454545454546,-7.66666666666667)(541.186868686869,-7.63636363636364)(552.383838383838,-7.54545454545455)(567.313131313131,-7.59090909090909)(574.777777777778,-7.63636363636364)(582.242424242424,-7.66666666666667)(597.171717171717,-7.78787878787879)(600.90404040404,-7.81818181818182)(612.10101010101,-7.95454545454546)(613.967171717172,-8)(619.565656565657,-8.18181818181818)(619.565656565657,-8.36363636363636)(612.10101010101,-8.5)(608.368686868687,-8.54545454545455)(597.171717171717,-8.63636363636364)(585.974747474747,-8.72727272727273)(582.242424242424,-8.75)(567.313131313131,-8.81818181818182)(552.383838383838,-8.81818181818182)(537.454545454546,-8.81818181818182)(522.525252525253,-8.81818181818182)(507.59595959596,-8.81818181818182)(496.39898989899,-8.72727272727273)(492.666666666667,-8.6969696969697)(477.737373737374,-8.63636363636364)(466.540404040404,-8.54545454545455)(462.808080808081,-8.52272727272727)(447.878787878788,-8.5)(440.414141414141,-8.36363636363636)(435.43771043771,-8.18181818181818)(440.414141414141,-8)(447.878787878788,-7.90909090909091)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (134.363636363636,-8.04545454545455)(138.09595959596,-8)(149.292929292929,-7.90909090909091)(164.222222222222,-7.86363636363636)(179.151515151515,-7.95454545454546)(186.616161616162,-8)(194.080808080808,-8.03030303030303)(209.010101010101,-8.15151515151515)(212.742424242424,-8.18181818181818)(223.939393939394,-8.31818181818182)(225.805555555556,-8.36363636363636)(223.939393939394,-8.45454545454545)(216.474747474747,-8.54545454545455)(209.010101010101,-8.57575757575757)(194.080808080808,-8.63636363636364)(179.151515151515,-8.63636363636364)(164.222222222222,-8.63636363636364)(149.292929292929,-8.56818181818182)(145.560606060606,-8.54545454545455)(134.363636363636,-8.45454545454545)(126.89898989899,-8.36363636363636)(126.89898989899,-8.18181818181818)(134.363636363636,-8.04545454545455)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182)(373.232323232323,-7.63636363636364)(1313.77777777778,-9.09090909090909)(1015.19191919192,-9.09090909090909)(194.080808080808,-9.09090909090909)(627.030303030303,-8.90909090909091)(223.939393939394,-7.45454545454546)(1104.76767676768,-8.18181818181818)(940.545454545455,-7.27272727272727)(1403.35353535354,-8.18181818181818)(134.363636363636,-8)(432.949494949495,-8.36363636363636)(1059.9797979798,-7.27272727272727)(836.040404040404,-7.81818181818182)(1298.84848484848,-10.1818181818182)(791.252525252525,-9.27272727272727)(1418.28282828283,-9.27272727272727)(940.545454545455,-9.27272727272727)(1104.76767676768,-9.45454545454546)(298.585858585859,-8.72727272727273)(597.171717171717,-7.27272727272727)(447.878787878788,-7.27272727272727)(1298.84848484848,-7.81818181818182)(985.333333333333,-10.1818181818182)(74.6464646464647,-8)(1239.13131313131,-8.72727272727273)(462.808080808081,-9.09090909090909)(1119.69696969697,-10.1818181818182)(776.323232323232,-8.54545454545455)(1000.26262626263,-8.54545454545455)(1388.42424242424,-10.1818181818182)(1179.41414141414,-7.45454545454546)(298.585858585859,-7.81818181818182)(119.434343434343,-8.72727272727273)(865.89898989899,-9.81818181818182)(656.888888888889,-8.72727272727273)(149.292929292929,-7.45454545454546)(1418.28282828283,-8.36363636363636)(955.474747474747,-8)(1224.20202020202,-9.45454545454546)(447.878787878788,-7.81818181818182)(612.10101010101,-8)(1104.76767676768,-8.54545454545455)(850.969696969697,-7.63636363636364)(895.757575757576,-8.72727272727273)(1224.20202020202,-10.1818181818182)(223.939393939394,-8.36363636363636)(1045.05050505051,-7.27272727272727)(597.171717171717,-9.09090909090909)(1448.14141414141,-8.90909090909091)(1030.12121212121,-9.45454545454546)(1328.70707070707,-7.63636363636364)(373.232323232323,-8.54545454545455)(1283.91919191919,-8.54545454545455)(1448.14141414141,-9.63636363636364)(955.474747474747,-7.27272727272727)(1059.9797979798,-10.1818181818182)(791.252525252525,-8.18181818181818)(1283.91919191919,-9.27272727272727)(910.686868686869,-10)(582.242424242424,-7.27272727272727) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_300.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1448.14141414141,-9)(1450.62962962963,-9.09090909090909)(1455.60606060606,-9.27272727272727)(1460.58249158249,-9.45454545454546)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.77272727272727)(1445.6531986532,-9.81818181818182)(1433.21212121212,-9.93181818181818)(1422.01515151515,-10)(1418.28282828283,-10.030303030303)(1403.35353535354,-10.1136363636364)(1397.75505050505,-10.1818181818182)(1388.42424242424,-10.2954545454545)(1373.49494949495,-10.3409090909091)(1366.0303030303,-10.3636363636364)(1358.56565656566,-10.3939393939394)(1351.10101010101,-10.3636363636364)(1343.63636363636,-10.3454545454545)(1328.70707070707,-10.3484848484848)(1313.77777777778,-10.3181818181818)(1298.84848484848,-10.2878787878788)(1283.91919191919,-10.2878787878788)(1268.9898989899,-10.3181818181818)(1254.06060606061,-10.3484848484848)(1246.59595959596,-10.3636363636364)(1239.13131313131,-10.3818181818182)(1224.20202020202,-10.3818181818182)(1216.73737373737,-10.3636363636364)(1209.27272727273,-10.3484848484848)(1194.34343434343,-10.2878787878788)(1179.41414141414,-10.3181818181818)(1164.48484848485,-10.3181818181818)(1149.55555555556,-10.3484848484848)(1134.62626262626,-10.2878787878788)(1119.69696969697,-10.2878787878788)(1104.76767676768,-10.2575757575758)(1089.83838383838,-10.2878787878788)(1074.90909090909,-10.3181818181818)(1063.71212121212,-10.3636363636364)(1059.9797979798,-10.3818181818182)(1045.05050505051,-10.3818181818182)(1037.58585858586,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.3181818181818)(1000.26262626263,-10.2878787878788)(985.333333333333,-10.2575757575758)(970.40404040404,-10.2)(966.671717171717,-10.1818181818182)(955.474747474747,-10.1363636363636)(940.545454545455,-10.1060606060606)(925.616161616162,-10.1363636363636)(910.686868686869,-10.1272727272727)(895.757575757576,-10.0681818181818)(890.159090909091,-10)(880.828282828283,-9.90909090909091)(865.89898989899,-9.84090909090909)(862.166666666667,-9.81818181818182)(850.969696969697,-9.76363636363636)(836.040404040404,-9.70454545454546)(828.575757575758,-9.63636363636364)(821.111111111111,-9.56818181818182)(811.780303030303,-9.45454545454546)(806.181818181818,-9.4)(793.118686868687,-9.27272727272727)(791.252525252525,-9.25)(778.189393939394,-9.09090909090909)(776.323232323232,-9.04545454545455)(770.724747474747,-8.90909090909091)(765.126262626263,-8.72727272727273)(772.590909090909,-8.54545454545455)(776.323232323232,-8.5)(783.787878787879,-8.36363636363636)(791.252525252525,-8.27272727272727)(796.85101010101,-8.18181818181818)(806.181818181818,-8.06818181818182)(813.646464646465,-8)(821.111111111111,-7.93181818181818)(833.552188552189,-7.81818181818182)(836.040404040404,-7.79545454545455)(850.969696969697,-7.69090909090909)(858.434343434343,-7.63636363636364)(865.89898989899,-7.56818181818182)(875.229797979798,-7.45454545454546)(880.828282828283,-7.36363636363636)(895.757575757576,-7.29545454545455)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(914.419191919192,-7.27272727272727)(925.616161616162,-7.31818181818182)(940.545454545455,-7.31818181818182)(951.742424242424,-7.27272727272727)(955.474747474747,-7.25)(970.40404040404,-7.14545454545455)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.13636363636364)(1015.19191919192,-7.25)(1018.92424242424,-7.27272727272727)(1030.12121212121,-7.31818181818182)(1045.05050505051,-7.34848484848485)(1059.9797979798,-7.31818181818182)(1074.90909090909,-7.31818181818182)(1089.83838383838,-7.31818181818182)(1101.03535353535,-7.27272727272727)(1104.76767676768,-7.24242424242424)(1112.23232323232,-7.27272727272727)(1119.69696969697,-7.28787878787879)(1134.62626262626,-7.28787878787879)(1149.55555555556,-7.4)(1164.48484848485,-7.34090909090909)(1179.41414141414,-7.3030303030303)(1194.34343434343,-7.31818181818182)(1205.5404040404,-7.45454545454546)(1209.27272727273,-7.46969696969697)(1224.20202020202,-7.56060606060606)(1239.13131313131,-7.53030303030303)(1254.06060606061,-7.5)(1268.9898989899,-7.46969696969697)(1283.91919191919,-7.46969696969697)(1298.84848484848,-7.5)(1313.77777777778,-7.54545454545455)(1328.70707070707,-7.61363636363636)(1332.43939393939,-7.63636363636364)(1343.63636363636,-7.69090909090909)(1358.56565656566,-7.78787878787879)(1366.0303030303,-7.81818181818182)(1373.49494949495,-7.84090909090909)(1388.42424242424,-7.93181818181818)(1403.35353535354,-7.96969696969697)(1405.84175084175,-8)(1412.68434343434,-8.18181818181818)(1418.28282828283,-8.31818181818182)(1420.14898989899,-8.36363636363636)(1427.61363636364,-8.54545454545455)(1433.21212121212,-8.68181818181818)(1435.70033670034,-8.72727272727273)(1446.27525252525,-8.90909090909091)(1448.14141414141,-9)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1418.28282828283,-9)(1420.14898989899,-9.09090909090909)(1420.77104377104,-9.27272727272727)(1418.28282828283,-9.36363636363636)(1415.79461279461,-9.45454545454546)(1405.84175084175,-9.63636363636364)(1403.35353535354,-9.68181818181818)(1395.88888888889,-9.81818181818182)(1388.42424242424,-9.87272727272727)(1373.49494949495,-9.93181818181818)(1362.29797979798,-10)(1358.56565656566,-10.0227272727273)(1343.63636363636,-10.0454545454545)(1328.70707070707,-10.0757575757576)(1313.77777777778,-10.0454545454545)(1298.84848484848,-10.0151515151515)(1283.91919191919,-10.0151515151515)(1268.9898989899,-10.0454545454545)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1060606060606)(1209.27272727273,-10.0757575757576)(1194.34343434343,-10.0151515151515)(1179.41414141414,-10.0454545454545)(1164.48484848485,-10.0454545454545)(1149.55555555556,-10.0757575757576)(1134.62626262626,-10.0151515151515)(1119.69696969697,-10.0151515151515)(1112.23232323232,-10)(1104.76767676768,-9.98181818181818)(1097.30303030303,-10)(1089.83838383838,-10.0151515151515)(1074.90909090909,-10.0454545454545)(1059.9797979798,-10.1060606060606)(1045.05050505051,-10.1060606060606)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0454545454545)(1000.26262626263,-10.0151515151515)(992.79797979798,-10)(985.333333333333,-9.98181818181818)(970.40404040404,-9.92424242424243)(955.474747474747,-9.86363636363636)(940.545454545455,-9.83333333333333)(925.616161616162,-9.86363636363636)(910.686868686869,-9.83333333333333)(906.954545454546,-9.81818181818182)(895.757575757576,-9.75)(883.316498316498,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.54545454545455)(850.969696969697,-9.46969696969697)(848.481481481482,-9.45454545454546)(836.040404040404,-9.34090909090909)(830.441919191919,-9.27272727272727)(821.111111111111,-9.15909090909091)(813.646464646465,-9.09090909090909)(806.181818181818,-9)(800.583333333333,-8.90909090909091)(806.181818181818,-8.77272727272727)(808.04797979798,-8.72727272727273)(811.780303030303,-8.54545454545455)(819.618181818182,-8.36363636363636)(821.111111111111,-8.33333333333333)(830.441919191919,-8.18181818181818)(836.040404040404,-8.12727272727273)(850.969696969697,-8.02272727272727)(853.457912457912,-8)(865.89898989899,-7.88636363636364)(877.09595959596,-7.81818181818182)(880.828282828283,-7.8)(895.757575757576,-7.70454545454546)(906.954545454546,-7.63636363636364)(910.686868686869,-7.61363636363636)(925.616161616162,-7.59090909090909)(940.545454545455,-7.59090909090909)(955.474747474747,-7.54545454545455)(967.915824915825,-7.45454545454546)(970.40404040404,-7.43939393939394)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.40909090909091)(1005.86111111111,-7.45454545454546)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.59090909090909)(1045.05050505051,-7.62121212121212)(1059.9797979798,-7.59090909090909)(1074.90909090909,-7.59090909090909)(1089.83838383838,-7.59090909090909)(1104.76767676768,-7.56818181818182)(1119.69696969697,-7.61363636363636)(1134.62626262626,-7.61363636363636)(1138.35858585859,-7.63636363636364)(1149.55555555556,-7.69090909090909)(1164.48484848485,-7.66666666666667)(1179.41414141414,-7.68181818181818)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.79545454545455)(1216.73737373737,-7.81818181818182)(1224.20202020202,-7.83636363636364)(1231.66666666667,-7.81818181818182)(1239.13131313131,-7.8030303030303)(1254.06060606061,-7.77272727272727)(1268.9898989899,-7.74242424242424)(1283.91919191919,-7.74242424242424)(1298.84848484848,-7.77272727272727)(1310.04545454545,-7.81818181818182)(1313.77777777778,-7.84090909090909)(1328.70707070707,-7.90909090909091)(1343.63636363636,-7.98484848484848)(1345.50252525253,-8)(1358.56565656566,-8.15909090909091)(1362.29797979798,-8.18181818181818)(1373.49494949495,-8.27272727272727)(1384.69191919192,-8.36363636363636)(1388.42424242424,-8.40909090909091)(1394.02272727273,-8.54545454545455)(1403.35353535354,-8.6969696969697)(1405.2196969697,-8.72727272727273)(1415.79461279461,-8.90909090909091)(1418.28282828283,-9)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (358.30303030303,-7.77272727272727)(365.767676767677,-7.63636363636364)(373.232323232323,-7.54545454545455)(388.161616161616,-7.47727272727273)(403.090909090909,-7.47727272727273)(410.555555555556,-7.45454545454546)(418.020202020202,-7.42424242424243)(432.949494949495,-7.40909090909091)(444.146464646465,-7.27272727272727)(447.878787878788,-7.24242424242424)(462.808080808081,-7.18181818181818)(477.737373737374,-7.12121212121212)(492.666666666667,-7.15909090909091)(507.59595959596,-7.10909090909091)(522.525252525253,-7.10909090909091)(537.454545454546,-7.11363636363636)(552.383838383838,-7.18181818181818)(567.313131313131,-7.12121212121212)(582.242424242424,-7.18181818181818)(597.171717171717,-7.24242424242424)(599.659932659933,-7.27272727272727)(612.10101010101,-7.42424242424243)(627.030303030303,-7.40909090909091)(630.762626262626,-7.45454545454546)(629.518518518518,-7.63636363636364)(640.093434343434,-7.81818181818182)(641.959595959596,-7.86363636363636)(649.424242424242,-8)(654.400673400673,-8.18181818181818)(656.888888888889,-8.27272727272727)(659.377104377104,-8.36363636363636)(656.888888888889,-8.45454545454545)(655.022727272727,-8.54545454545455)(652.410101010101,-8.72727272727273)(641.959595959596,-8.88636363636364)(638.227272727273,-8.90909090909091)(627.030303030303,-9)(612.10101010101,-9.06818181818182)(597.171717171717,-9.07272727272727)(589.707070707071,-9.09090909090909)(582.242424242424,-9.12121212121212)(567.313131313131,-9.18181818181818)(556.116161616162,-9.27272727272727)(552.383838383838,-9.3030303030303)(537.454545454546,-9.3030303030303)(522.525252525253,-9.3030303030303)(507.59595959596,-9.3030303030303)(492.666666666667,-9.3030303030303)(485.20202020202,-9.27272727272727)(477.737373737374,-9.24242424242424)(465.296296296296,-9.09090909090909)(462.808080808081,-9.06060606060606)(447.878787878788,-8.97727272727273)(436.681818181818,-8.90909090909091)(432.949494949495,-8.87878787878788)(418.020202020202,-8.75757575757576)(414.287878787879,-8.72727272727273)(403.090909090909,-8.63636363636364)(391.893939393939,-8.54545454545455)(388.161616161616,-8.51515151515152)(375.720538720539,-8.36363636363636)(373.232323232323,-8.33333333333333)(360.791245791246,-8.18181818181818)(360.169191919192,-8)(358.30303030303,-7.90909090909091)(356.436868686869,-7.81818181818182)(358.30303030303,-7.77272727272727)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1283.91919191919,-8.68181818181818)(1286.40740740741,-8.72727272727273)(1291.38383838384,-8.90909090909091)(1283.91919191919,-9.04545454545455)(1281.43097643098,-9.09090909090909)(1268.9898989899,-9.24242424242424)(1261.52525252525,-9.27272727272727)(1254.06060606061,-9.3030303030303)(1239.13131313131,-9.36363636363636)(1224.20202020202,-9.42424242424243)(1209.27272727273,-9.42424242424243)(1194.34343434343,-9.42424242424243)(1179.41414141414,-9.42424242424243)(1164.48484848485,-9.42424242424243)(1157.0202020202,-9.45454545454546)(1149.55555555556,-9.48484848484848)(1134.62626262626,-9.48484848484848)(1119.69696969697,-9.48484848484848)(1104.76767676768,-9.48484848484848)(1097.30303030303,-9.45454545454546)(1089.83838383838,-9.40909090909091)(1082.37373737374,-9.45454545454546)(1074.90909090909,-9.48484848484848)(1059.9797979798,-9.48484848484848)(1045.05050505051,-9.48484848484848)(1030.12121212121,-9.48484848484848)(1022.65656565657,-9.45454545454546)(1015.19191919192,-9.40909090909091)(1007.72727272727,-9.45454545454546)(1000.26262626263,-9.5)(992.79797979798,-9.45454545454546)(985.333333333333,-9.42424242424243)(970.40404040404,-9.42424242424243)(955.474747474747,-9.3030303030303)(948.010101010101,-9.27272727272727)(940.545454545455,-9.22727272727273)(925.616161616162,-9.12121212121212)(918.151515151515,-9.09090909090909)(910.686868686869,-9.04545454545455)(903.222222222222,-8.90909090909091)(898.245791245791,-8.72727272727273)(903.222222222222,-8.54545454545455)(910.686868686869,-8.40909090909091)(914.419191919192,-8.36363636363636)(925.616161616162,-8.22727272727273)(933.080808080808,-8.18181818181818)(940.545454545455,-8.15151515151515)(955.474747474747,-8.09090909090909)(970.40404040404,-8.09090909090909)(985.333333333333,-8.03030303030303)(1000.26262626263,-8.03030303030303)(1015.19191919192,-8.04545454545455)(1030.12121212121,-8.13636363636364)(1045.05050505051,-8.13636363636364)(1059.9797979798,-8.15151515151515)(1074.90909090909,-8.15151515151515)(1082.37373737374,-8.18181818181818)(1089.83838383838,-8.22727272727273)(1104.76767676768,-8.22727272727273)(1119.69696969697,-8.31818181818182)(1134.62626262626,-8.27272727272727)(1149.55555555556,-8.31818181818182)(1157.0202020202,-8.36363636363636)(1164.48484848485,-8.39393939393939)(1179.41414141414,-8.39393939393939)(1186.87878787879,-8.36363636363636)(1194.34343434343,-8.33333333333333)(1209.27272727273,-8.33333333333333)(1216.73737373737,-8.36363636363636)(1224.20202020202,-8.40909090909091)(1239.13131313131,-8.5)(1254.06060606061,-8.5)(1268.9898989899,-8.51515151515152)(1272.72222222222,-8.54545454545455)(1283.91919191919,-8.68181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-7.96969696969697)(87.0875420875421,-7.81818181818182)(89.5757575757576,-7.77272727272727)(100.772727272727,-7.63636363636364)(104.505050505051,-7.59090909090909)(111.969696969697,-7.45454545454546)(119.434343434343,-7.38636363636364)(134.363636363636,-7.42424242424243)(149.292929292929,-7.36363636363636)(164.222222222222,-7.43181818181818)(179.151515151515,-7.43181818181818)(186.616161616162,-7.45454545454546)(194.080808080808,-7.48484848484849)(209.010101010101,-7.54545454545455)(223.939393939394,-7.60606060606061)(231.40404040404,-7.63636363636364)(238.868686868687,-7.66666666666667)(253.79797979798,-7.66666666666667)(261.262626262626,-7.63636363636364)(268.727272727273,-7.61818181818182)(276.191919191919,-7.63636363636364)(283.656565656566,-7.66666666666667)(296.097643097643,-7.81818181818182)(298.585858585859,-7.84848484848485)(307.916666666667,-8)(313.515151515152,-8.13636363636364)(316.003367003367,-8.18181818181818)(319.113636363636,-8.36363636363636)(313.515151515152,-8.5)(311.026936026936,-8.54545454545455)(298.585858585859,-8.6969696969697)(294.853535353535,-8.72727272727273)(283.656565656566,-8.79545454545455)(271.215488215488,-8.90909090909091)(268.727272727273,-8.93939393939394)(253.79797979798,-9)(246.333333333333,-9.09090909090909)(238.868686868687,-9.15909090909091)(223.939393939394,-9.12121212121212)(209.010101010101,-9.12121212121212)(194.080808080808,-9.12121212121212)(179.151515151515,-9.24242424242424)(164.222222222222,-9.25)(149.292929292929,-9.12121212121212)(146.804713804714,-9.09090909090909)(135.856565656566,-8.90909090909091)(134.363636363636,-8.89393939393939)(119.434343434343,-8.85454545454546)(104.505050505051,-8.75757575757576)(100.772727272727,-8.72727272727273)(89.5757575757576,-8.59090909090909)(87.709595959596,-8.54545454545455)(77.1346801346801,-8.36363636363636)(74.6464646464647,-8.27272727272727)(72.1582491582492,-8.18181818181818)(72.1582491582492,-8)(74.6464646464647,-7.96969696969697)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.86363636363636)(450.367003367003,-7.81818181818182)(462.808080808081,-7.66666666666667)(466.540404040404,-7.63636363636364)(477.737373737374,-7.5)(492.666666666667,-7.48484848484849)(507.59595959596,-7.5)(522.525252525253,-7.5)(537.454545454546,-7.59090909090909)(552.383838383838,-7.54545454545455)(567.313131313131,-7.59090909090909)(574.777777777778,-7.63636363636364)(582.242424242424,-7.66666666666667)(597.171717171717,-7.78787878787879)(600.90404040404,-7.81818181818182)(612.10101010101,-7.95454545454546)(613.967171717172,-8)(619.565656565657,-8.18181818181818)(619.565656565657,-8.36363636363636)(614.589225589226,-8.54545454545455)(612.10101010101,-8.63636363636364)(597.171717171717,-8.6969696969697)(593.439393939394,-8.72727272727273)(582.242424242424,-8.79545454545455)(567.313131313131,-8.81818181818182)(552.383838383838,-8.81818181818182)(537.454545454546,-8.81818181818182)(522.525252525253,-8.81818181818182)(507.59595959596,-8.81818181818182)(496.39898989899,-8.72727272727273)(492.666666666667,-8.6969696969697)(477.737373737374,-8.6969696969697)(462.808080808081,-8.57575757575757)(447.878787878788,-8.56818181818182)(445.390572390572,-8.54545454545455)(440.414141414141,-8.36363636363636)(435.43771043771,-8.18181818181818)(440.414141414141,-8)(447.878787878788,-7.86363636363636)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (119.434343434343,-8.15151515151515)(131.875420875421,-8)(134.363636363636,-7.96969696969697)(149.292929292929,-7.90909090909091)(164.222222222222,-7.86363636363636)(179.151515151515,-7.86363636363636)(194.080808080808,-7.86363636363636)(209.010101010101,-7.96969696969697)(212.742424242424,-8)(223.939393939394,-8.13636363636364)(225.805555555556,-8.18181818181818)(233.270202020202,-8.36363636363636)(227.671717171717,-8.54545454545455)(223.939393939394,-8.59090909090909)(209.010101010101,-8.6969696969697)(201.545454545455,-8.72727272727273)(194.080808080808,-8.75)(179.151515151515,-8.86363636363636)(164.222222222222,-8.86363636363636)(153.025252525253,-8.72727272727273)(149.292929292929,-8.6969696969697)(134.363636363636,-8.56818181818182)(126.89898989899,-8.54545454545455)(119.434343434343,-8.5)(113.835858585859,-8.36363636363636)(116.946127946128,-8.18181818181818)(119.434343434343,-8.15151515151515)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182)(373.232323232323,-7.63636363636364)(1313.77777777778,-9.09090909090909)(1015.19191919192,-9.09090909090909)(194.080808080808,-9.09090909090909)(627.030303030303,-8.90909090909091)(223.939393939394,-7.45454545454546)(1104.76767676768,-8.18181818181818)(940.545454545455,-7.27272727272727)(1403.35353535354,-8.18181818181818)(134.363636363636,-8)(432.949494949495,-8.36363636363636)(1059.9797979798,-7.27272727272727)(836.040404040404,-7.81818181818182)(1298.84848484848,-10.1818181818182)(791.252525252525,-9.27272727272727)(1418.28282828283,-9.27272727272727)(940.545454545455,-9.27272727272727)(1104.76767676768,-9.45454545454546)(298.585858585859,-8.72727272727273)(597.171717171717,-7.27272727272727)(447.878787878788,-7.27272727272727)(1298.84848484848,-7.81818181818182)(985.333333333333,-10.1818181818182)(74.6464646464647,-8)(1239.13131313131,-8.72727272727273)(462.808080808081,-9.09090909090909)(1119.69696969697,-10.1818181818182)(776.323232323232,-8.54545454545455)(1000.26262626263,-8.54545454545455)(1388.42424242424,-10.1818181818182)(1179.41414141414,-7.45454545454546)(298.585858585859,-7.81818181818182)(119.434343434343,-8.72727272727273)(865.89898989899,-9.81818181818182)(656.888888888889,-8.72727272727273)(149.292929292929,-7.45454545454546)(1418.28282828283,-8.36363636363636)(955.474747474747,-8)(1224.20202020202,-9.45454545454546)(447.878787878788,-7.81818181818182)(612.10101010101,-8)(1104.76767676768,-8.54545454545455)(850.969696969697,-7.63636363636364)(895.757575757576,-8.72727272727273)(1224.20202020202,-10.1818181818182)(223.939393939394,-8.36363636363636)(1045.05050505051,-7.27272727272727)(597.171717171717,-9.09090909090909)(1448.14141414141,-8.90909090909091)(1030.12121212121,-9.45454545454546)(1328.70707070707,-7.63636363636364)(373.232323232323,-8.54545454545455)(1283.91919191919,-8.54545454545455)(1448.14141414141,-9.63636363636364)(955.474747474747,-7.27272727272727)(1059.9797979798,-10.1818181818182)(791.252525252525,-8.18181818181818)(1283.91919191919,-9.27272727272727)(910.686868686869,-10)(582.242424242424,-7.27272727272727)(253.79797979798,-8.90909090909091)(104.505050505051,-7.63636363636364)(1179.41414141414,-8.36363636363636)(1134.62626262626,-7.45454545454546)(462.808080808081,-8.72727272727273)(1030.12121212121,-8)(656.888888888889,-8)(1328.70707070707,-10.1818181818182)(791.252525252525,-9.09090909090909)(462.808080808081,-7.27272727272727)(74.6464646464647,-8.18181818181818)(1149.55555555556,-9.45454545454546)(149.292929292929,-8.90909090909091)(1239.13131313131,-7.63636363636364)(268.727272727273,-7.81818181818182)(910.686868686869,-9.09090909090909)(1373.49494949495,-8)(1059.9797979798,-8.72727272727273)(1179.41414141414,-10.1818181818182)(597.171717171717,-8.72727272727273) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_320.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1448.14141414141,-9.18181818181818)(1450.62962962963,-9.27272727272727)(1460.58249158249,-9.45454545454546)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.77272727272727)(1446.27525252525,-9.81818181818182)(1433.21212121212,-9.97727272727273)(1429.4797979798,-10)(1418.28282828283,-10.0909090909091)(1403.35353535354,-10.1590909090909)(1400.86531986532,-10.1818181818182)(1388.42424242424,-10.2954545454545)(1373.49494949495,-10.3409090909091)(1366.0303030303,-10.3636363636364)(1358.56565656566,-10.3939393939394)(1351.10101010101,-10.3636363636364)(1343.63636363636,-10.3454545454545)(1328.70707070707,-10.3484848484848)(1313.77777777778,-10.3181818181818)(1298.84848484848,-10.2575757575758)(1283.91919191919,-10.2575757575758)(1268.9898989899,-10.2878787878788)(1254.06060606061,-10.3484848484848)(1246.59595959596,-10.3636363636364)(1239.13131313131,-10.3818181818182)(1224.20202020202,-10.3818181818182)(1216.73737373737,-10.3636363636364)(1209.27272727273,-10.3484848484848)(1194.34343434343,-10.2878787878788)(1179.41414141414,-10.3181818181818)(1164.48484848485,-10.3181818181818)(1149.55555555556,-10.3484848484848)(1134.62626262626,-10.2878787878788)(1119.69696969697,-10.2878787878788)(1104.76767676768,-10.2575757575758)(1089.83838383838,-10.2878787878788)(1074.90909090909,-10.3181818181818)(1063.71212121212,-10.3636363636364)(1059.9797979798,-10.3818181818182)(1045.05050505051,-10.3818181818182)(1037.58585858586,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2878787878788)(1000.26262626263,-10.2575757575758)(985.333333333333,-10.2272727272727)(970.40404040404,-10.2)(966.671717171717,-10.1818181818182)(955.474747474747,-10.1363636363636)(940.545454545455,-10.1060606060606)(925.616161616162,-10.1363636363636)(910.686868686869,-10.1272727272727)(895.757575757576,-10.0681818181818)(890.159090909091,-10)(880.828282828283,-9.90909090909091)(865.89898989899,-9.84090909090909)(863.410774410775,-9.81818181818182)(850.969696969697,-9.72727272727273)(836.040404040404,-9.65909090909091)(833.552188552189,-9.63636363636364)(821.111111111111,-9.52272727272727)(813.646464646465,-9.45454545454546)(806.181818181818,-9.4)(793.118686868687,-9.27272727272727)(791.252525252525,-9.25)(778.189393939394,-9.09090909090909)(776.323232323232,-9)(774.457070707071,-8.90909090909091)(772.590909090909,-8.72727272727273)(776.323232323232,-8.63636363636364)(778.189393939394,-8.54545454545455)(783.787878787879,-8.36363636363636)(791.252525252525,-8.27272727272727)(796.85101010101,-8.18181818181818)(806.181818181818,-8.06818181818182)(813.646464646465,-8)(821.111111111111,-7.93181818181818)(833.552188552189,-7.81818181818182)(836.040404040404,-7.79545454545455)(850.969696969697,-7.69090909090909)(858.434343434343,-7.63636363636364)(865.89898989899,-7.56818181818182)(872.119528619529,-7.45454545454546)(880.828282828283,-7.29545454545455)(888.292929292929,-7.27272727272727)(895.757575757576,-7.24242424242424)(910.686868686869,-7.20454545454546)(918.151515151515,-7.27272727272727)(925.616161616162,-7.31818181818182)(940.545454545455,-7.28787878787879)(948.010101010101,-7.27272727272727)(955.474747474747,-7.25454545454546)(970.40404040404,-7.16666666666667)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.20454545454546)(1022.65656565657,-7.27272727272727)(1030.12121212121,-7.31818181818182)(1045.05050505051,-7.34848484848485)(1059.9797979798,-7.31818181818182)(1074.90909090909,-7.31818181818182)(1089.83838383838,-7.34848484848485)(1104.76767676768,-7.31818181818182)(1119.69696969697,-7.34848484848485)(1134.62626262626,-7.34848484848485)(1149.55555555556,-7.43636363636364)(1164.48484848485,-7.38636363636364)(1179.41414141414,-7.3030303030303)(1194.34343434343,-7.31818181818182)(1205.5404040404,-7.45454545454546)(1209.27272727273,-7.46969696969697)(1224.20202020202,-7.56060606060606)(1239.13131313131,-7.53030303030303)(1254.06060606061,-7.5)(1268.9898989899,-7.46969696969697)(1283.91919191919,-7.46969696969697)(1298.84848484848,-7.5)(1313.77777777778,-7.54545454545455)(1328.70707070707,-7.61363636363636)(1332.43939393939,-7.63636363636364)(1343.63636363636,-7.69090909090909)(1358.56565656566,-7.78787878787879)(1366.0303030303,-7.81818181818182)(1373.49494949495,-7.84090909090909)(1388.42424242424,-7.93181818181818)(1403.35353535354,-7.96969696969697)(1405.84175084175,-8)(1412.68434343434,-8.18181818181818)(1418.28282828283,-8.31818181818182)(1420.14898989899,-8.36363636363636)(1423.88131313131,-8.54545454545455)(1431.71919191919,-8.72727272727273)(1433.21212121212,-8.77272727272727)(1438.81060606061,-8.90909090909091)(1446.64848484848,-9.09090909090909)(1448.14141414141,-9.18181818181818)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1418.28282828283,-9.04545454545455)(1419.77575757576,-9.09090909090909)(1423.88131313131,-9.27272727272727)(1422.01515151515,-9.45454545454546)(1418.28282828283,-9.5)(1410.81818181818,-9.63636363636364)(1403.35353535354,-9.77272727272727)(1399.62121212121,-9.81818181818182)(1388.42424242424,-9.87272727272727)(1373.49494949495,-9.93181818181818)(1362.29797979798,-10)(1358.56565656566,-10.0227272727273)(1343.63636363636,-10.0454545454545)(1328.70707070707,-10.0757575757576)(1313.77777777778,-10.0454545454545)(1302.58080808081,-10)(1298.84848484848,-9.98181818181818)(1283.91919191919,-9.98181818181818)(1276.45454545455,-10)(1268.9898989899,-10.0151515151515)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1060606060606)(1209.27272727273,-10.0757575757576)(1194.34343434343,-10.0151515151515)(1179.41414141414,-10.0454545454545)(1164.48484848485,-10.0454545454545)(1149.55555555556,-10.0757575757576)(1134.62626262626,-10.0151515151515)(1119.69696969697,-10.0151515151515)(1112.23232323232,-10)(1104.76767676768,-9.98181818181818)(1097.30303030303,-10)(1089.83838383838,-10.0151515151515)(1074.90909090909,-10.0454545454545)(1059.9797979798,-10.1060606060606)(1045.05050505051,-10.1060606060606)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0151515151515)(1007.72727272727,-10)(1000.26262626263,-9.98181818181818)(985.333333333333,-9.95454545454546)(970.40404040404,-9.92424242424243)(955.474747474747,-9.86363636363636)(940.545454545455,-9.83333333333333)(925.616161616162,-9.86363636363636)(910.686868686869,-9.83333333333333)(906.954545454546,-9.81818181818182)(895.757575757576,-9.75)(883.316498316498,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.54545454545455)(853.457912457912,-9.45454545454546)(850.969696969697,-9.43181818181818)(836.040404040404,-9.32727272727273)(830.441919191919,-9.27272727272727)(821.111111111111,-9.15909090909091)(813.646464646465,-9.09090909090909)(806.181818181818,-9)(801.70303030303,-8.90909090909091)(806.181818181818,-8.77272727272727)(808.04797979798,-8.72727272727273)(811.780303030303,-8.54545454545455)(819.618181818182,-8.36363636363636)(821.111111111111,-8.33333333333333)(830.441919191919,-8.18181818181818)(836.040404040404,-8.12727272727273)(850.969696969697,-8.02272727272727)(853.457912457912,-8)(865.89898989899,-7.88636363636364)(873.363636363636,-7.81818181818182)(880.828282828283,-7.75)(893.26936026936,-7.63636363636364)(895.757575757576,-7.61363636363636)(910.686868686869,-7.52272727272727)(925.616161616162,-7.59090909090909)(940.545454545455,-7.56060606060606)(955.474747474747,-7.53030303030303)(967.915824915825,-7.45454545454546)(970.40404040404,-7.43939393939394)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1009.59343434343,-7.45454545454546)(1015.19191919192,-7.52272727272727)(1030.12121212121,-7.59090909090909)(1045.05050505051,-7.62121212121212)(1059.9797979798,-7.59090909090909)(1074.90909090909,-7.59090909090909)(1089.83838383838,-7.62121212121212)(1097.30303030303,-7.63636363636364)(1104.76767676768,-7.65454545454546)(1119.69696969697,-7.68181818181818)(1134.62626262626,-7.68181818181818)(1149.55555555556,-7.71212121212121)(1164.48484848485,-7.70454545454546)(1179.41414141414,-7.68181818181818)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.79545454545455)(1216.73737373737,-7.81818181818182)(1224.20202020202,-7.83636363636364)(1231.66666666667,-7.81818181818182)(1239.13131313131,-7.8030303030303)(1254.06060606061,-7.77272727272727)(1268.9898989899,-7.74242424242424)(1283.91919191919,-7.74242424242424)(1298.84848484848,-7.77272727272727)(1310.04545454545,-7.81818181818182)(1313.77777777778,-7.84090909090909)(1328.70707070707,-7.90909090909091)(1343.63636363636,-7.98484848484848)(1345.50252525253,-8)(1358.56565656566,-8.15909090909091)(1362.29797979798,-8.18181818181818)(1373.49494949495,-8.27272727272727)(1384.69191919192,-8.36363636363636)(1388.42424242424,-8.40909090909091)(1394.02272727273,-8.54545454545455)(1403.35353535354,-8.6969696969697)(1404.84646464646,-8.72727272727273)(1412.68434343434,-8.90909090909091)(1418.28282828283,-9.04545454545455)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (373.232323232323,-7.68181818181818)(376.964646464646,-7.63636363636364)(388.161616161616,-7.54545454545455)(403.090909090909,-7.47727272727273)(406.823232323232,-7.45454545454546)(418.020202020202,-7.36363636363636)(432.949494949495,-7.31818181818182)(440.414141414141,-7.27272727272727)(447.878787878788,-7.24242424242424)(462.808080808081,-7.18181818181818)(477.737373737374,-7.11363636363636)(492.666666666667,-7.14545454545455)(507.59595959596,-7.10606060606061)(522.525252525253,-7.10606060606061)(537.454545454546,-7.10909090909091)(552.383838383838,-7.15909090909091)(567.313131313131,-7.12121212121212)(582.242424242424,-7.18181818181818)(597.171717171717,-7.24242424242424)(599.659932659933,-7.27272727272727)(612.10101010101,-7.42424242424243)(627.030303030303,-7.40909090909091)(630.762626262626,-7.45454545454546)(629.518518518518,-7.63636363636364)(640.093434343434,-7.81818181818182)(641.959595959596,-7.90909090909091)(644.447811447811,-8)(649.424242424242,-8.18181818181818)(651.290404040404,-8.36363636363636)(651.290404040404,-8.54545454545455)(649.424242424242,-8.72727272727273)(641.959595959596,-8.87878787878788)(638.227272727273,-8.90909090909091)(627.030303030303,-9)(612.10101010101,-9.06818181818182)(597.171717171717,-9.07272727272727)(589.707070707071,-9.09090909090909)(582.242424242424,-9.12121212121212)(567.313131313131,-9.20454545454546)(556.116161616162,-9.27272727272727)(552.383838383838,-9.3030303030303)(537.454545454546,-9.3030303030303)(522.525252525253,-9.3030303030303)(507.59595959596,-9.3030303030303)(492.666666666667,-9.34090909090909)(477.737373737374,-9.3030303030303)(475.249158249158,-9.27272727272727)(462.808080808081,-9.12121212121212)(460.319865319865,-9.09090909090909)(447.878787878788,-8.97727272727273)(436.681818181818,-8.90909090909091)(432.949494949495,-8.87878787878788)(418.020202020202,-8.75757575757576)(414.287878787879,-8.72727272727273)(403.090909090909,-8.63636363636364)(395.626262626263,-8.54545454545455)(388.161616161616,-8.45454545454545)(380.69696969697,-8.36363636363636)(373.232323232323,-8.22727272727273)(370.744107744108,-8.18181818181818)(367.633838383838,-8)(365.767676767677,-7.81818181818182)(373.232323232323,-7.68181818181818)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1283.91919191919,-8.68181818181818)(1286.40740740741,-8.72727272727273)(1286.40740740741,-8.90909090909091)(1283.91919191919,-8.95454545454546)(1276.45454545455,-9.09090909090909)(1268.9898989899,-9.18181818181818)(1257.79292929293,-9.27272727272727)(1254.06060606061,-9.3030303030303)(1239.13131313131,-9.36363636363636)(1224.20202020202,-9.42424242424243)(1209.27272727273,-9.42424242424243)(1194.34343434343,-9.42424242424243)(1179.41414141414,-9.42424242424243)(1164.48484848485,-9.42424242424243)(1157.0202020202,-9.45454545454546)(1149.55555555556,-9.48484848484848)(1134.62626262626,-9.48484848484848)(1119.69696969697,-9.48484848484848)(1104.76767676768,-9.48484848484848)(1097.30303030303,-9.45454545454546)(1089.83838383838,-9.40909090909091)(1082.37373737374,-9.45454545454546)(1074.90909090909,-9.48484848484848)(1059.9797979798,-9.48484848484848)(1045.05050505051,-9.48484848484848)(1030.12121212121,-9.48484848484848)(1022.65656565657,-9.45454545454546)(1015.19191919192,-9.40909090909091)(1000.26262626263,-9.40909090909091)(985.333333333333,-9.36363636363636)(970.40404040404,-9.36363636363636)(955.474747474747,-9.3030303030303)(948.010101010101,-9.27272727272727)(940.545454545455,-9.22727272727273)(925.616161616162,-9.12121212121212)(918.151515151515,-9.09090909090909)(910.686868686869,-9.04545454545455)(903.222222222222,-8.90909090909091)(898.245791245791,-8.72727272727273)(908.198653198653,-8.54545454545455)(910.686868686869,-8.5)(921.883838383838,-8.36363636363636)(925.616161616162,-8.31818181818182)(936.813131313131,-8.18181818181818)(940.545454545455,-8.15151515151515)(955.474747474747,-8.09090909090909)(970.40404040404,-8.09090909090909)(985.333333333333,-8.09090909090909)(1000.26262626263,-8.09090909090909)(1015.19191919192,-8.13636363636364)(1030.12121212121,-8.13636363636364)(1045.05050505051,-8.13636363636364)(1059.9797979798,-8.15151515151515)(1067.44444444444,-8.18181818181818)(1074.90909090909,-8.21212121212121)(1089.83838383838,-8.31818181818182)(1104.76767676768,-8.31818181818182)(1119.69696969697,-8.31818181818182)(1134.62626262626,-8.27272727272727)(1149.55555555556,-8.31818181818182)(1157.0202020202,-8.36363636363636)(1164.48484848485,-8.39393939393939)(1179.41414141414,-8.39393939393939)(1186.87878787879,-8.36363636363636)(1194.34343434343,-8.33333333333333)(1209.27272727273,-8.33333333333333)(1216.73737373737,-8.36363636363636)(1224.20202020202,-8.40909090909091)(1239.13131313131,-8.5)(1254.06060606061,-8.5)(1268.9898989899,-8.51515151515152)(1272.72222222222,-8.54545454545455)(1283.91919191919,-8.68181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-7.96969696969697)(87.0875420875421,-7.81818181818182)(89.5757575757576,-7.77272727272727)(100.772727272727,-7.63636363636364)(104.505050505051,-7.59090909090909)(111.969696969697,-7.45454545454546)(119.434343434343,-7.38636363636364)(134.363636363636,-7.42424242424243)(149.292929292929,-7.42424242424243)(156.757575757576,-7.45454545454546)(164.222222222222,-7.48484848484849)(179.151515151515,-7.48484848484849)(194.080808080808,-7.48484848484849)(209.010101010101,-7.54545454545455)(223.939393939394,-7.60606060606061)(231.40404040404,-7.63636363636364)(238.868686868687,-7.66666666666667)(253.79797979798,-7.66666666666667)(261.262626262626,-7.63636363636364)(268.727272727273,-7.61818181818182)(276.191919191919,-7.63636363636364)(283.656565656566,-7.66666666666667)(296.097643097643,-7.81818181818182)(298.585858585859,-7.84848484848485)(307.916666666667,-8)(313.515151515152,-8.09090909090909)(320.979797979798,-8.18181818181818)(322.84595959596,-8.36363636363636)(316.003367003367,-8.54545454545455)(313.515151515152,-8.57575757575757)(298.585858585859,-8.70454545454545)(294.853535353535,-8.72727272727273)(283.656565656566,-8.79545454545455)(271.215488215488,-8.90909090909091)(268.727272727273,-8.93939393939394)(253.79797979798,-9)(246.333333333333,-9.09090909090909)(238.868686868687,-9.15909090909091)(223.939393939394,-9.12121212121212)(209.010101010101,-9.12121212121212)(194.080808080808,-9.12121212121212)(179.151515151515,-9.24242424242424)(164.222222222222,-9.25)(149.292929292929,-9.12121212121212)(146.804713804714,-9.09090909090909)(135.856565656566,-8.90909090909091)(134.363636363636,-8.89393939393939)(119.434343434343,-8.85454545454546)(104.505050505051,-8.75757575757576)(100.772727272727,-8.72727272727273)(89.5757575757576,-8.59090909090909)(87.709595959596,-8.54545454545455)(77.1346801346801,-8.36363636363636)(74.6464646464647,-8.27272727272727)(72.1582491582492,-8.18181818181818)(72.1582491582492,-8)(74.6464646464647,-7.96969696969697)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.90909090909091)(450.367003367003,-7.81818181818182)(462.808080808081,-7.66666666666667)(465.296296296296,-7.63636363636364)(475.871212121212,-7.45454545454546)(477.737373737374,-7.43939393939394)(492.666666666667,-7.43939393939394)(507.59595959596,-7.43181818181818)(522.525252525253,-7.43181818181818)(529.989898989899,-7.45454545454546)(537.454545454546,-7.5)(552.383838383838,-7.48484848484849)(567.313131313131,-7.5)(582.242424242424,-7.60606060606061)(585.974747474747,-7.63636363636364)(597.171717171717,-7.72727272727273)(604.636363636364,-7.81818181818182)(612.10101010101,-7.95454545454546)(613.967171717172,-8)(619.565656565657,-8.18181818181818)(619.565656565657,-8.36363636363636)(614.589225589226,-8.54545454545455)(612.10101010101,-8.63636363636364)(597.171717171717,-8.6969696969697)(593.439393939394,-8.72727272727273)(582.242424242424,-8.79545454545455)(567.313131313131,-8.87878787878788)(559.848484848485,-8.90909090909091)(552.383838383838,-8.93181818181818)(537.454545454546,-8.97727272727273)(522.525252525253,-8.97727272727273)(507.59595959596,-8.93181818181818)(503.863636363636,-8.90909090909091)(492.666666666667,-8.77272727272727)(485.20202020202,-8.72727272727273)(477.737373737374,-8.6969696969697)(462.808080808081,-8.57575757575757)(447.878787878788,-8.56818181818182)(445.390572390572,-8.54545454545455)(445.390572390572,-8.36363636363636)(440.414141414141,-8.18181818181818)(445.390572390572,-8)(447.878787878788,-7.90909090909091)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (119.434343434343,-8.15151515151515)(131.875420875421,-8)(134.363636363636,-7.96969696969697)(149.292929292929,-7.90909090909091)(164.222222222222,-7.86363636363636)(179.151515151515,-7.86363636363636)(194.080808080808,-7.86363636363636)(209.010101010101,-7.96969696969697)(212.742424242424,-8)(223.939393939394,-8.13636363636364)(225.805555555556,-8.18181818181818)(233.270202020202,-8.36363636363636)(227.671717171717,-8.54545454545455)(223.939393939394,-8.59090909090909)(209.010101010101,-8.6969696969697)(201.545454545455,-8.72727272727273)(194.080808080808,-8.75)(179.151515151515,-8.86363636363636)(164.222222222222,-8.86363636363636)(153.025252525253,-8.72727272727273)(149.292929292929,-8.6969696969697)(134.363636363636,-8.56818181818182)(126.89898989899,-8.54545454545455)(119.434343434343,-8.5)(113.835858585859,-8.36363636363636)(116.946127946128,-8.18181818181818)(119.434343434343,-8.15151515151515)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182)(373.232323232323,-7.63636363636364)(1313.77777777778,-9.09090909090909)(1015.19191919192,-9.09090909090909)(194.080808080808,-9.09090909090909)(627.030303030303,-8.90909090909091)(223.939393939394,-7.45454545454546)(1104.76767676768,-8.18181818181818)(940.545454545455,-7.27272727272727)(1403.35353535354,-8.18181818181818)(134.363636363636,-8)(432.949494949495,-8.36363636363636)(1059.9797979798,-7.27272727272727)(836.040404040404,-7.81818181818182)(1298.84848484848,-10.1818181818182)(791.252525252525,-9.27272727272727)(1418.28282828283,-9.27272727272727)(940.545454545455,-9.27272727272727)(1104.76767676768,-9.45454545454546)(298.585858585859,-8.72727272727273)(597.171717171717,-7.27272727272727)(447.878787878788,-7.27272727272727)(1298.84848484848,-7.81818181818182)(985.333333333333,-10.1818181818182)(74.6464646464647,-8)(1239.13131313131,-8.72727272727273)(462.808080808081,-9.09090909090909)(1119.69696969697,-10.1818181818182)(776.323232323232,-8.54545454545455)(1000.26262626263,-8.54545454545455)(1388.42424242424,-10.1818181818182)(1179.41414141414,-7.45454545454546)(298.585858585859,-7.81818181818182)(119.434343434343,-8.72727272727273)(865.89898989899,-9.81818181818182)(656.888888888889,-8.72727272727273)(149.292929292929,-7.45454545454546)(1418.28282828283,-8.36363636363636)(955.474747474747,-8)(1224.20202020202,-9.45454545454546)(447.878787878788,-7.81818181818182)(612.10101010101,-8)(1104.76767676768,-8.54545454545455)(850.969696969697,-7.63636363636364)(895.757575757576,-8.72727272727273)(1224.20202020202,-10.1818181818182)(223.939393939394,-8.36363636363636)(1045.05050505051,-7.27272727272727)(597.171717171717,-9.09090909090909)(1448.14141414141,-8.90909090909091)(1030.12121212121,-9.45454545454546)(1328.70707070707,-7.63636363636364)(373.232323232323,-8.54545454545455)(1283.91919191919,-8.54545454545455)(1448.14141414141,-9.63636363636364)(955.474747474747,-7.27272727272727)(1059.9797979798,-10.1818181818182)(791.252525252525,-8.18181818181818)(1283.91919191919,-9.27272727272727)(910.686868686869,-10)(582.242424242424,-7.27272727272727)(253.79797979798,-8.90909090909091)(104.505050505051,-7.63636363636364)(1179.41414141414,-8.36363636363636)(1134.62626262626,-7.45454545454546)(462.808080808081,-8.72727272727273)(1030.12121212121,-8)(656.888888888889,-8)(1328.70707070707,-10.1818181818182)(791.252525252525,-9.09090909090909)(462.808080808081,-7.27272727272727)(74.6464646464647,-8.18181818181818)(1149.55555555556,-9.45454545454546)(149.292929292929,-8.90909090909091)(1239.13131313131,-7.63636363636364)(268.727272727273,-7.81818181818182)(910.686868686869,-9.09090909090909)(1373.49494949495,-8)(1059.9797979798,-8.72727272727273)(1179.41414141414,-10.1818181818182)(597.171717171717,-8.72727272727273)(432.949494949495,-8.18181818181818)(836.040404040404,-9.63636363636364)(1418.28282828283,-9.45454545454546)(910.686868686869,-8.36363636363636)(1000.26262626263,-10.1818181818182)(164.222222222222,-7.45454545454546)(477.737373737374,-9.09090909090909)(895.757575757576,-7.45454545454546)(1433.21212121212,-8.72727272727273)(1418.28282828283,-10)(985.333333333333,-9.45454545454546)(1179.41414141414,-8.90909090909091)(418.020202020202,-7.45454545454546)(313.515151515152,-8.36363636363636)(776.323232323232,-8.72727272727273)(537.454545454546,-7.45454545454546)(1104.76767676768,-7.45454545454546)(1283.91919191919,-10.1818181818182)(1283.91919191919,-9.09090909090909)(1000.26262626263,-7.27272727272727) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_340.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1448.14141414141,-9.18181818181818)(1450.62962962963,-9.27272727272727)(1460.58249158249,-9.45454545454546)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.77272727272727)(1446.27525252525,-9.81818181818182)(1433.21212121212,-9.97727272727273)(1429.4797979798,-10)(1418.28282828283,-10.0909090909091)(1403.35353535354,-10.1590909090909)(1401.48737373737,-10.1818181818182)(1388.42424242424,-10.3409090909091)(1380.9595959596,-10.3636363636364)(1373.49494949495,-10.3939393939394)(1358.56565656566,-10.4318181818182)(1347.36868686869,-10.3636363636364)(1343.63636363636,-10.3454545454545)(1328.70707070707,-10.3484848484848)(1313.77777777778,-10.3181818181818)(1298.84848484848,-10.2575757575758)(1283.91919191919,-10.2575757575758)(1268.9898989899,-10.2878787878788)(1254.06060606061,-10.3484848484848)(1246.59595959596,-10.3636363636364)(1239.13131313131,-10.3818181818182)(1224.20202020202,-10.3818181818182)(1216.73737373737,-10.3636363636364)(1209.27272727273,-10.3484848484848)(1194.34343434343,-10.2878787878788)(1179.41414141414,-10.3181818181818)(1164.48484848485,-10.3181818181818)(1149.55555555556,-10.3484848484848)(1134.62626262626,-10.2878787878788)(1119.69696969697,-10.3181818181818)(1104.76767676768,-10.2878787878788)(1089.83838383838,-10.3181818181818)(1074.90909090909,-10.3181818181818)(1063.71212121212,-10.3636363636364)(1059.9797979798,-10.3818181818182)(1045.05050505051,-10.3818181818182)(1037.58585858586,-10.3636363636364)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.2878787878788)(1000.26262626263,-10.2575757575758)(985.333333333333,-10.2272727272727)(970.40404040404,-10.2)(966.671717171717,-10.1818181818182)(955.474747474747,-10.1363636363636)(940.545454545455,-10.0757575757576)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0909090909091)(895.757575757576,-10.0681818181818)(890.159090909091,-10)(880.828282828283,-9.90909090909091)(865.89898989899,-9.84090909090909)(863.410774410775,-9.81818181818182)(850.969696969697,-9.72727272727273)(836.040404040404,-9.69090909090909)(828.575757575758,-9.63636363636364)(821.111111111111,-9.56818181818182)(808.670033670034,-9.45454545454546)(806.181818181818,-9.43636363636364)(792.745454545455,-9.27272727272727)(791.252525252525,-9.24242424242424)(781.921717171717,-9.09090909090909)(777.816161616162,-8.90909090909091)(777.816161616162,-8.72727272727273)(778.189393939394,-8.54545454545455)(783.787878787879,-8.36363636363636)(791.252525252525,-8.27272727272727)(798.717171717172,-8.18181818181818)(806.181818181818,-8.11363636363636)(818.622895622896,-8)(821.111111111111,-7.97727272727273)(836.040404040404,-7.83636363636364)(837.906565656566,-7.81818181818182)(850.969696969697,-7.69090909090909)(858.434343434343,-7.63636363636364)(865.89898989899,-7.56818181818182)(872.119528619529,-7.45454545454546)(880.828282828283,-7.29545454545455)(888.292929292929,-7.27272727272727)(895.757575757576,-7.24242424242424)(910.686868686869,-7.20454545454546)(918.151515151515,-7.27272727272727)(925.616161616162,-7.31818181818182)(940.545454545455,-7.28787878787879)(948.010101010101,-7.27272727272727)(955.474747474747,-7.25454545454546)(970.40404040404,-7.16666666666667)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.20454545454546)(1022.65656565657,-7.27272727272727)(1030.12121212121,-7.31818181818182)(1045.05050505051,-7.34848484848485)(1059.9797979798,-7.31818181818182)(1074.90909090909,-7.31818181818182)(1089.83838383838,-7.34848484848485)(1104.76767676768,-7.31818181818182)(1119.69696969697,-7.34848484848485)(1134.62626262626,-7.34848484848485)(1149.55555555556,-7.43636363636364)(1164.48484848485,-7.38636363636364)(1179.41414141414,-7.3030303030303)(1194.34343434343,-7.31818181818182)(1205.5404040404,-7.45454545454546)(1209.27272727273,-7.46969696969697)(1224.20202020202,-7.56060606060606)(1239.13131313131,-7.5)(1254.06060606061,-7.46969696969697)(1261.52525252525,-7.45454545454546)(1268.9898989899,-7.43636363636364)(1276.45454545455,-7.45454545454546)(1283.91919191919,-7.46969696969697)(1298.84848484848,-7.5)(1313.77777777778,-7.54545454545455)(1328.70707070707,-7.61363636363636)(1331.19528619529,-7.63636363636364)(1343.63636363636,-7.72727272727273)(1356.07744107744,-7.81818181818182)(1358.56565656566,-7.83636363636364)(1373.49494949495,-7.88636363636364)(1388.42424242424,-7.93181818181818)(1403.35353535354,-7.96969696969697)(1405.84175084175,-8)(1412.68434343434,-8.18181818181818)(1418.28282828283,-8.27272727272727)(1422.76161616162,-8.36363636363636)(1425.74747474747,-8.54545454545455)(1431.96801346801,-8.72727272727273)(1433.21212121212,-8.77272727272727)(1438.81060606061,-8.90909090909091)(1446.64848484848,-9.09090909090909)(1448.14141414141,-9.18181818181818)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1418.28282828283,-9.04545454545455)(1419.77575757576,-9.09090909090909)(1423.88131313131,-9.27272727272727)(1422.01515151515,-9.45454545454546)(1418.28282828283,-9.5)(1410.81818181818,-9.63636363636364)(1403.35353535354,-9.77272727272727)(1399.62121212121,-9.81818181818182)(1388.42424242424,-9.88636363636364)(1373.49494949495,-9.96969696969697)(1369.76262626263,-10)(1358.56565656566,-10.0681818181818)(1343.63636363636,-10.0454545454545)(1328.70707070707,-10.0757575757576)(1313.77777777778,-10.0454545454545)(1302.58080808081,-10)(1298.84848484848,-9.98181818181818)(1283.91919191919,-9.98181818181818)(1276.45454545455,-10)(1268.9898989899,-10.0151515151515)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.1060606060606)(1209.27272727273,-10.0757575757576)(1194.34343434343,-10.0151515151515)(1179.41414141414,-10.0454545454545)(1164.48484848485,-10.0454545454545)(1149.55555555556,-10.0757575757576)(1134.62626262626,-10.0151515151515)(1119.69696969697,-10.0454545454545)(1104.76767676768,-10.0151515151515)(1089.83838383838,-10.0454545454545)(1074.90909090909,-10.0454545454545)(1059.9797979798,-10.1060606060606)(1045.05050505051,-10.1060606060606)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0151515151515)(1007.72727272727,-10)(1000.26262626263,-9.98181818181818)(985.333333333333,-9.95454545454546)(970.40404040404,-9.92424242424243)(955.474747474747,-9.86363636363636)(944.277777777778,-9.81818181818182)(940.545454545455,-9.8)(933.080808080808,-9.81818181818182)(925.616161616162,-9.83333333333333)(918.151515151515,-9.81818181818182)(910.686868686869,-9.79545454545455)(895.757575757576,-9.75)(883.316498316498,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.54545454545455)(853.457912457912,-9.45454545454546)(850.969696969697,-9.43181818181818)(836.040404040404,-9.36363636363636)(826.709595959596,-9.27272727272727)(821.111111111111,-9.18181818181818)(813.646464646465,-9.09090909090909)(806.181818181818,-9)(802.449494949495,-8.90909090909091)(806.181818181818,-8.77272727272727)(808.04797979798,-8.72727272727273)(811.780303030303,-8.54545454545455)(819.618181818182,-8.36363636363636)(821.111111111111,-8.34090909090909)(834.174242424242,-8.18181818181818)(836.040404040404,-8.16363636363636)(850.969696969697,-8.02272727272727)(853.457912457912,-8)(865.89898989899,-7.88636363636364)(873.363636363636,-7.81818181818182)(880.828282828283,-7.75)(893.26936026936,-7.63636363636364)(895.757575757576,-7.61363636363636)(910.686868686869,-7.52272727272727)(925.616161616162,-7.59090909090909)(940.545454545455,-7.56060606060606)(955.474747474747,-7.53030303030303)(967.915824915825,-7.45454545454546)(970.40404040404,-7.43939393939394)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1009.59343434343,-7.45454545454546)(1015.19191919192,-7.52272727272727)(1030.12121212121,-7.59090909090909)(1045.05050505051,-7.62121212121212)(1059.9797979798,-7.59090909090909)(1074.90909090909,-7.59090909090909)(1089.83838383838,-7.62121212121212)(1097.30303030303,-7.63636363636364)(1104.76767676768,-7.65454545454546)(1119.69696969697,-7.68181818181818)(1134.62626262626,-7.68181818181818)(1149.55555555556,-7.71212121212121)(1164.48484848485,-7.70454545454546)(1179.41414141414,-7.68181818181818)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.79545454545455)(1216.73737373737,-7.81818181818182)(1224.20202020202,-7.83636363636364)(1227.93434343434,-7.81818181818182)(1239.13131313131,-7.77272727272727)(1254.06060606061,-7.74242424242424)(1268.9898989899,-7.71212121212121)(1283.91919191919,-7.74242424242424)(1298.84848484848,-7.77272727272727)(1310.04545454545,-7.81818181818182)(1313.77777777778,-7.84090909090909)(1328.70707070707,-7.90909090909091)(1341.14814814815,-8)(1343.63636363636,-8.02272727272727)(1358.56565656566,-8.16363636363636)(1362.29797979798,-8.18181818181818)(1373.49494949495,-8.27272727272727)(1388.42424242424,-8.34090909090909)(1390.2904040404,-8.36363636363636)(1397.75505050505,-8.54545454545455)(1403.35353535354,-8.63636363636364)(1407.83232323232,-8.72727272727273)(1412.68434343434,-8.90909090909091)(1418.28282828283,-9.04545454545455)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (373.232323232323,-7.68181818181818)(376.964646464646,-7.63636363636364)(388.161616161616,-7.54545454545455)(403.090909090909,-7.47727272727273)(406.823232323232,-7.45454545454546)(418.020202020202,-7.36363636363636)(432.949494949495,-7.31818181818182)(440.414141414141,-7.27272727272727)(447.878787878788,-7.24242424242424)(462.808080808081,-7.18181818181818)(477.737373737374,-7.11363636363636)(492.666666666667,-7.14545454545455)(507.59595959596,-7.10606060606061)(522.525252525253,-7.10606060606061)(537.454545454546,-7.10606060606061)(552.383838383838,-7.14545454545455)(567.313131313131,-7.11363636363636)(582.242424242424,-7.18181818181818)(597.171717171717,-7.24242424242424)(599.659932659933,-7.27272727272727)(612.10101010101,-7.38636363636364)(627.030303030303,-7.36363636363636)(638.227272727273,-7.45454545454546)(634.494949494949,-7.63636363636364)(641.959595959596,-7.77272727272727)(643.825757575758,-7.81818181818182)(644.447811447811,-8)(654.400673400673,-8.18181818181818)(655.022727272727,-8.36363636363636)(655.022727272727,-8.54545454545455)(649.424242424242,-8.72727272727273)(641.959595959596,-8.87878787878788)(638.227272727273,-8.90909090909091)(627.030303030303,-9)(612.10101010101,-9.06818181818182)(604.636363636364,-9.09090909090909)(597.171717171717,-9.12121212121212)(582.242424242424,-9.20454545454546)(567.313131313131,-9.25454545454546)(559.848484848485,-9.27272727272727)(552.383838383838,-9.3030303030303)(537.454545454546,-9.3030303030303)(522.525252525253,-9.3030303030303)(507.59595959596,-9.3030303030303)(492.666666666667,-9.34090909090909)(477.737373737374,-9.3030303030303)(475.249158249158,-9.27272727272727)(462.808080808081,-9.12121212121212)(460.319865319865,-9.09090909090909)(447.878787878788,-8.97727272727273)(432.949494949495,-8.93181818181818)(429.217171717172,-8.90909090909091)(418.020202020202,-8.81818181818182)(406.823232323232,-8.72727272727273)(403.090909090909,-8.6969696969697)(393.760101010101,-8.54545454545455)(388.161616161616,-8.45454545454545)(380.69696969697,-8.36363636363636)(373.232323232323,-8.22727272727273)(370.744107744108,-8.18181818181818)(367.633838383838,-8)(365.767676767677,-7.81818181818182)(373.232323232323,-7.68181818181818)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1268.9898989899,-8.63636363636364)(1276.45454545455,-8.72727272727273)(1281.43097643098,-8.90909090909091)(1276.45454545455,-9.09090909090909)(1268.9898989899,-9.18181818181818)(1257.79292929293,-9.27272727272727)(1254.06060606061,-9.3030303030303)(1239.13131313131,-9.36363636363636)(1224.20202020202,-9.36363636363636)(1209.27272727273,-9.36363636363636)(1194.34343434343,-9.36363636363636)(1179.41414141414,-9.42424242424243)(1164.48484848485,-9.42424242424243)(1157.0202020202,-9.45454545454546)(1149.55555555556,-9.48484848484848)(1134.62626262626,-9.48484848484848)(1119.69696969697,-9.48484848484848)(1112.23232323232,-9.45454545454546)(1104.76767676768,-9.42424242424243)(1089.83838383838,-9.31818181818182)(1074.90909090909,-9.40909090909091)(1067.44444444444,-9.45454545454546)(1059.9797979798,-9.48484848484848)(1045.05050505051,-9.48484848484848)(1030.12121212121,-9.48484848484848)(1022.65656565657,-9.45454545454546)(1015.19191919192,-9.40909090909091)(1000.26262626263,-9.40909090909091)(985.333333333333,-9.36363636363636)(970.40404040404,-9.36363636363636)(955.474747474747,-9.3030303030303)(948.010101010101,-9.27272727272727)(940.545454545455,-9.22727272727273)(925.616161616162,-9.12121212121212)(921.883838383838,-9.09090909090909)(910.686868686869,-8.95454545454546)(908.198653198653,-8.90909090909091)(908.198653198653,-8.72727272727273)(910.686868686869,-8.63636363636364)(913.175084175084,-8.54545454545455)(923.127946127946,-8.36363636363636)(925.616161616162,-8.31818181818182)(936.813131313131,-8.18181818181818)(940.545454545455,-8.15151515151515)(955.474747474747,-8.09090909090909)(970.40404040404,-8.09090909090909)(985.333333333333,-8.09090909090909)(1000.26262626263,-8.09090909090909)(1015.19191919192,-8.13636363636364)(1030.12121212121,-8.13636363636364)(1037.58585858586,-8.18181818181818)(1045.05050505051,-8.21212121212121)(1059.9797979798,-8.21212121212121)(1074.90909090909,-8.27272727272727)(1089.83838383838,-8.31818181818182)(1104.76767676768,-8.31818181818182)(1119.69696969697,-8.31818181818182)(1134.62626262626,-8.27272727272727)(1149.55555555556,-8.31818181818182)(1157.0202020202,-8.36363636363636)(1164.48484848485,-8.39393939393939)(1179.41414141414,-8.39393939393939)(1194.34343434343,-8.39393939393939)(1209.27272727273,-8.39393939393939)(1224.20202020202,-8.5)(1239.13131313131,-8.5)(1246.59595959596,-8.54545454545455)(1254.06060606061,-8.59090909090909)(1268.9898989899,-8.63636363636364)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-8.09090909090909)(78.3787878787879,-8)(89.5757575757576,-7.86363636363636)(92.0639730639731,-7.81818181818182)(104.505050505051,-7.66666666666667)(106.371212121212,-7.63636363636364)(111.969696969697,-7.45454545454546)(119.434343434343,-7.38636363636364)(134.363636363636,-7.42424242424243)(149.292929292929,-7.42424242424243)(156.757575757576,-7.45454545454546)(164.222222222222,-7.47727272727273)(179.151515151515,-7.47727272727273)(194.080808080808,-7.48484848484849)(209.010101010101,-7.54545454545455)(223.939393939394,-7.60606060606061)(231.40404040404,-7.63636363636364)(238.868686868687,-7.65909090909091)(253.79797979798,-7.66666666666667)(261.262626262626,-7.63636363636364)(268.727272727273,-7.61818181818182)(276.191919191919,-7.63636363636364)(283.656565656566,-7.68181818181818)(291.121212121212,-7.81818181818182)(298.585858585859,-7.95454545454546)(300.45202020202,-8)(311.026936026936,-8.18181818181818)(313.515151515152,-8.22727272727273)(319.113636363636,-8.36363636363636)(316.003367003367,-8.54545454545455)(313.515151515152,-8.57575757575757)(298.585858585859,-8.70454545454545)(294.853535353535,-8.72727272727273)(283.656565656566,-8.79545454545455)(271.215488215488,-8.90909090909091)(268.727272727273,-8.93939393939394)(253.79797979798,-9.06060606060606)(251.309764309764,-9.09090909090909)(238.868686868687,-9.18181818181818)(223.939393939394,-9.15909090909091)(209.010101010101,-9.12121212121212)(194.080808080808,-9.12121212121212)(179.151515151515,-9.24242424242424)(164.222222222222,-9.25)(149.292929292929,-9.12121212121212)(146.804713804714,-9.09090909090909)(135.856565656566,-8.90909090909091)(134.363636363636,-8.89393939393939)(119.434343434343,-8.84090909090909)(106.993265993266,-8.72727272727273)(104.505050505051,-8.70454545454545)(91.4419191919192,-8.54545454545455)(89.5757575757576,-8.5)(78.3787878787879,-8.36363636363636)(74.6464646464647,-8.27272727272727)(72.1582491582492,-8.18181818181818)(74.6464646464647,-8.09090909090909)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.90909090909091)(450.367003367003,-7.81818181818182)(462.808080808081,-7.66666666666667)(465.296296296296,-7.63636363636364)(475.871212121212,-7.45454545454546)(477.737373737374,-7.43939393939394)(492.666666666667,-7.43939393939394)(507.59595959596,-7.43181818181818)(522.525252525253,-7.43181818181818)(537.454545454546,-7.43181818181818)(552.383838383838,-7.43939393939394)(567.313131313131,-7.43939393939394)(569.801346801347,-7.45454545454546)(582.242424242424,-7.60606060606061)(585.974747474747,-7.63636363636364)(597.171717171717,-7.72727272727273)(608.368686868687,-7.81818181818182)(612.10101010101,-7.90909090909091)(613.967171717172,-8)(623.29797979798,-8.18181818181818)(627.030303030303,-8.27272727272727)(628.274410774411,-8.36363636363636)(627.030303030303,-8.45454545454545)(623.29797979798,-8.54545454545455)(614.589225589226,-8.72727272727273)(612.10101010101,-8.74242424242424)(597.171717171717,-8.75)(582.242424242424,-8.87878787878788)(578.510101010101,-8.90909090909091)(567.313131313131,-8.95454545454546)(552.383838383838,-8.97727272727273)(537.454545454546,-8.97727272727273)(522.525252525253,-8.97727272727273)(507.59595959596,-8.93181818181818)(503.863636363636,-8.90909090909091)(492.666666666667,-8.77272727272727)(485.20202020202,-8.72727272727273)(477.737373737374,-8.6969696969697)(462.808080808081,-8.57575757575757)(447.878787878788,-8.56818181818182)(444.146464646465,-8.54545454545455)(445.390572390572,-8.36363636363636)(440.414141414141,-8.18181818181818)(445.390572390572,-8)(447.878787878788,-7.90909090909091)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (119.434343434343,-8.15151515151515)(131.875420875421,-8)(134.363636363636,-7.96969696969697)(149.292929292929,-7.84848484848485)(156.757575757576,-7.81818181818182)(164.222222222222,-7.8030303030303)(179.151515151515,-7.8030303030303)(186.616161616162,-7.81818181818182)(194.080808080808,-7.86363636363636)(209.010101010101,-7.90909090909091)(223.939393939394,-7.97727272727273)(226.427609427609,-8)(237.002525252525,-8.18181818181818)(238.868686868687,-8.27272727272727)(241.356902356902,-8.36363636363636)(238.868686868687,-8.45454545454545)(236.380471380471,-8.54545454545455)(231.40404040404,-8.72727272727273)(223.939393939394,-8.75)(209.010101010101,-8.75)(194.080808080808,-8.79545454545455)(179.151515151515,-8.86363636363636)(164.222222222222,-8.86363636363636)(153.025252525253,-8.72727272727273)(149.292929292929,-8.6969696969697)(134.363636363636,-8.56818181818182)(130.631313131313,-8.54545454545455)(119.434343434343,-8.40909090909091)(117.568181818182,-8.36363636363636)(116.946127946128,-8.18181818181818)(119.434343434343,-8.15151515151515)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182)(373.232323232323,-7.63636363636364)(1313.77777777778,-9.09090909090909)(1015.19191919192,-9.09090909090909)(194.080808080808,-9.09090909090909)(627.030303030303,-8.90909090909091)(223.939393939394,-7.45454545454546)(1104.76767676768,-8.18181818181818)(940.545454545455,-7.27272727272727)(1403.35353535354,-8.18181818181818)(134.363636363636,-8)(432.949494949495,-8.36363636363636)(1059.9797979798,-7.27272727272727)(836.040404040404,-7.81818181818182)(1298.84848484848,-10.1818181818182)(791.252525252525,-9.27272727272727)(1418.28282828283,-9.27272727272727)(940.545454545455,-9.27272727272727)(1104.76767676768,-9.45454545454546)(298.585858585859,-8.72727272727273)(597.171717171717,-7.27272727272727)(447.878787878788,-7.27272727272727)(1298.84848484848,-7.81818181818182)(985.333333333333,-10.1818181818182)(74.6464646464647,-8)(1239.13131313131,-8.72727272727273)(462.808080808081,-9.09090909090909)(1119.69696969697,-10.1818181818182)(776.323232323232,-8.54545454545455)(1000.26262626263,-8.54545454545455)(1388.42424242424,-10.1818181818182)(1179.41414141414,-7.45454545454546)(298.585858585859,-7.81818181818182)(119.434343434343,-8.72727272727273)(865.89898989899,-9.81818181818182)(656.888888888889,-8.72727272727273)(149.292929292929,-7.45454545454546)(1418.28282828283,-8.36363636363636)(955.474747474747,-8)(1224.20202020202,-9.45454545454546)(447.878787878788,-7.81818181818182)(612.10101010101,-8)(1104.76767676768,-8.54545454545455)(850.969696969697,-7.63636363636364)(895.757575757576,-8.72727272727273)(1224.20202020202,-10.1818181818182)(223.939393939394,-8.36363636363636)(1045.05050505051,-7.27272727272727)(597.171717171717,-9.09090909090909)(1448.14141414141,-8.90909090909091)(1030.12121212121,-9.45454545454546)(1328.70707070707,-7.63636363636364)(373.232323232323,-8.54545454545455)(1283.91919191919,-8.54545454545455)(1448.14141414141,-9.63636363636364)(955.474747474747,-7.27272727272727)(1059.9797979798,-10.1818181818182)(791.252525252525,-8.18181818181818)(1283.91919191919,-9.27272727272727)(910.686868686869,-10)(582.242424242424,-7.27272727272727)(253.79797979798,-8.90909090909091)(104.505050505051,-7.63636363636364)(1179.41414141414,-8.36363636363636)(1134.62626262626,-7.45454545454546)(462.808080808081,-8.72727272727273)(1030.12121212121,-8)(656.888888888889,-8)(1328.70707070707,-10.1818181818182)(791.252525252525,-9.09090909090909)(462.808080808081,-7.27272727272727)(74.6464646464647,-8.18181818181818)(1149.55555555556,-9.45454545454546)(149.292929292929,-8.90909090909091)(1239.13131313131,-7.63636363636364)(268.727272727273,-7.81818181818182)(910.686868686869,-9.09090909090909)(1373.49494949495,-8)(1059.9797979798,-8.72727272727273)(1179.41414141414,-10.1818181818182)(597.171717171717,-8.72727272727273)(432.949494949495,-8.18181818181818)(836.040404040404,-9.63636363636364)(1418.28282828283,-9.45454545454546)(910.686868686869,-8.36363636363636)(1000.26262626263,-10.1818181818182)(164.222222222222,-7.45454545454546)(477.737373737374,-9.09090909090909)(895.757575757576,-7.45454545454546)(1433.21212121212,-8.72727272727273)(1418.28282828283,-10)(985.333333333333,-9.45454545454546)(1179.41414141414,-8.90909090909091)(418.020202020202,-7.45454545454546)(313.515151515152,-8.36363636363636)(776.323232323232,-8.72727272727273)(537.454545454546,-7.45454545454546)(1104.76767676768,-7.45454545454546)(1283.91919191919,-10.1818181818182)(1283.91919191919,-9.09090909090909)(1000.26262626263,-7.27272727272727)(223.939393939394,-8)(821.111111111111,-8)(1254.06060606061,-7.63636363636364)(1104.76767676768,-10.1818181818182)(104.505050505051,-8.54545454545455)(627.030303030303,-7.63636363636364)(582.242424242424,-9.09090909090909)(238.868686868687,-8.90909090909091)(1209.27272727273,-8.36363636363636)(1358.56565656566,-7.81818181818182)(1059.9797979798,-8.18181818181818)(1089.83838383838,-9.27272727272727)(641.959595959596,-8.36363636363636)(925.616161616162,-10)(970.40404040404,-8.72727272727273)(89.5757575757576,-7.81818181818182)(418.020202020202,-8.72727272727273)(1373.49494949495,-10.1818181818182)(821.111111111111,-9.45454545454546)(1403.35353535354,-8.54545454545455) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_360.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1463.07070707071,-9.40909090909091)(1464.56363636364,-9.45454545454546)(1463.07070707071,-9.54545454545455)(1460.58249158249,-9.63636363636364)(1448.14141414141,-9.78787878787879)(1446.27525252525,-9.81818181818182)(1433.21212121212,-9.97727272727273)(1429.4797979798,-10)(1418.28282828283,-10.0909090909091)(1403.35353535354,-10.1590909090909)(1401.48737373737,-10.1818181818182)(1388.42424242424,-10.3409090909091)(1380.9595959596,-10.3636363636364)(1373.49494949495,-10.3939393939394)(1358.56565656566,-10.4318181818182)(1347.36868686869,-10.3636363636364)(1343.63636363636,-10.3454545454545)(1328.70707070707,-10.3484848484848)(1313.77777777778,-10.3181818181818)(1298.84848484848,-10.2575757575758)(1283.91919191919,-10.2575757575758)(1268.9898989899,-10.2878787878788)(1254.06060606061,-10.3484848484848)(1246.59595959596,-10.3636363636364)(1239.13131313131,-10.3818181818182)(1231.66666666667,-10.3636363636364)(1224.20202020202,-10.3484848484848)(1209.27272727273,-10.3181818181818)(1194.34343434343,-10.2575757575758)(1179.41414141414,-10.3181818181818)(1164.48484848485,-10.3181818181818)(1149.55555555556,-10.3484848484848)(1134.62626262626,-10.2878787878788)(1119.69696969697,-10.3181818181818)(1104.76767676768,-10.2878787878788)(1089.83838383838,-10.3181818181818)(1074.90909090909,-10.3181818181818)(1063.71212121212,-10.3636363636364)(1059.9797979798,-10.3818181818182)(1052.51515151515,-10.3636363636364)(1045.05050505051,-10.3484848484848)(1030.12121212121,-10.3181818181818)(1015.19191919192,-10.2575757575758)(1000.26262626263,-10.2575757575758)(985.333333333333,-10.2272727272727)(970.40404040404,-10.2)(966.671717171717,-10.1818181818182)(955.474747474747,-10.1363636363636)(940.545454545455,-10.0757575757576)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0909090909091)(895.757575757576,-10.0681818181818)(890.159090909091,-10)(880.828282828283,-9.90909090909091)(865.89898989899,-9.84090909090909)(863.410774410775,-9.81818181818182)(850.969696969697,-9.72727272727273)(836.040404040404,-9.69090909090909)(828.575757575758,-9.63636363636364)(821.111111111111,-9.56818181818182)(808.670033670034,-9.45454545454546)(806.181818181818,-9.43636363636364)(792.745454545455,-9.27272727272727)(791.252525252525,-9.24242424242424)(781.921717171717,-9.09090909090909)(777.816161616162,-8.90909090909091)(777.56734006734,-8.72727272727273)(777.816161616162,-8.54545454545455)(781.921717171717,-8.36363636363636)(791.252525252525,-8.25)(798.717171717172,-8.18181818181818)(806.181818181818,-8.11363636363636)(818.622895622896,-8)(821.111111111111,-7.97727272727273)(836.040404040404,-7.83636363636364)(837.284511784512,-7.81818181818182)(849.103535353535,-7.63636363636364)(850.969696969697,-7.60606060606061)(865.89898989899,-7.50909090909091)(869.631313131313,-7.45454545454546)(880.828282828283,-7.29090909090909)(888.292929292929,-7.27272727272727)(895.757575757576,-7.24242424242424)(910.686868686869,-7.20454545454546)(921.883838383838,-7.27272727272727)(925.616161616162,-7.28787878787879)(933.080808080808,-7.27272727272727)(940.545454545455,-7.25454545454546)(955.474747474747,-7.22727272727273)(970.40404040404,-7.16666666666667)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.20454545454546)(1022.65656565657,-7.27272727272727)(1030.12121212121,-7.31818181818182)(1045.05050505051,-7.34848484848485)(1059.9797979798,-7.31818181818182)(1074.90909090909,-7.31818181818182)(1089.83838383838,-7.34848484848485)(1104.76767676768,-7.31818181818182)(1119.69696969697,-7.34848484848485)(1134.62626262626,-7.34848484848485)(1149.55555555556,-7.40909090909091)(1164.48484848485,-7.36363636363636)(1179.41414141414,-7.29545454545455)(1194.34343434343,-7.31818181818182)(1205.5404040404,-7.45454545454546)(1209.27272727273,-7.46969696969697)(1224.20202020202,-7.56060606060606)(1239.13131313131,-7.5)(1254.06060606061,-7.46969696969697)(1261.52525252525,-7.45454545454546)(1268.9898989899,-7.43636363636364)(1276.45454545455,-7.45454545454546)(1283.91919191919,-7.46969696969697)(1298.84848484848,-7.53030303030303)(1313.77777777778,-7.58181818181818)(1324.97474747475,-7.63636363636364)(1328.70707070707,-7.65151515151515)(1343.63636363636,-7.72727272727273)(1356.07744107744,-7.81818181818182)(1358.56565656566,-7.83636363636364)(1373.49494949495,-7.88636363636364)(1388.42424242424,-7.93181818181818)(1403.35353535354,-7.96969696969697)(1405.84175084175,-8)(1412.68434343434,-8.18181818181818)(1418.28282828283,-8.27272727272727)(1422.76161616162,-8.36363636363636)(1425.74747474747,-8.54545454545455)(1431.96801346801,-8.72727272727273)(1433.21212121212,-8.77272727272727)(1438.81060606061,-8.90909090909091)(1446.64848484848,-9.09090909090909)(1448.14141414141,-9.13636363636364)(1455.60606060606,-9.27272727272727)(1463.07070707071,-9.40909090909091)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1418.28282828283,-9.04545454545455)(1419.77575757576,-9.09090909090909)(1425.74747474747,-9.27272727272727)(1425.74747474747,-9.45454545454546)(1418.28282828283,-9.5)(1410.81818181818,-9.63636363636364)(1403.35353535354,-9.77272727272727)(1399.62121212121,-9.81818181818182)(1388.42424242424,-9.88636363636364)(1373.49494949495,-9.96969696969697)(1369.76262626263,-10)(1358.56565656566,-10.0681818181818)(1343.63636363636,-10.0454545454545)(1328.70707070707,-10.0757575757576)(1313.77777777778,-10.0454545454545)(1302.58080808081,-10)(1298.84848484848,-9.98181818181818)(1283.91919191919,-9.98181818181818)(1276.45454545455,-10)(1268.9898989899,-10.0151515151515)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.0757575757576)(1209.27272727273,-10.0454545454545)(1198.07575757576,-10)(1194.34343434343,-9.98181818181818)(1190.61111111111,-10)(1179.41414141414,-10.0454545454545)(1164.48484848485,-10.0454545454545)(1149.55555555556,-10.0757575757576)(1134.62626262626,-10.0151515151515)(1119.69696969697,-10.0454545454545)(1104.76767676768,-10.0151515151515)(1089.83838383838,-10.0454545454545)(1074.90909090909,-10.0454545454545)(1059.9797979798,-10.1060606060606)(1045.05050505051,-10.0757575757576)(1030.12121212121,-10.0454545454545)(1018.92424242424,-10)(1015.19191919192,-9.98181818181818)(1000.26262626263,-9.98181818181818)(985.333333333333,-9.95454545454546)(970.40404040404,-9.92424242424243)(955.474747474747,-9.86363636363636)(944.277777777778,-9.81818181818182)(940.545454545455,-9.8)(933.080808080808,-9.81818181818182)(925.616161616162,-9.83333333333333)(918.151515151515,-9.81818181818182)(910.686868686869,-9.79545454545455)(895.757575757576,-9.75)(883.316498316498,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.54545454545455)(853.457912457912,-9.45454545454546)(850.969696969697,-9.43181818181818)(836.040404040404,-9.36363636363636)(826.709595959596,-9.27272727272727)(821.111111111111,-9.18181818181818)(813.646464646465,-9.09090909090909)(806.181818181818,-9)(802.449494949495,-8.90909090909091)(804.315656565657,-8.72727272727273)(806.181818181818,-8.63636363636364)(808.04797979798,-8.54545454545455)(816.632323232323,-8.36363636363636)(821.111111111111,-8.30909090909091)(834.174242424242,-8.18181818181818)(836.040404040404,-8.16363636363636)(849.476767676768,-8)(850.969696969697,-7.97727272727273)(864.032828282828,-7.81818181818182)(865.89898989899,-7.8030303030303)(880.828282828283,-7.65909090909091)(888.292929292929,-7.63636363636364)(895.757575757576,-7.61363636363636)(910.686868686869,-7.52272727272727)(925.616161616162,-7.56060606060606)(940.545454545455,-7.53030303030303)(955.474747474747,-7.5)(966.671717171717,-7.45454545454546)(970.40404040404,-7.43939393939394)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1009.59343434343,-7.45454545454546)(1015.19191919192,-7.52272727272727)(1030.12121212121,-7.59090909090909)(1045.05050505051,-7.62121212121212)(1059.9797979798,-7.59090909090909)(1074.90909090909,-7.59090909090909)(1089.83838383838,-7.62121212121212)(1097.30303030303,-7.63636363636364)(1104.76767676768,-7.65454545454546)(1119.69696969697,-7.68181818181818)(1134.62626262626,-7.68181818181818)(1149.55555555556,-7.68181818181818)(1164.48484848485,-7.65909090909091)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.62121212121212)(1183.14646464646,-7.63636363636364)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.79545454545455)(1216.73737373737,-7.81818181818182)(1224.20202020202,-7.83636363636364)(1227.93434343434,-7.81818181818182)(1239.13131313131,-7.77272727272727)(1254.06060606061,-7.74242424242424)(1268.9898989899,-7.71212121212121)(1283.91919191919,-7.74242424242424)(1298.84848484848,-7.8030303030303)(1302.58080808081,-7.81818181818182)(1313.77777777778,-7.87272727272727)(1328.70707070707,-7.92424242424242)(1341.14814814815,-8)(1343.63636363636,-8.02272727272727)(1358.56565656566,-8.16363636363636)(1362.29797979798,-8.18181818181818)(1373.49494949495,-8.27272727272727)(1388.42424242424,-8.34090909090909)(1390.2904040404,-8.36363636363636)(1397.75505050505,-8.54545454545455)(1403.35353535354,-8.63636363636364)(1407.83232323232,-8.72727272727273)(1412.68434343434,-8.90909090909091)(1418.28282828283,-9.04545454545455)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (373.232323232323,-7.66666666666667)(375.720538720539,-7.63636363636364)(388.161616161616,-7.48484848484849)(395.626262626263,-7.45454545454546)(403.090909090909,-7.42424242424243)(418.020202020202,-7.34090909090909)(432.949494949495,-7.31818181818182)(440.414141414141,-7.27272727272727)(447.878787878788,-7.24242424242424)(462.808080808081,-7.15909090909091)(477.737373737374,-7.10909090909091)(492.666666666667,-7.13636363636364)(507.59595959596,-7.10606060606061)(515.060606060606,-7.09090909090909)(522.525252525253,-7.07272727272727)(537.454545454546,-7.07272727272727)(544.919191919192,-7.09090909090909)(552.383838383838,-7.10909090909091)(567.313131313131,-7.11363636363636)(582.242424242424,-7.18181818181818)(593.439393939394,-7.27272727272727)(597.171717171717,-7.29545454545455)(612.10101010101,-7.43181818181818)(627.030303030303,-7.42424242424243)(634.494949494949,-7.45454545454546)(630.762626262626,-7.63636363636364)(641.959595959596,-7.77272727272727)(643.825757575758,-7.81818181818182)(644.447811447811,-8)(654.400673400673,-8.18181818181818)(655.022727272727,-8.36363636363636)(651.290404040404,-8.54545454545455)(646.438383838384,-8.72727272727273)(641.959595959596,-8.81818181818182)(630.762626262626,-8.90909090909091)(627.030303030303,-8.95454545454546)(612.10101010101,-9.06818181818182)(604.636363636364,-9.09090909090909)(597.171717171717,-9.12121212121212)(582.242424242424,-9.20454545454546)(567.313131313131,-9.25454545454546)(559.848484848485,-9.27272727272727)(552.383838383838,-9.3030303030303)(537.454545454546,-9.3030303030303)(522.525252525253,-9.3030303030303)(507.59595959596,-9.34090909090909)(492.666666666667,-9.36363636363636)(477.737373737374,-9.34090909090909)(472.138888888889,-9.27272727272727)(462.808080808081,-9.12121212121212)(460.319865319865,-9.09090909090909)(447.878787878788,-8.97727272727273)(432.949494949495,-8.93181818181818)(429.217171717172,-8.90909090909091)(418.020202020202,-8.81818181818182)(406.823232323232,-8.72727272727273)(403.090909090909,-8.6969696969697)(393.760101010101,-8.54545454545455)(388.161616161616,-8.45454545454545)(380.69696969697,-8.36363636363636)(373.232323232323,-8.27272727272727)(365.767676767677,-8.18181818181818)(363.901515151515,-8)(360.791245791246,-7.81818181818182)(373.232323232323,-7.66666666666667)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1268.9898989899,-8.68181818181818)(1271.47811447811,-8.72727272727273)(1276.45454545455,-8.90909090909091)(1268.9898989899,-9.04545454545455)(1265.25757575758,-9.09090909090909)(1254.06060606061,-9.22727272727273)(1246.59595959596,-9.27272727272727)(1239.13131313131,-9.3030303030303)(1224.20202020202,-9.36363636363636)(1209.27272727273,-9.3030303030303)(1194.34343434343,-9.3030303030303)(1179.41414141414,-9.36363636363636)(1164.48484848485,-9.42424242424243)(1157.0202020202,-9.45454545454546)(1149.55555555556,-9.48484848484848)(1134.62626262626,-9.48484848484848)(1119.69696969697,-9.48484848484848)(1112.23232323232,-9.45454545454546)(1104.76767676768,-9.42424242424243)(1089.83838383838,-9.31818181818182)(1074.90909090909,-9.40909090909091)(1067.44444444444,-9.45454545454546)(1059.9797979798,-9.48484848484848)(1045.05050505051,-9.48484848484848)(1030.12121212121,-9.48484848484848)(1026.38888888889,-9.45454545454546)(1015.19191919192,-9.31818181818182)(1000.26262626263,-9.31818181818182)(985.333333333333,-9.3030303030303)(970.40404040404,-9.36363636363636)(955.474747474747,-9.3030303030303)(948.010101010101,-9.27272727272727)(940.545454545455,-9.22727272727273)(925.616161616162,-9.12121212121212)(921.883838383838,-9.09090909090909)(910.686868686869,-8.95454545454546)(908.198653198653,-8.90909090909091)(908.198653198653,-8.72727272727273)(910.686868686869,-8.63636363636364)(913.175084175084,-8.54545454545455)(925.616161616162,-8.39393939393939)(928.104377104377,-8.36363636363636)(940.545454545455,-8.21212121212121)(948.010101010101,-8.18181818181818)(955.474747474747,-8.15151515151515)(970.40404040404,-8.09090909090909)(985.333333333333,-8.09090909090909)(1000.26262626263,-8.09090909090909)(1015.19191919192,-8.13636363636364)(1030.12121212121,-8.13636363636364)(1037.58585858586,-8.18181818181818)(1045.05050505051,-8.21212121212121)(1059.9797979798,-8.21212121212121)(1074.90909090909,-8.27272727272727)(1089.83838383838,-8.31818181818182)(1097.30303030303,-8.36363636363636)(1104.76767676768,-8.40909090909091)(1119.69696969697,-8.40909090909091)(1127.16161616162,-8.36363636363636)(1134.62626262626,-8.33333333333333)(1149.55555555556,-8.31818181818182)(1157.0202020202,-8.36363636363636)(1164.48484848485,-8.39393939393939)(1179.41414141414,-8.39393939393939)(1194.34343434343,-8.39393939393939)(1209.27272727273,-8.39393939393939)(1224.20202020202,-8.5)(1239.13131313131,-8.5)(1246.59595959596,-8.54545454545455)(1254.06060606061,-8.59090909090909)(1268.9898989899,-8.68181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-8.09090909090909)(78.3787878787879,-8)(89.5757575757576,-7.86363636363636)(92.0639730639731,-7.81818181818182)(104.505050505051,-7.66666666666667)(106.371212121212,-7.63636363636364)(111.969696969697,-7.45454545454546)(119.434343434343,-7.38636363636364)(134.363636363636,-7.42424242424243)(149.292929292929,-7.42424242424243)(156.757575757576,-7.45454545454546)(164.222222222222,-7.47727272727273)(179.151515151515,-7.47727272727273)(194.080808080808,-7.48484848484849)(209.010101010101,-7.60606060606061)(216.474747474747,-7.63636363636364)(223.939393939394,-7.65454545454546)(238.868686868687,-7.70454545454546)(253.79797979798,-7.66666666666667)(261.262626262626,-7.63636363636364)(268.727272727273,-7.61818181818182)(276.191919191919,-7.63636363636364)(283.656565656566,-7.68181818181818)(291.121212121212,-7.81818181818182)(298.585858585859,-7.95454545454546)(300.45202020202,-8)(311.026936026936,-8.18181818181818)(313.515151515152,-8.22727272727273)(319.113636363636,-8.36363636363636)(316.003367003367,-8.54545454545455)(313.515151515152,-8.57575757575757)(298.585858585859,-8.65909090909091)(287.388888888889,-8.72727272727273)(283.656565656566,-8.75)(268.727272727273,-8.87878787878788)(266.239057239057,-8.90909090909091)(253.79797979798,-9.06060606060606)(251.309764309764,-9.09090909090909)(238.868686868687,-9.18181818181818)(223.939393939394,-9.15909090909091)(209.010101010101,-9.12121212121212)(194.080808080808,-9.12121212121212)(179.151515151515,-9.22727272727273)(164.222222222222,-9.24242424242424)(151.781144781145,-9.09090909090909)(149.292929292929,-9.06818181818182)(136.229797979798,-8.90909090909091)(134.363636363636,-8.89393939393939)(119.434343434343,-8.84090909090909)(106.993265993266,-8.72727272727273)(104.505050505051,-8.70454545454545)(91.4419191919192,-8.54545454545455)(89.5757575757576,-8.5)(78.3787878787879,-8.36363636363636)(74.6464646464647,-8.27272727272727)(72.1582491582492,-8.18181818181818)(74.6464646464647,-8.09090909090909)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.72727272727273)(459.075757575758,-7.63636363636364)(462.808080808081,-7.60606060606061)(472.138888888889,-7.45454545454546)(477.737373737374,-7.40909090909091)(492.666666666667,-7.40909090909091)(507.59595959596,-7.43181818181818)(522.525252525253,-7.38636363636364)(537.454545454546,-7.38636363636364)(552.383838383838,-7.40909090909091)(567.313131313131,-7.43939393939394)(569.801346801347,-7.45454545454546)(582.242424242424,-7.60606060606061)(584.73063973064,-7.63636363636364)(597.171717171717,-7.75)(608.368686868687,-7.81818181818182)(612.10101010101,-7.90909090909091)(613.967171717172,-8)(623.29797979798,-8.18181818181818)(627.030303030303,-8.27272727272727)(628.274410774411,-8.36363636363636)(627.030303030303,-8.40909090909091)(619.565656565657,-8.54545454545455)(613.967171717172,-8.72727272727273)(612.10101010101,-8.74242424242424)(597.171717171717,-8.75)(582.242424242424,-8.87878787878788)(578.510101010101,-8.90909090909091)(567.313131313131,-8.95454545454546)(552.383838383838,-8.97727272727273)(537.454545454546,-8.97727272727273)(522.525252525253,-8.97727272727273)(507.59595959596,-9.02272727272727)(492.666666666667,-8.95454545454546)(488.934343434343,-8.90909090909091)(477.737373737374,-8.77272727272727)(474.005050505051,-8.72727272727273)(462.808080808081,-8.63636363636364)(447.878787878788,-8.61363636363636)(436.681818181818,-8.54545454545455)(440.414141414141,-8.36363636363636)(435.43771043771,-8.18181818181818)(435.43771043771,-8)(440.414141414141,-7.81818181818182)(447.878787878788,-7.72727272727273)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (119.434343434343,-8.15151515151515)(131.875420875421,-8)(134.363636363636,-7.96969696969697)(149.292929292929,-7.84848484848485)(156.757575757576,-7.81818181818182)(164.222222222222,-7.8030303030303)(179.151515151515,-7.8030303030303)(186.616161616162,-7.81818181818182)(194.080808080808,-7.86363636363636)(209.010101010101,-7.93181818181818)(223.939393939394,-7.98181818181818)(226.427609427609,-8)(237.002525252525,-8.18181818181818)(238.868686868687,-8.27272727272727)(241.356902356902,-8.36363636363636)(238.868686868687,-8.45454545454545)(236.380471380471,-8.54545454545455)(231.40404040404,-8.72727272727273)(223.939393939394,-8.75)(209.010101010101,-8.75)(194.080808080808,-8.79545454545455)(179.151515151515,-8.77272727272727)(164.222222222222,-8.77272727272727)(160.489898989899,-8.72727272727273)(149.292929292929,-8.65909090909091)(134.363636363636,-8.56818181818182)(130.631313131313,-8.54545454545455)(119.434343434343,-8.40909090909091)(117.568181818182,-8.36363636363636)(116.946127946128,-8.18181818181818)(119.434343434343,-8.15151515151515)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182)(373.232323232323,-7.63636363636364)(1313.77777777778,-9.09090909090909)(1015.19191919192,-9.09090909090909)(194.080808080808,-9.09090909090909)(627.030303030303,-8.90909090909091)(223.939393939394,-7.45454545454546)(1104.76767676768,-8.18181818181818)(940.545454545455,-7.27272727272727)(1403.35353535354,-8.18181818181818)(134.363636363636,-8)(432.949494949495,-8.36363636363636)(1059.9797979798,-7.27272727272727)(836.040404040404,-7.81818181818182)(1298.84848484848,-10.1818181818182)(791.252525252525,-9.27272727272727)(1418.28282828283,-9.27272727272727)(940.545454545455,-9.27272727272727)(1104.76767676768,-9.45454545454546)(298.585858585859,-8.72727272727273)(597.171717171717,-7.27272727272727)(447.878787878788,-7.27272727272727)(1298.84848484848,-7.81818181818182)(985.333333333333,-10.1818181818182)(74.6464646464647,-8)(1239.13131313131,-8.72727272727273)(462.808080808081,-9.09090909090909)(1119.69696969697,-10.1818181818182)(776.323232323232,-8.54545454545455)(1000.26262626263,-8.54545454545455)(1388.42424242424,-10.1818181818182)(1179.41414141414,-7.45454545454546)(298.585858585859,-7.81818181818182)(119.434343434343,-8.72727272727273)(865.89898989899,-9.81818181818182)(656.888888888889,-8.72727272727273)(149.292929292929,-7.45454545454546)(1418.28282828283,-8.36363636363636)(955.474747474747,-8)(1224.20202020202,-9.45454545454546)(447.878787878788,-7.81818181818182)(612.10101010101,-8)(1104.76767676768,-8.54545454545455)(850.969696969697,-7.63636363636364)(895.757575757576,-8.72727272727273)(1224.20202020202,-10.1818181818182)(223.939393939394,-8.36363636363636)(1045.05050505051,-7.27272727272727)(597.171717171717,-9.09090909090909)(1448.14141414141,-8.90909090909091)(1030.12121212121,-9.45454545454546)(1328.70707070707,-7.63636363636364)(373.232323232323,-8.54545454545455)(1283.91919191919,-8.54545454545455)(1448.14141414141,-9.63636363636364)(955.474747474747,-7.27272727272727)(1059.9797979798,-10.1818181818182)(791.252525252525,-8.18181818181818)(1283.91919191919,-9.27272727272727)(910.686868686869,-10)(582.242424242424,-7.27272727272727)(253.79797979798,-8.90909090909091)(104.505050505051,-7.63636363636364)(1179.41414141414,-8.36363636363636)(1134.62626262626,-7.45454545454546)(462.808080808081,-8.72727272727273)(1030.12121212121,-8)(656.888888888889,-8)(1328.70707070707,-10.1818181818182)(791.252525252525,-9.09090909090909)(462.808080808081,-7.27272727272727)(74.6464646464647,-8.18181818181818)(1149.55555555556,-9.45454545454546)(149.292929292929,-8.90909090909091)(1239.13131313131,-7.63636363636364)(268.727272727273,-7.81818181818182)(910.686868686869,-9.09090909090909)(1373.49494949495,-8)(1059.9797979798,-8.72727272727273)(1179.41414141414,-10.1818181818182)(597.171717171717,-8.72727272727273)(432.949494949495,-8.18181818181818)(836.040404040404,-9.63636363636364)(1418.28282828283,-9.45454545454546)(910.686868686869,-8.36363636363636)(1000.26262626263,-10.1818181818182)(164.222222222222,-7.45454545454546)(477.737373737374,-9.09090909090909)(895.757575757576,-7.45454545454546)(1433.21212121212,-8.72727272727273)(1418.28282828283,-10)(985.333333333333,-9.45454545454546)(1179.41414141414,-8.90909090909091)(418.020202020202,-7.45454545454546)(313.515151515152,-8.36363636363636)(776.323232323232,-8.72727272727273)(537.454545454546,-7.45454545454546)(1104.76767676768,-7.45454545454546)(1283.91919191919,-10.1818181818182)(1283.91919191919,-9.09090909090909)(1000.26262626263,-7.27272727272727)(223.939393939394,-8)(821.111111111111,-8)(1254.06060606061,-7.63636363636364)(1104.76767676768,-10.1818181818182)(104.505050505051,-8.54545454545455)(627.030303030303,-7.63636363636364)(582.242424242424,-9.09090909090909)(238.868686868687,-8.90909090909091)(1209.27272727273,-8.36363636363636)(1358.56565656566,-7.81818181818182)(1059.9797979798,-8.18181818181818)(1089.83838383838,-9.27272727272727)(641.959595959596,-8.36363636363636)(925.616161616162,-10)(970.40404040404,-8.72727272727273)(89.5757575757576,-7.81818181818182)(418.020202020202,-8.72727272727273)(1373.49494949495,-10.1818181818182)(821.111111111111,-9.45454545454546)(1403.35353535354,-8.54545454545455)(373.232323232323,-8)(1209.27272727273,-10.1818181818182)(537.454545454546,-7.27272727272727)(940.545454545455,-8.18181818181818)(223.939393939394,-7.63636363636364)(1194.34343434343,-9.45454545454546)(1164.48484848485,-7.63636363636364)(865.89898989899,-7.63636363636364)(1448.14141414141,-9.45454545454546)(1030.12121212121,-10.1818181818182)(806.181818181818,-8.54545454545455)(1119.69696969697,-8.36363636363636)(164.222222222222,-8.90909090909091)(1283.91919191919,-8.90909090909091)(492.666666666667,-9.09090909090909)(1000.26262626263,-9.45454545454546)(641.959595959596,-8.72727272727273)(403.090909090909,-7.63636363636364)(1313.77777777778,-7.63636363636364)(612.10101010101,-7.45454545454546) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_380.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1448.14141414141,-9.24242424242424)(1450.62962962963,-9.27272727272727)(1460.58249158249,-9.45454545454546)(1461.20454545455,-9.63636363636364)(1450.62962962963,-9.81818181818182)(1448.14141414141,-9.84848484848485)(1435.70033670034,-10)(1433.21212121212,-10.030303030303)(1418.28282828283,-10.1136363636364)(1403.35353535354,-10.1590909090909)(1401.48737373737,-10.1818181818182)(1388.42424242424,-10.3409090909091)(1373.49494949495,-10.3409090909091)(1358.56565656566,-10.3454545454545)(1343.63636363636,-10.2727272727273)(1328.70707070707,-10.2878787878788)(1313.77777777778,-10.2878787878788)(1298.84848484848,-10.2272727272727)(1283.91919191919,-10.2575757575758)(1268.9898989899,-10.2878787878788)(1254.06060606061,-10.3484848484848)(1246.59595959596,-10.3636363636364)(1239.13131313131,-10.3818181818182)(1231.66666666667,-10.3636363636364)(1224.20202020202,-10.3484848484848)(1209.27272727273,-10.3181818181818)(1194.34343434343,-10.2575757575758)(1179.41414141414,-10.3181818181818)(1164.48484848485,-10.3181818181818)(1153.28787878788,-10.3636363636364)(1149.55555555556,-10.3818181818182)(1145.82323232323,-10.3636363636364)(1134.62626262626,-10.3181818181818)(1119.69696969697,-10.3484848484848)(1104.76767676768,-10.2878787878788)(1089.83838383838,-10.3181818181818)(1074.90909090909,-10.3181818181818)(1063.71212121212,-10.3636363636364)(1059.9797979798,-10.3818181818182)(1052.51515151515,-10.3636363636364)(1045.05050505051,-10.3484848484848)(1030.12121212121,-10.2878787878788)(1015.19191919192,-10.2272727272727)(1000.26262626263,-10.2272727272727)(985.333333333333,-10.2272727272727)(970.40404040404,-10.2)(966.671717171717,-10.1818181818182)(955.474747474747,-10.1363636363636)(940.545454545455,-10.0757575757576)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0909090909091)(895.757575757576,-10.0909090909091)(886.426767676768,-10)(880.828282828283,-9.94545454545455)(865.89898989899,-9.88636363636364)(860.300505050505,-9.81818181818182)(850.969696969697,-9.72727272727273)(836.040404040404,-9.69090909090909)(828.575757575758,-9.63636363636364)(821.111111111111,-9.54545454545455)(813.646464646465,-9.45454545454546)(806.181818181818,-9.4)(795.731313131313,-9.27272727272727)(791.252525252525,-9.18181818181818)(783.787878787879,-9.09090909090909)(777.816161616162,-8.90909090909091)(777.56734006734,-8.72727272727273)(780.80202020202,-8.54545454545455)(788.76430976431,-8.36363636363636)(791.252525252525,-8.34090909090909)(806.181818181818,-8.20454545454546)(807.674747474747,-8.18181818181818)(821.111111111111,-8.01818181818182)(822.60404040404,-8)(836.040404040404,-7.83636363636364)(837.284511784512,-7.81818181818182)(849.103535353535,-7.63636363636364)(850.969696969697,-7.60606060606061)(865.89898989899,-7.50909090909091)(869.631313131313,-7.45454545454546)(880.828282828283,-7.29090909090909)(895.757575757576,-7.29090909090909)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(914.419191919192,-7.27272727272727)(925.616161616162,-7.31818181818182)(936.813131313131,-7.27272727272727)(940.545454545455,-7.25454545454546)(955.474747474747,-7.22727272727273)(970.40404040404,-7.16666666666667)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.20454545454546)(1026.38888888889,-7.27272727272727)(1030.12121212121,-7.28787878787879)(1045.05050505051,-7.31818181818182)(1059.9797979798,-7.28787878787879)(1074.90909090909,-7.31818181818182)(1089.83838383838,-7.34848484848485)(1104.76767676768,-7.31818181818182)(1119.69696969697,-7.34848484848485)(1134.62626262626,-7.34848484848485)(1149.55555555556,-7.40909090909091)(1164.48484848485,-7.36363636363636)(1179.41414141414,-7.29545454545455)(1194.34343434343,-7.31818181818182)(1205.5404040404,-7.45454545454546)(1209.27272727273,-7.46969696969697)(1224.20202020202,-7.56060606060606)(1239.13131313131,-7.5)(1254.06060606061,-7.46969696969697)(1261.52525252525,-7.45454545454546)(1268.9898989899,-7.43636363636364)(1276.45454545455,-7.45454545454546)(1283.91919191919,-7.46969696969697)(1298.84848484848,-7.53030303030303)(1313.77777777778,-7.58181818181818)(1324.97474747475,-7.63636363636364)(1328.70707070707,-7.65151515151515)(1343.63636363636,-7.72727272727273)(1356.07744107744,-7.81818181818182)(1358.56565656566,-7.83636363636364)(1373.49494949495,-7.88636363636364)(1388.42424242424,-7.93181818181818)(1403.35353535354,-7.96969696969697)(1405.84175084175,-8)(1410.81818181818,-8.18181818181818)(1416.7898989899,-8.36363636363636)(1418.28282828283,-8.45454545454545)(1420.14898989899,-8.54545454545455)(1424.50336700337,-8.72727272727273)(1431.96801346801,-8.90909090909091)(1433.21212121212,-8.95454545454546)(1438.81060606061,-9.09090909090909)(1448.14141414141,-9.24242424242424)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1418.28282828283,-9.18181818181818)(1423.88131313131,-9.27272727272727)(1422.01515151515,-9.45454545454546)(1418.28282828283,-9.54545454545455)(1414.5505050505,-9.63636363636364)(1403.35353535354,-9.77272727272727)(1399.62121212121,-9.81818181818182)(1388.42424242424,-9.88636363636364)(1373.49494949495,-9.93181818181818)(1358.56565656566,-9.97727272727273)(1343.63636363636,-9.97727272727273)(1336.17171717172,-10)(1328.70707070707,-10.0151515151515)(1313.77777777778,-10.0151515151515)(1310.04545454545,-10)(1298.84848484848,-9.95454545454546)(1283.91919191919,-9.98181818181818)(1276.45454545455,-10)(1268.9898989899,-10.0151515151515)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.1060606060606)(1224.20202020202,-10.0757575757576)(1209.27272727273,-10.0454545454545)(1198.07575757576,-10)(1194.34343434343,-9.98181818181818)(1190.61111111111,-10)(1179.41414141414,-10.0454545454545)(1164.48484848485,-10.0454545454545)(1149.55555555556,-10.1060606060606)(1134.62626262626,-10.0454545454545)(1119.69696969697,-10.0757575757576)(1104.76767676768,-10.0151515151515)(1089.83838383838,-10.0454545454545)(1074.90909090909,-10.0454545454545)(1059.9797979798,-10.1060606060606)(1045.05050505051,-10.0757575757576)(1030.12121212121,-10.0151515151515)(1026.38888888889,-10)(1015.19191919192,-9.95454545454546)(1000.26262626263,-9.95454545454546)(985.333333333333,-9.95454545454546)(970.40404040404,-9.92424242424243)(955.474747474747,-9.86363636363636)(944.277777777778,-9.81818181818182)(940.545454545455,-9.8)(933.080808080808,-9.81818181818182)(925.616161616162,-9.83333333333333)(918.151515151515,-9.81818181818182)(910.686868686869,-9.79545454545455)(895.757575757576,-9.79545454545455)(880.828282828283,-9.65151515151515)(877.09595959596,-9.63636363636364)(865.89898989899,-9.56818181818182)(853.457912457912,-9.45454545454546)(850.969696969697,-9.43181818181818)(836.040404040404,-9.36363636363636)(828.575757575758,-9.27272727272727)(821.111111111111,-9.12121212121212)(818.622895622896,-9.09090909090909)(806.181818181818,-8.97727272727273)(802.449494949495,-8.90909090909091)(804.315656565657,-8.72727272727273)(806.181818181818,-8.68181818181818)(810.660606060606,-8.54545454545455)(819.867003367003,-8.36363636363636)(821.111111111111,-8.34545454545454)(834.547474747475,-8.18181818181818)(836.040404040404,-8.16363636363636)(849.476767676768,-8)(850.969696969697,-7.97727272727273)(864.032828282828,-7.81818181818182)(865.89898989899,-7.8030303030303)(880.828282828283,-7.65909090909091)(895.757575757576,-7.65909090909091)(899.489898989899,-7.63636363636364)(910.686868686869,-7.56818181818182)(925.616161616162,-7.59090909090909)(940.545454545455,-7.53030303030303)(955.474747474747,-7.5)(966.671717171717,-7.45454545454546)(970.40404040404,-7.43939393939394)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1009.59343434343,-7.45454545454546)(1015.19191919192,-7.52272727272727)(1030.12121212121,-7.56060606060606)(1045.05050505051,-7.59090909090909)(1059.9797979798,-7.56060606060606)(1074.90909090909,-7.59090909090909)(1089.83838383838,-7.62121212121212)(1097.30303030303,-7.63636363636364)(1104.76767676768,-7.65454545454546)(1119.69696969697,-7.68181818181818)(1134.62626262626,-7.68181818181818)(1149.55555555556,-7.68181818181818)(1164.48484848485,-7.65909090909091)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.62121212121212)(1183.14646464646,-7.63636363636364)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.79545454545455)(1216.73737373737,-7.81818181818182)(1224.20202020202,-7.83636363636364)(1227.93434343434,-7.81818181818182)(1239.13131313131,-7.77272727272727)(1254.06060606061,-7.74242424242424)(1268.9898989899,-7.71212121212121)(1283.91919191919,-7.74242424242424)(1298.84848484848,-7.8030303030303)(1302.58080808081,-7.81818181818182)(1313.77777777778,-7.87272727272727)(1328.70707070707,-7.92424242424242)(1341.14814814815,-8)(1343.63636363636,-8.02272727272727)(1358.56565656566,-8.16363636363636)(1366.0303030303,-8.18181818181818)(1373.49494949495,-8.21212121212121)(1388.42424242424,-8.34090909090909)(1389.91717171717,-8.36363636363636)(1395.88888888889,-8.54545454545455)(1401.86060606061,-8.72727272727273)(1403.35353535354,-8.77272727272727)(1407.83232323232,-8.90909090909091)(1412.68434343434,-9.09090909090909)(1418.28282828283,-9.18181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (373.232323232323,-7.66666666666667)(375.720538720539,-7.63636363636364)(388.161616161616,-7.48484848484849)(395.626262626263,-7.45454545454546)(403.090909090909,-7.42424242424243)(418.020202020202,-7.34090909090909)(432.949494949495,-7.31818181818182)(440.414141414141,-7.27272727272727)(447.878787878788,-7.24242424242424)(462.808080808081,-7.11363636363636)(470.272727272727,-7.09090909090909)(477.737373737374,-7.07272727272727)(485.20202020202,-7.09090909090909)(492.666666666667,-7.10606060606061)(507.59595959596,-7.10606060606061)(515.060606060606,-7.09090909090909)(522.525252525253,-7.07272727272727)(537.454545454546,-7.07272727272727)(544.919191919192,-7.09090909090909)(552.383838383838,-7.10909090909091)(567.313131313131,-7.11363636363636)(582.242424242424,-7.18181818181818)(593.439393939394,-7.27272727272727)(597.171717171717,-7.29545454545455)(612.10101010101,-7.43181818181818)(627.030303030303,-7.42424242424243)(634.494949494949,-7.45454545454546)(630.762626262626,-7.63636363636364)(641.959595959596,-7.77272727272727)(643.825757575758,-7.81818181818182)(647.558080808081,-8)(655.022727272727,-8.18181818181818)(655.39595959596,-8.36363636363636)(651.290404040404,-8.54545454545455)(646.438383838384,-8.72727272727273)(641.959595959596,-8.81818181818182)(630.762626262626,-8.90909090909091)(627.030303030303,-8.95454545454546)(612.10101010101,-9.06818181818182)(604.636363636364,-9.09090909090909)(597.171717171717,-9.12121212121212)(582.242424242424,-9.25)(574.777777777778,-9.27272727272727)(567.313131313131,-9.29090909090909)(552.383838383838,-9.34090909090909)(537.454545454546,-9.3030303030303)(522.525252525253,-9.3030303030303)(507.59595959596,-9.34090909090909)(492.666666666667,-9.36363636363636)(477.737373737374,-9.34090909090909)(472.138888888889,-9.27272727272727)(462.808080808081,-9.12121212121212)(460.319865319865,-9.09090909090909)(447.878787878788,-8.97727272727273)(432.949494949495,-8.93181818181818)(429.217171717172,-8.90909090909091)(418.020202020202,-8.77272727272727)(414.287878787879,-8.72727272727273)(403.090909090909,-8.59090909090909)(401.224747474747,-8.54545454545455)(403.090909090909,-8.45454545454545)(405.579124579125,-8.36363636363636)(403.090909090909,-8.31818181818182)(388.161616161616,-8.25)(380.69696969697,-8.18181818181818)(373.232323232323,-8.04545454545455)(370.744107744108,-8)(360.791245791246,-7.81818181818182)(373.232323232323,-7.66666666666667)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1239.13131313131,-8.68181818181818)(1241.61952861953,-8.72727272727273)(1251.57239057239,-8.90909090909091)(1246.59595959596,-9.09090909090909)(1239.13131313131,-9.22727272727273)(1231.66666666667,-9.27272727272727)(1224.20202020202,-9.3030303030303)(1209.27272727273,-9.3030303030303)(1194.34343434343,-9.3030303030303)(1179.41414141414,-9.36363636363636)(1164.48484848485,-9.42424242424243)(1157.0202020202,-9.45454545454546)(1149.55555555556,-9.48484848484848)(1142.09090909091,-9.45454545454546)(1134.62626262626,-9.42424242424243)(1119.69696969697,-9.42424242424243)(1104.76767676768,-9.36363636363636)(1089.83838383838,-9.31818181818182)(1074.90909090909,-9.40909090909091)(1067.44444444444,-9.45454545454546)(1059.9797979798,-9.48484848484848)(1045.05050505051,-9.48484848484848)(1030.12121212121,-9.48484848484848)(1026.38888888889,-9.45454545454546)(1015.19191919192,-9.31818181818182)(1000.26262626263,-9.31818181818182)(985.333333333333,-9.3030303030303)(970.40404040404,-9.36363636363636)(955.474747474747,-9.3030303030303)(948.010101010101,-9.27272727272727)(940.545454545455,-9.22727272727273)(929.348484848485,-9.09090909090909)(925.616161616162,-9.06060606060606)(913.175084175084,-8.90909090909091)(913.175084175084,-8.72727272727273)(913.175084175084,-8.54545454545455)(925.616161616162,-8.39393939393939)(928.104377104377,-8.36363636363636)(940.545454545455,-8.21212121212121)(948.010101010101,-8.18181818181818)(955.474747474747,-8.15151515151515)(970.40404040404,-8.09090909090909)(985.333333333333,-8.09090909090909)(1000.26262626263,-8.09090909090909)(1015.19191919192,-8.13636363636364)(1030.12121212121,-8.13636363636364)(1037.58585858586,-8.18181818181818)(1045.05050505051,-8.21212121212121)(1059.9797979798,-8.21212121212121)(1074.90909090909,-8.27272727272727)(1089.83838383838,-8.31818181818182)(1097.30303030303,-8.36363636363636)(1104.76767676768,-8.40909090909091)(1119.69696969697,-8.40909090909091)(1127.16161616162,-8.36363636363636)(1134.62626262626,-8.33333333333333)(1149.55555555556,-8.31818181818182)(1157.0202020202,-8.36363636363636)(1164.48484848485,-8.39393939393939)(1179.41414141414,-8.45454545454545)(1194.34343434343,-8.45454545454545)(1209.27272727273,-8.45454545454545)(1220.4696969697,-8.54545454545455)(1224.20202020202,-8.59090909090909)(1239.13131313131,-8.68181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (74.6464646464647,-8.04545454545455)(78.3787878787879,-8)(89.5757575757576,-7.86363636363636)(92.0639730639731,-7.81818181818182)(104.505050505051,-7.66666666666667)(106.371212121212,-7.63636363636364)(111.969696969697,-7.45454545454546)(119.434343434343,-7.38636363636364)(134.363636363636,-7.42424242424243)(149.292929292929,-7.42424242424243)(156.757575757576,-7.45454545454546)(164.222222222222,-7.48484848484849)(179.151515151515,-7.54545454545455)(190.348484848485,-7.63636363636364)(194.080808080808,-7.65151515151515)(209.010101010101,-7.68181818181818)(223.939393939394,-7.72727272727273)(238.868686868687,-7.79545454545455)(253.79797979798,-7.78787878787879)(268.727272727273,-7.68181818181818)(283.656565656566,-7.72727272727273)(286.144781144781,-7.81818181818182)(292.987373737374,-8)(291.121212121212,-8.18181818181818)(298.585858585859,-8.22727272727273)(309.782828282828,-8.36363636363636)(306.050505050505,-8.54545454545455)(298.585858585859,-8.57575757575757)(283.656565656566,-8.59090909090909)(272.459595959596,-8.72727272727273)(268.727272727273,-8.77272727272727)(261.262626262626,-8.90909090909091)(253.79797979798,-9.04545454545455)(251.309764309764,-9.09090909090909)(238.868686868687,-9.18181818181818)(223.939393939394,-9.15909090909091)(209.010101010101,-9.12121212121212)(194.080808080808,-9.12121212121212)(179.151515151515,-9.22727272727273)(164.222222222222,-9.24242424242424)(151.781144781145,-9.09090909090909)(149.292929292929,-9.06818181818182)(136.229797979798,-8.90909090909091)(134.363636363636,-8.89393939393939)(119.434343434343,-8.84090909090909)(106.993265993266,-8.72727272727273)(104.505050505051,-8.70909090909091)(89.5757575757576,-8.57575757575757)(87.0875420875421,-8.54545454545455)(74.6464646464647,-8.39393939393939)(72.1582491582492,-8.36363636363636)(69.0479797979798,-8.18181818181818)(74.6464646464647,-8.04545454545455)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.72727272727273)(459.075757575758,-7.63636363636364)(462.808080808081,-7.59090909090909)(468.406565656566,-7.45454545454546)(477.737373737374,-7.37878787878788)(492.666666666667,-7.37878787878788)(507.59595959596,-7.43181818181818)(522.525252525253,-7.38636363636364)(537.454545454546,-7.38636363636364)(552.383838383838,-7.40909090909091)(567.313131313131,-7.43939393939394)(569.801346801347,-7.45454545454546)(582.242424242424,-7.60606060606061)(584.73063973064,-7.63636363636364)(597.171717171717,-7.75)(608.368686868687,-7.81818181818182)(612.10101010101,-7.86363636363636)(617.699494949495,-8)(627.030303030303,-8.15151515151515)(628.274410774411,-8.18181818181818)(630.762626262626,-8.36363636363636)(627.030303030303,-8.45454545454545)(619.565656565657,-8.54545454545455)(613.967171717172,-8.72727272727273)(612.10101010101,-8.74242424242424)(597.171717171717,-8.75)(584.108585858586,-8.90909090909091)(582.242424242424,-8.92424242424242)(567.313131313131,-8.98484848484848)(552.383838383838,-9.02272727272727)(537.454545454546,-8.97727272727273)(522.525252525253,-8.97727272727273)(507.59595959596,-9.02272727272727)(492.666666666667,-8.95454545454546)(488.934343434343,-8.90909090909091)(477.737373737374,-8.77272727272727)(474.005050505051,-8.72727272727273)(462.808080808081,-8.63636363636364)(447.878787878788,-8.61363636363636)(436.681818181818,-8.54545454545455)(442.280303030303,-8.36363636363636)(438.54797979798,-8.18181818181818)(438.54797979798,-8)(440.414141414141,-7.81818181818182)(447.878787878788,-7.72727272727273)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (119.434343434343,-8.15151515151515)(131.875420875421,-8)(134.363636363636,-7.96969696969697)(149.292929292929,-7.84848484848485)(164.222222222222,-7.86363636363636)(179.151515151515,-7.90909090909091)(194.080808080808,-7.97727272727273)(209.010101010101,-7.95454545454546)(220.207070707071,-8)(223.939393939394,-8.02272727272727)(237.002525252525,-8.18181818181818)(238.868686868687,-8.27272727272727)(241.356902356902,-8.36363636363636)(238.868686868687,-8.45454545454545)(236.380471380471,-8.54545454545455)(231.40404040404,-8.72727272727273)(223.939393939394,-8.75)(209.010101010101,-8.75)(194.080808080808,-8.79545454545455)(179.151515151515,-8.77272727272727)(164.222222222222,-8.77272727272727)(160.489898989899,-8.72727272727273)(149.292929292929,-8.65909090909091)(134.363636363636,-8.56818181818182)(130.631313131313,-8.54545454545455)(119.434343434343,-8.40909090909091)(116.946127946128,-8.36363636363636)(115.70202020202,-8.18181818181818)(119.434343434343,-8.15151515151515)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182)(373.232323232323,-7.63636363636364)(1313.77777777778,-9.09090909090909)(1015.19191919192,-9.09090909090909)(194.080808080808,-9.09090909090909)(627.030303030303,-8.90909090909091)(223.939393939394,-7.45454545454546)(1104.76767676768,-8.18181818181818)(940.545454545455,-7.27272727272727)(1403.35353535354,-8.18181818181818)(134.363636363636,-8)(432.949494949495,-8.36363636363636)(1059.9797979798,-7.27272727272727)(836.040404040404,-7.81818181818182)(1298.84848484848,-10.1818181818182)(791.252525252525,-9.27272727272727)(1418.28282828283,-9.27272727272727)(940.545454545455,-9.27272727272727)(1104.76767676768,-9.45454545454546)(298.585858585859,-8.72727272727273)(597.171717171717,-7.27272727272727)(447.878787878788,-7.27272727272727)(1298.84848484848,-7.81818181818182)(985.333333333333,-10.1818181818182)(74.6464646464647,-8)(1239.13131313131,-8.72727272727273)(462.808080808081,-9.09090909090909)(1119.69696969697,-10.1818181818182)(776.323232323232,-8.54545454545455)(1000.26262626263,-8.54545454545455)(1388.42424242424,-10.1818181818182)(1179.41414141414,-7.45454545454546)(298.585858585859,-7.81818181818182)(119.434343434343,-8.72727272727273)(865.89898989899,-9.81818181818182)(656.888888888889,-8.72727272727273)(149.292929292929,-7.45454545454546)(1418.28282828283,-8.36363636363636)(955.474747474747,-8)(1224.20202020202,-9.45454545454546)(447.878787878788,-7.81818181818182)(612.10101010101,-8)(1104.76767676768,-8.54545454545455)(850.969696969697,-7.63636363636364)(895.757575757576,-8.72727272727273)(1224.20202020202,-10.1818181818182)(223.939393939394,-8.36363636363636)(1045.05050505051,-7.27272727272727)(597.171717171717,-9.09090909090909)(1448.14141414141,-8.90909090909091)(1030.12121212121,-9.45454545454546)(1328.70707070707,-7.63636363636364)(373.232323232323,-8.54545454545455)(1283.91919191919,-8.54545454545455)(1448.14141414141,-9.63636363636364)(955.474747474747,-7.27272727272727)(1059.9797979798,-10.1818181818182)(791.252525252525,-8.18181818181818)(1283.91919191919,-9.27272727272727)(910.686868686869,-10)(582.242424242424,-7.27272727272727)(253.79797979798,-8.90909090909091)(104.505050505051,-7.63636363636364)(1179.41414141414,-8.36363636363636)(1134.62626262626,-7.45454545454546)(462.808080808081,-8.72727272727273)(1030.12121212121,-8)(656.888888888889,-8)(1328.70707070707,-10.1818181818182)(791.252525252525,-9.09090909090909)(462.808080808081,-7.27272727272727)(74.6464646464647,-8.18181818181818)(1149.55555555556,-9.45454545454546)(149.292929292929,-8.90909090909091)(1239.13131313131,-7.63636363636364)(268.727272727273,-7.81818181818182)(910.686868686869,-9.09090909090909)(1373.49494949495,-8)(1059.9797979798,-8.72727272727273)(1179.41414141414,-10.1818181818182)(597.171717171717,-8.72727272727273)(432.949494949495,-8.18181818181818)(836.040404040404,-9.63636363636364)(1418.28282828283,-9.45454545454546)(910.686868686869,-8.36363636363636)(1000.26262626263,-10.1818181818182)(164.222222222222,-7.45454545454546)(477.737373737374,-9.09090909090909)(895.757575757576,-7.45454545454546)(1433.21212121212,-8.72727272727273)(1418.28282828283,-10)(985.333333333333,-9.45454545454546)(1179.41414141414,-8.90909090909091)(418.020202020202,-7.45454545454546)(313.515151515152,-8.36363636363636)(776.323232323232,-8.72727272727273)(537.454545454546,-7.45454545454546)(1104.76767676768,-7.45454545454546)(1283.91919191919,-10.1818181818182)(1283.91919191919,-9.09090909090909)(1000.26262626263,-7.27272727272727)(223.939393939394,-8)(821.111111111111,-8)(1254.06060606061,-7.63636363636364)(1104.76767676768,-10.1818181818182)(104.505050505051,-8.54545454545455)(627.030303030303,-7.63636363636364)(582.242424242424,-9.09090909090909)(238.868686868687,-8.90909090909091)(1209.27272727273,-8.36363636363636)(1358.56565656566,-7.81818181818182)(1059.9797979798,-8.18181818181818)(1089.83838383838,-9.27272727272727)(641.959595959596,-8.36363636363636)(925.616161616162,-10)(970.40404040404,-8.72727272727273)(89.5757575757576,-7.81818181818182)(418.020202020202,-8.72727272727273)(1373.49494949495,-10.1818181818182)(821.111111111111,-9.45454545454546)(1403.35353535354,-8.54545454545455)(373.232323232323,-8)(1209.27272727273,-10.1818181818182)(537.454545454546,-7.27272727272727)(940.545454545455,-8.18181818181818)(223.939393939394,-7.63636363636364)(1194.34343434343,-9.45454545454546)(1164.48484848485,-7.63636363636364)(865.89898989899,-7.63636363636364)(1448.14141414141,-9.45454545454546)(1030.12121212121,-10.1818181818182)(806.181818181818,-8.54545454545455)(1119.69696969697,-8.36363636363636)(164.222222222222,-8.90909090909091)(1283.91919191919,-8.90909090909091)(492.666666666667,-9.09090909090909)(1000.26262626263,-9.45454545454546)(641.959595959596,-8.72727272727273)(403.090909090909,-7.63636363636364)(1313.77777777778,-7.63636363636364)(612.10101010101,-7.45454545454546)(89.5757575757576,-8.36363636363636)(1045.05050505051,-7.45454545454546)(910.686868686869,-8.90909090909091)(268.727272727273,-8.72727272727273)(1074.90909090909,-8.90909090909091)(1388.42424242424,-8.36363636363636)(1313.77777777778,-10.1818181818182)(880.828282828283,-9.81818181818182)(1134.62626262626,-10.1818181818182)(477.737373737374,-7.27272727272727)(627.030303030303,-8.18181818181818)(179.151515151515,-7.81818181818182)(1418.28282828283,-8.90909090909091)(1433.21212121212,-9.81818181818182)(806.181818181818,-9.27272727272727)(910.686868686869,-7.45454545454546)(418.020202020202,-8.18181818181818)(1239.13131313131,-8.54545454545455)(567.313131313131,-9.09090909090909)(1119.69696969697,-9.45454545454546) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_40.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00028436207,-4.18181818181818)(1478.00028436207,-4.36363636363636)(1478.00028436207,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478.00007109153,-6.54545454545455)(1478.00028436207,-6.72727272727273)(1478.00049762651,-6.90909090909091)(1478.00063979942,-7.09090909090909)(1478.00063979942,-7.27272727272727)(1478.00063979942,-7.45454545454546)(1478.00063979942,-7.63636363636364)(1478.00063979942,-7.81818181818182)(1478.00063979942,-8)(1478.00063979942,-8.18181818181818)(1478.00049762651,-8.36363636363636)(1478.00049762651,-8.54545454545455)(1478.00049762651,-8.72727272727273)(1478.00063979942,-8.90909090909091)(1478.00063979942,-9.09090909090909)(1478.00063979942,-9.27272727272727)(1478.00063979942,-9.45454545454546)(1478.00063979942,-9.63636363636364)(1478.00063979942,-9.81818181818182)(1478.00063979942,-10)(1478.00063979942,-10.1818181818182)(1478.00063979942,-10.3636363636364)(1478.00063979942,-10.5454545454545)(1478.00078196962,-10.7272727272727)(1478.0005687133,-10.9090909090909)(1478.00035545089,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000355450892342165,-8.72727272727273)(-0.000568713303462667,-8.54545454545455)(-0.000781969621696758,-8.36363636363636)(-0.00063979941985036,-8.18181818181818)(-0.00063979941985036,-8)(-0.00063979941985036,-7.81818181818182)(-0.00063979941985036,-7.63636363636364)(-0.00063979941985036,-7.45454545454546)(-0.00063979941985036,-7.27272727272727)(-0.00063979941985036,-7.09090909090909)(-0.00063979941985036,-6.90909090909091)(-0.00063979941985036,-6.72727272727273)(-0.000497626510092015,-6.54545454545455)(-0.000497626510092015,-6.36363636363636)(-0.000355450892342165,-6.18181818181818)(-0.000284362067949707,-6)(-7.1091532562972e-05,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-6.09090909090909)(7.46464646464646,-6)(14.9292929292929,-5.96969696969697)(29.8585858585859,-5.90909090909091)(44.7878787878788,-5.84848484848485)(52.2525252525253,-5.81818181818182)(59.7171717171717,-5.78787878787879)(74.6464646464647,-5.72727272727273)(89.5757575757576,-5.66666666666667)(97.040404040404,-5.63636363636364)(104.505050505051,-5.60606060606061)(119.434343434343,-5.54545454545455)(134.363636363636,-5.54545454545455)(149.292929292929,-5.54545454545455)(164.222222222222,-5.54545454545455)(179.151515151515,-5.54545454545455)(194.080808080808,-5.54545454545455)(209.010101010101,-5.54545454545455)(223.939393939394,-5.54545454545455)(238.868686868687,-5.60606060606061)(246.333333333333,-5.63636363636364)(253.79797979798,-5.66666666666667)(268.727272727273,-5.72727272727273)(283.656565656566,-5.72727272727273)(298.585858585859,-5.72727272727273)(313.515151515152,-5.72727272727273)(328.444444444444,-5.72727272727273)(343.373737373737,-5.72727272727273)(358.30303030303,-5.72727272727273)(373.232323232323,-5.72727272727273)(388.161616161616,-5.72727272727273)(403.090909090909,-5.72727272727273)(418.020202020202,-5.72727272727273)(432.949494949495,-5.72727272727273)(447.878787878788,-5.72727272727273)(462.808080808081,-5.72727272727273)(477.737373737374,-5.72727272727273)(492.666666666667,-5.72727272727273)(507.59595959596,-5.72727272727273)(522.525252525253,-5.78787878787879)(529.989898989899,-5.81818181818182)(537.454545454546,-5.84848484848485)(552.383838383838,-5.90909090909091)(567.313131313131,-5.96969696969697)(574.777777777778,-6)(582.242424242424,-6.03030303030303)(597.171717171717,-6.09090909090909)(612.10101010101,-6.15151515151515)(619.565656565657,-6.18181818181818)(627.030303030303,-6.21212121212121)(641.959595959596,-6.33333333333333)(649.424242424242,-6.36363636363636)(656.888888888889,-6.39393939393939)(671.818181818182,-6.51515151515151)(679.282828282828,-6.54545454545455)(686.747474747475,-6.57575757575758)(701.676767676768,-6.63636363636364)(712.873737373737,-6.54545454545455)(716.606060606061,-6.51515151515151)(731.535353535354,-6.51515151515151)(746.464646464646,-6.51515151515151)(753.929292929293,-6.54545454545455)(761.393939393939,-6.57575757575758)(765.126262626263,-6.54545454545455)(776.323232323232,-6.45454545454545)(783.787878787879,-6.36363636363636)(791.252525252525,-6.27272727272727)(798.717171717172,-6.18181818181818)(806.181818181818,-6.09090909090909)(813.646464646465,-6)(821.111111111111,-5.90909090909091)(832.308080808081,-5.81818181818182)(836.040404040404,-5.78787878787879)(850.969696969697,-5.66666666666667)(858.434343434343,-5.63636363636364)(865.89898989899,-5.60606060606061)(880.828282828283,-5.54545454545455)(895.757575757576,-5.54545454545455)(910.686868686869,-5.60606060606061)(918.151515151515,-5.63636363636364)(925.616161616162,-5.66666666666667)(940.545454545455,-5.72727272727273)(955.474747474747,-5.72727272727273)(970.40404040404,-5.72727272727273)(985.333333333333,-5.78787878787879)(992.79797979798,-5.81818181818182)(1000.26262626263,-5.84848484848485)(1015.19191919192,-5.90909090909091)(1030.12121212121,-5.90909090909091)(1045.05050505051,-5.90909090909091)(1059.9797979798,-5.90909090909091)(1074.90909090909,-5.90909090909091)(1089.83838383838,-5.90909090909091)(1104.76767676768,-5.90909090909091)(1119.69696969697,-5.90909090909091)(1134.62626262626,-5.84848484848485)(1142.09090909091,-5.81818181818182)(1149.55555555556,-5.78787878787879)(1164.48484848485,-5.72727272727273)(1179.41414141414,-5.66666666666667)(1186.87878787879,-5.63636363636364)(1194.34343434343,-5.60606060606061)(1209.27272727273,-5.48484848484849)(1216.73737373737,-5.45454545454546)(1224.20202020202,-5.42424242424242)(1239.13131313131,-5.36363636363636)(1254.06060606061,-5.36363636363636)(1268.9898989899,-5.36363636363636)(1283.91919191919,-5.42424242424242)(1298.84848484848,-5.42424242424242)(1313.77777777778,-5.42424242424242)(1328.70707070707,-5.42424242424242)(1336.17171717172,-5.45454545454546)(1343.63636363636,-5.48484848484849)(1358.56565656566,-5.60606060606061)(1362.29797979798,-5.63636363636364)(1373.49494949495,-5.72727272727273)(1380.9595959596,-5.81818181818182)(1388.42424242424,-5.90909090909091)(1395.88888888889,-6)(1403.35353535354,-6.09090909090909)(1410.81818181818,-6.18181818181818)(1418.28282828283,-6.27272727272727)(1425.74747474747,-6.36363636363636)(1433.21212121212,-6.45454545454545)(1444.40909090909,-6.54545454545455)(1448.14141414141,-6.57575757575758)(1463.07070707071,-6.6969696969697)(1470.53535353535,-6.72727272727273)(1478,-6.75757575757576)(1478.00017772375,-6.90909090909091)(1478.00031989971,-7.09090909090909)(1478.00031989971,-7.27272727272727)(1478.00031989971,-7.45454545454546)(1478.00031989971,-7.63636363636364)(1478.00031989971,-7.81818181818182)(1478.00031989971,-8)(1478.00031989971,-8.18181818181818)(1478.00017772375,-8.36363636363636)(1478.00017772375,-8.54545454545455)(1478.00017772375,-8.72727272727273)(1478.00031989971,-8.90909090909091)(1478.00031989971,-9.09090909090909)(1478.00031989971,-9.27272727272727)(1478.00031989971,-9.45454545454546)(1478.00031989971,-9.63636363636364)(1478.00031989971,-9.81818181818182)(1478.00031989971,-10)(1478.00031989971,-10.1818181818182)(1478.00031989971,-10.3636363636364)(1478.00031989971,-10.5454545454545)(1478.00046207296,-10.7272727272727)(1478.00024881207,-10.9090909090909)(1478.00003554509,-11.0909090909091)(1478,-11.1090909090909)(1470.53535353535,-11.0909090909091)(1463.07070707071,-11.0606060606061)(1448.14141414141,-11)(1433.21212121212,-11.0606060606061)(1425.74747474747,-11.0909090909091)(1418.28282828283,-11.1212121212121)(1403.35353535354,-11.2424242424242)(1395.88888888889,-11.2727272727273)(1388.42424242424,-11.3030303030303)(1373.49494949495,-11.3636363636364)(1358.56565656566,-11.4242424242424)(1351.10101010101,-11.4545454545455)(1343.63636363636,-11.4848484848485)(1328.70707070707,-11.5454545454545)(1313.77777777778,-11.5454545454545)(1298.84848484848,-11.5454545454545)(1283.91919191919,-11.5454545454545)(1268.9898989899,-11.5454545454545)(1254.06060606061,-11.5454545454545)(1239.13131313131,-11.5454545454545)(1224.20202020202,-11.5454545454545)(1209.27272727273,-11.5454545454545)(1194.34343434343,-11.5454545454545)(1179.41414141414,-11.5454545454545)(1164.48484848485,-11.5454545454545)(1149.55555555556,-11.5454545454545)(1134.62626262626,-11.5454545454545)(1119.69696969697,-11.5454545454545)(1104.76767676768,-11.5454545454545)(1089.83838383838,-11.5454545454545)(1074.90909090909,-11.4848484848485)(1067.44444444444,-11.4545454545455)(1059.9797979798,-11.4242424242424)(1045.05050505051,-11.3636363636364)(1030.12121212121,-11.3636363636364)(1015.19191919192,-11.3636363636364)(1000.26262626263,-11.3636363636364)(985.333333333333,-11.3030303030303)(977.868686868687,-11.2727272727273)(970.40404040404,-11.2424242424242)(955.474747474747,-11.1818181818182)(940.545454545455,-11.1212121212121)(933.080808080808,-11.0909090909091)(925.616161616162,-11.0606060606061)(910.686868686869,-11)(895.757575757576,-11)(880.828282828283,-10.9393939393939)(873.363636363636,-10.9090909090909)(865.89898989899,-10.8787878787879)(850.969696969697,-10.8181818181818)(836.040404040404,-10.7575757575758)(828.575757575758,-10.7272727272727)(821.111111111111,-10.6969696969697)(806.181818181818,-10.5757575757576)(798.717171717172,-10.5454545454545)(791.252525252525,-10.5151515151515)(776.323232323232,-10.3939393939394)(768.858585858586,-10.3636363636364)(761.393939393939,-10.3333333333333)(746.464646464646,-10.2727272727273)(731.535353535354,-10.2121212121212)(724.070707070707,-10.1818181818182)(716.606060606061,-10.1515151515152)(701.676767676768,-10.0909090909091)(686.747474747475,-10.0909090909091)(671.818181818182,-10.0909090909091)(656.888888888889,-10.030303030303)(649.424242424242,-10)(641.959595959596,-9.96969696969697)(627.030303030303,-9.96969696969697)(619.565656565657,-10)(612.10101010101,-10.030303030303)(597.171717171717,-10.0909090909091)(582.242424242424,-10.0909090909091)(567.313131313131,-10.0909090909091)(552.383838383838,-10.1515151515152)(544.919191919192,-10.1818181818182)(537.454545454546,-10.2121212121212)(522.525252525253,-10.2727272727273)(507.59595959596,-10.2727272727273)(492.666666666667,-10.3333333333333)(485.20202020202,-10.3636363636364)(477.737373737374,-10.3939393939394)(462.808080808081,-10.4545454545455)(447.878787878788,-10.4545454545455)(432.949494949495,-10.4545454545455)(418.020202020202,-10.4545454545455)(403.090909090909,-10.4545454545455)(388.161616161616,-10.3939393939394)(380.69696969697,-10.3636363636364)(373.232323232323,-10.3333333333333)(358.30303030303,-10.2727272727273)(343.373737373737,-10.2727272727273)(328.444444444444,-10.2727272727273)(313.515151515152,-10.2727272727273)(298.585858585859,-10.2727272727273)(283.656565656566,-10.2727272727273)(268.727272727273,-10.2727272727273)(253.79797979798,-10.2727272727273)(238.868686868687,-10.2727272727273)(223.939393939394,-10.2727272727273)(209.010101010101,-10.2727272727273)(194.080808080808,-10.2727272727273)(179.151515151515,-10.2727272727273)(164.222222222222,-10.2727272727273)(149.292929292929,-10.2121212121212)(141.828282828283,-10.1818181818182)(134.363636363636,-10.1515151515152)(119.434343434343,-10.0909090909091)(104.505050505051,-10.0909090909091)(89.5757575757576,-10.030303030303)(82.1111111111111,-10)(74.6464646464647,-9.96969696969697)(59.7171717171717,-9.84848484848485)(55.9848484848485,-9.81818181818182)(44.7878787878788,-9.72727272727273)(37.3232323232323,-9.63636363636364)(29.8585858585859,-9.5)(27.3703703703704,-9.45454545454546)(22.3939393939394,-9.27272727272727)(22.3939393939394,-9.09090909090909)(22.3939393939394,-8.90909090909091)(14.9292929292929,-8.81818181818182)(0,-8.74545454545454)(-3.55450892355425e-05,-8.72727272727273)(-0.00024881207026616,-8.54545454545455)(-0.000462072958277768,-8.36363636363636)(-0.000319899709928495,-8.18181818181818)(-0.000319899709928495,-8)(-0.000319899709928495,-7.81818181818182)(-0.000319899709928495,-7.63636363636364)(-0.000319899709928495,-7.45454545454546)(-0.000319899709928495,-7.27272727272727)(-0.000319899709928495,-7.09090909090909)(-0.000319899709928495,-6.90909090909091)(-0.000319899709928495,-6.72727272727273)(-0.000177723753604291,-6.54545454545455)(-0.000177723753604291,-6.36363636363636)(-3.55450892355425e-05,-6.18181818181818)(0,-6.09090909090909)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1074.90909090909,-8.93181818181818)(1087.97222222222,-9.09090909090909)(1087.97222222222,-9.27272727272727)(1074.90909090909,-9.43181818181818)(1071.17676767677,-9.45454545454546)(1059.9797979798,-9.5)(1045.05050505051,-9.5)(1033.85353535354,-9.45454545454546)(1030.12121212121,-9.43181818181818)(1015.19191919192,-9.31818181818182)(1013.32575757576,-9.27272727272727)(1013.32575757576,-9.09090909090909)(1015.19191919192,-9.06060606060606)(1030.12121212121,-8.93181818181818)(1033.85353535354,-8.90909090909091)(1045.05050505051,-8.86363636363636)(1059.9797979798,-8.86363636363636)(1071.17676767677,-8.90909090909091)(1074.90909090909,-8.93181818181818)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_400.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1448.14141414141,-9.24242424242424)(1450.62962962963,-9.27272727272727)(1460.58249158249,-9.45454545454546)(1461.20454545455,-9.63636363636364)(1450.62962962963,-9.81818181818182)(1448.14141414141,-9.84848484848485)(1435.70033670034,-10)(1433.21212121212,-10.030303030303)(1418.28282828283,-10.1136363636364)(1403.35353535354,-10.1590909090909)(1401.48737373737,-10.1818181818182)(1388.42424242424,-10.3409090909091)(1373.49494949495,-10.3454545454545)(1358.56565656566,-10.3484848484848)(1343.63636363636,-10.2878787878788)(1328.70707070707,-10.2878787878788)(1313.77777777778,-10.2878787878788)(1298.84848484848,-10.2272727272727)(1283.91919191919,-10.2272727272727)(1268.9898989899,-10.2272727272727)(1254.06060606061,-10.2878787878788)(1239.13131313131,-10.3484848484848)(1224.20202020202,-10.3484848484848)(1209.27272727273,-10.2878787878788)(1194.34343434343,-10.2272727272727)(1179.41414141414,-10.2878787878788)(1164.48484848485,-10.3181818181818)(1153.28787878788,-10.3636363636364)(1149.55555555556,-10.3818181818182)(1145.82323232323,-10.3636363636364)(1134.62626262626,-10.3181818181818)(1119.69696969697,-10.3484848484848)(1104.76767676768,-10.2878787878788)(1089.83838383838,-10.3484848484848)(1074.90909090909,-10.3484848484848)(1071.17676767677,-10.3636363636364)(1059.9797979798,-10.4090909090909)(1048.78282828283,-10.3636363636364)(1045.05050505051,-10.3484848484848)(1030.12121212121,-10.2878787878788)(1015.19191919192,-10.2272727272727)(1000.26262626263,-10.2272727272727)(985.333333333333,-10.2272727272727)(974.136363636364,-10.1818181818182)(970.40404040404,-10.1666666666667)(955.474747474747,-10.1060606060606)(940.545454545455,-10.0454545454545)(925.616161616162,-10.1060606060606)(910.686868686869,-10.0909090909091)(895.757575757576,-10.0909090909091)(886.426767676768,-10)(880.828282828283,-9.94545454545455)(865.89898989899,-9.88636363636364)(860.300505050505,-9.81818181818182)(850.969696969697,-9.72727272727273)(836.040404040404,-9.69090909090909)(828.575757575758,-9.63636363636364)(821.111111111111,-9.54545454545455)(813.646464646465,-9.45454545454546)(806.181818181818,-9.4)(795.731313131313,-9.27272727272727)(791.252525252525,-9.20454545454546)(778.811447811448,-9.09090909090909)(776.323232323232,-9)(774.830303030303,-8.90909090909091)(773.835016835017,-8.72727272727273)(776.323232323232,-8.68181818181818)(780.80202020202,-8.54545454545455)(788.76430976431,-8.36363636363636)(791.252525252525,-8.34090909090909)(804.315656565657,-8.18181818181818)(806.181818181818,-8.15151515151515)(818.622895622896,-8)(821.111111111111,-7.97727272727273)(836.040404040404,-7.83333333333333)(837.284511784512,-7.81818181818182)(849.103535353535,-7.63636363636364)(850.969696969697,-7.60606060606061)(865.89898989899,-7.50909090909091)(869.631313131313,-7.45454545454546)(880.828282828283,-7.29090909090909)(895.757575757576,-7.29090909090909)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(914.419191919192,-7.27272727272727)(925.616161616162,-7.31818181818182)(936.813131313131,-7.27272727272727)(940.545454545455,-7.25454545454546)(955.474747474747,-7.22727272727273)(970.40404040404,-7.16666666666667)(985.333333333333,-7.10606060606061)(1000.26262626263,-7.10606060606061)(1015.19191919192,-7.20454545454546)(1026.38888888889,-7.27272727272727)(1030.12121212121,-7.28787878787879)(1045.05050505051,-7.31818181818182)(1056.24747474747,-7.27272727272727)(1059.9797979798,-7.25454545454546)(1063.71212121212,-7.27272727272727)(1074.90909090909,-7.31818181818182)(1089.83838383838,-7.34848484848485)(1104.76767676768,-7.34848484848485)(1119.69696969697,-7.34848484848485)(1134.62626262626,-7.34848484848485)(1149.55555555556,-7.40909090909091)(1164.48484848485,-7.36363636363636)(1179.41414141414,-7.29545454545455)(1194.34343434343,-7.31818181818182)(1201.80808080808,-7.45454545454546)(1209.27272727273,-7.5)(1224.20202020202,-7.59090909090909)(1239.13131313131,-7.53030303030303)(1254.06060606061,-7.46969696969697)(1268.9898989899,-7.46969696969697)(1283.91919191919,-7.53030303030303)(1298.84848484848,-7.59090909090909)(1313.77777777778,-7.61818181818182)(1317.5101010101,-7.63636363636364)(1328.70707070707,-7.68181818181818)(1343.63636363636,-7.79545454545455)(1346.12457912458,-7.81818181818182)(1358.56565656566,-7.90909090909091)(1373.49494949495,-7.96969696969697)(1388.42424242424,-7.96969696969697)(1395.88888888889,-8)(1403.35353535354,-8.04545454545455)(1408.95202020202,-8.18181818181818)(1416.41666666667,-8.36363636363636)(1417.03872053872,-8.54545454545455)(1418.28282828283,-8.59090909090909)(1422.01515151515,-8.72727272727273)(1429.4797979798,-8.90909090909091)(1433.21212121212,-9)(1438.81060606061,-9.09090909090909)(1448.14141414141,-9.24242424242424)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1418.28282828283,-9.18181818181818)(1423.88131313131,-9.27272727272727)(1422.01515151515,-9.45454545454546)(1418.28282828283,-9.54545454545455)(1414.5505050505,-9.63636363636364)(1403.35353535354,-9.77272727272727)(1399.62121212121,-9.81818181818182)(1388.42424242424,-9.88636363636364)(1373.49494949495,-9.97727272727273)(1366.0303030303,-10)(1358.56565656566,-10.0227272727273)(1343.63636363636,-10.0151515151515)(1328.70707070707,-10.0151515151515)(1313.77777777778,-10.0151515151515)(1310.04545454545,-10)(1298.84848484848,-9.95454545454546)(1283.91919191919,-9.95454545454546)(1268.9898989899,-9.95454545454546)(1257.79292929293,-10)(1254.06060606061,-10.0151515151515)(1239.13131313131,-10.0757575757576)(1224.20202020202,-10.0757575757576)(1209.27272727273,-10.0151515151515)(1205.5404040404,-10)(1194.34343434343,-9.95454545454546)(1183.14646464646,-10)(1179.41414141414,-10.0151515151515)(1164.48484848485,-10.0454545454545)(1149.55555555556,-10.1060606060606)(1134.62626262626,-10.0454545454545)(1119.69696969697,-10.0757575757576)(1104.76767676768,-10.0151515151515)(1089.83838383838,-10.0757575757576)(1074.90909090909,-10.0757575757576)(1059.9797979798,-10.1363636363636)(1045.05050505051,-10.0757575757576)(1030.12121212121,-10.0151515151515)(1026.38888888889,-10)(1015.19191919192,-9.95454545454546)(1000.26262626263,-9.95454545454546)(985.333333333333,-9.95454545454546)(970.40404040404,-9.89393939393939)(955.474747474747,-9.83333333333333)(951.742424242424,-9.81818181818182)(940.545454545455,-9.77272727272727)(929.348484848485,-9.81818181818182)(925.616161616162,-9.83333333333333)(918.151515151515,-9.81818181818182)(910.686868686869,-9.79545454545455)(895.757575757576,-9.79545454545455)(880.828282828283,-9.65151515151515)(877.09595959596,-9.63636363636364)(865.89898989899,-9.56818181818182)(853.457912457912,-9.45454545454546)(850.969696969697,-9.43181818181818)(836.040404040404,-9.36363636363636)(828.575757575758,-9.27272727272727)(821.111111111111,-9.12121212121212)(817.378787878788,-9.09090909090909)(806.181818181818,-9.02272727272727)(799.961279461279,-8.90909090909091)(800.583333333333,-8.72727272727273)(806.181818181818,-8.63636363636364)(810.660606060606,-8.54545454545455)(817.378787878788,-8.36363636363636)(821.111111111111,-8.30909090909091)(831.561616161616,-8.18181818181818)(836.040404040404,-8.12727272727273)(849.103535353535,-8)(850.969696969697,-7.97727272727273)(864.032828282828,-7.81818181818182)(865.89898989899,-7.8030303030303)(880.828282828283,-7.65909090909091)(895.757575757576,-7.65909090909091)(899.489898989899,-7.63636363636364)(910.686868686869,-7.56818181818182)(925.616161616162,-7.59090909090909)(940.545454545455,-7.53030303030303)(955.474747474747,-7.5)(966.671717171717,-7.45454545454546)(970.40404040404,-7.43939393939394)(985.333333333333,-7.37878787878788)(1000.26262626263,-7.37878787878788)(1009.59343434343,-7.45454545454546)(1015.19191919192,-7.52272727272727)(1030.12121212121,-7.56060606060606)(1045.05050505051,-7.59090909090909)(1059.9797979798,-7.53030303030303)(1074.90909090909,-7.59090909090909)(1089.83838383838,-7.62121212121212)(1093.57070707071,-7.63636363636364)(1104.76767676768,-7.68181818181818)(1119.69696969697,-7.68181818181818)(1134.62626262626,-7.68181818181818)(1149.55555555556,-7.68181818181818)(1164.48484848485,-7.65909090909091)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.62121212121212)(1183.14646464646,-7.63636363636364)(1194.34343434343,-7.77272727272727)(1201.80808080808,-7.81818181818182)(1209.27272727273,-7.83636363636364)(1224.20202020202,-7.86363636363636)(1235.39898989899,-7.81818181818182)(1239.13131313131,-7.8030303030303)(1254.06060606061,-7.74242424242424)(1268.9898989899,-7.74242424242424)(1283.91919191919,-7.8030303030303)(1287.65151515152,-7.81818181818182)(1298.84848484848,-7.86363636363636)(1313.77777777778,-7.89393939393939)(1328.70707070707,-7.95454545454546)(1334.30555555556,-8)(1343.63636363636,-8.09090909090909)(1356.07744107744,-8.18181818181818)(1358.56565656566,-8.20454545454546)(1373.49494949495,-8.29545454545455)(1384.69191919192,-8.36363636363636)(1388.42424242424,-8.39393939393939)(1394.64478114478,-8.54545454545455)(1399.62121212121,-8.72727272727273)(1403.35353535354,-8.86363636363636)(1404.84646464646,-8.90909090909091)(1412.68434343434,-9.09090909090909)(1418.28282828283,-9.18181818181818)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (373.232323232323,-7.68181818181818)(375.720538720539,-7.63636363636364)(388.161616161616,-7.48484848484849)(395.626262626263,-7.45454545454546)(403.090909090909,-7.42424242424243)(418.020202020202,-7.34090909090909)(432.949494949495,-7.31818181818182)(440.414141414141,-7.27272727272727)(447.878787878788,-7.24242424242424)(462.808080808081,-7.11363636363636)(470.272727272727,-7.09090909090909)(477.737373737374,-7.07272727272727)(485.20202020202,-7.09090909090909)(492.666666666667,-7.10606060606061)(507.59595959596,-7.10606060606061)(515.060606060606,-7.09090909090909)(522.525252525253,-7.07272727272727)(537.454545454546,-7.07272727272727)(552.383838383838,-7.07272727272727)(567.313131313131,-7.07272727272727)(574.777777777778,-7.09090909090909)(582.242424242424,-7.12121212121212)(594.683501683502,-7.27272727272727)(597.171717171717,-7.29545454545455)(612.10101010101,-7.43181818181818)(627.030303030303,-7.42424242424243)(634.494949494949,-7.45454545454546)(630.762626262626,-7.63636363636364)(636.361111111111,-7.81818181818182)(637.480808080808,-8)(641.959595959596,-8.13636363636364)(644.447811447811,-8.18181818181818)(649.424242424242,-8.36363636363636)(644.447811447811,-8.54545454545455)(641.959595959596,-8.63636363636364)(639.47138047138,-8.72727272727273)(627.030303030303,-8.84090909090909)(619.565656565657,-8.90909090909091)(612.10101010101,-9)(597.171717171717,-9.07272727272727)(595.305555555556,-9.09090909090909)(582.242424242424,-9.25)(574.777777777778,-9.27272727272727)(567.313131313131,-9.29090909090909)(552.383838383838,-9.34090909090909)(537.454545454546,-9.3030303030303)(522.525252525253,-9.3030303030303)(507.59595959596,-9.34090909090909)(492.666666666667,-9.36363636363636)(477.737373737374,-9.34090909090909)(472.138888888889,-9.27272727272727)(462.808080808081,-9.15909090909091)(455.343434343434,-9.09090909090909)(447.878787878788,-9.02272727272727)(432.949494949495,-8.97727272727273)(425.484848484849,-8.90909090909091)(418.020202020202,-8.77272727272727)(414.287878787879,-8.72727272727273)(404.957070707071,-8.54545454545455)(410.555555555556,-8.36363636363636)(404.957070707071,-8.18181818181818)(403.090909090909,-8.15151515151515)(388.161616161616,-8.15151515151515)(375.720538720539,-8)(373.232323232323,-7.95454545454546)(362.035353535354,-7.81818181818182)(373.232323232323,-7.68181818181818)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1224.20202020202,-8.68181818181818)(1226.69023569024,-8.72727272727273)(1236.6430976431,-8.90909090909091)(1227.93434343434,-9.09090909090909)(1224.20202020202,-9.13636363636364)(1209.27272727273,-9.18181818181818)(1194.34343434343,-9.13636363636364)(1179.41414141414,-9.18181818181818)(1171.94949494949,-9.27272727272727)(1164.48484848485,-9.3030303030303)(1149.55555555556,-9.36363636363636)(1134.62626262626,-9.36363636363636)(1119.69696969697,-9.36363636363636)(1104.76767676768,-9.3030303030303)(1097.30303030303,-9.27272727272727)(1089.83838383838,-9.22727272727273)(1074.90909090909,-9.22727272727273)(1067.44444444444,-9.27272727272727)(1059.9797979798,-9.31818181818182)(1045.05050505051,-9.36363636363636)(1030.12121212121,-9.31818181818182)(1022.65656565657,-9.27272727272727)(1015.19191919192,-9.24242424242424)(1000.26262626263,-9.24242424242424)(992.79797979798,-9.27272727272727)(985.333333333333,-9.3030303030303)(970.40404040404,-9.3030303030303)(962.939393939394,-9.27272727272727)(955.474747474747,-9.22727272727273)(940.545454545455,-9.13636363636364)(933.080808080808,-9.09090909090909)(925.616161616162,-9.06060606060606)(913.175084175084,-8.90909090909091)(913.175084175084,-8.72727272727273)(913.175084175084,-8.54545454545455)(925.616161616162,-8.39393939393939)(928.104377104377,-8.36363636363636)(940.545454545455,-8.21212121212121)(948.010101010101,-8.18181818181818)(955.474747474747,-8.15151515151515)(970.40404040404,-8.09090909090909)(985.333333333333,-8.15151515151515)(1000.26262626263,-8.15151515151515)(1007.72727272727,-8.18181818181818)(1015.19191919192,-8.22727272727273)(1022.65656565657,-8.18181818181818)(1030.12121212121,-8.13636363636364)(1037.58585858586,-8.18181818181818)(1045.05050505051,-8.21212121212121)(1059.9797979798,-8.21212121212121)(1074.90909090909,-8.27272727272727)(1089.83838383838,-8.31818181818182)(1097.30303030303,-8.36363636363636)(1104.76767676768,-8.40909090909091)(1119.69696969697,-8.5)(1134.62626262626,-8.5)(1149.55555555556,-8.51515151515152)(1164.48484848485,-8.51515151515152)(1179.41414141414,-8.51515151515152)(1194.34343434343,-8.45454545454545)(1209.27272727273,-8.51515151515152)(1213.00505050505,-8.54545454545455)(1224.20202020202,-8.68181818181818)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.72727272727273)(459.075757575758,-7.63636363636364)(462.808080808081,-7.59090909090909)(468.406565656566,-7.45454545454546)(477.737373737374,-7.37878787878788)(492.666666666667,-7.37878787878788)(507.59595959596,-7.43181818181818)(522.525252525253,-7.38636363636364)(537.454545454546,-7.38636363636364)(552.383838383838,-7.37878787878788)(567.313131313131,-7.40909090909091)(574.777777777778,-7.45454545454546)(582.242424242424,-7.59090909090909)(584.73063973064,-7.63636363636364)(597.171717171717,-7.75)(604.636363636364,-7.81818181818182)(612.10101010101,-7.95454545454546)(613.345117845118,-8)(617.699494949495,-8.18181818181818)(625.164141414141,-8.36363636363636)(613.967171717172,-8.54545454545455)(612.10101010101,-8.59090909090909)(597.171717171717,-8.70454545454545)(594.683501683502,-8.72727272727273)(583.735353535354,-8.90909090909091)(582.242424242424,-8.92424242424242)(567.313131313131,-8.98484848484848)(552.383838383838,-9.02272727272727)(537.454545454546,-8.97727272727273)(522.525252525253,-8.97727272727273)(507.59595959596,-9.02272727272727)(492.666666666667,-8.95454545454546)(488.934343434343,-8.90909090909091)(477.737373737374,-8.77272727272727)(470.272727272727,-8.72727272727273)(462.808080808081,-8.68181818181818)(447.878787878788,-8.63636363636364)(436.681818181818,-8.54545454545455)(442.280303030303,-8.36363636363636)(438.54797979798,-8.18181818181818)(438.54797979798,-8)(440.414141414141,-7.81818181818182)(447.878787878788,-7.72727272727273)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (89.5757575757576,-8.04545454545455)(97.040404040404,-8)(104.505050505051,-7.90909090909091)(106.993265993266,-7.81818181818182)(111.969696969697,-7.63636363636364)(119.434343434343,-7.5)(134.363636363636,-7.60606060606061)(149.292929292929,-7.56818181818182)(164.222222222222,-7.60606060606061)(179.151515151515,-7.60606060606061)(186.616161616162,-7.63636363636364)(194.080808080808,-7.65151515151515)(209.010101010101,-7.71212121212121)(223.939393939394,-7.76363636363636)(231.40404040404,-7.81818181818182)(238.868686868687,-7.88636363636364)(253.79797979798,-7.95454545454546)(268.727272727273,-7.86363636363636)(283.656565656566,-7.86363636363636)(294.853535353535,-8)(283.656565656566,-8.09090909090909)(268.727272727273,-8.13636363636364)(266.239057239057,-8.18181818181818)(268.727272727273,-8.27272727272727)(283.656565656566,-8.31818181818182)(298.585858585859,-8.22727272727273)(309.782828282828,-8.36363636363636)(298.585858585859,-8.5)(283.656565656566,-8.40909090909091)(268.727272727273,-8.40909090909091)(264.248484848485,-8.54545454545455)(264.248484848485,-8.72727272727273)(256.286195286195,-8.90909090909091)(253.79797979798,-9)(250.065656565657,-9.09090909090909)(238.868686868687,-9.15909090909091)(227.671717171717,-9.09090909090909)(223.939393939394,-9.06818181818182)(209.010101010101,-9)(194.080808080808,-9.01515151515152)(179.151515151515,-9.07575757575758)(175.419191919192,-9.09090909090909)(164.222222222222,-9.22727272727273)(153.025252525253,-9.09090909090909)(149.292929292929,-9.06060606060606)(139.962121212121,-8.90909090909091)(134.363636363636,-8.86363636363636)(119.434343434343,-8.79545454545455)(108.237373737374,-8.72727272727273)(104.505050505051,-8.70454545454545)(91.4419191919192,-8.54545454545455)(89.5757575757576,-8.45454545454545)(82.1111111111111,-8.36363636363636)(78.3787878787879,-8.18181818181818)(89.5757575757576,-8.04545454545455)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (134.363636363636,-8.03030303030303)(136.851851851852,-8)(149.292929292929,-7.92424242424242)(164.222222222222,-7.93181818181818)(179.151515151515,-7.93181818181818)(194.080808080808,-7.97727272727273)(209.010101010101,-7.98484848484848)(212.742424242424,-8)(223.939393939394,-8.05454545454545)(234.389898989899,-8.18181818181818)(238.868686868687,-8.31818181818182)(240.361616161616,-8.36363636363636)(238.868686868687,-8.40909090909091)(233.270202020202,-8.54545454545455)(223.939393939394,-8.65909090909091)(209.010101010101,-8.65151515151515)(194.080808080808,-8.68181818181818)(179.151515151515,-8.68181818181818)(164.222222222222,-8.70454545454545)(149.292929292929,-8.61363636363636)(138.09595959596,-8.54545454545455)(134.363636363636,-8.52727272727273)(120.927272727273,-8.36363636363636)(125.032828282828,-8.18181818181818)(134.363636363636,-8.03030303030303)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182)(373.232323232323,-7.63636363636364)(1313.77777777778,-9.09090909090909)(1015.19191919192,-9.09090909090909)(194.080808080808,-9.09090909090909)(627.030303030303,-8.90909090909091)(223.939393939394,-7.45454545454546)(1104.76767676768,-8.18181818181818)(940.545454545455,-7.27272727272727)(1403.35353535354,-8.18181818181818)(134.363636363636,-8)(432.949494949495,-8.36363636363636)(1059.9797979798,-7.27272727272727)(836.040404040404,-7.81818181818182)(1298.84848484848,-10.1818181818182)(791.252525252525,-9.27272727272727)(1418.28282828283,-9.27272727272727)(940.545454545455,-9.27272727272727)(1104.76767676768,-9.45454545454546)(298.585858585859,-8.72727272727273)(597.171717171717,-7.27272727272727)(447.878787878788,-7.27272727272727)(1298.84848484848,-7.81818181818182)(985.333333333333,-10.1818181818182)(74.6464646464647,-8)(1239.13131313131,-8.72727272727273)(462.808080808081,-9.09090909090909)(1119.69696969697,-10.1818181818182)(776.323232323232,-8.54545454545455)(1000.26262626263,-8.54545454545455)(1388.42424242424,-10.1818181818182)(1179.41414141414,-7.45454545454546)(298.585858585859,-7.81818181818182)(119.434343434343,-8.72727272727273)(865.89898989899,-9.81818181818182)(656.888888888889,-8.72727272727273)(149.292929292929,-7.45454545454546)(1418.28282828283,-8.36363636363636)(955.474747474747,-8)(1224.20202020202,-9.45454545454546)(447.878787878788,-7.81818181818182)(612.10101010101,-8)(1104.76767676768,-8.54545454545455)(850.969696969697,-7.63636363636364)(895.757575757576,-8.72727272727273)(1224.20202020202,-10.1818181818182)(223.939393939394,-8.36363636363636)(1045.05050505051,-7.27272727272727)(597.171717171717,-9.09090909090909)(1448.14141414141,-8.90909090909091)(1030.12121212121,-9.45454545454546)(1328.70707070707,-7.63636363636364)(373.232323232323,-8.54545454545455)(1283.91919191919,-8.54545454545455)(1448.14141414141,-9.63636363636364)(955.474747474747,-7.27272727272727)(1059.9797979798,-10.1818181818182)(791.252525252525,-8.18181818181818)(1283.91919191919,-9.27272727272727)(910.686868686869,-10)(582.242424242424,-7.27272727272727)(253.79797979798,-8.90909090909091)(104.505050505051,-7.63636363636364)(1179.41414141414,-8.36363636363636)(1134.62626262626,-7.45454545454546)(462.808080808081,-8.72727272727273)(1030.12121212121,-8)(656.888888888889,-8)(1328.70707070707,-10.1818181818182)(791.252525252525,-9.09090909090909)(462.808080808081,-7.27272727272727)(74.6464646464647,-8.18181818181818)(1149.55555555556,-9.45454545454546)(149.292929292929,-8.90909090909091)(1239.13131313131,-7.63636363636364)(268.727272727273,-7.81818181818182)(910.686868686869,-9.09090909090909)(1373.49494949495,-8)(1059.9797979798,-8.72727272727273)(1179.41414141414,-10.1818181818182)(597.171717171717,-8.72727272727273)(432.949494949495,-8.18181818181818)(836.040404040404,-9.63636363636364)(1418.28282828283,-9.45454545454546)(910.686868686869,-8.36363636363636)(1000.26262626263,-10.1818181818182)(164.222222222222,-7.45454545454546)(477.737373737374,-9.09090909090909)(895.757575757576,-7.45454545454546)(1433.21212121212,-8.72727272727273)(1418.28282828283,-10)(985.333333333333,-9.45454545454546)(1179.41414141414,-8.90909090909091)(418.020202020202,-7.45454545454546)(313.515151515152,-8.36363636363636)(776.323232323232,-8.72727272727273)(537.454545454546,-7.45454545454546)(1104.76767676768,-7.45454545454546)(1283.91919191919,-10.1818181818182)(1283.91919191919,-9.09090909090909)(1000.26262626263,-7.27272727272727)(223.939393939394,-8)(821.111111111111,-8)(1254.06060606061,-7.63636363636364)(1104.76767676768,-10.1818181818182)(104.505050505051,-8.54545454545455)(627.030303030303,-7.63636363636364)(582.242424242424,-9.09090909090909)(238.868686868687,-8.90909090909091)(1209.27272727273,-8.36363636363636)(1358.56565656566,-7.81818181818182)(1059.9797979798,-8.18181818181818)(1089.83838383838,-9.27272727272727)(641.959595959596,-8.36363636363636)(925.616161616162,-10)(970.40404040404,-8.72727272727273)(89.5757575757576,-7.81818181818182)(418.020202020202,-8.72727272727273)(1373.49494949495,-10.1818181818182)(821.111111111111,-9.45454545454546)(1403.35353535354,-8.54545454545455)(373.232323232323,-8)(1209.27272727273,-10.1818181818182)(537.454545454546,-7.27272727272727)(940.545454545455,-8.18181818181818)(223.939393939394,-7.63636363636364)(1194.34343434343,-9.45454545454546)(1164.48484848485,-7.63636363636364)(865.89898989899,-7.63636363636364)(1448.14141414141,-9.45454545454546)(1030.12121212121,-10.1818181818182)(806.181818181818,-8.54545454545455)(1119.69696969697,-8.36363636363636)(164.222222222222,-8.90909090909091)(1283.91919191919,-8.90909090909091)(492.666666666667,-9.09090909090909)(1000.26262626263,-9.45454545454546)(641.959595959596,-8.72727272727273)(403.090909090909,-7.63636363636364)(1313.77777777778,-7.63636363636364)(612.10101010101,-7.45454545454546)(89.5757575757576,-8.36363636363636)(1045.05050505051,-7.45454545454546)(910.686868686869,-8.90909090909091)(268.727272727273,-8.72727272727273)(1074.90909090909,-8.90909090909091)(1388.42424242424,-8.36363636363636)(1313.77777777778,-10.1818181818182)(880.828282828283,-9.81818181818182)(1134.62626262626,-10.1818181818182)(477.737373737374,-7.27272727272727)(627.030303030303,-8.18181818181818)(179.151515151515,-7.81818181818182)(1418.28282828283,-8.90909090909091)(1433.21212121212,-9.81818181818182)(806.181818181818,-9.27272727272727)(910.686868686869,-7.45454545454546)(418.020202020202,-8.18181818181818)(1239.13131313131,-8.54545454545455)(567.313131313131,-9.09090909090909)(1119.69696969697,-9.45454545454546)(1224.20202020202,-7.63636363636364)(283.656565656566,-8.18181818181818)(821.111111111111,-8.18181818181818)(1000.26262626263,-8.18181818181818)(447.878787878788,-8.90909090909091)(1164.48484848485,-8.90909090909091)(955.474747474747,-9.27272727272727)(1074.90909090909,-7.45454545454546)(1358.56565656566,-8)(1194.34343434343,-10.1818181818182)(1074.90909090909,-10.1818181818182)(791.252525252525,-8.90909090909091)(134.363636363636,-8.72727272727273)(567.313131313131,-7.27272727272727)(1358.56565656566,-10)(955.474747474747,-10)(1030.12121212121,-8.72727272727273)(119.434343434343,-8)(1134.62626262626,-8.36363636363636)(627.030303030303,-8) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_486.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478,-8.90909090909091)(1478,-9.09090909090909)(1478,-9.27272727272727)(1478,-9.45454545454546)(1478,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(0,-7.63636363636364)(0,-7.45454545454546)(0,-7.27272727272727)(0,-7.09090909090909)(0,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1418.28282828283,-9.18181818181818)(1420.77104377104,-9.27272727272727)(1425.74747474747,-9.45454545454546)(1420.77104377104,-9.63636363636364)(1418.28282828283,-9.68181818181818)(1407.08585858586,-9.81818181818182)(1403.35353535354,-9.84848484848485)(1388.42424242424,-9.96969696969697)(1380.9595959596,-10)(1373.49494949495,-10.030303030303)(1358.56565656566,-10.0909090909091)(1343.63636363636,-10.0909090909091)(1328.70707070707,-10.0909090909091)(1313.77777777778,-10.0909090909091)(1298.84848484848,-10.0909090909091)(1283.91919191919,-10.0909090909091)(1268.9898989899,-10.0909090909091)(1254.06060606061,-10.0909090909091)(1239.13131313131,-10.0909090909091)(1224.20202020202,-10.0909090909091)(1209.27272727273,-10.0909090909091)(1194.34343434343,-10.0909090909091)(1179.41414141414,-10.0909090909091)(1164.48484848485,-10.0909090909091)(1149.55555555556,-10.0909090909091)(1134.62626262626,-10.0909090909091)(1119.69696969697,-10.0909090909091)(1104.76767676768,-10.0909090909091)(1089.83838383838,-10.0909090909091)(1074.90909090909,-10.0909090909091)(1059.9797979798,-10.0909090909091)(1045.05050505051,-10.0909090909091)(1030.12121212121,-10.0909090909091)(1015.19191919192,-10.0909090909091)(1000.26262626263,-10.0909090909091)(985.333333333333,-10.0909090909091)(970.40404040404,-10.030303030303)(962.939393939394,-10)(955.474747474747,-9.96969696969697)(940.545454545455,-9.90909090909091)(925.616161616162,-9.90909090909091)(910.686868686869,-9.90909090909091)(895.757575757576,-9.84848484848485)(888.292929292929,-9.81818181818182)(880.828282828283,-9.78787878787879)(865.89898989899,-9.66666666666667)(858.434343434343,-9.63636363636364)(850.969696969697,-9.60606060606061)(836.040404040404,-9.48484848484848)(832.308080808081,-9.45454545454546)(821.111111111111,-9.36363636363636)(813.646464646465,-9.27272727272727)(806.181818181818,-9.18181818181818)(798.717171717172,-9.09090909090909)(791.252525252525,-8.95454545454546)(788.76430976431,-8.90909090909091)(788.76430976431,-8.72727272727273)(791.252525252525,-8.68181818181818)(798.717171717172,-8.54545454545455)(806.181818181818,-8.45454545454545)(813.646464646465,-8.36363636363636)(821.111111111111,-8.27272727272727)(828.575757575758,-8.18181818181818)(836.040404040404,-8.09090909090909)(843.505050505051,-8)(850.969696969697,-7.90909090909091)(862.166666666667,-7.81818181818182)(865.89898989899,-7.78787878787879)(880.828282828283,-7.66666666666667)(888.292929292929,-7.63636363636364)(895.757575757576,-7.60606060606061)(910.686868686869,-7.54545454545455)(925.616161616162,-7.48484848484849)(933.080808080808,-7.45454545454546)(940.545454545455,-7.42424242424243)(955.474747474747,-7.36363636363636)(970.40404040404,-7.36363636363636)(985.333333333333,-7.36363636363636)(1000.26262626263,-7.36363636363636)(1015.19191919192,-7.36363636363636)(1030.12121212121,-7.42424242424243)(1037.58585858586,-7.45454545454546)(1045.05050505051,-7.48484848484849)(1059.9797979798,-7.54545454545455)(1074.90909090909,-7.54545454545455)(1089.83838383838,-7.54545454545455)(1104.76767676768,-7.54545454545455)(1119.69696969697,-7.54545454545455)(1134.62626262626,-7.54545454545455)(1149.55555555556,-7.54545454545455)(1164.48484848485,-7.60606060606061)(1171.94949494949,-7.63636363636364)(1179.41414141414,-7.66666666666667)(1194.34343434343,-7.72727272727273)(1209.27272727273,-7.72727272727273)(1224.20202020202,-7.72727272727273)(1239.13131313131,-7.72727272727273)(1254.06060606061,-7.72727272727273)(1268.9898989899,-7.72727272727273)(1283.91919191919,-7.72727272727273)(1298.84848484848,-7.72727272727273)(1313.77777777778,-7.78787878787879)(1321.24242424242,-7.81818181818182)(1328.70707070707,-7.84848484848485)(1343.63636363636,-7.96969696969697)(1347.36868686869,-8)(1358.56565656566,-8.09090909090909)(1366.0303030303,-8.18181818181818)(1373.49494949495,-8.27272727272727)(1380.9595959596,-8.36363636363636)(1388.42424242424,-8.45454545454545)(1395.88888888889,-8.54545454545455)(1403.35353535354,-8.68181818181818)(1405.84175084175,-8.72727272727273)(1410.81818181818,-8.90909090909091)(1415.79461279461,-9.09090909090909)(1418.28282828283,-9.18181818181818)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (432.949494949495,-7.90909090909091)(435.43771043771,-7.81818181818182)(447.878787878788,-7.66666666666667)(450.367003367003,-7.63636363636364)(462.808080808081,-7.48484848484849)(470.272727272727,-7.45454545454546)(477.737373737374,-7.42424242424243)(492.666666666667,-7.36363636363636)(507.59595959596,-7.36363636363636)(522.525252525253,-7.36363636363636)(537.454545454546,-7.36363636363636)(552.383838383838,-7.36363636363636)(567.313131313131,-7.42424242424243)(574.777777777778,-7.45454545454546)(582.242424242424,-7.48484848484849)(597.171717171717,-7.60606060606061)(600.90404040404,-7.63636363636364)(612.10101010101,-7.77272727272727)(614.589225589226,-7.81818181818182)(619.565656565657,-8)(619.565656565657,-8.18181818181818)(619.565656565657,-8.36363636363636)(614.589225589226,-8.54545454545455)(612.10101010101,-8.59090909090909)(600.90404040404,-8.72727272727273)(597.171717171717,-8.75757575757576)(582.242424242424,-8.87878787878788)(574.777777777778,-8.90909090909091)(567.313131313131,-8.93939393939394)(552.383838383838,-9)(537.454545454546,-9)(522.525252525253,-9)(507.59595959596,-9)(492.666666666667,-9)(477.737373737374,-8.93939393939394)(474.005050505051,-8.90909090909091)(462.808080808081,-8.81818181818182)(455.343434343434,-8.72727272727273)(447.878787878788,-8.63636363636364)(440.414141414141,-8.54545454545455)(432.949494949495,-8.40909090909091)(430.461279461279,-8.36363636363636)(425.484848484849,-8.18181818181818)(430.461279461279,-8)(432.949494949495,-7.90909090909091)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (134.363636363636,-7.96969696969697)(149.292929292929,-7.90909090909091)(164.222222222222,-7.90909090909091)(179.151515151515,-7.90909090909091)(194.080808080808,-7.96969696969697)(201.545454545455,-8)(209.010101010101,-8.03030303030303)(221.451178451178,-8.18181818181818)(223.939393939394,-8.22727272727273)(231.40404040404,-8.36363636363636)(223.939393939394,-8.5)(221.451178451178,-8.54545454545455)(209.010101010101,-8.6969696969697)(201.545454545455,-8.72727272727273)(194.080808080808,-8.75757575757576)(179.151515151515,-8.75757575757576)(171.686868686869,-8.72727272727273)(164.222222222222,-8.6969696969697)(149.292929292929,-8.57575757575757)(145.560606060606,-8.54545454545455)(134.363636363636,-8.45454545454545)(126.89898989899,-8.36363636363636)(121.922558922559,-8.18181818181818)(130.631313131313,-8)(134.363636363636,-7.96969696969697)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909)(850.969696969697,-9.27272727272727)(1478,-8.90909090909091)(1000.26262626263,-10.7272727272727)(701.676767676768,-7.45454545454546)(1134.62626262626,-8.90909090909091)(671.818181818182,-9.09090909090909)(253.79797979798,-7.27272727272727)(940.545454545455,-8)(462.808080808081,-6.72727272727273)(880.828282828283,-10.3636363636364)(1268.9898989899,-7.09090909090909)(104.505050505051,-7.81818181818182)(462.808080808081,-8)(1313.77777777778,-9.81818181818182)(1104.76767676768,-6.90909090909091)(895.757575757576,-7.27272727272727)(134.363636363636,-8.90909090909091)(1030.12121212121,-9.81818181818182)(1433.21212121212,-8)(1254.06060606061,-8.36363636363636)(253.79797979798,-8.18181818181818)(537.454545454546,-9.27272727272727)(298.585858585859,-9.27272727272727)(791.252525252525,-8.54545454545455)(612.10101010101,-6.90909090909091)(29.8585858585859,-8)(1015.19191919192,-8.72727272727273)(1478,-10)(119.434343434343,-7.09090909090909)(1179.41414141414,-9.81818181818182)(836.040404040404,-10)(1358.56565656566,-8.90909090909091)(1373.49494949495,-10.5454545454545)(1089.83838383838,-7.63636363636364)(656.888888888889,-8.36363636363636)(343.373737373737,-7.09090909090909)(1478,-9.09090909090909)(403.090909090909,-8.72727272727273)(1194.34343434343,-10.5454545454545)(940.545454545455,-7.09090909090909)(791.252525252525,-7.81818181818182)(522.525252525253,-7.63636363636364)(925.616161616162,-9.27272727272727)(1373.49494949495,-7.63636363636364)(761.393939393939,-9.27272727272727)(164.222222222222,-9.09090909090909)(1164.48484848485,-8.54545454545455)(1000.26262626263,-10.5454545454545)(492.666666666667,-6.72727272727273)(582.242424242424,-9.27272727272727)(1254.06060606061,-9.45454545454546)(1194.34343434343,-7.27272727272727)(209.010101010101,-8.18181818181818)(388.161616161616,-9.27272727272727)(985.333333333333,-8)(641.959595959596,-7.27272727272727)(388.161616161616,-7.81818181818182)(59.7171717171717,-8.36363636363636)(1373.49494949495,-10)(1089.83838383838,-10.1818181818182)(209.010101010101,-7.27272727272727)(880.828282828283,-8.36363636363636)(1283.91919191919,-8.18181818181818)(1074.90909090909,-9.09090909090909)(1448.14141414141,-8.36363636363636)(582.242424242424,-8.36363636363636)(89.5757575757576,-7.27272727272727)(1268.9898989899,-10.5454545454545)(1478,-9.45454545454546)(1045.05050505051,-7.09090909090909)(955.474747474747,-9.63636363636364)(821.111111111111,-9.81818181818182)(716.606060606061,-8.72727272727273)(253.79797979798,-9.09090909090909)(492.666666666667,-9.27272727272727)(865.89898989899,-7.45454545454546)(1358.56565656566,-9.09090909090909)(447.878787878788,-8.36363636363636)(418.020202020202,-7.09090909090909)(701.676767676768,-7.81818181818182)(104.505050505051,-8.72727272727273)(283.656565656566,-7.81818181818182)(1164.48484848485,-8.18181818181818)(1313.77777777778,-7.45454545454546)(1194.34343434343,-9.27272727272727)(880.828282828283,-8.90909090909091)(567.313131313131,-6.90909090909091)(1030.12121212121,-8.36363636363636)(1134.62626262626,-10.3636363636364)(1119.69696969697,-7.27272727272727)(1373.49494949495,-10.3636363636364)(298.585858585859,-8.54545454545455)(970.40404040404,-10.1818181818182)(552.383838383838,-7.63636363636364)(59.7171717171717,-7.81818181818182)(567.313131313131,-9.27272727272727)(1388.42424242424,-8)(746.464646464646,-9.09090909090909)(1478,-9.27272727272727)(806.181818181818,-7.81818181818182)(179.151515151515,-8.18181818181818)(1298.84848484848,-8.72727272727273)(1074.90909090909,-9.45454545454546)(1209.27272727273,-7.63636363636364)(910.686868686869,-7.27272727272727)(179.151515151515,-9.09090909090909)(268.727272727273,-7.45454545454546)(1254.06060606061,-9.63636363636364)(447.878787878788,-7.63636363636364)(627.030303030303,-8.54545454545455)(1015.19191919192,-8)(388.161616161616,-8.90909090909091)(1388.42424242424,-9.81818181818182)(955.474747474747,-8.90909090909091)(641.959595959596,-7.45454545454546)(1268.9898989899,-10.3636363636364)(850.969696969697,-9.81818181818182)(1119.69696969697,-8.72727272727273)(821.111111111111,-8.36363636363636)(134.363636363636,-7.45454545454546)(507.59595959596,-8.72727272727273)(1045.05050505051,-10.1818181818182)(1030.12121212121,-7.45454545454546)(1403.35353535354,-8.72727272727273)(358.30303030303,-8.18181818181818)(1343.63636363636,-7.63636363636364)(89.5757575757576,-8.54545454545455)(1224.20202020202,-8.36363636363636)(492.666666666667,-7.09090909090909)(686.747474747475,-8.18181818181818)(1164.48484848485,-10.1818181818182)(821.111111111111,-9.09090909090909)(238.868686868687,-8.54545454545455)(925.616161616162,-8.18181818181818)(507.59595959596,-9.27272727272727)(1194.34343434343,-7.45454545454546)(940.545454545455,-10)(1433.21212121212,-10)(1179.41414141414,-9.27272727272727)(582.242424242424,-7.81818181818182)(373.232323232323,-7.63636363636364)(1313.77777777778,-9.09090909090909)(1015.19191919192,-9.09090909090909)(194.080808080808,-9.09090909090909)(627.030303030303,-8.90909090909091)(223.939393939394,-7.45454545454546)(1104.76767676768,-8.18181818181818)(940.545454545455,-7.27272727272727)(1403.35353535354,-8.18181818181818)(134.363636363636,-8)(432.949494949495,-8.36363636363636)(1059.9797979798,-7.27272727272727)(836.040404040404,-7.81818181818182)(1298.84848484848,-10.1818181818182)(791.252525252525,-9.27272727272727)(1418.28282828283,-9.27272727272727)(940.545454545455,-9.27272727272727)(1104.76767676768,-9.45454545454546)(298.585858585859,-8.72727272727273)(597.171717171717,-7.27272727272727)(447.878787878788,-7.27272727272727)(1298.84848484848,-7.81818181818182)(985.333333333333,-10.1818181818182)(74.6464646464647,-8)(1239.13131313131,-8.72727272727273)(462.808080808081,-9.09090909090909)(1119.69696969697,-10.1818181818182)(776.323232323232,-8.54545454545455)(1000.26262626263,-8.54545454545455)(1388.42424242424,-10.1818181818182)(1179.41414141414,-7.45454545454546)(298.585858585859,-7.81818181818182)(119.434343434343,-8.72727272727273)(865.89898989899,-9.81818181818182)(656.888888888889,-8.72727272727273)(149.292929292929,-7.45454545454546)(1418.28282828283,-8.36363636363636)(955.474747474747,-8)(1224.20202020202,-9.45454545454546)(447.878787878788,-7.81818181818182)(612.10101010101,-8)(1104.76767676768,-8.54545454545455)(850.969696969697,-7.63636363636364)(895.757575757576,-8.72727272727273)(1224.20202020202,-10.1818181818182)(223.939393939394,-8.36363636363636)(1045.05050505051,-7.27272727272727)(597.171717171717,-9.09090909090909)(1448.14141414141,-8.90909090909091)(1030.12121212121,-9.45454545454546)(1328.70707070707,-7.63636363636364)(373.232323232323,-8.54545454545455)(1283.91919191919,-8.54545454545455)(1448.14141414141,-9.63636363636364)(955.474747474747,-7.27272727272727)(1059.9797979798,-10.1818181818182)(791.252525252525,-8.18181818181818)(1283.91919191919,-9.27272727272727)(910.686868686869,-10)(582.242424242424,-7.27272727272727)(253.79797979798,-8.90909090909091)(104.505050505051,-7.63636363636364)(1179.41414141414,-8.36363636363636)(1134.62626262626,-7.45454545454546)(462.808080808081,-8.72727272727273)(1030.12121212121,-8)(656.888888888889,-8)(1328.70707070707,-10.1818181818182)(791.252525252525,-9.09090909090909)(462.808080808081,-7.27272727272727)(74.6464646464647,-8.18181818181818)(1149.55555555556,-9.45454545454546)(149.292929292929,-8.90909090909091)(1239.13131313131,-7.63636363636364)(268.727272727273,-7.81818181818182)(910.686868686869,-9.09090909090909)(1373.49494949495,-8)(1059.9797979798,-8.72727272727273)(1179.41414141414,-10.1818181818182)(597.171717171717,-8.72727272727273)(432.949494949495,-8.18181818181818)(836.040404040404,-9.63636363636364)(1418.28282828283,-9.45454545454546)(910.686868686869,-8.36363636363636)(1000.26262626263,-10.1818181818182)(164.222222222222,-7.45454545454546)(477.737373737374,-9.09090909090909)(895.757575757576,-7.45454545454546)(1433.21212121212,-8.72727272727273)(1418.28282828283,-10)(985.333333333333,-9.45454545454546)(1179.41414141414,-8.90909090909091)(418.020202020202,-7.45454545454546)(313.515151515152,-8.36363636363636)(776.323232323232,-8.72727272727273)(537.454545454546,-7.45454545454546)(1104.76767676768,-7.45454545454546)(1283.91919191919,-10.1818181818182)(1283.91919191919,-9.09090909090909)(1000.26262626263,-7.27272727272727)(223.939393939394,-8)(821.111111111111,-8)(1254.06060606061,-7.63636363636364)(1104.76767676768,-10.1818181818182)(104.505050505051,-8.54545454545455)(627.030303030303,-7.63636363636364)(582.242424242424,-9.09090909090909)(238.868686868687,-8.90909090909091)(1209.27272727273,-8.36363636363636)(1358.56565656566,-7.81818181818182)(1059.9797979798,-8.18181818181818)(1089.83838383838,-9.27272727272727)(641.959595959596,-8.36363636363636)(925.616161616162,-10)(970.40404040404,-8.72727272727273)(89.5757575757576,-7.81818181818182)(418.020202020202,-8.72727272727273)(1373.49494949495,-10.1818181818182)(821.111111111111,-9.45454545454546)(1403.35353535354,-8.54545454545455)(373.232323232323,-8)(1209.27272727273,-10.1818181818182)(537.454545454546,-7.27272727272727)(940.545454545455,-8.18181818181818)(223.939393939394,-7.63636363636364)(1194.34343434343,-9.45454545454546)(1164.48484848485,-7.63636363636364)(865.89898989899,-7.63636363636364)(1448.14141414141,-9.45454545454546)(1030.12121212121,-10.1818181818182)(806.181818181818,-8.54545454545455)(1119.69696969697,-8.36363636363636)(164.222222222222,-8.90909090909091)(1283.91919191919,-8.90909090909091)(492.666666666667,-9.09090909090909)(1000.26262626263,-9.45454545454546)(641.959595959596,-8.72727272727273)(403.090909090909,-7.63636363636364)(1313.77777777778,-7.63636363636364)(612.10101010101,-7.45454545454546)(89.5757575757576,-8.36363636363636)(1045.05050505051,-7.45454545454546)(910.686868686869,-8.90909090909091)(268.727272727273,-8.72727272727273)(1074.90909090909,-8.90909090909091)(1388.42424242424,-8.36363636363636)(1313.77777777778,-10.1818181818182)(880.828282828283,-9.81818181818182)(1134.62626262626,-10.1818181818182)(477.737373737374,-7.27272727272727)(627.030303030303,-8.18181818181818)(179.151515151515,-7.81818181818182)(1418.28282828283,-8.90909090909091)(1433.21212121212,-9.81818181818182)(806.181818181818,-9.27272727272727)(910.686868686869,-7.45454545454546)(418.020202020202,-8.18181818181818)(1239.13131313131,-8.54545454545455)(567.313131313131,-9.09090909090909)(1119.69696969697,-9.45454545454546)(1224.20202020202,-7.63636363636364)(283.656565656566,-8.18181818181818)(821.111111111111,-8.18181818181818)(1000.26262626263,-8.18181818181818)(447.878787878788,-8.90909090909091)(1164.48484848485,-8.90909090909091)(955.474747474747,-9.27272727272727)(1074.90909090909,-7.45454545454546)(1358.56565656566,-8)(1194.34343434343,-10.1818181818182)(1074.90909090909,-10.1818181818182)(791.252525252525,-8.90909090909091)(134.363636363636,-8.72727272727273)(567.313131313131,-7.27272727272727)(1358.56565656566,-10)(955.474747474747,-10)(1030.12121212121,-8.72727272727273)(119.434343434343,-8)(1134.62626262626,-8.36363636363636)(627.030303030303,-8)(1433.21212121212,-9.09090909090909)(850.969696969697,-7.81818181818182)(432.949494949495,-7.45454545454546)(253.79797979798,-8.36363636363636)(910.686868686869,-8.72727272727273)(432.949494949495,-8.54545454545455)(1179.41414141414,-7.63636363636364)(850.969696969697,-9.63636363636364)(552.383838383838,-9.09090909090909)(1224.20202020202,-9.09090909090909)(925.616161616162,-7.45454545454546)(955.474747474747,-8.18181818181818)(1373.49494949495,-8.18181818181818)(1059.9797979798,-9.27272727272727)(612.10101010101,-8.72727272727273)(1418.28282828283,-9.63636363636364)(194.080808080808,-7.81818181818182)(492.666666666667,-7.27272727272727)(223.939393939394,-8.72727272727273)(791.252525252525,-8.72727272727273)(1045.05050505051,-8.18181818181818)(418.020202020202,-8)(612.10101010101,-7.81818181818182)(1059.9797979798,-7.45454545454546)(1149.55555555556,-10.1818181818182)(1403.35353535354,-10)(1209.27272727273,-8.54545454545455)(895.757575757576,-9.81818181818182)(836.040404040404,-8)(507.59595959596,-9.09090909090909)(1164.48484848485,-9.27272727272727)(925.616161616162,-9.09090909090909)(104.505050505051,-8.18181818181818)(1328.70707070707,-7.81818181818182)(1194.34343434343,-7.63636363636364)(552.383838383838,-7.27272727272727)(627.030303030303,-8.36363636363636)(238.868686868687,-8)(1030.12121212121,-8.90909090909091)(1433.21212121212,-9.27272727272727)(447.878787878788,-8.72727272727273)(1104.76767676768,-8.36363636363636)(149.292929292929,-8.72727272727273)(925.616161616162,-8.36363636363636)(806.181818181818,-8.36363636363636)(836.040404040404,-9.45454545454546)(134.363636363636,-7.81818181818182)(418.020202020202,-7.81818181818182)(238.868686868687,-8.72727272727273)(1104.76767676768,-9.27272727272727)(880.828282828283,-7.63636363636364)(597.171717171717,-8.90909090909091)(612.10101010101,-7.63636363636364)(970.40404040404,-9.27272727272727)(1209.27272727273,-9.09090909090909)(1388.42424242424,-10)(418.020202020202,-8.36363636363636)(507.59595959596,-7.27272727272727)(1030.12121212121,-8.18181818181818)(1194.34343434343,-8.54545454545455)(522.525252525253,-9.09090909090909)(985.333333333333,-8.72727272727273)(149.292929292929,-7.81818181818182)(1433.21212121212,-9.45454545454546)(253.79797979798,-8.54545454545455)(447.878787878788,-7.45454545454546)(1104.76767676768,-8.90909090909091)(462.808080808081,-8.90909090909091)(1030.12121212121,-9.27272727272727)(970.40404040404,-8.18181818181818)(597.171717171717,-7.63636363636364)(1089.83838383838,-8.36363636363636)(582.242424242424,-8.90909090909091)(925.616161616162,-8.90909090909091)(1224.20202020202,-8.90909090909091)(1149.55555555556,-9.27272727272727)(1418.28282828283,-9.81818181818182)(462.808080808081,-7.45454545454546)(925.616161616162,-8.54545454545455)(1045.05050505051,-9.27272727272727)(1179.41414141414,-8.54545454545455)(537.454545454546,-9.09090909090909)(582.242424242424,-7.45454545454546)(1015.19191919192,-8.18181818181818)(1433.21212121212,-9.63636363636364)(477.737373737374,-8.90909090909091) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_60.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478.00005529347,-8)(1478.00022117143,-8.18181818181818)(1478.00027646327,-8.36363636363636)(1478.00038704571,-8.54545454545455)(1478.00038704571,-8.72727272727273)(1478.00049762651,-8.90909090909091)(1478.00049762651,-9.09090909090909)(1478.00049762651,-9.27272727272727)(1478.00038704571,-9.45454545454546)(1478.00038704571,-9.63636363636364)(1478.00038704571,-9.81818181818182)(1478.00049762651,-10)(1478.00038704571,-10.1818181818182)(1478.00022117143,-10.3636363636364)(1478.00005529347,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(-5.52934727241102e-05,-8)(-0.000221171433450288,-7.81818181818182)(-0.000276463267890224,-7.63636363636364)(-0.000387045708090112,-7.45454545454546)(-0.000387045708090112,-7.27272727272727)(-0.000497626510092015,-7.09090909090909)(-0.000331754692772375,-6.90909090909091)(-0.000165879189445939,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-6.81818181818182)(14.9292929292929,-6.81818181818182)(29.8585858585859,-6.75757575757576)(37.3232323232323,-6.72727272727273)(44.7878787878788,-6.6969696969697)(59.7171717171717,-6.63636363636364)(74.6464646464647,-6.63636363636364)(89.5757575757576,-6.63636363636364)(104.505050505051,-6.63636363636364)(119.434343434343,-6.63636363636364)(134.363636363636,-6.63636363636364)(149.292929292929,-6.63636363636364)(164.222222222222,-6.63636363636364)(179.151515151515,-6.63636363636364)(194.080808080808,-6.63636363636364)(209.010101010101,-6.63636363636364)(223.939393939394,-6.63636363636364)(238.868686868687,-6.63636363636364)(253.79797979798,-6.63636363636364)(268.727272727273,-6.63636363636364)(283.656565656566,-6.63636363636364)(294.853535353535,-6.54545454545455)(298.585858585859,-6.51515151515151)(313.515151515152,-6.51515151515151)(328.444444444444,-6.51515151515151)(335.909090909091,-6.54545454545455)(343.373737373737,-6.57575757575758)(350.838383838384,-6.54545454545455)(358.30303030303,-6.51515151515151)(373.232323232323,-6.45454545454545)(388.161616161616,-6.45454545454545)(403.090909090909,-6.45454545454545)(418.020202020202,-6.45454545454545)(432.949494949495,-6.45454545454545)(447.878787878788,-6.45454545454545)(462.808080808081,-6.45454545454545)(477.737373737374,-6.45454545454545)(492.666666666667,-6.39393939393939)(500.131313131313,-6.36363636363636)(507.59595959596,-6.33333333333333)(522.525252525253,-6.27272727272727)(537.454545454546,-6.33333333333333)(544.919191919192,-6.36363636363636)(552.383838383838,-6.39393939393939)(567.313131313131,-6.45454545454545)(582.242424242424,-6.45454545454545)(597.171717171717,-6.45454545454545)(612.10101010101,-6.51515151515151)(619.565656565657,-6.54545454545455)(627.030303030303,-6.57575757575758)(641.959595959596,-6.6969696969697)(649.424242424242,-6.72727272727273)(656.888888888889,-6.75757575757576)(671.818181818182,-6.87878787878788)(679.282828282828,-6.90909090909091)(686.747474747475,-6.93939393939394)(701.676767676768,-7)(716.606060606061,-7.06060606060606)(724.070707070707,-7.09090909090909)(731.535353535354,-7.12121212121212)(746.464646464646,-7.18181818181818)(761.393939393939,-7.18181818181818)(776.323232323232,-7.18181818181818)(791.252525252525,-7.18181818181818)(806.181818181818,-7.12121212121212)(813.646464646465,-7.09090909090909)(821.111111111111,-7.06060606060606)(836.040404040404,-7)(850.969696969697,-7)(865.89898989899,-7)(880.828282828283,-6.93939393939394)(888.292929292929,-6.90909090909091)(895.757575757576,-6.87878787878788)(910.686868686869,-6.81818181818182)(925.616161616162,-6.81818181818182)(940.545454545455,-6.81818181818182)(955.474747474747,-6.75757575757576)(962.939393939394,-6.72727272727273)(970.40404040404,-6.6969696969697)(985.333333333333,-6.63636363636364)(1000.26262626263,-6.63636363636364)(1015.19191919192,-6.63636363636364)(1030.12121212121,-6.63636363636364)(1045.05050505051,-6.63636363636364)(1059.9797979798,-6.63636363636364)(1074.90909090909,-6.63636363636364)(1089.83838383838,-6.63636363636364)(1104.76767676768,-6.6969696969697)(1112.23232323232,-6.72727272727273)(1119.69696969697,-6.75757575757576)(1134.62626262626,-6.81818181818182)(1149.55555555556,-6.81818181818182)(1164.48484848485,-6.81818181818182)(1179.41414141414,-6.81818181818182)(1194.34343434343,-6.87878787878788)(1201.80808080808,-6.90909090909091)(1209.27272727273,-6.93939393939394)(1224.20202020202,-7)(1239.13131313131,-7)(1254.06060606061,-7)(1268.9898989899,-7)(1283.91919191919,-7)(1298.84848484848,-7.06060606060606)(1306.31313131313,-7.09090909090909)(1313.77777777778,-7.12121212121212)(1328.70707070707,-7.18181818181818)(1343.63636363636,-7.24242424242424)(1351.10101010101,-7.27272727272727)(1358.56565656566,-7.3030303030303)(1373.49494949495,-7.42424242424243)(1380.9595959596,-7.45454545454546)(1388.42424242424,-7.48484848484849)(1403.35353535354,-7.60606060606061)(1407.08585858586,-7.63636363636364)(1418.28282828283,-7.72727272727273)(1425.74747474747,-7.81818181818182)(1433.21212121212,-7.90909090909091)(1444.40909090909,-8)(1448.14141414141,-8.03030303030303)(1463.07070707071,-8.15151515151515)(1470.53535353535,-8.18181818181818)(1478,-8.27272727272727)(1478.00002764633,-8.36363636363636)(1478.00013823061,-8.54545454545455)(1478.00013823061,-8.72727272727273)(1478.00024881326,-8.90909090909091)(1478.00024881326,-9.09090909090909)(1478.00024881326,-9.27272727272727)(1478.00013823061,-9.45454545454546)(1478.00013823061,-9.63636363636364)(1478.00013823061,-9.81818181818182)(1478.00024881326,-10)(1478.00013823061,-10.1818181818182)(1478,-10.3333333333333)(1470.53535353535,-10.3636363636364)(1463.07070707071,-10.3939393939394)(1448.14141414141,-10.5151515151515)(1440.67676767677,-10.5454545454545)(1433.21212121212,-10.5757575757576)(1418.28282828283,-10.6363636363636)(1403.35353535354,-10.6969696969697)(1395.88888888889,-10.7272727272727)(1388.42424242424,-10.7575757575758)(1373.49494949495,-10.8181818181818)(1358.56565656566,-10.8181818181818)(1343.63636363636,-10.8181818181818)(1328.70707070707,-10.8181818181818)(1313.77777777778,-10.8181818181818)(1298.84848484848,-10.8181818181818)(1283.91919191919,-10.8181818181818)(1268.9898989899,-10.8787878787879)(1261.52525252525,-10.9090909090909)(1254.06060606061,-10.9393939393939)(1239.13131313131,-11)(1224.20202020202,-11)(1209.27272727273,-11)(1194.34343434343,-11)(1179.41414141414,-11)(1164.48484848485,-11)(1149.55555555556,-11)(1134.62626262626,-11)(1119.69696969697,-11)(1104.76767676768,-11)(1089.83838383838,-10.9545454545455)(1074.90909090909,-10.9545454545455)(1059.9797979798,-10.9545454545455)(1045.05050505051,-10.9393939393939)(1037.58585858586,-10.9090909090909)(1030.12121212121,-10.8787878787879)(1015.19191919192,-10.8181818181818)(1000.26262626263,-10.8181818181818)(985.333333333333,-10.8181818181818)(970.40404040404,-10.8181818181818)(955.474747474747,-10.7575757575758)(948.010101010101,-10.7272727272727)(940.545454545455,-10.6969696969697)(925.616161616162,-10.6363636363636)(910.686868686869,-10.5757575757576)(903.222222222222,-10.5454545454545)(895.757575757576,-10.5151515151515)(880.828282828283,-10.3939393939394)(873.363636363636,-10.3636363636364)(865.89898989899,-10.3333333333333)(850.969696969697,-10.2121212121212)(847.237373737374,-10.1818181818182)(836.040404040404,-10.0909090909091)(828.575757575758,-10)(821.111111111111,-9.90909090909091)(813.646464646465,-9.81818181818182)(806.181818181818,-9.72727272727273)(798.717171717172,-9.63636363636364)(791.252525252525,-9.54545454545455)(780.055555555556,-9.45454545454546)(776.323232323232,-9.42424242424243)(761.393939393939,-9.3030303030303)(753.929292929293,-9.27272727272727)(746.464646464646,-9.24242424242424)(731.535353535354,-9.12121212121212)(724.070707070707,-9.09090909090909)(716.606060606061,-9.06060606060606)(701.676767676768,-9)(686.747474747475,-9.06060606060606)(679.282828282828,-9.09090909090909)(671.818181818182,-9.12121212121212)(656.888888888889,-9.18181818181818)(641.959595959596,-9.18181818181818)(627.030303030303,-9.18181818181818)(612.10101010101,-9.24242424242424)(604.636363636364,-9.27272727272727)(597.171717171717,-9.3030303030303)(582.242424242424,-9.42424242424243)(574.777777777778,-9.45454545454546)(567.313131313131,-9.48484848484848)(552.383838383838,-9.54545454545455)(537.454545454546,-9.54545454545455)(522.525252525253,-9.54545454545455)(507.59595959596,-9.60606060606061)(500.131313131313,-9.63636363636364)(492.666666666667,-9.66666666666667)(477.737373737374,-9.72727272727273)(462.808080808081,-9.72727272727273)(447.878787878788,-9.72727272727273)(432.949494949495,-9.72727272727273)(418.020202020202,-9.72727272727273)(403.090909090909,-9.66666666666667)(395.626262626263,-9.63636363636364)(388.161616161616,-9.60606060606061)(373.232323232323,-9.54545454545455)(358.30303030303,-9.54545454545455)(343.373737373737,-9.54545454545455)(328.444444444444,-9.54545454545455)(313.515151515152,-9.54545454545455)(298.585858585859,-9.54545454545455)(283.656565656566,-9.48484848484848)(276.191919191919,-9.45454545454546)(268.727272727273,-9.42424242424243)(253.79797979798,-9.36363636363636)(238.868686868687,-9.38636363636364)(223.939393939394,-9.38636363636364)(209.010101010101,-9.34090909090909)(197.813131313131,-9.27272727272727)(194.080808080808,-9.24242424242424)(179.151515151515,-9.18181818181818)(164.222222222222,-9.12121212121212)(156.757575757576,-9.09090909090909)(149.292929292929,-9.06060606060606)(134.363636363636,-8.93939393939394)(126.89898989899,-8.90909090909091)(119.434343434343,-8.87878787878788)(104.505050505051,-8.75757575757576)(100.772727272727,-8.72727272727273)(89.5757575757576,-8.63636363636364)(78.3787878787879,-8.54545454545455)(74.6464646464647,-8.51515151515152)(59.7171717171717,-8.39393939393939)(55.9848484848485,-8.36363636363636)(44.7878787878788,-8.27272727272727)(37.3232323232323,-8.18181818181818)(29.8585858585859,-8.09090909090909)(22.3939393939394,-8)(14.9292929292929,-7.90909090909091)(3.73232323232323,-7.81818181818182)(0,-7.72727272727273)(-2.76463267876964e-05,-7.63636363636364)(-0.000138230610030762,-7.45454545454546)(-0.000138230610030762,-7.27272727272727)(-0.000248813255046008,-7.09090909090909)(-8.29386731914362e-05,-6.90909090909091)(0,-6.81818181818182)};

%\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1313.77777777778,-8.77272727272727)(1317.5101010101,-8.90909090909091)(1313.77777777778,-9.04545454545455)(1312.53367003367,-9.09090909090909)(1304.44696969697,-9.27272727272727)(1298.84848484848,-9.34090909090909)(1289.51767676768,-9.45454545454546)(1283.91919191919,-9.52272727272727)(1268.9898989899,-9.62121212121212)(1267.12373737374,-9.63636363636364)(1254.06060606061,-9.74242424242424)(1239.13131313131,-9.8030303030303)(1235.39898989899,-9.81818181818182)(1224.20202020202,-9.87272727272727)(1209.27272727273,-9.86363636363636)(1194.34343434343,-9.86363636363636)(1179.41414141414,-9.86363636363636)(1164.48484848485,-9.86363636363636)(1149.55555555556,-9.86363636363636)(1134.62626262626,-9.86363636363636)(1119.69696969697,-9.86363636363636)(1104.76767676768,-9.86363636363636)(1089.83838383838,-9.86363636363636)(1074.90909090909,-9.86363636363636)(1063.71212121212,-9.81818181818182)(1059.9797979798,-9.8030303030303)(1045.05050505051,-9.74242424242424)(1031.98737373737,-9.63636363636364)(1030.12121212121,-9.62121212121212)(1015.19191919192,-9.54545454545455)(1005.86111111111,-9.45454545454546)(1000.26262626263,-9.38636363636364)(990.931818181818,-9.27272727272727)(985.333333333333,-9.13636363636364)(983.840404040404,-9.09090909090909)(981.60101010101,-8.90909090909091)(981.60101010101,-8.72727272727273)(985.333333333333,-8.59090909090909)(986.577441077441,-8.54545454545455)(994.664141414141,-8.36363636363636)(1000.26262626263,-8.29545454545455)(1009.59343434343,-8.18181818181818)(1015.19191919192,-8.11363636363636)(1030.12121212121,-8.01515151515152)(1031.98737373737,-8)(1045.05050505051,-7.89393939393939)(1059.9797979798,-7.83636363636364)(1063.71212121212,-7.81818181818182)(1074.90909090909,-7.77272727272727)(1089.83838383838,-7.77272727272727)(1104.76767676768,-7.77272727272727)(1119.69696969697,-7.77272727272727)(1134.62626262626,-7.77272727272727)(1149.55555555556,-7.77272727272727)(1164.48484848485,-7.77272727272727)(1179.41414141414,-7.77272727272727)(1194.34343434343,-7.77272727272727)(1205.5404040404,-7.81818181818182)(1209.27272727273,-7.83333333333333)(1224.20202020202,-7.89393939393939)(1239.13131313131,-7.95454545454546)(1250.32828282828,-8)(1254.06060606061,-8.01515151515152)(1268.9898989899,-8.11363636363636)(1274.58838383838,-8.18181818181818)(1283.91919191919,-8.29545454545455)(1289.51767676768,-8.36363636363636)(1298.84848484848,-8.47727272727273)(1304.44696969697,-8.54545454545455)(1312.53367003367,-8.72727272727273)(1313.77777777778,-8.77272727272727)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1283.91919191919,-8.61363636363636)(1290.13973063973,-8.72727272727273)(1295.11616161616,-8.90909090909091)(1290.13973063973,-9.09090909090909)(1283.91919191919,-9.20454545454546)(1278.32070707071,-9.27272727272727)(1268.9898989899,-9.34848484848485)(1255.92676767677,-9.45454545454546)(1254.06060606061,-9.46969696969697)(1239.13131313131,-9.53030303030303)(1224.20202020202,-9.59090909090909)(1209.27272727273,-9.59090909090909)(1194.34343434343,-9.59090909090909)(1179.41414141414,-9.59090909090909)(1164.48484848485,-9.59090909090909)(1149.55555555556,-9.59090909090909)(1134.62626262626,-9.59090909090909)(1119.69696969697,-9.59090909090909)(1104.76767676768,-9.59090909090909)(1089.83838383838,-9.59090909090909)(1074.90909090909,-9.59090909090909)(1059.9797979798,-9.53030303030303)(1045.05050505051,-9.46969696969697)(1043.18434343434,-9.45454545454546)(1030.12121212121,-9.34848484848485)(1017.68013468013,-9.27272727272727)(1015.19191919192,-9.25)(1006.48316498317,-9.09090909090909)(1003.99494949495,-8.90909090909091)(1003.99494949495,-8.72727272727273)(1008.97138047138,-8.54545454545455)(1015.19191919192,-8.43181818181818)(1020.7904040404,-8.36363636363636)(1030.12121212121,-8.28787878787879)(1043.18434343434,-8.18181818181818)(1045.05050505051,-8.16666666666667)(1059.9797979798,-8.13636363636364)(1074.90909090909,-8.07575757575757)(1089.83838383838,-8.07575757575757)(1104.76767676768,-8.04545454545455)(1119.69696969697,-8.04545454545455)(1134.62626262626,-8.04545454545455)(1149.55555555556,-8.04545454545455)(1164.48484848485,-8.04545454545455)(1179.41414141414,-8.04545454545455)(1194.34343434343,-8.04545454545455)(1209.27272727273,-8.10606060606061)(1224.20202020202,-8.16666666666667)(1227.93434343434,-8.18181818181818)(1239.13131313131,-8.22727272727273)(1254.06060606061,-8.28787878787879)(1263.39141414141,-8.36363636363636)(1268.9898989899,-8.43181818181818)(1278.32070707071,-8.54545454545455)(1283.91919191919,-8.61363636363636)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/limno_bgape_imp_class_80.tex
Add implicit extension

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478.00022117143,-4.18181818181818)(1478.00022117143,-4.36363636363636)(1478.00022117143,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478.00005529347,-8.18181818181818)(1478.00011058654,-8.36363636363636)(1478.00027646327,-8.54545454545455)(1478.00038704571,-8.72727272727273)(1478.00049762651,-8.90909090909091)(1478.00049762651,-9.09090909090909)(1478.00049762651,-9.27272727272727)(1478.00038704571,-9.45454545454546)(1478.00038704571,-9.63636363636364)(1478.00038704571,-9.81818181818182)(1478.00038704571,-10)(1478.00022117143,-10.1818181818182)(1478.00005529347,-10.3636363636364)(1478,-10.5454545454545)(1478.00022117143,-10.7272727272727)(1478.00022117143,-10.9090909090909)(1478.00022117143,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(-0.000221171433450288,-8.72727272727273)(-0.000221171433450288,-8.54545454545455)(-0.000221171433450288,-8.36363636363636)(0,-8.18181818181818)(-5.52934727241102e-05,-8)(-0.000221171433450288,-7.81818181818182)(-0.000276463267890224,-7.63636363636364)(-0.000387045708090112,-7.45454545454546)(-0.000276463267890224,-7.27272727272727)(-0.000221171433450288,-7.09090909090909)(-5.52934727241102e-05,-6.90909090909091)(0,-6.72727272727273)(0,-6.54545454545455)(0,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-7.18181818181818)(3.73232323232323,-7.09090909090909)(14.9292929292929,-7)(26.1262626262626,-6.90909090909091)(29.8585858585859,-6.87878787878788)(44.7878787878788,-6.81818181818182)(59.7171717171717,-6.81818181818182)(74.6464646464647,-6.81818181818182)(89.5757575757576,-6.81818181818182)(104.505050505051,-6.81818181818182)(119.434343434343,-6.81818181818182)(134.363636363636,-6.81818181818182)(149.292929292929,-6.81818181818182)(164.222222222222,-6.81818181818182)(179.151515151515,-6.81818181818182)(194.080808080808,-6.81818181818182)(209.010101010101,-6.81818181818182)(223.939393939394,-6.81818181818182)(238.868686868687,-6.81818181818182)(253.79797979798,-6.81818181818182)(268.727272727273,-6.81818181818182)(283.656565656566,-6.81818181818182)(294.853535353535,-6.72727272727273)(298.585858585859,-6.6969696969697)(313.515151515152,-6.6969696969697)(328.444444444444,-6.6969696969697)(332.176767676768,-6.72727272727273)(343.373737373737,-6.81818181818182)(358.30303030303,-6.81818181818182)(373.232323232323,-6.81818181818182)(388.161616161616,-6.81818181818182)(403.090909090909,-6.81818181818182)(418.020202020202,-6.81818181818182)(432.949494949495,-6.75757575757576)(440.414141414141,-6.72727272727273)(447.878787878788,-6.6969696969697)(462.808080808081,-6.63636363636364)(477.737373737374,-6.63636363636364)(492.666666666667,-6.63636363636364)(507.59595959596,-6.63636363636364)(522.525252525253,-6.63636363636364)(537.454545454546,-6.63636363636364)(552.383838383838,-6.63636363636364)(567.313131313131,-6.6969696969697)(574.777777777778,-6.72727272727273)(582.242424242424,-6.75757575757576)(597.171717171717,-6.81818181818182)(612.10101010101,-6.87878787878788)(619.565656565657,-6.90909090909091)(627.030303030303,-6.93939393939394)(641.959595959596,-7.06060606060606)(649.424242424242,-7.09090909090909)(656.888888888889,-7.12121212121212)(671.818181818182,-7.24242424242424)(679.282828282828,-7.27272727272727)(686.747474747475,-7.3030303030303)(701.676767676768,-7.42424242424243)(709.141414141414,-7.45454545454546)(716.606060606061,-7.48484848484849)(731.535353535354,-7.60606060606061)(739,-7.63636363636364)(746.464646464646,-7.66666666666667)(761.393939393939,-7.72727272727273)(776.323232323232,-7.72727272727273)(791.252525252525,-7.72727272727273)(806.181818181818,-7.72727272727273)(821.111111111111,-7.66666666666667)(828.575757575758,-7.63636363636364)(836.040404040404,-7.60606060606061)(850.969696969697,-7.48484848484849)(858.434343434343,-7.45454545454546)(865.89898989899,-7.42424242424243)(880.828282828283,-7.3030303030303)(888.292929292929,-7.27272727272727)(895.757575757576,-7.24242424242424)(910.686868686869,-7.18181818181818)(925.616161616162,-7.12121212121212)(933.080808080808,-7.09090909090909)(940.545454545455,-7.06060606060606)(955.474747474747,-7)(970.40404040404,-6.97727272727273)(985.333333333333,-6.97727272727273)(1000.26262626263,-6.93181818181818)(1007.72727272727,-6.90909090909091)(1015.19191919192,-6.87878787878788)(1030.12121212121,-6.81818181818182)(1045.05050505051,-6.81818181818182)(1059.9797979798,-6.81818181818182)(1074.90909090909,-6.81818181818182)(1089.83838383838,-6.81818181818182)(1104.76767676768,-6.81818181818182)(1119.69696969697,-6.81818181818182)(1134.62626262626,-6.81818181818182)(1149.55555555556,-6.87878787878788)(1157.0202020202,-6.90909090909091)(1164.48484848485,-6.93939393939394)(1179.41414141414,-7)(1194.34343434343,-7)(1209.27272727273,-7)(1224.20202020202,-7)(1239.13131313131,-7)(1254.06060606061,-7)(1268.9898989899,-7.06060606060606)(1276.45454545455,-7.09090909090909)(1283.91919191919,-7.12121212121212)(1298.84848484848,-7.18181818181818)(1313.77777777778,-7.18181818181818)(1328.70707070707,-7.24242424242424)(1336.17171717172,-7.27272727272727)(1343.63636363636,-7.3030303030303)(1358.56565656566,-7.42424242424243)(1366.0303030303,-7.45454545454546)(1373.49494949495,-7.48484848484849)(1388.42424242424,-7.60606060606061)(1392.15656565657,-7.63636363636364)(1403.35353535354,-7.72727272727273)(1414.5505050505,-7.81818181818182)(1418.28282828283,-7.84848484848485)(1433.21212121212,-7.96969696969697)(1436.94444444444,-8)(1448.14141414141,-8.09090909090909)(1455.60606060606,-8.18181818181818)(1463.07070707071,-8.31818181818182)(1465.55892255892,-8.36363636363636)(1478,-8.51515151515152)(1478.00002764633,-8.54545454545455)(1478.00013823061,-8.72727272727273)(1478.00024881326,-8.90909090909091)(1478.00024881326,-9.09090909090909)(1478.00024881326,-9.27272727272727)(1478.00013823061,-9.45454545454546)(1478.00013823061,-9.63636363636364)(1478.00013823061,-9.81818181818182)(1478.00013823061,-10)(1478,-10.1515151515152)(1470.53535353535,-10.1818181818182)(1463.07070707071,-10.2121212121212)(1448.14141414141,-10.3333333333333)(1440.67676767677,-10.3636363636364)(1433.21212121212,-10.3939393939394)(1418.28282828283,-10.5151515151515)(1410.81818181818,-10.5454545454545)(1403.35353535354,-10.5757575757576)(1388.42424242424,-10.6363636363636)(1373.49494949495,-10.6363636363636)(1358.56565656566,-10.6363636363636)(1343.63636363636,-10.6363636363636)(1328.70707070707,-10.6363636363636)(1313.77777777778,-10.6363636363636)(1298.84848484848,-10.6363636363636)(1283.91919191919,-10.6363636363636)(1268.9898989899,-10.6363636363636)(1254.06060606061,-10.6363636363636)(1239.13131313131,-10.6363636363636)(1224.20202020202,-10.6363636363636)(1209.27272727273,-10.6363636363636)(1194.34343434343,-10.6363636363636)(1179.41414141414,-10.6363636363636)(1164.48484848485,-10.6363636363636)(1149.55555555556,-10.6363636363636)(1134.62626262626,-10.6363636363636)(1119.69696969697,-10.6363636363636)(1104.76767676768,-10.6363636363636)(1089.83838383838,-10.6363636363636)(1074.90909090909,-10.6363636363636)(1059.9797979798,-10.6969696969697)(1052.51515151515,-10.7272727272727)(1045.05050505051,-10.7575757575758)(1030.12121212121,-10.8181818181818)(1015.19191919192,-10.8181818181818)(1000.26262626263,-10.7575757575758)(992.79797979798,-10.7272727272727)(985.333333333333,-10.6969696969697)(970.40404040404,-10.6363636363636)(955.474747474747,-10.6363636363636)(940.545454545455,-10.6363636363636)(925.616161616162,-10.5757575757576)(918.151515151515,-10.5454545454545)(910.686868686869,-10.5)(895.757575757576,-10.4090909090909)(880.828282828283,-10.3939393939394)(877.09595959596,-10.3636363636364)(865.89898989899,-10.2727272727273)(854.70202020202,-10.1818181818182)(850.969696969697,-10.1515151515152)(836.040404040404,-10.030303030303)(832.308080808081,-10)(821.111111111111,-9.90909090909091)(813.646464646465,-9.81818181818182)(806.181818181818,-9.72727272727273)(798.717171717172,-9.63636363636364)(791.252525252525,-9.54545454545455)(780.055555555556,-9.45454545454546)(776.323232323232,-9.42424242424243)(761.393939393939,-9.3030303030303)(753.929292929293,-9.27272727272727)(746.464646464646,-9.24242424242424)(731.535353535354,-9.12121212121212)(724.070707070707,-9.09090909090909)(716.606060606061,-9.06060606060606)(701.676767676768,-9)(686.747474747475,-9.06060606060606)(679.282828282828,-9.09090909090909)(671.818181818182,-9.12121212121212)(656.888888888889,-9.18181818181818)(641.959595959596,-9.18181818181818)(627.030303030303,-9.18181818181818)(612.10101010101,-9.18181818181818)(597.171717171717,-9.24242424242424)(589.707070707071,-9.27272727272727)(582.242424242424,-9.3030303030303)(567.313131313131,-9.36363636363636)(552.383838383838,-9.36363636363636)(537.454545454546,-9.36363636363636)(522.525252525253,-9.36363636363636)(507.59595959596,-9.36363636363636)(492.666666666667,-9.36363636363636)(477.737373737374,-9.36363636363636)(462.808080808081,-9.36363636363636)(447.878787878788,-9.36363636363636)(432.949494949495,-9.36363636363636)(418.020202020202,-9.36363636363636)(403.090909090909,-9.36363636363636)(388.161616161616,-9.36363636363636)(373.232323232323,-9.36363636363636)(358.30303030303,-9.36363636363636)(343.373737373737,-9.36363636363636)(328.444444444444,-9.36363636363636)(313.515151515152,-9.36363636363636)(298.585858585859,-9.36363636363636)(283.656565656566,-9.36363636363636)(268.727272727273,-9.36363636363636)(253.79797979798,-9.36363636363636)(238.868686868687,-9.38636363636364)(223.939393939394,-9.34090909090909)(209.010101010101,-9.29545454545455)(205.277777777778,-9.27272727272727)(194.080808080808,-9.18181818181818)(179.151515151515,-9.18181818181818)(164.222222222222,-9.12121212121212)(156.757575757576,-9.09090909090909)(149.292929292929,-9.06060606060606)(134.363636363636,-8.93939393939394)(126.89898989899,-8.90909090909091)(119.434343434343,-8.88636363636364)(104.505050505051,-8.79545454545455)(97.040404040404,-8.72727272727273)(89.5757575757576,-8.63636363636364)(78.3787878787879,-8.54545454545455)(74.6464646464647,-8.51515151515152)(59.7171717171717,-8.39393939393939)(55.9848484848485,-8.36363636363636)(44.7878787878788,-8.27272727272727)(37.3232323232323,-8.18181818181818)(29.8585858585859,-8.09090909090909)(22.3939393939394,-8)(14.9292929292929,-7.90909090909091)(3.73232323232323,-7.81818181818182)(0,-7.72727272727273)(-2.76463267876964e-05,-7.63636363636364)(-0.000138230610030762,-7.45454545454546)(-2.76463267876964e-05,-7.27272727272727)(0,-7.18181818181818)};

%\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1373.49494949495,-8.95454545454546)(1377.22727272727,-9.09090909090909)(1374.98787878788,-9.27272727272727)(1373.49494949495,-9.31818181818182)(1367.89646464646,-9.45454545454546)(1358.56565656566,-9.56818181818182)(1352.96717171717,-9.63636363636364)(1343.63636363636,-9.72727272727273)(1328.70707070707,-9.8030303030303)(1324.97474747475,-9.81818181818182)(1313.77777777778,-9.86363636363636)(1298.84848484848,-9.92424242424243)(1283.91919191919,-9.98484848484848)(1280.18686868687,-10)(1268.9898989899,-10.0454545454545)(1254.06060606061,-10.0757575757576)(1239.13131313131,-10.0757575757576)(1224.20202020202,-10.0757575757576)(1209.27272727273,-10.0454545454545)(1194.34343434343,-10.0454545454545)(1179.41414141414,-10.0454545454545)(1164.48484848485,-10.0454545454545)(1149.55555555556,-10.0454545454545)(1134.62626262626,-10.0454545454545)(1119.69696969697,-10.0454545454545)(1104.76767676768,-10.0454545454545)(1089.83838383838,-10.0454545454545)(1074.90909090909,-10.0454545454545)(1059.9797979798,-10.0454545454545)(1045.05050505051,-10.0454545454545)(1033.85353535354,-10)(1030.12121212121,-9.98484848484848)(1015.19191919192,-9.92424242424243)(1000.26262626263,-9.86363636363636)(989.065656565657,-9.81818181818182)(985.333333333333,-9.8030303030303)(970.40404040404,-9.74242424242424)(957.340909090909,-9.63636363636364)(955.474747474747,-9.62121212121212)(940.545454545455,-9.52272727272727)(934.94696969697,-9.45454545454546)(925.616161616162,-9.34090909090909)(920.017676767677,-9.27272727272727)(911.930976430976,-9.09090909090909)(910.686868686869,-9.04545454545455)(906.954545454546,-8.90909090909091)(904.46632996633,-8.72727272727273)(908.820707070707,-8.54545454545455)(910.686868686869,-8.5)(916.285353535354,-8.36363636363636)(925.616161616162,-8.27272727272727)(940.545454545455,-8.1969696969697)(942.411616161616,-8.18181818181818)(955.474747474747,-8.07575757575757)(970.40404040404,-8.01515151515152)(972.270202020202,-8)(985.333333333333,-7.89393939393939)(1000.26262626263,-7.83333333333333)(1003.99494949495,-7.81818181818182)(1015.19191919192,-7.77272727272727)(1030.12121212121,-7.77272727272727)(1045.05050505051,-7.77272727272727)(1059.9797979798,-7.77272727272727)(1074.90909090909,-7.71212121212121)(1089.83838383838,-7.65151515151515)(1093.57070707071,-7.63636363636364)(1104.76767676768,-7.59090909090909)(1119.69696969697,-7.59090909090909)(1134.62626262626,-7.61818181818182)(1138.35858585859,-7.63636363636364)(1149.55555555556,-7.68181818181818)(1164.48484848485,-7.74242424242424)(1179.41414141414,-7.77272727272727)(1194.34343434343,-7.77272727272727)(1209.27272727273,-7.77272727272727)(1224.20202020202,-7.77272727272727)(1235.39898989899,-7.81818181818182)(1239.13131313131,-7.83333333333333)(1254.06060606061,-7.87272727272727)(1268.9898989899,-7.94545454545455)(1280.18686868687,-8)(1283.91919191919,-8.01515151515152)(1298.84848484848,-8.07575757575757)(1311.91161616162,-8.18181818181818)(1313.77777777778,-8.1969696969697)(1328.70707070707,-8.29545454545455)(1336.17171717172,-8.36363636363636)(1343.63636363636,-8.43181818181818)(1352.96717171717,-8.54545454545455)(1358.56565656566,-8.63636363636364)(1364.16414141414,-8.72727272727273)(1372.25084175084,-8.90909090909091)(1373.49494949495,-8.95454545454546)};

\addplot [fill=green!60!black,draw=none,forget plot] coordinates{ (1343.63636363636,-8.79545454545455)(1349.8569023569,-8.90909090909091)(1354.83333333333,-9.09090909090909)(1352.34511784512,-9.27272727272727)(1343.63636363636,-9.43181818181818)(1341.14814814815,-9.45454545454546)(1328.70707070707,-9.53030303030303)(1313.77777777778,-9.59090909090909)(1302.58080808081,-9.63636363636364)(1298.84848484848,-9.65151515151515)(1283.91919191919,-9.71212121212121)(1268.9898989899,-9.77272727272727)(1254.06060606061,-9.77272727272727)(1239.13131313131,-9.77272727272727)(1224.20202020202,-9.77272727272727)(1209.27272727273,-9.77272727272727)(1194.34343434343,-9.77272727272727)(1179.41414141414,-9.77272727272727)(1164.48484848485,-9.77272727272727)(1149.55555555556,-9.77272727272727)(1134.62626262626,-9.74242424242424)(1119.69696969697,-9.74242424242424)(1104.76767676768,-9.74242424242424)(1089.83838383838,-9.77272727272727)(1074.90909090909,-9.77272727272727)(1059.9797979798,-9.77272727272727)(1045.05050505051,-9.77272727272727)(1030.12121212121,-9.71212121212121)(1015.19191919192,-9.65151515151515)(1011.4595959596,-9.63636363636364)(1000.26262626263,-9.58181818181818)(985.333333333333,-9.50909090909091)(970.40404040404,-9.46969696969697)(968.537878787879,-9.45454545454546)(955.474747474747,-9.34848484848485)(946.143939393939,-9.27272727272727)(940.545454545455,-9.20454545454546)(934.324915824916,-9.09090909090909)(929.348484848485,-8.90909090909091)(927.109090909091,-8.72727272727273)(933.080808080808,-8.54545454545455)(940.545454545455,-8.46969696969697)(953.608585858586,-8.36363636363636)(955.474747474747,-8.34848484848485)(970.40404040404,-8.28787878787879)(983.467171717172,-8.18181818181818)(985.333333333333,-8.16666666666667)(1000.26262626263,-8.10606060606061)(1015.19191919192,-8.04545454545455)(1030.12121212121,-8.04545454545455)(1045.05050505051,-8.04545454545455)(1059.9797979798,-8.07575757575757)(1074.90909090909,-8.02272727272727)(1078.64141414141,-8)(1089.83838383838,-7.94545454545455)(1104.76767676768,-7.86363636363636)(1119.69696969697,-7.86363636363636)(1134.62626262626,-7.89393939393939)(1149.55555555556,-7.95454545454546)(1160.75252525253,-8)(1164.48484848485,-8.01818181818182)(1179.41414141414,-8.04545454545455)(1194.34343434343,-8.04545454545455)(1209.27272727273,-8.04545454545455)(1224.20202020202,-8.04545454545455)(1239.13131313131,-8.10606060606061)(1254.06060606061,-8.16666666666667)(1257.79292929293,-8.18181818181818)(1268.9898989899,-8.22727272727273)(1283.91919191919,-8.28787878787879)(1298.84848484848,-8.34848484848485)(1300.71464646465,-8.36363636363636)(1313.77777777778,-8.46969696969697)(1323.10858585859,-8.54545454545455)(1328.70707070707,-8.61363636363636)(1338.03787878788,-8.72727272727273)(1343.63636363636,-8.79545454545455)};
\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (791.252525252525,-14.9090909090909)(0,0)(1478,-4.36363636363636)(0,-8.54545454545455)(0,-18)(1478,-10.9090909090909)(1478,-18)(910.686868686869,0)(731.535353535354,-6.54545454545455)(0,-13.2727272727273)(0,-4.18181818181818)(1478,0)(686.747474747475,-10.7272727272727)(627.030303030303,-18)(537.454545454546,-2.72727272727273)(1478,-14.3636363636364)(1268.9898989899,-7.63636363636364)(1030.12121212121,-3.45454545454546)(1059.9797979798,-18)(328.444444444444,-15.2727272727273)(447.878787878788,0)(1089.83838383838,-12.1818181818182)(313.515151515152,-6.54545454545455)(268.727272727273,-11.0909090909091)(1000.26262626263,-9.27272727272727)(477.737373737374,-8.72727272727273)(1478,-8.54545454545455)(1089.83838383838,-5.63636363636364)(0,-10.9090909090909)(0,-6.36363636363636)(358.30303030303,-4.36363636363636)(1478,-6.36363636363636)(1239.13131313131,-10.1818181818182)(761.393939393939,-8.36363636363636)(1373.49494949495,-12.1818181818182)(597.171717171717,-5.45454545454546)(223.939393939394,-9.09090909090909)(985.333333333333,-7.27272727272727)(895.757575757576,-11.2727272727273)(1298.84848484848,-5.45454545454546)(865.89898989899,-5.63636363636364)(462.808080808081,-10.3636363636364)(522.525252525253,-7.27272727272727)(179.151515151515,-7.63636363636364)(164.222222222222,-5.81818181818182)(776.323232323232,-9.63636363636364)(1239.13131313131,-8.90909090909091)(1478,-9.63636363636364)(1074.90909090909,-10.7272727272727)(119.434343434343,-9.81818181818182)(1478,-7.45454545454546)(0,-7.45454545454546)(1179.41414141414,-6.72727272727273)(447.878787878788,-6)(1283.91919191919,-11.0909090909091)(612.10101010101,-9.27272727272727)(1074.90909090909,-8.18181818181818)(343.373737373737,-8)(328.444444444444,-9.81818181818182)(836.040404040404,-7.45454545454546)(910.686868686869,-10.1818181818182)(641.959595959596,-7.81818181818182)(1358.56565656566,-9.45454545454546)(910.686868686869,-8.54545454545455)(149.292929292929,-6.72727272727273)(1343.63636363636,-7.27272727272727)(1119.69696969697,-9.63636363636364)(1015.19191919192,-6.72727272727273)(597.171717171717,-6.54545454545455)(119.434343434343,-8.54545454545455)(388.161616161616,-7.27272727272727)(1358.56565656566,-8.36363636363636)(1478,-10.1818181818182)(447.878787878788,-9.45454545454546)(1149.55555555556,-10.9090909090909)(1149.55555555556,-7.81818181818182)(1358.56565656566,-10.7272727272727)(328.444444444444,-8.72727272727273)(567.313131313131,-8.36363636363636)(0,-7.09090909090909) 
};
\end{axis}
\end{tikzpicture}%

### 2013-03-21 figurefactory/files/voned_cl_41_imp_1.tex
Add implicit extension

--- 2013-03-19 figurefactory/files/voned_cl_40.tex
@@
 ymin=-2, ymax=4,
-tickwidth=0cm,
+tickwidth=0.1cm,
 ]
@@
 \addplot [
-color=darkgray,
-solid,
-only marks,
-mark=*,
-mark size=2.5pt,
+color=black,
+densely dashed,
+line width=1.5pt,
 forget plot
@@
 coordinates{
- (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
-};
-
-\addplot [
-color=red!40!yellow,
-solid,
-only marks,
-mark=*,
-mark size=2.5pt,
-forget plot
-]
-coordinates{
- (0.5,-2)(1.5,-2)
-};
-
-\addplot [
-color=locol,
-solid,
-only marks,
-mark=*,
-mark size=2.5pt,
-forget plot
-]
-coordinates{
- (1,-2)
-};
-
-\addplot [
-color=red,
-densely dashed,
-line width=2.0pt,
-forget plot
-]
-coordinates{
- (0,1.2)(2,1.2)
+ (0,3.825915)(2,3.825915)
 };
@@
 color=black,
-solid,
+densely dashed,
 line width=1.5pt,
-mark size=3pt,
-mark=-,
 forget plot
@@
 coordinates{
- (0,-0.1683)(0,3.5848)
+ (0,2.4975)(2,2.4975)
 };
-
-\addplot [
-color=black,
-solid,
-line width=1.5pt,
-mark size=3pt,
-mark=-,
-forget plot
-]
-coordinates{
- (2,-0.4448)(2,3.3083)
-};
-
-\node at (axis cs:0, -0.8) [anchor=south west,minimum size=16pt] {$Q_4(\*x_0)$};
-
-\node at (axis cs:1.78, -1) [anchor=south west,minimum size=16pt] {$Q_4(\*x_2)$};
 

### 2013-03-21 msthpres.tex
Add implicit extension

@@
 \documentclass[10pt,mathserif,serif]{beamer}
-%\documentclass[10pt,mathserif,serif,draft, handout]{beamer}
+%\documentclass[10pt,mathserif,serif,draft,handout]{beamer}
 
@@
 
-\section{Extensions}
+\section{Two extensions}
 
 \begin{frame}
-\begin{enumerate}
-\item bla
-\end{enumerate}
+\begin{itemize}
+\item<1-> What if we don't know $h$?
+\item<2-> Implicitly define the threshold level: $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
+\item<5-> \iacl:
+\begin{itemize}
+\item<5-> Need to accurately estimate the maximum (don't exclude points that could be maximizers)
+\item<6-> Slower classification
+\end{itemize}
+\end{itemize}
+\begin{center}
+\color{white}
+\only<1-2>{\includegraphics[draft,width=3.77in]{figures/voned_cl_41_imp_1}}
+\color{black}
+\only<3>{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_1}}
+\only<4->{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_2}}
+\end{center}
+\end{frame}
+
+\begin{frame}
+\begin{center}
+\includegraphics<1-14>[width=4in]{figures/limno_bgape_ls}
+\only<15>{\hspace{-1.9em}}
+\includegraphics<15>[width=3.78in]{figures/limno_bgape_class_354}
+\\
+
+\only<1>{\color{white}\small{$t = 0$\\}}
+\only<2>{\small{$t = 0$\\}}
+\only<3>{\small{$t = 20$\\}}
+\only<4>{\small{$t = 40$\\}}
+\only<5>{\small{$t = 60$\\}}
+\only<6>{\small{$t = 80$\\}}
+\only<7>{\small{$t = 100$\\}}
+\only<8>{\small{$t = 120$\\}}
+\only<9>{\small{$t = 140$\\}}
+\only<10>{\small{$t = 160$\\}}
+\only<11>{\small{$t = 180$\\}}
+\only<12>{\small{$t = 200$\\}}
+%\only<13>{\small{$t = 220$\\}}
+%\only<14>{\small{$t = 240$\\}}
+\only<13>{\small{$t = 340$\\}}
+%\only<16>{\small{$t = 280$\\}}
+%\only<17>{\small{$t = 300$\\}}
+%\only<18>{\small{$t = 320$\\}}
+%\only<19>{\small{$t = 340$\\}}
+\only<14>{\small{$t = 486$\\}}
+
+\hspace{-1.9em}
+\color{white}
+\includegraphics<1>[draft,width=3.78in]{figures/limno_bgape_class_20}
+\color{black}
+\includegraphics<2>[width=3.78in]{figures/limno_bgape_imp_class_0}
+\includegraphics<3>[width=3.78in]{figures/limno_bgape_imp_class_20}
+\includegraphics<4>[width=3.78in]{figures/limno_bgape_imp_class_40}
+\includegraphics<5>[width=3.78in]{figures/limno_bgape_imp_class_60}
+\includegraphics<6>[width=3.78in]{figures/limno_bgape_imp_class_80}
+\includegraphics<7>[width=3.78in]{figures/limno_bgape_imp_class_100}
+\includegraphics<8>[width=3.78in]{figures/limno_bgape_imp_class_120}
+\includegraphics<9>[width=3.78in]{figures/limno_bgape_imp_class_140}
+\includegraphics<10>[width=3.78in]{figures/limno_bgape_imp_class_160}
+\includegraphics<11>[width=3.78in]{figures/limno_bgape_imp_class_180}
+\includegraphics<12>[width=3.78in]{figures/limno_bgape_imp_class_200}
+\includegraphics<13>[width=3.78in]{figures/limno_bgape_imp_class_340}
+\includegraphics<14->[width=3.78in]{figures/limno_bgape_imp_class_486}
+\end{center}
+\end{frame}
+
+\begin{frame}
+\begin{center}
+\includegraphics[width=2.3in]{figures/ev_chl_imp}
+\includegraphics[width=2.3in]{figures/ev_bgape_imp}
+\end{center}
 \end{frame}

### 2013-03-22 figurefactory/files/limno_bgape_pp_0_1.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-19 figurefactory/files/limno_bgape_class_0.tex
@@
 
+\addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=1.6pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0)
+};
+
 \end{axis}

### 2013-03-22 figurefactory/files/limno_bgape_pp_0_2.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_0_1.tex
@@
 \addplot [
+draw=red!50!white,
+line width=0.6pt,
+forget plot
+]
+coordinates{
+ (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0)
+};
+
+\addplot [
 color=red,
@@
 
+\addplot [
+color=lime,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=3pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (731.535353535354,-4.36363636363636)
+};
+
+\addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=3pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (1478,0)
+};
+
 \end{axis}

### 2013-03-22 figurefactory/files/limno_bgape_pp_120_0.tex
Add batch/path planning; add summary; finish first draft

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478.00008294006,-8.36363636363636)(1478.00033175469,-8.54545454545455)(1478.00058056104,-8.72727272727273)(1478.00074642733,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00074642733,-9.27272727272727)(1478.00049762651,-9.45454545454546)(1478.0002488174,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(-0.000248817401863321,-7.81818181818182)(-0.000497626510092015,-7.63636363636364)(-0.000746427325097138,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000746427325097138,-7.09090909090909)(-0.000746427325097138,-6.90909090909091)(-0.000746427325097138,-6.72727272727273)(-0.000497626510092015,-6.54545454545455)(-0.000248817401863321,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-6.45454545454545)(14.9292929292929,-6.45454545454545)(29.8585858585859,-6.51515151515151)(37.3232323232323,-6.54545454545455)(44.7878787878788,-6.57575757575758)(59.7171717171717,-6.63636363636364)(74.6464646464647,-6.6969696969697)(82.1111111111111,-6.72727272727273)(89.5757575757576,-6.75757575757576)(104.505050505051,-6.87878787878788)(111.969696969697,-6.90909090909091)(119.434343434343,-6.93939393939394)(134.363636363636,-7)(149.292929292929,-7.06060606060606)(156.757575757576,-7.09090909090909)(164.222222222222,-7.12121212121212)(179.151515151515,-7.18181818181818)(194.080808080808,-7.18181818181818)(209.010101010101,-7.18181818181818)(223.939393939394,-7.18181818181818)(238.868686868687,-7.18181818181818)(253.79797979798,-7.18181818181818)(268.727272727273,-7.18181818181818)(283.656565656566,-7.18181818181818)(298.585858585859,-7.18181818181818)(313.515151515152,-7.18181818181818)(328.444444444444,-7.18181818181818)(343.373737373737,-7.18181818181818)(358.30303030303,-7.18181818181818)(373.232323232323,-7.12121212121212)(380.69696969697,-7.09090909090909)(388.161616161616,-7.06060606060606)(403.090909090909,-7)(418.020202020202,-6.93939393939394)(425.484848484849,-6.90909090909091)(432.949494949495,-6.87878787878788)(447.878787878788,-6.81818181818182)(462.808080808081,-6.81818181818182)(477.737373737374,-6.81818181818182)(492.666666666667,-6.81818181818182)(507.59595959596,-6.81818181818182)(522.525252525253,-6.81818181818182)(537.454545454546,-6.87878787878788)(541.186868686869,-6.90909090909091)(552.383838383838,-7)(559.848484848485,-7.09090909090909)(567.313131313131,-7.18181818181818)(578.510101010101,-7.27272727272727)(582.242424242424,-7.29545454545455)(597.171717171717,-7.42424242424243)(600.90404040404,-7.45454545454546)(612.10101010101,-7.54545454545455)(619.565656565657,-7.63636363636364)(627.030303030303,-7.72727272727273)(634.494949494949,-7.81818181818182)(641.959595959596,-7.95454545454546)(644.447811447811,-8)(654.400673400673,-8.18181818181818)(656.888888888889,-8.22727272727273)(664.353535353535,-8.36363636363636)(671.818181818182,-8.45454545454545)(679.282828282828,-8.54545454545455)(686.747474747475,-8.63636363636364)(694.212121212121,-8.72727272727273)(701.676767676768,-8.81818181818182)(712.873737373737,-8.90909090909091)(716.606060606061,-8.93939393939394)(731.535353535354,-9)(746.464646464646,-8.93939393939394)(750.19696969697,-8.90909090909091)(761.393939393939,-8.77272727272727)(765.126262626263,-8.72727272727273)(768.858585858586,-8.54545454545455)(773.835016835017,-8.36363636363636)(776.323232323232,-8.31818181818182)(783.787878787879,-8.18181818181818)(791.252525252525,-8.09090909090909)(798.717171717172,-8)(806.181818181818,-7.90909090909091)(817.378787878788,-7.81818181818182)(821.111111111111,-7.78787878787879)(836.040404040404,-7.66666666666667)(839.772727272727,-7.63636363636364)(850.969696969697,-7.56818181818182)(865.89898989899,-7.47727272727273)(873.363636363636,-7.45454545454546)(880.828282828283,-7.42424242424243)(895.757575757576,-7.29545454545455)(899.489898989899,-7.27272727272727)(910.686868686869,-7.20454545454546)(925.616161616162,-7.15909090909091)(940.545454545455,-7.11363636363636)(948.010101010101,-7.09090909090909)(955.474747474747,-7.06060606060606)(970.40404040404,-7)(985.333333333333,-7)(1000.26262626263,-6.97727272727273)(1015.19191919192,-7)(1030.12121212121,-7)(1045.05050505051,-7.04545454545455)(1059.9797979798,-7)(1074.90909090909,-7)(1089.83838383838,-7)(1104.76767676768,-7.06060606060606)(1112.23232323232,-7.09090909090909)(1119.69696969697,-7.13636363636364)(1134.62626262626,-7.18181818181818)(1149.55555555556,-7.18181818181818)(1164.48484848485,-7.15909090909091)(1179.41414141414,-7.18181818181818)(1194.34343434343,-7.18181818181818)(1209.27272727273,-7.18181818181818)(1224.20202020202,-7.24242424242424)(1231.66666666667,-7.27272727272727)(1239.13131313131,-7.29545454545455)(1254.06060606061,-7.34090909090909)(1268.9898989899,-7.36363636363636)(1283.91919191919,-7.42424242424243)(1291.38383838384,-7.45454545454546)(1298.84848484848,-7.48484848484849)(1313.77777777778,-7.59090909090909)(1328.70707070707,-7.60606060606061)(1336.17171717172,-7.63636363636364)(1343.63636363636,-7.66666666666667)(1358.56565656566,-7.78787878787879)(1362.29797979798,-7.81818181818182)(1373.49494949495,-7.95454545454546)(1380.9595959596,-8)(1388.42424242424,-8.02272727272727)(1403.35353535354,-8.11363636363636)(1414.5505050505,-8.18181818181818)(1418.28282828283,-8.22727272727273)(1433.21212121212,-8.33333333333333)(1440.67676767677,-8.36363636363636)(1448.14141414141,-8.39393939393939)(1463.07070707071,-8.51515151515152)(1470.53535353535,-8.54545454545455)(1478,-8.57575757575757)(1478.00020734323,-8.72727272727273)(1478.00037321366,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00037321366,-9.27272727272727)(1478.00012440663,-9.45454545454546)(1478,-9.54545454545455)(1463.07070707071,-9.60606060606061)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.66666666666667)(1433.21212121212,-9.79545454545455)(1425.74747474747,-9.81818181818182)(1418.28282828283,-9.84848484848485)(1403.35353535354,-9.96969696969697)(1388.42424242424,-9.96969696969697)(1384.69191919192,-10)(1373.49494949495,-10.0909090909091)(1358.56565656566,-10.0909090909091)(1347.36868686869,-10.1818181818182)(1343.63636363636,-10.2045454545455)(1328.70707070707,-10.2727272727273)(1313.77777777778,-10.3090909090909)(1298.84848484848,-10.2954545454545)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2727272727273)(1254.06060606061,-10.2121212121212)(1246.59595959596,-10.1818181818182)(1239.13131313131,-10.1666666666667)(1224.20202020202,-10.1666666666667)(1216.73737373737,-10.1818181818182)(1209.27272727273,-10.2121212121212)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.2727272727273)(1149.55555555556,-10.2954545454545)(1134.62626262626,-10.3090909090909)(1119.69696969697,-10.3484848484848)(1112.23232323232,-10.3636363636364)(1104.76767676768,-10.3818181818182)(1097.30303030303,-10.3636363636364)(1089.83838383838,-10.3484848484848)(1074.90909090909,-10.3181818181818)(1059.9797979798,-10.2878787878788)(1045.05050505051,-10.3090909090909)(1030.12121212121,-10.2954545454545)(1015.19191919192,-10.2727272727273)(1000.26262626263,-10.2727272727273)(985.333333333333,-10.2727272727273)(970.40404040404,-10.2121212121212)(962.939393939394,-10.1818181818182)(955.474747474747,-10.1666666666667)(940.545454545455,-10.0909090909091)(925.616161616162,-10.0681818181818)(914.419191919192,-10)(910.686868686869,-9.98484848484848)(895.757575757576,-9.94545454545455)(880.828282828283,-9.88636363636364)(869.631313131313,-9.81818181818182)(865.89898989899,-9.79545454545455)(858.434343434343,-9.81818181818182)(850.969696969697,-9.84090909090909)(843.505050505051,-9.81818181818182)(836.040404040404,-9.78787878787879)(821.111111111111,-9.72727272727273)(809.914141414141,-9.63636363636364)(806.181818181818,-9.59090909090909)(791.252525252525,-9.54545454545455)(776.323232323232,-9.48484848484848)(768.858585858586,-9.45454545454546)(761.393939393939,-9.42424242424243)(746.464646464646,-9.36363636363636)(731.535353535354,-9.36363636363636)(716.606060606061,-9.42424242424243)(709.141414141414,-9.45454545454546)(701.676767676768,-9.48484848484848)(686.747474747475,-9.54545454545455)(671.818181818182,-9.60606060606061)(664.353535353535,-9.63636363636364)(656.888888888889,-9.66666666666667)(641.959595959596,-9.72727272727273)(627.030303030303,-9.72727272727273)(612.10101010101,-9.72727272727273)(597.171717171717,-9.66666666666667)(589.707070707071,-9.63636363636364)(582.242424242424,-9.60606060606061)(567.313131313131,-9.54545454545455)(552.383838383838,-9.54545454545455)(541.186868686869,-9.45454545454546)(537.454545454546,-9.42424242424243)(522.525252525253,-9.36363636363636)(511.328282828283,-9.27272727272727)(507.59595959596,-9.24242424242424)(492.666666666667,-9.24242424242424)(477.737373737374,-9.18181818181818)(462.808080808081,-9.18181818181818)(447.878787878788,-9.12121212121212)(440.414141414141,-9.09090909090909)(432.949494949495,-9.06060606060606)(418.020202020202,-8.93939393939394)(410.555555555556,-8.90909090909091)(403.090909090909,-8.86363636363636)(388.161616161616,-8.75757575757576)(380.69696969697,-8.72727272727273)(373.232323232323,-8.68181818181818)(358.30303030303,-8.63636363636364)(343.373737373737,-8.63636363636364)(328.444444444444,-8.63636363636364)(313.515151515152,-8.63636363636364)(298.585858585859,-8.63636363636364)(283.656565656566,-8.63636363636364)(268.727272727273,-8.6969696969697)(261.262626262626,-8.72727272727273)(253.79797979798,-8.75757575757576)(238.868686868687,-8.87878787878788)(231.40404040404,-8.90909090909091)(223.939393939394,-8.93939393939394)(209.010101010101,-9)(194.080808080808,-9)(179.151515151515,-9)(164.222222222222,-9)(149.292929292929,-9)(134.363636363636,-9)(119.434343434343,-9)(104.505050505051,-8.93939393939394)(100.772727272727,-8.90909090909091)(89.5757575757576,-8.81818181818182)(82.1111111111111,-8.72727272727273)(74.6464646464647,-8.63636363636364)(67.1818181818182,-8.54545454545455)(59.7171717171717,-8.40909090909091)(57.2289562289562,-8.36363636363636)(47.2760942760943,-8.18181818181818)(44.7878787878788,-8.09090909090909)(42.2996632996633,-8)(29.8585858585859,-7.84848484848485)(26.1262626262626,-7.81818181818182)(14.9292929292929,-7.72727272727273)(0,-7.72727272727273)(-0.000124406627521346,-7.63636363636364)(-0.000373213662548569,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000373213662548569,-7.09090909090909)(-0.000373213662548569,-6.90909090909091)(-0.000373213662548569,-6.72727272727273)(-0.000124406627521346,-6.54545454545455)(0,-6.45454545454545)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1403.35353535354,-9.13636363636364)(1414.5505050505,-9.27272727272727)(1403.35353535354,-9.40909090909091)(1395.88888888889,-9.45454545454546)(1388.42424242424,-9.47727272727273)(1373.49494949495,-9.60606060606061)(1366.0303030303,-9.63636363636364)(1358.56565656566,-9.66666666666667)(1346.12457912458,-9.81818181818182)(1343.63636363636,-9.83636363636364)(1328.70707070707,-9.88636363636364)(1313.77777777778,-9.96969696969697)(1298.84848484848,-9.96969696969697)(1283.91919191919,-9.90909090909091)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.88636363636364)(1239.13131313131,-9.87272727272727)(1224.20202020202,-9.87272727272727)(1209.27272727273,-9.88636363636364)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.90909090909091)(1149.55555555556,-9.96969696969697)(1142.09090909091,-10)(1134.62626262626,-10.0151515151515)(1119.69696969697,-10.0757575757576)(1104.76767676768,-10.1060606060606)(1089.83838383838,-10.0757575757576)(1074.90909090909,-10.0454545454545)(1059.9797979798,-10.0151515151515)(1045.05050505051,-10.0151515151515)(1037.58585858586,-10)(1030.12121212121,-9.96969696969697)(1015.19191919192,-9.90909090909091)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.90909090909091)(970.40404040404,-9.88636363636364)(955.474747474747,-9.87272727272727)(944.277777777778,-9.81818181818182)(940.545454545455,-9.79545454545455)(925.616161616162,-9.75)(910.686868686869,-9.69090909090909)(899.489898989899,-9.63636363636364)(895.757575757576,-9.61363636363636)(880.828282828283,-9.52272727272727)(869.631313131313,-9.45454545454546)(865.89898989899,-9.42424242424243)(853.457912457912,-9.27272727272727)(850.969696969697,-9.22727272727273)(845.371212121212,-9.09090909090909)(843.505050505051,-8.90909090909091)(843.505050505051,-8.72727272727273)(838.528619528619,-8.54545454545455)(843.505050505051,-8.36363636363636)(848.481481481482,-8.18181818181818)(850.969696969697,-8.13636363636364)(862.166666666667,-8)(865.89898989899,-7.95454545454546)(877.09595959596,-7.81818181818182)(880.828282828283,-7.79545454545455)(895.757575757576,-7.72727272727273)(903.222222222222,-7.63636363636364)(910.686868686869,-7.56818181818182)(925.616161616162,-7.48484848484849)(940.545454545455,-7.48484848484849)(955.474747474747,-7.54545454545455)(970.40404040404,-7.54545454545455)(985.333333333333,-7.54545454545455)(1000.26262626263,-7.5)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.56818181818182)(1059.9797979798,-7.48484848484849)(1074.90909090909,-7.48484848484849)(1089.83838383838,-7.48484848484849)(1104.76767676768,-7.54545454545455)(1115.96464646465,-7.63636363636364)(1119.69696969697,-7.65909090909091)(1134.62626262626,-7.66666666666667)(1149.55555555556,-7.72727272727273)(1164.48484848485,-7.68181818181818)(1179.41414141414,-7.72727272727273)(1194.34343434343,-7.66666666666667)(1209.27272727273,-7.72727272727273)(1224.20202020202,-7.72727272727273)(1235.39898989899,-7.81818181818182)(1239.13131313131,-7.86363636363636)(1254.06060606061,-7.86363636363636)(1268.9898989899,-7.90909090909091)(1280.18686868687,-8)(1283.91919191919,-8.03030303030303)(1298.84848484848,-8.09090909090909)(1313.77777777778,-8.15909090909091)(1321.24242424242,-8.18181818181818)(1328.70707070707,-8.21212121212121)(1341.14814814815,-8.36363636363636)(1343.63636363636,-8.38636363636364)(1358.56565656566,-8.43181818181818)(1373.49494949495,-8.47727272727273)(1384.69191919192,-8.54545454545455)(1388.42424242424,-8.63636363636364)(1390.2904040404,-8.72727272727273)(1401.48737373737,-8.90909090909091)(1401.48737373737,-9.09090909090909)(1403.35353535354,-9.13636363636364)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (477.737373737374,-8.04545454545455)(480.225589225589,-8)(488.934343434343,-7.81818181818182)(492.666666666667,-7.78787878787879)(507.59595959596,-7.78787878787879)(522.525252525253,-7.72727272727273)(537.454545454546,-7.72727272727273)(552.383838383838,-7.72727272727273)(563.580808080808,-7.81818181818182)(567.313131313131,-7.86363636363636)(574.777777777778,-8)(582.242424242424,-8.13636363636364)(584.73063973064,-8.18181818181818)(589.707070707071,-8.36363636363636)(585.974747474747,-8.54545454545455)(582.242424242424,-8.63636363636364)(574.777777777778,-8.72727272727273)(567.313131313131,-8.75)(552.383838383838,-8.79545454545455)(537.454545454546,-8.81818181818182)(522.525252525253,-8.75757575757576)(515.060606060606,-8.72727272727273)(507.59595959596,-8.6969696969697)(492.666666666667,-8.57575757575757)(488.934343434343,-8.54545454545455)(477.737373737374,-8.40909090909091)(475.249158249158,-8.36363636363636)(470.272727272727,-8.18181818181818)(477.737373737374,-8.04545454545455)};

\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0)(1268.9898989899,-8.18181818181818)(1254.06060606061,-9.27272727272727)(1164.48484848485,-8.54545454545455)(1149.55555555556,-8.18181818181818)(1134.62626262626,-7.81818181818182)(1119.69696969697,-8.90909090909091)(1104.76767676768,-7.63636363636364)(1074.90909090909,-7.45454545454546)(1074.90909090909,-9.09090909090909)(1059.9797979798,-9.09090909090909)(1030.12121212121,-7.27272727272727)(1015.19191919192,-7.27272727272727)(970.40404040404,-9.27272727272727)(910.686868686869,-7.09090909090909)(880.828282828283,-9.09090909090909)(865.89898989899,-9.09090909090909)(865.89898989899,-7.09090909090909)(791.252525252525,-8.90909090909091)(791.252525252525,-7.27272727272727)(761.393939393939,-7.27272727272727)(746.464646464646,-8.72727272727273)(716.606060606061,-8.54545454545455)(686.747474747475,-7.63636363636364)(671.818181818182,-8.18181818181818)(656.888888888889,-8)(597.171717171717,-7.09090909090909)(537.454545454546,-8.72727272727273)(223.939393939394,-8.36363636363636)(194.080808080808,-7.09090909090909)(0,-9.45454545454546)(209.010101010101,-8.18181818181818)(268.727272727273,-8.72727272727273)(298.585858585859,-7.81818181818182)(313.515151515152,-7.81818181818182)(313.515151515152,-8.90909090909091)(373.232323232323,-9.09090909090909)(388.161616161616,-9.09090909090909)(418.020202020202,-7.63636363636364)(492.666666666667,-9.27272727272727)(522.525252525253,-9.27272727272727)(522.525252525253,-7.81818181818182)(567.313131313131,-8)(567.313131313131,-9.09090909090909)(836.040404040404,-8.36363636363636)(836.040404040404,-9.63636363636364)(850.969696969697,-9.81818181818182)(865.89898989899,-8)(940.545454545455,-10.1818181818182)(955.474747474747,-10.1818181818182)(1074.90909090909,-10.3636363636364)(1209.27272727273,-7.63636363636364)(1224.20202020202,-10.1818181818182)(1239.13131313131,-10.1818181818182)(1283.91919191919,-7.81818181818182)(1313.77777777778,-10)(1358.56565656566,-9.81818181818182)(1358.56565656566,-8.18181818181818)(1403.35353535354,-8.72727272727273)(1403.35353535354,-9.27272727272727)(1418.28282828283,-8.90909090909091)(1433.21212121212,-9.09090909090909)(1418.28282828283,-9.45454545454546)(1403.35353535354,-8.54545454545455)(1388.42424242424,-8.36363636363636)(1373.49494949495,-9.81818181818182)(1328.70707070707,-10)(1298.84848484848,-7.81818181818182)(1239.13131313131,-7.63636363636364)(1149.55555555556,-7.45454545454546)(1134.62626262626,-7.45454545454546)(1104.76767676768,-10.1818181818182)(1089.83838383838,-10.1818181818182)(1074.90909090909,-10.1818181818182)(925.616161616162,-7.45454545454546)(925.616161616162,-10)(880.828282828283,-9.81818181818182)(865.89898989899,-7.81818181818182)(821.111111111111,-9.27272727272727)(612.10101010101,-8.72727272727273)(597.171717171717,-8.90909090909091)(567.313131313131,-7.63636363636364)(477.737373737374,-7.63636363636364)(418.020202020202,-8.54545454545455)(388.161616161616,-8.36363636363636)(388.161616161616,-8.18181818181818)(268.727272727273,-8)(194.080808080808,-7.81818181818182)(164.222222222222,-8)(164.222222222222,-8.18181818181818) 
};

\addplot [
color=lime,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (149.292929292929,-8)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-22 figurefactory/files/limno_bgape_pp_120_1.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_120_0.tex
@@
 \addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=1.6pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (149.292929292929,-8)(134.363636363636,-7.81818181818182)(119.434343434343,-8)(119.434343434343,-8.18181818181818)(134.363636363636,-8.36363636363636)(164.222222222222,-8.54545454545455)(238.868686868687,-7.81818181818182)(253.79797979798,-8.36363636363636)(403.090909090909,-8)(403.090909090909,-8.36363636363636)(447.878787878788,-8.72727272727273)(492.666666666667,-7.45454545454546)(507.59595959596,-7.45454545454546)(507.59595959596,-9.09090909090909)(552.383838383838,-7.45454545454546)(597.171717171717,-9.09090909090909)(612.10101010101,-7.81818181818182)(627.030303030303,-8.90909090909091)(641.959595959596,-8.54545454545455)(806.181818181818,-8.90909090909091)(821.111111111111,-8.18181818181818)(850.969696969697,-7.81818181818182)(955.474747474747,-10)(955.474747474747,-7.27272727272727)(1045.05050505051,-7.27272727272727)(1119.69696969697,-10.1818181818182)(1134.62626262626,-10.1818181818182)(1224.20202020202,-7.63636363636364)(1328.70707070707,-8)(1433.21212121212,-8.90909090909091)(1433.21212121212,-9.27272727272727)
+};
+
+\addplot [
 color=lime,

### 2013-03-22 figurefactory/files/limno_bgape_pp_120_2.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_120_1.tex
@@
 \addplot [
+draw=red!50!white,
+line width=0.6pt,
+forget plot
+]
+coordinates{
+ (149.292929292929,-8)(134.363636363636,-7.81818181818182)(119.434343434343,-8)(119.434343434343,-8.18181818181818)(134.363636363636,-8.36363636363636)(164.222222222222,-8.54545454545455)(238.868686868687,-7.81818181818182)(253.79797979798,-8.36363636363636)(403.090909090909,-8)(403.090909090909,-8.36363636363636)(447.878787878788,-8.72727272727273)(492.666666666667,-7.45454545454546)(507.59595959596,-7.45454545454546)(507.59595959596,-9.09090909090909)(552.383838383838,-7.45454545454546)(597.171717171717,-9.09090909090909)(612.10101010101,-7.81818181818182)(627.030303030303,-8.90909090909091)(641.959595959596,-8.54545454545455)(806.181818181818,-8.90909090909091)(821.111111111111,-8.18181818181818)(850.969696969697,-7.81818181818182)(955.474747474747,-10)(955.474747474747,-7.27272727272727)(1045.05050505051,-7.27272727272727)(1119.69696969697,-10.1818181818182)(1134.62626262626,-10.1818181818182)(1224.20202020202,-7.63636363636364)(1328.70707070707,-8)(1433.21212121212,-8.90909090909091)(1433.21212121212,-9.27272727272727)
+};
+
+\addplot [
 color=white,
@@
 
+\addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=3pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (1433.21212121212,-9.27272727272727)
+};
+
 \end{axis}

### 2013-03-22 figurefactory/files/limno_bgape_pp_150_0.tex
Add batch/path planning; add summary; finish first draft

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478.00008294006,-8.54545454545455)(1478.00033175469,-8.72727272727273)(1478.00058056104,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00074642733,-9.27272727272727)(1478.00049762651,-9.45454545454546)(1478.0002488174,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(-0.000248817401863321,-7.81818181818182)(-0.000497626510092015,-7.63636363636364)(-0.000746427325097138,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000746427325097138,-7.09090909090909)(-0.000746427325097138,-6.90909090909091)(-0.000746427325097138,-6.72727272727273)(-0.000497626510092015,-6.54545454545455)(-0.000248817401863321,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.75757575757576)(1478.00020734323,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00037321366,-9.27272727272727)(1478.00012440663,-9.45454545454546)(1478,-9.54545454545455)(1463.07070707071,-9.60606060606061)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.66666666666667)(1433.21212121212,-9.79545454545455)(1425.74747474747,-9.81818181818182)(1418.28282828283,-9.84848484848485)(1403.35353535354,-9.96969696969697)(1388.42424242424,-9.96969696969697)(1384.69191919192,-10)(1373.49494949495,-10.0909090909091)(1358.56565656566,-10.0909090909091)(1347.36868686869,-10.1818181818182)(1343.63636363636,-10.2045454545455)(1328.70707070707,-10.2727272727273)(1313.77777777778,-10.3090909090909)(1298.84848484848,-10.2954545454545)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2727272727273)(1254.06060606061,-10.2121212121212)(1246.59595959596,-10.1818181818182)(1239.13131313131,-10.1666666666667)(1224.20202020202,-10.1666666666667)(1216.73737373737,-10.1818181818182)(1209.27272727273,-10.2121212121212)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.2954545454545)(1149.55555555556,-10.2727272727273)(1134.62626262626,-10.2575757575758)(1119.69696969697,-10.2878787878788)(1104.76767676768,-10.3484848484848)(1089.83838383838,-10.3484848484848)(1074.90909090909,-10.3181818181818)(1059.9797979798,-10.2878787878788)(1045.05050505051,-10.3090909090909)(1030.12121212121,-10.2954545454545)(1015.19191919192,-10.2727272727273)(1000.26262626263,-10.2727272727273)(985.333333333333,-10.2121212121212)(981.60101010101,-10.1818181818182)(970.40404040404,-10.1363636363636)(955.474747474747,-10.1060606060606)(940.545454545455,-10.0545454545455)(925.616161616162,-10.0681818181818)(914.419191919192,-10)(910.686868686869,-9.98484848484848)(895.757575757576,-9.94545454545455)(880.828282828283,-9.88636363636364)(869.631313131313,-9.81818181818182)(865.89898989899,-9.8)(858.434343434343,-9.81818181818182)(850.969696969697,-9.84090909090909)(843.505050505051,-9.81818181818182)(836.040404040404,-9.78787878787879)(821.111111111111,-9.72727272727273)(809.914141414141,-9.63636363636364)(806.181818181818,-9.59090909090909)(791.252525252525,-9.48484848484848)(787.520202020202,-9.45454545454546)(776.323232323232,-9.36363636363636)(768.858585858586,-9.27272727272727)(761.393939393939,-9.13636363636364)(758.905723905724,-9.09090909090909)(758.905723905724,-8.90909090909091)(761.393939393939,-8.81818181818182)(765.126262626263,-8.72727272727273)(768.858585858586,-8.54545454545455)(773.835016835017,-8.36363636363636)(776.323232323232,-8.31818181818182)(783.787878787879,-8.18181818181818)(791.252525252525,-8.09090909090909)(796.85101010101,-8)(806.181818181818,-7.88636363636364)(817.378787878788,-7.81818181818182)(821.111111111111,-7.78787878787879)(836.040404040404,-7.72727272727273)(847.237373737374,-7.63636363636364)(850.969696969697,-7.60606060606061)(865.89898989899,-7.48484848484849)(873.363636363636,-7.45454545454546)(880.828282828283,-7.42424242424243)(895.757575757576,-7.29545454545455)(899.489898989899,-7.27272727272727)(910.686868686869,-7.20454545454546)(925.616161616162,-7.15909090909091)(940.545454545455,-7.20454545454546)(955.474747474747,-7.24242424242424)(970.40404040404,-7.18181818181818)(981.60101010101,-7.09090909090909)(985.333333333333,-7.06060606060606)(1000.26262626263,-6.97727272727273)(1015.19191919192,-7.06060606060606)(1018.92424242424,-7.09090909090909)(1030.12121212121,-7.18181818181818)(1041.31818181818,-7.27272727272727)(1045.05050505051,-7.28787878787879)(1048.78282828283,-7.27272727272727)(1059.9797979798,-7.20454545454546)(1074.90909090909,-7.15909090909091)(1089.83838383838,-7.15909090909091)(1104.76767676768,-7.18181818181818)(1115.96464646465,-7.27272727272727)(1119.69696969697,-7.29090909090909)(1134.62626262626,-7.29545454545455)(1149.55555555556,-7.36363636363636)(1164.48484848485,-7.3030303030303)(1179.41414141414,-7.36363636363636)(1194.34343434343,-7.34090909090909)(1209.27272727273,-7.36363636363636)(1224.20202020202,-7.38636363636364)(1235.39898989899,-7.45454545454546)(1239.13131313131,-7.48484848484849)(1254.06060606061,-7.48484848484849)(1268.9898989899,-7.52272727272727)(1283.91919191919,-7.54545454545455)(1298.84848484848,-7.60606060606061)(1302.58080808081,-7.63636363636364)(1313.77777777778,-7.70454545454546)(1328.70707070707,-7.70454545454546)(1343.63636363636,-7.75)(1354.83333333333,-7.81818181818182)(1358.56565656566,-7.86363636363636)(1369.76262626263,-8)(1373.49494949495,-8.02272727272727)(1388.42424242424,-8.02272727272727)(1403.35353535354,-8.11363636363636)(1410.81818181818,-8.18181818181818)(1418.28282828283,-8.31818181818182)(1422.01515151515,-8.36363636363636)(1433.21212121212,-8.45454545454545)(1444.40909090909,-8.54545454545455)(1448.14141414141,-8.59090909090909)(1463.07070707071,-8.6969696969697)(1470.53535353535,-8.72727272727273)(1478,-8.75757575757576)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-6.45454545454545)(14.9292929292929,-6.51515151515151)(22.3939393939394,-6.54545454545455)(29.8585858585859,-6.57575757575758)(44.7878787878788,-6.63636363636364)(59.7171717171717,-6.63636363636364)(74.6464646464647,-6.6969696969697)(82.1111111111111,-6.72727272727273)(89.5757575757576,-6.75757575757576)(104.505050505051,-6.87878787878788)(111.969696969697,-6.90909090909091)(119.434343434343,-6.93939393939394)(134.363636363636,-7)(149.292929292929,-7.06060606060606)(156.757575757576,-7.09090909090909)(164.222222222222,-7.12121212121212)(179.151515151515,-7.18181818181818)(194.080808080808,-7.18181818181818)(209.010101010101,-7.18181818181818)(223.939393939394,-7.18181818181818)(238.868686868687,-7.18181818181818)(253.79797979798,-7.24242424242424)(261.262626262626,-7.27272727272727)(268.727272727273,-7.3030303030303)(283.656565656566,-7.36363636363636)(298.585858585859,-7.3030303030303)(306.050505050505,-7.27272727272727)(313.515151515152,-7.24242424242424)(328.444444444444,-7.18181818181818)(343.373737373737,-7.18181818181818)(358.30303030303,-7.18181818181818)(373.232323232323,-7.12121212121212)(380.69696969697,-7.09090909090909)(388.161616161616,-7.06060606060606)(403.090909090909,-7)(418.020202020202,-6.93939393939394)(425.484848484849,-6.90909090909091)(432.949494949495,-6.87878787878788)(447.878787878788,-6.81818181818182)(462.808080808081,-6.81818181818182)(477.737373737374,-6.81818181818182)(492.666666666667,-6.81818181818182)(507.59595959596,-6.81818181818182)(522.525252525253,-6.81818181818182)(537.454545454546,-6.87878787878788)(541.186868686869,-6.90909090909091)(552.383838383838,-7)(559.848484848485,-7.09090909090909)(567.313131313131,-7.15909090909091)(579.754208754209,-7.27272727272727)(582.242424242424,-7.29545454545455)(597.171717171717,-7.42424242424243)(600.90404040404,-7.45454545454546)(612.10101010101,-7.52272727272727)(624.542087542088,-7.63636363636364)(627.030303030303,-7.66666666666667)(636.361111111111,-7.81818181818182)(641.959595959596,-7.95454545454546)(644.447811447811,-8)(654.400673400673,-8.18181818181818)(656.888888888889,-8.27272727272727)(660.621212121212,-8.36363636363636)(668.085858585859,-8.54545454545455)(668.085858585859,-8.72727272727273)(664.353535353535,-8.90909090909091)(659.377104377104,-9.09090909090909)(656.888888888889,-9.13636363636364)(649.424242424242,-9.27272727272727)(641.959595959596,-9.36363636363636)(630.762626262626,-9.45454545454546)(627.030303030303,-9.48484848484848)(612.10101010101,-9.54545454545455)(597.171717171717,-9.54545454545455)(582.242424242424,-9.54545454545455)(567.313131313131,-9.54545454545455)(552.383838383838,-9.54545454545455)(541.186868686869,-9.45454545454546)(537.454545454546,-9.42424242424243)(522.525252525253,-9.38636363636364)(507.59595959596,-9.29545454545455)(492.666666666667,-9.29545454545455)(488.934343434343,-9.27272727272727)(477.737373737374,-9.18181818181818)(462.808080808081,-9.18181818181818)(447.878787878788,-9.12121212121212)(440.414141414141,-9.09090909090909)(432.949494949495,-9.06818181818182)(418.020202020202,-8.93939393939394)(410.555555555556,-8.90909090909091)(403.090909090909,-8.86363636363636)(388.161616161616,-8.75757575757576)(380.69696969697,-8.72727272727273)(373.232323232323,-8.68181818181818)(358.30303030303,-8.63636363636364)(343.373737373737,-8.63636363636364)(328.444444444444,-8.63636363636364)(313.515151515152,-8.63636363636364)(298.585858585859,-8.63636363636364)(283.656565656566,-8.63636363636364)(268.727272727273,-8.70454545454545)(261.262626262626,-8.72727272727273)(253.79797979798,-8.75757575757576)(238.868686868687,-8.87878787878788)(231.40404040404,-8.90909090909091)(223.939393939394,-8.93939393939394)(209.010101010101,-9)(194.080808080808,-9)(179.151515151515,-9)(164.222222222222,-9)(149.292929292929,-9)(134.363636363636,-9)(119.434343434343,-9)(104.505050505051,-8.93939393939394)(100.772727272727,-8.90909090909091)(89.5757575757576,-8.81818181818182)(82.1111111111111,-8.72727272727273)(74.6464646464647,-8.63636363636364)(67.1818181818182,-8.54545454545455)(59.7171717171717,-8.40909090909091)(57.2289562289562,-8.36363636363636)(47.2760942760943,-8.18181818181818)(44.7878787878788,-8.09090909090909)(42.2996632996633,-8)(29.8585858585859,-7.84848484848485)(26.1262626262626,-7.81818181818182)(14.9292929292929,-7.72727272727273)(0,-7.72727272727273)(-0.000124406627521346,-7.63636363636364)(-0.000373213662548569,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000373213662548569,-7.09090909090909)(-0.000373213662548569,-6.90909090909091)(-0.000373213662548569,-6.72727272727273)(-0.000124406627521346,-6.54545454545455)(0,-6.45454545454545)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1418.28282828283,-9.22727272727273)(1422.01515151515,-9.27272727272727)(1418.28282828283,-9.31818181818182)(1403.35353535354,-9.40909090909091)(1395.88888888889,-9.45454545454546)(1388.42424242424,-9.47727272727273)(1373.49494949495,-9.60606060606061)(1366.0303030303,-9.63636363636364)(1358.56565656566,-9.66666666666667)(1346.12457912458,-9.81818181818182)(1343.63636363636,-9.83636363636364)(1328.70707070707,-9.88636363636364)(1313.77777777778,-9.96969696969697)(1298.84848484848,-9.96969696969697)(1283.91919191919,-9.90909090909091)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.88636363636364)(1239.13131313131,-9.87272727272727)(1224.20202020202,-9.87272727272727)(1209.27272727273,-9.88636363636364)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.96969696969697)(1149.55555555556,-9.97727272727273)(1134.62626262626,-9.98181818181818)(1127.16161616162,-10)(1119.69696969697,-10.0151515151515)(1104.76767676768,-10.0757575757576)(1089.83838383838,-10.0757575757576)(1074.90909090909,-10.0454545454545)(1059.9797979798,-10.0151515151515)(1045.05050505051,-10.0151515151515)(1037.58585858586,-10)(1030.12121212121,-9.96969696969697)(1015.19191919192,-9.90909090909091)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.88636363636364)(970.40404040404,-9.83636363636364)(955.474747474747,-9.83333333333333)(951.742424242424,-9.81818181818182)(940.545454545455,-9.76363636363636)(925.616161616162,-9.75)(910.686868686869,-9.69090909090909)(899.489898989899,-9.63636363636364)(895.757575757576,-9.61363636363636)(880.828282828283,-9.56818181818182)(865.89898989899,-9.47272727272727)(858.434343434343,-9.45454545454546)(850.969696969697,-9.40909090909091)(845.371212121212,-9.27272727272727)(837.906565656566,-9.09090909090909)(836.040404040404,-9.04545454545455)(824.843434343434,-8.90909090909091)(824.843434343434,-8.72727272727273)(828.575757575758,-8.54545454545455)(828.575757575758,-8.36363636363636)(836.040404040404,-8.22727272727273)(839.772727272727,-8.18181818181818)(850.969696969697,-8.09090909090909)(862.166666666667,-8)(865.89898989899,-7.96969696969697)(878.340067340067,-7.81818181818182)(880.828282828283,-7.79545454545455)(895.757575757576,-7.72727272727273)(903.222222222222,-7.63636363636364)(910.686868686869,-7.56818181818182)(925.616161616162,-7.48484848484849)(940.545454545455,-7.52272727272727)(955.474747474748,-7.56818181818182)(970.40404040404,-7.56818181818182)(985.333333333333,-7.54545454545455)(1000.26262626263,-7.5)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.56818181818182)(1045.05050505051,-7.58181818181818)(1059.9797979798,-7.52272727272727)(1074.90909090909,-7.48484848484849)(1089.83838383838,-7.48484848484849)(1104.76767676768,-7.54545454545455)(1115.96464646465,-7.63636363636364)(1119.69696969697,-7.65909090909091)(1134.62626262626,-7.66666666666667)(1149.55555555556,-7.72727272727273)(1164.48484848485,-7.68181818181818)(1179.41414141414,-7.72727272727273)(1194.34343434343,-7.66666666666667)(1209.27272727273,-7.78787878787879)(1224.20202020202,-7.79545454545455)(1227.93434343434,-7.81818181818182)(1239.13131313131,-7.90909090909091)(1254.06060606061,-7.86363636363636)(1268.9898989899,-7.90909090909091)(1280.18686868687,-8)(1283.91919191919,-8.03030303030303)(1298.84848484848,-8.09090909090909)(1313.77777777778,-8.11363636363636)(1328.70707070707,-8.15151515151515)(1331.19528619529,-8.18181818181818)(1341.14814814815,-8.36363636363636)(1343.63636363636,-8.38636363636364)(1358.56565656566,-8.43181818181818)(1373.49494949495,-8.47727272727273)(1384.69191919192,-8.54545454545455)(1388.42424242424,-8.59090909090909)(1394.02272727273,-8.72727272727273)(1403.35353535354,-8.87878787878788)(1405.84175084175,-8.90909090909091)(1407.08585858586,-9.09090909090909)(1418.28282828283,-9.22727272727273)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (462.808080808081,-7.86363636363636)(464.674242424242,-7.81818181818182)(472.138888888889,-7.63636363636364)(477.737373737374,-7.54545454545455)(488.934343434343,-7.45454545454546)(492.666666666667,-7.42424242424243)(507.59595959596,-7.42424242424243)(515.060606060606,-7.45454545454546)(522.525252525253,-7.48484848484849)(537.454545454546,-7.48484848484849)(552.383838383838,-7.48484848484849)(567.313131313131,-7.56818181818182)(574.777777777778,-7.63636363636364)(582.242424242424,-7.77272727272727)(585.974747474747,-7.81818181818182)(593.439393939394,-8)(589.707070707071,-8.18181818181818)(589.707070707071,-8.36363636363636)(593.439393939394,-8.54545454545455)(589.707070707071,-8.72727272727273)(582.242424242424,-8.75)(567.313131313131,-8.84090909090909)(552.383838383838,-8.88636363636364)(548.651515151515,-8.90909090909091)(537.454545454546,-8.97727272727273)(522.525252525253,-8.97727272727273)(507.59595959596,-8.92727272727273)(503.863636363636,-8.90909090909091)(492.666666666667,-8.77272727272727)(485.20202020202,-8.72727272727273)(477.737373737374,-8.6969696969697)(462.808080808081,-8.59090909090909)(459.075757575758,-8.54545454545455)(455.343434343434,-8.36363636363636)(455.343434343434,-8.18181818181818)(455.343434343434,-8)(462.808080808081,-7.86363636363636)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (134.363636363636,-7.95454545454546)(149.292929292929,-7.95454545454546)(164.222222222222,-7.90909090909091)(179.151515151515,-7.96969696969697)(186.616161616162,-8)(194.080808080808,-8.09090909090909)(201.545454545455,-8.18181818181818)(194.080808080808,-8.22727272727273)(179.151515151515,-8.31818181818182)(164.222222222222,-8.31818181818182)(149.292929292929,-8.27272727272727)(134.363636363636,-8.22727272727273)(130.631313131313,-8.18181818181818)(130.631313131313,-8)(134.363636363636,-7.95454545454546)};

\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0)(1268.9898989899,-8.18181818181818)(1254.06060606061,-9.27272727272727)(1164.48484848485,-8.54545454545455)(1149.55555555556,-8.18181818181818)(1134.62626262626,-7.81818181818182)(1119.69696969697,-8.90909090909091)(1104.76767676768,-7.63636363636364)(1074.90909090909,-7.45454545454546)(1074.90909090909,-9.09090909090909)(1059.9797979798,-9.09090909090909)(1030.12121212121,-7.27272727272727)(1015.19191919192,-7.27272727272727)(970.40404040404,-9.27272727272727)(910.686868686869,-7.09090909090909)(880.828282828283,-9.09090909090909)(865.89898989899,-9.09090909090909)(865.89898989899,-7.09090909090909)(791.252525252525,-8.90909090909091)(791.252525252525,-7.27272727272727)(761.393939393939,-7.27272727272727)(746.464646464646,-8.72727272727273)(716.606060606061,-8.54545454545455)(686.747474747475,-7.63636363636364)(671.818181818182,-8.18181818181818)(656.888888888889,-8)(597.171717171717,-7.09090909090909)(537.454545454546,-8.72727272727273)(223.939393939394,-8.36363636363636)(194.080808080808,-7.09090909090909)(0,-9.45454545454546)(209.010101010101,-8.18181818181818)(268.727272727273,-8.72727272727273)(298.585858585859,-7.81818181818182)(313.515151515152,-7.81818181818182)(313.515151515152,-8.90909090909091)(373.232323232323,-9.09090909090909)(388.161616161616,-9.09090909090909)(418.020202020202,-7.63636363636364)(492.666666666667,-9.27272727272727)(522.525252525253,-9.27272727272727)(522.525252525253,-7.81818181818182)(567.313131313131,-8)(567.313131313131,-9.09090909090909)(836.040404040404,-8.36363636363636)(836.040404040404,-9.63636363636364)(850.969696969697,-9.81818181818182)(865.89898989899,-8)(940.545454545455,-10.1818181818182)(955.474747474747,-10.1818181818182)(1074.90909090909,-10.3636363636364)(1209.27272727273,-7.63636363636364)(1224.20202020202,-10.1818181818182)(1239.13131313131,-10.1818181818182)(1283.91919191919,-7.81818181818182)(1313.77777777778,-10)(1358.56565656566,-9.81818181818182)(1358.56565656566,-8.18181818181818)(1403.35353535354,-8.72727272727273)(1403.35353535354,-9.27272727272727)(1418.28282828283,-8.90909090909091)(1433.21212121212,-9.09090909090909)(1418.28282828283,-9.45454545454546)(1403.35353535354,-8.54545454545455)(1388.42424242424,-8.36363636363636)(1373.49494949495,-9.81818181818182)(1328.70707070707,-10)(1298.84848484848,-7.81818181818182)(1239.13131313131,-7.63636363636364)(1149.55555555556,-7.45454545454546)(1134.62626262626,-7.45454545454546)(1104.76767676768,-10.1818181818182)(1089.83838383838,-10.1818181818182)(1074.90909090909,-10.1818181818182)(925.616161616162,-7.45454545454546)(925.616161616162,-10)(880.828282828283,-9.81818181818182)(865.89898989899,-7.81818181818182)(821.111111111111,-9.27272727272727)(612.10101010101,-8.72727272727273)(597.171717171717,-8.90909090909091)(567.313131313131,-7.63636363636364)(477.737373737374,-7.63636363636364)(418.020202020202,-8.54545454545455)(388.161616161616,-8.36363636363636)(388.161616161616,-8.18181818181818)(268.727272727273,-8)(194.080808080808,-7.81818181818182)(164.222222222222,-8)(164.222222222222,-8.18181818181818)(149.292929292929,-8)(134.363636363636,-7.81818181818182)(119.434343434343,-8)(119.434343434343,-8.18181818181818)(134.363636363636,-8.36363636363636)(164.222222222222,-8.54545454545455)(238.868686868687,-7.81818181818182)(253.79797979798,-8.36363636363636)(403.090909090909,-8)(403.090909090909,-8.36363636363636)(447.878787878788,-8.72727272727273)(492.666666666667,-7.45454545454546)(507.59595959596,-7.45454545454546)(507.59595959596,-9.09090909090909)(552.383838383838,-7.45454545454546)(597.171717171717,-9.09090909090909)(612.10101010101,-7.81818181818182)(627.030303030303,-8.90909090909091)(641.959595959596,-8.54545454545455)(806.181818181818,-8.90909090909091)(821.111111111111,-8.18181818181818)(850.969696969697,-7.81818181818182)(955.474747474747,-10)(955.474747474747,-7.27272727272727)(1045.05050505051,-7.27272727272727)(1119.69696969697,-10.1818181818182)(1134.62626262626,-10.1818181818182)(1224.20202020202,-7.63636363636364)(1328.70707070707,-8)(1433.21212121212,-8.90909090909091) 
};

\addplot [
color=lime,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1433.21212121212,-9.27272727272727)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-22 figurefactory/files/limno_bgape_pp_150_1.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_150_0.tex
@@
 \addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=1.6pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (1433.21212121212,-9.27272727272727)(1418.28282828283,-8.72727272727273)(1388.42424242424,-9.81818181818182)(1298.84848484848,-10)(1194.34343434343,-7.63636363636364)(1104.76767676768,-7.45454545454546)(910.686868686869,-7.45454545454546)(895.757575757576,-9.81818181818182)(836.040404040404,-9.45454545454546)(806.181818181818,-9.09090909090909)(806.181818181818,-8.36363636363636)(627.030303030303,-8)(582.242424242424,-9.09090909090909)(552.383838383838,-7.27272727272727)(537.454545454546,-7.27272727272727)(507.59595959596,-7.27272727272727)(492.666666666667,-7.27272727272727)(492.666666666667,-9.09090909090909)(432.949494949495,-8.72727272727273)(432.949494949495,-7.63636363636364)(253.79797979798,-7.81818181818182)(223.939393939394,-8.54545454545455)(179.151515151515,-8.72727272727273)(164.222222222222,-7.63636363636364)(149.292929292929,-7.63636363636364)(134.363636363636,-7.63636363636364)(134.363636363636,-8.54545454545455)(119.434343434343,-8.54545454545455)(104.505050505051,-7.81818181818182)(89.5757575757576,-8)(89.5757575757576,-8.18181818181818)
+};
+
+\addplot [
 color=lime,

### 2013-03-22 figurefactory/files/limno_bgape_pp_150_2.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_150_1.tex
@@
 \addplot [
+draw=red!50!white,
+line width=0.6pt,
+forget plot
+]
+coordinates{
+ (1433.21212121212,-9.27272727272727)(1418.28282828283,-8.72727272727273)(1388.42424242424,-9.81818181818182)(1298.84848484848,-10)(1194.34343434343,-7.63636363636364)(1104.76767676768,-7.45454545454546)(910.686868686869,-7.45454545454546)(895.757575757576,-9.81818181818182)(836.040404040404,-9.45454545454546)(806.181818181818,-9.09090909090909)(806.181818181818,-8.36363636363636)(627.030303030303,-8)(582.242424242424,-9.09090909090909)(552.383838383838,-7.27272727272727)(537.454545454546,-7.27272727272727)(507.59595959596,-7.27272727272727)(492.666666666667,-7.27272727272727)(492.666666666667,-9.09090909090909)(432.949494949495,-8.72727272727273)(432.949494949495,-7.63636363636364)(253.79797979798,-7.81818181818182)(223.939393939394,-8.54545454545455)(179.151515151515,-8.72727272727273)(164.222222222222,-7.63636363636364)(149.292929292929,-7.63636363636364)(134.363636363636,-7.63636363636364)(134.363636363636,-8.54545454545455)(119.434343434343,-8.54545454545455)(104.505050505051,-7.81818181818182)(89.5757575757576,-8)(89.5757575757576,-8.18181818181818)
+};
+
+\addplot [
 color=white,
@@
 
+\addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=3pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (89.5757575757576,-8.18181818181818)
+};
+
 \end{axis}

### 2013-03-22 figurefactory/files/limno_bgape_pp_180_0.tex
Add batch/path planning; add summary; finish first draft

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478.0002488174,-8.72727272727273)(1478.00049762651,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00074642733,-9.27272727272727)(1478.00049762651,-9.45454545454546)(1478.0002488174,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(-0.000248817401863321,-7.63636363636364)(-0.000497626510092015,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000746427325097138,-7.09090909090909)(-0.000746427325097138,-6.90909090909091)(-0.00066349464153746,-6.72727272727273)(-0.0004146910621731,-6.54545454545455)(-0.000165879189445939,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-8.81818181818182)(1478.00012440663,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00037321366,-9.27272727272727)(1478.00012440663,-9.45454545454546)(1478,-9.54545454545455)(1463.07070707071,-9.60606060606061)(1459.33838383838,-9.63636363636364)(1448.14141414141,-9.70454545454546)(1435.70033670034,-9.81818181818182)(1433.21212121212,-9.84090909090909)(1418.28282828283,-9.90909090909091)(1405.84175084175,-10)(1403.35353535354,-10.0227272727273)(1388.42424242424,-10.030303030303)(1373.49494949495,-10.1136363636364)(1358.56565656566,-10.1590909090909)(1354.83333333333,-10.1818181818182)(1343.63636363636,-10.2363636363636)(1328.70707070707,-10.2878787878788)(1313.77777777778,-10.3181818181818)(1298.84848484848,-10.3090909090909)(1283.91919191919,-10.2954545454545)(1268.9898989899,-10.2727272727273)(1254.06060606061,-10.2121212121212)(1246.59595959596,-10.1818181818182)(1239.13131313131,-10.1666666666667)(1224.20202020202,-10.1666666666667)(1216.73737373737,-10.1818181818182)(1209.27272727273,-10.2121212121212)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.2954545454545)(1149.55555555556,-10.2727272727273)(1134.62626262626,-10.2575757575758)(1119.69696969697,-10.2878787878788)(1104.76767676768,-10.3484848484848)(1089.83838383838,-10.3484848484848)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.2575757575758)(1045.05050505051,-10.2878787878788)(1030.12121212121,-10.3090909090909)(1015.19191919192,-10.2954545454545)(1000.26262626263,-10.2727272727273)(985.333333333333,-10.2121212121212)(981.60101010101,-10.1818181818182)(970.40404040404,-10.1363636363636)(955.474747474747,-10.1060606060606)(940.545454545455,-10.0545454545455)(925.616161616162,-10.0227272727273)(918.151515151515,-10)(910.686868686869,-9.98484848484848)(895.757575757576,-9.95454545454546)(880.828282828283,-9.90909090909091)(871.497474747475,-9.81818181818182)(865.89898989899,-9.77272727272727)(850.969696969697,-9.77272727272727)(836.040404040404,-9.70454545454546)(821.111111111111,-9.66666666666667)(819.244949494949,-9.63636363636364)(810.660606060606,-9.45454545454546)(806.181818181818,-9.40909090909091)(791.252525252525,-9.4)(776.323232323232,-9.29545454545455)(773.835016835017,-9.27272727272727)(763.882154882155,-9.09090909090909)(761.393939393939,-9)(758.905723905724,-8.90909090909091)(761.393939393939,-8.81818181818182)(763.882154882155,-8.72727272727273)(766.992424242424,-8.54545454545455)(773.835016835017,-8.36363636363636)(776.323232323232,-8.31818181818182)(781.921717171717,-8.18181818181818)(791.252525252525,-8.06818181818182)(798.717171717172,-8)(806.181818181818,-7.93181818181818)(818.622895622896,-7.81818181818182)(821.111111111111,-7.79545454545455)(836.040404040404,-7.72727272727273)(848.481481481482,-7.63636363636364)(850.969696969697,-7.60606060606061)(863.410774410775,-7.45454545454546)(865.89898989899,-7.43181818181818)(880.828282828283,-7.38636363636364)(895.757575757576,-7.36363636363636)(910.686868686869,-7.29090909090909)(918.151515151515,-7.27272727272727)(925.616161616162,-7.24242424242424)(940.545454545455,-7.20454545454546)(955.474747474747,-7.24242424242424)(970.40404040404,-7.24242424242424)(985.333333333333,-7.24242424242424)(1000.26262626263,-7.18181818181818)(1015.19191919192,-7.24242424242424)(1030.12121212121,-7.24242424242424)(1037.58585858586,-7.27272727272727)(1045.05050505051,-7.28787878787879)(1048.78282828283,-7.27272727272727)(1059.9797979798,-7.20454545454546)(1074.90909090909,-7.15909090909091)(1089.83838383838,-7.18181818181818)(1102.27946127946,-7.27272727272727)(1104.76767676768,-7.28787878787879)(1119.69696969697,-7.36363636363636)(1134.62626262626,-7.38636363636364)(1149.55555555556,-7.36363636363636)(1164.48484848485,-7.36363636363636)(1171.94949494949,-7.45454545454546)(1179.41414141414,-7.5)(1194.34343434343,-7.5)(1209.27272727273,-7.54545454545455)(1224.20202020202,-7.47727272727273)(1239.13131313131,-7.54545454545455)(1254.06060606061,-7.5)(1268.9898989899,-7.60606060606061)(1272.72222222222,-7.63636363636364)(1283.91919191919,-7.70454545454546)(1298.84848484848,-7.72727272727273)(1313.77777777778,-7.75)(1328.70707070707,-7.75)(1343.63636363636,-7.79545454545455)(1346.12457912458,-7.81818181818182)(1352.96717171717,-8)(1358.56565656566,-8.06818181818182)(1373.49494949495,-8.11363636363636)(1388.42424242424,-8.15909090909091)(1403.35353535354,-8.15909090909091)(1405.84175084175,-8.18181818181818)(1415.79461279461,-8.36363636363636)(1418.28282828283,-8.38181818181818)(1433.21212121212,-8.43181818181818)(1442.54292929293,-8.54545454545455)(1448.14141414141,-8.68181818181818)(1455.60606060606,-8.72727272727273)(1463.07070707071,-8.75757575757576)(1478,-8.81818181818182)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.20454545454546)(1440.67676767677,-9.27272727272727)(1435.07828282828,-9.45454545454546)(1433.21212121212,-9.47727272727273)(1418.28282828283,-9.61363636363636)(1415.79461279461,-9.63636363636364)(1403.35353535354,-9.72727272727273)(1388.42424242424,-9.70454545454546)(1373.49494949495,-9.78787878787879)(1366.0303030303,-9.81818181818182)(1358.56565656566,-9.83333333333333)(1343.63636363636,-9.94545454545455)(1332.43939393939,-10)(1328.70707070707,-10.0151515151515)(1313.77777777778,-10.0454545454545)(1298.84848484848,-10.0151515151515)(1291.38383838384,-10)(1283.91919191919,-9.96969696969697)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.88636363636364)(1239.13131313131,-9.87272727272727)(1224.20202020202,-9.87272727272727)(1209.27272727273,-9.88636363636364)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.96969696969697)(1149.55555555556,-9.97727272727273)(1134.62626262626,-9.98181818181818)(1127.16161616162,-10)(1119.69696969697,-10.0151515151515)(1104.76767676768,-10.0757575757576)(1089.83838383838,-10.0757575757576)(1074.90909090909,-10.0151515151515)(1067.44444444444,-10)(1059.9797979798,-9.98181818181818)(1052.51515151515,-10)(1045.05050505051,-10.0151515151515)(1030.12121212121,-10.0151515151515)(1022.65656565657,-10)(1015.19191919192,-9.96969696969697)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.88636363636364)(970.40404040404,-9.83636363636364)(955.474747474747,-9.83333333333333)(951.742424242424,-9.81818181818182)(940.545454545455,-9.76363636363636)(925.616161616162,-9.72727272727273)(910.686868686869,-9.71212121212121)(895.757575757576,-9.68181818181818)(884.560606060606,-9.63636363636364)(880.828282828283,-9.61363636363636)(865.89898989899,-9.5)(850.969696969697,-9.5)(846.490909090909,-9.45454545454546)(836.040404040404,-9.29545454545455)(832.308080808081,-9.27272727272727)(821.111111111111,-9.18181818181818)(813.646464646465,-9.09090909090909)(806.181818181818,-9)(798.717171717172,-8.90909090909091)(806.181818181818,-8.77272727272727)(808.670033670034,-8.72727272727273)(806.181818181818,-8.63636363636364)(803.693602693603,-8.54545454545455)(806.181818181818,-8.45454545454545)(808.670033670034,-8.36363636363636)(815.512626262626,-8.18181818181818)(821.111111111111,-8.12727272727273)(836.040404040404,-8.05454545454545)(843.505050505051,-8)(850.969696969697,-7.93181818181818)(863.410774410775,-7.81818181818182)(865.89898989899,-7.8)(880.828282828283,-7.70454545454546)(895.757575757576,-7.65909090909091)(903.222222222222,-7.63636363636364)(910.686868686869,-7.61818181818182)(925.616161616162,-7.56818181818182)(940.545454545455,-7.52272727272727)(955.474747474748,-7.56818181818182)(970.40404040404,-7.56818181818182)(985.333333333333,-7.56818181818182)(1000.26262626263,-7.54545454545455)(1015.19191919192,-7.56818181818182)(1030.12121212121,-7.56818181818182)(1045.05050505051,-7.58181818181818)(1059.9797979798,-7.52272727272727)(1074.90909090909,-7.48484848484849)(1089.83838383838,-7.47727272727273)(1104.76767676768,-7.58181818181818)(1115.96464646465,-7.63636363636364)(1119.69696969697,-7.65909090909091)(1134.62626262626,-7.70454545454546)(1149.55555555556,-7.72727272727273)(1164.48484848485,-7.72727272727273)(1179.41414141414,-7.8)(1194.34343434343,-7.77272727272727)(1205.5404040404,-7.81818181818182)(1209.27272727273,-7.84090909090909)(1216.73737373737,-7.81818181818182)(1224.20202020202,-7.8030303030303)(1227.93434343434,-7.81818181818182)(1239.13131313131,-7.90909090909091)(1254.06060606061,-7.95454545454546)(1268.9898989899,-7.97727272727273)(1272.72222222222,-8)(1283.91919191919,-8.06818181818182)(1298.84848484848,-8.09090909090909)(1313.77777777778,-8.11363636363636)(1328.70707070707,-8.15909090909091)(1331.19528619529,-8.18181818181818)(1341.14814814815,-8.36363636363636)(1343.63636363636,-8.38636363636364)(1358.56565656566,-8.45454545454545)(1373.49494949495,-8.49090909090909)(1384.69191919192,-8.54545454545455)(1388.42424242424,-8.59090909090909)(1395.88888888889,-8.72727272727273)(1403.35353535354,-8.79545454545455)(1415.79461279461,-8.90909090909091)(1418.28282828283,-9)(1420.77104377104,-9.09090909090909)(1433.21212121212,-9.20454545454546)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-6.51515151515151)(7.46464646464646,-6.54545454545455)(14.9292929292929,-6.57575757575758)(29.8585858585859,-6.63636363636364)(44.7878787878788,-6.6969696969697)(52.2525252525253,-6.72727272727273)(59.7171717171717,-6.75757575757576)(74.6464646464647,-6.81818181818182)(89.5757575757576,-6.87878787878788)(97.040404040404,-6.90909090909091)(104.505050505051,-6.93939393939394)(119.434343434343,-7.06060606060606)(126.89898989899,-7.09090909090909)(134.363636363636,-7.12121212121212)(149.292929292929,-7.18181818181818)(164.222222222222,-7.24242424242424)(171.686868686869,-7.27272727272727)(179.151515151515,-7.36363636363636)(194.080808080808,-7.40909090909091)(209.010101010101,-7.36363636363636)(223.939393939394,-7.36363636363636)(238.868686868687,-7.42424242424243)(246.333333333333,-7.45454545454546)(253.79797979798,-7.48484848484849)(268.727272727273,-7.59090909090909)(283.656565656566,-7.59090909090909)(287.388888888889,-7.63636363636364)(298.585858585859,-7.72727272727273)(313.515151515152,-7.78787878787879)(328.444444444444,-7.78787878787879)(343.373737373737,-7.66666666666667)(350.838383838384,-7.63636363636364)(358.30303030303,-7.60606060606061)(373.232323232323,-7.48484848484849)(376.964646464646,-7.45454545454546)(388.161616161616,-7.36363636363636)(395.626262626263,-7.27272727272727)(403.090909090909,-7.18181818181818)(414.287878787879,-7.09090909090909)(418.020202020202,-7.06060606060606)(432.949494949495,-6.93939393939394)(440.414141414141,-6.90909090909091)(447.878787878788,-6.87878787878788)(462.808080808081,-6.81818181818182)(477.737373737374,-6.81818181818182)(492.666666666667,-6.81818181818182)(507.59595959596,-6.79545454545455)(522.525252525253,-6.79545454545455)(537.454545454546,-6.84090909090909)(544.919191919192,-6.90909090909091)(552.383838383838,-6.97727272727273)(561.714646464646,-7.09090909090909)(567.313131313131,-7.15909090909091)(579.754208754209,-7.27272727272727)(582.242424242424,-7.29090909090909)(597.171717171717,-7.34090909090909)(609.612794612795,-7.45454545454546)(612.10101010101,-7.47727272727273)(625.164141414141,-7.63636363636364)(627.030303030303,-7.68181818181818)(632.628787878788,-7.81818181818182)(641.959595959596,-7.96969696969697)(644.447811447811,-8)(655.022727272727,-8.18181818181818)(655.644781144781,-8.36363636363636)(656.888888888889,-8.45454545454545)(660.621212121212,-8.54545454545455)(660.621212121212,-8.72727272727273)(659.377104377104,-8.90909090909091)(656.888888888889,-8.95454545454546)(641.959595959596,-9.06060606060606)(634.494949494949,-9.09090909090909)(627.030303030303,-9.18181818181818)(612.10101010101,-9.22727272727273)(609.612794612795,-9.27272727272727)(597.171717171717,-9.42424242424243)(589.707070707071,-9.45454545454546)(582.242424242424,-9.48484848484848)(567.313131313131,-9.54545454545455)(552.383838383838,-9.54545454545455)(541.186868686869,-9.45454545454546)(537.454545454546,-9.42424242424243)(522.525252525253,-9.38636363636364)(507.59595959596,-9.32727272727273)(492.666666666667,-9.32727272727273)(481.469696969697,-9.27272727272727)(477.737373737374,-9.25)(462.808080808081,-9.20454545454546)(447.878787878788,-9.15909090909091)(440.414141414141,-9.09090909090909)(432.949494949495,-9)(425.484848484849,-8.90909090909091)(418.020202020202,-8.77272727272727)(410.555555555556,-8.72727272727273)(403.090909090909,-8.63636363636364)(395.626262626263,-8.54545454545455)(403.090909090909,-8.45454545454545)(406.823232323232,-8.36363636363636)(403.090909090909,-8.31818181818182)(388.161616161616,-8.31818181818182)(380.69696969697,-8.36363636363636)(373.232323232323,-8.40909090909091)(358.30303030303,-8.45454545454545)(343.373737373737,-8.45454545454545)(328.444444444444,-8.45454545454545)(313.515151515152,-8.45454545454545)(298.585858585859,-8.51515151515152)(291.121212121212,-8.54545454545455)(283.656565656566,-8.57575757575757)(268.727272727273,-8.70454545454545)(264.99494949495,-8.72727272727273)(253.79797979798,-8.79545454545455)(238.868686868687,-8.87878787878788)(231.40404040404,-8.90909090909091)(223.939393939394,-8.93939393939394)(209.010101010101,-9)(194.080808080808,-8.95454545454546)(186.616161616162,-8.90909090909091)(179.151515151515,-8.88636363636364)(164.222222222222,-8.88636363636364)(156.757575757576,-8.90909090909091)(149.292929292929,-8.95454545454546)(134.363636363636,-8.93939393939394)(126.89898989899,-8.90909090909091)(119.434343434343,-8.89090909090909)(104.505050505051,-8.79545454545455)(97.040404040404,-8.72727272727273)(89.5757575757576,-8.59090909090909)(85.8434343434344,-8.54545454545455)(74.6464646464647,-8.40909090909091)(70.9141414141414,-8.36363636363636)(59.7171717171717,-8.22727272727273)(57.2289562289562,-8.18181818181818)(47.2760942760943,-8)(44.7878787878788,-7.95454545454546)(37.3232323232323,-7.81818181818182)(29.8585858585859,-7.72727272727273)(18.6616161616162,-7.63636363636364)(14.9292929292929,-7.60606060606061)(0,-7.54545454545455)(-0.000124406627521346,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000373213662548569,-7.09090909090909)(-0.000373213662548569,-6.90909090909091)(-0.00029027890567471,-6.72727272727273)(-4.14691062186359e-05,-6.54545454545455)(0,-6.51515151515151)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (462.808080808081,-7.84848484848485)(464.674242424242,-7.81818181818182)(472.138888888889,-7.63636363636364)(477.737373737374,-7.58181818181818)(492.666666666667,-7.53030303030303)(507.59595959596,-7.47272727272727)(511.328282828283,-7.45454545454546)(522.525252525253,-7.31818181818182)(526.257575757576,-7.27272727272727)(537.454545454546,-7.20454545454546)(543.05303030303,-7.27272727272727)(552.383838383838,-7.38636363636364)(559.848484848485,-7.45454545454546)(567.313131313131,-7.52272727272727)(582.242424242424,-7.61818181818182)(585.974747474747,-7.63636363636364)(597.171717171717,-7.77272727272727)(598.664646464646,-7.81818181818182)(604.636363636364,-8)(608.368686868687,-8.18181818181818)(612.10101010101,-8.22727272727273)(617.699494949495,-8.36363636363636)(614.589225589226,-8.54545454545455)(612.10101010101,-8.57575757575757)(597.171717171717,-8.68181818181818)(593.439393939394,-8.72727272727273)(582.242424242424,-8.79545454545455)(567.313131313131,-8.87878787878788)(552.383838383838,-8.88636363636364)(548.651515151515,-8.90909090909091)(537.454545454546,-8.97727272727273)(522.525252525253,-9.02272727272727)(507.59595959596,-9)(492.666666666667,-8.96363636363636)(481.469696969697,-8.90909090909091)(477.737373737374,-8.86363636363636)(462.808080808081,-8.77272727272727)(460.319865319865,-8.72727272727273)(457.209595959596,-8.54545454545455)(450.367003367003,-8.36363636363636)(450.367003367003,-8.18181818181818)(450.367003367003,-8)(462.808080808081,-7.84848484848485)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (134.363636363636,-7.90909090909091)(149.292929292929,-7.93181818181818)(164.222222222222,-7.93181818181818)(179.151515151515,-7.98181818181818)(186.616161616162,-8)(194.080808080808,-8.03030303030303)(209.010101010101,-8.15151515151515)(211.498316498317,-8.18181818181818)(209.010101010101,-8.22727272727273)(197.813131313131,-8.36363636363636)(194.080808080808,-8.38636363636364)(179.151515151515,-8.45454545454545)(164.222222222222,-8.41818181818182)(149.292929292929,-8.47727272727273)(134.363636363636,-8.45454545454545)(123.166666666667,-8.36363636363636)(126.89898989899,-8.18181818181818)(126.89898989899,-8)(134.363636363636,-7.90909090909091)};

\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0)(1268.9898989899,-8.18181818181818)(1254.06060606061,-9.27272727272727)(1164.48484848485,-8.54545454545455)(1149.55555555556,-8.18181818181818)(1134.62626262626,-7.81818181818182)(1119.69696969697,-8.90909090909091)(1104.76767676768,-7.63636363636364)(1074.90909090909,-7.45454545454546)(1074.90909090909,-9.09090909090909)(1059.9797979798,-9.09090909090909)(1030.12121212121,-7.27272727272727)(1015.19191919192,-7.27272727272727)(970.40404040404,-9.27272727272727)(910.686868686869,-7.09090909090909)(880.828282828283,-9.09090909090909)(865.89898989899,-9.09090909090909)(865.89898989899,-7.09090909090909)(791.252525252525,-8.90909090909091)(791.252525252525,-7.27272727272727)(761.393939393939,-7.27272727272727)(746.464646464646,-8.72727272727273)(716.606060606061,-8.54545454545455)(686.747474747475,-7.63636363636364)(671.818181818182,-8.18181818181818)(656.888888888889,-8)(597.171717171717,-7.09090909090909)(537.454545454546,-8.72727272727273)(223.939393939394,-8.36363636363636)(194.080808080808,-7.09090909090909)(0,-9.45454545454546)(209.010101010101,-8.18181818181818)(268.727272727273,-8.72727272727273)(298.585858585859,-7.81818181818182)(313.515151515152,-7.81818181818182)(313.515151515152,-8.90909090909091)(373.232323232323,-9.09090909090909)(388.161616161616,-9.09090909090909)(418.020202020202,-7.63636363636364)(492.666666666667,-9.27272727272727)(522.525252525253,-9.27272727272727)(522.525252525253,-7.81818181818182)(567.313131313131,-8)(567.313131313131,-9.09090909090909)(836.040404040404,-8.36363636363636)(836.040404040404,-9.63636363636364)(850.969696969697,-9.81818181818182)(865.89898989899,-8)(940.545454545455,-10.1818181818182)(955.474747474747,-10.1818181818182)(1074.90909090909,-10.3636363636364)(1209.27272727273,-7.63636363636364)(1224.20202020202,-10.1818181818182)(1239.13131313131,-10.1818181818182)(1283.91919191919,-7.81818181818182)(1313.77777777778,-10)(1358.56565656566,-9.81818181818182)(1358.56565656566,-8.18181818181818)(1403.35353535354,-8.72727272727273)(1403.35353535354,-9.27272727272727)(1418.28282828283,-8.90909090909091)(1433.21212121212,-9.09090909090909)(1418.28282828283,-9.45454545454546)(1403.35353535354,-8.54545454545455)(1388.42424242424,-8.36363636363636)(1373.49494949495,-9.81818181818182)(1328.70707070707,-10)(1298.84848484848,-7.81818181818182)(1239.13131313131,-7.63636363636364)(1149.55555555556,-7.45454545454546)(1134.62626262626,-7.45454545454546)(1104.76767676768,-10.1818181818182)(1089.83838383838,-10.1818181818182)(1074.90909090909,-10.1818181818182)(925.616161616162,-7.45454545454546)(925.616161616162,-10)(880.828282828283,-9.81818181818182)(865.89898989899,-7.81818181818182)(821.111111111111,-9.27272727272727)(612.10101010101,-8.72727272727273)(597.171717171717,-8.90909090909091)(567.313131313131,-7.63636363636364)(477.737373737374,-7.63636363636364)(418.020202020202,-8.54545454545455)(388.161616161616,-8.36363636363636)(388.161616161616,-8.18181818181818)(268.727272727273,-8)(194.080808080808,-7.81818181818182)(164.222222222222,-8)(164.222222222222,-8.18181818181818)(149.292929292929,-8)(134.363636363636,-7.81818181818182)(119.434343434343,-8)(119.434343434343,-8.18181818181818)(134.363636363636,-8.36363636363636)(164.222222222222,-8.54545454545455)(238.868686868687,-7.81818181818182)(253.79797979798,-8.36363636363636)(403.090909090909,-8)(403.090909090909,-8.36363636363636)(447.878787878788,-8.72727272727273)(492.666666666667,-7.45454545454546)(507.59595959596,-7.45454545454546)(507.59595959596,-9.09090909090909)(552.383838383838,-7.45454545454546)(597.171717171717,-9.09090909090909)(612.10101010101,-7.81818181818182)(627.030303030303,-8.90909090909091)(641.959595959596,-8.54545454545455)(806.181818181818,-8.90909090909091)(821.111111111111,-8.18181818181818)(850.969696969697,-7.81818181818182)(955.474747474747,-10)(955.474747474747,-7.27272727272727)(1045.05050505051,-7.27272727272727)(1119.69696969697,-10.1818181818182)(1134.62626262626,-10.1818181818182)(1224.20202020202,-7.63636363636364)(1328.70707070707,-8)(1433.21212121212,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1418.28282828283,-8.72727272727273)(1388.42424242424,-9.81818181818182)(1298.84848484848,-10)(1194.34343434343,-7.63636363636364)(1104.76767676768,-7.45454545454546)(910.686868686869,-7.45454545454546)(895.757575757576,-9.81818181818182)(836.040404040404,-9.45454545454546)(806.181818181818,-9.09090909090909)(806.181818181818,-8.36363636363636)(627.030303030303,-8)(582.242424242424,-9.09090909090909)(552.383838383838,-7.27272727272727)(537.454545454546,-7.27272727272727)(507.59595959596,-7.27272727272727)(492.666666666667,-7.27272727272727)(492.666666666667,-9.09090909090909)(432.949494949495,-8.72727272727273)(432.949494949495,-7.63636363636364)(253.79797979798,-7.81818181818182)(223.939393939394,-8.54545454545455)(179.151515151515,-8.72727272727273)(164.222222222222,-7.63636363636364)(149.292929292929,-7.63636363636364)(134.363636363636,-7.63636363636364)(134.363636363636,-8.54545454545455)(119.434343434343,-8.54545454545455)(104.505050505051,-7.81818181818182)(89.5757575757576,-8) 
};

\addplot [
color=lime,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (89.5757575757576,-8.18181818181818)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-22 figurefactory/files/limno_bgape_pp_180_1.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_180_0.tex
@@
 \addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=1.6pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (89.5757575757576,-8.18181818181818)(104.505050505051,-8.36363636363636)(164.222222222222,-8.72727272727273)(179.151515151515,-7.63636363636364)(238.868686868687,-8.54545454545455)(268.727272727273,-8.18181818181818)(403.090909090909,-8.18181818181818)(418.020202020202,-7.81818181818182)(462.808080808081,-8.90909090909091)(477.737373737374,-7.27272727272727)(522.525252525253,-7.09090909090909)(567.313131313131,-7.27272727272727)(597.171717171717,-7.45454545454546)(612.10101010101,-8.90909090909091)(627.030303030303,-8.54545454545455)(627.030303030303,-8.36363636363636)(627.030303030303,-8.18181818181818)(791.252525252525,-8.72727272727273)(791.252525252525,-9.09090909090909)(821.111111111111,-9.45454545454546)(836.040404040404,-8)(850.969696969697,-9.63636363636364)(880.828282828283,-7.63636363636364)(1000.26262626263,-7.27272727272727)(1059.9797979798,-10.1818181818182)(1119.69696969697,-7.45454545454546)(1268.9898989899,-7.81818181818182)(1343.63636363636,-10)(1373.49494949495,-8.18181818181818)(1418.28282828283,-9.63636363636364)(1433.21212121212,-9.45454545454546)
+};
+
+\addplot [
 color=lime,

### 2013-03-22 figurefactory/files/limno_bgape_pp_180_2.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_180_1.tex
@@
 \addplot [
+draw=red!50!white,
+line width=0.6pt,
+forget plot
+]
+coordinates{
+ (89.5757575757576,-8.18181818181818)(104.505050505051,-8.36363636363636)(164.222222222222,-8.72727272727273)(179.151515151515,-7.63636363636364)(238.868686868687,-8.54545454545455)(268.727272727273,-8.18181818181818)(403.090909090909,-8.18181818181818)(418.020202020202,-7.81818181818182)(462.808080808081,-8.90909090909091)(477.737373737374,-7.27272727272727)(522.525252525253,-7.09090909090909)(567.313131313131,-7.27272727272727)(597.171717171717,-7.45454545454546)(612.10101010101,-8.90909090909091)(627.030303030303,-8.54545454545455)(627.030303030303,-8.36363636363636)(627.030303030303,-8.18181818181818)(791.252525252525,-8.72727272727273)(791.252525252525,-9.09090909090909)(821.111111111111,-9.45454545454546)(836.040404040404,-8)(850.969696969697,-9.63636363636364)(880.828282828283,-7.63636363636364)(1000.26262626263,-7.27272727272727)(1059.9797979798,-10.1818181818182)(1119.69696969697,-7.45454545454546)(1268.9898989899,-7.81818181818182)(1343.63636363636,-10)(1373.49494949495,-8.18181818181818)(1418.28282828283,-9.63636363636364)(1433.21212121212,-9.45454545454546)
+};
+
+\addplot [
 color=white,
@@
 
+\addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=3pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (1433.21212121212,-9.45454545454546)
+};
+
 \end{axis}

### 2013-03-22 figurefactory/files/limno_bgape_pp_210_0.tex
Add batch/path planning; add summary; finish first draft

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478,-8.36363636363636)(1478,-8.54545454545455)(1478,-8.72727272727273)(1478.00008294006,-8.90909090909091)(1478.00033175469,-9.09090909090909)(1478.00058056104,-9.27272727272727)(1478.00049762651,-9.45454545454546)(1478.0002488174,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(0,-7.81818181818182)(-0.000248817401863321,-7.63636363636364)(-0.000497626510092015,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000746427325097138,-7.09090909090909)(-0.000746427325097138,-6.90909090909091)(-0.00066349464153746,-6.72727272727273)(-0.0004146910621731,-6.54545454545455)(-0.000165879189445939,-6.36363636363636)(0,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (1478,-9.12121212121212)(1478.00020734323,-9.27272727272727)(1478.00012440663,-9.45454545454546)(1478,-9.54545454545455)(1463.07070707071,-9.56818181818182)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.72727272727273)(1442.54292929293,-9.81818181818182)(1433.21212121212,-9.90909090909091)(1418.28282828283,-9.95454545454546)(1407.08585858586,-10)(1403.35353535354,-10.0181818181818)(1388.42424242424,-10.030303030303)(1373.49494949495,-10.1136363636364)(1362.29797979798,-10.1818181818182)(1358.56565656566,-10.2)(1343.63636363636,-10.2363636363636)(1328.70707070707,-10.2878787878788)(1313.77777777778,-10.3181818181818)(1298.84848484848,-10.2727272727273)(1283.91919191919,-10.25)(1268.9898989899,-10.2121212121212)(1254.06060606061,-10.2121212121212)(1246.59595959596,-10.1818181818182)(1239.13131313131,-10.1666666666667)(1224.20202020202,-10.1666666666667)(1216.73737373737,-10.1818181818182)(1209.27272727273,-10.2121212121212)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.3409090909091)(1164.48484848485,-10.3454545454545)(1149.55555555556,-10.3181818181818)(1134.62626262626,-10.2575757575758)(1119.69696969697,-10.2878787878788)(1104.76767676768,-10.3484848484848)(1089.83838383838,-10.3484848484848)(1074.90909090909,-10.2878787878788)(1059.9797979798,-10.2878787878788)(1045.05050505051,-10.3181818181818)(1030.12121212121,-10.3484848484848)(1015.19191919192,-10.3181818181818)(1000.26262626263,-10.3090909090909)(985.333333333333,-10.2727272727273)(972.892255892256,-10.1818181818182)(970.40404040404,-10.1666666666667)(955.474747474747,-10.1363636363636)(940.545454545455,-10.0545454545455)(925.616161616162,-10.0227272727273)(918.151515151515,-10)(910.686868686869,-9.98484848484848)(895.757575757576,-9.95454545454546)(880.828282828283,-9.88636363636364)(875.229797979798,-9.81818181818182)(865.89898989899,-9.74242424242424)(850.969696969697,-9.74242424242424)(836.040404040404,-9.70454545454546)(824.843434343434,-9.63636363636364)(821.111111111111,-9.60606060606061)(813.646464646465,-9.45454545454546)(806.181818181818,-9.37878787878788)(791.252525252525,-9.36363636363636)(778.811447811448,-9.27272727272727)(776.323232323232,-9.22727272727273)(768.858585858586,-9.09090909090909)(763.260101010101,-8.90909090909091)(763.882154882155,-8.72727272727273)(765.872727272727,-8.54545454545455)(770.724747474747,-8.36363636363636)(776.323232323232,-8.22727272727273)(777.816161616162,-8.18181818181818)(791.252525252525,-8.01818181818182)(794.984848484849,-8)(806.181818181818,-7.94545454545455)(821.111111111111,-7.83333333333333)(824.843434343434,-7.81818181818182)(836.040404040404,-7.75)(848.481481481482,-7.63636363636364)(850.969696969697,-7.60606060606061)(863.410774410775,-7.45454545454546)(865.89898989899,-7.43181818181818)(880.828282828283,-7.38636363636364)(895.757575757576,-7.36363636363636)(910.686868686869,-7.29090909090909)(918.151515151515,-7.27272727272727)(925.616161616162,-7.24242424242424)(940.545454545455,-7.20454545454546)(955.474747474747,-7.24242424242424)(962.939393939394,-7.27272727272727)(970.40404040404,-7.28787878787879)(985.333333333333,-7.28787878787879)(992.79797979798,-7.27272727272727)(1000.26262626263,-7.24242424242424)(1015.19191919192,-7.24242424242424)(1030.12121212121,-7.24242424242424)(1037.58585858586,-7.27272727272727)(1045.05050505051,-7.28787878787879)(1052.51515151515,-7.27272727272727)(1059.9797979798,-7.25)(1067.44444444444,-7.27272727272727)(1074.90909090909,-7.28787878787879)(1089.83838383838,-7.28787878787879)(1104.76767676768,-7.34848484848485)(1119.69696969697,-7.36363636363636)(1134.62626262626,-7.38636363636364)(1149.55555555556,-7.42424242424243)(1157.0202020202,-7.45454545454546)(1164.48484848485,-7.46969696969697)(1179.41414141414,-7.56060606060606)(1194.34343434343,-7.53030303030303)(1209.27272727273,-7.54545454545455)(1224.20202020202,-7.47727272727273)(1239.13131313131,-7.54545454545455)(1254.06060606061,-7.59090909090909)(1261.52525252525,-7.63636363636364)(1268.9898989899,-7.65151515151515)(1283.91919191919,-7.72727272727273)(1298.84848484848,-7.69090909090909)(1313.77777777778,-7.72727272727273)(1328.70707070707,-7.72727272727273)(1343.63636363636,-7.79545454545455)(1346.12457912458,-7.81818181818182)(1354.08686868687,-8)(1358.56565656566,-8.05454545454545)(1373.49494949495,-8.09090909090909)(1388.42424242424,-8.15909090909091)(1395.88888888889,-8.18181818181818)(1403.35353535354,-8.22727272727273)(1410.81818181818,-8.36363636363636)(1418.28282828283,-8.41818181818182)(1433.21212121212,-8.51515151515152)(1435.70033670034,-8.54545454545455)(1440.67676767677,-8.72727272727273)(1448.14141414141,-8.86363636363636)(1450.62962962963,-8.90909090909091)(1463.07070707071,-9.02272727272727)(1474.26767676768,-9.09090909090909)(1478,-9.12121212121212)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1433.21212121212,-9.24242424242424)(1435.70033670034,-9.27272727272727)(1438.81060606061,-9.45454545454546)(1433.21212121212,-9.52272727272727)(1423.88131313131,-9.63636363636364)(1418.28282828283,-9.68181818181818)(1403.35353535354,-9.74242424242424)(1388.42424242424,-9.70454545454546)(1373.49494949495,-9.78787878787879)(1369.76262626263,-9.81818181818182)(1358.56565656566,-9.86363636363636)(1343.63636363636,-9.94545454545455)(1332.43939393939,-10)(1328.70707070707,-10.0151515151515)(1313.77777777778,-10.0454545454545)(1302.58080808081,-10)(1298.84848484848,-9.97727272727273)(1283.91919191919,-9.93181818181818)(1268.9898989899,-9.88636363636364)(1254.06060606061,-9.88636363636364)(1239.13131313131,-9.87272727272727)(1224.20202020202,-9.87272727272727)(1209.27272727273,-9.88636363636364)(1194.34343434343,-9.90909090909091)(1183.14646464646,-10)(1179.41414141414,-10.0151515151515)(1164.48484848485,-10.0454545454545)(1149.55555555556,-10.0454545454545)(1138.35858585859,-10)(1134.62626262626,-9.98181818181818)(1127.16161616162,-10)(1119.69696969697,-10.0151515151515)(1104.76767676768,-10.0757575757576)(1089.83838383838,-10.0757575757576)(1074.90909090909,-10.0151515151515)(1059.9797979798,-10.0151515151515)(1045.05050505051,-10.0454545454545)(1030.12121212121,-10.0757575757576)(1015.19191919192,-10.0454545454545)(1000.26262626263,-10.0151515151515)(992.79797979798,-10)(985.333333333333,-9.97727272727273)(970.40404040404,-9.87272727272727)(955.474747474747,-9.86363636363636)(948.010101010101,-9.81818181818182)(940.545454545455,-9.76363636363636)(925.616161616162,-9.72727272727273)(910.686868686869,-9.71212121212121)(895.757575757576,-9.68181818181818)(888.292929292929,-9.63636363636364)(880.828282828283,-9.56818181818182)(865.89898989899,-9.46969696969697)(850.969696969697,-9.46969696969697)(849.103535353535,-9.45454545454546)(836.040404040404,-9.29545454545455)(833.552188552189,-9.27272727272727)(821.111111111111,-9.15909090909091)(813.646464646465,-9.09090909090909)(806.181818181818,-9.02272727272727)(793.740740740741,-8.90909090909091)(798.717171717172,-8.72727272727273)(791.252525252525,-8.59090909090909)(790.008417508418,-8.54545454545455)(791.252525252525,-8.5)(796.85101010101,-8.36363636363636)(806.181818181818,-8.25)(813.646464646465,-8.18181818181818)(821.111111111111,-8.12727272727273)(836.040404040404,-8.09090909090909)(845.371212121212,-8)(850.969696969697,-7.93181818181818)(863.410774410775,-7.81818181818182)(865.89898989899,-7.8)(880.828282828283,-7.70454545454546)(895.757575757576,-7.65909090909091)(903.222222222222,-7.63636363636364)(910.686868686869,-7.61818181818182)(925.616161616162,-7.56818181818182)(940.545454545455,-7.52272727272727)(955.474747474748,-7.56818181818182)(970.40404040404,-7.58181818181818)(985.333333333333,-7.58181818181818)(1000.26262626263,-7.56818181818182)(1015.19191919192,-7.56818181818182)(1030.12121212121,-7.56818181818182)(1045.05050505051,-7.58181818181818)(1059.9797979798,-7.54545454545455)(1074.90909090909,-7.58181818181818)(1089.83838383838,-7.56060606060606)(1104.76767676768,-7.62121212121212)(1112.23232323232,-7.63636363636364)(1119.69696969697,-7.65909090909091)(1134.62626262626,-7.70454545454546)(1149.55555555556,-7.75)(1164.48484848485,-7.79545454545455)(1171.94949494949,-7.81818181818182)(1179.41414141414,-7.83636363636364)(1186.87878787879,-7.81818181818182)(1194.34343434343,-7.8030303030303)(1201.80808080808,-7.81818181818182)(1209.27272727273,-7.84090909090909)(1216.73737373737,-7.81818181818182)(1224.20202020202,-7.8030303030303)(1227.93434343434,-7.81818181818182)(1239.13131313131,-7.90909090909091)(1254.06060606061,-7.96969696969697)(1268.9898989899,-7.94545454545455)(1280.18686868687,-8)(1283.91919191919,-8.02272727272727)(1291.38383838384,-8)(1298.84848484848,-7.98484848484848)(1306.31313131313,-8)(1313.77777777778,-8.02272727272727)(1328.70707070707,-8.06818181818182)(1341.14814814815,-8.18181818181818)(1343.63636363636,-8.22727272727273)(1351.10101010101,-8.36363636363636)(1358.56565656566,-8.41818181818182)(1373.49494949495,-8.45454545454545)(1385.93602693603,-8.54545454545455)(1388.42424242424,-8.59090909090909)(1395.88888888889,-8.72727272727273)(1403.35353535354,-8.79545454545455)(1415.79461279461,-8.90909090909091)(1418.28282828283,-9)(1420.77104377104,-9.09090909090909)(1433.21212121212,-9.24242424242424)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (358.30303030303,-7.90909090909091)(369.5,-7.81818181818182)(373.232323232323,-7.78787878787879)(388.161616161616,-7.65909090909091)(391.893939393939,-7.63636363636364)(403.090909090909,-7.56818181818182)(418.020202020202,-7.52272727272727)(432.949494949495,-7.54545454545455)(444.146464646465,-7.45454545454546)(447.878787878788,-7.36363636363636)(455.343434343434,-7.27272727272727)(462.808080808081,-7.22727272727273)(477.737373737374,-7.15909090909091)(492.666666666667,-7.14545454545455)(503.863636363636,-7.09090909090909)(507.59595959596,-7)(522.525252525253,-7)(537.454545454546,-6.96363636363636)(552.383838383838,-7.06818181818182)(556.116161616162,-7.09090909090909)(567.313131313131,-7.15909090909091)(579.754208754209,-7.27272727272727)(582.242424242424,-7.29090909090909)(597.171717171717,-7.32727272727273)(612.10101010101,-7.42424242424243)(614.589225589226,-7.45454545454546)(627.030303030303,-7.60606060606061)(628.896464646465,-7.63636363636364)(634.494949494949,-7.81818181818182)(641.959595959596,-7.96969696969697)(644.447811447811,-8)(655.022727272727,-8.18181818181818)(655.644781144781,-8.36363636363636)(656.888888888889,-8.45454545454545)(660.621212121212,-8.54545454545455)(656.888888888889,-8.63636363636364)(653.156565656566,-8.72727272727273)(641.959595959596,-8.86363636363636)(638.227272727273,-8.90909090909091)(627.030303030303,-9)(615.833333333333,-9.09090909090909)(612.10101010101,-9.13636363636364)(600.90404040404,-9.27272727272727)(597.171717171717,-9.3030303030303)(582.242424242424,-9.31818181818182)(567.313131313131,-9.36363636363636)(552.383838383838,-9.31818181818182)(537.454545454546,-9.3030303030303)(522.525252525253,-9.34090909090909)(507.59595959596,-9.32727272727273)(492.666666666667,-9.29545454545455)(488.934343434343,-9.27272727272727)(477.737373737374,-9.20454545454546)(462.808080808081,-9.11363636363636)(447.878787878788,-9.11363636363636)(445.390572390572,-9.09090909090909)(432.949494949495,-8.93939393939394)(429.217171717172,-8.90909090909091)(418.020202020202,-8.77272727272727)(410.555555555556,-8.72727272727273)(403.090909090909,-8.68181818181818)(391.893939393939,-8.54545454545455)(395.626262626263,-8.36363636363636)(388.161616161616,-8.31818181818182)(380.69696969697,-8.36363636363636)(373.232323232323,-8.40909090909091)(358.30303030303,-8.39393939393939)(354.570707070707,-8.36363636363636)(345.861952861953,-8.18181818181818)(350.838383838384,-8)(358.30303030303,-7.90909090909091)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-6.51515151515151)(7.46464646464646,-6.54545454545455)(14.9292929292929,-6.57575757575758)(29.8585858585859,-6.63636363636364)(44.7878787878788,-6.6969696969697)(52.2525252525253,-6.72727272727273)(59.7171717171717,-6.75757575757576)(74.6464646464647,-6.81818181818182)(89.5757575757576,-6.87878787878788)(97.040404040404,-6.90909090909091)(104.505050505051,-6.93939393939394)(119.434343434343,-7.06060606060606)(126.89898989899,-7.09090909090909)(134.363636363636,-7.12121212121212)(149.292929292929,-7.24242424242424)(156.757575757576,-7.27272727272727)(164.222222222222,-7.31818181818182)(175.419191919192,-7.45454545454546)(179.151515151515,-7.5)(194.080808080808,-7.5)(209.010101010101,-7.54545454545455)(223.939393939394,-7.60606060606061)(227.671717171717,-7.63636363636364)(238.868686868687,-7.77272727272727)(253.79797979798,-7.78787878787879)(257.530303030303,-7.81818181818182)(268.727272727273,-7.95454545454546)(283.656565656566,-7.95454545454546)(291.121212121212,-8)(298.585858585859,-8.04545454545455)(306.050505050505,-8.18181818181818)(302.318181818182,-8.36363636363636)(298.585858585859,-8.39393939393939)(283.656565656566,-8.5)(279.924242424242,-8.54545454545455)(268.727272727273,-8.61363636363636)(256.286195286195,-8.72727272727273)(253.79797979798,-8.75)(238.868686868687,-8.75757575757576)(223.939393939394,-8.81818181818182)(209.010101010101,-8.77272727272727)(194.080808080808,-8.81818181818182)(179.151515151515,-8.84090909090909)(164.222222222222,-8.88636363636364)(149.292929292929,-8.89090909090909)(134.363636363636,-8.89090909090909)(119.434343434343,-8.81818181818182)(104.505050505051,-8.75)(102.016835016835,-8.72727272727273)(92.0639730639731,-8.54545454545455)(89.5757575757576,-8.45454545454545)(74.6464646464647,-8.40909090909091)(70.9141414141414,-8.36363636363636)(59.7171717171717,-8.22727272727273)(57.2289562289562,-8.18181818181818)(47.2760942760943,-8)(44.7878787878788,-7.95454545454546)(37.3232323232323,-7.81818181818182)(29.8585858585859,-7.72727272727273)(18.6616161616162,-7.63636363636364)(14.9292929292929,-7.60606060606061)(0,-7.54545454545455)(-0.000124406627521346,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000373213662548569,-7.09090909090909)(-0.000373213662548569,-6.90909090909091)(-0.00029027890567471,-6.72727272727273)(-4.14691062186359e-05,-6.54545454545455)(0,-6.51515151515151)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (447.878787878788,-7.97727272727273)(460.941919191919,-7.81818181818182)(462.808080808081,-7.79545454545455)(473.258585858586,-7.63636363636364)(477.737373737374,-7.58181818181818)(492.666666666667,-7.53030303030303)(507.59595959596,-7.47272727272727)(511.328282828283,-7.45454545454546)(522.525252525253,-7.36363636363636)(533.722222222222,-7.27272727272727)(537.454545454546,-7.25757575757576)(539.320707070707,-7.27272727272727)(552.383838383838,-7.4)(559.848484848485,-7.45454545454546)(567.313131313131,-7.52272727272727)(582.242424242424,-7.59090909090909)(597.171717171717,-7.62121212121212)(599.037878787879,-7.63636363636364)(604.636363636364,-7.81818181818182)(609.612794612795,-8)(608.368686868687,-8.18181818181818)(612.10101010101,-8.22727272727273)(617.699494949495,-8.36363636363636)(612.10101010101,-8.5)(608.368686868687,-8.54545454545455)(597.171717171717,-8.68181818181818)(593.439393939394,-8.72727272727273)(582.242424242424,-8.79545454545455)(567.313131313131,-8.87878787878788)(552.383838383838,-8.88636363636364)(548.651515151515,-8.90909090909091)(537.454545454546,-8.97727272727273)(522.525252525253,-9.02272727272727)(507.59595959596,-9)(492.666666666667,-8.92727272727273)(488.934343434343,-8.90909090909091)(477.737373737374,-8.81818181818182)(462.808080808081,-8.75)(460.319865319865,-8.72727272727273)(453.477272727273,-8.54545454545455)(447.878787878788,-8.40909090909091)(445.390572390572,-8.36363636363636)(436.681818181818,-8.18181818181818)(444.146464646465,-8)(447.878787878788,-7.97727272727273)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (134.363636363636,-7.86363636363636)(149.292929292929,-7.93181818181818)(164.222222222222,-7.93181818181818)(179.151515151515,-7.98181818181818)(186.616161616162,-8)(194.080808080808,-8.03030303030303)(209.010101010101,-8.15909090909091)(211.498316498317,-8.18181818181818)(209.010101010101,-8.22727272727273)(197.813131313131,-8.36363636363636)(194.080808080808,-8.38181818181818)(179.151515151515,-8.43939393939394)(164.222222222222,-8.41818181818182)(149.292929292929,-8.47727272727273)(134.363636363636,-8.45454545454545)(126.89898989899,-8.36363636363636)(128.765151515152,-8.18181818181818)(128.765151515152,-8)(134.363636363636,-7.86363636363636)};

\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0)(1268.9898989899,-8.18181818181818)(1254.06060606061,-9.27272727272727)(1164.48484848485,-8.54545454545455)(1149.55555555556,-8.18181818181818)(1134.62626262626,-7.81818181818182)(1119.69696969697,-8.90909090909091)(1104.76767676768,-7.63636363636364)(1074.90909090909,-7.45454545454546)(1074.90909090909,-9.09090909090909)(1059.9797979798,-9.09090909090909)(1030.12121212121,-7.27272727272727)(1015.19191919192,-7.27272727272727)(970.40404040404,-9.27272727272727)(910.686868686869,-7.09090909090909)(880.828282828283,-9.09090909090909)(865.89898989899,-9.09090909090909)(865.89898989899,-7.09090909090909)(791.252525252525,-8.90909090909091)(791.252525252525,-7.27272727272727)(761.393939393939,-7.27272727272727)(746.464646464646,-8.72727272727273)(716.606060606061,-8.54545454545455)(686.747474747475,-7.63636363636364)(671.818181818182,-8.18181818181818)(656.888888888889,-8)(597.171717171717,-7.09090909090909)(537.454545454546,-8.72727272727273)(223.939393939394,-8.36363636363636)(194.080808080808,-7.09090909090909)(0,-9.45454545454546)(209.010101010101,-8.18181818181818)(268.727272727273,-8.72727272727273)(298.585858585859,-7.81818181818182)(313.515151515152,-7.81818181818182)(313.515151515152,-8.90909090909091)(373.232323232323,-9.09090909090909)(388.161616161616,-9.09090909090909)(418.020202020202,-7.63636363636364)(492.666666666667,-9.27272727272727)(522.525252525253,-9.27272727272727)(522.525252525253,-7.81818181818182)(567.313131313131,-8)(567.313131313131,-9.09090909090909)(836.040404040404,-8.36363636363636)(836.040404040404,-9.63636363636364)(850.969696969697,-9.81818181818182)(865.89898989899,-8)(940.545454545455,-10.1818181818182)(955.474747474747,-10.1818181818182)(1074.90909090909,-10.3636363636364)(1209.27272727273,-7.63636363636364)(1224.20202020202,-10.1818181818182)(1239.13131313131,-10.1818181818182)(1283.91919191919,-7.81818181818182)(1313.77777777778,-10)(1358.56565656566,-9.81818181818182)(1358.56565656566,-8.18181818181818)(1403.35353535354,-8.72727272727273)(1403.35353535354,-9.27272727272727)(1418.28282828283,-8.90909090909091)(1433.21212121212,-9.09090909090909)(1418.28282828283,-9.45454545454546)(1403.35353535354,-8.54545454545455)(1388.42424242424,-8.36363636363636)(1373.49494949495,-9.81818181818182)(1328.70707070707,-10)(1298.84848484848,-7.81818181818182)(1239.13131313131,-7.63636363636364)(1149.55555555556,-7.45454545454546)(1134.62626262626,-7.45454545454546)(1104.76767676768,-10.1818181818182)(1089.83838383838,-10.1818181818182)(1074.90909090909,-10.1818181818182)(925.616161616162,-7.45454545454546)(925.616161616162,-10)(880.828282828283,-9.81818181818182)(865.89898989899,-7.81818181818182)(821.111111111111,-9.27272727272727)(612.10101010101,-8.72727272727273)(597.171717171717,-8.90909090909091)(567.313131313131,-7.63636363636364)(477.737373737374,-7.63636363636364)(418.020202020202,-8.54545454545455)(388.161616161616,-8.36363636363636)(388.161616161616,-8.18181818181818)(268.727272727273,-8)(194.080808080808,-7.81818181818182)(164.222222222222,-8)(164.222222222222,-8.18181818181818)(149.292929292929,-8)(134.363636363636,-7.81818181818182)(119.434343434343,-8)(119.434343434343,-8.18181818181818)(134.363636363636,-8.36363636363636)(164.222222222222,-8.54545454545455)(238.868686868687,-7.81818181818182)(253.79797979798,-8.36363636363636)(403.090909090909,-8)(403.090909090909,-8.36363636363636)(447.878787878788,-8.72727272727273)(492.666666666667,-7.45454545454546)(507.59595959596,-7.45454545454546)(507.59595959596,-9.09090909090909)(552.383838383838,-7.45454545454546)(597.171717171717,-9.09090909090909)(612.10101010101,-7.81818181818182)(627.030303030303,-8.90909090909091)(641.959595959596,-8.54545454545455)(806.181818181818,-8.90909090909091)(821.111111111111,-8.18181818181818)(850.969696969697,-7.81818181818182)(955.474747474747,-10)(955.474747474747,-7.27272727272727)(1045.05050505051,-7.27272727272727)(1119.69696969697,-10.1818181818182)(1134.62626262626,-10.1818181818182)(1224.20202020202,-7.63636363636364)(1328.70707070707,-8)(1433.21212121212,-8.90909090909091)(1433.21212121212,-9.27272727272727)(1418.28282828283,-8.72727272727273)(1388.42424242424,-9.81818181818182)(1298.84848484848,-10)(1194.34343434343,-7.63636363636364)(1104.76767676768,-7.45454545454546)(910.686868686869,-7.45454545454546)(895.757575757576,-9.81818181818182)(836.040404040404,-9.45454545454546)(806.181818181818,-9.09090909090909)(806.181818181818,-8.36363636363636)(627.030303030303,-8)(582.242424242424,-9.09090909090909)(552.383838383838,-7.27272727272727)(537.454545454546,-7.27272727272727)(507.59595959596,-7.27272727272727)(492.666666666667,-7.27272727272727)(492.666666666667,-9.09090909090909)(432.949494949495,-8.72727272727273)(432.949494949495,-7.63636363636364)(253.79797979798,-7.81818181818182)(223.939393939394,-8.54545454545455)(179.151515151515,-8.72727272727273)(164.222222222222,-7.63636363636364)(149.292929292929,-7.63636363636364)(134.363636363636,-7.63636363636364)(134.363636363636,-8.54545454545455)(119.434343434343,-8.54545454545455)(104.505050505051,-7.81818181818182)(89.5757575757576,-8)(89.5757575757576,-8.18181818181818)(104.505050505051,-8.36363636363636)(164.222222222222,-8.72727272727273)(179.151515151515,-7.63636363636364)(238.868686868687,-8.54545454545455)(268.727272727273,-8.18181818181818)(403.090909090909,-8.18181818181818)(418.020202020202,-7.81818181818182)(462.808080808081,-8.90909090909091)(477.737373737374,-7.27272727272727)(522.525252525253,-7.09090909090909)(567.313131313131,-7.27272727272727)(597.171717171717,-7.45454545454546)(612.10101010101,-8.90909090909091)(627.030303030303,-8.54545454545455)(627.030303030303,-8.36363636363636)(627.030303030303,-8.18181818181818)(791.252525252525,-8.72727272727273)(791.252525252525,-9.09090909090909)(821.111111111111,-9.45454545454546)(836.040404040404,-8)(850.969696969697,-9.63636363636364)(880.828282828283,-7.63636363636364)(1000.26262626263,-7.27272727272727)(1059.9797979798,-10.1818181818182)(1119.69696969697,-7.45454545454546)(1268.9898989899,-7.81818181818182)(1343.63636363636,-10)(1373.49494949495,-8.18181818181818)(1418.28282828283,-9.63636363636364) 
};

\addplot [
color=lime,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1433.21212121212,-9.45454545454546)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-22 figurefactory/files/limno_bgape_pp_30_0.tex
Add batch/path planning; add summary; finish first draft

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478.00044786535,-8.18181818181818)(1478.00089570383,-8.36363636363636)(1478.00134351545,-8.54545454545455)(1478.00134351545,-8.72727272727273)(1478.00134351545,-8.90909090909091)(1478.00134351545,-9.09090909090909)(1478.00134351545,-9.27272727272727)(1478.00089570383,-9.45454545454546)(1478.00044786535,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(-0.000447865351918085,-10.5454545454545)(-0.000895703833526601,-10.3636363636364)(-0.00134351544724879,-10.1818181818182)(-0.00134351544724879,-10)(-0.00134351544724879,-9.81818181818182)(-0.00134351544724879,-9.63636363636364)(-0.00134351544724879,-9.45454545454546)(-0.00134351544724879,-9.27272727272727)(-0.00134351544724879,-9.09090909090909)(-0.00134351544724879,-8.90909090909091)(-0.00134351544724879,-8.72727272727273)(-0.00134351544724879,-8.54545454545455)(-0.00134351544724879,-8.36363636363636)(-0.000895703833526601,-8.18181818181818)(-0.000447865351918085,-8)(-0.000447865351918085,-7.81818181818182)(-0.000895703833526601,-7.63636363636364)(-0.00134351544724879,-7.45454545454546)(-0.00134351544724879,-7.27272727272727)(-0.00134351544724879,-7.09090909090909)(-0.00134351544724879,-6.90909090909091)(-0.00134351544724879,-6.72727272727273)(-0.00134351544724879,-6.54545454545455)(-0.00134351544724879,-6.36363636363636)(-0.00134351544724879,-6.18181818181818)(-0.000895703833526601,-6)(-0.000447865351918085,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-5.90909090909091)(14.9292929292929,-5.90909090909091)(29.8585858585859,-5.96969696969697)(37.3232323232323,-6)(44.7878787878788,-6.03030303030303)(59.7171717171717,-6.09090909090909)(74.6464646464647,-6.09090909090909)(89.5757575757576,-6.09090909090909)(104.505050505051,-6.09090909090909)(119.434343434343,-6.09090909090909)(134.363636363636,-6.09090909090909)(149.292929292929,-6.09090909090909)(164.222222222222,-6.09090909090909)(179.151515151515,-6.09090909090909)(194.080808080808,-6.09090909090909)(209.010101010101,-6.15151515151515)(216.474747474747,-6.18181818181818)(223.939393939394,-6.21212121212121)(238.868686868687,-6.27272727272727)(253.79797979798,-6.27272727272727)(268.727272727273,-6.27272727272727)(283.656565656566,-6.27272727272727)(298.585858585859,-6.27272727272727)(313.515151515152,-6.27272727272727)(328.444444444444,-6.27272727272727)(343.373737373737,-6.33333333333333)(350.838383838384,-6.36363636363636)(358.30303030303,-6.39393939393939)(373.232323232323,-6.39393939393939)(380.69696969697,-6.36363636363636)(388.161616161616,-6.33333333333333)(403.090909090909,-6.27272727272727)(418.020202020202,-6.27272727272727)(432.949494949495,-6.27272727272727)(447.878787878788,-6.21212121212121)(455.343434343434,-6.18181818181818)(462.808080808081,-6.15151515151515)(477.737373737374,-6.09090909090909)(492.666666666667,-6.03030303030303)(500.131313131313,-6)(507.59595959596,-5.96969696969697)(522.525252525253,-5.90909090909091)(537.454545454546,-5.90909090909091)(552.383838383838,-5.90909090909091)(567.313131313131,-5.84848484848485)(574.777777777778,-5.81818181818182)(582.242424242424,-5.78787878787879)(597.171717171717,-5.72727272727273)(612.10101010101,-5.72727272727273)(627.030303030303,-5.72727272727273)(641.959595959596,-5.72727272727273)(656.888888888889,-5.72727272727273)(671.818181818182,-5.72727272727273)(686.747474747475,-5.72727272727273)(701.676767676768,-5.72727272727273)(716.606060606061,-5.72727272727273)(731.535353535354,-5.72727272727273)(746.464646464646,-5.72727272727273)(761.393939393939,-5.72727272727273)(776.323232323232,-5.72727272727273)(791.252525252525,-5.72727272727273)(806.181818181818,-5.72727272727273)(821.111111111111,-5.72727272727273)(836.040404040404,-5.72727272727273)(850.969696969697,-5.72727272727273)(865.89898989899,-5.72727272727273)(880.828282828283,-5.72727272727273)(895.757575757576,-5.72727272727273)(910.686868686869,-5.78787878787879)(918.151515151515,-5.81818181818182)(925.616161616162,-5.84848484848485)(940.545454545455,-5.90909090909091)(955.474747474747,-5.90909090909091)(970.40404040404,-5.90909090909091)(985.333333333333,-5.96969696969697)(992.79797979798,-6)(1000.26262626263,-6.03030303030303)(1015.19191919192,-6.09090909090909)(1030.12121212121,-6.09090909090909)(1045.05050505051,-6.09090909090909)(1059.9797979798,-6.15151515151515)(1067.44444444444,-6.18181818181818)(1074.90909090909,-6.21212121212121)(1089.83838383838,-6.27272727272727)(1104.76767676768,-6.27272727272727)(1119.69696969697,-6.27272727272727)(1134.62626262626,-6.27272727272727)(1149.55555555556,-6.27272727272727)(1164.48484848485,-6.27272727272727)(1179.41414141414,-6.27272727272727)(1194.34343434343,-6.27272727272727)(1209.27272727273,-6.27272727272727)(1224.20202020202,-6.27272727272727)(1239.13131313131,-6.27272727272727)(1254.06060606061,-6.27272727272727)(1268.9898989899,-6.27272727272727)(1283.91919191919,-6.27272727272727)(1298.84848484848,-6.33333333333333)(1306.31313131313,-6.36363636363636)(1313.77777777778,-6.39393939393939)(1328.70707070707,-6.51515151515151)(1332.43939393939,-6.54545454545455)(1343.63636363636,-6.63636363636364)(1351.10101010101,-6.72727272727273)(1358.56565656566,-6.81818181818182)(1366.0303030303,-6.90909090909091)(1373.49494949495,-7.04545454545455)(1375.98316498317,-7.09090909090909)(1385.93602693603,-7.27272727272727)(1388.42424242424,-7.36363636363636)(1390.91245791246,-7.45454545454546)(1400.86531986532,-7.63636363636364)(1403.35353535354,-7.68181818181818)(1410.81818181818,-7.81818181818182)(1418.28282828283,-7.90909090909091)(1425.74747474747,-8)(1433.21212121212,-8.09090909090909)(1444.40909090909,-8.18181818181818)(1448.14141414141,-8.21212121212121)(1463.07070707071,-8.27272727272727)(1478,-8.27272727272727)(1478.00022392596,-8.36363636363636)(1478.00067175772,-8.54545454545455)(1478.00067175772,-8.72727272727273)(1478.00067175772,-8.90909090909091)(1478.00067175772,-9.09090909090909)(1478.00067175772,-9.27272727272727)(1478.00022392596,-9.45454545454546)(1478,-9.54545454545455)(1463.07070707071,-9.60606060606061)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.66666666666667)(1433.21212121212,-9.78787878787879)(1429.4797979798,-9.81818181818182)(1418.28282828283,-9.90909090909091)(1407.08585858586,-10)(1403.35353535354,-10.030303030303)(1388.42424242424,-10.1515151515152)(1384.69191919192,-10.1818181818182)(1373.49494949495,-10.2727272727273)(1362.29797979798,-10.3636363636364)(1358.56565656566,-10.3939393939394)(1343.63636363636,-10.4545454545455)(1328.70707070707,-10.5151515151515)(1321.24242424242,-10.5454545454545)(1313.77777777778,-10.5757575757576)(1298.84848484848,-10.6363636363636)(1283.91919191919,-10.6363636363636)(1268.9898989899,-10.6363636363636)(1254.06060606061,-10.6363636363636)(1239.13131313131,-10.6363636363636)(1224.20202020202,-10.6363636363636)(1209.27272727273,-10.5757575757576)(1201.80808080808,-10.5454545454545)(1194.34343434343,-10.5151515151515)(1179.41414141414,-10.4545454545455)(1164.48484848485,-10.4545454545455)(1149.55555555556,-10.4545454545455)(1134.62626262626,-10.4545454545455)(1119.69696969697,-10.4545454545455)(1104.76767676768,-10.4545454545455)(1089.83838383838,-10.4545454545455)(1074.90909090909,-10.4545454545455)(1059.9797979798,-10.4545454545455)(1045.05050505051,-10.4545454545455)(1030.12121212121,-10.4545454545455)(1015.19191919192,-10.5151515151515)(1007.72727272727,-10.5454545454545)(1000.26262626263,-10.5757575757576)(985.333333333333,-10.6363636363636)(970.40404040404,-10.6363636363636)(955.474747474747,-10.6363636363636)(940.545454545455,-10.6363636363636)(925.616161616162,-10.6363636363636)(910.686868686869,-10.6363636363636)(895.757575757576,-10.6363636363636)(880.828282828283,-10.6363636363636)(865.89898989899,-10.6363636363636)(850.969696969697,-10.6363636363636)(836.040404040404,-10.6363636363636)(821.111111111111,-10.6363636363636)(806.181818181818,-10.6363636363636)(791.252525252525,-10.6363636363636)(776.323232323232,-10.5757575757576)(768.858585858586,-10.5454545454545)(761.393939393939,-10.5151515151515)(746.464646464646,-10.4545454545455)(731.535353535354,-10.4545454545455)(716.606060606061,-10.4545454545455)(701.676767676768,-10.4545454545455)(686.747474747475,-10.4545454545455)(671.818181818182,-10.4545454545455)(656.888888888889,-10.3939393939394)(649.424242424242,-10.3636363636364)(641.959595959596,-10.3333333333333)(627.030303030303,-10.2727272727273)(612.10101010101,-10.2727272727273)(597.171717171717,-10.2727272727273)(582.242424242424,-10.2121212121212)(574.777777777778,-10.1818181818182)(567.313131313131,-10.1515151515152)(552.383838383838,-10.0909090909091)(537.454545454546,-10.030303030303)(529.989898989899,-10)(522.525252525253,-9.96969696969697)(507.59595959596,-9.90909090909091)(492.666666666667,-9.84848484848485)(485.20202020202,-9.81818181818182)(477.737373737374,-9.78787878787879)(462.808080808081,-9.72727272727273)(447.878787878788,-9.72727272727273)(432.949494949495,-9.66666666666667)(425.484848484849,-9.63636363636364)(418.020202020202,-9.60606060606061)(403.090909090909,-9.54545454545455)(388.161616161616,-9.54545454545455)(373.232323232323,-9.54545454545455)(358.30303030303,-9.54545454545455)(343.373737373737,-9.54545454545455)(328.444444444444,-9.60606060606061)(320.979797979798,-9.63636363636364)(313.515151515152,-9.66666666666667)(298.585858585859,-9.72727272727273)(283.656565656566,-9.72727272727273)(268.727272727273,-9.78787878787879)(261.262626262626,-9.81818181818182)(253.79797979798,-9.84848484848485)(238.868686868687,-9.90909090909091)(223.939393939394,-9.96969696969697)(216.474747474747,-10)(209.010101010101,-10.030303030303)(194.080808080808,-10.0909090909091)(179.151515151515,-10.1515151515152)(171.686868686869,-10.1818181818182)(164.222222222222,-10.2121212121212)(149.292929292929,-10.2727272727273)(134.363636363636,-10.2727272727273)(119.434343434343,-10.3333333333333)(111.969696969697,-10.3636363636364)(104.505050505051,-10.3939393939394)(89.5757575757576,-10.4545454545455)(74.6464646464647,-10.4545454545455)(59.7171717171717,-10.4545454545455)(44.7878787878788,-10.4545454545455)(29.8585858585859,-10.4545454545455)(14.9292929292929,-10.4545454545455)(0,-10.4545454545455)(-0.00022392595838165,-10.3636363636364)(-0.000671757723624396,-10.1818181818182)(-0.000671757723624396,-10)(-0.000671757723624396,-9.81818181818182)(-0.000671757723624396,-9.63636363636364)(-0.000671757723624396,-9.45454545454546)(-0.000671757723624396,-9.27272727272727)(-0.000671757723624396,-9.09090909090909)(-0.000671757723624396,-8.90909090909091)(-0.000671757723624396,-8.72727272727273)(-0.000671757723624396,-8.54545454545455)(-0.000671757723624396,-8.36363636363636)(-0.00022392595838165,-8.18181818181818)(0,-8.09090909090909)(11.1969696969697,-8)(11.1969696969697,-7.81818181818182)(0,-7.72727272727273)(-0.00022392595838165,-7.63636363636364)(-0.000671757723624396,-7.45454545454546)(-0.000671757723624396,-7.27272727272727)(-0.000671757723624396,-7.09090909090909)(-0.000671757723624396,-6.90909090909091)(-0.000671757723624396,-6.72727272727273)(-0.000671757723624396,-6.54545454545455)(-0.000671757723624396,-6.36363636363636)(-0.000671757723624396,-6.18181818181818)(-0.00022392595838165,-6)(0,-5.90909090909091)};

\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0) 
};

\addplot [
color=lime,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1478,0)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-22 figurefactory/files/limno_bgape_pp_30_1.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_30_0.tex
@@
 \addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=1.6pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (1478,0)(1268.9898989899,-8.18181818181818)(1254.06060606061,-9.27272727272727)(1164.48484848485,-8.54545454545455)(1149.55555555556,-8.18181818181818)(1134.62626262626,-7.81818181818182)(1119.69696969697,-8.90909090909091)(1104.76767676768,-7.63636363636364)(1074.90909090909,-7.45454545454546)(1074.90909090909,-9.09090909090909)(1059.9797979798,-9.09090909090909)(1030.12121212121,-7.27272727272727)(1015.19191919192,-7.27272727272727)(970.40404040404,-9.27272727272727)(910.686868686869,-7.09090909090909)(880.828282828283,-9.09090909090909)(865.89898989899,-9.09090909090909)(865.89898989899,-7.09090909090909)(791.252525252525,-8.90909090909091)(791.252525252525,-7.27272727272727)(761.393939393939,-7.27272727272727)(746.464646464646,-8.72727272727273)(716.606060606061,-8.54545454545455)(686.747474747475,-7.63636363636364)(671.818181818182,-8.18181818181818)(656.888888888889,-8)(597.171717171717,-7.09090909090909)(537.454545454546,-8.72727272727273)(223.939393939394,-8.36363636363636)(194.080808080808,-7.09090909090909)(0,-9.45454545454546)
+};
+
+\addplot [
 color=lime,

### 2013-03-22 figurefactory/files/limno_bgape_pp_30_2.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_30_1.tex
@@
 \addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-5.90909090909091)(14.9292929292929,-5.90909090909091)(29.8585858585859,-5.96969696969697)(37.3232323232323,-6)(44.7878787878788,-6.03030303030303)(59.7171717171717,-6.09090909090909)(74.6464646464647,-6.09090909090909)(89.5757575757576,-6.09090909090909)(104.505050505051,-6.09090909090909)(119.434343434343,-6.09090909090909)(134.363636363636,-6.09090909090909)(149.292929292929,-6.09090909090909)(164.222222222222,-6.09090909090909)(179.151515151515,-6.09090909090909)(194.080808080808,-6.09090909090909)(209.010101010101,-6.15151515151515)(216.474747474747,-6.18181818181818)(223.939393939394,-6.21212121212121)(238.868686868687,-6.27272727272727)(253.79797979798,-6.27272727272727)(268.727272727273,-6.27272727272727)(283.656565656566,-6.27272727272727)(298.585858585859,-6.27272727272727)(313.515151515152,-6.27272727272727)(328.444444444444,-6.27272727272727)(343.373737373737,-6.33333333333333)(350.838383838384,-6.36363636363636)(358.30303030303,-6.39393939393939)(373.232323232323,-6.39393939393939)(380.69696969697,-6.36363636363636)(388.161616161616,-6.33333333333333)(403.090909090909,-6.27272727272727)(418.020202020202,-6.27272727272727)(432.949494949495,-6.27272727272727)(447.878787878788,-6.21212121212121)(455.343434343434,-6.18181818181818)(462.808080808081,-6.15151515151515)(477.737373737374,-6.09090909090909)(492.666666666667,-6.03030303030303)(500.131313131313,-6)(507.59595959596,-5.96969696969697)(522.525252525253,-5.90909090909091)(537.454545454546,-5.90909090909091)(552.383838383838,-5.90909090909091)(567.313131313131,-5.84848484848485)(574.777777777778,-5.81818181818182)(582.242424242424,-5.78787878787879)(597.171717171717,-5.72727272727273)(612.10101010101,-5.72727272727273)(627.030303030303,-5.72727272727273)(641.959595959596,-5.72727272727273)(656.888888888889,-5.72727272727273)(671.818181818182,-5.72727272727273)(686.747474747475,-5.72727272727273)(701.676767676768,-5.72727272727273)(716.606060606061,-5.72727272727273)(731.535353535354,-5.72727272727273)(746.464646464646,-5.72727272727273)(761.393939393939,-5.72727272727273)(776.323232323232,-5.72727272727273)(791.252525252525,-5.72727272727273)(806.181818181818,-5.72727272727273)(821.111111111111,-5.72727272727273)(836.040404040404,-5.72727272727273)(850.969696969697,-5.72727272727273)(865.89898989899,-5.72727272727273)(880.828282828283,-5.72727272727273)(895.757575757576,-5.72727272727273)(910.686868686869,-5.78787878787879)(918.151515151515,-5.81818181818182)(925.616161616162,-5.84848484848485)(940.545454545455,-5.90909090909091)(955.474747474747,-5.90909090909091)(970.40404040404,-5.90909090909091)(985.333333333333,-5.96969696969697)(992.79797979798,-6)(1000.26262626263,-6.03030303030303)(1015.19191919192,-6.09090909090909)(1030.12121212121,-6.09090909090909)(1045.05050505051,-6.09090909090909)(1059.9797979798,-6.15151515151515)(1067.44444444444,-6.18181818181818)(1074.90909090909,-6.21212121212121)(1089.83838383838,-6.27272727272727)(1104.76767676768,-6.27272727272727)(1119.69696969697,-6.27272727272727)(1134.62626262626,-6.27272727272727)(1149.55555555556,-6.27272727272727)(1164.48484848485,-6.27272727272727)(1179.41414141414,-6.27272727272727)(1194.34343434343,-6.27272727272727)(1209.27272727273,-6.27272727272727)(1224.20202020202,-6.27272727272727)(1239.13131313131,-6.27272727272727)(1254.06060606061,-6.27272727272727)(1268.9898989899,-6.27272727272727)(1283.91919191919,-6.27272727272727)(1298.84848484848,-6.33333333333333)(1306.31313131313,-6.36363636363636)(1313.77777777778,-6.39393939393939)(1328.70707070707,-6.51515151515151)(1332.43939393939,-6.54545454545455)(1343.63636363636,-6.63636363636364)(1351.10101010101,-6.72727272727273)(1358.56565656566,-6.81818181818182)(1366.0303030303,-6.90909090909091)(1373.49494949495,-7.04545454545455)(1375.98316498317,-7.09090909090909)(1385.93602693603,-7.27272727272727)(1388.42424242424,-7.36363636363636)(1390.91245791246,-7.45454545454546)(1400.86531986532,-7.63636363636364)(1403.35353535354,-7.68181818181818)(1410.81818181818,-7.81818181818182)(1418.28282828283,-7.90909090909091)(1425.74747474747,-8)(1433.21212121212,-8.09090909090909)(1444.40909090909,-8.18181818181818)(1448.14141414141,-8.21212121212121)(1463.07070707071,-8.27272727272727)(1478,-8.27272727272727)(1478.00022392596,-8.36363636363636)(1478.00067175772,-8.54545454545455)(1478.00067175772,-8.72727272727273)(1478.00067175772,-8.90909090909091)(1478.00067175772,-9.09090909090909)(1478.00067175772,-9.27272727272727)(1478.00022392596,-9.45454545454546)(1478,-9.54545454545455)(1463.07070707071,-9.60606060606061)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.66666666666667)(1433.21212121212,-9.78787878787879)(1429.4797979798,-9.81818181818182)(1418.28282828283,-9.90909090909091)(1407.08585858586,-10)(1403.35353535354,-10.030303030303)(1388.42424242424,-10.1515151515152)(1384.69191919192,-10.1818181818182)(1373.49494949495,-10.2727272727273)(1362.29797979798,-10.3636363636364)(1358.56565656566,-10.3939393939394)(1343.63636363636,-10.4545454545455)(1328.70707070707,-10.5151515151515)(1321.24242424242,-10.5454545454545)(1313.77777777778,-10.5757575757576)(1298.84848484848,-10.6363636363636)(1283.91919191919,-10.6363636363636)(1268.9898989899,-10.6363636363636)(1254.06060606061,-10.6363636363636)(1239.13131313131,-10.6363636363636)(1224.20202020202,-10.6363636363636)(1209.27272727273,-10.5757575757576)(1201.80808080808,-10.5454545454545)(1194.34343434343,-10.5151515151515)(1179.41414141414,-10.4545454545455)(1164.48484848485,-10.4545454545455)(1149.55555555556,-10.4545454545455)(1134.62626262626,-10.4545454545455)(1119.69696969697,-10.4545454545455)(1104.76767676768,-10.4545454545455)(1089.83838383838,-10.4545454545455)(1074.90909090909,-10.4545454545455)(1059.9797979798,-10.4545454545455)(1045.05050505051,-10.4545454545455)(1030.12121212121,-10.4545454545455)(1015.19191919192,-10.5151515151515)(1007.72727272727,-10.5454545454545)(1000.26262626263,-10.5757575757576)(985.333333333333,-10.6363636363636)(970.40404040404,-10.6363636363636)(955.474747474747,-10.6363636363636)(940.545454545455,-10.6363636363636)(925.616161616162,-10.6363636363636)(910.686868686869,-10.6363636363636)(895.757575757576,-10.6363636363636)(880.828282828283,-10.6363636363636)(865.89898989899,-10.6363636363636)(850.969696969697,-10.6363636363636)(836.040404040404,-10.6363636363636)(821.111111111111,-10.6363636363636)(806.181818181818,-10.6363636363636)(791.252525252525,-10.6363636363636)(776.323232323232,-10.5757575757576)(768.858585858586,-10.5454545454545)(761.393939393939,-10.5151515151515)(746.464646464646,-10.4545454545455)(731.535353535354,-10.4545454545455)(716.606060606061,-10.4545454545455)(701.676767676768,-10.4545454545455)(686.747474747475,-10.4545454545455)(671.818181818182,-10.4545454545455)(656.888888888889,-10.3939393939394)(649.424242424242,-10.3636363636364)(641.959595959596,-10.3333333333333)(627.030303030303,-10.2727272727273)(612.10101010101,-10.2727272727273)(597.171717171717,-10.2727272727273)(582.242424242424,-10.2121212121212)(574.777777777778,-10.1818181818182)(567.313131313131,-10.1515151515152)(552.383838383838,-10.0909090909091)(537.454545454546,-10.030303030303)(529.989898989899,-10)(522.525252525253,-9.96969696969697)(507.59595959596,-9.90909090909091)(492.666666666667,-9.84848484848485)(485.20202020202,-9.81818181818182)(477.737373737374,-9.78787878787879)(462.808080808081,-9.72727272727273)(447.878787878788,-9.72727272727273)(432.949494949495,-9.66666666666667)(425.484848484849,-9.63636363636364)(418.020202020202,-9.60606060606061)(403.090909090909,-9.54545454545455)(388.161616161616,-9.54545454545455)(373.232323232323,-9.54545454545455)(358.30303030303,-9.54545454545455)(343.373737373737,-9.54545454545455)(328.444444444444,-9.60606060606061)(320.979797979798,-9.63636363636364)(313.515151515152,-9.66666666666667)(298.585858585859,-9.72727272727273)(283.656565656566,-9.72727272727273)(268.727272727273,-9.78787878787879)(261.262626262626,-9.81818181818182)(253.79797979798,-9.84848484848485)(238.868686868687,-9.90909090909091)(223.939393939394,-9.96969696969697)(216.474747474747,-10)(209.010101010101,-10.030303030303)(194.080808080808,-10.0909090909091)(179.151515151515,-10.1515151515152)(171.686868686869,-10.1818181818182)(164.222222222222,-10.2121212121212)(149.292929292929,-10.2727272727273)(134.363636363636,-10.2727272727273)(119.434343434343,-10.3333333333333)(111.969696969697,-10.3636363636364)(104.505050505051,-10.3939393939394)(89.5757575757576,-10.4545454545455)(74.6464646464647,-10.4545454545455)(59.7171717171717,-10.4545454545455)(44.7878787878788,-10.4545454545455)(29.8585858585859,-10.4545454545455)(14.9292929292929,-10.4545454545455)(0,-10.4545454545455)(-0.00022392595838165,-10.3636363636364)(-0.000671757723624396,-10.1818181818182)(-0.000671757723624396,-10)(-0.000671757723624396,-9.81818181818182)(-0.000671757723624396,-9.63636363636364)(-0.000671757723624396,-9.45454545454546)(-0.000671757723624396,-9.27272727272727)(-0.000671757723624396,-9.09090909090909)(-0.000671757723624396,-8.90909090909091)(-0.000671757723624396,-8.72727272727273)(-0.000671757723624396,-8.54545454545455)(-0.000671757723624396,-8.36363636363636)(-0.00022392595838165,-8.18181818181818)(0,-8.09090909090909)(11.1969696969697,-8)(11.1969696969697,-7.81818181818182)(0,-7.72727272727273)(-0.00022392595838165,-7.63636363636364)(-0.000671757723624396,-7.45454545454546)(-0.000671757723624396,-7.27272727272727)(-0.000671757723624396,-7.09090909090909)(-0.000671757723624396,-6.90909090909091)(-0.000671757723624396,-6.72727272727273)(-0.000671757723624396,-6.54545454545455)(-0.000671757723624396,-6.36363636363636)(-0.000671757723624396,-6.18181818181818)(-0.00022392595838165,-6)(0,-5.90909090909091)};
+
+\addplot [
+draw=red!50!white,
+line width=0.6pt,
+forget plot
+]
+coordinates{
+ (1478,0)(1268.9898989899,-8.18181818181818)(1254.06060606061,-9.27272727272727)(1164.48484848485,-8.54545454545455)(1149.55555555556,-8.18181818181818)(1134.62626262626,-7.81818181818182)(1119.69696969697,-8.90909090909091)(1104.76767676768,-7.63636363636364)(1074.90909090909,-7.45454545454546)(1074.90909090909,-9.09090909090909)(1059.9797979798,-9.09090909090909)(1030.12121212121,-7.27272727272727)(1015.19191919192,-7.27272727272727)(970.40404040404,-9.27272727272727)(910.686868686869,-7.09090909090909)(880.828282828283,-9.09090909090909)(865.89898989899,-9.09090909090909)(865.89898989899,-7.09090909090909)(791.252525252525,-8.90909090909091)(791.252525252525,-7.27272727272727)(761.393939393939,-7.27272727272727)(746.464646464646,-8.72727272727273)(716.606060606061,-8.54545454545455)(686.747474747475,-7.63636363636364)(671.818181818182,-8.18181818181818)(656.888888888889,-8)(597.171717171717,-7.09090909090909)(537.454545454546,-8.72727272727273)(223.939393939394,-8.36363636363636)(194.080808080808,-7.09090909090909)(0,-9.45454545454546)
+};
 
@@
 
+\addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=3pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (0,-9.45454545454546)
+};
+
 \end{axis}

### 2013-03-22 figurefactory/files/limno_bgape_pp_60_0.tex
Add batch/path planning; add summary; finish first draft

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478.0002488174,-8.18181818181818)(1478.00049762651,-8.36363636363636)(1478.00074642733,-8.54545454545455)(1478.00074642733,-8.72727272727273)(1478.00074642733,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00074642733,-9.27272727272727)(1478.00049762651,-9.45454545454546)(1478.0002488174,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(-0.000248817401863321,-7.81818181818182)(-0.000497626510092015,-7.63636363636364)(-0.000746427325097138,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000746427325097138,-7.09090909090909)(-0.000746427325097138,-6.90909090909091)(-0.000746427325097138,-6.72727272727273)(-0.000746427325097138,-6.54545454545455)(-0.000497626510092015,-6.36363636363636)(-0.000248817401863321,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-6.27272727272727)(14.9292929292929,-6.27272727272727)(29.8585858585859,-6.33333333333333)(37.3232323232323,-6.36363636363636)(44.7878787878788,-6.39393939393939)(59.7171717171717,-6.51515151515151)(67.1818181818182,-6.54545454545455)(74.6464646464647,-6.57575757575758)(89.5757575757576,-6.6969696969697)(93.3080808080808,-6.72727272727273)(104.505050505051,-6.81818181818182)(115.70202020202,-6.90909090909091)(119.434343434343,-6.93939393939394)(134.363636363636,-7)(149.292929292929,-7.06060606060606)(156.757575757576,-7.09090909090909)(164.222222222222,-7.12121212121212)(179.151515151515,-7.18181818181818)(194.080808080808,-7.18181818181818)(209.010101010101,-7.12121212121212)(216.474747474747,-7.09090909090909)(223.939393939394,-7.06060606060606)(238.868686868687,-7)(253.79797979798,-7)(268.727272727273,-6.93939393939394)(276.191919191919,-6.90909090909091)(283.656565656566,-6.87878787878788)(298.585858585859,-6.81818181818182)(313.515151515152,-6.81818181818182)(328.444444444444,-6.75757575757576)(335.909090909091,-6.72727272727273)(343.373737373737,-6.6969696969697)(358.30303030303,-6.63636363636364)(373.232323232323,-6.63636363636364)(388.161616161616,-6.63636363636364)(403.090909090909,-6.63636363636364)(418.020202020202,-6.63636363636364)(432.949494949495,-6.63636363636364)(447.878787878788,-6.63636363636364)(462.808080808081,-6.63636363636364)(477.737373737374,-6.63636363636364)(492.666666666667,-6.63636363636364)(507.59595959596,-6.6969696969697)(515.060606060606,-6.72727272727273)(522.525252525253,-6.75757575757576)(537.454545454546,-6.87878787878788)(541.186868686869,-6.90909090909091)(552.383838383838,-7)(559.848484848485,-7.09090909090909)(567.313131313131,-7.18181818181818)(578.510101010101,-7.27272727272727)(582.242424242424,-7.3030303030303)(597.171717171717,-7.42424242424243)(600.90404040404,-7.45454545454546)(612.10101010101,-7.54545454545455)(619.565656565657,-7.63636363636364)(627.030303030303,-7.72727272727273)(634.494949494949,-7.81818181818182)(641.959595959596,-7.95454545454546)(644.447811447811,-8)(654.400673400673,-8.18181818181818)(656.888888888889,-8.22727272727273)(664.353535353535,-8.36363636363636)(671.818181818182,-8.45454545454545)(683.015151515152,-8.54545454545455)(686.747474747475,-8.57575757575757)(701.676767676768,-8.6969696969697)(709.141414141414,-8.72727272727273)(716.606060606061,-8.75757575757576)(731.535353535354,-8.81818181818182)(746.464646464646,-8.81818181818182)(757.661616161616,-8.72727272727273)(761.393939393939,-8.68181818181818)(768.858585858586,-8.54545454545455)(773.835016835017,-8.36363636363636)(776.323232323232,-8.31818181818182)(783.787878787879,-8.18181818181818)(791.252525252525,-8.09090909090909)(798.717171717172,-8)(806.181818181818,-7.90909090909091)(817.378787878788,-7.81818181818182)(821.111111111111,-7.78787878787879)(836.040404040404,-7.66666666666667)(843.505050505051,-7.63636363636364)(850.969696969697,-7.60606060606061)(865.89898989899,-7.48484848484849)(873.363636363636,-7.45454545454546)(880.828282828283,-7.42424242424243)(895.757575757576,-7.3030303030303)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(925.616161616162,-7.18181818181818)(940.545454545455,-7.12121212121212)(948.010101010101,-7.09090909090909)(955.474747474747,-7.06060606060606)(970.40404040404,-7)(985.333333333333,-6.93939393939394)(992.79797979798,-6.90909090909091)(1000.26262626263,-6.87878787878788)(1015.19191919192,-6.81818181818182)(1030.12121212121,-6.81818181818182)(1045.05050505051,-6.81818181818182)(1059.9797979798,-6.81818181818182)(1074.90909090909,-6.81818181818182)(1089.83838383838,-6.81818181818182)(1104.76767676768,-6.81818181818182)(1119.69696969697,-6.81818181818182)(1134.62626262626,-6.81818181818182)(1149.55555555556,-6.81818181818182)(1164.48484848485,-6.75757575757576)(1171.94949494949,-6.72727272727273)(1179.41414141414,-6.6969696969697)(1194.34343434343,-6.63636363636364)(1209.27272727273,-6.63636363636364)(1224.20202020202,-6.63636363636364)(1239.13131313131,-6.63636363636364)(1254.06060606061,-6.63636363636364)(1268.9898989899,-6.6969696969697)(1276.45454545455,-6.72727272727273)(1283.91919191919,-6.75757575757576)(1298.84848484848,-6.81818181818182)(1313.77777777778,-6.87878787878788)(1317.5101010101,-6.90909090909091)(1328.70707070707,-7)(1339.90404040404,-7.09090909090909)(1343.63636363636,-7.12121212121212)(1356.07744107744,-7.27272727272727)(1358.56565656566,-7.3030303030303)(1371.00673400673,-7.45454545454546)(1373.49494949495,-7.5)(1384.69191919192,-7.63636363636364)(1388.42424242424,-7.66666666666667)(1403.35353535354,-7.78787878787879)(1407.08585858586,-7.81818181818182)(1418.28282828283,-7.90909090909091)(1425.74747474747,-8)(1433.21212121212,-8.09090909090909)(1444.40909090909,-8.18181818181818)(1448.14141414141,-8.21212121212121)(1463.07070707071,-8.27272727272727)(1478,-8.27272727272727)(1478.00012440663,-8.36363636363636)(1478.00037321366,-8.54545454545455)(1478.00037321366,-8.72727272727273)(1478.00037321366,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00037321366,-9.27272727272727)(1478.00012440663,-9.45454545454546)(1478,-9.54545454545455)(1463.07070707071,-9.60606060606061)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.66666666666667)(1433.21212121212,-9.78787878787879)(1429.4797979798,-9.81818181818182)(1418.28282828283,-9.90909090909091)(1407.08585858586,-10)(1403.35353535354,-10.030303030303)(1388.42424242424,-10.1515151515152)(1384.69191919192,-10.1818181818182)(1373.49494949495,-10.2727272727273)(1362.29797979798,-10.3636363636364)(1358.56565656566,-10.3939393939394)(1343.63636363636,-10.4545454545455)(1328.70707070707,-10.5151515151515)(1321.24242424242,-10.5454545454545)(1313.77777777778,-10.5757575757576)(1298.84848484848,-10.6363636363636)(1283.91919191919,-10.6363636363636)(1268.9898989899,-10.6363636363636)(1254.06060606061,-10.6363636363636)(1239.13131313131,-10.6363636363636)(1224.20202020202,-10.6363636363636)(1209.27272727273,-10.5757575757576)(1201.80808080808,-10.5454545454545)(1194.34343434343,-10.5151515151515)(1179.41414141414,-10.4545454545455)(1164.48484848485,-10.4545454545455)(1149.55555555556,-10.4545454545455)(1134.62626262626,-10.4545454545455)(1119.69696969697,-10.4545454545455)(1104.76767676768,-10.4545454545455)(1089.83838383838,-10.4545454545455)(1074.90909090909,-10.4545454545455)(1059.9797979798,-10.4545454545455)(1045.05050505051,-10.4545454545455)(1030.12121212121,-10.4545454545455)(1015.19191919192,-10.5151515151515)(1007.72727272727,-10.5454545454545)(1000.26262626263,-10.5757575757576)(985.333333333333,-10.6363636363636)(970.40404040404,-10.6363636363636)(955.474747474747,-10.6363636363636)(940.545454545455,-10.6363636363636)(925.616161616162,-10.6363636363636)(910.686868686869,-10.6363636363636)(895.757575757576,-10.6363636363636)(880.828282828283,-10.6363636363636)(865.89898989899,-10.6363636363636)(850.969696969697,-10.6363636363636)(836.040404040404,-10.6363636363636)(821.111111111111,-10.6363636363636)(806.181818181818,-10.5757575757576)(798.717171717172,-10.5454545454545)(791.252525252525,-10.5151515151515)(776.323232323232,-10.4545454545455)(761.393939393939,-10.4545454545455)(746.464646464646,-10.3939393939394)(739,-10.3636363636364)(731.535353535354,-10.3333333333333)(716.606060606061,-10.2727272727273)(701.676767676768,-10.2727272727273)(686.747474747475,-10.2727272727273)(671.818181818182,-10.2727272727273)(656.888888888889,-10.2727272727273)(641.959595959596,-10.2727272727273)(627.030303030303,-10.2727272727273)(612.10101010101,-10.2727272727273)(597.171717171717,-10.2727272727273)(582.242424242424,-10.2121212121212)(574.777777777778,-10.1818181818182)(567.313131313131,-10.1515151515152)(552.383838383838,-10.0909090909091)(537.454545454546,-10.030303030303)(529.989898989899,-10)(522.525252525253,-9.96969696969697)(507.59595959596,-9.90909090909091)(492.666666666667,-9.84848484848485)(485.20202020202,-9.81818181818182)(477.737373737374,-9.78787878787879)(462.808080808081,-9.72727272727273)(447.878787878788,-9.72727272727273)(432.949494949495,-9.66666666666667)(425.484848484849,-9.63636363636364)(418.020202020202,-9.60606060606061)(403.090909090909,-9.54545454545455)(388.161616161616,-9.54545454545455)(373.232323232323,-9.54545454545455)(358.30303030303,-9.54545454545455)(343.373737373737,-9.54545454545455)(328.444444444444,-9.60606060606061)(320.979797979798,-9.63636363636364)(313.515151515152,-9.66666666666667)(298.585858585859,-9.72727272727273)(283.656565656566,-9.72727272727273)(268.727272727273,-9.72727272727273)(253.79797979798,-9.72727272727273)(238.868686868687,-9.72727272727273)(223.939393939394,-9.72727272727273)(209.010101010101,-9.66666666666667)(201.545454545455,-9.63636363636364)(194.080808080808,-9.60606060606061)(179.151515151515,-9.54545454545455)(164.222222222222,-9.48484848484848)(160.489898989899,-9.45454545454546)(149.292929292929,-9.36363636363636)(138.09595959596,-9.27272727272727)(134.363636363636,-9.24242424242424)(119.434343434343,-9.12121212121212)(115.70202020202,-9.09090909090909)(104.505050505051,-9)(97.040404040404,-8.90909090909091)(89.5757575757576,-8.81818181818182)(82.1111111111111,-8.72727272727273)(74.6464646464647,-8.63636363636364)(67.1818181818182,-8.54545454545455)(59.7171717171717,-8.40909090909091)(57.2289562289562,-8.36363636363636)(47.2760942760943,-8.18181818181818)(44.7878787878788,-8.09090909090909)(42.2996632996633,-8)(29.8585858585859,-7.84848484848485)(26.1262626262626,-7.81818181818182)(14.9292929292929,-7.72727272727273)(0,-7.72727272727273)(-0.000124406627521346,-7.63636363636364)(-0.000373213662548569,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000373213662548569,-7.09090909090909)(-0.000373213662548569,-6.90909090909091)(-0.000373213662548569,-6.72727272727273)(-0.000373213662548569,-6.54545454545455)(-0.000124406627521346,-6.36363636363636)(0,-6.27272727272727)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1313.77777777778,-8.68181818181818)(1316.26599326599,-8.72727272727273)(1321.24242424242,-8.90909090909091)(1321.24242424242,-9.09090909090909)(1313.77777777778,-9.22727272727273)(1311.28956228956,-9.27272727272727)(1298.84848484848,-9.42424242424243)(1291.38383838384,-9.45454545454546)(1283.91919191919,-9.48484848484848)(1268.9898989899,-9.60606060606061)(1261.52525252525,-9.63636363636364)(1254.06060606061,-9.66666666666667)(1239.13131313131,-9.72727272727273)(1224.20202020202,-9.72727272727273)(1209.27272727273,-9.72727272727273)(1194.34343434343,-9.78787878787879)(1186.87878787879,-9.81818181818182)(1179.41414141414,-9.84848484848485)(1164.48484848485,-9.90909090909091)(1149.55555555556,-9.90909090909091)(1134.62626262626,-9.90909090909091)(1119.69696969697,-9.90909090909091)(1104.76767676768,-9.90909090909091)(1089.83838383838,-9.90909090909091)(1074.90909090909,-9.90909090909091)(1059.9797979798,-9.90909090909091)(1045.05050505051,-9.90909090909091)(1030.12121212121,-9.90909090909091)(1015.19191919192,-9.90909090909091)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.84848484848485)(977.868686868687,-9.81818181818182)(970.40404040404,-9.78787878787879)(955.474747474747,-9.72727272727273)(940.545454545455,-9.72727272727273)(925.616161616162,-9.66666666666667)(918.151515151515,-9.63636363636364)(910.686868686869,-9.60606060606061)(895.757575757576,-9.48484848484848)(888.292929292929,-9.45454545454546)(880.828282828283,-9.42424242424243)(865.89898989899,-9.3030303030303)(862.166666666667,-9.27272727272727)(850.969696969697,-9.13636363636364)(848.481481481482,-9.09090909090909)(848.481481481482,-8.90909090909091)(850.969696969697,-8.86363636363636)(858.434343434343,-8.72727272727273)(865.89898989899,-8.63636363636364)(873.363636363636,-8.54545454545455)(880.828282828283,-8.45454545454545)(888.292929292929,-8.36363636363636)(895.757575757576,-8.27272727272727)(903.222222222222,-8.18181818181818)(910.686868686869,-8.09090909090909)(921.883838383838,-8)(925.616161616162,-7.96969696969697)(940.545454545455,-7.90909090909091)(955.474747474747,-7.84848484848485)(962.939393939394,-7.81818181818182)(970.40404040404,-7.78787878787879)(985.333333333333,-7.72727272727273)(1000.26262626263,-7.66666666666667)(1007.72727272727,-7.63636363636364)(1015.19191919192,-7.60606060606061)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.56818181818182)(1059.9797979798,-7.48484848484849)(1074.90909090909,-7.48484848484849)(1089.83838383838,-7.48484848484849)(1104.76767676768,-7.60606060606061)(1112.23232323232,-7.63636363636364)(1119.69696969697,-7.66666666666667)(1134.62626262626,-7.72727272727273)(1149.55555555556,-7.78787878787879)(1157.0202020202,-7.81818181818182)(1164.48484848485,-7.84848484848485)(1179.41414141414,-7.90909090909091)(1194.34343434343,-7.90909090909091)(1209.27272727273,-7.96969696969697)(1216.73737373737,-8)(1224.20202020202,-8.03030303030303)(1239.13131313131,-8.09090909090909)(1254.06060606061,-8.09090909090909)(1268.9898989899,-8.15151515151515)(1272.72222222222,-8.18181818181818)(1283.91919191919,-8.27272727272727)(1291.38383838384,-8.36363636363636)(1298.84848484848,-8.45454545454545)(1306.31313131313,-8.54545454545455)(1313.77777777778,-8.68181818181818)};

\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0)(1268.9898989899,-8.18181818181818)(1254.06060606061,-9.27272727272727)(1164.48484848485,-8.54545454545455)(1149.55555555556,-8.18181818181818)(1134.62626262626,-7.81818181818182)(1119.69696969697,-8.90909090909091)(1104.76767676768,-7.63636363636364)(1074.90909090909,-7.45454545454546)(1074.90909090909,-9.09090909090909)(1059.9797979798,-9.09090909090909)(1030.12121212121,-7.27272727272727)(1015.19191919192,-7.27272727272727)(970.40404040404,-9.27272727272727)(910.686868686869,-7.09090909090909)(880.828282828283,-9.09090909090909)(865.89898989899,-9.09090909090909)(865.89898989899,-7.09090909090909)(791.252525252525,-8.90909090909091)(791.252525252525,-7.27272727272727)(761.393939393939,-7.27272727272727)(746.464646464646,-8.72727272727273)(716.606060606061,-8.54545454545455)(686.747474747475,-7.63636363636364)(671.818181818182,-8.18181818181818)(656.888888888889,-8)(597.171717171717,-7.09090909090909)(537.454545454546,-8.72727272727273)(223.939393939394,-8.36363636363636)(194.080808080808,-7.09090909090909) 
};

\addplot [
color=lime,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (0,-9.45454545454546)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-22 figurefactory/files/limno_bgape_pp_60_1.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_60_0.tex
@@
 \addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=1.6pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (0,-9.45454545454546)(209.010101010101,-8.18181818181818)(268.727272727273,-8.72727272727273)(298.585858585859,-7.81818181818182)(313.515151515152,-7.81818181818182)(313.515151515152,-8.90909090909091)(373.232323232323,-9.09090909090909)(388.161616161616,-9.09090909090909)(418.020202020202,-7.63636363636364)(492.666666666667,-9.27272727272727)(522.525252525253,-9.27272727272727)(522.525252525253,-7.81818181818182)(567.313131313131,-8)(567.313131313131,-9.09090909090909)(836.040404040404,-8.36363636363636)(836.040404040404,-9.63636363636364)(850.969696969697,-9.81818181818182)(865.89898989899,-8)(940.545454545455,-10.1818181818182)(955.474747474747,-10.1818181818182)(1074.90909090909,-10.3636363636364)(1209.27272727273,-7.63636363636364)(1224.20202020202,-10.1818181818182)(1239.13131313131,-10.1818181818182)(1283.91919191919,-7.81818181818182)(1313.77777777778,-10)(1358.56565656566,-9.81818181818182)(1358.56565656566,-8.18181818181818)(1403.35353535354,-8.72727272727273)(1403.35353535354,-9.27272727272727)(1418.28282828283,-8.90909090909091)
+};
+
+\addplot [
 color=lime,

### 2013-03-22 figurefactory/files/limno_bgape_pp_60_2.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_60_1.tex
@@
 \addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1313.77777777778,-8.68181818181818)(1316.26599326599,-8.72727272727273)(1321.24242424242,-8.90909090909091)(1321.24242424242,-9.09090909090909)(1313.77777777778,-9.22727272727273)(1311.28956228956,-9.27272727272727)(1298.84848484848,-9.42424242424243)(1291.38383838384,-9.45454545454546)(1283.91919191919,-9.48484848484848)(1268.9898989899,-9.60606060606061)(1261.52525252525,-9.63636363636364)(1254.06060606061,-9.66666666666667)(1239.13131313131,-9.72727272727273)(1224.20202020202,-9.72727272727273)(1209.27272727273,-9.72727272727273)(1194.34343434343,-9.78787878787879)(1186.87878787879,-9.81818181818182)(1179.41414141414,-9.84848484848485)(1164.48484848485,-9.90909090909091)(1149.55555555556,-9.90909090909091)(1134.62626262626,-9.90909090909091)(1119.69696969697,-9.90909090909091)(1104.76767676768,-9.90909090909091)(1089.83838383838,-9.90909090909091)(1074.90909090909,-9.90909090909091)(1059.9797979798,-9.90909090909091)(1045.05050505051,-9.90909090909091)(1030.12121212121,-9.90909090909091)(1015.19191919192,-9.90909090909091)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.84848484848485)(977.868686868687,-9.81818181818182)(970.40404040404,-9.78787878787879)(955.474747474747,-9.72727272727273)(940.545454545455,-9.72727272727273)(925.616161616162,-9.66666666666667)(918.151515151515,-9.63636363636364)(910.686868686869,-9.60606060606061)(895.757575757576,-9.48484848484848)(888.292929292929,-9.45454545454546)(880.828282828283,-9.42424242424243)(865.89898989899,-9.3030303030303)(862.166666666667,-9.27272727272727)(850.969696969697,-9.13636363636364)(848.481481481482,-9.09090909090909)(848.481481481482,-8.90909090909091)(850.969696969697,-8.86363636363636)(858.434343434343,-8.72727272727273)(865.89898989899,-8.63636363636364)(873.363636363636,-8.54545454545455)(880.828282828283,-8.45454545454545)(888.292929292929,-8.36363636363636)(895.757575757576,-8.27272727272727)(903.222222222222,-8.18181818181818)(910.686868686869,-8.09090909090909)(921.883838383838,-8)(925.616161616162,-7.96969696969697)(940.545454545455,-7.90909090909091)(955.474747474747,-7.84848484848485)(962.939393939394,-7.81818181818182)(970.40404040404,-7.78787878787879)(985.333333333333,-7.72727272727273)(1000.26262626263,-7.66666666666667)(1007.72727272727,-7.63636363636364)(1015.19191919192,-7.60606060606061)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.56818181818182)(1059.9797979798,-7.48484848484849)(1074.90909090909,-7.48484848484849)(1089.83838383838,-7.48484848484849)(1104.76767676768,-7.60606060606061)(1112.23232323232,-7.63636363636364)(1119.69696969697,-7.66666666666667)(1134.62626262626,-7.72727272727273)(1149.55555555556,-7.78787878787879)(1157.0202020202,-7.81818181818182)(1164.48484848485,-7.84848484848485)(1179.41414141414,-7.90909090909091)(1194.34343434343,-7.90909090909091)(1209.27272727273,-7.96969696969697)(1216.73737373737,-8)(1224.20202020202,-8.03030303030303)(1239.13131313131,-8.09090909090909)(1254.06060606061,-8.09090909090909)(1268.9898989899,-8.15151515151515)(1272.72222222222,-8.18181818181818)(1283.91919191919,-8.27272727272727)(1291.38383838384,-8.36363636363636)(1298.84848484848,-8.45454545454545)(1306.31313131313,-8.54545454545455)(1313.77777777778,-8.68181818181818)};
+
+\addplot [
+draw=red!50!white,
+line width=0.6pt,
+forget plot
+]
+coordinates{
+ (0,-9.45454545454546)(209.010101010101,-8.18181818181818)(268.727272727273,-8.72727272727273)(298.585858585859,-7.81818181818182)(313.515151515152,-7.81818181818182)(313.515151515152,-8.90909090909091)(373.232323232323,-9.09090909090909)(388.161616161616,-9.09090909090909)(418.020202020202,-7.63636363636364)(492.666666666667,-9.27272727272727)(522.525252525253,-9.27272727272727)(522.525252525253,-7.81818181818182)(567.313131313131,-8)(567.313131313131,-9.09090909090909)(836.040404040404,-8.36363636363636)(836.040404040404,-9.63636363636364)(850.969696969697,-9.81818181818182)(865.89898989899,-8)(940.545454545455,-10.1818181818182)(955.474747474747,-10.1818181818182)(1074.90909090909,-10.3636363636364)(1209.27272727273,-7.63636363636364)(1224.20202020202,-10.1818181818182)(1239.13131313131,-10.1818181818182)(1283.91919191919,-7.81818181818182)(1313.77777777778,-10)(1358.56565656566,-9.81818181818182)(1358.56565656566,-8.18181818181818)(1403.35353535354,-8.72727272727273)(1403.35353535354,-9.27272727272727)(1418.28282828283,-8.90909090909091)
+};
 
@@
 
+\addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=3pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (1418.28282828283,-8.90909090909091)
+};
+
 \end{axis}

### 2013-03-22 figurefactory/files/limno_bgape_pp_90_0.tex
Add batch/path planning; add summary; finish first draft

% This file was created by matlab2tikz v0.2.3.
% Copyright (c) 2008--2012, Nico Schlömer <nico.schloemer@gmail.com>
% All rights reserved.
% 
% 
%

% defining custom colors
\definecolor{locol}{rgb}{0.26, 0.45, 0.65}

\begin{tikzpicture}

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

\addplot [fill=locol,draw=none,forget plot] coordinates{ (0,0)(14.9292929292929,0)(29.8585858585859,0)(44.7878787878788,0)(59.7171717171717,0)(74.6464646464647,0)(89.5757575757576,0)(104.505050505051,0)(119.434343434343,0)(134.363636363636,0)(149.292929292929,0)(164.222222222222,0)(179.151515151515,0)(194.080808080808,0)(209.010101010101,0)(223.939393939394,0)(238.868686868687,0)(253.79797979798,0)(268.727272727273,0)(283.656565656566,0)(298.585858585859,0)(313.515151515152,0)(328.444444444444,0)(343.373737373737,0)(358.30303030303,0)(373.232323232323,0)(388.161616161616,0)(403.090909090909,0)(418.020202020202,0)(432.949494949495,0)(447.878787878788,0)(462.808080808081,0)(477.737373737374,0)(492.666666666667,0)(507.59595959596,0)(522.525252525253,0)(537.454545454546,0)(552.383838383838,0)(567.313131313131,0)(582.242424242424,0)(597.171717171717,0)(612.10101010101,0)(627.030303030303,0)(641.959595959596,0)(656.888888888889,0)(671.818181818182,0)(686.747474747475,0)(701.676767676768,0)(716.606060606061,0)(731.535353535354,0)(746.464646464646,0)(761.393939393939,0)(776.323232323232,0)(791.252525252525,0)(806.181818181818,0)(821.111111111111,0)(836.040404040404,0)(850.969696969697,0)(865.89898989899,0)(880.828282828283,0)(895.757575757576,0)(910.686868686869,0)(925.616161616162,0)(940.545454545455,0)(955.474747474747,0)(970.40404040404,0)(985.333333333333,0)(1000.26262626263,0)(1015.19191919192,0)(1030.12121212121,0)(1045.05050505051,0)(1059.9797979798,0)(1074.90909090909,0)(1089.83838383838,0)(1104.76767676768,0)(1119.69696969697,0)(1134.62626262626,0)(1149.55555555556,0)(1164.48484848485,0)(1179.41414141414,0)(1194.34343434343,0)(1209.27272727273,0)(1224.20202020202,0)(1239.13131313131,0)(1254.06060606061,0)(1268.9898989899,0)(1283.91919191919,0)(1298.84848484848,0)(1313.77777777778,0)(1328.70707070707,0)(1343.63636363636,0)(1358.56565656566,0)(1373.49494949495,0)(1388.42424242424,0)(1403.35353535354,0)(1418.28282828283,0)(1433.21212121212,0)(1448.14141414141,0)(1463.07070707071,0)(1478,0)(1478,-0.181818181818183)(1478,-0.363636363636363)(1478,-0.545454545454547)(1478,-0.727272727272727)(1478,-0.90909090909091)(1478,-1.09090909090909)(1478,-1.27272727272727)(1478,-1.45454545454545)(1478,-1.63636363636364)(1478,-1.81818181818182)(1478,-2)(1478,-2.18181818181818)(1478,-2.36363636363636)(1478,-2.54545454545455)(1478,-2.72727272727273)(1478,-2.90909090909091)(1478,-3.09090909090909)(1478,-3.27272727272727)(1478,-3.45454545454546)(1478,-3.63636363636364)(1478,-3.81818181818182)(1478,-4)(1478,-4.18181818181818)(1478,-4.36363636363636)(1478,-4.54545454545455)(1478,-4.72727272727273)(1478,-4.90909090909091)(1478,-5.09090909090909)(1478,-5.27272727272727)(1478,-5.45454545454546)(1478,-5.63636363636364)(1478,-5.81818181818182)(1478,-6)(1478,-6.18181818181818)(1478,-6.36363636363636)(1478,-6.54545454545455)(1478,-6.72727272727273)(1478,-6.90909090909091)(1478,-7.09090909090909)(1478,-7.27272727272727)(1478,-7.45454545454546)(1478,-7.63636363636364)(1478,-7.81818181818182)(1478,-8)(1478,-8.18181818181818)(1478.00008294006,-8.36363636363636)(1478.00033175469,-8.54545454545455)(1478.00058056104,-8.72727272727273)(1478.00074642733,-8.90909090909091)(1478.00074642733,-9.09090909090909)(1478.00074642733,-9.27272727272727)(1478.00049762651,-9.45454545454546)(1478.0002488174,-9.63636363636364)(1478,-9.81818181818182)(1478,-10)(1478,-10.1818181818182)(1478,-10.3636363636364)(1478,-10.5454545454545)(1478,-10.7272727272727)(1478,-10.9090909090909)(1478,-11.0909090909091)(1478,-11.2727272727273)(1478,-11.4545454545455)(1478,-11.6363636363636)(1478,-11.8181818181818)(1478,-12)(1478,-12.1818181818182)(1478,-12.3636363636364)(1478,-12.5454545454545)(1478,-12.7272727272727)(1478,-12.9090909090909)(1478,-13.0909090909091)(1478,-13.2727272727273)(1478,-13.4545454545455)(1478,-13.6363636363636)(1478,-13.8181818181818)(1478,-14)(1478,-14.1818181818182)(1478,-14.3636363636364)(1478,-14.5454545454545)(1478,-14.7272727272727)(1478,-14.9090909090909)(1478,-15.0909090909091)(1478,-15.2727272727273)(1478,-15.4545454545455)(1478,-15.6363636363636)(1478,-15.8181818181818)(1478,-16)(1478,-16.1818181818182)(1478,-16.3636363636364)(1478,-16.5454545454545)(1478,-16.7272727272727)(1478,-16.9090909090909)(1478,-17.0909090909091)(1478,-17.2727272727273)(1478,-17.4545454545455)(1478,-17.6363636363636)(1478,-17.8181818181818)(1478,-18)(1463.07070707071,-18)(1448.14141414141,-18)(1433.21212121212,-18)(1418.28282828283,-18)(1403.35353535354,-18)(1388.42424242424,-18)(1373.49494949495,-18)(1358.56565656566,-18)(1343.63636363636,-18)(1328.70707070707,-18)(1313.77777777778,-18)(1298.84848484848,-18)(1283.91919191919,-18)(1268.9898989899,-18)(1254.06060606061,-18)(1239.13131313131,-18)(1224.20202020202,-18)(1209.27272727273,-18)(1194.34343434343,-18)(1179.41414141414,-18)(1164.48484848485,-18)(1149.55555555556,-18)(1134.62626262626,-18)(1119.69696969697,-18)(1104.76767676768,-18)(1089.83838383838,-18)(1074.90909090909,-18)(1059.9797979798,-18)(1045.05050505051,-18)(1030.12121212121,-18)(1015.19191919192,-18)(1000.26262626263,-18)(985.333333333333,-18)(970.40404040404,-18)(955.474747474747,-18)(940.545454545455,-18)(925.616161616162,-18)(910.686868686869,-18)(895.757575757576,-18)(880.828282828283,-18)(865.89898989899,-18)(850.969696969697,-18)(836.040404040404,-18)(821.111111111111,-18)(806.181818181818,-18)(791.252525252525,-18)(776.323232323232,-18)(761.393939393939,-18)(746.464646464646,-18)(731.535353535354,-18)(716.606060606061,-18)(701.676767676768,-18)(686.747474747475,-18)(671.818181818182,-18)(656.888888888889,-18)(641.959595959596,-18)(627.030303030303,-18)(612.10101010101,-18)(597.171717171717,-18)(582.242424242424,-18)(567.313131313131,-18)(552.383838383838,-18)(537.454545454546,-18)(522.525252525253,-18)(507.59595959596,-18)(492.666666666667,-18)(477.737373737374,-18)(462.808080808081,-18)(447.878787878788,-18)(432.949494949495,-18)(418.020202020202,-18)(403.090909090909,-18)(388.161616161616,-18)(373.232323232323,-18)(358.30303030303,-18)(343.373737373737,-18)(328.444444444444,-18)(313.515151515152,-18)(298.585858585859,-18)(283.656565656566,-18)(268.727272727273,-18)(253.79797979798,-18)(238.868686868687,-18)(223.939393939394,-18)(209.010101010101,-18)(194.080808080808,-18)(179.151515151515,-18)(164.222222222222,-18)(149.292929292929,-18)(134.363636363636,-18)(119.434343434343,-18)(104.505050505051,-18)(89.5757575757576,-18)(74.6464646464647,-18)(59.7171717171717,-18)(44.7878787878788,-18)(29.8585858585859,-18)(14.9292929292929,-18)(0,-18)(0,-17.8181818181818)(0,-17.6363636363636)(0,-17.4545454545455)(0,-17.2727272727273)(0,-17.0909090909091)(0,-16.9090909090909)(0,-16.7272727272727)(0,-16.5454545454545)(0,-16.3636363636364)(0,-16.1818181818182)(0,-16)(0,-15.8181818181818)(0,-15.6363636363636)(0,-15.4545454545455)(0,-15.2727272727273)(0,-15.0909090909091)(0,-14.9090909090909)(0,-14.7272727272727)(0,-14.5454545454545)(0,-14.3636363636364)(0,-14.1818181818182)(0,-14)(0,-13.8181818181818)(0,-13.6363636363636)(0,-13.4545454545455)(0,-13.2727272727273)(0,-13.0909090909091)(0,-12.9090909090909)(0,-12.7272727272727)(0,-12.5454545454545)(0,-12.3636363636364)(0,-12.1818181818182)(0,-12)(0,-11.8181818181818)(0,-11.6363636363636)(0,-11.4545454545455)(0,-11.2727272727273)(0,-11.0909090909091)(0,-10.9090909090909)(0,-10.7272727272727)(0,-10.5454545454545)(0,-10.3636363636364)(0,-10.1818181818182)(0,-10)(0,-9.81818181818182)(0,-9.63636363636364)(0,-9.45454545454546)(0,-9.27272727272727)(0,-9.09090909090909)(0,-8.90909090909091)(0,-8.72727272727273)(0,-8.54545454545455)(0,-8.36363636363636)(0,-8.18181818181818)(0,-8)(-0.000248817401863321,-7.81818181818182)(-0.000497626510092015,-7.63636363636364)(-0.000746427325097138,-7.45454545454546)(-0.000746427325097138,-7.27272727272727)(-0.000746427325097138,-7.09090909090909)(-0.000746427325097138,-6.90909090909091)(-0.000746427325097138,-6.72727272727273)(-0.00066349464153746,-6.54545454545455)(-0.0004146910621731,-6.36363636363636)(-0.000165879189445939,-6.18181818181818)(0,-6)(0,-5.81818181818182)(0,-5.63636363636364)(0,-5.45454545454546)(0,-5.27272727272727)(0,-5.09090909090909)(0,-4.90909090909091)(0,-4.72727272727273)(0,-4.54545454545455)(0,-4.36363636363636)(0,-4.18181818181818)(0,-4)(0,-3.81818181818182)(0,-3.63636363636364)(0,-3.45454545454546)(0,-3.27272727272727)(0,-3.09090909090909)(0,-2.90909090909091)(0,-2.72727272727273)(0,-2.54545454545455)(0,-2.36363636363636)(0,-2.18181818181818)(0,-2)(0,-1.81818181818182)(0,-1.63636363636364)(0,-1.45454545454545)(0,-1.27272727272727)(0,-1.09090909090909)(0,-0.90909090909091)(0,-0.727272727272727)(0,-0.545454545454547)(0,-0.363636363636363)(0,-0.181818181818183)(0,0)};

\addplot [fill=darkgray,draw=none,forget plot] coordinates{ (0,-6.33333333333333)(7.46464646464646,-6.36363636363636)(14.9292929292929,-6.39393939393939)(29.8585858585859,-6.45454545454545)(44.7878787878788,-6.51515151515151)(52.2525252525253,-6.54545454545455)(59.7171717171717,-6.57575757575758)(74.6464646464647,-6.63636363636364)(89.5757575757576,-6.6969696969697)(93.3080808080808,-6.72727272727273)(104.505050505051,-6.81818181818182)(115.70202020202,-6.90909090909091)(119.434343434343,-6.93939393939394)(134.363636363636,-7)(149.292929292929,-7.06060606060606)(156.757575757576,-7.09090909090909)(164.222222222222,-7.12121212121212)(179.151515151515,-7.18181818181818)(194.080808080808,-7.18181818181818)(209.010101010101,-7.18181818181818)(223.939393939394,-7.18181818181818)(238.868686868687,-7.18181818181818)(253.79797979798,-7.18181818181818)(268.727272727273,-7.18181818181818)(283.656565656566,-7.18181818181818)(298.585858585859,-7.18181818181818)(313.515151515152,-7.18181818181818)(328.444444444444,-7.18181818181818)(343.373737373737,-7.18181818181818)(358.30303030303,-7.12121212121212)(365.767676767677,-7.09090909090909)(373.232323232323,-7.06060606060606)(388.161616161616,-7)(403.090909090909,-7)(418.020202020202,-6.93939393939394)(425.484848484849,-6.90909090909091)(432.949494949495,-6.87878787878788)(447.878787878788,-6.81818181818182)(462.808080808081,-6.81818181818182)(477.737373737374,-6.81818181818182)(492.666666666667,-6.81818181818182)(507.59595959596,-6.81818181818182)(522.525252525253,-6.81818181818182)(537.454545454546,-6.87878787878788)(541.186868686869,-6.90909090909091)(552.383838383838,-7)(559.848484848485,-7.09090909090909)(567.313131313131,-7.18181818181818)(578.510101010101,-7.27272727272727)(582.242424242424,-7.3030303030303)(597.171717171717,-7.42424242424243)(600.90404040404,-7.45454545454546)(612.10101010101,-7.54545454545455)(619.565656565657,-7.63636363636364)(627.030303030303,-7.72727272727273)(634.494949494949,-7.81818181818182)(641.959595959596,-7.95454545454546)(644.447811447811,-8)(654.400673400673,-8.18181818181818)(656.888888888889,-8.22727272727273)(664.353535353535,-8.36363636363636)(671.818181818182,-8.45454545454545)(679.282828282828,-8.54545454545455)(686.747474747475,-8.63636363636364)(694.212121212121,-8.72727272727273)(701.676767676768,-8.81818181818182)(712.873737373737,-8.90909090909091)(716.606060606061,-8.93939393939394)(731.535353535354,-9)(746.464646464646,-8.93939393939394)(750.19696969697,-8.90909090909091)(761.393939393939,-8.77272727272727)(765.126262626263,-8.72727272727273)(768.858585858586,-8.54545454545455)(773.835016835017,-8.36363636363636)(776.323232323232,-8.31818181818182)(783.787878787879,-8.18181818181818)(791.252525252525,-8.09090909090909)(798.717171717172,-8)(806.181818181818,-7.90909090909091)(817.378787878788,-7.81818181818182)(821.111111111111,-7.78787878787879)(836.040404040404,-7.66666666666667)(843.505050505051,-7.63636363636364)(850.969696969697,-7.60606060606061)(865.89898989899,-7.48484848484849)(873.363636363636,-7.45454545454546)(880.828282828283,-7.42424242424243)(895.757575757576,-7.3030303030303)(903.222222222222,-7.27272727272727)(910.686868686869,-7.24242424242424)(925.616161616162,-7.18181818181818)(940.545454545455,-7.12121212121212)(948.010101010101,-7.09090909090909)(955.474747474747,-7.06060606060606)(970.40404040404,-7)(985.333333333333,-7)(1000.26262626263,-6.97727272727273)(1015.19191919192,-7)(1030.12121212121,-6.93939393939394)(1037.58585858586,-6.90909090909091)(1045.05050505051,-6.87878787878788)(1059.9797979798,-6.81818181818182)(1074.90909090909,-6.81818181818182)(1089.83838383838,-6.81818181818182)(1104.76767676768,-6.81818181818182)(1119.69696969697,-6.81818181818182)(1134.62626262626,-6.81818181818182)(1149.55555555556,-6.81818181818182)(1164.48484848485,-6.81818181818182)(1179.41414141414,-6.81818181818182)(1194.34343434343,-6.81818181818182)(1209.27272727273,-6.81818181818182)(1224.20202020202,-6.81818181818182)(1239.13131313131,-6.81818181818182)(1254.06060606061,-6.87878787878788)(1261.52525252525,-6.90909090909091)(1268.9898989899,-6.93939393939394)(1283.91919191919,-7.06060606060606)(1291.38383838384,-7.09090909090909)(1298.84848484848,-7.12121212121212)(1313.77777777778,-7.24242424242424)(1317.5101010101,-7.27272727272727)(1328.70707070707,-7.36363636363636)(1339.90404040404,-7.45454545454546)(1343.63636363636,-7.48484848484849)(1358.56565656566,-7.60606060606061)(1362.29797979798,-7.63636363636364)(1373.49494949495,-7.72727272727273)(1380.9595959596,-7.81818181818182)(1388.42424242424,-7.90909090909091)(1399.62121212121,-8)(1403.35353535354,-8.03030303030303)(1418.28282828283,-8.15151515151515)(1422.01515151515,-8.18181818181818)(1433.21212121212,-8.27272727272727)(1444.40909090909,-8.36363636363636)(1448.14141414141,-8.39393939393939)(1463.07070707071,-8.51515151515152)(1470.53535353535,-8.54545454545455)(1478,-8.57575757575757)(1478.00020734323,-8.72727272727273)(1478.00037321366,-8.90909090909091)(1478.00037321366,-9.09090909090909)(1478.00037321366,-9.27272727272727)(1478.00012440663,-9.45454545454546)(1478,-9.54545454545455)(1463.07070707071,-9.60606060606061)(1455.60606060606,-9.63636363636364)(1448.14141414141,-9.66666666666667)(1433.21212121212,-9.78787878787879)(1429.4797979798,-9.81818181818182)(1418.28282828283,-9.90909090909091)(1407.08585858586,-10)(1403.35353535354,-10.030303030303)(1388.42424242424,-10.0909090909091)(1373.49494949495,-10.1590909090909)(1366.0303030303,-10.1818181818182)(1358.56565656566,-10.2121212121212)(1343.63636363636,-10.2727272727273)(1328.70707070707,-10.2954545454545)(1313.77777777778,-10.2954545454545)(1298.84848484848,-10.2954545454545)(1283.91919191919,-10.2727272727273)(1268.9898989899,-10.2727272727273)(1254.06060606061,-10.2121212121212)(1246.59595959596,-10.1818181818182)(1239.13131313131,-10.1666666666667)(1224.20202020202,-10.1666666666667)(1216.73737373737,-10.1818181818182)(1209.27272727273,-10.2121212121212)(1194.34343434343,-10.2727272727273)(1179.41414141414,-10.2727272727273)(1164.48484848485,-10.3333333333333)(1157.0202020202,-10.3636363636364)(1149.55555555556,-10.3939393939394)(1134.62626262626,-10.4545454545455)(1119.69696969697,-10.4545454545455)(1104.76767676768,-10.4545454545455)(1089.83838383838,-10.3939393939394)(1074.90909090909,-10.3939393939394)(1059.9797979798,-10.3939393939394)(1045.05050505051,-10.4545454545455)(1030.12121212121,-10.3939393939394)(1022.65656565657,-10.3636363636364)(1015.19191919192,-10.3333333333333)(1000.26262626263,-10.2727272727273)(985.333333333333,-10.2727272727273)(970.40404040404,-10.2121212121212)(962.939393939394,-10.1818181818182)(955.474747474747,-10.1666666666667)(940.545454545455,-10.1636363636364)(925.616161616162,-10.1590909090909)(910.686868686869,-10.1515151515152)(895.757575757576,-10.0909090909091)(880.828282828283,-10.0909090909091)(869.631313131313,-10)(865.89898989899,-9.96969696969697)(850.969696969697,-9.93181818181818)(836.040404040404,-9.88636363636364)(821.111111111111,-9.88636363636364)(809.914141414141,-9.81818181818182)(806.181818181818,-9.78787878787879)(791.252525252525,-9.66666666666667)(783.787878787879,-9.63636363636364)(776.323232323232,-9.60606060606061)(761.393939393939,-9.54545454545455)(746.464646464646,-9.48484848484848)(739,-9.45454545454546)(731.535353535354,-9.42424242424243)(716.606060606061,-9.42424242424243)(709.141414141414,-9.45454545454546)(701.676767676768,-9.48484848484848)(686.747474747475,-9.54545454545455)(671.818181818182,-9.60606060606061)(664.353535353535,-9.63636363636364)(656.888888888889,-9.66666666666667)(641.959595959596,-9.72727272727273)(627.030303030303,-9.72727272727273)(612.10101010101,-9.72727272727273)(597.171717171717,-9.66666666666667)(589.707070707071,-9.63636363636364)(582.242424242424,-9.60606060606061)(567.313131313131,-9.54545454545455)(552.383838383838,-9.54545454545455)(541.186868686869,-9.45454545454546)(537.454545454546,-9.42424242424243)(522.525252525253,-9.36363636363636)(511.328282828283,-9.27272727272727)(507.59595959596,-9.24242424242424)(492.666666666667,-9.24242424242424)(477.737373737374,-9.18181818181818)(462.808080808081,-9.18181818181818)(447.878787878788,-9.12121212121212)(440.414141414141,-9.09090909090909)(432.949494949495,-9.06060606060606)(418.020202020202,-9)(403.090909090909,-8.93939393939394)(395.626262626263,-8.90909090909091)(388.161616161616,-8.87878787878788)(373.232323232323,-8.81818181818182)(358.30303030303,-8.81818181818182)(343.373737373737,-8.81818181818182)(328.444444444444,-8.75757575757576)(320.979797979798,-8.72727272727273)(313.515151515152,-8.6969696969697)(298.585858585859,-8.6969696969697)(283.656565656566,-8.6969696969697)(276.191919191919,-8.72727272727273)(268.727272727273,-8.75757575757576)(253.79797979798,-8.75757575757576)(238.868686868687,-8.87878787878788)(231.40404040404,-8.90909090909091)(223.939393939394,-8.93939393939394)(209.010101010101,-9)(194.080808080808,-9)(179.151515151515,-9)(164.222222222222,-9)(149.292929292929,-9)(134.363636363636,-9)(119.434343434343,-9)(104.505050505051,-8.93939393939394)(100.772727272727,-8.90909090909091)(89.5757575757576,-8.81818181818182)(82.1111111111111,-8.72727272727273)(74.6464646464647,-8.63636363636364)(67.1818181818182,-8.54545454545455)(59.7171717171717,-8.40909090909091)(57.2289562289562,-8.36363636363636)(47.2760942760943,-8.18181818181818)(44.7878787878788,-8.09090909090909)(42.2996632996633,-8)(29.8585858585859,-7.84848484848485)(26.1262626262626,-7.81818181818182)(14.9292929292929,-7.72727272727273)(0,-7.72727272727273)(-0.000124406627521346,-7.63636363636364)(-0.000373213662548569,-7.45454545454546)(-0.000373213662548569,-7.27272727272727)(-0.000373213662548569,-7.09090909090909)(-0.000373213662548569,-6.90909090909091)(-0.000373213662548569,-6.72727272727273)(-0.00029027890567471,-6.54545454545455)(-4.14691062186359e-05,-6.36363636363636)(0,-6.33333333333333)};

\addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1373.49494949495,-8.68181818181818)(1377.22727272727,-8.72727272727273)(1384.69191919192,-8.90909090909091)(1384.69191919192,-9.09090909090909)(1377.22727272727,-9.27272727272727)(1373.49494949495,-9.31818181818182)(1366.0303030303,-9.45454545454546)(1358.56565656566,-9.59090909090909)(1354.83333333333,-9.63636363636364)(1343.63636363636,-9.72727272727273)(1328.70707070707,-9.77272727272727)(1313.77777777778,-9.77272727272727)(1306.31313131313,-9.81818181818182)(1298.84848484848,-9.84848484848485)(1283.91919191919,-9.84848484848485)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.88636363636364)(1239.13131313131,-9.87272727272727)(1224.20202020202,-9.87272727272727)(1209.27272727273,-9.88636363636364)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.90909090909091)(1149.55555555556,-9.90909090909091)(1134.62626262626,-9.90909090909091)(1119.69696969697,-9.90909090909091)(1104.76767676768,-9.90909090909091)(1089.83838383838,-9.90909090909091)(1074.90909090909,-9.90909090909091)(1059.9797979798,-9.90909090909091)(1045.05050505051,-9.90909090909091)(1030.12121212121,-9.90909090909091)(1015.19191919192,-9.90909090909091)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.90909090909091)(970.40404040404,-9.88636363636364)(955.474747474747,-9.87272727272727)(940.545454545455,-9.83636363636364)(933.080808080808,-9.81818181818182)(925.616161616162,-9.78787878787879)(910.686868686869,-9.72727272727273)(895.757575757576,-9.66666666666667)(892.025252525252,-9.63636363636364)(880.828282828283,-9.54545454545455)(869.631313131313,-9.45454545454546)(865.89898989899,-9.42424242424243)(853.457912457912,-9.27272727272727)(850.969696969697,-9.22727272727273)(843.505050505051,-9.09090909090909)(843.505050505051,-8.90909090909091)(843.505050505051,-8.72727272727273)(843.505050505051,-8.54545454545455)(850.969696969697,-8.40909090909091)(854.70202020202,-8.36363636363636)(865.89898989899,-8.22727272727273)(868.387205387205,-8.18181818181818)(880.828282828283,-8.03030303030303)(888.292929292929,-8)(895.757575757576,-7.96969696969697)(910.686868686869,-7.84848484848485)(918.151515151515,-7.81818181818182)(925.616161616162,-7.78787878787879)(940.545454545455,-7.72727272727273)(955.474747474747,-7.66666666666667)(962.939393939394,-7.63636363636364)(970.40404040404,-7.60606060606061)(985.333333333333,-7.54545454545455)(1000.26262626263,-7.5)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.56818181818182)(1059.9797979798,-7.48484848484849)(1074.90909090909,-7.48484848484849)(1089.83838383838,-7.48484848484849)(1104.76767676768,-7.60606060606061)(1112.23232323232,-7.63636363636364)(1119.69696969697,-7.66666666666667)(1134.62626262626,-7.72727272727273)(1149.55555555556,-7.72727272727273)(1164.48484848485,-7.72727272727273)(1179.41414141414,-7.72727272727273)(1194.34343434343,-7.72727272727273)(1209.27272727273,-7.78787878787879)(1216.73737373737,-7.81818181818182)(1224.20202020202,-7.86363636363636)(1239.13131313131,-7.90909090909091)(1254.06060606061,-7.90909090909091)(1268.9898989899,-7.90909090909091)(1283.91919191919,-7.96969696969697)(1287.65151515152,-8)(1298.84848484848,-8.13636363636364)(1306.31313131313,-8.18181818181818)(1313.77777777778,-8.21212121212121)(1328.70707070707,-8.33333333333333)(1332.43939393939,-8.36363636363636)(1343.63636363636,-8.43181818181818)(1358.56565656566,-8.52272727272727)(1362.29797979798,-8.54545454545455)(1373.49494949495,-8.68181818181818)};

\addplot [
color=white,
draw=white,
only marks,
mark=x,
mark options={solid},
mark size=2.0pt,
line width=0.3pt,
forget plot
]
coordinates{
 (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0)(1268.9898989899,-8.18181818181818)(1254.06060606061,-9.27272727272727)(1164.48484848485,-8.54545454545455)(1149.55555555556,-8.18181818181818)(1134.62626262626,-7.81818181818182)(1119.69696969697,-8.90909090909091)(1104.76767676768,-7.63636363636364)(1074.90909090909,-7.45454545454546)(1074.90909090909,-9.09090909090909)(1059.9797979798,-9.09090909090909)(1030.12121212121,-7.27272727272727)(1015.19191919192,-7.27272727272727)(970.40404040404,-9.27272727272727)(910.686868686869,-7.09090909090909)(880.828282828283,-9.09090909090909)(865.89898989899,-9.09090909090909)(865.89898989899,-7.09090909090909)(791.252525252525,-8.90909090909091)(791.252525252525,-7.27272727272727)(761.393939393939,-7.27272727272727)(746.464646464646,-8.72727272727273)(716.606060606061,-8.54545454545455)(686.747474747475,-7.63636363636364)(671.818181818182,-8.18181818181818)(656.888888888889,-8)(597.171717171717,-7.09090909090909)(537.454545454546,-8.72727272727273)(223.939393939394,-8.36363636363636)(194.080808080808,-7.09090909090909)(0,-9.45454545454546)(209.010101010101,-8.18181818181818)(268.727272727273,-8.72727272727273)(298.585858585859,-7.81818181818182)(313.515151515152,-7.81818181818182)(313.515151515152,-8.90909090909091)(373.232323232323,-9.09090909090909)(388.161616161616,-9.09090909090909)(418.020202020202,-7.63636363636364)(492.666666666667,-9.27272727272727)(522.525252525253,-9.27272727272727)(522.525252525253,-7.81818181818182)(567.313131313131,-8)(567.313131313131,-9.09090909090909)(836.040404040404,-8.36363636363636)(836.040404040404,-9.63636363636364)(850.969696969697,-9.81818181818182)(865.89898989899,-8)(940.545454545455,-10.1818181818182)(955.474747474747,-10.1818181818182)(1074.90909090909,-10.3636363636364)(1209.27272727273,-7.63636363636364)(1224.20202020202,-10.1818181818182)(1239.13131313131,-10.1818181818182)(1283.91919191919,-7.81818181818182)(1313.77777777778,-10)(1358.56565656566,-9.81818181818182)(1358.56565656566,-8.18181818181818)(1403.35353535354,-8.72727272727273)(1403.35353535354,-9.27272727272727) 
};

\addplot [
color=lime,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1418.28282828283,-8.90909090909091)
};

\end{axis}
\end{tikzpicture}%

### 2013-03-22 figurefactory/files/limno_bgape_pp_90_1.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_90_0.tex
@@
 \addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=1.6pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (1418.28282828283,-8.90909090909091)(1433.21212121212,-9.09090909090909)(1418.28282828283,-9.45454545454546)(1403.35353535354,-8.54545454545455)(1388.42424242424,-8.36363636363636)(1373.49494949495,-9.81818181818182)(1328.70707070707,-10)(1298.84848484848,-7.81818181818182)(1239.13131313131,-7.63636363636364)(1149.55555555556,-7.45454545454546)(1134.62626262626,-7.45454545454546)(1104.76767676768,-10.1818181818182)(1089.83838383838,-10.1818181818182)(1074.90909090909,-10.1818181818182)(925.616161616162,-7.45454545454546)(925.616161616162,-10)(880.828282828283,-9.81818181818182)(865.89898989899,-7.81818181818182)(821.111111111111,-9.27272727272727)(612.10101010101,-8.72727272727273)(597.171717171717,-8.90909090909091)(567.313131313131,-7.63636363636364)(477.737373737374,-7.63636363636364)(418.020202020202,-8.54545454545455)(388.161616161616,-8.36363636363636)(388.161616161616,-8.18181818181818)(268.727272727273,-8)(194.080808080808,-7.81818181818182)(164.222222222222,-8)(164.222222222222,-8.18181818181818)(149.292929292929,-8)
+};
+
+\addplot [
 color=lime,

### 2013-03-22 figurefactory/files/limno_bgape_pp_90_2.tex
Add batch/path planning; add summary; finish first draft

--- 2013-03-22 figurefactory/files/limno_bgape_pp_90_1.tex
@@
 \addplot [fill=red!40!yellow,draw=none,forget plot] coordinates{ (1373.49494949495,-8.68181818181818)(1377.22727272727,-8.72727272727273)(1384.69191919192,-8.90909090909091)(1384.69191919192,-9.09090909090909)(1377.22727272727,-9.27272727272727)(1373.49494949495,-9.31818181818182)(1366.0303030303,-9.45454545454546)(1358.56565656566,-9.59090909090909)(1354.83333333333,-9.63636363636364)(1343.63636363636,-9.72727272727273)(1328.70707070707,-9.77272727272727)(1313.77777777778,-9.77272727272727)(1306.31313131313,-9.81818181818182)(1298.84848484848,-9.84848484848485)(1283.91919191919,-9.84848484848485)(1268.9898989899,-9.90909090909091)(1254.06060606061,-9.88636363636364)(1239.13131313131,-9.87272727272727)(1224.20202020202,-9.87272727272727)(1209.27272727273,-9.88636363636364)(1194.34343434343,-9.90909090909091)(1179.41414141414,-9.90909090909091)(1164.48484848485,-9.90909090909091)(1149.55555555556,-9.90909090909091)(1134.62626262626,-9.90909090909091)(1119.69696969697,-9.90909090909091)(1104.76767676768,-9.90909090909091)(1089.83838383838,-9.90909090909091)(1074.90909090909,-9.90909090909091)(1059.9797979798,-9.90909090909091)(1045.05050505051,-9.90909090909091)(1030.12121212121,-9.90909090909091)(1015.19191919192,-9.90909090909091)(1000.26262626263,-9.90909090909091)(985.333333333333,-9.90909090909091)(970.40404040404,-9.88636363636364)(955.474747474747,-9.87272727272727)(940.545454545455,-9.83636363636364)(933.080808080808,-9.81818181818182)(925.616161616162,-9.78787878787879)(910.686868686869,-9.72727272727273)(895.757575757576,-9.66666666666667)(892.025252525252,-9.63636363636364)(880.828282828283,-9.54545454545455)(869.631313131313,-9.45454545454546)(865.89898989899,-9.42424242424243)(853.457912457912,-9.27272727272727)(850.969696969697,-9.22727272727273)(843.505050505051,-9.09090909090909)(843.505050505051,-8.90909090909091)(843.505050505051,-8.72727272727273)(843.505050505051,-8.54545454545455)(850.969696969697,-8.40909090909091)(854.70202020202,-8.36363636363636)(865.89898989899,-8.22727272727273)(868.387205387205,-8.18181818181818)(880.828282828283,-8.03030303030303)(888.292929292929,-8)(895.757575757576,-7.96969696969697)(910.686868686869,-7.84848484848485)(918.151515151515,-7.81818181818182)(925.616161616162,-7.78787878787879)(940.545454545455,-7.72727272727273)(955.474747474747,-7.66666666666667)(962.939393939394,-7.63636363636364)(970.40404040404,-7.60606060606061)(985.333333333333,-7.54545454545455)(1000.26262626263,-7.5)(1015.19191919192,-7.54545454545455)(1030.12121212121,-7.54545454545455)(1045.05050505051,-7.56818181818182)(1059.9797979798,-7.48484848484849)(1074.90909090909,-7.48484848484849)(1089.83838383838,-7.48484848484849)(1104.76767676768,-7.60606060606061)(1112.23232323232,-7.63636363636364)(1119.69696969697,-7.66666666666667)(1134.62626262626,-7.72727272727273)(1149.55555555556,-7.72727272727273)(1164.48484848485,-7.72727272727273)(1179.41414141414,-7.72727272727273)(1194.34343434343,-7.72727272727273)(1209.27272727273,-7.78787878787879)(1216.73737373737,-7.81818181818182)(1224.20202020202,-7.86363636363636)(1239.13131313131,-7.90909090909091)(1254.06060606061,-7.90909090909091)(1268.9898989899,-7.90909090909091)(1283.91919191919,-7.96969696969697)(1287.65151515152,-8)(1298.84848484848,-8.13636363636364)(1306.31313131313,-8.18181818181818)(1313.77777777778,-8.21212121212121)(1328.70707070707,-8.33333333333333)(1332.43939393939,-8.36363636363636)(1343.63636363636,-8.43181818181818)(1358.56565656566,-8.52272727272727)(1362.29797979798,-8.54545454545455)(1373.49494949495,-8.68181818181818)};
+
+\addplot [
+draw=red!50!white,
+line width=0.6pt,
+forget plot
+]
+coordinates{
+ (1418.28282828283,-8.90909090909091)(1433.21212121212,-9.09090909090909)(1418.28282828283,-9.45454545454546)(1403.35353535354,-8.54545454545455)(1388.42424242424,-8.36363636363636)(1373.49494949495,-9.81818181818182)(1328.70707070707,-10)(1298.84848484848,-7.81818181818182)(1239.13131313131,-7.63636363636364)(1149.55555555556,-7.45454545454546)(1134.62626262626,-7.45454545454546)(1104.76767676768,-10.1818181818182)(1089.83838383838,-10.1818181818182)(1074.90909090909,-10.1818181818182)(925.616161616162,-7.45454545454546)(925.616161616162,-10)(880.828282828283,-9.81818181818182)(865.89898989899,-7.81818181818182)(821.111111111111,-9.27272727272727)(612.10101010101,-8.72727272727273)(597.171717171717,-8.90909090909091)(567.313131313131,-7.63636363636364)(477.737373737374,-7.63636363636364)(418.020202020202,-8.54545454545455)(388.161616161616,-8.36363636363636)(388.161616161616,-8.18181818181818)(268.727272727273,-8)(194.080808080808,-7.81818181818182)(164.222222222222,-8)(164.222222222222,-8.18181818181818)(149.292929292929,-8)
+};
 
@@
 
+\addplot [
+color=red,
+draw=black,
+only marks,
+mark=*,
+mark options={solid},
+mark size=3pt,
+line width=0.2pt,
+forget plot
+]
+coordinates{
+ (149.292929292929,-8)
+};
+
 \end{axis}

### 2013-03-22 msthpres.tex
Add batch/path planning; add summary; finish first draft

@@
-\documentclass[10pt,mathserif,serif]{beamer}
-%\documentclass[10pt,mathserif,serif,draft,handout]{beamer}
+%\documentclass[10pt,mathserif,serif]{beamer}
+\documentclass[10pt,mathserif,serif,handout]{beamer}
 
@@
 
+\begin{frame}
+\begin{itemize}
+\item<1-> Up to this point we have assumed a fixed cost per sample
+\item<2-> What about the traveling distance between measurements?
+\item<3-> Plan ahead:
+\begin{itemize}
+\item Select a \emph{batch} of sampling locations
+\item Connect them using a Euclidean TSP path
+\item Traverse the path and collect measurements
+\end{itemize}
+\end{itemize}
+
+\begin{center}
+\color{white}
+\includegraphics<1-3>[draft,width=3.78in]{figures/limno_bgape_pp_0_0}
+\color{black}
+\includegraphics<4>[width=3.78in]{figures/limno_bgape_pp_0_0}
+\includegraphics<5>[width=3.78in]{figures/limno_bgape_pp_0_1}
+\includegraphics<6>[width=3.78in]{figures/limno_bgape_pp_0_2}
+\includegraphics<7>[width=3.78in]{figures/limno_bgape_pp_30_0}
+\includegraphics<8>[width=3.78in]{figures/limno_bgape_pp_30_1}
+\includegraphics<9>[width=3.78in]{figures/limno_bgape_pp_30_2}
+\includegraphics<10>[width=3.78in]{figures/limno_bgape_pp_60_0}
+\includegraphics<11>[width=3.78in]{figures/limno_bgape_pp_60_1}
+\includegraphics<12>[width=3.78in]{figures/limno_bgape_pp_60_2}
+\includegraphics<13>[width=3.78in]{figures/limno_bgape_pp_90_0}
+\includegraphics<14>[width=3.78in]{figures/limno_bgape_pp_90_1}
+\includegraphics<15>[width=3.78in]{figures/limno_bgape_pp_90_2}
+\includegraphics<16>[width=3.78in]{figures/limno_bgape_pp_120_0}
+\includegraphics<17>[width=3.78in]{figures/limno_bgape_pp_120_1}
+\includegraphics<18>[width=3.78in]{figures/limno_bgape_pp_120_2}
+\includegraphics<19>[width=3.78in]{figures/limno_bgape_pp_150_0}
+\includegraphics<20>[width=3.78in]{figures/limno_bgape_pp_150_1}
+\includegraphics<21>[width=3.78in]{figures/limno_bgape_pp_150_2}
+\includegraphics<22>[width=3.78in]{figures/limno_bgape_pp_180_0}
+\includegraphics<23>[width=3.78in]{figures/limno_bgape_pp_180_1}
+\includegraphics<24>[width=3.78in]{figures/limno_bgape_pp_180_2}
+\includegraphics<25>[width=3.78in]{figures/limno_bgape_pp_210_0}
+\includegraphics<26>[width=2.7in]{figures/ev_bgape_pp}
+\end{center}
+\end{frame}
+
 \section*{Conclusion}
@@
 \begin{frame}
-\begin{enumerate}
-\item bla
-\end{enumerate}
+\begin{center}
+\large Summary
+\end{center}
+\vspace{-1em}
+\begin{itemize}
+\item<1-> \acl algorithm:
+\begin{itemize}
+\item<2-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
+\item<3-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
+\end{itemize}
+\item<4-> Two useful extensions:
+\begin{itemize}
+\item<5-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
+\item<6-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Batch sampling $\rightarrow$ path planning & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
+\end{itemize}
+\item<7-> Look out for algae when swimming in Lake Zurich! =)
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\begin{center}
+\large Questions?\\
+\vspace{2em}
+\includegraphics[width=3in]{figures/dilbert}
+\end{center}
 \end{frame}

### 2013-03-22 msthpres.tex
Fix image source style

--- 2013-03-21 msthpres.tex
@@
 \documentclass[10pt,mathserif,serif]{beamer}
-%\documentclass[10pt,mathserif,serif,draft,handout]{beamer}
+%\documentclass[10pt,mathserif,serif,handout]{beamer}
 
@@
 
+\newcommand{\sig}[2]{%
+\begin{tabular}{r}
+#1\\[-0.7em]
+{\tiny \color{darkgray}\it #2\hspace{0.5em}}
+\end{tabular}}
+
 \newcommand{\qauth}[1]{{\footnotesize\par\normalfont\hfill---\ \emph{#1}\par}}
@@
 \vspace{0.2in}
-\includegraphics[width=4in]{figures/swimmers.jpg}\\[-0.5em]
-{\tiny (Source: Steffen Schmidt / EPA)}
+\sig{\includegraphics[width=4in]{figures/swimmers.jpg}}{Steffen Schmidt / EPA}
 \end{center}
@@
 \uncover<1->{
-\minipage[c][0.75\textheight][s]{\columnwidth}
-\includegraphics[width=1.7in]{figures/pr.jpeg}\\[-0.5em]
-{\tiny (Source: www.limnobotics.ch)}\\
-\vfill
-\includegraphics[width=1.7in]{figures/bloom.jpg}\\[-0.5em]
-{\tiny (Source: Flickr/Dr. Jennifer L. Graham/U.S. Geological Survey)}
-\endminipage
+\sig{\includegraphics[width=1.7in]{figures/pr.jpeg}}{www.limnobotics.ch}\\[1em]
+\sig{\includegraphics[width=1.7in]{figures/bloom.jpg}}{Flickr/Dr. Jennifer L. Graham/U.S. Geological Survey}
 }
-
 \column{0.6\textwidth}
-\minipage[c][0.75\textheight][s]{\columnwidth}
+\minipage[c][0.80\textheight][s]{\columnwidth}
 \uncover<1->{
@@
 \only<1>{
-\includegraphics[width=2in]{figures/manual.jpg}\\[-0.5em]
-{\tiny (Source: www.limnobotics.ch)}}
+\sig{\includegraphics[width=2in]{figures/manual.jpg}}{www.limnobotics.ch}
+}
 \only<2>{
-\includegraphics[width=4in]{figures/boat.jpg}\\[-0.5em]
-{\tiny (Source: www.limnobotics.ch)}}
+\sig{\includegraphics[width=4in]{figures/boat.jpg}}{www.limnobotics.ch}
+}
 \only<3>{
-\includegraphics[width=4in]{figures/lake.png}\\[-0.5em]
-{\tiny (Source: www.limnobotics.ch)}}
+\sig{\includegraphics[width=4in]{figures/lake.png}}{www.limnobotics.ch}
+}
 \end{center}
@@
 
+\begin{frame}
+\begin{itemize}
+\item<1-> Up to this point we have assumed a fixed cost per sample
+\item<2-> What about the traveling distance between measurements?
+\item<3-> Plan ahead:
+\begin{itemize}
+\item Select a \emph{batch} of sampling locations
+\item Connect them using a Euclidean TSP path
+\item Traverse the path and collect measurements
+\end{itemize}
+\end{itemize}
+
+\begin{center}
+\color{white}
+\includegraphics<1-3>[draft,width=3.78in]{figures/limno_bgape_pp_0_0}
+\color{black}
+\includegraphics<4>[height=1.8in]{figures/limno_bgape_pp_0_0}
+\includegraphics<5>[height=1.8in]{figures/limno_bgape_pp_0_1}
+\includegraphics<6>[height=1.8in]{figures/limno_bgape_pp_0_2}
+\includegraphics<7>[height=1.8in]{figures/limno_bgape_pp_30_0}
+\includegraphics<8>[height=1.8in]{figures/limno_bgape_pp_30_1}
+\includegraphics<9>[height=1.8in]{figures/limno_bgape_pp_30_2}
+\includegraphics<10>[height=1.8in]{figures/limno_bgape_pp_60_0}
+\includegraphics<11>[height=1.8in]{figures/limno_bgape_pp_60_1}
+\includegraphics<12>[height=1.8in]{figures/limno_bgape_pp_60_2}
+\includegraphics<13>[height=1.8in]{figures/limno_bgape_pp_90_0}
+\includegraphics<14>[height=1.8in]{figures/limno_bgape_pp_90_1}
+\includegraphics<15>[height=1.8in]{figures/limno_bgape_pp_90_2}
+\includegraphics<16>[height=1.8in]{figures/limno_bgape_pp_120_0}
+\includegraphics<17>[height=1.8in]{figures/limno_bgape_pp_120_1}
+\includegraphics<18>[height=1.8in]{figures/limno_bgape_pp_120_2}
+\includegraphics<19>[height=1.8in]{figures/limno_bgape_pp_150_0}
+\includegraphics<20>[height=1.8in]{figures/limno_bgape_pp_150_1}
+\includegraphics<21>[height=1.8in]{figures/limno_bgape_pp_150_2}
+\includegraphics<22>[height=1.8in]{figures/limno_bgape_pp_180_0}
+\includegraphics<23>[height=1.8in]{figures/limno_bgape_pp_180_1}
+\includegraphics<24>[height=1.8in]{figures/limno_bgape_pp_180_2}
+\includegraphics<25>[height=1.8in]{figures/limno_bgape_pp_210_0}
+\includegraphics<26>[height=1.8in]{figures/ev_bgape_pp}
+\end{center}
+\end{frame}
+
 \section*{Conclusion}
@@
 \begin{frame}
-\begin{enumerate}
-\item bla
-\end{enumerate}
+\begin{center}
+\large Summary
+\end{center}
+\vspace{-1em}
+\begin{itemize}
+\item<1-> \acl algorithm:
+\begin{itemize}
+\item<2-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
+\item<3-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
+\end{itemize}
+\item<4-> Two useful extensions:
+\begin{itemize}
+\item<5-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
+\item<6-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Batch sampling $\rightarrow$ path planning & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
+\end{itemize}
+\item<7-> Look out for algae when swimming in Lake Zurich! =)
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\begin{center}
+\large Questions?\\
+\vspace{2em}
+\sig{\includegraphics[width=3in]{figures/dilbert}}{www.dilbert.com}
+\end{center}
 \end{frame}

### 2013-03-22 msthpres.tex
Revert to sans serif; fixes in algorithm
More fixes all around

@@
-\documentclass[10pt,mathserif,serif]{beamer}
-%\documentclass[10pt,mathserif,serif,handout]{beamer}
+\documentclass[10pt,mathserif]{beamer}
+%\documentclass[10pt,mathserif,handout]{beamer}
 
@@
 \column{0.4\textwidth}
-\uncover<1->{
+\uncover<2->{
 \sig{\includegraphics[width=1.7in]{figures/pr.jpeg}}{www.limnobotics.ch}\\[1em]
@@
 for a population explosion of algae including \emph{Planktothrix rubescens},
-[...]''
+[\ldots]''
 \qauth{Scientific American}
-}
-\vfill
-\uncover<2->{
-\small
-``\emph{Planktotrhix rubescens} can account for half of the total
-phytoplankton biomass in Lake Zurich in summer [...]''
-\vspace{1em}
-
-``\emph{Planktotrhix rubescens} are among the most important
-producers of hepatotoxic microcystins in freshwaters [...]''
-\qauth{Silke Van den Wyngaert \emph{et al.}, ASLO, 2011}
 }
@@
 \small
-``Microcystins [...] are cyanotoxins and can be very toxic for plants and
+``\emph{Planktotrhix rubescens} can account for half of the total
+phytoplankton biomass in Lake Zurich in summer [\ldots]''
+\vspace{1em}
+
+``\emph{Planktotrhix rubescens} are among the most important
+producers of hepatotoxic microcystins in freshwaters [\ldots]''
+\qauth{Silke Van den Wyngaert \emph{et al.}, ASLO, 2011}
+}
+\vfill
+\uncover<4->{
+\small
+``Microcystins [\ldots] are cyanotoxins and can be very toxic for plants and
 animals including humans.
@@
 \vspace{1em}
-\item<4-> More importantly: they provide \textbf{variance estimates}!\\
+\item<4-> They provide \textbf{variance estimates}!\\
           Construct confidence intervals: $Q_t(\*x) = \left[\mu_{t-1}(\*x) \pm \beta_t^{1/2} \sigma_{t-1}(\*x)\right]$
@@
 \begin{columns}[t]
-\column{0.5\textwidth}
+\column{0.45\textwidth}
 {\footnotesize
-\begin{algorithmic}[1]
-  \REQUIRE sample set $D$, GP prior ($\mu_0 = 0$, $k$, $\sigma_0$),\\
-           \hspace{1.35em}threshold value $h$, accuracy parameter $\epsilon$
+\begin{algorithmic}
+  \REQUIRE sample set $D$, GP prior ($\mu_0$, $k$, $\sigma_0$),\\
+           \hspace{2.2em}thr. value $h$, accuracy parameter $\epsilon$
   \ENSURE predicted sets $\hat{H}$, $\hat{L}$
@@
     \uncover<5->{
-    \CLET{c3}{$\*x_t$}{$\argmax_{\*x \in U_t}(a_t(\*x))$} \label{lin:sel1}
+    \CLET{c3}{$\*x_t$}{$\argmax \{a_t(\*x)\mid \*x \in U_t\}$} \label{lin:sel1}
     \CLET{c3}{$y_t$}{$f(\*x_t) + n_t$} \label{lin:sel2}
@@
     \uncover<6->{
-    \CSTATE{c4}Compute $\mu_t(\*x)$ and $\sigma_t(\*x)$, for all $\*x \in U_t$ \label{lin:inf}
+    \CSTATE{c4}Compute $\mu_t(\*x)$ and $\sigma_t(\*x)$, $\forall\*x \in U_t$ \label{lin:inf}
     }
@@
 }
-\column{0.5\textwidth}
+\column{0.55\textwidth}
 \begin{center}
@@
  \uncover<11->{
- \node[st,left=2em of amb] (t0) {Monotonicity}
+ \node[st,left=1.5em of amb] (t0) {Monotonicity}
    edge[pil] (amb);
@@
  \uncover<15->{
- \node[st,right=2em of loss] (rules) {Class. rules}
+ \node[st,right=1.5em of loss] (rules) {Class. rules}
    edge[pil] (loss);
@@
  \uncover<16->{ 
- \node[st,right=2em of est] (delta) {$\delta$}
+ \node[st,right=1.5em of est] (delta) {$\delta$}
    edge[pil] (est);
@@
 \item Connect them using a Euclidean TSP path
-\item Traverse the path and collect measurements
+\item Traverse path and collect measurements
 \end{itemize}
@@
 \begin{itemize}
-\item<2-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
-\item<3-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
+\item<2-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
+\item<3-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
 \end{itemize}
@@
 \begin{itemize}
-\item<5-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
-\item<6-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Batch sampling $\rightarrow$ path planning & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
+\item<5-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
+\item<6-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Batch sampling $\rightarrow$ path planning & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
 \end{itemize}

### 2013-03-22 msthpres.tex
Reduce/simplify theory

@@
 \subsection*{Theoretical analysis}
-\begin{frame}
-How do we judge the ``accuracy'' of a solution $(\hat{H}, \hat{L})$?
-\uncover<2->{
-\begin{definition}[Misclassification loss]
-%\begin{align*}
-$\ell_h(\*x) = \twopartdef{\max\{0, f(\*x) - h\}}{\*x\in \hat{L}}{\max\{0, h - f(\*x)\}}{\*x\in \hat{H}}$
-%\end{align*}
-\end{definition}
-\begin{center}
-\includegraphics[width=3.5in]{figures/misclass}
-\end{center}
-}
-\end{frame}
+%\begin{frame}
+%How do we judge the ``accuracy'' of a solution $(\hat{H}, \hat{L})$?
+%\uncover<2->{
+%\begin{definition}[Misclassification loss]
+%%\begin{align*}
+%$\ell_h(\*x) = \twopartdef{\max\{0, f(\*x) - h\}}{\*x\in \hat{L}}{\max\{0, h - f(\*x)\}}{\*x\in \hat{H}}$
+%%\end{align*}
+%\end{definition}
+%\begin{center}
+%\includegraphics[width=3.5in]{figures/misclass}
+%\end{center}
+%}
+%\end{frame}
 
-\begin{frame}
-\footnotesize
-\begin{tikzpicture}[node distance=1cm, auto,]
- \uncover<1->{
- \node[st] (conv) {Convergence};
- }
+%\begin{frame}
+%\footnotesize
+%\begin{tikzpicture}[node distance=1cm, auto,]
+% \uncover<1->{
+% \node[st] (conv) {Convergence};
+% }
+%
+% \uncover<3->{
+% \node[st,below=3em of conv] (clas) {All points in $D$ have been classified}
+%   edge[pil] (conv);
+% }
+%
+% \uncover<4->{
+% \node[st,text width=14em,below=3em of clas] (amb)
+% {\makecell[c]
+%   {Conf. intervals ($\Leftrightarrow$ ambiguities)\\
+%    get small enough ($<2\epsilon$)\uncover<12->{:\\[0.5em]
+%    $a_t(\*x_t) \sim \mathcal{O}\left(\sqrt{\displaystyle\frac{\beta_t\gamma_t}{t}}\right)$
+%    }
+%   }
+% } edge[pil] (clas);
+% 
+% \uncover<4->{ 
+% \node[st,right=1.5em of clas] (eps) {$\epsilon$}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<18->{ 
+% \node[st,right=1.5em of clas,fill=c6] (eps) {$\epsilon$}
+%   edge[pil] (amb);
+% }
+% 
+% \node[st,draw=none,below=3em of amb] (dummy) {};
+% }
+%
+% \uncover<11->{
+% \node[st,left=1.5em of amb] (t0) {Monotonicity}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<5->{
+% \node[st,left=3em of dummy] (t1) {Samples ($t$)}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<6->{
+% \node[st,right=1em of t1] (t2) {Kernel ($k$)}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<7->{
+% \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<8->{
+% \node[st,right=3em of t3] (t4) {$\beta_t$}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<18->{
+% \node[st,right=3em of t3,fill=c6] (t4) {$\beta_t$}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<9->{
+% \node[draw=black,densely dotted,line width=0.7pt,fit=(t1)(t3)] (fit1) {};}
+% 
+% \uncover<9->{
+% \node[st,below=3em of fit1] (gamma)
+% {\makecell[c]
+%   {Quantify by max. information gain (Srinivas \emph{et al.}, 2010):\\[0.5em]
+%    $\gamma_t = \max_{\*y_t} I(\*y_{1:t}; f)$\uncover<10->{\\[0.5em]
+%    For SE kernel $\gamma_t \sim \mathcal{O}\left((\log t)^{d+1}\right)$
+%    }
+%   }
+% } edge[pil] (fit1);
+% }
+%
+% \uncover<2->{
+% \node[st,right=9em of conv] (acc) {Solution accuracy};
+% }
+%
+% \uncover<14->{
+% \node[st,below=3em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
+%   edge[pil] (acc)
+%   edge[pil,<-] (eps);
+% }
+%
+% \uncover<15->{
+% \node[st,right=1.5em of loss] (rules) {Class. rules}
+%   edge[pil] (loss);
+% }
+%
+% \uncover<16->{ 
+% \node[st,below=3em of loss] (est) {Correctly estimate $f$ w.h.p.}
+%   edge[pil] (loss);
+% }
+%
+% \uncover<16->{ 
+% \node[st,right=1.5em of est] (delta) {$\delta$}
+%   edge[pil] (est);
+% }
+%
+% \uncover<17->{
+% \node[st,below=3em of est] (large) {Conf. intervals are large enough}
+%   edge[pil] (est)
+%   edge[pil,<-] (t4);
+% }
+%\end{tikzpicture}
+%\end{frame}
 
- \uncover<3->{
- \node[st,below=3em of conv] (clas) {All points in $D$ have been classified}
-   edge[pil] (conv);
- }
-
- \uncover<4->{
- \node[st,text width=14em,below=3em of clas] (amb)
- {\makecell[c]
-   {Conf. intervals ($\Leftrightarrow$ ambiguities)\\
-    get small enough ($<2\epsilon$)\uncover<12->{:\\[0.5em]
-    $a_t(\*x_t) \sim \mathcal{O}\left(\sqrt{\displaystyle\frac{\beta_t\gamma_t}{t}}\right)$
-    }
-   }
- } edge[pil] (clas);
-
- \uncover<4->{ 
- \node[st,right=1.5em of clas] (eps) {$\epsilon$}
-   edge[pil] (amb);
- }
-
- \uncover<18->{ 
- \node[st,right=1.5em of clas,fill=c6] (eps) {$\epsilon$}
-   edge[pil] (amb);
- }
-
- \node[st,draw=none,below=3em of amb] (dummy) {};
- }
-
- \uncover<11->{
- \node[st,left=1.5em of amb] (t0) {Monotonicity}
-   edge[pil] (amb);
- }
-
- \uncover<5->{
- \node[st,left=3em of dummy] (t1) {Samples ($t$)}
-   edge[pil] (amb);
- }
-
- \uncover<6->{
- \node[st,right=1em of t1] (t2) {Kernel ($k$)}
-   edge[pil] (amb);
- }
-
- \uncover<7->{
- \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
-   edge[pil] (amb);
- }
-
- \uncover<8->{
- \node[st,right=3em of t3] (t4) {$\beta_t$}
-   edge[pil] (amb);
- }
-
- \uncover<18->{
- \node[st,right=3em of t3,fill=c6] (t4) {$\beta_t$}
-   edge[pil] (amb);
- }
-
- \uncover<9->{
- \node[draw=black,densely dotted,line width=0.7pt,fit=(t1)(t3)] (fit1) {};}
-
- \uncover<9->{
- \node[st,below=3em of fit1] (gamma)
- {\makecell[c]
-   {Quantify by max. information gain (Srinivas \emph{et al.}, 2010):\\[0.5em]
-    $\gamma_t = \max_{\*y_t} I(\*y_{1:t}; f)$\uncover<10->{\\[0.5em]
-    For SE kernel $\gamma_t \sim \mathcal{O}\left((\log t)^{d+1}\right)$
-    }
-   }
- } edge[pil] (fit1);
- }
-
- \uncover<2->{
- \node[st,right=9em of conv] (acc) {Solution accuracy};
- }
-
- \uncover<14->{
- \node[st,below=3em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
-   edge[pil] (acc)
-   edge[pil,<-] (eps);
- }
-
- \uncover<15->{
- \node[st,right=1.5em of loss] (rules) {Class. rules}
-   edge[pil] (loss);
- }
-
- \uncover<16->{ 
- \node[st,below=3em of loss] (est) {Correctly estimate $f$ w.h.p.}
-   edge[pil] (loss);
- }
-
- \uncover<16->{ 
- \node[st,right=1.5em of est] (delta) {$\delta$}
-   edge[pil] (est);
- }
-
- \uncover<17->{
- \node[st,below=3em of est] (large) {Conf. intervals are large enough}
-   edge[pil] (est)
-   edge[pil,<-] (t4);
- }
-\end{tikzpicture}
-\end{frame}
+%\begin{frame}
+%\footnotesize
+%\begin{tikzpicture}[node distance=1cm, auto,]
+% \uncover<1->{
+% \node[st] (conv) {Convergence};
+% }
+%
+% \uncover<1->{
+% \node[st,below=3em of conv] (clas) {All points in $D$ have been classified}
+%   edge[pil] (conv);
+% }
+%
+% \uncover<1->{
+% \node[st,text width=14em,below=3em of clas] (amb)
+% {\makecell[c]
+%   {Conf. intervals ($\Leftrightarrow$ ambiguities)\\
+%    get small enough ($<2\epsilon$)\uncover<1->{:\\[0.5em]
+%    $a_t(\*x_t) \sim \mathcal{O}\left(\sqrt{\displaystyle\frac{\beta_t\gamma_t}{t}}\right)$
+%    }
+%   }
+% } edge[pil] (clas);
+% 
+% \uncover<1->{ 
+% \node[st,right=1.5em of clas] (eps) {$\epsilon$}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<1->{ 
+% \node[st,right=1.5em of clas,fill=c6] (eps) {$\epsilon$}
+%   edge[pil] (amb);
+% }
+% 
+% \node[st,draw=none,below=3em of amb] (dummy) {};
+% }
+%
+% \uncover<1->{
+% \node[st,left=1.5em of amb] (t0) {Monotonicity}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<1->{
+% \node[st,left=3em of dummy] (t1) {Samples ($t$)}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<1->{
+% \node[st,right=1em of t1] (t2) {Kernel ($k$)}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<1->{
+% \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<1->{
+% \node[st,right=3em of t3] (t4) {$\beta_t$}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<1->{
+% \node[st,right=3em of t3,fill=c6] (t4) {$\beta_t$}
+%   edge[pil] (amb);
+% }
+% 
+% \uncover<1->{
+% \node[draw=black,densely dotted,line width=0.7pt,fit=(t1)(t3)] (fit1) {};}
+% 
+% \uncover<1->{
+% \node[st,below=3em of fit1] (gamma)
+% {\makecell[c]
+%   {Quantify by max. information gain (Srinivas \emph{et al.}, 2010):\\[0.5em]
+%    $\gamma_t = \max_{\*y_t} I(\*y_{1:t}; f)$\uncover<1->{\\[0.5em]
+%    For SE kernel $\gamma_t \sim \mathcal{O}\left((\log t)^{d+1}\right)$
+%    }
+%   }
+% } edge[pil] (fit1);
+% }
+%
+% \uncover<1->{
+% \node[st,right=9em of conv] (acc) {Solution accuracy};
+% }
+%
+% \uncover<1->{
+% \node[st,below=3em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
+%   edge[pil] (acc)
+%   edge[pil,<-] (eps);
+% }
+%
+% \uncover<1->{
+% \node[st,right=1.5em of loss] (rules) {Class. rules}
+%   edge[pil] (loss);
+% }
+%
+% \uncover<1->{ 
+% \node[st,below=3em of loss] (est) {Correctly estimate $f$ w.h.p.}
+%   edge[pil] (loss);
+% }
+%
+% \uncover<1->{ 
+% \node[st,right=1.5em of est] (delta) {$\delta$}
+%   edge[pil] (est);
+% }
+%
+% \uncover<1->{
+% \node[st,below=3em of est] (large) {Conf. intervals are large enough}
+%   edge[pil] (est)
+%   edge[pil,<-] (t4);
+% }
+%\end{tikzpicture}
+%\end{frame}
 
@@
 \begin{theorem}[Convergence of \acl]
-\label{thm:acl}
 For any $h\in\mathbb{R}$, $\delta \in (0, 1)$, and $\epsilon > 0$,
@@
 \end{align*}
+\end{theorem}
+\end{frame}
+
+\begin{frame}
+\begin{theorem}[Simplified]
+If we choose $\beta_t$ large enough, then:
+\begin{itemize}
+\item<2-> \acl terminates after a number of iterations $T$
+\begin{enumerate}
+\item<3-> smoother kernel $\Rightarrow T \downarrow$
+\item<4-> $\sigma \uparrow\ \Rightarrow T \uparrow$
+\item<5-> ${\color<7>{red}\epsilon} \uparrow\ \Rightarrow T \downarrow$
+\end{enumerate}
+\item<6-> The solution returned is {\color<7>{red}$\epsilon$}-accurate with high probability
+\end{itemize}
 \end{theorem}

### 2013-03-23 figurefactory/files/ev_bgape_eps.tex
More fixes and reductions

@@
 \begin{axis}[%
-tick label style={font=\tiny},
-label style={font=\tiny},
+tick label style={font=\scriptsize},
+label style={font=\scriptsize},
+label shift={-4pt},
 xlabel shift={-6pt},
-ylabel shift={-4pt},
-legend style={font=\tiny},
+legend style={font=\scriptsize},
 view={0}{90},

### 2013-03-23 msthpres.tex
More fixes and reductions

@@
 \item<4-> Obtain noisy observation ($y_t = f(x_t) + n_t$)
-\item<5-> Update our estimate of the underlying function (e.g. algae concentration)
+\item<5-> Update our estimate of the underlying function
 \end{itemize}
@@
 \item<1-> What if we don't know $h$?
+\vspace{1em}
 \item<2-> Implicitly define the threshold level: $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
-\item<5-> \iacl:
+\vspace{1em}
+\item<3-> \iacl:
 \begin{itemize}
-\item<5-> Need to accurately estimate the maximum (don't exclude points that could be maximizers)
-\item<6-> Slower classification
+\item<4-> Need to also estimate the maximum
+\item<5-> Slower classification due to uncertainty about $h$
 \end{itemize}
@@
 \begin{center}
-\color{white}
-\only<1-2>{\includegraphics[draft,width=3.77in]{figures/voned_cl_41_imp_1}}
-\color{black}
-\only<3>{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_1}}
-\only<4->{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_2}}
+%\color{white}
+%\only<1-2>{\includegraphics[draft,width=3.77in]{figures/voned_cl_41_imp_1}}
+%\color{black}
+%\only<3>{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_1}}
+%\only<4->{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_2}}
 \end{center}
@@
 
-\begin{frame}
-\begin{center}
-\includegraphics[width=2.3in]{figures/ev_chl_imp}
-\includegraphics[width=2.3in]{figures/ev_bgape_imp}
-\end{center}
-\end{frame}
+%\begin{frame}
+%\begin{center}
+%\includegraphics[width=2.3in]{figures/ev_chl_imp}
+%\includegraphics[width=2.3in]{figures/ev_bgape_imp}
+%\end{center}
+%\end{frame}
 
@@
 \color{white}
-\includegraphics<1-3>[draft,width=3.78in]{figures/limno_bgape_pp_0_0}
+\includegraphics<1-3>[draft,height=1.8in]{figures/limno_bgape_pp_0_0}
 \color{black}
@@
 \includegraphics<19>[height=1.8in]{figures/limno_bgape_pp_150_0}
-\includegraphics<20>[height=1.8in]{figures/limno_bgape_pp_150_1}
-\includegraphics<21>[height=1.8in]{figures/limno_bgape_pp_150_2}
-\includegraphics<22>[height=1.8in]{figures/limno_bgape_pp_180_0}
-\includegraphics<23>[height=1.8in]{figures/limno_bgape_pp_180_1}
-\includegraphics<24>[height=1.8in]{figures/limno_bgape_pp_180_2}
-\includegraphics<25>[height=1.8in]{figures/limno_bgape_pp_210_0}
-\includegraphics<26>[height=1.8in]{figures/ev_bgape_pp}
+%\includegraphics<20>[height=1.8in]{figures/limno_bgape_pp_150_1}
+%\includegraphics<21>[height=1.8in]{figures/limno_bgape_pp_150_2}
+%\includegraphics<22>[height=1.8in]{figures/limno_bgape_pp_180_0}
+%\includegraphics<23>[height=1.8in]{figures/limno_bgape_pp_180_1}
+%\includegraphics<24>[height=1.8in]{figures/limno_bgape_pp_180_2}
+%\includegraphics<25>[height=1.8in]{figures/limno_bgape_pp_210_0}
+\includegraphics<20>[height=1.8in]{figures/ev_bgape_pp}
 \end{center}

### 2013-03-24 figurefactory/proof.tex
Small fixes

@@
 
+\definecolor{col1}{RGB}{140,191,38}
+
 \begin{document}
@@
    edge[pil] (amb);
- \node[st,right=3em of t3] (t4) {$\beta_t$}
+ \node[st,right=3em of t3,fill=col1] (t4) {$\beta_t$}
    edge[pil] (amb);
@@
 
- \node[st,right=2em of loss] (rules) {Classification rules}
+ \node[st,right=2em of loss] (rules) {Class. rules}
    edge[pil] (loss);
@@
 
- \node[st,right=1.5em of clas] (eps) {$\epsilon$}
+ \node[st,right=1.5em of clas,fill=col1] (eps) {$\epsilon$}
    edge[pil] (amb)

### 2013-03-25 msthpres.tex
Small fixes

@@
 \begin{align*}
-\*x_t &= \argmax_{\*x\in D} 1.96\sigma_{t-1}(\*x)-|\mu_{t-1}(\*x) - h|\\
-&\approx \argmax_{\*x\in D} a_{t-1}(\*x) \tag{for $\beta_t = 1.96$}
+%\*x_t &= \argmax_{\*x\in D} 1.96\sigma_{t-1}(\*x)-|\mu_{t-1}(\*x) - h|\\
+\*x_t \approx \argmax_{\*x\in D} a_{t-1}(\*x) \tag{for $\beta_t^{1/2} = 1.96$}
 \end{align*}
@@
 \hspace{4pt}\includegraphics<1->[width=4in]{figures/limno_chl_ls}\\[0.5em]
-\uncover<2->{\includegraphics[width=2.3in]{figures/ev_chl_seq}}
-\uncover<3>{\includegraphics[width=2.3in]{figures/ev_chl_eps}}
+\uncover<2->{\includegraphics[width=2.3in]{figures/ev_chl_eps}}
+\uncover<3->{\includegraphics[width=2.3in]{figures/ev_chl_seq}}
 \end{center}
@@
 \begin{itemize}
-\item Select a \emph{batch} of sampling locations
+\item Select a \emph{batch} of sampling locations (\bacl)
 \item Connect them using a Euclidean TSP path
@@
 \end{itemize}
-\item<7-> Look out for algae when swimming in Lake Zurich! =)
+\item<7-> Look out for algae when swimming in Lake Zurich! {\color{blue}$\ddot\smile$}
 \end{itemize}
@@
 \vspace{2em}
-\sig{\includegraphics[width=3in]{figures/dilbert}}{www.dilbert.com}
+\sig{\includegraphics[width=3.5in]{figures/dilbert}}{www.dilbert.com}
 \end{center}

### 2013-04-23 ijcai13pres.tex
Initial changes for IJCAI; add ping slide

--- 2013-03-25 msthpres.tex
@@
 
-\author[Alkis Gkotovos]{
+\author[Alkis Gotovos \emph{et al.}]{
 \footnotesize
-M.Sc. Thesis by Alkis Gkotovos\\
-Department of Computer Science\\
-ETH Zurich
+Alkis Gotovos\inst{1}
+\and
+Nathalie Casati\inst{1,2}\and
+Gregory Hitz\inst{1}\and
+Andreas Krause\inst{1}
 }
 
-\date[M.Sc. Thesis presentation]{
-\footnotesize
-Supervised by Prof. Andreas Krause
+\institute[ETH Zurich]{\inst{1} Department of Computer Science\\ETH Zurich \and %
+                      \inst{2} IBM Research -- Zurich}
 
+\date[IJCAI 2013]{
+IJCAI 2013
 }
@@
 
-%\pgfdeclareimage[height=0.5cm]{university-logo}{figures/eth_logo_black.pdf}
-%\logo{\pgfuseimage{university-logo}}
+%\pgfdeclareimage[height=0.5cm]{eth-logo}{figures/eth-logo.eps}
+%\logo{\pgfuseimage{eth-logo}}
 
@@
 
+\begin{frame}
+\begin{center}
+\large Geolocating internet latency
+\end{center}
+\begin{itemize}
+\item<1-> Which world regions have low enough latency (e.g. < $150$ ms)
+      for video chatting, online gaming, etc.?
+\item<2-> Ideal setting for batch sampling $\rightarrow$ multiple pings in parallel
+\end{itemize}
+\begin{center}
+\color{white}
+\includegraphics<1-2>[draft,height=2.5in]{figures/map}
+\color{black}
+\includegraphics<3>[height=2.5in]{figures/map}
+\includegraphics<4>[height=2.5in]{figures/map_ls_150}
+\end{center}
+\end{frame}
+
 \section*{Conclusion}
@@
 \item<5-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
-\item<6-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Batch sampling $\rightarrow$ path planning & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
+\item<6-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Batch sampling & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
 \end{itemize}

### 2013-05-01 figurefactory/files/ev_bgape_eps.tex
Most of the changes discussed with Andreas

--- 2013-03-20 figurefactory/files/ev_bgape_eps.tex
@@
 \begin{axis}[%
-tick label style={font=\tiny},
-label style={font=\tiny},
+tick label style={font=\footnotesize},
+label style={font=\footnotesize},
+label shift={-4pt},
 xlabel shift={-6pt},
-ylabel shift={-4pt},
-legend style={font=\tiny},
+legend style={font=\footnotesize},
 view={0}{90},

### 2013-05-01 figurefactory/files/ev_chl_eps.tex
Most of the changes discussed with Andreas

--- 2013-03-20 figurefactory/files/ev_chl_eps.tex
@@
 %
+
+\usetikzlibrary{shapes,arrows,fit,calc,positioning}
 
@@
 \begin{axis}[%
-tick label style={font=\tiny},
-label style={font=\tiny},
+tick label style={font=\normalsize},
+label style={font=\normalsize},
+label shift={-4pt},
 xlabel shift={-6pt},
-ylabel shift={-4pt},
-legend style={font=\tiny},
+legend style={font=\normalsize},
 view={0}{90},
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=red!88!black,draw=red!88!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=red!92!black,draw=red!92!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=red!96!black,draw=red!96!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=red,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=red,draw=red,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor1,draw=mycolor1,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor2,draw=mycolor2,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor3,draw=mycolor3,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor4,draw=mycolor4,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor5,draw=mycolor5,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor6,draw=mycolor6,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor7,draw=mycolor7,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor8,draw=mycolor8,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor9,draw=mycolor9,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor10,draw=mycolor10,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor11,draw=mycolor11,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor12,draw=mycolor12,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor13,draw=mycolor13,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor14,draw=mycolor14,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor15,draw=mycolor15,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor16,draw=mycolor16,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor17,draw=mycolor17,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor18,draw=mycolor18,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor19,draw=mycolor19,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor20,draw=mycolor20,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor21,draw=mycolor21,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor22,draw=mycolor22,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor23,draw=mycolor23,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor24,draw=mycolor24,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor25,draw=mycolor25,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor26,draw=mycolor26,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor27,draw=mycolor27,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor28,draw=mycolor28,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor29,draw=mycolor29,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor30,draw=mycolor30,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor31,draw=mycolor31,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor32,draw=mycolor32,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor33,draw=mycolor33,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor34,draw=mycolor34,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor35,draw=mycolor35,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor36,draw=mycolor36,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor37,draw=mycolor37,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor38,draw=mycolor38,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor39,draw=mycolor39,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor40,draw=mycolor40,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor41,draw=mycolor41,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor42,draw=mycolor42,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor43,draw=mycolor43,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor44,draw=mycolor44,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor45,draw=mycolor45,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor46,draw=mycolor46,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor47,draw=mycolor47,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor48,draw=mycolor48,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor49,draw=mycolor49,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor50,draw=mycolor50,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor51,draw=mycolor51,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor52,draw=mycolor52,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor53,draw=mycolor53,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor54,draw=mycolor54,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor55,draw=mycolor55,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue,draw=blue,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!88!black,draw=blue!88!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!80!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!80!black,draw=blue!80!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!68!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!68!black,draw=blue!68!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!60!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!60!black,draw=blue!60!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!52!black,draw=blue!52!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor56,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor56,draw=mycolor56,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor57,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor57,draw=mycolor57,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor58,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor58,draw=mycolor58,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor59,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor59,draw=mycolor59,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor60,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor60,draw=mycolor60,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor61,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor61,draw=mycolor61,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor62,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor62,draw=mycolor62,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor63,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor63,draw=mycolor63,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor64,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor64,draw=mycolor64,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor65,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor65,draw=mycolor65,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor66,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor66,draw=mycolor66,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor67,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor67,draw=mycolor67,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor68,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor68,draw=mycolor68,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor69,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor69,draw=mycolor69,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor70,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor70,draw=mycolor70,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor71,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor71,draw=mycolor71,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor72,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor72,draw=mycolor72,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!96!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!96!black,draw=blue!96!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!92!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!92!black,draw=blue!92!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!84!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!84!black,draw=blue!84!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!76!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!76!black,draw=blue!76!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!72!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!72!black,draw=blue!72!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=blue!64!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=blue!64!black,draw=blue!64!black,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor73,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor73,draw=mycolor73,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor74,draw=mycolor74,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=mycolor75,draw=mycolor75,line width=0.05pt},
 forget plot
@@
 \addplot [
-color=blue,
-mark size=1.3pt,
-only marks,
-mark=*,
-mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},
+%
+mark size=1.9pt,
+only marks,
+mark=*,
+mark options={fill=red!84!black,draw=red!84!black,line width=0.05pt},
 forget plot
@@
 };
+
+\node at (axis cs:230, 0.57) [shape=circle,draw=black,line width=1.2pt,inner sep=0.2pt,anchor=west,minimum size=20pt] {\LARGE$\epsilon$};
+\node at (axis cs:90, 0.6) [anchor=west,minimum size=16pt] {\large \emph{large}};
+\node at (axis cs:390, 0.6) [anchor=east,minimum size=16pt] {\large \emph{small}};
+
+\draw[<-,line width=1.2pt] (axis cs:90, 0.57) -- (axis cs:230, 0.57);
+\draw[->,line width=1.2pt] (axis cs:258, 0.57) -- (axis cs:390, 0.57);
+
 \end{axis}

### 2013-05-01 figurefactory/files/limno_bgape_cl.tex
Most of the changes discussed with Andreas

@@
 \begin{axis}[%
-tick label style={font=\tiny},
-label style={font=\tiny},
+tick label style={font=\footnotesize},
+label style={font=\footnotesize},
 xlabel shift={-10pt},
 ylabel shift={-17pt},
-legend style={font=\tiny},
+legend style={font=\footnotesize},
 view={0}{90},

### 2013-05-01 figurefactory/files/voned_0_0.tex
Most of the changes discussed with Andreas

--- 2013-03-19 figurefactory/files/voned_0.tex
@@
 \begin{axis}[%
-tick label style={font=\tiny},
-label style={font=\tiny},
+tick label style={font=\footnotesize},
+label style={font=\footnotesize},
 label shift={-4pt},
 xlabel shift={-6pt},
-legend style={font=\tiny},
+legend style={font=\footnotesize},
 view={0}{90},
@@
 
+%\addplot [
+%color=black,
+%solid,
+%line width=1.5pt,
+%mark size=3pt,
+%mark=-,
+%forget plot
+%]
+%coordinates{
+% (1.25,-1)(1.25,3)
+%};
+%
+%\node at (axis cs:0.1, 1.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)$};
+%\draw[->,line width=1pt] (axis cs:0.29, 1.5) to[in=90,out=0] (axis cs:0.4, 1.1);
+%
+%\node at (axis cs:1.47, 1.5) [anchor=east,minimum size=20pt] {\large$Q_t(\*x)$};
+%
+%\node at (axis cs:0.1, 3.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)+2\sigma_t(\*x)$};
+%\draw[->,line width=1pt] (axis cs:0.55, 3.5) to[in=90,out=0] (axis cs:0.65, 3.1);
+%\node at (axis cs:0.1, -1.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)-2\sigma_t(\*x)$};
+%\draw[->,line width=1pt] (axis cs:0.55, -1.5) to[in=270,out=0] (axis cs:0.65, -1.1);
+
 \end{axis}

### 2013-05-01 figurefactory/files/voned_0_2.tex
Most of the changes discussed with Andreas

--- 2013-05-01 figurefactory/files/voned_0_0.tex
@@
 %};
-%
-%\node at (axis cs:0.1, 1.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)$};
-%\draw[->,line width=1pt] (axis cs:0.29, 1.5) to[in=90,out=0] (axis cs:0.4, 1.1);
-%
+
+\node at (axis cs:0.1, 1.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)$};
+\draw[->,line width=1pt] (axis cs:0.29, 1.5) to[in=90,out=0] (axis cs:0.4, 1.1);
+
 %\node at (axis cs:1.47, 1.5) [anchor=east,minimum size=20pt] {\large$Q_t(\*x)$};
-%
-%\node at (axis cs:0.1, 3.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)+2\sigma_t(\*x)$};
-%\draw[->,line width=1pt] (axis cs:0.55, 3.5) to[in=90,out=0] (axis cs:0.65, 3.1);
-%\node at (axis cs:0.1, -1.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)-2\sigma_t(\*x)$};
-%\draw[->,line width=1pt] (axis cs:0.55, -1.5) to[in=270,out=0] (axis cs:0.65, -1.1);
+
+\node at (axis cs:0.1, 3.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)+\beta_t^{1/2}\sigma_t(\*x)$};
+\draw[->,line width=1pt] (axis cs:0.65, 3.5) to[in=90,out=0] (axis cs:0.75, 3.1);
+\node at (axis cs:0.1, -1.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)-\beta_t^{1/2}\sigma_t(\*x)$};
+\draw[->,line width=1pt] (axis cs:0.65, -1.5) to[in=270,out=0] (axis cs:0.75, -1.1);
 

### 2013-05-01 figurefactory/files/voned_1_0.tex
GP explanation and intro to LSE
Most of the changes discussed with Andreas

--- 2013-03-19 figurefactory/files/voned_0.tex
@@
 
+\addplot [
+color=green!60!black,
+only marks,
+mark=*,
+mark size=2.5pt,
+line width=1.0pt,
+forget plot
+]
+coordinates{
+ (1.5,-2)
+};
+
 \end{axis}

### 2013-05-01 figurefactory/files/voned_2_1.tex
GP explanation and intro to LSE
Most of the changes discussed with Andreas

--- 2013-03-19 figurefactory/files/voned_2_0.tex
@@
 color=green!60!black,
+densely dotted,
+line width=1.0pt,
+forget plot
+]
+coordinates{
+ (0.5,-2)(0.5,2.8)
+};
+
+\addplot [
+color=green!60!black,
 only marks,
@@
 
+\addplot [
+color=green!60!black,
+only marks,
+mark=x,
+mark size=3.5pt,
+line width=1.5pt,
+forget plot
+]
+coordinates{
+ (0.5,2.8)
+};
+
 \end{axis}

### 2013-05-01 figurefactory/files/voned_3_1.tex
GP explanation and intro to LSE
Most of the changes discussed with Andreas

--- 2013-03-19 figurefactory/files/voned_3_0.tex
@@
 color=green!60!black,
+densely dotted,
+line width=1.0pt,
+forget plot
+]
+coordinates{
+ (1,-2)(1,0.5)
+};
+
+\addplot [
+color=green!60!black,
 only marks,
@@
 
+\addplot [
+color=green!60!black,
+only marks,
+mark=x,
+mark size=3.5pt,
+line width=1.5pt,
+forget plot
+]
+coordinates{
+ (1,0.5)
+};
+
 \end{axis}

### 2013-05-01 figurefactory/files/voned_cl_01.tex
GP explanation and intro to LSE
Most of the changes discussed with Andreas

--- 2013-03-19 figurefactory/files/voned_cl_00.tex
@@
 
+\addplot [
+color=red,
+densely dashed,
+line width=2.0pt,
+forget plot
+]
+coordinates{
+ (0,1.2)(2,1.2)
+};
+
 \end{axis}

### 2013-05-01 figurefactory/files/voned_cl_11.tex
GP explanation and intro to LSE
Most of the changes discussed with Andreas

--- 2013-03-19 figurefactory/files/voned_cl_10.tex
@@
 \addplot [
+color=red!40!yellow,
+solid,
+only marks,
+mark=*,
+mark size=2.5pt,
+forget plot
+]
+coordinates{
+ (0.5,-2)
+};
+
+\addplot [
 color=red,

### 2013-05-01 figurefactory/files/voned_cl_21.tex
GP explanation and intro to LSE
Most of the changes discussed with Andreas

--- 2013-03-19 figurefactory/files/voned_cl_20.tex
@@
 coordinates{
- (0.5,-2)
+ (0.5,-2)(1.5,-2)
 };

### 2013-05-01 figurefactory/files/voned_cl_41_amb_0.tex
LSE algorithm
Most of the changes discussed with Andreas

--- 2013-03-19 figurefactory/files/voned_cl_41.tex
@@
 
+\addplot [
+color=black,
+solid,
+line width=1.5pt,
+mark=-,
+mark size=3pt,
+forget plot
+]
+coordinates{
+ (1.23,0.0268)(1.23,1.9195)
+};
+
+\addplot [
+color=black,
+solid,
+line width=1.5pt,
+mark=-,
+mark size=3pt,
+forget plot
+]
+coordinates{
+ (0.23,0.9288)(0.23,3.8259)
+};
+
 \end{axis}

### 2013-05-01 figurefactory/files/voned_cl_41_imp_2.tex
Add implicit extension
Most of the changes discussed with Andreas

--- 2013-03-21 figurefactory/files/voned_cl_41_imp_1.tex
@@
 
+\addplot [
+color=red,
+densely dashed,
+line width=1.5pt,
+forget plot
+]
+coordinates{
+ (0,1.9129575)(2,1.9129575)
+};
+
+\addplot [
+color=red,
+densely dashed,
+line width=1.5pt,
+forget plot
+]
+coordinates{
+ (0,1.24875)(2,1.24875)
+};
+
 \end{axis}

### 2013-05-01 ijcai13pres.tex
Minor fix
Most of the changes discussed with Andreas

@@
 %\usepackage[T1]{fontenc}
+
+\usepackage{grfext}\PrependGraphicsExtensions*{.png,.PNG}
+
+%\usepackage{graphicx}
+%\usepackage{epstopdf}
+%\epstopdfDeclareGraphicsRule{.pdf}{png}{.png}{convert -density 200 #1 \OutputFile}
 
@@
 
-\date[IJCAI 2013]{
-IJCAI 2013
+\date[IJCAI '13]{
+IJCAI '13
 }
@@
 
-\begin{frame}{Outline}
-  \tableofcontents
-  % You might wish to add the option [pausesections]
-\end{frame}
+%\begin{frame}{Outline}
+%  \tableofcontents
+%  % You might wish to add the option [pausesections]
+%\end{frame}
 
@@
 \begin{frame}
+Pose as a sequential decision making problem (\emph{pool-based active learning}):
 \begin{itemize}
-\item<1-> Pose as a sequential decision making problem (\emph{pool-based active learning}):
-\begin{itemize}
-\item<2-> No measurements available in advance, just a set (pool) of possible sampling locations ($D$)
+\item<1-> No measurements available in advance, just a set (pool) of possible\\sampling locations ($D$)
 \vspace{0.5em}
-\item<3->[]\hspace{-1.5em} At each iteration $t \geq 1$:
-\item<3-> Decide where to measure next ($x_t$)
-\item<4-> Obtain noisy observation ($y_t = f(x_t) + n_t$)
-\item<5-> Update our estimate of the underlying function
+\item<2->[]\hspace{-1.5em} At each iteration $t \geq 1$:
+\item<2-> Decide where to measure next ($\*x_t \in D$)
+\item<3-> Obtain noisy observation ($y_t = f(\*x_t) + n_t$)
+\item<4-> Update our estimate of $f$
 \end{itemize}
-\end{itemize}
-\begin{center}
-\color{white}
-\includegraphics<1>[draft,width=4.45in]{figures/oned_0}
-\color{black}
-\includegraphics<2>[width=4.45in]{figures/oned_0}
-\includegraphics<3>[width=4.45in]{figures/oned_1_0}
-\includegraphics<4>[width=4.45in]{figures/oned_1_1}
-\includegraphics<5>[width=4.45in]{figures/oned_1_2}
-\includegraphics<6>[width=4.45in]{figures/oned_2_0}
-\includegraphics<7>[width=4.45in]{figures/oned_2_1}
-\includegraphics<8>[width=4.45in]{figures/oned_2_2}
-\end{center}
+%\begin{center}
+%\color{white}
+%\includegraphics<1>[draft,width=4.45in]{figures/oned_0}
+%\color{black}
+%\includegraphics<2>[width=4.45in]{figures/oned_0}
+%\includegraphics<3>[width=4.45in]{figures/oned_1_0}
+%\includegraphics<4>[width=4.45in]{figures/oned_1_1}
+%\includegraphics<5>[width=4.45in]{figures/oned_1_2}
+%\includegraphics<6>[width=4.45in]{figures/oned_2_0}
+%\includegraphics<7>[width=4.45in]{figures/oned_2_1}
+%\includegraphics<8>[width=4.45in]{figures/oned_2_2}
+%\end{center}
 \end{frame}
@@
 
-\begin{frame}
-\begin{center}
-\uncover<1->{\large Why GPs are nice}
-\end{center}
-\begin{itemize}
-\item<2-> \textbf{Nonparametric}:\\
-      Impose ``smoothness'' assumptions via kernel $k(x, x')$.
-\vspace{1em}
-\item<3-> \textbf{Bayesian}, yet \textbf{efficient}:
-      \begin{align*}
-        \mu_t(\*x) &= \*k_t(\*x)^T\left(\*K_t + \sigma^2 \*I\right)^{-1}\*y_t\\
-        k_t(\*x, \*x') &= k(\*x, \*x') - \*k_t(\*x)^T\left(\*K_t + \sigma^2 \*I\right)^{-1}\*k_t(\*x)\notag\\
-        \sigma_t^2(\*x) &= k_t(\*x, \*x)
-      \end{align*}
-      Suitable for step-by-step updates.
-\vspace{1em}
-\item<4-> They provide \textbf{variance estimates}!\\
-          Construct confidence intervals: $Q_t(\*x) = \left[\mu_{t-1}(\*x) \pm \beta_t^{1/2} \sigma_{t-1}(\*x)\right]$
-\end{itemize}
-\end{frame}
+%\begin{frame}
+%\begin{center}
+%\uncover<1->{\large Why GPs are nice}
+%\end{center}
+%\begin{itemize}
+%\item<2-> \textbf{Nonparametric}:\\
+%      Impose ``smoothness'' assumptions via kernel $k(x, x')$.
+%\vspace{1em}
+%\item<3-> \textbf{Bayesian}, yet \textbf{efficient}:
+%      \begin{align*}
+%        \mu_t(\*x) &= \*k_t(\*x)^T\left(\*K_t + \sigma^2 \*I\right)^{-1}\*y_t\\
+%        k_t(\*x, \*x') &= k(\*x, \*x') - \*k_t(\*x)^T\left(\*K_t + \sigma^2 \*I\right)^{-1}\*k_t(\*x)\notag\\
+%        \sigma_t^2(\*x) &= k_t(\*x, \*x)
+%      \end{align*}
+%      Suitable for step-by-step updates.
+%\vspace{1em}
+%\item<4-> They provide \textbf{variance estimates}!\\
+%          Construct confidence intervals: $Q_t(\*x) = \left[\mu_{t-1}(\*x) \pm \beta_t^{1/2} \sigma_{t-1}(\*x)\right]$
+%\end{itemize}
+%\end{frame}
 
@@
 \begin{center}
-\includegraphics<1>[width=4.45in]{figures/voned_0}
-\includegraphics<2>[width=4.45in]{figures/voned_1_0}
-\includegraphics<3>[width=4.45in]{figures/voned_1_1}
-\includegraphics<4>[width=4.45in]{figures/voned_1_2}
-\includegraphics<5>[width=4.45in]{figures/voned_2_0}
-\includegraphics<6>[width=4.45in]{figures/voned_2_1}
-\includegraphics<7>[width=4.45in]{figures/voned_2_2}
-\includegraphics<8>[width=4.45in]{figures/voned_3_0}
-\includegraphics<9>[width=4.45in]{figures/voned_3_1}
-\includegraphics<10>[width=4.45in]{figures/voned_3_2}
+\large Gaussian processes
+\end{center}
+\begin{itemize}
+\item<1-> \textbf{Nonpaparametric}: impose ``smoothness'' assumptions via kernel $k(\*x, \*x')$
+\item<2-> Mean \textbf{and variance} estimates: construct confidence intervals $Q_t(\*x)$
+\item<7-> \textbf{Bayesian}, yet \textbf{efficient}: suitable for step-by-step updates
+\end{itemize}
+\begin{center}
+\color{white}
+\includegraphics<1-2>[draft,width=4in]{figures/voned_0_0}
+\color{black}
+\includegraphics<3>[width=4in]{figures/voned_0_0}
+\includegraphics<4>[width=4in]{figures/voned_0_1}
+\includegraphics<5>[width=4in]{figures/voned_0_2}
+\includegraphics<6-7>[width=4in]{figures/voned_0_3}
+\includegraphics<8>[width=4in]{figures/voned_1_0}
+\includegraphics<9>[width=4in]{figures/voned_1_1}
+\includegraphics<10>[width=4in]{figures/voned_1_2}
+\includegraphics<11>[width=4in]{figures/voned_2_0}
+\includegraphics<12>[width=4in]{figures/voned_2_1}
+\includegraphics<13>[width=4in]{figures/voned_2_2}
+\includegraphics<14>[width=4in]{figures/voned_3_0}
+\includegraphics<15>[width=4in]{figures/voned_3_1}
+\includegraphics<16>[width=4in]{figures/voned_3_2}
 \end{center}
@@
 \vspace{0.3em}
-\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<24->{\Large\color{green!70!black}\checkmark}
+\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<22->{\Large\color{green!70!black}\checkmark}
 \uncover<16->{
 \begin{itemize}
-\item<16-> Pick among the yet unclassified.
-\item<17-> Doesn't really matter which!\\
-           \uncover<18->{(e.g. max. variance, }\uncover<19->{max. ambiguity}\uncover<23->{, or even random)}
+\item<16-> Pick among the yet unclassified\ldots
+\item<17-> \ldots the most ``ambiguous'' point
+           \uncover<21->{(max. variance or random also work)}
 \end{itemize}}
@@
 \color{white}
-\includegraphics<1>[draft,width=3.5in]{figures/voned_cl_00}
+\includegraphics<1>[draft,width=3.7in]{figures/voned_cl_00}
 \color{black}
-\includegraphics<2-4>[width=3.5in]{figures/voned_cl_00}
-\includegraphics<5>[width=3.5in]{figures/voned_cl_01}
-\includegraphics<6>[width=3.5in]{figures/voned_cl_10}
-\includegraphics<7>[width=3.5in]{figures/voned_cl_11}
-\includegraphics<8>[width=3.5in]{figures/voned_cl_20}
-\includegraphics<9>[width=3.5in]{figures/voned_cl_21}
-\includegraphics<10>[width=3.5in]{figures/voned_cl_30}
-\includegraphics<11>[width=3.5in]{figures/voned_cl_31}
-\includegraphics<12>[width=3.5in]{figures/voned_cl_40}
-\includegraphics<13-19>[width=3.5in]{figures/voned_cl_41}
-\includegraphics<20>[width=3.5in]{figures/voned_cl_41_amb_0}
-\includegraphics<21>[width=3.5in]{figures/voned_cl_41_amb_1}
-\includegraphics<22->[width=3.5in]{figures/voned_cl_41_amb_2}
+\includegraphics<2-4>[width=3.7in]{figures/voned_cl_00}
+\includegraphics<5>[width=3.7in]{figures/voned_cl_01}
+\includegraphics<6>[width=3.7in]{figures/voned_cl_10}
+\includegraphics<7>[width=3.7in]{figures/voned_cl_11}
+\includegraphics<8>[width=3.7in]{figures/voned_cl_20}
+\includegraphics<9>[width=3.7in]{figures/voned_cl_21}
+\includegraphics<10>[width=3.7in]{figures/voned_cl_30}
+\includegraphics<11>[width=3.7in]{figures/voned_cl_31}
+\includegraphics<12>[width=3.7in]{figures/voned_cl_40}
+\includegraphics<13-17>[width=3.7in]{figures/voned_cl_41}
+\includegraphics<18>[width=3.7in]{figures/voned_cl_41_amb_0}
+\includegraphics<19>[width=3.7in]{figures/voned_cl_41_amb_1}
+\includegraphics<20->[width=3.7in]{figures/voned_cl_41_amb_2}
 \end{center}
@@
 \begin{center}
-\includegraphics<8->[width=2in]{figures/voned_cl_41_eps}
+\includegraphics<8->[width=2.5in]{figures/voned_cl_41_eps}
 \end{center}
@@
 \end{align*}
-\item<3-> ``Straddle'' heuristic (Bryan \emph{et al.}, 2005):
+\item<3-> State of the art ``straddle'' heuristic (Bryan \emph{et al.}, 2005):
 \vspace{-0.5em}
@@
 \hspace{4pt}\includegraphics<1->[width=4in]{figures/limno_chl_ls}\\[0.5em]
-\uncover<2->{\includegraphics[width=2.3in]{figures/ev_chl_eps}}
-\uncover<3->{\includegraphics[width=2.3in]{figures/ev_chl_seq}}
+\uncover<2->{\includegraphics[width=2.4in]{figures/ev_chl_eps}}
+\uncover<3->{\includegraphics[width=2.25in]{figures/ev_chl_seq}}
 \end{center}
@@
 \color{black}
-\only<2-4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq}}
-\color{white}
-\only<2>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_eps}}
-\color{black}
-\only<3>{\includegraphics[width=2.3in]{figures/ev_bgape_eps}}
-\only<4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq_str_sc}}
-\only<5>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_class_354}}
-\only<6>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_str_class_400}}
-\only<7>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_var_class_400}}
+\only<2>{\includegraphics[width=2.3in]{figures/ev_bgape_seq}}
+%\color{white}
+%\only<2>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_eps}}
+%\color{black}
+%\only<3>{\includegraphics[width=2.3in]{figures/ev_bgape_eps}}
+%\only<4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq_str_sc}}
+%\only<5>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_class_354}}
+%\only<6>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_str_class_400}}
+%\only<7>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_var_class_400}}
 \end{center}
@@
 \begin{itemize}
-\item<1-> What if we don't know $h$?
+\item<1-> What if we don't know the threshold level $h$?
 \vspace{1em}
-\item<2-> Implicitly define the threshold level: $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
+\item<2-> Implicitly define $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
 \vspace{1em}
-\item<3-> \iacl:
+\item<3-> No existing algorithms for this problem (to our knowledge)
+\vspace{1em}
+\item<4-> We extend \acl (and its theory!) to this setting
+\vspace{1em}
+\item<5->\iacl algorithm:
 \begin{itemize}
-\item<4-> Need to also estimate the maximum
-\item<5-> Slower classification due to uncertainty about $h$
+\item<6-> Need to accurately estimate the maximum $\rightarrow$ modified selection rule
+\item<7-> $h$ is now an estimated quantity $\rightarrow$ modified classification rules
 \end{itemize}
@@
 \item<2-> What about the traveling distance between measurements?
-\item<3-> Plan ahead:
+\item<3-> We extend \acl to select a \emph{batch} of sampling locations at each step (\bacl)
+\item<3-> Use this to plan ahead:
 \begin{itemize}
-\item Select a \emph{batch} of sampling locations (\bacl)
+\item Select a batch of sampling locations
 \item Connect them using a Euclidean TSP path
@@
 \begin{center}
-\large Geolocating internet latency
+\large Come to the poster session for more\ldots
 \end{center}
 \begin{itemize}
-\item<1-> Which world regions have low enough latency (e.g. < $150$ ms)
-      for video chatting, online gaming, etc.?
-\item<2-> Ideal setting for batch sampling $\rightarrow$ multiple pings in parallel
+\item<2-> \ldots theory: sample complexity bounds in more detail
+\item<3-> \ldots applications: estimate world regions of low internet latency\\[0.5em]
+\hspace{3em}\includegraphics[height=2in]{figures/map}
+\item<4-> \ldots results: why does \acl greatly outperform ``straddle'' in some cases?
 \end{itemize}
-\begin{center}
-\color{white}
-\includegraphics<1-2>[draft,height=2.5in]{figures/map}
-\color{black}
-\includegraphics<3>[height=2.5in]{figures/map}
-\includegraphics<4>[height=2.5in]{figures/map_ls_150}
-\end{center}
 \end{frame}
+%\begin{itemize}
+%\item<1-> Which world regions have low enough latency (e.g. < $150$ ms)
+%      for video chatting, online gaming, etc.?
+%\item<2-> Ideal setting for batch sampling $\rightarrow$ multiple pings in parallel
+%\end{itemize}
+%\begin{center}
+%\color{white}
+%\includegraphics<1-2>[draft,height=2.5in]{figures/map}
+%\color{black}
+%\includegraphics<3>[height=2.5in]{figures/map}
+%\includegraphics<4>[height=2.5in]{figures/map_ls_150}
+%\end{center}
 
@@
 
-\begin{frame}
-\begin{center}
-\large Questions?\\
-\vspace{2em}
-\sig{\includegraphics[width=3.5in]{figures/dilbert}}{www.dilbert.com}
-\end{center}
-\end{frame}
+%\begin{frame}
+%\begin{center}
+%\large Questions?\\
+%\vspace{2em}
+%\sig{\includegraphics[width=3.5in]{figures/dilbert}}{www.dilbert.com}
+%\end{center}
+%\end{frame}
 

### 2013-05-01 ijcai13pres.tex
Fix typo

@@
 \item<2-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
-\item<3-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
+\item<3-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Competitive with the state of the art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
 \end{itemize}

### 2013-05-01 ijcai13pres.tex
Finish changes discussed with Andreas

@@
 \setbeamertemplate{enumerate mini template}{\insertenumlabel}
+
+\definecolor{locol}{rgb}{0.26, 0.45, 0.65}
 
@@
 \small
-``The warming waters of one of central Europe's most popular holiday
-destinations, Switzerland's Lake Zurich, have created an ideal environment
-for a population explosion of algae including \emph{Planktothrix rubescens},
+``[\ldots]Switzerland's Lake Zurich [\ldots] an ideal environment
+for a population explosion of algae including \emph{Planktothrix rubescens}
 [\ldots]''
@@
 \small
-``\emph{Planktotrhix rubescens} can account for half of the total
-phytoplankton biomass in Lake Zurich in summer [\ldots]''
-\vspace{1em}
-
 ``\emph{Planktotrhix rubescens} are among the most important
@@
 \vspace{0.2in}
+%\only<1>{
+%\sig{\includegraphics[width=2in]{figures/manual.jpg}}{www.limnobotics.ch}
+%}
 \only<1>{
-\sig{\includegraphics[width=2in]{figures/manual.jpg}}{www.limnobotics.ch}
+Autonomous surface vehicle developed by the Autonomous Systems Lab of ETH\\[1em]
+\sig{\includegraphics[width=4in]{figures/boat.jpg}}{www.limnobotics.ch}
 }
 \only<2>{
-\sig{\includegraphics[width=4in]{figures/boat.jpg}}{www.limnobotics.ch}
-}
-\only<3>{
+Take measurements on a vertical transect of the lake\\[1em]
 \sig{\includegraphics[width=4in]{figures/lake.png}}{www.limnobotics.ch}
@@
 \vspace{0.2in}
-\includegraphics<1>[width=4.7in]{figures/limno_bgape_sc}
-\includegraphics<2>[width=4.7in]{figures/limno_bgape}
+\only<1>{
+Original algae concentration measurements ($\sim 2000$)\\[1em]
+\includegraphics[width=4.7in]{figures/limno_bgape_sc}
+}
+\only<2>{
+Interpolated algae concentration field\\[1em]
+\includegraphics[width=4.7in]{figures/limno_bgape}
+}
+\only<3>{
+Focus on accurately estimating regions of ``high'' concentration (e.g. $\geq 7$)\\[1em]
 \includegraphics<3>[width=4.7in]{figures/limno_bgape_ls}
-\only<4>{\hspace{-2em}\includegraphics[width=4.45in]{figures/limno_bgape_cl}}
+}
+\only<4>{
+Classify transect into a {\color{red!40!yellow}super-} and a {\color{locol}sub}level set\\[1em]
+\hspace{-2em}\includegraphics[width=4.45in]{figures/limno_bgape_cl}
+}
 \end{center}
@@
 \begin{itemize}
-\item<1-> No measurements available in advance, just a set (pool) of possible\\sampling locations ($D$)
+\item<2-> No measurements available in advance, just a set (pool) of possible\\sampling locations ($D$)
 \vspace{0.5em}
-\item<2->[]\hspace{-1.5em} At each iteration $t \geq 1$:
-\item<2-> Decide where to measure next ($\*x_t \in D$)
-\item<3-> Obtain noisy observation ($y_t = f(\*x_t) + n_t$)
-\item<4-> Update our estimate of $f$
+\item<3->[]\hspace{-1.5em} At each iteration $t \geq 1$:
+\item<3-> Decide where to measure next ($\*x_t \in D$)
+\item<4-> Obtain noisy observation ($y_t = f(\*x_t) + n_t$)
+\item<5-> Update our estimated classification
 \end{itemize}
@@
 \begin{enumerate}
-\item<1-> How do we \textbf{estimate} the function?
+\item<1-> How do we \textbf{estimate} the underlying function from measurements?
 \vspace{1em}
@@
 \begin{frame}
+\begin{center}
+\large Implicit threshold level
+\end{center}
 \begin{itemize}
@@
 \vspace{1em}
-\item<5->\iacl algorithm:
+\item<5->\textbf{\iacl} algorithm:
 \begin{itemize}
@@
 \begin{frame}
+\begin{center}
+\large Batch sampling
+\end{center}
 \begin{itemize}
-\item<1-> Up to this point we have assumed a fixed cost per sample
-\item<2-> What about the traveling distance between measurements?
-\item<3-> We extend \acl to select a \emph{batch} of sampling locations at each step (\bacl)
-\item<3-> Use this to plan ahead:
+\item<1-> Up to this point we have assumed a fixed cost per sample.\\
+          What about the traveling distance between measurements?
+\vspace{1em}
+\item<2-> We extend \acl to select a \emph{batch} of sampling locations at each step
+\vspace{1em}
+\item<3-> Plan ahead:
 \begin{itemize}
-\item Select a batch of sampling locations
+\item Use \textbf{\bacl} to select a batch of sampling locations
 \item Connect them using a Euclidean TSP path
@@
 \includegraphics<13>[height=1.8in]{figures/limno_bgape_pp_90_0}
-\includegraphics<14>[height=1.8in]{figures/limno_bgape_pp_90_1}
-\includegraphics<15>[height=1.8in]{figures/limno_bgape_pp_90_2}
-\includegraphics<16>[height=1.8in]{figures/limno_bgape_pp_120_0}
-\includegraphics<17>[height=1.8in]{figures/limno_bgape_pp_120_1}
-\includegraphics<18>[height=1.8in]{figures/limno_bgape_pp_120_2}
-\includegraphics<19>[height=1.8in]{figures/limno_bgape_pp_150_0}
+%\includegraphics<14>[height=1.8in]{figures/limno_bgape_pp_90_1}
+%\includegraphics<15>[height=1.8in]{figures/limno_bgape_pp_90_2}
+%\includegraphics<16>[height=1.8in]{figures/limno_bgape_pp_120_0}
+%\includegraphics<17>[height=1.8in]{figures/limno_bgape_pp_120_1}
+%\includegraphics<18>[height=1.8in]{figures/limno_bgape_pp_120_2}
+%\includegraphics<19>[height=1.8in]{figures/limno_bgape_pp_150_0}
 %\includegraphics<20>[height=1.8in]{figures/limno_bgape_pp_150_1}
@@
 %\includegraphics<25>[height=1.8in]{figures/limno_bgape_pp_210_0}
-\includegraphics<20>[height=1.8in]{figures/ev_bgape_pp}
+\includegraphics<14>[height=1.8in]{figures/ev_bgape_pp}
 \end{center}
 \end{frame}
+
+\section{Conclusion}
 
@@
 
-\section*{Conclusion}
-
 \begin{frame}
@@
 \end{center}
-\vspace{-1em}
+\vspace{-1.5em}
 \begin{itemize}
-\item<1-> \acl algorithm:
-\begin{itemize}
-\item<2-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
-\item<3-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Competitive with the state of the art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
-\end{itemize}
-\item<4-> Two useful extensions:
-\begin{itemize}
-\item<5-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
-\item<6-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Batch sampling & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
-\end{itemize}
-\item<7-> Look out for algae when swimming in Lake Zurich! {\color{blue}$\ddot\smile$}
+\item<2-> \acl algorithm:\vspace{0.5em}
+\begin{tabular}{>{\centering\arraybackslash} m{5cm}>{\centering\arraybackslash} m{5.5cm}}
+Theoretical guarantees & Competitive with the state of the art\\
+\includegraphics[height=0.9in]{figures/thm.png} & \includegraphics[height=1in]{figures/ev_chl_seq_long}
+\end{tabular}
+\item<3-> Two useful extensions:\vspace{0.5em}
+\begin{tabular}{>{\centering\arraybackslash} m{5.25cm}>{\centering\arraybackslash} m{5.25cm}}
+Implicit threshold level (\iacl) & Batch sampling (\bacl)\\
+\includegraphics[height=0.95in]{figures/limno_bgape_imp_class_140} & \includegraphics[height=0.95in]{figures/limno_bgape_pp_30_2}
+\end{tabular}
+\item<4-> Look out for algae when swimming in Lake Zurich! {\color{blue}$\ddot\smile$}
 \end{itemize}

### 2013-07-31 figurefactory/files/ev_chl_eps.tex
Many small fixes

@@
 \begin{axis}[%
-tick label style={font=\normalsize},
-label style={font=\normalsize},
+tick label style={font=\Large},
+label style={font=\Large},
 label shift={-4pt},
 xlabel shift={-6pt},
-legend style={font=\normalsize},
+legend style={font=\Large},
 view={0}{90},
@@
 
-\node at (axis cs:230, 0.57) [shape=circle,draw=black,line width=1.2pt,inner sep=0.2pt,anchor=west,minimum size=20pt] {\LARGE$\epsilon$};
-\node at (axis cs:90, 0.6) [anchor=west,minimum size=16pt] {\large \emph{large}};
-\node at (axis cs:390, 0.6) [anchor=east,minimum size=16pt] {\large \emph{small}};
+\node at (axis cs:230, 0.57) [shape=circle,draw=black,line width=1.2pt,inner sep=0.2pt,anchor=west,minimum size=20pt] {\Huge$\epsilon$};
+\node at (axis cs:90, 0.6) [anchor=west,minimum size=16pt] {\LARGE \emph{large}};
+\node at (axis cs:390, 0.6) [anchor=east,minimum size=16pt] {\LARGE \emph{small}};
 

### 2013-07-31 figurefactory/files/ev_chl_eps_poster.tex
Many small fixes

--- 2013-07-31 figurefactory/files/ev_chl_eps.tex
@@
 \begin{axis}[%
-tick label style={font=\Large},
-label style={font=\Large},
+tick label style={font=\Huge},
+label style={font=\Huge},
 label shift={-4pt},
 xlabel shift={-6pt},
-legend style={font=\Large},
+legend style={font=\Huge},
 view={0}{90},
@@
 xmin=0, xmax=400,
+xtick={0, 100, 200, 300, 400},
 xlabel={Samples},
@@
 \node at (axis cs:230, 0.57) [shape=circle,draw=black,line width=1.2pt,inner sep=0.2pt,anchor=west,minimum size=20pt] {\Huge$\epsilon$};
-\node at (axis cs:90, 0.6) [anchor=west,minimum size=16pt] {\LARGE \emph{large}};
-\node at (axis cs:390, 0.6) [anchor=east,minimum size=16pt] {\LARGE \emph{small}};
+\node at (axis cs:90, 0.6) [anchor=west,minimum size=16pt] {\huge \emph{large}};
+\node at (axis cs:390, 0.6) [anchor=east,minimum size=16pt] {\huge \emph{small}};
 

### 2013-07-31 figurefactory/files/limno_bgape_cl.tex
Many small fixes

--- 2013-03-18 figurefactory/files/limno_bgape_cl.tex
@@
 \begin{axis}[%
-tick label style={font=\tiny},
-label style={font=\tiny},
+tick label style={font=\normalsize},
+label style={font=\normalsize},
 xlabel shift={-10pt},
 ylabel shift={-17pt},
-legend style={font=\tiny},
+legend style={font=\normalsize},
 view={0}{90},

### 2013-07-31 figurefactory/files/limno_bgape_class_354_poster.tex
Many small fixes

--- 2013-03-19 figurefactory/files/limno_bgape_class_354.tex
@@
 \begin{axis}[%
-tick label style={font=\tiny},
-label style={font=\tiny},
+tick label style={font=\Large},
+label style={font=\Large},
 xlabel shift={-10pt},
 ylabel shift={-17pt},
-legend style={font=\tiny},
+legend style={font=\Large},
 view={0}{90},
@@
 mark options={solid},
-mark size=2.0pt,
-line width=0.3pt,
+mark size=3.5pt,
+line width=1.3pt,
 forget plot

### 2013-07-31 figurefactory/files/limno_bgape_sc.tex
Many small fixes

--- 2013-03-18 figurefactory/files/limno_bgape_sc.tex
@@
 
-\addplot[scatter,only marks,mark size=0.6pt,scatter src=explicit,scatter/use mapped color={mark=*,draw=mapped color,fill=mapped color}] plot coordinates{ (0,-0.831) [9.000000e-01] (0.396123095452957,-0.832) [9.000000e-01] (16.8850657170843,-2.228) [9.000000e-01] (19.386309378027,-2.485) [1] (20.7170231970803,-2.774) [1] (21.6989675078734,-3.031) [1.200000e+00] (22.8071472777201,-3.289) [1.400000e+00] (24.5610830029506,-3.559) [1.500000e+00] (25.9984308826544,-3.773) [1.700000e+00] (27.8988551242371,-4.005) [1.800000e+00] (29.1617886372451,-4.262) [2.200000e+00] (62.5565899293934,-9.656) [4.900000e+00] (62.5565899293934,-9.727) [4.800000e+00] (70.9331967712539,-9.716) [4.700000e+00] (70.5118107778974,-9.674) [4.600000e+00] (71.7410292630623,-9.816) [4.500000e+00] (72.8642052039513,-9.938) [4.400000e+00] (75.0082362859188,-9.97) [4.300000e+00] (76.7726194267189,-10.033) [4.200000e+00] (78.6602249298857,-10.233) [4.100000e+00] (80.0953847487801,-10.526) [4] (81.4237947228505,-10.853) [3.800000e+00] (82.4094012394071,-11.137) [3.800000e+00] (90.4064215094236,-12.599) [3.200000e+00] (91.7791118891167,-12.761) [3.200000e+00] (93.2690607870255,-12.927) [3.300000e+00] (94.9258643776602,-13.131) [3.200000e+00] (96.4233119768856,-13.315) [3.100000e+00] (97.7794091531292,-13.539) [3] (99.2566050421831,-13.721) [2.900000e+00] (100.834528136853,-13.918) [2.800000e+00] (102.038059375172,-14.076) [2.700000e+00] (103.564851467609,-14.21) [2.700000e+00] (105.10292010624,-14.316) [2.500000e+00] (106.352328039151,-14.45) [2.500000e+00] (107.570853984965,-14.606) [2.400000e+00] (109.162235182079,-14.748) [2.400000e+00] (110.512369431851,-14.892) [2.300000e+00] (111.678350262332,-15.037) [2.300000e+00] (113.235254720706,-15.144) [2.200000e+00] (114.500486265143,-15.249) [2.200000e+00] (115.691203492305,-15.382) [2.100000e+00] (115.815129572001,-15.528) [2.100000e+00] (117.676456857818,-15.642) [2] (119.477680213669,-15.649) [2] (121.68110463208,-15.667) [1.900000e+00] (123.336430499725,-15.756) [1.900000e+00] (124.837654253971,-15.889) [1.900000e+00] (125.874974432477,-16.079) [1.900000e+00] (127.464940685869,-16.178) [1.800000e+00] (129.19548862963,-16.275) [1.800000e+00] (130.857541771519,-16.416) [1.800000e+00] (132.21363502171,-16.627) [1.800000e+00] (133.550247559459,-16.799) [1.900000e+00] (134.959009363721,-16.962) [2] (136.520336217567,-17.12) [1.800000e+00] (137.872711335487,-17.243) [1.800000e+00] (139.076945489566,-17.415) [1.700000e+00] (140.399268842806,-17.544) [1.800000e+00] (141.977956830779,-17.703) [1.800000e+00] (143.325077182371,-17.802) [1.700000e+00] (144.660151796424,-17.868) [1.800000e+00] (146.571133738,-17.888) [1.800000e+00] (148.269322831534,-17.76) [1.800000e+00] (149.626182665483,-17.551) [1.800000e+00] (151.662688380933,-17.391) [1.800000e+00] (152.718137136586,-17.26) [1.900000e+00] (153.837406694506,-17.099) [1.800000e+00] (155.125065343297,-16.946) [1.800000e+00] (157.211165026066,-16.724) [1.700000e+00] (158.777742720471,-16.503) [1.700000e+00] (160.189513695575,-16.363) [1.900000e+00] (161.502800912108,-16.229) [1.900000e+00] (162.89502879595,-16.13) [1.800000e+00] (164.148212512045,-15.928) [1.800000e+00] (165.084159331749,-15.722) [1.900000e+00] (166.140376448098,-15.548) [1.900000e+00] (168.073974836101,-15.419) [1.900000e+00] (171.903368566451,-15.398) [1.700000e+00] (173.569902526982,-17.024) [1.300000e+00] (175.53259191065,-16.566) [1.400000e+00] (177.935861325938,-16.19) [1.500000e+00] (179.811407222947,-15.874) [1.600000e+00] (181.880781436237,-15.569) [1.600000e+00] (183.237574077208,-15.215) [1.700000e+00] (184.995797300345,-14.884) [1.800000e+00] (186.783495133997,-14.578) [1.900000e+00] (187.952482126714,-14.274) [2.100000e+00] (189.258334913618,-13.899) [2.200000e+00] (190.738599459577,-13.554) [2.200000e+00] (192.463118747332,-13.211) [2.200000e+00] (194.003421319868,-12.947) [2.300000e+00] (195.57383981248,-12.748) [2.300000e+00] (196.983300606632,-12.597) [2.300000e+00] (198.481506135811,-12.432) [2.300000e+00] (200.168477251637,-12.264) [2.300000e+00] (201.114162264182,-12.13) [2.400000e+00] (202.394383846677,-12.051) [2.400000e+00] (203.75431396949,-11.953) [2.400000e+00] (205.330754700682,-11.83) [2.400000e+00] (206.892138374923,-11.74) [2.500000e+00] (207.741581757429,-11.685) [2.500000e+00] (209.102985706053,-11.61) [2.600000e+00] (211.135704464084,-11.467) [2.700000e+00] (212.557210594941,-11.291) [2.700000e+00] (214.108788883075,-11.101) [2.800000e+00] (215.157375520155,-11.056) [2.900000e+00] (216.15643461017,-10.923) [3.100000e+00] (217.950858027716,-10.784) [3.300000e+00] (219.060511686867,-10.537) [3.300000e+00] (220.557241700015,-10.4) [3.500000e+00] (221.391560315826,-10.222) [3.800000e+00] (222.696512075325,-10.14) [4.100000e+00] (224.639715159097,-9.899) [4.500000e+00] (226.372497123793,-9.749) [4.800000e+00] (227.744407109268,-9.586) [5.500000e+00] (228.880265172045,-9.464) [5.900000e+00] (230.235578800823,-9.304) [6.500000e+00] (231.748069617228,-9.108) [6.800000e+00] (233.558252978639,-8.875) [7] (235.063246470297,-8.73) [7.100000e+00] (236.020206310127,-8.554) [7.100000e+00] (237.432741377094,-8.429) [7.200000e+00] (238.858024551416,-8.262) [7.100000e+00] (240.511864989205,-8.107) [6.800000e+00] (242.258165228102,-7.934) [6.600000e+00] (243.650385776785,-7.836) [6.400000e+00] (245.109501714279,-7.66) [6.200000e+00] (246.41003125226,-7.468) [6] (247.91047415366,-7.229) [5.800000e+00] (249.408674496533,-7.087) [5.500000e+00] (250.905335539608,-6.901) [5.300000e+00] (252.429101641981,-6.732) [5.100000e+00] (254.261837265445,-6.508) [4.900000e+00] (256.077338317457,-6.347) [4.700000e+00] (257.562018696169,-6.134) [4.500000e+00] (258.874594918112,-6.023) [4.300000e+00] (260.562968311294,-5.811) [4.100000e+00] (262.146131130528,-5.613) [3.900000e+00] (263.724810180359,-5.365) [3.800000e+00] (265.261324877772,-5.226) [3.500000e+00] (266.695641668371,-4.999) [3.400000e+00] (268.071397382789,-4.805) [3.200000e+00] (269.50725304322,-4.552) [3] (270.879226899651,-4.345) [2.800000e+00] (272.529283359421,-4.089) [2.700000e+00] (274.421414868838,-3.899) [2.500000e+00] (276.528515938972,-3.657) [2.400000e+00] (278.224450469698,-3.467) [2.300000e+00] (279.852654000009,-3.213) [2.200000e+00] (281.380900404519,-2.967) [2.100000e+00] (282.910687914953,-2.692) [2.100000e+00] (284.340519646842,-2.457) [2] (285.643290082154,-2.181) [1.900000e+00] (286.883581618075,-1.945) [1.800000e+00] (288.129196146879,-1.684) [1.800000e+00] (289.668018103901,-1.46) [1.700000e+00] (291.718798937234,-1.22) [1.700000e+00] (293.480855222687,-0.988) [1.600000e+00] (295.087271814318,-0.83) [1.600000e+00] (296.946972721786,-0.798) [1.500000e+00] (298.652642321077,-0.83) [1.500000e+00] (300.10874040534,-0.909) [1.400000e+00] (301.305531104619,-0.978) [1.400000e+00] (302.585043928458,-1.136) [1.400000e+00] (303.913378375254,-1.404) [1.500000e+00] (305.470971595757,-1.672) [1.500000e+00] (306.92854127026,-1.939) [1.500000e+00] (308.210996786529,-2.209) [1.500000e+00] (309.714513617752,-2.477) [1.500000e+00] (310.96089607739,-2.74) [1.500000e+00] (312.301209440349,-3.024) [1.500000e+00] (313.842201832416,-3.269) [1.600000e+00] (314.94653232983,-3.551) [1.800000e+00] (316.189901233967,-3.763) [1.900000e+00] (317.843665738257,-4.031) [2] (319.262080173156,-4.255) [2.100000e+00] (320.718176108592,-4.52) [2.200000e+00] (321.911954198816,-4.732) [2.500000e+00] (323.378556571735,-5.026) [2.800000e+00] (324.913593203712,-5.256) [3.100000e+00] (326.006645836546,-5.507) [3.500000e+00] (327.553729582038,-5.694) [4] (328.869245116202,-5.916) [4.500000e+00] (330.669681375372,-6.094) [4.900000e+00] (331.861986586285,-6.351) [5.200000e+00] (333.832351781839,-6.545) [5.700000e+00] (335.219313382338,-6.757) [6.100000e+00] (336.676178566863,-6.917) [6.500000e+00] (337.793956904831,-7.134) [6.800000e+00] (339.0560970724,-7.311) [7] (340.45279368349,-7.528) [7.100000e+00] (341.845707518994,-7.672) [7.100000e+00] (343.47089012962,-7.851) [7.200000e+00] (345.114845293166,-7.963) [7.200000e+00] (346.776171422735,-8.152) [7.100000e+00] (348.35036028571,-8.301) [7.100000e+00] (349.459871648953,-8.528) [7.100000e+00] (350.616033398694,-8.703) [7] (351.497758437856,-8.86) [6.900000e+00] (353.034334026721,-8.989) [6.700000e+00] (354.586669071716,-9.074) [6.600000e+00] (356.179630516457,-9.155) [6.400000e+00] (357.438757186451,-9.271) [6.200000e+00] (358.529425133756,-9.39) [6.100000e+00] (359.478813004749,-9.532) [5.800000e+00] (361.113870203384,-9.675) [5.700000e+00] (362.460972905081,-9.782) [5.500000e+00] (363.784751087263,-9.879) [5.300000e+00] (365.233348925488,-9.969) [5.200000e+00] (366.592499170642,-10.101) [5] (368.268111476218,-10.237) [4.900000e+00] (369.818974559425,-10.419) [4.700000e+00] (371.642733276156,-10.685) [4.600000e+00] (372.877833114694,-11.001) [4.400000e+00] (373.847532867175,-11.19) [4.300000e+00] (375.693074138188,-11.412) [4.100000e+00] (377.630304671522,-11.463) [4] (379.09697275044,-11.528) [3.800000e+00] (380.372556803692,-11.64) [3.700000e+00] (381.856454982116,-11.776) [3.500000e+00] (383.005119923821,-11.919) [3.300000e+00] (384.857455777906,-12.088) [3.200000e+00] (386.078266002381,-12.239) [3.200000e+00] (387.260475696,-12.362) [3.200000e+00] (389.108956134072,-12.409) [3.100000e+00] (390.953653796453,-12.432) [2.900000e+00] (392.525527147113,-12.5) [2.800000e+00] (393.960604190631,-12.689) [2.800000e+00] (395.779878336545,-12.859) [2.800000e+00] (397.904264438766,-13.094) [2.700000e+00] (399.214520508063,-13.314) [2.600000e+00] (400.393232341897,-13.571) [2.500000e+00] (401.647874011237,-13.774) [2.500000e+00] (402.939357986557,-13.984) [2.400000e+00] (404.591714086049,-14.176) [2.400000e+00] (406.2718054043,-14.32) [2.400000e+00] (407.533939067413,-14.519) [2.400000e+00] (408.688554066189,-14.637) [2.400000e+00] (410.549851784699,-14.788) [2.300000e+00] (412.090132781494,-14.83) [2.200000e+00] (413.592872714638,-15.015) [2.200000e+00] (414.827198547541,-15.209) [2.200000e+00] (416.789364884208,-15.394) [2.200000e+00] (418.043378717052,-15.55) [2.100000e+00] (419.387464912905,-15.93) [2] (420.472873767022,-16.192) [2] (421.724427922257,-16.478) [2] (423.503552062762,-16.562) [1.900000e+00] (424.828169183932,-16.685) [1.900000e+00] (426.354087009002,-16.739) [1.900000e+00] (427.785377809461,-16.807) [1.700000e+00] (429.073076401396,-16.926) [1.700000e+00] (430.106652771831,-17.068) [1.600000e+00] (431.401219934598,-17.158) [1.600000e+00] (433.205431349417,-17.248) [1.600000e+00] (434.578866109566,-17.353) [1.500000e+00] (436.204110128149,-17.507) [1.500000e+00] (437.46701398703,-17.658) [1.400000e+00] (438.906569154545,-17.852) [1.400000e+00] (440.101808404137,-17.969) [1.500000e+00] (441.330806400502,-18.097) [1.500000e+00] (443.360487222009,-18.182) [1.400000e+00] (444.585774223355,-18.25) [1.400000e+00] (445.447251768488,-18.17) [1.400000e+00] (447.12362865369,-17.912) [1.300000e+00] (448.757908036852,-17.697) [1.400000e+00] (450.639589132766,-17.439) [1.400000e+00] (451.816205698007,-17.237) [1.300000e+00] (452.9941430965,-17.065) [1.400000e+00] (454.324782973168,-16.989) [1.400000e+00] (455.645539375936,-16.878) [1.400000e+00] (456.434723634116,-16.729) [1.500000e+00] (456.720912797513,-16.525) [1.400000e+00] (457.811644272833,-16.327) [1.600000e+00] (459.498525417922,-16.033) [1.600000e+00] (461.469577023641,-15.747) [1.600000e+00] (463.191832955192,-15.465) [1.600000e+00] (464.677192693975,-15.222) [1.600000e+00] (466.37086931058,-14.943) [1.600000e+00] (468.175076857479,-14.739) [1.600000e+00] (470.070274909105,-14.536) [1.500000e+00] (471.191898749391,-14.413) [1.600000e+00] (472.485619237177,-14.316) [1.800000e+00] (473.894352188464,-14.297) [1.800000e+00] (475.2843152821,-14.247) [1.800000e+00] (476.772760414979,-14.174) [1.900000e+00] (477.794282650237,-14.062) [1.900000e+00] (479.272147329054,-13.973) [2] (481.272548904457,-13.839) [2] (483.080465268393,-13.733) [2.100000e+00] (484.381601955964,-13.665) [2.200000e+00] (485.775969040986,-13.563) [2.300000e+00] (487.077181092446,-13.401) [2.300000e+00] (489.279028768061,-13.204) [2.400000e+00] (490.763687600189,-13.02) [2.500000e+00] (491.869402232016,-12.837) [2.500000e+00] (493.070662947826,-12.64) [2.500000e+00] (494.53802035846,-12.458) [2.700000e+00] (496.492539449225,-12.275) [2.800000e+00] (497.893005483946,-12.122) [2.800000e+00] (499.123616082126,-11.968) [2.800000e+00] (500.490249812515,-11.835) [2.900000e+00] (501.848619204718,-11.682) [2.900000e+00] (503.312963977375,-11.566) [3] (504.493136941834,-11.409) [3.100000e+00] (505.878540989002,-11.274) [3.300000e+00] (507.491032689709,-11.118) [3.400000e+00] (508.862918091176,-10.935) [3.500000e+00] (511.147488495327,-10.796) [3.800000e+00] (512.948604172493,-10.614) [4] (514.328755259145,-10.438) [4.200000e+00] (516.083989741004,-10.3) [4.400000e+00] (517.537827675343,-10.172) [4.800000e+00] (519.392317458851,-10.061) [5.200000e+00] (520.815259503113,-9.944) [5.600000e+00] (522.379553032858,-9.792) [6] (523.810063323146,-9.61) [6.400000e+00] (525.637516703518,-9.414) [6.800000e+00] (527.023691376214,-9.321) [7.300000e+00] (528.15651341941,-9.149) [7.400000e+00] (529.172082217439,-8.984) [7.700000e+00] (530.85293204054,-8.836) [7.800000e+00] (532.357130095883,-8.71) [8] (533.626051093809,-8.573) [8.200000e+00] (534.898679503406,-8.452) [8.300000e+00] (536.107429634038,-8.264) [8.200000e+00] (537.799631396382,-8.075) [8.100000e+00] (540.384899305627,-7.876) [8] (541.339910154951,-7.715) [7.700000e+00] (542.511119680717,-7.661) [7.300000e+00] (543.880839780806,-7.633) [7.100000e+00] (545.200893674116,-7.409) [6.800000e+00] (546.475838257982,-7.245) [6.600000e+00] (547.608736611513,-7.032) [6.300000e+00] (549.143057840604,-6.86) [6] (550.521736593632,-6.726) [5.800000e+00] (552.116151548903,-6.522) [5.500000e+00] (553.811287547934,-6.305) [5.400000e+00] (555.298181574116,-6.105) [5.300000e+00] (556.74073906526,-5.926) [5.100000e+00] (557.826209757301,-5.717) [4.800000e+00] (559.27401937813,-5.489) [4.600000e+00] (559.306150016763,-5.28) [4.500000e+00] (554.03698251721,-5.057) [4.200000e+00] (550.895504015747,-5.033) [4.100000e+00] (557.717371908828,-5.156) [3.900000e+00] (561.272322234517,-5.281) [3.800000e+00] (563.747903483793,-5.203) [3.600000e+00] (564.998287509892,-4.978) [3.500000e+00] (566.837092085808,-4.748) [3.300000e+00] (568.695439782222,-4.514) [3.200000e+00] (569.834361750772,-4.302) [3.100000e+00] (571.248417125722,-4.023) [2.800000e+00] (572.80529153421,-3.801) [2.600000e+00] (574.549320164143,-3.571) [2.500000e+00] (576.188068158497,-3.327) [2.400000e+00] (578.026021500922,-3.09) [2.200000e+00] (579.600891674788,-2.832) [2.200000e+00] (581.740317445334,-2.59) [2.100000e+00] (583.303910184611,-2.314) [1.900000e+00] (584.752411942598,-2.064) [1.800000e+00] (586.321176517195,-1.813) [1.800000e+00] (588.424530119685,-1.551) [1.700000e+00] (590.44747590734,-1.304) [1.700000e+00] (592.019332554757,-1.041) [1.700000e+00] (593.690365127009,-0.8) [1.600000e+00] (595.153075403151,-0.696) [1.600000e+00] (596.676036840976,-0.739) [1.500000e+00] (598.709327188053,-0.795) [1.400000e+00] (601.300749078113,-2.544) [1.300000e+00] (602.105991355403,-2.71) [1.400000e+00] (602.931707421628,-2.856) [1.400000e+00] (604.097821108785,-3.021) [1.400000e+00] (605.605105678937,-3.159) [1.500000e+00] (606.909319136346,-3.331) [1.600000e+00] (607.979110811731,-3.493) [1.600000e+00] (609.188014567845,-3.646) [1.800000e+00] (610.690046607554,-3.809) [1.900000e+00] (612.411437982475,-4.003) [2] (614.375596230447,-4.17) [2.100000e+00] (616.187897873787,-4.376) [2.400000e+00] (617.94682586952,-4.576) [2.400000e+00] (618.749668182145,-4.779) [2.600000e+00] (620.273480998677,-4.971) [2.900000e+00] (621.701663395038,-5.196) [3.300000e+00] (623.128379160792,-5.442) [3.700000e+00] (624.704017811359,-5.668) [4.100000e+00] (625.890205708112,-5.859) [4.500000e+00] (627.184768119437,-6.025) [4.900000e+00] (628.376288411573,-6.173) [5.400000e+00] (629.95416652508,-6.417) [5.900000e+00] (631.361339658358,-6.624) [6.100000e+00] (632.467039445835,-6.799) [6.500000e+00] (633.877225704956,-6.956) [6.700000e+00] (634.377821438691,-7.18) [6.900000e+00] (635.886569630999,-7.328) [7] (637.87413280914,-7.457) [7.100000e+00] (639.081327361336,-7.556) [7.200000e+00] (640.297640667434,-7.738) [7.300000e+00] (641.772475802155,-7.909) [7.300000e+00] (643.080473498388,-8.053) [7.500000e+00] (644.590686114394,-8.199) [7.400000e+00] (646.167016013546,-8.389) [7.300000e+00] (647.243442658802,-8.559) [7.300000e+00] (648.343970668986,-8.723) [7.100000e+00] (649.684333638446,-8.831) [7] (651.167431792837,-8.938) [6.700000e+00] (652.901641882458,-9.081) [6.600000e+00] (654.338248404371,-9.243) [6.300000e+00] (655.474846404656,-9.424) [6.100000e+00] (657.13915376985,-9.627) [6] (658.702740091544,-9.773) [5.900000e+00] (660.580459086924,-9.973) [5.700000e+00] (662.026020678454,-10.183) [5.400000e+00] (663.454278583737,-10.426) [5.200000e+00] (664.918608256291,-10.574) [5.100000e+00] (666.458173966181,-10.646) [4.900000e+00] (668.330721643186,-10.788) [4.600000e+00] (669.558311123957,-10.94) [4.400000e+00] (671.25188905276,-11.118) [4.200000e+00] (672.389951047011,-11.246) [4] (674.707480115744,-11.353) [3.900000e+00] (675.728374949706,-11.489) [3.700000e+00] (677.108510448648,-11.599) [3.600000e+00] (679.2440557551,-11.705) [3.500000e+00] (681.03990082214,-11.873) [3.300000e+00] (682.434326451909,-12.131) [3.200000e+00] (683.467879725312,-12.398) [3] (684.649502814835,-12.614) [2.900000e+00] (685.759066706,-12.651) [2.900000e+00] (687.378953344612,-12.667) [2.900000e+00] (689.062024894014,-12.646) [2.700000e+00] (690.203181255074,-12.758) [2.600000e+00] (691.420265703543,-12.874) [2.600000e+00] (692.68013752651,-13.063) [2.400000e+00] (694.521863875757,-13.218) [2.300000e+00] (695.88632611914,-13.466) [2.400000e+00] (697.552177888773,-13.663) [2.300000e+00] (698.993949654389,-13.954) [2.200000e+00] (699.936593147191,-14.207) [2.100000e+00] (701.709024055777,-14.439) [2.100000e+00] (703.513131741756,-14.529) [2.200000e+00] (704.763963356725,-14.689) [2.100000e+00] (706.036575719774,-14.831) [2.100000e+00] (707.20080998498,-15.004) [2.100000e+00] (708.929071683957,-15.065) [2] (710.481543569578,-15.128) [1.900000e+00] (712.215914938905,-15.152) [1.900000e+00] (713.715535694763,-15.381) [1.900000e+00] (714.842317245742,-15.592) [2] (716.293816454677,-15.756) [1.900000e+00] (717.707006268394,-15.856) [1.900000e+00] (718.838180573656,-15.98) [2] (719.965567172751,-16.117) [1.900000e+00] (721.823820049284,-16.151) [1.900000e+00] (723.697136289684,-16.202) [1.900000e+00] (725.150266789064,-16.221) [1.900000e+00] (726.538141129001,-16.297) [1.900000e+00] (727.790604063571,-16.461) [1.800000e+00] (729.143013490269,-16.715) [1.800000e+00] (730.396856512014,-16.988) [1.800000e+00] (731.709323504927,-17.227) [1.700000e+00] (733.194736747184,-17.449) [1.600000e+00] (734.552313078727,-17.626) [1.500000e+00] (736.01284813964,-17.818) [1.400000e+00] (737.570231800915,-18) [1.400000e+00] (739.057883158724,-18.103) [1.300000e+00] (740.58160404782,-18.17) [1.300000e+00] (741.891057055759,-18.245) [1.400000e+00] (743.346254819787,-18.143) [1.400000e+00] (743.715041281529,-17.892) [1.500000e+00] (743.372501862502,-17.724) [1.400000e+00] (745.983919066963,-17.728) [1.400000e+00] (747.118878011834,-17.766) [1.400000e+00] (748.204335323046,-17.714) [1.500000e+00] (749.921836001063,-17.627) [1.600000e+00] (751.85808119249,-17.399) [1.600000e+00] (753.443353552948,-17.167) [1.500000e+00] (755.020276379409,-16.882) [1.500000e+00] (756.722107327212,-16.622) [1.600000e+00] (758.217849965371,-16.404) [1.700000e+00] (759.600472320502,-16.237) [1.700000e+00] (760.890382266074,-16.048) [1.800000e+00] (762.251915034731,-15.834) [1.900000e+00] (763.556890150241,-15.676) [1.900000e+00] (764.824330880797,-15.518) [1.800000e+00] (766.085660622746,-15.363) [1.700000e+00] (767.303515412042,-15.243) [1.800000e+00] (768.707746775803,-15.12) [1.800000e+00] (770.035275901486,-14.985) [1.900000e+00] (771.45749898875,-14.849) [1.800000e+00] (772.960126365527,-14.688) [1.900000e+00] (774.436410707631,-14.525) [2] (775.964604761534,-14.353) [2] (777.462755076765,-14.189) [1.900000e+00] (778.832378667063,-14.032) [1.900000e+00] (780.093793662851,-13.878) [1.800000e+00] (781.446113566901,-13.752) [1.900000e+00] (782.834503461074,-13.586) [1.800000e+00] (784.288319505995,-13.497) [1.800000e+00] (785.599318236394,-13.405) [1.900000e+00] (786.924607986195,-13.283) [2.100000e+00] (788.248433341269,-13.18) [2.200000e+00] (789.524138038227,-13.07) [2.400000e+00] (790.91709024823,-12.952) [2.500000e+00] (792.288176484898,-12.877) [2.500000e+00] (793.366829955702,-12.776) [2.600000e+00] (794.642446761998,-12.629) [2.800000e+00] (796.212734421098,-12.47) [3] (797.200481206599,-12.267) [3.100000e+00] (798.647581243616,-12.004) [3.200000e+00] (800.583991269068,-11.717) [3.500000e+00] (802.90744059022,-11.483) [3.700000e+00] (804.338700017224,-11.325) [3.800000e+00] (806.056278527151,-11.18) [4.200000e+00] (807.985111391972,-11.039) [4.300000e+00] (809.40285440908,-10.905) [4.600000e+00] (810.612357085689,-10.72) [4.800000e+00] (811.859479372142,-10.588) [5] (813.389994187876,-10.469) [5.300000e+00] (814.731034966986,-10.353) [5.900000e+00] (816.271277168218,-10.164) [6.400000e+00] (817.730428419094,-10.007) [6.800000e+00] (819.284273172684,-9.883) [7] (820.654668793693,-9.801) [7.300000e+00] (822.52108780309,-9.643) [7.500000e+00] (824.253041726866,-9.508) [7.800000e+00] (824.840833412025,-9.375) [8.100000e+00] (825.621798949205,-9.168) [8.300000e+00] (826.630547947332,-8.977) [8.400000e+00] (831.387618680305,-8.688) [8.100000e+00] (832.009593889613,-8.736) [8] (833.13129049664,-8.678) [7.700000e+00] (834.55738448232,-8.491) [7.300000e+00] (836.29381328966,-8.28) [7.100000e+00] (837.783693679666,-8.09) [6.800000e+00] (838.642402030511,-7.945) [6.500000e+00] (839.946772788831,-7.77) [6.200000e+00] (841.338348668701,-7.611) [6] (842.878677529188,-7.483) [5.800000e+00] (844.115207810356,-7.353) [5.600000e+00] (845.405796651774,-7.164) [5.400000e+00] (847.348138962983,-6.937) [5.300000e+00] (849.439057126407,-6.71) [5.100000e+00] (851.269312551894,-6.508) [4.800000e+00] (852.633501755337,-6.361) [4.500000e+00] (853.946733414982,-6.169) [4.400000e+00] (855.284935676456,-5.981) [4.200000e+00] (856.693903191344,-5.759) [4] (857.946273251773,-5.559) [3.800000e+00] (859.17385121571,-5.328) [3.600000e+00] (860.447224319571,-5.155) [3.400000e+00] (861.974037716558,-4.943) [3.300000e+00] (863.154179017472,-4.784) [3.100000e+00] (864.559686758026,-4.588) [2.900000e+00] (865.969848287846,-4.383) [2.900000e+00] (867.286867711739,-4.149) [2.800000e+00] (868.260319609999,-3.964) [2.600000e+00] (869.90360330309,-3.753) [2.500000e+00] (871.737734871017,-3.54) [2.400000e+00] (873.290023959297,-3.36) [2.400000e+00] (875.221085368602,-3.144) [2.400000e+00] (876.822958650073,-2.923) [2.300000e+00] (878.168558335542,-2.678) [2.200000e+00] (879.80133966195,-2.437) [2.100000e+00] (881.004900626457,-2.218) [2] (882.346711287478,-1.994) [1.900000e+00] (883.697561755581,-1.767) [1.700000e+00] (885.452750792101,-1.535) [1.600000e+00] (887.555980861665,-1.306) [1.500000e+00] (889.205200278853,-1.061) [1.600000e+00] (890.644715820389,-0.827) [1.600000e+00] (892.012869115298,-0.748) [1.600000e+00] (893.553879938004,-0.801) [1.500000e+00] (894.906967633035,-0.868) [1.500000e+00] (896.429897494422,-0.934) [1.500000e+00] (898.206359610865,-0.995) [1.300000e+00] (899.742210724292,-1.063) [1.300000e+00] (901.288470982272,-1.254) [1.200000e+00] (903.073700720065,-1.51) [1.100000e+00] (904.056099232407,-1.782) [1.200000e+00] (905.661577359442,-2.038) [1.300000e+00] (907.309240966211,-2.306) [1.400000e+00] (909.364346881288,-2.578) [1.500000e+00] (910.446869560287,-2.838) [1.600000e+00] (911.88862146923,-3.104) [1.700000e+00] (913.17326682145,-3.367) [1.900000e+00] (914.652547754957,-3.618) [2.100000e+00] (916.223188387228,-3.881) [2.100000e+00] (916.929453947779,-4.175) [2.300000e+00] (949.594894040151,-9.763) [7.400000e+00] (949.808442506302,-9.812) [7.200000e+00] (954.119267223631,-10.245) [6.100000e+00] (955.077367636151,-10.285) [6] (955.870193070796,-10.436) [5.900000e+00] (956.973622504513,-10.602) [5.700000e+00] (957.974781187876,-10.738) [5.400000e+00] (959.174455579098,-10.807) [5.200000e+00] (960.59579086236,-10.891) [5.100000e+00] (962.045024189117,-10.985) [4.900000e+00] (963.425911060813,-11.064) [4.800000e+00] (964.813321619232,-11.136) [4.700000e+00] (966.231642458392,-11.247) [4.600000e+00] (966.694102289736,-11.395) [4.400000e+00] (967.312982504803,-11.498) [4.200000e+00] (968.686475163626,-11.494) [4] (970.423758967149,-11.394) [3.800000e+00] (971.967186212811,-11.307) [3.700000e+00] (973.608225517697,-11.336) [3.600000e+00] (975.241000484524,-11.459) [3.600000e+00] (976.294257303585,-11.632) [3.500000e+00] (977.599308908957,-11.904) [3.500000e+00] (978.903584586514,-12.164) [3.400000e+00] (980.006235914641,-12.393) [3.200000e+00] (981.364566598335,-12.584) [3.100000e+00] (982.397411548232,-12.729) [2.900000e+00] (983.378530622847,-12.912) [2.900000e+00] (989.79094801466,-13.235) [2.600000e+00] (995.224455677119,-13.41) [2.500000e+00] (1000.14019726013,-13.706) [2.400000e+00] (1002.25207355658,-14.247) [2.200000e+00] (1000.65341649522,-14.931) [2.200000e+00] (997.295887116171,-15.812) [2.200000e+00] (994.919876553112,-16.289) [2.100000e+00] (994.332094927043,-16.622) [2.100000e+00] (995.485103280614,-16.682) [2.100000e+00] (996.923150762594,-16.607) [2] (998.196112979616,-16.548) [1.900000e+00] (1000.67604527668,-17.357) [1.500000e+00] (1001.93259553678,-17.288) [1.500000e+00] (1002.22561334395,-17.297) [1.600000e+00] (1003.20868579264,-17.338) [1.600000e+00] (1004.78410622502,-17.339) [1.600000e+00] (1005.48465970795,-17.355) [1.600000e+00] (1005.85593613862,-17.341) [1.500000e+00] (1007.06785016757,-17.295) [1.600000e+00] (1008.06297600792,-17.305) [1.500000e+00] (1008.80348316173,-17.345) [1.600000e+00] (1009.85654903618,-17.359) [1.600000e+00] (1011.20282240245,-17.344) [1.600000e+00] (1012.60324586046,-17.296) [1.600000e+00] (1014.21473272895,-17.231) [1.600000e+00] (1015.62342006652,-17.223) [1.600000e+00] (1017.13758234084,-17.182) [1.700000e+00] (1018.17431059987,-17.194) [1.700000e+00] (1019.64239789447,-17.222) [1.700000e+00] (1021.02026602436,-17.262) [1.600000e+00] (1022.49030262215,-17.315) [1.700000e+00] (1023.69162054579,-17.364) [1.600000e+00] (1024.8659118696,-17.41) [1.500000e+00] (1026.33623415529,-17.439) [1.500000e+00] (1027.80879272144,-17.5) [1.500000e+00] (1029.3551368915,-17.576) [1.500000e+00] (1030.66543718858,-17.673) [1.500000e+00] (1031.78538741735,-17.819) [1.400000e+00] (1033.27379069361,-17.983) [1.300000e+00] (1034.9056886297,-18.147) [1.400000e+00] (1036.38719108639,-18.326) [1.500000e+00] (1038.29470453214,-18.468) [1.500000e+00] (1039.41241759212,-18.662) [1.500000e+00] (1039.85018497153,-18.872) [1.500000e+00] (1041.09272505679,-18.793) [1.500000e+00] (1041.98129417478,-18.667) [1.500000e+00] (1043.34030054281,-18.513) [1.500000e+00] (1044.48960879633,-18.295) [1.500000e+00] (1045.85843405255,-18.043) [1.600000e+00] (1047.17096979954,-17.765) [1.600000e+00] (1048.3632461971,-17.507) [1.600000e+00] (1049.54725960384,-17.334) [1.600000e+00] (1050.59594536694,-17.217) [1.600000e+00] (1051.87085792077,-17.119) [1.500000e+00] (1052.99090194634,-17.03) [1.500000e+00] (1054.12971004,-16.957) [1.500000e+00] (1055.32266730831,-16.84) [1.500000e+00] (1056.72979576895,-16.701) [1.500000e+00] (1058.11738334515,-16.545) [1.500000e+00] (1059.3733385923,-16.392) [1.500000e+00] (1060.89401664355,-16.143) [1.600000e+00] (1062.18623248286,-15.915) [1.600000e+00] (1063.40329834032,-15.696) [1.600000e+00] (1064.57895149249,-15.546) [1.500000e+00] (1065.70579996237,-15.429) [1.600000e+00] (1066.97701680064,-15.293) [1.600000e+00] (1068.1782366588,-15.225) [1.600000e+00] (1069.49067382348,-15.171) [1.700000e+00] (1070.63327145846,-15.094) [1.700000e+00] (1071.61050304224,-14.96) [1.800000e+00] (1072.80938929815,-14.838) [1.800000e+00] (1073.96248623326,-14.688) [1.800000e+00] (1075.20648142696,-14.503) [1.700000e+00] (1076.64150979507,-14.343) [1.800000e+00] (1078.19601714235,-14.142) [1.900000e+00] (1079.76851039381,-13.994) [1.900000e+00] (1081.18623283987,-13.781) [2] (1082.59792771605,-13.623) [2.100000e+00] (1084.10431214011,-13.514) [2.100000e+00] (1085.90234959274,-13.381) [2.100000e+00] (1087.05398663402,-13.231) [2.200000e+00] (1088.57087081702,-13.053) [2.100000e+00] (1090.09008725511,-12.9) [2.100000e+00] (1091.4769918407,-12.772) [2.100000e+00] (1092.84513281712,-12.649) [2.200000e+00] (1094.24341218875,-12.522) [2.300000e+00] (1095.51394781334,-12.438) [2.400000e+00] (1096.1619996381,-12.383) [2.600000e+00] (1097.01206795742,-12.425) [2.700000e+00] (1099.014838651,-12.447) [2.900000e+00] (1100.39396114136,-12.309) [3.400000e+00] (1102.24594919868,-11.997) [3.800000e+00] (1104.00344501749,-11.681) [4.100000e+00] (1105.51128452111,-11.427) [4.400000e+00] (1107.12577098928,-11.181) [4.800000e+00] (1107.86715291421,-10.985) [5.200000e+00] (1109.350979832,-10.768) [5.500000e+00] (1110.98977308767,-10.523) [5.700000e+00] (1112.74367271982,-10.308) [6] (1114.19308776837,-10.146) [6.400000e+00] (1115.51086868174,-10.013) [6.800000e+00] (1116.88056518392,-9.896) [7.200000e+00] (1118.40123673035,-9.858) [7.700000e+00] (1119.77161229719,-9.812) [8.100000e+00] (1120.82456904281,-9.688) [8.500000e+00] (1121.82123851495,-9.578) [8.800000e+00] (1122.88575493397,-9.357) [9] (1124.42451016549,-9.221) [9.300000e+00] (1126.24355474329,-9.142) [9] (1127.67945653535,-8.966) [9] (1129.14763301534,-8.868) [9.100000e+00] (1130.56612978604,-8.765) [9] (1131.53665172696,-8.636) [8.900000e+00] (1132.91976023767,-8.484) [8.800000e+00] (1134.07684413984,-8.301) [8.500000e+00] (1135.01780587406,-8.116) [8.200000e+00] (1136.86260253337,-7.922) [7.700000e+00] (1143.78281335461,-7.406) [5.900000e+00] (1144.95183244868,-7.148) [5.700000e+00] (1147.24158909297,-6.876) [5.400000e+00] (1147.44895053885,-6.646) [5.200000e+00] (1146.53928710166,-6.497) [5] (1145.94752157509,-6.361) [4.900000e+00] (1147.76499124173,-6.235) [4.700000e+00] (1149.71565228853,-6.108) [4.600000e+00] (1151.26402471399,-5.943) [4.400000e+00] (1152.86976213877,-5.753) [4.200000e+00] (1154.37011162885,-5.579) [4] (1155.88854477508,-5.444) [3.800000e+00] (1157.56709413638,-5.27) [3.500000e+00] (1158.84511433255,-5.088) [3.400000e+00] (1160.10796309328,-4.93) [3.100000e+00] (1161.46492281255,-4.745) [3] (1162.9720785239,-4.565) [2.800000e+00] (1164.44841634584,-4.378) [2.600000e+00] (1165.9428369353,-4.157) [2.400000e+00] (1167.50035013104,-3.934) [2.300000e+00] (1169.04600948072,-3.706) [2.200000e+00] (1170.1113188371,-3.482) [2.100000e+00] (1171.51531979886,-3.269) [2] (1172.97279402392,-3.059) [1.900000e+00] (1174.45204455426,-2.837) [1.800000e+00] (1176.02296795244,-2.635) [1.700000e+00] (1177.56940506485,-2.405) [1.700000e+00] (1179.12691785991,-2.181) [1.400000e+00] (1179.88384728466,-1.953) [1.400000e+00] (1180.87157080448,-1.718) [1.400000e+00] (1182.22230031307,-1.514) [1.300000e+00] (1183.39191592362,-1.309) [1.200000e+00] (1183.84659478021,-1.093) [1.200000e+00] (1186.07762491598,-0.919) [1.200000e+00] (1188.46440227703,-0.789) [1.200000e+00] (1190.661499174,-0.73) [1.200000e+00] (1192.57219419704,-0.788) [1.300000e+00] (1195.23748059964,-0.842) [1.300000e+00] (1196.96939848037,-0.906) [1.300000e+00] (1198.78337303955,-0.975) [1.300000e+00] (1200.24250369573,-1.105) [1.300000e+00] (1201.64145577211,-1.351) [1.300000e+00] (1203.01707432754,-1.622) [1.300000e+00] (1204.39648551966,-1.878) [1.400000e+00] (1205.68266482191,-2.171) [1.500000e+00] (1206.99508854765,-2.433) [1.500000e+00] (1208.22555873589,-2.689) [1.600000e+00] (1209.34335883212,-2.959) [1.700000e+00] (1210.60464559154,-3.221) [1.600000e+00] (1211.8946179894,-3.473) [1.600000e+00] (1213.3189327837,-3.719) [1.700000e+00] (1214.61784457113,-3.975) [1.800000e+00] (1216.00619472316,-4.227) [1.700000e+00] (1217.34652371687,-4.479) [1.900000e+00] (1218.87097976344,-4.721) [2] (1220.7248737587,-4.977) [2.100000e+00] (1221.98626234077,-5.247) [2.200000e+00] (1222.78938611222,-5.557) [2.400000e+00] (1223.98009727317,-5.796) [2.600000e+00] (1224.93486893376,-6.018) [3.100000e+00] (1225.9325136813,-6.22) [3.500000e+00] (1227.33447808197,-6.436) [3.800000e+00] (1228.50195886306,-6.668) [4.200000e+00] (1229.63238698508,-6.932) [4.700000e+00] (1230.80433677276,-7.124) [5.100000e+00] (1231.89511164539,-7.285) [5.600000e+00] (1233.07667630422,-7.435) [6.200000e+00] (1234.66354595031,-7.585) [6.500000e+00] (1236.33964681948,-7.713) [7] (1238.30573416926,-7.911) [7.400000e+00] (1239.19284199324,-8.064) [7.800000e+00] (1240.2670895661,-8.168) [8.200000e+00] (1241.95088108564,-8.293) [8.400000e+00] (1243.16793852173,-8.474) [8.600000e+00] (1244.56756398881,-8.701) [8.800000e+00] (1246.10485348372,-8.901) [8.900000e+00] (1247.40745218822,-9.047) [9] (1248.77703927679,-9.187) [8.900000e+00] (1250.789999579,-9.341) [8.900000e+00] (1251.89563609244,-9.476) [8.600000e+00] (1253.28486677653,-9.659) [8.300000e+00] (1254.62955908615,-9.837) [8] (1256.26075601036,-10.015) [7.600000e+00] (1257.4101500688,-10.185) [7.300000e+00] (1258.91438674125,-10.325) [7] (1260.31099690458,-10.502) [6.700000e+00] (1261.60688989225,-10.664) [6.500000e+00] (1263.21350636205,-10.809) [6.300000e+00] (1264.71685952279,-10.954) [6] (1265.98338961353,-11.19) [5.700000e+00] (1266.73226112732,-11.393) [5.500000e+00] (1267.7071425454,-11.554) [5.300000e+00] (1269.72903828236,-11.626) [5] (1270.27325560719,-11.698) [4.800000e+00] (1271.18437252059,-11.796) [4.700000e+00] (1272.74691494272,-11.9) [4.500000e+00] (1274.05309607591,-11.959) [4.400000e+00] (1276.06158390439,-11.954) [4.200000e+00] (1278.22795215536,-11.968) [3.800000e+00] (1280.0078803631,-12.01) [3.700000e+00] (1281.5564452019,-12.113) [3.500000e+00] (1283.19143353155,-12.287) [3.300000e+00] (1285.03008670274,-12.514) [3.200000e+00] (1286.80476550434,-12.713) [3.100000e+00] (1288.14353123638,-12.931) [2.900000e+00] (1289.43484858004,-13.167) [2.900000e+00] (1290.8908552334,-13.364) [2.900000e+00] (1292.49112588285,-13.555) [2.800000e+00] (1294.02986696077,-13.741) [2.700000e+00] (1294.75384418361,-13.958) [2.600000e+00] (1295.804755227,-14.182) [2.500000e+00] (1297.13000945056,-14.372) [2.400000e+00] (1298.48217956594,-14.497) [2.300000e+00] (1299.9620885554,-14.599) [2.200000e+00] (1301.49033216845,-14.715) [2.200000e+00] (1302.84349389597,-14.882) [2.200000e+00] (1304.19977636202,-15.022) [2.200000e+00] (1305.4980057917,-15.231) [2] (1307.01788060733,-15.459) [1.900000e+00] (1308.40622256463,-15.637) [1.900000e+00] (1309.7847402734,-15.805) [1.800000e+00] (1311.17542256977,-15.963) [1.800000e+00] (1312.40364871271,-16.098) [1.700000e+00] (1313.88298765571,-16.257) [1.600000e+00] (1315.07436739274,-16.415) [1.600000e+00] (1316.41458462095,-16.57) [1.400000e+00] (1317.71001305514,-16.709) [1.400000e+00] (1318.98558132077,-16.852) [1.400000e+00] (1319.83116048681,-17.064) [1.400000e+00] (1320.98959498518,-17.268) [1.400000e+00] (1322.46882723301,-17.461) [1.400000e+00] (1323.97362799299,-17.56) [1.300000e+00] (1325.32221361779,-17.597) [1.300000e+00] (1326.85627103847,-17.614) [1.300000e+00] (1328.30177718925,-17.633) [1.300000e+00] (1329.71043785175,-17.698) [1.300000e+00] (1331.10827995892,-17.768) [1.300000e+00] (1332.6523732995,-17.822) [1.400000e+00] (1334.47783129625,-17.829) [1.400000e+00] (1335.85120592223,-17.945) [1.400000e+00] (1337.10688025979,-18.177) [1.500000e+00] (1338.26063147237,-18.392) [1.500000e+00] (1339.68323188759,-18.67) [1.300000e+00] (1339.9581389525,-18.799) [1.300000e+00] (1340.67732573557,-18.784) [1.300000e+00] (1341.21753081328,-18.63) [1.300000e+00] (1342.94957195777,-18.381) [1.300000e+00] (1344.40323176751,-18.093) [1.400000e+00] (1346.17052779674,-17.84) [1.400000e+00] (1347.9066835279,-17.536) [1.400000e+00] (1349.55060342417,-17.276) [1.400000e+00] (1351.14047768772,-17.017) [1.400000e+00] (1352.44473305526,-16.732) [1.500000e+00] (1353.96839755711,-16.419) [1.500000e+00] (1355.50635264854,-16.138) [1.500000e+00] (1357.11129881878,-15.86) [1.500000e+00] (1358.53513639307,-15.575) [1.500000e+00] (1359.70261216194,-15.361) [1.500000e+00] (1361.2488302731,-15.218) [1.600000e+00] (1362.58088957364,-15.111) [1.600000e+00] (1363.61236525458,-15.043) [1.600000e+00] (1364.85041088957,-15.045) [1.600000e+00] (1366.07036971485,-15.082) [1.500000e+00] (1367.13400802831,-15.091) [1.500000e+00] (1368.40588516614,-15.031) [1.500000e+00] (1369.5347367272,-14.91) [1.600000e+00] (1370.90576622876,-14.792) [1.600000e+00] (1372.24140296951,-14.659) [1.600000e+00] (1373.52700687035,-14.42) [1.600000e+00] (1375.30111058419,-14.254) [1.600000e+00] (1376.63384049369,-14.122) [1.500000e+00] (1377.83404143197,-14.026) [1.500000e+00] (1378.87590570485,-13.925) [1.600000e+00] (1379.9274857251,-13.773) [1.500000e+00] (1381.43852547062,-13.578) [1.600000e+00] (1382.91104905107,-13.409) [1.500000e+00] (1384.29569773182,-13.288) [1.500000e+00] (1385.56679272203,-13.196) [1.700000e+00] (1386.99130139299,-13.068) [1.600000e+00] (1388.34524157429,-12.941) [1.700000e+00] (1389.21124576909,-12.901) [1.800000e+00] (1389.98334522926,-12.9) [1.800000e+00] (1391.0488726273,-12.801) [2] (1393.74950605546,-12.776) [2.400000e+00] (1394.97002432265,-12.698) [2.700000e+00] (1396.22504644985,-12.473) [2.900000e+00] (1398.05555037586,-12.144) [3.200000e+00] (1399.1181873029,-11.824) [3.600000e+00] (1401.64920663085,-11.48) [4.200000e+00] (1403.44642385463,-11.258) [4.600000e+00] (1404.68926236817,-11.005) [4.800000e+00] (1405.90709396026,-10.804) [5.100000e+00] (1407.43600136379,-10.614) [5.400000e+00] (1409.00622151415,-10.435) [5.600000e+00] (1410.64722942181,-10.298) [6] (1411.94634451724,-10.143) [6.400000e+00] (1413.21297101755,-10.041) [6.700000e+00] (1414.46385239472,-9.968) [7] (1415.92431418593,-9.906) [7.200000e+00] (1417.36155049859,-9.807) [7.200000e+00] (1418.68221953631,-9.675) [7.200000e+00] (1420.20967378253,-9.48) [7.300000e+00] (1421.67091600235,-9.317) [7.200000e+00] (1422.98923979945,-9.171) [7.200000e+00] (1424.22582926871,-8.984) [7.200000e+00] (1425.78477066576,-8.755) [6.900000e+00] (1427.58712355013,-8.535) [6.600000e+00] (1429.05573673518,-8.346) [6.300000e+00] (1430.79142762825,-8.097) [6.200000e+00] (1432.37147033703,-7.846) [5.900000e+00] (1433.98701834985,-7.676) [5.600000e+00] (1435.64912808587,-7.556) [5.500000e+00] (1437.12320908543,-7.416) [5.300000e+00] (1438.75282710198,-7.268) [5.200000e+00] (1440.11402407316,-7.118) [5] (1441.70590362958,-6.951) [4.800000e+00] (1443.1476036757,-6.699) [4.700000e+00] (1444.73378655567,-6.53) [4.600000e+00] (1446.3830544746,-6.366) [4.500000e+00] (1447.90001042533,-6.182) [4.400000e+00] (1449.34405574091,-5.969) [4.400000e+00] (1450.64607334099,-5.769) [4.200000e+00] (1452.09670606906,-5.551) [4.100000e+00] (1453.60740936325,-5.32) [4] (1454.97072700506,-5.149) [3.900000e+00] (1456.47640506205,-4.964) [3.700000e+00] (1458.17245669575,-4.764) [3.500000e+00] (1459.46085205005,-4.569) [3.300000e+00] (1460.82818876259,-4.343) [3] (1462.50827288093,-4.125) [2.800000e+00] (1463.84244686445,-3.909) [2.600000e+00] (1465.40149558962,-3.698) [2.400000e+00] (1466.52676194585,-3.463) [2.300000e+00] (1467.92871193727,-3.244) [2.100000e+00] (1469.68617260176,-3.026) [2.100000e+00] (1471.11201506838,-2.817) [2.100000e+00] (1472.59748306645,-2.601) [2] (1474.07546982089,-2.369) [1.800000e+00] (1475.78156797342,-2.13) [1.700000e+00] (1477.61472914717,-1.899) [1.600000e+00] (1467.60446488409,-18.751) [1.100000e+00] (1466.58437849054,-18.578) [1.100000e+00] (1465.49115594547,-18.426) [1.200000e+00] (1464.4061968499,-18.23) [1.100000e+00] (1463.37929844506,-18.173) [1.100000e+00] (1462.43658902727,-18.086) [1.200000e+00] (1461.23204683625,-17.887) [1.200000e+00] (1459.85287508218,-17.681) [1.200000e+00] (1458.36015006729,-17.466) [1.200000e+00] (1456.86731162039,-17.203) [1.300000e+00] (1455.5192925405,-16.868) [1.300000e+00] (1454.31419145351,-16.542) [1.300000e+00] (1450.64071654329,-15.98) [1.500000e+00] (1448.138509899,-15.593) [1.600000e+00] (1446.51134828992,-15.316) [1.600000e+00] (1444.69694014989,-14.952) [1.700000e+00] (1442.94628759967,-14.61) [1.700000e+00] (1441.41503928239,-14.241) [1.700000e+00] (1440.04692088087,-13.935) [1.700000e+00] (1438.41953602032,-13.647) [1.900000e+00] (1436.88002474145,-13.396) [2.100000e+00] (1435.2195896949,-13.153) [2.100000e+00] (1433.90182745959,-12.964) [2.300000e+00] (1432.13029292342,-12.785) [2.500000e+00] (1430.76217231493,-12.641) [2.600000e+00] (1429.47600842649,-12.489) [2.700000e+00] (1428.02749550952,-12.368) [2.700000e+00] (1426.41976101012,-12.238) [2.700000e+00] (1424.70595225822,-12.071) [2.700000e+00] (1423.23633762869,-11.893) [2.700000e+00] (1421.55479823343,-11.719) [2.800000e+00] (1420.07479730604,-11.573) [2.900000e+00] (1417.8192306451,-11.462) [3.100000e+00] (1415.249793885,-11.356) [3.100000e+00] (1413.73606909636,-11.402) [3.400000e+00] (1413.25438261309,-11.716) [3.400000e+00] (1413.83120554272,-12.001) [3.500000e+00] (1413.97837015015,-12.097) [3.700000e+00] (1413.27080885722,-12.012) [3.900000e+00] (1412.51813951515,-11.777) [4.200000e+00] (1411.39130711559,-11.52) [4.600000e+00] (1410.17649085623,-11.307) [4.900000e+00] (1408.79720226103,-11.078) [5.300000e+00] (1407.37213280066,-10.896) [5.700000e+00] (1406.17462295122,-10.718) [6] (1405.24084633161,-10.546) [6.600000e+00] (1403.56767805647,-10.304) [7] (1402.06299671626,-10.116) [7.300000e+00] (1400.53029312182,-9.965) [7.600000e+00] (1399.1975649316,-9.821) [7.900000e+00] (1397.75128348039,-9.642) [7.900000e+00] (1396.53501406379,-9.446) [7.900000e+00] (1395.05724325484,-9.277) [8] (1393.55691886572,-9.113) [7.800000e+00] (1392.22865747505,-8.993) [7.600000e+00] (1390.74641900698,-8.828) [7.500000e+00] (1389.36177164464,-8.623) [7.200000e+00] (1387.89673019638,-8.443) [7] (1386.15589676663,-8.302) [6.600000e+00] (1384.65177529787,-8.161) [6.400000e+00] (1383.41808922181,-7.995) [6.100000e+00] (1382.23933724953,-7.785) [5.900000e+00] (1380.6360629875,-7.596) [5.800000e+00] (1378.8869657072,-7.399) [5.500000e+00] (1377.46781319561,-7.191) [5.200000e+00] (1376.0102530205,-6.949) [5.100000e+00] (1374.66088951669,-6.727) [4.800000e+00] (1373.08619735126,-6.59) [4.700000e+00] (1371.94585264192,-6.422) [4.500000e+00] (1370.66940066178,-6.242) [4.400000e+00] (1369.69576279155,-6.048) [4.300000e+00] (1368.43214999165,-5.859) [4.100000e+00] (1367.11750557345,-5.68) [4] (1365.82687018668,-5.514) [3.800000e+00] (1358.0491112121,-4.428) [3] (1356.91412223239,-4.282) [2.800000e+00] (1355.4671650152,-4.083) [2.700000e+00] (1354.08631040554,-3.901) [2.600000e+00] (1352.36802622931,-3.685) [2.500000e+00] (1350.49576365711,-3.505) [2.400000e+00] (1349.08263794274,-3.322) [2.300000e+00] (1347.21473544621,-3.093) [2.200000e+00] (1345.5444662084,-2.864) [2.200000e+00] (1343.97647319727,-2.6) [2] (1342.33177247173,-2.367) [1.900000e+00] (1340.28900331513,-2.124) [1.800000e+00] (1338.82317714085,-1.871) [1.800000e+00] (1336.97346597111,-1.607) [1.600000e+00] (1335.13113023837,-1.339) [1.700000e+00] (1333.24893362696,-1.07) [1.600000e+00] (1331.79807220526,-0.794) [1.600000e+00] (1330.28412264903,-0.73) [1.600000e+00] (1328.05924709374,-0.783) [1.600000e+00] (1326.7399172119,-0.846) [1.500000e+00] (1325.14567940565,-0.905) [1.500000e+00] (1323.7947525533,-0.995) [1.500000e+00] (1321.92305171687,-1.226) [1.500000e+00] (1320.43321613918,-1.499) [1.500000e+00] (1319.30113144111,-1.77) [1.600000e+00] (1318.25993743423,-2.048) [1.600000e+00] (1316.62193764001,-2.31) [1.700000e+00] (1315.36133409805,-2.583) [1.700000e+00] (1314.59515654598,-2.852) [1.800000e+00] (1313.05049450631,-3.124) [1.800000e+00] (1311.33911983747,-3.365) [1.900000e+00] (1310.13344862224,-3.644) [2] (1309.00895235099,-3.905) [2.200000e+00] (1307.89864040397,-4.17) [2.300000e+00] (1306.45245882977,-4.393) [2.400000e+00] (1305.17454847706,-4.631) [2.400000e+00] (1304.16115840331,-4.913) [2.500000e+00] (1303.13269599313,-5.173) [2.600000e+00] (1301.98028958134,-5.379) [2.700000e+00] (1300.21096728202,-5.571) [2.900000e+00] (1299.56582512303,-5.78) [3.200000e+00] (1298.72684237099,-6.01) [3.500000e+00] (1296.73062616818,-6.193) [4] (1295.25965387372,-6.341) [4.500000e+00] (1294.18696787251,-6.551) [5.100000e+00] (1292.99111826921,-6.768) [5.600000e+00] (1291.57429744316,-6.969) [6.100000e+00] (1289.70883195093,-7.141) [6.600000e+00] (1288.40010416754,-7.292) [6.900000e+00] (1286.97860315129,-7.521) [7.300000e+00] (1285.72090744522,-7.685) [7.600000e+00] (1284.36483533216,-7.817) [7.800000e+00] (1282.95539129053,-7.971) [7.900000e+00] (1281.72705808084,-8.094) [7.900000e+00] (1280.01848277533,-8.247) [8.100000e+00] (1278.56704875759,-8.42) [8.300000e+00] (1276.54536417516,-8.63) [8.300000e+00] (1275.55083824411,-8.945) [8.100000e+00] (1274.74490616559,-9.244) [8.100000e+00] (1274.4520582803,-9.45) [7.800000e+00] (1272.55857732872,-9.553) [7.600000e+00] (1270.99951456589,-9.636) [7.400000e+00] (1269.97562573783,-9.723) [7.200000e+00] (1268.23030811423,-9.793) [7] (1267.44012253526,-9.92) [6.800000e+00] (1265.98556826663,-10.057) [6.600000e+00] (1264.77687956989,-10.214) [6.400000e+00] (1263.81093573556,-10.345) [6.200000e+00] (1262.33684147126,-10.419) [6] (1260.453389761,-10.418) [5.800000e+00] (1259.69246261962,-10.516) [5.600000e+00] (1258.29517832209,-10.658) [5.300000e+00] (1256.87377918654,-10.789) [5.200000e+00] (1255.54628833979,-10.886) [5] (1253.79270600637,-10.99) [4.800000e+00] (1252.19554818548,-11.13) [4.700000e+00] (1250.33755918074,-11.308) [4.500000e+00] (1248.78384727515,-11.516) [4.400000e+00] (1247.65300567139,-11.736) [4.100000e+00] (1246.14731314699,-11.923) [3.900000e+00] (1244.15690734271,-12.099) [3.700000e+00] (1242.85254201573,-12.238) [3.700000e+00] (1241.5257249022,-12.453) [3.600000e+00] (1239.70827050957,-12.646) [3.400000e+00] (1238.47401072197,-12.812) [3.300000e+00] (1237.18102511146,-12.951) [3.200000e+00] (1235.77838608894,-13.092) [3] (1234.92724201865,-13.271) [2.800000e+00] (1233.25862419952,-13.427) [2.800000e+00] (1231.69373668181,-13.516) [2.700000e+00] (1230.16413608929,-13.684) [2.600000e+00] (1228.80067933978,-13.848) [2.500000e+00] (1227.52879323466,-13.989) [2.300000e+00] (1225.76169411969,-14.134) [2.300000e+00] (1224.39064988976,-14.318) [2.200000e+00] (1223.29374430628,-14.448) [2.100000e+00] (1221.75655623334,-14.598) [2] (1220.28178216083,-14.719) [1.900000e+00] (1218.84754398989,-14.884) [1.800000e+00] (1217.48320418753,-15.031) [1.600000e+00] (1216.02864650973,-15.162) [1.700000e+00] (1214.52305365948,-15.266) [1.700000e+00] (1213.09629942697,-15.383) [1.600000e+00] (1211.73866451105,-15.477) [1.600000e+00] (1210.3088953757,-15.589) [1.600000e+00] (1208.98509239242,-15.678) [1.600000e+00] (1207.56514484015,-15.779) [1.600000e+00] (1206.20984579138,-15.881) [1.500000e+00] (1204.76063891286,-15.962) [1.300000e+00] (1203.44821429867,-16.075) [1.400000e+00] (1202.04255779459,-16.209) [1.500000e+00] (1200.58129397006,-16.332) [1.500000e+00] (1199.21326203556,-16.458) [1.500000e+00] (1197.77980076775,-16.585) [1.600000e+00] (1196.51695501576,-16.73) [1.600000e+00] (1195.36901388762,-16.876) [1.500000e+00] (1193.99942338997,-16.995) [1.600000e+00] (1192.64110946744,-17.121) [1.600000e+00] (1191.25197854405,-17.236) [1.600000e+00] (1189.8470998028,-17.356) [1.600000e+00] (1188.55489161248,-17.476) [1.700000e+00] (1187.30555785631,-17.587) [1.600000e+00] (1185.71956521724,-17.698) [1.700000e+00] (1184.48899151613,-17.768) [1.700000e+00] (1183.20504677524,-17.891) [1.700000e+00] (1181.87006597298,-17.857) [1.600000e+00] (1180.51408748793,-17.71) [1.700000e+00] (1179.21527491556,-17.532) [1.700000e+00] (1177.55267730216,-17.397) [1.700000e+00] (1175.8991208432,-17.283) [1.800000e+00] (1174.75798642428,-17.231) [1.900000e+00] (1174.10827590382,-17.186) [1.800000e+00] (1173.41559139117,-17.132) [1.700000e+00] (1171.92049305529,-16.974) [1.700000e+00] (1170.73736461812,-16.889) [1.700000e+00] (1169.62044235932,-16.756) [1.700000e+00] (1168.32901196076,-16.614) [1.800000e+00] (1167.16833665748,-16.422) [1.800000e+00] (1166.17759826385,-16.263) [1.800000e+00] (1164.65100297407,-16.072) [1.900000e+00] (1163.09047622275,-15.905) [1.800000e+00] (1161.57194348978,-15.672) [1.800000e+00] (1160.0347489412,-15.497) [1.800000e+00] (1158.69966508499,-15.299) [1.900000e+00] (1156.7492062204,-15.122) [2] (1155.41577959662,-14.99) [2.100000e+00] (1154.00944150736,-14.904) [2.200000e+00] (1152.70283927249,-14.772) [2.200000e+00] (1151.45485883103,-14.676) [2.200000e+00] (1149.95305257152,-14.522) [2.200000e+00] (1148.63615195832,-14.381) [2.300000e+00] (1147.34102719149,-14.204) [2.400000e+00] (1145.82103639964,-14.04) [2.400000e+00] (1144.74892179738,-13.848) [2.600000e+00] (1143.56792615695,-13.716) [2.600000e+00] (1142.35018458587,-13.602) [2.600000e+00] (1141.65187477676,-13.491) [2.600000e+00] (1140.30425583196,-13.382) [2.600000e+00] (1138.82791586104,-13.233) [2.600000e+00] (1137.18251807842,-13.105) [2.700000e+00] (1135.59875521519,-12.947) [2.700000e+00] (1134.26075561296,-12.762) [2.800000e+00] (1133.03698558365,-12.587) [2.800000e+00] (1131.26015143414,-12.428) [2.800000e+00] (1130.22575918218,-12.33) [2.900000e+00] (1128.87269085595,-12.251) [3] (1127.56463102108,-12.13) [3.100000e+00] (1126.03793230557,-12.02) [3.100000e+00] (1124.6570592156,-11.9) [3.300000e+00] (1123.48141170852,-11.745) [3.400000e+00] (1122.05251433599,-11.596) [3.500000e+00] (1120.54166164881,-11.451) [3.700000e+00] (1119.30359974042,-11.308) [3.900000e+00] (1117.97084917283,-11.201) [4.200000e+00] (1116.76506195247,-11.128) [4.700000e+00] (1115.52388738955,-10.998) [5.100000e+00] (1114.06708615421,-10.884) [5.500000e+00] (1112.90203572806,-10.767) [5.900000e+00] (1111.48742851512,-10.605) [6.400000e+00] (1109.30596956348,-10.398) [6.800000e+00] (1107.88902697108,-10.193) [7.100000e+00] (1106.47286300133,-10.049) [7.600000e+00] (1105.07322590136,-9.923) [8] (1103.8073583699,-9.776) [8.300000e+00] (1102.3896380727,-9.614) [8.500000e+00] (1101.1365061219,-9.466) [8.700000e+00] (1099.64742802074,-9.296) [8.700000e+00] (1098.08096586433,-9.195) [8.800000e+00] (1097.40520745745,-9.079) [8.800000e+00] (1097.40520745745,-8.921) [8.900000e+00] (1094.21064647718,-8.686) [8.600000e+00] (1091.40446483745,-8.448) [8.200000e+00] (1089.8424730639,-8.213) [8] (1087.99475856794,-7.98) [7.600000e+00] (1086.07160169445,-7.758) [7.300000e+00] (1084.60935340063,-7.561) [7] (1083.08799843377,-7.451) [6.500000e+00] (1081.81619933602,-7.328) [6.300000e+00] (1079.1385388049,-6.985) [5.700000e+00] (1077.74570397125,-6.806) [5.500000e+00] (1075.8613386601,-6.601) [5.300000e+00] (1074.6226901946,-6.406) [5.200000e+00] (1073.3772368842,-6.223) [5.100000e+00] (1071.81679794179,-6.058) [4.900000e+00] (1070.29388578812,-5.885) [4.700000e+00] (1069.06184758176,-5.705) [4.400000e+00] (1067.97097000306,-5.499) [4.100000e+00] (1066.61410523025,-5.298) [3.900000e+00] (1065.01001506618,-5.076) [3.700000e+00] (1063.42099365522,-4.917) [3.500000e+00] (1061.67934088511,-4.744) [3.300000e+00] (1060.29311502131,-4.554) [3.200000e+00] (1058.8272692515,-4.356) [3.100000e+00] (1057.35101926743,-4.137) [2.900000e+00] (1055.91375421798,-3.9) [2.800000e+00] (1054.31345448368,-3.696) [2.600000e+00] (1052.81309462103,-3.482) [2.500000e+00] (1051.1007989871,-3.245) [2.500000e+00] (1049.3847134108,-3.021) [2.200000e+00] (1048.03309632509,-2.8) [2.100000e+00] (1046.54547161327,-2.547) [2] (1044.95256033064,-2.301) [1.800000e+00] (1043.36723208579,-2.06) [1.800000e+00] (1041.79240268213,-1.822) [1.600000e+00] (1040.44904904586,-1.568) [1.600000e+00] (1039.08693180037,-1.321) [1.600000e+00] (1037.69623386343,-1.079) [1.600000e+00] (1036.08465451642,-0.868) [1.500000e+00] (1034.44371585572,-0.783) [1.400000e+00] (1033.01169895211,-0.809) [1.300000e+00] (1031.81047651529,-0.884) [1.300000e+00] (1030.48452302764,-0.952) [1.300000e+00] (1029.18034673384,-1.076) [1.200000e+00] (1027.77389653641,-1.321) [1.100000e+00] (1026.29161594517,-1.603) [1.200000e+00] (1024.95963488762,-1.873) [1.100000e+00] (1023.55473969911,-2.15) [1.100000e+00] (1022.15509437549,-2.42) [1.200000e+00] (1020.91547149935,-2.691) [1.300000e+00] (1019.53760293993,-2.956) [1.400000e+00] (1018.0906119683,-3.226) [1.500000e+00] (1016.85176547873,-3.472) [1.700000e+00] (1015.44609304413,-3.729) [1.700000e+00] (1013.98549327128,-3.968) [1.900000e+00] (1012.72564643332,-4.216) [2] (1011.50040877402,-4.458) [2.100000e+00] (1010.18271655804,-4.693) [2.200000e+00] (1008.81690184902,-4.906) [2.400000e+00] (1007.49541834364,-5.12) [2.600000e+00] (1006.07924486067,-5.318) [2.700000e+00] (1004.80656649648,-5.51) [2.900000e+00] (1003.43919637738,-5.701) [3.300000e+00] (1001.96439935303,-5.881) [3.800000e+00] (1000.42952018238,-6.067) [4.100000e+00] (999.025399661174,-6.246) [4.500000e+00] (997.639265044581,-6.463) [5.100000e+00] (996.359876921423,-6.666) [5.600000e+00] (995.352506686828,-6.863) [6.400000e+00] (994.088185969619,-7.043) [6.900000e+00] (992.909420795723,-7.216) [7.500000e+00] (991.676506447192,-7.366) [7.800000e+00] (990.383509522842,-7.546) [8.300000e+00] (989.014679080286,-7.697) [8.600000e+00] (987.664612705648,-7.809) [8.900000e+00] (986.142468285034,-7.963) [9] (984.908188211044,-8.161) [9.200000e+00] (983.809139806535,-8.371) [9.300000e+00] (982.538014273264,-8.517) [9.200000e+00] (981.584017314541,-8.678) [9.100000e+00] (980.236963636116,-8.833) [9] (978.820009840593,-8.966) [8.900000e+00] (977.579702196686,-9.142) [8.700000e+00] (976.333366983251,-9.291) [8.400000e+00] (974.995354029198,-9.436) [8.100000e+00] (973.748335279327,-9.584) [8] (972.383977025846,-9.742) [7.700000e+00] (970.971589587974,-9.878) [7.400000e+00] (969.771046389772,-9.985) [7] (968.438965977565,-10.063) [7] (967.252713368873,-10.184) [6.700000e+00] (965.947755072429,-10.319) [6.500000e+00] (964.704432125032,-10.502) [6.200000e+00] (963.615200860472,-10.611) [5.900000e+00] (962.416210435395,-10.753) [5.700000e+00] (961.219550058383,-10.836) [5.400000e+00] (960.044667305046,-10.976) [5.300000e+00] (958.835175372754,-11.115) [5.100000e+00] (957.424246998191,-11.266) [4.900000e+00] (956.046466991233,-11.354) [4.700000e+00] (954.647592008332,-11.481) [4.500000e+00] (953.57187362845,-11.668) [4.300000e+00] (952.314259690758,-11.837) [4.300000e+00] (950.79357218468,-11.974) [4.100000e+00] (949.145137406695,-12.058) [3.900000e+00] (947.571076682795,-12.207) [3.700000e+00] (946.170647637567,-12.346) [3.400000e+00] (944.661235818084,-12.487) [3.400000e+00] (943.210447999136,-12.585) [3.300000e+00] (941.662730797541,-12.775) [3.200000e+00] (940.293027279379,-12.973) [3.200000e+00] (939.004594592698,-13.165) [3.100000e+00] (937.636536209829,-13.33) [3.100000e+00] (936.11507059816,-13.467) [3] (934.62150079421,-13.592) [3] (933.23759910671,-13.692) [2.900000e+00] (931.893555574444,-13.848) [2.800000e+00] (930.551748781447,-13.986) [2.700000e+00] (929.248247399485,-14.097) [2.600000e+00] (927.747098170069,-14.231) [2.600000e+00] (926.301559385583,-14.371) [2.500000e+00] (924.867388650044,-14.492) [2.400000e+00] (923.572242650441,-14.625) [2.300000e+00] (922.27097892514,-14.741) [2.200000e+00] (920.924697335324,-14.918) [2.200000e+00] (919.688082514908,-15.092) [2.100000e+00] (918.430465539635,-15.243) [2] (917.186364114915,-15.374) [2.100000e+00] (915.82200202236,-15.502) [2.100000e+00] (914.424583065523,-15.625) [2.100000e+00] (913.015111634495,-15.772) [2] (911.719873731302,-15.879) [1.900000e+00] (910.212788033911,-15.976) [1.900000e+00] (908.793591023742,-16.075) [1.900000e+00] (907.31577047193,-16.206) [1.800000e+00] (906.010031061392,-16.345) [1.800000e+00] (904.674249259621,-16.479) [1.700000e+00] (903.277606718308,-16.586) [1.700000e+00] (902.046332405872,-16.711) [1.500000e+00] (900.691784759011,-16.787) [1.500000e+00] (899.168855327436,-16.949) [1.500000e+00] (897.633871185916,-17.075) [1.500000e+00] (896.286811060699,-17.175) [1.500000e+00] (894.941212205776,-17.279) [1.500000e+00] (893.451337431782,-17.408) [1.500000e+00] (892.046429692659,-17.514) [1.700000e+00] (890.675262842406,-17.627) [1.600000e+00] (889.465676485758,-17.746) [1.500000e+00] (888.108799766306,-17.857) [1.500000e+00] (886.656545061023,-17.962) [1.500000e+00] (885.383859907284,-17.912) [1.500000e+00] (884.01889959068,-17.724) [1.600000e+00] (882.901082477351,-17.523) [1.600000e+00] (881.802806248483,-17.323) [1.600000e+00] (880.498616544693,-17.138) [1.700000e+00] (879.026820095559,-16.931) [1.600000e+00] (877.809744039519,-16.644) [1.700000e+00] (876.429627107761,-16.397) [1.700000e+00] (875.025493577463,-16.178) [1.800000e+00] (873.410104774697,-16) [1.700000e+00] (871.791017962395,-15.804) [1.800000e+00] (870.537186602619,-15.615) [1.800000e+00] (868.694701458534,-15.415) [1.700000e+00] (867.08757745238,-15.223) [1.800000e+00] (865.614227399732,-15.017) [1.900000e+00] (864.385873937612,-14.841) [2] (862.610365940251,-14.677) [2] (861.020455064246,-14.538) [2] (859.453187436334,-14.406) [2] (857.99033937838,-14.318) [2] (856.571822954067,-14.22) [2] (854.978212291562,-14.087) [1.900000e+00] (853.520614127641,-13.95) [2] (852.117851340282,-13.827) [2.100000e+00] (850.861692255118,-13.705) [2.100000e+00] (849.461255932683,-13.577) [2.100000e+00] (848.147248345326,-13.504) [2.100000e+00] (846.819725236414,-13.433) [2] (845.412486304952,-13.343) [2] (844.093228422723,-13.258) [2] (843.008464706853,-13.176) [2] (841.739565598268,-13.075) [2.100000e+00] (840.369171696223,-12.955) [2.100000e+00] (838.998090674602,-12.825) [2.100000e+00] (837.579663116557,-12.692) [2.100000e+00] (836.165709954415,-12.531) [2.100000e+00] (834.610492651815,-12.388) [2.200000e+00] (833.273929335062,-12.189) [2.100000e+00] (831.820893974603,-12.039) [2.300000e+00] (830.445248000617,-11.842) [2.300000e+00] (829.067364399022,-11.769) [2.400000e+00] (827.567756652624,-11.585) [2.500000e+00] (826.543678783466,-11.478) [2.700000e+00] (825.166569332433,-11.338) [2.800000e+00] (824.108060359763,-11.327) [3] (822.891246831437,-11.222) [3.100000e+00] (821.550981951035,-11.135) [3.200000e+00] (820.181273908338,-10.933) [3.300000e+00] (818.591447513916,-10.779) [3.300000e+00] (816.733293301337,-10.624) [3.500000e+00] (815.407406012638,-10.487) [3.600000e+00] (814.196441607155,-10.307) [3.800000e+00] (812.971186182143,-10.191) [4.200000e+00] (811.725702753407,-10.067) [4.500000e+00] (810.427532796457,-9.957) [4.900000e+00] (809.264602505868,-9.838) [5.200000e+00] (807.970133253125,-9.748) [5.600000e+00] (806.181878268759,-9.589) [5.900000e+00] (804.594287782957,-9.559) [6.300000e+00] (802.105555486717,-9.486) [6.700000e+00] (800.381863293485,-9.376) [7] (798.783770412051,-9.249) [7.300000e+00] (797.011179855664,-9.063) [7.800000e+00] (795.607037184189,-8.843) [7.700000e+00] (794.659749559802,-8.668) [7.700000e+00] (793.302178844221,-8.469) [7.500000e+00] (791.987392378577,-8.3) [7.300000e+00] (790.411766075439,-8.112) [7.200000e+00] (788.89407616534,-7.907) [6.900000e+00] (787.509387404899,-7.692) [6.600000e+00] (786.169032943847,-7.578) [6.300000e+00] (784.654355729727,-7.359) [6.100000e+00] (783.2185318382,-7.2) [5.900000e+00] (781.634727798284,-7.013) [5.600000e+00] (780.26510374907,-6.825) [5.400000e+00] (778.882739217905,-6.62) [5.200000e+00] (777.507088946264,-6.467) [5] (776.020216065958,-6.23) [4.900000e+00] (774.687436157821,-6.063) [4.600000e+00] (773.289231904957,-5.865) [4.500000e+00] (771.727205517642,-5.652) [4.200000e+00] (770.211063508091,-5.418) [4] (768.843677144825,-5.289) [3.600000e+00] (767.339499718543,-5.098) [3.400000e+00] (765.648947064977,-4.894) [3.300000e+00] (763.967431982819,-4.717) [3.100000e+00] (762.349793431481,-4.537) [3] (760.780966270365,-4.291) [2.800000e+00] (759.322585789947,-4.052) [2.700000e+00] (757.678604662749,-3.841) [2.500000e+00] (756.224011888574,-3.615) [2.500000e+00] (754.822708024827,-3.376) [2.400000e+00] (753.404959821386,-3.137) [2.400000e+00] (752.036797588258,-2.926) [2.300000e+00] (750.655119833938,-2.693) [2.300000e+00] (749.306499373713,-2.454) [2.300000e+00] (747.881175786812,-2.226) [2.200000e+00] (746.286089956341,-2.016) [2.100000e+00] (744.90819901951,-1.767) [2] (743.457393550743,-1.543) [1.900000e+00] (742.086218221031,-1.313) [1.900000e+00] (740.592541529239,-1.089) [1.900000e+00] (739.105665640431,-0.847) [1.900000e+00] (737.7164968392,-0.676) [1.700000e+00] (736.467131767602,-0.628) [1.700000e+00] (735.135123890202,-0.685) [1.600000e+00] (733.718148548226,-0.741) [1.600000e+00] (732.301173664802,-0.81) [1.700000e+00] (730.732427802551,-0.883) [1.600000e+00] (729.376400202102,-0.948) [1.600000e+00] (728.017359475809,-1.048) [1.700000e+00] (726.529017903125,-1.291) [1.700000e+00] (725.048855443399,-1.575) [1.700000e+00] (724.063259916447,-1.853) [1.600000e+00] (722.862015102309,-2.127) [1.600000e+00] (721.779400983767,-2.401) [1.700000e+00] (721.059813058517,-2.663) [1.700000e+00] (719.74355749989,-2.924) [1.700000e+00] (718.640712252961,-3.171) [1.700000e+00] (717.080312399596,-3.439) [1.800000e+00] (715.637162724711,-3.711) [1.900000e+00] (714.717848681874,-3.989) [2] (713.795522402028,-4.25) [2.200000e+00] (712.4732401908,-4.505) [2.300000e+00] (711.563571891685,-4.745) [2.400000e+00] (710.429215845819,-5.008) [2.700000e+00] (708.613226077895,-5.21) [2.800000e+00] (707.463805349647,-5.419) [2.900000e+00] (706.149788365231,-5.616) [3.200000e+00] (704.48264035703,-5.833) [3.600000e+00] (703.082964775302,-5.999) [4.100000e+00] (701.378971766709,-6.211) [4.700000e+00] (699.766577063555,-6.414) [5] (698.412010820508,-6.62) [5.100000e+00] (697.28135820226,-6.828) [5.300000e+00] (695.723027419745,-7.009) [5.500000e+00] (693.925028085888,-7.176) [5.500000e+00] (692.01046930519,-7.311) [5.500000e+00] (690.546833372907,-7.521) [5.500000e+00] (688.969042947106,-7.744) [5.300000e+00] (687.477600932657,-7.97) [5.200000e+00] (686.001222740964,-8.176) [5.100000e+00] (684.535347403717,-8.413) [5.100000e+00] (683.18448415858,-8.566) [5] (681.766730826862,-8.751) [4.800000e+00] (680.154334404616,-8.881) [4.900000e+00] (678.643350216711,-9.073) [4.800000e+00] (677.427647231597,-9.246) [4.700000e+00] (675.909172397437,-9.432) [4.500000e+00] (674.521463292103,-9.613) [4.400000e+00] (673.066173827466,-9.773) [4.200000e+00] (671.757405935361,-9.883) [4.100000e+00] (670.499079748215,-10.018) [3.900000e+00] (669.162587845816,-10.214) [3.800000e+00] (667.686982056748,-10.411) [3.700000e+00] (666.335425013387,-10.614) [3.700000e+00] (664.983012665348,-10.763) [3.700000e+00] (663.78245649205,-10.844) [3.500000e+00] (662.517331307941,-10.916) [3.400000e+00] (661.261162053384,-11.024) [3.300000e+00] (659.833676951407,-11.13) [3.100000e+00] (658.893880722283,-11.263) [3] (657.489723293332,-11.381) [3] (656.038218468331,-11.511) [2.800000e+00] (654.64077845257,-11.601) [2.700000e+00] (653.198310310169,-11.77) [2.600000e+00] (652.005325995222,-11.966) [2.600000e+00] (650.819832756161,-12.174) [2.500000e+00] (649.680913250323,-12.358) [2.400000e+00] (648.514961354301,-12.52) [2.400000e+00] (647.255779032033,-12.684) [2.300000e+00] (645.969645043784,-12.852) [2.200000e+00] (644.835285588577,-12.973) [2.200000e+00] (643.809057558051,-13.065) [2.100000e+00] (642.577681346561,-13.175) [2] (641.42532707258,-13.286) [2.100000e+00] (640.168464937323,-13.368) [2] (639.223335911926,-13.427) [2] (638.222755741307,-13.542) [2] (637.205727647829,-13.651) [2] (636.106746591512,-13.781) [2] (635.017575881011,-13.872) [1.900000e+00] (633.795317993951,-13.939) [1.800000e+00] (632.0468972664,-13.954) [1.800000e+00] (630.951008283034,-13.974) [1.800000e+00] (629.405737615541,-13.993) [1.800000e+00] (627.225769032791,-14.015) [1.800000e+00] (625.121887779129,-14.154) [1.700000e+00] (621.551514734018,-14.31) [1.800000e+00] (619.900719910773,-14.515) [1.800000e+00] (618.054506527998,-14.815) [1.900000e+00] (616.722406206452,-15.044) [1.900000e+00] (615.389453246023,-15.222) [1.900000e+00] (613.606504179905,-15.332) [1.900000e+00] (611.7717275025,-15.455) [1.800000e+00] (610.45383747623,-15.615) [1.700000e+00] (609.309504508075,-15.77) [1.700000e+00] (607.701578271135,-15.912) [1.700000e+00] (606.007140826818,-16.065) [1.600000e+00] (604.578876846683,-16.26) [1.600000e+00] (604.579944728651,-16.448) [1.600000e+00] (602.816058880144,-17.675) [1.500000e+00] (601.360921292768,-17.85) [1.400000e+00] (600.091391460551,-17.933) [1.500000e+00] (598.824794459762,-17.917) [1.500000e+00] (597.396609455813,-17.918) [1.400000e+00] (596.325431902945,-17.884) [1.400000e+00] (594.77543626897,-17.841) [1.400000e+00] (593.20219325654,-17.849) [1.400000e+00] (591.218648551032,-17.893) [1.400000e+00] (589.956529988152,-18.024) [1.400000e+00] (588.412638664266,-18.182) [1.400000e+00] (582.336623377122,-17.886) [1.400000e+00] (581.114974725035,-17.673) [1.500000e+00] (579.406245030146,-17.449) [1.500000e+00] (577.859181396896,-17.216) [1.500000e+00] (576.218036074547,-16.96) [1.500000e+00] (574.871644878632,-16.696) [1.600000e+00] (574.101622676206,-16.423) [1.500000e+00] (573.088755141335,-16.269) [1.600000e+00] (572.01765346925,-16.235) [1.500000e+00] (571.115710711763,-16.258) [1.500000e+00] (570.11366093119,-16.202) [1.500000e+00] (568.835089143089,-16.04) [1.500000e+00] (567.203989259495,-15.781) [1.500000e+00] (565.714856658791,-15.552) [1.500000e+00] (564.110633535895,-15.333) [1.600000e+00] (562.323118373242,-15.117) [1.700000e+00] (560.845956633901,-14.925) [1.700000e+00] (558.693089904352,-14.678) [1.700000e+00] (556.77395379491,-14.459) [1.700000e+00] (555.322281132898,-14.267) [1.800000e+00] (553.985698563551,-14.124) [1.800000e+00] (552.830168170264,-13.968) [1.800000e+00] (551.241779437419,-13.825) [1.900000e+00] (550.045775579096,-13.684) [2] (548.78365311927,-13.566) [2] (547.64094573849,-13.475) [2.100000e+00] (546.247281709027,-13.393) [2.200000e+00] (544.864894225709,-13.29) [2.200000e+00] (543.675610016303,-13.124) [2.200000e+00] (542.262402895629,-12.959) [2.100000e+00] (540.754421576806,-12.819) [2.100000e+00] (539.812463344637,-12.683) [2.200000e+00] (538.417254196222,-12.56) [2.200000e+00] (537.355726574113,-12.45) [2.300000e+00] (536.175479506121,-12.368) [2.300000e+00] (535.025355553696,-12.339) [2.400000e+00] (533.976650514154,-12.292) [2.300000e+00] (532.90840327187,-12.193) [2.400000e+00] (531.945358606919,-12.092) [2.400000e+00] (530.807284462883,-12.001) [2.400000e+00] (527.235027128636,-11.747) [2.900000e+00] (526.042883274045,-11.672) [3] (524.60040034535,-11.509) [3.300000e+00] (522.839914622353,-11.305) [3.400000e+00] (521.397431263821,-11.086) [3.700000e+00] (519.694103741061,-10.819) [3.800000e+00] (518.208827218271,-10.547) [3.900000e+00] (516.93241250787,-10.353) [4] (515.450071510865,-10.218) [4.300000e+00] (514.217993765289,-10.058) [4.700000e+00] (512.707073453311,-9.95) [5.100000e+00] (511.298496015165,-9.809) [5.400000e+00] (509.637339639398,-9.679) [5.900000e+00] (508.222356493428,-9.598) [6.400000e+00] (506.457387488947,-9.468) [6.500000e+00] (503.337214264038,-9.275) [6.900000e+00] (504.013696442417,-9.182) [7.100000e+00] (500.802379777837,-8.83) [7.400000e+00] (496.377132778696,-8.687) [7.400000e+00] (494.824658580862,-8.493) [7.700000e+00] (493.371515019616,-8.271) [8] (491.46364903889,-8.071) [8] (490.176029649865,-7.884) [7.900000e+00] (488.813799911123,-7.688) [7.700000e+00] (487.44716532124,-7.51) [7.400000e+00] (485.841467802819,-7.344) [7] (484.422154797968,-7.157) [6.800000e+00] (482.920192767225,-6.919) [6.600000e+00] (481.396448211589,-6.719) [6.400000e+00] (479.886992869078,-6.51) [6.200000e+00] (478.461654988851,-6.314) [5.800000e+00] (477.141597285648,-6.113) [5.400000e+00] (476.059754372661,-5.864) [5.100000e+00] (474.662298856012,-5.656) [4.800000e+00] (473.372288015914,-5.452) [4.500000e+00] (472.003336909058,-5.306) [4.300000e+00] (470.420267446521,-5.114) [4] (469.318957264921,-4.93) [3.800000e+00] (468.328178443739,-4.74) [3.700000e+00] (466.802192276234,-4.557) [3.400000e+00] (466.072110445456,-4.38) [3.300000e+00] (464.397353067545,-4.175) [3.200000e+00] (463.323849885504,-3.982) [3] (462.121816453522,-3.843) [2.900000e+00] (460.885179290108,-3.638) [2.800000e+00] (459.689169873697,-3.435) [2.700000e+00] (458.499109538703,-3.256) [2.600000e+00] (457.153558373643,-3.062) [2.400000e+00] (455.846319727767,-2.881) [2.200000e+00] (454.849515601345,-2.71) [2.200000e+00] (453.717386270204,-2.514) [2.100000e+00] (452.289108938242,-2.32) [2.100000e+00] (450.942784998619,-2.134) [2] (449.543858896415,-1.925) [1.900000e+00] (448.331392642486,-1.733) [1.800000e+00] (447.124876387937,-1.526) [1.700000e+00] (445.53037884952,-1.316) [1.500000e+00] (444.043474938491,-1.118) [1.600000e+00] (442.586692337034,-0.911) [1.500000e+00] (441.311814492722,-0.735) [1.600000e+00] (440.0640461795,-0.656) [1.400000e+00] (438.629046132091,-0.692) [1.400000e+00] (437.292602570498,-0.756) [1.300000e+00] (435.862927751959,-0.824) [1.300000e+00] (434.345202885215,-0.889) [1.300000e+00] (432.884562631887,-0.966) [1.300000e+00] (431.354788444461,-1.04) [1.200000e+00] (429.827255038153,-1.249) [1.100000e+00] (428.154660527987,-1.524) [1.100000e+00] (426.650452558797,-1.795) [1.200000e+00] (425.147016934149,-2.061) [1.100000e+00] (423.91794452047,-2.341) [1.100000e+00] (422.603906506131,-2.611) [1.200000e+00] (421.437942262887,-2.879) [1.200000e+00] (420.039710992459,-3.129) [1.300000e+00] (418.866951765254,-3.384) [1.400000e+00] (417.506262475924,-3.65) [1.400000e+00] (416.27417696535,-3.909) [1.500000e+00] (414.786499019738,-4.183) [1.600000e+00] (413.449907053332,-4.418) [1.700000e+00] (411.87208275713,-4.638) [1.900000e+00] (410.711371532222,-4.879) [2.300000e+00] (409.558925075052,-5.088) [2.600000e+00] (408.143464651823,-5.339) [3.100000e+00] (406.213105668329,-5.576) [3.500000e+00] (404.934368453107,-5.82) [4] (403.509798706878,-6.026) [4.500000e+00] (402.231832488814,-6.248) [4.700000e+00] (400.939648408512,-6.508) [5.200000e+00] (399.8000218685,-6.782) [5.600000e+00] (398.428897091865,-7.009) [6.100000e+00] (397.144207670668,-7.19) [6.400000e+00] (395.809926976744,-7.373) [6.500000e+00] (394.264390812682,-7.487) [6.500000e+00] (392.887242049321,-7.659) [6.400000e+00] (391.595057539338,-7.824) [6.400000e+00] (389.945084922732,-7.994) [6.200000e+00] (388.619768242425,-8.137) [6] (387.257607478938,-8.319) [5.800000e+00] (386.070628670456,-8.481) [5.600000e+00] (384.63709276194,-8.642) [5.500000e+00] (383.298256547178,-8.788) [5.400000e+00] (381.759442296891,-8.932) [5.200000e+00] (380.392028114153,-9.128) [5.100000e+00] (378.620245872335,-9.316) [5] (377.146853672631,-9.45) [4.800000e+00] (375.758425755201,-9.586) [4.600000e+00] (374.431636654369,-9.812) [4.500000e+00] (373.026749634537,-9.992) [4.200000e+00] (371.633767944389,-10.181) [4] (370.147556344525,-10.372) [3.900000e+00] (368.772645754694,-10.537) [3.800000e+00] (367.419520384683,-10.72) [3.800000e+00] (365.718340112779,-10.891) [3.700000e+00] (364.53731402696,-11.024) [3.500000e+00] (363.142860804626,-11.194) [3.400000e+00] (361.837854716421,-11.343) [3.200000e+00] (360.308845968063,-11.465) [3.100000e+00] (358.891067337667,-11.541) [3.100000e+00] (357.468805826649,-11.64) [3] (356.081846833763,-11.805) [3.100000e+00] (354.687393640509,-12.03) [3.100000e+00] (353.56436406112,-12.177) [2.900000e+00] (352.092439955415,-12.367) [2.800000e+00] (350.815941430591,-12.459) [2.700000e+00] (349.210231907574,-12.532) [2.600000e+00] (347.835320487121,-12.681) [2.500000e+00] (346.313734675275,-12.842) [2.400000e+00] (344.722313476962,-12.962) [2.400000e+00] (343.578129296234,-13.139) [2.400000e+00] (342.343797417454,-13.309) [2.400000e+00] (341.160528831294,-13.438) [2.300000e+00] (339.802917084292,-13.576) [2.200000e+00] (338.470872415071,-13.772) [2.100000e+00] (337.123067430278,-13.946) [2] (335.963122504192,-14.113) [1.900000e+00] (334.516833731827,-14.28) [2] (333.135967010073,-14.407) [1.900000e+00] (331.800138705769,-14.518) [1.900000e+00] (330.585278625369,-14.621) [1.900000e+00] (328.944333951,-14.743) [1.900000e+00] (327.462672256065,-14.817) [2] (325.863053656869,-14.956) [1.900000e+00] (324.267147858687,-15.048) [1.800000e+00] (322.789267162244,-15.187) [1.800000e+00] (321.547368901744,-15.314) [1.900000e+00] (320.434774066272,-15.475) [1.900000e+00] (318.941063968179,-15.593) [1.900000e+00] (317.374505816666,-15.746) [1.800000e+00] (315.678644240174,-15.888) [1.800000e+00] (314.236836199551,-16.018) [1.700000e+00] (313.025055694277,-16.127) [1.700000e+00] (311.47194713154,-16.285) [1.600000e+00] (309.951197964876,-16.378) [1.600000e+00] (308.346255112257,-16.52) [1.600000e+00] (307.066041265706,-16.728) [1.600000e+00] (305.757950015311,-16.904) [1.500000e+00] (304.228166000962,-17.04) [1.400000e+00] (302.837420393518,-17.21) [1.500000e+00] (301.38888694296,-17.305) [1.500000e+00] (300.125972740781,-17.421) [1.400000e+00] (298.885545669475,-17.498) [1.400000e+00] (297.497812299326,-17.64) [1.400000e+00] (296.186777955744,-17.75) [1.400000e+00] (295.077193179508,-17.95) [1.400000e+00] (293.818061323182,-18.021) [1.300000e+00] (292.831688676552,-18.15) [1.400000e+00] (291.631116119339,-18.135) [1.500000e+00] (290.767321429905,-18.024) [1.600000e+00] (289.851691562145,-17.851) [1.500000e+00] (288.879675867614,-17.737) [1.500000e+00] (287.788162191773,-17.6) [1.500000e+00] (286.795130956376,-17.523) [1.500000e+00] (285.551827183263,-17.406) [1.500000e+00] (284.290452797649,-17.276) [1.500000e+00] (282.823845639159,-17.113) [1.600000e+00] (281.499290901627,-16.954) [1.500000e+00] (280.021405878581,-16.781) [1.500000e+00] (278.72767166716,-16.576) [1.500000e+00] (277.142268008781,-16.423) [1.500000e+00] (275.607996729204,-16.27) [1.500000e+00] (274.272934235597,-16.157) [1.500000e+00] (272.625255381976,-15.987) [1.500000e+00] (271.167749090406,-15.859) [1.600000e+00] (269.557615771968,-15.682) [1.600000e+00] (268.169177453186,-15.495) [1.500000e+00] (267.007054756922,-15.455) [1.500000e+00] (266.115383180306,-15.444) [1.500000e+00] (265.284515238342,-15.483) [1.400000e+00] (264.289942954844,-15.486) [1.400000e+00] (263.362968860198,-15.512) [1.500000e+00] (262.368396576777,-15.477) [1.500000e+00] (261.624099037979,-15.475) [1.600000e+00] (260.974571138378,-15.504) [1.600000e+00] (260.234825136624,-15.507) [1.700000e+00] (259.516929398633,-15.546) [1.700000e+00] (258.667489942075,-15.551) [1.700000e+00] (257.718797047891,-15.541) [1.700000e+00] (256.513805422619,-15.453) [1.700000e+00] (255.238842044868,-15.289) [1.700000e+00] (253.892500397529,-15.069) [1.700000e+00] (252.540905301887,-14.791) [1.800000e+00] (251.135934381069,-14.547) [1.800000e+00] (249.629469270326,-14.262) [1.700000e+00] (248.307154512368,-14.009) [1.800000e+00] (247.062306625014,-13.859) [1.800000e+00] (245.870064483537,-13.79) [1.800000e+00] (244.640275918067,-13.678) [1.900000e+00] (243.466872720712,-13.62) [1.800000e+00] (242.302504399783,-13.493) [1.800000e+00] (241.107250050036,-13.362) [1.900000e+00] (240.115622294194,-13.256) [1.900000e+00] (239.07145656035,-13.162) [1.900000e+00] (237.810011427514,-13.081) [2] (236.76731771346,-12.946) [2] (235.572062933929,-12.859) [2] (234.058166030276,-12.752) [2.100000e+00] (232.803513215808,-12.602) [2.200000e+00] (231.524832652155,-12.382) [2.400000e+00] (230.312276909916,-12.242) [2.500000e+00] (228.961382465307,-12.025) [2.500000e+00] (227.440625992459,-11.781) [2.600000e+00] (225.910834642978,-11.517) [2.600000e+00] (224.328437147144,-11.306) [2.700000e+00] (222.966265726449,-11.074) [2.900000e+00] (221.624405728609,-10.955) [2.900000e+00] (220.277291393918,-10.845) [3] (219.176034396724,-10.817) [3.200000e+00] (217.876271471216,-10.759) [3.300000e+00] (216.625397907096,-10.632) [3.400000e+00] (215.474481010066,-10.524) [3.600000e+00] (214.282940866645,-10.368) [3.900000e+00] (212.944860519937,-10.21) [4.100000e+00] (211.566222000067,-10.085) [4.500000e+00] (210.420559010051,-9.937) [4.800000e+00] (209.215497984919,-9.768) [5.200000e+00] (208.040487836099,-9.618) [5.900000e+00] (206.379213886203,-9.469) [6.300000e+00] (205.008775090025,-9.312) [6.700000e+00] (203.713495991791,-9.097) [7] (202.159674285664,-8.827) [7.200000e+00] (201.018496441257,-8.636) [7.300000e+00] (199.746540973915,-8.446) [7.500000e+00] (198.303952481099,-8.305) [7.900000e+00] (196.941075223403,-8.194) [7.800000e+00] (195.637530038682,-8.056) [7.700000e+00] (194.636163375407,-7.879) [7.600000e+00] (193.422195413169,-7.748) [7.300000e+00] (192.200538519048,-7.601) [7] (190.756347918267,-7.416) [6.700000e+00] (189.429479590574,-7.281) [6.500000e+00] (188.240244012092,-7.165) [6.200000e+00] (187.114956199569,-7.004) [6] (185.752076734914,-6.85) [5.700000e+00] (184.34408844842,-6.649) [5.400000e+00] (182.866899406683,-6.41) [5] (181.335629962636,-6.237) [4.800000e+00] (179.841203225041,-6.022) [4.400000e+00] (178.464803796198,-5.851) [4.200000e+00] (177.109421255634,-5.659) [4] (175.454870195167,-5.414) [3.800000e+00] (173.674795848668,-5.182) [3.600000e+00] (171.965332357637,-4.993) [3.400000e+00] (170.288226915292,-4.724) [3.200000e+00] (168.632138361122,-4.528) [3] (166.890380117385,-4.347) [2.900000e+00] (165.223781571413,-4.123) [2.700000e+00] (163.664702090405,-3.934) [2.600000e+00] (162.044750347582,-3.72) [2.400000e+00] (160.566853662593,-3.461) [2.200000e+00] (159.021292856571,-3.226) [2.100000e+00] (157.400571463901,-2.964) [2] (155.943754504227,-2.722) [2] (154.368910264961,-2.511) [2] (152.584284927235,-2.268) [2] (150.923708189979,-2.007) [1.900000e+00] (149.460804894204,-1.76) [1.700000e+00] (147.84309307329,-1.507) [1.700000e+00] (146.244924802141,-1.238) [1.500000e+00] (144.900815770371,-1.004) [1.600000e+00] (143.470269634734,-0.819) [1.600000e+00] (141.974301936405,-0.758) [1.500000e+00] (140.533951733203,-0.813) [1.500000e+00] (139.065024938698,-0.907) [1.400000e+00] (137.659980837027,-0.95) [1.400000e+00] (136.259484689078,-1.016) [1.400000e+00] (134.810100097212,-1.159) [1.300000e+00] (133.352449848955,-1.397) [1.300000e+00] (132.065432597066,-1.666) [1.200000e+00] (130.707802712561,-1.954) [1.200000e+00] (129.47492781155,-2.229) [1.100000e+00] (128.01958207023,-2.481) [1.200000e+00] (126.909988785689,-2.77) [1.200000e+00] (125.711714491731,-3.053) [1.200000e+00] (124.473584824369,-3.305) [1.300000e+00] (123.188103776746,-3.56) [1.400000e+00] (121.783120764148,-3.843) [1.500000e+00] (120.439010013312,-4.074) [1.600000e+00] (119.167817290445,-4.314) [1.800000e+00] (118.014589468897,-4.555) [2] (116.73359445556,-4.806) [2.200000e+00] (115.336876669515,-5.006) [2.500000e+00] (114.089006230463,-5.247) [2.900000e+00] (112.845621366624,-5.501) [3.200000e+00] (111.442112638754,-5.695) [3.700000e+00] (110.116776246778,-5.903) [4.300000e+00] (108.766641997032,-6.131) [4.700000e+00] (107.363900253314,-6.301) [5] (105.871709197718,-6.442) [5.300000e+00] (104.399829536001,-6.645) [5.900000e+00] (103.164710357685,-6.891) [6.200000e+00] (101.764211631149,-7.088) [6.500000e+00] (100.452455403654,-7.248) [6.900000e+00] (99.1256434665944,-7.419) [6.800000e+00] (97.8138262082112,-7.572) [6.900000e+00] (96.4456837531614,-7.747) [6.800000e+00] (95.0910621799263,-7.904) [6.700000e+00] (93.8258894888612,-8.108) [6.600000e+00] (92.4712674857886,-8.265) [6.500000e+00] (91.1993042826323,-8.413) [6.300000e+00] (89.8108500040459,-8.586) [6.200000e+00] (88.4675045472981,-8.778) [6] (87.2233505504801,-8.882) [5.900000e+00] (85.9964957392214,-9.078) [5.600000e+00] (84.5538977914222,-9.213) [5.500000e+00] (82.9722548164121,-9.334) [5.300000e+00] (81.6845268547643,-9.468) [5.200000e+00] (80.2584611374513,-9.613) [5] (78.8421963632209,-9.803) [4.900000e+00] (77.4747594605468,-9.955) [4.700000e+00] (76.0201768357193,-10.138) [4.600000e+00] (74.4649253703916,-10.29) [4.400000e+00] (73.0658395257547,-10.487) [4.300000e+00] (72.0216639070358,-10.694) [4.200000e+00] (70.9030332254584,-10.903) [4.100000e+00] (69.6167808958216,-11.103) [4] (68.3109841567949,-11.223) [3.900000e+00] (66.8631301533118,-11.33) [3.800000e+00] (65.4543627619866,-11.421) [3.700000e+00] (64.0959585290907,-11.544) [3.500000e+00] (62.7428099801227,-11.67) [3.400000e+00] (61.499422137068,-11.78) [3.300000e+00] (60.0959086527029,-11.931) [3.100000e+00] (58.7314822392054,-12.087) [3] (57.4038976438461,-12.225) [3] (56.0259503486373,-12.377) [2.900000e+00] (54.5811059167043,-12.505) [2.800000e+00] (53.3647589774474,-12.611) [2.700000e+00] (51.9417028894792,-12.698) [2.600000e+00] (50.5945747730972,-12.829) [2.600000e+00] (49.2136152988279,-12.976) [2.500000e+00] (47.7905574337383,-13.137) [2.400000e+00] (46.4434302349562,-13.28) [2.200000e+00] (45.2263154517417,-13.464) [2.100000e+00] (43.9813901439844,-13.587) [2] (42.7237127157393,-13.721) [2] (41.2721370546646,-13.854) [2] (39.9024541265132,-13.976) [1.900000e+00] (38.4576088640612,-14.069) [1.800000e+00] (37.0571054390084,-14.173) [1.800000e+00] (35.595727516336,-14.264) [1.800000e+00] (34.1794588741853,-14.401) [1.700000e+00] (32.8030437995526,-14.528) [1.800000e+00] (31.4867349197922,-14.672) [1.700000e+00] (30.2493666784941,-14.846) [1.800000e+00] (28.8631506897011,-14.954) [1.700000e+00] (27.5378083096434,-15.088) [1.600000e+00] (26.0328551041201,-15.203) [1.700000e+00] (24.6022977364807,-15.333) [1.600000e+00] (23.2303696133712,-15.447) [1.600000e+00] (21.8215983541257,-15.571) [1.500000e+00] (20.4962555443606,-15.687) [1.600000e+00] (19.0717190389646,-15.846) [1.500000e+00] (17.706521773341,-15.959) [1.500000e+00] (16.3338258065844,-16.087) [1.400000e+00] (14.8694353038863,-16.235) [1.500000e+00] (13.476428402087,-16.436) [1.400000e+00] (11.8399253450121,-16.599) [1.300000e+00] (10.4807502888891,-16.697) [1.300000e+00] (9.08927689692154,-16.787) [1.200000e+00] (7.78347631897693,-16.917) [1.200000e+00] (5.9876150635571,-17.024) [1.200000e+00] (4.93215682376435,-17.209) [1.200000e+00] (3.75188262730727,-17.434) [1.200000e+00] };
+\addplot[scatter,only marks,mark size=1pt,scatter src=explicit,scatter/use mapped color={mark=*,draw=mapped color,fill=mapped color}] plot coordinates{ (0,-0.831) [9.000000e-01] (0.396123095452957,-0.832) [9.000000e-01] (16.8850657170843,-2.228) [9.000000e-01] (19.386309378027,-2.485) [1] (20.7170231970803,-2.774) [1] (21.6989675078734,-3.031) [1.200000e+00] (22.8071472777201,-3.289) [1.400000e+00] (24.5610830029506,-3.559) [1.500000e+00] (25.9984308826544,-3.773) [1.700000e+00] (27.8988551242371,-4.005) [1.800000e+00] (29.1617886372451,-4.262) [2.200000e+00] (62.5565899293934,-9.656) [4.900000e+00] (62.5565899293934,-9.727) [4.800000e+00] (70.9331967712539,-9.716) [4.700000e+00] (70.5118107778974,-9.674) [4.600000e+00] (71.7410292630623,-9.816) [4.500000e+00] (72.8642052039513,-9.938) [4.400000e+00] (75.0082362859188,-9.97) [4.300000e+00] (76.7726194267189,-10.033) [4.200000e+00] (78.6602249298857,-10.233) [4.100000e+00] (80.0953847487801,-10.526) [4] (81.4237947228505,-10.853) [3.800000e+00] (82.4094012394071,-11.137) [3.800000e+00] (90.4064215094236,-12.599) [3.200000e+00] (91.7791118891167,-12.761) [3.200000e+00] (93.2690607870255,-12.927) [3.300000e+00] (94.9258643776602,-13.131) [3.200000e+00] (96.4233119768856,-13.315) [3.100000e+00] (97.7794091531292,-13.539) [3] (99.2566050421831,-13.721) [2.900000e+00] (100.834528136853,-13.918) [2.800000e+00] (102.038059375172,-14.076) [2.700000e+00] (103.564851467609,-14.21) [2.700000e+00] (105.10292010624,-14.316) [2.500000e+00] (106.352328039151,-14.45) [2.500000e+00] (107.570853984965,-14.606) [2.400000e+00] (109.162235182079,-14.748) [2.400000e+00] (110.512369431851,-14.892) [2.300000e+00] (111.678350262332,-15.037) [2.300000e+00] (113.235254720706,-15.144) [2.200000e+00] (114.500486265143,-15.249) [2.200000e+00] (115.691203492305,-15.382) [2.100000e+00] (115.815129572001,-15.528) [2.100000e+00] (117.676456857818,-15.642) [2] (119.477680213669,-15.649) [2] (121.68110463208,-15.667) [1.900000e+00] (123.336430499725,-15.756) [1.900000e+00] (124.837654253971,-15.889) [1.900000e+00] (125.874974432477,-16.079) [1.900000e+00] (127.464940685869,-16.178) [1.800000e+00] (129.19548862963,-16.275) [1.800000e+00] (130.857541771519,-16.416) [1.800000e+00] (132.21363502171,-16.627) [1.800000e+00] (133.550247559459,-16.799) [1.900000e+00] (134.959009363721,-16.962) [2] (136.520336217567,-17.12) [1.800000e+00] (137.872711335487,-17.243) [1.800000e+00] (139.076945489566,-17.415) [1.700000e+00] (140.399268842806,-17.544) [1.800000e+00] (141.977956830779,-17.703) [1.800000e+00] (143.325077182371,-17.802) [1.700000e+00] (144.660151796424,-17.868) [1.800000e+00] (146.571133738,-17.888) [1.800000e+00] (148.269322831534,-17.76) [1.800000e+00] (149.626182665483,-17.551) [1.800000e+00] (151.662688380933,-17.391) [1.800000e+00] (152.718137136586,-17.26) [1.900000e+00] (153.837406694506,-17.099) [1.800000e+00] (155.125065343297,-16.946) [1.800000e+00] (157.211165026066,-16.724) [1.700000e+00] (158.777742720471,-16.503) [1.700000e+00] (160.189513695575,-16.363) [1.900000e+00] (161.502800912108,-16.229) [1.900000e+00] (162.89502879595,-16.13) [1.800000e+00] (164.148212512045,-15.928) [1.800000e+00] (165.084159331749,-15.722) [1.900000e+00] (166.140376448098,-15.548) [1.900000e+00] (168.073974836101,-15.419) [1.900000e+00] (171.903368566451,-15.398) [1.700000e+00] (173.569902526982,-17.024) [1.300000e+00] (175.53259191065,-16.566) [1.400000e+00] (177.935861325938,-16.19) [1.500000e+00] (179.811407222947,-15.874) [1.600000e+00] (181.880781436237,-15.569) [1.600000e+00] (183.237574077208,-15.215) [1.700000e+00] (184.995797300345,-14.884) [1.800000e+00] (186.783495133997,-14.578) [1.900000e+00] (187.952482126714,-14.274) [2.100000e+00] (189.258334913618,-13.899) [2.200000e+00] (190.738599459577,-13.554) [2.200000e+00] (192.463118747332,-13.211) [2.200000e+00] (194.003421319868,-12.947) [2.300000e+00] (195.57383981248,-12.748) [2.300000e+00] (196.983300606632,-12.597) [2.300000e+00] (198.481506135811,-12.432) [2.300000e+00] (200.168477251637,-12.264) [2.300000e+00] (201.114162264182,-12.13) [2.400000e+00] (202.394383846677,-12.051) [2.400000e+00] (203.75431396949,-11.953) [2.400000e+00] (205.330754700682,-11.83) [2.400000e+00] (206.892138374923,-11.74) [2.500000e+00] (207.741581757429,-11.685) [2.500000e+00] (209.102985706053,-11.61) [2.600000e+00] (211.135704464084,-11.467) [2.700000e+00] (212.557210594941,-11.291) [2.700000e+00] (214.108788883075,-11.101) [2.800000e+00] (215.157375520155,-11.056) [2.900000e+00] (216.15643461017,-10.923) [3.100000e+00] (217.950858027716,-10.784) [3.300000e+00] (219.060511686867,-10.537) [3.300000e+00] (220.557241700015,-10.4) [3.500000e+00] (221.391560315826,-10.222) [3.800000e+00] (222.696512075325,-10.14) [4.100000e+00] (224.639715159097,-9.899) [4.500000e+00] (226.372497123793,-9.749) [4.800000e+00] (227.744407109268,-9.586) [5.500000e+00] (228.880265172045,-9.464) [5.900000e+00] (230.235578800823,-9.304) [6.500000e+00] (231.748069617228,-9.108) [6.800000e+00] (233.558252978639,-8.875) [7] (235.063246470297,-8.73) [7.100000e+00] (236.020206310127,-8.554) [7.100000e+00] (237.432741377094,-8.429) [7.200000e+00] (238.858024551416,-8.262) [7.100000e+00] (240.511864989205,-8.107) [6.800000e+00] (242.258165228102,-7.934) [6.600000e+00] (243.650385776785,-7.836) [6.400000e+00] (245.109501714279,-7.66) [6.200000e+00] (246.41003125226,-7.468) [6] (247.91047415366,-7.229) [5.800000e+00] (249.408674496533,-7.087) [5.500000e+00] (250.905335539608,-6.901) [5.300000e+00] (252.429101641981,-6.732) [5.100000e+00] (254.261837265445,-6.508) [4.900000e+00] (256.077338317457,-6.347) [4.700000e+00] (257.562018696169,-6.134) [4.500000e+00] (258.874594918112,-6.023) [4.300000e+00] (260.562968311294,-5.811) [4.100000e+00] (262.146131130528,-5.613) [3.900000e+00] (263.724810180359,-5.365) [3.800000e+00] (265.261324877772,-5.226) [3.500000e+00] (266.695641668371,-4.999) [3.400000e+00] (268.071397382789,-4.805) [3.200000e+00] (269.50725304322,-4.552) [3] (270.879226899651,-4.345) [2.800000e+00] (272.529283359421,-4.089) [2.700000e+00] (274.421414868838,-3.899) [2.500000e+00] (276.528515938972,-3.657) [2.400000e+00] (278.224450469698,-3.467) [2.300000e+00] (279.852654000009,-3.213) [2.200000e+00] (281.380900404519,-2.967) [2.100000e+00] (282.910687914953,-2.692) [2.100000e+00] (284.340519646842,-2.457) [2] (285.643290082154,-2.181) [1.900000e+00] (286.883581618075,-1.945) [1.800000e+00] (288.129196146879,-1.684) [1.800000e+00] (289.668018103901,-1.46) [1.700000e+00] (291.718798937234,-1.22) [1.700000e+00] (293.480855222687,-0.988) [1.600000e+00] (295.087271814318,-0.83) [1.600000e+00] (296.946972721786,-0.798) [1.500000e+00] (298.652642321077,-0.83) [1.500000e+00] (300.10874040534,-0.909) [1.400000e+00] (301.305531104619,-0.978) [1.400000e+00] (302.585043928458,-1.136) [1.400000e+00] (303.913378375254,-1.404) [1.500000e+00] (305.470971595757,-1.672) [1.500000e+00] (306.92854127026,-1.939) [1.500000e+00] (308.210996786529,-2.209) [1.500000e+00] (309.714513617752,-2.477) [1.500000e+00] (310.96089607739,-2.74) [1.500000e+00] (312.301209440349,-3.024) [1.500000e+00] (313.842201832416,-3.269) [1.600000e+00] (314.94653232983,-3.551) [1.800000e+00] (316.189901233967,-3.763) [1.900000e+00] (317.843665738257,-4.031) [2] (319.262080173156,-4.255) [2.100000e+00] (320.718176108592,-4.52) [2.200000e+00] (321.911954198816,-4.732) [2.500000e+00] (323.378556571735,-5.026) [2.800000e+00] (324.913593203712,-5.256) [3.100000e+00] (326.006645836546,-5.507) [3.500000e+00] (327.553729582038,-5.694) [4] (328.869245116202,-5.916) [4.500000e+00] (330.669681375372,-6.094) [4.900000e+00] (331.861986586285,-6.351) [5.200000e+00] (333.832351781839,-6.545) [5.700000e+00] (335.219313382338,-6.757) [6.100000e+00] (336.676178566863,-6.917) [6.500000e+00] (337.793956904831,-7.134) [6.800000e+00] (339.0560970724,-7.311) [7] (340.45279368349,-7.528) [7.100000e+00] (341.845707518994,-7.672) [7.100000e+00] (343.47089012962,-7.851) [7.200000e+00] (345.114845293166,-7.963) [7.200000e+00] (346.776171422735,-8.152) [7.100000e+00] (348.35036028571,-8.301) [7.100000e+00] (349.459871648953,-8.528) [7.100000e+00] (350.616033398694,-8.703) [7] (351.497758437856,-8.86) [6.900000e+00] (353.034334026721,-8.989) [6.700000e+00] (354.586669071716,-9.074) [6.600000e+00] (356.179630516457,-9.155) [6.400000e+00] (357.438757186451,-9.271) [6.200000e+00] (358.529425133756,-9.39) [6.100000e+00] (359.478813004749,-9.532) [5.800000e+00] (361.113870203384,-9.675) [5.700000e+00] (362.460972905081,-9.782) [5.500000e+00] (363.784751087263,-9.879) [5.300000e+00] (365.233348925488,-9.969) [5.200000e+00] (366.592499170642,-10.101) [5] (368.268111476218,-10.237) [4.900000e+00] (369.818974559425,-10.419) [4.700000e+00] (371.642733276156,-10.685) [4.600000e+00] (372.877833114694,-11.001) [4.400000e+00] (373.847532867175,-11.19) [4.300000e+00] (375.693074138188,-11.412) [4.100000e+00] (377.630304671522,-11.463) [4] (379.09697275044,-11.528) [3.800000e+00] (380.372556803692,-11.64) [3.700000e+00] (381.856454982116,-11.776) [3.500000e+00] (383.005119923821,-11.919) [3.300000e+00] (384.857455777906,-12.088) [3.200000e+00] (386.078266002381,-12.239) [3.200000e+00] (387.260475696,-12.362) [3.200000e+00] (389.108956134072,-12.409) [3.100000e+00] (390.953653796453,-12.432) [2.900000e+00] (392.525527147113,-12.5) [2.800000e+00] (393.960604190631,-12.689) [2.800000e+00] (395.779878336545,-12.859) [2.800000e+00] (397.904264438766,-13.094) [2.700000e+00] (399.214520508063,-13.314) [2.600000e+00] (400.393232341897,-13.571) [2.500000e+00] (401.647874011237,-13.774) [2.500000e+00] (402.939357986557,-13.984) [2.400000e+00] (404.591714086049,-14.176) [2.400000e+00] (406.2718054043,-14.32) [2.400000e+00] (407.533939067413,-14.519) [2.400000e+00] (408.688554066189,-14.637) [2.400000e+00] (410.549851784699,-14.788) [2.300000e+00] (412.090132781494,-14.83) [2.200000e+00] (413.592872714638,-15.015) [2.200000e+00] (414.827198547541,-15.209) [2.200000e+00] (416.789364884208,-15.394) [2.200000e+00] (418.043378717052,-15.55) [2.100000e+00] (419.387464912905,-15.93) [2] (420.472873767022,-16.192) [2] (421.724427922257,-16.478) [2] (423.503552062762,-16.562) [1.900000e+00] (424.828169183932,-16.685) [1.900000e+00] (426.354087009002,-16.739) [1.900000e+00] (427.785377809461,-16.807) [1.700000e+00] (429.073076401396,-16.926) [1.700000e+00] (430.106652771831,-17.068) [1.600000e+00] (431.401219934598,-17.158) [1.600000e+00] (433.205431349417,-17.248) [1.600000e+00] (434.578866109566,-17.353) [1.500000e+00] (436.204110128149,-17.507) [1.500000e+00] (437.46701398703,-17.658) [1.400000e+00] (438.906569154545,-17.852) [1.400000e+00] (440.101808404137,-17.969) [1.500000e+00] (441.330806400502,-18.097) [1.500000e+00] (443.360487222009,-18.182) [1.400000e+00] (444.585774223355,-18.25) [1.400000e+00] (445.447251768488,-18.17) [1.400000e+00] (447.12362865369,-17.912) [1.300000e+00] (448.757908036852,-17.697) [1.400000e+00] (450.639589132766,-17.439) [1.400000e+00] (451.816205698007,-17.237) [1.300000e+00] (452.9941430965,-17.065) [1.400000e+00] (454.324782973168,-16.989) [1.400000e+00] (455.645539375936,-16.878) [1.400000e+00] (456.434723634116,-16.729) [1.500000e+00] (456.720912797513,-16.525) [1.400000e+00] (457.811644272833,-16.327) [1.600000e+00] (459.498525417922,-16.033) [1.600000e+00] (461.469577023641,-15.747) [1.600000e+00] (463.191832955192,-15.465) [1.600000e+00] (464.677192693975,-15.222) [1.600000e+00] (466.37086931058,-14.943) [1.600000e+00] (468.175076857479,-14.739) [1.600000e+00] (470.070274909105,-14.536) [1.500000e+00] (471.191898749391,-14.413) [1.600000e+00] (472.485619237177,-14.316) [1.800000e+00] (473.894352188464,-14.297) [1.800000e+00] (475.2843152821,-14.247) [1.800000e+00] (476.772760414979,-14.174) [1.900000e+00] (477.794282650237,-14.062) [1.900000e+00] (479.272147329054,-13.973) [2] (481.272548904457,-13.839) [2] (483.080465268393,-13.733) [2.100000e+00] (484.381601955964,-13.665) [2.200000e+00] (485.775969040986,-13.563) [2.300000e+00] (487.077181092446,-13.401) [2.300000e+00] (489.279028768061,-13.204) [2.400000e+00] (490.763687600189,-13.02) [2.500000e+00] (491.869402232016,-12.837) [2.500000e+00] (493.070662947826,-12.64) [2.500000e+00] (494.53802035846,-12.458) [2.700000e+00] (496.492539449225,-12.275) [2.800000e+00] (497.893005483946,-12.122) [2.800000e+00] (499.123616082126,-11.968) [2.800000e+00] (500.490249812515,-11.835) [2.900000e+00] (501.848619204718,-11.682) [2.900000e+00] (503.312963977375,-11.566) [3] (504.493136941834,-11.409) [3.100000e+00] (505.878540989002,-11.274) [3.300000e+00] (507.491032689709,-11.118) [3.400000e+00] (508.862918091176,-10.935) [3.500000e+00] (511.147488495327,-10.796) [3.800000e+00] (512.948604172493,-10.614) [4] (514.328755259145,-10.438) [4.200000e+00] (516.083989741004,-10.3) [4.400000e+00] (517.537827675343,-10.172) [4.800000e+00] (519.392317458851,-10.061) [5.200000e+00] (520.815259503113,-9.944) [5.600000e+00] (522.379553032858,-9.792) [6] (523.810063323146,-9.61) [6.400000e+00] (525.637516703518,-9.414) [6.800000e+00] (527.023691376214,-9.321) [7.300000e+00] (528.15651341941,-9.149) [7.400000e+00] (529.172082217439,-8.984) [7.700000e+00] (530.85293204054,-8.836) [7.800000e+00] (532.357130095883,-8.71) [8] (533.626051093809,-8.573) [8.200000e+00] (534.898679503406,-8.452) [8.300000e+00] (536.107429634038,-8.264) [8.200000e+00] (537.799631396382,-8.075) [8.100000e+00] (540.384899305627,-7.876) [8] (541.339910154951,-7.715) [7.700000e+00] (542.511119680717,-7.661) [7.300000e+00] (543.880839780806,-7.633) [7.100000e+00] (545.200893674116,-7.409) [6.800000e+00] (546.475838257982,-7.245) [6.600000e+00] (547.608736611513,-7.032) [6.300000e+00] (549.143057840604,-6.86) [6] (550.521736593632,-6.726) [5.800000e+00] (552.116151548903,-6.522) [5.500000e+00] (553.811287547934,-6.305) [5.400000e+00] (555.298181574116,-6.105) [5.300000e+00] (556.74073906526,-5.926) [5.100000e+00] (557.826209757301,-5.717) [4.800000e+00] (559.27401937813,-5.489) [4.600000e+00] (559.306150016763,-5.28) [4.500000e+00] (554.03698251721,-5.057) [4.200000e+00] (550.895504015747,-5.033) [4.100000e+00] (557.717371908828,-5.156) [3.900000e+00] (561.272322234517,-5.281) [3.800000e+00] (563.747903483793,-5.203) [3.600000e+00] (564.998287509892,-4.978) [3.500000e+00] (566.837092085808,-4.748) [3.300000e+00] (568.695439782222,-4.514) [3.200000e+00] (569.834361750772,-4.302) [3.100000e+00] (571.248417125722,-4.023) [2.800000e+00] (572.80529153421,-3.801) [2.600000e+00] (574.549320164143,-3.571) [2.500000e+00] (576.188068158497,-3.327) [2.400000e+00] (578.026021500922,-3.09) [2.200000e+00] (579.600891674788,-2.832) [2.200000e+00] (581.740317445334,-2.59) [2.100000e+00] (583.303910184611,-2.314) [1.900000e+00] (584.752411942598,-2.064) [1.800000e+00] (586.321176517195,-1.813) [1.800000e+00] (588.424530119685,-1.551) [1.700000e+00] (590.44747590734,-1.304) [1.700000e+00] (592.019332554757,-1.041) [1.700000e+00] (593.690365127009,-0.8) [1.600000e+00] (595.153075403151,-0.696) [1.600000e+00] (596.676036840976,-0.739) [1.500000e+00] (598.709327188053,-0.795) [1.400000e+00] (601.300749078113,-2.544) [1.300000e+00] (602.105991355403,-2.71) [1.400000e+00] (602.931707421628,-2.856) [1.400000e+00] (604.097821108785,-3.021) [1.400000e+00] (605.605105678937,-3.159) [1.500000e+00] (606.909319136346,-3.331) [1.600000e+00] (607.979110811731,-3.493) [1.600000e+00] (609.188014567845,-3.646) [1.800000e+00] (610.690046607554,-3.809) [1.900000e+00] (612.411437982475,-4.003) [2] (614.375596230447,-4.17) [2.100000e+00] (616.187897873787,-4.376) [2.400000e+00] (617.94682586952,-4.576) [2.400000e+00] (618.749668182145,-4.779) [2.600000e+00] (620.273480998677,-4.971) [2.900000e+00] (621.701663395038,-5.196) [3.300000e+00] (623.128379160792,-5.442) [3.700000e+00] (624.704017811359,-5.668) [4.100000e+00] (625.890205708112,-5.859) [4.500000e+00] (627.184768119437,-6.025) [4.900000e+00] (628.376288411573,-6.173) [5.400000e+00] (629.95416652508,-6.417) [5.900000e+00] (631.361339658358,-6.624) [6.100000e+00] (632.467039445835,-6.799) [6.500000e+00] (633.877225704956,-6.956) [6.700000e+00] (634.377821438691,-7.18) [6.900000e+00] (635.886569630999,-7.328) [7] (637.87413280914,-7.457) [7.100000e+00] (639.081327361336,-7.556) [7.200000e+00] (640.297640667434,-7.738) [7.300000e+00] (641.772475802155,-7.909) [7.300000e+00] (643.080473498388,-8.053) [7.500000e+00] (644.590686114394,-8.199) [7.400000e+00] (646.167016013546,-8.389) [7.300000e+00] (647.243442658802,-8.559) [7.300000e+00] (648.343970668986,-8.723) [7.100000e+00] (649.684333638446,-8.831) [7] (651.167431792837,-8.938) [6.700000e+00] (652.901641882458,-9.081) [6.600000e+00] (654.338248404371,-9.243) [6.300000e+00] (655.474846404656,-9.424) [6.100000e+00] (657.13915376985,-9.627) [6] (658.702740091544,-9.773) [5.900000e+00] (660.580459086924,-9.973) [5.700000e+00] (662.026020678454,-10.183) [5.400000e+00] (663.454278583737,-10.426) [5.200000e+00] (664.918608256291,-10.574) [5.100000e+00] (666.458173966181,-10.646) [4.900000e+00] (668.330721643186,-10.788) [4.600000e+00] (669.558311123957,-10.94) [4.400000e+00] (671.25188905276,-11.118) [4.200000e+00] (672.389951047011,-11.246) [4] (674.707480115744,-11.353) [3.900000e+00] (675.728374949706,-11.489) [3.700000e+00] (677.108510448648,-11.599) [3.600000e+00] (679.2440557551,-11.705) [3.500000e+00] (681.03990082214,-11.873) [3.300000e+00] (682.434326451909,-12.131) [3.200000e+00] (683.467879725312,-12.398) [3] (684.649502814835,-12.614) [2.900000e+00] (685.759066706,-12.651) [2.900000e+00] (687.378953344612,-12.667) [2.900000e+00] (689.062024894014,-12.646) [2.700000e+00] (690.203181255074,-12.758) [2.600000e+00] (691.420265703543,-12.874) [2.600000e+00] (692.68013752651,-13.063) [2.400000e+00] (694.521863875757,-13.218) [2.300000e+00] (695.88632611914,-13.466) [2.400000e+00] (697.552177888773,-13.663) [2.300000e+00] (698.993949654389,-13.954) [2.200000e+00] (699.936593147191,-14.207) [2.100000e+00] (701.709024055777,-14.439) [2.100000e+00] (703.513131741756,-14.529) [2.200000e+00] (704.763963356725,-14.689) [2.100000e+00] (706.036575719774,-14.831) [2.100000e+00] (707.20080998498,-15.004) [2.100000e+00] (708.929071683957,-15.065) [2] (710.481543569578,-15.128) [1.900000e+00] (712.215914938905,-15.152) [1.900000e+00] (713.715535694763,-15.381) [1.900000e+00] (714.842317245742,-15.592) [2] (716.293816454677,-15.756) [1.900000e+00] (717.707006268394,-15.856) [1.900000e+00] (718.838180573656,-15.98) [2] (719.965567172751,-16.117) [1.900000e+00] (721.823820049284,-16.151) [1.900000e+00] (723.697136289684,-16.202) [1.900000e+00] (725.150266789064,-16.221) [1.900000e+00] (726.538141129001,-16.297) [1.900000e+00] (727.790604063571,-16.461) [1.800000e+00] (729.143013490269,-16.715) [1.800000e+00] (730.396856512014,-16.988) [1.800000e+00] (731.709323504927,-17.227) [1.700000e+00] (733.194736747184,-17.449) [1.600000e+00] (734.552313078727,-17.626) [1.500000e+00] (736.01284813964,-17.818) [1.400000e+00] (737.570231800915,-18) [1.400000e+00] (739.057883158724,-18.103) [1.300000e+00] (740.58160404782,-18.17) [1.300000e+00] (741.891057055759,-18.245) [1.400000e+00] (743.346254819787,-18.143) [1.400000e+00] (743.715041281529,-17.892) [1.500000e+00] (743.372501862502,-17.724) [1.400000e+00] (745.983919066963,-17.728) [1.400000e+00] (747.118878011834,-17.766) [1.400000e+00] (748.204335323046,-17.714) [1.500000e+00] (749.921836001063,-17.627) [1.600000e+00] (751.85808119249,-17.399) [1.600000e+00] (753.443353552948,-17.167) [1.500000e+00] (755.020276379409,-16.882) [1.500000e+00] (756.722107327212,-16.622) [1.600000e+00] (758.217849965371,-16.404) [1.700000e+00] (759.600472320502,-16.237) [1.700000e+00] (760.890382266074,-16.048) [1.800000e+00] (762.251915034731,-15.834) [1.900000e+00] (763.556890150241,-15.676) [1.900000e+00] (764.824330880797,-15.518) [1.800000e+00] (766.085660622746,-15.363) [1.700000e+00] (767.303515412042,-15.243) [1.800000e+00] (768.707746775803,-15.12) [1.800000e+00] (770.035275901486,-14.985) [1.900000e+00] (771.45749898875,-14.849) [1.800000e+00] (772.960126365527,-14.688) [1.900000e+00] (774.436410707631,-14.525) [2] (775.964604761534,-14.353) [2] (777.462755076765,-14.189) [1.900000e+00] (778.832378667063,-14.032) [1.900000e+00] (780.093793662851,-13.878) [1.800000e+00] (781.446113566901,-13.752) [1.900000e+00] (782.834503461074,-13.586) [1.800000e+00] (784.288319505995,-13.497) [1.800000e+00] (785.599318236394,-13.405) [1.900000e+00] (786.924607986195,-13.283) [2.100000e+00] (788.248433341269,-13.18) [2.200000e+00] (789.524138038227,-13.07) [2.400000e+00] (790.91709024823,-12.952) [2.500000e+00] (792.288176484898,-12.877) [2.500000e+00] (793.366829955702,-12.776) [2.600000e+00] (794.642446761998,-12.629) [2.800000e+00] (796.212734421098,-12.47) [3] (797.200481206599,-12.267) [3.100000e+00] (798.647581243616,-12.004) [3.200000e+00] (800.583991269068,-11.717) [3.500000e+00] (802.90744059022,-11.483) [3.700000e+00] (804.338700017224,-11.325) [3.800000e+00] (806.056278527151,-11.18) [4.200000e+00] (807.985111391972,-11.039) [4.300000e+00] (809.40285440908,-10.905) [4.600000e+00] (810.612357085689,-10.72) [4.800000e+00] (811.859479372142,-10.588) [5] (813.389994187876,-10.469) [5.300000e+00] (814.731034966986,-10.353) [5.900000e+00] (816.271277168218,-10.164) [6.400000e+00] (817.730428419094,-10.007) [6.800000e+00] (819.284273172684,-9.883) [7] (820.654668793693,-9.801) [7.300000e+00] (822.52108780309,-9.643) [7.500000e+00] (824.253041726866,-9.508) [7.800000e+00] (824.840833412025,-9.375) [8.100000e+00] (825.621798949205,-9.168) [8.300000e+00] (826.630547947332,-8.977) [8.400000e+00] (831.387618680305,-8.688) [8.100000e+00] (832.009593889613,-8.736) [8] (833.13129049664,-8.678) [7.700000e+00] (834.55738448232,-8.491) [7.300000e+00] (836.29381328966,-8.28) [7.100000e+00] (837.783693679666,-8.09) [6.800000e+00] (838.642402030511,-7.945) [6.500000e+00] (839.946772788831,-7.77) [6.200000e+00] (841.338348668701,-7.611) [6] (842.878677529188,-7.483) [5.800000e+00] (844.115207810356,-7.353) [5.600000e+00] (845.405796651774,-7.164) [5.400000e+00] (847.348138962983,-6.937) [5.300000e+00] (849.439057126407,-6.71) [5.100000e+00] (851.269312551894,-6.508) [4.800000e+00] (852.633501755337,-6.361) [4.500000e+00] (853.946733414982,-6.169) [4.400000e+00] (855.284935676456,-5.981) [4.200000e+00] (856.693903191344,-5.759) [4] (857.946273251773,-5.559) [3.800000e+00] (859.17385121571,-5.328) [3.600000e+00] (860.447224319571,-5.155) [3.400000e+00] (861.974037716558,-4.943) [3.300000e+00] (863.154179017472,-4.784) [3.100000e+00] (864.559686758026,-4.588) [2.900000e+00] (865.969848287846,-4.383) [2.900000e+00] (867.286867711739,-4.149) [2.800000e+00] (868.260319609999,-3.964) [2.600000e+00] (869.90360330309,-3.753) [2.500000e+00] (871.737734871017,-3.54) [2.400000e+00] (873.290023959297,-3.36) [2.400000e+00] (875.221085368602,-3.144) [2.400000e+00] (876.822958650073,-2.923) [2.300000e+00] (878.168558335542,-2.678) [2.200000e+00] (879.80133966195,-2.437) [2.100000e+00] (881.004900626457,-2.218) [2] (882.346711287478,-1.994) [1.900000e+00] (883.697561755581,-1.767) [1.700000e+00] (885.452750792101,-1.535) [1.600000e+00] (887.555980861665,-1.306) [1.500000e+00] (889.205200278853,-1.061) [1.600000e+00] (890.644715820389,-0.827) [1.600000e+00] (892.012869115298,-0.748) [1.600000e+00] (893.553879938004,-0.801) [1.500000e+00] (894.906967633035,-0.868) [1.500000e+00] (896.429897494422,-0.934) [1.500000e+00] (898.206359610865,-0.995) [1.300000e+00] (899.742210724292,-1.063) [1.300000e+00] (901.288470982272,-1.254) [1.200000e+00] (903.073700720065,-1.51) [1.100000e+00] (904.056099232407,-1.782) [1.200000e+00] (905.661577359442,-2.038) [1.300000e+00] (907.309240966211,-2.306) [1.400000e+00] (909.364346881288,-2.578) [1.500000e+00] (910.446869560287,-2.838) [1.600000e+00] (911.88862146923,-3.104) [1.700000e+00] (913.17326682145,-3.367) [1.900000e+00] (914.652547754957,-3.618) [2.100000e+00] (916.223188387228,-3.881) [2.100000e+00] (916.929453947779,-4.175) [2.300000e+00] (949.594894040151,-9.763) [7.400000e+00] (949.808442506302,-9.812) [7.200000e+00] (954.119267223631,-10.245) [6.100000e+00] (955.077367636151,-10.285) [6] (955.870193070796,-10.436) [5.900000e+00] (956.973622504513,-10.602) [5.700000e+00] (957.974781187876,-10.738) [5.400000e+00] (959.174455579098,-10.807) [5.200000e+00] (960.59579086236,-10.891) [5.100000e+00] (962.045024189117,-10.985) [4.900000e+00] (963.425911060813,-11.064) [4.800000e+00] (964.813321619232,-11.136) [4.700000e+00] (966.231642458392,-11.247) [4.600000e+00] (966.694102289736,-11.395) [4.400000e+00] (967.312982504803,-11.498) [4.200000e+00] (968.686475163626,-11.494) [4] (970.423758967149,-11.394) [3.800000e+00] (971.967186212811,-11.307) [3.700000e+00] (973.608225517697,-11.336) [3.600000e+00] (975.241000484524,-11.459) [3.600000e+00] (976.294257303585,-11.632) [3.500000e+00] (977.599308908957,-11.904) [3.500000e+00] (978.903584586514,-12.164) [3.400000e+00] (980.006235914641,-12.393) [3.200000e+00] (981.364566598335,-12.584) [3.100000e+00] (982.397411548232,-12.729) [2.900000e+00] (983.378530622847,-12.912) [2.900000e+00] (989.79094801466,-13.235) [2.600000e+00] (995.224455677119,-13.41) [2.500000e+00] (1000.14019726013,-13.706) [2.400000e+00] (1002.25207355658,-14.247) [2.200000e+00] (1000.65341649522,-14.931) [2.200000e+00] (997.295887116171,-15.812) [2.200000e+00] (994.919876553112,-16.289) [2.100000e+00] (994.332094927043,-16.622) [2.100000e+00] (995.485103280614,-16.682) [2.100000e+00] (996.923150762594,-16.607) [2] (998.196112979616,-16.548) [1.900000e+00] (1000.67604527668,-17.357) [1.500000e+00] (1001.93259553678,-17.288) [1.500000e+00] (1002.22561334395,-17.297) [1.600000e+00] (1003.20868579264,-17.338) [1.600000e+00] (1004.78410622502,-17.339) [1.600000e+00] (1005.48465970795,-17.355) [1.600000e+00] (1005.85593613862,-17.341) [1.500000e+00] (1007.06785016757,-17.295) [1.600000e+00] (1008.06297600792,-17.305) [1.500000e+00] (1008.80348316173,-17.345) [1.600000e+00] (1009.85654903618,-17.359) [1.600000e+00] (1011.20282240245,-17.344) [1.600000e+00] (1012.60324586046,-17.296) [1.600000e+00] (1014.21473272895,-17.231) [1.600000e+00] (1015.62342006652,-17.223) [1.600000e+00] (1017.13758234084,-17.182) [1.700000e+00] (1018.17431059987,-17.194) [1.700000e+00] (1019.64239789447,-17.222) [1.700000e+00] (1021.02026602436,-17.262) [1.600000e+00] (1022.49030262215,-17.315) [1.700000e+00] (1023.69162054579,-17.364) [1.600000e+00] (1024.8659118696,-17.41) [1.500000e+00] (1026.33623415529,-17.439) [1.500000e+00] (1027.80879272144,-17.5) [1.500000e+00] (1029.3551368915,-17.576) [1.500000e+00] (1030.66543718858,-17.673) [1.500000e+00] (1031.78538741735,-17.819) [1.400000e+00] (1033.27379069361,-17.983) [1.300000e+00] (1034.9056886297,-18.147) [1.400000e+00] (1036.38719108639,-18.326) [1.500000e+00] (1038.29470453214,-18.468) [1.500000e+00] (1039.41241759212,-18.662) [1.500000e+00] (1039.85018497153,-18.872) [1.500000e+00] (1041.09272505679,-18.793) [1.500000e+00] (1041.98129417478,-18.667) [1.500000e+00] (1043.34030054281,-18.513) [1.500000e+00] (1044.48960879633,-18.295) [1.500000e+00] (1045.85843405255,-18.043) [1.600000e+00] (1047.17096979954,-17.765) [1.600000e+00] (1048.3632461971,-17.507) [1.600000e+00] (1049.54725960384,-17.334) [1.600000e+00] (1050.59594536694,-17.217) [1.600000e+00] (1051.87085792077,-17.119) [1.500000e+00] (1052.99090194634,-17.03) [1.500000e+00] (1054.12971004,-16.957) [1.500000e+00] (1055.32266730831,-16.84) [1.500000e+00] (1056.72979576895,-16.701) [1.500000e+00] (1058.11738334515,-16.545) [1.500000e+00] (1059.3733385923,-16.392) [1.500000e+00] (1060.89401664355,-16.143) [1.600000e+00] (1062.18623248286,-15.915) [1.600000e+00] (1063.40329834032,-15.696) [1.600000e+00] (1064.57895149249,-15.546) [1.500000e+00] (1065.70579996237,-15.429) [1.600000e+00] (1066.97701680064,-15.293) [1.600000e+00] (1068.1782366588,-15.225) [1.600000e+00] (1069.49067382348,-15.171) [1.700000e+00] (1070.63327145846,-15.094) [1.700000e+00] (1071.61050304224,-14.96) [1.800000e+00] (1072.80938929815,-14.838) [1.800000e+00] (1073.96248623326,-14.688) [1.800000e+00] (1075.20648142696,-14.503) [1.700000e+00] (1076.64150979507,-14.343) [1.800000e+00] (1078.19601714235,-14.142) [1.900000e+00] (1079.76851039381,-13.994) [1.900000e+00] (1081.18623283987,-13.781) [2] (1082.59792771605,-13.623) [2.100000e+00] (1084.10431214011,-13.514) [2.100000e+00] (1085.90234959274,-13.381) [2.100000e+00] (1087.05398663402,-13.231) [2.200000e+00] (1088.57087081702,-13.053) [2.100000e+00] (1090.09008725511,-12.9) [2.100000e+00] (1091.4769918407,-12.772) [2.100000e+00] (1092.84513281712,-12.649) [2.200000e+00] (1094.24341218875,-12.522) [2.300000e+00] (1095.51394781334,-12.438) [2.400000e+00] (1096.1619996381,-12.383) [2.600000e+00] (1097.01206795742,-12.425) [2.700000e+00] (1099.014838651,-12.447) [2.900000e+00] (1100.39396114136,-12.309) [3.400000e+00] (1102.24594919868,-11.997) [3.800000e+00] (1104.00344501749,-11.681) [4.100000e+00] (1105.51128452111,-11.427) [4.400000e+00] (1107.12577098928,-11.181) [4.800000e+00] (1107.86715291421,-10.985) [5.200000e+00] (1109.350979832,-10.768) [5.500000e+00] (1110.98977308767,-10.523) [5.700000e+00] (1112.74367271982,-10.308) [6] (1114.19308776837,-10.146) [6.400000e+00] (1115.51086868174,-10.013) [6.800000e+00] (1116.88056518392,-9.896) [7.200000e+00] (1118.40123673035,-9.858) [7.700000e+00] (1119.77161229719,-9.812) [8.100000e+00] (1120.82456904281,-9.688) [8.500000e+00] (1121.82123851495,-9.578) [8.800000e+00] (1122.88575493397,-9.357) [9] (1124.42451016549,-9.221) [9.300000e+00] (1126.24355474329,-9.142) [9] (1127.67945653535,-8.966) [9] (1129.14763301534,-8.868) [9.100000e+00] (1130.56612978604,-8.765) [9] (1131.53665172696,-8.636) [8.900000e+00] (1132.91976023767,-8.484) [8.800000e+00] (1134.07684413984,-8.301) [8.500000e+00] (1135.01780587406,-8.116) [8.200000e+00] (1136.86260253337,-7.922) [7.700000e+00] (1143.78281335461,-7.406) [5.900000e+00] (1144.95183244868,-7.148) [5.700000e+00] (1147.24158909297,-6.876) [5.400000e+00] (1147.44895053885,-6.646) [5.200000e+00] (1146.53928710166,-6.497) [5] (1145.94752157509,-6.361) [4.900000e+00] (1147.76499124173,-6.235) [4.700000e+00] (1149.71565228853,-6.108) [4.600000e+00] (1151.26402471399,-5.943) [4.400000e+00] (1152.86976213877,-5.753) [4.200000e+00] (1154.37011162885,-5.579) [4] (1155.88854477508,-5.444) [3.800000e+00] (1157.56709413638,-5.27) [3.500000e+00] (1158.84511433255,-5.088) [3.400000e+00] (1160.10796309328,-4.93) [3.100000e+00] (1161.46492281255,-4.745) [3] (1162.9720785239,-4.565) [2.800000e+00] (1164.44841634584,-4.378) [2.600000e+00] (1165.9428369353,-4.157) [2.400000e+00] (1167.50035013104,-3.934) [2.300000e+00] (1169.04600948072,-3.706) [2.200000e+00] (1170.1113188371,-3.482) [2.100000e+00] (1171.51531979886,-3.269) [2] (1172.97279402392,-3.059) [1.900000e+00] (1174.45204455426,-2.837) [1.800000e+00] (1176.02296795244,-2.635) [1.700000e+00] (1177.56940506485,-2.405) [1.700000e+00] (1179.12691785991,-2.181) [1.400000e+00] (1179.88384728466,-1.953) [1.400000e+00] (1180.87157080448,-1.718) [1.400000e+00] (1182.22230031307,-1.514) [1.300000e+00] (1183.39191592362,-1.309) [1.200000e+00] (1183.84659478021,-1.093) [1.200000e+00] (1186.07762491598,-0.919) [1.200000e+00] (1188.46440227703,-0.789) [1.200000e+00] (1190.661499174,-0.73) [1.200000e+00] (1192.57219419704,-0.788) [1.300000e+00] (1195.23748059964,-0.842) [1.300000e+00] (1196.96939848037,-0.906) [1.300000e+00] (1198.78337303955,-0.975) [1.300000e+00] (1200.24250369573,-1.105) [1.300000e+00] (1201.64145577211,-1.351) [1.300000e+00] (1203.01707432754,-1.622) [1.300000e+00] (1204.39648551966,-1.878) [1.400000e+00] (1205.68266482191,-2.171) [1.500000e+00] (1206.99508854765,-2.433) [1.500000e+00] (1208.22555873589,-2.689) [1.600000e+00] (1209.34335883212,-2.959) [1.700000e+00] (1210.60464559154,-3.221) [1.600000e+00] (1211.8946179894,-3.473) [1.600000e+00] (1213.3189327837,-3.719) [1.700000e+00] (1214.61784457113,-3.975) [1.800000e+00] (1216.00619472316,-4.227) [1.700000e+00] (1217.34652371687,-4.479) [1.900000e+00] (1218.87097976344,-4.721) [2] (1220.7248737587,-4.977) [2.100000e+00] (1221.98626234077,-5.247) [2.200000e+00] (1222.78938611222,-5.557) [2.400000e+00] (1223.98009727317,-5.796) [2.600000e+00] (1224.93486893376,-6.018) [3.100000e+00] (1225.9325136813,-6.22) [3.500000e+00] (1227.33447808197,-6.436) [3.800000e+00] (1228.50195886306,-6.668) [4.200000e+00] (1229.63238698508,-6.932) [4.700000e+00] (1230.80433677276,-7.124) [5.100000e+00] (1231.89511164539,-7.285) [5.600000e+00] (1233.07667630422,-7.435) [6.200000e+00] (1234.66354595031,-7.585) [6.500000e+00] (1236.33964681948,-7.713) [7] (1238.30573416926,-7.911) [7.400000e+00] (1239.19284199324,-8.064) [7.800000e+00] (1240.2670895661,-8.168) [8.200000e+00] (1241.95088108564,-8.293) [8.400000e+00] (1243.16793852173,-8.474) [8.600000e+00] (1244.56756398881,-8.701) [8.800000e+00] (1246.10485348372,-8.901) [8.900000e+00] (1247.40745218822,-9.047) [9] (1248.77703927679,-9.187) [8.900000e+00] (1250.789999579,-9.341) [8.900000e+00] (1251.89563609244,-9.476) [8.600000e+00] (1253.28486677653,-9.659) [8.300000e+00] (1254.62955908615,-9.837) [8] (1256.26075601036,-10.015) [7.600000e+00] (1257.4101500688,-10.185) [7.300000e+00] (1258.91438674125,-10.325) [7] (1260.31099690458,-10.502) [6.700000e+00] (1261.60688989225,-10.664) [6.500000e+00] (1263.21350636205,-10.809) [6.300000e+00] (1264.71685952279,-10.954) [6] (1265.98338961353,-11.19) [5.700000e+00] (1266.73226112732,-11.393) [5.500000e+00] (1267.7071425454,-11.554) [5.300000e+00] (1269.72903828236,-11.626) [5] (1270.27325560719,-11.698) [4.800000e+00] (1271.18437252059,-11.796) [4.700000e+00] (1272.74691494272,-11.9) [4.500000e+00] (1274.05309607591,-11.959) [4.400000e+00] (1276.06158390439,-11.954) [4.200000e+00] (1278.22795215536,-11.968) [3.800000e+00] (1280.0078803631,-12.01) [3.700000e+00] (1281.5564452019,-12.113) [3.500000e+00] (1283.19143353155,-12.287) [3.300000e+00] (1285.03008670274,-12.514) [3.200000e+00] (1286.80476550434,-12.713) [3.100000e+00] (1288.14353123638,-12.931) [2.900000e+00] (1289.43484858004,-13.167) [2.900000e+00] (1290.8908552334,-13.364) [2.900000e+00] (1292.49112588285,-13.555) [2.800000e+00] (1294.02986696077,-13.741) [2.700000e+00] (1294.75384418361,-13.958) [2.600000e+00] (1295.804755227,-14.182) [2.500000e+00] (1297.13000945056,-14.372) [2.400000e+00] (1298.48217956594,-14.497) [2.300000e+00] (1299.9620885554,-14.599) [2.200000e+00] (1301.49033216845,-14.715) [2.200000e+00] (1302.84349389597,-14.882) [2.200000e+00] (1304.19977636202,-15.022) [2.200000e+00] (1305.4980057917,-15.231) [2] (1307.01788060733,-15.459) [1.900000e+00] (1308.40622256463,-15.637) [1.900000e+00] (1309.7847402734,-15.805) [1.800000e+00] (1311.17542256977,-15.963) [1.800000e+00] (1312.40364871271,-16.098) [1.700000e+00] (1313.88298765571,-16.257) [1.600000e+00] (1315.07436739274,-16.415) [1.600000e+00] (1316.41458462095,-16.57) [1.400000e+00] (1317.71001305514,-16.709) [1.400000e+00] (1318.98558132077,-16.852) [1.400000e+00] (1319.83116048681,-17.064) [1.400000e+00] (1320.98959498518,-17.268) [1.400000e+00] (1322.46882723301,-17.461) [1.400000e+00] (1323.97362799299,-17.56) [1.300000e+00] (1325.32221361779,-17.597) [1.300000e+00] (1326.85627103847,-17.614) [1.300000e+00] (1328.30177718925,-17.633) [1.300000e+00] (1329.71043785175,-17.698) [1.300000e+00] (1331.10827995892,-17.768) [1.300000e+00] (1332.6523732995,-17.822) [1.400000e+00] (1334.47783129625,-17.829) [1.400000e+00] (1335.85120592223,-17.945) [1.400000e+00] (1337.10688025979,-18.177) [1.500000e+00] (1338.26063147237,-18.392) [1.500000e+00] (1339.68323188759,-18.67) [1.300000e+00] (1339.9581389525,-18.799) [1.300000e+00] (1340.67732573557,-18.784) [1.300000e+00] (1341.21753081328,-18.63) [1.300000e+00] (1342.94957195777,-18.381) [1.300000e+00] (1344.40323176751,-18.093) [1.400000e+00] (1346.17052779674,-17.84) [1.400000e+00] (1347.9066835279,-17.536) [1.400000e+00] (1349.55060342417,-17.276) [1.400000e+00] (1351.14047768772,-17.017) [1.400000e+00] (1352.44473305526,-16.732) [1.500000e+00] (1353.96839755711,-16.419) [1.500000e+00] (1355.50635264854,-16.138) [1.500000e+00] (1357.11129881878,-15.86) [1.500000e+00] (1358.53513639307,-15.575) [1.500000e+00] (1359.70261216194,-15.361) [1.500000e+00] (1361.2488302731,-15.218) [1.600000e+00] (1362.58088957364,-15.111) [1.600000e+00] (1363.61236525458,-15.043) [1.600000e+00] (1364.85041088957,-15.045) [1.600000e+00] (1366.07036971485,-15.082) [1.500000e+00] (1367.13400802831,-15.091) [1.500000e+00] (1368.40588516614,-15.031) [1.500000e+00] (1369.5347367272,-14.91) [1.600000e+00] (1370.90576622876,-14.792) [1.600000e+00] (1372.24140296951,-14.659) [1.600000e+00] (1373.52700687035,-14.42) [1.600000e+00] (1375.30111058419,-14.254) [1.600000e+00] (1376.63384049369,-14.122) [1.500000e+00] (1377.83404143197,-14.026) [1.500000e+00] (1378.87590570485,-13.925) [1.600000e+00] (1379.9274857251,-13.773) [1.500000e+00] (1381.43852547062,-13.578) [1.600000e+00] (1382.91104905107,-13.409) [1.500000e+00] (1384.29569773182,-13.288) [1.500000e+00] (1385.56679272203,-13.196) [1.700000e+00] (1386.99130139299,-13.068) [1.600000e+00] (1388.34524157429,-12.941) [1.700000e+00] (1389.21124576909,-12.901) [1.800000e+00] (1389.98334522926,-12.9) [1.800000e+00] (1391.0488726273,-12.801) [2] (1393.74950605546,-12.776) [2.400000e+00] (1394.97002432265,-12.698) [2.700000e+00] (1396.22504644985,-12.473) [2.900000e+00] (1398.05555037586,-12.144) [3.200000e+00] (1399.1181873029,-11.824) [3.600000e+00] (1401.64920663085,-11.48) [4.200000e+00] (1403.44642385463,-11.258) [4.600000e+00] (1404.68926236817,-11.005) [4.800000e+00] (1405.90709396026,-10.804) [5.100000e+00] (1407.43600136379,-10.614) [5.400000e+00] (1409.00622151415,-10.435) [5.600000e+00] (1410.64722942181,-10.298) [6] (1411.94634451724,-10.143) [6.400000e+00] (1413.21297101755,-10.041) [6.700000e+00] (1414.46385239472,-9.968) [7] (1415.92431418593,-9.906) [7.200000e+00] (1417.36155049859,-9.807) [7.200000e+00] (1418.68221953631,-9.675) [7.200000e+00] (1420.20967378253,-9.48) [7.300000e+00] (1421.67091600235,-9.317) [7.200000e+00] (1422.98923979945,-9.171) [7.200000e+00] (1424.22582926871,-8.984) [7.200000e+00] (1425.78477066576,-8.755) [6.900000e+00] (1427.58712355013,-8.535) [6.600000e+00] (1429.05573673518,-8.346) [6.300000e+00] (1430.79142762825,-8.097) [6.200000e+00] (1432.37147033703,-7.846) [5.900000e+00] (1433.98701834985,-7.676) [5.600000e+00] (1435.64912808587,-7.556) [5.500000e+00] (1437.12320908543,-7.416) [5.300000e+00] (1438.75282710198,-7.268) [5.200000e+00] (1440.11402407316,-7.118) [5] (1441.70590362958,-6.951) [4.800000e+00] (1443.1476036757,-6.699) [4.700000e+00] (1444.73378655567,-6.53) [4.600000e+00] (1446.3830544746,-6.366) [4.500000e+00] (1447.90001042533,-6.182) [4.400000e+00] (1449.34405574091,-5.969) [4.400000e+00] (1450.64607334099,-5.769) [4.200000e+00] (1452.09670606906,-5.551) [4.100000e+00] (1453.60740936325,-5.32) [4] (1454.97072700506,-5.149) [3.900000e+00] (1456.47640506205,-4.964) [3.700000e+00] (1458.17245669575,-4.764) [3.500000e+00] (1459.46085205005,-4.569) [3.300000e+00] (1460.82818876259,-4.343) [3] (1462.50827288093,-4.125) [2.800000e+00] (1463.84244686445,-3.909) [2.600000e+00] (1465.40149558962,-3.698) [2.400000e+00] (1466.52676194585,-3.463) [2.300000e+00] (1467.92871193727,-3.244) [2.100000e+00] (1469.68617260176,-3.026) [2.100000e+00] (1471.11201506838,-2.817) [2.100000e+00] (1472.59748306645,-2.601) [2] (1474.07546982089,-2.369) [1.800000e+00] (1475.78156797342,-2.13) [1.700000e+00] (1477.61472914717,-1.899) [1.600000e+00] (1467.60446488409,-18.751) [1.100000e+00] (1466.58437849054,-18.578) [1.100000e+00] (1465.49115594547,-18.426) [1.200000e+00] (1464.4061968499,-18.23) [1.100000e+00] (1463.37929844506,-18.173) [1.100000e+00] (1462.43658902727,-18.086) [1.200000e+00] (1461.23204683625,-17.887) [1.200000e+00] (1459.85287508218,-17.681) [1.200000e+00] (1458.36015006729,-17.466) [1.200000e+00] (1456.86731162039,-17.203) [1.300000e+00] (1455.5192925405,-16.868) [1.300000e+00] (1454.31419145351,-16.542) [1.300000e+00] (1450.64071654329,-15.98) [1.500000e+00] (1448.138509899,-15.593) [1.600000e+00] (1446.51134828992,-15.316) [1.600000e+00] (1444.69694014989,-14.952) [1.700000e+00] (1442.94628759967,-14.61) [1.700000e+00] (1441.41503928239,-14.241) [1.700000e+00] (1440.04692088087,-13.935) [1.700000e+00] (1438.41953602032,-13.647) [1.900000e+00] (1436.88002474145,-13.396) [2.100000e+00] (1435.2195896949,-13.153) [2.100000e+00] (1433.90182745959,-12.964) [2.300000e+00] (1432.13029292342,-12.785) [2.500000e+00] (1430.76217231493,-12.641) [2.600000e+00] (1429.47600842649,-12.489) [2.700000e+00] (1428.02749550952,-12.368) [2.700000e+00] (1426.41976101012,-12.238) [2.700000e+00] (1424.70595225822,-12.071) [2.700000e+00] (1423.23633762869,-11.893) [2.700000e+00] (1421.55479823343,-11.719) [2.800000e+00] (1420.07479730604,-11.573) [2.900000e+00] (1417.8192306451,-11.462) [3.100000e+00] (1415.249793885,-11.356) [3.100000e+00] (1413.73606909636,-11.402) [3.400000e+00] (1413.25438261309,-11.716) [3.400000e+00] (1413.83120554272,-12.001) [3.500000e+00] (1413.97837015015,-12.097) [3.700000e+00] (1413.27080885722,-12.012) [3.900000e+00] (1412.51813951515,-11.777) [4.200000e+00] (1411.39130711559,-11.52) [4.600000e+00] (1410.17649085623,-11.307) [4.900000e+00] (1408.79720226103,-11.078) [5.300000e+00] (1407.37213280066,-10.896) [5.700000e+00] (1406.17462295122,-10.718) [6] (1405.24084633161,-10.546) [6.600000e+00] (1403.56767805647,-10.304) [7] (1402.06299671626,-10.116) [7.300000e+00] (1400.53029312182,-9.965) [7.600000e+00] (1399.1975649316,-9.821) [7.900000e+00] (1397.75128348039,-9.642) [7.900000e+00] (1396.53501406379,-9.446) [7.900000e+00] (1395.05724325484,-9.277) [8] (1393.55691886572,-9.113) [7.800000e+00] (1392.22865747505,-8.993) [7.600000e+00] (1390.74641900698,-8.828) [7.500000e+00] (1389.36177164464,-8.623) [7.200000e+00] (1387.89673019638,-8.443) [7] (1386.15589676663,-8.302) [6.600000e+00] (1384.65177529787,-8.161) [6.400000e+00] (1383.41808922181,-7.995) [6.100000e+00] (1382.23933724953,-7.785) [5.900000e+00] (1380.6360629875,-7.596) [5.800000e+00] (1378.8869657072,-7.399) [5.500000e+00] (1377.46781319561,-7.191) [5.200000e+00] (1376.0102530205,-6.949) [5.100000e+00] (1374.66088951669,-6.727) [4.800000e+00] (1373.08619735126,-6.59) [4.700000e+00] (1371.94585264192,-6.422) [4.500000e+00] (1370.66940066178,-6.242) [4.400000e+00] (1369.69576279155,-6.048) [4.300000e+00] (1368.43214999165,-5.859) [4.100000e+00] (1367.11750557345,-5.68) [4] (1365.82687018668,-5.514) [3.800000e+00] (1358.0491112121,-4.428) [3] (1356.91412223239,-4.282) [2.800000e+00] (1355.4671650152,-4.083) [2.700000e+00] (1354.08631040554,-3.901) [2.600000e+00] (1352.36802622931,-3.685) [2.500000e+00] (1350.49576365711,-3.505) [2.400000e+00] (1349.08263794274,-3.322) [2.300000e+00] (1347.21473544621,-3.093) [2.200000e+00] (1345.5444662084,-2.864) [2.200000e+00] (1343.97647319727,-2.6) [2] (1342.33177247173,-2.367) [1.900000e+00] (1340.28900331513,-2.124) [1.800000e+00] (1338.82317714085,-1.871) [1.800000e+00] (1336.97346597111,-1.607) [1.600000e+00] (1335.13113023837,-1.339) [1.700000e+00] (1333.24893362696,-1.07) [1.600000e+00] (1331.79807220526,-0.794) [1.600000e+00] (1330.28412264903,-0.73) [1.600000e+00] (1328.05924709374,-0.783) [1.600000e+00] (1326.7399172119,-0.846) [1.500000e+00] (1325.14567940565,-0.905) [1.500000e+00] (1323.7947525533,-0.995) [1.500000e+00] (1321.92305171687,-1.226) [1.500000e+00] (1320.43321613918,-1.499) [1.500000e+00] (1319.30113144111,-1.77) [1.600000e+00] (1318.25993743423,-2.048) [1.600000e+00] (1316.62193764001,-2.31) [1.700000e+00] (1315.36133409805,-2.583) [1.700000e+00] (1314.59515654598,-2.852) [1.800000e+00] (1313.05049450631,-3.124) [1.800000e+00] (1311.33911983747,-3.365) [1.900000e+00] (1310.13344862224,-3.644) [2] (1309.00895235099,-3.905) [2.200000e+00] (1307.89864040397,-4.17) [2.300000e+00] (1306.45245882977,-4.393) [2.400000e+00] (1305.17454847706,-4.631) [2.400000e+00] (1304.16115840331,-4.913) [2.500000e+00] (1303.13269599313,-5.173) [2.600000e+00] (1301.98028958134,-5.379) [2.700000e+00] (1300.21096728202,-5.571) [2.900000e+00] (1299.56582512303,-5.78) [3.200000e+00] (1298.72684237099,-6.01) [3.500000e+00] (1296.73062616818,-6.193) [4] (1295.25965387372,-6.341) [4.500000e+00] (1294.18696787251,-6.551) [5.100000e+00] (1292.99111826921,-6.768) [5.600000e+00] (1291.57429744316,-6.969) [6.100000e+00] (1289.70883195093,-7.141) [6.600000e+00] (1288.40010416754,-7.292) [6.900000e+00] (1286.97860315129,-7.521) [7.300000e+00] (1285.72090744522,-7.685) [7.600000e+00] (1284.36483533216,-7.817) [7.800000e+00] (1282.95539129053,-7.971) [7.900000e+00] (1281.72705808084,-8.094) [7.900000e+00] (1280.01848277533,-8.247) [8.100000e+00] (1278.56704875759,-8.42) [8.300000e+00] (1276.54536417516,-8.63) [8.300000e+00] (1275.55083824411,-8.945) [8.100000e+00] (1274.74490616559,-9.244) [8.100000e+00] (1274.4520582803,-9.45) [7.800000e+00] (1272.55857732872,-9.553) [7.600000e+00] (1270.99951456589,-9.636) [7.400000e+00] (1269.97562573783,-9.723) [7.200000e+00] (1268.23030811423,-9.793) [7] (1267.44012253526,-9.92) [6.800000e+00] (1265.98556826663,-10.057) [6.600000e+00] (1264.77687956989,-10.214) [6.400000e+00] (1263.81093573556,-10.345) [6.200000e+00] (1262.33684147126,-10.419) [6] (1260.453389761,-10.418) [5.800000e+00] (1259.69246261962,-10.516) [5.600000e+00] (1258.29517832209,-10.658) [5.300000e+00] (1256.87377918654,-10.789) [5.200000e+00] (1255.54628833979,-10.886) [5] (1253.79270600637,-10.99) [4.800000e+00] (1252.19554818548,-11.13) [4.700000e+00] (1250.33755918074,-11.308) [4.500000e+00] (1248.78384727515,-11.516) [4.400000e+00] (1247.65300567139,-11.736) [4.100000e+00] (1246.14731314699,-11.923) [3.900000e+00] (1244.15690734271,-12.099) [3.700000e+00] (1242.85254201573,-12.238) [3.700000e+00] (1241.5257249022,-12.453) [3.600000e+00] (1239.70827050957,-12.646) [3.400000e+00] (1238.47401072197,-12.812) [3.300000e+00] (1237.18102511146,-12.951) [3.200000e+00] (1235.77838608894,-13.092) [3] (1234.92724201865,-13.271) [2.800000e+00] (1233.25862419952,-13.427) [2.800000e+00] (1231.69373668181,-13.516) [2.700000e+00] (1230.16413608929,-13.684) [2.600000e+00] (1228.80067933978,-13.848) [2.500000e+00] (1227.52879323466,-13.989) [2.300000e+00] (1225.76169411969,-14.134) [2.300000e+00] (1224.39064988976,-14.318) [2.200000e+00] (1223.29374430628,-14.448) [2.100000e+00] (1221.75655623334,-14.598) [2] (1220.28178216083,-14.719) [1.900000e+00] (1218.84754398989,-14.884) [1.800000e+00] (1217.48320418753,-15.031) [1.600000e+00] (1216.02864650973,-15.162) [1.700000e+00] (1214.52305365948,-15.266) [1.700000e+00] (1213.09629942697,-15.383) [1.600000e+00] (1211.73866451105,-15.477) [1.600000e+00] (1210.3088953757,-15.589) [1.600000e+00] (1208.98509239242,-15.678) [1.600000e+00] (1207.56514484015,-15.779) [1.600000e+00] (1206.20984579138,-15.881) [1.500000e+00] (1204.76063891286,-15.962) [1.300000e+00] (1203.44821429867,-16.075) [1.400000e+00] (1202.04255779459,-16.209) [1.500000e+00] (1200.58129397006,-16.332) [1.500000e+00] (1199.21326203556,-16.458) [1.500000e+00] (1197.77980076775,-16.585) [1.600000e+00] (1196.51695501576,-16.73) [1.600000e+00] (1195.36901388762,-16.876) [1.500000e+00] (1193.99942338997,-16.995) [1.600000e+00] (1192.64110946744,-17.121) [1.600000e+00] (1191.25197854405,-17.236) [1.600000e+00] (1189.8470998028,-17.356) [1.600000e+00] (1188.55489161248,-17.476) [1.700000e+00] (1187.30555785631,-17.587) [1.600000e+00] (1185.71956521724,-17.698) [1.700000e+00] (1184.48899151613,-17.768) [1.700000e+00] (1183.20504677524,-17.891) [1.700000e+00] (1181.87006597298,-17.857) [1.600000e+00] (1180.51408748793,-17.71) [1.700000e+00] (1179.21527491556,-17.532) [1.700000e+00] (1177.55267730216,-17.397) [1.700000e+00] (1175.8991208432,-17.283) [1.800000e+00] (1174.75798642428,-17.231) [1.900000e+00] (1174.10827590382,-17.186) [1.800000e+00] (1173.41559139117,-17.132) [1.700000e+00] (1171.92049305529,-16.974) [1.700000e+00] (1170.73736461812,-16.889) [1.700000e+00] (1169.62044235932,-16.756) [1.700000e+00] (1168.32901196076,-16.614) [1.800000e+00] (1167.16833665748,-16.422) [1.800000e+00] (1166.17759826385,-16.263) [1.800000e+00] (1164.65100297407,-16.072) [1.900000e+00] (1163.09047622275,-15.905) [1.800000e+00] (1161.57194348978,-15.672) [1.800000e+00] (1160.0347489412,-15.497) [1.800000e+00] (1158.69966508499,-15.299) [1.900000e+00] (1156.7492062204,-15.122) [2] (1155.41577959662,-14.99) [2.100000e+00] (1154.00944150736,-14.904) [2.200000e+00] (1152.70283927249,-14.772) [2.200000e+00] (1151.45485883103,-14.676) [2.200000e+00] (1149.95305257152,-14.522) [2.200000e+00] (1148.63615195832,-14.381) [2.300000e+00] (1147.34102719149,-14.204) [2.400000e+00] (1145.82103639964,-14.04) [2.400000e+00] (1144.74892179738,-13.848) [2.600000e+00] (1143.56792615695,-13.716) [2.600000e+00] (1142.35018458587,-13.602) [2.600000e+00] (1141.65187477676,-13.491) [2.600000e+00] (1140.30425583196,-13.382) [2.600000e+00] (1138.82791586104,-13.233) [2.600000e+00] (1137.18251807842,-13.105) [2.700000e+00] (1135.59875521519,-12.947) [2.700000e+00] (1134.26075561296,-12.762) [2.800000e+00] (1133.03698558365,-12.587) [2.800000e+00] (1131.26015143414,-12.428) [2.800000e+00] (1130.22575918218,-12.33) [2.900000e+00] (1128.87269085595,-12.251) [3] (1127.56463102108,-12.13) [3.100000e+00] (1126.03793230557,-12.02) [3.100000e+00] (1124.6570592156,-11.9) [3.300000e+00] (1123.48141170852,-11.745) [3.400000e+00] (1122.05251433599,-11.596) [3.500000e+00] (1120.54166164881,-11.451) [3.700000e+00] (1119.30359974042,-11.308) [3.900000e+00] (1117.97084917283,-11.201) [4.200000e+00] (1116.76506195247,-11.128) [4.700000e+00] (1115.52388738955,-10.998) [5.100000e+00] (1114.06708615421,-10.884) [5.500000e+00] (1112.90203572806,-10.767) [5.900000e+00] (1111.48742851512,-10.605) [6.400000e+00] (1109.30596956348,-10.398) [6.800000e+00] (1107.88902697108,-10.193) [7.100000e+00] (1106.47286300133,-10.049) [7.600000e+00] (1105.07322590136,-9.923) [8] (1103.8073583699,-9.776) [8.300000e+00] (1102.3896380727,-9.614) [8.500000e+00] (1101.1365061219,-9.466) [8.700000e+00] (1099.64742802074,-9.296) [8.700000e+00] (1098.08096586433,-9.195) [8.800000e+00] (1097.40520745745,-9.079) [8.800000e+00] (1097.40520745745,-8.921) [8.900000e+00] (1094.21064647718,-8.686) [8.600000e+00] (1091.40446483745,-8.448) [8.200000e+00] (1089.8424730639,-8.213) [8] (1087.99475856794,-7.98) [7.600000e+00] (1086.07160169445,-7.758) [7.300000e+00] (1084.60935340063,-7.561) [7] (1083.08799843377,-7.451) [6.500000e+00] (1081.81619933602,-7.328) [6.300000e+00] (1079.1385388049,-6.985) [5.700000e+00] (1077.74570397125,-6.806) [5.500000e+00] (1075.8613386601,-6.601) [5.300000e+00] (1074.6226901946,-6.406) [5.200000e+00] (1073.3772368842,-6.223) [5.100000e+00] (1071.81679794179,-6.058) [4.900000e+00] (1070.29388578812,-5.885) [4.700000e+00] (1069.06184758176,-5.705) [4.400000e+00] (1067.97097000306,-5.499) [4.100000e+00] (1066.61410523025,-5.298) [3.900000e+00] (1065.01001506618,-5.076) [3.700000e+00] (1063.42099365522,-4.917) [3.500000e+00] (1061.67934088511,-4.744) [3.300000e+00] (1060.29311502131,-4.554) [3.200000e+00] (1058.8272692515,-4.356) [3.100000e+00] (1057.35101926743,-4.137) [2.900000e+00] (1055.91375421798,-3.9) [2.800000e+00] (1054.31345448368,-3.696) [2.600000e+00] (1052.81309462103,-3.482) [2.500000e+00] (1051.1007989871,-3.245) [2.500000e+00] (1049.3847134108,-3.021) [2.200000e+00] (1048.03309632509,-2.8) [2.100000e+00] (1046.54547161327,-2.547) [2] (1044.95256033064,-2.301) [1.800000e+00] (1043.36723208579,-2.06) [1.800000e+00] (1041.79240268213,-1.822) [1.600000e+00] (1040.44904904586,-1.568) [1.600000e+00] (1039.08693180037,-1.321) [1.600000e+00] (1037.69623386343,-1.079) [1.600000e+00] (1036.08465451642,-0.868) [1.500000e+00] (1034.44371585572,-0.783) [1.400000e+00] (1033.01169895211,-0.809) [1.300000e+00] (1031.81047651529,-0.884) [1.300000e+00] (1030.48452302764,-0.952) [1.300000e+00] (1029.18034673384,-1.076) [1.200000e+00] (1027.77389653641,-1.321) [1.100000e+00] (1026.29161594517,-1.603) [1.200000e+00] (1024.95963488762,-1.873) [1.100000e+00] (1023.55473969911,-2.15) [1.100000e+00] (1022.15509437549,-2.42) [1.200000e+00] (1020.91547149935,-2.691) [1.300000e+00] (1019.53760293993,-2.956) [1.400000e+00] (1018.0906119683,-3.226) [1.500000e+00] (1016.85176547873,-3.472) [1.700000e+00] (1015.44609304413,-3.729) [1.700000e+00] (1013.98549327128,-3.968) [1.900000e+00] (1012.72564643332,-4.216) [2] (1011.50040877402,-4.458) [2.100000e+00] (1010.18271655804,-4.693) [2.200000e+00] (1008.81690184902,-4.906) [2.400000e+00] (1007.49541834364,-5.12) [2.600000e+00] (1006.07924486067,-5.318) [2.700000e+00] (1004.80656649648,-5.51) [2.900000e+00] (1003.43919637738,-5.701) [3.300000e+00] (1001.96439935303,-5.881) [3.800000e+00] (1000.42952018238,-6.067) [4.100000e+00] (999.025399661174,-6.246) [4.500000e+00] (997.639265044581,-6.463) [5.100000e+00] (996.359876921423,-6.666) [5.600000e+00] (995.352506686828,-6.863) [6.400000e+00] (994.088185969619,-7.043) [6.900000e+00] (992.909420795723,-7.216) [7.500000e+00] (991.676506447192,-7.366) [7.800000e+00] (990.383509522842,-7.546) [8.300000e+00] (989.014679080286,-7.697) [8.600000e+00] (987.664612705648,-7.809) [8.900000e+00] (986.142468285034,-7.963) [9] (984.908188211044,-8.161) [9.200000e+00] (983.809139806535,-8.371) [9.300000e+00] (982.538014273264,-8.517) [9.200000e+00] (981.584017314541,-8.678) [9.100000e+00] (980.236963636116,-8.833) [9] (978.820009840593,-8.966) [8.900000e+00] (977.579702196686,-9.142) [8.700000e+00] (976.333366983251,-9.291) [8.400000e+00] (974.995354029198,-9.436) [8.100000e+00] (973.748335279327,-9.584) [8] (972.383977025846,-9.742) [7.700000e+00] (970.971589587974,-9.878) [7.400000e+00] (969.771046389772,-9.985) [7] (968.438965977565,-10.063) [7] (967.252713368873,-10.184) [6.700000e+00] (965.947755072429,-10.319) [6.500000e+00] (964.704432125032,-10.502) [6.200000e+00] (963.615200860472,-10.611) [5.900000e+00] (962.416210435395,-10.753) [5.700000e+00] (961.219550058383,-10.836) [5.400000e+00] (960.044667305046,-10.976) [5.300000e+00] (958.835175372754,-11.115) [5.100000e+00] (957.424246998191,-11.266) [4.900000e+00] (956.046466991233,-11.354) [4.700000e+00] (954.647592008332,-11.481) [4.500000e+00] (953.57187362845,-11.668) [4.300000e+00] (952.314259690758,-11.837) [4.300000e+00] (950.79357218468,-11.974) [4.100000e+00] (949.145137406695,-12.058) [3.900000e+00] (947.571076682795,-12.207) [3.700000e+00] (946.170647637567,-12.346) [3.400000e+00] (944.661235818084,-12.487) [3.400000e+00] (943.210447999136,-12.585) [3.300000e+00] (941.662730797541,-12.775) [3.200000e+00] (940.293027279379,-12.973) [3.200000e+00] (939.004594592698,-13.165) [3.100000e+00] (937.636536209829,-13.33) [3.100000e+00] (936.11507059816,-13.467) [3] (934.62150079421,-13.592) [3] (933.23759910671,-13.692) [2.900000e+00] (931.893555574444,-13.848) [2.800000e+00] (930.551748781447,-13.986) [2.700000e+00] (929.248247399485,-14.097) [2.600000e+00] (927.747098170069,-14.231) [2.600000e+00] (926.301559385583,-14.371) [2.500000e+00] (924.867388650044,-14.492) [2.400000e+00] (923.572242650441,-14.625) [2.300000e+00] (922.27097892514,-14.741) [2.200000e+00] (920.924697335324,-14.918) [2.200000e+00] (919.688082514908,-15.092) [2.100000e+00] (918.430465539635,-15.243) [2] (917.186364114915,-15.374) [2.100000e+00] (915.82200202236,-15.502) [2.100000e+00] (914.424583065523,-15.625) [2.100000e+00] (913.015111634495,-15.772) [2] (911.719873731302,-15.879) [1.900000e+00] (910.212788033911,-15.976) [1.900000e+00] (908.793591023742,-16.075) [1.900000e+00] (907.31577047193,-16.206) [1.800000e+00] (906.010031061392,-16.345) [1.800000e+00] (904.674249259621,-16.479) [1.700000e+00] (903.277606718308,-16.586) [1.700000e+00] (902.046332405872,-16.711) [1.500000e+00] (900.691784759011,-16.787) [1.500000e+00] (899.168855327436,-16.949) [1.500000e+00] (897.633871185916,-17.075) [1.500000e+00] (896.286811060699,-17.175) [1.500000e+00] (894.941212205776,-17.279) [1.500000e+00] (893.451337431782,-17.408) [1.500000e+00] (892.046429692659,-17.514) [1.700000e+00] (890.675262842406,-17.627) [1.600000e+00] (889.465676485758,-17.746) [1.500000e+00] (888.108799766306,-17.857) [1.500000e+00] (886.656545061023,-17.962) [1.500000e+00] (885.383859907284,-17.912) [1.500000e+00] (884.01889959068,-17.724) [1.600000e+00] (882.901082477351,-17.523) [1.600000e+00] (881.802806248483,-17.323) [1.600000e+00] (880.498616544693,-17.138) [1.700000e+00] (879.026820095559,-16.931) [1.600000e+00] (877.809744039519,-16.644) [1.700000e+00] (876.429627107761,-16.397) [1.700000e+00] (875.025493577463,-16.178) [1.800000e+00] (873.410104774697,-16) [1.700000e+00] (871.791017962395,-15.804) [1.800000e+00] (870.537186602619,-15.615) [1.800000e+00] (868.694701458534,-15.415) [1.700000e+00] (867.08757745238,-15.223) [1.800000e+00] (865.614227399732,-15.017) [1.900000e+00] (864.385873937612,-14.841) [2] (862.610365940251,-14.677) [2] (861.020455064246,-14.538) [2] (859.453187436334,-14.406) [2] (857.99033937838,-14.318) [2] (856.571822954067,-14.22) [2] (854.978212291562,-14.087) [1.900000e+00] (853.520614127641,-13.95) [2] (852.117851340282,-13.827) [2.100000e+00] (850.861692255118,-13.705) [2.100000e+00] (849.461255932683,-13.577) [2.100000e+00] (848.147248345326,-13.504) [2.100000e+00] (846.819725236414,-13.433) [2] (845.412486304952,-13.343) [2] (844.093228422723,-13.258) [2] (843.008464706853,-13.176) [2] (841.739565598268,-13.075) [2.100000e+00] (840.369171696223,-12.955) [2.100000e+00] (838.998090674602,-12.825) [2.100000e+00] (837.579663116557,-12.692) [2.100000e+00] (836.165709954415,-12.531) [2.100000e+00] (834.610492651815,-12.388) [2.200000e+00] (833.273929335062,-12.189) [2.100000e+00] (831.820893974603,-12.039) [2.300000e+00] (830.445248000617,-11.842) [2.300000e+00] (829.067364399022,-11.769) [2.400000e+00] (827.567756652624,-11.585) [2.500000e+00] (826.543678783466,-11.478) [2.700000e+00] (825.166569332433,-11.338) [2.800000e+00] (824.108060359763,-11.327) [3] (822.891246831437,-11.222) [3.100000e+00] (821.550981951035,-11.135) [3.200000e+00] (820.181273908338,-10.933) [3.300000e+00] (818.591447513916,-10.779) [3.300000e+00] (816.733293301337,-10.624) [3.500000e+00] (815.407406012638,-10.487) [3.600000e+00] (814.196441607155,-10.307) [3.800000e+00] (812.971186182143,-10.191) [4.200000e+00] (811.725702753407,-10.067) [4.500000e+00] (810.427532796457,-9.957) [4.900000e+00] (809.264602505868,-9.838) [5.200000e+00] (807.970133253125,-9.748) [5.600000e+00] (806.181878268759,-9.589) [5.900000e+00] (804.594287782957,-9.559) [6.300000e+00] (802.105555486717,-9.486) [6.700000e+00] (800.381863293485,-9.376) [7] (798.783770412051,-9.249) [7.300000e+00] (797.011179855664,-9.063) [7.800000e+00] (795.607037184189,-8.843) [7.700000e+00] (794.659749559802,-8.668) [7.700000e+00] (793.302178844221,-8.469) [7.500000e+00] (791.987392378577,-8.3) [7.300000e+00] (790.411766075439,-8.112) [7.200000e+00] (788.89407616534,-7.907) [6.900000e+00] (787.509387404899,-7.692) [6.600000e+00] (786.169032943847,-7.578) [6.300000e+00] (784.654355729727,-7.359) [6.100000e+00] (783.2185318382,-7.2) [5.900000e+00] (781.634727798284,-7.013) [5.600000e+00] (780.26510374907,-6.825) [5.400000e+00] (778.882739217905,-6.62) [5.200000e+00] (777.507088946264,-6.467) [5] (776.020216065958,-6.23) [4.900000e+00] (774.687436157821,-6.063) [4.600000e+00] (773.289231904957,-5.865) [4.500000e+00] (771.727205517642,-5.652) [4.200000e+00] (770.211063508091,-5.418) [4] (768.843677144825,-5.289) [3.600000e+00] (767.339499718543,-5.098) [3.400000e+00] (765.648947064977,-4.894) [3.300000e+00] (763.967431982819,-4.717) [3.100000e+00] (762.349793431481,-4.537) [3] (760.780966270365,-4.291) [2.800000e+00] (759.322585789947,-4.052) [2.700000e+00] (757.678604662749,-3.841) [2.500000e+00] (756.224011888574,-3.615) [2.500000e+00] (754.822708024827,-3.376) [2.400000e+00] (753.404959821386,-3.137) [2.400000e+00] (752.036797588258,-2.926) [2.300000e+00] (750.655119833938,-2.693) [2.300000e+00] (749.306499373713,-2.454) [2.300000e+00] (747.881175786812,-2.226) [2.200000e+00] (746.286089956341,-2.016) [2.100000e+00] (744.90819901951,-1.767) [2] (743.457393550743,-1.543) [1.900000e+00] (742.086218221031,-1.313) [1.900000e+00] (740.592541529239,-1.089) [1.900000e+00] (739.105665640431,-0.847) [1.900000e+00] (737.7164968392,-0.676) [1.700000e+00] (736.467131767602,-0.628) [1.700000e+00] (735.135123890202,-0.685) [1.600000e+00] (733.718148548226,-0.741) [1.600000e+00] (732.301173664802,-0.81) [1.700000e+00] (730.732427802551,-0.883) [1.600000e+00] (729.376400202102,-0.948) [1.600000e+00] (728.017359475809,-1.048) [1.700000e+00] (726.529017903125,-1.291) [1.700000e+00] (725.048855443399,-1.575) [1.700000e+00] (724.063259916447,-1.853) [1.600000e+00] (722.862015102309,-2.127) [1.600000e+00] (721.779400983767,-2.401) [1.700000e+00] (721.059813058517,-2.663) [1.700000e+00] (719.74355749989,-2.924) [1.700000e+00] (718.640712252961,-3.171) [1.700000e+00] (717.080312399596,-3.439) [1.800000e+00] (715.637162724711,-3.711) [1.900000e+00] (714.717848681874,-3.989) [2] (713.795522402028,-4.25) [2.200000e+00] (712.4732401908,-4.505) [2.300000e+00] (711.563571891685,-4.745) [2.400000e+00] (710.429215845819,-5.008) [2.700000e+00] (708.613226077895,-5.21) [2.800000e+00] (707.463805349647,-5.419) [2.900000e+00] (706.149788365231,-5.616) [3.200000e+00] (704.48264035703,-5.833) [3.600000e+00] (703.082964775302,-5.999) [4.100000e+00] (701.378971766709,-6.211) [4.700000e+00] (699.766577063555,-6.414) [5] (698.412010820508,-6.62) [5.100000e+00] (697.28135820226,-6.828) [5.300000e+00] (695.723027419745,-7.009) [5.500000e+00] (693.925028085888,-7.176) [5.500000e+00] (692.01046930519,-7.311) [5.500000e+00] (690.546833372907,-7.521) [5.500000e+00] (688.969042947106,-7.744) [5.300000e+00] (687.477600932657,-7.97) [5.200000e+00] (686.001222740964,-8.176) [5.100000e+00] (684.535347403717,-8.413) [5.100000e+00] (683.18448415858,-8.566) [5] (681.766730826862,-8.751) [4.800000e+00] (680.154334404616,-8.881) [4.900000e+00] (678.643350216711,-9.073) [4.800000e+00] (677.427647231597,-9.246) [4.700000e+00] (675.909172397437,-9.432) [4.500000e+00] (674.521463292103,-9.613) [4.400000e+00] (673.066173827466,-9.773) [4.200000e+00] (671.757405935361,-9.883) [4.100000e+00] (670.499079748215,-10.018) [3.900000e+00] (669.162587845816,-10.214) [3.800000e+00] (667.686982056748,-10.411) [3.700000e+00] (666.335425013387,-10.614) [3.700000e+00] (664.983012665348,-10.763) [3.700000e+00] (663.78245649205,-10.844) [3.500000e+00] (662.517331307941,-10.916) [3.400000e+00] (661.261162053384,-11.024) [3.300000e+00] (659.833676951407,-11.13) [3.100000e+00] (658.893880722283,-11.263) [3] (657.489723293332,-11.381) [3] (656.038218468331,-11.511) [2.800000e+00] (654.64077845257,-11.601) [2.700000e+00] (653.198310310169,-11.77) [2.600000e+00] (652.005325995222,-11.966) [2.600000e+00] (650.819832756161,-12.174) [2.500000e+00] (649.680913250323,-12.358) [2.400000e+00] (648.514961354301,-12.52) [2.400000e+00] (647.255779032033,-12.684) [2.300000e+00] (645.969645043784,-12.852) [2.200000e+00] (644.835285588577,-12.973) [2.200000e+00] (643.809057558051,-13.065) [2.100000e+00] (642.577681346561,-13.175) [2] (641.42532707258,-13.286) [2.100000e+00] (640.168464937323,-13.368) [2] (639.223335911926,-13.427) [2] (638.222755741307,-13.542) [2] (637.205727647829,-13.651) [2] (636.106746591512,-13.781) [2] (635.017575881011,-13.872) [1.900000e+00] (633.795317993951,-13.939) [1.800000e+00] (632.0468972664,-13.954) [1.800000e+00] (630.951008283034,-13.974) [1.800000e+00] (629.405737615541,-13.993) [1.800000e+00] (627.225769032791,-14.015) [1.800000e+00] (625.121887779129,-14.154) [1.700000e+00] (621.551514734018,-14.31) [1.800000e+00] (619.900719910773,-14.515) [1.800000e+00] (618.054506527998,-14.815) [1.900000e+00] (616.722406206452,-15.044) [1.900000e+00] (615.389453246023,-15.222) [1.900000e+00] (613.606504179905,-15.332) [1.900000e+00] (611.7717275025,-15.455) [1.800000e+00] (610.45383747623,-15.615) [1.700000e+00] (609.309504508075,-15.77) [1.700000e+00] (607.701578271135,-15.912) [1.700000e+00] (606.007140826818,-16.065) [1.600000e+00] (604.578876846683,-16.26) [1.600000e+00] (604.579944728651,-16.448) [1.600000e+00] (602.816058880144,-17.675) [1.500000e+00] (601.360921292768,-17.85) [1.400000e+00] (600.091391460551,-17.933) [1.500000e+00] (598.824794459762,-17.917) [1.500000e+00] (597.396609455813,-17.918) [1.400000e+00] (596.325431902945,-17.884) [1.400000e+00] (594.77543626897,-17.841) [1.400000e+00] (593.20219325654,-17.849) [1.400000e+00] (591.218648551032,-17.893) [1.400000e+00] (589.956529988152,-18.024) [1.400000e+00] (588.412638664266,-18.182) [1.400000e+00] (582.336623377122,-17.886) [1.400000e+00] (581.114974725035,-17.673) [1.500000e+00] (579.406245030146,-17.449) [1.500000e+00] (577.859181396896,-17.216) [1.500000e+00] (576.218036074547,-16.96) [1.500000e+00] (574.871644878632,-16.696) [1.600000e+00] (574.101622676206,-16.423) [1.500000e+00] (573.088755141335,-16.269) [1.600000e+00] (572.01765346925,-16.235) [1.500000e+00] (571.115710711763,-16.258) [1.500000e+00] (570.11366093119,-16.202) [1.500000e+00] (568.835089143089,-16.04) [1.500000e+00] (567.203989259495,-15.781) [1.500000e+00] (565.714856658791,-15.552) [1.500000e+00] (564.110633535895,-15.333) [1.600000e+00] (562.323118373242,-15.117) [1.700000e+00] (560.845956633901,-14.925) [1.700000e+00] (558.693089904352,-14.678) [1.700000e+00] (556.77395379491,-14.459) [1.700000e+00] (555.322281132898,-14.267) [1.800000e+00] (553.985698563551,-14.124) [1.800000e+00] (552.830168170264,-13.968) [1.800000e+00] (551.241779437419,-13.825) [1.900000e+00] (550.045775579096,-13.684) [2] (548.78365311927,-13.566) [2] (547.64094573849,-13.475) [2.100000e+00] (546.247281709027,-13.393) [2.200000e+00] (544.864894225709,-13.29) [2.200000e+00] (543.675610016303,-13.124) [2.200000e+00] (542.262402895629,-12.959) [2.100000e+00] (540.754421576806,-12.819) [2.100000e+00] (539.812463344637,-12.683) [2.200000e+00] (538.417254196222,-12.56) [2.200000e+00] (537.355726574113,-12.45) [2.300000e+00] (536.175479506121,-12.368) [2.300000e+00] (535.025355553696,-12.339) [2.400000e+00] (533.976650514154,-12.292) [2.300000e+00] (532.90840327187,-12.193) [2.400000e+00] (531.945358606919,-12.092) [2.400000e+00] (530.807284462883,-12.001) [2.400000e+00] (527.235027128636,-11.747) [2.900000e+00] (526.042883274045,-11.672) [3] (524.60040034535,-11.509) [3.300000e+00] (522.839914622353,-11.305) [3.400000e+00] (521.397431263821,-11.086) [3.700000e+00] (519.694103741061,-10.819) [3.800000e+00] (518.208827218271,-10.547) [3.900000e+00] (516.93241250787,-10.353) [4] (515.450071510865,-10.218) [4.300000e+00] (514.217993765289,-10.058) [4.700000e+00] (512.707073453311,-9.95) [5.100000e+00] (511.298496015165,-9.809) [5.400000e+00] (509.637339639398,-9.679) [5.900000e+00] (508.222356493428,-9.598) [6.400000e+00] (506.457387488947,-9.468) [6.500000e+00] (503.337214264038,-9.275) [6.900000e+00] (504.013696442417,-9.182) [7.100000e+00] (500.802379777837,-8.83) [7.400000e+00] (496.377132778696,-8.687) [7.400000e+00] (494.824658580862,-8.493) [7.700000e+00] (493.371515019616,-8.271) [8] (491.46364903889,-8.071) [8] (490.176029649865,-7.884) [7.900000e+00] (488.813799911123,-7.688) [7.700000e+00] (487.44716532124,-7.51) [7.400000e+00] (485.841467802819,-7.344) [7] (484.422154797968,-7.157) [6.800000e+00] (482.920192767225,-6.919) [6.600000e+00] (481.396448211589,-6.719) [6.400000e+00] (479.886992869078,-6.51) [6.200000e+00] (478.461654988851,-6.314) [5.800000e+00] (477.141597285648,-6.113) [5.400000e+00] (476.059754372661,-5.864) [5.100000e+00] (474.662298856012,-5.656) [4.800000e+00] (473.372288015914,-5.452) [4.500000e+00] (472.003336909058,-5.306) [4.300000e+00] (470.420267446521,-5.114) [4] (469.318957264921,-4.93) [3.800000e+00] (468.328178443739,-4.74) [3.700000e+00] (466.802192276234,-4.557) [3.400000e+00] (466.072110445456,-4.38) [3.300000e+00] (464.397353067545,-4.175) [3.200000e+00] (463.323849885504,-3.982) [3] (462.121816453522,-3.843) [2.900000e+00] (460.885179290108,-3.638) [2.800000e+00] (459.689169873697,-3.435) [2.700000e+00] (458.499109538703,-3.256) [2.600000e+00] (457.153558373643,-3.062) [2.400000e+00] (455.846319727767,-2.881) [2.200000e+00] (454.849515601345,-2.71) [2.200000e+00] (453.717386270204,-2.514) [2.100000e+00] (452.289108938242,-2.32) [2.100000e+00] (450.942784998619,-2.134) [2] (449.543858896415,-1.925) [1.900000e+00] (448.331392642486,-1.733) [1.800000e+00] (447.124876387937,-1.526) [1.700000e+00] (445.53037884952,-1.316) [1.500000e+00] (444.043474938491,-1.118) [1.600000e+00] (442.586692337034,-0.911) [1.500000e+00] (441.311814492722,-0.735) [1.600000e+00] (440.0640461795,-0.656) [1.400000e+00] (438.629046132091,-0.692) [1.400000e+00] (437.292602570498,-0.756) [1.300000e+00] (435.862927751959,-0.824) [1.300000e+00] (434.345202885215,-0.889) [1.300000e+00] (432.884562631887,-0.966) [1.300000e+00] (431.354788444461,-1.04) [1.200000e+00] (429.827255038153,-1.249) [1.100000e+00] (428.154660527987,-1.524) [1.100000e+00] (426.650452558797,-1.795) [1.200000e+00] (425.147016934149,-2.061) [1.100000e+00] (423.91794452047,-2.341) [1.100000e+00] (422.603906506131,-2.611) [1.200000e+00] (421.437942262887,-2.879) [1.200000e+00] (420.039710992459,-3.129) [1.300000e+00] (418.866951765254,-3.384) [1.400000e+00] (417.506262475924,-3.65) [1.400000e+00] (416.27417696535,-3.909) [1.500000e+00] (414.786499019738,-4.183) [1.600000e+00] (413.449907053332,-4.418) [1.700000e+00] (411.87208275713,-4.638) [1.900000e+00] (410.711371532222,-4.879) [2.300000e+00] (409.558925075052,-5.088) [2.600000e+00] (408.143464651823,-5.339) [3.100000e+00] (406.213105668329,-5.576) [3.500000e+00] (404.934368453107,-5.82) [4] (403.509798706878,-6.026) [4.500000e+00] (402.231832488814,-6.248) [4.700000e+00] (400.939648408512,-6.508) [5.200000e+00] (399.8000218685,-6.782) [5.600000e+00] (398.428897091865,-7.009) [6.100000e+00] (397.144207670668,-7.19) [6.400000e+00] (395.809926976744,-7.373) [6.500000e+00] (394.264390812682,-7.487) [6.500000e+00] (392.887242049321,-7.659) [6.400000e+00] (391.595057539338,-7.824) [6.400000e+00] (389.945084922732,-7.994) [6.200000e+00] (388.619768242425,-8.137) [6] (387.257607478938,-8.319) [5.800000e+00] (386.070628670456,-8.481) [5.600000e+00] (384.63709276194,-8.642) [5.500000e+00] (383.298256547178,-8.788) [5.400000e+00] (381.759442296891,-8.932) [5.200000e+00] (380.392028114153,-9.128) [5.100000e+00] (378.620245872335,-9.316) [5] (377.146853672631,-9.45) [4.800000e+00] (375.758425755201,-9.586) [4.600000e+00] (374.431636654369,-9.812) [4.500000e+00] (373.026749634537,-9.992) [4.200000e+00] (371.633767944389,-10.181) [4] (370.147556344525,-10.372) [3.900000e+00] (368.772645754694,-10.537) [3.800000e+00] (367.419520384683,-10.72) [3.800000e+00] (365.718340112779,-10.891) [3.700000e+00] (364.53731402696,-11.024) [3.500000e+00] (363.142860804626,-11.194) [3.400000e+00] (361.837854716421,-11.343) [3.200000e+00] (360.308845968063,-11.465) [3.100000e+00] (358.891067337667,-11.541) [3.100000e+00] (357.468805826649,-11.64) [3] (356.081846833763,-11.805) [3.100000e+00] (354.687393640509,-12.03) [3.100000e+00] (353.56436406112,-12.177) [2.900000e+00] (352.092439955415,-12.367) [2.800000e+00] (350.815941430591,-12.459) [2.700000e+00] (349.210231907574,-12.532) [2.600000e+00] (347.835320487121,-12.681) [2.500000e+00] (346.313734675275,-12.842) [2.400000e+00] (344.722313476962,-12.962) [2.400000e+00] (343.578129296234,-13.139) [2.400000e+00] (342.343797417454,-13.309) [2.400000e+00] (341.160528831294,-13.438) [2.300000e+00] (339.802917084292,-13.576) [2.200000e+00] (338.470872415071,-13.772) [2.100000e+00] (337.123067430278,-13.946) [2] (335.963122504192,-14.113) [1.900000e+00] (334.516833731827,-14.28) [2] (333.135967010073,-14.407) [1.900000e+00] (331.800138705769,-14.518) [1.900000e+00] (330.585278625369,-14.621) [1.900000e+00] (328.944333951,-14.743) [1.900000e+00] (327.462672256065,-14.817) [2] (325.863053656869,-14.956) [1.900000e+00] (324.267147858687,-15.048) [1.800000e+00] (322.789267162244,-15.187) [1.800000e+00] (321.547368901744,-15.314) [1.900000e+00] (320.434774066272,-15.475) [1.900000e+00] (318.941063968179,-15.593) [1.900000e+00] (317.374505816666,-15.746) [1.800000e+00] (315.678644240174,-15.888) [1.800000e+00] (314.236836199551,-16.018) [1.700000e+00] (313.025055694277,-16.127) [1.700000e+00] (311.47194713154,-16.285) [1.600000e+00] (309.951197964876,-16.378) [1.600000e+00] (308.346255112257,-16.52) [1.600000e+00] (307.066041265706,-16.728) [1.600000e+00] (305.757950015311,-16.904) [1.500000e+00] (304.228166000962,-17.04) [1.400000e+00] (302.837420393518,-17.21) [1.500000e+00] (301.38888694296,-17.305) [1.500000e+00] (300.125972740781,-17.421) [1.400000e+00] (298.885545669475,-17.498) [1.400000e+00] (297.497812299326,-17.64) [1.400000e+00] (296.186777955744,-17.75) [1.400000e+00] (295.077193179508,-17.95) [1.400000e+00] (293.818061323182,-18.021) [1.300000e+00] (292.831688676552,-18.15) [1.400000e+00] (291.631116119339,-18.135) [1.500000e+00] (290.767321429905,-18.024) [1.600000e+00] (289.851691562145,-17.851) [1.500000e+00] (288.879675867614,-17.737) [1.500000e+00] (287.788162191773,-17.6) [1.500000e+00] (286.795130956376,-17.523) [1.500000e+00] (285.551827183263,-17.406) [1.500000e+00] (284.290452797649,-17.276) [1.500000e+00] (282.823845639159,-17.113) [1.600000e+00] (281.499290901627,-16.954) [1.500000e+00] (280.021405878581,-16.781) [1.500000e+00] (278.72767166716,-16.576) [1.500000e+00] (277.142268008781,-16.423) [1.500000e+00] (275.607996729204,-16.27) [1.500000e+00] (274.272934235597,-16.157) [1.500000e+00] (272.625255381976,-15.987) [1.500000e+00] (271.167749090406,-15.859) [1.600000e+00] (269.557615771968,-15.682) [1.600000e+00] (268.169177453186,-15.495) [1.500000e+00] (267.007054756922,-15.455) [1.500000e+00] (266.115383180306,-15.444) [1.500000e+00] (265.284515238342,-15.483) [1.400000e+00] (264.289942954844,-15.486) [1.400000e+00] (263.362968860198,-15.512) [1.500000e+00] (262.368396576777,-15.477) [1.500000e+00] (261.624099037979,-15.475) [1.600000e+00] (260.974571138378,-15.504) [1.600000e+00] (260.234825136624,-15.507) [1.700000e+00] (259.516929398633,-15.546) [1.700000e+00] (258.667489942075,-15.551) [1.700000e+00] (257.718797047891,-15.541) [1.700000e+00] (256.513805422619,-15.453) [1.700000e+00] (255.238842044868,-15.289) [1.700000e+00] (253.892500397529,-15.069) [1.700000e+00] (252.540905301887,-14.791) [1.800000e+00] (251.135934381069,-14.547) [1.800000e+00] (249.629469270326,-14.262) [1.700000e+00] (248.307154512368,-14.009) [1.800000e+00] (247.062306625014,-13.859) [1.800000e+00] (245.870064483537,-13.79) [1.800000e+00] (244.640275918067,-13.678) [1.900000e+00] (243.466872720712,-13.62) [1.800000e+00] (242.302504399783,-13.493) [1.800000e+00] (241.107250050036,-13.362) [1.900000e+00] (240.115622294194,-13.256) [1.900000e+00] (239.07145656035,-13.162) [1.900000e+00] (237.810011427514,-13.081) [2] (236.76731771346,-12.946) [2] (235.572062933929,-12.859) [2] (234.058166030276,-12.752) [2.100000e+00] (232.803513215808,-12.602) [2.200000e+00] (231.524832652155,-12.382) [2.400000e+00] (230.312276909916,-12.242) [2.500000e+00] (228.961382465307,-12.025) [2.500000e+00] (227.440625992459,-11.781) [2.600000e+00] (225.910834642978,-11.517) [2.600000e+00] (224.328437147144,-11.306) [2.700000e+00] (222.966265726449,-11.074) [2.900000e+00] (221.624405728609,-10.955) [2.900000e+00] (220.277291393918,-10.845) [3] (219.176034396724,-10.817) [3.200000e+00] (217.876271471216,-10.759) [3.300000e+00] (216.625397907096,-10.632) [3.400000e+00] (215.474481010066,-10.524) [3.600000e+00] (214.282940866645,-10.368) [3.900000e+00] (212.944860519937,-10.21) [4.100000e+00] (211.566222000067,-10.085) [4.500000e+00] (210.420559010051,-9.937) [4.800000e+00] (209.215497984919,-9.768) [5.200000e+00] (208.040487836099,-9.618) [5.900000e+00] (206.379213886203,-9.469) [6.300000e+00] (205.008775090025,-9.312) [6.700000e+00] (203.713495991791,-9.097) [7] (202.159674285664,-8.827) [7.200000e+00] (201.018496441257,-8.636) [7.300000e+00] (199.746540973915,-8.446) [7.500000e+00] (198.303952481099,-8.305) [7.900000e+00] (196.941075223403,-8.194) [7.800000e+00] (195.637530038682,-8.056) [7.700000e+00] (194.636163375407,-7.879) [7.600000e+00] (193.422195413169,-7.748) [7.300000e+00] (192.200538519048,-7.601) [7] (190.756347918267,-7.416) [6.700000e+00] (189.429479590574,-7.281) [6.500000e+00] (188.240244012092,-7.165) [6.200000e+00] (187.114956199569,-7.004) [6] (185.752076734914,-6.85) [5.700000e+00] (184.34408844842,-6.649) [5.400000e+00] (182.866899406683,-6.41) [5] (181.335629962636,-6.237) [4.800000e+00] (179.841203225041,-6.022) [4.400000e+00] (178.464803796198,-5.851) [4.200000e+00] (177.109421255634,-5.659) [4] (175.454870195167,-5.414) [3.800000e+00] (173.674795848668,-5.182) [3.600000e+00] (171.965332357637,-4.993) [3.400000e+00] (170.288226915292,-4.724) [3.200000e+00] (168.632138361122,-4.528) [3] (166.890380117385,-4.347) [2.900000e+00] (165.223781571413,-4.123) [2.700000e+00] (163.664702090405,-3.934) [2.600000e+00] (162.044750347582,-3.72) [2.400000e+00] (160.566853662593,-3.461) [2.200000e+00] (159.021292856571,-3.226) [2.100000e+00] (157.400571463901,-2.964) [2] (155.943754504227,-2.722) [2] (154.368910264961,-2.511) [2] (152.584284927235,-2.268) [2] (150.923708189979,-2.007) [1.900000e+00] (149.460804894204,-1.76) [1.700000e+00] (147.84309307329,-1.507) [1.700000e+00] (146.244924802141,-1.238) [1.500000e+00] (144.900815770371,-1.004) [1.600000e+00] (143.470269634734,-0.819) [1.600000e+00] (141.974301936405,-0.758) [1.500000e+00] (140.533951733203,-0.813) [1.500000e+00] (139.065024938698,-0.907) [1.400000e+00] (137.659980837027,-0.95) [1.400000e+00] (136.259484689078,-1.016) [1.400000e+00] (134.810100097212,-1.159) [1.300000e+00] (133.352449848955,-1.397) [1.300000e+00] (132.065432597066,-1.666) [1.200000e+00] (130.707802712561,-1.954) [1.200000e+00] (129.47492781155,-2.229) [1.100000e+00] (128.01958207023,-2.481) [1.200000e+00] (126.909988785689,-2.77) [1.200000e+00] (125.711714491731,-3.053) [1.200000e+00] (124.473584824369,-3.305) [1.300000e+00] (123.188103776746,-3.56) [1.400000e+00] (121.783120764148,-3.843) [1.500000e+00] (120.439010013312,-4.074) [1.600000e+00] (119.167817290445,-4.314) [1.800000e+00] (118.014589468897,-4.555) [2] (116.73359445556,-4.806) [2.200000e+00] (115.336876669515,-5.006) [2.500000e+00] (114.089006230463,-5.247) [2.900000e+00] (112.845621366624,-5.501) [3.200000e+00] (111.442112638754,-5.695) [3.700000e+00] (110.116776246778,-5.903) [4.300000e+00] (108.766641997032,-6.131) [4.700000e+00] (107.363900253314,-6.301) [5] (105.871709197718,-6.442) [5.300000e+00] (104.399829536001,-6.645) [5.900000e+00] (103.164710357685,-6.891) [6.200000e+00] (101.764211631149,-7.088) [6.500000e+00] (100.452455403654,-7.248) [6.900000e+00] (99.1256434665944,-7.419) [6.800000e+00] (97.8138262082112,-7.572) [6.900000e+00] (96.4456837531614,-7.747) [6.800000e+00] (95.0910621799263,-7.904) [6.700000e+00] (93.8258894888612,-8.108) [6.600000e+00] (92.4712674857886,-8.265) [6.500000e+00] (91.1993042826323,-8.413) [6.300000e+00] (89.8108500040459,-8.586) [6.200000e+00] (88.4675045472981,-8.778) [6] (87.2233505504801,-8.882) [5.900000e+00] (85.9964957392214,-9.078) [5.600000e+00] (84.5538977914222,-9.213) [5.500000e+00] (82.9722548164121,-9.334) [5.300000e+00] (81.6845268547643,-9.468) [5.200000e+00] (80.2584611374513,-9.613) [5] (78.8421963632209,-9.803) [4.900000e+00] (77.4747594605468,-9.955) [4.700000e+00] (76.0201768357193,-10.138) [4.600000e+00] (74.4649253703916,-10.29) [4.400000e+00] (73.0658395257547,-10.487) [4.300000e+00] (72.0216639070358,-10.694) [4.200000e+00] (70.9030332254584,-10.903) [4.100000e+00] (69.6167808958216,-11.103) [4] (68.3109841567949,-11.223) [3.900000e+00] (66.8631301533118,-11.33) [3.800000e+00] (65.4543627619866,-11.421) [3.700000e+00] (64.0959585290907,-11.544) [3.500000e+00] (62.7428099801227,-11.67) [3.400000e+00] (61.499422137068,-11.78) [3.300000e+00] (60.0959086527029,-11.931) [3.100000e+00] (58.7314822392054,-12.087) [3] (57.4038976438461,-12.225) [3] (56.0259503486373,-12.377) [2.900000e+00] (54.5811059167043,-12.505) [2.800000e+00] (53.3647589774474,-12.611) [2.700000e+00] (51.9417028894792,-12.698) [2.600000e+00] (50.5945747730972,-12.829) [2.600000e+00] (49.2136152988279,-12.976) [2.500000e+00] (47.7905574337383,-13.137) [2.400000e+00] (46.4434302349562,-13.28) [2.200000e+00] (45.2263154517417,-13.464) [2.100000e+00] (43.9813901439844,-13.587) [2] (42.7237127157393,-13.721) [2] (41.2721370546646,-13.854) [2] (39.9024541265132,-13.976) [1.900000e+00] (38.4576088640612,-14.069) [1.800000e+00] (37.0571054390084,-14.173) [1.800000e+00] (35.595727516336,-14.264) [1.800000e+00] (34.1794588741853,-14.401) [1.700000e+00] (32.8030437995526,-14.528) [1.800000e+00] (31.4867349197922,-14.672) [1.700000e+00] (30.2493666784941,-14.846) [1.800000e+00] (28.8631506897011,-14.954) [1.700000e+00] (27.5378083096434,-15.088) [1.600000e+00] (26.0328551041201,-15.203) [1.700000e+00] (24.6022977364807,-15.333) [1.600000e+00] (23.2303696133712,-15.447) [1.600000e+00] (21.8215983541257,-15.571) [1.500000e+00] (20.4962555443606,-15.687) [1.600000e+00] (19.0717190389646,-15.846) [1.500000e+00] (17.706521773341,-15.959) [1.500000e+00] (16.3338258065844,-16.087) [1.400000e+00] (14.8694353038863,-16.235) [1.500000e+00] (13.476428402087,-16.436) [1.400000e+00] (11.8399253450121,-16.599) [1.300000e+00] (10.4807502888891,-16.697) [1.300000e+00] (9.08927689692154,-16.787) [1.200000e+00] (7.78347631897693,-16.917) [1.200000e+00] (5.9876150635571,-17.024) [1.200000e+00] (4.93215682376435,-17.209) [1.200000e+00] (3.75188262730727,-17.434) [1.200000e+00] };
 

### 2013-07-31 figurefactory/files/voned_0_3.tex
Most of the changes discussed with Andreas
Many small fixes

--- 2013-03-19 figurefactory/files/voned_1_1.tex
@@
 \begin{axis}[%
-tick label style={font=\tiny},
-label style={font=\tiny},
+tick label style={font=\Large},
+label style={font=\Large},
 label shift={-4pt},
 xlabel shift={-6pt},
-legend style={font=\tiny},
+legend style={font=\Large},
+xticklabel shift={2pt},
 view={0}{90},
@@
 mark=*,
-mark size=2.5pt,
+mark size=3.5pt,
 forget plot
@@
 \addplot [
-color=green!60!black,
-densely dotted,
-line width=1.0pt,
+color=black,
+solid,
+line width=1.5pt,
+mark size=3pt,
+mark=-,
 forget plot
@@
 coordinates{
- (1.5,-2)(1.5,2)
+ (1.25,-1)(1.25,3)
 };
 
-\addplot [
-color=green!60!black,
-only marks,
-mark=*,
-mark size=2.5pt,
-line width=1.0pt,
-forget plot
-]
-coordinates{
- (1.5,-2)
-};
+\node at (axis cs:0.1, 1.5) [anchor=west,minimum size=20pt] {\LARGE$\mu(\*x)$};
+\draw[->,line width=1pt] (axis cs:0.32, 1.5) to[in=90,out=0] (axis cs:0.42, 1.1);
 
-\addplot [
-color=green!60!black,
-only marks,
-mark=x,
-mark size=3.5pt,
-line width=1.5pt,
-forget plot
-]
-coordinates{
- (1.5,2)
-};
+\node at (axis cs:1.5, 1.5) [anchor=east,minimum size=20pt] {\LARGE$C(\*x)$};
+
+\node at (axis cs:0.1, 3.5) [anchor=west,minimum size=20pt] {\LARGE$\mu(\*x)+\beta\sigma(\*x)$};
+\draw[->,line width=1pt] (axis cs:0.68, 3.5) to[in=90,out=0] (axis cs:0.78, 3.1);
+\node at (axis cs:0.1, -1.5) [anchor=west,minimum size=20pt] {\LARGE$\mu(\*x)-\beta\sigma(\*x)$};
+\draw[->,line width=1pt] (axis cs:0.68, -1.5) to[in=270,out=0] (axis cs:0.78, -1.1);
 

### 2013-07-31 figurefactory/files/voned_0_3_poster.tex
Many small fixes

--- 2013-07-31 figurefactory/files/voned_0_3.tex
@@
 \begin{axis}[%
-tick label style={font=\Large},
-label style={font=\Large},
+tick label style={font=\Huge},
+label style={font=\Huge},
 label shift={-4pt},
 xlabel shift={-6pt},
-legend style={font=\Large},
-xticklabel shift={2pt},
+legend style={font=\Huge},
 view={0}{90},
@@
 solid,
-line width=2.0pt,
+line width=3.0pt,
 forget plot
@@
 \addplot [
-color=darkgray,
-solid,
-only marks,
-mark=*,
-mark size=3.5pt,
-forget plot
-]
-coordinates{
- (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
-};
-
-\addplot [
 color=black,
 solid,
-line width=1.5pt,
-mark size=3pt,
+line width=2.5pt,
+mark size=4pt,
 mark=-,
@@
 
-\node at (axis cs:0.1, 1.5) [anchor=west,minimum size=20pt] {\LARGE$\mu(\*x)$};
-\draw[->,line width=1pt] (axis cs:0.32, 1.5) to[in=90,out=0] (axis cs:0.42, 1.1);
+\node at (axis cs:0.1, 1.5) [anchor=west,minimum size=20pt] {\Huge$\mu(\*x)$};
+\draw[->,line width=1.5pt] (axis cs:0.43, 1.5) to[in=90,out=0] (axis cs:0.58, 1.1);
 
-\node at (axis cs:1.5, 1.5) [anchor=east,minimum size=20pt] {\LARGE$C(\*x)$};
+\node at (axis cs:1.6, 1.5) [anchor=east,minimum size=20pt] {\Huge$C(\*x)$};
 
-\node at (axis cs:0.1, 3.5) [anchor=west,minimum size=20pt] {\LARGE$\mu(\*x)+\beta\sigma(\*x)$};
-\draw[->,line width=1pt] (axis cs:0.68, 3.5) to[in=90,out=0] (axis cs:0.78, 3.1);
-\node at (axis cs:0.1, -1.5) [anchor=west,minimum size=20pt] {\LARGE$\mu(\*x)-\beta\sigma(\*x)$};
-\draw[->,line width=1pt] (axis cs:0.68, -1.5) to[in=270,out=0] (axis cs:0.78, -1.1);
+\node at (axis cs:0.1, 3.5) [anchor=west,minimum size=20pt] {\Huge$\mu(\*x)+\beta\sigma(\*x)$};
+\draw[->,line width=1.5pt] (axis cs:0.95, 3.5) to[in=90,out=0] (axis cs:1.1, 3.1);
+\node at (axis cs:0.1, -1.5) [anchor=west,minimum size=20pt] {\Huge$\mu(\*x)-\beta\sigma(\*x)$};
+\draw[->,line width=1.5pt] (axis cs:0.95, -1.5) to[in=270,out=0] (axis cs:1.1, -1.1);
 

### 2013-07-31 figurefactory/files/voned_1_0.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_0.tex
@@
 
+\addplot [
+color=green!60!black,
+only marks,
+mark=*,
+mark size=3.5pt,
+line width=1.0pt,
+forget plot
+]
+coordinates{
+ (1.5,-2)
+};
+
 \end{axis}

### 2013-07-31 figurefactory/files/voned_1_1.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_0.tex
@@
 
+\addplot [
+color=green!60!black,
+densely dotted,
+line width=1.0pt,
+forget plot
+]
+coordinates{
+ (1.5,-2)(1.5,2)
+};
+
+\addplot [
+color=green!60!black,
+only marks,
+mark=*,
+mark size=3.5pt,
+line width=1.0pt,
+forget plot
+]
+coordinates{
+ (1.5,-2)
+};
+
+\addplot [
+color=green!60!black,
+only marks,
+mark=x,
+mark size=4.5pt,
+line width=1.5pt,
+forget plot
+]
+coordinates{
+ (1.5,2)
+};
+
 \end{axis}

### 2013-07-31 figurefactory/files/voned_1_2.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_1_2.tex
@@
 mark=*,
-mark size=2.5pt,
+mark size=3.5pt,
 line width=1.0pt,
@@
 mark=x,
-mark size=3.5pt,
+mark size=4.5pt,
 line width=1.5pt,

### 2013-07-31 figurefactory/files/voned_2_1.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_2_0.tex
@@
 color=green!60!black,
+densely dotted,
+line width=1.0pt,
+forget plot
+]
+coordinates{
+ (0.5,-2)(0.5,2.8)
+};
+
+\addplot [
+color=green!60!black,
 only marks,
 mark=*,
-mark size=2.5pt,
+mark size=3.5pt,
 line width=1.0pt,
@@
 
+\addplot [
+color=green!60!black,
+only marks,
+mark=x,
+mark size=4.5pt,
+line width=1.5pt,
+forget plot
+]
+coordinates{
+ (0.5,2.8)
+};
+
 \end{axis}

### 2013-07-31 figurefactory/files/voned_3_1.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_3_0.tex
@@
 color=green!60!black,
+densely dotted,
+line width=1.0pt,
+forget plot
+]
+coordinates{
+ (1,-2)(1,0.5)
+};
+
+\addplot [
+color=green!60!black,
 only marks,
 mark=*,
-mark size=2.5pt,
+mark size=3.5pt,
 line width=1.0pt,
@@
 
+\addplot [
+color=green!60!black,
+only marks,
+mark=x,
+mark size=4.5pt,
+line width=1.5pt,
+forget plot
+]
+coordinates{
+ (1,0.5)
+};
+
 \end{axis}

### 2013-07-31 figurefactory/files/voned_3_2_poster.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_41.tex
@@
 \begin{axis}[%
-tick label style={font=\tiny},
-label style={font=\tiny},
+tick label style={font=\Huge},
+label style={font=\Huge},
 label shift={-4pt},
 xlabel shift={-6pt},
-legend style={font=\tiny},
+legend style={font=\Huge},
 view={0}{90},
@@
 \addplot [
-color=darkgray,
-solid,
-only marks,
-mark=square*,
-mark size=2.5pt,
+color=black,
+dotted,
+line width=2.5pt,
 forget plot
@@
 coordinates{
- %(0,-2)
- (0.01,-2)(0.02,-2)(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)(1.98,-2)(1.99,-2)
- %(2,-2) 
+ (1,-2)(1,0.5)
 };
@@
 \addplot [
-color=red!40!yellow,
-solid,
-only marks,
-mark=square*,
-mark size=2.5pt,
+color=black,
+dotted,
+line width=2.5pt,
 forget plot
@@
 coordinates{
- (0.28,-2)(0.29,-2)(0.3,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)(0.35,-2)(0.36,-2)(0.37,-2)(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2)
+ (1.5,-2)(1.5,2)
 };
@@
 \addplot [
-color=locol,
-solid,
-only marks,
-mark=square*,
-mark size=2.5pt,
+color=black,
+dotted,
+line width=2.5pt,
 forget plot
@@
 coordinates{
- (0.93,-2)(0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2)(1.09,-2) 
+ (0.5,-2)(0.5,2.8)
 };
@@
 \addplot [
-color=red,
-densely dashed,
+color=black,
+only marks,
+mark=*,
+mark size=2.5pt,
 line width=2.0pt,
@@
 coordinates{
- (0,1.2)(2,1.2)
+ (0.5,-2)(1,-2)(1.5,-2)
+};
+
+\addplot [
+color=black,
+only marks,
+mark=x,
+mark size=7.5pt,
+line width=2.5pt,
+forget plot
+]
+coordinates{
+ (0.5,2.8)(1,0.5)(1.5,2)
 };

### 2013-07-31 figurefactory/files/voned_cl_01.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_00.tex
@@
 
+\addplot [
+color=red,
+dashed,
+line width=2.5pt,
+forget plot
+]
+coordinates{
+ (0,1.2)(2,1.2)
+};
+
 \end{axis}

### 2013-07-31 figurefactory/files/voned_cl_10.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_00.tex
@@
 
+\addplot [
+color=red,
+dashed,
+line width=2.5pt,
+forget plot
+]
+coordinates{
+ (0,1.2)(2,1.2)
+};
+
+\addplot [
+color=black,
+solid,
+line width=2pt,
+mark size=3pt,
+mark=-,
+forget plot
+]
+coordinates{
+ (0.5,2.4902)(0.5,3.026)
+};
+
+\node at (axis cs:0.45, 3) [anchor=south west,minimum size=16pt] {\Large$C(0.5)$};
+
 \end{axis}

### 2013-07-31 figurefactory/files/voned_cl_11.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_00.tex
@@
 
+\addplot [
+color=red!40!yellow,
+solid,
+only marks,
+mark=*,
+mark size=3.5pt,
+forget plot
+]
+coordinates{
+ (0.5,-2)
+};
+
+\addplot [
+color=red,
+dashed,
+line width=2.5pt,
+forget plot
+]
+coordinates{
+ (0,1.2)(2,1.2)
+};
+
+\addplot [
+color=black,
+solid,
+line width=2pt,
+mark size=3pt,
+mark=-,
+forget plot
+]
+coordinates{
+ (0.5,2.4902)(0.5,3.026)
+};
+
+\node at (axis cs:0.45, 3) [anchor=south west,minimum size=16pt] {\Large$C(0.5)$};
+
 \end{axis}

### 2013-07-31 figurefactory/files/voned_cl_20.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_10.tex
@@
 \addplot [
+color=red!40!yellow,
+solid,
+only marks,
+mark=*,
+mark size=3.5pt,
+forget plot
+]
+coordinates{
+ (0.5,-2)
+};
+
+\addplot [
 color=red,
-densely dashed,
-line width=2.0pt,
+dashed,
+line width=2.5pt,
 forget plot
@@
 solid,
-line width=1.5pt,
+line width=2pt,
 mark size=3pt,
@@
 coordinates{
- (0.5,2.4902)(0.5,3.026)
+ (1.5,1.7052)(1.5,2.241)
 };
 
-\node at (axis cs:0.45, 3) [anchor=south west,minimum size=16pt] {$Q_4(\*x_{0.5})$};
+\node at (axis cs:1.4, 2.3) [anchor=south west,minimum size=16pt] {\Large$C(1.5)$};
 

### 2013-07-31 figurefactory/files/voned_cl_21.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_10.tex
@@
 \addplot [
+color=red!40!yellow,
+solid,
+only marks,
+mark=*,
+mark size=3.5pt,
+forget plot
+]
+coordinates{
+ (0.5,-2)(1.5,-2)
+};
+
+\addplot [
 color=red,
-densely dashed,
-line width=2.0pt,
+dashed,
+line width=2.5pt,
 forget plot

### 2013-07-31 figurefactory/files/voned_cl_30.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_20.tex
@@
 color=red,
-densely dashed,
-line width=2.0pt,
+dashed,
+line width=2.5pt,
 forget plot
@@
 coordinates{
- (1.5,1.7052)(1.5,2.241)
+ (1,0.2645)(1,0.7996)
 };
 
-\node at (axis cs:1.4, 2.3) [anchor=south west,minimum size=16pt] {$Q_4(\*x_{1.5})$};
+\node at (axis cs:0.88, -0.4) [anchor=south west,minimum size=16pt] {\Large$C(1)$};
 

### 2013-07-31 figurefactory/files/voned_cl_31.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_20.tex
@@
 coordinates{
- (0.5,-2)
+ (0.5,-2)(1.5,-2)
+};
+
+\addplot [
+color=locol,
+solid,
+only marks,
+mark=*,
+mark size=3.5pt,
+forget plot
+]
+coordinates{
+ (1,-2)
 };

### 2013-07-31 figurefactory/files/voned_cl_40.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_30.tex
@@
 tickwidth=0cm,
+clip=false
 ]
@@
 \addplot [
+color=locol,
+solid,
+only marks,
+mark=*,
+mark size=3.5pt,
+forget plot
+]
+coordinates{
+ (1,-2)
+};
+
+\addplot [
 color=red,
-densely dashed,
-line width=2.0pt,
+dashed,
+line width=2.5pt,
 forget plot
@@
 coordinates{
- (1,0.2645)(1,0.7996)
+ (0,-0.1683)(0,3.5848)
 };
 
-\node at (axis cs:0.88, -0.4) [anchor=south west,minimum size=16pt] {$Q_4(\*x_1)$};
+\addplot [
+color=black,
+solid,
+line width=2pt,
+mark size=3pt,
+mark=-,
+forget plot
+]
+coordinates{
+ (2,-0.4448)(2,3.3083)
+};
+
+\node at (axis cs:0, -0.8) [anchor=south west,minimum size=16pt] {\Large$C(0)$};
+
+\node at (axis cs:1.78, -1) [anchor=south west,minimum size=16pt] {\Large$C(2)$};
 

### 2013-07-31 figurefactory/files/voned_cl_41.tex
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_40.tex
@@
 only marks,
-mark=*,
-mark size=2.5pt,
+mark=square*,
+mark size=3.5pt,
 forget plot
@@
 coordinates{
- (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
+ %(0,-2)
+ %(0.019,-2)
+(0.02,-2)(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)(1.98,-2)
+%(1.981,-2)
+ %(2,-2) 
 };
@@
 coordinates{
- (0.5,-2)(1.5,-2)
+ (0.28,-2)(0.29,-2)(0.3,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)(0.35,-2)(0.36,-2)(0.37,-2)(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2)
 };
@@
 coordinates{
- (1,-2)
+ (0.93,-2)(0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2)(1.09,-2) 
 };
@@
 
-\addplot [
-color=black,
-solid,
-line width=1.5pt,
-mark size=3pt,
-mark=-,
-forget plot
-]
-coordinates{
- (0,-0.1683)(0,3.5848)
-};
-
-\addplot [
-color=black,
-solid,
-line width=1.5pt,
-mark size=3pt,
-mark=-,
-forget plot
-]
-coordinates{
- (2,-0.4448)(2,3.3083)
-};
-
-\node at (axis cs:0, -0.8) [anchor=south west,minimum size=16pt] {$Q_4(\*x_0)$};
-
-\node at (axis cs:1.78, -1) [anchor=south west,minimum size=16pt] {$Q_4(\*x_2)$};
-
 \end{axis}

### 2013-07-31 figurefactory/files/voned_cl_41_amb_2.tex
Most of the changes discussed with Andreas
Many small fixes

--- 2013-03-19 figurefactory/files/voned_cl_41.tex
@@
 mark=square*,
-mark size=2.5pt,
+mark size=3.5pt,
 forget plot
@@
  %(0,-2)
- (0.01,-2)(0.02,-2)(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)(1.98,-2)(1.99,-2)
+ %(0.019,-2)
+(0.02,-2)(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)(1.98,-2)
+%(1.981,-2)
  %(2,-2) 
@@
 
+\addplot [
+color=black,
+solid,
+line width=2pt,
+mark=-,
+mark size=3pt,
+forget plot
+]
+coordinates{
+ (1.23,0.0268)(1.23,1.9195)
+};
+
+\addplot [
+color=yellow,
+solid,
+line width=4pt,
+forget plot
+]
+coordinates{
+ (1.23,1.2)(1.23,1.9195)
+};
+
+\addplot [
+color=black,
+solid,
+line width=2pt,
+mark=-,
+mark size=3pt,
+forget plot
+]
+coordinates{
+ (0.23,0.9288)(0.23,3.8259)
+};
+
+\addplot [
+color=yellow,
+solid,
+line width=4pt,
+forget plot
+]
+coordinates{
+ (0.23,0.9288)(0.23,1.2)
+};
+
 \end{axis}

### 2013-07-31 figurefactory/files/voned_cl_41_amb_poster.tex
Many small fixes

--- 2013-07-31 figurefactory/files/voned_3_2_poster.tex
@@
 xlabel shift={-6pt},
+xticklabel shift={5pt},
 legend style={font=\Huge},
@@
 \addplot [
-color=black,
-dotted,
-line width=2.5pt,
+color=darkgray,
+solid,
+only marks,
+mark=square*,
+mark size=5pt,
 forget plot
@@
 coordinates{
- (1,-2)(1,0.5)
+ %(0,-2)
+ %(0.01,-2)
+(0.023,-2)
+(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)
+(1.977,-2)
+%(1.99,-2)
+ %(2,-2) 
+};
+
+\addplot [
+color=red!40!yellow,
+solid,
+only marks,
+mark=square*,
+mark size=5pt,
+forget plot
+]
+coordinates{
+ (0.28,-2)(0.29,-2)(0.3,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)(0.35,-2)(0.36,-2)(0.37,-2)(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2)
+};
+
+\addplot [
+color=locol,
+solid,
+only marks,
+mark=square*,
+mark size=5pt,
+forget plot
+]
+coordinates{
+ (0.93,-2)(0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2)(1.09,-2) 
+};
+
+\addplot [
+color=red,
+dashed,
+line width=3.0pt,
+forget plot
+]
+coordinates{
+ (0,1.2)(2,1.2)
 };
@@
 color=black,
-dotted,
-line width=2.5pt,
+solid,
+line width=3pt,
+mark=-,
+mark size=4pt,
 forget plot
@@
 coordinates{
- (1.5,-2)(1.5,2)
+ (1.23,0.0268)(1.23,1.9195)
+};
+
+\addplot [
+color=yellow,
+solid,
+line width=5pt,
+forget plot
+]
+coordinates{
+ (1.23,1.2)(1.23,1.9195)
 };
@@
 coordinates{
- (0.5,-2)(0.5,2.8)
+ (0.23,0.9288)(0.23,3.8259)
 };
@@
 \addplot [
-color=black,
-only marks,
-mark=*,
-mark size=2.5pt,
-line width=2.0pt,
+color=yellow,
+solid,
+line width=5pt,
 forget plot
@@
 coordinates{
- (0.5,-2)(1,-2)(1.5,-2)
-};
-
-\addplot [
-color=black,
-only marks,
-mark=x,
-mark size=7.5pt,
-line width=2.5pt,
-forget plot
-]
-coordinates{
- (0.5,2.8)(1,0.5)(1.5,2)
+ (0.23,0.9288)(0.23,1.2)
 };

### 2013-07-31 figurefactory/files/voned_cl_41_imp_2_poster.tex
Many small fixes

--- 2013-07-31 figurefactory/files/voned_3_2_poster.tex
@@
 xmin=0, xmax=2,
+xticklabel shift={5pt},
 xtick={0, 0.5, 1, 1.5, 2},
 ymin=-2, ymax=4,
-tickwidth=0cm,
+tickwidth=0.1cm,
+clip=false
 ]
@@
 solid,
-line width=3.0pt,
+line width=3pt,
 forget plot
@@
 coordinates{
- (1,-2)(1,0.5)
+ %(0,-2)
+ %(0.01,-2)
+(0.023,-2)
+(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.28,-2)(0.29,-2)(0.30,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)
+(0.35,-2)(0.36,-2)(0.37,-2)
+(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)
+(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)
+(1.41,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)
+(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2)
+(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)
+(1.977,-2)
+%(1.99,-2)
+ %(2,-2) 
+};
+
+\addplot [
+color=red!40!yellow,
+solid,
+only marks,
+mark=square*,
+mark size=5pt,
+forget plot
+]
+coordinates{
+(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)
+};
+
+\addplot [
+color=locol,
+solid,
+only marks,
+mark=square*,
+mark size=5pt,
+forget plot
+]
+coordinates{
+ (0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2) 
+};
+
+\addplot [
+color=green!90!black,
+solid,
+only marks,
+mark=square*,
+mark size=5pt,
+forget plot
+]
+coordinates{
+(0.023,-1.7)(0.03,-1.7)(0.04,-1.7)(0.05,-1.7)(0.06,-1.7)(0.07,-1.7)(0.08,-1.7)(0.09,-1.7)(0.10,-1.7)(0.11,-1.7)(0.12,-1.7)(0.13,-1.7)(0.14,-1.7)(0.15,-1.7)(0.16,-1.7)(0.17,-1.7)(0.18,-1.7)(0.19,-1.7)(0.20,-1.7)(0.21,-1.7)(0.22,-1.7)(0.23,-1.7)(0.24,-1.7)(0.25,-1.7)(0.26,-1.7)(0.27,-1.7)(0.28,-1.7)(0.29,-1.7)(0.30,-1.7)(0.31,-1.7)(0.32,-1.7)(0.33,-1.7)(0.34,-1.7)(0.35,-1.7)(0.36,-1.7)(0.37,-1.7)(0.38,-1.7)(0.39,-1.7)(0.40,-1.7)(0.41,-1.7)(0.42,-1.7)(0.43,-1.7)(0.44,-1.7)(0.45,-1.7)(0.46,-1.7)(0.47,-1.7)(0.48,-1.7)(0.49,-1.7)(0.50,-1.7)(0.51,-1.7)(0.52,-1.7)(0.53,-1.7)(0.54,-1.7)(0.55,-1.7)(0.56,-1.7)(0.57,-1.7)(0.58,-1.7)(0.59,-1.7)(0.60,-1.7)(0.61,-1.7)(0.62,-1.7)(0.63,-1.7)(0.64,-1.7)(0.65,-1.7)(0.66,-1.7)(0.67,-1.7)(0.68,-1.7)(0.69,-1.7)(0.70,-1.7)(0.71,-1.7)(0.72,-1.7)(0.73,-1.7)(0.74,-1.7)(0.75,-1.7)(1.56,-1.7)(1.57,-1.7)(1.58,-1.7)(1.59,-1.7)(1.60,-1.7)(1.61,-1.7)(1.62,-1.7)(1.63,-1.7)(1.64,-1.7)(1.65,-1.7)(1.66,-1.7)(1.67,-1.7)(1.68,-1.7)(1.69,-1.7)(1.70,-1.7)(1.71,-1.7)(1.72,-1.7)(1.73,-1.7)(1.74,-1.7)(1.75,-1.7)(1.76,-1.7)(1.77,-1.7)(1.78,-1.7)(1.79,-1.7)(1.80,-1.7)(1.81,-1.7)(1.82,-1.7)(1.83,-1.7)(1.84,-1.7)(1.85,-1.7)(1.86,-1.7)(1.87,-1.7)(1.88,-1.7)(1.89,-1.7)(1.90,-1.7)(1.91,-1.7)(1.92,-1.7)(1.93,-1.7)(1.94,-1.7)(1.95,-1.7)(1.96,-1.7)(1.97,-1.7)(1.977,-1.7)
+};
+
+\addplot [fill=red,draw=none,opacity=0.2,forget plot] coordinates{ (0,1.1)(0,1.9)(2,1.9)(2,1.1) };
+
+%\addplot [
+%color=black,
+%dashed,
+%line width=3pt,
+%forget plot
+%]
+%coordinates{
+% (0,3.825915)(2,3.825915)
+%};
+%
+%\addplot [
+%color=black,
+%dashed,
+%line width=3pt,
+%forget plot
+%]
+%coordinates{
+% (0,2.4975)(2,2.4975)
+%};
+
+\addplot [
+color=red,
+dashed,
+line width=3pt,
+forget plot
+]
+coordinates{
+ (0,1.9)(2,1.9)
+};
+
+\addplot [
+color=red,
+dashed,
+line width=3pt,
+forget plot
+]
+coordinates{
+ (0,1.1)(2,1.1)
 };
@@
 color=black,
-dotted,
+solid,
 line width=2.5pt,
+mark size=3pt,
+mark=-,
 forget plot
@@
 coordinates{
- (1.5,-2)(1.5,2)
+ (0.5,2.4902)(0.5,3.026)
 };
@@
 coordinates{
- (0.5,-2)(0.5,2.8)
+ (1.5,1.7052)(1.5,2.241)
 };
@@
 color=black,
-only marks,
-mark=*,
-mark size=2.5pt,
-line width=2.0pt,
+solid,
+line width=2.5pt,
+mark size=3pt,
+mark=-,
 forget plot
@@
 coordinates{
- (0.5,-2)(1,-2)(1.5,-2)
+ (1,0.2645)(1,0.7996)
 };
@@
 color=black,
-only marks,
-mark=x,
-mark size=7.5pt,
+solid,
 line width=2.5pt,
+mark size=3pt,
+mark=-,
 forget plot
@@
 coordinates{
- (0.5,2.8)(1,0.5)(1.5,2)
+ (0,-0.1683)(0,3.5848)
 };
+
+\addplot [
+color=black,
+solid,
+line width=2.5pt,
+mark size=3pt,
+mark=-,
+forget plot
+]
+coordinates{
+ (2,-0.4448)(2,3.3083)
+};
+
+%\node at (axis cs:1.3, 3.1) [anchor=south west,minimum size=16pt] {\LARGE$\max\{\mu(\*x) + \beta \sigma(\*x)\}$};
+%\node at (axis cs:0.7, 2.4) [anchor=south west,minimum size=16pt] {\LARGE$\max\{\mu(\*x) - \beta \sigma(\*x)\}$};
 

### 2013-07-31 figurefactory/files/voned_cl_41_poster.tex
Many small fixes

--- 2013-07-31 figurefactory/files/voned_cl_41_amb_poster.tex
@@
 solid,
-line width=3pt,
+line width=2.5pt,
+mark size=3pt,
 mark=-,
-mark size=4pt,
 forget plot
@@
 coordinates{
- (1.23,0.0268)(1.23,1.9195)
-};
-
-\addplot [
-color=yellow,
-solid,
-line width=5pt,
-forget plot
-]
-coordinates{
- (1.23,1.2)(1.23,1.9195)
+ (0.5,2.4902)(0.5,3.026)
 };
@@
 coordinates{
- (0.23,0.9288)(0.23,3.8259)
+ (1.5,1.7052)(1.5,2.241)
 };
@@
 \addplot [
-color=yellow,
+color=black,
 solid,
-line width=5pt,
+line width=2.5pt,
+mark size=3pt,
+mark=-,
 forget plot
@@
 coordinates{
- (0.23,0.9288)(0.23,1.2)
+ (1,0.2645)(1,0.7996)
 };
+
+\addplot [
+color=black,
+solid,
+line width=2.5pt,
+mark size=3pt,
+mark=-,
+forget plot
+]
+coordinates{
+ (0.005,-0.1683)(0.005,3.5848)
+};
+
+\addplot [
+color=black,
+solid,
+line width=2.5pt,
+mark size=3pt,
+mark=-,
+forget plot
+]
+coordinates{
+ (1.997,-0.4448)(1.997,3.3083)
+};
+
+\node at (axis cs:0.4, 3) [anchor=south west,minimum size=16pt] {\Huge$Q(0.5)$};
+\node at (axis cs:1.35, 2.3) [anchor=south west,minimum size=16pt] {\Huge$Q(1.5)$};
+\node at (axis cs:0.88, -0.8) [anchor=south west,minimum size=16pt] {\Huge$Q(1)$};
+\node at (axis cs:0.02, -0.8) [anchor=south west,minimum size=16pt] {\Huge$Q(0)$};
+\node at (axis cs:1.72, -0.8) [anchor=south west,minimum size=16pt] {\Huge$Q(2)$};
 

### 2013-07-31 figurefactory/proof.tex
Many small fixes

@@
 
-\usepackage{libertine}
+\usepackage{lmodern}
 
@@
 
- \node[st,below=3em of conv] (clas) {All points in $D$ have been classified}
+ \node[st,below=2em of conv] (clas) {All points in $D$ have been classified}
    edge[pil] (conv);
@@
 
- \node[st,draw=none,below=3em of amb] (dummy) {};
+ \node[st,draw=none,below=2em of amb] (dummy) {};
 
- \node[st,left=2em of amb] (t0) {Monotonicity}
+ \node[st,left=1.5em of amb] (t0) {Monotonicity}
    edge[pil] (amb);
@@
 
- \node[st,below=3em of fit1] (gamma)
+ \node[st,below=2em of fit1] (gamma)
  {\makecell[c]
@@
 
- \node[st,below=3em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
+ \node[st,below=2em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
    edge[pil] (acc);
 
- \node[st,right=2em of loss] (rules) {Class. rules}
+ \node[st,right=1.5em of loss] (rules) {Class. rules}
    edge[pil] (loss);
 
- \node[st,below=3em of loss] (est) {Correctly estimate $f$ w.h.p.}
+ \node[st,below=2em of loss] (est) {Correctly estimate $f$ w.h.p.}
    edge[pil] (loss);
 
- \node[st,right=2em of est] (delta) {$\delta$}
+ \node[st,right=1.5em of est] (delta) {$\delta$}
    edge[pil] (est);
 
- \node[st,below=3em of est] (large) {Conf. intervals are large enough}
+ \node[st,below=2em of est] (large) {Conf. intervals are large enough}
    edge[pil] (est)

### 2013-07-31 ijcai13pres.tex
Fix typo
Many small fixes

@@
 \item<4-> Obtain noisy observation ($y_t = f(\*x_t) + n_t$)
-\item<5-> Update our estimated classification
+\item<5-> Update our classification estimate
 \end{itemize}
@@
 \begin{itemize}
-\item<1-> \textbf{Nonpaparametric}: impose ``smoothness'' assumptions via kernel $k(\*x, \*x')$
-\item<2-> Mean \textbf{and variance} estimates: construct confidence intervals $Q_t(\*x)$
-\item<7-> \textbf{Bayesian}, yet \textbf{efficient}: suitable for step-by-step updates
+\item<1-> Mean \textbf{and variance} estimates: construct confidence intervals $C(\*x)$
+\item<2-> \textbf{Bayesian}, yet \textbf{efficient}: suitable for step-by-step updates
+\item<3-> Impose prior ``smoothness'' assumptions via kernel $k(\*x, \*x')$
 \end{itemize}
 \begin{center}
-\color{white}
-\includegraphics<1-2>[draft,width=4in]{figures/voned_0_0}
-\color{black}
-\includegraphics<3>[width=4in]{figures/voned_0_0}
-\includegraphics<4>[width=4in]{figures/voned_0_1}
-\includegraphics<5>[width=4in]{figures/voned_0_2}
-\includegraphics<6-7>[width=4in]{figures/voned_0_3}
-\includegraphics<8>[width=4in]{figures/voned_1_0}
-\includegraphics<9>[width=4in]{figures/voned_1_1}
-\includegraphics<10>[width=4in]{figures/voned_1_2}
-\includegraphics<11>[width=4in]{figures/voned_2_0}
-\includegraphics<12>[width=4in]{figures/voned_2_1}
-\includegraphics<13>[width=4in]{figures/voned_2_2}
-\includegraphics<14>[width=4in]{figures/voned_3_0}
-\includegraphics<15>[width=4in]{figures/voned_3_1}
-\includegraphics<16>[width=4in]{figures/voned_3_2}
+%\color{white}
+%\includegraphics<1>[draft,width=4in]{figures/voned_0_0}
+%\color{black}
+%\includegraphics<1>[width=4in]{figures/voned_0_0}
+%\includegraphics<4>[width=4in]{figures/voned_0_1}
+%\includegraphics<5>[width=4in]{figures/voned_0_2}
+\includegraphics<1-3>[width=4in]{figures/voned_0_3}
+%\includegraphics<4>[width=4in]{figures/voned_1_0}
+\includegraphics<4>[width=4in]{figures/voned_1_1}
+\includegraphics<5>[width=4in]{figures/voned_1_2}
+%\includegraphics<7>[width=4in]{figures/voned_2_0}
+\includegraphics<6>[width=4in]{figures/voned_2_1}
+\includegraphics<7>[width=4in]{figures/voned_2_2}
+%\includegraphics<10>[width=4in]{figures/voned_3_0}
+\includegraphics<8>[width=4in]{figures/voned_3_1}
+\includegraphics<9>[width=4in]{figures/voned_3_2}
 \end{center}
@@
 \vspace{0.3em}
-\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<22->{\Large\color{green!70!black}\checkmark}
+\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<19>{\Large\color{green!70!black}\checkmark}
 \uncover<16->{
@@
 \item<17-> \ldots the most ``ambiguous'' point
-           \uncover<21->{(max. variance or random also work)}
+           %\uncover<21->{(max. variance or random also work)}
 \end{itemize}}
@@
 \includegraphics<13-17>[width=3.7in]{figures/voned_cl_41}
-\includegraphics<18>[width=3.7in]{figures/voned_cl_41_amb_0}
-\includegraphics<19>[width=3.7in]{figures/voned_cl_41_amb_1}
-\includegraphics<20->[width=3.7in]{figures/voned_cl_41_amb_2}
+\includegraphics<18->[width=3.7in]{figures/voned_cl_41_amb_2}
 \end{center}
@@
 \definecolor{c4}{RGB}{240,150,9}
-\definecolor{c5}{RGB}{255,255,255}
+\definecolor{c5}{RGB}{240,230,60}
 \definecolor{c3}{RGB}{230,113,184}
+\definecolor{cwhite}{RGB}{255,255,255}
 %\colorlet{c1}{cyan}
@@
 \begin{columns}[t]
-\column{0.45\textwidth}
+\column{0.55\textwidth}
+\begin{center}
+The Level Set Estimation (\acl) algorithm
+\end{center}
+\vspace{5pt}
 {\footnotesize
 \begin{algorithmic}
-  \REQUIRE sample set $D$, GP prior ($\mu_0$, $k$, $\sigma_0$),\\
-           \hspace{2.2em}thr. value $h$, accuracy parameter $\epsilon$
-  \ENSURE predicted sets $\hat{H}$, $\hat{L}$
-  \uncover<2->{
-  \CSTATE{c1}$H_0 \gets \varnothing$,\enskip $L_0 \gets \varnothing$,\enskip $U_0 \gets D$ \label{lin:init1}
+  \REQUIRE sample space $D$, threshold level $h$
+  \ENSURE predicted super- and sublevel sets
+  \STATE
+  %\uncover<2->{
+  %\CSTATE{c1}$H_0 \gets \varnothing$,\enskip $L_0 \gets \varnothing$,\enskip $U_0 \gets D$ \label{lin:init1}
   %\LET{$H_0$}{$\varnothing$} \label{lin:init1}
@@
   %\LET{$U_0$}{$D$}
-  \CLET{c1}{$C_0(\*x)$}{$\mathbb{R}$, for all $\*x \in D$} \label{lin:init2}
-  \CLET{c1}{$t$}{1}
-  }
-  \uncover<3->{
-  \CWHILE{c6}{$U_{t-1} \neq \varnothing$}
-    \CSTATE{c6}$H_t \gets H_{t-1}$,\enskip $L_t \gets L_{t-1}$,\enskip $U_t \gets U_{t-1}$
+  %\CLET{c1}{$C_0(\*x)$}{$\mathbb{R}$, for all $\*x \in D$} \label{lin:init2}
+  %\CLET{c1}{$t$}{1}
+  %}
+  \uncover<2->{
+  \CWHILE{cwhite}{$\exists$ unclassified points in $D$}
+    %\CSTATE{c6}$H_t \gets H_{t-1}$,\enskip $L_t \gets L_{t-1}$,\enskip $U_t \gets U_{t-1}$
     }
@@
     %\LET{$U_t$}{$U_{t-1}$}
+    \uncover<3->{
+    \CFORALL{cwhite}{unclassified points $\*x\in D$}
+      \CIF{c2}{$C_t(\*x)$ lies above $h$}
+        \CSTATE{c2}classify $\*x$ into superlevel set
+      \CELSIF{c2}{$C_t(\*x)$ lies below $h$}
+        \CSTATE{c2}classify $\*x$ into sublevel set
+      \CELSE
+        \CSTATE{c2}leave $\*x$ unclassified
+      \CENDIF{c2} \label{lin:class2}
+    \CENDFOR{cwhite}
+    }
     \uncover<4->{
-    \CFORALL{c2}{$\*x \in U_{t-1}$}
-      \CLET{c2}{$C_{t}(\*x)$}{$C_{t-1}(\*x) \cap Q_t(\*x)$} \label{lin:upd}
-      \CIF{c2}{$\min(C_t(\*x)) + \epsilon > h$} \label{lin:class1}
-        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
-        \CLET{c2}{$H_t$}{$H_t \cup \{\*x\}$} 
-      \CELSIF{c2}{$\max(C_t(\*x)) - \epsilon \leq h$} \label{lin:classr2}
-        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
-        \CLET{c2}{$L_t$}{$L_t \cup \{\*x\}$}
-      \CENDIF{c2} \label{lin:class2}
-    \CENDFOR{c2}
-    }
-    \uncover<5->{
     \CLET{c3}{$\*x_t$}{$\argmax \{a_t(\*x)\mid \*x \in U_t\}$} \label{lin:sel1}
@@
     }
-    \uncover<6->{
-    \CSTATE{c4}Compute $\mu_t(\*x)$ and $\sigma_t(\*x)$, $\forall\*x \in U_t$ \label{lin:inf}
-    }
-    \uncover<3->{
-    \CLET{c6}{$t$}{$t + 1$}
-  \CENDWHILE{c6}
+    \uncover<5->{
+    \CSTATE{c4}perform GP inference
     }
     \uncover<2->{
-  \CLET{c5}{$\hat{H}$}{$H_{t-1}$} \label{lin:ret1}
-  \CLET{c5}{$\hat{L}$}{$L_{t-1}$} \label{lin:ret2}
+    %\CLET{c6}{$t$}{$t + 1$}
+  \CENDWHILE{cwhite}
   }
+  %\uncover<2->{
+  %\CLET{c5}{$\hat{H}$}{$H_{t-1}$} \label{lin:ret1}
+  %\CLET{c5}{$\hat{L}$}{$L_{t-1}$} \label{lin:ret2}
+  %}
 \end{algorithmic}
+\vspace{30pt}
 }
-\column{0.55\textwidth}
-\begin{center}
-The Level Set Estimation (\acl) algorithm
-\end{center}
-\only<3-6>{\vspace{34pt}$\leftarrow$ {\small loop until all points have been classified\\}\vspace{40pt}}
-\only<4-6>{$\leftarrow$ {\small classify\\}\vspace{52pt}}
-\only<5-6>{$\leftarrow$ {\small select max. ambiguity point\\}\vspace{3pt}}
-\only<6>{$\leftarrow$ {\small update GP estimate}}
-\only<7->{
-\vspace{3pt}
+\column{0.45\textwidth}
+{\only<3-5>{\begin{center}\end{center}\vspace{83pt}}
+%\only<3-6>{\vspace{34pt}$\leftarrow$ {\small loop until all points have been classified\\}\vspace{40pt}}
+\only<3-5>{$\leftarrow$ {\small classify\\}\vspace{39pt}}
+\only<4-5>{$\leftarrow$ {\small sample\\}}
+%\only<6>{$\leftarrow$ {\small update GP estimate}}
+\only<6->{
+\vspace{15pt}
 \begin{itemize}
-\only<7->{
+\only<6->{
 \item Monotonicity of
@@
 }
-\vspace{0em}
-\only<8->{
-\item Relaxed classification rules by an accuracy parameter $\epsilon$\\
-      (trades off sampling cost for accuracy)
+\vspace{10pt}
+\only<7->{
+\item Relax classification rules by an accuracy parameter $\epsilon$
 }
@@
 }
+\vspace{-20pt}
 \begin{center}
-\includegraphics<8->[width=2.5in]{figures/voned_cl_41_eps}
+\includegraphics<7->[width=2.2in]{figures/voned_cl_41_amb_2}
 \end{center}
+}
 \end{columns}
@@
 \begin{theorem}[Simplified]
-If we choose $\beta_t$ large enough, then:
+If we choose $\beta$ appropriately (large enough), then:
 \begin{itemize}
@@
 %\only<5>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_class_354}}
-%\only<6>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_str_class_400}}
+\only<3>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_str_class_400}}
 %\only<7>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_var_class_400}}
@@
 \begin{itemize}
-\item<6-> Need to accurately estimate the maximum $\rightarrow$ modified selection rule
-\item<7-> $h$ is now an estimated quantity $\rightarrow$ modified classification rules
+\item<6-> $h$ is now an estimated quantity $\rightarrow$ modified classification rules
+\item<7-> Need to accurately estimate the maximum $\rightarrow$ modified selection rule
 \end{itemize}
@@
 \color{black}
-\includegraphics<2>[width=3.78in]{figures/limno_bgape_imp_class_0}
+\includegraphics<2>[width=3.78in]{figures/limno_bgape_class_0}
 \includegraphics<3>[width=3.78in]{figures/limno_bgape_imp_class_20}
@@
 \begin{center}
-\large Come to the poster session for more\ldots
+\large In our paper, more\ldots
 \end{center}
 \begin{itemize}
-\item<2-> \ldots theory: sample complexity bounds in more detail
+\item<2-> \ldots theory: sample complexity bounds and their proofs in more detail
 \item<3-> \ldots applications: estimate world regions of low internet latency\\[0.5em]
 \hspace{3em}\includegraphics[height=2in]{figures/map}
-\item<4-> \ldots results: why does \acl greatly outperform ``straddle'' in some cases?
+\item<4-> \ldots experimental results
 \end{itemize}
